I was not entirely a stranger to stressful situations. Infiltrating a group required intruding into a social dynamic where you couldn’t know all the variables. A mistake in judgement or inability to adapt and improvise could easily result in imprisonment or worse. The threat of the Ministry of Morale always lurked in the background of our thoughts, made worse for the fear that our failure could be a danger to our sisters. Ponies had the terrifying ability to rip memories from our very minds and turn them against us; death was preferable.

One could not be an Infiltrator if one was weak of will.

Yet I have to admit, I had no experience with the fear that comes from staring down the barrel of a gun.

The stallion practically growled around the rifle’s bit. “Who the hell are you? And what the hell are you doing here?”

The other ponies were quickly collecting themselves. The other armored stallion, a bit larger than the one questioning me, had retrieved his own rifle. He trained it on me, but he seemed much more calm; wary, but not angry.

The unicorn mare lifted her weapon as well, but didn’t level it at me. She looked uncertainly over the scene, her weapon pointed in the air above my head. It was only then that I could see the glint of a lens at the end of the long, thin weapon. She was carrying a magical energy weapon. Two, in fact, as she had a pistol of some sort tucked into a holster.

I also couldn’t help but note the PipBuck she had, though she didn’t wear it on her leg. Instead, it hung on a strap looped around her neck.

The couple—both older ponies, I noted—looked even more uncertain. The mare had her gun in her mouth, but it was still pointing at the ground. The stallion hadn’t drawn his.

I remembered then that I had been asked a question, and I was fairly certain that it was generally a good idea to oblige well-armed individuals when they ask you something. That goes doubly so when they seem so incredibly angry. Sure, I had expected a bit of wariness at my approach, but between the profanity and the amount of arms being pointed in my direction, I was concerned that I had done something terrible to offend them. “M-my name is Whisper Winds,” I said, trying to aim for just the right amount of nervous and innocent in my tone. “I saw your fire, so I wanted to come and say hello…”

That didn’t seem to impress him. “Really? You’re telling me you were just wandering around the wastes and \textit{happened} to stumble across us?” He was surprisingly good at talking around his gun’s grip, and at keeping his aim steady while doing so. The combination made me think he might be an experienced combatant. That would explain the attitude, too; plenty of ponies responded poorly to the stress of combat. Some grew particularly erratic, which was of special concern when a flick of his tongue could end my life.

Fortunately, the unarmored older stallion came to my rescue. “Easy there, Sharps. She don’t exactly look like some terrifying raider, now does she?”

\leavevmode\llap{“}Lots of dangerous ponies out there that aren’t raiders, Pops,” the pony I took to be named Sharps replied. The gun still refused to waver.

\leavevmode\llap{“}Lots of potential customers, too, so long as you don’t go shootin’ ‘em, first,” the older stallion said as he stepped up beside Sharps. “And if you call me Pops again, you can just go findin’ your own dinner.” He delivered the last line with a disarming smile, as if to tell Sharps he was just playing. ‘Pops’ was a talker, it seemed.

Sharps lowered his gun a hair, visibly considering the other pony’s words for several seconds before finally rolling his eyes. “Fine, but I’m keeping an eye on her, all the same.” He proceeded to sit again, his rifle resting in easy reach. Contrary to his own assertion, his eyes instead swept every direction except mine, searching for other threats.

\leavevmode\llap{“}Don’t mind him,” the older stallion said, smiling as he stepped up to me. “Sharps means well, even if he can be a bit prickly at times. My name’s Long Haul, and this lovely mare here is Silver.” He gestured to the mare that I assumed was his partner. She was pale white to his orange, and about the same age, though she wore the years quite well. She even smiled and nodded to me, once she had re-holstered her pistol.

\leavevmode\llap{“}You’ve already met Sharps,” Long Haul continued, before motioning to the other armored stallion. “This here is Thunderhead. Don’t mind if he doesn’t say much, that’s just his way.” Thunderhead gave a small smile and nodded, a scruffy blond mane bobbing over his face. His rifle hung from its strap, set aside for the moment.

\leavevmode\llap{“}And the lady there with the long gun is Starlight.”

With the potential conflict seemingly averted, Starlight smiled brightly at me, giving a friendly wave of a hoof. The dark-blue mare seemed a fair bit younger than the other ponies.

\leavevmode\llap{“}Now then,” Long Haul said, turning his smile back to me. “How about you tell me what a pretty little filly like you is doing out all on her own in the middle of nowhere?”

It seemed he didn’t entirely trust my sudden appearance, either, even if he was being much nicer about it than Sharps was. That was just fine with me, though. I much preferred a confrontation of words over arms. It was time to put my improvised little backstory to work. “I’m sorry, I didn’t mean to startle you all. It’s just… I have no idea where I am, and you’re the first ponies I’ve seen.”

Sharps gave a quiet grunt, but Long Haul simply nodded. “Well, you must have come from somewhere, am I right? Figure if you know where you came from, you gotta know where you are.”

\leavevmode\llap{“}Oh, yeah, of course. I came from a farm.” Because an isolated homestead was a perfect excuse to have absolutely no knowledge of current events. “Back that way,” I added, sweeping a hoof vaguely in the direction I came.

\leavevmode\llap{“}Wait,” Sharps said, abandoning his scanning of the horizon to look back at me. “You’re trying to tell us you lived on an actual, working farm, and just decided… what, ‘fuck it, I’m going for a walk?’”

I winced at the harshness of that, though I appreciated the disapproving look Long Haul shot his way. “N-no, I—”

\leavevmode\llap{“}Wait!” Starlight said, her pale-blue eyes lighting up. “You went by the tower, then, right? You saw what happened?”

Sharps groaned. “Enough about the fucking tower already!”

I quickly looked back, to see if I could catch any sign of what she was talking about. “I… don’t know. What happened to the tower?”

\leavevmode\llap{“}It exploded,” she cheerfully replied. “With rainbows!”

\textit{With rainbows}, I silently repeated in my mind. Yeah, that sounded so incredibly \textit{pony}. At the same time, I \textit{hadn’t} seen an explosion. She seemed likely to pump me for details about it, and I was sure to get something wrong. I had to improvise to cover my ignorance. “...I guess that might explain some things,” I slowly replied, reaching up a hoof to rub at the side of my head. “I woke up a few hours ago with a horrible headache, but I didn’t remember falling asleep. And there was this big chunk of wreckage nearby. It was the size of a house and looked like it just dropped right out of the sky.”

And, you know, some big explosion happens at the same time I woke up from a (possibly) two-hundred year nap? That seemed unlikely to be a coincidence.

\leavevmode\llap{“}Woah,” Starlight said, surprised. “You must have been pretty close. Wait, does that mean you missed all the rainbows?”

Sharps cut in again. “How about we get back to where she walked off a damn farm to go wandering the Wasteland? I want to hear about that.”

Long Haul made a silencing gesture toward him before looking to me. “Well, how about it, miss? Seems kinda odd to walk off from someplace with food, without havin’ any idea where you’re goin’.”

Yeah, it wouldn’t, but… “My… my mother died recently. She was the one who did the farming. I-I could never figure it out. Heck, I couldn’t even grow a weed.” I swallowed, managing to tear up a bit as I put on an act of trying to stay strong. “I-I mean, I spent all my time reading all these dumb old books instead, and then she… I couldn’t…” I paused, sniffing, then took a deep, steadying breath. “If I didn’t find that box of military rations in those ruins earlier today, I might have starved. I’m not even sure how long it had been since I had something to eat.”

Long Haul nodded understandingly. “So the farm’s a bust, and you went out lookin’ to find some food?”

\leavevmode\llap{“}Yeah,” I said. “Or better yet, some town where I could get a job. It’s just… I don’t really know anything outside the farm and what I’ve read in a bunch of old books.”

\leavevmode\llap{“}I see,” Long Haul said, nodding, and raised a hoof to his chin. After a few seconds, he looked back to me. “Well, tell you what. We’re heading to a little town called Rust to do some trading. If—”

\leavevmode\llap{“}Oh, \textit{hell} no!” Sharps said, rising to his hooves again. “Look, Pops. You’re paying me to protect you. You’re not paying me to foalsit some tag-along, and especially not some weird filly we found in the middle of nowhere. She could be working with some fucking raiders, buddying up with traveling merchants just to see if they’re worth hitting.”

Long Haul rolled his eyes. “She don’t look like no raider to me, Sharps.”

\leavevmode\llap{“}That’d be the point,” Sharps said. “Besides, I didn’t say she was a raider. You know they’ve been getting worse, lately, that’s why you hired me. Maybe they hit some other group, and they’re forcing her to work for them. You know, ‘do this or your mom gets it.’” He glared at me. “That what this is?”

I almost recoiled at the accusation, but I held firm; it would have likely been seen as confirmation of his suspicions. I shook my head. “No.”

Still, I was concerned about this talk of raiders. “Dangerous ponies,” Sharps had called them, and evidently the reason for such a hostile greeting. They were scared of other ponies.

How bad had things gotten?

\leavevmode\llap{“}Sharps, look here. I get that you’re tryin’ to protect us, but this is my little caravan, and I ain’t leaving somepony out here all on her own. It ain’t my way.”

\leavevmode\llap{“}Yeah, fine, whatever,” Sharps said. “But this still isn’t the job I signed on for. You start bringing in extra ponies like some fucking Wasteland tour group, you’re making \textit{my} job harder.”

\leavevmode\llap{“}Fair enough,” Long Haul said in a reasonable tone. “I figure most of the work is in guarding the brahmin and the group as a whole rather than any one individual, and we’re halfway to Rust already, but I’ll round up a bit. Figure an extra... five percent on your pay should be generous enough.”

I have to admit, I kind of liked the old guy. He kept his cool, negotiating a compromise to satisfy both sides of the situation. I could appreciate that.

Sharps stared back for a moment before grunting again. “Fine,” he grumbled, sitting once again.

\leavevmode\llap{“}Um…” Starlight started to say, raising her hoof.

\leavevmode\llap{“}Y’all too, yes,” Long Haul said, to which Starlight grinned even more.

Thunderhead just gave a soft, pleased-sounding grunt.

\leavevmode\llap{“}Thank you,” I said to Long Haul, who turned his smile to me.

\leavevmode\llap{“}Just doing what’s decent, miss,” he said, giving a little chuckle. “Can’t really be a good merchant if I’m turnin’ ponies away and all that. Now, I’ll be ‘spectin’ you to pitch in if we need an extra hoof and all that, and if you got anything you can spare to make up for the extra expense, I’d appreciate it, but I’m not gonna insist.”

\leavevmode\llap{“}I’d like to,” I told him, “but I’m afraid I don’t have much to offer, other than those rations I found.” I almost didn’t want to mention them, but I figured that he was the kind of pony who would appreciate honesty. I also figured that a pony who was so charitable in giving up bits for my benefit wouldn’t deprive me of my only food, and I was right.

\leavevmode\llap{“}Heck, it don’t feel right takin’ food from you if that’s all you got,” he said, even frowning at the thought. His smile returned a moment later. “Still, I could probably get some pretty good caps for some military rations. How ‘bout a trade, then? You trade a meal of your rations, and I give you a meal of my own cooking?” He chuckled, putting a hoof to his chest. “I promise, it can’t taste any worse than two-hundred year old army chow.”

\leavevmode\llap{“}\textit{Ehahaha!}” I blurted out, then cringed and placed a hoof over my face. It took a few moments before I was able to still the sudden rapid breathing and re-order my thoughts. I lowered my hoof, doing my best to look as if I weren’t in a very fragile mental state. “S-sorry. It’s… been a very exhausting day, both physically and mentally.” I smiled. “I think that’s a very fair offer, thank you.”

\leavevmode\llap{“}Well… okay then,” he said, an eyebrow quirked questioningly at the outburst, but he refrained from asking. “Grab a seat by the fire and make yourself at home. Dinner should be ready soon.”

I thanked him again and carefully made my way to an open spot near the fire. He returned to his pot, pulling out a few more ingredients to add to the mix. I had hardly sat down—my limbs thanking me for the chance to rest—before Starlight leaned in. “So, you lived on a farm?”

\leavevmode\llap{“}Yes, I did,” I said with a nod, and returned her smile as evenly as I could manage, given my shaky mental state at the time. She seemed eager and excitable, which might also mean easily swayed. A good, quick “friendship” had sounded particularly appetizing, at the moment.

Of course, it also prompted her to ask a question I would rather avoid.

\leavevmode\llap{“}So, what was it like?”

\leavevmode\llap{“}It was… boring,” I said, exhausting the majority of my knowledge of farming within three words. I diverted. “It’s why I spent so much time reading old books. All stuff from the war, and before.” I swallowed, trying to fight down my growing nervousness. “What he said… has it really been two hundred years?”

\leavevmode\llap{“}Since… what, since the megaspells? Yeah, something like that.” She floated up her PipBuck, hitting a couple buttons as she looked over the screen. “Two hundred and two years,” she said, dropping it to hang from her neck again.

\leavevmode\llap{“}Ah,” I said, suppressing a tremble as my hopes were crushed under the unyielding hooves of fact.

After a couple moments of my silence, Starlight decided to prompt me for further conversation. “So… what are you planning on doing, now?”

Her question snapped me out of my silent mourning. “I… don’t really know. Hopefully someone at Rust will have a job I can do.” I disliked that so much of my plan amounted to nothing more than improvisation.

\leavevmode\llap{“}I’m sure you’ll find something,” she said. “I, uh… I know it can be a little hard, suddenly being on your own, but don’t worry. There’s plenty of opportunity out there.”

Sharps gave a dismissive exhale, but she didn’t seem to notice.

\leavevmode\llap{“}Thanks,” I said, smiling again, which made Starlight smile more. “Problem is, I don’t even know what’s out there.”

\leavevmode\llap{“}Afraid I can’t help much with that,” Starlight said. “I only hooked up with Long Haul a week ago—”

Sharps quietly muttered. “It’s only been a week?”

\leavevmode\llap{“}—And I didn’t travel much before that. I lived in Dodge Junction, a little run-down town not far from the Dodge City ruins. Traveled between the two every now and then for scavenging runs, but that was about it.”

I was disappointed to hear that Dodge City was in ruins. Not surprised, mind you, but still disappointed. A large pony settlement would have been convenient. I forced myself to continue on, rather than slipping into silence once again; I wasn’t going to make friends by being reclusive. “Why did you leave?”

She shrugged. “Eh. It was just… well, boring.” She flashed me a smile at hitting a common element between us. “I wanted to get out there and \textit{do} something. Long Haul came through on his rounds, and I thought it was perfect. I’m a great shot, and I’ve got the most awesome gun in the Wasteland. A guard job lets me earn caps, \textit{and} I get to help keep ponies safe. What could be better than that?”

I noted that she referred to money as caps, rather than bits. I remember thinking it was strange to name money after headwear, but figured it was probably just a name. It wasn’t as if bits actually resembled mouth-bits, after all. And then there was the concerning repetition of the word “Wasteland”, which sounded more than a little ominous—and this coming from someling hatched in a place called the Badlands.

Despite the slight mental sidetrack, I kept up the conversation. “That sounds pretty good,” I said. It sounded pretty pony-like, too, and in a good way.

\leavevmode\llap{“}Yeah, it’s great,” she said. “Best decision I ever made.” She reached over, picking up her long weapon. She ran a hoof gently along the long, lean frame. “Heck, I pretty much had to, after getting this. Seems a waste to only ever use her for hunting.”

I almost missed what she said. My hunger dug at my mind, almost frantic at the traces of love I could feel radiating from her. It was faint and weak, but at the time, it was the most amazing thing I had ever sensed. I fought back a fresh trembling. “That’s… very nice,” I said, struggling to keep my voice even. I was so hungry!

It was probably a good thing that Long Haul interrupted when he did, before I could do something reckless. “Alright y’all. Chow’s ready!” Bowls clattered as he served out portions of a thick vegetable stew and passed them around. When he set a bowl before me, I gripped my medical box in my hooves and popped open the lid.

Sharps jerked so hard he almost spilled his own bowl, biting down on the bit of his rifle again, and I froze, the lid only barely open. “Woah, easy. I don’t have a weapon. I was just getting a ration to trade.” While Long Haul frowned at Sharps, I slowly opened the box the rest of the way to show the contents, then gingerly reached in to slide some of the rations aside. Having done so, I picked one up, passing it to Long Haul, who gave another smile and nod to me.

Eventually, Sharps relaxed, though he didn’t entirely relent. “What are those crystals?”

\leavevmode\llap{“}They belonged to my mother,” I said, ears drooping.

\leavevmode\llap{“}And that… device?”

Starlight spoke up before I could, her words slurred around a mouthful of stew. “Es uh dahah-hor.” Then she coughed and sputtered a moment before managing to swallow, thumping a hoof against her chest. “Oof… yeah, data-store. They plug into PipBucks and you can read stuff off them.”

\leavevmode\llap{“}Or any terminal with a proper slot,” I added, picking up my bowl as I started to eat. I have to admit, Long Haul could cook. “It was my mother’s, too. She left a message on it for me.”

\leavevmode\llap{“}What was it?” Starlight asked.

\leavevmode\llap{“}I don’t know. It’s damaged.”

\leavevmode\llap{“}Oh,” Starlight said, her enthusiasm curling up and dying.

\leavevmode\llap{“}I might be able to fix it,” I said, and was rewarded by a hopeful smile. “I just need to find the right software tools, and I might be able to extract the data.”

Out of the corner of my eyes, I could see Sharps leveling a suspicious look over his bowl. I took another swig of my stew—we seemed to lack spoons—and added, “We had an old terminal at the farm, dug out of some ruined building, and a bunch of books on programming. I poked around at it a lot when I wasn’t reading. Got pretty good at it, I guess, but it didn’t have the tools I’d need to fix this.”

It was a weak excuse, but I hoped it would be enough to explain my training in computer intrusion techniques. I also hoped that those techniques would be enough to help me retrieve whatever my Queen had left for me. I was already getting the impression that there were not many computer specialists left.

It worked well enough for Starlight, at least. “Cool! Hey, think my PipBuck would have what you need?”

\leavevmode\llap{“}Maybe,” I said, my ears perking up. “Stable-Tec loads all sorts of features in those things.” I hastily added, “Or at least that old Stable-Tec manual said they did.”

She quickly gulped down the rest of her stew, setting the bowl aside, and scooted up next to me. “Just don’t break it, okay? These things are hard to replace!” Her tone was joking, but it struck me as that kind of joking one does to soften just how serious they really are about it. Considering that it was a two-hundred year old piece of advanced arcano-science computer tech, I couldn’t imagine these things were common. If there were still cities in ruin, I had some serious doubts about Equestria’s manufacturing capabilities.

She leaned in close as she shifted the PipBuck around so I could use it, and I immediately lost my train of thought. She was so close! If I could just coax out that feeling of love again, I could get a quick snack. “Thank you,” I said as I held the PipBuck in my hooves, practically leashing her in place thanks to that strap around her neck. As I began flipping through the various menus, I asked, “So, you said something about the most awesome gun in the Wasteland?”

\leavevmode\llap{“}Oh yeah!” she said, and ducked her head to slip easily out from my imperfect leash. I mentally cursed as she moved away to retrieve her gun. “This beauty! It’s a Lancer, and it’s pretty much one-of-a-kind. It ain’t some old-world antique, either. No factories or nothing; just some old unicorn in Gemstone that made some of the best weapons in the world!”

It was quite graceful looking, for a weapon. It was twice as long as her and very narrow, with an open metal frame around a central, barrel-like core. The whole thing was painted dark brown, like wood. The only protrusions were the mouth-grip and telescopic sight near the midline of the weapon, and the bulge at the rear.

That faint sense of love flickered into being again. It taunted me, just out of reach.

\leavevmode\llap{“}It doesn’t fire very fast,” Starlight said. “In fact, it can only fire once before I have to swap out crystals to charge. But Celestia above, one is all she needs! I could hit a galloping radhog a mile out with this thing. Hell, I’ve done it!”

\leavevmode\llap{“}Right,” Sharps muttered.

\leavevmode\llap{“}Hey! I have!” She shot him a glare before turning back to me. “Don’t mind Captain Grumpy-Pants over there. He’s just jealous because I’ve got the cooler gun.”

\leavevmode\llap{“}Guns don’t need to be cool,” Sharps said in a weary tone. “They just have to do the job right.”

\leavevmode\llap{“}Uh-huh,” Starlight said, smirking. “And how far away can you hit a pony with that hacked-together hunk of junk?”

I glanced to the gun in question. It seemed far less impressive when not staring down the muzzle. It looked as if someone had simply taken a pipe and welded on a bit, stock, and sights, stuck a magazine in the bottom of it, and hung a worn strap between the two ends. It looked crude, but functional.

Sharps shrugged, playing nonchalant, though I saw his jaw tighten. “A few hundred yards.”

\leavevmode\llap{“}Sounds like your gun sucks.”

\leavevmode\llap{“}And I can shoot a half-dozen ponies and make all their buddies scramble for cover in the time it takes you to get off a single shot. There’s more to a gun than range.”

\leavevmode\llap{“}That sounds like the excuse of a pony that misses a lot.”

\leavevmode\llap{“}Children,” Long Haul said, his voice cutting through the conversation despite remaining calm and conversational in tone. “Settle down, now. Y’all have your own merits, no need to make it a contest. Way I see it, we can use the diversity. Y’all with the automatics can put out enough firepower already. I figure having one piece with a bit more range and punch should complement that nicely, don’t you?”

Thunderhead was nodding, his sole contribution to the conversation thus far. Sharps held out for a bit before finally sighing. “Yeah, fine.”

Long Haul nodded, then looked to Starlight. “As for you, I get that you like your gun. Heck, it’s a mighty fine piece, I gotta say. I can see why you’re proud of it. But don’t you ever let me hear you insulting another pony’s piece again. Critique, sure. But insulting it, to a pony like that? One who hangs their life on their gun? Way I figure it, you insult his piece, you might as well be insultin’ his soul.”

Starlight cringed back, eyes wide and ears drooped. “I-I didn’t mean—”

\leavevmode\llap{“}Now, now,” Long Haul said, reaching out to pat her on the shoulder. “I know you didn’t mean nothin’ by it. Least, not like that. You’re a good filly, even if you just don’t think quite so much ‘bout what you’re sayin’ at times.” He drew back, returning to his playful smile. “And maybe tone down the braggin’ a bit, okay?”

She weakly smiled back. “Okay.”

He nodded, and we all returned to eating. I took quick sips of my stew as I browsed through the PipBuck. Eventually I sighed, holding it out to Starlight. “Thanks, but it looks like it doesn’t have any of the tools I need.”

\leavevmode\llap{“}Aww,” she said, frowning as she slipped the loop over her head. “Well, I guess it was worth a try.”

\leavevmode\llap{“}Of course,” I said, smiling. “Thank you.”

Her smile returned. “You’re welcome.”

The food was finished quickly. Tired from a long day of walking (Or, in my case, from my body’s complete lack of endurance), the conversation died down pretty quickly. We were all ready to get some sleep. All but Sharps, who volunteered to take first watch. Apparently things were dangerous enough around there that we needed to keep an eye out even while we slept.

Bedrolls were laid out and ponies settled in for the night. Lacking any such supplies myself, I simply found a patch of dirt free of rocks and lay down, using my box as a makeshift and fairly uncomfortable pillow. I missed my chitin.

A minute later, a blanket hung in front of me. I looked up to see Thunderhead holding it by one edge. He dropped it in front of me. “Got an extra you can use.”

I smiled. “Thank you.”

\leavevmode\llap{“}Mmmhmm,” he replied, giving a nod and a soft smile. Then he turned back to his bedroll and lay down.

I remember hoping that his barding was warm. He lied to me. He didn’t have an extra blanket.

{\br}%
I woke to the faint light of pre-dawn and the ache of my entire body protesting my own existence.

It was better than the previous night, but it would evidently take more than a single night’s rest to recover from two centuries of inactivity. I wanted to just lay there for a while, but I couldn’t help mentally grumbling that I had spent far too long doing nothing for the past two hundred years, thank you very much.

I had apparently moved past denying reality and on to being bitter about it.

Still, the irritation gave me enough motivation to finally push aside my borrowed blanket and get up.

Everypony was still asleep, except Silver, who was lying back against the side of one of the cattle a short distance away—the single-headed one, it turned out. She looked over as I rose, giving a silent nod that I returned.

I took the edge of the blanket in my teeth, dragging it back over to Thunderhead. The pre-dawn morning was chilly, but it didn’t seem to be bothering him any. He was sprawled out on his back, legs askew. Still, I pulled the blanket over him. He mumbled something in his sleep, curling up and immediately entangling himself in the blanket’s folds.

I slipped away from the sleeping ponies, making my way over to where Silver sat.

She smiled as I approached, her voice just above a whisper. “He likes you.”

\leavevmode\llap{“}What?” I said, wincing as my voice came out louder than I meant. Quieting down, and casting a glance back to who I suspected she meant, I asked, “Who, Thunderhead?”

\leavevmode\llap{“}Mmmhmm,” she said with a nod.

\leavevmode\llap{“}I thought he was just being nice,” I said. I hadn’t sensed any particular affection from him. Then again, I wouldn’t have off of such a brief encounter. There was quite a difference between liking someone based off a first impression and forming the kind of close connection that would produce affection I could feed on. “You sure?”

\leavevmode\llap{“}Oh yeah,” she said, laughing softly. “I think he said more to you last night than he has since leaving Mareford. Ain’t like he’s shy or nothin’, he just doesn’t seem to have much use for words. He’s about as nice as they come, though.”

I smiled as I glanced over to him again. He did seem like a pretty nice pony, from the little bit I’d seen of him. If he really did like me, I could culture a nice friendship out of it. Maybe even something more.

She chuckled softly at my smile, then patted the ground. “Go on, take a seat. Probably be a little bit before everypony’s up, anyway. Wouldn’t mind the company.”

I accepted her offer and sat, though I groaned softly as I did so. My legs felt rubbery. Silver looked concerned. “I’m just feeling pretty sore from yesterday,” I said. “I’m not used to traveling. I just hope I can keep up with everypony.”

\leavevmode\llap{“}Well, we tend to take regular breaks for the brahmin to graze,” she said, gently placing a hoof on the head of what was apparently called a brahmin, now, because ‘cattle’ was so two centuries ago. “And heck, if you’re feeling like you need more of a break, you can probably take a load off and ride for a while. Old Chuck here could use the company.”

I had to ask. “Chuck?”

\leavevmode\llap{“}Yep,” she said, cracking a smile. “Odd name, I know. It’s what Moorice named him; I think it was some sort of joke. He was Chuck’s better half.”

Silver nodded to the other side of Chuck, at the scarred tissue along one side of his off-center neck. “Moorice got a face-full of barbs from some mutated fly… \textit{thing}. Poor thing got a nasty infection from the wounds, just started rotting him away from the inside. When he passed, we amputated the head. Old Chuck here may not have had much upstairs, but he’s a tough one. Pulled through strong as ever.” She smiled softly, giving him an affectionate rub between the ears. “He’s kind of become our good-luck charm, I guess.”

That was both somewhat charming and horrifically morbid. I hardly noted it, though. I was too preoccupied by the glorious sensation of love! Silver truly cared for Chuck. It wasn’t the powerful love of a romantic relationship, or even the affection of a close friendship. It was more like the gentle love of a favorite pet; not nearly as filling, but it would suffice. I carefully slid in closer as she was distracted by the brahmin, hoping to pretend I was merely sitting closer to keep our conversation quiet.

I nearly trembled as I drew in the emotion. I couldn’t draw it in very fast without getting uncomfortably close, but that was just fine with me; I wanted to be slow and gentle, so as to not alarm her. Even that little trickle of love was spectacular to my starved mind.

Sadly, it faded before I could get more than a little nibble, but I was content. I hadn’t even drawn enough for a half a day’s survival, but I would have many more opportunities. A little here, a little there, and I would be just fine. It just required a little bit of patience.

I covered for my closeness by reaching out to lightly run a hoof along Chuck’s side. Silver smiled softly at that.

\leavevmode\llap{“}Well I’ll be,” came Long Haul’s quiet voice, as he stepped quietly over to us. “Somepony who gets up before I do. Now that’s a pleasant change.”

Silver broke into a wide grin. “You must be getting old,” she teased, rising up to meet him. “Sleeping in so late, letting this wonderful day waste away while you’re lazing about in bed.” It was still mostly dark, and the dark clouds that filled most of the sky, scattered about in the most chaotic fashion, were anything but wonderful. At least it was still clear above us.

He chuckled as they both leaned in, nuzzling fondly. I’m normally loath to use insect metaphors, but I have to admit, the one about a moth being drawn to flame seemed particularly apt at that moment, especially when it would probably end just as poorly if I followed the instinct that welled up in me. The love I felt between them was intoxicating!

Eventually they parted, starting on morning routines. A fire was lit, and the cooking pot came out again. Meanwhile, faint wisps of love still lingered between them. I considered moving to be between them, hoping to catch a little of that love between them. Sure, it would be inefficient, drawing only a tiny fraction of it, but even a little bit would have been wonderful. Despite that, I stayed put. A little patience would get me all I needed, without needing to act strange and drawing attention to myself.

Sadly, Long Haul turned down my offer to help with breakfast, shooting down my best excuse to be close to him. “It’s a bit too simple to need much help with,” he said, despite the appreciative smile. I’d have to wait just a little longer for my opportunity.

It wasn’t long before the scent of cooking vegetables reached the noses of the sleeping ponies, and within minutes they had all woken. Food and water was passed around, bedrolls and blankets were packed, and a few discreet trips were made to an unfortunate dead bush a short distance away.

\leavevmode\llap{“}It’s still clear,” Starlight said, in quiet wonderment, her eyes to the sky. Sure enough, the ring of clear sky still hung over us, the last few stars twinkling in the growing light. I pondered her reaction.

\leavevmode\llap{“}Better dress warm, all the same,” Sharps noted, tugging on the straps of his barding. “Those are some dark clouds we’re heading towards. I wouldn’t be surprised if it starts raining soon.”

The statement seemed immediately strange to me. I spent enough time in Equestria to be used to weather happening on a precise schedule. There was never any question about whether it would rain or not on a certain day, unless some weather pony screwed up the schedule. Something seemed off to me, but I certainly wasn’t going to speak up and highlight my own ignorance. Even as a recluse on an isolated farmstead, it would be hard to explain a misconception about the weather. I’d simply have to roll with it.

Starlight tore her gaze away from the sky to root around in her small saddlebags. She eventually pulled out a light jacket and put it on.

Sharps, who had supplemented his thick barding with a large poncho, simply stared at her for several seconds before giving a soft snort, shaking his head, and turning back to his packs.

He made no comment about my attire, as nonexistent as it was. I was tempted to ask Thunderhead if I could borrow that blanket again, or a spare jacket, or \textit{anything} in case it did rain. When I glanced his way, his look immediately changed my mind. I got the impression he was considering the exact same thing. I didn’t need to ask. If it did start to rain, it would spur things on quite well if he were to “come to my rescue”.

Soon the brahmin were up and ready to go, with Long Haul giving a few final tugs on the straps holding the bulging packs on. “Okay,” he said, glancing back to us. “Looks like we’re all set, and if we keep up the pace, we should make Rust by tomorrow night. Let’s get this show on the road.”

{\br}%
The tiny bit of love I had pilfered was just enough to keep me going. It pushed that ache in my limbs to the background. They were still sore, and still eager for some rest, but I was able to persevere.

That tiny bit of love probably saved my life.

By mid-day, we had passed under the edge of the cloud cover, following the train tracks as they wound through the broken, barren terrain. The dark clouds above continued to slowly churn and drift. They bunched up in places, stretching thin in others. Every now and then a thin crack would form, a spear of sunlight lancing through the gray dimness to light some small, distant piece of land before inevitably fading away once again.

There were no pegasi, I noted. It was as if the clouds were left to float aimlessly on their own. Was the weather really left entirely uncontrolled here? Sure, we were toward the edge of Equestria, but I thought it strange.

Contemplating the strange weather led me to an epiphany: I knew where I had seen that strange piece of debris near the C.L.T. facility. The curved white surface was just like those weather-control towers the Ministry of Awesome had been working on, and would explain what Starlight meant by a “tower” exploding. Had they actually gotten those online?

The tower’s destruction made sense of what I was seeing above. If they’d been using it to keep the weather under control, its loss would explain why things had ended up in chaos up above.

And yes, my hive knew what those towers were all about. They built almost 50 cloud-high spires at tremendous expense. Every single ministry was involved in them, in some part. It was the MAw’s greatest secret. Of \textit{course} we knew.

I was contemplating what—if anything—that information might mean for my situation when I was interrupted by a shockingly loud \textit{SnapSnapSnap!}

The three sharp sounds were so close together that they were almost one. A couple puffs of dirt kicked up beside Thunderhead, who was walking just in front of me, and the stallion toppled forward. His chin and chest hit the dirt, hindquarters lifting up with his momentum before flopping to the side.

Sharps lunged forward past me, shouting. “Ambush right!” He bit down on the grip of his rifle, and everything became explosions.

I lurched back a step, ears pinning back against an assault of sound so loud I could feel it in my chest. I barely noticed the dark-blue blur of Starlight throwing herself off the path and into a narrow depression beside the tracks, and I followed, wincing as something hot smacked me on the cheek.

I collapsed on my side beside Starlight, covering my head with my forehooves. Sharp’s rifle continued to fire in an unbroken string, each shot brutally loud.

Then the assault of sound ended. I pried a hoof away from my face to see Sharps reach up to his rifle, and the magazine fell away, spent. He shot a look over at us and shouted, his voice oddly small and distant. “Fucking shoot!”

Starlight yelped something as she scrambled up, her “Lancer” swinging around while Sharps pulled a fresh magazine from a pouch at his side. Another sharp snap sounded, and Starlight yelped again, ducking down below the edge of the depression once again. Sharps merely flinched, but didn’t stop. He slammed the magazine into the bottom of the weapon, pulled back the handle protruding from the weapon’s side, and fired again.

This time I put my hooves over my ears, muffling the powerful sound. Sharps paced his shots, firing short bursts as he advanced up onto the rise we were hiding behind. Starlight, as if encouraged by his firing, poked up again. Another pair of sharp cracks made her flinch, but she stayed up.

The brahmin we had been beside—the one with both heads—staggered along the far side of the tracks, stumbled, and collapsed. Thunderhead hadn’t moved at all, lying still atop the tracks.

A strange, hissing snap sounded, and Starlight ducked down again. “Shit!” she cried out as her magic practically tore open the chamber at the rear of her rifle. She pulled out a dull red crystal, quickly replacing it with a glowing one, and sealed it up again. Then she rose up once more.

The flicker of flame caught my attention. I watched in stunned fascination as a pinwheel of fire silently arced through the air, fixed to the neck of a bottle. It came down to shatter against Chuck’s side, fire bursting forth and flowing across Long Haul and Silver.

Several sharp snaps made me wince, and dirt sprayed over me as Sharps fell back into the depression with a mangled curse, limbs flailing. Starlight shrieked something, wavering, but resumed her aim, snapping off another shot. Then she ducked down, reloading again.

Sharps had managed to haul himself into a sitting position, though his left foreleg was held close to his side, injured. He fumbled for a moment to get a good grip on the bit of his rifle and brought it up again, emptying the rest of the magazine in a brief string of hammering shots. One of his casings landed on my side; I yelped at the searing pain, kicking it away.

I couldn’t see Long Haul and Silver. The depression they had been in was smokey and smoldering. I hoped they had gotten out. Across the tracks, Chuck was lowing and galloping awkwardly away, his packs burning.

Only having one good foreleg slowed Sharps’s reload. He had just slammed a new magazine home when there was a soft \textit{thunk}, and a spear appeared, buried in his neck so deeply that the tip jutted out of his back.

The stallion’s eyes went wide, his rifle falling to the ground. I stared in horror.

For some reason, the thought my mind decided to focus on was: \textit{shouldn’t there be more blood?}

I looked to Starlight in time to see her fire off another shot, another whining hiss and snap sounding as her weapon loosed a red beam of light, searing a line in my vision. As she reloaded, I realized that she was the only one still in the fight. The only one between me and whoever was out there, trying to kill us all!

My eyes fell to Sharps’s rifle. I lunged forward, grabbing the bit in my teeth, and ignoring the grit of dirt as I scrambled back into cover. Taking just a moment to steady myself, I took a deep breath, then raised up, leveled the rifle up the rocky slope in the same direction Sharps had been firing—I didn’t actually see anypony at the moment—and tongued the trigger.

Nothing happened. There wasn’t even a click.

With a distressed whimper, I dropped back down behind cover, dropping the rifle into my hooves. It \textit{should} work. I’d just seen Sharps reload it before he went down. I played back watching him load the first time. I pushed on the magazine to make sure it was in all the way, and then grabbed the handle on the side, pulling it back. The breach opened, and the handle locked back. I pushed and jiggled it, trying to get it to shut and chamber a round, but it wouldn’t move.

I heard a distant yell, and in desperation, I lifted the rifle to try again, hoping the weapon was working as intended. As I rose up, I saw the movement of a pony coming down the slope. I don’t remember any details about them in that frantic moment. I think it was a mare, and she might have had something in her mouth. She must have seen me rising up, as she turned and dove for a large rock. I tongued the trigger again, and the rifle roared.

It also slammed back against me, nearly pulling free of my mouth and bashing the stock against my shoulder and neck. I have no idea where my shots went. Honestly, I was probably lucky I didn’t hit Starlight.

I slumped back, getting a good grip on the bit again. When I rose up this time, I cinched the semicircular base of the stock snug against my shoulder and the base of my neck. I squeezed the trigger again, and the thundering crack of the shot drove the rifle squarely into my body, but this time, I kept it under control. A spattering of dirt puffs kicked up all around the rock the pony had hidden behind, even knocking off a few shards of stone.

Another searing flash of light dazzled my vision, and I dropped back down again, blinking. A glance back showed that Sharps had pulled free the spear—\textit{there’s blood, now}, I noted—and had collapsed on his side. He was weakly fumbling at a pouch on his chest. I, however, had focused on another pouch, the one that held more magazines for his rifle. I felt I was going to need it, very soon.

I scrambled out again, snatching the pouch and pulling against its strap. Sharps even relented in his own efforts, lifting his foreleg to let me pull the strap free before returning to his fumbling.

I threw the strap around my neck, the pouch thumping against my medical box. I could hear more yelling. \textit{Lots} of yelling.

I took one look back to the fallen brahmin, just past the tracks. I didn’t even think before I was on my hooves, running as fast as my weary legs could carry me. I dove over the fallen animal a moment before several sharp snaps sounded, all around me.

After only a moment to take a breath, I rose up, just barely exposing my head as I laid the barrel of the rifle across one of the brahmin’s packs, sighted in on a cloud of dust drifting down the slope, and fired a long burst. Dirt kicked up all around the slope, leaving the ridge in a dusty haze.

The rifle lurched with the final shot, the bolt slamming shut. I dropped behind the brahmin, releasing the bit and quickly pulling back on the handle once again. When it locked back, I saw that there were no more bullets in the magazine. This was followed by a few frantic seconds as I scrambled to find the release, which ended up being a small lever just behind the magazine. Pulling the empty magazine free, I fished out a new one—I didn’t even see how many I had, just that there were more—and fumbled with it for a moment before finally sliding it into place.

I took up my firing position again, only to see Starlight, her Lancer’s chamber sitting open and spent as a pony leaped over the edge of the depression she lay in. Of all the odd bits and pieces that adorned the pony, the only thing that caught my eye was the machete clenched in her teeth.

I swung around the rifle, but it was too late. The mare came down on Starlight, the blade slicing at her head.

There was a flash of sparks as Starlight instinctively raised her rifle to protect herself, the other mare’s blade cutting into the weapon. Then the other pony crashed down into her, sending them into a tumble, obscured by the slight rise of the train tracks.

Movement on the slope caught my attention again. At least two more ponies were running toward us, one of which held a spear in his teeth, with several more on his back. I sighted in on him and tongued the trigger, blasting out several shots. Both ponies dropped behind cover once again.

A rapid series of sharp discharges sounded from just across the tracks, and Starlight scrambled back, her pistol floating just in front of her, firing frantically. Blue lines of light struck out. With the rise of the tracks obscuring my sight, all I could see of the other pony was a leg that spasmed up into view, which promptly burned away into a cloud of blue particles. Starlight’s pistol jerked several more times, no longer firing.

I caught a glimpse of movement up on the slope above, and immediately squeezed off another burst; Starlight winced and dropped behind cover again. Sharps, I noted, was no longer moving.

Letting go of the bit, I shouted out. “Starlight! We have to go!”

Now, I’m sure some of you wonder why I didn’t just leave her. After all, I had just met these ponies the previous evening. They were nothing more than food to me, at the time. Heck, I could drop my disguise and fly off.

I’d like to say that it was a carefully measured decision of logic. I was in the middle of nowhere, more than a day’s travel on hoof from the nearest settlement, dangerously low on love, and physically exhausted. If Rust didn’t lie on the tracks we’d been traveling along, I might completely miss it, assuming I could even make it there. I needed guidance, I needed assistance, and I needed food; Starlight could give me all of those.

But that wasn’t my reason. The simple fact is, I didn’t even think of it.

I was so preoccupied with the hellish chaos all around me that I wasn’t thinking in terms of logic and reason. I was lost to emotional response. Two of them, actually.

The first, terrified of the terrible and abrupt violence of the previous minute, was screaming at me to run away.

The second, possessive and protective, insisted that these ponies were \textit{mine}.

I suppose it was that “valued livestock” thing I mentioned earlier. Yes, I had just met them, and yes, I was probably going to part ways with them upon arriving in civilization, but that would be done on \textit{my} terms. These ponies had value to me. I \textit{liked} these ponies. I didn’t like seeing ponies get hurt, much less when they were ponies I \textit{liked}. These other ponies were hurting my ponies. They were \textit{killing} my ponies. They were taking from me, and I didn’t like it. I hated it. I was terrified of it.

The emotions combined, dragging me along to flee with any ponies I could salvage.

Starlight stared at me with wide eyes, and I beckoned to her. She glanced over to Sharps, trembling for a moment before snatching up her bent rifle and galloping toward me.

I saw the puff of dust near the top of the ridge an instant before another snap hammered at my ears, and tongued the trigger to send another burst his way. Dirt kicked up, clustered loosely around where the shot had come from.

Starlight collapsed at my side, panting and trembling, but intact.

I cast a quick glance backwards, hoping the glimpse I had caught during my dive across the brahmin had been correct. It was; just ten yards away was a shallow gully, just deep enough to conceal a galloping pony. I pointed a hoof, shouting at the top of my lungs over the muffled buzz in my ears. “Go!”

Then I turned back and fired again. The rifle blared twice more and fell silent, its magazine spent.

I dropped down and turned, to find Starlight still laying beside me. “Go!” I repeated, and hooked a leg under her shoulder to haul her up. I half-dragged her along until she finally got the idea and got her hooves under her, and together we dove for the gully.

A burst of snaps sounded all around me, puffs of dust kicking up from the far side of the gully. Then we fell, collapsing into the dried streambed.

I panted, my heart hammering in my ears, clear even past the buzzing. Starlight was staring straight up, eyes wide and glistening as she trembled. She suddenly blurted out, “Fuck!”

\textit{Keep going}, my mind insisted, and I obeyed. I hauled myself up despite my fatigue. “Are you okay?” I asked as I kicked out the spent magazine. Retrieving a fresh one—the second from last—I slammed it home.

\leavevmode\llap{“}I… y-yeah,” she stammered, patting herself with her hooves a couple times. “I-I’m okay. I’m okay.” She pushed herself up, shaking. “Uh… you?”

\leavevmode\llap{“}I don’t think I’m injured,” I replied, my words sounding mushy to my ears. I pulled back the rifle’s handle, gripped the bit again, and peeked over the edge of the gully.

More shots sounded, but they were quieter; distant, echoing pops, not the brutally sharp snaps and cracks from before. I saw a few ponies, clad in patchy, cobbled-together barding. They were galloping, but not toward us. Instead, they were chasing after the flaming, lumbering bulk of Chuck.

I dropped back, silently hoping that he would give them a good, long chase. “We’ve got to run,” I said, pointing away from where the other ponies were headed. “Down the gully. Go.”

Starlight struggled to her hooves, looking dazed for a moment as my words processed. “R-right,” she said, staggering for a few moments before working up to a canter. I could see tears trickling down her cheek.

Slowly, the rush of adrenaline faded. The jittery tremble stilled, and a tremendous fatigue crashed down on me. After only a couple minutes, our canter slowed to a trot, then a walk. Not much later, I started to stumble, unable to lift my hooves enough to clear the occasional bump in the dirt.. We’d just left the gully when I fell. Starlight cried out, stumbling back to me. “W-Whisper! C-come on!”

I tried to push myself up. If not for Starlight’s magic, I wouldn’t have been able to. I panted. I couldn’t even hold my head up as I staggered another step.

\leavevmode\llap{“}Come on, Whisper!” she cried out, voice wavering as more tears flowed. “W-we have to keep going!”

\leavevmode\llap{“}I… I can’t,” I weakly murmured, staggering again. Only her magic kept me from falling. My body, atrophied by centuries of inactivity and pushed to the extremes by adrenaline, was failing.

\leavevmode\llap{“}No,” she whimpered, coming close against my side. “No, no, no! Were you hit?”

I swallowed, shaking my head. My leg tried to give out, and I ended up leaning heavily against Starlight’s side. “No… muscles… giving out…”

She pulled with her magic, staggering forward. Even as light as I was, it seemed a tremendous strain on her. I pressed on, my abused body feeling numb and heavy and sick.

I pushed away, stumbling another step before collapsing to the ground and vomiting. For the second time in as many days, I lay there, gut burning as I retched. Starlight dropped to my side, crying as she tugged with her magic “Whisper! Whisper, come on, w-we can’t stop. They… they’ll…”

I coughed and spit. Somehow, with the help of her magic lifting me, I got my hooves under me. I almost fell as my stomach clenched again, sending agonizing stabs through my abdomen, and I spit up a bit of bile. “Please,” Starlight cried. “Please, come on! Please... don’t…”

I wavered as I made one more step. I was suddenly completely preoccupied by the fact that I had dropped the rifle somewhere. I almost fell when I looked back, and Starlight gave another tug with her magic, her shoulder pressing firmly against my side. I felt a dull sense of relief when I noticed the rifle floating along beside her.

Then I stumbled again, almost knocking Starlight down.

My words came out slurred and muffled. “I… can’t…”

Starlight shuddered with a quiet sob. “Please.”

\leavevmode\llap{“}...Hide,” I mumbled. “There.”

She turned to where I was looking; a few large rocks just a hundred yards away, a few of many that dotted the landscape, and nestled in the crook of a tiny ravine. It was small and inconspicuous, and a pony would have to walk right on top of us to find us hiding there.

She pulled with her magic, pressing her shoulder against my side, and we slowly limped our way over.

We collapsed in exhaustion in the tiny hiding place, sprawling haphazardly against each other. For a few moments, we lay there, trembling and panting with exhaustion. My body was \textit{done}. Then Starlight’s breathing hitched, she shuddered, and finally rolled against me, hooves grabbing at me as she cried into my chest. I forced a barely-responsive foreleg to lift up and drape across her shoulder as she clung tight, muffling her anguish with my body. I caught myself starting to sob, and struggled to keep myself under control. Tears flowed down my cheek as I clung weakly to her.

I didn’t understand what had just happened. It wasn’t just chaotic; it was \textit{wrong}. This wasn’t some minor scuffle, or even a battle. It was ponies—\textit{ponies!}—ambushing other ponies, for… for what? The merchant’s wares?

I didn’t understand, and that, more than anything else, \textit{terrified} me. I had come horrifyingly close to dying, and I didn’t understand why. If I didn’t understand why, I couldn’t take action to avoid it. If I didn’t understand why, I was helpless against whatever cause had nearly killed me. All my life, all my training, all my experience, relied on understanding how ponies thought, but I could not understand the motivation for what had just happened.

If I was going to survive for long, I was going to need to learn, and learn fast.

But that was long-term.

Short-term, I was in bad shape, too. I was beyond exhaustion. Everything hurt. I could hardly lift a hoof to defend myself. My ears were filled with a strange buzzing, and everything felt lopsided. I was still terribly low on magic and lost in the middle of a barren and empty land.

The one thing I did have, however, was a \textit{pony}.

I didn’t want to hurt her.

I kept a hoof gently on the back of her shoulder as I focused a little bit of magic. Crying into my chest, she didn’t notice the flash of green above as a horn sprouted from my forehead.

I didn’t want to hurt her, so I took my time crafting the spell that followed. When I released the bolt, Starlight didn’t jerk at all. She just slowly went slack, relaxing against me as she lost consciousness.

My own vision wavered, my head growing even heavier as everything skewed and wobbled. The tiny effort I had given was exhausting, and for a moment I feared I would fall unconscious before I could act, but I clung on.

Then I pulled. This wasn’t the gentle, subtle feeding that comes from drawing on the love a pony feels toward something. Those feelings are at the front of their mind, drawing the energy out toward the object of their affection and leaving it exposed and vulnerable, easy to feast upon.

No, this was reaching deep inside of her, into the depths of her mind, and tearing out the love within.

She tensed, giving a little gasp and fidgeting in her sleep. Moments later she gave a weak, strangled cry, her legs kicking out.

I fed, and as the strength flowed into me, I tightened my grip. I held her head tight against my chest, muffling the whimpers and cries of anguish, her limbs weakly struggling against me. I could only imagine the horrible dreams that flooded her mind as I ripped the love and happiness from her.

I didn’t want to hurt her, but I did.