Some ponies seem to have strange misconceptions about changelings.

We feed on love, yes. To do so, we have to turn to other species, impersonating them as we secretly feast. We need to do this in order to live. So, while it is completely wrong, I can at least comprehend how some ponies think changelings can not feel love.

We can. We are not emotional cripples or mindless drones. We have likes and dislikes. We have friends. We have close personal bonds to those we like. We love.

What we don’t do is generate magic.

There is great magic to love and friendship. Ponies know that—or at least, they did once. When a pony loves, there is magic there. I don’t know why we’re different. I’m not a biologist, or a thaumatologist, or whatever kind of -ologist I would need to be to really understand the \textit{why} of it. All I know is that we can feed on those emotions, and in doing so, we consume the magic that is tied up within those emotions. We can even draw on another changeling’s store of magic by feeding upon their emotions, though it’s considered vile to do so without their consent.

My point is, we are not heartless monsters. That’s not to say we’re saints that can do no wrong; I’m certainly not skilled enough of an Infiltrator to pass off a lie like that, especially with the example some changelings have made. No, there are changelings who are every bit as cruel and vile as the worst ponies, but there are also those who are as kind and generous as the nicest pony.

Our situation has placed our species in conflict, but we’re not so fundamentally different as some would assume.

That knowledge has come as a terrifying revelation to many in the past, and I’m sure it will continue to plague the thoughts of others in the future. Some even find it so terrible that they refuse to accept it, no matter how plainly it’s staring them in the face. After all, It’s easier to see the world in black and white. It’s much harder to find yourself in conflict with a people you find you can empathize with.

I mention all this because I want you to understand how much I disliked seeing Starlight suffer, twitching and whimpering as she slept, and why I stayed with her, gently stroking a hoof over her mane as she trembled at my side, her rest punctuated by the occasional weak cry.

I liked her. I don’t mean as some serious attraction or anything. I don’t know if I’d even consider us to be casual friends. All the same, I found her to be generally nice and friendly, which had earned her a favorable opinion in my mind. And so, I disliked the pain I had inflicted on her, despite how necessary and correct it had been to do so.

Physically, I felt better than I had since before my long sleep. My muscles still felt faintly sore, but it had receded to a simple background sensation, soothed by the love I had consumed. It was no longer the crippling loss of strength I had been experiencing. Much of the love I had taken had already been burned up by my body, spent repairing whatever damage I had caused from my overexertion, but there was still a comfortable reserve. It was enough that I didn’t have to be quite so conservative with my magic.

A quick change had pushed a bit of that surplus toward improving my body, strengthening joints and muscles to something a little more appropriate for an earth pony. It was nothing major, nothing more than could be expected of a lean earth pony who had spent her life reading books instead of working, but I no longer felt dangerously frail. The improved muscles could hold up to the strain of traveling much better than they had before.

Despite my minor windfall, I did exercise some measure of rationing. I held only a modest amount of love, and Starlight wouldn’t be good feeding until she had recovered. So long as I was careful and kept her in good health, starvation was no longer an imminent risk.

Well, starving from lack of love. Starving from lack of \textit{physical} food was a little closer. Despite having several days of rations, I had no source of further food until we got to civilization. I doubted the edibility of the few dead or dying bits of brush we had seen. A lack of water was more concerning. I hadn’t rooted around in Starlight’s packs, but if she had no water on her, we needed to find some.

Maybe we’d get lucky, and the dark clouds above would start raining. I quietly cursed the lazy pegasi for no longer keeping weather to a neat schedule, like it should be.

I considered Starlight as she slept. She was young, barely into adulthood. As a unicorn, her lean frame was hardly surprising, but it wasn’t the stereotypical skinny of a bookish mare, or the slender grace of a model. She had the kind of athletic build I normally associated with pegasi.

The mane I was stroking was silver, like my own assumed form. Unlike my mane, hers was cropped fairly short, giving it a somewhat spiky appearance when it stood up from her head. She was in good health, with no apparent injuries, and only a little scuffed up and dusty from the hellish encounter we had escaped. Other than that, she was quite well-groomed. Her cutie mark, looking like a falling star or comet, was a mystery to me.

Mostly, though, I was concerned about her mental state. The change from enthusiastic and boisterous to sobbing into my chest had been sharp, and I worried that those other ponies had inflicted some irreparable harm upon her, even if she had escaped their blades and bullets.

I had put additional strain on her through my feeding, though not without reason. She could heal this injury, but if I had not fed on her, I’m certain I would have died.

I’d do my best to aid her, of course. “Valued livestock” means I tend to the ponies I feed upon, and I still had some hope of building some sort of longer-term relationship that could sustain me without such a drastic invasion.

Setting that aside for the moment, I reluctantly considered a new resource I had acquired: Sharps’s rifle. I have to admit, despite its contribution toward my survival, I disliked the device by its nature. It was large, extremely unsubtle, and spoke of a profound failure in finding less direct methods of achieving one’s goals. Still, it \textit{had} saved my life. If there were more ponies out there like the ones we had come across—a thought that still terrified me!—it may well save my life again. For the moment, I considered it an unfortunately useful survival tool, and as such, I needed to understand it.

I picked it up, releasing and removing the magazine. Setting it aside for the moment, I examined the weapon. Even without the magazine, the handle and bolt refused to move. I held it in one hoof as I depressed the trigger, which released the bolt, and I slid it forward to rest on the empty chamber. Surprisingly, the weapon producing a distinct “click” as it came to rest, which I guessed must have been the firing pin. That seemed strange to me, seeing as I was no longer holding the trigger.

A little more examination turned up a safety, which I engaged. The sights were simple metal posts sticking up from the side of the barrel, and the stock was a heavy piece of wood with a semi-circular base wrapped in rugged cloth. Otherwise, there wasn’t much to the weapon. It was extremely simple, and fairly heavy. I hoped that meant “rugged” rather than “cheap”.

Setting down the rifle, I retrieved the magazine and started removing rounds. The chunky box held eighteen of the things, and they looked as crude and basic as the rifle itself. The stubby bullets were large, heavy, round-nosed things, and were seated in a case that was not the usual brass I had seen before, but appeared to be thick, welded steel. I didn’t really know enough about firearms to know if that was significant, just that it seemed unusual.

I reloaded the magazine, and slid it back into the weapon. I only had two magazines, for thirty-six shots. I’d spent as many rounds escaping from those other ponies. I found it extremely strange to be in a situation where I wondered if thirty-six bullets would be enough.

It occurred to me then that I had tried to kill a pony. And I do mean “tried”, as I’m reasonably certain that I hadn’t actually hit any of the ponies I had shot at, barring some freakish stroke of luck. But still, I had pulled that trigger fully intending to end the life of a pony.

It was a topic that I had considered before, during the long, idle times I had spent in Appleloosa. Other, more experienced Infiltrators were occasionally given missions that required more direct action, and that sometimes would include the “neutralization” of a pony whose actions impeded the goals of our hive. Being an assassin did have a certain air of power and prestige to it, so it wasn’t surprising that many Infiltrators idly pondered what their life would be like if they were to receive the order to end a pony’s life.

And honestly, most of the very few ponies our hive targeted were the kind of scum it would be hard to feel sorry for. Ponies who helped drive their own nation into darkness for their own ambitions. I’ve come back to the subject many times as I thought things over, and every time, I’ve come to the conclusion that what we did was right.

Fact is, if we’d been a bit more aggressive in our actions, it’s possible the megaspells would have never happened.

So I didn’t feel any sort of horrid shock or revulsion at my own actions. I was not troubled that I had tried to end the lives of those ponies. They had tried to kill me, and it was rational and reasonable to use whatever means were necessary to prevent that from happening. It was merely something to contemplate, an unexpected first for me, and one that led me to further contemplate my future.

The only thing that bothered me about it was in not understanding the motivations behind the ponies that attacked us. They had risked and lost the lives of at least one of their own to achieve a goal I did not understand. It seemed unlikely to me that the contents of that tiny caravan could be worth so much.

I was wrestling with the task of understanding their mysterious motivations when a shadow swept over me. I jerked with surprise, hooves clutching at my rifle as my gaze snapped upward. I caught the last flicker of feathers passing by, and a cold chill shot through me. Did those ponies have a pegasus out searching for us?

My surprised movement was enough to finally wake Starlight. She jerked as well, giving a whimpered cry before snapping awake, blinking at me. She continued to blink for a couple seconds, her breathing fast and panicked as she took in the situation. “W-Whisper?”

\leavevmode\llap{“}It’s okay,” I said, stroking her mane again. “We’re safe.”

\leavevmode\llap{“}Oh,” she said, relaxing slightly. Her gaze drifted off, her eyes dull. “Okay.”

\leavevmode\llap{“}But we need to get going,” I said. “I don’t want to stick around here. We need to get somewhere safer.” I didn’t want to mention the pegasus. We’d be much more visible in the open, but we didn’t have the option of waiting, and I worried that mentioning it would only scare her.

She wavered a moment, looking around. “Yeah. I guess we should go.” She rose to her hooves, her movements mechanical, and wavered slightly. She blinked several times, groggy and lost.

I stood as well, moving close to her side. “Should we go to Rust, then?”

\leavevmode\llap{“}Yeah,” she dryly intoned, looking down to her PipBuck. She stared for several seconds, her ears slowly drooping.

\leavevmode\llap{“}We’ll be okay,” I said, placing a hoof gently on her shoulder, but she cringed and pulled away, her ears drooping further, her tail between her legs.

So I changed tactics. I made a show of taking a deep and unsteady breath. I blinked several times, conjuring up the saddest thoughts I could find; an easy task, given the previous day’s worth of activities. Then I swallowed, speaking slowly and haltingly. “Thank you. For… for saving me.”

Starlight looked up, meeting my eyes, but her expression held a flicker of confusion before fading away. “I didn’t save you,” she said, eyes sinking down again. “I almost got killed. You saved me.”

\leavevmode\llap{“}No I didn’t,” I said, shuffling a hoof to add to my visual discomfort. “I just yelled. You fought off that other pony and got away on your own. I couldn’t even keep up, but you stayed behind.” I swallowed, a few tears starting to run down my cheek as I blinked some more. “You could have kept running, but you stayed for me. You dragged me to cover. If you didn’t, they could have seen me. They could have killed me.”

I gave a teary smile, my voice choking slightly as I added, “Thank you.”

She looked up to me again. The corners of her mouth trembled upward; a weak smile, but still a smile. It faded again a moment later. “I just…” She swallowed, blinking as her eyes watered up again. “I didn’t want to be alone again.”

I took that as a cue to step in and wrap her in a hug, and she returned it. “Well, you’re not alone,” I said. “I’ll stick right there with you. Together. We can do this.”

She pulled away again, but that time it was gentle. “Yeah,” she said, wiping at her eyes. “Yeah, we can do this.”

I smiled as I watched her getting her hooves under her again, and wiped away my own tears. “All right. So… which way do we go?”

She nodded, horn lighting as she lifted her PipBuck. “Rust is the closest town, and it’s that way.” She pointed roughly in the direction we had come from. “I don’t think we should go straight that way.”

\leavevmode\llap{“}Good thinking,” I said, though it was pretty obvious. Meanwhile, Starlight turned back and forth, still looking at the screen.

\leavevmode\llap{“}If we go that way,” she said, pointing again, off to the right of where Rust lay, “we can go through some rougher terrain. It’ll be a little slower, but… well, it’ll give us plenty of places to hide.”

\leavevmode\llap{“}Sounds good,” I said, nodding encouragingly. “Lead the way, I guess.”

She paused to eye me. “Are you sure you’re up for this? You’re feeling better?”

\leavevmode\llap{“}Yeah. I think the rest did me a lot of good.”

\leavevmode\llap{“}Right,” she said, nodding, and we set off, eyes darting about for threats.

She did have water, it turns out, though only a single bottle. We each took a sip, saving the rest for later.

As she tucked it away in her saddlebags again, I decided it was time for me to peel away some of my ignorance.

\leavevmode\llap{“}So. I lived on a farm all my life, and I really have no idea what’s going on out here.” I wasn’t entirely comfortable asking the question that followed, given her mental state, but I had to ask. “Do you have any idea who those other ponies were?”

I was surprised how hard Starlight’s voice was when she replied. “Raiders.”

\leavevmode\llap{“}And… who are raiders?”

\leavevmode\llap{“}They’re evil,” Starlight said. “They like hurting and killing and mutilating other ponies because they think it’s fun. They’re monsters, and I’m \textit{glad} I killed her.”

I reeled at the thought of that. I knew of some scummy ponies, thanks to my work, but enjoying murder? \textit{Mutilating?} I hoped that Starlight’s assessment was borne out of grief or bias. The alternative was horrifying. You might find a rare pony with such vile interests if you looked in the recesses of Equestrian history; great, vilified figures that tainted the world with their darkness before being defeated, often by the princesses themselves. But to have so many working together as to have a name, an entire \textit{category} of pony turned to the worst extents of depravity?

Her steps slowed slightly. “I’ve never killed a pony, before,” she said, her words quiet.

\leavevmode\llap{“}You did the right thing.”

\leavevmode\llap{“}I know,” she said, her pace resuming. “It’s just… I don’t know. Strange. Like, I’m glad that I killed her, but I feel like I shouldn’t be.” She looked to me. “Does that sound normal?”

\leavevmode\llap{“}You killed a pony, and you’re worried about whether it was the right thing and how you’re feeling about it,” I said. “That seems pretty normal to me. Maybe better than normal. You did the right thing, and you \textit{should} feel good about that.”

\leavevmode\llap{“}I guess.” She went quiet as we continued to walk. We crossed the railroad tracks we had walked along earlier in the day, a mile or so from where we had been ambushed. I kept glancing toward the sky for the pegasus I had glimpsed earlier. Starlight had stopped looking around, merely watching where her hooves were stepping. Despite my nervousness, I didn’t want to leave her in silence, and I still had a lot to learn.

\leavevmode\llap{“}So, I don’t really know much about the world, except what I read in a bunch of two-hundred-year-old books. What’s the world really like, now?”

\leavevmode\llap{“}Eh.” She shrugged a little, then gestured to the side with her snout. “It’s pretty much all like this.”

I looked around at the barren dirt and rock, with barely a hint of dead vegetation. “But this place was always a desert,” I said. “The old books I was reading talked about all sorts of other places. Forests, for example.”

\leavevmode\llap{“}Oh, yeah.” She gave a half-hearted nod, though her attention at least lifted from her hooves. “I guess I’ve heard stories. There’s some forests to the north, but I heard they’re full of poisonous plants and monsters mutated by radiation. And I guess there’s the swamps out to the east, near Baltimare. That place is supposed to be really bad.”

\leavevmode\llap{“}I see,” I said, although I wasn’t sure I did. “What happened?”

\leavevmode\llap{“}Megaspells,” she replied, as if that said everything.

\leavevmode\llap{“}But there are still ponies. Surely it can’t be bad everywhere?”

\leavevmode\llap{“}Oh, there are less-bad places,” she said. “I mean, most of the world is just barren. Just avoid any place that’s radioactive.” She frowned. “Or that has nasty wildlife. Or raiders. Or is poisonous. Or has collapsing ruins.” She sighed, kicking a rock. “Most of the world sucks.”

I was finding this less and less encouraging. I had expected more recovery after such a long time. “But ponies survived.”

\leavevmode\llap{“}Yeah,” she said, nodding faintly. “Well, those that were in the Stables. I guess everypony else died.” I hoped she was wrong; I wasn’t sure how accurate her knowledge of such old history truly was, but that was worse than our most severe predictions. “Well, plenty of the ponies in Stables died, too. I heard a bunch of them turned into death traps. Still, enough of them worked. Pretty much every pony you’ll find is here only because their ancestors lived in a Stable. Even the fucking raiders.”

I was done with learning about history for the evening.

{\br}%
We continued on, mostly in silence. The rugged terrain made our passage a bit slower, but we weren’t held back waiting on heavily laden brahmin. We made good progress, winding our way through ravines and valleys.

\leavevmode\llap{“}We should find a place to spend the night,” Starlight said some time later, looking at the screen of her PipBuck. “It’ll be getting dark in an hour.”

\leavevmode\llap{“}Shelter would be good,” I said, looking up. “I expect it’ll rain, soon.”

She nodded. “Looks like there used to be some mine just a couple miles thataway, with another small compound near the tracks. There might be some buildings we could hide out in.”

\leavevmode\llap{“}Lead the way,” I said with a smile. She weakly echoed the expression, though it still looked strained.

Half an hour later, we caught sight of buildings ahead, across a shallow valley. After two hundred years, it wasn’t much to look at. There were some water towers, one of which still stood, a half-collapsed coal tower, a long loading structure that had long since fallen onto the tracks it was meant to serve, and the skeletal remains of a warehouse. A short distance further up the slope were the burned-out remains of what had possibly been an office, and a dilapidated building that looked to have been the workers’ barracks. Separate from those were a pair of outhouses that shared the dubious distinction of being the most intact-looking structures of the lot.

Our destination in sight, we made our way toward the barracks. We were halfway up the slope to the barracks when the sound of wood smacking against wood came from ahead of us. We halted, both instinctively shrinking down toward the ground.

In the following silence, we could hear the dry earth crunching under hooves.

As quietly as I could, I unslung my rifle, biting down on the bit. Starlight followed suit, pulling out her pistol, all gleaming metal and faintly glowing blue gems. Then we went still again, waiting.

The sound of hoofsteps on the dry earth slowly grew louder, walking roughly in line with the ridge of the slope we were approaching.

A head came over the ridge, some twenty yards away. It was a unicorn, and one of those slender, graceful, model-like types, at that. Her coat was purple, and she sported a long horn, with a flowing mane of dark blue and violet that blew lightly in the breeze. I was just noticing that I didn’t feel a breeze when she shuffled her wings—and I locked up.

An alicorn. I was looking at an alicorn. It wasn’t one of the princesses—the color was wrong—but there was no doubt that it was, truly, an alicorn.

Starlight cringed back, brushing against me, and froze again.

The alicorn walked on, seemingly oblivious to our presence. Then she stopped, turned her head, and stared straight at the pair of us, blinking.

I flinched back. If I hadn’t forgotten to disengage the safety on my rifle, I would have shot at her. I worry over what could have happened to me if I had.

For several seconds we stared at each other in silence. We trembled, while she continued to stare, blinking, impassive in her expression.

Her ear flicked, darting one way, then moments later turning another. She broke her gaze—Starlight and I both giving a nearly silent exhale—and turned her eyes upward. A moment later, I caught the sound that had drawn her attention: the faint pattering of the occasional raindrop.

Without a word, or even a glance back our way, the alicorn turned and walked off toward the barracks.

The moment she was out of sight, Starlight leaped up, giving me a tug as she scrambled back down the slope. I didn’t argue, having no desire to be going \textit{toward} some strange alicorn. We hurried back down to the railyard as the darkness spread. I could see the curtain of rain sweeping toward us.

The rain hit like a wave. In the span of seconds, the occasional droplet of water turned into a solid sheet of rain, soaking us through. Visibility dropped so sharply that I could hardly see the cluster of ruined structures we were heading toward, not even a hundred yards away. Water rapidly pooled around our hooves, and we splashed through swiftly forming puddles as we made our way to the closest thing to cover: the partially collapsed coal tower.

A flash of light lit up our surroundings, followed almost instantly by a bone-rattling BOOM of thunder.

We reached the coal tower and stumbled into the darkness, panting and dripping. Starlight eventually got the light of her PipBuck on, letting us see the inside of the ruin we found ourselves in. The hopper of the coal tower had ruptured as it collapsed, its remaining coal forming a large mound while the body of the hopper shielded us. The rain hammered relentlessly at the metal above our heads, turning our sanctuary into a giant metal drum, punctuated by the occasional boom and rumble of thunder. The inside was filthy, but at least it was dry.

After a moment to catch her breath, Starlight looked back. “Do you think it followed us?” she asked, her voice barely audible over the pounding of the rain.

I shook my head, moving closer so we could speak easily. “She was walking away,” I said. “I’ve never seen an alicorn before.”

She shuddered and shook her head. “Me neither, but… I heard stories, from up north. They’re not ponies. Not like normal ponies, anyway. They’re like the worst of raiders and slavers, only—”

\leavevmode\llap{“}Wait,” I said, holding up a hoof. “Slavers? As in, taking slaves?”

\leavevmode\llap{“}Well… yeah? Why else would they be called slavers?”

I have to admit that it had been a pretty stupid question. To be fair, I had asked it not because I couldn’t work out the meaning of the word but because it seemed so utterly bizarre to me. Ponies didn’t take slaves. Well, they took prisoners, and they would rarely make use of those prisoners in somewhat questionable ways, but I didn’t consider that the same thing, because…

I shook my head. “Right. Anyway, you were saying?”

\leavevmode\llap{“}Uh… yeah, just, from what I heard, they’re like the worst of raiders and slavers, only they’re super-powerful and basically impossible to kill. Sometimes they foalnap ponies, sometimes they just kill everypony. I heard they even \textit{eat} ponies, and that some can get into your head and charbroil your brain!”

I slowly nodded. Something didn’t quite seem right with that, but it was all third-hoof information, and from a single source. Still… “So why did she just walk off?”

Starlight was silent, and eventually gave a weary shrug. “I don’t know. Maybe it thought we wouldn’t be entertaining? As long as it leaves us alone, I don’t care why. My head hurts and I want to sleep.”

Ponies terrified of alicorns. It seemed so strange, but I had to remind myself that, despite how the time had seemed like a long nap from my perspective, there were two hundred (and two) years of context I had missed. Given the sudden relevance of the subject matter, it was time to learn more about my missing years.

\leavevmode\llap{“}The only alicorns I’d ever heard of were the ones I read about,” I said. “The princesses. What happened to them?”

Starlight turned away. “They passed on,” she said, missing my look of alarm. So many fears and objections clamored for attention in my mind. Meanwhile, Starlight gestured upward. “They ascended. Became goddesses, watching over us.”

I had doubts, but to tell the truth, the stories I had heard of the princesses made them sound halfway there already. Moving the sun and the moon? That’s not normal. Clearly someone was still moving them. I suspected that the only part of Starlight’s story that was likely to be outright truth was that the Princesses of Equestria were dead, but the continued motion of the sun and moon gave the idea of their ascension some measure of plausibility.

Then again, the sun and moon had moved before Celestia and Luna came to Equestria.

Starlight had started to climb the pile of coal that formed the floor of our temporary housing. She wavered atop it, as if she were about to lay down, but halted. Lifting a hoof, she wrinkled her nose. Her hooves were already blackened by the coal. I once again found myself wishing for my chitin; cleaning hair and fur was a pain. At least coal stains wouldn’t show up too much on my gray coat.

Starlight pulled out her bedroll, laying it out atop the coal heap before laying atop it. She looked to me in the ghostly green light. “It’s a little small, but we can share this. If you want.”

\leavevmode\llap{“}Thanks,” I said, smiling as I approached, but I halted as a thought struck me. I lifted my medical box, popping open the lid. “Could you hold these in one of your bags for a bit?” I asked, showing the contents.

\leavevmode\llap{“}I guess.”

We shoveled my possessions into her bag, and I returned to the gap we had slipped into. The rain poured just outside, and I set the box just outside. I didn’t have to wait long before pulling it back, filled to the brim, though the box proved somewhat leaky. I drank as much as I could, and returned to Starlight.

She gave a dry snort, but drank as well. After filling her bottle, I set the box outside so we would have plenty to drink in the morning. When I returned, she had already brought out her blanket. She held it up for me, and I lay down beside her on the narrow bedroll.

We didn’t mind the cramped accommodations once night fell. The damp blanket did little to stave off the cold, and we spent the night curled up close together, sharing what warmth we had.

{\br}%
I spent the waking moments of the night thinking of alicorns.

It hadn’t been one of the princesses, but that didn’t tell me where she had come from. Had one of the princesses had a daughter? It seemed strange that, after so many centuries, one of them would choose to have a daughter, but it was hardly impossible. From the stories I heard, the Ministry Mare Twilight Sparkle had practically been like a daughter to Princess Celestia. Maybe she had gotten a taste for such things, and decided to have a child of her own. It would be funny if her child had turned out to have such a similar coloration.

Or was this another recently-ascended alicorn, like Princess Cadenza? And with that particular coloration? If her cutie mark had matched the pony I was thinking of, that would seem likely, but it occurred to me that, for whatever reason, the alicorn hadn’t had a cutie mark. That strange fact struck me as unnatural.

It was then that I had realized what I had seen.

I had just seen the legacy of the Ministry of Arcane Science.

There had been a program in that ministry to brainstorm the possibility of forcing alicorn ascension on a large scale, all under the administration of Twilight Sparkle. It was very hush-hush, but Equestria was never terribly good at proper security practices and procedures. I hadn’t heard many details about the program in the information that crossed my path, but I had been under the impression that it hadn’t progressed past feasibility studies.

What I saw that day suggested that they had progressed much further than that.

Despite the lack of a cutie mark, that coloration led me to wonder if I had just met an ancient and immortal Twilight Sparkle.

As many things did those days, the thought terrified me. I had heard horror stories of what happened to changelings that fell into the hooves of the M.A.S..

I did my best to push the thought from my mind and sleep.

{\br}%
While the rain did not cease by morning, it had at least relented enough that I could downgrade my assessment of the downpour from “torrential” to merely “heavy”.

We had a quick breakfast, where I split a ration with Starlight, and she split a snack cake with me. I had rarely indulged in the cheap, packaged snack cakes in the past, being sad alternatives to the real thing that I could easily acquire from any nearby bakery. It tasted exactly as I remembered, though I wasn’t sure if that was a testament to the amount of preservatives contained within them or a simple indictment of their taste even when new. Either way, the sweet and vaguely fruity flavor was a pleasant contrast to the dull-tasting rations.

After retrieving my medical box and drinking our fill, we prepared for our outing. Starlight had decided her light jacket was completely unsuited to the weather we were facing, and set about resolving that. To that end, her blanket and bedroll were repurposed into crude ponchos. She gave me the blanket, pointing out that she had her jacket, and the bedroll was too narrow and thin to provide much warmth. The use of a few spare straps and a length of rope secured them to our bodies, and we were ready to set out.

At the narrow exit from our shelter, she halted, and we looked out on the landscape. The rain had turned the hard, dry ground to mud. A stream had appeared, muddy water flowing between the ruined buildings as it ran off the slopes above. The rain turned the distant terrain into a murky haze, a gray miasma that twisted an already harsh land into something oddly sinister.

Starlight pointed out through the downpour, toward the intact water tower. “I want to go there first,” she said over the rain. “I want to get up there and have a look around, see if that alicorn is still around.”

The structure was a good twenty yards high, at least, the rain coursing off of it. I eyed the long ladder dubiously. “I don’t know. It looks pretty slick.”

\leavevmode\llap{“}I’ve climbed worse than that,” she said. “Hell, it’s got a ladder.”

She set off before I could say any more, and I quickly followed. The blanket hung over my head, keeping the rain mostly out of my eyes, but water splashed up my legs with every step. I had just started getting used to being dry, too.

By the time I had reached the water tower, she had already started climbing. I wanted to huddle under the tower to get out of the rain, but instead I stayed back, crouching at the edge of the ruined structure that had once loaded the mine’s output into awaiting trains. I wanted to keep an eye out, not just for any potentially unfriendly ponies—though I hoped the weather would encourage them to stay indoors—but in case Starlight fell.

Fortunately, she did not, though she came down swiftly enough that, for a moment, I thought she had. I think I surprised myself when my reflex was to pull on my magic, intending to discard my disguise and catch her. Fortunately, I realized that she had hooked her hooves around the edge of the ladder and was sliding down, and stopped myself.

She hit the ground hard, spinning around. “Whisper!” she called out, immediately cantering over as she saw me. “We’re leaving.”

\leavevmode\llap{“}Did you see her?” I asked, scrambling to keep up as she passed me, our hooves splashing through the mud.

\leavevmode\llap{“}No,” she said. “Raiders! The ones that attacked us. They’re camped out at the mine!”

\leavevmode\llap{“}The same ones?”

She nodded hard, the bit of bedroll hanging over her head flapping in the wind. We hit another downward slope, silent for a moment as we skittered and slid through the slippery mud. We each fell to our haunches a couple times, but kept going. When we hit the bottom, we broke out into a trot.

\leavevmode\llap{“}You’re sure?” I asked, already panting.

\leavevmode\llap{“}I saw them,” she said, faring no better than I was. “I scoped out their camp. They’ve got Thunderhead and Sharps!”

\leavevmode\llap{“}What?” I managed to reach out, hooking a hoof over her shoulder, and we came to a halt. “What do you mean, they have them? I thought—”

\leavevmode\llap{“}They hung their bodies from the walls!” Starlight shouted. Now that we were stopped, I could see she was trembling. The rain hid it, but I was pretty sure she was crying.

My hoof fell away. I felt numb. Sure, she had told me of the horrific acts raiders committed, but it still seemed so obscene as to be unreal.

Starlight shivered, and I’m pretty sure it wasn’t from the cold. It was enough to jostle me from my own thoughts, and I stepped forward, wrapping her in a wet and slightly muddy hug. The trembles quickly faded as she held on, and after several seconds, she spoke again. “Whisper, we need to keep going.”

\leavevmode\llap{“}Right,” I said, releasing her and giving a weak smile. “Lead the way.”

We set off again, eager to be gone from that place.

{\br}%
We lay still atop the ridge, unconcerned about the mud that soaked into our coats. After the many hours of trudging through the unrelenting rain, it no longer registered with us. My body was halfway numb from the cold as we lay there.

I was also sore, once again. My legs ached from a long day of slogging through the mud. When I wasn’t fighting against the pull of mud that clung to my hooves with every step, I was scrambling to keep my balance as my hooves slid in the wet muck. Such slipping led to the occasional fall, further adding to our misery. I was pretty sure I weighed a good ten pounds more from all the mud clinging to my body, and the thick wool blanket might as well have been made of lead. I was already longing for the dry, dead desert I had first woken to.

At least we had plenty to drink.

And just for further insult, my neck hurt. My medical box and ammunition pouch were light, but after hours of walking, even their light weight was threatening to rub my neck raw. I’d even taken to wearing my rifle strapped across my back. It would be slower to get to in an emergency, but it was \textit{not} light by any measure. I’d have to look into getting proper saddle bags once I got to Rust; as much as the idea of settling down and never traveling outside of a nice, comfy town again appealed to me on that muddy, rain-thrashed hill, my journey to discover the fate of my hive would not let me rest there longer than absolutely necessary.

Ignoring the long-term goals for what lay immediately before me, I shifted the neck straps once more, then called out over the wind and rain. “What do you see?”

Starlight slowly swept her broken Lancer around, peering through the telescopic sight attached to its side. The rain had continued to abate, having settled into what I would consider a more “normal” rate of precipitation. In its place, the wind had picked up dramatically, chilling me even through the makeshift poncho.

\leavevmode\llap{“}I’m not seeing anypony,” Starlight said, and turned her scope back to the center of the valley before us.

The tracks ran across the open ground and passed through the remains of a tiny town, maybe a mile from where we lay. There was little still standing. The wooden water tower was collapsed and broken. Of the roughly two dozen structures that had comprised the tiny settlement, barely a quarter had roofs, and through the hazy mist of the rain it looked like few of those were intact. Most buildings were little more than empty foundations. The skeletal remains of a locomotive lay beside the tracks, stripped down by scavengers and abandoned.

Starlight lowered her Lancer. “Okay. Those are the same tracks we were on before. They’ll lead us right to Rust. If we followed them, we could probably get there around dusk.” She nodded toward the ghost town. “Or we could find some shelter in there, wait out the rest of the rain, and set off in the morning.”

I nodded. “As much as I’d love to get to Rust tonight, I’m pretty sick of this weather. I can barely feel my hooves.”

\leavevmode\llap{“}Yeah,” she said, slinging her Lancer across her back and rising. “Okay, let’s head in, see if there’s any good shelter. And keep your eyes open. There’s probably not any salvage left, but there could always be something dangerous in those buildings.”

I nodded, pulling my rifle from my back to hang at my chest, ready to grab. Starlight checked her holster, and we set off.

The wind pushed against us as we walked, the ghostly forms of the ruined town slowly drawing closer.

What had once been the main—and really, \textit{only}—street of the tiny town had been reduced to a muddy morass, which gripped and pulled at our hooves with every step. We slowly made our way into town, past several gutted buildings. Anything of value had long since been removed. I trudged up to the first relatively intact building, peering in only to find that the inside had been stripped away. The roof had partially collapsed, crashing through the floor and into the cellar. No furniture remained. It didn’t even have a front door. It would give minimal shelter at best, but anything was better than remaining outside.

Starlight continued on, leaning against the wind, and I moved on to the next building. She eventually halted before one of the last buildings, a small shack, and lifted her PipBuck to look at the screen. After a moment she lowered it again and stood there, frowning. Unlike the other buildings, the shack actually had a door.

I finally caught up, ducking my head to keep the wind out of my eyes. “What’s wrong?”

\leavevmode\llap{“}Nothing, I think,” she said in reply, squinting at the door. “Just wondering if there’s anypony home.”

I considered that for a moment before deciding that there was a very simple way to find out; I stepped up onto the decaying porch and gave three firm, loud knocks.

I hoped that, if there really was somepony living here, they might overlook the mud I had spattered across their door.

There was no answer. Starlight moved up to the structure and tried to peer in the window beside the door, but it had been boarded up. She turned to look at me and shrugged.

I gave the door a push, but it rattled and refused to open. After giving it another couple wiggles, Starlight found a catch at the top of the door. She pressed it, and the door swung open under the force of the wind. Then she lifted her PipBuck again, flicking on its light to illuminate the dark room beyond, while I bit down on the grip of my rifle.

It was cramped and full of debris. A broken-down couch was shoved against one wall, its cushions badly torn and stained. Some old, rusty tools were laid out atop a rickety table, while a large heap of bones filled most of the space beneath it. There were probably a dozen skulls among the bones, at least two of which looked to be pony skulls. There was trash everywhere, covering shelves, chests, and scattered across the floor: old, empty bottles, crumpled wrappers, mangled food cans, empty pill bottles and potion vials, discarded injectors, and all manners of other detritus. It looked like somepony had used the shack as a trash heap.

The building seemed to have held up well enough. There were only a few steady drips from the roof above.

Starlight looked to me, and I shrugged. After a moment’s consideration, she slid out her pistol and slowly stepped inside, the shadows twisting as she moved. I followed, the door behind me thumping against a pile of junk with each gust of wind. Starlight moved various heaps of debris, thoroughly searching the room before declaring, “Looks like there’s nopony hiding here.” I turned to close the door as her nose wrinkled up. “Oh, Luna, this place reeks. This isn’t a home. Somepony was using it as a dump!”

I hadn’t even noticed, but with the threat of possible combat passed, I finally registered the smell of decay permeating the air, with the lingering background hint of urine. I almost left the door open, just to see if we could air the place out, but I judged the smell to be less troublesome than the cold and shut it anyway.

Satisfied that there were no lurking threats, and with the fury of the storm muted by our questionable shelter, Starlight holstered her pistol, and we started poking around through the heaps of junk. Most of it was utterly worthless, but I found a couple bottles of cola, and a box on one of the shelves contained a mix of all manner of drugs. There was quite a variety there, with no particular theme or organization. There were a wide assortment of bottles, tins, inhalers, and injectors, running the gamut of medical, recreational, enhancement, and even combat drugs. Jostling the box to shift the contents around—I didn’t dare reach in when I saw several uncovered needles—showed that many were partially empty, but there must have been near a hundred doses of various pharmaceuticals in that box.

I set the box back on the shelf, contemplating its contents. I had no idea what sort of market, cultural, or legal changes might have occurred over the past two hundred years, but if the prices of various drugs had remained anywhere in the vicinity of their prices from before the megaspells, that was a rather valuable box. Also, exceptionally illegal, though recent events had led me to doubt the efficacy of any remaining Equestrian law enforcement agency.

\leavevmode\llap{“}I found food,” Starlight declared, drawing my attention to the chest she had pried open. A variety of old, heavily preserved food-like substances filled the case, many of which bore colorful wrappers showing what real food they were a shallow imitation of. A few had been opened and partially eaten, and what had once been an antique apple-flavored “pie” was now a gelatinous lump of mold. Still, there were almost twenty unopened packages, plus several bottles of water.

Starlight’s nose scrunched up again as she eyed the former pie. “Well that’s disgusting,” she muttered. “Not sure why somepony would leave all this here, but screw ‘em.”

\leavevmode\llap{“}I’m not so sure they just left it,” I said, looking over the contents, then glancing back at the box I found. “I think somepony is living here.”

She shook her head. “I’ve done a lot of scavenging. Stuff like that,” she said, pointing to the moldy pie, “takes months to go that bad once opened. Whoever left this stuff hasn’t been back here in a long time.”

Still, I felt uncomfortable. “I just don’t like the idea of taking somepony else’s stuff.”

\leavevmode\llap{“}Everything used to belong to somepony,” she said, fishing around in the chest to dig out a can of peaches. “Just some of them died a few centuries earlier than others.” She gave me a wry, humorless smile. “Welcome to the joys of scavenging. This is how ponies live when they’re not lucky enough to grow up on a farm.”

\leavevmode\llap{“}I… get that,” I said, sinking down to sit on my haunches, and ignoring how wet and filthy the touch of my own body felt. “It just feels like this might be less scavenging and more stealing.”

She frowned, looking over the can of peaches. I could practically see the silent battle being waged in her mind as she wavered back and forth, then finally sighed and tossed the can back into the chest. “Yeah, fine. We’ll leave the stash for whoever left it. We don’t really need the food that bad.” She was silent a moment longer before adding, “Though I might just check back in a few weeks. If nobody’s touched it by then, I figure it’s safe to call it abandoned.”

It felt to me like that was skirting a very blurry line, but at the same time, I had to admit that I lacked the perspective to give an accurate judgement. She had lived in the world I found myself in, and I was still fresh and new to it. I couldn’t be certain on her judgement, particularly given her dubious mental state at the time, but I couldn’t deny that she had experience I lacked. “That sounds fine to me.”

We shared a quick meal of our own shared food, splitting Starlight’s last snack cake. After one final short outing to a nearby ruin for certain biological necessities, we were quite happy to be done with the outside world, and shed our sodden and improvised garments. Only casual attempts were made to free ourselves of the mud that clung to our coats, stomping our hooves against the floor to knock most of it away, and wearily ignoring the rest.

Then it was time to rest. Despite the drippy roof, the shack held back the cold enough that we didn’t really need the sodden blanket. Huddling together on the saggy couch was enough to keep us warm. It wasn’t even that uncomfortable, despite how worn and smelly it was.

I must have just fallen asleep when the door slammed open with a blast of wind, followed by a loud and slightly muffled bellow.

\leavevmode\llap{“}The fuck are you two cunts doing in my house?!”

I jerked awake to find a hulking form standing in the doorway, silhouetted against the near-dark skies beyond. The voice was deep and gravelly, but also vaguely feminine, which made the pony seem all the more terrifying; she was \textit{huge!} And I don’t mean obese; I mean shockingly tall and stocky, almost bear-like in appearance.

Which, naturally, made the furious and profane outburst all the more frightening. “W-wait!” I shouted, raising my hooves as I sat up. “We’re not here to cause trouble! My name’s Whisper, and we—”

She stormed up to me, snarling, stomping, and clanking. In the darkness of the shack, the soft glow of Starlight’s PipBuck cast faint, glossy highlights on the metal armor that encased the giant mare, a pair of distant reflections coming from deep within the mask. A large, bladed horn rose like a spear from the forehead of the helmet.

I backpedaled, but there was nowhere to go. At the last moment, I realized my rifle was laying right next to me, but it was too late. The mare reared up, and two metal-clad hooves lashed out at me. With a sudden chill, I saw the pair of wicked, curving blades that jutted out over each hoof. Starlight cried out as they descended at me.

Instead of feeling those blades sink into me, I felt her mud-soaked hooves grab me by the chest and haul me up. She rose to her full height on her hind legs, lifting me up and slamming me back against the wall; the impact knocked my breath out and cracked one of the boards. My hindlegs kicked, dangling in mid-air as she she held me there. She kept me pinned by a single hoof as she raised her other hoof—and its attached blades!—menacingly. “Did I ask you your fucking name? What the—”

Her head snapped to the side as a faint blue glow joined the green. “If that gun so much as twitches, I’m going to \textit{fucking feed it to you!}”

Starlight stared back, wide-eyed and trembling. She swallowed, eyes darting from the menacing face-mask to the raised hoof and back. Then she slowly raised her forehooves, the magic around her horn—and the grip of her holstered pistol—winking out.

The mare turned back to me, her face pressed close. I could barely see the glint of light off her eyes, but I could see the snarl under her mask; while most of the helm was solid metal, her snout was covered by a thick-barred muzzle, like you might see placed on a vicious animal. That somepony would wear something like that, seemingly of their own will, sent my mind into a tumble.

She growled, her words faintly muffled by the muzzle. “Now answer the fucking question before I start tearing off limbs, little bitch!”

To back up her words, she raised her hoof to my face again. While my attention had initially been on the blades curving over them, the proximity gave me a clear view of the underside of the hoof itself. It was not a regular shoe as I had expected. Instead, the underside looked like the head of a meat tenderizer.

Don’t know what a meat tenderizer is? Ask a griffon sometime. It’s a mallet with a particularly vicious-looking grid of pyramid-like metal spikes. They use it to tenderize meat and lack any imagination for names.

At that moment, I had something much like that threatening to tenderize my face.

\leavevmode\llap{“}We just needed shelter!” I quickly sputtered. “We weren’t going to take anything, we just needed a place to get out of the storm for a night!”

The glints of light under the helm winked out for just an instant as the mare blinked at my reply. It was enough to give just a hint of overly optimistic hope—”Haha, I guess this was all just a big misunderstanding!”—but that was shattered when her snarl grew.

\leavevmode\llap{“}Does this look like a fucking hotel to you?” She punctuated the bellowing by pressing her hoof against my cheek, smearing it in mud, though I was far more concerned with the blade that hovered inches from my eye. Somewhere past the adrenaline, I was starting to notice how much the spiked hoof on my chest was hurting.

\leavevmode\llap{“}No, and I’m sorry,” I quickly said, cringing away from the spiked hoof. “We just needed a place to get out of the storm, and would have left again in the morning. We wouldn’t have intruded if we knew it was somepony’s home!”

\leavevmode\llap{“}Well now you know!” The hoof pulled back from my face, returning to my chest only for her to pick me up again and throw me across the room! Everything became a jumble; I was able to work out afterwards that I had struck the wall, bounced off the table, and tumbled to the floor. Reeling from the impact, I barely managed a groan before the hulking mare kicked my medical box, which pegged me right in the face with a hollow \textit{pang!} “So get the fuck out!”

She followed up by grabbing the next of our possessions to throw at me, which thankfully ended up being the wet blanket. I then ducked as she followed up by throwing my rifle out the door, and we scrambled to grab our belongings and get out. Starlight’s magic served her well, and she bolted out the door just in front of me.

Starlight immediately tripped and went tumbling, and I nearly fell off the porch dodging around her. The funny, light-headed feeling in my head didn’t help my coordination. Then Starlight screamed. I looked back to see her scrambling away from what she had tripped over.

It was a fishing net, full of severed pony heads.

\leavevmode\llap{“}Shut the fuck up with that screaming!” the armored mare shouted, grabbing the net and tossing it back into the darkness of her shack. “And if I see either of you cunts around here again, I’ll stomp your fucking heads in!”

She stepped back into the darkness and slammed the door. Starlight immediately grabbed up her belongings again, giving out a cry as she bolted, galloping away into the pouring rain. I quickly retrieved my belongings, snatching the rifle out of the mud, and hurried after her. She quickly outpaced me, limited as I was by trying to carry everything with one leg while running with the other three. Before long I was following her only by the glimpses of light from her PipBuck, flickering in the darkness.

Fortunately, she stopped just a minute later. As I drew closer, I could hear her calling out, her voice small behind the wind and rain. “Whisper? Whisper!” Her head was turning back and forth until I drew close enough for her to see, and she looked to me with wide, fearful eyes. She panted hard, trembling, but she calmed quickly as I approached. By the time I stood next to her, she had stilled herself, eyes closed and head hung as she panted.

\leavevmode\llap{“}Are you okay?” I asked, and her head snapped up.

\leavevmode\llap{“}I’m fine,” she quickly replied. She sat there a moment, giving only the faintest hint of a tremble, before pulling her bedroll over her once more. “I guess we’re going on to Rust tonight. We can’t stay around here.” She cast a glance back the way we came, her eyes betraying her fear. “Not with a raider living here.”

I have to admit, I had no desire to stay around a pony who seemed to make a habit of collecting ponies’ heads. Still, I looked up at the sky; there was only the faintest hint of light making its way through the clouds. In a few minutes, it would be near pitch black. Starlight turned on her PipBuck light, but its illumination struggled to pierce through the rain and gloom.

She looked around everywhere but at me, her ears drooping low as she secured her impromptu garment. I busied myself getting my own gear organized and the blanket draped over me. The ammo pouch bounced against my chest as I slipped its strap over my neck, and I winced at its touch. With the adrenaline fading, I was starting to feel just how scraped up my chest was from those spiked hooves. I silently cursed my fleshy assumed form with its lack of proper chitin as I carefully prodded at the injuries, revealing several long but shallow scratches.

\leavevmode\llap{“}You’re bleeding!” Starlight looked at me with ears perked once again, my actions having finally drawn her attention back to me.

\leavevmode\llap{“}It’s just a few scratches,” I said, lowering my hoof again; sympathy was nice and all, and very conducive to building up affection I could feed upon, but I had the feeling I should be gentle on her mental state at that moment. I could act up the pain to draw out more sympathy once we were safely to Rust.

\leavevmode\llap{“}That’s a lot of blood,” Starlight said, and I realized she was staring not at my chest, but at my face.

Touching my snout with my hoof made me wince again, the strange, numb sensation in my face replaced with pain for a moment. I gave a wet sniff, then immediately coughed as I tasted copper. “Jud a bluddeh node,” I said, holding a hoof to the side of my snout to stem the bleeding. “Ahm okah.”

She looked doubtful, but didn’t press the subject. Instead, she wavered back and forth, as if in silent debate with herself. Eventually she grumbled, “I’m tempted to go back there and shoot that bitch.”

I had to restrain myself from showing the shock I felt at that remark. I didn’t like where this was going, and I really didn’t like what the stresses of the previous days had done to Starlight. Sitting around the caravan campfire, I certainly wouldn’t have pictured that cheerful and exuberant young mare ever contemplating murdering another pony. Sure, it was a bit of a complicated situation, but it was still a concerning development. One that I’d certainly had a hoof in.

There was one point of comfort, however. She hadn’t declared that she would; she had raised the possibility, looking to receive validation from me. I got the impression that she shared some of my own concerns. Whether she consciously intended it or not, she was giving me the opportunity to steer her decision.

I lowered my hoof to talk a little more clearly. “I don’t know about that,” I said. “I think we’d be better off just hurrying on to Rust.”

She hesitated, and I could see her wavering a bit more. “...She’s a raider,” she said. “You saw that sack. She killed a bunch of ponies and took their heads. We’d be doing the Wasteland a favor.”

\leavevmode\llap{“}That was… concerning,” I admitted. “But I’m a bit wary of doing something so permanent without knowing what’s really going on. After all, she didn’t try to kill us.”

Starlight hesitated a moment longer, though her tense stance relaxed. “Even though she found us squatting in her home. Yeah. Fuck.” She gave another tug at her saddlebags before starting to walk, her expression downcast. “Let’s go. It’s still a few hours to Rust.”

Only a few seconds later, her walking slowed. “But what if those were ponies from Rust?”

\leavevmode\llap{“}Then at least we’d know what’s going on and who’s responsible,” I said, hobbling along on three legs as I carefully poked at my nose. I think the bleeding had stopped by then. “Though I doubt that’s what happened. If she just murdered a bunch of ponies in a town, I doubt she’d have any compunctions about doing the same to a couple travelers.”

The whole statement just sounded surreal to me at the time. I mean, I was talking about \textit{ponies} doing these things. Even with the recent memory of the raider attack, I found the idea of a pony being a mass-murderer and collecting a few dozen heads of her victims to be too bizarre.

\leavevmode\llap{“}Well if she did, I’m coming right back out here,” Starlight said, resuming her pace.

I nodded as I followed along. “Me too.”

We continued on, walking into the darkness.

{\br}%
Our way was slow. The feeble light gave us only a few feet of visibility in the downpour, and more than once we found ourselves backtracking to go around some sharp rise or rocky formation. The rare bolt of lightning gave us ghostly glimpses of the world around us, frozen in the flash of light. The rest of the time, our entire world was nothing more than a few feet of illumination in an endless darkness.

Not even the faintest hint of moonlight could pierce the heavy clouds above us.

We continued to slog on, our hooves dragging through the mud. Starlight was doing better than me; even with the improvements I had incorporated into my assumed form, she was still more fit than I was. My entire body ached, my eyelids drooped, and I silently stumbled on, following the bobbing, nearly hypnotic light of Starlight’s PipBuck. I had long since moved past being concerned about the cold and wet. I no longer noticed it, save for the soft, almost soothing sound of rainfall all around me.

I’m not sure how much time passed in that half-asleep state before an exclamation from Starlight brought me back to conscious thought. I raised my head, blinking the weariness from my eyes. Ahead of us, maybe a few hundred yards away, several lights faintly cut through the haze of the rain, dimly outlining the squared-off silhouette of structures.

Starlight consulted her PipBuck, then let it fall back to her chest. “We’re there. That’s Rust.”

I gave a weary, happy sigh. “Good. I’m about ready to collapse.”

As we continued to walk, I expected her mood to pick up. Instead, I saw her ears drooping lower, her eyes sinking toward the ground, her stance growing slack. “What’s wrong?” I asked.

She immediately tensed up again, mouth opening for a quick reply, but then she shut it again. The silent struggle ended quickly as she let out a low sigh. She came to a halt, her head sinking a bit as she looked on toward the dimly lit silhouette of our destination. “I just don’t know what I’m going to do now.”

I stopped beside her, our shoulders nearly touching. “What’s wrong with your old plan?”

\leavevmode\llap{“}What, being a guard?” She gave a weak, bitter snort. “Yeah, some guard I turned out to be. They’re all dead, and I couldn’t do anything to stop it.”

\leavevmode\llap{“}We were ambushed by a larger group,” I said, “but you still got both of us out of there alive.”

\leavevmode\llap{“}You did half the work,” she grumbled.

I almost sighed, but I checked myself. Instead, I saw an opportunity. “Okay, we did it together, then.” I gave her a gentle nudge on the shoulder. “And if we can get through that, I’m sure we can get through whatever comes next, together.”

She hesitated. I did not miss the poorly concealed look of hope in her eyes. “Together?”

\leavevmode\llap{“}Yeah,” I said, giving her a smile. “That’s what friends do, right?”

Her ears perked up. For a moment, she simply stared at me. Then, slowly, she smiled. It was the first genuine, wholehearted smile I had seen from her since the attack. “...Yeah.”

I reached out, placing a hoof on her shoulder, and this time, she didn’t pull away.

Smiling, we continued on to Rust. Together.