Appleloosa was a small town. Founded less than forty years before I had been assigned there, it hadn’t had the time to grow like some pony settlements had. Despite that, it had done well for itself. It had become an important place on the rail-lines of southern Equestria, grew to be a large supplier of food for the region, and had even started to industrialize.

Still, it was a small town. The kind of town that harkened back to its roots just a few decades earlier, when a small group of ponies built it from scratch.

Since waking from that chrysalis, I had seen only dust and decay. Equestria, it seemed, had fallen to ruin. Railways lay unused and unmaintained. Mines were abandoned. Towns had turned into ghost towns, and then ruins. To hear Starlight tell it, the land was harsh and inhospitable. There would be no bustling metropolises, no thriving towns. Given that, I set my expectations low.

It had been concerning to see that the town of Rust, set right across the train tracks, was entirely surrounded by metal walls comprised of toppled box-cars and scrap metal. Given the raiders we had encountered, we could hardly blame them, but it spoke volumes about how dangerous the land was outside that town.

We were eager to get in, but the massive iron gate blocked our way. We pounded on it, shouting over the rain and wind. Starlight waved the light of her PipBuck, trying to draw attention. Eventually she resorted to pulling out her pistol and firing three shots into the air, brilliant lines of light that flashed and sparkled in the rain. Less than a minute later, a pony in a rain poncho peered over the wall to see us there, waving.

It was another few minutes before the gate opened, the first pony having been joined by three others, all sporting firearms of one type or another.

We were ushered in, and I saw my first glimpse of the town of Rust.

I had set my expectations low, and I was still disappointed.

The muddy courtyard beyond the gate was lit by a pair of hanging lights and surrounded by various structures. Everything was made of mismatched pieces of metal all welded together. Many of the pieces looked to have come from train cars, but I saw parts of skywagons, sheet metal, and various building materials in the mix. The only thing that elevated it all above the level of “crude shacks” was the concrete bases they had made for several buildings. At least they had electricity.

But the town as a whole barely extended past that courtyard. There were only about twenty buildings, and while most were multi-story, there couldn’t be many ponies living there. It wasn’t a town as I thought of the term, but in the most technical of senses. It was a shanty town, poor and run-down, slowly rusting away.

We were guided into a nearby building, with everypony pausing under an overhang to shake off some of the rain before stepping in. It wasn’t much to look at. A pair of cots were set on one side, with several cabinets nearby. A crude desk and chair sat before the shuttered window, and behind it was a couch that looked like it must have been old even before the war. A bare lightbulb in the ceiling cast a sharp light across the room.

As we shuffled in, stomping the mud from our hooves, I got a better look at the ponies that had met us. They all had firearms—a rifle, two shotguns, and a pistol—and two of them wore heavy barding, with bulky, angular metal plates covering their chests and flanks. It was an unnerving display, but I had certainly seen the need for caution and protection lately. A pair of strangers showing up with guns in the middle of the night might not look entirely friendly.

Fortunately, they didn’t look on-edge about the situation. I can’t imagine we looked like much of a threat as we shivered, dripping wet.

One of the ponies, a tan unicorn with one of the shotguns and much lighter barding, seemed to be in charge, judging by the way the others would glance his way, following his lead. He was older than the two armored ponies, though not nearly so old as the one who had first spotted us. Once we were all inside, the unicorn stepped forward, shotgun pointed at the ground, and spoke in a casual, conversational tone. “Okay, no offense intended, but we’re going to have to hold on to your guns while you’re here.”

Starlight took a half step back. “These… these are very important to me,” she said, ears pinning back.

\leavevmode\llap{“}You’ll get them back when you leave, I promise,” he assured her calmly, though I noted at least one of the earth ponies tightening his grip on his bit. “We just can’t let armed strangers run around with weapons within the walls.”

That seemed perfectly reasonable to me, all things considered, and I unslung my rifle, passing it—stock first—to one of the other ponies. It wasn’t like I was in any position to argue the point, if they insisted. Starlight hesitated a moment longer before cautiously saying, “Okay.” She slid her pistol out of her holster, and the other unicorn took it in his magic. Setting it on the desk, he motioned to her broken Lancer. Her expression was pained as she hoofed it over, and for just a moment I could detect a faint trickle of love.

It joined her pistol and my rifle on the desk, and the atmosphere in the room relaxed considerably. Pistols were holstered and longarms were slung. The tan unicorn took a moment to brush his wet mane out of his eyes again, before casting a critical eye over us. “Okay. So, you mind telling me why the hell you two came pounding on our gate, in a storm, in the middle of the night?”

\leavevmode\llap{“}It wasn’t our original plan,” I said, giving a wry smile. It was hard to pull off, what with how my body was insisting on shivering. For some reason, stepping into the comfortable and dry room had reminded my body of just how cold it was.

\leavevmode\llap{“}We were in a caravan on the way here,” Starlight said. “We got hit by raiders yesterday. We barely got out alive.”

The tan unicorn stared at her for a second before his expression slumped. “Shit.”

One of the armored earth ponies, a pale-blue stallion, grunted. “Raiders have been getting worse.”

\leavevmode\llap{“}Yeah,” the unicorn said, grumbling, and looked to Starlight again. “Whose caravan was it?”

\leavevmode\llap{“}Long Haul and Silver’s,” Starlight said.

The unicorn’s eyes went wide, and he sank back to his haunches. “Goddesses,” he said, his voice weak. He just stared off into space.

The other armored pony, a bright red mare, whistled.

\leavevmode\llap{“}Time to raise the bounty,” the blue stallion muttered. “I’ll pitch in.” The red mare nodded, and the elderly stallion, still wearing his rain poncho, grunted in agreement.

The unicorn slowly nodded, his focus returning. “Yeah. Maybe it’s time to make it fifty caps. Ask around in the morning, see what we can scrounge up.”

There were a few nods, while Starlight asked, “Bounty?”

The unicorn slowly rose to his hooves again and nodded, though his voice wavered slightly. “Yeah. Raiders have always been a nuisance, and we take our protection seriously. Anypony who takes some of them out does us a favor, and we like to build a reputation for fair trade here in Rust. Somepony kills themselves a raider, they just need to bring us proof of the act, and we pay them.”

Starlight slowly nodded. “What do you take as proof?”

The unicorn reached up, tapping the side of his head. “The right ear. Cut it off and bring it here, we’ll give you forty caps for it. Fifty now, I suppose.”

If I weren’t halfway frozen, I would have blanched. Mutilating ponies for a bit of money? Even if they were bad ponies, the idea made my stomach twist.

\leavevmode\llap{“}Oh,” Starlight said. “So… I suppose turning them to ash is out, huh?”

The unicorn mulled over that for a moment, even glancing back to the armored ponies. The mare gave a half smile and a shrug. Eventually he looked back, sighing. “Afraid I can’t just take a stranger’s word on that. Tell you what, though. I’ll talk to Mustard, see if he’ll put you up for a couple nights, no charge. Figure you likely had to kill one of them bastards that got Long Haul and Silver if you two got out of there alive, and it’d be mighty unkind of us to not show some appreciation for the fact.”

Starlight smiled. “That would be perfect. All I want to do right now is find a good bed and sleep half the day away.”

\leavevmode\llap{“}As long as it’s warm,” I added.

\leavevmode\llap{“}I think we can do that,” he said, giving a half-hearted smile that quickly faded away. “So, what do I call you two?”

\leavevmode\llap{“}Starlight.”

\leavevmode\llap{“}Whisper Winds.”

He took turns shaking our hooves. “My name’s Steel Shot. Welcome to Rust.”

{\br}%
Starlight and I quickly scrubbed at our coats, letting the icy rain carry away the mud and dirt. We shivered and stomped our hooves as muddy water ran off the narrow balcony, cleaning as quickly as we could. We even took turns quickly wiping clean places we couldn’t reach well while the other stood there, trying not to shake too much from the cold.

As soon as we were done we bolted back into the room Steel Shot had arranged for us.

\leavevmode\llap{“}Holy \textit{shit} that was cold!” Starlight said, bounding over to one of the beds to pull off the blanket and wrap herself in it. I did the same with the other bed, and we both huddled up next to the radiator, greedily soaking in the warmth. I might not be quite so prone to profanity as many ponies seemed to be, but I agreed wholeheartedly with her sentiment.

\leavevmode\llap{“}At least we’ve got a nice warm room,” I said, tugging the blanket a little tighter around me.

\leavevmode\llap{“}Thank goodness for that,” she agreed, and we sat there, silent but for the chattering of teeth.

The descriptor of “nice” may have been a bit generous, if not for comparison to recent events. That’s not to say it was bad, though. Mustard ran what was essentially a hotel, giving ponies a place to sleep. At three stories tall, it was one of the largest buildings in Rust. The common room on the first floor gave cheap lodging to those who didn’t need privacy, while the second and third floor had a few rooms each. The three rooms on the top floor were the largest, and surprisingly, it was one of these rooms that Steel Shot had arranged for us.

Despite being one of the “best” rooms, it was fairly sparse. It was small, with just enough room for the two beds, a table with a couple of chairs, a pair of dressers, and the radiator that we were huddled in front of. None of that really mattered to me. It held the warmth in and the rain out, so I was hardly going to complain.

As the warmth slowly sank into our bodies, the shivers faded away, until we sat silently, side-by-side. Freed from obsessing over how cold I was, my mind turned to considering my companion, my lifeline in this strange new land I found myself in. Despite showing improvement, I worried about her.

She apparently had little resources of her own. When mentioning needing to find some way to earn a living, she had noted that she had little in the way of money. She hadn’t been paid for guarding the caravan, as that was going to be handled on their arrival in Rust. Other than a few days' worth of food, most of which was the rations I had found, we had little that could be traded for more money. The spirit of cooperation was all well and good, but even pooled together our resources were sorely lacking. If we couldn’t find paying jobs quickly, we were in trouble.

Given the size of the town, employment seemed like it would pose a challenge, and less savory methods of acquiring money and resources would be problematic at best. Theft was entirely out of the question. Even utilizing deception and misdirection, suspicion would naturally fall on the strange newcomers who arrived in the middle of the night. I didn’t mind having a good practical excuse to avoid theft, though. With how harsh the world appeared to be, I didn’t favor the idea of stealing something from a pony who might need it to survive.

Still, I had options that Starlight might not. Despite finding civilization, my survival over the next few weeks was far from ensured. Starlight, lacking my flexibility, was likely at even more risk. She might want to stay here in Rust, making a more stable life, rather than heading out into the Wasteland, risking everything. I, however, had no option of remaining there. I would stay long enough to recover and ensure my own safety, but soon I had to set out again.

But more than that, I figured the lack of resources, and the added drain I would be putting on them, had to be putting more stress on her at a time when stress was the last thing she needed. We might soon be facing the choice of selling off resources we wanted to keep—as much as I disliked the need for such a thing, I did not want to sell my newly acquired rifle—or setting out to find a living elsewhere, outside the safety of Rust’s walls.

All these concerns mounted, and it made me worry about how Starlight was taking things.

So I was a bit surprised when the first thing she said was, “I’ve never had a friend before.”

After a moment to reorganize my thoughts, I managed a smile. “I’m sure you’ll be surprised to hear I haven’t, either, what with growing up on an isolated farm in the middle of nowhere.” She shook slightly with a silent chuckle. “Still, I find that hard to believe. You seem so friendly and cheerful most of the time, it’s hard to imagine you’ve never made a friend before.”

\leavevmode\llap{“}Well, okay, there were a few others that I talked with, and I guess we were \textit{friendly}, but I don’t know if I’d really call them friends.” She relaxed a bit more, leaning against me. “At least… not like proper friends. There weren’t really any ponies my age where I grew up, and I didn’t spend much time in town. My mom and I were always out hunting or salvaging. I liked some of the ponies I met, but… I never really had the opportunity to have a friend.”

As we’d only known each other for barely two days, I felt the distinction she was making was perhaps a bit fine. Still, they had been two extremely eventful days, where our lives had depended on the other. It might be a bit quick, but I intended to prove her assumption correct.

I reached out, wrapping my foreleg and blanket around her shoulders, a silent reply to her statement. She didn’t say anything in return, merely leaning into the sideways hug. A tiny hint of affection met my senses. It was faint, but holding. I left it alone. Just as one does not graze on a seedling, I was not going to eat away at that nascent emotion.

We sat there, eyes growing heavy. At some point her head turned as she looked at me, and I felt her tense. “Those look bad.”

I followed her gaze to my chest, then raised a hoof to touch the deep scrapes in my chest. No longer numb from the cold, the wounds stung. Scrapes crossed all over my chest. The ones in the center, where the spiked hoof had pinned me against the wall, were the deepest. They were not so deep to as to be serious, although a few leaked a little bit of blood. “Eh, I’ll live.”

\leavevmode\llap{“}We should take care of those,” she said, pulling out from under my hoof as she faced me, looking closely at the cuts. “Don’t you have one of those magic-laced bandages?”

\leavevmode\llap{“}I’d rather save it in case of something serious,” I said. “This will heal up quick enough on its own.”

\leavevmode\llap{“}Yeah, unless it gets infected,” she said, reaching out to touch beside one of the scrapes. I winced, giving a short, soft hiss of pain. “Who knows what kind of gunk she had encrusted on those hooves?” Her expression tightened, ears standing alert. “She probably had pony blood on them.”

She remained silent and tense for only a moment before giving a decisive shake of her head. “No.” Her horn lit, levitating over her bags and pulling out supplies. “We need to clean out your wounds, get them bandaged, and give you a good dose of antibiotics to be sure. I don’t plan on losing my first friend to some infection.”

I thought she was over-reacting, but I relented. Given her earlier worries, it was probably worthwhile to give her something to feel useful about. “I take it you’ve done this before?”

\leavevmode\llap{“}On your back,” she said, motioning with her hooves as she pulled out medical supplies, and I complied. “And yes, quite a bit. I don’t know any of that fancy doctoring stuff, but mom made sure I knew plenty about basic first-aid. There’s all sorts of ways you can get scraped up when scavenging, and most of the things you can scrape yourself on haven’t been clean in a couple hundred years. Mom knew some other scavengers that lost limbs to some tiny cut that got infected.”

She lifted a foreleg up, wiggling her hoof and smiling. “You might not be able to tell, but I got scraped up plenty as a kid. Probably all sorts of tiny little scars all over my legs, just you can’t tell under my coat. Only reason I’m not scarred-up like some ponies is because we treated each and every scrape seriously.”

Setting her hoof down again, she leaned in and used her magic to prod at my wounds. I grunted and tensed, trying to stay silent. “Sorry,” she quietly murmured, though she kept going. “Wow. Yeah, there’s a bunch of dirt ground in there.” She sat back, looking at my chest as she quietly chewed on her lip.

Eventually she picked up a pill bottle, opened it, and retrieved a single pill. “Here, take this,” she said, passing it and the bottle of water to me.

\leavevmode\llap{“}Is this the antibiotic?”

\leavevmode\llap{“}Painkiller.” She gave a lopsided smile. “Sorry. This is going to suck.”

I sighed, but downed the pill.

\leavevmode\llap{“}I’ll give it a few minutes to kick in,” she said as she sorted through her medical supplies. In addition to a few bandages, she had medical tape, two bottles, another pill bottle, and a broken toothbrush. “Don’t worry, I gave you the good stuff. You might feel a bit out of it when it kicks in.”

\leavevmode\llap{“}If I feel any more out of it, I’ll be asleep.”

\leavevmode\llap{“}That might be for the better,” she said, the lopsided smile returning as she lifted the broken toothbrush. “This should have been done hours ago, so I’m going to be thorough. I need to get all the dirt and nasty crap out and sterilize the wounds.”

I looked at the toothbrush, recognizing what was about to happen. I really didn’t like the idea, but merely groaned as I laid my head back.

She let me rest for a few minutes, while I just lay there. I kind of lost track of time. Eventually I felt a tapping on my side. I lifted my head, which felt strangely heavy. I felt sluggish, and the whole world seemed just a bit further away. “You still with me?” she asked, and I nodded.

\leavevmode\llap{“}I think it’s kicked in,” I said, my words oddly distant in my ears.

She chuckled softly, rinsing her brush with a bit of fluid from one of the bottles, and then got to work. Even with the painkillers dulling my senses, having a brush jammed into a deep scrape and vigorously dragged back and forth was less than pleasant. I grunted, gritting my teeth, and did my best to remain still.

I didn’t actually see most of what she did. There was a lot of scrubbing, which left my chest feeling raw and wrong. I would have gladly reverted to my natural form just to escape the flaws of that flesh-covered body I had assumed, except then I’d probably have the dirty wounds on the inside of my exoskeleton. Instead, I simply endured. She eventually set the brush aside, wiping my chest down with a damp cloth. Then she dribbled something into the wounds that stung even through the painkillers, and again wiped with the damp cloth.

I’m not sure how long it was until she told me to sit up, a task that I, embarrassingly, needed help with. Once I was upright, she wrapped the bandage tightly around my chest. She remained there, helping to keep me from falling over as she floated over a pill. “Antibiotic,” she said, and I downed the pill. “And candy,” she added with a smile, floating a single piece of hard candy before me. I chuckled faintly, popping it in my mouth, and only barely stopping myself from swallowing it like the pill before it.

Sour apple. It was delicious.

\leavevmode\llap{“}And now we need to get you in bed,” Starlight said, nudging me lightly.

I didn’t move. “I think I’ll just fall down and sleep here,” I said, my words slurring together. I almost spit out my candy on accident.

\leavevmode\llap{“}Nope,” Starlight said, pressing her shoulder against me as she tried to get me up. “Bed rest means bed. Doctor’s orders.”

I relented, struggling up to my hooves. The ground swayed, and if not for her pressing against my side, I probably would have fallen. Despite all that, I found myself in a surprisingly good mood, with a lazy smile plastered across my muzzle as we slowly made our way to one of the cots. “I don’t think you’re a real medical doctor,” I said, the words mushy in my mouth. “Can I see your medical license?”

\leavevmode\llap{“}Sure,” she said, smiling beside me. “Just as soon as I pull one out of my butt.”

\leavevmode\llap{“}On second thought, I’ll take your word for it.” I finally flopped down on the bed. My candy fell from my open mouth to land on the cot beside me, and it took a couple tries before I managed to close my mouth around it again. I can only imagine Starlight rolling her eyes in reaction to my drugged behavior. I honestly don’t remember most of what was going on. She brought me my blanket, and I think I tried to say something to her.

The next thing I remembered was waking up around mid-day, slow and groggy, with a worn-down piece of hard candy stuck to my cheek.

{\br}%
My assessment of Rust was marginally improved by seeing it in the light of day.

The rain had ended by the time I woke, apart from the occasional drip from high above. The clouds even looked a fair bit lighter. The town itself, however, was still soaking wet. The ground was all mud and deep puddles, while water pooled on any flat surface and dripped slowly from everything else. Even without the rain, everything was sodden and damp.

Fortunately, the shanty-town-like construction of Rust, with its multiple levels of structures, meant you could go from one end of the little town to the other without actually touching the ground. Sure, the metal walkways had their own share of puddles, and it wasn’t long before my fetlocks were soaked with icy water, but at least it was just water instead of mud.

The walkways were also dangerously slippery in places, though the rails set alongside the more elevated paths saved me from any serious falls. Each slip was accompanied by a pained sensation in my chest as that stupid, fleshy pony skin twisted and pulled at the wounds.

Daylight also let me see that there was a bit more to the town than I had first assumed. The town proper was just as small and compact as I had thought, but there was more beyond that. Quite a few train cars lay scattered about the tracks, victims first of some ancient derailment, and more recently of scavengers who had cut away entire sections of them. More notably, there was a large field full of crops set right next to the town, with a dozen ponies working among the plants. The crops appeared to be mostly corn and wheat, and the entire area was enclosed in a crude fence. It was a far cry from the farmlands I had seen before, even at Appleloosa, but it was the first significant vegetation I had seen since waking.

But at the same time, I couldn’t help feeling even more disappointed by what I found. Or more, what I didn’t find.

Even with the flurry of paranoia and propaganda, there had always been a certain feeling to pony settlements. The best comparison I can think of is living near a particularly prolific bakery, with the constant smell of fresh baking bread. You could feel the love in the air, as if it had soaked into the town itself.

Rust didn’t have that feeling.

Starlight and I had split up after breakfast, setting out to look for work. I had set my sights on Steel Shot, and was told that I could find him that morning in “the overlook”. The overlook ended up being the tallest point in town, an enclosed platform with heavy, shuttered windows, built atop another three-story building that served as both the town hall and Steel Shot’s home.

I climbed the rickety stairs into the platform. Inside, I found that the only furnishings were a pair of chairs and a mounted gun. The gun caught me off-guard, not for its presence, but for its size. I had paid close attention to Equestrian military technology, so I recognized it right away, even in its worn state: a “Model 1” heavy machine gun. It was a new weapon that they had started mounting on some military vehicles for field tests, intended to counter zebra combat robots and light vehicles. The texts and diagrams did little to prepare me for seeing it myself; even though I recognized the shape and design, I had never grasped the \textit{scale} of the weapon before then.

It was huge in every way. The bullets themselves were the size of the entire round for my rifle, but tapered to a point, and the tremendous casings flared even wider. Its heavy mount held it high enough that it could easily shoot out of the open windows, and could even be moved around if needed, if one were particularly strong. The combination of gun and mount probably weighed more than I did.

Honestly, it struck me as overkill, though I worried that I might be wrong.

Steel Shot was there, looking out over the town walls, as was the armored red mare from the previous night. She was in the middle of yawning as I came up, looking as if she had been up all night. They both gave me a nod as they saw me enter, and Steel Shot passed the binoculars to the mare before speaking to me. “Something we can help you with, miss?” Then, noting the bandage around my chest, asked, “You all right, there?”

\leavevmode\llap{“}Oh, I’m fine, thank you,” I said with a smile. “Just got a bit scraped up on the way here. I can’t complain, all things considered.” There was a flicker of a grimace in his expression, clearly understanding what I meant. “I also wanted to thank you, for putting us up for the night. It was very generous of you.”

\leavevmode\llap{“}Think nothing of it,” he replied, though his smile was halfhearted. “Mustard had plenty of open rooms, and I’m certainly not the one to be ungrateful to someone who’s been tussling with raiders.”

\leavevmode\llap{“}Nonetheless, I wanted to thank you,” I said. “It’s more than some would do. I also had something else I wanted to talk about.”

When he gave a curious raise of an eyebrow, I continued. “Well… since our caravan got hit, we don’t have much to our names. Just what we had on us at the time, which isn’t much. We’re not looking for charity, but we were hoping there might be some work we could do here, to earn our keep?”

The concerned look that crossed his face told me the answer even before he spoke. “We’re a small town, don’t really have a lot of work to be done that we don’t take care of ourselves.” Still, he thought on it for a bit before asking, “You any good with plants?”

\leavevmode\llap{“}I grew up on a farm, but I’ve never been any good at it. I could dig and water where somepony tells me, but other than that…”

He frowned and nodded. “Well, how about metal-working, then? Or mechanics?”

I shook my head. “Starlight might.”

He sighed. “If she does, we might be able to find a little work helping out here and there, but I doubt it would be very much. Sorry.”

\leavevmode\llap{“}No, it’s okay,” I said, giving a sad smile in reply. “Thank you for the consideration, at least.”

I suppose there was some meager consolation that it meant Starlight would have little reason to remain here when I had to leave.

\leavevmode\llap{“}Hey,” he called out, as I turned to leave. Looking back, he pointed out the window, toward the largest building in the town. “You might want to head down to the foundry. I can’t promise you anything, but maybe Scrap or Singe have some odd jobs you might be able to help with.”

\leavevmode\llap{“}Thanks,” I said. “I’ll go check it out.”

I descended the stairs again before making my way to the building he had indicated. It was almost as tall as Mustard’s place, but even as I approached I could see it was only a single level. The cavernous space had a large assortment of machines, the purpose of which I could only guess at. It looked almost like a factory, albeit one with rusted equipment and a leaky roof.

Yet as run-down and industrial as the place was, it had the one thing the rest of Rust lacked; it \textit{felt} like a pony’s place. It felt like somepony had spent a life of love and happiness there. It was the first place I had found since waking up that felt \textit{right}.

I entered, shielding my eyes against the sudden flash of sparks. A red-coated mare that looked to be Starlight’s age was cutting into a gutted skywagon that hung in the middle of the chamber. She sat on its roof, cutting away with a torch.

\leavevmode\llap{“}Look out below!” she called out a moment before the shower of sparks ended, and the side of the skywagon fell free. I jumped, ears pinning back at the deafening clang of several hundred pounds of metal striking the concrete floor.

The mare was laughing as she lifted her face-mask, looking down at her hoof-work. Her grin turned even brighter when she saw me. “Hey, new-face! Whatcha you lookin’ for?”

I remember noting that she seemed to be faintly smoking. Judging by the state of her frazzled mane and coat, it seemed that was a common occurrence.

Taking a moment to roll my jaw and pop my ears after the aural assault, I replied. “Steel Shot told me to come here. Said I should ask around to see if anyone had any work they needed done. I’m kind of looking for a job.”

She laughed again before swinging down from the side of the suspended skywagon, hanging in mid-air for a moment before dropping to the ground. “Hah, he ain’t lookin’ to replace me, is he?”

\leavevmode\llap{“}No, I don’t—”

\leavevmode\llap{“}I’m kidding,” she said with a chuckle, and offered me a hoof that I cautiously shook. “He’d never be able to replace me. But anyway, work? I don’t know.” She released my hoof and turned, shouting out across the room. “Hey, Scrap! You got any work you need done?”

The head of a large blue stallion peeked up over a dividing wall. “What? I thought you needed to finish cutting up that stupid wagon?”

\leavevmode\llap{“}Not for me, dingus,” she replied with an exaggerated roll of her eyes, and motioned my way. “For her!”

He looked at me for a moment before dropping back below the wall. A few seconds later he emerged from behind the machinery, walking up to us with a curious expression. “What’s this about work, then?”

\leavevmode\llap{“}She’s lookin’ for a job,” the red mare said.

\leavevmode\llap{“}A job?” He frowned, cocking his head at me as he came to a halt. He was quite a bit taller than me. “I don’t know, not really much need for extra hooves, right now.”

I nodded, unsurprised by his answer. “I don’t suppose there’s anything I could do to help you with, in exchange for a few caps?”

\leavevmode\llap{“}I don’t know,” he said, raising a large, oil-stained hoof to his chin. “Maybe if you’re some super-genius mechanic, I could let you take a poke at the water pump. Other than that… heck, we need material more than we need hooves to work it.”

\leavevmode\llap{“}Oh? What kind of material?”

\leavevmode\llap{“}Scrap and parts, mostly,” he said with a shrug. “Machine parts, bearings, lubricants, new tools, gaskets. Heck, anything with rubber. Not so much electronics, but just about anything else. Well, except steel, we got plenty of that.”

\leavevmode\llap{“}Well… if I find any, I’ll let you know.”

I headed out, disappointed, and mulled over my options. Right then, I was still on the “survive” part of my plan. I needed enough love to search for signs of my hive, and that meant I needed some friends. There were plenty of ponies I could steer into friendships there in Rust, but I would need bits—sorry, caps—to live there. I had built up a friendship with Starlight, but she would need caps to live there, too. Without caps, she would have to move on, and I was inclined to go with her.

On the plus side, she had a past of scavenging, digging up relics of the old world. While it seemed she had set her sights on a new career, she might find that to be an acceptable way of earning the money needed to stay here. On the other hoof, it also would likely mean long periods away from town. I expected that the areas around any towns would have been picked clean decades ago. That meant longer trips, and fewer ponies to befriend.

But it also meant fewer ties to one place, giving me more freedom to go looking for my hive. If the ponies I fed on could accompany me during my search, that would ease things immensely.

I still wanted more ponies, though. Starlight could keep me alive on her own, but I’d put a fair drain on her simply surviving. Any excess magic use would put a potentially dangerous amount of strain on her, on top of the stress of regular travel. I needed more ponies, or I would be facing fairly sharp limitations on my own ability.

Just in case you didn’t know, changelings \textit{really} don’t like limitations.

I was still pondering these things, and meandering aimlessly around the town, when Starlight came bounding up to me. She was grinning. “I found us a job!”

I blinked in surprise, and smiled, though my thoughts had left me uncertain how to feel about the issue. “That’s great! What is it?”

She came to a halt before me, standing tall and proud as she declared, “Salvage!”

I blinked once again. “Uh, salvage?”

\leavevmode\llap{“}Yep!” She said, practically bouncing as she moved up beside me and leaned in, speaking in a hushed voice. “Met a guy who knows of a place that hasn’t been touched since the war!” She gave me a nudge. “Come on, he wanted to meet up with you before we settle on anything!”

I followed, trying not to show my uncertainty.

She led me to a building with an ancient sign that simply read “Food”, right across from a general store with a crude sign that read “Stuff”. The bottom floor of “Food” was part restaurant, part bar, and part grocery store. Wide windows encircled almost the entire building, the metal shutters raised to let in the light. It also let in the breeze. Fortunately, it had started to warm up once the rain had stopped.

Only a few ponies were inside, grabbing a quick lunch. Looking them over, I had a strong suspicion which one we were there to meet. My suspicions proved true as Starlight led me back to a grumpy looking yellow earth pony stallion by the back wall, nursing a drink. Judging from his demeanor, I assumed he sat there because it was the closest he could get to a gloomy back corner in the fairly well-lit room.

He saw our approach, eying me with a glower. I got the impression he didn’t approve of what he saw.

\leavevmode\llap{“}We’re back!” Starlight helpfully announced.

\leavevmode\llap{“}Uh-huh,” he said in reply, frowning.

My first impression of the stallion was not very positive.

Being one whose career was built primarily upon social skills, I decided to suppress the more natural reaction the cold welcome encouraged, and instead responded diplomatically. “My name is Whisper Winds. I’m afraid Starlight forgot to tell me your name.”

Starlight looked to me, looking quite amused. The stallion, however, was not. “Dusty.”

After coming to the realization that he was not going to continue, I spoke again. “I understand you had some sort of job for us?”

He continued to frown for a moment before replying. “I found out about a place. Problem is, I can’t find any pony worth a damn in a fight who’s willing to leave town, and I’m not going out on my own. So I’m just stuck here waiting, hoping nopony else finds my prize.” He paused to look me over. “And no offense, but neither of you look like the type that’s good in a fight.”

\leavevmode\llap{“}Hey!” Starlight snapped. “We can fight. Hell, we were in a big fight just a couple days ago. Got ambushed by raiders, but we made it through just fine.”

He looked between the two of us. “So you two were in the caravan that got hit.”

I nodded, and after a moment he relaxed, slumping back in his seat. “Suppose that explains where you two came from. Guess I’m not the only one having a shitty month.”

As much as I would have loved to make some sarcastic retort, since I was fairly certain he couldn’t even \textit{imagine} how bad the past few days had been for me, I instead offered a sympathetic response. “Yeah, that seems to be going around.”

He grunted a weak approximation of a laugh, but the disapproving glower had vanished. He even lifted his glass, tipping it in our direction before downing the rest of it. Setting it back down, he asked, “So what kind of combat experience do you two have?”

We sat down at the table, and Starlight grinned proudly. “I’ve gone hunting pretty much since I could walk,” she said. It wasn’t the first time I had heard her mention hunting, though it still seemed strange to me. Ponies don’t generally eat meat, though I suppose there was the occasional fish. One of the more disappointing parts of living among ponies is the excessively herbivorous diet.

\leavevmode\llap{“}I’m a great shot, too. Just… need to get my rifle fixed. One of the raiders broke it.” She smirked. “Killed her, though. Killed another one before that. Well, probably. I vaporized his shoulder, and I think part of his chest, too.”

\leavevmode\llap{“}Uh-huh,” he said, and looked to me. Starlight’s eyes narrowed.

I shrugged. “I’ve got basic firearm training, but that ambush was the only time I’ve been in a gunfight. All I managed to do was put out some suppressing fire while we retreated.” That sounded a lot better than aimlessly spraying bullets while running away. “Are you expecting a fight?”

\leavevmode\llap{“}No, but you don’t always have a say in that when you’re in the Wasteland, and I’m not going to go unprepared.” He slowly looked between us. “...And you’re not exactly inspiring much confidence. Raiders make for shitty soldiers. Most of them are pretty easy to kill. And you.” He gestured my way. “...You did at least \textit{shoot} guns during your training, right? Hell, you’re wounded.”

\leavevmode\llap{“}They’re just scratches,” I said, pulling down the edge of a bandage to show them. “The bandage is only there to keep them from getting infected.”

\leavevmode\llap{“}Fair enough,” he said, “but I’m not interested in putting my life in the hooves of ponies with no experience.”

\leavevmode\llap{“}Oh yeah?” Starlight said as she leaned over the table. “And how much experience do you have with scavenging, then? Or dangerous ruins? Do you have any idea what to look out for, or what kind of scrap is valuable instead of junk? I’ve been in and out of Dodge City more times than you can count. How about you?”

His expression didn’t show it, but I got the impression from the momentary pause that something she had said made him reconsider his judgement. His eyes flickered my way, and I quickly threw a bit more fuel on the fire Starlight had started. “And I know all about the old world and its tech.”

Starlight smiled again. “So you’re not just getting a couple ponies who can hold their own in a fight, you’re also getting a couple experts at scavenging to make sure you get the best prizes.” She leaned in even further. “And more importantly, we’re here, now. I know how rumors of big hauls spread. If you know about some prime loot, you can bet some other pony does, and you need to get there before they do. We can make sure you get all the juiciest stuff before anypony else.”

He looked away, muttering something under his breath, but considering her words nonetheless. I waited in silence until he finally looked back. “Two conditions,” he said, and Starlight immediately relaxed, grinning.

\leavevmode\llap{“}First, when it comes to a fight, you do what I say, right then, no questions asked. I’m used to dealing with professional soldiers, not hot-shot know-it-all mercs. You might have some skills, but you don’t have shit for experience. I do. Good?”

\leavevmode\llap{“}Yeah,” Starlight said, though I suspected she didn’t intend to uphold the agreement. I merely nodded.

\leavevmode\llap{“}Second, the split is fifty-fifty, and you’re not going to renegotiate that later, no matter what happens.”

\leavevmode\llap{“}No way,” Starlight said. “It’s a three-way split, nice and even. We’re the salvage experts, so we’re going to be doing most of the work.”

\leavevmode\llap{“}I don’t need you,” Dusty said, glowering. “The only reason I’m even considering you is because there’s nopony else around, and I need somepony to watch my back. I figure between the two of you, you \textit{might} add up to a single decent fighter. Hell, I wouldn’t even be bringing both of you, except I get the impression you’re a package deal. Am I right?”

Starlight gave a sharp nod. “Yep.”

\leavevmode\llap{“}Then you can either both come with me and get half of the loot \textit{I} lead you to, or you can both stay here and get nothing.”

The pair of them continued to glare at each other for several seconds, while I sat back and waited. Eventually Starlight wavered, glancing my way. I nodded, and she finally relented. “Fine. Since it’s your stake, you can keep half of it. But when it comes to salvaging, you do what \textit{we} say. Fair?”

He nodded, though he didn’t look happy about it. “Deal.”

They reached over the table, shaking hooves, and we all stood. “How soon can you two be ready to move out?”

I was going to say we were ready then, but Starlight spoke first. “It depends. Where are we going?”

\leavevmode\llap{“}Hah, no,” he said, frowning at her again. “You want to find this place, you’ll have to follow me.”

Starlight rolled her eyes. “Is it urban or rural? Are we going to need to be ready to climb up buildings? Are we climbing down? Is this above ground or below? Do we expect lots of locked doors? Robotic security? Radiation? Taint? Poison gas? Hostile wildlife? Is it likely to be booby-trapped?” She leveled a flat glare at him. “Or do you expect us to over-equip ourselves to account for every single possibility because you won’t give us basic information?”

I had to admit, I was a little surprised at the list of concerns she rattled off. It was perhaps a bit too blunt and confrontational, but it seemed to do the job, as Dusty sighed. “It’s an old Army depot, out in the desert. I don’t know what’s inside it, just that it has a few skywagons and a motorwagon inside the fence, and they supposedly looked in good shape. I figure if anypony else knew about the place, those would be gone or stripped, especially the motorwagon.”

\leavevmode\llap{“}Okay,” Starlight said, nodding. “Did you see anything else?”

\leavevmode\llap{“}I didn’t see the place myself. It was a merchant that saw it, maybe two weeks ago. He doesn’t like old ruins, so he didn’t check it out himself. Something about bad experiences. Anyway, he told me about it since I helped him out, and since I don’t have any better prospects, I figured I’d give it a look.”

Starlight was looking at her PipBuck; I saw she had switched to the map. “A depot in the desert. I’m guessing we’re heading east, then?”

Dusty narrowed his eyes, silent for a moment before replying. “Yeah. Now how does that matter?”

\leavevmode\llap{“}Because I’d like to make a detour,” she replied, letting her PipBuck fall back to her chest and smiling. “Gemstone is out east, and I’d like to stop by there.”

\leavevmode\llap{“}Why?”

\leavevmode\llap{“}Because my Lancer was made by a unicorn living in Gemstone,” she said. “I figure that’s the best place to look for someone who can fix it up.”

\leavevmode\llap{“}Hiring a merc with a broken gun,” Dusty grumbled, then motioned to her PipBuck. “Let me see that.” Unlike when she shared it with me, Starlight looked much more wary about sharing with him, and she kept a hoof resting atop it as he looked at the screen. He scanned over the map for a few moments before sighing again. “Yeah, I suppose. It’ll be maybe half a day out of our way.”

\leavevmode\llap{“}Good,” Starlight said, pulling back her PipBuck. “Then we’ll be ready to go as soon as we get our weapons back from Steel Shot.”

\leavevmode\llap{“}Okay, then,” Dusty said. “Get your shit. I’ll meet you outside the gate. We can still get most of a day’s travel in, and I expect you two to hustle to make up for the time lost on your little detour.”

\leavevmode\llap{“}You got it!” Starlight said, and turned to loop a foreleg around my shoulder and give a squeeze. “Come on, Whisper! Let’s get going!”

We separated from Dusty and hurried back to our room. Starlight seemed in such a good mood that I was reluctant to voice any concerns. She could really use the opportunity for some relief, I thought. Still, the concerns would not resolve themselves, and once we were back in our room, I had to address them. “So, do you think this is a good idea?”

\leavevmode\llap{“}What, the scavenging run?” She shrugged as she gathered up her belongings, left scattered about during her digging for first-aid supplies. “Yeah. I mean, it’s not exactly what I’d \textit{like} to do, but I’ve done it enough it’ll be easy going. We need caps, and if he’s really got a fresh claim, we could get a small fortune out of it.”

\leavevmode\llap{“}The money would be useful,” I admitted.

\leavevmode\llap{“}Yeah. Heck, the only thing I don’t like about the whole deal is how we’re only getting half a share each. Sure, I get that it’s his find, but still.” She shrugged. “Maybe we can get him to reconsider, later.”

\leavevmode\llap{“}He seemed pretty clear that he would not.”

\leavevmode\llap{“}Eh, sure,” she said, waving a hoof. “But we’ll see. I can be very persuasive.”

I couldn’t help frowning at that. She didn’t seem to want to let it go, but I couldn’t imagine Dusty would be very happy about her going back on our agreement like that. “How about this,” I said, hoping I might find a more amiable solution. “He seems to dislike you, so he’s probably going to be pretty defensive if you bring it up. How about you let me handle that part. I can be subtle about it, make sure he sees just how useful we really are without bringing up the matter of money directly.” That, or maybe making it my responsibility might distract her long enough to forget about the whole thing.

\leavevmode\llap{“}Hmm.” She thought on it for a moment, slowly smiling. “Yeah, that could work. Hell, he’ll see how useful we are once we get there, that’s for sure. Dumbass.”

I shook my head, but remained silent as we gathered up our belongings. My part was simple, especially when Starlight snatched up my medical box, loaded her own medical supplies into it, and stuffed it into her own bags. “We need to get you real bags once we get to Gemstone, so you’re not wearing everything around your neck.” She gave a little magical tug on her PipBuck’s strap. “It can get a little tiring, I know.”

\leavevmode\llap{“}Yeah, that wire isn’t a very comfortable strap. Thanks.” I smiled, and she beamed back at me. “Although why wait till Gemstone? Shouldn’t they have saddlebags in that store we saw? And we could probably use some ponchos or something.”

\leavevmode\llap{“}Nah,” she said, her nose scrunching up for a moment as if she’d bitten something sour. “I looked in there, earlier. If it’s not made of metal it costs a small fortune.” She shrugged, already back to smiling. “Besides, it shouldn’t rain again like that for weeks. Months, probably.”

\leavevmode\llap{“}Thank goodness for that,” I said, earning a pleasant laugh from Starlight.

A minute later we headed down. We thanked Mustard for his hospitality before heading back to the gate. Steel Shot wasn’t there, but another pony was, clad in the same metal armor that the other armored guards had worn. With our weapons returned, we stepped out of Rust, and back into the expanse of the Wasteland beyond.

Dusty stood by the side of the gate, a cigarette between his lips. He was certainly geared up; he wore thick cloth barding, a dirty brown, which completely covered his chest and limbs. Thicker patches were sewn over his knees, and a large number of pouches adorned the worn outfit, complemented by a pair of large saddlebags. A holster on his right leg held a pistol, binoculars dangled from his neck, and a rifle that looked very similar to my own was strapped across his back.

When he saw us, he frowned again, took a deep draw, and spit the butt of his cigarette into the dirt. “What, that’s it?” he asked. “Not even any barding?”

\leavevmode\llap{“}We like to travel light,” Starlight replied with a smug grin.

\leavevmode\llap{“}So much for needing the specifics for gearing up,” he said, giving Starlight a pointed look that she returned with equal sharpness.

\leavevmode\llap{“}What specifics?” she said. “All you even know about the place is that it’s in the desert. That doesn’t tell me anything I need to know to better prepare. I’ve got good basic gear to cover most common situations, and you’ll just have to be happy with that. Or do you want to front the caps for expensive specialist equipment we might not even need?”

Dusty replied with a roll of his eyes. “Your funeral. Just try not to make it mine, too.”

He turned and started to walk along the tracks. Starlight took the opportunity to pull a face and mockingly mime a few words behind his back before following along.

Myself, I simply hoped that our little outing would be over swiftly.

{\br}%
Traveling was much easier than our previous day spent in the Wasteland. We still had to trudge through the mud, but there was no rain or howling wind, and the air was a fairly pleasant temperature. Sure, we were quickly muddy up to our knees, but we weren’t soaked through and miserable. It was simply an annoyance.

Dusty led the way, eyes scanning around vigilantly, while we followed in silence. I felt some small comfort that he seemed to know what he was doing. It couldn’t quite make up for how his presence stifled Starlight’s good mood; every time she started to relax, she’d look at him again, and she’d go back to being grumpy.

It was a long walk.

We continued on, even as the sky started to darken. Dusty wanted to get every mile of distance we could out of the day, to make up for time lost to our detour, and I was inclined to agree. The daylight had almost entirely faded when we saw a point of light in the distance, miles away.

The strange thing was, it came not from the ground, but the sky.

The light fell slowly from the clouds, flickering in the darkness. Dusty halted, shaking the mud off his hoof before lifting his binoculars. A moment later he grimaced, ears perking upright.

\leavevmode\llap{“}What?” I asked, and he lowered the binoculars, eyes still tracking the falling light.

Starlight had unslung her Lancer, peering through the sight. “Oh, shit.”

\leavevmode\llap{“}What?” I asked again. This time, Dusty held the binoculars out to me.

I wiped off a hoof and took them. The light had descended most of the way to the ground, and another had fallen through the bottom of the clouds, casting its flickering light across their underside for a moment before falling away. I lifted the binoculars and sighted in on the second light. It took a few moments, the light flashing across my field of view a few times before I managed to find and track it.

The light was a pony, a pegasus, engulfed in flames and tumbling lifelessly through the air.

\leavevmode\llap{“}Oh.” My voice was barely a whisper as I lowered the binoculars.

A light was growing beyond the clouds, casting a soft, orange glow through them. The clouds started to bulge downward, then split open, a black blade tearing a deep wound in the sky. That blade was a sharp, angular prow, and the orange glow grew brighter as it tore its way free of the clouds. Lightning crackled through the remnants of clouds streaming from its side, and a great fire cast a glow across the Wasteland below as it was freed of the shroud of clouds.

A Raptor. A tremendous war machine, a cloudship, one of Equestria’s greatest weapons; there it was, two hundred years later, in its death throes.

I raised the binoculars again. I’d just settled on the prow of the cloudship, with the name \textit{Cumulonimbus} painted across it, when a gout of flame reached out from the clouds, striking the side of the falling ship. Something in the ship burst, exploded, tearing out a section of the ship’s side and throwing out flaming debris and shrapnel. A moment later I realized that some of that shrapnel was the ship’s crew, maimed or killed by the explosion to join their companions, tumbling toward the ground below.

I lowered the binoculars again, letting Dusty reclaim them. I didn’t need to see the gruesome details of the mighty ship’s demise. Instead, I watched from a distance as the failing cloud at its side gave one last bright flash of lighting and tore away. The ship’s struggle finally came to an end as it rolled over, its descent losing all semblance of control. A couple flashes of light reached up toward the clouds, the doomed ship’s gunners defiantly loosing a few final shots toward whoever had struck them down.

Dusty snorted faintly, letting his binoculars rest against his chest again. “Whole damn world’s going to shit.”

With that, he turned and continued walking. Starlight and I exchanged worried glances before silently following.

It was almost a minute later when the distant, thundering sound of the mighty old-world relic’s demise echoed across the Wasteland.