The Enclave.

For once, I was not the only one lacking in knowledge. Starlight hadn’t heard that name before, nor did she know anything about what the pegasi had been up to since the war. We both had much to learn as Dusty gave us what details he knew.

After seeing the devastation that had befallen the land, it was hard to believe that there was an entire nation up in the clouds, thriving so far as to still field mighty warships like the one we had seen—dozens of them, according to Dusty, and even several of the tremendous Thunderheads!

I won’t lie; I was tempted to abandon the wasteland of mud and misery to fly up to those clouds. It would be far easier to find an abundance of food in a safe, comfortable city in the sky than it would down here, surrounded by raiders and the constant struggle to survive. Still, I had reasons to resist that temptation.

If I were to find any sign of my hive, it would be down here, on the ground. Yes, if my hive still existed, I figured they would probably have Infiltrators up in the clouds, feeding on the ponies that lived up there. That didn’t help me. Infiltrators are intentionally hard to find, and even if I did somehow find one, there was a good chance she would not be a \textit{friendly} Infiltrator. If my hive survived, others might have survived as well, and we did not always get along. My path might eventually lead me up above the clouds, but for now it remained below them.

Of course, I could go up there to find food and safety—although the destruction of the Raptor made me question the latter—and return down to the ground once I was more prepared. That would mean leaving Starlight behind, however. If it came down to her or my hive, there was no contest, but between my own comfort and having both a source of food and a potential ally on the ground? That was a much more difficult quandary, but I had the feeling that keeping Starlight would be more beneficial to my mission.

Which was convenient, seeing as I’d feel a little bad about just abandoning her. I liked her.

But even if I decided to go above the clouds—not dying to raiders would be even more beneficial to my mission!—there was still one thing that troubled me: the Grand Pegasus Enclave was supposedly a thriving nation, and yet the ponies down on the ground lived in horrific conditions. How much love and safety could I find in a nation that would turn a blind eye to the suffering of their fellow ponies?

Dusty was particularly blunt in his evaluation.

\leavevmode\llap{“}They’re monsters,” he had said, taking a long drag on his cigarette. “They’re worse than the raiders. The Enclave, they make every single pony in the Equestrian Wasteland suffer because they just don’t give a shit about us. It’d make their cushy little lives a little less luxurious if they had to share with us on the ground. So instead, they just roll up the sky so they don’t even have to look at us. They stole the fucking sun and moon from us!”

He took another drag of his cigarette, scowling.

Starlight’s voice was small. “I saw the sky.”

Dusty’s scowl disappeared as he looked her way. She was looking off into the darkness. “One of those towers exploded,” she said. “This wave of rainbows tore open the clouds, and… and I saw the sun. I’d never seen the sun before.” She smiled, almost dreamily. “And that night, I saw the moon.”

A small smile crept up behind Dusty’s cigarette, and he gave a quiet, sympathetic nod. “I wish I could have seen that.”

\leavevmode\llap{“}You probably still can,” Starlight said, her smile holding even as she addressed Dusty. “The tower’s gone, and I don’t think the clouds are coming back. It’s just open sky, for \textit{miles}.”

\leavevmode\llap{“}May have to make my way over there after we’re done,” he said. His smile slipped away, replaced by a more thoughtful look. “Wonder if that’s what kicked the Enclave into making a move.”

When he was met by a questioning look from Starlight, he gave a dry, humorless laugh. “I’m guessing you don’t get the radio this far south if you ain’t heard of the Enclave. Yeah, they finally decided they’re going to get involved. Came down ‘bout a week or two ago. Said they were here to ‘save us’.” He snorted, flicking the butt of his cigarette away; the glowing ember spun off into the darkness. “So far, their version of ‘saving us’ has been to wipe out every single settlement they can get their hooves on. Fucking butchers, the lot of them.”

Starlight slumped, her ears drooping. “Oh…”

While they were having their little exchange, I listened in horrified silence. It was just… too much. Raiders attacking ponies to steal food at least made some sort of sick, twisted sense, even if it was hard to wrap my mind around. But a nation, living in relative comfort, coming down to the Wasteland and slaughtering the ponies they should be helping? “...How have ponies become so horrible to each other?”

Dusty looked at me. I expected a look of scorn for my naivety. Instead, I saw only sadness in his eyes. The gaze held for just a moment before he looked away, looking much more tired than he had moments earlier. “Wish I knew.”

On that cheery note, we turned in for the night.

Dusty took first watch, leaving Starlight and myself to sleep. It was then that we realized we still had only a single bedroll and blanket between the two of us. While there had been no hesitation before, when the shared bedding was a matter of survival, Dusty’s presence seemed to change the context of the situation for Starlight. I would have found some other course, to spare her the embarrassment of having our situation potentially misinterpreted, but I couldn’t see any way of doing so without one of us spending the night without a blanket.

Well, I could ask to use Dusty’s bedding while he wasn’t using it, but that seemed an entirely different sort of awkward. After working to prove ourselves competent traveling companions, it seemed counterproductive to announce that we had failed to acquire sufficient bedding for the two of us.

Fortunately, despite the blush she was trying to hide, Starlight was still gracious enough to raise the edge of the blanket toward me in a silent offer. I accepted, settling into the slightly too-small bed to sleep as best I could beside the fuzzy ball of awkwardness lying beside me.

{\br}%
We arrived at Gemstone around mid-day, despite Starlight’s attempts to divert us. “Think of all the salvage!” had been the core of her argument, combined with eager gestures made in the direction we had seen the Raptor falling.

\leavevmode\llap{“}Think of all the Enclave,” had been Dusty’s retort. “That wreck is going to be crawling. Even if it’s not the Enclave or whoever—or \textit{whatever}—shot it down, every scavenger and raider within fifty miles is going to be saying the same thing you are. They’re all going to go swarming all over it like vultures, and there’s going to be blood.”

\leavevmode\llap{“}But we could be rich!” Starlight said. “Salvage like that, we’d just need to hold onto it, and we’d be set for life!”

\leavevmode\llap{“}Sure we would,” Dusty replied. “‘Specially since that ‘life’ would probably be just a few hours.”

\leavevmode\llap{“}Hey, we can fight!”

\leavevmode\llap{“}I don’t care if you’re the best damn soldiers in the world,” he said, scowling. “Three ponies ain’t holding against what’s coming down on that, and we don’t want to be anywhere near it when it does.”

Starlight steamed over that for most of the trip, but she did finally relent. The argument that finally seemed to sway her was that, if everypony around was swarming toward the wreck of the \textit{Cumulonimbus}, there would be fewer ponies trying to make their way to Dusty’s claim. It wasn’t a particularly persuasive argument, as I could see it giving more reason why another detour wouldn’t hurt us, but she seemed to accept it.

In more pleasant and personal news, the bandages had worked their magic, and my scrapes had closed up. There was no sign of infection, though my chest still itched if I thought too much on the subject. At least I was free of the bandages. I like to make a good first impression, when possible.

Gemstone was nestled in a particularly rough and rocky patch of land, rising up into a string of jagged hills. An old rail line ran up a shallow slope to the base of what used to be another mining camp. Just beyond that, where the tall, jagged rocks formed a small valley, a wall of wood and steel formed the border of the town.

While still small, the initial impression the town of Gemstone gave was significantly greater than the one Rust had given. Mostly, that was from their fortifications; while the wall was nothing new or impressive, what was set atop it certainly was. Having considered Rust’s heavy machine-gun to be potential overkill, I was at a bit of a loss at how to categorize Gemstone’s defenses. The wall was topped by three emplaced magical energy weapons! The one in the middle appeared to be a multi-barrel plasma cannon, of the type one might have seen mounted to a sky-tank, and looking little worse for wear after so many years. The others I did not recognize, looking more hacked-together; they were crude-looking devices of tubes and wires built around large crystals, but I couldn’t say they looked any less dangerous to someone who found themselves in their sights.

Several ponies were idling atop the wall, with another visible in a tall tower set behind it. The pony in the tower was the first to see us as we approached the walls. She walked to the edge of her platform, calmly ringing a bell that hung there. It didn’t have the sound of an alarm, lacking any sense of frantic urgency. It was less “look out!” and more “hey, come look at this.”

The ponies atop the wall milled about, joined by a few more. Each of the three mighty weapons had a pony beside it, with two more ponies posted between them, though they all seemed quite relaxed. Given the amount of firepower they had at hoof, I could hardly blame them.

The earth pony mare by the plasma cannon was leaning casually against her weapon, eyeing us as we drew nearer. She eventually looked back, stomping a hoof and calling out. “Open up!”

With a few dull thumps, the gate slowly swung open. “Come on in,” the mare called out, sounding quite congenial despite resting against a giant machine of magical death.

We passed through the gate, into a small town built among the remnants of the old mining structures. Despite the somewhat run-down and pieced-together appearance, the town was refreshingly colorful after our stay in Rust. Somepony had discovered the invention of paint, and applied various colors to different buildings. Strings of lights and a few colorful signs accented the town. Past the mildly decrepit construction and the lingering mud, they gave Gemstone a true appearance of civilization.

And behind all of that, it simply \textit{felt} like a pony town.

The mare who had called out to us hopped down from the wall to join us, landing heavily before offering a pleasant smile. “Welcome to Gemstone. So what brings you three ‘round our way?”

Her heavy barding suggested that she was a guard, possibly Gemstone’s equivalent of Steel Shot, and the way she shook off the drop spoke well of her physical condition. That was put into strange contrast by her short but elegant purple mane and pristine white coat, both of which looked expertly cared for. She also wore a weapon strapped across her back, a rifle-shaped device made of polished metal and neatly bound wires, with a purple crystal at its core. It was a magical energy weapon, for sure, but not any pre-war design I was familiar with.

In fact, as I looked around, I saw that almost every pony in sight had a similar weapon. They were of different sizes and designs, but they were all similar in the basics of their construction.

\leavevmode\llap{“}Heard there was a pony here good with energy weapons,” Dusty said, taking the lead. “Was hoping to get some repairs done, maybe pick up some supplies.”

\leavevmode\llap{“}You could say that,” the mare said with a laugh. “You’d be looking for Arclight, then. He’s got the huge workshop right by the mine entrance, can’t miss it. Anyway, I’m Dazzle.”

She held out a hoof, and after pausing to wipe his own hoof off, Dusty shook it. “I take it you’re in charge here?”

\leavevmode\llap{“}Hah, nah,” she said, continuing down the line to shake our hooves as we introduced ourselves. “In charge of the guards, sure, but that’s about it. If anypony were in charge, it’d be Arclight or Emerald.” She paused to point to the nearest building, with its colorful sign. “Emerald runs the store and inn, you’ll meet her if you’re looking for supplies. Arclight brings in the trade, but Emerald’s kind of become the heart of our town.”

For just an instant, Dazzle’s expression flashed to one of searching suspicion, but it was gone a moment later as she smiled again. “Why, you looking for some sort of contract work or something?”

\leavevmode\llap{“}Nothing like that,” Dusty said, offering a dry smile that quickly faded away. “Just like to know where I stand. Tend to step on fewer hooves that way.”

Dazzle gave a soft laugh in reply. “Sounds good to me. If you go stepping on too many hooves, I have to get involved, and that’s a conversation we can both do without.”

Dusty nodded. “Agreed.”

\leavevmode\llap{“}Well, I’ll get out of your manes and back to my post,” Dazzle said. “It’s a small town, but if you need any help or directions, just flag down a guard or ask around, somepony should be glad to help.”

We parted ways after a quick goodbye, and made our way through town. Dusty left us alone, heading to the store while we headed further into town. Dazzle hadn’t been kidding about not being able to miss Arclight’s place; it was the one pre-war building still standing, some old workshop or warehouse, and easily the largest building in town.

On entering through the front door, we found that the place was absolutely packed with machines, workstations, parts, and several complete weapons. Despite the size and the sheer number of objects within the large space, there was only a single pony within. He was a young yellow unicorn, wearing the kind of head-mounted lenses I associated with jewelers. A loupe, I believe it’s called. It seemed particularly appropriate for him, as at that moment he was examining a pale-blue crystal. He paused in his work to flip up the lens and look our way, and smiled as he saw he had visitors.

\leavevmode\llap{“}Oh, hello there!” he called out as he stood, working his way through the crowded shop. “I thought I heard the bell. Did you come to do some shopping? Maybe a commission?”

Starlight drew in a slow, deep breath. “Actually, we were hoping to find somepony who could do repairs.”

\leavevmode\llap{“}Ah, yes! I do tune-ups and repairs as well, especially for my own—”

He staggered to a halt as his eyes fell on the broken weapon Starlight lifted in her magic. His mouth hung open as he sat, gingerly reaching out to take it in his hooves. “Oh,” he said, his voice hushed as he looked over it. “Oh, what happened to you?”

Starlight spoke quietly, as if following his lead. “We were attacked by raiders,” she said. “One tried to take my head off. She hit my gun, instead.”

\leavevmode\llap{“}Oh.” He looked to her, then back to the gun, nodding. “Well… better it than you, yes. Still…” He gently caressed the weapon’s length with a hoof. “It’s sad to see her in such a state. It’s rare that I get to work on a Lancer. My grandfather did such incredible work on these.”

\leavevmode\llap{“}Can you fix it?” Starlight asked. I think she was trying to remain still and calm, but I noticed her subtly shifting her balance back and forth in anxiety.

\leavevmode\llap{“}Maybe,” he said, focusing his attention on the point of damage, with its mangled barrel and crushed-in supports. “The lasing chamber is wrecked, but the damage is all in the housing. That’s the easiest part. Internal damage should be minimal, if any. Yes, I should be able to get her all fixed up.”

Starlight sagged in relief. “Thank you! I don’t have many caps right now, but I’m finishing a job in a couple days, and I should have plenty to pay for any repairs after that.”

Arclight frowned slightly, his eyes still fixed on the weapon. After a few moments of silence, he asked, “You said it was a raider that did this, right?”

Starlight must have noticed the change in tone, as her reply came hesitantly. “Yes?”

He slowly nodded. “In that case… well, I don’t think I’d feel right charging you.” To Starlight’s expression of confusion, he smiled. “My family’s got a policy. Well, several, actually, but the one I’m talking about is that anypony who takes one of our weapons from a raider can bring it here, and we tune and fix it, free of charge. It’s not quite the same, but… close enough, I think.”

\leavevmode\llap{“}That’s… very generous. Thank you.”

I couldn’t help but note the pause, as if Starlight was searching for some sort of ulterior motive. I couldn’t blame her; weapon crafting never struck me as a terribly altruistic profession.

\leavevmode\llap{“}My family has always made weapons to protect ponies,” Arclight said. “We don’t like the idea of raiders getting their hooves on our work and using it to hurt the ponies we’re trying to help, so we do what we can to prevent that.”

\leavevmode\llap{“}And you don’t have problems with people lying about where they got their weapon to get free repairs?”

Arclight swept several scattered parts off of a workbench, setting the Lancer down and gathering several tools. “Nah. Our weapons aren’t very common, and it’d be pretty obvious if a pony keeps “finding” the same gun. Might happen every once in a while, but I’m not really worried about it.”

Starlight finally smiled. “Well… thank you. That’s a lot more than most ponies would do.”

He shrugged in response, levitating several tools. “It’s just how we are, here. Gemstone’s a nice place. Besides, I couldn’t pass up the opportunity to work on one of my grandfather’s Lancers. I might be better at the practical side of making weapons, but I could never match his artistry.”

As he started unscrewing the outer frame, Starlight leaned in, watching intently. She chewed on her lip for a few moments before asking, “How long will it take to fix her up?”

\leavevmode\llap{“}Hard to say,” Arclight mumbled, eyes fixed on the weapon as he worked. “I’ve got to disassemble everything to see if there’s any internal damage. If there is, those will need repairs or replacement. Then I need to patch up the housing, seal up the chamber. And then it’s the long process of carefully tweaking and aligning everything so it doesn’t vaporize itself when you try to fire.” Detaching the base of the frame, he slowly slid it off, leaving the long barrel exposed. “We’re looking at at least a day of work, maybe two. More if the emitter or lens is damaged, since I’d have to fabricate those from scratch. Nothing I have now would match. These Lancers are pretty amazing, but they’re practically antiques, and incredibly finicky.”

\leavevmode\llap{“}Oh.” Starlight looked to me. “We can’t wait that long, can we?”

\leavevmode\llap{“}We can get it on the way back,” I offered.

\leavevmode\llap{“}Yeah,” she said, though hesitantly. She eyed the partially disassembled Lancer, a hint of that love cropping up once again. “I just don’t like the idea of leaving it behind.”

\leavevmode\llap{“}You’ll have to leave it with him, anyway. At least this way you won’t be sitting around, waiting for it.”

\leavevmode\llap{“}At least then I’d be nearby,” she said, but then she shook her head. “But you’re right. I… I guess we can do the job while we wait.”

Arclight had looked up from his work again. “Is there anything else I can help you with?” He looked to me in particular. “Maybe I could interest you in a better—uh, new weapon?”

\leavevmode\llap{“}I’m afraid I’m fairly poor at the moment,” I said, “but I may have to take a look at what you have when we get back.”

\leavevmode\llap{“}I’ll be here,” he said with a smile, though his attention was increasingly distracted by the weapon he was disassembling. I turned to leave, looking back to Starlight. She hesitated a moment longer, heaving a long, deep breath before turning to follow me out.

She remained silent as we walked down the dirt path, her head held low and eyes on the ground. It didn’t take a genius of psychology to tell that this was a big deal to her, or that she might need a bit of comfort and reassurance. “You okay, there?”

Her head snapped back up. “Yeah, I’m fine,” she said, and managed to do a halfway reasonable job of sounding it. “Why?”

I replied with a faint, uneven smile, measured to be gently comforting without seeming insensitive. “You care a lot about your rifle, don’t you?”

She drew her head back, mouth opening. I could see the denial forming, but she stopped herself, and after a moment, she sighed, head drooping again. “It was my mom’s. She gave me most of my stuff, even my pistol, but… but the PipBuck and Lancer were hers.” She swallowed. “They’re just… you know, important to me.”

I slowly nodded in understanding. “I know what you mean.”

Again her mouth opened to reply, a flash of anger crossing her expression. Again she stopped herself, her mouth closing again, and her expression softened again. “...Yeah, I guess you do.”

There was a long moment of silence that followed before she abruptly perked up, putting on a slightly too-large smile. “Anyway! Let’s go get you some saddlebags and stuff!”

I allowed her the sudden change of topic and followed along as she picked up her pace. It was a fairly short walk, and we soon entered the town’s only store.

That’s where we met Emerald.

My first observation of Emerald was that she was green. As in, \textit{excessively} green. She had a light green coat, while her long and flowing mane and tail were dark green. Her eyes matched her mane, as did her cutie mark, which was, as you might have guessed, an emerald.

This all came from a single second of observation as we stepped in the door of the shop to see her standing behind the counter, her forelegs crossed atop it. She was middle-aged, and possibly a bit on the lean side for an earth pony, but only a little. She was also looking right at us, a smile already making its way across her muzzle. “Ah, and you must be Starlight and Whisper,” she said, her voice soft and friendly. “Welcome!”

I should probably note that I have something of a dislike for ponies knowing more about me than I know about them. Dusty must have been talking, and I found myself worrying how much he might have said. I knew it was a mostly irrational fear, as he hardly knew anything about me, but some ingrained reactions can be hard to shake. I shot a glance his way, seeing only his flank as he looked over some goods, before looking back to Emerald.

With my momentary delay, Starlight spoke first. What she said, however, wasn’t a greeting, but an observation. “You have a PipBuck!”

I know that seems like something I should have noticed right away, but in my defense, it had only been a few seconds since I had stepped into the store. And let’s be honest, a pony’s legs are the last place you look when first taking in their appearance. Face, mane, and cutie mark, those are useful identifiers. If anything, I’d trained myself to disregard ponies’ legs. They were useful identifiers for changelings, but not so much for ponies.

As I reconsidered that order of priority, Emerald gave a momentary look of confusion before laughing softly. She had a nice laugh. “Oh! Yes, this old thing. Heck, I’ve had it so long I forget it’s there half the time.” She nodded to Starlight, looking to the PipBuck that hung around her neck. “They’re remarkably useful things, aren’t they?”

\leavevmode\llap{“}Yeah,” Starlight said, nodding in a way that I can only describe as “dumbly”; she was entirely fixated on the other mare’s PipBuck. “Are… are you from a Stable?”

\leavevmode\llap{“}Oh, no!” Emerald said with a chuckle. “I try to avoid those places. Nothing but trouble in most of them.” She patted the case of her PipBuck. “No, I found this beauty in my days of wandering, back before I settled down here.”

Starlight nodded again, her ears perking up. “You found it? So, um… you had to put it on?” Suddenly, her interest made perfect sense. “Do you have the tools or keys or whatever it is to unlock them?”

She had her hooves on the counter by the end of her question, leaning in with wide, eager eyes. I found myself saddened as Emerald’s expression fell. “Sorry, hon,” she said, giving a lopsided but sympathetic smile as she raised her hoof to show the backside of her PipBuck. “I’m afraid the one I found is kind of different.”

I stared in confusion at what I saw. Instead of the mostly blank plate that I understood to be the underside of a PipBuck, the backside of hers was dominated by a large, heavy latch. For whatever reason, her PipBuck was designed to be easily removed.

Okay, yes, it makes sense to design it that way. Semi-permanently bolting something to your leg always struck me as a poor idea, and I’m pretty sure that’s not simply a changeling’s natural aversion toward permanence. It just seemed more convenient to be able to remove it. If nothing else, I know how much of a hassle proper coat-care can be, and can only imagine how oily and grimy it must get under one of those things after a while.

No, what really bothered me was that I had never heard of Stable-Tec designing another model of PipBuck with a latch instead of a lock. I paid attention to stuff like that. There was never any press announcement or advertisement for such a thing, and if any Infiltrator had heard word of it, it hadn’t come my way. I suspect that meant noling knew of it, as PipBucks were a potential danger to Infiltrators, one we would surely be apprised of. A device that can detect hostile intent is a dangerous and scary thing to one who relies on subterfuge and deception.

That did leave the possibility of it being a post-war modification. Perhaps one of the Stable populations had gotten tired of needing to lock and unlock the things every time somepony wanted to take it off, or even just to transfer one onto a new generation of ponies?

I nearly missed the following conversation as I mentally grappled with how casually I had just thought of the many generations I had missed. Generations that had been born, lived their lives, and died, all while I slept.

While I quietly recovered from that thought, Starlight was withdrawing from her conversation. “Oh,” she said, her hooves returning to the floor, her expression crestfallen. “Uh, thanks anyway.”

Emerald gave her a sympathetic smile. “I can always keep my eye out for a set,” she said. “They’re not common items, but I’m good friends with a lot of traders. One of them might be able to find something.”

That glimmer of hope, as small as it was, was enough to turn around Starlight’s expression. “Thanks,” she said, with much more warmth.

\leavevmode\llap{“}Until then, is there anything I can help you with?” Emerald’s smile grew. “Need a place to stay for the night? Maybe some shopping?”

\leavevmode\llap{“}We can’t stay,” Dusty called out from the other side of the store, near a glass counter displaying various types of ammunition. “We’re moving out soon.”

\leavevmode\llap{“}No on the room, then,” Emerald noted, chuckling softly. “I take it you’re here for supplies?”

\leavevmode\llap{“}Yes, please,” Starlight said. “Whisper needs some new saddlebags.” Quietly, she added, “Also maybe a bedroll and blanket.”

I’m sure she thought she was being subtle. Unfortunately, the sudden change of volume was more likely to draw Dusty’s attention than it was to cause him to dismiss it. Sure enough, I caught him casting a glance our way.

\leavevmode\llap{“}Sure thing!” Emerald said with an eager grin, and quickly escorted me over to where a large variety of clothing and wearable items were displayed; despite the somewhat worn-down and generally post-apocalyptic look about the town, she had quite the inventory. Rows of shelves were stocked full of items, all carefully arranged and cared for.

While Starlight said I could get what I wanted, I was very mindful of the price. After a few moments of browsing, I eventually selected a set of small but sturdy canvas bags.

Emerald insisted I try them on, to make sure they fit right. I agreed, unslinging my rifle and setting it aside so I could do so.

I’m not sure which concerned me more about what that simple action said, in regards to the world I found myself in: that a store owner would show absolutely no reaction to one of her customers handling a very lethal weapon in close proximity to her, or that I had done so without even thinking anything of it at the time. Three days seemed far too brief a period of time to have become so accustomed to carrying such a weapon, but I’d taken it off and set it aside as if it were no more significant than a jacket. I really didn’t like that.

In any case, Emerald helped strap the bags on. “How’s that?” she asked, giving one of the straps a gentle tug. “Are they sitting well? Not too tight around the barrel?”

I rolled my shoulders and swung my hips, testing how the bags sat as I moved. “That’s good. It fits perfectly. Thank you.”

Emerald grinned upon seeing my smile. “Of course! Now let’s see about getting you some bedding.”

Soon I had a blanket and bedroll strapped atop my bags, and Starlight bought a few boxes of antique food, rounding out our supplies. Emerald didn’t stop there.

\leavevmode\llap{“}So, any other supplies I could interest you in?” She swept a hoof enthusiastically across the store. “Some ammo? Maybe some barding? It can be pretty rough out there, and I’d really like to see you all again.”

She spoke to all of us, but her smile seemed to favor Starlight. I’m not sure if it was because she was the one spending caps, or something else. Starlight appeared to believe it was something else, judging by the awkward expression and ensuing heavy blush. I made a silent mental note of that for possible later use. “I, uh… we’re kind of low on caps.” She rubbed one foreleg nervously against the other. “Maybe when we get back?” The light of inspiration brightened up her expression, abruptly chasing away her embarrassment. “Actually, we might be coming into a good deal of salvage soon. Is there anything you’re looking to buy that we could look for?”

Dusty turned from the display he was looking in. “We’re not coming back here. We’re getting the stuff, then heading right back to Rust. No more detours.”

\leavevmode\llap{“}We’ve got to come back here,” Starlight replied. “Arclight won’t be done fixing up my Lancer until tomorrow, so unless you’re wanting to stay here that long, we’re coming back through here. Besides, she might give us better prices for some things.”

She quickly looked to Emerald, who had raised a hoof thoughtfully to her chin. “Well now, I don’t know what kinds of prices they’re paying in Rust, but I can certainly try. I could sell just about anything, especially if it’s intact pre-war tech that doesn’t need repairs. Other than that, I’ll pay top value for any electrical components you might find. Arclight can always use more.”

\leavevmode\llap{“}Ugh, fine,” Dusty said, rolling his eyes in exasperation.

\leavevmode\llap{“}Wouldn’t that mean Arclight would pay more?” Starlight asked, as tactless as it was, but Emerald took no offense.

\leavevmode\llap{“}Nah.” She smiled. “It’s not like I’d be charging him for the parts I buy off you, so I don’t have to buy low and mark it up.”

\leavevmode\llap{“}Wait, you’d just give it away for free?” Starlight tilted her head, looking on with clear skepticism, which drew a laugh from Emerald.

\leavevmode\llap{“}Of course. Arclight’s business is the reason we get so many traders, so anything I can do to encourage that means more business for me.” She shrugged. “And besides, I’ve always had a thing for Kindness and Generosity.”

Now there were a pair of words that caught my interest. On their own, they might have just seemed like words, but paired together, and the way she had said them? The Elements of Harmony were heard of less and less as the war progressed, but here was a pony two centuries later, making casual mention of them. It was even more notable to me for being two of the Elements that seemed most alien to the Wasteland. Only Laughter seemed as far removed from what I had seen.

It made me very curious about what had happened to them.

\leavevmode\llap{“}Pardon me saying so,” Dusty said, intruding once more, “but ‘generosity’ is an unusual trait to find in a businesspony.”

Despite his bluntness, Emerald laughed again. “Or most ponies, it seems,” she said. “But that’s just how we try to be here in Gemstone. We’ve got a wonderful community, one that knows you don’t fight the Wasteland by embracing its ways. You fight the Wasteland by being better than it, by helping each other. Kindness returns kindness.”

I’ve got to say, I really liked the sentiment.

\leavevmode\llap{“}Be nice if the more ponies thought that way,” Dusty said. “Too bad there are so many who’d see kindness as a chance to buck your face in and steal all your stuff.”

Emerald’s smile turned mischievous. “I’ll admit, having an excessive amount of firepower thanks to our local weaponsmith makes the altruism a bit easier.” Her expression turned more serious. “But that’s all part of my point. Everything we have here is because we decided to work together, instead of just for ourselves. Sometimes that means giving a friend some free supplies or a warm meal. Sometimes it means taking up our guns to protect somepony. Sometimes it even means doing something nice for a stranger. We all do our part to make the world a little bit better for somepony else, and that makes the world a little bit better for us, too.”

The mischievous smile returned as she touched a hoof to the display case he had been eying, full of bullets. “So, ammo?”

Dusty gave a snort of amusement, but quickly returned to his frowning expression and shook his head. “I’m good for now. I guess we’re swinging by again later, so we’ll see then.” He looked toward Starlight and myself. “How many rounds do you two have?”

\leavevmode\llap{“}Enough,” Starlight quickly replied, which earned her a scowl from Dusty.

\leavevmode\llap{“}‘Enough’ isn’t a number.”

\leavevmode\llap{“}Okay, \textit{infinite} then,” Starlight shot back, matching his glare.

\leavevmode\llap{“}Bullshit. How much—”

\leavevmode\llap{“}Don’t ‘bullshit’ me, you colossal jack—”

\leavevmode\llap{“}Hey, hey! Calm down,” Emerald said as she stepped between the two. She didn’t raise her voice, but they both halted. She looked between the two of them. “It’s better to talk things out before assuming the worst about each other.” Her eyes settled on Starlight, smiling softly. “Could you tell us what you meant?”

\leavevmode\llap{“}What I meant—” Starlight’s angry retort died on her lips in the face of Emerald’s gentle smile. When she tried again, she spoke much more calmly. “What I meant was, my pistol doesn’t use ammunition.”

Dusty blinked. “What?”

I saw Starlight’s jaw tighten, but she managed to keep her voice level. “It’s a Recharger.” Her horn lit, and she slid the pistol from its holster, showing it off. I hadn’t taken a good look at it before, but I studied it then. It was a fairly sleek weapon, with a frame that held three angular barrels, each with a blue crystal at its base. A thick cylinder extended a hoof’s width from the rear, and I could see various wires snaking out from it, all nestled neatly behind the crystals. “It’s got a miniature spark generator or something. Holds about twenty or so shots, and it slowly recharges them.”

\leavevmode\llap{“}Huh,” was Dusty’s initial reply, which was rather more mild than my own response.

\leavevmode\llap{“}That’s quite impressive,” I said, earning a smile from Starlight. Possibly more impressive since I’d never heard of a pre-war weapon that did so. It did lead me to question why, however. All the pieces were there. Small spark generators were uncommon and fairly expensive, but the military seemed to spend so much money that I could hardly imagine it being a drain on its resources.

\leavevmode\llap{“}How long does it take to recharge?” Dusty asked.

\leavevmode\llap{“}A few minutes.”

He looked as if he were about to say something more, but his eyes darted Emerald’s way, and he quickly turned to me instead. “How about you? How much ammo do you have?”

\leavevmode\llap{“}Thirty six rounds,” I said, feeling fairly happy that I could give an exact number. Unfortunately, that number produced a grimace from Dusty.

\leavevmode\llap{“}Thirty six rounds for an automatic pipe rifle,” he grumbled. “Yeah, she’ll need more ammo.”

\leavevmode\llap{“}‘She’ can’t afford more ammo,” I said, staring back at him.

\leavevmode\llap{“}You can afford it a lot more than you can afford dying because you ran out in the middle of a fight,” Dusty replied, fixing me with a glare.

\leavevmode\llap{“}That won’t do me any good if I can’t afford to eat.”

Emerald cut in again. “I think I can solve those problems for you.” When we looked to her, she smiled. “You’re coming back through here for the gun she’s getting fixed up, right?”

We nodded, even though it seemed a rhetorical question.

\leavevmode\llap{“}So how about this: I can lend you some spare ammo for your trip, and when you get back you can pay for it then, or just return it if you didn’t need it. Sound good?”

I blinked, staring at her smiling face for a couple seconds. Dusty was staring at the back of her head with a deeply suspicious expression. I have to admit, I immediately felt the urge to be suspicious of her motivation as well, but I couldn’t see any tangible way that she could take advantage of us by giving us free ammunition.

That didn’t mean it wasn’t there, just that I couldn’t see it. The closest I came was the possibility that she planned on ingratiating herself with us in hopes of influencing us in the future, but that posed no meaningful threat when I could simply say “no”.

That, or she was truly genuine in her embracing of Kindness and Generosity.

\leavevmode\llap{“}That’s very generous,” I said, smiling softly. “Thank you.”

\leavevmode\llap{“}Of course,” she said, her smile brightening just a bit more before turning back to the ammo display and opening it. “Half-inch pipe rifle, is it?”

\leavevmode\llap{“}Uh…” I had no idea, but I did know that “close enough” wasn’t exactly a thing where firearm ammunition was concerned. I glanced helplessly at Dusty, who rolled his eyes and nodded. “Yes,” I said. “Yes it is.”

She started plucking items out of the case, while Dusty stared at me. He stared long enough that I was starting to get concerned, when he abruptly walked over to me and grabbed the barrel of my rifle.

I objected, but he replied calmly. “Oh, settle down. I’m just looking.”

I was \textit{not} happy with him tugging on an extremely lethal device strapped to my back. Neither was Starlight, whose “Recharger” pistol was again hovering beside her. Still, I restricted my reaction to merely glaring at him. “You could have asked.”

\leavevmode\llap{“}Yeah, I could have,” he said, pulling the barrel of the rifle around to look into the muzzle, though he had the sense to look into it from an angle rather than staring straight down the barrel. He frowned at what he saw, though it was a more thoughtful expression than a disapproving one. Finally, he released the barrel. “Well, at least you got one with rifling.”

\leavevmode\llap{“}It’s not like I had much selection,” I said, grumpily shrugging my shoulders to get the heavy weapon to rest comfortably again. “And seriously, ponies make \textit{rifles} without \textit{rifling}? That’s kind of an important part of a \textit{rifle}.”

\leavevmode\llap{“}Yeah, it is,” Dusty said. “But it’s also harder to do, so when ponies make cheap-ass weapons like yours, it tends to get skipped over.”

You know, I might not particularly \textit{like} the big, cumbersome, obnoxiously un-subtle weapon I was carrying, but I dislike hypocrisy even more. Despite that, I laced my voice with only a \textit{little} bit of irritation. “You’ve got the same kind of gun I do.”

Dusty turned away, a growl entering his voice. “Not by choice.”

I wasn’t entirely sure how to reply to that, as there was clearly something going on that I wasn’t quite seeing. I was distracted from him when I saw Emerald had finished rooting around, and three fresh and fully loaded magazines were sitting atop the counter. “Here,” she said, patting them with a hoof. “Might want to make sure they fit right. You never really know with that kind of gun.”

It was a reasonable concern. Standardized measurements in manufacturing probably went out of style with the bombs. I unslung my rifle again. While I busied myself with making sure the magazines all fit correctly in the weapon, Emerald turned to Dusty. “So, what happened?”

He looked back over his shoulder. “What?”

\leavevmode\llap{“}‘Not by choice’ makes it sound like something bad happened,” she said, her voice soft and comforting. Inviting.

He considered her, face contorting to a scowl, but it slowly relaxed. After a few moments of silence under her attention, he relented. “There was a pony I worked with, a while back. It’s always good to have somepony watching your back, right? Working together, and all that.” He snorted in disgust, looking away again. “We just finished a big job, one that would have set us nice and comfy for a good while. Fucker stabbed me in the back. Took all the caps and my rifle, and just split.”

Emerald nodded, silently.

Starlight’s reaction was far from silent.

\leavevmode\llap{“}What a dick!”

We all looked over to her. She stood wide-eyed and incredulous, and quickly turning toward anger. “You don’t know where he is, do you?”

\leavevmode\llap{“}No,” he said, though hesitantly. “Why do you care?”

\leavevmode\llap{“}Why?” she asked, as if surprised to be asked that question. “Because… because! You just don’t do shit like that!”

He grunted. “Yeah, well, they did.”

\leavevmode\llap{“}Well \textit{I} kind of want to kick his stupid flank,” Starlight said.

\leavevmode\llap{“}Sorry, I’ve got dibs on it,” Dusty said. I even saw a hint of a smile trying to make its way past his grimace. It didn’t last long as he quickly changed the subject. “Now if you two are done shopping, let’s go.”

He paused long enough to thank Emerald, then walked out of the store. I tucked the three gifted magazines into the pouch with the other one, and adjusted its strap so it sat across my shoulder instead of hanging from my neck. Meanwhile, Starlight paid for our acquisitions with a large part of our—and by that, I mean \textit{her}—caps.

Oh, yes. I believe that was when I found out what caps really were. I’ll spare you the lengthy ranting I could probably level at that discovery. Suffice to say, there were many things about this new world that I found to be strange, and the idea that ponies would use bottlecaps for currency was well up there on the list.

I refrained from making comment of it, and soon we headed out to rejoin Dusty, who was waiting just outside. It was a short walk to the gate, and we left with a wink and a wave from Dazzle, still lounging beside her cannon.

As we walked off past the remnants of the mining camp below the town, I couldn’t help looking back at Gemstone. I still had concerns that there was something seedy lurking under the surface. After the horrors I had seen since waking up, that concern was hardly unjustified, but those experiences were limited. They comprised only a couple days and a single settlement. Gemstone seemed like a genuinely nice place. There was love there. Despite the guns that adorned their walls and the armaments they produced, there was a sense of peace and happiness that had become uncommon during the war. It gave me a small glimmer of hope that maybe, just maybe, the Wasteland wasn’t quite as bad as I had been led to believe.

That hope didn’t last long.

{\br}%
“How bad is it?”

Dusty grunted, peering through his binoculars. It was still fairly early in the morning by the time we reached the sandy ridge we were lying upon. Out in the flat and empty basin beyond, perhaps a mile away, was the depot Dusty had guided us toward. That, and a fair bit more.

\leavevmode\llap{“}Bad,” Dusty said, passing the binoculars my way.

I took them, bracing against a rock for stability; despite the relatively short walk and the night’s rest, my legs were still quite unhappy with the workload I’d given them lately. I peered through the binoculars, my view swinging around until I finally found what I was looking for.

Even with the binoculars, I couldn’t make out all the fine details at such a range, but I didn’t need to. The recent construction was perfectly obvious.

The perimeter was lined with a chain-link fence that had been reinforced or patched in several places with scrap. What had once been a wagon shelter had partially collapsed, but fabric hung from the remaining parts to form simple shelters, swaying in the light breeze. A rope bridge ran from a patched-up watch tower to the roof of a warehouse, where a few more crude structures had been built. Just beyond the warehouse was a line of railway tracks, with a second line running along the loading dock of the warehouse. The most significant construction was a haphazard wall, anchored by the watchtower at one end and the fence at the other, with a large gate in the middle. It was nothing compared to the gates of Rust or Gemstone, but that hardly mattered. Somepony had found our claim.

In front of that gate was an object that I thought might have been a pony. On scrutinizing it in the binoculars, I came to the horrified realization that I was close. It was \textit{most} of a pony. Specifically, a dismembered and decapitated torso, impaled on a pole. Several dark birds appeared to be gathered around, presumably feeding on it.

I passed the binoculars back, not needing to see further details of \textit{that}. “So… raiders?”

\leavevmode\llap{“}Probably,” Dusty replied, taking his binoculars back. He continued to silently scan over the depot.

I watched as well, though there was little I could make out from so far away. “So… that’s it, then? We’re not planning on fighting a bunch of raiders, are we?”

\leavevmode\llap{“}No, we’re not.” He continued to watch the compound. “I don’t think we’ll have to.”

\leavevmode\llap{“}I’m not sure I like the sound of that,” I said, giving him a concerned look.

\leavevmode\llap{“}The sound of what?” Starlight called up to us. She was watching our rear, at Dusty’s insistence, and was sitting a ways back from where we lay. It occurred to me that meant she had no idea about the torso-pony.

\leavevmode\llap{“}I’m not seeing any ponies,” Dusty said. “Nopony’s manning the lookout posts, and I haven’t seen any movement inside the fence. I \textit{do} see two… maybe three bodies. Plenty of crows, too. It looks like whoever it was got hit.”

\leavevmode\llap{“}I’m liking the sound of this even less.”

\leavevmode\llap{“}What do you mean, bodies?” Starlight asked.

\leavevmode\llap{“}The depot has dead ponies in it,” Dusty called back.

\leavevmode\llap{“}And we have no idea who killed them,” I added.

\leavevmode\llap{“}But whoever it was seems to have moved on.” He mulled the situation over for a moment before making a decision. “We need to get a closer look. If they really have cleared out, we could still find a lot of salvage.”

I frowned. Even if everything he said made sense, I disliked the idea of getting closer to the depot of death. Still, I had to admit I agreed with him. In fact, I’d much rather take the chance and scope it out rather than stay away due to personal risk. The risk was there either way; our supply of caps was rapidly dwindling, and we were unlikely to find another prospect so promising on our way back. The life of an Infiltrator often demands risks, and he \textit{was} just proposing a scouting run.

\leavevmode\llap{“}Okay,” I said, nodding. “We should be careful, though.”

\leavevmode\llap{“}Of course,” Dusty said, lowering the binoculars. “You see that streambed off to the left of the depot?”

After a moment, I found what he was talking about: a shallow crevice in the ground, only a few feet lower than the terrain around it and snaking slowly off to our left. “Yeah, I see it.”

\leavevmode\llap{“}That’s our approach. It should keep us in defilade to anypony on the ground most of the way there. The last hundred yards will be in the open, but we can scout it out before crossing.”

I nodded again.

\leavevmode\llap{“}Scoot back,” he said, and we shuffled backwards until we were out of sight of the depot. Keeping low, we crept back to Starlight. “Let’s see that map.”

Starlight levitated her PipBuck out between us, flipping over to the map screen. After zooming in, Dusty pointed to it. “Okay, there. That stream on the northwest side of the compound? It hooks around this high ground just to our north. That’s our entrance. It’s also our primary exit. The ground around the compound is barren with almost no cover, so if we have to retreat, we want to go that way. Once we make it to the streambed, we can either retreat back north, or continue on south.”

\leavevmode\llap{“}Makes sense,” Starlight said, though she seemed reluctant to admit it. I merely nodded.

\leavevmode\llap{“}If you see anypony, you’re only to fire if they see us, and either have a weapon pointed at us or are shooting at us. Anything else, you wait for my word before shooting.” He looked around at us, his expression sharp and deadly serious. “Understood?”

\leavevmode\llap{“}Sure,” Starlight said. I nodded once more.

Dusty continued to stare at her for a second before speaking again. “Just remember, that was part of the deal. Until we’ve cleared the entire compound, this is a combat zone. That means you need to do exactly what I say, when I say it. No questions asked or second-guessing, no improvisation, just following orders. You got that?”

\leavevmode\llap{“}Yeah,” Starlight said, with only the faintest hint of bitterness. “It’s your show. I got it.”

The twitch of his jaw was subtle, but I could tell he’d caught that tone. He decided not to press the matter, though. “Okay. Check and ready your weapons.” He pulled his own rifle around to hang from his neck, in easy reach, and pulled back the bolt. I did the same. Starlight merely looked at us both with a bored expression, her pistol hovering beside her.

Dusty nodded. “I’ll lead. Starlight, you’re on me. Whisper, you’re bringing up the rear. Let’s move out.”

With the first tingles of adrenaline playing at the edge of my senses, we started to walk.