The trek to our planned camp was slow and quiet. After the thundering adrenaline of combat, the tension of searching through ancient compounds, and the troubling horrors we had encountered, I was feeling wiped out. The lack of sleep simply made it all worse.

The others I was traveling with fared no better. Dusty was perhaps the most unaffected, but I could tell it was wearing on him. Even Sickle trudged along behind us, her head held lower than usual. I’m not sure if her lethargy was due to a lack of sleep, the after-effects of the multiple drugs she had taken, or simply her injuries affecting her more than she let on.

And then there were the two newcomers. The younger mare, Quicksilver, limped along with her head low, ears flattened. If she still had her tail, I imagine it would have been tucked between her legs. It was a pitiful sight, one that hurt to watch. Even as her limping worsened and she had to lean against her mother, she kept going. The only sound either of them made was when Silverline leaned in to quietly murmur to her.

When we had been waiting for night to fall, so we could infiltrate Paradise Beach in the dark, Dusty had scouted out a place for us to camp. It was a narrow draw along the slope of a low hill, lined with dry brush that offered the small site some measure of concealment. We were all quite relieved to return there, shedding our saddlebags and bundles of loot.

Dusty turned to the two mares, pulling the two extra bundles from his back. “Here, these are for you. I tried to find you the best I could, but I’m afraid we didn’t have much selection.”

Silverline looked to the two bundles, slowly nodding. “Thank you.”

\leavevmode\llap{“}Seems like the least I could do, with them being there and all,” Dusty replied, giving an awkward smile that quickly slid away. “Anyways, uh, we’ll try to give you two some privacy.”

She hung back a short distance away as Dusty walked back to us, speaking up. “It’s about four hours until dawn,” he said, “so we won’t be staying long. We’ll get some rest, but I want to be heading out at first light, just in case there are any more raiders out there that might come looking.”

Sickle snorted as she pulled off her helmet, letting it drop to the ground with a heavy thump. “Really? ‘Cause I’ve got like twenty fucking ears in my cans. I don’t even know how Gutfuck got \textit{that} many dumbasses following him, and you think he’s got even more?”

Starlight groaned quietly. “Oh, wonderful. You managed to make his name even worse.”

\leavevmode\llap{“}What I think is that we don’t know how many he had,” Dusty replied. “So until we’re back behind Rust’s walls, we’re going to keep an eye out for trouble.”

\leavevmode\llap{“}Yeah, sure,” Sickle grumbled, removing her spiked hoof-boots.

Out of curiosity, and with my reluctance to speak with her eroded due to fatigue diminishing my common sense, I asked her, “Was this an unusually large group of raiders?”

\leavevmode\llap{“}Unusual?” she echoed with an irritated snort. “Fuck yes, it is. I don’t know how Gutfuck managed it, but he got the second biggest band of raiders I’ve ever seen.”

\leavevmode\llap{“}Only the second?”

\leavevmode\llap{“}Yeah. First biggest was the crew I used to roll with.” A short distance from the rest of us, Silverline’s ears perked up, swiveling our way. “At least, they were,” Sickle continued, “before I killed every single one of them.”

After a couple seconds of silence, Starlight quietly spoke up. “Do you make a habit of killing the ponies you work with?”

Sickle shot her a glare, snarling. “Go fuck yourself, you mouthy cunt. And no. I make a habit of killing raiders.”

She turned away, continuing to unbuckle armor, while Starlight rolled her eyes and pulled out her blanket.

With that sidetrack out of the way, Dusty spoke up again. “So anyway, I’ll take watch for half our stop, but I’ll need a volunteer for the other half.”

\leavevmode\llap{“}Fuck that shit,” Sickle said.

Considering our options, I reluctantly volunteered to take first watch. I was accustomed to getting fairly little sleep and staying up far too late. Admittedly, that was under much better conditions, where I had a healthy supply of love to keep myself in top condition. Despite my current state, I hoped that experience would help me, as I seemed to be the best option remaining. I figured Starlight could use the rest more, given her injury; besides, her health was my health, at the moment.

Much to everyone’s relief, Sickle removed her armor and spent some time with a rag and a bottle of murky water to crudely clean it, as well as getting most of the dried blood out of her coat. I think she might have looked even more horrific out of her armor. Aside from her snout, her neck was completely covered, as was the inside of one of her thighs. Her cleaning was far from complete, but at least when she was done it looked more like “slightly dirty” rather than “horror story slasher”.

My standards continued to slip in unpleasant ways.

The wound in her neck was a small but jagged cut, and removing the armor seemed to have opened it up again, sending a slow trickle of fresh blood down her neck. Sickle eventually fished out another healing potion, which brought the bleeding to a halt. It also produced a questioning look from Starlight.

\leavevmode\llap{“}Uh, you never got the bullet out, did you?” Starlight asked.

\leavevmode\llap{“}Yeah, so?” Sickle said, tossing aside the bottle and returning to work on her armor. “Wouldn’t be the first time. Probably got a dozen of them rattling around in me.”

\leavevmode\llap{“}Doesn’t that hurt?”

Sickle snorted. “Maybe if I was a little bitch about it.”

Starlight glared at her for several seconds before speaking again. “You enjoy being unpleasant, don’t you?”

While Sickle didn’t answer, she grinned as she continued cleaning her armor.

\leavevmode\llap{“}That would be a ‘yes’,” Dusty helpfully informed us, which drew a scowl from Starlight.

\leavevmode\llap{“}I can see how the two of you hooked up, before,” she grumbled. “You’re both colossal asses when you want to be.”

Dusty shot her a scowl. “Hey, I’m not \textit{that} bad.”

\leavevmode\llap{“}Yes he is,” Sickle said, still grinning.

Starlight was silent for several seconds before turning to Dusty. “What was up with shooting that pony?”

Dusty blinked. “Uh, might need to be a bit more specific. We kinda shot a lot of ponies today.”

\leavevmode\llap{“}The one in front of Stable-Tec,” Starlight said. “I mean, yeah, he was a raider—hell, I’m glad he’s dead!—but just straight-up executing an unarmed and wounded pony? That doesn’t seem right.”

For a moment, Dusty simply sat there, frowning. Then he slowly shook his head. “If it were any other kind of pony, I’d agree with you a hundred percent. But a raider? A pony like that’s got to be put down. You’ve seen what they do. You leave them alive, you’re letting them do their horrible shit to more ponies down the road. Besides, it’s better to make sure they don’t get back up and come after you when you think you’re safe.”

\leavevmode\llap{“}He’s right about that,” Sickle said with a chuckle. “First pony I ever killed thought I wasn’t a threat any more.” She turned back to cleaning her armor, and quietly muttered, “Had fun castrating the bastard, too.”

\leavevmode\llap{“}I dunno,” Starlight said, shaking her head. “It just… I don’t know…”

After a moment of consideration, Dusty spoke again “If it’s any consolation, he was dead either way. Even if he didn’t die from his injuries, we couldn’t just leave him free to keep on doing his raider thing. We’d have to take him prisoner, and that means hauling him all the way back to Rust with us, and you know what they’d do with him. I just saved them some rope.”

When Starlight didn’t object, Dusty turned to one of the bags of food. “Let’s get something to eat and hit the hay. Tomorrow’s going to be a long day of walking.”

He retrieved a few cans, produced a small folding knife with a can opener, and passed the opened cans around. While most of the cans were labeled as beans, I ended up with an unlabeled can of ravioli. They tasted like old tomatoes and grease, and had a gelatinous consistency. I’m not sure what the contents of the pasta were. It was probably some form of cheese, or at least some substance which had once passed for cheese. With our lack of utensils, I had to resort to slurping the contents straight from the can.

Another mystery can had turned out to be peaches. Dusty gave that and a can of beans to Silverline and Quicksilver, as well as a bottle of water. Silverline accepted them, murmuring a quiet thanks.

They seemed so withdrawn and morose. Quicksilver in particular seemed almost robotic as she ate. Given what they had been through, I wasn’t surprised. I wasn’t a professional psychologist—at least, not in that sense—but I knew all about how actions and events could affect the emotions and mentality of a pony. Those two had been through some of the worst that the Wasteland had to offer.

That eventually led my thoughts back to Emerald, and her idea of how to fight back against the Wasteland itself: Kindness and Generosity.

I set my can down, wiped my mouth off, and turned to root around in my bags. It didn’t take long to find what I was looking for.

Silverline looked up with an expression of caution as I stepped up to her. Behind her, Quicksilver focused very intently on the can she held in her hooves.

\leavevmode\llap{“}Here,” I said around the edge of the packages as I held out a pair of snack cakes, among the last that I had acquired in Rust. “I thought you might like some dessert.”

She hesitated for a moment, looking at me and my weak smile, before carefully reaching out to take them. “Thank you,” she said, and I think I saw a hint of a smile, if only for a moment. I simply nodded and headed back to my own meal.

As soon as everyone had eaten, things wound down. Dusty took the time to give his rifle a quick cleaning, which made me realize I had nothing to maintain my own weapon; I’d have to fix that at some point. Sickle eventually finished cleaning her armor, as well as dislodging the fragments of a bullet that had wedged themselves between the plates of her neck armor. She grinned with satisfaction as she looked over the pieces. They had struck right in the seam where two plates overlapped, and most of the fragments had stuck between one of the plates and the mesh behind it. The wound in her neck had likely come from a fragment of that bullet. I’m not sure why that amused her.

Soon everypony settled down to sleep, though not before Sickle had re-donned her armor and popped yet another pill. I was the exception, sitting back a little ways to keep an eye out, my rifle hanging against my chest. I tried to occupy my time by slowly loading some of the new-found ammunition into the extra magazines. It didn’t take long, and a few minutes later I had five spare magazines resting in my ammo pouch. While I was uncertain of the quality of ammunition the raiders had carried, at least they had plenty of it. It seemed strange to have ended a fight with more ammo than I had started it with, especially when my method of firing had been to simply empty the magazine in the general direction of my enemy.

I missed the time when my “enemies” were dealt with primarily through words.

With nothing else to do, I settled in to wait through my two-hour watch. Apart from the occasional whimper from Quicksilver and the answering murmurs from Silverline, the night was almost perfectly silent. Only the faintest buzz lingered in my ears, a final reminder of that night’s fighting.

It was probably half an hour later that Silverline rose, whispering a few gentle words to her daughter before carefully and quietly walking my way. I met her with a tiny, gentle smile.

\leavevmode\llap{“}I’m sorry to disturb you,” she whispered, barely audible with the way she hung back from me. “My daughter is having a lot of trouble sleeping, and… and I was wondering if you might have something that could help her.”

My smile wilted in sympathy, but after a moment of thought, I forced it back. “I might be able to find something.”

I got up, quietly approaching the slumbering form of Starlight. I whispered her name, but received no reply. After a few seconds of contemplation, I leaned down to nudge open her bags, pulling out the medical supplies.

Starlight murmured, “Huh?” as her eyes cracked open a tiny bit to look at me, and I just smiled back.

\leavevmode\llap{“}I just needed to get a painkiller. Go back to sleep.”

Her eyes closed, murmuring something indistinct. A few moments later I found the bottle I was looking for. I opened it, retrieving a single pill before closing the bottle again and returning the medical supplies to Starlight’s bags. Then I slipped away again, returning to Silverline.

\leavevmode\llap{“}Here you go,” I whispered as I offered her the pill. “It’s a strong painkiller. I had to use one, once. It put me right out. I don’t think I even dreamed that night.”

She swallowed as she gingerly took the pill in one hoof. “Thank you,” she whispered, her voice growing thick, and in the dim light, I was fairly sure I saw her blinking back tears. She quickly turned away, hobbling on three legs as she made her way back to her daughter. There were a few more whispers, and some shuffling as Silverline fetched the bottle of water. Soon they settled down again. This time, they were still.

The rest of my watch passed in silence.

{\br}%
I slept like a rock once Dusty relieved me.

That surprised me. When I had lain down, anxiety had been gnawing at my gut. In just a few short hours, I had seen such extreme violence, witnessed the aftermath of atrocities, and nearly died. While Silverline and Quicksilver had my sympathies, it was the last one that weighed heaviest on my mind. My hive may well be depending on me, and if I died, I would have failed them all.

So I took it as a sign of just how exhausting and draining the previous week or so had been that I remember nothing after pulling the blanket over my shoulders.

Starlight told me afterwards that she prodded me for almost a full minute before my eyes finally opened to the dim predawn light. The first few minutes of morning went by in an indistinct blur. Mostly, I just remember feeling miserable. I think I felt more tired than I had before going to sleep.

Breakfast was quick, as Starlight and I shared a quick meal of a few vegetables and a can of baked beans. Then we were packing to go.

Quicksilver looked as tired as I did, struggling to keep her eyes open as she sat there, while her mother bundled up their bedding. As soon as she finished, Silverline whispered a few words to her daughter before walking up to us. There was a fresh sense of determination to her; she still looked cautious, but not cowed. “I wanted to thank you for… for what you did.”

Dusty gave a half smile. “I’m glad we could help, ma’am.”

Both Starlight and I echoed the sentiment. Sickle just took another sip from a dark bottle, making some weak rumble; while it was hard to tell under the helmet, even with the steel muzzle dangling free at the side, I got the impression she was as tired as I was.

\leavevmode\llap{“}And I’m glad you did,” Silverline said, nodding shakily. “We had nearly given up hope that anypony was coming for us. That anyone even cared.”

Dusty’s ears drooped, and he glanced our way before speaking again. “I’m sorry to say it, but we had no idea you were there. We were in the area for a job. We just happened to come across you. Damn glad we did, too.”

It struck me as harsh, as if he were dashing her hopes that somepony had been looking out for them. I probably would have omitted that detail, myself. Still, she was bound to discover the truth eventually.

\leavevmode\llap{“}Oh,” she said, ears drooping a bit. “Th-then thank the goddesses you found us.” She swallowed, her determination wavering for a moment. Then she took a deep breath, finding her resolve once more. “Thank you for what you’ve done, but I have to get my daughter home. I can’t offer you anything now, but if you ever make your way to Mareford, I’ll do anything I can to repay you for saving us.”

\leavevmode\llap{“}Hold on, there,” Dusty said, his ears perking up. “That’s not necessary. But, did you say Mareford? That’s quite a ways away. How’d you two end up here?”

She hesitated to answer, but only for a moment. “We were with the water caravan, coming back from Rust.”

\leavevmode\llap{“}What?” Dusty’s eyes widened. “They hit the water caravan? What about the Militia guards?”

I was surprised by the sharp edge to Silverline’s voice. “There weren’t any. Gun’s been hiring mercenaries to guard the caravans for almost a year, now, and they took off half an hour before the raiders showed up.”

Dusty’s jaw dropped, followed by sputtering. “He… they… what?”

The information troubled me, as well. It didn’t take a very cynical mind to draw a connection between the two events, and I turned to dig through my bags, seeking out the most immediate potential source of information: Gutrip’s notebook.

I flipped through it until the writing stopped, then slowly made my way backwards, scanning over the randomly scribbled notes and pornographic doodles in hopes of finding anything that stood out.

I found what I was looking for almost immediately. Every head turned to me as I read one note, scrawled along the side of the last page of writing. “Water caravan, Rust to Mareford, three days, Rotwater bridge, no guards. The last bit’s underlined.”

Dusty broke the following silence. “Son of a bitch.”

\leavevmode\llap{“}Well that fucking explains it,” Sickle rumbled. “No wonder that dumbass was doing so well. Gutfuck got himself a patron.”

\leavevmode\llap{“}Shit,” Starlight murmured. “Someone’s hiring raiders?”

\leavevmode\llap{“}Naw,” Sickle said with a sneer. “I’m sure those mercs just fucked off for the fun of it, and Gut was a fucking psychic.”

Starlight rolled her eyes, grumbling under her breath.

\leavevmode\llap{“}What the hell is Big Gun thinking?” Dusty said, scowling. “The Militia is supposed to take care of stuff like this. And for that matter, why the hell does he have any say in it? Hardwood’s the one in charge of that stuff!”

\leavevmode\llap{“}Hardwood stepped down last year,” Silverline said. “Gun’s in charge of Mareford, now.”

Dusty blinked, evidently surprised again. “I know Big Gun’s wanted to be mayor for years, but how in the hay did that happen?”

\leavevmode\llap{“}I don’t know,” Silverline replied. “Politics was more my—” She cut herself off, trembling for a moment before speaking again. “It doesn’t matter right now. I need to go and get my daughter home. Thank you for—”

\leavevmode\llap{“}Now hold on there,” Dusty said, raising a hoof. “Mareford’s a long hike, and I’m not going to leave a pair of unarmed ponies to do it alone. We—” He stopped, mouth shutting as he looked back at us, and continued. “Well, I can’t speak for anypony else, but I intend to make sure you get there safe. I’ll go with you.”

\leavevmode\llap{“}Us too!” Starlight quickly added, before looking to me. “I mean, if that’s okay with you?”

\leavevmode\llap{“}Absolutely,” I said, giving a decisive nod.

Sickle dissented. “Fuck that.” She swept her hoof around, gesturing to all of us. “We’re all going to Rust,” she said, before pointing a hoof at Dusty, “so that you can pay me what you fucking owe me.”

\leavevmode\llap{“}Relax,” he said, scowling. “We’ll be going by Rust. It’s on the way. You’ll get paid, and we can all be on our way.”

\leavevmode\llap{“}Right,” Sickle said, sitting back. “Good.”

Dusty slowly nodded, then looked back to Starlight. “Long as that’s all okay with you, that is.”

Silverline swallowed as she nodded, her eyes glistening as she blinked. “Th-thank you.”

\leavevmode\llap{“}No need to thank us,” Dusty said, offering a smile. “I’m just doing what’s right.” The smile faded quickly. “Besides, I’d like to talk to Big Gun and find out what the hell he thinks he’s doing, leaving ponies high and dry like that.”

Even with her eyes tearing up, that sharpness returned to Silverline’s expression. “Me too.”

{\br}%
That first day was almost entirely uneventful. There was fairly little talking, and the scenery hadn’t been that pretty even before the apocalypse. We stopped for lunch, breaking out another can each. Dusty even offered Silverline and Quicksilver some of his cigarettes, though they declined. While we ate and rested, I pored through the contents of the data-store.

It tried to resist me.

The moment I tried to pull up a file, my portable terminal beeped and froze. I flipped a switch, changing modes to peer at the crude spell matrix built into the data-store and the malicious bit of code it had tried to execute. It was small, but effective; if I had been using a regular terminal, the resulting spell would have caused its spell matrix to implode. Restarting it would have required a rather lengthy and difficult process, made all the more difficult for not having the proper tools on me.

Instead, I smiled, stabbed a button with my hoof, and killed the vicious little spell before it could form.

I released my terminal’s ironclad grip on the data-store’s spell-matrix processes, and began perusing the thousands of files contained within. It was far too much to give more than a cursory skimming before we would have to hoof it over to Amber. If I was going to give the data the proper analysis that it deserved, I needed more time. To do so, I turned to Starlight.

Her hoof raised protectively to her PipBuck when I mentioned my plan. “But why do you have to use this? Don’t you have a data-store? And didn’t you say that one there has some dangerous spell in it?”

\leavevmode\llap{“}My data-store is damaged,” I said, resisting the urge to wilt at its mention. “I… I hope I can recover the information on it, but if I copy more onto it, I could destroy what’s already there. My terminal has almost no storage, so your PipBuck is the only other option. As for the spell, it’s not dangerous. I’ll be copying the data through my terminal, and that means the data-store can only do something if I allow it. Even if that didn’t work, it’d hit my terminal, not your PipBuck.”

It took a bit more convincing, including some technical details that appeared to go well over her head, before she reluctantly passed her PipBuck to me. I plugged in both devices. The transfer went off without a hitch, much to Starlight’s relief.

Fortunately, Starlight considered me a good enough of a friend to trust me further with her precious PipBuck. I had taken a spare strap from one of the bags Sickle carried through the day, and crudely fastened them to my terminal. The intent had been to keep it slung around my neck, like some crude and bulky mockery of Starlight’s setup, in order to get a little bit of reading during the trip. Of course, that promised to be incredibly awkward, what with the tiny screen bouncing around on the bulky device, not to mention putting that much weight on my neck.

When she discovered my intention, she laughed, and offered to let me carry her PipBuck while we traveled, much to my neck’s relief. I hugged her in thanks.

It was still awkward, naturally. The screen was actually larger than my portable terminal’s, but I had to either stop walking or go on three legs whenever I needed to scroll or change files. At least I could get a little reading while we traveled.

Emphasis on “a little”. There’s only so much reading I can do from a bouncing screen while stumbling along uneven ground before my head starts feeling distinctly fuzzy. The entire day’s worth of reading while walking probably added up to less than half an hour of reading while resting or eating, but at least it let me feel as if I were doing something with my time.

{\br}%
Black insectoid forms chased colorful ponies through the morning sky.

I had been making another attempt at reading when Starlight’s faint gasp drew my attention first to her, then up in the direction she was looking. I stumbled at the sight, my gut lurching in shock.

They were descending rapidly, swerving around in corkscrew patterns. I couldn’t even guess at the distance. Half a mile? A mile, at most? It was far enough that I could only make out the most vague of details. There was a blue-green blob and a yellow blob, the rapid beating of their wings only faintly visible as a vague suggestion of motion at their sides. Behind them flew two black forms, swerving and turning to track the colorful ponies before them, with the light glinting off their carapaces.

And I stared, mouth hanging open as I watched, desperately trying to shake myself from my shock and decide what to \textit{do} about it.

I was not surprised—though perhaps a touch concerned—when the black forms began to fire magic at the ponies they chased. I \textit{was} surprised, however, when they turned out to not be bolts of green, but sharp lines of pink. As they flew closer, I could pick out the hint of amber color of the black figures’ eyes, and the thick tail trailing behind them. I let out the breath I had held, feeling a strange mixture of relief and disappointment.

They were just armored ponies. Given the survival of the Raptors and Thunderheads, I wasn’t even surprised to see the now-ancient pegasus power armors in action. I was only worried that these might be members of the Enclave that Dusty had mentioned; while I couldn’t be certain how accurate his information was, it still painted a very negative picture of them.

Seeing a pair of power-armored pegasi chasing a pair of apparently unarmed ponies certainly lent credence to Dusty’s claims.

Dusty had stopped beside me, his binoculars held up to his eyes. “Guess that must be the Enclave… chasing after some of their own?”

One of the pink beams struck the yellow pony. That pegasus flared pink for a moment, casting off trailing embers as the former pony burnt away like a disintegrating meteor. The blue-green pegasus swerved, narrowly evading a similar fate. The pops of the magical energy weapons’ discharge echoed across the Wasteland a couple seconds later, the sound turned soft by the distance.

\leavevmode\llap{“}Oh, shit,” Starlight murmured, lowering her Lancer’s scope to look wide-eyed at the scattering pink embers. Then her expression hardened, and she raised her weapon again.

Dusty shot an alarmed look her way, mouth opening to give a warning, but it never came. He stopped himself, then turned, looking back to the sky.

I heard the soft exhale of Starlight’s breath. In the following silence, another pink beam found the blue-green pegasus, turning the pony’s swerving dive into an uncontrolled plummet. An instant later, that shot was answered by the hissing crack of Starlight’s Lancer, its crimson beam slicing through air and armor alike. One of the armored ponies tumbled wildly, scattering glowing motes of red from whatever part the magic had just incinerated. The other dark figure veered off sharply and pulled out of its dive. I could just make out the amber of the armored goggles as the pony searched for the source of the shot that had felled their companion.

Starlight stared grimly down her scope, her magic already opening the chamber at the weapon’s rear. She continued to track the remaining pegasus; he arced around and began to dive again, aimed roughly in our direction and closing rapidly, while she swapped out the crystals and sealed her weapon again.

A moment later she fired; the red beam struck the pegasus in the chest, sending him tumbling.

It lasted only a moment before the pony stabilized, arcing up again and beating its wings hard to get distance.

\leavevmode\llap{“}Son of a bitch!” Starlight snapped, and started to reload her rifle again. She grit her teeth, muttering under her breath as she tracked the pony’s evasive maneuvering. “Hell no, you’re not getting away with that, you…”

The chamber slammed shut. The magic lashed out, striking the fleeing pony’s side with a burst of glowing embers and burning feathers.

\leavevmode\llap{“}Hah!” Starlight shouted, pumping a hoof in the air in celebration and grinning. “That’s what you get!”

The armored pony’s momentum carried him up for another second before gravity reasserted itself, and he fell toward the earth below. His legs flailed, the remaining wing flapping wildly as he tried to slow his descent.

Starlight’s victorious grin rapidly wilted as she watched the pony plummeting through the air. For several seconds, she seemed frozen. Then she blinked and started through the motions of reloading her Lancer.

By the time she had closed the chamber again, the pony had fallen behind a hill and out of sight. Starlight continued to stare, her ears drooping. Finally, she turned away, her voice quiet and subdued. “Come on, let’s go.”

I moved up to her side, intending to comfort her. I didn’t get the chance, as she cut me off before I could speak.

\leavevmode\llap{“}I know,” she said, giving a faint, wry smile that died off a moment later. “I just… really didn’t mean for that to go quite the way it did.” She looked off to the side, toward the hill the falling pony had disappeared behind. “Seems like such a horrible way to go.”

I nearly winced when Sickle snorted, already anticipating her nastiness. “That was, what, ten seconds? Heh, you ain’t seen shit if you think \textit{that} was a bad way to go.”

Starlight’s jaw tightened as she shot a glare back to Sickle, lacing her words with a nearly toxic amount of sarcasm. “Gee, thanks. That helps so much.”

Sickle sneered back. “Any time, runt.”

\leavevmode\llap{“}It was a good shot,” Dusty said, his eyes still sweeping around the sky. “But even a weapon as powerful as that can’t always kill cleanly.”

Starlight bristled, but Dusty wasn’t done. “But you tried, and that’s what matters.”

Those words knocked Starlight’s anger right out of her, and she eyed him questioningly. He didn’t look back, keeping his eyes scanning for further threats, which conveniently kept him from looking her way.

Eventually, she looked away again, seemingly satisfied with Dusty’s words.

\leavevmode\llap{“}So, what?” Sickle said, following along. “We ain’t going to find and loot them?”

There was a momentary hitch in Starlight’s step, as if quickly considering and rejecting the idea.

\leavevmode\llap{“}No,” Dusty said. “If those were Enclave, they might have gotten a radio call out to any of their buddies. Even if they didn’t, they’re going to have a superior officer that misses them soon. We want to get the hell out of here as quickly as possible.”

Sickle huffed quietly under her muzzle. “Run away from another fight. Sure, why not?”

Fortunately, she didn’t argue the point. We continued on, quickly slipping into silence once more.

{\br}%
By evening, we arrived at Rust.

Fatigue had become an issue, and not just for me. Starlight’s limp had returned. Both Silverline and Quicksilver were dragging their hooves. Even Sickle lagged behind, her hoof-falls heavy as she trudged along behind us. That ended when she downed another pill, which seemed to chase away her fatigue. Unfortunately, it also made her ever so slightly twitchy. The tip of her intact ear was just long enough to be visible, poking out of the small gap in her helmet designed for such a purpose, and it flicked and twitched at even the slightest sound. After the second time her head snapped around to stare at me for clipping a hoof against a rock—and therefore making noise near her—I kept my distance.

Only Dusty seemed to fare well, despite always being on-guard. He kept sweeping his eyes around, watching out for any threats descending from the clouds. The skies remained quiet, dull, and gray.

It was a relief to see the armored walls of Rust again. Even Silverline gave a weak smile at the sight of safety, though her daughter kept her eyes down at her hooves.

Unlike our sighs of relief, Sickle grumbled at the sight. She sat back heavily, popping open one of her cases to root around, eventually producing a couple more pills and a bottle of hard cider. She didn’t even bother removing her muzzle, simply slapping the pills in between the bars, then throwing her head back and lifting the bottle over her snout. She even managed to get most of the booze in her mouth.

Despite having some concerns about mixing pharmaceuticals and alcohol, I remained silent. Starlight, as usual, did not.

\leavevmode\llap{“}How many drugs are you on, anyway?” she asked, frowning at the larger mare.

\leavevmode\llap{“}The fuck do you care?” Sickle replied, tipping the bottle back once more to make sure she got every last drop.

\leavevmode\llap{“}I only care because I have to be near you,” Starlight replied, with only a hint of grumbling. “That, and you’re drugging up before going into a town I kinda like, and I’d like the place to remain un-trashed.”

\textit{Relatively speaking}, I silently added.

\leavevmode\llap{“}I ain’t going to trash the fucking place,” Sickle said, lowering her head to look at Starlight. A bit of cider dripped from her chin and muzzle. “This little shithole ain’t worth it. But I gotta go in there and get my bounty, and I sure as \textit{fuck} ain’t dealing with Steel Shot’s brahminshit sober.”

As if to emphasize her point, she reared up on her hind legs and threw her bottle as hard as she could toward Rust. At that distance it didn’t even make it halfway, bouncing once off the ground before shattering on one of the train tracks leading to the town. When I looked back, I saw Sickle was licking at the inside of her muzzle, completely preoccupied with getting the last bits of cider.

When we finally approached Rust, the welcome was somewhat less warm than our previous visit. Steel Shot and his guards waited atop the walls, while the gate remained shut. Some of them had their weapons out and resting against the walls. Up in the central tower of the town, I could see a pony crewing their heavy gun.

I felt distinctly vulnerable as we walked closer.

It wasn’t until we were about a hundred yards away when Steel Shot visibly relaxed, letting his gun hang against its strap. “Well, shit,” he called out to us, across the distance. “If it was anypony other than you, Dusty, I’d have thought Sickle there had started up a new gang. What’s got you two traveling together?”

The other guards started to relax as well as Dusty called back. “We needed an extra set of hooves to deal with a band of raiders. She’s just here to collect the bounty.”

\leavevmode\llap{“}The usual, then,” Steel Shot replied with a sense of weariness. “Well, come on in, might as well get this all over with.”

He waved a hoof, and soon the gate began to open. A minute later, we were all inside. Steel Shot and a few of his guards had come down to greet us. Their angular armor, which had once struck me as heavy and tough, now seemed underwhelming when compared to Sickle’s. Most of the guards looked wary. The armored red mare I had seen before watched Sickle with an intense glare.

\leavevmode\llap{“}Good to see you’re still in one piece,” Steel Shot said as he stepped up to Dusty, and they shook hooves. “Was getting a bad feeling about your job and that strange little mare that hired you. Everything went well, then?”

\leavevmode\llap{“}Was a bit more than we expected,” Dusty said, “but nothing we couldn’t handle. Anyway, Sickle here has a bunch of ears to turn in, and the rest of us are going to go find that ‘strange little mare’ to get our pay.”

\leavevmode\llap{“}Well, I’m sure you know where to find her,” Steel Shot said. “Mustard said she’s barely stepped hoof out of her room since you left.” He then turned his attention to our newest traveling companions. “And you’ve made some new friends. Have we met before, miss…?”

When Silverline hesitated, Dusty was quick to cut in. “They hired me to escort them home. We’ll be setting out again in the morning, once we’re done with our business here.”

\leavevmode\llap{“}We were with the water caravan,” Silverline said. While everypony else looked at her, I noticed Dusty giving a faint grimace. It seems I was the only one to see it.

\leavevmode\llap{“}You were?” Steel Shot asked, raising an eyebrow. “Then what are you doing—” He halted abruptly, his eyes widening before looking to Dusty. “Oh, no. You don’t mean—”

\leavevmode\llap{“}Afraid so,” Dusty said, slowly shaking his head. “They got hit by the same band of raiders we came across. We came across these two, decided we’d make sure they get home safe and sound.”

\leavevmode\llap{“}But—”

Sickle’s growling voice cut through the conversation. “The fuck did you just say?”

Everypony’s heads snapped around to look at her, matching glares with the red guard-mare. Despite the guard’s own metal armor, it was a ridiculously mismatched face-off. That didn’t seem to faze the red mare, as she didn’t give an inch. Instead, she sneered back at Sickle. “Nothing.”

\leavevmode\llap{“}That’s fucking right,” Sickle said, advancing a step to press her face close to the other mare’s. “That’s all you fucking are, you little cunt, and you better remember it.”

Steel Shot stepped forward and raised a hoof, trying to intervene. “Hey now, calm down, there—”

Sickle wheeled around on him. “And fuck you too, Steel! How many raiders have I killed for you and your little fuckstain town? You dumb cunts ought to be licking my fucking hooves for everything I’ve done for you, but every time I come in it’s nothing but bitching and moaning. How about you start showing a little fucking respect?”

The red mare muttered loud enough to be sure we could all hear it. “How about you start acting in a way that deserves it.”

Sickle turned back to her, baring her teeth as she growled. “Steel? You better get over here and shove your dick down this cunt’s throat before she says something you’re both going to regret.”

\leavevmode\llap{“}Sickle,” Starlight called out, with a warning tone to her voice. Sickle turned on her.

\leavevmode\llap{“}Oh, fuck off, Star! Mind your own fucking business for a change.” Sickle shuddered, shaking her head for a moment as if she were shaking water out of her mane, then turned back to the red guard-mare. Then she stopped, seeing Steel Shot whispering to the mare. She continued to stare for several seconds until the other mare gave a quiet snort and nodded to Steel Shot. With a final glare Sickle’s way, she turned and walked away with barely restrained rage.

\leavevmode\llap{“}There,” Steel Shot said, doing his best to be calm and conciliatory. “That better? We’re all friends here, right?”

Sickle snorted, looking one last time at the guard-mare, storming off into town, before looking back at Steel. “Better for now.”

\leavevmode\llap{“}Okay, good,” Steel Shot said, nodding. “So… we’ve got business to talk, then? Well, uh… let’s step into my office, we can get this all sorted out.”

\leavevmode\llap{“}About fucking time,” Sickle muttered.

This time, it was Dusty who decided to speak out in warning. “Sickle…”

Her head snapped around toward him, and I got the distinct impression that she was only a few words away from murdering somepony.

I quickly lifted a hoof, placing it gently on Dusty’s shoulder. The unexpected contact drew a start from him, cutting off what he was going to say next. He looked to me, while I gave my best soft, gently concerned look in reply, while desperately hoping he’d get the message.

After a couple seconds, the tightness that had grown in his jaw slowly relaxed, and he let out a quiet sigh before looking back to Sickle. “We’re going to go talk to Amber to get the rest of our pay. You can meet us at Mustard’s place after you’re done here, to get your cut.” He hesitated for a moment before adding, “And try not to get into \textit{too} much trouble.”

Sickle just snorted out a dry chuckle before turning away and walking toward the small building we had been led into our first night in Rust. “Come on, Steel. You owe me some caps.”

With our volatile and foul-mouthed powder keg seemingly appeased for the moment, we parted ways, heading toward Mustard’s inn.

\leavevmode\llap{“}Eesh,” Starlight quietly murmured. “And that’s \textit{after} medicating herself. I don’t know if she’d be better or \textit{worse} sober.”

\leavevmode\llap{“}Hard to be much worse,” Dusty said.

\leavevmode\llap{“}She didn’t kill anyone,” I pointed out. Dusty merely shrugged.

We met with Mustard, arranging for three rooms for the night. Dusty paid for Silverline and Quicksilver’s room. Once we had gotten them settled in and unloaded our spare bags of goods, we went to see Amber.

Dusty’s knocking was answered by a bored, condescending response. “Who is it?”

\leavevmode\llap{“}Dusty.”

Once again, we were answered by the sound of hoofsteps and shifting furniture before the door opened to reveal “Lady” Amber, looking as elegant and haughty as ever. “And am I to assume that you have completed your task?”

\leavevmode\llap{“}We have,” he replied. “Whisper?”

I stuck my snout into my bag and pulled out the data-store. The moment I held it out, Amber snatched it away from me. “Good. I will verify the data, and if it is as you say, I will return with your reward.”

With that, she shut the door in our faces.

Or at least, she would have, if Dusty hadn’t put a hoof in the way. Amber, who had just started to turn away, stopped and shot him a sharp glare.

\leavevmode\llap{“}I don’t think so,” Dusty said, meeting her glare. “We went through a lot for that data, and it’s not leaving our sight until we get paid for it. And before you think of anything funny with your ‘verifying’, the deal was to get you whatever was on those servers. We did that. If that data ain’t what you expected, it’s not our problem.”

Amber held firm. “But it is your problem if the data isn’t what you claim it to be, or from where you claim to have gotten it. Hence, I must verify the data.”

\leavevmode\llap{“}Then you do that,” Dusty said. “But that thing’s staying right where I can see it until we’ve got our caps.”

Amber tilted her head every so slightly, regarding him for several seconds. “Fine. One of you may enter and watch over it while I check the data.”

\leavevmode\llap{“}All of us.”

Amber’s lip twitched, eyes narrowing again. “And leave myself surrounded by mercenaries, outnumbered and out of sight, with thousands of caps on the line? I think not.”

Dusty scowled. “If we were going to rob you, we wouldn’t be having this conversation. We would have forced our way in the moment you unbarricaded the door. You, on the other hoof, have five thousand little reasons to try and pull a fast one on us.”

She stared at him for several long seconds. Finally she stepped back, letting the door swing open again. “Very well.” She turned, eying us over her shoulder as she walked over to the bed and the saddlebags set beside it. “To be just as infantile as you are acting, you shall stay on your side of the room, and I shall stay on mine.”

\leavevmode\llap{“}Works for me,” Dusty said as he walked into the room, and we followed, single file. He sat and took a load off, shucking his saddlebags and unslinging his rifle. I noted that it also left his rifle within quick reach. I followed his lead.

Amber made a point of turning to face us as she set the data-store on the bed, then lifted her bags onto the bed. She gave us a wary look before nudging a flap open and slipping her muzzle in, searching around. We waited, patiently.

Finally, she found what she was searching for. She drew back, a pistol aimed straight at Dusty. “Uhhn oohf.”

Dusty twitched, but thought better of trying to out-draw a mare who already had a pistol leveled at him. I have to admire his composure, though. The shock of adrenaline tore at my nerves, and I had to fight to keep myself still. Dusty, however, looked perfectly calm, though I could see the fire in his eyes. “You don’t want to do that.”

\leavevmode\llap{“}Eh-ahhgs,” Amber mumbled around the grip of her pistol. “Eh uh ehh-ah-hun.”

Dusty merely blinked. “You’re not very good at that. I can’t understand a thing you’re saying.”

Her eyes narrowed, and she pointed the muzzle of her gun towards his hooves, then gestured upward. Reluctantly, Dusty raised his forehooves. Starlight and I followed suit.

Keeping her eyes on us as best she could, Amber reached a hoof into her bag. After a couple tugs, I was relieved to see her pull a computer cable from the bag. She blindly fumbled with the data-store until she got the cable plugged into it. Then her hoof returned to the bag, opening it enough that she could see inside, though her eyes remained on us at first. The pistol remained steady, even when she cast a quick glance down and back again.

I became increasingly aware of the way Starlight was watching Amber’s actions. “Stay calm,” I whispered. “We’re good.”

The pistol jerked over in my direction, making me twitch. “Eye-uhh.” I reached my hooves a little higher, and the muzzle returned to Dusty.

We remained like that for almost a minute as Amber poked at something within her bag. I heard the occasional, quiet beep. Finally, her shoulders relaxed. Keeping her eyes locked squarely on us, she crouched down, reaching under the bed. After a couple probes, she found what she was looking for, and dragged out a large bag, about the size of both my saddlebags combined. I could see the effort it took as she hefted it in her hooves, then tossed it before us. It landed with a solid thump and a loud jingle.

She followed up by tossing her pistol onto the bed. “There’s your payment.”

She hadn’t even finished the sentence before Dusty was on his hooves, his rifle pointed at her. He practically growled around the bit, speaking much more clearly than she had. “I don’t appreciate being held at gunpoint by my so-called ‘employer’.”

\leavevmode\llap{“}And \textit{I} don’t appreciate being intimidated and bullied by two-bit thugs that kill other ponies for caps,” she replied, glaring haughtily down her snout. She showed no concern over the large rifle leveled at her. “Given your propensity towards violence, I took a reasonable precaution in case your data turned out to be fraudulent. Now I have the data my patron wants, and you have the money you want. Seeing as neither of us have anything more to be gained here, you should leave.”

Though she did a good job of acting confident, I’d been taught to look for the more subtle signs. They were all there: the tension in her neck and jaw, the steady but deep breaths to conceal a need for more rapid breathing, even the way the hairs of her coat raised slightly. As odd as it might sound, those hints of fear spoke well of her, though it made me feel even more uncomfortable. She knew exactly how much danger she was in, but was remaining calm.

Dusty, meanwhile, looked as if he was seriously contemplating murdering her. It wasn’t until I had picked up the bag of caps that he finally lowered the weapon. He didn’t even say anything, simply tossing his saddlebags across his back and storming out.

The door slammed shut behind us, followed by the sound of the dresser being pushed back across it.

\leavevmode\llap{“}Glad that’s done with,” Dusty muttered.

Starlight abruptly spun around, reared back, and bucked both hind-hooves against the wall. I jumped a bit, and Starlight stumbled forward from her kick. She trembled. “Holy \textit{fuck!} That… that…” She let out a strangled growl and stomped on the ground. “Great. Now I’m sympathizing with Sickle. That stupid bitch!”

Dusty grunted. “Let’s go downstairs, get some drinks, and cool off.”

\leavevmode\llap{“}Yeah, right,” Starlight said, her hooves shaking as she followed him. “We’re in town! It’s supposed to be safe in town! We’re not supposed to get guns pulled on us in town!”

\leavevmode\llap{“}Wish it was that simple,” Dusty said. We’d made it to the corner of the hall, near the stairs, when he sighed and came to a halt. “Put the bag down.”

\leavevmode\llap{“}Huh?” I mumbled around the strap of the bag, raising an eyebrow questioningly.

\leavevmode\llap{“}I want to check it,” he said. “Make sure she isn’t screwing us.”

I set it down, while Starlight stepped up to peer over his shoulder. “You think she didn’t give us all our pay?”

\leavevmode\llap{“}I’m more worried she put a bomb in here,” Dusty said, and Starlight immediately took a step back. I almost did the same, though I recognized it as pointless. If Dusty’s worry proved accurate, I doubt a single step would make a difference.

He opened the flap, revealing the huge pile of pristine bottle caps that filled the bag. He then plunged his hoof into it. Caps rattled and clanked as he slowly fished around inside the bag, rolling it from side to side, thoroughly checking every inch. Finally he drew his hoof out, picking out a single bottle cap. “Looks like we don’t have any explosive surprises waiting for us.”

\leavevmode\llap{“}Shiny,” Starlight said as she stepped up, levitating out one of the caps. “I don’t think I’ve ever seen bottle caps so clean. Or so many of them at once, for that matter.”

Dusty was frowning down at his cap. “I’m kind of concerned by that. Why are they so clean? And they look kinda weird, for some reason.”

\leavevmode\llap{“}Yeah, they do,” Starlight said, a smile slowly spreading. “These caps aren’t… crimped? I think that’s the word.”

\leavevmode\llap{“}What do you mean?”

Starlight’s smile had grown into a wide grin. “I mean, I’m pretty sure these caps have never been used.”

Dusty continued to stare at his cap for a few seconds before his ears shot up, his eyes widening, and he turned to Starlight. “You don’t think…”

\leavevmode\llap{“}Mmm-hmm!” Starlight grinned, flicking her cap back into the bag. “Explains how her mystery patron guy has so many caps to throw around.”

Dusty gave a low whistle, looking back to the cap in his hoof with something bordering on reverence.

Feeling entirely out of the loop, I had to step in. “I have the feeling I’m missing something again.”

Starlight chuckled. “You know how much soda ponies drank back before the megaspells, right?”

Let’s see. The population of Equestria, times the percentage that drank soda, times the average number of bottles consumed per day, and the answer was: “A lot.”

\leavevmode\llap{“}A hell of a lot,” Starlight said. “A bottle factory could put out tens, hell, \textit{hundreds} of thousands of bottles in a freaking day, and every single one of those needed bottle caps. Finding an intact bottling factory… that’s like every scavenger’s dream. That’s the kind of find you can retire off of. Fuck, your \textit{kids} could retire off that.”

\leavevmode\llap{“}If you live that long,” Dusty said, placing his cap back in the bag and closing it before looking to me. “Have you heard of… right, you grew up under a rock.” He looked to Starlight. “Have \textit{you} heard of the Soda War?”

\leavevmode\llap{“}The what now?”

Dusty huffed out a dry chuckle as he stood, and I picked up the bag of caps once more to follow him. “Don’t know if it’s a true story,” he said, “but it sounded true enough. Way I heard it, it was way up north, near Manehattan or something, and about a hundred years ago. Somepony found an untouched Sparkle-Cola plant and managed to disable the defenses. He got wagon-loads of caps out of it. Literally tons. I’m not entirely clear on the details, but the way I hear it, things went to shit as soon as other ponies found out. Something about trade collapsing, two successful settlements dying off, cannibalism, that kind of stuff. Whole area was depopulated for decades afterwards. Ponies get stupid around caps.”

\leavevmode\llap{“}All because of bottle caps,” I muttered, shaking my head.

\leavevmode\llap{“}Yep,” Dusty said, oblivious to my own continuing internal incredulity over the current state of Equestrian economics. “But it’s a good reason for Amber’s employer to keep to the shadows.”

\leavevmode\llap{“}Also means they may have a lot more caps to offer to anyone needing work,” Starlight said. That said work had resulted in her employer pulling a gun on her seemed to have been forgotten already.

Dusty, however, certainly remembered. “I’m not keen on having anything to do with them. If they come to me with a job offer, I might consider it, but I’d be looking over the job very carefully before accepting. Other than that, I’ll keep my distance. This has ‘volatile’ written all over it.”

We started making our way downstairs. We got as far as the first landing when Starlight stopped. “Uh… I kinda just thought of something.”

The rest of us stopped, looking back to her. “What’s that?” I asked.

\leavevmode\llap{“}Well… that Amber mare seems a bit sketchy, right?”

Dusty snorted. “That’s one way of putting it.”

\leavevmode\llap{“}Yeah,” Starlight said. “And she hired us to do a job, which just \textit{happened} to get us in a fight with a bunch of raiders, who had just \textit{happened} to have gotten some outside help taking down a caravan…”

Dusty stared off into space for several seconds before replying. “I don’t know. Seems a bit convoluted to me.”

Starlight turned to me. “What about you? What do you think?”

\leavevmode\llap{“}It’s… suspicious,” I said, “but also very circumstantial. I wouldn’t dismiss the idea outright. It’s certainly plausible, and I’m always a little wary of coincidence, but it seems unlikely.”

Starlight frowned, even though I hadn’t completely shot down her idea. “Why’s that?”

\leavevmode\llap{“}She seemed far more concerned with what was on the data store, to the point of escalating a tense situation over it. I suppose a clever individual could have done that as an act to lure us away from her true motivations, but it’s quite the gamble. More notably, though, she didn’t inquire into what happened out there. If she were using us to hide her tracks, or her patron’s, I’d expect her to want to know what happened to the raiders. After all, we came very close to getting through the whole outing without alerting them.”

Starlight’s frown held, though she relented with a sigh. “I suppose.”

Seeing her looking so down at the refutation of her theory, I offered a little bit of consolation. “But, like I said, I wouldn’t dismiss the idea outright. She could still be involved, somehow.”

Dusty grunted. “If you really want to find out who set the whole thing up, there’s only one set of ponies we know for sure were involved, and that’s the worthless mercs that walked off and left those ponies to die. Ponies like that, I’ll bet they get to talking right quick when you push ‘em.”

\leavevmode\llap{“}And they’re not likely to show their faces around Rust \textit{or} Mareford,” I noted. “The best lead on who they are and where they went would probably be whoever hired them to guard the caravan.”

\leavevmode\llap{“}Yep,” Dusty said, giving a grim smile. “And that’s why I want to have a nice long chat with Big Gun when we get to Mareford.”

When we finally got downstairs, Dusty generously ordered a round of ciders for all of us. I don’t particularly like alcohol, between the chemical taste and the deleterious effect it has upon mental faculties, but it was necessary on occasion. I was not in the position to be shunning a social gesture just yet, so I graciously accepted his offer, and made a point of hiding my distaste whenever I took a sip.

Alcohol tasted bad enough even when it wasn’t two hundred years past its prime.

We sat and waited, with a little idle chit-chat. I don’t remember all of what was said. Mostly, it was the kind of forgettable, meaningless, time-passing chatter that fills the need for social interaction. Only one part of the conversation stuck in my memory as notable, after Starlight asked Dusty if he’d ever been up north to where he’d been talking about.

\leavevmode\llap{“}Nah,” he replied, taking a small draw from his bottle before continuing on. “Furthest north I’ve ever been was Appleloosa. Or… Old Appleloosa, I guess, since some ponies made a new one way down the rails and couldn’t come up with a new name.” He paused, glancing around at us in a way that suggested he was hesitant to continue. “I saw an alicorn there.”

\leavevmode\llap{“}Really?” Starlight said, perking up as the conversation suddenly became interesting.

\leavevmode\llap{“}Yep,” Dusty said, nodding. “Was working as a guard for a caravan, ‘bout three or four months ago. The pony running it heard that there were ponies living in Appleloosa again, so he thought he’d go up there, hit an untapped market and all that. Nopony ran trade routes up north.

\leavevmode\llap{“}So we get there, and you know, I like being cautious. I had the caravan wait while I climbed up a ridge and glassed the place. Damn good thing I did, too. I couldn’t make out too much at that range, even with my binocs, but the ponies there didn’t look too savory. They didn’t look as wild and disorganized as your typical raider, but it was close. They weren’t the worst, though. That was the alicorn.”

He paused, pulling out a cigarette, and took his time lighting it. Starlight leaned in, anticipation growing with every moment. I partially hid my smirk behind a bottle, and caught the corner of Dusty’s lips twitch upwards in response. Finally, Starlight prompted him. “...And?”

Dusty took a deep draw, then blew out a long, thin stream of smoke—and I’ll note, he blew it away from us, a courtesy some ponies never grasped. “And, I got a good view of her frying some pony’s brain. She lit up her horn, and the pony standing in front of her dropped and started flailing around like he was burning alive. Shit, I must have been at least a thousand yards out, and I could \textit{still} hear him screaming.

\leavevmode\llap{“}So I just turned right around, and we all got the fuck out of there.”

Starlight sat back, looking thoughtful. “You don’t think it was the same one, do you?”

\leavevmode\llap{“}Not unless they can change color,” he said, taking another draw from his cigarette. “That one was dark green, not purple. Way I hear it, there are a lot of them alicorns. Though last I heard, a bunch of them got blown up.”

\leavevmode\llap{“}Heard from where?” I asked. Sources of information were a valuable commodity.

\leavevmode\llap{“}Traders,” he replied. “Not from up north, mind you. I don’t think anyone ranges past Old Appleloosa. But Mareford’s close enough that they pick up some radio broadcasts from the north, and the news slowly trickles out from there. Mostly, it makes me glad I’m down here, instead. The north sounds like shit.”

We were still quietly contemplating that when the door slammed open, and Sickle walked in, carrying even more bags than the last time we saw her. Dusty sighed, muttering something under his breath as she approached.

\leavevmode\llap{“}Hey, cunts,” Sickle said, grinning from behind her muzzle. At least she seemed to be in a good mood. “You got the caps?”

\leavevmode\llap{“}Yeah,” Dusty said, patting a hoof on the bag, which gave a faint jingle. Then he eyed the new bags on her back. “Did you go shopping?”

\leavevmode\llap{“}Yep. Steel didn’t have a thousand caps on him. I was just going to beat the last six hundred out of him, but he got the store owner to make up the difference. Hope you bitches didn’t want any chems or booze. I cleaned him out.”

She sat down with a crash of metal armor, the many bags on her back clanking as they slid to the floor.

\leavevmode\llap{“}I think we’re good,” Dusty said, tapping a hoof against his empty bottle.

\leavevmode\llap{“}Yeah, I don’t really give a shit,” Sickle said. “Just give me my caps, already.”

In the end, we agreed that counting out fifteen hundred caps each would be way too tedious. Instead, Dusty added the caps we had gotten up-front—which, upon inspection, turned out to be just as clean and unused as the rest—and divided the lot into four evenly sized piles. Sickle insisted on getting first pick, and claimed a pile she was certain was the largest.

Starlight and I kept our piles separate, not because we were terribly concerned about whose money it really was, but more because it was a \textit{lot} of caps, and I would have felt guilty making her carry all of it herself. I had never before had to measure currency in pounds.

As we started packing the caps, Sickle asked, “So, you’re all running off to Mareford, huh?”

Dusty grunted, securing the sizable bag of money in his packs. “Yeah. What of it?”

Sickle shrugged, metal plates clanking with the motion. “I figured I’d tag along, see what happens.”

Starlight’s head snapped up from packing her own bags, and she blurted out a sharp, “What?”

\leavevmode\llap{“}Why?” Dusty asked, his eyes narrowed suspiciously.

\leavevmode\llap{“}Why not?” Sickle replied, grinning. “This was fun, and I’m betting you fuckers won’t go a week without stirring up some shit. What else would I do? Lie around that little shitstain of a hut, getting high all on my own? Sounds boring as shit. You cunts are a lot more entertaining.”

After a pause, her grin grew a bit more. “‘Sides, I kinda like Star.”

Starlight blinked. “Oh, fuck no. \textit{No}. You’re not coming with us.”

Sickle leaned over the table, one heavy, metal-clad hoof thumping down on top of it. “I’d like to see you stop me,” she said, still grinning.

Starlight stared, mouth hanging open as she completely failed to come up with a retort. That lasted right up until Sickle reached out and snagged her half-empty bottle, which only made it halfway back to her before Starlight’s magic yanked it out of her grasp. “Hey! You’ve got your own damn booze!”

Sickle chuckled, then looked back at Dusty. “So yeah, I think I’ll stick around for a while. ‘Till I get bored of you, anyway.”

Dusty grumbled for a moment before replying. “If you’re going to insist on tagging along with us, you’d better be on your best behavior.”

\leavevmode\llap{“}Yeah, yeah, no killing and raping all the innocent townsfolk and traders. I got it.”

\leavevmode\llap{“}And maybe lay off the drugs a bit,” Starlight muttered.

I felt compelled to add to the objections. “And the profanity, while we’re at it.”

She pointed a hoof at me. “Fuck you.” Then she looked back to Starlight. “And what the fuck’s your problem with my drugs? How about you get on Dusty’s case about his fucking smoking.” She leered at him. “That shit’s just nasty.”

Dusty groaned and stood. “Yeah, screw this. I’m going to bed. We’re heading out in the morning. Feel free to sleep in and miss it.”

\leavevmode\llap{“}Need any company?” she said, grinning in a way I could only describe as cruel. “Maybe getting laid would help your shitty attitude. How long has it been, anyway?”

\leavevmode\llap{“}Don’t remember,” Dusty growled, finishing off his bottle and grabbing his bags. “Was too damn drunk.”

\leavevmode\llap{“}Oh, shit!” Sickle said, laughing. “That long? Hah! You mean you’ve been traveling around with a whole herd of mares and you ain’t fucked any of them? You’ve got to be the dumbest motherfucker I know!”

She continued laughing as Dusty walked off, and ignored Starlight’s disapproving glower. The laughter died off as he slipped out of sight. A moment later she wobbled, and abruptly shook her head violently. Both Starlight and I cringed back from the spear-like horn, though it thankfully didn’t come near us. After a moment Sickle stopped, leaning against the table. In the dark recesses of her helm’s eye-slits, the faint light reflecting from her eyes flickered as she blinked several times.

\leavevmode\llap{“}Uh, you okay there?” Starlight asked, sounding far more skeptical than concerned.

\leavevmode\llap{“}Sorry,” Sickle rumbled, and raised a hoof to rub at the side of her armored head. “Mixing Buck and painkillers always gets weird. ‘Specially with booze.”

Starlight stared at her as if Sickle had just grown a second head. “Did… you just apologize?”

Sickle’s hoof dropped as she looked at Starlight, simply blinking for a few seconds. “...The fuck are you talking about?”

\leavevmode\llap{“}Never mind,” Starlight said, rolling her eyes. “I must have heard wrong.”

\leavevmode\llap{“}Yeah, whatever,” Sickle said, slowly rolling her head around and stretching. “Shit. Yeah, think I’ll hit the hay, too. So Dirt’s being a little bitch, guess that means I’m bunking with you two.”

Starlight’s expression hardened instantly. “You can get your own room, Sickle.”

Sickle shrugged. “Worth a try. Hey, Ketchup!”

The stallion, who had been doing quite a good job of staying well clear of us, sighed from the counter at the front of the room. “It’s Mustard.”

\leavevmode\llap{“}I don’t give a shit. I need a room.”

Starlight and I decided it would be a good idea to retire, too, but I had one thing I wanted to do. One thing that, while I had little hope of succeeding, I had to at least try. So I delayed, nursing my bottle of cider so that we headed to our room at the same time as Sickle. As the three of us walked to our rooms, I turned to Sickle, speaking quietly.

\leavevmode\llap{“}Hey, Sickle? Could I talk to you for a moment?”

She snorted, not even looking at me as she walked. “Yeah. Talk.”

\leavevmode\llap{“}In private?”

She bared her teeth in a grin. “Shit, I ain’t shy, Whimper. If you want to get under my tail, just dive right in. I don’t mind an audience.”

\leavevmode\llap{“}I mean talk. Literally.”

She groaned, and from the movement of her head I guessed she was wasting a perfectly good eye-roll behind that thick helm of hers. Despite the protest, she did stop. “Fiiine.”

Starlight gave me a concerned look, but I replied with a smile and a nod, and after a moment of hesitation she went on without us. I waited until she had passed around the next corner before turning back to Sickle.

\leavevmode\llap{“}I understand that you have this violent, angry persona,” I said, trying to sound as gentle as possible. “I can see that being very useful, with the way the world is, and I’m not going to try to convince you otherwise.”

Her head slowly turned until she was staring straight at me, silent.

\leavevmode\llap{“}But you don’t need to be relentlessly aggressive to keep that perception intact. We’ve all seen what you can do. You’re the strongest pony I’ve ever seen, and you shrugged off attacks that would have likely killed any of us. Everypony knows you’re big and powerful and not to be messed with.”

She continued to stare.

\leavevmode\llap{“}You don’t need to be so hard on Dusty and Starlight just to keep us thinking that. We get it. It’s just… there’s a time and a place for aggression. Friendly ponies are a lot more likely to be helpful, but they don’t remain friendly for long if somepony is constantly insulting or threatening them. I think if you’d save the aggression for fighting, or when somepony is actually insulting you, you’d find things go a lot more smoothly.”

Still, she remained silent.

\leavevmode\llap{“}I mean… ponies tend to respond the way they’ve been treated, right? Threatening a pony that’s been insulting you encourages them to not threaten you, but if you’re threatening a pony that’s been trying to help you, it just encourages them to not help you. If you want a pony to do something for you, they’re a lot more inclined to do that if you’ve been good to them. Or… at least, not \textit{bad} to them. So...”

The silence lingered on for several more seconds as I trailed off, hoping to prompt her into replying. It’s incredibly hard to get a good read on a pony when you can see only the barest hint of their eyes.

Finally, she broke the silence. “You’re a talker.”

I blinked. “Um… I guess I am?”

She moved forward. It wasn’t particularly quick, but it didn’t have to be; she was so huge, I had nowhere to go. A moment later she shoved me up against the wall, her foreleg nearly cutting off my breath as it pressed against my neck. The blades welded to the leg armor arced up beside my head, thankfully pointing away.

She leaned in close, giving me a good face-full of her sour breath. “I’m not. I actually \textit{do} shit instead of just whining about it all day.” She lowered her head, and I winced back as the blade-like horn lowered just above my face. Her free hoof jabbed up, pointing at it. “You see this horn?”

I gripped at the foreleg pinning me to the wall, trying to relieve the pressure of being held up in such a fashion. It was hard to speak, but I managed. “Yeah, I see it.”

\leavevmode\llap{“}Good,” she said, raising her head and pressing her armored muzzle against my snout. We were so close that I could make out her eyes in the darkness of her helm, narrowed to angry slits. “Because I’m going to face-fuck you with this horn if you keep running your little cunt mouth. Got it?”

I nodded. The pressure on my neck had increased, and I made little choking sounds every time I struggled to breathe in.

Then the pressure relented as she threw me to the side. I hit the floor and rolled onto my back, coughing. Sickle sneered down at me.

\leavevmode\llap{“}See? I can get ponies to do what I want just fine.” She walked off, making me wince as an armored hoof clopped heavily beside my head. “See you in the morning, Whimper.”

I lay there until she had disappeared around the corner, and I heard the sound of a door shutting. Only then did I finally haul myself up, slowly making my way to my own room as I fought against the trembling in my limbs.

I had the feeling our little trip was going to be a lot more tiring than I had expected.