“It’s a three day trip to Mareford, if we keep to a steady pace. I figure we’ve got enough supplies, but if there’s anything you’re going to need, you better get it now.”

That was the advice Dusty gave us as we walked to the store with the “Stuff” sign, our bag of looted weapons and ammo in tow for trade. Silverline and Quicksilver were waiting in the “Food” shop, enjoying a fresh-cooked meal courtesy of Starlight.

With an abundance of food and more than a hundred rounds for my rifle, there was little that I could ask for. In fact, only two things came to mind.

The first was a bust. Given the violence we had encountered, I was re-evaluating my prior decision on armored barding. Sadly, none of the armors they had in Rust were to my taste. All of them looked far too thick and heavy for me, all consisting of thick metal plates. While I wanted protection, that wouldn’t do me any good if it left me too slow to keep out of danger, not to mention the concerns of being worn out even before a fight started simply from hauling the armor around.

Fortunately, the other item I looked for was one they had.

Dusty looked a little confused when I returned, grinning. Then he saw the binoculars hung around my neck, and started to chuckle.

\leavevmode\llap{“}I figured I’ve been borrowing yours enough,” I said, and he nodded appreciatively. And you know, I actually felt a bit of affection from him. It wasn’t a lot, just enough to know that he had decided he liked me more than he hated me, but it was there. That really helped my mood. It felt like progress.

Granted, that mood was slightly dampened when I stepped out of the store to see Sickle sitting outside.

She concerned me. Not just for the obvious reason of being a huge, violent, profanity-prone potential psychopath, although that certainly didn’t help. The bigger reason was that I didn’t understand her. I didn’t get how she worked, how she thought. When your job is manipulating ponies to achieve your goals, you rely entirely upon understanding how they think. Sickle, though, was alien to me, and that scared me more than any of her threats. It meant I couldn’t be sure of how she’d react, if something I said would make her laugh or send her into a murderous rage. It meant I had to place my trust in Dusty and Starlight, and their understanding of her.

For an Infiltrator, this was very unfamiliar territory.

I did realize then that it was perhaps foolish to have thought I understood her as well as I did. Ponies are the product of the world around them, at least in part. I didn’t understand this new, broken world I found myself in. How could I expect to properly understand the ponies that grew up with it?

I may have figured out many of the parts, but I clearly had more to learn.

I followed Dusty as he returned to the “Food” store, to meet up with our newest traveling companions. They were picking at the last of their food when we entered. Quicksilver looked like she was trying to hide behind the table as much as she could while still reaching her plate, her eyes fixed downward. Her ears flicked when Dusty spoke, but she didn’t look up.

\leavevmode\llap{“}We’re about set to head out, if you two are ready,” Dusty said to Silverline. “Are you both good to make the trip? We might be able to find a cart if walking will be a problem.”

\leavevmode\llap{“}No,” Silverline quickly replied, then more quietly, “No, thank you. We can walk.”

Dusty frowned, but nodded. “Okay, then.”

Ten minutes later, we were assembled at the town gate as it slowly ground open. The days of travel ahead loomed large before us. My legs practically ached at the thought of it, made all the worse by the ever-increasing load I was carrying.

But at the same time, I had a substantial amount of currency, at least one friend, and once we’d escorted our charges to Mareford, a complete lack of commitments tying us down. While I had almost nothing in the way of leads towards any remnants of my hive, Starlight seemed fairly impulsive and suggestible. It shouldn’t be too hard to convince her to go the way I wanted.

It was time to move beyond simply struggling to survive, and on to accomplishing something useful.

As we set out past those gates and into the Wasteland once more, each step I took was one step closer to my kin, wherever they might be.

{\br}%
I have no idea what Rotwater Creek might have been called before the end of the world, but the name seemed perfectly fitting for what it had become. The thin trickle passing through the ravine looked more like sludge than water, and the dead brush and occasional bone down there suggested that it was anything but healthy. The ravine itself seemed little more than a deep crack, splitting the rugged hills our thin trail passed through. It was maybe fifty feet across, and not even half that deep. A bridge of crudely lashed timbers crossed it, looking ancient and ramshackle.

Beyond it, partially hidden behind the slope of a hill, lay the charred and broken remains of a wagon. A few crows gathered there, cawing idly.

Dusty lowered his binoculars and sighed. His cigarette rolled between his lips as he contemplated the situation. After several seconds, he looked around, his eyes finally alighting upon the ridge beside us.

\leavevmode\llap{“}Starlight, set yourself up there, get good eyes out over the path ahead.” When she nodded, he looked to Silverline. “You two can stay with her. We just need to check it out real quick, then we can all go around it.”

\leavevmode\llap{“}Wait,” Silverline said, and turned to her daughter. Her voice was quiet, gentle, and perfectly motherly. “Stay with Miss Starlight, honey. You’ll be safe with her.”

Starlight’s smile vanished as she gave a grim, serious nod in reply. Quicksilver simply looked up to her mother, eyes wide and nervous, but she swallowed and nodded.

\leavevmode\llap{“}I’ll be right back,” Silverline said, wrapping her daughter up in a hug. “I promise.”

When she finally released her daughter again, Silverline turned to Dusty. “I’m coming with you.”

Dusty chewed on the end of his cigarette. “You sure you—”

\leavevmode\llap{“}Yes.”

After a moment of silent consideration, Dusty slowly nodded. “All right then.”

We waited while Starlight climbed the ridge, with Quicksilver reluctantly following. She kept glancing back to her mother, who held a weak, shaky smile. Eventually, Silverline spoke again. “I don’t want to drag her through all of this again,” she said, her fragile smile holding, “but I need to take care of things. I need to…”

Dusty and I both nodded, silent. Sickle just snorted, and I couldn’t help but read a sense of disdain into the simple sound.

Once Starlight was in place, we moved forward.

As we followed the uneven path, we came around the slope of the hill, revealing the vehicular carnage ahead.

Several wagons lay, gutted by flame. Giant water-tanks, with wooden frames and massive wheels to carry them through the desert, lay on their sides beside the path, destroyed. A few bullet holes marred the metal surfaces, while the impact with the ground looked to have split them both open. The dirt was still dark and muddy around them.

And then there were the bodies.

I suppose it was some small comfort that the scene could have been much worse. They weren’t decaying, butchered corpses, like we had found at the Army depot. They weren’t even like some of the raiders from a few nights back, looking almost alive except for the vacant, unseeing stares and splotches of blood. The ponies of the caravan had been picked over by scavengers, leaving little more than discolored bones among the ragged tatters of barding and bits of flesh. A few crows still lingered, picking at the scant bits of meat that remained. They cawed loudly before moving away, keeping their distance from us.

Beside me, Silverline was breathing deep and steady as she walked with us.

On my other side, Sickle had a faint, almost content-looking smile. I had to suppress a shudder.

I guessed about ten ponies had died there, though it was hard to tell for sure. Bones were scattered around. I spotted a partial skeleton at the edge of one of the ruined water tanks, as if the pony had been crushed by it.

The largest collection of bones was by the front-most of three wagons. Spent casings lay among the bones, and the wagon itself, while not burnt like the others, was riddled with holes. The mercenaries hired to guard the caravan may have left them to their fate, but some of these ponies had been armed, and they had fought back. Unfortunately, Gutrip’s raiders had prevailed.

More disturbing were the traces left by those raiders. A pole was planted in the ground beside the wagon, with a skull impaled upon it and several bones scattered around. Several ropes were tied to various points on the wagon and the wrecked water tank nearby, hanging slack. Most of the loops were vacant, but a few still held bones that hadn’t been pried away. Whatever vile display the raiders had established had been mostly undone by scavengers feeding on the remains.

While Sickle walked right up to the wagon and started searching, Silverline held back. She took a few deep breaths before turning and walking. Despite the faint tremble in her jaw, there was a look of desperate determination to her expression; a hardness in her eyes that threatened to crack at any moment, but which held firm.

She didn’t walk toward any of the wagons, but toward a low ridge a short distance away from the ruined caravan.

As we approached, I soon saw the signs of prior travel. Dead brush lay broken and hoofprints marred the sandy dirt, indicating the passage of several ponies. Silverline followed that trail.

Coming over the ridge, we saw the remains of a simple camp. A few rocks and dead logs were pulled around the ashes of a long-dead fire, likely to serve as places to sit. Two skeletons lay there. One was set beside the makeshift seating. The other was a bit more scattered. While the limbs and skull had fallen to the ground, the pelvis and ribcage were still hung up on a spit running over the crude fire-pit.

My stomach turned at the implications.

Before anyone calls me out for hypocrisy, there’s a huge difference between a changeling feeding on ponies’ emotions and what those raiders did. I try my best to avoid bringing harm to the ponies I feed upon. In fact, I generally try to help them, both before and after.

And no, that one raider mare doesn’t count.

Silverline hesitated for a moment before continuing on toward the camp, though her pace had slowed. She slowed further as she moved between a couple dead logs, practically creeping up on the fire-pit. She finally stopped, staring down at the pony’s skull. Tears were slowly running down her cheeks as she lifted a shaking hoof and reached out, gingerly touching it.

She remained silent, except for her ragged breathing. I carefully stepped up to her, hoping I could express some sympathy, rather than leaving her silent and alone. I spoke, quiet and gentle. “Who is it?”

She swallowed, slowly brushing her hoof down along the top of the snout. When she spoke, her voice was hoarse. “My husband.” She lowered her hoof to the ground again, blinking away the tears. “I-I had to come, to… to put him to rest.” She swallowed, her eyes slowly moving to the other skeleton. “And the others, too.”

A tremble passed through her, but she huffed out a deep breath. Then she knelt down, gingerly reaching down to pick up her husband’s skull.

When she tried to pull down the spit, I moved in without a word to take the other end. Dusty and I helped her gather up the bones, and she pulled out her blanket to carry them. We set them down gently, respectfully.

Once both skeletons had been set on the blanket, Dusty helped her carry it back to the ruins of the caravan, to the wagon where most of the ponies had fallen. We spread out, slowly gathering all the remains and setting them together in a slowly growing pile. Even Sickle helped, though in a more aggressive, physical fashion befitting her: she slammed her shoulder against one of the fallen water tanks and lifted it enough for Dusty to pull out the bones of the crushed pony.

She also smashed the front-most wagon with several powerful bucks, allowing Dusty and myself to retrieve several pieces of unburnt wood. We leaned those across the small pile of bones.

We sat back, waiting for Silverline. She remained still, continuing to stare down at the skull, while tears silently rolled down her cheeks. Finally, she took a deep, shaky breath, lifting the skull and placing it atop the pile.

When she stepped back, she opened her mouth to speak. She only produced a croak before clamping her mouth shut, a small tremor passing through her. After a moment to regain her composure, she looked to Dusty. That time, she simply nodded.

Dusty stepped forward with his lighter. Soon, the kindling at the base of the pile caught, the flames quickly spreading through the funeral pyre.

Silverline sat there, watching the flames rise. Her breathing was heavy and shaky. Then her breath caught, her fragile stand of determination crumbled, and she broke down sobbing.

I scooted in closer, lifting a foreleg around her shoulder to comfort her. I was a little worried that she might pull away, but instead she turned to me, throwing her forelegs around me and burying her face in my chest and muffling her cries. I held her close, gentle and supporting.

I could sympathize with her, especially as I watched the small funeral pyre burning. It all felt so familiar. The thought brought a lump to my throat, and I had to blink back tears.

I hate to admit it, but a tiny part of me wanted to think that she had it easy. She had lost one of the ponies closest to her, and had watched her daughter suffer horrible abuse, but they were both still alive. Everyling I had known was almost certainly dead, including my queen. I had nobody to turn to, and even if any of my hive survived, I had no idea if I’d ever find them. She had her daughter and, presumably, all the other ponies back in Mareford.

But did she, really? They had been betrayed by ponies that were supposed to protect them, and it was quite possible that some of the ponies involved were still there in Mareford. Would the town be a comfort to them, or would that knowledge always be lurking in the background?

That thought clung to my mind as I held her shaking shoulders, offering what sympathy and comfort I could.

{\br}%
After many long minutes of sobbing and shaking, seemingly without end, Silverline pulled away. She still breathed heavily, her hooves quickly wiping away tears, but her crying had ended almost as abruptly as it had started.

\leavevmode\llap{“}Thank you,” she said, her voice hoarse, and she took a couple more deep breaths before continuing. “We can go.”

Dusty rose to his hooves, his eyes full of concern. “You sure you’re ready?”

\leavevmode\llap{“}Yes,” she said, giving another wipe at her eyes and a final sniffle before standing as well. “I need to get my daughter home.”

He considered her for a couple more seconds before nodding. “All right. Let’s go back to them, and we can get going.

Her pace was slow and shaky, and I caught a few more sniffles as we made our way back. Despite that, she kept on going. The only time she stopped was when we neared the bridge. It was just a couple seconds as she breathed in and out, deep and slow, her eyes closed. Then her eyes opened and she continued on, with that same sense of steady determination. She even managed a small smile as her daughter looked to her, though I had a feeling it was a far more fragile expression than she was letting on.

She helped Quicksilver to her hooves, murmuring quiet and supporting words, and soon we set out again, giving the ruins of the caravan a wide berth.

{\br}%
It was around noon of the next day, about halfway into our trip, when a sound softly crept over the quiet wasteland around us. It was faint, barely audible, just a soft, repetitive thumping sound. It was too soft and regular to be gunfire, but I couldn’t immediately place it. I barely even heard it, and probably wouldn’t have if I hadn’t noticed how alert Dusty had become. His ears perked up and he lifted his binoculars to scan the horizon.

I looked as well, but all I could see was barren rolling hills. The faint sound echoed around them, indistinct enough that I couldn’t tell for sure what direction it was coming from. Already, the sound was fading.

\leavevmode\llap{“}What is it?” I asked.

Dusty lowered his binoculars, sighing. “We might have company soon.”

Starlight started to bring around her Lancer, but Dusty quickly interrupted her. “Don’t. Keep your weapons slung and holstered. They’re not raiders or anything, but they tend to be a bit twitchy about armed ponies.”

She slid her weapon back into place along her back. “And who exactly are ‘they’?”

Dusty was quiet for a moment, looking as if he were debating whether he should wait for some dramatic reveal or be practical and explain things. In the end, practicality won out. “Mareford Militia. Probably the only organization worthy of being called a professional army. They’re about the last ponies you want to piss off. Good news is, they tend to be pretty reasonable, and they keep travelers near Mareford safe.” He glanced to Sickle. “So unless they mistake Sickle for an actual raider and try to ambush us, we’re good.”

\leavevmode\llap{“}Gee,” Starlight said, rolling her eyes, “I feel so much safer. How could they \textit{ever} mistake Sickle for a raider?”

Sickle rumbled deeply, muttering. “Probably because they’ll see me ripping your fucking head off if you keep that shit up.”

\leavevmode\llap{“}Ooh, scary.”

Dusty snorted. “Oh, shut up, both of you. Let’s at least get to town without killing each other.”

Sickle and Starlight exchanged sneers, but remained silent.

We continued walking.

Almost half an hour later, I was starting to think that our “company” wasn’t going to show, when a distant voice called out. “Is that Dusty Trails?”

Dusty halted, looking to our side. Beside the path, the rugged terrain rose in a ragged series of hills and ridges. Maybe a hundred yards away, if that, a pony had risen up, one hoof raised in a wave.

\leavevmode\llap{“}Yeah, it is!” he shouted back. “Is that Bitsy?”

The distant pony’s hoof dropped. “It’s Two Bits, you jackass!” Despite the harsh language, I saw the white of teeth as he grinned, and I swear I heard a hint of laughter.

It was then that I noticed another pony, lying almost entirely concealed behind a rock. I could only see a little of his head. Most of that was obstructed by his gun, resting on a bipod, and the scope mounted atop it.

Then Two Bits looked around, calling something out and gesturing, and several more ponies appeared. They stood from the various bits of dead brush, rocks, and little ridges they had been hiding behind, revealing the multitude of weapons that had been readied against us. Soon there were a half dozen ponies following him down the slope toward us, and while they were no longer leveling their guns at us, they were still ready to be used at a moment’s notice.

As they approached, I could finally appreciate just how well-equipped they were. Their barding was just like Dusty’s, adorned with all manner of pockets and pouches, dyed a mottled sandy brown to blend in with the ground. Unlike Dusty, they also wore light helmets, painted in the same colors, and were either wearing goggles or had them pushed up on their helmet. A few even wore cloth wrapped around their faces, concealing brightly colored coats.

Their limbs were covered, too. Unlike Dusty, there was a thick bulge on the left foreleg of every one of them, with a cloth cover strapped in place. The only thing I was aware of that was of that size and worn in that location was a PipBuck, which made me immediately wary; I wasn’t entirely certain what their threshold was for declaring something hostile, and how much deceit might cross over that threshold.

A quick glance over at Dusty revealed that his garments had a similar adaptation, but without the bulk of a PipBuck beneath it. Instead, the fabric was folded in, and the covering flap wrapped around the leg to strap securely in place, simple and insignificant enough to blend in amongst the other straps and pouches.

And of course, these new ponies were armed, and not with cheap pipe rifles. Most had rifles that looked much like the late-war Equestrian Army model, though with simpler grips and stocks. Instead of those fancy plastic stocks, of which I was only aware of due to the incredible amounts of divisive arguments they had produced, these guns had simpler metal parts. A couple ponies carried what looked to be belt-fed variants, complete with bipods, though I didn’t recall the Equestrian Army ever fielding such a weapon. One pony carried a rifle like Dusty’s, only with metal instead of wood for the stock and grips, and sporting a larger scope than the other rifles. Each pony had a pistol holstered at their side.

As if that wasn’t enough, I saw that Two Bits actually had a \textit{third} weapon, which took me a moment to recognize: a short-barreled, breech-loaded grenade launcher.

These ponies were armed to the teeth.

Beside me, Quicksilver pressed in against her mother’s side. Silverline was eying the new ponies very warily, a fact that set me on edge.

Two Bits seemed friendly enough, at least, as he walked right up to Dusty. “Well, shit. Sergeant Dusty Trails. I didn’t think I’d be seeing you again.”

While Starlight looked to me with wide, questioning eyes, silently mouthing the word, “Sergeant?” Dusty just shrugged.

\leavevmode\llap{“}Got a job that sent me this way.” His gaze dropped to the other pony’s gear, then back. “They made you a sergeant?”

Two Bits laughed, bringing a hoof up to his chest. “Oh, ouch! That hurts, Dusty. Are you saying I’m not good enough?”

Dusty cracked a smile, then offered a hoof. “I’m saying you were a private last I saw you. Congratulations.”

\leavevmode\llap{“}Hey, thanks,” Two Bits said, grinning as he shook Dusty’s hoof, though his smile turned a little sour. “Though I guess there wasn’t a lot of competition for the spot. Would you believe that I’m one of the most senior soldiers in the Militia, now?

Dusty’s eyes widened slightly, glancing around at the other ponies who had gathered loosely behind Two Bits. “That’s… not combat casualties, I hope?”

\leavevmode\llap{“}Oh, no,” Two Bits said, giving a laugh that died down to a nervous chuckle. “No. Just… ponies leaving and being replaced. You, Sharps, and Plucky were just the—”

\leavevmode\llap{“}Wait,” Starlight said, her ears shooting up. “What?”

When everypony looked to her, I articulated the question Starlight had been thinking. “Did you say Sharps?”

\leavevmode\llap{“}Yeah,” Two Bits said, looking over us with a raised eyebrow. “Why, you know him?”

\leavevmode\llap{“}Uh, kinda,” Starlight said, awkwardly rubbing one leg against the other.

\leavevmode\llap{“}He was in the same caravan we were in,” I added. “The one that got wiped out by raiders.”

\leavevmode\llap{“}Oh.”

A moment of silence followed. In the middle of it, Dusty’s eyes glanced down to my rifle, then back to meet my eyes, subtly cocking an eyebrow. I was naturally nervous about what he might do with the knowledge that I was carrying his deceased colleague’s weapon, but I also recognized that he was being very subtle in how he asked. I gave a tiny nod in answer.

\leavevmode\llap{“}Well, shit,” Two Bits said, shaking his head. “I’m sorry to hear that.” He paused, then gave a faint, weak chuckle. “Even if he was kind of an asshole.”

\leavevmode\llap{“}Yeah,” Dusty said, nodding along.

After another moment, Two Bits looked up again. “So, you said you’re in the area for a job?”

\leavevmode\llap{“}Oh, yeah,” Dusty said, inclining his head toward Silverline and Quicksilver. “These two ladies hired me to escort them home.”

Two Bits glanced over at them—Silverline moved protectively in front of her daughter—then gave Dusty another questioning look. “So… what, you’re a mercenary, now?”

Dusty shrugged. “At least I get to pick my jobs.”

Two Bits blinked, then sighed, his ears drooping just a tad. “Yeah, I hear you there.”

\leavevmode\llap{“}Anyway,” Dusty said, “I’m glad there was someone I knew on the team. Looks like you had quite the warm welcome set up there.”

\leavevmode\llap{“}Oh!” Two Bits chuckled. “Sorry about that. We spotted that big armored one from miles out. We just wanted to see who you guys were and what you were doing, since… well, she kinda looked like a raider.”

Sickle snorted. “And you look like a walking shitstain.”

Two Bits blinked at her, frowning for a moment before giving Dusty a flat look. “Wow. Your marefriend’s kind of a bitch.”

Dusty sighed, which, unfortunately for him, gave Sickle enough time to reply first.

\leavevmode\llap{“}It’s ‘cause he ain’t been satisfying me in bed, lately,” she said, a cruel grin showing under her muzzle.

\leavevmode\llap{“}Oh, shut up, Sickle!” Dusty snapped, then turned back to Two Bits. “She isn’t my marefriend. Hell, I’m not sure I’d even call her a friend at all. She’s just working with us, though I’m still not sure why.”

\leavevmode\llap{“}Sickle, huh?” Two Bits said, looking her over with a critical eye, and I swore I caught a faint hint of color dancing in his pupils. “Charming name. If I go back to base and look into that name, I’m not going to turn up anything unsavory, am I?”

\leavevmode\llap{“}Not out here,” Sickle said. Her grin returned. “Not yet, anyway.”

\leavevmode\llap{“}Don’t even start that shit,” Dusty said.

\leavevmode\llap{“}Fuck you, Dirt.”

Two Bits looked back and forth between the two of them. “Oookay. Just don’t cause any trouble while you’re in Mareford territory, or we’ll have to put a stop to it.”

Sickle sneered. “You’re going to need a bigger gun.”

\leavevmode\llap{“}That, we can do,” Two Bits said, before looking back to Dusty. “So, hey, since you’re here, did you come through Rust or thereabouts?”

Dusty sighed, then nodded. “Yeah. You’re going out to check on the water caravan, aren’t you?”

\leavevmode\llap{“}Yeah,” Two Bits said, his ears sagging again. “So something bad did happen.”

\leavevmode\llap{“}Afraid so. Raiders hit it at the Rotwater crossing. Wrecked the caravan.” His voice lowered a bit. “Killed everypony but these two.” Two Bit’s attention immediately snapped over to Silverline and Quicksilver, but Dusty brought it back just as quickly. “And Bitsy, the mercs that were hired to guard them? They split just before the raiders showed up.”

Two Bit’s eyes went wide, his expression slack. “...You’re shitting me.”

\leavevmode\llap{“}That’s what they told me,” he said, inclining his head again. “And before you ask, their story checks out. I looked over the scene myself. The caravaners tried to put up a fight, but there was no sign of guards. They would have at least inflicted some casualties among the raiders. That, and somepony told the raider leader where and when to hit the caravan, and that there wouldn’t be any guards.”

\leavevmode\llap{“}Shit,” Two Bits said. His gaze was distant for a moment as he thought. “And… any idea where we could find this leader?”

\leavevmode\llap{“}He’s dead,” Dusty said. “We wiped out his whole gang.”

Sickle chuckled. “Gutrip got gutted.”

Two Bits was slowly nodding. “We need to report this. This is… troubling.” His focus returned to the group, and specifically to Silverline. “You were in the caravan?”

She nodded, though one of her hooves inched back. Her unease with the situation was clear.

\leavevmode\llap{“}My commander would like to talk to you, then,” Two Bits said. “We can give you a lift back to Mareford. It’s a lot quicker than walking.”

She hesitated, glancing at Dusty.

\leavevmode\llap{“}Bitsy’s a friend,” he said. “I trust him. Still, it’s your decision. You hired us, after all.”

She frowned a little. “I’m not even paying you anything.”

Dusty smiled. “Hey, we both agreed to a contract. It’s a bit late for you to be complaining about how much you’re paying for our services.”

She looked at him for a full second before giving a faint snort of amusement and a momentary smile. Finally, she looked back to Two Bits. “Thank you, but I think I’ll stay with Mister Trails.”

\leavevmode\llap{“}You sure?”

She nodded.

\leavevmode\llap{“}Well… okay then,” Two Bits said. He considered them for a moment before turning back to one of the ponies arrayed behind him. “Call Vulture for a pickup.” He gestured off to the left of us. “Just north of the path should be good.”

The mare he had spoken to nodded, then turned and walked off on three legs, while raising the fourth, with its cloth-covered bulge, to her face. “Vulture, Ground.”

Whatever she said next was lost behind Two Bit’s voice as he spoke to Silverline again. “Come by the barracks once you’re back in town. Ponies need to know what happened out here.”

She nodded.

Two Bits turned to Dusty. “Was good seeing you again, Sarge. We need to get going, though. We should have been out here days ago, but they only cleared us to go searching today. We need to go check on what you said, then get word of this back home.” He gave a lopsided smile. “No offense. I believe you, but you know how it goes.”

\leavevmode\llap{“}None taken, Bitsy.” Dusty reached up, clapping the other pony on the shoulder. “And keep an eye out. I don’t know who those mercenaries were, but if they hear somepony’s digging around the caravan, they might try to do something about it.”

\leavevmode\llap{“}Banger.”

Dusty blinked, having apparently misheard Two Bits’ statement in the same way I did. “Pardon?”

\leavevmode\llap{“}Banger,” he repeated. “He was the leader of the merc team. Don’t know if that’s his whole name or a nickname or what. Thought you might want to know.”

\leavevmode\llap{“}Yeah,” Dusty said, nodding. “Yeah, I do.”

The sound from before had returned. The distant, barely audible sound steadily grew louder by the second, until the rhythmic, repetitive thumping was quite clear.

The source was another old-world relic, one which skimmed the top of a ridge a few hundred yards away before arcing slowly through the air. I’d rarely seen a whirligig before, and this was one of the big ones; a Griffinchaser IV or V, I think. I found myself wishing I had paid more attention to those aerial oddities. While they had been generally unimpressive compared to sky-wagons, there was something remarkable about seeing that pony-powered contraption flying through the air, like a phoenix rising from the destruction of its world.

The whirligig yawed to the side as it slowed, settling neatly into a patch of flat ground a short distance from the path. As Two Bits’ team hustled toward the vehicle to join the ponies already crewing it, he called out one last time. “See you around, Dusty! And look me up when you get to town. I’ll buy you a drink!”

\leavevmode\llap{“}I’ll look forward to it!” Dusty called back, and waved.

The ponies piled into the back of the whirligig, and moments later the vehicle lifted free of the ground, its nose dipping as it accelerated away, back the way we had come.

We watched silently as the old-world contraption flew away, until Starlight finally broke the growing silence.

\leavevmode\llap{“}Okay. Spill it.”

She was staring at Dusty, who frowned. “There’s nothing to spill.”

\leavevmode\llap{“}Oh, yeah, sure,” Starlight said with a sarcastic roll of her eyes. “You were just part of some special military unit roaming the Wasteland with a flying machine and heavy weapons, and now you’re out on your own doing small-time jobs. So come on, spill.”

He sighed, turning to walk down the path, but Starlight kept right on him. “Dusty!”

\leavevmode\llap{“}Look,” he said, his jaw tense. “I just wanted to help ponies. That’s why I joined the Militia. That’s why I became a Ranger, like those ponies. Only it started to become less about helping ponies, and more about helping a few \textit{specific} ponies. I didn’t like where things were going, so I left.”

We walked along the sparse trail, trailing behind Starlight and Dusty as the pair talked. “Okay,” Starlight said, nodding. “So what happened?”

Dusty’s jaw tightened a little more, but after a moment it relaxed, and he sighed. “It pretty much all comes down to Big Gun. He’s always been an ambitious asshole. Him and his twisted little marefriend, Wild Runner. They got ahold of this old Ironshod factory when they were young, and Big Gun used some contacts to get the stuff he needed to get some of the equipment up and running. Long story short, Gun and Runner became the Wasteland’s biggest firearm and ammunition producers.

\leavevmode\llap{“}It’s not all bad. It means the Mareford Militia has the best guns and plenty of ammunition for training. It’s why we… why \textit{they} get so good at what they do. Rangers probably fire more ammunition in a month than most mercs do in a lifetime, and that’s just training. It also brings a lot of business to Mareford. It’s made the town the biggest and safest place in the Wasteland, or at least this little part of it.

\leavevmode\llap{“}Problem is, it also means Big Gun has a lot of influence in town. He’d lean on ponies, and they’d usually do what they could to accommodate him. The problems really started when he started getting influence over the Militia.”

He grumbled something, pausing to fish out a cigarette and light it. Once it was lit, he took a long, unusually deep drag.

\leavevmode\llap{“}Normally, we’d keep settlements safe, run off raiders, that kinda thing. ‘Cept then, things got weird with some of the nearby settlements. First, Stinkpit takes one of Big Gun’s traders hostage, then Hayseed opens up on a Mareford caravan. Mareford Militia shows up, shuts things down, and in the end, they become more of Mareford’s territory, run by ponies that won’t “stab us in the back”. Except, wouldn’t you know it, Big Gun’s suddenly getting the supplies he needs for a fraction of the cost. Stinkpit was a rotten little place, but it wasn’t the raider sanctuary we were led to believe, and the ponies in Hayseed all said it was the Mareford caravan that opened up on them.”

Dusty snorted. “It didn’t sit well with us. There was lots of grumbling, but most ponies just went along with it. Me, I didn’t like it. That shit wasn’t why I’d joined up. So I resigned.”

Starlight mulled that over for a minute as we walked. “You don’t think the same thing is going to happen to Rust, do you?”

\leavevmode\llap{“}Rust is pretty much the metalworking capital of the region,” Dusty said. “Not to mention the best nearby source of both steel and drinking water. The water caravan runs almost constantly, and it’s probably Mareford’s largest single expense.”

Starlight frowned. “Shit.”

Dusty grunted in agreement, but added, “I’m not sure it’s related, but Big Gun and Wild Runner have been involved in some shady stuff before. If they’re in charge of Mareford, who knows what kind of shit they’re getting into now?”

We continued on, with this new information weighing heavily on our minds.

{\br}%
The rest of the trip was uneventful, save for when the whirligig flew past us in the opposite direction later that evening.

By the next afternoon, we could see the angular shapes of ancient buildings on the horizon. Those slowly drew closer throughout the rest of the day, giant skeletons of centuries-dead buildings, stretching up into the grimy sky. I found it particularly depressing, and remarkably eerie. Starlight told me it had been hit by a balefire bomb at the end of the war, but I was struck by how many buildings still stood. The balefire had left a giant crater on the other side of the city, she said, but it seemed the necromantic fire that had swept through the city had simply burned all the life from the place, rather than leveling everything.

Hundreds of thousands of ponies had likely died there, while those towers loomed over it all like giant tombstones.

The town of Mareford was set along the very southern edge of those ruins, where the devastation was less severe.

And I must say, if I hadn’t been so familiar with the height of Equestria prior to its fall, Mareford would have been quite impressive. The place was big, covering quite a bit more ground than even Paradise Beach had. A tall wall ringed the town, mostly built between existing buildings, with various towers and walkways along its length. Almost all of the buildings that had once been set outside those walls had been torn down, leaving nothing more than scattered foundations. The few exceptions were the occasional farm buildings, set alongside the sparse fields.

The agricultural development was meager even compared to Appleloosa, but I found myself happy to see it. It was progress.

The farmers tending those thin fields paid us no mind as we walked along what had, at some point, turned into a “proper” dirt road. Militia guards manned the wall and lookout towers, and I saw at least one heavy weapon partially concealed within the upper levels of an old, ruined apartment building.

To my surprise, several motorwagons were waiting just outside the gates, under those guards’ watchful eyes. All of them bore the signs of the Wasteland, with rusted armor plates welded onto their frames to turn what had originally been open-top vehicles into something well-protected and enclosed. The two smaller wagons each had a roof-mounted machine gun, crewed by ponies poking up from the roof. The much larger, heavy-cargo motorwagon had similar weapons at each end, and at least half a dozen individuals—including a pair of griffons—mounted atop it, all carrying personal weapons.

There was a fourth vehicle that I wasn’t sure how to classify. It looked like somepony had simply taken a particularly big motorwagon motor and affixed a large wheel at either end. It was long and narrow, and made the cloth-wrapped and goggle-wearing pony straddling the contraption look small in comparison.

I was later told it was called a motorcycle, as some sort of bizarre portmanteau of motorwagon and bicycle. Personally, it seemed immensely impractical, potentially suicidal, and likely very fast.

A few of the caravan guards eyed our approach. One of the ponies in the smaller wagons swung his machine gun over in our direction, though the barrel remained pointing up into the air. Given the excessive amounts of firepower at their disposal, and the Mareford guards nearby, they didn’t have much to worry about.

\leavevmode\llap{“}That’s the Trotsen convoy,” Dusty said, tipping his head their way. “Don’t worry about the guns. They’re very protective of their wagons, but they’ve always been pretty decent types.”

He followed it up by giving a casual wave, and a few of the caravan guards returned the gesture. Even the one who had turned his gun toward us looked pretty relaxed, leaning back against the rim of the roof opening.

At the gate, Dusty exchanged pleasantries with another armed pony who recognized him. The other guards relaxed as the two greeted each other, and after a quick chat, we were on our way past the multi-story-tall gates and into Mareford.

Stepping through the gates, I got my first good view of the town itself. A paved road formed the main thoroughfare, surrounded by multi-story buildings. While most of the buildings were from before the megaspells, many appeared to be newer. Additionally, while it was apparent that the buildings had been built or patched with salvaged materials, it looked like there had been some very skilled ponies working on them, ponies who knew how to make something \textit{good}, rather than something that was simply good \textit{enough}.

It wasn’t quite as upbeat and colorful as Gemstone, but it was clean and well-maintained, and it \textit{felt} like a pony town, even if that feeling was somewhat faint. There were still all the problems of the Wasteland out there, past the walls and out of the sight of their well-equipped guards. Inside the walls, however, were hundreds of colorful ponies living in relative comfort. Many were working or moving supplies around, some were stopping by modestly stocked shops to trade, and a few stopped in the streets to chat.

It was pleasant, and it almost brought a smile to my face.

Almost, I say, because of the suspicion that something dark lingered behind it all. It’s something I was quite familiar with, well before stepping out into the Wasteland. While most of the ponies of the old Equestria were nice, friendly, loving sorts, Infiltrators became intimately familiar with the few unpleasant ponies that lurked in the background. The ponies who fed on the war and strife for their own gain. They were rare, but they were still there. I imagine the Wasteland is the sort of place where that kind of pony can thrive.

Silverline took the lead, guiding us down the road and past the various ponies moving about. The road was busy with ponies wearing packs and hauling carts, loading and unloading goods from the caravan sitting outside the gate. Most paid us no mind. A few curious looks came from ponies tending the occasional shop or passing by, though most were focused more on Sickle than Silverline and Quicksilver.

We soon turned off the main road, leaving the busy line of ponies behind. Our hooves clopped sharply on the paved street, criss-crossed with patched cracks from the years of wear. Instead of the shops and businesses that lined the main street, we passed buildings that had been converted to apartments, and even the occasional house. A few ponies were still out and about, though more relaxed than those that had been hauling goods. There was even a small field, where several younger ponies kicked around a ball that looked to have been patched so much that I couldn’t tell if there was any original material still present.

Finally, Silverline came to a halt before a group of single-story houses. She stared at one for a few moments before looking back to Dusty.

\leavevmode\llap{“}This is my place. You, uh… you can stay here, if you’d like.”

\leavevmode\llap{“}Probably be a bit crowded with all of us,” Dusty said, smiling. “We’ll just hit an inn, leave you two with your privacy. Thanks for the offer, though.”

\leavevmode\llap{“}Oh, uh… I guess…”

\leavevmode\llap{“}Is Cinder Block’s Inn still running?”

Silverline blinked, then looked off in thought for a moment. “Yeah, I’m pretty sure it is.”

\leavevmode\llap{“}Ah, good,” Dusty said, nodding. “Always liked him. We’ll probably get a room there, if you need to get ahold of us.”

She nodded, blinking a few times before speaking. “Thank you, again.”

Dusty casually shrugged. “Glad to help.”

Goodbyes were brief, and soon the pair were walking off towards the steps of their home. We stood back, watching them go.

It felt good, having been able to help them. Not good enough to make up for what had happened to them, but there was a sense of satisfaction, that we’d made a difference, no matter how small it might have been.

And then Sickle spoke up, with her deep, rumbling voice. “The mom’ll do fine. The kid’s fucked, though.”

Dusty groaned. “Way to spoil the mood,” he grumbled as he turned away, walking back the way we came.

Starlight leveled a glare at her. “What the hell, Sickle? Seriously?”

\leavevmode\llap{“}What?” Sickle shot back, looking down at her. “I’ve seen plenty of ponies get raped ‘n shit. I know how it goes. They either harden the fuck up and deal with it, or they learn to be good little victims the rest of their lives. Pretty clear which is which, and whining about it ain’t going to change shit.”

Starlight continued to glare as Sickle turned around to follow Dusty. “And what about you, huh?” Starlight asked. “You ever rape a pony?”

\leavevmode\llap{“}Naw,” Sickle said, without even looking back. “I was one of those \textit{nice} raiders that never hurt anypony.”

Starlight stayed put, eyes narrowed to slits as she watched Sickle walking away. She remained perfectly still and silent until I stepped up beside her, at which point she hissed between clenched teeth. “It’s so damn tempting to just shoot her and be done with it.”

I lifted a hoof, placing it gently on her shoulder, and the tension fled her. She turned her head, looking to me.

I couldn’t think of anything useful to say. Instead, I just gave a faint, lopsided smile. “Not in town.”

She snorted out a weak laugh, then sighed, and we both set out to catch up with Dusty.

{\br}%
Cinder Block’s Inn was a big place, larger than Mustard’s, and occupying a properly built reinforced concrete building rather than a crudely welded metal structure. The first floor served as a bar, and it was clear that it was a reasonably popular place, with close to twenty ponies enjoying drinks and meals. It looked like the place had been a bar before the war, and while the colors had faded from the walls, the current owner had done a good job keeping the place clean and in good repair. The air was full of talk and happiness, set to the backdrop of a static-laced and vaguely familiar tune played on an old radio at the bar.

Dusty arranged for a room for us, a large one intended for traders and other traveling groups. We made our way up, claiming our cots and unloading our supplies. Then we were heading out again.

The town hall and mayoral “mansion” were the same building, a prestigious-looking three-story building set behind a small, paved courtyard. Once we stepped into the main lobby, a young buck behind a desk looked up to us; the reflexive smile faltered as he saw Sickle, but he recovered quickly. “Welcome to town hall. Is there something I could help you with?”

\leavevmode\llap{“}Yes,” Dusty said as he approached the desk. “Is Big Gun here?”

\leavevmode\llap{“}He’s in his office. Should I let him know that you’d like to speak with him?”

\leavevmode\llap{“}No need,” Dusty said, smiling as he passed the desk. “I’ll tell him myself.”

The young pony’s smile slipped away as we all walked right past him. “Um, but, you can’t… uh…”

His half-formed protests ended as Sickle passed close to him, her metal-clad head turning to keep her gaze locked straight on him. He backed up, almost tripping on his chair.

Dusty knew exactly where he was going. He led us up the stairs at the back of the lobby, turned, and walked up to a set of unmarked double doors. He threw them open, to the surprise of the small group of ponies beyond.

He leveled a glare at one of them as he entered. “What the hell is going on, Gun?”

The unicorn seated on a couch nearby had a hard look as he turned, shifting his balance forward as if preparing to rise and fight. Fortunately, the pistol holstered at his side remained in place. Standing beside a huge desk, a teal mare watched us enter, a smirk spreading across her face. She was also a unicorn, if a good deal older than the tan stallion, though her wiry frame looked just as fit.

The pony Dusty had addressed sat behind that desk, his face lit by the screen of a terminal. He was the oldest of the lot, probably in his fifties, and the one earth pony in the room before our intrusion. He frowned across the desk at us. “Mister Trails, isn’t it? Would you mind telling me why you’re leading a group of armed mercenaries into my office?”

\leavevmode\llap{“}Because I want some answers,” Dusty replied, storming right up to the end of the desk to glower at the older pony. “Like why you hired a bunch of worthless mercenaries to guard the water caravan. Mercenaries that left them high and dry when the raiders showed up.”

Big Gun stared at him for several seconds before standing. The terminal’s glow winked out as he pressed a button, and he followed up by gesturing the same hoof at the stallion seated on the nearby couch. “Mister Trails, I’d like to introduce you to Fireline, leader of those ‘worthless mercenaries’, as you call them. He and I were just discussing how to uncover exactly what happened before you barged in and interrupted us.”

Dusty didn’t even look at the other pony. “I already know what happened, Gun. You hired a bunch of mercs instead of using the Militia, and \textit{somepony} got them to abandon those ponies—right after telling a bunch of raiders when and where to hit them.”

\leavevmode\llap{“}So I’ve heard,” Gun replied coolly. “Though the Rangers sent to investigate weren’t able to find anything conclusive, Fireline has expressed his confidence that the squad he assigned to the caravan should have held off even a large raider band, had they still been present. Isn’t that correct?”

The unicorn stallion nodded, his expression wary as he watched us. “Yes. Six experienced soldiers, well rested after a stay in town, and equipped with the best arms and armor available. They should have been able to hold off any raider gang, or if not, inflict a crippling number of casualties upon them. It does suggest that they weren’t present at all.”

\leavevmode\llap{“}We already know they weren’t ‘present’,” Dusty snapped, then looked to Gun again. “And why are you hiring a bunch of outsiders instead of using the Militia? You know, the ponies whose \textit{job} it is to protect those ponies?”

\leavevmode\llap{“}Because the Militia is stretched too thin protecting the settlements under our care. Perhaps if a significant number of their ranks hadn’t taken after certain unreliable ponies and abandoned their pledge, we could have afforded the soldiers to keep the caravan safe, but the Militia simply doesn’t have the ponies to be everywhere at once.”

Dusty bristled, pointing a hoof at him. “Don’t you even try to lay that shit on me, Gun.”

\leavevmode\llap{“}When you come in here, accusing me of failing the very ponies you walked out on?” Big Gun scoffed, raising his nose. “These were my assets those raiders destroyed, my caps that were lost, my ponies that were killed. I know you have a low opinion of me, Mister Trails, but even you know I don’t throw away resources or ponies.”

\leavevmode\llap{“}No,” Dusty said, eyes narrowed. “You just spend them like caps.”

The mare standing beside Big Gun’s desk, who had been silent this whole time, stepped forward. She had a cruel grin that reminded me of Sickle, though it wasn’t nearly as effective in comparison. “You better watch what you say, ‘less you want to try saying it with no \textit{fucking teeth}.”

\leavevmode\llap{“}Now, now, Wild,” Big Gun said. “No need for that.”

As he was speaking, the sound of hoof-steps drew our attention back to the entrance of the room, just as four Militia soldiers entered; while their weapons were slung in easy reach across their chests, their looks were more curious and wary than aggressive.

\leavevmode\llap{“}After all, I believe Mister Trails and his friends were just leaving,” Big Gun said, his eyes still locked on Dusty’s as he smiled. He spoke a little louder as he addressed the soldiers. “Sorry to disturb you fine ponies, but it seems we’ve concluded our business. Would you kindly see Mister Trails and his companions out?”

Dusty continued to glare for several seconds before snorting and turning away to stomp toward the door.

\leavevmode\llap{“}Oh, and Mister Trails?”

Dusty stopped, glaring over his shoulder.

Big Gun’s smile had vanished, returning to a more serious look. “You intend to continue pursuing this matter, I presume?”

\leavevmode\llap{“}Yeah, Gun. I’m going to find whoever it was who set those raiders on a bunch of innocent ponies.”

Gun considered him a moment longer before nodding. “Then wait in the lobby, and I might be able to help with that. If you’re going to stick your hoof in the pot, I may as well make sure it helps us.”

Dusty continued to glare for another second before giving a sharp nod and walking out. We followed after him.

He had already cooled off by the time I stepped up beside him. We walked back to the lobby in silence, flanked by the Militia soldiers.

Once we arrived there, we sat on the couches along the side wall, while the soldiers explained the situation to the pony we had brushed past earlier.

As soon as the soldiers left, Dusty called out to him. “Hey, sorry about earlier. Didn’t mean to cause you any trouble.”

The pony blinked. “Oh, uh… yeah.” He continued casting glances our way, until Sickle bared her teeth at him. He then became entirely absorbed with the papers before him.

Eventually, Dusty’s eyes drifted over to me. More specifically, to the portable terminal strapped atop my saddlebags; while I had left the food and water supplies back in the inn room, I felt much more comfortable keeping the rare and irreplaceable old-world technology on me, even if it was a bit heavy.

\leavevmode\llap{“}Something on your mind?” I asked.

\leavevmode\llap{“}Nothing,” Dusty said, sitting back. He then immediately contradicted himself. “Was just wondering what interesting information we might find if we could get into that terminal of his.”

I smiled, keeping my voice low. “I could do that.”

Dusty remained quiet after that.

It was only a couple minutes before Fireline came down the stairs. He eyed us warily as he approached, finally stopping just before Dusty. “I understand you’re a mercenary?”

Dusty frowned. “Only when I like the job.”

\leavevmode\llap{“}Good,” Fireline said with a nod. “Because Big Gun has offered a contract: ten thousand caps for the capture or death of the pony ultimately responsible for the attack on the caravan. The one condition is that I subcontract you as a… ‘reliable and morally driven’ pony independent of my own command, and split the payment fifty-fifty.”

Starlight’s eyes went wide.

Dusty didn’t visibly react at all. “And what does the job entail?”

\leavevmode\llap{“}First, we need to track down Banger. He was the pony leading the squad. If someone bought them off, he’d be the one making the deal. As for how we do that, the first step is heading to my base. We’re set up in an old army fort east of here. Some of my ponies should know enough about Banger to know where to start looking.”

\leavevmode\llap{“}And after that?”

Fireline looked off to the side, thinking for a moment before turning back to Dusty. “I’m not sure, yet. We can work out how to proceed once we know where to look.”

Dusty slowly nodded. “And when did you want to set out?”

\leavevmode\llap{“}In the morning,” Fireline said. “It’s too late to make the trip. Meet me by the south gate at ten, and we’ll head out.”

Dusty mulled the offer over for several seconds before speaking. “Okay. I’ll meet you there.”

\leavevmode\llap{“}Good,” Fireline said.

There was a silent moment of awkwardness before he turned and walked off again. With a sigh, Dusty rose to his hooves, and we followed him out.

As soon as we were on the street, and away from any other traveling ponies, Starlight stepped up next to him. “Yeah, this doesn’t seem suspicious at all.”

Dusty snorted softly. “Yeah. If Gun’s putting out a ten thousand cap reward for his own head, he’s planning something.”

\leavevmode\llap{“}You’re sure it’s him, then?”

\leavevmode\llap{“}Oh, yeah,” Dusty said. “There was only one question I had when I went in there, and he answered it, whether he knows it or not.”

I looked over to him. “You know him fairly well, then?”

\leavevmode\llap{“}Well enough to know that if you accused him of slitting a pony’s throat and he gets pissed, it’s because he didn’t do it.” He looked back to me. “But if he gets smug, it’s because he knows you can’t prove it.”

I nodded. While I couldn’t be certain if his read of Gun’s reaction was correct, if it was true, I had to respect his creativity in getting there.

Starlight didn’t approve of the implications of that, however. “So this is a trap.”

\leavevmode\llap{“}Or he’s hoping to lead us off on a wild goose chase,” Dusty said. “Maybe Fireline isn’t involved in all of this. But yeah, it’s probably a trap.”

\leavevmode\llap{“}So we’re… not meeting up with him?”

Dusty blinked. “We?”

Starlight halted, blinking as well. “Oh, uh… well, I mean, I guess we don’t \textit{have} to go with you, but I kinda want to figure out what’s going on around here, and I don’t \textit{really} have anywhere else to go, so…”

A smirk played at Dusty’s lips as she trailed off, but finally, he nodded. “Well, I could certainly use some ponies to back me up. Especially since the plan right now is to go along with Fireline in the morning.”

Starlight looked thoroughly skeptical of the plan. “Uh, I was kinda hoping to follow you \textit{not} into a trap, actually.”

\leavevmode\llap{“}I don’t plan on walking into a trap,” Dusty said. “I’m thinking the four of us go along with Fireline, and as soon as we’re out of sight of town, we stop and have a nice long chat about him and his employer.”

\leavevmode\llap{“}And if he’s \textit{not} involved?”

\leavevmode\llap{“}Hey, I said chat,” Dusty said. “Not beat or shoot or anything, just chat. If he gives us that option.”

\leavevmode\llap{“}Yyyeah,” Starlight said. I could completely empathize with her; I didn’t like the idea of threatening or hurting an innocent.

I was still going to go along with it, of course. Being an Infiltrator means doing the occasional thing you’d rather not do, and I had come to peace with that long ago. The chances of him being uninvolved struck me as practically nonexistent.

Granted, there was the small question of \textit{why} I was going along with the plan. It was another distraction. It didn’t get me any closer to my hive. But really, what option did I have? I didn’t buy Starlight’s excuse of having nothing better to do any more than Dusty had. After seeing Silverline and Quicksilver, she wasn’t going to just walk away from this, and I still needed her. Dusty, who was starting to have positive feelings for me, was thoroughly committed.

For better or worse, the quickest way to get back on track was to deal with this distraction as quickly and efficiently as possible. Better yet, I felt much more confident about dealing with this problem. Investigating, maybe even spying and infiltrating? That’s what I lived for.

Besides, I spent just as much time around Silverline and Quicksilver as Starlight did. While I didn’t consider myself as impulsive or emotionally driven as her, if this little distraction saw justice done for them, then I could consider it time well spent.

Oblivious to my own thoughts, Dusty replied to Starlight. “Hey, I’d love to know for sure if Fireline is involved before we get into this,” he said, “but we can’t really do that. All we know is he’s right in the middle of everything, he takes his orders from Big Gun, and it’s one of his guys that went missing. If he isn’t involved, then he’s the blindest merc captain in history.”

I took that as my cue to step in. “Actually, we might have a way to know before we meet up with him.”

Dusty shot me a questioning look, and I tilted my head back, gesturing to my portable terminal. Quietly, I said, “I can get into that terminal of his, see what sort of records he’s got. He might have something that gives us a better picture.”

He frowned, then shook his head. “Much as I’d like to see that, you’re more likely to get yourself shot, and give Big Gun a perfect excuse to just lock us all up.”

Starlight snorted. “What, and bursting into his office didn’t?”

\leavevmode\llap{“}Too many witnesses,” Dusty replied. “The buck out front, the Militia soldiers, they’d all see we didn’t start a fight.” He gestured to me. “But if you go breaking in, ponies know we’re together, and he can just say we conspired against him.”

I just smiled, confident in my abilities, even if I couldn’t share all of them. “Trust me, Dusty. I’ve got tricks you haven’t even seen yet. I can get in and out without anypony knowing I was there. Even if they do catch on that somepony was there, I’ll have them running in the completely wrong direction.”

He stared at me for several seconds, my confident smile versus his skeptical frown. Finally, he shook his head. “No. It’s too much of a risk for something we don’t need. We’ll find out if he’s involved tomorrow, anyway.”

My smile faded away. “Fine,” I said.

I’d just have to sneak off and do it on my own. I had no intention of going in blind.

Sickle rumbled. “Whatever. Kicking some merc ass should be fun.”

When we returned to Cinder Block’s Inn, the atmosphere had changed completely. There were still just as many ponies in there, but they were all gathered close around the bar, listening to the scratchy and staticky radio, as an energetic stallion and elegantly voiced mare spoke. All the ponies listened with rapt attention, eyes wide. Some were smiling, while others focused intently on the old radio. Even Cinder Block, the big earth pony behind the bar, had stopped to listen.

\leavevmode\llap{“}What’s going on?” Dusty asked, approaching the group.

A few ponies quietly shushed him, remaining focused on the radio. The nearest stallion, however, turned to us, with an awed smile and tears in his eyes. He spoke in a hushed tone. “Celestia is alive!”

Suffice to say, our interest was thoroughly caught.

We joined the crowd, listening eagerly to the radio, and then to the recap of what we had missed. There were tales of huge battles in the heartland of Equestria, and civil war among the Enclave. Of the activation of the S.P.P. towers and an event that had come to be known as “The Day of Sunshine and Rainbows”. Of warlords and heroes, hostile plants and friendly alicorns. Of a living princess-slash-goddess, a (possibly) still-living Ministry Mare, and one very significant little pony; a mare of almost mythological standing, who had been at the heart of all of this.

I sat, and listened, and slowly pieced together a little more of the world around me.