Two weeks.

That’s how long it had been since the whole “Sunshine and Rainbows” event. That’s also exactly how long it had been since I had woken up from my centuries-long slumber. The day I had met Starlight, and the day one of the weather-control towers had exploded upon activation. That explosion had sent debris across the countryside, including to a certain C.L.T. facility. A facility that had \textit{coincidentally} suffered a failure of its power systems at that very moment, prompting an emergency evacuation for the one surviving being within: me.

It was a sobering thought. By everything I knew, I had survived through pure chance, and a fairly slim one at that. Had that precise chain of events not occurred, how long might I have remained in that chrysalis? Would I have ever woken up? Or would I have met the same fate as my sisters?

Mostly, I tried to ignore those thoughts. They were depressing, and at that moment, I needed to participate in the festivities.

The ponies in Cinder Block’s Inn were in high spirits with the news of Celestia’s survival. Sure, she was somehow bound to the S.P.P hub, however that worked, but she was alive, and those ponies were quite happy to celebrate that fact.

Myself, I was quite happy to join in, share in their happiness, and siphon off a tiny bit of the camaraderie and friendship that filled the air. I did my best to ignore how utterly strange the whole situation was. Two weeks in the Equestrian Wasteland had done wonders to further develop my ability to simply accept things I didn’t understand. The whole world had gone crazy, and I had no option but to roll with it.

Starlight joined in, too, dancing to the music in a way that left much to be desired in form, but certainly wasn’t lacking for energy. Dusty kicked back with a few ponies he knew, swapping stories. Even Sickle shed her armor to join in, to rather mixed results. I stayed well clear, especially as she soon had a small gathering of the rowdier ponies, as well as an excess of alcohol and a general lack of common decency. Fortunately, she headed out with them before she got us all got kicked out.

Despite getting a fairly good meal out of the gathering, I turned in a little early. I had plans for that night, and I needed my rest.

I napped, waking only as ponies returned to our shared room. Starlight was the first, returning shortly after I had arrived. Sickle was the last, returning well after dark. Her hoof-falls came unevenly as she staggered back to her cot and collapsed with a groan. The smell hit me almost immediately, with the stench of alcohol nearly masking the musky scent lingering behind it.

She was snoring only moments later. I suppose I should mention that her snoring is much like everything else she does, excessively loud and grating, and it seemed to be made even worse for the amount of alcohol she had consumed that night.

If there was one small upside to Sickle’s presence, it was that her snoring perfectly concealed what little sound I made as I slipped out of the room.

{\br}%
Some ponies would think that the best time to sneak into a place would be in the middle of the night.

That couldn’t be further from the truth.

The best time to sneak into a place is in the middle of the day, when things are at their busiest. When ponies are coming and going constantly, and something is always going on. When they \textit{expect} ponies, rather than their presence being unexpected. When a disguised changeling is simply one more face in the crowd, rather than the only pony around.

So while I made my move at night, I did so out of necessity, rather than desirability. Fortunately, I had one very notable advantage; unlike the ponies living in Mareford, I could fly.

I skimmed low over the roof-tops in my temporary guise: a navy-blue pegasus stallion, light and lean. I had only a small amount of gear weighing me down: my portable terminal, tucked into a bag that had previously carried our loot, the holster holding my pistol and spare magazines, and my binoculars.

The first step of any infiltration is gathering intelligence. I already saw a little of the internal layout of the town hall, enough to know the basic layout of the first two floors. While that included my objective, I had plenty of time to scope the place out. There was no rush.

I landed atop the tallest building, an old five-story office building that appeared to be converted to stores and apartments. From there, I had a good view of the town hall building through the lenses of my binoculars.

That included the window to Big Gun’s office, which was lit. Though the worn blinds were closed, I could see the occasional shadow of movement.

After a couple minutes, I decided it was time to get closer.

I stepped off the edge of the building, the wind rushing past me as I fell, and pulled out of the dive to skim low over the neighboring buildings. The last stretch was straight across the street, and then I landed atop the town hall. I peeked back over the edge; nopony was around to have seen me.

Again, I slipped over the edge of the roof, but this time my wings beat to keep my descent slow, until I hovered just beside the window. While I couldn’t very well sneak in while the room was occupied, I could always eavesdrop. Though muffled through the old glass and worn blinds, I could hear Wild Runner’s voice.

\leavevmode\llap{“}...ain’t selling as well as they used to. Said he’s getting more and more ponies trying to haggle or scrape up more caps to get rifling, and the old ones aren’t moving.”

Big Gun’s voice sounded quite pleased, perhaps even smug. “That would be market saturation, my dear. The old smooth-bores have become common, so ponies looking for a hoof up on their neighbor are looking towards something better. I’ll pass word on to Good Deal to reduce the price for the smooth-bores, and bump up the price for rifled pipes. And I think it’ll be time for Forge to put more focus on the production of proper weapons. If the trend continues, demand should be increasing soon enough.”

\leavevmode\llap{“}I’m still glad you like all this business management stuff. I think I’d have to slit my own throat if I had to listen to Deal rambling on about margins and sales incentives.” There was a short pause, followed by a muted laugh. “Nah, I’d probably just slit \textit{his} throat.”

\leavevmode\llap{“}Now, now,” Big Gun said, suppressing a chuckle. “Don’t be too hard on the help. They’re hard to replace, and there are plenty of other ponies that deserve it more.”

\leavevmode\llap{“}Yeah, I know,” Wild Runner said, her tone sharp and bitter. “Except you’re keeping me here instead of letting me deal with them. I’m \textit{bored}. I liked it more before we had Fireline working for us.”

\leavevmode\llap{“}This again?” A chair squeaked against the floor, followed by the faint sounds of hooves, which stopped a moment later. “There are a lot more skulls in need of cracking, my dear. I can’t expect you to cover every aspect of our growing little empire.”

\leavevmode\llap{“}How about \textit{any?}”

\leavevmode\llap{“}Patience. You’ll have plenty of opportunity for fun, soon enough. As I’ve said so many times tonight, let Fireline earn his keep by disposing of this annoying little moral crusader. If you must know, I’ve got something \textit{much} more entertaining in store for you, if you’re willing to be just a little patient.”

There was a moment of silence. When Wild Runner spoke again, there was a hint of eager amusement to her voice. “Oh, entertaining, now? Well, come on, spill it!”

\leavevmode\llap{“}And ruin the surprise, my dear?” Big Gun chuckled. “I think not.”

\leavevmode\llap{“}Yeah, you and your surprises. A hint, then.”

I heard Big Gun hum softly. “...No, I’m afraid not. Wouldn’t want to go spoiling your birthday present, after all.”

There was a thump and rattle, as if somepony had just bumped firmly against the desk. Wild Runner practically cooed, barely audible through the window. “Oh, a birthday present, hmm?”

\leavevmode\llap{“}Indeed. And that’s all you’re getting out of me until then.”

A moment of silence followed, followed by a louder rattle from the desk. “Jackass,” Wild Runner said, though she nearly laughed as she did so. “This better be a damn good surprise.”

\leavevmode\llap{“}I’m sure you’ll have more fun than I’ll want to know about.”

\leavevmode\llap{“}Tease.” More hoofsteps. “And you better wrap up all your business shit nice and quick. I’ll be waiting for you.”

A door opened and shut. There were a few more hoofsteps, then the sound of the chair squeaking again.

I took that as my cue to leave. As satisfying as it would have been to wait until he left and break into his terminal, it was no longer necessary. While I didn’t have any specifics, there were a fairly limited number of ways to “dispose” of a pony.

I skimmed the roof-tops, returning to the inn.

{\br}%
I woke to the soft morning light, feeling remarkably relaxed and rested. The aching in my legs had slipped off into the background, and for the moment, I felt content.

The peace was eventually broken by Sickle’s groan and the loud rattling of bottles clinking against each other. She muttered in barely audible and mostly incoherent fragments. “Fucking… where… dumb bottle…”

I cracked an eye open to see her leaned over the edge of her cot, fumbling at a bag with one hoof. Her eyes were thin slits, barely opened, and her ears were laid back against her skull. The side of her face was wet, probably with drool.

On my opposite side, Starlight stirred and groaned. “Ugh… what’s going on now?”

\leavevmode\llap{“}Need a drink,” Sickle muttered, finally extracting a bottle from the bag and sending a few more rolling across the floor. She flopped back in her cot, sprawling out on her back in a way made especially lewd by way her coat was matted in certain places. She pried the bottle cap off with her teeth, spit it out, and proceeded to start chugging the bottle. She even managed to do it without spilling \textit{too} much of her drink.

\leavevmode\llap{“}And now you’re getting drunk again,” Starlight said, grumbling a little as she sat up and rubbed the sleep from her eyes. “And history repeats.”

\leavevmode\llap{“}Hey, fuck you,” Sickle muttered as she lowered the bottle, squinting against the light. “Drinking fixes hangovers. ‘Sides, I had a great fucking night, unlike you lame-asses.”

\leavevmode\llap{“}I had plenty of fun,” Starlight said, stretching. “And unlike a certain \textit{somepony}, I did it without a massive headache in the morning.”

Sickle, however, had stopped paying attention. She was looking off into the distance, eyes opening a little more as she steadily blinked. Then she cracked a smile. “Hah, shit. I just made a pun. That was a pun, right? Great \textit{fucking} night?” She broke down in snickering, which soon devolved into a groan as she laid her head back.

\leavevmode\llap{“}Clever,” Starlight dryly intoned before hopping off her cot, landing on the floor with a sharp clatter of hooves and drawing a small wince from Sickle.

\leavevmode\llap{“}Well I thought it was funny,” Sickle grumbled, though a moment later she started to smile. “Been way too fucking long since I’ve had a good rut.” She tipped back the bottle again, draining the last of the contents, and then dropped it beside her cot. “Shit, almost makes me miss my old crew. ‘Course, it took most of them to do a half decent job of it.”

\leavevmode\llap{“}Really don’t need to be hearing all of this!” Starlight said, which just made Sickle snicker more.

\leavevmode\llap{“}What, jealous?” Sickle grinned, spreading her hind legs wider. “I’m up for another round or two if you’re that desperate.”

I turned so I wasn’t looking at Sickle any more, and started slowly gathering my things. On the far end of the room, Dusty was already up, casting the occasional disapproving look down the room as he finished reassembling his rifle. He already had his gear ready to go.

Starlight grunted. “Ugh, no.” She glanced past me toward Sickle, grimaced, and looked away again. “And if you’re going to keep that up, the least you could do is clean up. That’s disgusting.”

\leavevmode\llap{“}See?” Sickle grunted. “You’re all a bunch of lame-asses.” She groaned a bit more, and from the creaking of her cot, I could tell she had sat up. “Urgh… how hard is it to find ponies that like to fuck as much as they like to fight?”

Starlight turned back to her. “Hey! I don’t \textit{like} to fight. It’s just a job.”

I looked back to see Sickle wincing, rubbing a hoof against an ear. “Yeah, sure you don’t,” she rumbled. “You just \textit{really} like your job, huh?”

\leavevmode\llap{“}I don’t—”

Dusty cut in. “\textit{Children}. That’s enough. We’ve only got an hour before we’re meeting with Fireline, so why don’t you all get some breakfast before we head out. And Sickle, go clean up. Right now somepony could shoot you by scent.”

\leavevmode\llap{“}Eat a dick,” Sickle muttered.

\leavevmode\llap{“}Uh-huh. Better make it quick if you don’t want to miss the ‘fun’.”

While she grumbled and rubbed at her eyes, Dusty slung his freshly assembled rifle and stood to leave. It seemed the best time to speak up.

\leavevmode\llap{“}Oh, Dusty? Just so you know, this is absolutely a trap. Big Gun intends Fireline to ‘dispose’ of us. Well, no, he specified \textit{you}, but I’m assuming it’s a package deal.”

Dusty hesitated, giving me a questioning look. “And how, exactly, would you know that?”

I shrugged as nonchalantly as possible. “Because while you were all preoccupied last night, I sneaked out and eavesdropped on Big Gun and Wild Runner as they discussed various aspects of their business, including how to deal with us.”

He stared, eyes widening for a moment before blurting, “You \textit{what?}”

\leavevmode\llap{“}Also, I get the impression Wild Runner isn’t exactly the most \textit{pleasant} of ponies.”

\leavevmode\llap{“}Yeah, she’s not,” Dusty said, turning to face me with an angry narrowing of his eyes. “She’s the kind of pony who likes stomping in the heads of ponies she catches eavesdropping on her. What the hell were you thinking? Do you have any idea how dangerous that is?”

\leavevmode\llap{“}Yes,” I replied. “I wasn’t acting impulsively or incautiously, if that’s what you’re thinking. I carefully considered every aspect of potential risk and my own abilities, and took a course of action that I was certain was safe for all of us. I could also point out that it went precisely as I expected it to.”

\leavevmode\llap{“}This time, maybe!” Dusty shot back. “But if you keep trying to play at being a spy like in some ancient book you read, you’re going to get yourself and all of us into trouble.”

\leavevmode\llap{“}I’m not \textit{playing} at anything, Dusty. We all have our own skills.” I pointed a hoof at him. “You’re a soldier.” I set my hoof down again, and gave a little smile. “I’m not.”

He glared at me, mulling over my statement for several seconds before replying. “Fine. But you’re also a part of a \textit{team} right now, and that means you don’t go running off to do your own thing. The fallout from anything you do is going to land on all of us, so don’t you ever go cutting us all out of it again. Got it?”

\leavevmode\llap{“}As long as you don’t dismiss us out-of-hoof and give actual consideration toward our skills and expertise?” I held out a hoof. “Deal.”

He had to consider it for a few more moments before taking my hoof and giving it a quick shake. “So long as your idea of your own skills match reality. Considering the risk you took for nothing, I’m not terribly impressed, so far.”

My smile grew a bit more as I picked up my saddlebags, slinging them over my back. “Oh, it wasn’t for nothing. In fact, I think what we’ve gotten out of it will be quite valuable.”

\leavevmode\llap{“}What, that this is a trap? We already knew that.”

\leavevmode\llap{“}No, we didn’t. We \textit{suspected}. \textit{Strongly} suspected, but still only suspected.” I slipped the sling of my rifle over my neck, then paused to look square at him. “What we’ve gotten out of it is complete freedom from any lingering concerns that we might be about to aggressively interrogate an innocent and uninvolved pony.”

He frowned, eventually shaking his head. “I don’t know if that’s worth the risk you took. We’d find out soon enough, anyway.”

\leavevmode\llap{“}And I think everypony will be considerably more comfortable with the plan with this knowledge.”

Sickle grumbled from nearby, a hoof still lying across her eyes. “I don’t actually give a shit one way or the other.”

\leavevmode\llap{“}Everypony other than Sickle, then.”

Dusty sighed, shaking his head again. “Fine. No point complaining about it now, since you already went and did it anyway.”

\leavevmode\llap{“}Indeed,” I said, smiling again. “Now is the time for more productive things. Like breakfast.”

{\br}%
Dusty was still a little grumpy by the time we arrived at Mareford’s south gate, passing through the thin morning crowd. The sight that met us didn’t improve his mood any.

Fireline was there, sitting back against the wall. What we hadn’t expected was the four armed ponies gathered around him, decked out with saddlebags and weapons. Good weapons, too, like the Militia used.

\leavevmode\llap{“}Well, shit,” Dusty grumbled under his breath as we continued to walk toward them.

Starlight leaned in. “Change of plans?”

Dusty thought on it for a moment before shaking his head and murmuring back. “Plan stays. As long as we draw first, we’re good.”

\leavevmode\llap{“}I don’t know,” Starlight said, and I had to agree.

\leavevmode\llap{“}Weren’t you just talking about unnecessary risks?” I asked, keeping my voice low; while we were still a good ways away, we didn’t want one of the occasional ponies passing by to overhear our plans to abduct one of their employed mercenaries.

Dusty shook his head slightly. “We’ll be starting with Sickle in close quarters with all of them.” He glanced back to her, speaking up just loud enough for her to hear. “I’ll get your attention just before it all goes down, and you can lay out whichever one is closest to you. Okay?”

Sickle was, naturally, in her armor once again. I wouldn’t describe her appearance at the time as “clean” so much as “cleaner”, or at least cleaned up to the point where it was no longer blatantly obvious what she had been doing the night before. “Sounds fun,” she rumbled, all signs of her hangover having passed some time ago. “I’ll take the closest three. You cunts should be able to finish off the leftovers, right?”

\leavevmode\llap{“}Just don’t kill Fireline,” Dusty said. “Don’t maim him, either. In fact, I’d prefer if you didn’t kill anypony at all.”

\leavevmode\llap{“}Yeah,” Sickle said, snorting out a quiet chuckle. “‘Cause I give two shits what you’d ‘prefer’.”

Starlight rolled her eyes. “Yeah, this isn’t going to go wrong or anything.”

\leavevmode\llap{“}Yeah, fuck you too, runt.” Sickle snickered, and added, “‘Sides, we outnumber them.”

\leavevmode\llap{“}There are five of them,” Starlight said, staring flatly up at Sickle. “There are only four of us.”

\leavevmode\llap{“}Yeah, but I’m worth at least three of them,” Sickle replied, grinning behind her muzzle.

\leavevmode\llap{“}That’s not how outnumbering works,” Starlight grumbled.

\leavevmode\llap{“}Okay, quiet down,” Dusty said. We were getting close, and the ponies we were approaching had taken note of us.

Fireline was geared up like his companions, having donned armored barding, and with an assault rifle slung across his chest. He stood as we approached.

\leavevmode\llap{“}Good morning,” he said, eying over each of us in turn. It was a calculating look, I thought. He was sizing us up.

\leavevmode\llap{“}Good morning,” Dusty said, and he even sounded moderately pleasant about it.

The furthest mercenary, a green stallion, leaned over to his nearest companion, and spoke in a hushed but clearly audible voice. “Holy shit, that’s one big bitch.”

Sickle focused on him like a laser. “You better watch out, shrimp. Tiny little thing like you might get stepped on.”

He sneered back. “Yeah, you just—”

\leavevmode\llap{“}That’s enough,” Fireline said, shooting the mercenary a harsh glare. “Save the comments for later.”

It was Sickle’s turn to sneer. “Yeah, listen to your boss, little bitch.”

Fireline shot her the same glare, but said nothing before turning back to Dusty. “You’re ready to go, then?”

\leavevmode\llap{“}We are,” Dusty said, nodding and giving a little smile. “Lead the way.”

I caught a moment of hesitation from Fireline before he nodded. I don’t think he liked the idea of any of us being behind him. “Okay. Let’s go.”

With a wave from Fireline, the gates slowly opened. Dusty took the opportunity to chamber a round and ensure his rifle was ready to go. I did the same, acting as casual as I could as I locked my rifle’s bolt back.

Starlight merely smirked. Her Lancer was still slung loosely across her back, but her holstered Recharger was only a momentary thought away.

Fireline looked back, glancing down to our rifles before speaking. “No need to worry about that. If anything does come up, my team can keep us safe.”

Dusty just shrugged. “Better safe than sorry.”

I did my best to seem disarming. “We wouldn’t want to be freeloaders when we can help.”

\leavevmode\llap{“}Uh-huh,” Fireline said, frowning just a tiny bit before hiding the expression. “Just be careful where you point those things.”

Once the gates had opened enough, we set out, hooves slowly beating against the cracked pavement and dry earth.

It wasn’t the most conversational traveling group I had ever encountered. That was hardly surprising, I suppose, when both sides intended violence upon the other. If anything, it was surprising that there wasn’t \textit{more} tension there.

On the plus side, this gave me plenty of time to evaluate the ponies we were traveling with. While Fireline led the way, the four ponies with him had fanned out, taking up the sides of our little formation. It had the simple effect of making it look like they were protecting us, while in fact surrounding us.

On the left, closest to myself, was a violet mare. She was wrapped up in thick cloth over her barding, which left very little of her visible. She was also the only one of the formation who kept her attention entirely focused outward, rather than glancing in to check on us.

In front of her, by Dusty, was a lean young buck, the only unicorn other than Fireline. His gear was clean and neat. From the hints of dirt ground into his off-white coat, I got the impression that his gear was new, rather than fastidiously maintained. He was also quite alert. Possibly too alert, with his ears constantly flicking back and forth, and he would regularly glance into the group before immediately looking outward once again.

To the right, beside Sickle, was the largest of the mercenaries, a dark-brown stallion who would have looked moderately big and strong beside anypony else in our group. He looked almost bored as he walked along. Though his gear was worn and scratched up in places, there were a few additions that caught my attention. Instead of a pistol, he had a small shotgun holstered at his side. A few bulging pouches held what looked to be drum magazines for his rifle, but he didn’t have any of them loaded. Instead, he had a regular magazine in it, although one with with a thin band of red ribbon tied around it. My immediate suspicion was that it indicated the magazine was loaded with a special kind of ammo.

Behind him was the green stallion who had spoken up earlier. Of the entire group, he was the only one who acted completely casual. He hummed to himself on occasion, and was often smiling. It wasn’t a good smile, though; it was the smug kind of smile a pony gets when he knows something nopony else does.

His smile slipped a bit only minutes into our journey as he sniffed at the air. He sniffed a few more times before leaning a little closer to Sickle’s flanks and sniffing again.

Sickle didn’t even look back as she growled. “Unless you’re about to eat me out, you better back the fuck off before you get your face broken.”

He gave an amused snort as he returned to his place, wearing that smug smile once again.

Rather than heading back the way we had come to the city, our course took us east, first along Mareford’s walls, under the protective eyes of the Militia guards, and then out into the crumbling suburban ruins on the outskirts of Dodge City. Few buildings still stood near Mareford, having likely been torn down for materials long ago, but the skeletal remains of the old city grew more prominent as we got further from town.

We walked down the cracked remains of a wide paved street, some old thoroughfare that had run through the ruined neighborhood. Even close to a mile away, we could still see Mareford’s walls behind us, but that was soon to change. As we passed more and more buildings, we were quickly approaching the point where we would pass out of sight. That knowledge came with an acidic twinge in my gut, a hint of adrenaline at what was soon to come.

Dusty made no attempt to hide his wary glances around at the buildings we passed, eventually taking the bit of his rifle between his teeth. “How much trouble have you guys been having with the manticores, lately?”

\leavevmode\llap{“}Not a bit,” Fireline said, glancing back. His eyes dipped down to Dusty’s rifle before adding, “Relax. We drove the last of them off last year, and we sweep through every month or two to make sure it’s still clear. Got to keep the roads safe for traders, right?”

\leavevmode\llap{“}Right,” Dusty agreed, giving a little sigh and visibly relaxing, though he kept the bit in his mouth. “I’m glad to hear it. I never did like this stretch.”

I had to give Dusty credit. He was a decent actor at times.

The silence returned as we continued on, passing an old, burnt-out restaurant. The road curved along its front before opening into an old city square. It might have been beautiful once, but now the benches were broken, the plants withered, and the grand statue at its center was reduced to four hooves surrounded by rubble.

The curve also led us out of sight of the distant Mareford walls. That led me to look to our “escort” once more. As I was walking behind Dusty, the easiest to look at was the young unicorn beside him. That’s the only reason I caught the simple action that initiated everything.

While his rifle was slung across his chest, his horn was lit, his magic holding the weapon’s grips. With the jostling of his equipment, I would have never picked out the sound of him disengaging his safety, nor would I have seen it if I had not been looking right at it.

Dusty spoke. “Oh, hey, Sickle?”

Her head turned toward him. “What?”

Rather than answering, his head immediately turned away. His rifle swung around toward the young unicorn, and all hell broke loose.

Even expecting a confrontation, the loudness of his rifle made me jerk back. To my side, Sickle was already moving, throwing herself into the fight before I had even taken up my own weapon.

Dusty’s rifle swung around on the violet mare beside me, before I could bring mine to bear. He yelled. She moved. Another assault of sound hammered at my ears as Dusty’s rifle blared. She twisted and fell.

I staggered back, turning the other way. Fireline staggered sideways toward us, blood falling from his snout. Starlight had her repeater out, aimed in the air at nopony. The green stallion lay several yards past her, writhing and holding his blood-soaked face. The final mercenary was mostly hidden behind Sickle’s bulk; I could only see his hind-legs, jerking and twitching as Sickle turned, one of her spiked hooves rising up, dripping with blood.

I didn’t notice Fireline’s rifle lying on the ground, likely having fallen there at the same moment his nose had been bloodied, until his magic grabbed it again. I swung my rifle back toward him, yelling out what I had intended as a warning, but which came out as an incoherent shout of raw noise. Dusty also shouted, likely much more coherently than myself, though in the heat of the moment I missed whatever he said.

Sickle moved quicker than all of us. She reared around, smashing one hoof down on the rifle. The other, bloodied hoof caught Fireline on the top of the head, and shoved his face into the pavement. “Sit the fuck down!” she bellowed, loud enough that I remembered it clearly even over the jarring amount of adrenaline pumping through me.

The whole fight couldn’t have lasted more than a couple seconds.

Starlight muttered a string of profanity as she quickly looked around, turning her Repeater toward the green stallion, who did little more than moan and curl up. I didn’t get a good look at his face, between his legs obscuring it and my lack of desire to see what a buck from Sickle could do to a pony’s snout. All I saw was blood.

As Sickle leaned over Fireline, chuckling, Starlight finally broke her quiet tirade of curses to look towards Dusty. “What happened to not kill—”

She was interrupted by the most terrifying sound I have ever heard.

The sound was loud and sharp, yet seemingly without end. It wasn’t a single gunshot, or even the rapid cracking of automatic fire. It was less a string of distinct sounds and more of a \textit{tone}, a horrible, tremendous sound that tore through the air just as a hundred bullets tore into the area around Sickle, throwing up sprays of dirt, shattered pavement, and blood.

Sickle fell.

I scrambled back, unable to hear whatever I saw Dusty shouting. He, Starlight, and myself threw ourselves to the ground beside the wall of the old restaurant. Old, long-vacant windows gave a good view over the street, but we huddled behind the low brick wall beneath them, taking what protection we could get.

The \textit{tone} paused for a split second, echoing in the distance, and then resumed, louder and angrier, as the tide of bullets tore into the wall we hid behind. Bricks shattered and fell, peppering us in fragments and filling the air with dust. I could have been screaming and not have even known.

Dusty shoved me forward, and I crawled frantically in the direction he had pushed me, too terrified to do anything but follow his direction.

A quick glance back caught sight of Sickle scrambling to her hooves and lurching in our direction. Her armor, ever impressive, had saved her life from the terrible assault. The same could not be said of Fireline or that smug green stallion, both of which were quite clearly deceased.

I made it to the rear of the restaurant, past the edge of the windows and to the relative safety of having most of a building between us and the source of that tremendous fusillade of fire. The sound tore through the air again as another volley ripped up the edge of the restaurant and smashed into the side of Sickle’s armor. Cans of food poured from one of the shredded bags on her back as the assault sent her stumbling and falling; this time, however, she fell behind the partially destroyed wall, giving her a little relief from the fire.

The bullets still struck out, but most now hit the wall, with relatively few puffs of bullets shattering on the plates of her armor as she scrambled forward again, and moments later she made it to us. The terrifying gunfire stopped.

I can’t overstate just how relieved I felt when Sickle made it to us. While I certainly had my reasons to dislike her, this was precisely the sort of situation where having a heavily armored and psychotically vicious killer at my side was likely a \textit{good} thing.

That, and I was burdened with the concern that, if someone or something were able to take down a mare like Sickle, what chance would I have?

That relief was diminished a moment later when Sickle staggered and nearly fell. Her head weaved from side to side, as if she were about to collapse. It was only then that I noticed the blood streaming from her. It was practically pouring from behind the plates over her right shoulder and side, as well as dribbling from her chin. Behind the thick bars of her muzzle, all I could see was blood and teeth.

Dusty was up beside us, his words finally registering with me. “Next building! Move!”

He rammed his shoulder against Sickle’s as she teetered, and she leaned against him without protest, while I looked in the way Dusty had indicated. Across the small back lot was a two-story building of some sort, likely a store. I hesitated, looking to my right, but the line of old buildings looked to give good cover from whoever had been shooting at us.

I obediently rushed forward, leaping through a vacant window. Safely in cover, I sat, trying to catch my breath. My heart hammered hard in my ears, beating away everything else.

Starlight arrived moments after me, followed several seconds later by Sickle and Dusty. Sickle shoved her way awkwardly through the nearby doorway, then collapsed. She uttered a few barely recognizable curse words as she awkwardly fumbled with her armored saddlebags.

Despite the unexpected chaos, Dusty took charge of the situation. “Whisper! Cover that way!” He pointed a hoof further down the back lot we had crossed, while aiming his own rifle out the window the way we had come. “Starlight! Help Sickle! Get a couple healing potions in her as quick as you can. We need to move fast.”

Starlight drew back from the window and moved further into the room, while I crouched by the doorway. I resisted the urge to look back and check on her, keeping my eye down the sight of my rifle. I ignored the clattering and rustling behind me as seconds sped by. I focused on the corner of the far building, where an alley led back into the lot, ready to pull the trigger the moment a head poked out.

I almost squeezed off a shot by accident when Dusty fired off a burst, the sound hammering at my head and kicking up dust in the confined space. He immediately followed up by shouting, “Fall back, now!”

I didn’t need any more encouragement, turning and running back into the building. I passed Starlight and Sickle, who was climbing awkwardly to her hooves.

\leavevmode\llap{“}She’s hurt bad,” Starlight said as Dusty entered the room.

\leavevmode\llap{“}I’m fine,” Sickle growled, her words slurred as she staggered forward.

Dusty pulled his snout out of a pouch, a mine clutched between his teeth. “Keep moving!” he said as he armed it, and tossed the device to the rubble-strewn floor behind us. I put on a bit more speed, running outside.

It was maybe ten yards to the next building, and every inch of it left me terrified that I was about to be shot by some unseen assailant.

One corner of the building had collapsed, and Dusty and I once again took covering positions over the remains of a wall, while Sickle collapsed onto the rubble-strewn floor behind us.

As soon as she had, Dusty spoke again. “Sickle, take whatever you need to get moving again.”

She grunted, and I heard the clatter of her armor and metal cases, followed by a couple loud, angry, pained growls. Those sounds continued in turns, second by second, while I focused on the corner of the building we had come from.

A powerful, almost impossibly deep \textit{bang} shook the air, as a wave of dust and smoke burst from every opening of the building we had just vacated.

Dusty chanced a glance back before speaking to me. “Whisper, peel back to the next building, then set up to cover for everypony else.”

\leavevmode\llap{“}Got it,” I blurted, spinning to run back. I caught only a quick glimpse of Sickle—her metal muzzle hung open, giving me a quick glimpse of her mangled snout—before I was past them, moving as quick as I could across the rubbled, uneven terrain. Then I darted out the doorway on the far side of the building, and out into the alley beyond.

The next building had no windows facing our direction, but halfway down the side wall was a recessed doorway. I took position there, aiming back past the building I had just emerged from, and casting wary glances toward the windows and alleyway looming beside me.

I crouched there, waiting in silence with nopony around. After the tremendous, frantic madness, the quiet was unnerving.

I’m quite glad that, despite the humming tone that had returned to my ears, I heard Sickle’s armored hooves as she approached. With how tense I was, I can’t be certain I wouldn’t have accidentally shot her if she just appeared around the corner.

She lumbered by, with Starlight tagging along beside her. Starlight gave me a quick, concerned glance before passing by me. Her Lancer was out, floating just beside her head, ready to shoot.

The sound of their hooves rapidly faded behind me as I waited, covering their retreat.

Dusty’s rifle fired again, the sound loud and distinct. There was a long burst of automatic fire, followed by several shorter bursts before the weapon went silent. I heard no return fire.

Several seconds later, Dusty came running around the corner. He slowed as he came along beside me. “Wait ten seconds, then bound past me.”

With that, he was gone again, hurrying down the alley in the same direction Sickle and Starlight had gone. I understood his intent, then. We would move alternately, one covering while the other fell back.

And at that moment, I was the one in front. It was my turn to lay down a wall of fire against those who pursued us. Adrenaline built with every moment, as the seemingly inevitable clash drew closer. I counted down the seconds, hoping that my allotted time would expire without the arrival of any hostile ponies.

It was with a wave of relief that I finally reached “ten”. I turned, hooves shifting to gallop away.

The first sighting of the ponies pursuing us came not from the corner I had been covering, but the alley leading off to my side. A pony—the instant was too quick to pick out any details of their appearance—galloped around the corner of the neighboring building and toward me. A weight dropped in my gut; that pony had run around to catch us in the flank, and the path of my retreat lay open and exposed to him.

Instead, I continued my turn, lunged forward through the doorway I had stood in, and threw myself to the side. I landed hard on the rubble-strewn floor at the same instant gunfire erupted behind me, throwing shards of plaster and brick from the wall behind me.

I immediately scrambled to my hooves and down the dark passage I found myself in. I managed to keep my footing despite the cluttered bits of fallen plaster, rushing past doorways that led even further from my companions. The dark hallway turned one way, then the other, and finally opened into an old storage room. Shelves lay askew, and shards of broken crates lay scattered about. I rushed through the room, leaping over a fallen shelf. I was so consumed with my frantic escape that I hadn’t even consider the possibility of nails among those broken remains, and likely escaped that hazard through pure chance.

I burst through the door on the far side of the room and into a completely looted store, and the much-welcome sight of muted sunlight. Unfortunately, the same floor-to-ceiling windows that brought in the sunlight also brought the much less-welcomed sight of three heavily armed ponies galloping down the street, one of whom was already looking in my direction.

I threw myself behind the counter, keeping low as I ran along it. Gunfire erupted once again, throwing more clouds of pulverized plaster into the air as bullets tore into the wall behind me—and to my horror, blasted shards of wood from the counter that stood between me and the shooter, as the bullets tore straight through the flimsy barrier. The only protection it offered was to obscure my position, but enough bullets would eventually find their mark.

I rushed forward as more bullets punched more holes, and leaped through the window at the far end. I landed in the small gap between that building and the next, and leaped again, diving through the much smaller window facing me.

It was another hall. The gunfire died off behind me as I galloped in the growing darkness of the building. I passed by the closed doors, unwilling to take the time to open them, and the hall quickly ended in a set of stairs. I bounded up them, finding myself in another hall. I could already hear the hoofsteps and shouts behind me.

Thinking of Dusty’s earlier tactics, I stopped at the top of the stairs, turned, and fired a short burst down the way I had come. Then I was running again. I knew I wasn’t going to hit any of my pursuers with the random shots, but it might give them a moment of pause, and right then, every second was precious.

I galloped down the hall, catching bits of light where the crumbling building let in the sun. A pile of debris from a collapsed section of ceiling forced me to run through an open doorway. The room beyond, originally an apartment, was strewn with ruined furniture, and I leaped over a sagging couch before rushing through the back door and into a bedroom.

The building had suffered a fire at some point in the past, leaving the bed a gutted mess of springs and the floor and walls blackened, but its misfortune turned into my good fortune; the wall of the bedroom had burnt badly enough to partially collapse, and I leaped through the gap into the adjacent room.

I passed through room after room, weaving back into the hall, slipping through fallen sections of wall, or leaping through narrow holes. The burnt floor crunched under-hoof, and at one point I had to shoulder my way through the remains of a wall, the old, charred wood practically falling apart and smearing me in black dust.

The building ended abruptly, the outer wall having collapsed to open up into the narrow alleyway. The building across the way had also been burnt away, its upper story almost entirely opened up. The gap couldn’t have been even ten feet across; an easy jump. I didn’t hesitate, galloping on and leaping the gap.

I really shouldn’t have been surprised to discover that the fire had weakened the building. In my defense, I had much more pressing matters at hoof than the state of the building I was fleeing through—or at least, I did until the floor I landed on smashed in under hoof. The entire floor caved in under my sudden weight, and I fell.

I immediately called up my magic. There wasn’t any time for fancy magics or calculated transformations. I simply stripped away my disguise, my wings buzzing. Then I slammed into the ground, my poor and tired legs collapsing as I tumbled. I came to a halt when I smashed into something hard. My right shoulder bore the brunt of the impact, sending a shock of pain through me, but I was intact. Between the bit of deceleration I had managed and the protection of my carapace, I seemed mostly unharmed, sore shoulder aside.

I quickly shoved myself up, appraising the situation. The object I had run into was a counter, and the broken remains of tables and stools littered the room. It had been a restaurant, it seemed, or perhaps a tavern. Though partially blocked by rubble, the windows gave me a good view of the street outside. Two doors on opposite sides of the room led deeper into the building.

I heard Dusty’s rifle, three rapid shots echoing around the buildings. It sounded so distant.

Unfortunately, my unexpected trip downstairs had cost me time. My lead was shrinking, and though my shoulder only felt sore, I feared it might slow me down. I could hear the hoof-beats of ponies drawing closer.

It was time to change tactics.

The front door of the restaurant smashed open as a well-armed stallion rushed in, but he didn’t find a changeling, or even a gray-coated, silver-maned mare. Instead, he found an off-white unicorn buck.

I was already calling out before the stallion had taken in the scene. “The back door!” I wheezed, holding my right foreleg tight against my chest as I leaned against the counter, and waved the other in the direction of the back door. “She went out the back door!”

He took one look at the apparently wounded pony, then rushed off in the direction I had indicated. I remained where I was, wheezing and panting. More ponies ran by, most on the street, with only a couple more following through the building. They paid me no more than a passing glance, too caught up in the moment to question the young unicorn’s survival. I’m not even sure if they recognized him, specifically, or if they had accepted my apparent help as proof that I was on their side.

I waited only about ten seconds before hauling myself up to my hooves and limping over to the window. There’s an important lesson in deception and consistency, there; if you’re going to fake something, keep faking it, even when you think you won’t be observed. It not only prevents you from being discovered by accident, but it’s a good way to keep yourself “in character”.

While I still heard hooves clattering on the cracked street and through broken buildings, they were all heading away. I had time to think and plan. Unfortunately, I wasn’t terribly happy with my situation.

I had escaped the immediate threat, but it left me in a troublesome position. While disguising myself as one of the mercenaries might give me a degree of freedom among them, it would also lead to my own companions mistaking me for an enemy. While I could move past the mercenaries with relatively little difficulty, it would do me no good if I were then shot by the very ponies I was trying to reach. It would also do me little good if all these mercenaries killed my companions anyway. While I had every respect for their fighting ability, they were three ponies against many, and I had no doubt that these ponies would be of higher skill than the raiders we had faced before.

So I was faced with a problem, and I needed to figure out a solution, quickly.

As always, the first step was information.

Peering out the windows, I looked around the buildings nearby. It wasn’t hard to find what I was looking for; all I had to do was look up and see what building rose the highest. The answer was an old bell tower atop a building just half a block away. I stepped out, heading there in a limping trot.

A couple more ponies were trotting down the street past me, but after a quick glance, ignored me, and I stepped into what I assumed had once been a government building. Despite the many offices and decaying decor, it wasn’t hard to find the stairs to the bell tower.

The bell was long gone, and the tower’s roof was likely one good gust from finally collapsing, but it served my purposes perfectly. While only slightly taller than some of the other buildings around it, it gave me a clear vantage of what lay ahead.

I raised my binoculars with my magic, keeping myself barely exposed. Starlight was out there somewhere, with her powerful and long-ranged weapon, and I had no desire for her to mistake me for one of the ponies attacking us.

And there were a lot of them. I could see almost a dozen moving down streets and through buildings, and by the rising sound of gunfire, there were many more of them. Past the gunfire, I could hear the occasional crack of Dusty’s rifle, and even more occasionally, the sharp pop of Starlight’s Lancer tearing the air apart in its wake. It made them easy to locate, though my hopes dwindled when I had; their retreat had led them down a long line of buildings, eventually ending in an old skywagon charging station a few hundred yards away. Ponies were taking up positions in several buildings across the street from it, and the paved lot behind the station offered no cover. Dusty’s fighting retreat had gone as far as it could.

I was taking in the scene when I heard hooves on the stairs below me. I suppressed the urge to run and hide—especially since my only escape would be onto the slanted roof beside the tower—and remained where I was, exactly as if I was supposed to be there.

I was still looking out the binoculars, and doing my best to keep my breathing in check, when the pony arrived. She was a blue earth pony, with light barding, a brown cloak draped across her back, and a long rifle held in her teeth. She dropped into a crouch beside the wall, swinging her rifle up to rest it across the edge. “Hey,” she said, glancing my way. “You see where they’re at?”

\leavevmode\llap{“}Yeah, you can see them perfectly from here” I said, lowering the binoculars and raising a hoof to point. She raised her rifle, peering down the scope. “See that street one over? Follow it up to the intersection and you’ll see a service station. They’re in there. Watch the left—”

The sharp \textit{clack} of my pistol echoed within the confined space, and the mare collapsed, her head smacking against the wall as she fell.

\leavevmode\llap{“}—window,” I finished, lowering myself beside her. Aside from the faint thump of her fall and the huff of air leaving her body, the only other sound was the faint pinging of the casing clattering on the roof.

In the back of my mind, I noted that this was the first pony I knew I had killed. It’s possible I had killed one before, with the copious amounts of ammunition I had spent in our previous engagements, but I honestly doubted it. In any case, this was the first one I could be sure of.

I don’t note that because of any particularly strong feelings on the matter. There wasn’t any internal debate over the morality of having done so. At best, these were soldiers employed to pursue goals that ran contrary to those of myself and, as its only known agent, my hive. At worst, they were knowing accessories to rape and murder. I felt no particular remorse for killing her.

It simply felt like something noteworthy, significant only as something new. A milestone, in a way.

It was a first for me. The first of what I expected would soon be many.

I floated her rifle over to my side, removed her cloak, and rolled her onto her back. It took a surprising amount of effort. Though she naturally didn’t resist, it’s easy to forget just how heavy a pony can be, and how awkward a limp body can be. Once I had her on her back, I took a few moments to examine her, quickly taking in the details of her appearance. She was lean, with a thin frame and fine features, but reasonably fit. No visible injuries, aside from the obvious, nor any notable blemishes. She had a very short blue-green mane and a short tail, both straight and simple. Lifting the flanks of her light barding revealed her cutie mark to be a single bullet, long and narrow.

Nodding in satisfaction, I called up my magic, and in a flash, mimicked her appearance.

Next I opened her small bags, dumping out the contents. Food and water were pushed aside, while a single healing potion and a ragged first-aid kit were quickly tucked into my own bags. The only item I examined was a small notepad, but it disappointed me; she wasn’t so thoughtful as to have written her own name in it, and I had no time to pore through it. It, too, was added to my bags.

I did notice a word etched into the stock of her rifle, however. “Thunder”. I had no idea whether it was her name, or one she had given the rifle, but I remembered it in case anypony addressed me by it.

As for the rifle itself, it was a long, bolt-action weapon, with a large scope. It was of wartime make, worn by the years, but well cared for. The pouch resting across the mare’s chest contained a few dozen rounds for it, looking very much like the kind of round Dusty’s rifle used. I took that, as well.

With my quick check complete, I swept the cloak over my back, and returned to the edge of the bell tower. I lifted the binoculars, sweeping around the area again. The shooting was slow but steady, and I could see several puffs of bullet impacts from the walls of the service station. Fortunately, the structure had been built along practical, industrial lines rather than for aesthetics; the building was thick and blocky, and even the centuries of wear hadn’t worn down its concrete walls. Even if they had been forced to a dead end, Dusty had led them to what was possibly the most fortified building in the area.

The front of the service station was a wide but short window, like a long slit in the concrete wall. Deep within it, I saw a subtle flash. A second later I heard the sound of Dusty’s rifle echoing across the ruined buildings. Dozens of gunshots answered, peppering the area, but thankfully, none of the mercenaries were trying to move up.

That made sense to me. They had their targets trapped. Why risk moving in when they could simply pepper them at range? I just hoped they wouldn’t tire of the situation before I did something about it.

Not that I had any clue what that would be.

It looked like the mercenaries had taken position within three buildings. On the right was a long, narrow motel, two stories tall, of which the back half had long ago collapsed. To the left was what looked to be a small grocery store. Directly across from the service station was a convenience store, its colorful post-topping sign—”\textit{Shop ‘n Dash}”—having long ago faded and fallen across the street beside it.

I could see several ponies in them, peeking out of windows or moving around, far more concerned with staying in cover from the ponies to their front than some unseen changeling behind them.

How convenient of this mare to have given me what appeared to be a long-range, high-accuracy rifle.

If only I were a decent enough of a shot to make good use of it. No, I needed another approach.

I continued scanning before something caught my eye. A pony, one of the mercenaries, was hauling a wagon up the street behind the motel. There were a few boxes and a barrel, but also several ammo containers and a few weapons, including a heavy machine gun. There was even a small basket full of grenades.

It seemed like a good place to start.

I drew back, slinging the scoped rifle across my back, while my own rested against my chest. I hurried down the stairs, past the long-abandoned offices, and out the back door of the building to canter after him and that wagon. I took care to always keep something solid between myself and the service station.

By the time I had caught up with the wagon, it was parked by the fence behind the motel. The pony who had been hauling it, a large stallion with a holstered pistol and a shotgun at his side, was pulling the heavy machine gun from the wagon, and grunting under the effort. I trotted up to him, imitating the blue mare’s tone. “Hey, you need any help?”

\leavevmode\llap{“}I got this,” he grunted as he hauled the tripod-mounted weapon across his back, and took a step toward the edge of the fence. “You can grab some ammo for it, though.”

\leavevmode\llap{“}Sure thing,” I said, walking behind him to get to the wagon.

Rather than getting the ammo, I used the opportunity to grab the bit of my pistol in my teeth, draw it, and bring it around on him.

For whatever reason, he started to glance back just as I fired. The shot caught him off-center at the back of his head, and he toppled over. The gun fell to the ground with a metal-on-concrete crack, and he rolled onto his back, groaning something made incoherent by the likely mortal, but not immediately fatal wound.

I had much more time to line up my second shot. His head fell back against the street, his body jerking, and then he slumped onto his side, dead.

I holstered my pistol again, clambered up into the wagon, and started rooting through their supplies.

I was not disappointed.

Amidst the food, water, medical supplies, and miscellaneous equipment, there were ammo cases containing hundreds of rounds of several different types, a good number of grenades, a few spare pipe rifles, and one case that particularly excited me. Inside were the sort of thing that could make a destruction-minded changeling weep for joy: a pair of large demolition charges, old Equestrian Army models complete with blasting caps and a radio detonator.

And to think, I had once considered my short course on demolitions and improvised explosives to be completely useless. Contingency planning wins again.

I wasted no time in making use of them. The radio detonator was a simple model, and I soon had each charge prepped, ready to go. I switched the detonator to “Arm”, and a small red light appeared. After that, it was a simple matter of getting them to where they would do the most good.

They were much too heavy to haul both at once. I turned the detonator back to “Safe” and engaged the physical safety, then tucked it into my bags. After that, I pulled out one of the demolition charges, closing the case over the other. I hauled my chosen charge around, swinging it onto my back. I grunted a little at the weight; it must have been about fifty pounds.

I carried it to the edge of the fence and peered around. I could see the roof of the service station, and while the yard and murky swimming pool behind the crumbling motel were wide open, the burnt-out husk of a skywagon provided enough concealment to get to the ruined building.

The gunfire had faded to background noise, a slow but steady cacophony. As I rushed toward the rear of the motel, crouched low, the nearby gunshots came to the forefront of my attention. They were coming from the front of the building, naturally, and I quickly picked my way through the rubble toward them.

I heard another shot from Dusty. They were so close, but the difference in the volume of fire was concerning. I had no idea how much longer his ammo would last.

Only the last three rooms of the ground floor were still standing, and the partially collapsed roof had rendered all but the last room upstairs impassable. I climbed over the mountain of debris until I could enter the back of what still stood, making my way steadily toward the nearby sounds of gunfire.

I crawled through a half-collapsed wall, into a debris-strewn bathroom, and then into a bedroom. The door between units had been battered down at some point. I peeked through it, finding myself right next to a closet, while a pony at the far end of the room crouched behind a couch, his rifle aiming out the window.

The pop of Starlight’s Lancer firing echoed across the street, and the pony across from me started firing again, putting a half-dozen rounds downrange. More guns blazed nearby, both in a neighboring room and from the floor above.

I took advantage of the noise to set the demolition charge inside the open closet and back out.

The canter back to the wagon was much easier without the extra weight. I hopped over the dead pony and retrieved the final charge, returning to the edge of the fence.

The convenience store was much more open. While there was still the occasional bit of broken skywagon or wall that had not yet fallen, there were enough gaps to make the prospect of crossing the distance twice look very unappealing. From there to the neighboring grocery store was much easier.

I decided I wouldn’t be returning to the wagon after that, so I set the charge down and loaded as many of the grenades as I could into my ammo pouch. Then I retrieved the explosive, took a deep breath, and galloped to the first piece of cover.

I practically slammed against the hulk of the skywagon as I arrived. I paused there for only a moment, taking another couple deep breaths before darting forward again to a low wall. Then a toppled dumpster, filled with debris. I was making the short gallop between the dumpster and an old delivery wagon when a terrifyingly loud \textit{snap} nearly sent me stumbling. I threw myself to the ground behind it as the hail of return fire answered Dusty’s shot.

I quickly got to my hooves, taking advantage of the return fire to run the final gap, finding myself in the strange position of hoping their fire kept Dusty’s head down for just that moment.

The convenience store was small. I slipped in the back door, entering a tiny office that led into the store itself. Several ponies were in the front area, taking cover behind the edge of the window and the counter. One lay dead beside the front door, and another was nursing a bleeding leg.

One of the ponies noticed the movement and looked my way. He saw me, then immediately turned back to the window. After all, that’s where the danger was.

I set the demo charge against the front wall of the office, closest to them, and slipped out the back.

There was only one building left, and I was out of bombs.

I galloped across the narrow gap into the grocery store’s back lot, coming to a halt once I was in safety once again. The lot itself was cluttered with debris, broken crates, and old equipment. To my surprise, I wasn’t alone. A single pony crouched at the back of the lot, behind a refrigerator. Unlike the others, he was facing away from the service station, scanning over the buildings everypony had just come through.

A quick glance around confirmed that we were alone, so I moved toward him.

\leavevmode\llap{“}Hey,” I called out as I neared. “How come you’re out here?”

He glanced my way, then looked out again. “Covering our asses. That gray mare got away, so Storm’s got me watching our rear in case she shows up.”

\leavevmode\llap{“}So they stuck you out here all on your own?”

\leavevmode\llap{“}Yeah,” he replied, a hint of bitterness to his tone. “Not that I don’t mind \textit{not} being shot at, but I’d rather be up front with—”

I recognized a certain measure of irony as my bullet smashed through the back of his skull. The sharp \textit{clack} of my pistol echoed faintly across the lot, almost certainly inaudible past the occasional gunshots from within the building. He fell against the fridge and slid down into an awkward heap on the ground.

Pausing behind an old food crate, I retrieved the detonator, arming it once more. I didn’t trigger it just yet, though. Instead, I hung it on the strap of my ammo pouch, close to hoof in case I could make use of such a dramatic distraction.

The back door of the store lay fallen on the ground, giving me access to the storage room at its rear. I picked my way through the room to the door leading into the store, and peeked in.

Rows of battered shelves left most of the store hidden to me, though the scattered gunshots from the front told me there were plenty of ponies there. I could only see two of the occupants, both sitting behind a battered freezer cabinet at the rear of an aisle. One was a large mare, who wore no barding, but made up for it with her weapon; she wore a battle saddle sporting a minigun, with a chute leading to a large ammo drum opposite it.

Surprisingly, it was the other mare that caught my attention. She wasn’t like the other mercenaries I had seen. She looked like a member of the Mareford Militia. My eyes immediately dropped to her foreleg, spotting the cloth-covered bulge of a PipBuck, and the adrenaline mounted once more. I had no doubts that fancy little arcano-tech device would consider me to be hostile, destroying any benefit my disguise could provide.

I considered my options for a few seconds, then began to pull out all the grenades I had acquired, setting them all on the floor beside the door. As I did so, the ponies outside continued talking.

\leavevmode\llap{“}Because ammo’s expensive. It ain’t like we’re on a time crunch, here.”

\leavevmode\llap{“}Some civilians might investigate the gunfire. We’re not supposed to arrive until after the fight’s over.”

\leavevmode\llap{“}So you arrived when it’s still going on, big deal. I’m sure Shard knows what she’s doing.”

\leavevmode\llap{“}After seeing your ambush, I’m not so certain of that.”

The other mare snorted. “Hey, nopony expected them to just stomp in Fireline’s head and kill his team. None of this shit makes any sense.”

I missed whatever came next. I had taken a grenade with each hoof, pulled their pins with my teeth—which is not nearly as easy as you might think—and after a quick glance around the edge of the doorway, threw one, then the other. As soon as the second one had left my hoof, I threw myself down against the wall, flipped the safety on the detonator, and smashed my hoof against the trigger.

It was as if I’d been bucked in the chest.

The explosion transcended sound, a terrible, angry wall of presence that smashed into me, even behind the intervening bulk of the building. The world felt disjointed afterwards, almost as if I couldn’t tell which way was up or down, and dust filled the air with a dense haze. I never even heard the grenades go off. It was a few seconds before I could pick myself up, detangle myself from my cloak, and look through the doorway again.

The two ponies I had spied upon lay motionless in the smoke and haze. The entire far wall of the store, closest to the convenience store and its bomb, had collapsed, a whole section of the roof coming down with it and giving a view of the sky. Dust choked the air, billowing away from the collapsed area. Past the dust and broken shelves, I could see a few more ponies inside the front of the grocery store, moving away from the destruction.

One by one, I picked up a grenade, pulled its pin, and threw it across the store. I could feel every explosion, though the sharp bangs felt somewhat muted and muffled after the tremendous detonation that had preceded them.

When the last grenade was thrown, I rushed over to the two dead ponies. Green fire erupted from my forehead as I added a horn to my disguise, then used my magic to quickly unbuckle the minigun-equipped battle saddle.

I think my reasoning at the time had been that anything which had survived two demolition charges and a dozen grenades would need something truly excessive to put down.

I had just pulled the battle saddle free when a dust-caked stallion came staggering out of one of the aisles, barely twenty feet away.

Maybe I could have bluffed my way further on. Maybe he would have missed that one of the many ponies there had grown a horn, especially with how dazed he looked. Maybe I could have talked my way into a better position and silently removed a few more ponies before things turned loud.

But the adrenaline was flowing strong, and I had a minigun. I swung the battle saddle around, shoved my shoulder against the back of the frame to brace it, and squeezed my magic around the bit.

The sound that had been so terrifying to be on the receiving end of was so amazingly empowering from the other side of the weapon. The battle saddle jerked and bucked back against me as the minigun roared, tearing into everything before it.

I didn’t aim so much as point it in the general direction and set it loose to do its own thing. I let off the trigger just a second after squeezing it. Amidst the dust that the minigun had kicked up, I could see the motionless form of the stallion, his side shredded by a dozen bullet wounds.

Sharp cracks of gunfire tore through the air, striking shelves in front of me. I dove back behind the freezer cabinet; someone in the front of the store was firing blindly through the shelves in my direction. I brought the battle saddle around, and answered with a much bigger gun. A single second of fire put out a tremendous volume of fire, shredding the vacant display before me. A couple aisles’ shelves finally gave in and collapsed

I let off the trigger, bringing the bucking battle saddle back into control just as a grenade bounced off the remains of the next aisle’s shelves and onto the ground.

I skittered around the cabinet and galloped down the aisle. I was halfway down it when the grenade went off, well behind me.

The adrenaline had taken complete control by then. I rushed forward, intending to get to the end of the aisle, turn the corner, and hose down any remaining mercenaries.

Instead, I got to the corner at the same moment another pony did. We were only feet apart, too close for me to bring my stolen weapon to bear, or for him to aim the assault rifle he held in his teeth.

Lacking any better options, and with the fury of adrenaline pumping through me, I dropped my shoulder and rammed him.

It went about as well as you’d expect.

My disguised form was light and lean, and though he staggered with the impact, he quickly looped a foreleg around me, twisted, and slammed me down atop a section of fallen roof.

I remember having just enough time to be surprised at suddenly looking at clouds before his weight landed atop me; I had just managed to catch my hoof in the sling of his rifle and pull him down with me. He responded with a swift hoof to the side, knocking the wind out of me. When that didn’t get his rifle free, he lowered his head to his chest, drawing back a moment later with a knife clutched in his teeth.

I threw my hooves up at his chest, halting his attack for only a moment. He immediately swiped with a hoof, shoving one of my much weaker legs away, then moved to do the same with the next. The knife loomed above me.

Fortunately, I had two things going for me. One: I’m a changeling. And two: fire tends to provoke very visceral reactions.

Green fire flashed over me as I tore away my disguise, and the stallion flinched back from my sudden and unexpected immolation. It delayed my imminent stabbing by only a moment, but that was all I needed as I snapped my head forward, firing a blast of magic from my horn that sent him stumbling and falling backwards. As he fell, I grabbed my rifle in my magic and emptied the magazine at him. At least one round hit, as he didn’t get up again.

I scrambled up to my hooves, grabbing the fallen battle saddle with my magic once more. I saw then that several ponies lay scattered along the front wall of the store, twisted and limp in death. At least two wore Mareford Militia barding. The store itself, already decayed through the centuries of neglect, had been devastated by my assault. Shelves lay twisted and crumpled in the aisles, and the ceiling was drooping and crumbling, as if it might give in and collapse at any moment. It was hard to believe that anything had survived.

Another pony stepped out around the counter at the end of the next aisle. He looked at me in wide-eyed horror, though whether it was my insectoid appearance or the minigun held in the green fire of my magic, I could only guess. I brought the battle saddle around, and he dove back behind the counter as I opened up, shredding what remained of the shelving and tearing apart the counter in a barrage of sound and bullets. So emboldened was I with my newfound weapons, I pushed harder against the back of the battle saddle’s frame, advancing toward the counter while firing short bursts of a few dozen rounds each.

A grenade arced up, bounced off the remains of the countertop, and landed at my hooves.

I leaped back, my wings buzzing frantically as I shot upward. The grenade went off, hammering at me with the blast. After all the chaos, all the explosions, all the adrenaline, I felt numb.

The pony rose up over the counter, a submachine gun held in his teeth. It would have been the perfect follow-up, except for one fatal flaw.

He hadn’t expected an opponent who could fly.

He was just looking up when I pressed the battle saddle’s frame against my chest and squeezed the firing bit.

With enough bullets, even I can hit what I’m shooting at.

I kept firing until the minigun ran dry a with a jolt, the barrels still spinning as I held the trigger. I floated down, landing in the street just before the grocery store. My right front leg almost gave out as I landed. A quick glance revealed a thin trickle of blood leaking out from a crack in my carapace. I ignored the wound. I couldn’t feel it, so clearly it couldn’t be important. Instead, I looked back to the store, panting. Nothing stirred within it.

To my left, the demolition charge had completed what the apocalypse and two centuries of decay had started, having finally flattened what was left of the motel.

Closer by, the convenience store had ceased to exist, with chunks of wall and ceiling scattered liberally about the lot it had once occupied.

And across the street from it, three faces stared out from behind the service station’s counter.

I was an unfamiliar face, an alien creature of unknown intent. My final armor was stripped away. I stood looking back at the wide-eyed, wary expressions of Dusty and Starlight, and the psychotic, blood-caked grin of Sickle. I was completely exposed, and out of tricks.

My magic flickered out, letting the battle saddle drop noisily to the pavement. I wavered on my hooves.

Lacking any better options, I gave a weak and uncertain smile, my voice rather small after all the storm I had just passed through.

\leavevmode\llap{“}Hey, guys.”