As I’m sure you’ve concluded, I didn’t die there in the street, staring down the barrel of Dusty’s rifle. If he had gunned me down, I obviously wouldn’t be able to record these events. While there were still all sorts of consequences that could have transpired—and indeed, some which did—you at least know that I lived.

I, however, didn’t have the advantage of such information with which to make such conclusions. I just had a very serious and very deadly pony keeping his rifle on me as he gave orders.

\leavevmode\llap{“}Stop right there,” Dusty said, and I obediently came to a halt just a couple yards away from the service station window. He stayed within, in the relative safety, as did Starlight and Sickle. My pistol and rifle, as well as the bolt-action rifle I had taken, lay in the middle of the street where Dusty had me set them.

Unarmed, in the open, held at gunpoint, and without a disguise; it was about the most vulnerable I had ever felt.

\leavevmode\llap{“}Speak,” Dusty commanded, the muzzle of his rifle hardly twitching as he spoke. “Who are you?”

\leavevmode\llap{“}Fuck that,” Starlight said, shoving up to the window. Her eyes glanced to my chest, where my magazine pouch and binoculars still hung, and a moment later I had the muzzle of her Lancer right in my face. “Where did you get that shit?”

I cringed back, eyes squinting as if it would somehow offer some form of protection. “Starlight, wait, it’s me!” I said, only barely keeping myself from backpedaling. “I’m Whisper!”

Her expression contorted to one of supreme disbelief, and it was a full second before she blurted out a sharp, “What?!”

\leavevmode\llap{“}I’m a shapeshifter!”

I’ll be honest, I had been a little tempted to come up with some other story, some way of preserving my actual identity. Perhaps I could have convinced them that Whisper was still out there in the ruins, waiting to be found. Perhaps, but likely not, and even if I did, chances were that the secret would be coming out eventually.

Starlight simply stared at me in silence, skepticism etched into her features. Dusty watched me calmly, past the sights of his rifle. Sickle, meanwhile, had her front legs splayed over the counter, leaning against it and grinning like this was the most entertaining thing she had ever seen. Or at least, I think she was grinning. Between all the blood covering her face and the seemingly misshapen figure under that metal muzzle, it was hard to tell for sure.

After a moment of silence, I relaxed, despite the gleam of the Lancer’s focusing crystal only inches from my face. I gave a small shrug, and a weak and \textit{very} awkward smile. “Like I said in Mareford: I’ve got tricks you hadn’t seen yet.”

Dusty’s eyes narrowed slightly, but it was Starlight who spoke. “Brahminshit. If you’re a shapeshifter, then… shapeshift!”

\leavevmode\llap{“}Okay,” I said, giving a cautious nod. “I can do that, but… could you maybe not have your weapons pointing at me when I do? It’s very sudden and flashy, and I’d really rather not be shot because I startled you.”

Both she and Dusty looked unhappy with the idea, but after a moment Dusty lowered the muzzle of his rifle to point at the ground between my hooves, and a moment later Starlight did the same. It would take them only an instant to bring their weapons to bear, but at least I had more than a single unintentional twitch between me and death.

\leavevmode\llap{“}Okay, fine,” Dusty said. “Now get on with it.”

I nodded, then closed my eyes as I called up my magic.

Adrenaline is an amazing thing. It kicks everything into overdrive, from heart-rate to metabolism, and can even heighten senses in ways. It also dulls pain. That’s useful when you need to fight through an injury. It’s not so useful when you really needed to know you were hurt.

I cried out as pain tore through me. I collapsed to the ground, clutching a foreleg tight against my left side as if I could physically contain the terrible sensation that had erupted there. It felt as if a blade had just been driven in along the edge of my thoracic plate, or between the ribs it had turned into.

My cry died away into a grunt as I grit my teeth, sucking in deep breaths and hissing out again as I held my side. A spot of dampness was slowly but steadily growing.

\leavevmode\llap{“}Okay,” Dusty said, his voice sharp. “What the hell was that all about?”

I wheezed between clenched teeth. “Think… I’ve been shot. Or shrapnel. Something inside… cut me up when I changed.”

That was enough talking for me, I curled up a little more, holding my side. After several seconds, I felt stable enough to crack my eyes open.

Both Dusty and Starlight had their weapons pointed at me. They had been exchanging quiet murmurs, but stopped the moment I looked at them. Sickle, meanwhile, had leaned further out over the counter so she could still see me, though she looked as if she were about to tip over.

I spoke up, trying not to whimper, and not entirely succeeding. “I could really use some medical attention.”

Starlight stared down at me, with only the faintest hint of sympathy behind her glare. “So you can look like her. That doesn’t mean you \textit{are} her. Just… I don’t know, tell me something only she would know.”

If I had ever given serious thought to the previously ludicrous scenario of having to convince a pony that I really was the same individual I had been disguised as, after having revealed my true nature to that pony, perhaps I wouldn’t have felt quite so lost as I did at that moment. Instead, I stammered, eyes wandering as I tried to think past the pain. After several seconds of weak panting, it hit me. I looked up to meet Starlight’s eyes, my voice quiet. “Midnight.”

Starlight’s head drew back at the name, her eyes widening slightly. The muzzle of her Lancer drooped, wavered, and finally lowered all the way. “Holy shit,” she murmured, slowly looking me over from head to hoof.

Slowly, laboriously, I managed to disentangle myself from my stolen cloak and push myself up until I was sitting. As I took a break, panting softly, Dusty finally spoke up, his voice calm. “I always knew you were full of shit. I just didn’t think it went \textit{this} far.”

\leavevmode\llap{“}I’m sorry,” I said, wincing as I shifted my position to put less weight on my side. “I tried to be as honest as I could without—”

Dusty’s expression changed in an instant, eyes narrowing as he snapped, “Well you sure didn’t try very hard!”

The pain made it hard to maintain a calm, neutral expression, but I somehow managed. “It’s not as if I’m the only one who kept secrets, \textit{sergeant}.”

He bristled, the muzzle of his rifle rising to point at me as he growled around its bit. “That’s not even close to the same thing. Fuck, I don’t even know what the hell you are!”

\leavevmode\llap{“}No, it’s not the same thing,” I replied, as my body tried to squeeze out its final dregs of adrenaline. I did my best to stay calm, though my legs trembled, more from pain than from fear. “My secret was a matter of survival. You saw what I look like!” I winced again at the stab of pain in my side, taking a few more breaths to calm down. “...How long do you think I’d last if I wasn’t disguised as a pony? My shapeshifting is the only advantage I have out here. The more ponies know about it, the weaker that advantage becomes… but I was willing to risk giving that up to save your lives.”

Dusty was rigid and silent for several seconds. Then he slowly relaxed, the muzzle of his rifle dropping again. After another second of staring, he finally spoke again. “Starlight? Get her fixed up. Just drag her ass in here first, I don’t want you out in the open if a straggler shows up. And you,” he said to me, “are going to tell us everything, and I mean \textit{fucking everything}.”

I nodded.

Starlight opened the metal door on the backside of the structure and walked up to me, looking entirely uncertain about the situation. After a few moments of indecisive wavering, she lit up her horn. Her magic lifted up under me, helping me get to my hooves and giving me a little stability as I hobbled my way in.

I didn’t think to mention before, but the small service station building bore impressive scars from the fighting. The concrete face of the building had been chewed up and cratered by the incoming fire, leaving small heaps of pulverized concrete around its base, but the building had held strong. When I had stepped in through the door, I saw that the back wall also bore quite a few craters from bullet impacts, forming a nearly perfect rectangle in mirror of the window at the building’s front. The amount of incoming fire must have been intense.

I finally collapsed onto my side behind the counter, my cloak giving a little protection against the small chunks of concrete scattered about the floor.. Dusty glanced my way, but mostly kept his eyes outward while Starlight pulled out her medical supplies. Sickle still leaned on the counter, but had twisted around to see me, leaving her leaning at an awkward angle. With the way she slowly wavered, I half expected her to collapse at any moment.

\leavevmode\llap{“}Well?” Dusty said, casting a sharp glare my way before looking outward again. “Get talking.”

I sighed. This was exactly the sort of thing I had wanted to avoid, but there was no getting around it. “Have you ever heard of changelings?”

\leavevmode\llap{“}Nope,” Dusty said. The relief I felt at having the opportunity to plead my case free of any pre-existing bias clashed with the disappointment at not finding any potential lead on my own kind.

\leavevmode\llap{“}Well, that’s what I am,” I said. “We’re shapeshifters. We use our ability so we can live safely among ponies, and…”

I hesitated, glancing back to where Starlight was laying out her medical supplies.

\leavevmode\llap{“}And?” Dusty prompted with an impatient tone.

I can’t stress enough just how much I did \textit{not} want to elaborate on the subject, but I didn’t see that I had much choice. After all, if I didn’t, and they ever learned even the most basic details of changelings at a later date, it would destroy any chance that they would trust me. As much as I hated it, my only option was to tell them, and hope they were decent enough to not do anything drastic.

\leavevmode\llap{“}...And I want you to appreciate that I could easily not mention what I’m about to tell you. It’s absolutely not in my personal interest for you to know. It’s something you wouldn’t know if I didn’t tell you, and if I were trying to deceive you, it’s the sort of thing I wouldn’t tell you. I’m putting a lot of trust in you by telling you this, and I just want you to consider that.”

Dusty cast another glance my way, rightfully suspicious.

I winced a little as Starlight nudged my leg from my side and pulled aside the cloak. She carefully dabbed a cloth around the deceptively tiny wound to wash away some of the blood.

I took another deep breath, and forced myself to speak. “Changelings need magic. We die without it. Unlike ponies, though, we don’t produce it. So, in order to live, we… we have to get magic from ponies.”

Starlight’s cleaning halted, while Dusty’s attention was fully focused on me. “What?” he asked.

\leavevmode\llap{“}A-and magic is closely tied to emotions, especially positive ones like love. So changelings, we… we can feed on that love to get the magic we need to live…”

That statement broke Sickle. While Dusty and Starlight stared at me, the armored mare cracked up. “Oh, oh wow!” she cried out past her laughter. She finally lost her struggle for balance, collapsing to the side to sit propped up against the wall. “You eat \textit{love?} Hah, you are so \textit{fucked!}”

I couldn’t help scowling at her. “Yeah, it kind of sucks at times. Thanks.”

\leavevmode\llap{“}Shut the fuck up,” Dusty snapped to Sickle before turning to me, glaring. “You mean to tell me you’ve been \textit{feeding} on us this entire time?”

\leavevmode\llap{“}No,” I said, casting an awkward glance to my side. “...Just Starlight. She’s the only one who liked me enough to get anything from.” Using the past tense hurt, even if it was true at the moment. “Even then, I’ve been close to starvation this whole time.”

Starlight sat stock still for a second, then returned to cleaning the wound with a little more firmness.

Sickle was clutching her bloody side, still laughing. “Oh fuck, that hurts. Heh! Wait, so Starlight loves you?” Her laughter grew louder. “I knew you two cunts were fucking! Hah!”

I gritted my teeth as Starlight jabbed the cloth against me again. “Romantic love doesn’t require physical intimacy, nor is it the only kind of love,” I said, even though I was fairly certain Sickle wasn’t actually listening. “Starlight and I are friends.” I hesitated, casting an uncertain look her way. “At least, I hope we still are.”

She didn’t answer, or even meet my eyes. She focused entirely on her work. The cloth floated away, replaced with the forceps. She stuck the tip of them into the wound, and I jerked, grunting out in pain.

\leavevmode\llap{“}Don’t move,” she murmured.

\leavevmode\llap{“}That really hurts,” I grunted between clenched teeth.

She didn’t answer, while I did my best to remain still as she probed around in my wound. My best wasn’t very good, and my panting soon grew increasingly strained.

As Starlight worked, she gave the occasional mumble, though it seemed more to herself or Dusty than to me. “This isn’t like a wound track,” she said, twisting the forceps and moving her head to get a better view while I squirmed. “It’s more like ground meat in here.”

I grunted and whimpered, tears clouding my eyes. “C-can I please have a painkiller? That really, \textit{really} hurts.”

\leavevmode\llap{“}It’s going to hurt a lot more if you keep squirming,” Starlight murmured. “This should be quick.”

The forceps twisted, and I cried out. “Starlight! I’m sorry, okay? Please!”

The forceps froze as Starlight looked me in the face, her eyes suddenly wide. She looked at my pleading expression, then the tears rolling down my cheeks, and her jaw trembled. She wavered for a moment, then the forceps slipped away. I groaned in relief, and she turned, digging through her medical supplies once more.

She didn’t bother with the pills. A few seconds later, a needle floated over to my side. The pricking sensation was barely noticeable beside the pain of my wound, and within moments I could feel that pain slowly but steadily sliding into the background.

Starlight sat silently, staring down at my wound, as if refusing to make eye contact with me. She murmured, “Let me know when it’s working.”

I laid my head down, slowly panting. The feeling of pain didn’t exactly go away. I could still feel it there; it just didn’t \textit{hurt}. “Okay,” I said between breaths. “Thank you.”

She went to work again, but this time the forceps twisting around inside me simply provoked feelings of unease instead of excruciating pain. The feeling of something \textit{tugging} inside of me, and of the fleshy body distending around it, was particularly disturbing. I whimpered quietly as the object was pulled out.

Though I had closed my eyes, I could picture Starlight’s expression of skepticism just from her voice. “Uh, that isn’t a bullet, or shrapnel.”

Dusty stepped over, speaking up a second later. “Is that bone?”

\leavevmode\llap{“}I think it’s part of a rib.”

I whimpered a little more.

The forceps returned, probing through the wound. Eventually, she fished out two twisted fragments of metal and another shard of bone. “Looks like that’s everything,” Starlight said, finally setting those accursed forceps aside.

We eventually retrieved a healing potion from my bags. The vial had cracked at some point, but it had leaked only enough to dampen the bottle. I downed its contents, then lay back again while it went to work.

Past the painkillers, I could feel the strange sensation of my fleshy disguise shifting and mending in a distinctly unnatural way. My breathing slowed, and just half a minute later I felt steady enough to sit up again under my own power. Only a tiny feeling of pain lingered in my side, muted to mere discomfort by the painkillers. “Thank you,” I said, quietly.

Starlight looked away as she packed up the medical supplies again, her ears hanging low.

\leavevmode\llap{“}Okay,” Dusty said, still eying me cautiously. “So you’ve told us what a changeling is. What about \textit{you?}” He stepped away from the counter to sit right in front of me, staring me in the eyes. “Extensive knowledge of old-world tech, particularly military and industrial tech, an expert at hacking, talented at stealth and deception, and a clever talker. Now we can add demolitions and heavy weapons. You didn’t just walk off a farm a few weeks ago.”

They hadn’t shot me—yet—over the whole issue of feeding on them, so the rest was relatively easy. “I’m what’s referred to as an Infiltrator. Or… at least, I was.” I shook my head. “Infiltrators go out from the hive to blend in among ponies. Mostly, it’s to get love, so the hive doesn’t starve. Sometimes… well, we’re already blending in among ponies anyway, so every Infiltrator gets some education in espionage, just in case.”

Dusty stared at me. “So you’re a spy.”

My gaze lowered to the ground. I felt very small. “Basically.”

He was silent for several seconds as he considered me. “Magic-stealing shapeshifting bugs, hiding among ponies, looking like whoever they want. Celestia knows I’ve seen some fucked up things out there, but that takes the cake.” He snorted, then leaned in. “How many of you changelings are there?”

My ears drooped. “As far as I can tell… one.”

Dusty practically growled. “Brahminshit. What was that you were saying about a hive, then?”

I sighed, trying to piece together exactly how to say what I had to say. Unfortunately, Dusty didn’t have the patience to wait.

\leavevmode\llap{“}Hey!” he said, shoving a hoof against my shoulder. “I’m about done with this. No more delaying. No more sidetracks. No thinking up excuses. Just answer the fucking question!”

\leavevmode\llap{“}It’s complicated,” I said, meekly.

\leavevmode\llap{“}No it’s not!” he shouted. “You open your fucking mouth, and you tell us the truth. That’s not complicated!”

\leavevmode\llap{“}Yes it is,” I replied, a little more forcefully. “I could come up with a dozen different lies that you’d buy without problem, but the truth? Dusty, I \textit{lived} through it, and even \textit{I} have a hard time believing it!”

\leavevmode\llap{“}I don’t fucking care!”

Starlight stirred. “Dusty,” she cautioned, but her voice was resigned and quiet, with no strength behind it.

A shudder passed through me. “Fine! You want the truth? You know why I know so much about the old world? It’s because I \textit{lived} it!” Dusty’s eyes narrowed a little more, but I didn’t spare the time to consider what he might be thinking. I just pressed on. “I hatched just after the war kicked off. I grew up and trained while ponies and zebras were all killing each other. I spent \textit{years} in Equestria, right up until you all tried to kill the world!

\leavevmode\llap{“}I got called back, stuffed into a chrysalis to sleep. Except it didn’t go right, did it? I woke up two weeks ago. I wake up to find my queen is dead. My sisters are dead. The whole world is wrecked. S-so I go out, hoping to find others. The first day I’m out, I get held at gunpoint just for approaching some ponies. The second day, I see most of them get slaughtered by raiders!”

Starlight twitched, looking at me.

\leavevmode\llap{“}And it just keeps getting worse!” I was trembling as I rose to my hooves. “I live on \textit{love} of all things, and here I am, stuck in some ruined hellscape where ponies murder each other for \textit{fun!} I’ve barely made it two weeks. I’m starving, and lost, and I’ve nearly died so many times, a-a-and the only thing keeping me going is this p-pointless hope that my entire hive isn’t \textit{fucking dead!}”

Dusty was blinking as he stared back at me, though his glare was gone. When I finally realized I had pressed up, muzzle-to-muzzle with him, I tried to step back, but I was trembling too much. My hind-leg gave out, and I sat back, hard. My vision had gone blurry as tears flowed. When I spoke again, it was barely a whisper. “A-and I just threw all of that away to save the only friends I had, and…”

I was met with silence. Then Sickle stirred, her metal plates clattering noisily in the sudden silence. “Holy shit,” she rumbled, a touch of amusement lingering in her slurred voice. “Must be serious. Whisper used a cuss word.”

She gave a quiet snicker, but I didn’t find the amusement in it. I just sat there, trying not to sob.

Say what you want. I managed to hold out for two whole weeks before the inevitable emotional breakdown. I think I did rather well, all things considered.

The silence dragged on for several seconds before Dusty spoke again. The heat was gone. If anything, his voice was soft and gentle, though cautious. “Is there any way you can prove that?”

I sniffled, raising a shaky hoof to wipe at my eyes. “...What do you want, Dusty?”

He was frowning slightly, his eyes slowly wandering. “Just… anything that would show me I could trust you again.”

\leavevmode\llap{“}I don’t know,” I murmured, slowly shaking my head and sniffling. “Maybe… maybe the place I woke up. There might be something. Or… my old hive… if it’s still there…”

He mulled it over for several long seconds before slowly nodding. “Okay. Okay, if it’s not too far, you can take us there and show us. It’ll have to wait until we’re done here, though. And… sorry, but I’m not letting you carry any weapons until then.”

I nodded weakly.

\leavevmode\llap{“}Shouldn’t take too long. Those explosions you set off will draw a lot of attention. The Militia should have a patrol heading this way already. Soon as they get here, we can get this all sorted out for good.”

A chill passed through me.

Dusty must have noticed my expression, as he added, “I’ll just tell them you got separated and came up behind them. Don’t need to get into details.”

\leavevmode\llap{“}I appreciate it,” I said, wiping at my eyes again and swallowing past the lump in my throat. “But there might be a problem with that.”

Dusty frowned. “What’s that?”

\leavevmode\llap{“}I-I know you might not trust what I have to say, but… but there’s something you should see.”

He considered me, and finally nodded. “Okay. What is it?”

I pushed myself up, standing on still-shaky legs. “It’s in the grocery store.”

There was a hint of suspicion to the way he looked over me, but he finally gestured toward the door. “Lead the way.”

We started out—and immediately halted as Sickle struggled to right herself. “I got it,” she insisted, though her uncoordinated efforts merely left her slumped against a wall.

I could relate, to a degree, not that it stirred much sympathy in me. It was just enough for me to ask, “What’s wrong with Sickle?”

\leavevmode\llap{“}She’s a raging psychopathic bitch,” Starlight said as she pressed a shoulder against Sickle’s, using it and her magic to help the armored mare up. “Aside from that, she lost like a gallon of blood and downed half a bottle of painkillers. Incidentally, if she falls asleep, make sure Dusty or I know it, or she might not ever wake up again.”

\leavevmode\llap{“}I’m fine,” Sickle said, staggering for a couple steps before getting her hooves properly under her. Starlight took a step away, watching the larger mare waver, but despite a stumble, Sickle remained upright. “Fucking cunt,” she added, though she followed that with a quiet chuckle.

We made our way to the grocery store, with Dusty and Starlight scanning for threats. I kept a half-hearted eye out as well, for all the good it would do.

When we got to the edge of the grocery store, I halted at a blown-out window, pointing in. Dusty stepped up next to me, then jerked to a halt. It was at least three seconds before he found the ability to speak again. “What the fuck?”

He climbed in through the window and moved up to the twisted corpse of a mare in Mareford Militia garb. He halted, staring down at her, motionless.

Sickle staggered up to lean against the edge of the window, peering in. As she looked around, I got a good, grisly view of the damage to her face. While the healing potions had worked their magic, I could tell that her muzzle had been broken and set at a slight angle, and the side of it had been mangled to the point where her lips were twisted up, showing off her teeth. It looked rather horrific, especially with the bars of her muzzle leaving some of the details to my imagination.

She didn’t seem to be bothered by it as she looked around the carnage of the store interior. It looked just like what I imagined a war zone would; torn-up walls, broken shelves, hundreds of spent casings, and several dead ponies. She gave a quiet chuckle. “Not bad,” she said in her low rumble, before looking my way and giving a rather mangled grin. “For a little bitch.”

I gave a weak snort and turned away. A moment later I blinked, then turned back on her. “Seriously? After all this, you find out what I really am, and suddenly you \textit{like} me?”

It wasn’t much, but there was a clear hint of… well, perhaps calling it affection would be stretching the definition of the word, as this was still Sickle, but there was certainly some positive emotion there.

\leavevmode\llap{“}What?” Sickle said, leaning back against the edge of the window so she could lift a hoof, gesturing at me. “Ain’t like I needed to see all that bug shit to know you’re a… a two-faced, manipulative little cunt. Nothing new there.”

\leavevmode\llap{“}Then what?” I demanded, as silly as it was to make demands of this mare who could probably still squish me flat even in her drugged state.

She just shrugged.

Dusty suddenly stirred into action, pulling away the dead mare’s assault rifle. “Everypony! Grab what you can, quick. We need to get the hell out of here!”

Starlight, suddenly drawn away from Sickle and my exchange, looked over in surprise. “Huh, what? Why?”

\leavevmode\llap{“}Because this is a Ranger,” he said, quickly throwing the contents of her pouches into his bags. “And when the Militia shows up and sees that we killed some Rangers, we’re as good as dead!”

Sickle chuckled, looked to me, and gestured out to the street. “Better grab your shit.”

I turned and hobbled over to my discarded weapons, grabbing them all up, including the scoped rifle and battle saddle; while I’d spent all of its ammo, it seemed likely it would be worth quite a bit. That was possibly among the least important things to consider at the moment, but it took only a moment to grab the harness in my teeth.

Dusty had just finished stripping the second Ranger when I returned, and anger flashed across his face when he saw me. “Hey! I said no guns!”

\leavevmode\llap{“}We’re a little pressed for time,” I pointed out, and swallowed around the fading lump that still lingered in my throat. Before he could continue to object, I added, “They have a supply wagon, parked behind the ruined motel. Lots of ammo and supplies, and we might need it to get Sickle out of here.”

\leavevmode\llap{“}Hey, I can walk just fine,” Sickle said, stumbling a bit as she pushed off from the wall.

Dusty grit his teeth, but looked back to his looting, grabbing up weapons and supplies. “Fine! Grab what you can and let’s go. Quickly!”

There wasn’t much finesse to our passage. We snatched up loose equipment and saddle bags, grabbing what immediately leaped to our attention rather than taking time to dig deeper. I led them out the back of the store, pausing for only a moment as Dusty grabbed a few things off the Ranger lying there. From there, it was a short trot to where the wagon had been parked, slowed only by Sickle’s pace.

Dusty whistled when he saw the heavy machine gun lying on the ground. “Shit. Bet you’re happy they didn’t open up on you with this instead of that minigun,” he said, glancing to Sickle.

\leavevmode\llap{“}Yeah,” she grumbled. “I’m fucking ecstatic.”

I threw my collected guns into the back, as did everypony else.

\leavevmode\llap{“}You should be,” Dusty said, hooking a leg under it to haul it over; Starlight quickly moved to his side, contributing her magic. “Big gun like this, it’d go through that armor like tissue. Miniguns are pretty shit against armor. They just hit you with enough rounds to finally find some weak points. That or they mixed some AP rounds in there.”

\leavevmode\llap{“}Nopony fucking cares,” Sickle said, hooking a hoof over the edge of the wagon in an attempt to haul herself up, though she only made it halfway. “I’m going to take a nap.”

\leavevmode\llap{“}No you’re not!” Starlight called out. “No sleeping! Take another healing potion or something.”

Sickle grumbled some more, while Starlight and Dusty hauled the machine gun back into the wagon. Once it was in, they both helped Sickle up into the wagon. I offered what meager assistance I could, which mostly consisted of Sickle planting a hoof on top of my head and almost flattening me.

I panted softly afterward, while Dusty turned to me. His eyes looked down to the guns hanging around my neck. “Put them in the wagon.”

I sighed, but relented, placing them in one by one. Still, I couldn’t help arguing my case. “You know, if I intended to harm you, we wouldn’t be here right now.”

\leavevmode\llap{“}I’m giving you a second chance. Don’t push it.” He slipped under the wagon’s harness, getting it good and settled, and started to pull. The wagon creaked under the weight of its contents, but rolled forward. Grit and rubble crunched under the wheels as he pulled it through the ruined lot and toward the street.

Despite the wonders of the healing potion, my side still felt sore, and I could feel a steadily developing limp. “Dusty? Do you mind if I ride in the wagon? I’m feeling pretty weak right now.”

He looked at me, then sighed, looking forward again. “Might as well. Not like I’ll even notice compared to Sickle.”

\leavevmode\llap{“}Thanks,” I said, moving to the rear of the wagon and hauling myself up. I collapsed amidst the pile of guns and ammo, ignoring the bits of metal pressed against my side—my unwounded side, that is—as I curled up. I pulled the cloak over me and closed my eyes. It helped to hold back the tears that still threatened to come back at any moment.

I felt so utterly pathetic. I’d managed to both give up my secret and completely lose control over my own emotions. Worse yet, my own words echoed in my mind. All I had to go on was hope, but my outburst finally consciously acknowledged the fear that I was simply deluding myself. Two centuries was a long time.

I heard Starlight climbing into the wagon behind me, followed by Dusty’s objection. “Hey! Not you. You need to be keeping an eye out!”

\leavevmode\llap{“}And I can see better from up here,” Starlight replied. “Besides, I’m just as light as Whisper.”

Dusty grumbled, muttering under his breath, but didn’t argue any further.

We continued on to the quiet grind of the wheels, the rattle of loosely stored equipment, and the quiet clattering of Sickle’s movements. I heard her unlatch her muzzle and drink something, presumably a healing potion. Otherwise, we rode on in silence, which proceeded to grow more and more overbearing by the minute.

Eventually, Starlight spoke up in a quiet murmur. “...Was kind of cool.”

Sickle rumbled. “What?”

\leavevmode\llap{“}Not you,” Starlight said.

I cracked an eye open to see Starlight looking at me, her expression downcast and ears low. She immediately looked away, her eyes instead settling on the minigun.

Her voice remained quiet as she continued. “Just… we were stuck in that building with fifteen bajillion ponies shooting at us. Then there’s all these explosions, and you come flying out of that building, blazing away with that minigun. It was… kind of badass, I guess.”

She was silent again, looking awkward as her eyes lingered on the weapon.

I sighed faintly, closing my eyes, though it was only a moment before my conscience started to prod at me. As awkward and reluctant as it was, she was reaching out to me, and as miserable as I was feeling for myself, I didn’t need to be shoving her away just so I could wallow a little more.

\textit{Especially} when my own survival was at stake.

So I wiped my eyes again, forced back the remaining sniffles, and spoke. “Not really,” I said in a hoarse murmur. I cleared my throat, swallowed, and tried speaking again. “Mostly lucky. And sneaky.”

She was quiet for a moment before speaking again. “Was still pretty badass, I guess.” She reached out, poking at the minigun’s barrels. “You kind of tore the place up with this thing.”

I gave a weak snort. “Luck and rate of fire, then,” I grumbled. “Dusty was wrong. I don’t have any talent with heavy weapons. I’ve never even touched one before today. I probably fired four or five hundred rounds and hit, what, two ponies?”

She shrugged weakly, still not looking at me. “I think it was more than that.”

\leavevmode\llap{“}Maybe I hit some with the blind fire. Still did better with my pistol.”

Sickle rumbled. “Oh, yeah, you suck,” she said, applying sarcasm about as subtly as she did anything else. I looked over to see that she had unlatched her muzzle. While that last potion had mostly healed the flesh, it did nothing for the poorly-set bone, leaving her snout even more lumpy and misshapen than before her injury. “I mean, you only just killed an entire band of mercs all on your own. \textit{Lame}.”

She snickered a little while I just looked away, feeling strangely annoyed at her contribution. After a couple seconds, her snickering abruptly stopped. “Oh, shit. That means Whimper’s killed more ponies than I have. That just ain’t fucking right!”

I turned to scowl at her. “I’m quite certain that’s not true,” I said, but she just clumsily waved a hoof in my direction, almost jabbing me with her blades by accident.

\leavevmode\llap{“}I mean since we’ve been traveling together, dumbass.”

I grumbled, looking away again.

It was a minute before Starlight spoke again. “So… you were really alive during the war?”

I sighed and reluctantly nodded. “Yeah, I was.”

\leavevmode\llap{“}It’s hard to believe,” she said, before a flash of concern crossed her face. “I mean, it’s strange, not… I don’t…”

She shut her mouth, looking away again with a sudden scowl. It slowly faded over several seconds before she spoke again. “And you’re some kind of super-spy.”

I mumbled my reply. “Not super.”

\leavevmode\llap{“}And you… \textit{feed}… on ponies.”

I sighed, unable to do any more than nod.

Again, she was silent, while I hoped this developing trend of long, awkward pauses wasn’t going to become a common occurrence.

It dragged on, and on, and on, until finally she spoke again, her voice subdued. “You should have told me.”

\leavevmode\llap{“}I’m sorry. I—”

\leavevmode\llap{“}Yeah, I get why you didn’t,” she shot back, then immediately looked away again, as if ashamed at raising her voice. She finished quietly. “You still should have told me.”

She didn’t wait for a reply. She simply stood and hopped off the edge of the wagon to walk next to Dusty. I sighed, laying my head down once more, and feeling even more miserable.

Up ahead, hidden from sight by the edge of the wagon, I heard her speaking to Dusty. “So where the hell are we going, anyway?”

\leavevmode\llap{“}Away,” Dusty answered. “We need to put as much distance between us and here as possible, before they start searching for us. About the only good news is that the explosions were so close that they’ll probably send out a hoof patrol to see what happened, instead of sending one of the birds. Unless they know there were Rangers involved; then we’re fucked.”

\leavevmode\llap{“}So what do we do after we get away?”

\leavevmode\llap{“}I don’t know,” Dusty said, sounding very tired. “We can’t go back to Mareford. We show up there, they’re more likely to shoot us than listen to us, especially with a bunch of dead Rangers.”

Despite how miserable I felt, I decided to speak up. If they knew all about me, I might as well make use of that, especially if it helped rebuild some trust with them. “I could.”

There was a moment of silence from the front of the wagon before Dusty spoke again. “You could what?”

\leavevmode\llap{“}Go to Mareford.”

Again, I heard only the creaking of the wheels. When he finally replied, it was with a bitter tone. “Not sure it would do any good.”

Part of me wanted to just sulk silently, even though I knew it wouldn’t do any good. It was time to be professional. “Depends on how you were hoping to deal with Big Gun,” I said. “Were you wanting to get information that would get him arrested, or whatever it is they do now? Were you wanting to get rid of him through whatever means necessary?”

\leavevmode\llap{“}Are you talking about \textit{murdering} him?”

\leavevmode\llap{“}I’m asking how you want this to end,” I said. Then, in a quieter tone, added “Though after what he did to Silverline, and Quicksilver, and all the other ponies in that caravan, I can’t say I’d mind if it went that way.”

He mulled that over for several seconds before replying. “No. He needs to be dealt with right, so everypony knows exactly how it went down. I’ll… figure something out.”

\leavevmode\llap{“}So what do we do until then?” Starlight asked.

\leavevmode\llap{“}I don’t know. I’ll think of something.” Another pause. “Whisper? Where was that place you were talking about?”

I blinked, stirring enough to lift my head to see him and Starlight looking back at me. “The… place I woke up? I’m not sure, precisely. Near where that tower exploded.”

While Dusty had only a vague idea of what I was talking about, Starlight immediately turned to her PipBuck, looking over the map. It took only a few moments. “Right about there,” she said, floating the device over so Dusty could see it, too. “Could probably get there by tomorrow night.”

\leavevmode\llap{“}If we cut through the city, maybe,” Dusty said.

Starlight smiled. “I’ve been through there probably a hundred times. It might be a dangerous place, but it’s safe enough if you know what you’re doing.” Her smile faded. “Plus, the Mareford guys probably won’t follow us in.”

Dusty grunted. “Through it is, then.”

We continued on, the wagon rocking and shaking slightly with every crack in the ancient road. I lay my head down again, watching the occasional wall of the buildings we passed.

Sickle rustled around in one of her metal saddlebags, followed moments later by the sound of a bottle opening.

Starlight’s reply was immediate. “Hey! I told you, no alcohol! Not with the amount of painkillers you took.”

I looked up as Sickle spit out the bottle cap. “Yeah, and I told you to eat me,” she replied. “Guess you didn’t listen, either.” She followed that up by tilting back the bottle and taking a long drink from it.

All I heard from Starlight in reply was some quiet muttering.

Sickle downed half the bottle in one go. Then she lowered it and, of all things, held it out to me. I stared at it for a few seconds before reaching out and taking it.

Yeah, I don’t like alcohol, but it seemed appropriate at the time. Not so much for the inebriating effects, although at that moment I could understand how some might find that desirable. Instead, it went back to the whole “social interaction” thing; Sickle was making a social gesture, and as depressing as it was, she was the only one currently giving even a glimmer of positive emotions toward me. So I accepted her offer, tilted back the bottle, and took a drink.

I only got a couple gulps in before she snatched the bottle away, spilling cider down my chin. “Hey, fuck-head, I didn’t say you could have the whole damn thing!” I recoiled, but despite the harshness of her reprimand, she was actually smiling. “You want some booze that bad, you should have bought some for yourself,” she said, then tilted back the bottle to drain the rest of it.

I may not have understood Sickle very much, but she had decided she liked me. Perhaps my rampage of gunfire and explosions had earned some respect from her, though with how little I understood her, I wouldn’t even bet on that. At the moment, I had to take what little I could get.

And honestly? I could really use the knowledge that at least one of my companions was fine with me.

So I gave her a weak little smile before laying my head down again, watching the ever increasing number of buildings roll by.

{\br}%
The short trip through Dodge City was not as tense or frantic as I had expected. In fact, it was remarkably placid. Starlight guided Dusty through the maze of streets and ruins, with the occasional backtrack when her PipBuck warned of radiation. There were a few patches of particularly rough ground where the going was difficult, but the numerous healing potions Sickle had taken had worked their magic, and she took over the duty of pulling, easily muscling through the rougher spots.

Despite that, it was an eerie place. Even though the city was in ruins, it seemed wrong to me that it was so quiet. I’d been to Dodge City a few times. It was the only real city in that region of Equestria, and while it wasn’t a teeming metropolis like some cities in the heart of Equestria, it had still been quite a bustling place. Now it was reduced to an empty shell; a silent grave for all the ponies who had lived there, and another vivid reminder to me of how much the world had changed.

My downcast mood started to break around the same time we reached the edge of the city and started out into the barren land beyond. I’d allowed a few hours of feeling sorry for myself, perhaps venting some of the feelings I had been holding back those two weeks. Now it was time to focus again.

So I sat quietly in the wagon, trying to figure what to do next as we continued on into the evening.

It was getting dark when Dusty finally called a halt, many miles away from Dodge City. The rugged terrain had slowed our progress, but it made it easy to find a fairly safe place to camp. Sickle pulled the wagon into a narrow draw, and I wearily hopped down.

A quiet lingered over our group as we set about feeding ourselves. I got a can of beans, which I ate without enthusiasm. I was only about halfway through it when Starlight’s curiosity finally led her to break the silence.

\leavevmode\llap{“}So… do you even need to eat, even though you feed on… love?”

I was surprised it had taken so long for the subject to be brought up again. The topic had been thoroughly sidetracked by more pressing matters, but I had known that was only delaying the inevitable. I was simply surprised at how long that delay had been.

\leavevmode\llap{“}Yes,” I said, plainly. I’d spent enough of the day moping; it was time to be clear and open. “I have similar nutritional needs as a pony, especially when I’m in the form of one. The need for magic is separate from that. Magic is required for several biological functions, especially mental processes. Without it, a changeling rapidly degenerates and dies.”

Starlight frowned, looking me over before asking, “Degenerates how?”

I swallowed another mouthful of beans before answering. “It affects a lot of things, but it hits the nervous system hardest. Early stages of magic starvation include headaches, difficulty focusing, and confusion, as well as physical weakness and a loss of coordination. Once the final bits of magic are used up, it progresses rapidly into severe dementia, paralysis, and organ failure. The whole process from magic depletion to brain death is less than half an hour.”

She had blanched, staring at me. After a moment, she blinked, shaking her head. “That sounds horrible.” Then a questioning, perhaps even suspicious look crossed her face. “You sound awfully calm about it, too.”

\leavevmode\llap{“}I’ve been living with it my whole life,” I said, shrugging. “For me, it’s just one more on the long list of things I need to live. Food, water, air, livable temperature, etcetera, etcetera… and magic.”

Sickle snickered, helpfully adding, “Booze, chems, sex—”

Starlight ignored her. “Yeah, except you take magic from ponies. That’s a bit different.”

Tossing her can aside, Sickle grabbed another. “Hey, didn’t we take this food from some ponies?”

I ignored Sickle as well, even though I was a little impressed by her insight. “Yes, I have to get magic from ponies. That’s the part that causes problems.”

\leavevmode\llap{“}I bet,” Starlight muttered, and focused on her food for a minute, as if taking her anger out on the poor can of pickled beets. Eventually she spoke up again. “So if you’ve been \textit{feeding} on me this whole time, how the hell does that work? And what the hell does that make us to you? Prey?”

I stiffened, ears shooting up. My reply was sharp and simple. “No.”

Dusty looked up from his own food, quirking an eyebrow at me. “You got awful defensive, there.”

I gave him a firm stare. “You could call it a cultural issue,” I said.

He stared right back. “Well why don’t you explain it, then?”

I held his gaze for a few seconds before turning away with a snort. “There are… were… \textit{whatever}... some changelings who saw ponies that way, but their views were antithetical to my hive’s.”

\leavevmode\llap{“}Uh-huh,” Dusty said. “And why the difference?”

\leavevmode\llap{“}History,” I said.

\leavevmode\llap{“}Boring,” Sickle said, jamming a leg-mounted blade into her unmarked can in a crude attempt to open it. I continued to ignore her.

\leavevmode\llap{“}It used to be that most changelings felt that way. Back then, changelings were all united in a single hive.” I snorted. “Ruled by the great Queen Chrysalis,” I said, lacing my words with every ounce of sarcasm and disdain I could muster. “She led our people against Equestria time and again, trying to enslave every pony so she’d have a huge source of magical power. When tensions started rising between ponies and zebras, she helped promote it, hoping to weaken Equestria enough that she could prevail.

\leavevmode\llap{“}Eventually, Equestria had enough. They sent one of their newly equipped armies south, hoping to force Chrysalis to stop her raids, or maybe even capture her. Of course, she fought back. Led the army, even. I don’t think she appreciated just how much had changed. She was very distinctive, and I suspect every soldier there wanted to be the hero that ended her threat. Enough fire battered her defenses that a single bullet got through, striking her in the chest. That was enough to bring down the great Queen.

\leavevmode\llap{“}Lots of changelings died, fighting for her. Some were captured, taken prisoner. They were treated well enough, I suppose, but it didn’t prevent most of them escaping. Most of the survivors, though, scattered. They formed new hives. Some clung to Chrysalis’s ideas. Others recognized them as misguided.

\leavevmode\llap{“}My hive was one of the latter. We recognized that we needed ponies to live, but that didn’t have to lead to hostility. We sought a safer and more beneficial relationship. We still had to feed on ponies, but we sought to help and protect them, too. We made friends, helped ponies who needed it, that sort of thing. It wasn’t a perfect coexistence, but it was a decent arrangement, and one far less likely to provoke retribution.”

\leavevmode\llap{“}How generous of you,” Starlight murmured before getting another mouthful of food.

\leavevmode\llap{“}It was a very practical arrangement,” I replied. “And for those of us who grew up having never seen ponies as prey, it was also easier on the conscience.”

Starlight scowled, through her expression had faded by the time she finished chewing and swallowing her last bite. “And how does—”

\leavevmode\llap{“}Oh, fuck yeah!” Sickle suddenly bellowed. “Pineapple!” We all looked over to see her grinning over the mangled but open can. Her grin slipped away as she noticed the attention. “What? Fuck off, this can’s mine. Get your own!”

She tilted back the can to get at its contents, and we ignored her once more.

\leavevmode\llap{“}Anyway,” Starlight said, pointedly looking at Sickle before turning back to me. “How does this whole ‘feeding’ thing work, anyway?”

I sighed, knowing this was a particularly tricky subject. “Emotions are closely intertwined with magic. Ponies used to celebrate that, back before the war, but it slowly faded away.” I shook my head. “Anyway, when a pony feels strong emotions, some of their magic gets mixed up in it. A changeling can pull those emotions out to feed on them, but it’s extremely obvious, and rather unpleasant. If the pony is feeling love for someone or something, though, that makes things much easier. If a changeling is near enough to that love, or better yet, is the recipient of it, we can feed on it, and extract some of that magic.”

She scowled. “What I mean is, what the hell has that been doing to me?”

\leavevmode\llap{“}Nothing significant or lasting,” I assured her. “Obviously, any magic I drain from a pony isn’t there for them to use, but most ponies generate magic faster than a changeling needs to burn through it to survive. I’ve been as restrained as possible. I’ve also only had fairly mild emotions. Friendly affection works for feeding, but it doesn’t carry much magic. I’ve barely gotten enough to get by, but it means you shouldn’t notice any difference at all.”

She muttered around another beet. “Doesn’t make it any better just because I don’t know about it.” Then she swallowed and spoke again. “So what happens to a pony if you \textit{do} eat more?”

\leavevmode\llap{“}For the most part, it would be like if they spent the magic themselves. They’d simply have less magical reserves.” I hesitated before continuing further. “If drained excessively, the pony would start developing more notable symptoms. Heavy depletion leads to emotional suppression, where all emotions become increasingly muted. The pony would start getting headaches, an increasing sense of fatigue, and their natural magic weakens.”

Starlight’s eyes darted back and forth as she thought. I sighed, my ears drooping, and spoke up before her train of thought brought her to where I could see it going. “And yes, you’ve felt those symptoms before.”

Her eyes focused on me as I continued, quietly. “It was after the raiders ambushed us. I… was in bad shape. It was less than twenty four hours since I’d woken up from centuries of inactivity. If not for my magic, and the ability to shapeshift, I don’t think I could have walked. My body, my natural body, was atrophied, and I was burning through magic just to keep going. I was already suffering borderline magical exhaustion, and I’d pushed my body to the breaking point. I needed a lot of magic right then, or… or I would have probably been dead by the time you woke up. I’m sorry.”

She stared at me for several seconds before huffing and turning back to her food. “Sorry, huh? Why? I’m just like air to you, right?”

I winced. “No! Starlight, I \textit{am} sorry. I had to feed or I would have died, but I didn’t want to hurt you. I don’t want to hurt \textit{anypony}, especially not one I consider my friend.”

Her expression softened slightly, though she remained focused on her food. It was a minute before she replied. “Friends don’t do stuff like that to friends.”

\leavevmode\llap{“}I know,” I said. “That’s why I’m sorry.”

She cast a glance my way. Her eyes lingered for a moment before drifting back over to her food, and she sighed. She didn’t say anything else.

When it was obvious our conversation wasn’t continuing, Dusty chimed in. “So, new rule: no feeding on us.”

I frowned at him. “You might as well tell me I can’t drink anything. That would kill me about about as quickly.”

\leavevmode\llap{“}I’m sure you’ll find a way.”

\leavevmode\llap{“}Dusty, I’ll be lucky to last two days, and that’s with minimal physical exertion and no more magic use than simply maintaining my form.”

He shrugged, though from his frown, I got the impression he wasn’t completely dismissing what I said. “Then why don’t you just drop the whole shapeshifting thing? We all saw what you looked like.”

\leavevmode\llap{“}That might get me a couple hours, if that,” I said. “Unless I need to disguise myself again, at which point I’ll run out even quicker. It takes a lot more to assume a form than it does to maintain it, and I don’t intend to let anypony else know what I am. You three are the only exception to that.”

Sickle spoke up again. “Eh, don’t mind those pussies, just because they’re all creeped out by the whole bug-monster brain-feeding shit.” She rose from her sitting position just to shift around, sprawling back against the side of the wagon so she could spread her legs in a familiarly lewd manner. An armored hoof patted at her crotch. “I’ve got all the lovin’ you can eat, right here.”

I fixed her with my best flat glare. “That’s not how it works,” I said. I looked away, but a moment later my glare faded away as my emotional reaction relented to more practical considerations. “Are you proposing a trade?”

Sickle’s armored head tilted, and she frowned. “What?”

\leavevmode\llap{“}Are you proposing a trade?” I repeated. “Sex for food?”

Starlight finally looked up from her food, giving me a shocked look. “Seriously?”

I didn’t quite meet her gaze. “I have fairly limited options at the moment.”

Sickle growled. “I’m proposing sex because it’s fun, you dumb cunt.” She snorted, tipping back the can to slurp down some more pineapple chunks, then immediately started talking with her mouth full. “Ain’t like I give a flying fuck if you sip a bit of magic or whatever the fuck it is you do, so long as it doesn’t bother me none. Eat away.” She finished off the can and tossed it aside. “If you can find any love in there, you’re welcome to it.”

I frowned, finding that line rather concerning, but eventually I nodded. “In that case, I’ll have to decline the offer of sex. But… thank you.”

Starlight kept watching me out of the corner of her eye as I finished up my can. I looked up to meet her eyes, but she looked away, and I returned to my meal. Soon she was watching me again. I pretended not to notice.

It wasn’t long before our meal was done, and we prepared to sleep. I was just settling onto my bedroll and pulling my blanket over me when Dusty approached Sickle about standing watch. “You’re going to have to step up and actually take a shift tonight, since Whisper is out.”

\leavevmode\llap{“}Fuck that,” Sickle rumbled, stretching out with the faint clinking and clanking of her armor. She rolled onto her side, facing away from him. “She can watch just like she always has.”

\leavevmode\llap{“}Look, with any luck, we’ll get this all sorted out tomorrow, so it’ll just be the one night. Until then, she’s not carrying a gun, and that means she’s not standing watch.”

Sickle draped a foreleg across her face, muffling her voice. “Hey, I don’t carry a gun either, guess I can’t stand watch either.”

\leavevmode\llap{“}You know what I mean.”

\leavevmode\llap{“}Yeah, well, what you mean is fucking stupid,” Sickle replied, then lifted her hoof again to look at him. “She just murdered like forty fucking mercs—”

I quietly interjected, “It wasn’t that many.”

\leavevmode\llap{“}Oh really?” Sickle said, rolling over to look at me. “So just how many ponies do \textit{you} think you killed, today?”

I glared at her for a couple seconds before finally relenting with a sigh. “Probably… somewhere between twenty and thirty.”

\leavevmode\llap{“}Twenty or thirty,” Sickle repeated. “And they weren’t a bunch of dumbass raiders, either. These fuckers were all well-armed mercs and fancy-ass Rangers.” She rolled over again, once more draping her foreleg across her face. “But yeah, I’m sure the only reason she ain’t fucked you up is because you said she can’t have a gun.”

Dusty looked between the two of us, as if uncertain which one was more deserving of his disapproving glare.

I simply muttered, “I don’t think you’re helping, Sickle.”

\leavevmode\llap{“}Who said shit about helping?” she replied.

Finally, Dusty sighed, shaking his head. “You’re really not going to pitch in, are you?”

\leavevmode\llap{“}Fuck off,” Sickle muttered. “I’m sleeping.”

It was still several long seconds before Dusty finally turned away. “Fine. Star and I will make do.”

Sickle muttered something under her breath, but didn’t stir.

Myself, I simply pulled my blanket up a bit more and closed my eyes.

{\br}%
A hoof thumped firmly against my back, stirring me. I don’t think I’d even had time to drift off to sleep. I opened my eyes, looking back over my shoulder, and saw Starlight standing over me. Her expression was tight and wary, and she spoke as soon as I looked up to her. “Were you really going to make that deal with Sickle?”

I sighed, laying my head down again. “I’m an Infiltrator,” I said, my voice quiet. “That means that sometimes I have to do things I’d rather not. If that’s what I had to do to survive, then yeah, I would.”

I could tell from her silence that she wasn’t comfortable with the idea. It took a minute before she replied.

\leavevmode\llap{“}Yeah, look. I’m not happy with all this shit, but I don’t want to make you starve to death just because you were a colossal ass. So if it starts getting to that point, then I’ll… help you.”

I looked up to her again. I could have pointed out how it would be a little more complicated than that, when there were no affection present, but I didn’t. I simply gave a weak smile. “Thanks.”

\leavevmode\llap{“}Only if it’s necessary,” she quickly added. “If I start getting random headaches, I’m kicking your ass, okay?”

My smile grew a little more, along with a soft chuckle. “Okay.”

\leavevmode\llap{“}Okay,” she echoed. I thought I might have caught a tiny hint of a smile. Then she gestured with a hoof. “Get back to sleep.”

I laid my head down again as she walked off, feeling as if a tiny bit of hope had returned.