Being an Infiltrator, I was used to adapting to strange or unexpected circumstances. Improvisation is key when your job involves dozens of unpredictable factors. I always considered myself good at adapting, and it’s one of the skills that saw me placed as an Infiltrator.

The Wasteland tested that adaptability. While it had challenged me in ways I had never expected, and I had certainly stumbled in my attempts to handle that challenge, I had pressed on. While I was certain there were still many facets of this new world that I had yet to face, I was increasingly confident that I could, eventually, face them with the same confidence that I had faced the challenge of infiltrating a largely alien society consumed with xenophobia and war.

I was doing what changelings do best: I was adapting.

In just a couple weeks, the constantly overcast skies had become a simple fact of life. Seeing clear sky again was almost jarring, but in the most pleasant way imaginable.

As we passed under the ragged edge of the clouds and into the warmth of the bare afternoon sunlight, our attention turned upwards. Dusty and Starlight were practically enraptured by the sight. They had seen the sky before, in tiny glimpses, but never in such a wide expanse. To them, the sun had always been held back behind the clouds, like a prisoner glimpsed past the bars of her cell. Seeing it free of constraint, beaming its warmth down upon us, was an experience as new to them as the Wasteland had been to me.

Even Sickle cast the occasional glance upwards, typically followed by pretending she hadn’t.

As for myself, it was an instant dose of nostalgia. Despite all the problems I still faced, I couldn’t help smiling. The dark mood that had lingered over our group faded, as if burned away by the light.

Soon the sky turned to pink and amber as the sun descended to the horizon. We continued on, even as the final light of day faded and the stars began to shine in the darkness. The night was every bit as beautiful as the day as we continued on. It was only a couple more miles to our destination. With the lack of clouds, the night was reasonably bright, lit by the moon that already hung high in the sky above us.

I found it quite fitting that Starlight found the night sky so fascinating. She tripped and stumbled many times, but it didn’t keep her from gazing up at the stars.

About half an hour later, we came across the spur of railroad tracks that had split off from the main line, and followed them up the gentle slope leading to the C.L.T. facility. The first thing to come into view was the building-sized piece of debris lying outside the fence, with its smooth white face and jagged metal back. It loomed in the darkness as we approached.

\leavevmode\llap{“}Woah,” Starlight said as we approached, and she could finally make out the details. “Is that… is that part of that tower that exploded?”

\leavevmode\llap{“}It is,” I replied, nodding. “It was still smoking when I got outside.”

She whistled, peering closely at it as we walked by.

As we made our way around it, the facility came into view: the ratty fence, the vacant guard shack, the collapsed wagon shelter, and finally, the bunker-like concrete entryway, protruding from the side of the hill. The dim light made the whole place feel even more dead and vacant.

Starlight paused beside the guard shack, reading the weather-worn sign. “Crystal Life Technologies, Experimental Site Alpha.” She cocked her head, frowning for a moment, and looked back to me. “What exactly is this place?”

\leavevmode\llap{“}I’m not sure, precisely,” I said, as we passed through the gate. “What I do know is that C.L.T. was a medical company focused on long-term health and longevity, that they were the primary developer of suspended animation technology, and that they tested some of that technology here. It’s that technology that had caught my hive’s interests.”

\leavevmode\llap{“}Is that how you, uh…” Starlight looked around as if searching for the right words. “...got here?”

\leavevmode\llap{“}It seems that way,” I said. “Some combination of that and a hibernation chrysalis.”

She immediately halted. “Wait. Isn’t that the queen you said tried to take over Equestria?”

\leavevmode\llap{“}The word ‘chrysalis’ basically just means cocoon,” I said, suppressing a sigh before continuing. “Although I suppose it’s technically inaccurate, if you want to get down to semantics, so I guess it’s more of a tradition.” A moment’s thought led to a frown. “I suppose that’s probably because of \textit{her}, too.”

\leavevmode\llap{“}Uh-huh.”

I don’t think she quite appreciated the cultural and etymological issues evoked by that word.

We made our way through the vacant yard, toward the gaping maw of the facility entrance. Sickle parked the wagon and unhitched herself while Dusty eyed over the scene.

\leavevmode\llap{“}Any dangers in there we should know about?”

\leavevmode\llap{“}There weren’t any when I left,” I told him. “Unless something moved in during the last couple weeks, it should be clear. There were no turrets or other defenses.” A sudden thought occurred to me. “Do we have any rope? There’s a collapsed stairway to get down to where I woke up, maybe thirty feet deep. I just flew up it, but that’s not really an option for the rest of you.”

Starlight gave me a sideways look, hesitating for a moment before coming back to the conversation. “Yeah, I’ve got some rope. I’m not sure if it’s strong enough to support Sickle.”

Sickle stepped up behind us. “You calling me fat, runt?”

\leavevmode\llap{“}Yeah, Sickle,” Starlight said with a roll of her eyes. “Those were the exact words I used.”

Sickle responded by lifting up a forehoof and “lightly” pushing Starlight, which sent the much smaller pony sprawling. While Starlight grumbled and picked herself up, Sickle just chuckled.

Dusty cut off any further nonsense. “It’s getting late. Let’s check this out and be done with it, so we can get some rest.”

After everyone agreed, we set out. Dusty had me lead once more.

The large hydraulic door, a foot thick, was retracted into the ceiling. It looked like it probably weighed several tons. I didn’t even remember it from when I had left the place just two weeks earlier, which I felt spoke much of my state of mind at the time. It made sense, though; the place had been locked down for two hundred years, so it seemed unsurprising that it should have a serious door to keep it sealed.

Stepping into the lobby was both slightly familiar and incredibly alien at the same time. While the memories were fuzzy from their proximity to my long sleep, I could vaguely remember following these same steps into a well-lit lobby, one that had been clean and simple. The only sign of the troubles of the world had been my hive’s soldiers, keeping guard over the entrance and without disguises.

This time, it was nearly pitch black. Only a narrow cone of floor was dimly lit by the moonlight, which shone softly through the entryway. Starlight lifted her PipBuck, turning up the screen’s brightness until the soft green glow faintly lit the far wall. It gave the space a cavernous and unwelcoming feeling, with the corners of the room fading away into the darkness. Dust coated the surface of the desk we passed as we cautiously walked deeper into the room. The only sound to be heard was the dry echoing of our own hooves and the rattle of our equipment.

The place was dark, silent, and dead.

We slowly made our way back to the hallway at the lobby’s rear and followed it. The lights that had once lit the place so well were now dark, and many of them hung askew or had fallen to the floor. Even the emergency lighting that had illuminated my escape had gone out. In the glow of Starlight’s PipBuck, only the nearest objects were well-lit, cast into sharp contrast with the shadows and muted into a monotonous green. That light quickly faded, leaving us in a tiny island of visibility. Darkness filled the distance, marred only by the occasional glint of green light reflecting off something glossy.

Silence had taken over as we moved, a somber mood quickly settling in. For my companions, I expect it was the nerves of going into this strange place with unknown dangers. For me, it was the knowledge of what had happened in the depths of this facility, and what I was slowly drawing closer to.

As such, I found it remarkably relieving when, as we walked past a small lounge area, Starlight broke the mood.

\leavevmode\llap{“}Oh, hey!” she called out, pointing her PipBuck light toward the back corner of the area beside us. The hallway past us was plunged into darkness as the lounge lit up a little brighter. “Got a couple soda machines here. Think they’re still full?”

Dusty huffed out a faint chuckle that likely would have been inaudible if not for how quiet the place was.

\leavevmode\llap{“}I don’t know,” I said, peering at them from the hall. “I didn’t consider checking them.”

\leavevmode\llap{“}We can do that on the way out,” Dusty said. “I don’t want to get sidetracked until we’ve done what we came here for.”

So we continued on. A few quiet drips pierced the silence as we walked past several broken pipes. Dusty and Starlight kept looking around, alert for both trouble and opportunities, while I led them deeper.

Dusty said nothing when we passed the clusters of pock-marks scarring the walls where bullets had struck them. They were the only signs of wear and tear that I remembered from before my sleep. If anything, they were less notable, now. After two centuries, there was no more sign of the splashes of blood that had marred the scene.

The ruined store-room drew only a cursory glance, though the few rations I hadn’t carried with me on my first pass were quickly added to Starlight’s bags. I picked up the pace, moving toward the stairway. I was suddenly eager to get us all down it as quickly as possible.

Of course, Starlight’s curious searching immediately turned up the reason for my eagerness.

\leavevmode\llap{“}Holy shit!”

I froze, ears drooping, and looked back over my shoulder. Starlight had stepped back from the doorway beside her, casting nervous glances between the room beyond and me.

Dusty stepped up beside her, his expression tightening as he turned to me. “What the hell happened here?”

I sagged, reluctantly turning around to walk back. “I’m not certain of the details,” I said, my voice quiet in the tomb-like atmosphere. “When I got here—the first time, that is, the day the megaspells went off—there were signs of fighting. Bullet holes, a few spots of blood, that sort of thing. I wasn’t told what happened, and… I didn’t ask. I just assumed that the ponies here weren’t keen on letting a bunch of changelings use their facility.”

I stepped up beside Dusty, looking through the doorway at the dimly lit heap of bones beyond.

Dusty watched me for several long seconds before speaking. “So you killed them so you could take their place.”

\leavevmode\llap{“}The world was ending,” I said, my voice sounding weak and tiny. “My Queen wouldn’t have made this move if there was any other way for us to survive.”

\leavevmode\llap{“}Better some ponies die than some changelings, huh?”

I winced, looking away. “It’s not like that. It wasn’t about ponies or changelings. It was about… trying to preserve \textit{something}. Ponies had the Stables. But these ponies? They… they were going to die either way, but we had a chance. I don’t know how it all worked, but I know there was a reason we had to combine a changeling chrysalis with their tech to survive for so long, and even then… most of us didn’t make it.”

I could practically feel his gaze on the back of my head. The silence dragged on for a painful time, finally broken when I heard him exhale. “Plenty of ponies would put their own kin before outsiders,” he said. “Still can’t say I like it.”

\leavevmode\llap{“}I can’t say I do, either,” I replied.

We left the room behind, moving instead to the gaping chasm that had once been a stairway. With Starlight’s PipBuck held out over the abyss, the light shone on the glassy-smooth water below, pierced by several lumps of debris. The landing of the next lower floor was barely visible across the way.

\leavevmode\llap{“}Yeah, fuck that,” Sickle rumbled.

\leavevmode\llap{“}Yeah,” Starlight agreed. “That’s a pretty good drop, and a sheer wall. If the rope can’t hold you, I don’t think you’d be getting out again.”

\leavevmode\llap{“}You might have to wait here,” Dusty said. “The rest of us should make it just fine.”

\leavevmode\llap{“}You fuckers need better ropes,” Sickle grumbled.

Dusty shot her a glare. “Or maybe you need to bring your own supplies.”

As Starlight pulled out her rope, I called up my magic. The faintest tug was all it took to unwind my disguise, and in a flash, my fleshy pony form was stripped away to reveal glossy chitin and diaphanous wings.

\leavevmode\llap{“}Fuck!” Starlight yelped as she jumped away, and nearly collided with a wall. Dusty had his gun up, though with the way it pointed between us, it seemed as if he was uncertain what he might need it for.

Starlight spent a few moments with her eyes closed, taking deep breaths to calm herself down. “Holy hell,” she muttered, finally looking up to shoot me a glare. “It’s easy to forget you’re some weird bug-pony thing until you do shit like that.”

I hesitated before answering quietly. “I suppose I could take that as a compliment of my acting skills.”

While it earned a single quiet snicker from Sickle, Starlight seemed entirely unamused at my attempt at defusing the situation through humor. “Just… give me some damn warning before you do the freaky bug-magic, okay?” She angrily hauled out her rope, focusing on the task at hoof and ignoring me.

She tied the rope around the largest and most stable-looking pipes running overhead, and tossed the other end out into the void. While she and Dusty climbed down one at a time, I pushed my cloak back to clear my wings, and simply flew.

The partially collapsed room beyond was as still and silent as the rest of the facility. The warbling speaker now lay silent, and the spinning orange emergency lights were still and dark. The light from Starlight’s PipBuck bobbed and weaved behind me as she climbed down the rope, and even with the superior low-light vision of my natural eyes, it did little to pierce the gloom.

Hooves splashed down in the water behind me, and a few moments later Starlight stepped out beside me, lighting the room a little better. “So this is all super-creepy,” she muttered, probably more to herself than to me.

I nodded. “It was not the most welcoming of places to have woken up in.”

She glanced my way, silent for a moment. “...Even your voice sounds weird.”

My ears drooped, though I didn’t reply, and a minute later Dusty joined us, followed by Sickle’s voice echoing after us. “Don’t you cunts take too long down there!”

We continued on.

We made our way to the far side of the room and proceeded down the long, straight hallway beyond, the metal grate flooring rattling faintly with each step. We passed doorway after doorway, steadily drawing closer to our destination. Finally, there was only a single doorway left. I came to a halt a few feet away.

\leavevmode\llap{“}What’s wrong?” Dusty asked.

I drew in a deep breath and slowly let it out, doing my best to ignore the suspicious tone of Dusty’s question. “This place has some hard memories,” I said.

I started to draw in breath to elaborate, but I stopped myself. I could delay things for quite a long time, if allowed. Instead, I forced myself forward.

I stepped into the room, the same room I had escaped not so long ago. For a moment, it was a dark void, with only a tiny patch of the floor lit up by the doorway. Distant glints of light reflected what little of the PipBuck’s light pierced the darkness. Two weeks deep in the stagnant air had done little to improve the atmosphere, and a faint but foul undercurrent of rot lingered in the background, along with a subtlest hint of ash.

Then Starlight followed around the corner of the doorway. The light spilled out, my own stark shadow sweeping across the room.

I realized I had halted. I forced myself to continue to walk, past the sodden lump of scattered ash, the murky puddles, and the remains of the first tattered and destroyed chrysalis. I continued on until I stood before the fourth one from the left. Slowly, I raised a hoof to prod at the deflated remains. A bit of fluid sloshed, caught in the folds of the membrane, while the wires hanging from it swayed with the motion.

\leavevmode\llap{“}I was here,” I said; my voice, though quiet, filled the silent space. “I woke up in this chrysalis two weeks ago. I had to tear my way free.”

I took a step back, my hoof falls sharp and prominent as I looked around the room again. “That’s… when I found out I was alone. I was the only one who made it. My sisters, my queen, they were all dead.”

My throat had tightened again, though I didn’t feel the need to cry. I had done that enough already. It still hurt—probably always will—but I could accept it.

I turned to the side, walking slowly over to where I had had gathered them. “She was lying right here,” I said, dipping my muzzle.

A few quiet hoofsteps followed me, and Starlight stepped up beside me. Before us was an uneven lump of ash, turned to a sodden mush by the slow but steady trickle of water leaking down the walls.

In the quiet, I could hear the soft huff of Starlight’s breath.

\leavevmode\llap{“}I barely made it,” I said, breaking the silence. “My body had atrophied from a lack of activity, and I was completely starved. I was on the verge of death, myself, but…” I paused, and then found myself smiling. “But she saved me.”

I turned my head, opening the flap of my saddlebag as I continued. “Queen Ephema wasn’t like most queens. Most of them saw the changelings in their hives as extensions of their will. As minions. She wasn’t like that. Any changeling would gladly give their life for their queen or hive, but only the greatest of queens would give their own life for us.”

Having retrieved my dented medical box, I set it on the ground before me and opened the lid. “She must have woken up before the rest of us, but she was trapped inside. The facility was locked down, and was supposed to remain that way until the computer thought it was safe outside. She had no way out.

\leavevmode\llap{“}She could have woken us up. One of us probably had the electrical knowledge to force the door to open. I might have been able to reprogram the computer to lift the lockdown. But the computer said it was unsafe outside. If she did that, she might be condemning us all to death.

\leavevmode\llap{“}Or maybe she could have traded places with one of us. Any of us would have gladly given her our place if it meant she would have a chance to live.”

My horn lit up, adding to the green glow filling the room. I was distressingly low on magic at that point, but it felt like this gesture deserved the effort. A single love crystal floated up, wrapped in my magic. “Instead, she put her love into these, and let us sleep. She gave up her life so that we might have a chance.”

I looked back over my shoulder. “And then most of us died, anyway.” The smile was gone. The light of my magic winked out as I set the crystal down again.

\leavevmode\llap{“}Ephema,” Starlight said, staring off into space for a moment before looking to me. “You said that was your mother’s name.”

\leavevmode\llap{“}It was.”

\leavevmode\llap{“}...Oh.” She left it at that.

I was silent for a long time before I finally spoke again. “She should be here, instead of me. I don’t even know why I’m here. I’m not special.”

At my side, Starlight recoiled faintly, some reflexive revulsion to what I had said. Her voice croaked for a moment, as if uncertain she should say anything, but she finally spoke. “Why would you say that?”

\leavevmode\llap{“}Because it’s true.”

\leavevmode\llap{“}But you were a…” She searched for the word. “An Infiltrator. That’s something.”

\leavevmode\llap{“}One of a hundred or so,” I said. “Any of them could do what I do. Most of them could probably do it \textit{better}.” I gave a weak snort, finally looking at Starlight. “I’m not some super-spy like you think. I wasn’t infiltrating corrupt organizations, or coordinating intel with the Ministries, or hunting out zebra spies. You know what I really did?”

She blinked back at me, as if uncertain how to reply, so I simply continued on. “I gathered love for the hive. Food. I was one step up from a farmer. The closest I got to espionage was when we discovered the smuggling going through Appleloosa. I got to keep eyes on some drug-runners. That’s it.”

I turned, slowly looking around the room. “I don’t even know why I’m here. I don’t know why I was directed here. I don’t know why I was given a chrysalis. There must have been a few dozen other changelings here, so why did I get one of the few spots?”

\leavevmode\llap{“}Well, you made it,” Starlight said, though hesitantly.

\leavevmode\llap{“}By random chance,” I replied. I motioned a hoof to the back of the room. “From what I gathered from the terminal, I was woken up and released because the generators finally gave out and put the facility on backup power, triggering an emergency evacuation. If that hadn’t happened, I’d still be asleep in that chrysalis. I’d probably have died, just like all my sisters.”

They both remained silent. Dusty hadn’t said a single thing since we entered the room, electing to look around and listen. Starlight kept her attention on me, and in the meager lighting, she looked concerned.

I sighed. “Whatever the reason is, I’m here now. My queen was counting on us to carry on. She even gave her own life to ensure that. I might not have been special, but now I’m the only one left here to carry out that duty.”

I closed up my medical box again, sliding it into my bag before turning back to them. “I know this isn’t the most ideal time for it, but I’d like to ask you for a favor.”

Dusty frowned slightly. “Depends on the favor.”

\leavevmode\llap{“}What is is?” Starlight asked.

\leavevmode\llap{“}Help me find whatever is left of my hive,” I said, looking from one to the other. “There must have been other places like this, other plans to make sure some of us made it. Queen Ephema wasn’t the type to rely on a single point of failure. She would have had other plans in place. Some others might have made it. They might even still be asleep, waiting to be woken up. I owe it to my queen and hive to try to find them.

\leavevmode\llap{“}I’d originally planned on nudging you in the direction I needed to go, so I could do what investigating I could on my own, but now you know what I am, so there’s little reason for me to not ask you directly for your help.”

They glanced at each other, but before they could decide, I added my own offer of assistance. “In exchange, I can offer my services, in full, for whatever task you might need of me. Since I no longer have to hide my true nature from you, we can take full advantage of my abilities.”

Dusty was still frowning. “You mean spying? Assassination?”

\leavevmode\llap{“}If necessary,” I replied. “I know you want Big Gun brought to justice for what he’s done. There were plenty of ponies like him during the war, pursuing profits and power at the expense of other ponies. They use deception and manipulation to get what they want, and that’s exactly what you need to fight them.”

His jaw had tightened. “Just because something \textit{works} doesn’t mean it’s the right thing to do.”

I frowned as well, my eyes wandering as I considered how best to reason with him. After a moment, my eyes settled on his gun. I looked back to his face. “Would you say it’s wrong to kill ponies?”

His head drew back just a hair, and he hesitated before replying. He could see where I was going with this. “That depends.”

\leavevmode\llap{“}Exactly,” I said, then dipped my muzzle, gesturing to his gun. “Lies are like guns, Dusty. I don’t like using guns, but sometimes they’re the right tool for the job, so I use them. Lies are another tool, and just like guns, they can be incredibly dangerous if used irresponsibly. Careless lies can get ponies killed just as easily as bullets, but well-placed lies can save lives. Do you have any idea how much espionage went into protecting Equestria? Because I do. I might not have been involved directly in the major operations, but I caught bits and pieces. The fact is, if we had a few more well-placed lies, the end of the world may have never happened.”

\leavevmode\llap{“}I still don’t like it,” he said.

I nodded. “I doubt you like killing ponies, either.”

He was silent for several seconds before replying. “Depends on the pony.” He shook his head, and changed the topic. “So what happens if you find your… hive?”

\leavevmode\llap{“}I don’t know,” I said, though I felt slightly uncomfortable with the answer. “That depends on them, what state they’re in, and how I can best help them. I might stay with them, or stay out here. Whatever helps the most.”

He nodded, slowly and thoughtfully. “And what happens to us?” he asked. “You told us how important your secret was to you. What if they don’t like the idea of some random outsiders knowing all about them?”

\leavevmode\llap{“}You wouldn’t be in any danger, if that’s what you’re worried about. We don’t turn on our allies, and I’ll be there to speak for you. They might want to keep some things secret from you, but that’s just how espionage goes. Besides, it wouldn’t be the first time we’ve worked with ponies who knew what we are.”

\leavevmode\llap{“}Is that so?” he asked, though he sounded doubtful.

\leavevmode\llap{“}It is,” I said. “While we mostly operated in secret, there were times when it was beneficial to be more open about our assistance. I don’t know all the details—compartmentalization of information, and all that—but I do know there were some high-up members of the Ministry of Awesome who were happy to make use of some changeling Infiltrators against a mutual foe. I even heard rumors that the Ministry Mare herself was involved.”

\leavevmode\llap{“}The Ministry of Awesome?” Starlight asked, an eyebrow raised skeptically. “They got shut down and turned into a storage lot for the other ministries. I mean, their buildings are great for scavenging if you can get past the insane security, but otherwise...”

\leavevmode\llap{“}Officially, yes,” I said. “Many ponies eventually saw it as a wasted effort, led by a showboating braggart who used the Ministry to bolster her own image.” I gave a thin smile. “But that was one of those well-placed lies. In truth, Rainbow Dash ran Equestria's espionage and black-ops.”

\leavevmode\llap{“}And your hive just happened to be helping them,” Dusty said.

\leavevmode\llap{“}We had mutual interests,” I replied, nodding. “Even speaking in purely practical terms, our hive was on the edge of Equestrian territory, and we were much more invested in Equestrian society than the zebras’. We preferred that Equestria should win the war, or at least emerge no worse than it had entered. After the war was over, we might even benefit from having highly placed ponies who knew our hive had come to their aid.”

He looked away, thinking.

\leavevmode\llap{“}Practical reasons aside,” I continued, “we simply liked ponies more. I didn’t like everything about your kind, especially not the rampant xenophobia that had grown over the decades of war, but we understand emotions quite well. Fear and anger were natural, given the situation. The zebras, though, took it to new levels. There’s a reason Equestria developed megaspells that healed and protected, while the zebras turned them into weapons that could kill by the millions.”

Starlight had drawn back a step, her ears hanging low. “So… the zebras really were like all those posters say? I thought those were all exaggerations... “

Dusty snorted angrily. “That’s a load of crap.”

I shook my head. “No, once you get past the lens of culture and experiences, zebras are just like ponies. Individually, they’re quite nice. The problem lay in those cultural differences, and how it subtly colored their view of the world. The short version is, zebras had gotten the idea that your Princess Luna had turned to evil again, and had to be stopped at all costs.”

Starlight slowly shook her head. “This… this is just so freaking weird…”

\leavevmode\llap{“}I think we’re getting off topic,” Dusty said. “But, fine. Let’s say your... hive was nice and friendly with ponies, helped out with the war, all that crap. That was two hundred years ago. What happens if they’re not like that now?”

My ears drooped. I’d done a good job of not consciously dwelling on the possibility, but it couldn’t be avoided forever. I drew in a deep breath and sighed it out. “...If they have changed so much that they would cast aside our ideals and turn on an ally like that, then they are no longer of my hive, and I would have no duty to them.”

Dusty cocked his head, eying me suspiciously. “You’d seriously turn your back on your own kin for a few ponies you met a couple weeks ago?”

\leavevmode\llap{“}It’s not about kin,” I said. I had unconsciously raised my head, adopting a stronger, prouder stance. “It’s about what’s right. It’s how my hive was \textit{founded}. I wasn’t alive for the sundering of the hive, but our people splintered into dozens of hives. Sisters turned into rivals, even fought each other for what they believed. Queen Ephema and my sisters faced many difficulties because of our choices, and I am not going to dishonor their ideals simply because some distant relative has chosen to cast them aside!”

Dusty continued to eye me, but his expression had softened. Finally, he relaxed, nodding. “Okay.”

\leavevmode\llap{“}Okay?”

\leavevmode\llap{“}Okay,” he repeated. “We’ll help.” Then he cast a glance Starlight’s way. “Or I will, at least.”

She nodded faintly. “Yeah.”

\leavevmode\llap{“}But!” Dusty said, holding a hoof up. “You’re going to have to be patient. This doesn’t mean we’re going to drop everything and go running off wherever you want. We’ve got something important to deal with now.”

\leavevmode\llap{“}It’s been two centuries,” I said, forcing myself to shrug. “A few more weeks seems unlikely to make a difference. Does this mean you have an idea of how to proceed?”

\leavevmode\llap{“}I’ll think of something.”

I raised an eyebrow, which earned a quick scowl.

\leavevmode\llap{“}I will,” he asserted. “Look, if we’re done here, let’s head up and get some sleep. We can worry about plans later.”

I agreed, and we turned away to return to the surface.

Just outside the door, Starlight paused to look down the hall. “What’s down that way?”

\leavevmode\llap{“}I don’t know,” I said, looking at the heavy door, barely within the radius of her light. “The door wouldn’t open.”

\leavevmode\llap{“}Yeah?” she asked, taking a step that way. “You don’t think there’d be more of those chrysa-pods back there, do you?”

I hesitated, but after a couple seconds, I shook my head. “Unlikely. We passed several similar rooms on the way here, and none of them held changelings.”

She continued to stare at the door. “You… want to check?”

I hesitated again, and even longer. It was Dusty that spoke first. “Do you think you can get that door open?”

\leavevmode\llap{“}Uh, hello, salvage expert.” She cast a smirk back at Dusty. “Yeah, I can get it open, unless the door’s tracks are all warped. Then it might take a while.”

My input was no longer required as she strode over to the door. Just as I had remembered, it had raised barely a hoof’s width before stopping. Starlight got down to peer under it, then rose again, checking around the edges of the door frame. It took only a few moments to find what she was looking for. She tapped her hoof against a long panel, smiling in the darkness.

A small tool kit floated from her bags, and she pulled out a socket wrench. A quick check found the socket she was looking for, and a minute later, she had removed the long panel, setting it against the wall. Inside, the cables and thick gears that drove the door lay exposed.

I watched her poke around inside the cavity for a minute before she gave a satisfied grunt and turned back to her pack. She produced an odd, long device that I didn’t recognize, sliding it into the gap under the door. She hooked a short rod on an eyelet at one end, and started to crank.

As the device expanded upwards, Dusty leaned in to look. “What is that?”

\leavevmode\llap{“}Scissor jack,” she replied, continuing to spin the crank until the top of the jack had pressed against the underside of the door. She stood again, returning to the open panel. “Mom said she got it at some abandoned train yard. Or was it the tank depot? Anyway, it’s great for getting in small gaps and lifting big, heavy things.”

\leavevmode\llap{“}Just how many tools do you have in those little bags?”

\leavevmode\llap{“}You’ve seen most of it,” she said, and with her muzzle stuck inside the open panel, her voice echoed strangely. “Cutter, jack, prybar, a few basic tools like that socket wrench, a little electrician’s kit, a chisel, stuff like that. Mom and I used to haul around a sledge, too, but it was a bit heavy for going on my own.”

\leavevmode\llap{“}Decent kit,” Dusty noted. While his tone was neutral, I couldn’t help but read a hint of approval in his words.

\leavevmode\llap{“}Eh, it’s a start.” Starlight continued working as she talked. “I’d love to get a more complete set of tools, especially if we’ve got a wagon to haul stuff in. I’m set for most common bolts and such, but every now and then I run into something that I have to improvise with or just cut.” She suddenly stopped, ears perking up as she drew back. “Oh, shit. I could get that hydraulic rescue tool.”

It was perhaps a bit opportunistic of me, but such a clear expression of desire was one I could hardly pass up. “What’s that, now?”

She grinned a little, but quickly hid it by returning to her work. “About a year ago, my mom and I were trading with somepony who had this portable hydraulic tool. Could pry things open like that screw jack, but could also clamp down or even cut right through solid steel. No cranking or anything. I guess rescue ponies used them to get ponies out of bad skywagon crashes, when they couldn’t just muscle or magic their way out. We didn’t get it because it cost more than we made in a year, but now… shit, I could actually afford that.”

\leavevmode\llap{“}Hmm.” I nodded. “Guess I’ll add that to the list, right after PipBuck keys.”

It was a relief when she actually chuckled in reply. “Hell, you find me one of those, you can have all the love you want!”

I saw her smile fade away almost immediately, as if she had finally processed what she had just said. I tried to continue on before the moment had entirely slipped away. “I don’t think it quite works that way, but… thank you for the gesture.”

A moment later, there was a sharp pop from inside the panel, and a deeper \textit{thump} as the door settled in its tracks, held up by the screw jack. Dusty had flinched back, his mouth moving halfway to his gun before he realized how silly the gesture was. “What the heck was that?”

\leavevmode\llap{“}I just disengaged the braking mechanism,” Starlight replied as she stepped back from the panel. Her horn lit again, grasping the handle attached to the screw jack. “Now all the machinery should spin freely.”

She started to crank, and though it was clear it took a good amount of effort, the jack ever so slowly expanded. Just a couple of minutes later, the jack stood at full extension, having opened the gap up to almost one foot in height.

Starlight panted softly, but was already removing her saddlebags. “Not sure if you’ll fit, Dusty. I’ll go check out the rest.”

\leavevmode\llap{“}I’ll go with you,” I said, already removing my own saddlebags and cloak. She hesitated for a moment before nodding.

She dropped to the ground and slid under the door like a slippery eel, and her magic pulled her bags through after her. I was significantly less smooth and swift with my own passage.

It didn’t help that I was acutely focused on the massive steel door brushing against my chest as I squirmed under it, a subtle tactile reminder that I had only a relatively flimsy and ancient screw jack holding back a gruesome death.

Given the typical surroundings during our upbringing, the idea of claustrophobia is almost alien to most changelings, but crawling under that door felt like a moment of understanding. I was surprised just how relieved I was to rise to my hooves again.

\leavevmode\llap{“}Don’t be too long,” Dusty said. I can’t imagine he was too happy about being left alone in the dark. It occurred to me then that he at least had an emergency light source, if need be. His smoking habit had one advantageous side-effect.

We didn’t find much. The rest of the facility was just as worn-down and decrepit as the parts we had already seen, and the diminished numbers of our party made the silence and darkness all the more oppressive. We peeked in on dormitories and offices, none of which held anything of interest. There was no sign of any changelings having ever been there.

The whole time, Starlight kept casting wary glances my way, before turning away and pretending she hadn’t.

We found an evacuation map at an intersection of halls, and paused to read it. It was heavily stained by leaking water, but still readable. It confirmed that we had seen all of the lab areas. The level we were on was mostly labs, living spaces, and all the other areas ponies would commonly use. An entire section had caved in, destroying a good amount of living space and, to Starlight’s disappointment, the medical clinic; she briefly mourned the loss of untouched medical supplies and all the caps it could bring before moving on.

The level below us was all utility, with the map pointing out pumps, water processing, air systems, and all the other mechanisms required to keep the facility operational. It was also completely flooded, almost up to the ceiling. We declined to explore any further.

But after all of that, it was our last stop that proved the most significant. It was a completely incidental stop, one we almost didn’t make. We didn’t expect to find anything useful in the facility’s power station. We simply looked for the sake of thoroughness, at the one last room on the level.

It was clear that something was wrong when Starlight cranked the circular handle on the ship-style door, only for the door to refuse to budge. She gave it a couple of firm kicks before breaking out the pry bar.

It took several hard heaves before the door produced a loud, metallic \textit{ping}. It flew open, banging against the inside wall, propelled by a sudden wind that ended as abruptly as it had begun. My ears popped. “What the heck was that?”

\leavevmode\llap{“}I don’t know,” Starlight said, stepping up to the door to peer in. I stepped up beside her to peer into the burnt-out ruins of the power-monitoring room. As we slowly made our way into the ruined space, I felt an increasing sense of nervousness.

Or so I thought. All the signs were there. My breathing was speeding up, as was my heart-rate. But it kept going. A moment later, Starlight had turned, shoving her shoulder against me. I stumbled and almost fell. Dully, I noticed that my chest felt \textit{wrong}, and the world felt like it was off-balance. She kept pushing, shouting something I didn’t catch, but the sound of alarm was enough to drive home that something was seriously wrong.

We ran back down the hall we had come from, though my hooves felt uncoordinated. The whole world seemed to be closing in, my vision narrowing while everything else turned fuzzy. I don’t think I could even hear my own hoof-steps as I stumbled my way along the grate-covered floor. My head had started pounding at some point.

I must have stumbled and fallen, though I can’t remember the transition from running to being hauled up in Starlight’s hooves.

The world returned to normal almost as quickly as it had devolved, and I found myself lying atop a desk, with Starlight’s hooves wrapped around me. My head still felt thick and foggy, but my senses returned as we lay there, panting.

\leavevmode\llap{“}Holy fuck,” Starlight gasped between pants. I could feel the vibration of her words, with my head resting against her chest. “I hate… this underground… shit!”

I groaned, reaching up to rub my hooves at the sides of my head. “What was that?”

\leavevmode\llap{“}Bad air,” she said, switching to slower, deeper breaths. “There was a fire. Burned up the air. Couldn’t breathe it.”

I blinked, then groaned louder, covering my eyes. When I felt her shift beneath my head, likely questioning my reaction, I spoke again. “I’m an idiot. I grew up in an underground environment. I know how important ventilation is. I should have recognized the signs of carbon dioxide build-up a lot quicker.” I let my hooves fall to my sides again. “Though I guess I’ve barely been back to the hive, lately. I mean, before...”

We lay panting for a few moments before I added, “Thanks.”

I felt her tense for one awkward moment, but to my relief, she relaxed again, dismissing it with an awkward laugh. “Well, I was running for my life in this general direction, anyway, so…”

It was remarkably relieving to share a simple, quiet laugh together. The fading adrenaline and lingering fuzziness in my head made for an almost euphoric moment of relief.

In our entire search of the ancient facility, that moment was the most important thing we found. My relief wasn’t only for having survived my near-asphyxiation. It felt like a moment of reconnection, where Starlight looked at me and simply didn’t see chitin and holes.

We gave the air a good ten minutes to mix and even out before heading back. We were much more acutely focused on our breathing as we headed back to the power station. It was just a quick check to see if there was anything notable, though given the evidence of fire, our hopes were low.

What we found was a giant shard of metal jutting down through the roof of the generator room. Though blackened and warped from fire, the jagged supports on one side contrasting with the once-smooth face of the other made its origins clear. It was another part of that S.P.P. tower that had exploded. This fragment had smashed down here, piercing through both the earth above and the metal ceiling, and destroyed the remaining generators. I had to wonder if another fragment hadn’t been responsible for the collapsed section of the facility.

The resulting inferno must have been intense. The generators looked like they had turned to wax and melted, leaving misshapen mounds of metal in their place. Catwalks had melted across the concrete supports, and the sloping floor ended in a glassy smooth pool, as if it had been filled with water that had, somehow, frozen into steel. The steel covering the ceiling had drooped as it melted, leaving metallic icicles hanging like waiting blades. The remains of the tower had been fused in place, sealing the whole place air-tight.

We headed back. The return trip was considerably more relaxed, almost like a casual stroll through the decrepit halls. No longer distracted by focusing so much on me, Starlight took the opportunity to duck into a few rooms to grab odds and ends. There wasn’t much: a small electronics toolkit, a couple healing potions from a Ministry of Peace first-aid box, and some pony’s stash of candy bars. She even tossed me one of those, and we enjoyed a little treat on the way out.

Starlight slid under the door as easily as she had the first time, and once I had squirmed my way under, she held out a hoof to help me up.

Dusty watched us with a faint frown. “Did you find any more?” He didn’t ask what had taken so long, or about the sudden shifting of air that he would have felt even from back there.

We briefly described what little we had found before heading back.

At the stairwell, I simply flew up ahead of the group. The light from Starlight’s PipBuck barely reached up there, and as I landed, I could only barely make out the silhouette of Sickle lying in the hall, her head resting against one wall and her hind-hooves kicked up against the opposite. She rattled and clinked as she turned her head toward me. “Well you fuckers sure took your sweet time.”

\leavevmode\llap{“}We’re done now,” I said, and given by her lack of reply, that seemed to be sufficient.

Dusty slowly climbed up the rope, which seemed particularly awkward to me given how he had to use his mouth to get a good grip on it. Starlight, naturally, made it look easy and ascended almost as quickly as I had flown. Once they had joined us, Sickle finally sat up. “So, are we all done with this stupid shit, yet?”

Starlight gave a quick roll of her eyes as she retrieved her rope. “Yeah, Sickle. It’s all sorted out.”

\leavevmode\llap{“}About fucking time,” Sickle said as she stood. She never asked about what we’d found down there.

We returned to the entrance of the facility, pausing just long enough for Starlight to break into and loot the soda machines. Then we slept.

{\br}%
I helped take inventory in the morning. While we’d gotten a vague idea of the wagon’s contents before, we hadn’t taken the time to get a detailed count. I reclaimed my weapons with an almost anticlimactic lack of response, and then Dusty and I started going through everything while Starlight recorded the information on her PipBuck.

The details are mostly unimportant. There were hundreds of rounds of ammunition for most of our weapons, including a box of almost one hundred rounds for the monstrous machine gun. A large medical kit carried everything we would need for field surgery except the skill to do so. A dozen grenades had been spared my explosive rampage, and we uncovered a box of mines, although there were only four within it. Then there were the tools for weapons maintenance, a portable field kitchen, all the tarps, poles, and ropes needed for setting up tents or canopies, and some other basic camping gear.

And of course, there were the weapons, including some pistols, submachine guns, shotguns and a small assortment of various rifles. I was actually surprised when Dusty offered me one of the assault rifles. It struck me as a gesture of trust, or perhaps a peace offering.

Practical, too. “It’s more accurate than your pipe rifle,” he said. “It’s also faster firing and a lot more controllable on automatic. Larger magazine and lighter ammo, too.”

While I considered such a weapon largely wasted on me, I had no reason to decline. We had more ammo for it than we did for my pipe rifle, and even I would benefit from the weapon’s advantages.

So it was a bit of a surprise to me that I was hesitant to relinquish my rifle. I eventually justified the upgrade by reasoning that I would still own the old rifle, even if I wasn’t using or carrying it. I spent a fair amount of time thinking on that decision, later in the day. At some point it had ceased to be “Sharps’ rifle” and had become “my rifle”, a curious sort of sentimental attachment that I wasn’t certain I was entirely comfortable with, particularly given the object of that attachment.

Dusty even took the time to show me the finer details of operating the weapon, including how to break it down for cleaning, something he said I’d want to do more than I had for the pipe rifle.

Speaking of which, even after spending a few years as an earth pony, I’m still occasionally amazed by how adept some of them can be at manipulating things with their mouth. Watching Dusty fully strip and reassemble the weapon was impressive, and I’m still not sure how he did it without getting a bunch of oil in his mouth. As it was, I struggled a bit to mimic his feat even with the aid of magic.

I was halfway through assembling the weapon again when Sickle, kicked back against the exterior wall of the guard shack, asked the question that had been lingering in the back of our minds. “So, where the fuck are we going now?”

Starlight shrugged, watching me work.

Dusty frowned, as if thinking.

While I could come up with some destinations of more personal interest, I opted to volunteer a slightly more neutral course. “We do still need to deal with Big Gun.”

\leavevmode\llap{“}Yeah,” Dusty said, though his frown remained. “I’m still trying to think of how to do that.”

I paused in my assembly. “You mean, a way to do that which doesn’t involve my abilities.”

His frown deepened. “Yeah.”

\leavevmode\llap{“}You know he’s just going to keep—”

He quickly held up a hoof. “I know! Look, I just… just give me a little more time to think on this. If I can’t think of anything, then… we’ll do it your way.”

I turned back to assembling my new rifle. “I’m not sure if I like it being called ‘my way’. I don’t like it much, either. I just don’t see that we have many other options in dealing with him before he hurts more ponies.”

He grunted in what seemed to be begrudging agreement.

\leavevmode\llap{“}Oookay,” Sickle slowly said. “So, until Dirt here stops cunting it up, \textit{where the fuck are we going now?}”

Dusty scowled at her. “Oh, fuck off, Sickle. This is serious.”

\leavevmode\llap{“}Yeah, you’re always trying too hard to be serious,” she replied, sneering inside her muzzle. “Just pull the fucking log out of your ass already and let’s get moving.”

Dusty held his tongue, returning to watching me assemble my weapon with an extra-critical eye.

Starlight looked up, offering a suggestion. “If we’re not doing that, what about looking for Whisper’s family?”

Dusty looked over to her, thinking for a moment before finally nodding. “Yeah, we could do that.”

Despite having missed the entire conversation down in the depths of the C.L.T. labs, Sickle shrugged. “Eh, at least it’s better than sitting around and whining all day. So… where the fuck are they?”

\leavevmode\llap{“}I don’t know,” I said.

Starlight chimed in. “That’s kind of implied with the whole “looking for” thing, Sickle.”

Sickle snorted, baring her teeth in a grin. “Go fuck yourself, runt.” She raised a spiked hoof, gesturing to me. “I figure Whimper’s got to know where to start looking.”

\leavevmode\llap{“}I’ve got a few ideas,” I said, though I was aware I sounded rather uncertain. “It’s possible that we had operations at other C.L.T. facilities. That seems like the most likely place to start.”

Dusty nodded. “Okay. Where are those?”

I hesitated before admitting, “I don’t know.”

Sickle gave an annoyed groan, plates rattling as she thumped her head back against the wall.

\leavevmode\llap{“}I need to go through the data we got from Paradise Beach. There might be an address list tucked away in there, though I didn’t see anything obvious. There’s a lot of data, and it didn’t look very well-organized.”

\leavevmode\llap{“}Okay,” Dusty said. “How long will that take?”

\leavevmode\llap{“}A quick but thorough skimming should take a few hours, though I might luck out and find something sooner. A thorough digging through the data could take days.”

\leavevmode\llap{“}Boring,” Sickle said.

\leavevmode\llap{“}I’m not even sure it would turn anything up,” I said. “I found a few references to other offices, but only referred to by region and name. It looked like all of the shipping from that facility went through their regional office in Baltimare.”

Starlight whistled.

\leavevmode\llap{“}Baltimare,” Dusty echoed. “That’s a long ways off, and I’ve only heard bad things about the swamps around there. Even the caravans don’t try to make that run.”

\leavevmode\llap{“}What about your home?” Starlight asked. “I mean, wherever you came from before coming to Equestria. Wouldn’t there be something there?”

I slid the final retaining pin into place on the assault rifle, and pulled the charging handle to make sure the weapon cycled properly. It gave a good excuse to cover my hesitation. I barely noticed Dusty’s nod of approval as I set the weapon down again. “...There might be some clues at the hive. I don’t know. I’m worried about what I’d find there.”

Starlight’s ears drooped. “Oh. Yeah.”

I sighed. “But it’s one of two places I can think of that might offer some sort of lead, and it \textit{is} a lot closer than Baltimare.”

\leavevmode\llap{“}Where?” Dusty asked.

\leavevmode\llap{“}South,” I replied. “Just inside the Badlands.”

Sickle perked up. “Badlands? That sounds fun.”

Dust had his thinking frown on once again. “How far?”

\leavevmode\llap{“}Not far. Probably three or four days on hoof.”

Dusty and Starlight looked to each other. Starlight took his lack of objection as consent, floating up her PipBuck to present the map to me. “So, where are we headed?”

I stared at the map for several long seconds before finally reaching up to manipulate the controls, placing a marker on the map. “You know, you might be the first ponies in history to know the location of our hive.”

She set her PipBuck down between us, and we looked over the map. It wasn’t too far away, and a fraction of the distance to Baltimare. It was even shorter than the same trip would have been during the war; a huge expanse of empty wilderness between us and my hive had been under the administration of the Equestrian Army, but they were no longer around to object to us trespassing. It would even lead us through a settlement, one which hadn’t existed during the war.

A different detail had caught Starlight’s attention. She stared at the screen in silence, her eyes narrowed slightly, ears back. She continued to stare at the screen as she spoke. “Sickle, you seem to know a lot about the raiders around here, right?”

\leavevmode\llap{“}The ones that I ain’t killed yet, yeah.” She chuckled quietly to herself, her armor rattling faintly with the movement.

Starlight raised a hoof, stabbing it down at the screen. “There’s a mine near the tracks, about halfway between here and your shack. Do you know of a group of raiders based there?”

\leavevmode\llap{“}Nah,” Sickle said with a shrug. “Psycho used to run a gang out of there, but she ran off like a little bitch. She knew what I’d do to her if she ever came back.”

\leavevmode\llap{“}Well there was a bunch of raiders there two weeks ago.”

Sickle sat up. Her voice was suddenly serious. “Really?”

\leavevmode\llap{“}Yeah,” Starlight said. “They’re the ones who hit Long Haul’s caravan, the one we were in.”

Dusty grunted, also staring down at the map. A slow smile spread across Sickle’s face.

\leavevmode\llap{“}So I’m thinking,” Starlight said, “we go check out Whisper’s hive.” She poked at the map again. “But we make a little detour along the way.”

Dusty nodded. Sickle started to chuckle, a deep and predatory sound.

Starlight looked up to me.

It was a potentially dangerous diversion, but I didn’t object. “I’m okay with that.”

Though I think that may have been a lie. The truth is, I think I was looking forward to it.