We found only bones.

Dusty and Sickle led the way through the compound. He moved smooth and swift, his rifle tracking over any threatening doorways or windows in the cobbled-together buildings. She trotted along, clanking and rattling, as if she owned the place.

The time we had spent in scouting the raider camp, though a reasonable precaution, had been meaningless. There wasn’t a single living being within the walls.

I had been the first to see the bones lying within. It was the first time we had taken advantage of my abilities. The ridge above the mine was surrounded by rocky slopes and cliffs, but I simply slipped around to the far side and flew up. I was so close when I peered over the edge that I didn’t even need my binoculars to scout the place out. That’s when I saw the skeletons scattered around the area.

When I had rejoined the others and passed on what I saw, we decided to move in. The silence of the raider camp was as oppressive as it was unexpected.

But what really confused and concerned us as we passed among the skeletons was the lack of any sign of violence.

Oh, there were signs of death and grotesquery in abundance, as one would expect of a raider camp led by a pony named “Psycho”. Skulls and other bones were lashed to the front wall, a caged-in circle in the middle of the yard was stained with blood, and a pair of decaying pony pelts were hung like banners before one of the buildings.

But the skeletal remains showed no obvious signs of violence. Several crows still lingered, but they hopped and flew away lazily, as if largely unconcerned by our presence. They had already picked most of the meat from the bones, and it seemed like their actions were the only reason the skeletons weren’t perfectly intact. They looked disturbingly peaceful.

Once we’d ensured that there were no living ponies, we looked closer at the bodies. Their barding and gear hung loose around their bones. None of the bones were broken. None of the barding was pierced. The ground beneath them wasn’t stained with blood. Their weapons lay beside them. Of the two firearms we found, an automatic pipe rifle and a rusty bolt-action, neither had been fired. They had fallen to the ground with full magazines and loaded chambers. It was as if the raiders had simply dropped dead.

So it was all a little unnerving.

We had entered the main building, a crude shack built into the entrance of the mine, when Sickle approached one of the skeletons, cursing. “Fuck. That’s got to be Psycho. Some fucker killed that bitch before I could.”

I assume she identified the raider by the rather distinctive barding the former-pony had worn. A thick, metal chest-piece had a fan of four spikes across the back, each with a pony skull impaled on it. Another skull had straps bolted onto it, resting loosely above her own skull. A sledgehammer with a blade welded on lay beside her.

We continued on. The raiders’ structure extended a fair way into the entrance of the mine, eventually ending with a door, bolted shut on our side. We opened the door to briefly check the other side, then closed and bolted it again. We expected the mines ran much deeper than we cared to explore.

Returning, we did a quick search of the compound. It became immediately apparent that the place hadn’t been looted. Sickle accumulated a small stockpile of chems and booze, and we turned up a fair amount of food, water, and even a small stash of caps. It was nothing significant compared to what we already had loaded in our wagon, but it was something.

I have to admit, I found myself just a little disappointed. While I was satisfied that these dangerous raiders had been removed, I had wanted to be a part of that solution. Arriving to find them all dead felt almost as if I had been cheated. It was absurd, I told myself; practically speaking, our objective in coming here had been achieved, one way or another, and it had required no effort or risk on our part.

Emotionally speaking, I recognized that I had sought some form of retribution, whether for the lives these ponies had taken or the harsh introduction to the Wasteland that they had inflicted upon me. It was unhealthy and unproductive thinking.

Sickle took it a good deal worse, and spent a few minutes kicking at walls, demolishing what had once been Psycho’s home.

The rest of us gathered in the courtyard, looking at a few of the skeletons laid out there.

\leavevmode\llap{“}At least a week,” Dusty said, nudging a skull with his hoof. “Maybe longer.”

\leavevmode\llap{“}How’d they die?” Starlight asked from a bit further away.

\leavevmode\llap{“}I don’t know.” Dusty circled slowly around the body, looking over the bones. “Maybe it was your alicorn friend.”

He hadn’t been too happy to hear that we’d first seen the alicorn around here. Our recon had been as much to make sure she wasn’t still there as it was to get a tactical appraisal of the raider camp.

Sickle stuck her head out a hole she had kicked in the wall. “Whoever it was, I’m going beat the fuck out of them!” Her head withdrew, followed a moment later by the loud clang and smash of her armored hooves kicking something heavy and metallic.

We moved on as soon as she was finished tearing the place apart. It was already late in the evening, and we wanted to put as much distance between us and that place as we could.

{\br}%
It was early the next day when the questions inevitably began to flow.

\leavevmode\llap{“}So, what was Appleloosa like during the war?”

I looked up from PipBuck to look over to Starlight. She had lent it to me so I could read through the data we had downloaded from Paradise Beach. Reading while riding in the wagon was a lot easier than reading while walking, but the motion made my head feel fuzzy if I kept at it for too long. I didn’t mind the distraction.

\leavevmode\llap{“}It was nice enough,” I said with a shrug. “There were a few thousand ponies living there by the time I moved in, and a good deal of the rail traffic went through the town. The ponies were nice enough, even if there was the occasional tension between them and the buffalo.”

\leavevmode\llap{“}You didn’t see much of the war, then?”

I shook my head. “No. I was a long ways away from it. Not my field. Saw the occasional military train come through with troops or tanks, but that’s it. The Zebra military never came near Appleloosa. If not for the arms factory, the news, and the visits from the Ministries, it might have been easy to forget there was a war going on.”

She slowly nodded. “Sounds kinda nice, yeah.”

We continued on, the wagon lightly bouncing as it rolled across the dry earth. Some time later, she asked, “Did you ever meet one of the princesses?”

I actually laughed, though quietly. “Thank goodness, no.” To her surprised expression, I explained, “They were ancient and incredibly powerful beings that we didn’t entirely understand, and their previous encounters with changelings had been less than ideal. I wouldn’t be surprised if they’d developed magic that let them recognize a changeling on sight. I’d rather not take that chance.”

Soon, the questions became more like a game. “Okay, favorite pre-apocalypse pastime.”

\leavevmode\llap{“}Hmm… tossup between reading and lazy conversations with friends.” I smiled.

\leavevmode\llap{“}Those holes in your legs. Are they, uh, normal?”

\leavevmode\llap{“}Yes.”

\leavevmode\llap{“}So all changelings have them? Why?”

\leavevmode\llap{“}I might as well ask why ponies don’t.” I shrugged. “We just do.”

\leavevmode\llap{“}Best place in Equestria, before, you know…?”

\leavevmode\llap{“}I always wanted to see Canterlot. The pictures looked amazing. I’m not sure I’d have the courage for it, though.”

Several more casual questions came as we traveled, until she hit one that gave me pause.

\leavevmode\llap{“}Which princess do you think was better?”

I blinked, taking a moment before replying. “I’ve seen that question start fights. Though that usually involved alcohol.”

She snickered, but stuck to her guns. “You didn’t answer the question.”

\leavevmode\llap{“}Not much of an answer to give. Mind, my impression was entirely second-hoof, but they each seemed like they had their own strengths, and their own flaws. They were both decent, I guess. Just… from a distance.”

She nodded, thinking on that before asking, “Okay, how about the Ministries? You said they visited Appleloosa?”

\leavevmode\llap{“}Yeah, and I tried to stay as far away from that as possible. Mostly it was the Ministry of Wartime Technology, which wasn’t so bad. I saw the Ministry Mare, Applejack, a few times, though only from a distance. The one that scared me the most was the Ministry of Morale.”

Starlight laughed. “What, the ‘Pinkie Pie is watching you’ Ministry? Yeah, those posters are \textit{still} creepy as hell.”

I sighed. “Oh, wonderful. Of all the things that survived, those had to make it.”

\leavevmode\llap{“}Lots of posters made it,” she said. “Which is kind of weird, actually. I’ve seen burned out buildings that still had unburnt posters in them. I’ve heard jokes that the ghost of Pinkie Pie goes around putting them up.”

She laughed, until she realized I wasn’t. I was staring off into space, thinking, until she finally spoke up again. “...What?”

I blinked, refocusing. “Sorry. I was just thinking. Miss Pie was a bit of an enigmatic figure. From the stories I’ve heard of her, that story is… just on the edge of plausibility.”

\leavevmode\llap{“}What?” she repeated, almost stumbling. “Seriously? I just figured ponies were redecorating or something.”

\leavevmode\llap{“}She was a strange one,” I said. “From what I heard, even her life-long friends couldn’t understand her. I know she had the most peculiar manifestations of earth pony magic, to the point that she would just intuitively \textit{know} things. I’ve heard she discovered an Infiltrator from another hive because she got an \textit{itch}. And she ran Equestria’s counterspying efforts, so we paid a lot of attention to her. Still, we mostly knew old stories and rumors, and I don’t know which ones to believe. Coming back from death as a poster-planting spirit wouldn’t be the strangest thing I’ve heard attributed to her.”

\leavevmode\llap{“}Wow.” Starlight stared off into space for a moment before shuddering. “Luna, those posters were creepy enough before I knew that. What if they’re true, and she’s \textit{still} watching us?!”

Sickle called back. “We’ll just have to give the bitch a good show, then.”

\leavevmode\llap{“}Hah, hah,” Starlight said, before looking back to me. “So… what kinds of stories did you hear?”

\leavevmode\llap{“}Plenty. She was a very public figure, helped save Equestria a few times, bore one of the Elements of Harmony, that kind of thing. Many of the stories were historically documented events, while others are just rumors. For example, we’d hear weird rumors, like her being in two places at once or vanishing if you weren’t looking right at her, which all seemed impossible, but then we have the stories we know were true, such as how she defeated one of Nightmare Moon’s plots by singing and laughing.”

\leavevmode\llap{“}Huh.” Starlight walked along in silence for several seconds before speaking again. “So, uh… how exactly does that work?”

I considered that for a few moments. Then I moved a hoof, turning off the PipBuck’s screen. “Well…”

{\br}%
A fair portion of the day was spent telling tales of the Ministry Mares, slowly branching out into other celebrities, and even into bits of the war and daily life. Starlight found it surprising to hear that my “pony” job in Appleloosa had been that of a shipping clerk, though after a moment of consideration, she said it was easy to picture me doing that.

Dusty cleverly noted that it let me keep tabs on materials shipped through the area. Even if it was unlikely to be terribly useful information to my hive, such seemingly insignificant details could contribute to a better understanding of complex situations.

All in all, the scattered stories made our travels less tedious, filling the time as we crossed the last of the rougher hills south of Rust, and into the increasingly flat desert beyond.

The next morning, we made our way down the shallow draw of an ancient, dry stream, and emerged into a broad, flat basin. On the far horizon, barely visible in the overcast gloom, was the hazy sight of the hills that marked the edge of the Badlands. Between them and us lay dozens of miles of mostly-flat terrain, all dry earth cluttered with scattered shrubs.

We caught the glint of metal almost ten minutes before we finally drew near its source. A chain-link fence lay across our path, stretching off to the end of our sight in either direction. It had fallen over in several places. The metal signs attached to it every couple hundred yards or so were all worn and rusted, but the large letters declaring it to be the property of the Equestrian Army were clearly visible, as were the warning of extreme danger and the use of lethal force to prevent trespassing. Fortunately, the warnings were about two hundred years out of date.

Dusty read over the nearby sign as we angled for a gap in the fence. “What is this place?”

\leavevmode\llap{“}It’s an Equestrian Army military testing ground,” I said. “The Pale Sands Spell Range.”

Dusty’s ears pinned back, while Starlight asked, “What did they test here?”

\leavevmode\llap{“}Megaspells.” In what was perhaps a little morbidly dramatic, I added, “This is where Equestria practiced the end of the world.”

\leavevmode\llap{“}I’ve heard of this place,” Dusty said, eyes sweeping along the horizon. “It’s supposed to be dangerous. I guess scavengers would go in, hoping to find some old military equipment, and most of them never made it out. Traders avoid the area. Maybe raiders, maybe something worse.”

\leavevmode\llap{“}Probably old military robots,” Starlight said.

Sickle merely chuckled. “Sounds good. This trip’s been boring as shit.”

\leavevmode\llap{“}Just keep your eyes out,” Dusty said. “That includes you, Whisper. I want you glassing the horizon regularly. We might even take advantage of those wings and send you on some recon flights.” He looked me over. “The black stands out a bit. Can you shapeshift into something that blends in a bit better?”

\leavevmode\llap{“}I could,” I said, with a tone that made it clear I’d rather not. “But shapeshifting takes a fair amount of energy, and I’m running pretty low. I’d prefer to conserve what little I have left.”

Starlight’s ears perked up. “You’re still low on, er… magic?”

I nodded.

Starlight chewed on her lip a moment. Then she turned, clambering up the side of the wagon beside me. I was about to ask what she was doing when she grabbed me in a tight hug, burying her head beside mine.

I stiffened in surprise, but slowly relaxed, and even chuckled softly as I looped my forelegs around her. “It doesn’t quite work that way, but… thank you.”

\leavevmode\llap{“}Try making out!” Sickle called back. “Some good fucking should get the love flowing.”

\leavevmode\llap{“}And it \textit{definitely} doesn’t work that way!” I replied as Starlight drew back, trying to hide a blush.

\leavevmode\llap{“}Sorry,” Starlight said. “I just, you know… I don’t want you to starve or anything.”

\leavevmode\llap{“}I appreciate it,” I said, offering a smile. “Though that concern for my health should do enough on its own. I won’t be able to do much magic, but at least I can survive off what I’m getting from you and Sickle.”

Her head drew back with an expression of skepticism that bordered on distaste, as if the thought itself was going to dirty her. “Sickle?”

I shrugged and sighed. “Yeah. For some reason, she likes me now. Go figure.”

\leavevmode\llap{“}Huh.” Starlight looked at the heavily armored mare ahead of us. “Guess you impressed her with that fight near Mareford.”

\leavevmode\llap{“}Oh, yeah,” Sickle said. “I’m all super impressed with how she shot a bunch of ponies in the back like a cowardly little bitch. Woo.”

Starlight frowned. “Or she’s an erratic psychopath, and we shouldn’t bother trying to figure out what she likes.”

\leavevmode\llap{“}Oh, that’s easy,” Sickle replied. “I like long romantic walks in the desert. And ice cream.”

Even though I found her sarcasm distasteful, a reply came to mind that I couldn’t resist. “And pineapple.”

\leavevmode\llap{“}Fuck yeah,” Sickle said, and though she didn’t look back, I had no doubt she was grinning. “Pineapple is awesome.”

Even Starlight chuckled a bit at that, though she made a visible effort to resist. She quickly tried to turn back the subject. “So, is that why you haven’t shapeshifted? I thought you’d want to look like a normal pony in case we came across anypony.”

\leavevmode\llap{“}I’m just conserving my energy,” I said. “I’ll change before we meet anypony, but for now I’ll take advantage of no longer needing to hide myself from you.” I reached up with a hoof, pulling at the edge of my new attire. “Though I’m glad I got this cloak to conceal myself with. After so many years of hiding what I am, I’m feeling a \textit{little} bit exposed.”

She slowly nodded. “Still… if you’re that, um, hungry, isn’t there anything we can do?”

\leavevmode\llap{“}A vacation might help,” I said, smiling a little, then shrugged. “Otherwise, not really. Time together should do enough. Anything else would be… either manipulative or unpleasant.”

\leavevmode\llap{“}How so?”

I frowned a little, but I didn’t allow my hesitation with the subject to keep me silent. “Manipulative would be trying to steer a conversation toward a topic that would draw out feelings of love for something or somepony, which would let me feed on it. Something like… your mother.” Her ears flicked back. “Unpleasant would be… \textit{forcefully} feeding. It’s a practice my hive frowns upon in all but the most dire circumstances. It basically amounts to reaching in and pulling out a pony’s magic, but it’s… unpleasant is probably insufficient. It’s emotionally torturous on the pony. It’s literally ripping the love out of them.”

Starlight’s sat there, silently, as her gaze lowered to our hooves, meandering around for a few moments before fixing on her PipBuck, laid before us. She got up to move, but rather than leaving, she sidled up and lay beside me, close enough that her soft coat brushed against my carapace.

One forehoof reached out, lightly brushing against the PipBuck’s case. “My mother inherited this from her own mother,” she said, her voice quiet. “It’s been passed down from mother to daughter, ever since my great, great grandmother left Stable 63. Each of them left diaries and notes and recordings. The map is dotted with markers showing where they’ve been. Some nights, my mom and I would sit down, and she’d read some of her mother’s stories to me, or we’d listen to some of the music on it, or…”

She paused, then pulled out a set of earbuds in her magic. One end plugged into the PipBuck. The two earbuds floated between us, with one offered to me. I accepted it, and we each slipped our respective earbud into an ear.

Starlight flicked through the menus, then hit play. I recognized the music with the first few notes, even before Sweetie Belle started to sing. It was one of her more recent pieces, slow and soft in tone, but full of emotion. I don’t remember the words, but I remember the tune, and I remember the feelings. There was sadness and worry, but also a sense of hope that made the song beautiful to my ears. To hear it now, as clear and perfect as the song had been two centuries ago, was wonderfully surreal, as if that time was truly as recent as my own memories made it seem.

That hope carried a bittersweet undertone when I realized that she had probably died along with the millions of other ponies who had perished in the apocalypse. Even if her position in Stable-Tec had allowed her to survive the megaspells, she would have still died well over a century ago.

The song ended, and Starlight took a deep breath, slowly letting it out. Her eyes were watering. “There’s a bunch of faster paced songs I really like, but this one’s always been my favorite. My mom would play it for me any time I asked, or even just to cheer me up. I… haven’t listened to it since she died.”

A moment later she was tapping the buttons again, navigating through the directories. One was a list of names. I only recognized the last two, Starlight and Midnight. Above them were Nova, Firelight, and Dusk. She selected Midnight. A list of files appeared, sorted by date. She opened the first file, twenty-something years old.

The voice that came across the earbud was almost indistinguishable from Starlight. Midnight’s voice was thick with emotion, as if she had been crying recently, though she spoke with a sure confidence.

\leavevmode\llap{“}I don’t know who you are, yet. I don’t know what I’ll name you, or what you’re like. I just… I just know that I love you, and I can’t wait to get to know you…”

The recording ended, and Starlight sniffled. “She recorded that three years before I was born. It’s like… she knew…”

There was so much love. There was even a strong undercurrent of affection for me. But, even though I couldn’t sense it the same way I could sense love, I knew there was also a great sadness. I reached up a foreleg, slipping it around her shoulders, and gave a firm squeeze. She was enduring some very strong emotions for my sake.

She leaned into the hug, then wiped at her eyes. “Were… were you close with Ephema?”

\leavevmode\llap{“}Not as close as you were with your own mother, I think. Our duties kept us apart, and there were so many of us for her to care for.” I gave a weak smile. “But I loved her, and I know she loved us. She always found little ways to show it.”

I blinked, finding that I had teared up a little at the memory.

Starlight noticed, too, and nudged me lightly with her shoulders. “Hey, don’t cry. Creepy bug-monsters shouldn’t cry.” She smiled, a fragile smile that betrayed a fear that I wouldn’t appreciate the joke.

I chuckled softly, and she relaxed. “Hey, now,” I said, smiling. “If you think I’m all weird and creepy, imagine what it was like for me coming to Equestria. All you ponies, with your squishy hides and garish colors. And hair, hair \textit{everywhere}, getting into \textit{everything}. It was a nightmare!”

She giggled, wiping at her eyes again. “Okay, the hair can be a little annoying at times. But hey, we’re not \textit{all} garish!”

\leavevmode\llap{“}True,” I said, giving another squeeze before releasing her. “You’re a rather soothing shade of dark blue. It’s a lot better than all the pinks and purples and rainbows everywhere.”

\leavevmode\llap{“}Hey!” Sickle called back. “The fuck is wrong with pink?”

\leavevmode\llap{“}It was a bit excessive,” I said. “Though I guess it’s not quite as ever-present now as it was back then.”

\leavevmode\llap{“}There’s nothing wrong with pink,” Sickle grumbled. “‘Sides, all the best parts are pink.”

\leavevmode\llap{“}Ignoring that,” Starlight said before nudging me again. “I guess you’ve got a kind of cool black and armored look going for you.” Her smile faltered. “Though it kinda reminds me of those Enclave goons. Er, no offense.”

I shook my head. “Glossy black and solidly colored eyes? Yeah, I understand what you mean. In fact, I heard rumors that the pegasus power armor was inspired by changelings. There was some talk that Rainbow Dash had some sort of fascination with changelings, for better or worse, which might have influenced their design. They were a collaboration between the Ministries of Awesome and Image.”

Starlight tilted her head, looking curiously at me. “Fascination, huh?”

\leavevmode\llap{“}Yeah. Depending on the rumor you listened to, she was either fascinated with our ability to shapeshift for personal reasons, focused on practicality and our possible utility as spies for Equestria, or secretly wanted to exterminate our entire species. I have no clue which, if any, was true.”

\leavevmode\llap{“}Huh.” She looked down at my chest, then reached out and prodded me. Naturally, my hard outer shell didn’t give like flesh would. “So… is that like armor, then? How much protection does it give?”

\leavevmode\llap{“}Not as much as I’d like,” I said, giving a wry smile. “That wasn’t so much of a concern in the past, but given the amount of firefights I’ve gotten in since waking up here, I think my priorities have changed.” I tapped my own hoof against my chest, producing a soft clopping sound. “A changeling’s exoskeleton is good protection against minor cuts, abrasions, and bruises, but that’s about it. It might help a little if somepony tries to kick me, but I don’t think it’d even slow down a bullet.”

Starlight blinked, a hint of unease coloring her expression. “Exoskeleton. That’s… just weird.”

\leavevmode\llap{“}It’s just as weird going the other way,” I said, chuckling a little. “I remember the first time I took an endoskeletal form. I was… four, I think. I freaked out. It was weird enough feeling parts \textit{jiggling} every time I moved. Somehow, I got this absurd idea that I’d messed up my transformation and I was melting. But the weirdest part? Feeling the bones inside me. I could press against the squishy, possibly melting parts and feel something \textit{solid} under them, moving along with me. That freaked me out, like there was some alien \textit{thing} inside my body, trying to tear its way out. I had nightmares for a week!”

Starlight responded to my childhood trauma by falling back against the heap of supplies and laughing. To be fair, I chuckled a bit at my own expense, as well.

Her laughter faded, eventually ending in a long sigh. “Ahhhh… that’s kinda creepy.”

I gave another chuckle and shrugged. “You get used to some weirdness when you can change shape at will.”

Lying on her back, Starlight stared up at the gray, overcast sky, lost in thought for a moment. “I could see advantages to that.”

After a moment of silence, I added a bit more to my story. “The other reason I remember that whole event was because of Ephema. She took the time to comfort me, to assure me that everything was okay. She must have had many other responsibilities that she needed to attend to, but she made the time to care for me.”

Starlight smiled, still looking up at the clouds.

The silence lingered on for several seconds before Dusty spoke up. “I really hate to be that guy and break up the mood, but if Star’s right about the robots, we need to keep an eye out.”

Starlight groaned. “Dusty…”

\leavevmode\llap{“}No, he’s right,” I said. “Duty first.” I gave her a smile. “We can always talk more later.”

She sighed, but relented. She stood and moved to the edge of the wagon, but I raised a hoof to stop her before she hopped off. “Starlight,” I said, keeping my voice low. “Thank you for what you did, but… I can live off what I’ve been able to get. You don’t need to hurt yourself just to help me.”

She hesitated, finally shrugging. “It’s nothing. I just wanted to help.”

I watched her fidget for a couple seconds before giving her a soft smile—which, in retrospect, was probably not quite as effective with my natural set of teeth. “Well, I do appreciate it, so… thank you.”

She wavered a moment before replying, “Hey, that’s what friends are for, right?”

My smile grew, and she flashed a smile my way before hopping down.

I sat back in the wagon, lifting my binoculars, and scanned the horizon.

{\br}%
“About twenty to twenty five structures in total. Looks like a lot of houses, a store, a rail depot with no rails, and a large power substation. Looks to be in very good condition, no scrap-building or other signs of modification.”

Dusty squinted through his own binoculars as he took in my report. “And the ponies?”

\leavevmode\llap{“}Still haven’t moved,” I said. The figures stood by the buildings a few miles away, too far for me to make out details even with my binoculars, especially with the dim morning light struggling to pierce the cloud-cover. “I count at least fifteen scattered around in loose gatherings, but they’re not doing anything.” I lowered my binoculars. “I think they’re fake.”

Starlight peered down her scope, her Lancer resting across the side of the wagon. “Could be military robots, just standing guard?”

\leavevmode\llap{“}Possible,” I said, and scanned across the town again. “I’m not aware of any pony-form robots, but that wouldn’t preclude some experimental line developed in secret.” I swept my view over, out of town. A ring of dirt tracks surrounded the strip of buildings, built on either side of a paved road. That road ended at the edge of the town. A single dirt road met it, stretching off into the distance alongside a set of power lines. Other than that one line, the tight cluster of buildings stood isolated, like an island in the middle of an ocean. I focused again on a lone sign at the edge of town, the letters just barely too small to read at that distance.

It had been about twenty four hours since we passed the fence on the edge of the Pale Sands Spell Range, and that tiny, lonely town was the first indication we had seen that ponies had ever been here.

\leavevmode\llap{“}Soooo…” Starlight glanced over to Dusty and me. “Should we check it out?”

\leavevmode\llap{“}Could be dangerous,” Dusty said. “We’ve already got a goal, I’d rather not take risky side-trips.”

\leavevmode\llap{“}Pussy,” Sickle growled.

\leavevmode\llap{“}Look at the size of that power station,” Starlight said. “I’ve seen factories with smaller stations. What does a little town like that need with so much power?” She paused, thinking. “Could be a Stable.”

\leavevmode\llap{“}Stables have their own power source,” I said, focusing on the substation. “Still, that \textit{is} a big substation. Could be something. I don’t think it’d hurt to look a bit closer, get a better idea of what the place is. Because the only thing I can tell from here is that it’s \textit{not} just a normal little village.”

Dusty thought a moment before shrugging. “If you don’t mind the delay, sure. There’s a small rise just to the right, probably half a mile out from town. We’ll glass it from there, see how it looks. Unless we see something juicy, I’d recommend steering clear. This has all sorts of wrong written all over it.”

Sickle grumbled something under her breath, no doubt complaining once again about our cautiousness, but continued on all the same.

We were about halfway to the rise when I could finally read the sign, despite the jostling of the wagon. I read it out loud. “Welcome to Ponytown. Population: 98.”

\leavevmode\llap{“}Just a random town of ninety eight out in the middle of the desert,” Starlight said.

\leavevmode\llap{“}With a rail station that has no rails,” I added.

I could see that the structures had once been garishly painted, much like the welcome sign, though the years had faded the colors badly. The pony-shaped figures gathered around outside them remained unmoving.

Between the buildings, I could see glimpses of multiple skywagons along the street, and even a few motorwagons. Their bright paint had held up better than that of the buildings.

It wasn’t long before we reached the small rise Dusty had indicated. I gave one final scan to confirm what I had seen before lowering my binoculars. “They’re not robots. They’re mannequins, and they’ve probably been there since the war.”

Starlight cast a glance my way before peering down her scope again. “Why would anypony build a town in the middle of the desert and stick a bunch of—”

\leavevmode\llap{“}It’s a test site,” I said, and she glanced at me again.

\leavevmode\llap{“}A test site? What would they test—”

She abruptly halted, blanching, and finally returned to her scope. “Well, that’s…”

We both looked over the array of figures we could see. The fancy, upscale, but faded houses had many pony figures visible. The nearest group, gathered in a back yard with a very out-of-place picket fence, looked like a large family, including a few colts and fillies. Almost all of the adults wore clothes of varying types, mostly reduced to tatters by the years of weather. The foals were posed as if playing, forever frozen in place.

\leavevmode\llap{“}...extremely creepy,” Starlight finished.

\leavevmode\llap{“}So, no secret military lab or valuable loot,” Dusty noted.

\leavevmode\llap{“}No secret military lab,” I agreed, but then continued on. “Possibly loot, though. I saw a film about their megaspell testing, something the Ministry of Image put together to reassure the public. They made the test villages as close to life as possible, stocked up with food and all. There should be everything you’d expect in a real town, and I don’t see any signs of looting.”

Starlight murmured quietly as she slowly panned her scope around the place. “Doesn’t look like anypony’s touched it since the war.”

I nodded, then raised a hoof to point. “But what’s really got my attention are those motorwagons. They look to be in good condition, and there are several to salvage parts from.”

Even Dusty’s ears perked up at that, and he spent some time gazing through his binoculars at them. “...Would certainly be convenient,” he finally said, then nodded. “Okay. Leave the wagon here, and we’ll check it out. Just keep an eye out. There’s got to be some reason this place hasn’t been hit for salvage, and I doubt that reason is rumors and the remote location.”

Sickle unhitched herself, following after Dusty. As for myself, I decided to err on the side of caution. I flashed over in green fire as I expended some of the love Starlight had shared with me to retake my Whisper Winds disguise, and quickly followed along with the others. While we had no idea what was waiting for us in that town, I didn’t want to take any chances of being discovered.

Besides, I find handling and aiming a weapon to be easier when it’s held in my teeth rather than floating freely beside me, and fangs get in the way of that. Not that I’m a great shot to begin with, but I could use every advantage I could get.

We made it to the edge of the little town without incident. Our path led us past the group of mannequins we had been eying before, gathered together as if enjoying a backyard picnic. Faded and decayed clothes rustled faintly in the breeze, while the fake ponies on display held eternal smiles, oblivious of the fate that had been intended for them.

Our destination was one of the motorwagons, painted in a cherry red that was only moderately faded and pitted with time. It was parked under an awning on a small strip of concrete beside the fake family’s house. Dusty moved by it, sweeping his weapon around to cover corners as he passed them, until he could scan around the street in front of the house.

Sickle followed behind him, but had slowed notably. Her head twitched this way and that as she looked around, and she growled quietly. “I don’t like it. Something ain’t right with this shit.”

Starlight moved up to the side window of the house and peered through, first over the sights of her Repeater, then leaning in for a closer look. A moment later, she gave a low whistle. “That is the most thoroughly stocked kitchen I’ve seen in my entire life.”

Through the window, I could see that the inside of the houses had endured much better than the outside. It looked like a cushy and lavishly stocked suburban home. The colors had remained more vivid in the shade of the interior, with their cheerfulness diminished only slightly by the thick coating of dust over everything. Beyond the kitchen, I could see a table with several mannequins sitting around it, posed as if sharing a family meal.

\leavevmode\llap{“}Check the motorwagon,” Dusty said, crouching at the front of the vehicle. “See if it runs, or if we can fix it up.”

\leavevmode\llap{“}On it,” Starlight said, holstering her Repeater again as she scrambled up into the driver’s position.

I had moved up near Dusty, until he told me to watch our rear. I followed his directions, moving to the rear of the motorwagon and watching the back sides of the neighboring buildings. Sickle remained near him, her tail flicking in agitation as she muttered. “Something’s seriously fucked here…”

\leavevmode\llap{“}Well, the motorwagon doesn’t start,” Starlight said. “Might be out of charge, or something might have come loose. Let me see.”

She climbed over the top of the vehicle to the motor, and as much as I wanted to watch her work, I kept my eyes out for danger.

It was just moments later that we heard the sound, low and distant.

I had previously described the sound of a minigun firing at us as the most terrifying sound I had ever heard, and while I would still consider that to be true, I would point out that there are different kinds of terror. That had been the visceral terror of overwhelming power and impending death tearing through the air around me.

This was different. This low sound was almost inaudible at first as it filtered across the distance to us, but it grew steadily, almost impossibly, in both pitch and volume. The banshee wail of the air raid siren echoed across the basin, a creeping terror that conjured up the worst nightmares of your own imagination. The hairs of my disguised form stood on end.

\leavevmode\llap{“}Well that isn’t good,” Dusty muttered, before speaking up. “Stay alert. Starlight, how—shit!”

My head snapped around to see Dusty rise and take a step back, bringing his rifle up; a pure-white earth pony had stepped out from the house across the street, staring at us.

I immediately realized that something was wrong with this pony. I paid a lot of attention to the fine details of appearance, and my eyes went straight toward the oddities. It wasn’t just her coat that was white. What flesh I could see was almost entirely devoid of color, with only the faintest suggestion of pink. Her eyes were pink. I recognized the signs of albinism, but the oddity didn’t stop there.

Her eyes were fully dilated, and even as she stared at us, they seemed unfocused. While her coat was perfect, her pale-pink mane and tail were thin and limp. She had come to a halt and wavered, as I’d expect of a pony abruptly coming face-to-face with a rifle-armed soldier, but I could see no sign of fear, or even comprehension.

Then those pink eyes narrowed. Her scraggly mane and tail flicked about as if caught in some unfelt breeze. Then she opened her mouth, and as she let out an unearthly shriek of rage, her mane and tail burst into flame, and she charged.

She only made it to the edge of the street when Dusty’s rifle hammered twice at my ears. At least one bullet, if not both, found their mark, and the pony tumbled to the ground. She squirmed about for a moment until a third bullet took off part of her head, and the flames flickered out.

\leavevmode\llap{“}What the \textit{fuck?!}” Sickle bellowed.

Past the echoing sound of Dusty’s gunshots, I could hear more shrieks.

Dusty shouted back to us. “Whisper! Get airborne, see what’s coming down on us! Star! Get—”

I missed the rest of what he said as I transformed. Rather than discard my disguise, I hastily added a pair of wings to my current form, threw back my cloak, and launched myself up into the air.

It’s amazing just how much your perception can change with a little bit of elevation. From just above the rooftop, I could see the whole settlement. Several more white ponies were emerging from various buildings, with the same flaming-albino look as the first. None carried arms or armor. I figured Sickle could likely take them all on herself.

My elevated point of view also changed my perception of the area around the town. That little bit of height was enough for all the scrub and subtle rolling of the terrain to fall beneath me, giving me a clear view of the basin in every direction. Without those in the way, I could see the distant white forms milling about, roughly a mile past the little town.

I raised my binoculars to quickly scope out the distant forms, in case they should pose some risk to us.

There were dozens of them, milling about in agitation around an open-girder tower, maybe a hundred feet tall. For a moment, I thought it might have been an antenna, only without any lines attached to it. Then I thought it might be a water tower with an unusually narrow tank.

Then I caught the faint, sickly colors that slowly twisted and churned within the upper confines of the tower.

My stomach dropped, a chill flooding through my veins.

I landed heavily atop the motorwagon, making Starlight jump in surprise. “Run!”

Dusty didn’t question me as he drew back. “Move, now! Go!”

\leavevmode\llap{“}Oh for fuck’s sake,” Sickle growled, throwing a pill bottle back into her saddlebag.

\leavevmode\llap{“}Damnit!” Starlight snapped as she hopped down, trotting toward the rear of the vehicle. “I can fix it!”

\leavevmode\llap{“}Go!” Dusty repeated, breaking into a trot.

\leavevmode\llap{“}Run!” I shouted as I galloped past them, only slowing to shout back. “The megaspell they were going to test, it’s still here!”

\leavevmode\llap{“}Oh, you’ve got to be fucking kidding me!” Sickle growled as she broke out into a full gallop; while her loping pace looked slow and heavy, her huge stride ate up the distance. The others cursed and followed her, fleeing the little town. I soon had to take flight to keep up, even with Starlight and Dusty pausing to turn and shoot at the ponies who gave chase.

Past the clanking and crashing of Sickle’s armor, the echoing air-raid siren slowly wound down to silence. We kept going.

I skimmed the ground, staying low and agonizingly slow as I kept pace with the others, despite how much I wanted to flee as fast as possible.

By the time we reached the wagon, the albino ponies had stopped chasing us. Sickle was slowing down, panting hard, and both Dusty and Starlight were looking winded.

Dusty called out. “Sickle! Grab the wagon!”

\leavevmode\llap{“}Fuck… the wagon!” Sickle shouted back, running right past it. Dusty swore and turned, galloping over to the wagon and quickly strapping himself in.

\leavevmode\llap{“}Whisper!” He called out, and I darted over to hover beside him. “How big of a blast do those things make? How far away do we need to get?”

He was already pulling the wagon along before I could answer, quickly reaching a rapid trot, and I flew along beside him. “Depends on the design of the megaspell. I only know vague generalizations, not firm—”

\leavevmode\llap{“}That’ll do!”

\leavevmode\llap{“}The rough estimates I heard for a city-killing balefire megaspell were one mile for near-total destruction and death, two miles for serious destruction and casualties, and four miles for minor damage and injury.”

\leavevmode\llap{“}Shit.” He urged himself onward, picking up the pace. I looped back and pushed against the back of the wagon to help; I had wingpower just going to waste, after all.

\leavevmode\llap{“}If you see a flash, hit the dirt and cover up!” I called out. “The megaspell was a mile past the town. This far out, we might avoid serious injury if we’re not directly exposed!”

We continued on, though our pace was rapidly flagging. We made it barely a mile from town before exhaustion started to really kick in from our rapid retreat. Sickle had started to trail behind Starlight, while Dusty and I took up the rear. Starlight paused at a dry streambed for us to catch up. Sickle simply collapsed inside the shallow ravine, and Dusty and I soon followed.

\leavevmode\llap{“}Catch your breath,” Dusty said, panting. “Sixty seconds, then we’re moving out at a trot.”

There were a few weak grumbles, but we all wanted to get as far away from the megaspell as possible.

Sickle dug out an inhaler, and practically tore off her muzzle before taking a hit. The effect was immediate, and while she was still panting hard, she went from slack and exhausted to tense and ready to go. Then the pill bottle came out again, and she downed a pair of tablets. By the time everyone else was getting up again, she had pulled out a second inhaler, took another draw, and threw it away. “Okay, let’s fucking do this already!”

Dusty went back to the wagon, but Sickle shoved him to the ground, snarling. “Give me that, you pussy ass bitch!” As Dusty picked himself up again, Sickle quickly threw on the harness and muscled the wagon across the streambed, nearly tipping it over in the process. Her helmet’s muzzle, still open, bounced and slapped against the side of her head.

I trotted alongside Dusty and Starlight, and Sickle broke out into a full-speed, loping gallop.

\leavevmode\llap{“}Slow down!” Dusty shouted out.

\leavevmode\llap{“}Fuck you!” Sickle shouted back. “Get your weak ass in the cart if you can’t fucking keep up!”

We broke into weary gallops as well in an attempt to catch up, but Sickle didn’t slow down for us to catch up. In annoyance, I took to the air again, looping my forelegs around Starlight’s chest—much to her surprise!—and ferrying her to the wagon. I returned to do the same for Dusty, depositing him beside Starlight, and then landed beside both of them. I figured if Sickle was going to be that way, she could carry me, too.

As it was, I had to clutch the side of the wagon to keep from bouncing out as Sickle galloped along much more quickly than the wagon or its occupants were happy with.

Starlight lay on her side in the bouncing wagon, panting. “Okay. Pegasus Whisper is handy.”

\leavevmode\llap{“}Flying has its advantages,” I agreed, while seriously considering taking to the air and flying along beside the wagon just to be spared the rough ride. “Feathers suck, though.”

She gave a weak chuckle, then groaned. “I fucking hate ferals. And what the heck was with them, anyway?”

\leavevmode\llap{“}Hell if I know,” Dusty replied, holding onto the edge of the wagon as he watched behind us. “They sure acted like ghouls, but I’ve never seen ones like those.”

\leavevmode\llap{“}Wait,” I said, spreading my wings for balance. “Ferals? Ghouls?”

Starlight propped herself up against a row of ammunition cases. “Yeah, you know—”

She stopped, and blinked. “...Right, you don’t know. Of course.” She looked over to Dusty. “Hell, I don’t even know where to start.”

Dusty took over for her. “Ghouls are ponies that died and came back to life because of magical radiation,” he said. “Some keep their minds. Ferals are the ones who didn’t. They’re more like animals than ponies, now.”

I stared at him in disbelief. “Died and…” It suddenly clicked. “Balefire is necromantic in origin. Huh. That always conjured up images of zombie ponies, but I never imagined that would actually happen.”

Dusty gave a weak snort of laughter. “Yeah, don’t call a ghoul that. Never seen one who liked that name.”

\leavevmode\llap{“}Really?” I asked, finding the peculiar pedantry even more bizarre than the idea of balefire-animated undead. “Of the two, \textit{ghoul} is the less offensive?”

\leavevmode\llap{“}Hey, I didn’t make the rules,” Dusty said. “Though, fair warning? Most ghouls look pretty badly decayed, like they rotted for a few days before coming back. Those ones back there were weird. I’ve heard of a few different kinds of ghouls, before, but never ones like that.”

\leavevmode\llap{“}Why the difference?”

Dusty shrugged. “Hell if I know.”

The wagon bounced clear of the ground, eliciting a yelp from Starlight. I caught air, beating my wings a couple times before landing atop it once more. Dusty turned and yelled. “Damnit, Sickle! Slow down! You’re going to break a wheel at this rate!”

Sickle’s only reply was the growling tone her panting took on.

Dusty muttered, turning around to look back. I continued to watch Sickle. The plates on her back shifted and clanked with every stride, like an old, rickety, yet powerful machine. We hit another bump, jostling us all around, and I ended up sprawling against Starlight, who spent the next few moments cursing at Sickle.

I sat up, clutching to the side of the wagon once more. “She’s got to slow down sooner or later.”

\leavevmode\llap{“}Sure,” Starlight said, shoving away a small heap of guns that had slid up against her. “I give her a couple more minutes before the drugs wear off, and she just passes out and eats dirt.”

I settled in again, as best I could with unsecured cargo randomly assaulting me. Eventually I looked back.

Dusty was looking behind us with the binoculars. His ears had perked up alertly, but then drooped down. He lowered his binoculars, continuing to stare off into space.

\leavevmode\llap{“}What’s wrong?” I asked.

He turned to me, his expression hardening in an instant. “You two are cursed, aren’t you?” He looked to Starlight. “Like, literally cursed. That’s what this is, isn’t it?”

Starlight frowned. “The heck are you talking about, Dusty?”

\leavevmode\llap{“}I’m talking about running into some weird new pyrotechnic ghouls, getting chased off by a megaspell of all things…” He pointed a hoof back toward the horizon. “And now your damn alicorn friend is back!”

Starlight sat bolt upright, despite the shaking of the wagon. I balanced with my wings as I raised my own binoculars, searching in the direction Dusty had pointed. The jostling made it difficult, but I soon caught a few shaky glimpses of a purple form banking slowly around. She was circling the town we had just left. Searching.

I lowered my binoculars. “Okay. Running into her at Paradise Beach could have been a coincidence. Showing up here, now? Yeah, that’s suspicious.”

\leavevmode\llap{“}Damn right it’s suspicious,” Dusty said. “What the hell did you two do?”

\leavevmode\llap{“}Hey!” Starlight shouted, bracing as the wagon lurched again. “We didn’t do anything!”

\leavevmode\llap{“}Then why the hell is it following us?”

\leavevmode\llap{“}I don’t know, Dusty! What do you—”

It was at that moment that Starlight’s earlier prediction came true.

I wasn’t looking in Sickle’s direction, so I didn’t see if she wavered, sagged, or gave any other sign of exhaustion before simply collapsing. My first knowledge of the event came when the wagon abruptly and violently upended, hurtling me into the air. I tumbled, only barely able to reorient myself with those clumsy pegasus wings in time to save myself from impacting the ground.

The rest of the wagon’s occupants hadn’t been so lucky. Sickle had collapsed, and her weight had born one of the leading poles of the wagon into the ground. Momentum had done the rest as it sent the cart tumbling, throwing its contents across the ground. Unfortunately, those contents were Dusty, Starlight, and several hundred pounds of unsecured equipment.

The crash was already over by the time I had gotten under control. A few boxes were still tumbling along the ground amidst a cloud of dust. Starlight and Dusty both groaned—until Starlight moved, and the groan turned into a sharp yell of pain.

I darted over, landing beside her as she rolled onto her back, cradling a foreleg against her chest. She grit her teeth against the pain, hissing and grunting.

\leavevmode\llap{“}Starlight?” I said, her eyes opening to a sliver at the sound of her name. “Are you okay?”

She grimaced, closing her eyes again for a moment, and winced once more as she moved her leg. She practically growled past her clenched teeth. “I think it’s broken.”

\leavevmode\llap{“}Are you sure?”

She hesitated, then lifted her leg a fraction of an inch. She immediately hissed in pain. “Yep!” She laid her leg down again, taking a couple deep breaths. “Hooo… yeah, pretty sure.”

Dusty had gotten up by then, and hobbled over on three legs. The fourth was held to his side. He grunted as he sat beside her, then held out a hoof near hers. “Let me see.”

Again, she hesitated, then slowly moved her other leg away. Though he was clearly in pain himself, he carefully touched along the length of Starlight’s leg, eliciting a hiss of pain each time. I stood back and watched, feeling useless.

\leavevmode\llap{“}Yeah,” Dusty said, sitting back and cradling his side again. “Seems like a pretty clean break. Hey, Whisper? See if you can find where the medical kit went, dig up a splint.”

Starlight cursed under her breath, frowning down at her leg.

By the time I had found where the medical supplies had ended up and found a splint within the disorganized mess within, Dusty had gotten Starlight’s saddlebags off and was digging out a healing potion.

I handed over the splint, then sat beside Starlight as Dusty carefully lifted Starlight’s leg. She grit her teeth, but bore the pain well, and moments later she relaxed again as he set the limb down across the splint’s bindings. I placed a hoof gently on her shoulder.

She winced again as Dusty tightened the bindings, lashing the splint onto her leg. As he did so, he spoke to me. “Whisper, what’s that alicorn doing?”

I twitched in alarm, and quickly turned around. I scanned along the horizon and the sky just above it, both by eye and with my binoculars.

\leavevmode\llap{“}I don’t see her.”

\leavevmode\llap{“}At least she isn’t coming this way,” Dusty muttered as he continued to work. Tightening the last strap, he had Starlight lift her leg. She did so, and without any fresh shocks of pain. Satisfied, Dusty passed over the healing potion. “Drink this. It should heal the bone up, but it might be weak for a while. Keep the splint on and stay off that leg for now until—”

\leavevmode\llap{“}I know, I know.” She downed the healing potion in one quick gulp, then set the bottle down again. “Don’t want to break it again while it’s weak and all that.” Then, almost apologetically, she added, “Thanks.”

Dusty nodded. A silence grew between us until, several seconds later, Dusty finally spoke again. “I suppose we should check on Sickle.”

Starlight answered with an unenthusiastic grunt as she stood up, balancing on three legs. I had offered a hoof to help her, but she was determined to do it on her own.

Sickle lay where she had fallen, still harnessed to the wagon. The limp sprawl would have looked like she had simply dropped dead, if not for her sides moving with her shallow, rapid breathing. Frothy spittle clung to her lips and chin, making her look more like a rabid beast. Her eyes were half-open, staring vacantly from behind the slits of her helm. One of the wagon poles lay beneath her, broken from the crash.

Dusty stared down at her for several seconds before looking up to us again. “And this, my little ponies, is why you don’t abuse combat drugs.”

One of Sickle’s legs shifted a few inches, and she emitted a quiet string of mostly incoherent sounds. The only word I caught was “Cunt”.

Starlight snorted and walked past her, muttering. “Dumb bitch.” Sickle replied with another incoherent mumble.

Sitting beside Sickle, Dusty placed a hoof atop her helmet. “You okay in there?”

More mumbles. A foreleg dragged its way across the ground to her head, but lacked the strength to do any more.

\leavevmode\llap{“}You’re lucky you didn’t give yourself a heart attack or a stroke or something,” Dusty said, reaching over to Sickle’s armored saddlebags. That finally provoked a bit more of a reaction from her as she twisted around, grabbing at his leg. He drew it back just in time, then scowled down at her. “Relax. I’m just getting a healing potion for you.”

\leavevmode\llap{“}‘M fine,” she mumbled, slowly relaxing again. Her twisting around left her sprawled on her back and even more tangled up.

\leavevmode\llap{“}You just ran until the drugs couldn’t keep you going,” Dusty said. “Last pony I saw do that blew his heart up.”

\leavevmode\llap{“}Fuck tha’,” she said between pants, laying her head back until the helm’s horn dug into the ground. “‘Spensive shit. ‘M fine.”

Dusty sighed, frowning down at her.

A short distance away, Starlight was starting to gather our scattered supplies. She might have been down a hoof, for the time being, but that didn’t affect her magic. I helped her, gathering up scattered ammo cases, bundles of tarps, and guns.

Dusty eventually fed Sickle one of his own healing potions to get around her protests. She remained lying there for several minutes as we gathered things up. He coaxed her to get up so he could get her unstrapped from the wagon, though she wavered drunkenly as she did so. Once freed, she staggered off for a few steps before sitting down heavily. Her head wavered from side to side, as if unable to properly focus. She soon gave up and flopped down on her side once more.

The wagon was salvageable. The back right wheel had broken off at the axle, and one of the two harness poles—I’m sure they have a name, I simply haven’t encountered it before—was broken in half. The other wheels were fine, and while Dusty said the pivot point for the front wheels was bent, it was still functional. He reasoned that, with the proper load balance and a bit of effort, the wagon should work. For now.

The sound of Sickle’s saddlebags opening drew our attention. Dusty immediately dropped what he was doing and trotted up to her. “Oh, no,” he said, a hoof reaching out to stop the pill bottle she just pulled out. “No more drugs. The last thing—”

Sickle came to life. Her other leg lashed out, catching Dusty around the neck, and carried him in an arc over her prone form and into the ground beyond. She was instantly on top of him, spittle flying from her lips as she roared. “Listen here, you little fucking shitstain!”

Starlight and I both shouted out objections as we rushed over to help, but Sickle ignored us. She jammed a hoof in Dusty’s face, leg-blades hovering over his eyes. “You don’t fucking tell me what I can and can’t do, bitch! You can, can \textit{ask}, and if I… uh…”

She wobbled, then went completely limp, collapsing face-first into the dirt and flopping onto her side.

Dusty groaned, half beneath her. “Damnit, Sickle,” he grumbled, shoving at her side to little effect.

We went to help roll her off of him. A moment later she moved, her head rolling to the side—then suddenly exploded into motion again, her legs kicking out defensively as she let out an incoherent, babbling yell. Just as quick as it came, she stopped, frozen in place and panting. Inside her helm, I could see the flickering reflection of her eyes blinking. “W-wha…?”

I had to admire Dusty’s patience and self control. “Sickle?” he asked, reaching up to place a hoof on the side of her helm.

She seemed to have trouble focusing on him, given the way her head continued to wobble and tilt even with his assistance. “...Dusty?”

He nodded. “Do you remember where you are?”

\leavevmode\llap{“}I was… in a maze…” She slowly looked around, expression slack. “...We’re in the desert.” Then she focused on him again. “Were we fucking?”

Dusty gave a snort. “No, we weren’t. Could you get off me?”

\leavevmode\llap{“}Yeah,” she said, rolling over to sprawl on her back once more. The lingering effects of her brief unconsciousness quickly faded, and when she lifted her head again, she didn’t wobble any. “I was about to kick your ass, wasn’t I?”

Dusty rose to his hooves, once again holding one leg against his side. “You just passed out because the accelerants you were using wore off, and your body couldn’t keep up with the strain. The healing potion will help with any muscle or circulatory damage it caused, but you should probably take it easy for a bit.”

She raised her forehooves to her face. I saw her bare her teeth for a moment, as if angry once more at being told what to do, but she soon relaxed. “Urgh. A nap \textit{is} sounding kinda good right now…”

\leavevmode\llap{“}Go ahead and grab a spot in the wagon,” Dusty said.

We helped her into the wagon, getting her situated in the front left to counter-balance for the missing wheel. She flopped down limply, her head resting across the edge of the wagon. The rest of the wagon’s contents were loaded around her, and Dusty took the time to get things tied down as best he could, despite giving a wince of pain every time he twisted.

Once everything was loaded, he walked over to the front of the cart, with the harness hanging from the single pole. “Well this is going to be a pain in the ass,” he said, reaching for it.

I stopped his hoof with my own. “Are you okay?”

\leavevmode\llap{“}I’m fine,” he said. When I gave him a flat glare, he rolled his eyes. “I landed on a box of rations. I might have cracked a rib, but I don’t think so. I’ll be fine.”

\leavevmode\llap{“}You should get a healing potion and some rest,” I said.

He shook his head. “I’m not using a healing potion for every little injury. I want to save them for emergency use.”

\leavevmode\llap{“}We’ve got plenty of caps to buy more potions when we find them, and we’ll still have plenty for emergencies. And, speaking of emergencies, we’ll need you in good shape if we run into any trouble.”

He eyed me a moment, chewing on the inside of his cheek, but finally nodded. “Yeah, you’re right. I’ll take a potion.”

He reached out for the harness again, but I stopped his hoof with my own.

\leavevmode\llap{“}And you’ll get some rest,” I insisted.

\leavevmode\llap{“}Wish I could,” he said. “But the cart’s half busted, and it’s going to be a right pain in the flank to haul it like it is. Sickle’s out, and no offense, but you and Star aren’t exactly the strongest ponies around.”

I smiled. “I can change that.”

He opened his mouth, then shut it again, blinking. “...Just how much can you do with that shapeshifting?”

\leavevmode\llap{“}As much as I have the magic for,” I said. “Get some rest. I can handle the wagon.”

I placed my belongings in the cart, and focused. I thought back to a particularly large stallion I had encountered, back in wartime Appleloosa, and imagined what he might have looked like in his prime. Huge, muscular, with a deep brown coat and a cute white stripe running down his muzzle. Then I called up my magic, pouring energy into the spell. The magical flames sprang into being and washed across me, consuming most of my reserve. It was a lot more magic than I would have liked to spend, but after Starlight’s gesture, I was feeling much more comfortable with my prospects.

The world stretched and warped in strange ways as I changed, and I blinked away the dazzling light to see the whole world had shrunk in perspective. I looked back to Starlight’s wide eyes, even with my own as she sat in the wagon.

She blinked. “Holy shit.”

I grinned, half-turning. The huge body felt only slightly cumbersome, but also immensely powerful and stable. “Shapeshifting has its advantages.” My voice rumbled, almost as deep as Sickle’s.

She blinked again, her head drawing back in alarm. “You’re a stallion!” she blurted, her eyes darting to my hindquarters—then jerking away, sputtering for a moment, and finally covering her face with a hoof.

Sickle broke out in uncontrolled laughter, while a blush rapidly spread across Starlight’s cheeks. She cast a flat glare at the laughing mare. “Oh, shut up.”

Sickle laughed herself into exhaustion, leaving her lying there, panting. I strapped myself into the lopsided harness while Dusty muttered to himself. “I’m surrounded by crazy mares. Wonderful.”

The uneven load and missing wheel made the going rough, but my assumed form made it fairly easy to deal with.

It was just a couple minutes later when Sickle hummed approvingly. “Nice view.”

I tucked my tail between my legs, while she chuckled. The wagon shook as she shifted her position. A few minutes later, she started to snore.

\leavevmode\llap{“}So,” Starlight said, once she was certain Sickle was sleeping deeply, “we’ve finally found something Sickle is scared of.”

\leavevmode\llap{“}Combat drugs make for extreme and erratic behavior,” Dusty said. “I wouldn’t read too much into it. Though let’s be fair; you can’t kick a balefire bomb.”

\leavevmode\llap{“}You can,” I said. “It just doesn’t tend to improve your situation.”

Dusty snickered. “Okay, you can’t kick a balefire \textit{explosion}.”

\leavevmode\llap{“}It still got her running so hard she passed out,” Starlight said. “Twice.”

\leavevmode\llap{“}Dash makes you do stupid stuff like that,” Dusty said. “I wasn’t kidding about the guy who blew up his heart.” I heard him shifting around to lie back, grunting faintly, and finally sighing. “Summer Breeze. Decent buck, if a bit lazy. He was in the militia, but wanted to be a Ranger. Problem was, he didn’t have the endurance. One of the tests for Rangers is a five-mile run in full gear. He couldn’t make it in time, and he didn’t have the patience to exercise to get there.

\leavevmode\llap{“}Instead of giving up or exercising more, he somehow got ahold of some Dash and tried again. Nopony knew, of course, but we found four empty inhalers on him. He chain-dosed on his run. The Dash told him he could keep going, so he went all-out. He probably felt unstoppable.

\leavevmode\llap{“}Problem was, Dash lies. You don’t know how much strain you’re putting on your body until something fails. He made three miles at a full gallop with fifty pounds of gear, then \textit{bam}—” he clopped his hooves together, “—he just drops. Unlike Sickle, he was done. Stone dead. Doc said the muscles in his heart gave out, but the Dash kept him running until his brain choked.” He huffed softly, laying his head down. “It’s some scary shit.”

Starlight whistled, low and quiet.

\leavevmode\llap{“}Yeah,” Dusty said. It was several seconds before he spoke again. “Rangers tend to carry a dose of combat drugs for emergency use. I had to use Dash once. It’s potent, and it can be amazingly useful at times, but I’ll be happy if I never have to use anything like it ever again.”

\leavevmode\llap{“}So,” Starlight said, slow and thoughtfully, “something you don’t like the idea of using, but are willing to use if it becomes necessary?”

Dusty snorted, bitterly. “Yeah, yeah. I get your point.”

\leavevmode\llap{“}Will you cunts shut up,” Sickle mumbled. “I’m trying to sleep.”

Starlight and Dusty both became very quiet as we continued on across the desert.

As for me, I kept casting glances back. We watched behind us the whole way out of Pale Sands, but we saw no more signs of that alicorn.