We passed the chain link fence that marked the southern edge of the Pale Sands territory exactly two days after passing its twin to the north. Other than Ponytown, the entire expanse between those two points had been barren, empty desert.

The low mountains at the edge of the badlands drew near.

For the most part, we had recovered from the “incident” near Ponytown. Starlight’s splint had been removed, and after a bit of ginger testing and a warning to go easy on it, she was walking normally once again. Healing potions are truly remarkable things. Both she and Dusty still felt a little sore from their injuries, but it was nothing significant. I just hoped Starlight was actually healed, rather than stubbornly refusing to acknowledge her injuries.

As for Sickle, she had taken up wagon duties once more, allowing me to retake my normal, less exhausting disguise. She was unhappy with it, though possibly not for the reason you would think.

\leavevmode\llap{“}Fucking wasted potential,” she grumbled as she pulled the cart. “I mean, come on. You give yourself a fuckstick like that and you don’t even use it? Dumb cunt.”

We did our best to ignore her.

By mid-day, we were approaching the settlement on Starlight’s map, a place nestled between Pale Sands and the Badlands, cheerfully named “World’s End”.

When we laid eyes on the place, I recognized it. Not the settlement, of course, as it hadn’t been there before the megaspells. The terrain, however, I recognized. World’s End was built between a pair of rock formations that jutted up higher than the rest of the rocky hills around them. It was a distinctive landmark, one that could be used by returning changelings to orient themselves on their way home.

We were close.

The cliffs between the two formations were now adorned with several structures, some of which were even suspended over open space, with rope bridges criss-crossing the gap. The only presence on the ground was a fortified structure, with what looked to be a large winch-lift hanging down from above. The lowest level of cliff-hanging structures had metal scrap strapped to them, and looked to give excellent firing positions over the lone access point. A few more structures were set around the tops of the rock formations, though it seemed most of the space up there had, somehow, been converted to crops. I found myself pondering how difficult irrigation must have been.

The distant tones of a bell rung out across the distance, almost as soon as we were in sight. We could see movement along the rope bridges as the inhabitants moved to take up defensive positions.

We continued on. Dusty gave a wave when we were were still a few hundred yards out. “It’s good to look friendly,” he quietly said. Starlight and I waved, as well.

As we drew near to the fortified lift-house I could see clearly that not all of the residents were ponies. I saw the hulking forms of a few buffalo among their numbers, and to my surprise, the stripes and exotic stylings of a pair of zebras. There was even a pony whose face looked like it had been skinned and left to rot for a week. I figured she had to be one of those ghouls Dusty had told me about. Either that, or one of the most unfortunate ponies of all time. Possibly both. Even from the distance, the sight provoked simultaneous feelings of sympathy and nausea.

We were only a hundred feet away when a heavily armored mare atop the lower fortification called out. “Hold up, there. We saw you coming in. You came through the Pale.”

It seemed more like an accusation than a question, but Dusty answered anyway. “We did.”

She glanced to her side, to a buffalo who had what could only be described as a cannon strapped to his side. He stepped forward and spoke, his deep words echoing clearly without raising his voice. “The pale ponies reign over that land. They are the harbingers of death itself. No one passes through their domain.” He gave a short pause, as if for drama. “How did you escape their influence?”

\leavevmode\llap{“}We ran,” Dusty said. “Very fast.”

The buffalo continued to stare at him for several seconds. I was starting to grow worried, when his shoulders suddenly shook, and he let out a deep laugh. “You must have run very fast indeed, pony, to outrun death itself.” He turned back to the mare, giving a nod.

She nodded back and turned to us. “Okay, what’s your business here.”

\leavevmode\llap{“}We’re traveling south,” Dusty replied. “Our wagon’s damaged from our trip through the Pale, so we were hoping to get some repairs. Maybe a safe bed for the night. That’s it.”

\leavevmode\llap{“}There ain’t anything to the south of here. What’s your interest there?”

Dusty cast a quick glance my way before answering. “It’s personal business I’d rather not shout out across the whole town, if that’s okay with you.”

She mulled that over for a moment before nodding. “Fair enough. Any trade in there?”

\leavevmode\llap{“}We’ve got some supplies we might be convinced to part with, if the caps are right.”

The mare considered us for a few seconds, tapping her hoof on the edge of the wall, and finally nodded once more. “Okay. Leave the wagon in the bunker, along with your weapons, and you can come up.” She turned and called out. “Open the gate!”

A minute later, we were riding the lift on the short journey up. We were just lifting up through a hole in the floor of the winch room when a set of massive claws reached out to grab the edge of the lift. Starlight yelled out in surprise and slammed into the opposite rail of the lift. I turned toward the threat, and my veins ran cold as I laid eyes on my first hellhound, mere feet from my face.

He loomed over us, towering over even Sickle. His claws were nearly as long as my foreleg, and sharp fangs protruded past his lips. A coat of dark fur covered his muscular body, thick and ragged.

\leavevmode\llap{“}Chickenshit,” Sickle muttered at Starlight, as the hellhound held the lift stable and opened the gate. Then Sickle turned to the hound. “What the fuck are you doing here, Spot?”

The hellhound frowned down at her. His voice rumbled deep enough that I could have sworn I \textit{felt} his words as much as heard them. “Ain’t my name, Peenk.”

She glared back at him for several long seconds, before finally breaking into a grin. “Shit, it’s been a long time. Didn’t think I’d find you out in the ass end of Equestria.”

My heart-rate slowly returned to normal as it became clear that the hulking, heavily clawed monstrosity wasn’t about to reduce us to bloody chunks. I only then noticed that there were a few other townsponies there, including the pair that had greeted us at the walls. Starlight still looked quite pale, backed up against the far side of the lift. Dusty just looked a little more wary than usual.

\leavevmode\llap{“}Yeah, been uh long time,” the hellhound said in a stilted, awkward accent, and flashed a grin full of vicious teeth. He reached out, flicking a claw against Sickle’s breastplate. “You must be doeen well. Didn’t theenk I’d see you in dis.” His head tilted. “You the new boss, huh?”

\leavevmode\llap{“}Nah,” Sickle said, shrugging. “I’m done with that shit.”

The hellhound nodded. “Good,” he said. “Change ees good.”

The mare who had addressed us before cut in. “If you’re done terrifying our guests,” she said with a teasing tone and a smile, which earned a chuckle from the hellhound. Then she looked to Dusty. “My name’s Granite. I’m the mayor of our nice little town. So who might you be?”

We introduced ourselves, and she nodded along as she listened.

\leavevmode\llap{“}Good, good. Now then, we’re not shouting across the whole town any more. What brings four well-armed ponies way down here?”

I had a moment of concerned reflection on how I had come to be a well-armed pony despite my best intentions. It was certainly an accurate description. I had been carrying two firearms, a pair of grenades, and more than two hundred rounds of ammunition, and that wasn’t counting the pipe rifle with another hundred rounds I had packed away, or the significant arsenal contained within our wagon. I quickly shook off the feeling of distress and refocused on the conversation.

Fortunately, it seems Dusty had used the short delay of our ride up to plan a response that didn’t involve looking for an ancient changeling hive. “We were looking for a pony, and heard he headed out into the Badlands.”

The townsponies exchanged wary glances. Granite frowned slightly before continuing. “So you’re bounty hunters, then?”

Dusty shook his head. “No. We’re not after him for money. We’re just trying to bring a bad pony to justice.”

She mulled it over for a few moments, her frown deepening. “I see. And who is this pony you’re looking for?”

\leavevmode\llap{“}His name is Banger. I’m afraid the name is all I have to go on. He sold out a bunch of ponies to be raped and murdered.”

\leavevmode\llap{“}Never heard of him,” Granite said, but finally nodded. “Ain’t our business what you do out there. Just \textit{keep} it out there. We won’t be having any of that in our town. Got it?”

\leavevmode\llap{“}Got it,” Dusty said.

\leavevmode\llap{“}Good.” She turned, gesturing a hoof to the stallion beside her. “Sundown can show you to the lower berths. Anypony that wants to trade will meet you there, and there are beds in the back if you’re spending the night. A hundred caps, and the place is yours for the day.” She fixed Dusty with a firm stare. “I’d suggest not staying too long. Once word gets out that you’re hunting somepony, you ain’t going to find many friendly faces.”

\leavevmode\llap{“}We’re just passing through,” Dusty said. “We’re not here for anypony in your town, just—”

\leavevmode\llap{“}Ain’t anypony going to care \textit{who} you’re after,” the mare shot back. “And we ain’t going to care about \textit{why} you’re after them. Just that you \textit{are} after them. Now, we’re going to be gracious hosts and let you rest for the night, but I expect you to be on your kindest behavior.” She looked around at us. “And I expect you to be gone in the morning. You got that?”

Dusty hesitated, but finally nodded. “Yes, ma’am.”

\leavevmode\llap{“}Good,” she said with a sharp nod. “And if you ever have to come around again for another pony, I suggest you steer clear of here. We don’t take kindly to that sort of thing.”

Dusty nodded again.

Sundown led us along a series of walkways and rope bridges, until we descended to a low-hanging structure a short distance away. Wide windows gave a good view over the crevice between the two giant pillars of rock, while inside were a few tables, a half dozen chairs, and a few simple cots.

On the way, Dusty also filled me in on hellhounds, and how the diamond dogs, ever on the bottom end of Equestrian society, had somehow won the magical-radiation-mutation lottery to become the most dangerous creatures in the Wasteland.

Once we had arrived at our lodgings, Sundown informed us that we were to remain in the lower town, between the ‘berth’ we were in and the lift down. The rest of the town was off-limits.

As soon as he had left, Dusty started grumbling. “So. Apparently tracking down an accessory to rape and murder is a \textit{bad} thing, now.”

\leavevmode\llap{“}Well, I thought it was a good story,” I said.

He flashed a wry smile, which died as quickly as it came. “And I can’t help but note that they stuck us in the lowest part of their town, with only a single, easily defended route back into the rest.”

I looked back. The stairs leading up from our current residence ended on an open platform, connected to the rest of the lower town by a long rope bridge. One of the defensive positions overlooked the entire length of it, and I couldn’t help but notice that it was occupied. The earth pony with a double-barrel shotgun was the most obvious, but it was the zebra that really caught my attention. She was almost entirely hidden under her cloak, but it didn’t hide the long, slender rifle she had braced on the frame of the window. While the earth pony was relaxed and laid back, though with the shotgun within easy reach, the zebra appeared completely focused, as if expecting trouble.

\leavevmode\llap{“}Well that’s comforting,” Starlight said. “And our guns are all down on the ground.”

\leavevmode\llap{“}You dumb fucks and your guns,” Sickle grumbled as she dug around in her armored bags. She eventually retrieved another pill bottle, popping it open and slapping a pill back between the bars of her muzzle.

Dusty scowled. “Seriously? After what happened yesterday?”

\leavevmode\llap{“}Fuck off,” Sickle snarled, turning to head back the way we came.

\leavevmode\llap{“}Hey, wait!” Dusty called out after her. “Where are you going?”

She halted, turning to look over her shoulder. “Me? I just spent half a day staring at the ass-end of a big beefy stallion and thinking of all the fun I could have with somepony I don’t have to worry about breaking in half. Except Whimper’s a fucking pussy. So I’m going to go find Spot again, pin that mutt to the first flat surface I can find, and fuck his dumb little brains out.”

\leavevmode\llap{“}You’re going to… with a \textit{hellhound?}” Starlight blurted, looking at Sickle in shock.

\leavevmode\llap{“}Fuck yeah, with a hellhound,” Sickle said. “Spot’s about the only one who’s ever matched me in wrestling, and he’s a lot better at fucking than most stallions.” She grinned. “‘Sides, hellhounds are a lot more interesting. Ponies, they’re all just smooth and boring, but hellhound cocks are—”

\leavevmode\llap{“}Oh, \textit{goddesses}, I don’t care!” Starlight replied, bringing both forehooves over her ears.

\leavevmode\llap{“}Then why the fuck did you ask?” Sickle said, her grin taking on an increasingly sadistic twist. “Or are you jealous?” She hiked her scraggly tail, leaving her bare and unarmored rear fully exposed. “Come on, then! Stick your face right up in there and put that mouth of yours to use for once!”

\leavevmode\llap{“}You’re revolting,” Starlight said, turning away, her eyes narrowed in an angry glare and color tinting her cheeks.

Sickle laughed. “Nah, I just know how to have some fucking fun instead of being a little bitch all the time.” Her tail lowered again. “And if you cunts are going to be so damn uptight, then I’ll just have to find someone that \textit{does} know how to relax.”

She climbed the stairs and left.

Dusty sighed. “I really hope she isn’t about to get us all into trouble.”

\leavevmode\llap{“}When does she \textit{not?}” Starlight asked with a grumble, tossing her saddlebags onto one of the cots. “Maybe we should just go. We’re obviously not welcome here.”

\leavevmode\llap{“}Tempting,” Dusty said. “But I’d still like to see if we can get our wagon fixed. The terrain ahead is a lot more rough. Even if the wagon holds up, it’s going to be a pain in the ass to haul with a broken wheel.”

Starlight flopped out on one of the cots, burying her face in an old straw pillow that muffled her voice. “Yeah, well, that’d be Sickle’s problem.”

\leavevmode\llap{“}Except I’m sure it’d make her even more irritable, and then she’d make it \textit{our} problem. ‘Sides, all our stuff is in the wagon.”

She sighed. “Yeah, fine.”

Dusty and I sat at one of the tables. Lacking anything better to do, I dug out one of the packages of ancient, pre-cooked food from my saddlebags. I was halfway through it when Sundown returned with a couple of the townsponies to discuss trade.

One was the ghoul I had spotted before, giving me a good look at her. Or at least, as good as I could get without being obvious in my attention. It was, to my surprise, less concerning up close. Yes, it gave me a clear view of the decay the poor pony had suffered, to the point that I could see bare skull in a couple places, but it also let me see that her condition appeared relatively stable. I had imagined the decay as active, festering rot, but it was actually fairly clean.

If not for the difference in appearance, I probably wouldn’t have even noted her. She participated in the negotiations with the same cautiously friendly attitude of her companions, showing no sign of burden over her condition.

In the end, Dusty managed to get lodging for the night and repairs to the wagons for the exorbitant price of two of our spare assault rifles and ten loaded magazines. We could afford it, though; after looting most of a mercenary company and seizing their supply wagon, it was a small portion of what we owned. We were, apparently, moderately wealthy by Wasteland standards.

We returned to our accommodations for the evening while the other ponies worked on our cart. Dusty took a chair and dragged it to the edge of the structure, and spent his time leaning against the window frame. It gave him the perfect vantage point to watch over our wagon.

I rested my forelegs on the windowsill beside him and looked down. A buffalo had shoved his shoulder under the edge of the wagon, lifting it up while a pony used a length of wood to brace it in place.

\leavevmode\llap{“}You’re worried,” I said, keeping my voice low.

\leavevmode\llap{“}You’re not?”

\leavevmode\llap{“}I’m always a little paranoid,” I said. “Comes with the profession.”

He gave a short huff, and the corner of his mouth twitched upwards. “I guess we’ve got that in common.”

\leavevmode\llap{“}I guess we do,” I agreed.

He slowly nodded, his voice quieting to a whisper. “So, I know the soldier’s take of the situation. What’s the spy’s take?”

\leavevmode\llap{“}Concerned,” I said. “There are few reasons to react that poorly to the story of bringing a pony to justice.”

\leavevmode\llap{“}Yeah,” Dusty said. “That’s what I was thinking. Shit. And here I thought it made a good story.”

\leavevmode\llap{“}No, it was good,” I said, giving him a smile. “The creative use of true events is one of the best ways to fabricate a cover story. Consistency is one of the most important factors when constructing a long-term falsehood, and it’s much easier to be consistent when you’re using real-world facts.”

He cast a sideways glance my way before looking back to our wagon. “Thanks, I guess. Still backfired.”

\leavevmode\llap{“}It’s a rare lie that doesn’t have the chance to backfire,” I said. “And since I’d really rather not advertise to everyone that we’re looking for a specific \textit{place} instead of a specific \textit{pony}, I’d have likely come up with a similar story, myself. They might draw the wrong conclusions about what’s out there, and I’d really rather not have a bunch of treasure hunting ponies digging around my hive. I appreciate the discretion.”

He gave another little huff, a shadow of a laugh. “Thanks.” Then he shook his head. “Not that it seems to have helped our situation.”

I nodded. “True. Fortunately, whatever their reasons to dislike us, the town as a group doesn’t seem intent on harming us. I’m concerned that individuals in the town might not share that thinking, however. I think we’ll be safe during the day, while their guards are watching us, but I’m not sure if—”

\leavevmode\llap{“}We’re not staying the night,” Dusty said. “I’d been thinking the same thing. We’ll head out as soon as they get that wagon fixed.” He looked back to me. “Get some rest. Just be ready to do your thing if somepony starts something.”

I hesitated, but nodded. I’m not sure what he expected “my thing” to be. I suppose I’d have to improvise.

The rest of the evening was uneventful, despite the constant low-level tension. It was a familiar feeling. From Dusty’s relaxed posture and perceptive eyes, it seemed one he was quite familiar with, as well.

The sun was getting low when Dusty stood up. “Looks like they finished. Let’s get going. Where’s Sickle?”

Sickle wasn’t in the small portion of the town that we were told to stay in, to absolutely nobody’s surprise. A few armed ponies, as well as the cannon-armed buffalo, met us when we made our way to the lift, and one of the ponies headed off to track her down. Several minutes later, Sickle and her hulking hellhound friend made their way down to us along the ramps and walkways.

Sickle wore a very satisfied smirk as she walked up. “Hey, bitches. The fuck’s up, now?”

\leavevmode\llap{“}We’re leaving,” Dusty said, and Sickle halted, scowling.

\leavevmode\llap{“}Seriously? We just fucking got here!”

\leavevmode\llap{“}The wagon’s fixed,” Dusty said. “We can get a few more hours in before it gets dark, so we’re heading out.”

Sickle groaned. “Wonderful. We finally get to a place we can relax and have fun, and you dumb cunts are trying to drag me off already. Could have spent the whole night fucking like mad, but no…”

The hellhound gave a quick wince, ears folding back, and he cast a quick glance at the couple of townsponies nearby. None of them seemed to notice. Their attention was focused on Sickle.

\leavevmode\llap{“}Isn’t like you have to come with us,” Starlight grumbled.

Sickle gave an angry snort, but then grinned. “Nah, I ain’t going to miss out on this shit.” Then she lifted a hoof to point at Dusty. “But you’re hauling the cart. I’m done for the day.”

\leavevmode\llap{“}Fine,” Dusty said.

The hellhound reached out, placing his huge claws across Sickle’s shoulders. “You shud stay, Peenk. This is uh good place.”

She looked back to him, pausing only a moment before letting out a snort. “If it’s a good place, you \textit{really} don’t want me here. ‘Sides, I’d get bored. Not enough fighting.” She chuckled a little, flashing a grin up at the hellhound. “Might have to swing by and visit every now and then. It’s been way too fucking long.”

The hellhound chuckled in reply, though his sideways glance toward the other ponies made it seem slightly awkward to me.

We loaded into the lift, and the hellhound unlatched it, letting us descend. Granite watched us from the nearest guard post. So did several other ponies, and I caught at least a couple disapproving glares.

We retrieved our gear, and Dusty strapped himself into the restored harness. While we strapped on pouches and guns, Sickle climbed up into the wagon, flopping back heavily with a satisfied grunt.

Soon the cart was rolling along, down the slight slope leading away from the town.

The sound of glass bottles clinking together rose from the wagon as Sickle rooted around in her bags, finally pulling out a couple bottles of antique beer. “Shit, it’s been a long time since I saw Spot,” she said, dropping all but one of the bottles beside her. “Met him when I was still with my old gang. He hit the same caravan we were setting up to jump.” She popped open the bottle and took a long swig. Then she snickered. “He popped out of the ground right under their brahmin. Fuck, you should have seen it. It was like the damn thing just exploded! Meat and guts everywhere!”

She laughed, while beside me, Starlight scowled and muttered. “Must have been love at first sight.”

\leavevmode\llap{“}Hah! Fuck no. That was our caravan, not his.‘Course, most of those pussies didn’t want anything to do with a hellhound, but I went down there and butted heads with him.” She tapped the lip of the bottle against the cheek of her helm, then traced down along her neck to her shoulder. “Can still kinda see the scar where he caught me, damn near took my head off. Heh, I remember him grinning all smug like until I planted a hoof right in his gut. Should have seen his dumb expression when he looked up and realized he just got pinned by a pony!”

\leavevmode\llap{“}You have such a charming way of making friends.”

Sickle shrugged and took another swig of her drink before continuing. “Eh, I almost wanted to kill him for clawing my face up, but I was so high I couldn’t even feel it. ‘Sides, it was fun. We kinda just wrestled and beat on each other until we were both exhausted. Then we kicked back and shared some beers.” She grinned over her bottle. “And then we fucked.”

\leavevmode\llap{“}Of course you did,” Starlight muttered. “Because the first thing you think when you see some monstrous creature tearing an animal to pieces is, ‘Hey, I wonder if I can have sex with it?’”

Sickle snickered. “Pretty sure you’d think it, too, if you ever gave it a chance.” She waved her bottle our way. “Should get your marefriend to turn into a hellhound and give you a good hard fucking. You’ll see.”

Starlight’s ears laid back as she grimaced, color rising in her cheeks. “I’ll pass, thanks.”

\leavevmode\llap{“}Come on,” Sickle teased. “I thought you liked the cock? And two-leggers just let it all hang out in the open. You can’t tell me you didn’t get a good eyeful of that sheath.” She took another draw from her bottle before tossing it out behind us. “I ain’t kidding, though, you should try it. I’ve fucked lots of things: buffalo, zebras, donkeys, even a pair of griffons this one time. And \textit{lots} of ponies. Hellhounds got them all beat, easy.”

Starlight shot her a glare. “Seriously, how do you not have, like, every disease ever?”

Sickle stared at her for a few seconds before shrugging. “Health potions?”

\leavevmode\llap{“}They don’t…” Starlight stopped herself, shook her head, and simply continued walking.

Sickle just chuckled quietly and laid back, relaxing. There were several seconds of silence before she muttered. “Fuck. Now I’m horny again.”

We ignored her, of course. We even continued to ignore her when she unstrapped one of her spiked hoof-boots. The side-walls of the wagon helped, concealing most of the contents of the wagon from us, but they did little to block sound. Sickle was, as with all things she did, extremely unsubtle.

Dusty continued on with equal measures of disgust and determination, with his ears laid back against the sound and his scowling gaze fixed straight ahead. Starlight and I drifted a little further from the cart. I did my best to not dwell on the situation.

None of us said anything about it, naturally.

We were almost a mile away from the town when I noticed Dusty’s head dip down to reach into the folds of his cloth barding, drawing out the pistol he had concealed there, and returning it to its holster.

{\br}%
If there’s one thing the Badlands have going for them, it’s the desolation.

I can’t imagine how much worse my reaction to the Equestrian Wasteland would have been if I hadn’t grown up in the Badlands. Admittedly, I had spent most of my time there in the hive, rather than on the barren and largely lifeless surface, and after that, I had lived in Equestria for several years. Still, it made the transition less jarring than if I had lived in the northern parts of Equestria, with their rolling, grassy fields and sprawling forests, all teeming with life.

That desolation was ideal for changelings seeking to remain hidden. With the surface devoid of food and water, and the ground split into a maze of canyons and hills, it was rare for anyone of any sense to wander out that way.

It also meant that the land was almost entirely unchanging. I had no need of Starlight’s PipBuck and its map to guide us. When we set out that morning, I knew exactly where we were. By mid-day, the pale slice of sky ahead of us had stretched over half the sky, as we passed under the ragged edge of the Enclave’s cloud cover. Looking ahead, it was as if I had stepped back in time. The bare sun beat down on bleached rocks, the air growing hotter and drier by the moment, just as I remembered it. The rugged canyons and valleys we followed led up between sheer cliffs, leaving plateaus and spires of rock decorating the land.

I know not many outside my hive would share the opinion, but I always found the Badlands to be beautiful.

We walked on, pebbles and dry earth crunching under our hooves and the wagon’s wheels. I even sprouted wings, taking to the air to get the same perspective I would have had on my return trips to the hive.

Everything was exactly as I remembered it. Even in the few places where the centuries had worn down a slope or rocky formation, they were still immediately recognizable.

The heat was certainly unchanged. Starlight and Dusty’s almost awed attention to the sun was quickly stifled. Without the protective layer of the clouds, it beat down on us, unrelenting. Sickle had it the hardest. Between muscling the heavy wagon over the broken and hilly terrain, the ever increasing altitude, and the heavy armor she wore, it wasn’t long before she was panting in exhaustion.

I’m not sure how long she would have stubbornly pressed on if Dusty hadn’t called for a break. We sheltered beside one of the many rocky columns that stretched up from the ground, which had always looked to me as if someone had stacked rocks atop each other. It gave us a little shade.

Sickle unharnessed herself and tore her helmet off. It banged down against the rocks as she flopped down, moving only enough to retrieve the pair of bottles that she chugged, one after the other.

\leavevmode\llap{“}How far is it to your hive?” Dusty asked.

\leavevmode\llap{“}Probably about thirty miles,” I said. “Sorry, I think my estimate of our travel time was a little low. I always flew. I hadn’t expected how much slower it would be to walk, especially with a wagon in tow.”

Even Sickle’s abrasiveness was worn down by her exhaustion, though she still huffed out a retort between pants. “You’re welcome to haul it yourself if you think I’m too fucking slow.”

Ignoring her, Dusty asked me, “Is the terrain like this the whole way?”

\leavevmode\llap{“}Worse.”

\leavevmode\llap{“}Then I’m thinking we leave the wagon here. It’ll be a lot easier to carry a few days of food and water than it will to drag that thing with us.”

\leavevmode\llap{“}Sounds good to me,” Sickle mumbled as she pulled out another bottle.

\leavevmode\llap{“}And drink some water,” Dusty said, looking to her. “Alcohol isn’t going to help.”

\leavevmode\llap{“}Alcohol always helps,” Sickle grumbled as she popped open the bottle. “Stop being such a cunt.”

Dusty frowned at her, silent for several seconds before replying. “You know, I might find that more insulting if you didn’t throw it around every other word.”

\leavevmode\llap{“}Like I give two shits what you think,” Sickle said before tipping back the bottle and chugging it all in one go. When it ran dry, she threw it back the way we came. The sunlight twinkled off the final drops streaming from the bottle as it spun through the air, remarkably vivid and strangely beautiful after the dullness below the constant cloud-cover.

An hour later, we had each packed five days’ worth of food and water in our saddlebags. As we prepared to set out, I laid out the course for the rest of the day. “There’s an outpost along the way to the hive,” I said. “A way station and hideout for returning Infiltrators, among other things. It’ll be a good place to stop for the night.”

The moon and stars were shining overhead by the time we reached the familiar rocky formation, and the narrow gap in the rocks below it. I paused before the opening to tug at my magic, unwinding my disguise. This was a changeling place; it felt appropriate to return in my natural form.

I stepped into the passage, pushing just enough magic into my horn to cast a faint light. The rocky ground was covered in dry earth and grit, entirely undisturbed. We crept forward in the dimly lit space, following the tunnel almost fifty feet before it ended in a metal door. It was unlocked. I pushed it open, and stepped into the small bunker beyond.

It wasn’t an impressive space, but it was immediately familiar. Many times I had stopped in this place. It was a single room, with a small alcove at one end. The main part of the room held boxes that had once held supplies for passing changelings, a large table that doubled as both a dining surface and a map table, and a tiny kitchen. The alcove at its end held two sets of bunks set into the smooth rock walls, stacked three high, and at the back was a toilet and shower.

Without a thought, I reached out with my magic. The switch beside the door clicked loudly in the silent space, and to my surprise and relief, the lights flickered and struggled to life. I let out a shuddering sigh. A soft rattle sounded from the tiny vent at the back of the room, the stale air stirring as it mixed with the fresh air being drawn in.

While the outpost was coated with dust, it was intact. I simply stood there, marveling at it. That small part of my hive had survived. This one place that I had been so familiar with was still there, unchanged. With a little bit of sweeping, it would have been indistinguishable from my last visit, two hundred years ago.

Dusty eventually stepped up beside me. “Should we look around?”

I pulled myself away from my nostalgic thoughts and nodded. “Of course.”

As he checked over the stack of boxes, Starlight followed me to the table at the center of the room. There was a substantial amount of papers spread across it, with a box of neatly arranged writing implements set to the side. Some were maps, others were printed reports. My attention was immediately drawn to the small stack of papers near the center of the table. I gently slid them over with my magic, brushing away the dust.

The top paper was a printout of a simple grid of letters. I gave a soft huff of amusement, which caught Starlight’s attention.

\leavevmode\llap{“}What’s that?”

\leavevmode\llap{“}A vigeneigh cipher table,” I said, sliding the paper over to her. “One of the low-security methods used for—”

The page below was covered in writing that formed the familiar jumble of nonsense of a ciphertext. “...encoded messages.” I drew the paper over, scanning over the words.

\leavevmode\llap{“}Like a code?” Starlight asked, peering at the new paper as well. “What’s it say?”

I gave a soft chuckle and smiled. “I may be good with cryptography, but not that good. I’ll have to take some time to decode it.”

\leavevmode\llap{“}Oh,” Starlight said, her ears drawing back as if she had just said something very stupid. That lasted only about a second before perking forward again. “So how long will that take?”

\leavevmode\llap{“}When it comes to cryptography, I’m afraid the key is patience. Complex ciphers can take a lot of work to decrypt.” I picked up the cipher table before her, setting it down with the encoded message. “But if it was left here, it was probably meant for any changeling from our hive to read. We’ll see.”

The next paper had only eight words written on it.

Siphon. Bulwark. Scatter. Umbra. Shale. Flitter. Cinder. Desire.

My throat had already tightened as I started to read, but as I reached the last one, it felt like a weight had dropped in my gut.

Starlight stepped in close beside me, her voice soft and concerned. “What is it?”

\leavevmode\llap{“}They’re names.” I swallowed around the lump in my throat. “My sisters.”

Starlight’s ears drooped in sympathy.

Somewhere behind us, Sickle rumbled quietly.

\leavevmode\llap{“}Desire was an Infiltrator, too,” I finally said. “We trained together. We were close.”

A thin, neat line crossed through her name, as well as Scatter’s and Umbra’s.

Starlight reached over my shoulder, giving me a comforting squeeze. I leaned into it for a moment before drawing in a deep breath and refocusing.

I returned to the stack of papers, but there was nothing more to find. All that remained were supply requests and the final reports destined for analysts in the hive, left undelivered for two centuries. I even recognized one of my own reports on strategic supplies shipped through Appleloosa in the week before the end, as well as records of what smuggling activity I had been able to track. I felt an unreasonable urge to take that report, to scour it for anything I might have missed, as if I might have somehow prevented what had happened.

I set it aside with the rest of the reports, to be ignored.

Dusty had finished searching through the supply boxes. Every single one had been emptied long ago and neatly stacked back in place.

As we sat and ate a late dinner, I started working to decrypt the message left so many years ago.

My suspicions turned out to be correct. The message used a simple cipher, one that would never be used for high-security traffic, but which served the purpose of quickly protecting a message from casual observation. Even without the key, I could have likely broken it in a few hours at most. But it really was intended for any changeling in our hive to read, and as such, it used a common and well-known key. It took only a couple minutes to transcribe the entire message to plaintext.

I sat back, reading the message as I held it, floating, before me. Then I read it again.

I was starting on a third read-through when Starlight finally spoke up. “What’s it say?”

I had to force myself to speak. “The changelings who came here all received substantial amounts of magical radiation,” I said. “The ones who survived headed north into Equestria.” I folded the paper, which crackled dryly. “They were looking for C.L.T. facilities.”

\leavevmode\llap{“}What, any of them?” Starlight asked.

I tucked the folded paper into my saddlebags. “It seems that way. Maybe not all, but… it does appear to have been a widespread project.”

A hint of concern touched Starlight’s expression, as if sensing something was wrong. “That’s… good, right?”

I huffed out a short breath, and nodded. I even managed a weak smile. “Yes. It means there may still be some of my sisters out there, waiting.”

I settled in with my own as-yet untouched food.

Starlight finished eating well before I did. She sat awkwardly for almost a minute before speaking up again. “You keep using the word ‘sister’ a lot. How many sisters did you have?”

I shrugged weakly and spoke around a soggy bite of limp, canned hay. “Almost the whole hive.” When her eyes widened in surprise, I added, “The queen laid all our eggs. It’s just how changelings are. Even the few that weren’t laid by her were treated as sisters.”

Dusty had a questioning look, but remained silent. I suspect Starlight’s next question was the same on on his mind. “No brothers?”

\leavevmode\llap{“}No,” I said. “We don’t really have any use for males.”

Dusty’s expression had turned skeptical, but he only managed a cautious “Um...” before I continued.

\leavevmode\llap{“}That isn’t an expression of bigotry,” I said. “It’s biology. Ponies have only small differences between the sexes, but male changelings are very limited compared to females. Different biological castes. The only reason male changelings are even a thing is to ensure the queen can be fertilized.” I shrugged. “But seeing as female changelings can shapeshift to change sex, there isn’t any reason for a healthy hive to produce males.”

That just seemed to make Dusty even more uneasy. “So… what do you do with male, um… hatchlings?”

\leavevmode\llap{“}Nymphs,” I corrected. “And we just don’t have any. Fertilized eggs are always female.”

Sickle cut in with a chuckle. “Oh, sure, and you all get bitchy whenever I start talking about sex.”

\leavevmode\llap{“}I’m not talking about sex,” I said, casting a flat glare her way. “I’m talking about reproduction. Of all the ponies in the room, I would think \textit{you} would be particularly clear on the distinction between the two.”

\leavevmode\llap{“}Oh, ouch,” Sickle said, chuckling some more. “Whimper grew a bit of spine under that shell.” Then she stopped and blinked. “Wait, do bugs even have spines?”

I looked away from her, returning to the previous conversation. “Anyway, yes, pretty much any changeling in the hive could be considered my sister, even if it isn’t quite biologically true. It’s not quite like a pony family, but…” I trailed off, remaining silent for several seconds. They all waited patiently, until I spoke again. “But I guess it kind of is. At least, it was in my hive. We’d do anything for our sisters, even if we’d never met before.”

There were a few silent nods, and after a short moment of contemplation, I returned to my food.

We were about ready to settle in for the night when Starlight looked to the back of the alcove. “Do you think those showers work?”

I shrugged. “The outpost still has power, so maybe.” A thought struck me, and I frowned. “But the catchment hasn’t been cleaned or maintained in two hundred years. I doubt it’s safe to drink.”

\leavevmode\llap{“}As long as it’s not radioactive, that should be just fine,” Starlight said as she walked over. “I don’t need a drink. I just want to feel clean for a change.”

She stood to the side, reaching out with her magic to turn the faucet handle. A deep, rattling groan sounded from somewhere below, and she quickly turned the handle back. “Well, that’s—”

\leavevmode\llap{“}That’s normal,” I said, smiling at the knowledge that the outpost was largely functional. “This place wouldn’t get used for weeks at a time, and the water always drained from the pipes. You have to let it run for a bit.”

She nodded and turned the handle again. Again, the rattling groan started up, growing louder. Starlight jumped back when the first explosive sputter of water burst from the shower head, followed a second later by another, and rapidly grew into a steady spray marred by only the occasional hiccuping sputter. The water was murky and brown with the first few sprays, but was already lightening by the time the flow had stabilized.

As it ran clear, Starlight grinned, murmuring a quiet thanks to Luna and stripping off her belongings. She dove into the water, and let out a sharp gasp. “Damn that’s cold!” Despite that, she closed her eyes and plunged her head under the flowing water, grinning happily.

She opened her eyes to see an unusual luxury floating before her in my magic: one of the bottles of soap I had salvaged from Paradise Beach. She laughed and snatched it, and soon was lathering up. She arched her back and turned this way and that, practically dancing under the steady stream of water, her hooves splashing in the water that swirled around the floor drain.

The rest of us sat back, unable to help smiling at the simple pleasure and enthusiasm of something that had once been so mundane.

Starlight was halfway between panting and shivering when she finished, but grinned as wide as I had ever seen as she walked away from the shower, dripping wet and clean. As she fetched a towel to dry off, I took my own turn at the shower.

The water was icy cold, but it still felt amazingly good as it flowed over my carapace. I fetched an old, faded washcloth set beside the shower and scrubbed all over, removing the weeks of grime and oil and gunk that had remained even after multiple transformations. It felt liberating.

And I have to admit to a moment of narcissism as I admired the glossy luster of my shell, shining as the water flowed over me.

I was interrupted by a grind of metal on concrete, and looked back in alarm. Sickle was partly wedged into one of the lower bunks, her armor scraping and screeching against the top edge of the nook as she tried to force herself into a space that was far too small for her. “Oh, this is brahminshit!” she finally growled as she gave up, and then spent a couple seconds wrenching on the cot mounted within before it tore away with a crack of sheared-off bolts. She threw the frame to the ground and flopped down atop it.

I was tempted to object, but I let it go.

When I finally finished with my showering, I was met by Dusty, who smiled and inclined his head to the bottle of soap. “Mind if I use a little of that?”

I smiled back, floating it over. “Not at all.”

As he started to shower, I quickly toweled off. I shook out my wings, casting off the final drops of water, and lifted into the air. I floated up to hook my forelegs over the edge of the top bunk, hovering beside it; Starlight was already lying there, grooming her coat with an old brush.

I met her smile with my own, and spoke. “Hey, do you mind if I take this one?”

Her smile turned to curiosity. “Sure. Why?”

I suddenly felt very silly, my ears folding back. “Oh, uh… it’s just that every time I came here, I always slept in this bunk…”

She stared back blankly for a couple seconds, as my concern grew. Then a smirk crept across her face. Her shoulders shook in barely constrained laughter as she lifted a hoof to point at me. “Holy crap, that’s not fair. No! Creepy bug monsters shouldn’t look that cute and pitiable!”

I blinked in surprised and, I’ll admit, confusion. After a few moments of laughter, she finally controlled herself enough to speak again. “Yeah, you can have it,” she said between laughs.

She scooted to the side and slid out, a hoof holding onto the edge to neatly swing herself into the bunk below. I blinked again, and finally gave a chuckle of my own as I processed what had just happened. I floated up and dropped myself onto the cot, rolling over to my side.

Starlight’s hoof was still holding onto the edge of the alcove. Her laughter had stopped. A couple seconds later another hoof joined the first, and her head peeked up over the edge. “Hey, Whisper…”

\leavevmode\llap{“}It’s okay,” I said, giving her a smile. “Even if I’m most certainly not ‘cute’.”

She chuckled, flashing a smile. The expression quickly faded away again. “That’s good, but… I mean, are you okay? With…” she glanced around, her eyes lingering on the table and its stack of papers before returning to me. “...all this?”

My smile withered away. After a moment, I nodded. “I’ll be fine.”

She hesitated, as if deciding what to make of my reply. Finally, she hauled herself up to sit beside me. Her eyes were full of worry. “You want to talk about it?” she asked, her voice gentle and full of caring.

I remained silent for several seconds, but slowly relaxed. “If you want,” I said, a faint smile returning. “I’m sure this whole expedition of ours is going to be an emotional rollercoaster for me, but… we’re doing something good. I think I’ll be just fine.”

She stared back into my eyes for several seconds before her concern slowly melted away, and she leaned comfortingly into my side, mirroring my own soft smile. We sat there, quiet and relaxed.

Eventually, she spoke again. “I never had much of a family. Never knew my dad, no brothers or sisters. It was just my mom and me.” She heaved out a sigh before continuing. “What were they like? The ones you were close to, like Desire.”

My throat threatened to tighten again. “Desire was… energetic. Active. Enthusiastic.” I found myself smiling again, just a little. “And very social and friendly. She liked people.”

Starlight gave a soft chuckle. “Sounds a little like me.”

\leavevmode\llap{“}A little,” I said, nodding. “But she was a lot more… flirtatious.” I gave a chuckle of my own. “Which she cultivated into a fine skill set as an Infiltrator. She enjoyed her work, and I’m sure she left a long line of mares and stallions longing after her alter-egos.”

I told her about more of my sisters, but mostly about the rest of our small group, Infiltrators who had bonded during our time in training. There was Shadow, gentle and kind, and so quiet that you might mistake her for being shy, but always so clever, especially when it came to avoiding attention. There was Dagger, always bold and playful, yet probably the most aggressively calculating of us. And then there was Ripple, amazingly brilliant in many fields, but particularly in understanding how others thought; a natural manipulator.

The stories didn’t last long; we were both quite tired and relaxed by then. I was still smiling as I drifted off to sleep, with the warmth of Starlight’s body, and her friendly affection, right beside me on the slightly-too-small cot.

{\br}%
We set out shortly after sunrise the next morning. I felt remarkably refreshed. I was clean, well-rested, and comfortably fed. Despite all that, I was troubled. The happy memories recalled the previous night made way for worry and doubt.

\leavevmode\llap{“}I don’t know what we’ll find at the hive,” I said as we buckled on saddlebags and slung our weapons. “I don’t even know if… if there will \textit{be} a hive left. The message mentioned magical radiation, and I know at least one balefire bomb was detonated in the Badlands. I saw the flash.”

That news had a chilling effect on Starlight and Dusty; if Sickle felt anything at the news, her reaction was hidden under her helm.

\leavevmode\llap{“}Why?” Dusty asked. “Balefire was zebras, right? Why would they bomb a wasteland?”

\leavevmode\llap{“}To kill the changelings who were helping Equestria, perhaps,” I said, darkly. “Or perhaps one queen wanted to remove a rival, and was able to acquire a megaspell through some scheme.”

\leavevmode\llap{“}Well there’s a terrifying thought,” Starlight said. “Stealing a megaspell.”

I shrugged. “Why not? My hive did.”

She gawked at me.

\leavevmode\llap{“}Or so the rumors went,” I said. “It’s quite likely we had something to do with Equestria getting information on zebra megaspells. We might have even been the reason they had balefire bombs to test. I don’t know for sure. Not my field.”

We traveled throughout the morning and early afternoon, winding our way through narrow canyons as we drew closer. With every step, the tension in my gut grew, as if chewing at my insides. Our progress was agonizingly slow in the rough terrain as our path twisted this way and that, and we were forced to climb over obstacles or navigate steep slopes. Several times, my wings buzzed anxiously, ready to draw me up into the sky, to cover the last miles in an aerial sprint, but my hooves felt as heavy as lead. The whole time we traveled, I remained silent, save for the most basic of directions.

A terrible sense of dread dug at the back of my mind as we ascended toward one more ridge. Part of me wanted to turn back and never return, but I couldn’t stop.

We climbed higher, and the shattered spires of rock that had stood on the barren slopes above my hive came into view. Many had fallen, and unfamiliar cracks ran through some of the cliffs, but the land above the hive, though battered, remained. Off to one side, the familiarity of the terrain abruptly ended. Just a mile from my hive, the rocky ridges had been torn away, ancient canyons opening abruptly into a deep crater that had been carved into the rugged terrain. Even in the daylight, wisps of green were faintly visible, flickering and rippling in the depths of the crater even after all these years.

The balefire bomb had detonated frighteningly close to my hive, but it had missed its mark. A mile away, and nestled deep below the rocky surface, my hive waited.

We pressed on with a renewed pace. The path to the main entrance was so broken, twisting, and narrow that it was easily overlooked, and wound through difficult terrain, intended to make any ground assault near impossible. A sheer wall of rock lined one side, while the opposite was a straight drop to the canyon floor, hundreds of feet below. Fallen rocks and crumbling cliff faces made the path even more difficult, forcing my companions to climb over or squeeze around several obstacles. Many sections were passed with me hovering anxiously beside the narrow path, offering a little more support for the rougher sections.

Starlight jerked when her PipBuck clicked, quickly snatching it up. A couple more clicks followed a few seconds later.

\leavevmode\llap{“}What’s that?” Dusty asked, ears perking up alertly.

\leavevmode\llap{“}Radiation,” she said, and let the PipBuck hang on its strap again. It let out another lonely click.

Dusty frowned, his expression tense. “How bad?”

\leavevmode\llap{“}We’re fine,” she said, giving a playful smirk. “Unless you plan on camping out here for the next few months.

Finally, we reached a large split in the cliff face, looking like any of the hundreds of other gaps and crevices filling the landscape. The crack was wide with a relatively flat bottom as it led back into the cliff face. Unlike the other crevices, which ended after just tens of feet, this one snaked its way back, eventually turning into a tunnel that pierced deep into the stone. The brilliant sunlight quickly faded behind us, leaving us once again navigating by the light of Starlight’s PipBuck. The air was chilly, a sharp contrast from the Badlands outside.

The tunnel turned sharply to the side, then doubled back, before abruptly opening into a smooth-walled chamber. The ground simply ended, falling away in a pit that extended far beyond the weak light of the PipBuck, and about thirty feet across. Narrow metal-grate stairs were bolted to the walls, descending into the darkness in a steep spiral. The small lights that ran along them, normally casting off barely enough light to navigate by, lay dark.

We made our way down, the sound of hooves on metal echoing in the stillness. The powerful clanging of Sickle’s spiked shoes drowned out the groaning of metal caused by her passage, and the occasional click of Starlight’s PipBuck.

\leavevmode\llap{“}How deep is this?” Starlight asked, a couple of minutes later.

\leavevmode\llap{“}Four hundred feet,” I replied. “We should be most of the way there.”

Finally, we reached the bottom of the shaft. A single, wide tunnel led out, and as we stepped into it, Starlight’s light illuminated the giant steel-cog door.

\leavevmode\llap{“}Huh,” Dusty said, a much more subdued reaction than Starlight’s.

\leavevmode\llap{“}Holy shit,” she said. “That looks like a Stable door.”

\leavevmode\llap{“}It should,” I said, smiling for the first time that day. “It was stolen from Stable-Tec themselves, with the theft disguised as war profiteering from a corrupt official. I wish I could claim credit for it. I did manage to re-route an entire shipment of concrete and rebar, and pin it on a smuggler who had just died in a firefight with the authorities.”

I stepped up to the blast door, reaching out to touch the metal surface. It was covered in a thick layer of dust. “We already lived underground. It wouldn’t take much to turn the hive into a fully functional Stable.” My hoof slid down, leaving a streak in the dust before settling on the ground again. “We were less than a year from completing the project.”

I turned away, moving to the access panel beside the door. I lifted the protective cover. Thankfully, the “ready” light lit up. Beside it, another blinked red, indicating that the door was operating on backup power only. I started pressing keys, typing in a long sequence of numbers. My hoof moved to the large red button at the side, hovered over it for a long moment, and with a deep, steadying breath, I pressed it.

An electric buzz hummed out from the wall, stretching on for several seconds. My stomach did a flip at the loud, mechanical \textit{thump} that emanated from the door, and then, with a shriek of metal scraping against concrete that filled the cavern with a wall of sound, the great door ground its way open.

I glanced over to my companions. Sickle had bared her teeth, and pawed at the ground, the sound lost behind the scrape of the door. Starlight glanced my way, giving a cautious but reassuring smile.

Beyond the door, everything was dark. As it rolled open, the PipBuck’s light spilled across the entryway of the hive, with several overturned trolleys and crates lying scattered about. I caught quick glimpses of the security station, the door machinery, all the regular sights of the entryway. My attention, however, was immediately drawn to the hall beyond where, just at the edge of the light, movement drew my eye, and I froze. Stepping out from around the corner was the one thing I hadn’t dared to hope for: a changeling.

She stopped, head turned to stare at us, one pale eye reflecting the green light. To my sinking horror, I realized the other eye was nothing but a vacant pit. The changeling’s jaw hung askew, the entire plate of her cheek shattered and caved in. Her wings lifted, revealing the tattered ribbons that remained. Her carapace was dull and pitted.

The blast door thumped loudly as it came to rest, followed immediately by the walking husk’s clicking, rattling cry—and the dozens, \textit{hundreds} of cries that answered it.

There was a shout. A hoof shoved against my chest. I stumbled and staggered back. My hind legs gave out, and I fell to my haunches.

Then the sound of gunfire tore through the air, echoing through the halls of my dead hive.