I am almost tempted to play up the symbolism of our departure from the hive. Almost, but not quite. I tend to scoff when others see symbolism in random events. Silently, of course; it seems unnecessarily rude to call others out on it, even if I know better than to believe it myself.

Still, I couldn’t help but appreciate the surreal beauty as we stepped out of the darkened crevice that led into the hive, and out into the brilliant evening sunlight illuminating the badlands. The shock of heat was welcome after the chill down below.

I think we needed that change of scenery. We had been weary enough before, but after the four hundred foot climb to exit the hive under the heavy load of equipment we had salvaged from the armory, we were outright exhausted. Leaving the hive behind for the light and warmth of the outside world may have been just enough to keep us going, working our way along the precarious cliff-side path until we reached flat ground.

Our renewed energy was spent by then, and we collapsed beside a crumbling rocky pillar. There were groans and sighs of relief as we sprawled out on the warm rocks. As for myself, I simply flopped down on my belly, eyes closed.

Starlight groaned somewhere off to my side. “Ugh. My head feels like Sickle stepped on it, and my legs feel like I ran all the way here from Rust. How long is this going to last?”

It took me a second before I realized she had been speaking to me, and another couple of seconds for me to gather the energy to reply. “Don’t know. Normally I’d say a few hours, or a day at worst, but I don’t even know why it’s this bad. I didn’t use that much magic.”

\leavevmode\llap{“}That was a lot of fire,” Starlight pointed out.

I would have shaken my head, but the rough rock it was lying on felt too comfortable under my cheek for me to move. “I had a good reserve going in, and I didn’t use that much,” I replied in a barely coherent mumble. “Either I should have more love, or you guys shouldn’t be so drained. This was something else.”

Sickle grumbled from somewhere off to my side, too worn down to put much vehemence behind her words. “I told you dumb cunts, that place was fucking with our heads.” There was a quiet rattle of metal as she sprawled out a little more, groaning softly. “Maybe it’s like… I don’t know, the changeling version of radiation?”

I murmured in reply. “Only megaspells produce magical radiation. We didn’t have any.”

\leavevmode\llap{“}You said you guys stole some.”

\leavevmode\llap{“}Maybe,” I said. “But even if we did, those would have been zebra magic, not changeling magic.”

Dusty cut in. “What about the ghouls?”

I wearily lifted my head to glance his way. He was lying nearby, his rifle set before him. When he saw my questioning look, he elaborated. “I know feral pony ghouls try to eat other ponies, for whatever reason, but these guys were originally changelings, so…”

I laid my head down again. “I was wondering about that, too. I don’t know. Maybe. Maybe not. I don’t have a clue how ghouls work.”

We were moving again just half an hour later, though we only made it a couple miles before Dusty called for a halt. My head was feeling a little better, though my legs were feeling sore once more. While everypony was tired from the walk, the crushing fatigue was already lifting, and hooves that had been lethargically dragging over the dusty rocks once again moved surely and swiftly.

I was careful, siphoning only the tiniest bit of energy from them, just enough to keep my dwindling reserves from falling any further. We had several long days of travel ahead of us. I could afford to let them regain their strength before tapping it for myself.

We settled in for the night. Dinner was, once again, a blank-can lottery. I got a can of concentrated soup for the third time in a row. Starlight got a can of pears in heavy syrup. We shared.

Then I made both Dusty and Starlight nearly choke on their food with a single question to Sickle.

\leavevmode\llap{“}Why did you become a raider?”

While Starlight coughed around a half-chewed bite of pear and Dusty tensed, Sickle merely turned to stare at me, her metal muzzle dangling beside her head as she slowly chewed a mouthful of canned greens. It made for several very uncomfortable seconds before she finally swallowed and spoke, baring her teeth. “The fuck do you care?”

I made a point of remaining still, not flinching away or squirming despite how much I wanted to. “Because I don’t get you,” I said. “Not entirely. Considering that my profession revolves around understanding how ponies think, I don’t like that.” I tilted my head slightly, trying to look more inquisitive. “I think I understand you a little more than I used to, especially after the hive, but there’s a lot I still don’t get, and I’m curious.”

She snorted derisively. “What’s to get? I like to fuck and kill ponies. So do raiders. Ain’t hard to figure that shit out.”

\leavevmode\llap{“}But something changed.”

\leavevmode\llap{“}Not really,” she said, tilting back the can to chew on a bit more of something that superficially resembled two hundred year old vegetables. With a full mouth, she added, “Just changed which ponies I fuck, and which ponies I kill.” She sneered. “Mostly.”

\leavevmode\llap{“}Something led you to become a raider,” I said. “And something led you to stop being a raider.”

\leavevmode\llap{“}And maybe ‘something’ is none of your fucking business.”

I held her gaze for a second before replying. “And would that ‘something’ explain why you were being relatively nice in there?”

She stopped chewing, fixing me with a silent glare.

\leavevmode\llap{“}It wasn’t emotional suppression,” I said, refusing to look away even under that terrifying death-stare. “I could feel that you liked me.”

She bared her teeth again, growling. “Yeah? And does it feel like I like you now?”

I smiled, and didn’t even hide the smugness. “Yes, a little.”

Her snarl vanished, and a moment later she snorted and returned to her food. “Ain’t like I need to kick you when you’re wading through the bodies of your family. Too easy.”

I winced, and looked away. She grumbled something as she continued eating.

Dusty eyed her curiously, but wisely said nothing.

{\br}%
The trip back was long, and almost entirely uneventful. It was made all the longer by the amount of supplies we had requisitioned. Even if Sickle was carrying half of it herself, it was still a tremendous amount of weight.

We were all quite happy when we reached the wagon the next evening, and could finally offload all that weight. As we piled everything into the wagon, it highlighted just how much we had taken. The roughly two dozen weapons and tens of pounds of ammunition and spark packs was just the start. Dusty had insisted on taking a full set of suppressors for various calibers. I had apparently made quite the impression with my pyrotechnic display in the outskirts of Dodge City, so we also acquired a wide assortment of explosives, including a couple large demolition charges that Sickle had to carry for us. Then there was the personal gear. In addition to the flashlights, we now had a full set of four respirator masks, one each, with replacement lenses and filters, small air tanks, and detachable hoods. I wasn’t sure if they’d be useful, but Starlight liked the idea of having them. Not only would it be good protection from “bad air”, but there were apparently industrial sites that had noxious chemicals that were extremely unhealthy to breathe, not to mention the dangers that could come from inhaling particulates infused with magical radiation.

The wagon made much better progress descending from the rough terrain than it had climbing it. Sometimes, that progress was a little \textit{too} fast, as Sickle and it slid down slopes with hardly any control. She snarled and cursed the whole way as her hooves skidded against the rocks and cut furrows through the dry earth, but each time she laughed once they had settled on more even terrain.

We continued on, towards the looming shadows of Equestria.

The line of ragged clouds cast a sharp contrast between the brightly lit badlands and the darkened lands we were hiking towards. It hadn’t looked so dark under those clouds while we had been beneath them, but from where we stood, it looked dark and ominous.

Not that the land of sunlight was all that peaceful and ideal, and I don’t just mean the state of my hive. Above those clouds, basking in the glow of the sun and in vivid colors that reminded me of Equestria at its height, a battle raged.

We were too far to make out all the details, but I could see three Raptors weaving and circling in a deadly dance. Lances of light flashed between the clouds, and occasionally we could catch a glimpse of tiny black forms flying through the sky around them. They circled and closed, exchanging a fusillade of fire before withdrawing, the intensity of combat fading as they circled once more, like wrestlers looking for an opening.

The battle continued, off and on, for over an hour. Two of the Raptors hounded the third, which narrowly evaded their grasp time and again. Eventually the pair withdrew, with one of their Raptors smoking heavily. The two sides parted ways, disappearing behind the scattered clouds.

Eventually, we passed under the edge of the Enclave cloud cover. The heat of the sun faded as we returned to the softly lit grayness of Equestria.

After the events of our outbound journey, we avoided World’s End, and while we passed through Pale Sands once more, we gave Ponytown a wide berth. The journey took several days, with little to see or do. We spotted another set of structures in Pale Sands, but we steered clear. It kept our progress uninterrupted, but it also made the whole trip blur into one long string of nothingness. As we trekked across the miles of empty desert, only one brief event stood out.

{\br}%
We had halted for a brief stop just north of Pale Sands when Sickle grew restless. She was standing not far from me when her tail started to flick in agitation, the tip of her intact ear swiveling back and forth as if searching for a sound.

Dusty had tensed up immediately, setting down the bottle of water and shifting his rifle on its sling.

\leavevmode\llap{“}What’s wrong?” I asked.

\leavevmode\llap{“}Dunno,” Sickle rumbled, her head turning one way, then the other, scanning the horizon. “Something ain’t r—”

A black form smashed into the ground before us with a tremendous crash, sending me leaping back. It hit hard enough to rebound off the ground—and Sickle had already spun around, planting a powerful double-hoof buck that sent the black-armored pegasus pinwheeling into a nearby boulder.

All of that happened before I had even finished my startled jump, and I froze as I landed, watching the black form crumple to the ground. With her lumbering bulk, it was easy to forget how terrifyingly quick Sickle could be.

\leavevmode\llap{“}What the \textit{fuck?}” Sickle snapped, spinning back around to face the very dead pegasus. Then her head snapped up, quickly searching the sky, and she took a step back.

I jerked back once more, and looked up just in time to see a magical energy rifle fall to the ground in front of Sickle, smashing itself on the hard ground.

\leavevmode\llap{“}Shit,” Dusty grunted, ducking down beside the wagon and looking upwards. His rifle was up, searching for threats.

In the distance, I could see another armored pegasus, far from us and falling limply through the sky.

\leavevmode\llap{“}What the hell is going on?” Starlight said, scurrying under the edge of the wagon.

Dusty watched the dead pegasus fall below a nearby rise, out of sight. “We must be under a battle.”

\leavevmode\llap{“}What, the Enclave are killing themselves?” Starlight snorted. “Good riddance.”

\leavevmode\llap{“}Yeah,” Dusty muttered. “Unless one of them lands on us.”

\leavevmode\llap{“}Stop being such a bunch of pussies,” Sickle rumbled as she walked over to the fallen pegasus. While she did cast a glance upward, she appeared much more relaxed. “There ain’t any more falling at us.”

I kept a much more attentive eye on the sky above as I hurried over to examine the Enclave soldier.

She’d clearly been dead before hitting the ground. A ragged hole was burned through her side, deep and charred black. One side of the armor was dented and dirty from the impact with the ground. Even if she had survived that, I doubt she would have survived Sickle’s buck; her chest-plate was buckled in around a pair of deep dents, likely crushing her chest.

Once we were confident no more bodies were falling directly over us, Starlight hurried over to the fallen pegasus, eager to salvage the advanced armor. That enthusiasm quickly faded as she drew up close, her eyes lingering on the askew and broken-tooth jaw, the rich orange coat speckled with dirt. Starlight slowly reached out, hesitated, and drew back. Finally, she reached out again, gingerly undoing the helmet clasp. The soldier’s head lolled to the side at an unhealthy angle, her long red mane spilling out across her crumpled chest-plate.

Before her violent end, the mare had been quite beautiful.

Starlight shuddered a little, then reached over to the mare’s shoulder, pulling her forward. “Help me get this off her,” she quietly asked me, and I stepped forward to help roll the pegasus onto her belly, feeling a bit like a vulture.

As I did so, I gave her a concerned look. She glanced my way, and hastily looked away again. Her voice was quiet. “Power armor is valuable. A working suit is probably worth more than everything in that wagon, if we can find a buyer.” She carefully searched around the edge of the back armor plate, looking for a way to release it. “Even if it can’t be fixed, the parts and material would be worth something.”

She glanced at me, still with my concerned look, and her ears pinned back. She muttered. “When I find things to take, their owner’s usually been dead for centuries, not… minutes.”

\leavevmode\llap{“}Make it quick,” Dusty called out, while Sickle lethargically slipped on the wagon’s harness. “I don’t want to be here if any of her buddies come looking for her.”

\leavevmode\llap{“}I’m trying,” Starlight said, her hoof digging at the edge of the armor. Sickle was fully strapped in before Starlight finally found the release along one edge of the chest. It clicked open, and she found its twin on the other side, though it was deformed from the impact and jammed shut. Eventually, she had to take her prybar to the armor, wrenching on it until the other latch opened with a loud crack, and we peeled open the armor.

The effects of a magical energy weapon are not at all pretty. The mare’s belly had been burned out, leaving nothing but a charred pit of flesh. The only consolation was that the wounds were cauterized; I felt queasy enough at the gruesome wound even without blood.

It took some doing, but we eventually got her free, leaving her crumpled on the ground as we loaded the broken remains of the armor into the wagon. We couldn’t just leave her there, though. After a brief conversation, I bent my head beside the fallen pegasus, letting my magic wash over and consume her body, finishing what the magical energy weapon had started.

{\br}%
Five days after leaving my hive, as afternoon turned to evening, we once again laid eyes on Gemstone. Still miles away, it was a strangely comforting piece of familiarity. It was a place I could actually look forward to being at. My legs were feeling almost as rubbery as my first few days in the Wasteland, and between Starlight’s weary limp and Sickle’s slow trudge, I imagine the rest of us were looking forward to a good bed for the night.

Dusty called a halt, motioning for us to join him behind the wagon.

Once we were there, he turned to me. “First off, I assume you’ll want to change up before we hit town.”

\leavevmode\llap{“}Indeed,” I said, and called up my magic. My companions had recovered well enough for me to start replenishing my magic, and the quick change drained fairly little of what I had accumulated. Green flame flashed over me, returning me to my earth pony guise.

Starlight’s eyes widened. “Woah, wait a second!” she blurted, looking over me. “Did you just burn up that armor?”

I gave a smug smile. “Nope,” I said as I rolled my shoulders, shifting my cloak and saddlebags slightly to better suit my current form. “Changeling armor is special. I’m not fully versed on how it’s made, but we can hide it with our shapeshifting magic.” I reached up, touching a hoof to the soft coat covering my chest. “It doesn’t give any protection like this, but it’s only a moment away, if I need it.”

\leavevmode\llap{“}Wow,” Starlight said, a smile spreading across her face. “That is so cool!”

I chuckled, setting my hoof down. “And more importantly, it means it doesn’t get in the way of my shapeshifting.”

\leavevmode\llap{“}Neat trick,” Dusty said, nodding in approval. “Any other items you can do that with?”

I shook my head. “As I understand, it only works on simple devices. Something about the materials and magic involved. I know some changelings had made small blades that could be concealed in a similar fashion, but that’s not as useful as it sounds, and anyway, I didn’t see any in the armory.”

He nodded, and changed topic. “Okay. I wanted to stop and discuss future plans before we got into town. I figure some changeling stuff might come up, and I thought you might like to deal with that away from any curious ears.”

\leavevmode\llap{“}I appreciate it,” I said with a nod.

He sat, and we all followed suit.

\leavevmode\llap{“}Now then,” Dusty said. “The first question is, where would we look for Whisper’s hive?”

\leavevmode\llap{“}We need to find C.L.T. facilities,” I said.

\leavevmode\llap{“}Except we have no idea where those are,” Starlight said.

\leavevmode\llap{“}Baltimare holds the Crystal Life Technologies regional headquarters. That should tell us where every facility in the region is located.”

Dusty grimaced. “Yeah, I remember. That’s still a hell of a long trip, and not an easy one.”

\leavevmode\llap{“}I’d never even heard of Crystal Life before Paradise Beach,” Starlight said. “Scavengers tend to hear about places like that. There’s definitely none around Dodge City, unless they were in the crater. Maybe some trader heard of something, but I dunno.” She looked to Dusty. “We need something to go on.”

He sighed, but nodded. “Yeah. We can ask in town, see if anyone’s heard of anything. If not… yeah, okay, we can look into making a trip to Baltimare. I’m not even sure if it’s feasible or not, but… we’ll look into it.”

I smiled, giving him a grateful nod. “Thank you.”

\leavevmode\llap{“}Second question,” he said. “What do we do about Big Gun?”

He was answered with complete silence.

After a moment, he sighed again, and looked to me. “Whisper, how hard would it be to find some evidence that could be used to take him down?”

I frowned, considering the question for a moment before answering with one of my own. “Do you mean finding the evidence, or making sure that evidence actually takes him down?”

He quirked an eyebrow questioningly. “What do you mean?”

\leavevmode\llap{“}He’s been in power some time now, hasn’t he?” When Dusty nodded, I continued. “He also has an independent group of mercenaries in his employ, and a lucrative industry that keeps him rich and well-armed. He’s got political, economic, and military power. Even if we find enough support for that evidence to condemn him, we know he had some Rangers helping those mercenaries that ambushed us. We’d need to be sure where the Militia would fall on this matter, especially if his mercenary forces have been replenished. If they fall on the wrong side, they would need to be dealt with before we could proceed.”

Dusty was frowning deeply by the time I had finished. He was silent for several seconds, and eventually fished out a cigarette. He lit it, smoking in silence for a few more moments before asking, “How long would that take?”

\leavevmode\llap{“}You’re asking for an infiltration of multiple levels of government, such as it is, and two separate military organizations,” I said. “Optimistically? Weeks, and that’s if I am \textit{incredibly} lucky and stumble into something big.”

He slowly nodded, sighing out a long stream of smoke. “And pessimistically?”

\leavevmode\llap{“}Months, inconclusive data, and possible loss of committed assets.”

\leavevmode\llap{“}Loss of—”

\leavevmode\llap{“}I die.”

He blinked, looking up with a questioning expression. “Do you think that’s likely?”

\leavevmode\llap{“}Infiltration is never without risk,” I said. “No, I don’t think it’s likely, but it’s possible. I’m confident in my abilities, and they lack many of the resources wartime Equestria had that might make Infiltration more difficult, but there’s always a risk.” I motioned a hoof toward him. “You seem to be an excellent soldier, but there’s always the chance you could take a bullet to the head from some random, blind shot. We can minimize the risk, but it’s always going to be there, and we can’t always see it coming. The longer I’m poking around investigating dangerous individuals and organizations, the greater the risk.”

Dusty considered that a moment, taking another slow puff before asking, “And if you… \textit{took care} of him the other way? How well would that work?”

I looked off into space for a moment, considering several factors. Then I looked back at him. “I could be back by dawn.”

His ears folded back, and he looked away to take a particularly long drag from his cigarette.

Starlight quietly murmured beside me. “You’re kinda creepy when you talk shop.”

I blinked, my own ears drooping a bit. “Sorry. I just… wanted to consider things as factually as possible.”

\leavevmode\llap{“}It’s okay,” she said, awkwardly looking around the ground near her hooves. “...It’s kinda cool, too.”

I raised an eyebrow, and she finally looked up to me. She hesitated a moment, then smiled a little. “...More cool than creepy, I guess. Our little superspy bug.”

I huffed out a soft laugh, though my amusement slowly faded as I considered the source of her concern. “I don’t want to kill ponies,” I said, and her faint smile faltered in surprise. “What he did to Silverline and Quicksilver makes it easier to deal with, but I’d prefer if there were a better solution. I just don’t think there is one, here.”

Off to the side, Sickle snorted and muttered. “Dumb cunts.”

Starlight looked to her with shocked surprise. Even Dusty looked up from his thoughts. Sickle looked around at our reactions, frowning. “What? Just kill the fucker already! Don’t just sit around whining and trying to come up with some pussy-ass reason for it. Those two little raider fucktoys should be reason enough for you dumbasses to stomp his fucking skull in.”

I spoke up. “There’s a lot more to consider.”

\leavevmode\llap{“}No there isn’t,” she snapped back. “You like those two, for whatever fucking reason you’ve got. He hurt them, so you go back and hurt him worse. Simple.”

\leavevmode\llap{“}Charming,” Starlight muttered, while I remained silent, eying Sickle.

Dusty broke the ensuing silence. “Okay.” He took another long drag on his cigarette, killing it in record time, and dropped it to the ground, grinding it into the dirt with a hoof. “Okay. Whisper will take out Big Gun.”

\leavevmode\llap{“}And Wild Runner,” I said, my attention returning to him. “She seems every bit as bad as him, if not worse, and she’d just step into his horseshoes if he dies. With both of them removed, there’s no stable base. Things might get messy, especially if the Militia tries for a power grab, but it would be manageable.”

He nodded. “Her too.”

\leavevmode\llap{“}I’ll also dig around for evidence while I’m there. Implicating him after the fact will be much easier, and I may be able to discover something that clears our names. Lethal force means more direct and expedient information gathering.”

Dusty hesitated, but nodded again.

\leavevmode\llap{“}Okay,” I said. “Should I get started on that?”

Dusty shook his head. “No. That was planning for later. Right now, we’re all going into town, getting some comfortable rooms, and resting. At least one week R\&R, then we can move on.”

\leavevmode\llap{“}A week?” I said, ears perking up sharply. “We don’t need that long. I can take care of Big Gun and Wild Runner by morning, and I’m sure Emerald will have anything we need for the trip to Baltimare. If Sickle doesn’t mind me taking a nap in the wagon when I get back, we could be on the way tomorrow.”

Dusty shook his head. “No, Whisper. We’re taking a good long break before we set out for Baltimare. We need some down time.”

I stared at him in disbelief. Then I blinked. “No, I don’t. I need to find the rest of my hive. That’s more important than my own comfort.”

\leavevmode\llap{“}I’m not talking about comfort,” Dusty said; though it was without anger, the words were sharp, and my ears pinned back. “I’ve been with you for, what, three weeks? Four? And in that time, we’ve been traveling almost constantly. We haven’t had even a single full day to rest and recover.” He touched a hoof to his chest, or more accurately, to the old barding he wore. “I’ve been a soldier most of my life. I’ve seen what happens when you keep a unit going for weeks or months without rest. Ponies start breaking down or making mistakes. Even the best can’t keep going forever.”

He gestured around with his hoof. “Every single one of us has been injured. Sickle’s been shot more times than I can count. Star’s limp has been getting worse. And Whisper, we were picking shards of bone out of you, not to mention the emotional trauma you’ve been through. We all need a break, but you need it most of all.”

\leavevmode\llap{“}I can handle it,” I said, though my ears remained back; distantly, I recognized I was being defensive. “It’s fine.”

\leavevmode\llap{“}You’re not fine!” Dusty said. “Shit, Whisper. I’ve seen you go into a full breakdown at least three or four times. Every time I’ve woken you up these last few days, you jerked like you were being attacked. You’ve been crying in your sleep!”

My mouth shut on any further protests, staring back at him with wide eyes. Had I really? I remember being a little surprised when he woke me up, but it couldn’t be that bad, right?

I looked over to the others. Starlight looked down at the ground, as if unable to meet my gaze.

Sickle’s lips pulled back in a smirk. “Crying like a little bitch.”

While Starlight hit her on the shoulder, \textit{hard}, and Sickle gave a firm shove in return, I looked back to Dusty. I was surprised to see him moving in close, and even more when he reached out, placing a hoof softly on my shoulder. I blinked.

\leavevmode\llap{“}Whisper, I can’t even imagine how hard all of this must be for you,” he said, his voice surprisingly calming. “Shit, I don’t know if I’ve met a pony that could handle something like this as well as you are, but even strong ponies need a break from time to time. You’re not going to do your family any good if you push yourself past the breaking point.”

\leavevmode\llap{“}I… I can handle it,” I said, my throat tightening. “I have to.”

\leavevmode\llap{“}No, you don’t,” he said, giving my shoulder a squeeze. “It’s been two hundred years. How likely do you think it is that they would survive two hundred years, but not be able to survive two hundred years and seven days?”

I wanted to object, to contradict him, but I couldn’t make any words come out. Every objection I tried to conjure reeked of self-deception.

\leavevmode\llap{“}You have an objective,” he continued on. “It’s an important objective, but it’s not a time critical one. If you keep pursuing it as if it was and drive yourself to death, you will \textit{fail} that objective.” I flinched. “The smart move is to step back, regain your strength, plan things out, and only set out again when you’re at your strongest.”

I deflated. The lump in my throat had swollen, my breathing growing hoarse. I think what finally did it for me was the tears building up in the corners of my eyes. I was on the verge of breaking down and crying just because someone was—rightly!—making me slow down.

I sniffled, blinking back tears, and nodded. With the matter concluded, Starlight stepped up to me, wrapping me in a firm, soft hug. I simply tucked my muzzle in against her neck, taking comfort in her soft coat and warm emotions.

Starlight gives good hugs.

After a minute, I drew back, wiping my eyes and swallowing down the last of the lump in my throat. “Okay,” I said, finally looking up to Dusty again. “One week.”

\leavevmode\llap{“}One week,” he agreed. “We’ll see from there.”

I nodded.

He gave me another minute to gather myself up, and then we continued on toward Gemstone. The better part of an hour was spent crossing those last few miles, and while it might have been a lie to say I felt much better by the time we crossed the train tracks and started up the gentle slope toward the gate, I at least felt more stable.

The bell lazily rang in the tower as we approached, and atop the wall, I could see Dazzle resting against the center magical energy cannon.

Sickle rumbled. “So, what’s this town like? It like Rust?”

\leavevmode\llap{“}Better,” Starlight said. “Much better.”

Sickle snorted. “Wonderful.” Then she started fishing around in her pack, downing a couple pills and a whole bottle of beer. Dusty muttered under his breath, too quiet for her to hear.

As we approached the walls, Dazzle gave a lazy wave, and called out once we were close enough. “Well, well! Welcome back, little Star. Come to break some more hearts?”

Starlight scowled up at Dazzle’s grinning face. “Do you actually do anything other than lie around on that wall and heckle travelers?”

\leavevmode\llap{“}Hey,” she replied with a laugh. “Looking pretty is hard work, and somepony’s got to hold this thing down.” She patted the cannon with a hoof. “And hey, you’ve got a new buddy. You got enough armor, there, pal?”

I could practically hear Sickle’s sneer. “How about you come down here and find out, bitch?”

\leavevmode\llap{“}Oh-ho!” Dazzle replied, her ears perking up and her grin growing. “A rough and tough mare, huh? I like it.” Her hoof tapped against the cannon again. “Just don’t go starting \textit{too} much trouble, you know? You ain’t got enough armor for it.”

Sickle rumbled, and I swear I heard a bit of a chuckle in there. “Eat me.”

\leavevmode\llap{“}Sorry, big stuff,” Dazzle replied with a laugh and a wink. “I’m on duty, here.” She looked back, waving a hoof, and the gate opened.

We entered Gemstone, with Dusty leading the way to Emerald’s store and inn. Sickle kicked off the harness and followed us inside; she wore a distressingly predatory grin under that muzzle of hers.

Emerald was putting away a broom as we entered, already turning her bright smile our way. “Well, hello again! Glad to see you’re all back and doing well. You even picked up a new friend, I see!”

Sickle’s smile vanished, and I’m pretty sure I could see her eyes blinking in the shadows of her eye-slits. It suppose I shouldn’t be surprised that she’d find the reaction unusual; I can’t imagine many ponies are all that pleased to meet her.

Emerald continued on, seemingly oblivious to Sickle’s reaction. She stepped up to the counter, crossing her forelegs over it and smiling at us. “So, what brings you all my way today?”

Dusty stepped up to the counter, meeting her smile with one of his own. “We’re looking to unload and unwind after a long job. We figured you’re about the best place to trade outside of Mareford.”

She chuckled. “Well, I thank you for the compliment. As for unwinding, does that mean you’ll be needing rooms for the night?”

\leavevmode\llap{“}For the week,” Dusty said. “Maybe a little longer.”

Her smile grew. “Ah, good! Ponies like you, I bet you’ve got some fun stories to share, don’t you?”

Dusty hesitated, casting a quick glance my way before replying. “I’m sure we’ve got a few we could share.”

\leavevmode\llap{“}I’ll look forward to it! But for now, we should get you all set with a place to sleep. Are you wanting the regular rooms or a suite this time?”

\leavevmode\llap{“}What’s in the suite?” Dusty asked.

\leavevmode\llap{“}A big front room, one large bedroom, a slightly smaller bedroom, and a whole bunch of cots in the back for everypony else. Great for caravans and other large groups, or ponies who just want a bit more room.”

\leavevmode\llap{“}That sounds good.”

\leavevmode\llap{“}Okay,” she said with a nod, and gestured to the stairs at the back of the room. “Take either of the upstairs rooms. Pull that cart around to the back lot and I’ll get it locked up safe and sound for you.” Then she turned her smile to Starlight. “And while they take care of that, I’ve got something for you, hon.”

\leavevmode\llap{“}For me?” Starlight asked, tilting her head.

\leavevmode\llap{“}For you,” Emerald said. “I think you’ll want to see this.”

\leavevmode\llap{“}Oh, um…” She glanced back my way. “I guess I’ll catch up with you?”

\leavevmode\llap{“}I’ll only keep her a minute,” Emerald assured me, and I nodded, hiding any hesitation I felt about this.

\leavevmode\llap{“}I’ll just browse for a bit,” I said.

\leavevmode\llap{“}Let me know if you find anything you like!” Emerald said. Then she motioned for Starlight to follow her, leading the way to the door at the back of the room.

I made a show of looking over the shelves, even after they disappeared and the door shut, but my ears were alert. It was perhaps a bit silly, being suspicious of Emerald only because she seemed too nice, but Infiltrators learn to be suspicious of everypony.

I didn’t really expect that she was in any danger, or I would have insisted on accompanying her. Still, I wanted to stay nearby. To be honest, I wasn’t really sure what else to do.

It was a couple minutes later when Starlight stepped through the doorway again. Her wide eyes were tearing up. I took a step towards her, my stomach lurching in alarm. But then, as she saw me, she smiled, wide and euphoric, her eyes practically dancing with light. She moved my way, and only then did I notice that her PipBuck wasn’t bouncing at her chest.

It was clasped snugly on her leg, just above her hoof.

Starlight practically leaped upon me, gripping me in a crushing hug. A giggle quickly grew to unrestrained laughter of pure joy as she bounced, while in the doorway behind her, Emerald looked on with a proud smile.

She finally released me, looking around as she wiped a hoof across her cheek. “This is \textit{amazing!}” she squeaked out between laughs, her eyes darting around at things I couldn’t even see. She turned around a couple times, still laughing, until she finally staggered and fell to her haunches.

Starlight lifted her foreleg, staring down at the PipBuck and giggling. As she stroked a hoof along the device, Emerald finally left the doorway, stepping up beside her and producing a small set of tools tucked into a cloth wrap. She held out the thin bundle to Starlight, who looked up, blinking away tears.

After a few moments of incomprehension, Emerald wiggled the bundle, as if to say, “Take it.”

Starlight blinked again, then reached out and took the tools. “Thank you so much.” She cradled the tools against her and looked over her PipBuck again, turning her leg to admire it. “Oh! Caps!” She turned to her saddlebags, lifting the flap to rummage around inside. “How much do you want?”

Emerald laughed, soft and pleasant. “No need for that, hon. It’s not as if I have use for those tools, after all.”

Starlight looked up from her bags, a pouch of caps dangling from her teeth. She let it drop back to speak. “But this is… I’ve got to give you \textit{something!}”

\leavevmode\llap{“}Then you can give me a smile,” Emerald said, “and I’ll consider myself well-paid.”

Starlight stared back at her for a second, as if surprised, before a smile spread once more across her face.

Emerald smiled back. “There, see?”

Starlight was tearing up again, even as a hint of a blush spread across her cheeks. She stood and practically leaped onto Emerald, wrapping her in a tight hug. “Thank you!” she said, over and over.

\leavevmode\llap{“}You’re very welcome, dear,” Emerald said, patting her softly on the back. “It always fills my heart to see a pony so happy. Something like that, it’s worth all the caps in the world.”

\leavevmode\llap{“}If there’s any way I can repay you, just tell me!” Starlight insisted. “I owe you, seriously.”

Emerald chuckled and placed her hooves firmly on Starlight’s shoulders, holding her back to look her in the eyes. “You don’t owe me anything, hon. If you really want to pay me back, then just be a good pony, bring a bit of happiness to another pony’s life. Generosity and Kindness, right?” She smiled, lifting a hoof to brush away some of the dampness from Starlight’s cheeks. “Now why don’t you go on? I don’t want to keep you when you’re probably dying to give that thing a spin.”

Starlight broke out in a wide grin. She pushed past Emerald’s hooves to give the older mare one last hug, then bounded my way. I had only a moment to brace before she practically tackled me, giving a firm hug and nuzzling affectionately at the side of my head. When she released her death grip, her PipBuck-clad leg remained around my shoulder, pulling me along as she guided me to the front door. “Come on, Whisper! I need to try this thing out!”

{\br}%
Starlight was in heaven.

She trotted along with energetic, bouncing steps, pausing only to lift her leg and fiddle with her PipBuck. Her gaze danced this way and that, as if the world were a completely new and fascinating thing, but I knew what she was really looking at was something only she could see. Every now and then, if I was looking closely enough, I could catch a tiny glimpse of light dancing about her eyes, so subtle that you’d never notice it if you didn’t know what to look for.

But mostly, I watched her smile. Her enthusiastic, unbridled joy was contagious, as if my own troubles were diminished by it.

Of course, Starlight being Starlight, we headed to Arclight’s place. She had no problem finding him inside the cluttered building. ”I can see his mark, right there,” she had said, pointing at a wall, and guided us around until we found him, completely focused on his work. We greeted him, and moments later were on our way to his weapon range. Of all the features the PipBuck had that only functioned when worn, Starlight was most interested in trying out its targeting spell.

I have to admit, it was pretty effective. After a few warm-up tests to get familiar with its functionality, Starlight started to have fun with it, giggling as she slew cans, bottles, and wooden targets with her Recharger. We ended with some trick shots; she had me grab three bottles and throw them all together. Without her PipBuck’s magic, she could reliably get one before they land, and occasionally a second.

After a few throws, it was time to give the spell a try. “Throw ‘em,” she said, her eyes looking eagerly in the air, her pistol floating in her magic, just below her gaze.

I reared back, three bottles clutched in my forehooves, and hurtled them into the air.

The pistol smoothly snapped up, and with three sharp pops, the broken and half-melted remains of the three bottles peppered the ground of the range.

She turned back to me with an almost manic grin. “This is amazing!”

I was smiling, too. “Again?”

\leavevmode\llap{“}Just a sec,” she said, eyes darting off to some unseen indicator. A moment later she nodded. “Okay, do it!”

Three more times I threw. Three more times, she hit every bottle before they hit the ground. Even the time she missed a shot, the follow-up came so smoothly that it could have been mistaken for being planned; there was no hesitation, just an unbroken cadence of shots.

We eventually stopped when it started getting dark out, once Arclight pointed out that ponies would be going to bed soon.

Starlight was still bouncing as we made our way back to Emerald’s place, and immediately ran up to give the older mare another hug.

\leavevmode\llap{“}I take it everything’s working well?” Emerald said with a chuckle.

\leavevmode\llap{“}It’s perfect!” Starlight said, releasing her again. “And now I’m feeling like celebrating. Plus I’m hungry. You got any fancy food we could buy?”

Emerald chuckled. “If it were a few hours earlier, I’d point you to Pumpkin’s place. She and her husband make some amazing food. The fanciest I can offer is some old pre-made dinners. Got a couple of stir-fried veggies and one with cheesy pasta. I also have drinks, and some packages of cookies or snack cakes.”

Starlight’s ears perked up. “We’ll take one of each of the dinners, and all the snack cakes.”

\leavevmode\llap{“}I’ve got five boxes of snack cakes, are you—”

\leavevmode\llap{“}All the snack cakes!” Starlight said with a dramatic flourish of her hooves, which contrasted sharply with the fit of giggling that followed.

It made for a much better dinner than the mystery cans we’d been living off of for the previous couple of weeks. Emerald even heated the pre-packaged dinners for us. The veggies were limp and the cheesy pasta was rubbery and greasy, but it was still one of the better meals I’d had since waking up in the Wasteland. Even just the simple touch of warming the food, once such a normal and mundane thing, gave the meal a hint of luxury.

We finished off both dinners and almost a whole box of snack cakes before heading up to our room.

Dusty groaned softly from the side of the front room as we entered, wearily lifting his head to look our way. “Oh, it’s you,” he murmured, laying his head down again, and lifted a hoof to gesture vaguely off to the side. “Sickle’s using the big room. You two can have the small one.”

We quietly made our way back, past the table and the assortment of chairs. The bedroom was still quite spacious, with a large bed, a pair of dressers, a couple footlockers, and a wash basin. A window overlooked the front of the town, its shutter standing open.

Starlight was still enthusiastic about her PipBuck, going on so much about it that she didn’t even spare a second thought as we slipped into the same bed. I noted it, of course, but was far too amused to bring it up and embarrass her.

\leavevmode\llap{“}...And any locations the map has marked will show up as pointers,” she said as she slid under the covers. “I can just set a destination and it’ll show the way. It also spots ponies, even through walls, and knows if they’re dangerous or not. Plus it’s got some fancy medical system that will flash warnings if something bad happens, and it gives even more details in the menus. It’s pretty—”

She stopped abruptly, frowning. Then her hoof slipped out from under the blanket, casting a faint green glow around the room as she flipped through menus. She halted, staring at the screen for a couple seconds before speaking. “I have a broken leg?”

\leavevmode\llap{“}What?”

\leavevmode\llap{“}It says I have a broken leg,” she repeated. She tapped a button, reading the details it called up. “An ‘incomplete fracture of the right large metacarpal.’” She followed up by touching a hoof to her right leg. “I mean, sure, it’s been sore, but it’s not broken.”

\leavevmode\llap{“}I think that means it’s cracked, but not broken all the way through?” I shifted my position, sitting up to look at her.

\leavevmode\llap{“}I guess so,” she said, laying her hoof down again. “It sure doesn’t feel that bad. Guess I’d better go easy on it until it heals.”

I couldn’t help chuckling. “With how much you’ve been bouncing around, you might want another healing potion.” When she started to object, I added, “I’m sure Emerald has more we can buy, and it’s a lot better to take care of it now instead of breaking it entirely.”

She sighed. “Yeah. Would kinda suck all the fun out of the day if I break my leg from celebrating.”

She fished out a potion, downing it, then turned back to her PipBuck. She watched for several seconds, a smile slowly spreading across her face once more as the medical summary rapidly shortened. “That is so cool.”

We settled in to sleep. After a few moments, she scooted up close to me, slipping a foreleg over me to give a soft hug. She nuzzled in against my cheek, murmuring. “This has been the best day ever.”

I smiled, lifting a hoof to gently stroke at her mane. “I’m glad.”

She held the hug for a couple more seconds before releasing and rolling onto her back. She also took most of the blankets with her, but a quick tug fixed that situation.

\leavevmode\llap{“}...I ate way too much,” she said with a faint groan.

I chuckled.

{\br}%
We slept in late, well past sunrise. It was probably another half hour before the sound of hooves out in the main room finally convinced us to finally get up and join the rest of the world.

Starlight led the way out, and then froze immediately on the other side.

The hooves we had heard were Dazzle’s, who was standing in the middle of the room, her barding slung across the back to reveal the blue starburst of her cutie mark When she saw us, she paused, flashing a playful smile and brushing back her tousled mane with a hoof. “‘Morning.”

\leavevmode\llap{“}Uh...” was all Starlight managed to say for a moment. “...What are you doing here?”

Dazzle chuckled softly, walking again. “I’d love to stay and chat, but I’ve got to go. I slept in too late.”

\leavevmode\llap{“}But—”

\leavevmode\llap{“}Sorry, gotta gallop. But hey, you want to talk, feel free to swing by the gate. I can always spare some time for a pretty mare.” She gave a wink, and then the door was swinging shut behind her.

\leavevmode\llap{“}I’m not…” Starlight trailed off with the other mare’s disappearance, then sighed. “What the hell?”

A couple heavy thumps from within Sickle’s room caught our ears, and Starlight glanced that way. “Wait, was she with…”

Dawning realization slowly broke across her features, followed immediately by a deep grimace. “Ew. Ew!”

Starlight then proceeded to rub her hooves against her head, as if trying to ward off the mental images that had just come to mind, all the while making continued sounds of disgust.

The door opened again as Dusty returned, a small bundle clutched in his teeth. He spared a momentary raised eyebrow at Starlight’s antics before speaking. “I see you two finally decided to join us in the world of the living.”

He wasn’t wearing his barding, and I was suddenly struck by how unusual that seemed to me. Granted, he looked about as travel-worn as his barding had, but it occurred to me that it was the first time I’d seen him completely naked, so long as I overlooked the holster still strapped to his shoulder. I leaned my head to the side, peering at his flank, with its image of a shield with what looked to be a rifle round emblazoned upon it. “Is this seriously the first time I’ve seen your cutie mark?”

He glanced back, looking a little confused for a moment, and shrugged. “I guess so.”

\leavevmode\llap{“}Huh.”

\leavevmode\llap{“}Anyway, I brought you all breakfast,” Dusty said, setting the bundle on the table. A few boxes and packages of wartime food spilled out. “Nothing too fancy, but it beats canned goods.”

\leavevmode\llap{“}I think I already lost my appetite,” Starlight said, but that didn’t stop her from grabbing a seat at the table and snagging a box of crackers.

I got a package of shredded potatoes and another of snap peas that didn’t quite live up to their name, but were still surprisingly delicious. I’m not sure how that kind of food could last for so long. I assume there’s some sort of preservative magic involved.

We were about halfway through when the door to Sickle’s room opened, and she slowly staggered out, bleary eyed. While it was a little odd seeing Dusty without his barding, it was outright bizarre seeing Sickle without her armor, as if it were a sudden reminder that there really was a pony under all that metal. Not that she looked any less imposing, with her heavily scarred and battle-worn features. It was hard to find an inch of her body that didn’t show some sign of past battles.

As she stumbled toward the table, muttering something profane under her breath, I couldn’t help but feel there was something off about her. It wasn’t until Starlight spoke that I realized what it was.

\leavevmode\llap{“}Holy shit,” Starlight said, her head drawing back in surprise as she eyed Sickle over. “Did you \textit{bathe?}”

Sickle halted at the table, blinking at Starlight for a couple seconds before mumbling. “The fuck are you talking about?”

\leavevmode\llap{“}You’re—” Starlight stopped herself, mouth closing on the word she was about to say, and then continuing on with a slightly more accurate phrase. “...not filthy.”

There were several seconds spent as that statement slowly processed in Sickle’s mind, until the huge mare finally blinked. “Oh. Yeah, that.” She sat on the floor with a deep thump that rattled the table, and rested her forelegs across it. Despite not using a chair, she loomed over her corner of the table. “That mare’s weird, kept trying to clean me. Eh, I was high as fuck, anyway. Long as she kept eating me out, I don’t give a fuck what else she’s into.”

She groaned softly, eyes half-closing. Her hoof came down on the bundle of food, scattering the remaining boxes and packages as she searched through them, and finally grunted. “What, no drinks?”

Dusty gave a dry chuckle. “Sorry, I didn’t get any booze. Did you run out?”

\leavevmode\llap{“}Nah,” Sickle rumbled, resting her chin on the table as she slid over a package of sliced carrots. “But it’s all in there,” she said, indicating her room with a flick of a hoof, “and I’m in here.” She stared at the package, as if willing it to open itself. “Fuck me. Hangovers suck.”

\leavevmode\llap{“}Alcohol dehydrates you,” Dusty said. “Drink some water, you’ll feel better. Anyway, Emerald’s ready to trade. I figured you’d all want to be in on that, get whatever supplies you need. We’re good on basics, but there might be some specialty items we want. Maybe more rifle ammo, if Whisper keeps shooting like she has been.”

I gave a self-deprecating snicker. “Yeah, I have to work on that. You offered to teach me. Maybe we could do that afterwards?”

\leavevmode\llap{“}This week is for relaxing and recovering,” Dusty said. “Training can be almost as stressful as the real thing, if it’s done right.”

\leavevmode\llap{“}I know some ponies go shooting for fun,” I countered. A thought occurred to me, and I amended my statement. “At least, they did back before. I suppose that’s not so common any more.”

Dusty eyed me, frowning, as if I were trying to pull one over on him. “There’s a big difference between popping off a few rounds at the range and serious training. Still, I suppose it wouldn’t hurt to have you run a few mags in a more relaxed setting. Getting used to firing a weapon can’t hurt.”

When we had all finished eating, and Sickle had gotten a drink to chase away the hangover—more beer, to our annoyance—we headed downstairs.

Emerald looked up from a clipboard, dropping a pencil atop it as she smiled at us. “Well, good morning, sleepyheads. I was starting to wonder if I’d see you fillies today. You must have needed the sleep.”

\leavevmode\llap{“}That was the most comfortable bed I’ve slept in in weeks,” Starlight said. “Yeah, I needed that.”

\leavevmode\llap{“}A good night’s sleep can do wonders,” Emerald said.

Sickle rumbled, plodding up behind us. “A good night’s fucking is even better.”

Emerald’s smile wavered for a moment. “Yes, well… that can certainly be a pleasant way to spend the night, at times.” She recovered quickly, switching topics. “So, you’re all looking to do some trading?”

We dug through our wagon, showing what we had that we’d be willing to trade, while Emerald made notes on her clipboard. Once we were done, she scanned over the list.

\leavevmode\llap{“}Quite the impressive haul,” she said. “Why, it’d put most small caravans to shame. Quite a bit of high-end weaponry here, too, and all in good condition. Some impressive heavy ordinance. Three machine guns and a minigun? And a set of power armor? Where in the world did you come into all of this hardware?”

\leavevmode\llap{“}An untouched, underground wartime facility,” I said. “We cleaned out the armory.”

While the first part was true, the second certainly wasn’t. The hive’s armory was intended to supply a variety of options for special operations, as well as to equip guards and militia in the case the hive was attacked. We took everything we could carry and hardly put a dent in it.

\leavevmode\llap{“}Well you certainly struck it rich,” Emerald said with an approving nod. “Plenty of ammo, too, even five boxes of subsonics. Looks like you won’t be needing the box I snagged for a good long time.”

Maybe that whole Generosity thing was wearing off. “Actually, I’ll take it. I’ve only used a couple of them, but they saved all our lives, and I doubt there will be many other buyers.”

Emerald smiled. “I’m glad they helped. What happened?”

Dusty and Starlight both glanced my way. Starlight looked particularly uneasy.

\leavevmode\llap{“}We got attacked,” I said, and did what I had learned to do through years of training and experience: I told just enough of the truth to conceal the rest. “We got separated. Somehow, I ended up behind the ponies that were shooting at the rest of us. They didn’t know I was there, so I was able to do enough damage for us to come out on top. It was a narrow thing, though.”

She sighed. “It’s a grim business. Sad to say, sometimes it comes down to that.” She was quiet for a moment before looking me in the eyes. “Bad ponies?”

I nodded. “At best, they were working for bad ponies, but I’m pretty sure they knew what they were doing.”

She slowly nodded. “Sad it had to go that way, but I’m glad you came out on top. Sometimes bad ponies have to be stopped. Just so long as it’s for good reasons.”

\leavevmode\llap{“}It was.”

Her smile returned. “Good to hear.” Then she gave a soft chuckle, as if to chase off the darker mood. Fetching her pencil to scribble a note on her clipboard, she added, “I’ll add the subsonics to the list.”

\leavevmode\llap{“}We’ll buy all the five-five-six you have, too,” Dusty said.

Emerald raised an eyebrow at that. “Really? You’ve got three cans and change already. You looking to outfit an army?”

\leavevmode\llap{“}Nope,” Dusty said, then pointed a hoof at me. “But I’m planning on teaching this one to shoot and fight, and I’m going to do it right, so at least one whole can is going down-range before we’re done.”

Emerald gave a low whistle before picking up her pencil and scribbling a few more notes. “Well, you’ve certainly got the caps for it. A bit of preparation can make all the difference in the world. Afraid my stock won’t make much of a dent in that. I’ve only got a little over two boxes of the stuff. I tend not to stock too much ammo when Mareford owns the market for kinetics.”

\leavevmode\llap{“}Every bit helps,” Dusty said.

Looking over her list, Emerald slowly shook her head. “That’s a lot of firepower. Are you wanting to sell all of it?”

Dusty looked my way. “Did you want to keep your pipe rifle?”

I hesitated. “My neck’s a lot happier with the assault rifle,” I said. With the new rifle, I’d been carrying more than twice the ammo for barely half the weight, which made quite the difference when I had been spending it as I had. Still, I couldn’t deny some sentiment for the rifle that had saved my life in my first firefight. “Though we might want to keep it, so we have something that fires that kind of ammo. Seems raiders use the stuff a lot.”

\leavevmode\llap{“}And don’t tend to have pipe guns of decent quality. Okay, we’ll keep that and the heavy-barrel one, probably sell most of the ammo. Sell the shotguns and all their ammo. I think we’ll keep one of the pistols as a spare, sell all the other handguns. Other than that…” He scanned over the piles of weapons, then looked back to Starlight. “Do you want any of the magical energy weapons?”

\leavevmode\llap{“}Not much point,” she replied, then raised her PipBuck-clad hoof. “Especially now.”

\leavevmode\llap{“}If we get in a close-in fight again, there might,” Dusty said. “Your Recharger is good for brief encounters, but it recharges pretty slowly once it’s spent. It started lagging at the end of those ghoul fights. That carbine there might be good for you if we end up in a longer close quarters fight.”

For a single moment, I thought Starlight might argue the point, but she simply shrugged. “Eh, sure. Can keep it as a backup or something.”

\leavevmode\llap{“}Okay,” Dusty said. “We’ll keep that one, trade the others. I think we’ll keep the two submachine guns to keep our options open. For the large-caliber rifles, we’ll keep the bolt and the scoped semi-auto, sell the others. I’ll put the smaller belt-fed as a ‘maybe’, but we’re keeping the heavy. For the small calibers, we’ll keep the long-barrel and the light machine gun, and two of the regular rifles, sell the others.” He paused, looking over the sizable arsenal. “I think that covers it.”

Emerald pointed with the pencil in her mouth. “The minigun?”

Dusty hummed a moment. “Tempted to keep that for emergencies. It was useful, until the ammo ran out. Don’t suppose you carry any for it?”

\leavevmode\llap{“}Afraid not,” Emerald said with a laugh. “Not many ponies toting miniguns around, after all. Heck, I’ve seen more ponies using those rounds as spare change than as ammunition.”

\leavevmode\llap{“}Not surprised,” Dusty said. “The thing basically just pisses caps. Still… I think we’ll hold onto it, just in case.”

\leavevmode\llap{“}Suits me fine, hon. I doubt I’d be able to give you a good price on it, anyhow.” She gestured to the set of Enclave armor. “That goes double for the power armor. It’d need a lot of repairs to sell as armor. Best I could do is part it out. I’m sure some of the internals would sell for a pretty pile of caps, but it wouldn’t be anything near what it’d be worth if it were working right. If you want a good value, you’d need to get it fixed up. I don’t know if there are any ponies this side of Trotsen that could do that. Maybe someone in Rust might be able to cobble something together.”

\leavevmode\llap{“}I think we’ll hang onto it, then,” Dusty said. “We’ve probably got more than enough to trade already.”

\leavevmode\llap{“}That you certainly do!” Emerald laughed softly as she looked over her list, then shook her head. “Thirty guns. Afraid I don’t have nearly enough caps to give you a fair price on all of that, much less the ammo and anything else you want to offload. Got plenty to trade, though, if you’re looking for any supplies.”

\leavevmode\llap{“}Always,” Dusty said, smiling. “Especially medical supplies.”

\leavevmode\llap{“}And I’ve been thinking of getting some barding,” Starlight said, flashing an awkward smile. “Would feel kinda weird being the only pony without. Plus, you know, getting shot really sucked.”

\leavevmode\llap{“}I do generally advise against it,” Emerald said, “even with barding. Better with than without, though, and I’ve certainly got plenty. What’d you have in mind?”

\leavevmode\llap{“}Something light,” Starlight said. “I need to be able to run and jump and climb with it. Leather, I guess?”

Emerald chuckled. “Leather barding is pretty heavy for the protection it gives, hon. Hot and stiff, too. It’s just cheap. It’s a step up from strapping on road signs and clipboards. You want lightweight and mobile, you want something metal, or better yet, cloth reinforced with metal.” She smiled. “Could even make you something custom-tailored, if you’d like. Might take a while for me to get that done, but it sounds like you’re planning on sticking around for a while.”

Starlight grinned. “That sounds great.”

\leavevmode\llap{“}Perfect!” Emerald said, giving her a pat on the shoulder, then looked over to me. “So does that mean you’re looking for barding, too?”

\leavevmode\llap{“}I’ve got something arranged,” I said, giving just enough of a sly smile to sell the tale.

\leavevmode\llap{“}Oh-ho,” Emerald said, matching my smile. “Sounds like there’s an interesting story there. Don’t suppose it’s one you can share?”

\leavevmode\llap{“}Sorry,” I said, though I held the smile. “But maybe later.”

\leavevmode\llap{“}Gotcha,” Emerald said with a conspiratorial wink, and turned back to the rest of the group. “Okay, what else can I interest you in?”

I nearly jumped at Sickle’s rumble, having nearly forgotten she was there. “Got any chems or booze?”

\leavevmode\llap{“}Ah,” Emerald said, with a good deal less enthusiasm. “Well, I’ve got some drinks, sure. I’m afraid I don’t stock combat drugs, so the only chems I have are painkillers.”

\leavevmode\llap{“}Figures,” Sickle grumbled. “Whatever. I’ll take it all.”

Emerald raise an eyebrow, but nodded. “Sure thing. I’ve got probably a dozen bottles of various beers and one of—”

\leavevmode\llap{“}I didn’t ask for a fucking inventory,” Sickle growled. “I said I’ll take it \textit{all}.”

Starlight hissed. “Sickle…”

But Emerald simply smiled. “Well, you can certainly afford it. I’ll add it to the list.” She scribbled out a couple quick words, then looked up again. “Anything else?”

In the end, Dusty bought the three packs of cigarettes she had behind the counter, as well as most of the food and the few healing potions she had in stock. That brought us up to two healing potions each, with one spare. While we had found medical supplies within the hive, they were irradiated through centuries of low-level exposure. None of us were particularly excited to find out what magical radiation might do to potent healing magic.

Emerald had a short discussion with Starlight about barding, and eventually pulled out one of the sets for her to try on. It was a fairly light set that only covered the chest and abdomen, but it was made of some fancy black armor fabric that was highly resistant to bullets, and had internal pouches with metal plates to give extra protection to the chest. Emerald helped adjust it to fit Starlight’s lean frame, and I have to admit, it hugged her body quite nicely. The addition of a set of thick pads to protect her knees completed the look, and she turned and posed several different ways, admiring herself in the mirror Emerald had provided.

Even Emerald’s repeated warnings that it was one of the more expensive sets of barding couldn’t dissuade her. She bounced happily, enthused over how light it felt. “It’s like it’s not even there. I like it!”

She spent the rest of the time prancing about in her new barding while Dusty hashed out the final details of the trading. Even after the armor and all the other purchases, we walked away a few thousand caps richer.

Starlight was in the mood to celebrate again, not to mention strut around in her new barding, so she and I went to Pumpkin’s place to see if the food was as good as Emerald said it was.

Pumpkin was a pleasant orange mare, who greeted us as warmly as Emerald had. We settled in at one of the tables, and she was soon grilling up a variety of veggies for us in the back while we sipped on glasses of lukewarm water.

We were just relaxing when Dazzle pulled out a chair and sat with us. “Heya, hot flanks,” she said, grinning at Starlight. “I’ve got to say, that looks damn good on you.”

Pumpkin called out from the grill at the back of the store. “Hey, Dazzle! Can I get you anything?”

\leavevmode\llap{“}Nah, I’m just here to chat with my friends,” she called back.

\leavevmode\llap{“}Okay, then. Just don’t go chasing off my customers, hmm?”

\leavevmode\llap{“}I wouldn’t dream of it!”

Starlight was rolling her eyes during their exchange, but was still smiling when Dazzle looked back to her. “Sorry, Dazzle. I’m in way too good of a mood to be bothered by your teasing.”

\leavevmode\llap{“}It’s not teasing,” Dazzle said with a laugh, then leaned forward with a sultry look in her eyes. “It’s flirting.”

\leavevmode\llap{“}It isn’t going to work,” Starlight said, her tone amused. “First off, I’m not into mares—”

\leavevmode\llap{“}So I and every stallion in town heard,” Dazzle said, smirking, “but I don’t quite buy it.”

\leavevmode\llap{“}—And second,” Starlight continued, her smile slipping, “you slept with Sickle. Seriously, ew.”

Dazzle’s smile fizzled, her ears twitching back. “Ouch. Yeah, not my finest moment, I suppose.” She gave a wry smile. “But, you know, beggars and choosers…”

Starlight blinked at the sudden change in tone, her mouth opening and then closing again while she tried to decide what to say. Myself, I remained quiet and outwardly neutral, but all my attention was locked on Dazzle.

Eventually, Starlight sighed and spoke. “Should I even ask what that means?”

\leavevmode\llap{“}Desperate times,” Dazzle said, and gave a weak chuckle. “It means there ain’t exactly a lot of available mares around, so sometimes I have to go with what I can get. A year of watching delicious flanks walking in and out of that gate without a taste was a bit too long, so… yeah.”

\leavevmode\llap{“}Yeah, okay. But still, \textit{Sickle?}”

Dazzle laughed, though awkwardly. “Yeah, yeah, I know. Only thing is, she’s available.” She smirked, eying Starlight again. “Because, trust me, other than being available, she ain’t my type.”

\leavevmode\llap{“}Neither am I.”

Dazzle’s laugh was much more sincere, this time. “Are you kidding? A fine young mare like you? You’re lean, strong, and athletic. I really like your mane, the style just shouts ‘playful and energetic’. Your coat’s nice and clean and even, so you obviously know how to care for yourself. Emerald likes you, which means you’re a good pony, and I know you’ve seen action, so you know how to fight. You’re pleasant to be around. And now you’ve got some of the sexiest, curve-hugging barding I’ve seen.” She leaned in, her eyes hungry. “Sweetie, you couldn’t be more my type if you were already sprawled out on my bed.”

Starlight’s face was bright red, her ears pinned back as she stared back.

Dazzle gave a playful smirk, resting her chin atop her hooves. “And you blush way too much at some flirting for somepony who isn’t into mares.”

Starlight swallowed. “Flattery isn’t going to change my mind.”

\leavevmode\llap{“}Again, it isn’t flattery, it’s flirting.” Dazzle winked, then glanced my way. Then she scooted a little closer to Starlight, leaning over to say, “Though I have to admit, your friend here has a lot going for her, too.”

Starlight blinked, her expression turning to one of curiosity. “Oh?”

As for myself, I focused on retaining a natural, neutral reaction, rather than narrowing my eyes in disapproval. Perhaps I was reading too much into Dazzle’s behavior, what with my training in manipulating ponies, but it all seemed so very familiar to me.

\leavevmode\llap{“}Oh yeah,” Dazzle said, her eyes on me as she leaned in a little closer to Starlight, as if sharing a moment with her. “I mean, I may be more into the athletic look, myself, but look at her! Everything about her is sleek and graceful. Not a single imperfection, and each curve is more delicious than the last. Her coat is perfect! Smooth and clean, not a hair out of place, and the perfect healthy shine. And that tail and mane! I don’t know how she grew them so full and long, but she obviously knows how to care for them. I mean, I’m envious! I wish I could grow my mane that long.” She chuckled. “Heck, I’d love to take her home and brush her mane for a few hours, just to feel it. Maybe chat about mane-care, while we’re at it, since she clearly knows a few things.”

\leavevmode\llap{“}You can save the flattery, \textit{and} the flirting,” I said, while Starlight was silently looking me over. “It’s really not going to work on me.”

\leavevmode\llap{“}A pity. I was serious, though. You just came in from the desert, but you look immaculate.” She smiled. “I like ponies who know how to take care of their appearance. Actually, that’s part of why I came over here. Mostly it was to flirt with a couple of the hottest mares I’ve ever laid eyes on, but I thought I might be able to offer my services.”

Starlight blinked, suddenly looking away from me and back to Dazzle. “What?”

Dazzle reached up, brushing a hoof along her sleek mane. “I’ve always taken pride in my appearance, and I’ve kind of made a side business out of it. I’ve got the closest thing to a salon you’ll find this side of the war. There aren’t enough pretty mares coming through to make it a full-time business, but it gets me some extra caps, and I love the work. Emerald’s amazing at getting supplies, too.”

\leavevmode\llap{“}A convenient excuse to get your hooves all over some ponies,” I softly noted.

\leavevmode\llap{“}A purely innocent but very happy coincidence,” Dazzle replied with a wink. “But seriously, I can keep it entirely professional if you prefer that. I just saw how weary you looked coming into town, so I thought you might like to relax and unwind with some pampering.” She looked back to Starlight, who seemed to finally realize just how close Dazzle was sitting to her. “I offer everything. Deep, full body cleaning, grooming, trimming, dying, treatments to care for your skin, coat, mane, and tail, hooficure, horn-care, full-body deep-tissue massage—\textit{everything}. I even rigged a setup that makes for a passable sauna, and if you haven’t tried one before, you would not \textit{believe} how wonderfully relaxing they can be.”

When she was met with our skeptical looks, she laughed softly and raised her hooves in surrender. “Honest! Ask Emerald, she’ll tell you.”

\leavevmode\llap{“}Yeah,” Starlight said, her voice laced with skepticism. “I’ll do that.”

Dazzle lightly clopped her hooves against the table. “Good! So, I take that to mean you’re interested?”

Starlight chewed her lip. “Well… I mean, it sounds nice, but I dunno…”

\leavevmode\llap{“}I think I’ll pass,” I said, eying Dazzle carefully.

\leavevmode\llap{“}Aww, please?” Dazzle said, blinking in my direction. “You’ll love it, I promise.”

I frowned a little. “Do you pursue all potential customers this aggressively?”

She grinned. “Nope. But for a couple of the most beautiful mares in the Wasteland, and ones Emerald speaks well of? I think that’s worth the extra effort.” Then she sat back, placing a hoof across her chest. “I promise: you’ll love every moment of it, you’ll feel so much better afterwards, and there won’t be any slips or wandering hooves intruding on the experience. Caps-back guarantee.”

\leavevmode\llap{“}I dunno,” Starlight repeated. “Sounds nice. I mean, if Emerald says it’s okay, then—”

\leavevmode\llap{“}Excellent!” Dazzle replied, clopping her hoof against the table again. “Are you available today? If I go fire up the heater now, I should be able to have things ready by the time you’re done eating and checking in with Emerald.”

Starlight blinked. “Uh… sure? I mean, I guess that works.”

\leavevmode\llap{“}Perfect!” Dazzle turned her smile to me. “I don’t suppose I could convince you to change your mind and give it a shot?”

I sighed. As bad of an idea as I knew this was, I wasn’t going to leave Starlight to face it alone. “I’ll go, too.”

\leavevmode\llap{“}Even better!” Dazzle grinned and stood. “I’ll go get things ready. My place is past the gate, second house on the left. Just let yourself in if I don’t answer, I might not hear you knock if I’m in the back setting things up. See you two soon!”

And with that, she turned and strutted off, with far too much of a bounce to her step for a simple business arrangement.

Starlight watched her leave, her cheeks still faintly colored. “...Did I just make a horrible mistake?”

\leavevmode\llap{“}I’m pretty sure she just wants to get her hooves all over you,” I said. “You can say no.”

\leavevmode\llap{“}I guess,” Starlight said, though her tone sounded unconvinced. “Still, she made it sound really nice.” She looked up to me, then leaned in, dropping to a whisper. “There were a lot of salons around before the megaspells, right? Did you ever go to one?”

My ears flicked back, realizing where this was going. “A couple times. And yes, they can be nice, but it really depends on who’s doing it.” I inclined my head the way Dazzle had gone. “And I think she’s more interested in getting under your tail than in grooming it.”

Starlight flushed at my targeted use of euphemism, chewing on her lip for a moment. “...Yeah, probably. But I mean, we’ve got a lot of caps now, and I’d like to do \textit{something} fancy with it, just once. And if Emerald says she’s okay…” After a moment, she chuckled, her smile returning. “Besides, there are two of us and one of her. Pretty sure we can kick her flank if she tries anything.”

I could have shut the whole thing down right then. Dazzle did a good job of pushing Starlight along, but she wasn’t there any more. Maybe I should have. But Starlight was clearly excited by the idea, to even consider putting up with Dazzle’s nonsense. She could use something nice.

Besides, I’d be right there, watching out for her.

So I put on a sly smile. “Just be sure to give her a good, swift buck if she tries to sneak a grope.”

She giggled. “Can do.”

I nodded, and with that, resigned myself to spend the evening at the salon.

So much for relaxing.