After a delicious meal of grilled vegetables and a drink that made a passable attempt at being tea, Starlight and I returned to Emerald, who immediately dashed my one last hope.

\leavevmode\llap{“}Oh, yes,” Emerald said with a chuckle. “I wouldn’t exactly call it a business, more like a hobby, but she certainly puts some effort into it.”

Starlight smiled a little, sounding genuinely surprised. “Huh. I kinda thought she just came up with it to get her hooves on me.”

Emerald laughed softly. “Oh, no. She came up with it a long time ago to get her hooves on any mare she could. That poor filly’s never had any luck with love. Still, she managed to channel something productive out of it. She’s good, too.”

Starlight hummed thoughtfully, while I, still feeling suspicious, pressed on.

\leavevmode\llap{“}And how many of her customers get treated to wandering hooves?”

Emerald leaned on the counter, giving me a knowing smile. “Best I can say is nopony’s ever complained. As far as I know, she’s never gone too far with a pony who wasn’t receptive to her advances, and it really isn’t my business what happens with the ones who \textit{were}.”

There was just a hint of color to Starlight’s cheeks. “Well we’re not.”

\leavevmode\llap{“}Wouldn’t be my business if you are or not,” Emerald said. “But as long as you’re clear with Dazzle as to where you stand, I expect that’ll be all there is to it. She might come on a bit strong, but she’s good at heart.” She watched Starlight’s skeptical expression for a couple seconds before smiling, and added, “If it makes you feel any safer, tell her I’ll thump her head if she tries anything, okay, hon?”

Starlight grumbled softly. “I guess.” After a moment, she glanced up again. “So she’s, you know, good at that stuff?”

\leavevmode\llap{“}Oh, very,” Emerald said with a nod. “She’s got a real talent for it.”

\leavevmode\llap{“}Well… okay, then. I guess we can give it a try.” She glanced my way, seeking to reassure me. “We can always leave if it starts getting, um… weird.”

\leavevmode\llap{“}I suppose,” I said, even though I felt like it was already there. I turned to Emerald. “How exactly does a guard also run a spa? I’ve heard of some strange business combinations before, but that’s stranger than usual.”

\leavevmode\llap{“}Guard work is a volunteer thing,” she replied with a shrug. “Dazzle’s taken to it well enough that the others consider her to be in charge, but it’s all pretty informal. So long as at least one pair of eyes are on lookout, we don’t need a bunch of ponies lining the walls at all hours of the day. She’s usually up on the wall, but it’s no trouble for her to slip away for some side business.”

I suppose that made sense. I turned back to Starlight. “Okay. I’m going to go up and talk to Dusty real quick, then we can go.”

We parted ways, and I returned to our suite. Dusty’s reaction was pretty much as I expected.

\leavevmode\llap{“}So let me get this straight,” he said, his expression a skeptical combination of amusement and annoyance. “You argued with me to get the chance to go shooting, and now you’re wanting to blow it off to go take a bath?”

\leavevmode\llap{“}No,” I said, giving a wry smile. “I’m putting it off to stand guard over Starlight while \textit{she} takes a bath.”

Dusty let out a long sigh. “Whisper, we’re supposed to be here to relax.”

\leavevmode\llap{“}I know that,” I replied, and quickly dialed back the harshness that had crept into my voice. “But Starlight’s gotten excited by this idea, and I’m concerned about what might happen if I let Dazzle have too much time alone with her. At least if I’m there, I can make sure it’s just a nice, relaxing evening rather than something she’ll regret.”

The sound of empty bottles clanking in the next room preceded Sickle’s entrance from her room. She was grinning, her eyes just a little too wide. “Hah. Somepony’s jealous.”

My ears pinned back as I fixed her with a glare. “Starlight is my friend, and I’m protective of my friends, especially now.”

\leavevmode\llap{“}Maaarefrieeend,” Sickle teased, tongue lolling from the side of her mouth for a moment. Then her ears flicked and she gave a full-body shudder.

I scowled. “Sickle? Shut up, you’re… are you high?”

\leavevmode\llap{“}Fuck yeah,” Sickle replied, a little too loudly. “Buck and Dash. Dash is the best fucking hangover cure ever, and add in some Buck? It’s just… fuck yeah! I can do fucking anything! Hah!”

\leavevmode\llap{“}Except expand your vocabulary,” I dryly noted, actually earning a laugh from her.

\leavevmode\llap{“}Eh, fuck words,” she said. “Anyway, you two have fun slobbering all over that weird mare. You can have her. Town like this has to have plenty of pent up stallions ready for a good rut. Time to show these cunts how to party!”

Dusty groaned softly. “Please don’t get us kicked out of town. I like this town.”

\leavevmode\llap{“}You would,” Sickle rumbled with a sneer, then turned to trot off. “Later, losers!”

If you’ve never seen a pony that size trotting along in the upper story of a Wasteland-era building with an energetic, drug-fueled bounce to her steps, be glad. It could have easily passed as a minor earthquake.

Dusty shook his head once the thumping finally stopped. “Maybe somepony should be keeping an eye on \textit{her}.”

I smirked back at him. “Well I’m watching over Starlight today, so have fun with that.”

He gave a short, dry laugh. “Hey, I need to relax, too.” Then he sighed. “Anyway, have fun. And I mean it, at least \textit{try} to have fun.”

\leavevmode\llap{“}I’ll try,” I said, though from his look, it didn’t seem very convincing. I quickly changed the subject. “Want to do the shooting thing tomorrow?”

\leavevmode\llap{“}...Yeah, sure.”

\leavevmode\llap{“}Okay, then. See you later.”

I headed downstairs to meet up with Starlight, and together, we set out.

Dazzle’s house was rather large, and while obviously of post-war construction, it appeared quite well-made and sturdy, with a blue paint job that was only slightly faded and worn. The only unusual aspects were the large water tank beside the house, and a sign hanging on the front wall, with the word “Dazzle’s” painted in delicate, curving letters.

Starlight halted several yards away, staring at the sign for several seconds.

I looked back at her. “Did you change your mind?” I was perhaps a bit hopeful.

Instead, she slowly cracked a smile and snickered. “This is so stupid. I mean, I’ve ran right into raider dens without a worry, but now I’m all nervous about going into a freaking \textit{salon}.”

\leavevmode\llap{“}It makes sense to me,” I said. “It’s an unfamiliar and more uncertain situation, with more complex possible consequences, where the danger is less direct and more abstract. It lacks the clarity of potential combat. It’s not surprising that it would be uncomfortable.”

\leavevmode\llap{“}Thanks,” she dryly replied, then gave a snort of amusement as she advanced toward the door. “It’s still stupid.”

Just seconds after she rapped on the door, it flew open to reveal Dazzle’s grin. “Hey! You made good time. Come in! Come in!”

We shuffled into her living room, and she shut the door behind us. Our hooves clopped softly on the wooden floor, which was actually sanded smooth and finished with enough skill that it might have been passable back before the megaspells. The space was fairly sparsely furnished, with a trio of mismatched ancient couches around a more recently constructed coffee table. One wall had a line of bookshelves, full of magazines.

Starlight took one look at them, and color started to touch her cheeks again. “Are those porno mags?”

Dazzle laughed. “No, those are \textit{fashion} magazines. Mostly focused on beautification, mane care, coat care, stuff like that.” She stepped past us toward the hallway at the back of the room, giving Starlight a wink over her shoulder. “Though I’m sure I could dig up something a little harder if that’s what you’re looking for.”

\leavevmode\llap{“}It’s not,” Starlight replied, the color in her cheeks spreading.

\leavevmode\llap{“}Well, come on back,” Dazzle said as she reached the hall. “I’ve got almost everything ready to go. So, have you decided what exactly you want? Or shall I just go with the full deluxe treatment?”

I made a point of suspiciously eying her, though I kept my expression otherwise neutral. “That depends entirely on what you intend that to include.”

\leavevmode\llap{“}Now, now, strictly professional,” Dazzle said with a sly smile, before slipping into a more business-like demeanor. “The full treatment starts with a thorough cleaning, down to the skin, and complete with one of the finest set of beautification products available in the Wasteland. After that, there’s a full trim and groom, hooficure, a horn-filing for Star here, a few cycles through the sauna with cool-down sessions and warming hoof-baths in between, and all ending with a deep massage and a final touch-up grooming to make sure you leave here feeling as relaxed and beautiful as possible.”

She smiled proudly at the conclusion. I had the immediate impression of somepony throwing down a challenge.

\leavevmode\llap{“}Sounds thorough,” Starlight said, though cautiously.

\leavevmode\llap{“}And of course, I can customize the session any way you like,” Dazzle said, her smile softening. “The whole point is to pamper yourself, after all. We can just start with that list as a baseline, just feel free to make any requests that come to mind. Does that sound good?”

Starlight nodded.

Dazzle grinned. “Good! Then let’s get started. But first, as much as I hate to interrupt things with the talk of money, we should get that out of the way now. Even if I find a couple of beautiful mares to be a reward in itself, I’m still running a business, such as it is. Normally I’d charge about fifty caps for a full session, but Emerald likes you, I’m a sucker for pretty mares, and I’ll throw in a bit of a group discount, and call it… say, seventy for the pair of you?”

I’d been to salons before. Compared to the prices I’d seen back before the fall of Equestria, that seemed on the low side. Starlight, however, had no such frame of reference.

\leavevmode\llap{“}That seems like a lot of caps for some bathing and a massage.”

\leavevmode\llap{“}It’s worth every cap and more,” Dazzle said, still smiling. “Trust me. That goes on the whole ‘caps-back guarantee’ deal, too. When you walk out of here, you’ll be thinking it’s the best seventy caps you ever spent.”

Starlight chewed on her lip a moment, but finally pulled out a pouch of caps.

\leavevmode\llap{“}We’ll see,” I said.

\leavevmode\llap{“}Yes, you will,” Dazzle said with a wink, then turned to Starlight, who had moved to the coffee table to count out her caps.

When Starlight was done, Dazzle swept up the caps into another pouch, pausing for a moment as she fished out one of the un-crimped caps. “Huh, that’s a funny looking one.” She turned it over in her hoof, then shrugged and dropped it in with the others. “Anyway, that’s all taken care of, so let’s get to it. Follow me!”

She had an energetic, tail-swishing walk as we followed her down the spacious hallway of her home. We entered into what was easily the largest bathroom I had been in, with multiple doors in and out. An old bathtub that could have fit one of the princesses—or my own queen—with room to spare sat empty in the corner of the room, with a crude wooden framework built around it to hold it in place. The centerpiece of the room was the wide-open shower, with mismatched tiles and metal making for an effective shower floor, if not a terribly attractive one. The plumbing ran along the ceiling, exposed, and ended in a shower head that looked to have been made out of a metal bowl with tiny holes drilled through it. A rubber garden hose ran down to connect to another, detachable shower head, an old pre-war model made of faded plastic. Somewhere in the distance, I could hear a generator running.

Back during the war, a salon looking like this would have been looked down on as a miserable pit, if not outright condemned, but with the way things were after the megaspells, it was rather impressive. Dazzle had put some serious effort into this.

Not that it let me overlook that Dazzle had just led us into her own personal bathroom. That was something that still suggested a degree of intimacy to me. Ponies have a strong separation between private and public areas, and all manner of implications tended to stem from those.

\leavevmode\llap{“}Is the shower okay?” Dazzle asked. “There was a good storm a month back, so I’ve still got enough water for a bath, but I’d have to charge extra.”

\leavevmode\llap{“}A shower is fine,” I said, and Starlight nodded.

Dazzle nodded. “Good! Then all I need you to do is strip down. You can stash your bags on the counter.”

Starlight’s expression tightened in alarm, especially when Dazzle motioned toward her leg. “PipBuck, too. You’ll want to get cleaned under there pretty regularly.”

When Starlight’s hoof moved protectively over her PipBuck, Dazzle added, “I can’t really clean there when you’re wearing it.”

I set down my saddlebags. “We can clean ourselves.”

\leavevmode\llap{“}I can tell,” Dazzle said, smiling at me. “I’m curious. When’s the last time you had a proper shower? Soap and all.”

My ears twitched. “Almost a week ago,” I said, hiding a flash of shame that was, in hindsight, rather absurd.

Dazzle laughed. “I knew it! Goddesses, I love a mare who knows how to take care of herself.” She continued chuckling as she scooped up my bags and deposited them on the counter beside a large sink. “But anyway, another set of hooves does wonders for getting clean in all those hard-to-reach places. While I’m sure the two of you could take care of that yourselves, that’s what you’re paying me for, so just relax and enjoy a bit of pampering, okay?”

\leavevmode\llap{“}...Okay,” Starlight said, her voice full of reluctance as she unlocked her PipBuck. She set it reverently on the counter, her eyes lingering on it for a moment before turning back to Dazzle.

Dazzle smiled at us. “Now, I’m afraid my business is still fairly small, so I’ve only got the single set of hooves available. I’ll try to alternate between the two of you so you don’t feel left out. So, who gets to go first?”

Starlight and I exchanged glances, and I asked her, “Do you mind if I go first?”

Not that I was eager to have Dazzle’s hooves all over me. I wanted to see what it was she was going to do before she had a chance to do it to Starlight.

Starlight simply nodded.

\leavevmode\llap{“}Well, step on up,” Dazzle said with a wave of her hoof, before turning to walk to the back of the shower. “Time to get you all good and wet.”

I fixed her with a flat glare as I stepped up to stand under the shower. She answered my glare with a snicker as she snatched up the detachable shower head. A quick flip of one lever sent a cascade of warm water across my back. “Now, this is rainwater, so it’s very slightly radioactive. It’s fine for bathing, just try not to drink too much of it.” Flipping a second lever sent another spray from the shower head held in her teeth, which she used to spray the areas that the overhead shower didn’t reach. She also didn’t seem to mind the water, and by the time she deemed me suitably soaked, she was almost as wet as I was.

\leavevmode\llap{“}Go ahead and take a seat for a sec,” Dazzle said to me, then motioned to Starlight. “Come on in, let’s get you ready.”

Starlight hesitantly stepped under the shower, her short mane flattening to her neck as the water coursed over her. I kept a close eye on Dazzle as she sprayed down Starlight, especially the brief moment where she angled the shower head to spray along her belly.

Once Dazzle was satisfied, she shut off the detachable shower head and hung it up again. “Now you just enjoy the water for now,” she said to Starlight. “I’m going to get your friend here all lathered up real quick.”

She stepped over to a cabinet, opening it to reveal dozens of different bottles. What followed was a series of questions about our coats, manes, and tails, until Dazzle finally selected a suitable set of bottles for each of us. While Starlight remained under the warm flow of water, Dazzle took one of the bottles and poured a small amount of liquid along my back. Then she went to work, scrubbing her hooves through my coat, starting with my shoulders and working down along my chest. Naturally, this put her body very close to my own, something I’m sure was not at all unintended.

\leavevmode\llap{“}You’ve got such a clean coat,” Dazzle said as her hooves scrubbed down along the side of my chest, pausing for a moment to push back the hair and peer at the skin beneath. “Hardly any grease or grime. I’m impressed. You must have found some good soaps or shampoos out there, hmm?”

\leavevmode\llap{“}We found a little in some ruins a while back,” I said, vaguely.

\leavevmode\llap{“}Well I’d say you put it to good use,” she said with a chuckle. “You ever have any extra you want to sell, I’m always in the market. Or I can use it on you, if you’d rather. I could give a huge discount for that.”

Off to the side, Starlight snickered softly. “We’ll keep that in mind if any of the wartime facilities we track down end up to be a day spa.”

Dazzle laughed softly, her hooves finishing with my legs and moving to my side. “If you do, I’d certainly appreciate it. Emerald is amazing at digging up the most unusual and uncommon supplies, but I can always use more.”

\leavevmode\llap{“}She sure is,” Starlight said, a smile crossing her face. “I have no idea how she managed to get her hooves on a set of PipBuck keys.”

\leavevmode\llap{“}She knows pretty much every trader in the region,” Dazzle replied, her hooves scrubbing down along my side and belly. “In fact, she—oh, hold on; fair warning, getting to the tender bits.” My jaw tightened reflexively as her hooves scrubbed further down my belly and between my legs. My first instinct was to rear back and buck her, but I held firm. It would have been easy for her to give a little more sensual attention to those parts, but her hooves didn’t linger, simply working the shampoo into my coat the same as she had elsewhere.

Then she patted me on the flank. “You can relax again,” she said, a hint of teasing to her voice. I huffed out a quick breath, doing my best to relax, and she started to scrub down along my thigh. “Anyway, I was going to say, Emerald’s the whole reason I even started this project. You might not believe it, but I used to be a shy, lonely little filly.”

Starlight snorted softly. “Yeah, that’s kinda hard to believe.”

\leavevmode\llap{“}But it’s true,” Dazzle said, working her hooves along my leg; my tail flicked anxiously when her hoof rubbed along the inside of my thigh, but she didn’t seem to notice. “Shy and quiet, no friends, no family, and the worst possible luck when it came to love. I was a sad, miserable little filly. Anyway, I came to Emerald, hoping to get some of those porno mags you were asking about, so I could at least get a look at some pretty mares I could pretend might like me.”

She finished with one hind-leg, repositioning to sit alongside the other. I twitched a little when her hoof rubbed along the top of my inner thigh once more. “Anyway, I don’t think she was comfy with the idea of digging up some porn to sell to me, seeing as I was still a bit on the young side. I think she was overreacting a bit, but it turned out well enough. She got some trader to bring some fashion mags, and convinced me to take them instead. I figured, sure, why not? It’s still a bunch of pretty mares to look at. Except they also had some nice tips on how to get looking that pretty. So I started trying some of them. And you know what? I \textit{liked} it. Pretty soon, I’ve got my cutie mark, I’m strutting around feeling all pretty and happy, all of it.”

I gave a dry snicker. “So you’re saying we can blame Emerald for all this.”

Dazzle let out a loud laugh. “Hah! Yeah, I guess that’s one way of putting it! She seemed pretty happy with how things turned out, for sure.”

Her hooves slipped away from my ankles, then patted me on the flank. “Okay, let’s get you back in the shower. ‘Scuse us, Star.”

Starlight stepped out of the water, and I stepped in. Dazzle grabbed the second shower head and had me close my eyes before quickly working a bit more shampoo into the coat of my face, scrubbing, and rinsing it out again. Then she went to work washing out the rest of my coat, her hooves once again running all over my body as the water coursed over me. I was keenly aware of her body right up close to mine, just as soaking wet as I was under the shower’s stream.

I tensed up once again as she leaned in, her hooves once again scrubbing down my belly and between my legs, this time accompanied by the spray of water she angled in there. Once again, she kept the attention purely professional, scrubbing and rinsing without any special attention given, but she hardly needed to; it’s still a very delicate and sensitive area of the body to have another pony rubbing all over.

It was thankfully brief, and she moved on to scrubbing along my legs. It was then that I finally noticed that Starlight was very intently staring at a blank wall, away from us.

Dazzle’s hoof patted my flank again. “You go ahead and enjoy the shower, relax some.” Then she turned and stepped up to Starlight. “Okay, little Star. Your turn.”

She repeated the process with Starlight, her hooves scrubbing all over. I stayed under the stream of water, but my attention remained entirely focused on Dazzle. She practically hovered over Starlight, standing so close that they had to be brushing against each other, while her hooves explored all over Starlight’s body. The sultry look on Dazzle’s face didn’t help matters any, nor did the way she swayed her hips, or the way her tail was hiked just a little too high.

Dazzle gave the same warning she had given me. I could hear the sudden intake of breath from Starlight even over the shower, her cheeks flushing with color. Dazzle’s expression looked just a hair too smug for my liking, but she didn’t do anything explicit that I could have clearly objected to.

And then she was moving on, her hooves moving to Starlight’s flank, while Starlight tucked her tail between her legs.

\leavevmode\llap{“}So,” Dazzle said in a pleasant, conversational tone. “Are you two a couple?”

\leavevmode\llap{“}No,” Starlight huffed, then took a deep, calming breath. “I told you, I’m not into mares.”

\leavevmode\llap{“}Mmm-hmm,” Dazzle said, brushing Starlight’s tail out of the way to scrub down along her leg. Then she leaned in to speak almost conspiratorially, a motion which brought her head far too close to Starlight’s hips for my comfort. “I just couldn’t help noticing that Whisper is watching us like a jealous lover.”

Starlight glanced my way, while I frowned at Dazzle, which probably didn’t help that impression any.

\leavevmode\llap{“}We’re not lovers,” I said, firm and clear.

Dazzle chuckled softly as she continued scrubbing down Starlight’s legs. “Hey, a couple, ‘like sisters’, comrades in arms, unrequited lovers...” Her smile developed a hint of a smirk at that last one. “Whatever it is, you’re protective of her. I get it. And you don’t have to worry. I might be a shameless tease, but I’m not the type to take things too far.” She cast a sly smile my way. “\textit{Especially} not with a couple of dangerous mares like you.”

\leavevmode\llap{“}Dangerous?” Starlight asked, glancing back.

\leavevmode\llap{“}Mmm-hmm!” Dazzle hummed, the patted her on the flank. “Shower time.”

We swapped places, the conversation briefly on hold until Dazzle finished cleaning over Starlight’s face. When she finished, Starlight opened her eyes to find Dazzle’s face right in front of hers, the water flowing over her.

\leavevmode\llap{“}I saw that shot you popped off last time, when you were leaving town,” Dazzle said, her voice soft in what I could only describe as ‘seductive’; I realized I was glaring again. “You tagged a tree from across the valley. Must have been close to a mile, hmm?”

Starlight was blushing, her ears folding back. “Yeah. Maybe.”

Dazzle chuckled softly, slipping off to the side to start scrubbing again, and Starlight huffed out a near-silent sigh of relief.

\leavevmode\llap{“}Hell of a shot,” Dazzle said. “I mean, sure, I could have hit that tree too, but that’s because I’ve got a giant fuck-off cannon that fires half a dozen bolts per second of exploding magical fire. Give me a good long burst, sure, I’d hit that tree. I’d just blow up half the hillside in the process. But you?” She nudged Starlight’s side playfully. “Heck, I’m betting you could tag a raider right in the head at that range and not even singe the mane of the pretty mare standing next to him.”

Starlight was blushing again, though she replied with a modest, “Maybe.”

Dazzle chuckled, then leaned over Starlight’s back to look at me. “And then there’s you. Hoo, if even half the stories about you are true, you are one mare I do \textit{not} want to piss off.”

I had to fight against the tinge of adrenaline building in my gut to keep my expression neutral, my eyes fixed on her. “What sort of stories did you hear?”

Dazzle grinned at me. “Something about you leveling three city blocks and flying around on a minigun, all while taking out forty or fifty heavily-armed mercenaries.” She snickered a little, still eying me as she continued scrubbing. “Granted, most of this came from the unreliable lips of a very heavily drugged-out pony, but it got me curious just how much of that was true.”

I made a mental note to discuss information security with Sickle, as soon as I figured out how to do so without being maimed in the process. “There may have been some exaggeration involved.”

\leavevmode\llap{“}Oh, I figured,” Dazzle said, still scrubbing at Starlight’s side. “Like what?”

\leavevmode\llap{“}There weren’t forty or fifty mercenaries. It was about half that, thirty at the absolute most.” I caught the rise of her eyebrow and quickly added, “And it wasn’t all me! Dusty took out…” I thought back, tallying what I had seen. “...at least two? Oh! And the first four were all Dusty and Sickle.”

\leavevmode\llap{“}Ohhh,” Dazzle said with an exaggerated nod of her head. “So you only took out \textit{all but six} of the thirty mercenaries yourself.”

\leavevmode\llap{“}At least six,” I said, my voice gone quiet. “They might have gotten more.”

\leavevmode\llap{“}I don’t think we did,” Starlight said. I shot her a glance, but her eyes were closed.

I looked away again, grumbling. “It wasn’t nearly as impressive as it sounds.”

\leavevmode\llap{“}Uh-huh,” Dazzle said.

\leavevmode\llap{“}And it was three buildings, not three blocks, and one was really small. Maybe two and a half, the motel was partially collapsed already. Also, most of the supermarket is still there.” I just kept digging the hole deeper. “...And there was a minigun involved, but I most certainly wasn’t ‘flying around’ on it. I just kinda held down the trigger until it stopped...”

Dazzle was staring at me over Starlight’s back. There were a few seconds where the only sound was the water falling on them and the tile below. Then Dazzle laughed, resting a hoof on Starlight’s back. “Holy crap, it’s all true. Hah! And here I thought she was pulling my leg.” She resumed scrubbing, leaning in close to Starlight. “Sorry, little Star. I think I might be falling for your friend.”

While Starlight gave a surprised and concerned look her way, I gave a flat glare. Dazzle ignored both of our reaction, simply snickering as she continued to scrub.

The rest of the scrubbing went without incident, save for Starlight’s sharp intake of breath when Dazzle scrubbed between her legs again. A couple minutes later, Dazzle sat back to look between us. “So, that’s coats done. Now for the manes and tails.”

That went quicker, despite Dazzle’s pausing to admire my mane and tail while sitting right alongside me. And then there was the moment she started working the shampoo into the base of my tail, the underside of which was remarkably sensitive to having hooves pressing and rubbing all along it. I tensed up at her touch, but moments later she was working her way down my tail, and I slowly relaxed.

It went much quicker with Starlight, given the relative lengths of our manes and tails. She also gave a jerk and a sharp inhale of breath when Dazzle’s hoof slipped under her tail. My jaw tightened, but Dazzle was already speaking. “Sorry, Star, got to get this worked right into the base of the tail for it to do good.”

Starlight grunted out something quiet in reply and remained perfectly still as Dazzle worked her way down the short tail.

With that, we were done.

And then we got to do the whole process over again with conditioner.

Another go-around, with Dazzle’s wet body hovering close beside us in the comforting flow of warm water, her hooves roving over every single inch of our bodies. By the end, Starlight’s face seemed to be locked in ‘permanent blush’ mode, and she gave several deep huffs to calm her breathing. As for myself, I had to work at keeping a neutral expression, or at most, showing only a tiny bit of the irritation I felt. Dazzle didn’t have to do anything overt to make the whole scene exceptionally sensual, and I’m sure she knew it.

After what felt like an eternity, the shower was finally over. Dazzle turned off the water, which was starting to lose its warmth, and fetched three matching sets of towels. She insisted on helping us dry off, of course. Yet another excuse to rub her hooves all over Starlight and myself, though the towels at least gave some sense of a barrier.

Not that it helped too much when she got to drying certain parts.

Once the two of us were merely damp rather than soaking wet, she dried herself. Neither of us offered to help. In fact, Starlight was fixated on the wall once again, while Dazzle happily swayed her hips and hummed as she worked.

When she had finished, she tossed the towel aside with a playful flourish. “Now then, time for some trimming and grooming. Follow me!”

She led us out, strutting the whole way. Starlight spent the whole time staring down at her own hooves.

Our destination was a spare room beside the bathroom, with a couple of plush chairs, a pair of stools, and a few cabinets. Dazzle fetched a toolbox filled with scissors, files, brushes, and other grooming implements. “So, trimming. Either of you have any preferences? Any cute new mane or tail styles you’d like to try out? I could trim back your coat a bit if it’s been a bit too thick and warm, or even to adjust your contours.”

Starlight eventually settled on trimming her mane and tail just a little, since she thought it was growing out a little long, while I passed on the offer.

\leavevmode\llap{“}Normally I’d insist on at least trimming out any split ends,” Dazzle said with a playful smile, and ran a hoof along my mane. “But I think I’d have a hard time finding any.”

Then there was the grooming. Dazzle spent a good amount of time cooing over my mane and tail some more, even pausing at one point to simply run her hooves through my mane and admire how it fell across my shoulders. Grooming Starlight’s was quite brief by comparison, as it only took a couple passes of the brush to get the hairs in order, in what Dazzle described as, “Neat and playfully tousled.”

Grooming our coats seemed like another good excuse to rub all over us, though this time with a brush between her hoof and our body. At least she refrained from brushing over the most sensitive areas, as I’m sure even she recognized that such a harsh sensation would be counterproductive. I still kept a careful eye on her as she brushed the inside of Starlight’s thighs.

With that out of the way, she had us sit back in the more comfortable plush chairs, and started polishing our hooves. “You’ll want to keep up on hoof care,” she said as she filed one of Starlight’s hind hooves. “They’re a bit of a mess. Lots of digging through old ruins without any filing, I’m guessing?”

Starlight looked away, ears pinning back. “I try to take care of them.”

\leavevmode\llap{“}Well, you avoided any nasty cracks or the like, so I suppose you’ve done better than a lot of ponies.” Dazzle continued filing, slowly smoothing out the surface. “Just a little bit of care and the occasional polish should keep them in good shape.

When it was my turn, the tune was completely different. “Now your hooves, they are immaculate. I’d almost think you didn’t use them at all, if I didn’t know better. All they need is a little polish to be perfect!”

She had a few bottles of polish, and after joking around about a couple different colors, she gave our hooves a thin coating of a clear polish.

Starlight spent a few moments looking at her hooves with a mixture of uncertainty and admiration. I distantly noted that my own hooves were as smooth and glossy as my shell, something I had always liked about hooficures back in the old Equestria, but I pushed that thought to the back of my mind.

While Starlight admired her hooves, Dazzle moved on to her horn. As Starlight hadn’t the slightest clue about horn fashion, they eventually settled on simply smoothing the surface nice and even, rather than getting fancy about tip and groove shape.

Once the hoof polish had dried, Dazzle brought in a pair of shallow bins filled with heated water. She had us soak our hooves for a couple minutes, then led us through the back door of the room.

That led us into her makeshift sauna. It was a cramped space, with just enough room for the ring of three small single-pony benches and the pile of large rocks in the center, which radiated a powerful heat throughout the room. I could hear the generator a little more clearly, no doubt powering whatever it was that heated those rocks.

\leavevmode\llap{“}Take a seat and relax,” Dazzle said with a smile. “We’ll do a few rounds here, about fifteen minutes each. If you start feeling dizzy or uncomfortable, come on out and cool down. There’s some bottles of water under the bench to pour over the stones if it’s too dry for you, and I’ll have cold ones outside for you. Anything else I can get for you while you’re here?”

She said that last bit with a subtle sway of her hips that I’m sure was supposed to be suggestive. “We’re good,” I said.

\leavevmode\llap{“}Okay, then!” she said, turning around to step out. It made for an even more suggestive pose as she turned to speak over her shoulder. “See you in fifteen!”

The door shut, leaving us alone for the moment.

While I settled down on one bench, Starlight flopped down on the next, groaning softly.

\leavevmode\llap{“}Feeling relaxed yet?” I asked, dryly.

\leavevmode\llap{“}More like exhausted,” Starlight replied, slowly rolling over onto her back. Once there, she lifted a hoof again, looking at the fine polish. “I didn’t expect it to be quite so… much.”

\leavevmode\llap{“}We can always leave.”

She sighed, lowering her hoof. “...Nah. Might as well finish this. I mean, we’re almost done, right?”

\leavevmode\llap{“}There’s still the massage. Another chance for Dazzle to run her hooves all over you.”

Starlight grimaced. After a couple seconds of silence, she flipped over to lie on her belly. “Well she better not try to massage… \textit{there}, or I \textit{will} kick her.”

I gave an unamused snicker. “Me too.”

\leavevmode\llap{“}Good,” she said, chuckling a little as she fidgeted around a bit to get comfy. After she finally settled into place, she laid down her head, groaning softly. “It’s way too hot in here.”

\leavevmode\llap{“}I’m afraid that’s the point of a sauna,” I said, closing my eyes as I relaxed. “I think the old saunas were a little hotter than this, even.

Starlight merely grunted in reply, already breathing a bit more heavily.

It seemed like hardly any time had passed before Dazzle was back. “Okay, that should be good enough for this round,” she said as she stepped through the doorway. “Let’s get you some air and cooled down, hmm?”

She led us back to the shower and turned it on, and we both crowded under the welcome flow of chilly water. Starlight gasped out at first, but was soon practically dancing around as she turned this way and that beside me, eyes closed and repeatedly bumping into me as she enjoyed the feeling of the cool water running over her. As nice as it was, though, I couldn’t help but note that Dazzle was standing nearby, watching the pair of us with interest.

Once the feel of the water had turned from “refreshingly cool” to “rather chilly”, Dazzle turned off the water. She fetched the bins, which had been refilled with warm water, and had us stand in them as she quickly toweled away most of the water. At least it was brief. Starlight hardly even reacted to the attention, her eyes closed throughout, merely giving a faint huff and lifting a hind-leg just a hair to let Dazzle finish a little quicker.

Then it was back into the sauna.

We repeated the cycle two more times. By the end of the third, I was feeling almost dead on my hooves, with my body so relaxed that I felt like I might collapse if I didn’t focus on staying upright. Starlight looked to be in the same condition, her head hanging low and eyes closed.

It was in that state that Dazzle led us out and into another room. “Hop on up,” Dazzle said to us with a smile.

I was feeling so lethargic that it was only then that I noticed the giant bed, large enough for one of the princesses, and probably a couple suitors as well. “...Why are we in your bedroom?”

Starlight stopped and looked down, having already placed her forehooves on the bed before realizing where we were.

Dazzle’s smile grew. “Because I haven’t been able to scrounge up any massage tables yet, and this is more comfortable than the floor.” When I continued to frown, she rolled her eyes. “No funny business, I know. I’m just working with what I’ve got, here.”

Starlight had finished climbing up and lying down, so I relented. “Fine,” I said, stepping up to lie beside her. I sank into the mattress, which was more worn-out than soft, but otherwise in remarkably good condition given its age.

\leavevmode\llap{“}Just relax,” Dazzle said as she climbed onto the bed beside me, her hooves moving to my shoulders. She pressed and rubbed, squishing the flaccid flesh against the hard, interlinking structure of bones beneath in a way that was simultaneously disconcerting and strangely soothing.

She had to pause to remind me to relax several times as her hooves worked over my body. I closed my eyes, and tried my best to do so, which was usually followed by her asking me to relax once more. It became particularly difficult when her hooves made their way over my hips, massaging my rump. She had just moved her hooves to massage down my legs, with one rubbing firmly over my inner thigh, when she snickered softly. “You must be really enjoying this to have your tail lifted \textit{that} high.”

My eyes snapped open, my tail jerking down again. “That is a natural reflexive reaction to the manual stimulation of an erogenous zone,” I said, remaining as still as possible. “It doesn’t mean anything more significant than that.”

\leavevmode\llap{“}Mmm.” She continued to work her way along my leg. “So I know little Star’s off-limits. What about you?”

I grumbled, closing my eyes again. “It’s not going to happen.”

\leavevmode\llap{“}Aww,” she said in a mock-hurt tone. “I suppose you’re not into mares either, hmm?”

\leavevmode\llap{“}Mares are fine. It’s still not going to happen.”

\leavevmode\llap{“}Can I ask why?”

I fought back the urge to snap at her, and instead kept my voice calm and level. “Because you hardly know us, yet you immediately slept with Sickle, relentlessly pursued Starlight, and then turned to me when that didn’t work. None of that would have been a big deal, except you pressured Starlight into coming here just so you could rub your hooves all over her, all with the hopes that you’d get her so worked up that she’d give in and have sex with you, against her better judgment and despite her repeated rejections. You’re trying to \textit{manipulate} her into having sex rather than \textit{convincing} her, and I don’t appreciate anypony trying to manipulate my friends.”

And no, that’s not hypocritical, except in the most casual reading of that statement.

Dazzle’s hooves froze for an instant, then resumed their work, a little slower and softer. “...Yeah,” Dazzle said, her voice quiet and low. “Sorry.”

I have to admit, not arguing it might have bumped her up a step in my opinion. Not that I was going to let her off entirely easy for a momentary change of heart. “I’m not the only one you need to apologize to.”

\leavevmode\llap{“}Sorry,” she repeated, and I cracked an eye open to see Starlight’s eyes were barely open, looking a little thoughtful and a little concerned, but mostly looking as if she were about to drift off to sleep.

Dazzle sighed as she continued her massage, moving to the other leg. “The thing is, I kind of have to move fast. I love this town, but ponies only come here for some quick trade or a new weapon. I get a day or two to make some sort of impression, then they’re gone again. It’s either come on strong, or don’t even get noticed.”

I frowned a little at the sudden change in tone, mentally chewing that over as she worked down my leg. After the experience so far, I was sorely tempted to just tell her off, but I didn’t. Maybe the massage was just that relaxing. “What is it you’re looking for, exactly?”

Her hooves paused without answering, so I clarified my question. “Are you looking for casual sex? A long-term relationship? Something in between?”

She gave a soft snort of amusement. “Hell, I’d settle for some casual sex every now and then,” she said, resuming the massage. “But something more would be… nice. Very nice.”

\leavevmode\llap{“}Then a little advice: manipulation and tricks might get you something short-term, but it’s very likely to be destructive to the kind of trust you’ll need for anything longer. Pressuring somepony into something they don’t want to do is more likely to just hurt them.” My eye opened again, head lifting just enough to look back over my shoulder. “And if there’s one thing I like less than somepony manipulating my friends, it’s somepony \textit{hurting} them.”

She looked down at her work, not meeting my eyes.

My point made, I laid my head down and closed my eyes again. “If you want something longer, put some effort into knowing a pony first. Know what they like, and give them a reason to like you. With the effort you’ve put into your appearance, I’m sure you can appreciate that. And if you absolutely have to go for casual sex, at least stick to flirting to seduce a pony, instead of pressuring them. You’re less likely to make them regret the time spent with you.

\leavevmode\llap{“}And yes, it’ll take some time and effort, but it sounds like Emerald has made quite a few friends among visitors. There must be a fair number who stop in regularly. There must also be a few ponies who stay longer than just a day. We’re planning to be here a whole week, for that matter.”

\leavevmode\llap{“}Easier said than done,” she said, finishing with my ankle. I felt the bed shift as she sat back. “Wish I’d known you were in town longer. I don’t suppose you’re saying that because I still have a shot, are you?”

I gave a soft snort. “I won’t lie; you made a horrible first impression, and I’ll remember it. I’ll probably be suspicious of anything you do around Starlight or myself, but I know better than most that first impressions can be inaccurate. I don’t foresee anything working out between us, for reasons you wouldn’t even imagine, but I won’t stop you from trying. Maybe the whole Kindness and Generosity thing is rubbing off a bit.”

Or maybe I just don’t like to burn bridges when I don’t have to, even when the bridge is already soaked in oil and I have magical fire just a single thought away.

She huffed out a quiet chuckle. “Shit. Emerald really was right about you. You really are one of the good ones. Most ponies probably would have just stormed off instead of giving me pointers and another chance.”

I shrugged. “I try.”

\leavevmode\llap{“}More than most ponies do,” Dazzle said. The bed shifted again as she moved up between Starlight and myself. “Question is, how good \textit{are} you? You’re not going to shoot me if I try flirting with you, are you?”

\leavevmode\llap{“}Seems like a bit of an over-reaction. Maybe a swift buck if you’re planting hooves where they don’t belong.”

\leavevmode\llap{“}Noted,” she said, with a soft chuckle. A bit of humor was returning to her voice. “So, should I take that to mean you won’t shoot me if I flirt with little Star, here?”

\leavevmode\llap{“}Now that’s entirely up to her, isn’t it? Starlight can take care of herself.” I gave a hint of a smile. “So not unless she asks me to.”

\leavevmode\llap{“}Tempting,” Starlight murmured.

\leavevmode\llap{“}Aw, don’t be like that,” Dazzle said, and I could practically hear the smile in her voice. “You haven’t even experienced one of my massages, yet.”

Starlight snorted faintly, while the bed shifted with Dazzle’s movements. She settled in a moment later, followed by the slow, rhythmic motions of the massage. Starlight grunted faintly with the first one. Then she groaned, quietly at first, and growing in volume as the massage continued, with the occasional murmur of what might have been obscenities behind them.

While I was fairly sure Dazzle wouldn’t have tried something too direct immediately after the exchange we just had, I still cracked open an eye to look. Sure enough, Starlight was sprawled out, groaning happily as Dazzle’s hooves massaged down her back. Dazzle’s smile grew as she worked her way down, and was just starting to massage Starlight’s rump when she paused. “You know, it’s really hard to resist teasing you when you’re moaning into my bedding with your tail up in the air.”

Said tail immediately snapped down, and Starlight’s face flushed again. “Well you just keep on resisting,” she said, sounding a bit short of breath. “It’s not going to work, anyway.”

\leavevmode\llap{“}Mmm,” was all Dazzle said in reply, though she resumed her massage. Starlight’s blush grew as the hooves worked down over her rear and thighs, her breathing growing just a bit faster in response to the physical stimulation.

A minute later, we were done. Dazzle brought out the brushes again, giving us one final brush down. I felt so relaxed and tired that I might have fallen asleep, except for the desire to keep an eye on Dazzle.

When that was done, she sat back, smiling. “Well, as much as I’d love to have a pair of beautiful mares spending the night in my bed, I’m sure you’ve got your own beds to get to.”

Starlight made some mumbled, wordless reply before pushing herself up. “Yeah, we should go,” she said, still sounding a bit short of breath.

\leavevmode\llap{“}Well, come on,” Dazzle said, smiling. “I’ll lead you out.”

There was less of a strut to Dazzle’s walk as she led us back to our possessions. Starlight had just locked her PipBuck back in place on her leg when her ears shot up. “How is it that late already?”

\leavevmode\llap{“}Time flies when you’re having fun?” Dazzle said, leaning against the doorframe. “Beauty takes time.”

\leavevmode\llap{“}Did I fall asleep in there or something?” Starlight shook her head, slipping on her bags. “I didn’t think it was that long.”

Sure enough, when Dazzle led us to the front door, the sky was rapidly darkening with the onset of night. She lingered at the door for a minute as we walked away, watching us go.

\leavevmode\llap{“}Oof,” Starlight said, once we had gone far enough to speak freely. “So that was a little… intense.”

\leavevmode\llap{“}I’m not normally the type to say ‘I told you so’...”

\leavevmode\llap{“}Yeah, yeah,” Starlight said with a weak chuckle. “Still, it was nice. I don’t think I’ve felt this good in… ever.” She smiled, though I caught the hint of a shiver go through her. Arousal has a way of leading ponies into situations they would normally avoid, and I was pretty sure Dazzle knew it.

\leavevmode\llap{“}She was probably counting on that.”

\leavevmode\llap{“}Yeah, probably,” Starlight said, casting a glance over her shoulder, and shivered again. “It still ain’t happening.”

Given her reaction, I had to suspect it might have, had I not been there. I don’t mean to sound like I’m disrespecting Starlight, or that I think she can’t stand up for herself. It’s simply that I know quite well how even a strong-willed pony can be manipulated.

Emerald was reading an old house-care magazine when we returned, and we exchanged brief pleasantries before heading up to our suite. The massage had loosened up things in that strange way they did for ponies and other weird endoskeletal creatures, making my body feel so wonderfully relaxed, but also strangely heavy and even more alien than usual.

So I just went straight to bed, dropping my saddlebags and holster beside the bed, with hardly even a thought towards how the latter had become part of my “walking around town” apparel. Then I slipped into bed. Starlight followed moments later. I only vaguely remember her fidgeting about to get comfortable before I drifted off to sleep.

{\br}%
I woke to find that I was oddly chilly. Not outright cold, per se, but certainly cooler than I would have preferred. The reason, I discovered on opening my bleary eyes, was that I had only a small corner of the blanket draped across my side. Turning my head further, I found where the rest had gone; Starlight was tangled up in the blanket, most of which had ended up in a bundle with her legs wrapped around it.

I gave my corner of the blanket a light tug, but she simply pulled the blankets in tighter, murmuring faintly. I released, and the corner slowly slid from my side.

Sighing, I took that as a sign to get up. I gave a long, slow stretch—my body really did feel much better—before sliding out of bed.

The motion finally woke Starlight, who groaned softly into the blankets, moving around a bit before lifting her head and looking over her shoulder. Then she made a sound that roughly approximated, “Good morning.”

\leavevmode\llap{“}Good morning,” I echoed back, much more clearly. “Should I be getting us a second blanket?”

She blinked a couple times before fully processing what I had asked. Then a hint of a blush touched her cheeks, and she kicked her legs, quickly disentangling herself and spreading out the blanket again. “Sorry. I, uh… didn’t sleep very well last night.”

\leavevmode\llap{“}Maybe you should try getting some more sleep,” I said. “We don’t have anything going on, today.”

She hesitated for a moment, then grunted and kicked off the blankets. “No, I should get up,” she said, quickly rolling off the edge of the bed and onto her hooves. “I mean, I don’t want to spend all day in bed, after all.” She stood stiffly, her expression a little too tight.

I cocked an eyebrow. “Are you bothered about how last night went?”

\leavevmode\llap{“}What? No!” she quickly replied. “Dazzle will have to work a lot harder to bother me.”

I blinked, then opened my mouth to speak again, but she cut me off. “We should get breakfast! I’m hungry.”

She turned and walked briskly to the door, and I couldn’t help but note that she was keeping her tail tucked low between her legs. Not bothered, indeed.

Dusty looked up from a book as we entered, and smiled. “Morning.” He gestured with a hoof to the table, where an ancient coffee pot sat beside a plate with a few carrots and apples. “Emerald made coffee and insisted on sharing. Should still be hot.”

Starlight descended on the food with a passion, while I took a somewhat more leisurely pace. I even had some of the coffee; I don’t normally care for the taste, but a bit of caffeine was sounding like a good idea.

As I sat back with a carrot and a well-worn mug of lukewarm coffee, I looked down at the book Dusty held. “What’s that?”

\leavevmode\llap{“}Some war story Emerald rented to me for a cap,” he replied. “A special team goes into the Zebra lands to assassinate their Caesar and end the war.”

I gave a dry chuckle. “So it’s fiction, I see. Is it any good?”

\leavevmode\llap{“}It’s entertaining enough,” Dusty said. “Just as long as I overlook how the combat is basically nonsense.”

I smiled. “Speaking of which, are you still willing to go shooting today?”

He nodded. “Sure. Just say when.”

I tipped back the cup, draining it dry. “How about now?”

He shrugged. “Let me get to the end of the chapter, then sure.”

Starlight looked up from the apple she was halfway through. “Hehh, hoo—” She paused, swallowed an overly large bite, and tried again. “Hey, you mind if I tag along?”

\leavevmode\llap{“}It’s not like you need my permission to use Arclight’s range,” Dusty said with a chuckle. “But sure, might as well make it a party.”

We set out shortly, after we had gathered a small collection of weapons, ammunition, and equipment. Dusty purchased a set of earplugs for both Starlight and myself, and then led us back to our wagon.

When we arrived, we found Sickle, her shoulders wedged under the wagon as she did push-ups, lifting the whole vehicle, cargo and all, with each repetition.

Starlight was, naturally, the first to speak upon seeing the odd scene. “Sickle, what the hell are you doing?”

Sickle paused, her chin nearly touching the ground. “The fuck does it look like I’m doing?”

\leavevmode\llap{“}Uhhh…”

Sickle blinked. “...I’m exercising.” She pushed herself up again, the contents of the wagon rattling. “Ain’t been going around in my armor and hauling shit all the time. Got to do something to keep in shape.” She sneered a bit as she lowered and pushed herself up again. “What, you think I got this big lying around and fucking all the time?”

Starlight frowned. “I just thought it was the Buck.”

\leavevmode\llap{“}Eh, sure, that helps,” Sickle said with a shrug that shook the wagon.

Dusty stepped up beside the wagon. “Think you could stop for a second? We need to get some stuff.”

She didn’t stop. “So get the stuff. Ain’t like I can’t lift your ass, too.”

Dusty sighed, then grabbed the edge of the wagon and hauled himself up. The extra weight seemed to mean nothing to Sickle.

He balanced atop the wagon with remarkable ease as he dug through the equipment within, and eventually hopped down with three of the suppressors he had acquired in the hive. Two went into his bags, while the last, one of the two smaller ones, he held out to me.

I took it, though I gave him a questioning look. “You know I don’t have subsonic ammunition for my rifle, right?”

\leavevmode\llap{“}They’re still useful, for lots of reasons” he said, closing the flap of his bag and motioning for us to follow. “But today, the only reason that matters is that it’s easier on the ears.”

We made our way to the range, and after Dusty and I fixed the suppressors to our rifles, started shooting.

Starlight went at it with a gusto, popping pieces of scrap, old cans, and broken bottles with her weapons. She even spent a while with both weapons out, giggling as she used her targeting spell to employ them simultaneously against multiple targets. Dusty was a good deal slower and more methodical, first spending some time carefully tuning the pair of rifles he had brought—the older, heavier rifle, and an assault rifle like my own—before going for a more combat-style shoot, where he rapidly engaged multiple targets, placing two rounds on-target before switching to the next. Each shot still produced the sharp crack of the bullet flying downrange, but between the earplugs and the suppressor, even his heavy rifle had lost its ear-pounding bark.

As for myself? Well, I mostly missed a lot. After my third shot missed a stationary bottle halfway across the small field, I looked over to Dusty. “Think you could give me some pointers, here? I feel like I’m doing something wrong.”

\leavevmode\llap{“}We’re not teaching today,” he said, peering down his sights as he made a tiny adjustment. “This is just for fun.”

\leavevmode\llap{“}It’d be a lot more fun if I could hit anything,” I said, laying the bitterness on a bit thick. “I’m not even sure if the sights on this thing are accurate.”

He considered that for a moment before offering to give my weapon a try. I hoofed it over, and he took the bit. “Hmm,” he said, staring down the sights for a moment. “Well, you’ve got the sights set to three hundred yards and you’re shooting about fifty, but that should only put you a couple inches high. Firing.”

A moment later, the rifle cracked, and the bottle went tumbling, the upper half of it vanishing in a burst of glass shards.

\leavevmode\llap{“}Yeah, a couple inches at most,” Dusty said, then shifted his aim. He fired another three times, kicking up a thin cloud of dirt behind a board sticking out of the ground. Setting my rifle down, he lifted his binoculars to look closer at his work. “Yep. Sights are good. Holds a decent pattern, too.”

He picked up my rifle again and passed it back to me. “Just take your time. If you want to get used to aiming it, shoot one of those boards out there. Pick a clear mark to aim at, fire a few rounds, then glass it to see where they land.”

\leavevmode\llap{“}Okay,” I said, taking the bit in my mouth and squeezing the stock against my shoulders. I leaned in, peering through the rear sight to line up the front, then lined the front sight up on the same mark he had been shooting. I tongued the trigger, and the rifle made its strangely muted clack-crack as a puff of dirt boiled up from behind the board.

\leavevmode\llap{“}A couple more,” Dusty said, looking through his binoculars. I fired twice more, taking my time. When I had finished, he nodded. “Not bad.”

I grabbed my binoculars and peered through them. While I could see some of the holes unaided, it gave me a much better picture of my accuracy which, as expected, was not terribly good. A small X was painted in near the middle of the board. A couple inches above that was a jagged and uneven hole that I could see easily without the binoculars, but which I could now see were likely the result of Dusty’s three rounds striking at nearly the same point. A couple smaller holes were scattered loosely above that, just a couple inches higher, and a third hole pierced the board a good six inches off to the side.

I lowered my binoculars. “Not bad? I’d hate to see what you \textit{would} count as bad.”

\leavevmode\llap{“}Oh, we’ve got some work ahead of us,” Dusty said, the corner of his mouth inching upward. “But you put every round on the board, almost held a pattern, and didn’t shoot yourself, so you’re already above average for a beginner. Plus you keep your eyes open when you shoot.”

I quirked an eyebrow questioningly at him, but he merely gestured out toward the field again. “Enough lessons for now. Go on.” He flashed a smile and turned back to his own weapons.

I settled into shooting, firing a few rounds before looking through my binoculars to get a good idea of where I was hitting. Slowly, the holes drifted more reliably together. When I started on the second magazine, I even adjusted the range on my sights. When I found that they only went down to one hundred yards, I switched to shooting the distant line of targets, set at about that distance.

My last ten rounds all landed in a pattern just about the size of my head, with a single stray off to the side. I smiled as I scoped it out, a small bit of pride building within me; I was making progress.

I’d never really understood why ponies might find firing off guns at inanimate objects for no discernible purpose to be an engaging form of entertainment, yet there I was.

Starlight was giddy the whole way back to the inn, thoroughly enthused by the experience with her targeting spell, and retelling several of the fancier tricks as if we hadn’t been there to see them. Dusty remained relatively quiet, though he wore a faint smile. It further amused me to reflect on that, and just how much the social dynamic had changed between those two. I might even go so far as to call them friends.

Emerald was distracted by a merchant who had just arrived in town, so we simply waved and headed up to our room.

As we climbed the stairs, Dusty asked us, “What are you planning to do with the rest of the day?”

While Starlight shrugged, I replied, “I think I’ll sit down with my mother’s data-store and see if I can recover anything. I should have the tools for it, now.”

Dusty’s smile slipped. “I’m not sure if you’re getting the idea of relaxing and having fun.”

\leavevmode\llap{“}What?” I said, frowning at him. “Working with computers is fun.”

It would also be a productive use of my time, but I figured that reasoning wouldn’t carry much weight at the moment.

\leavevmode\llap{“}If you say so,” he said, his tone full of doubt. “Just remember, we’re supposed to be relaxing.”

\leavevmode\llap{“}I’m going to be kicked back in bed, playing with a digital puzzle,” I said, smiling again to sell the story. “It’ll be plenty relaxing.”

He huffed out faint chuckle, but didn’t object.

So when I got back to my room, I pulled out one of the new terminals from the hive and its collection of software tools, and the data-store my queen had left behind. I set them on the bed, lying out as I hooked things up.

Starlight came in, as well. “I think I’ll kick back and read some,” she said, lifting her PipBuck. “Maybe listen to some music. You don’t mind, do you?”

\leavevmode\llap{“}Of course not,” I said, connecting the old data-store. A data-backup tool made copying over the corrupted contents quick and easy.

Starlight laid out on the end of the bed. “That was fun,” she said, flashing a smile my way. “Looked like you were enjoying it, too.”

I nodded. “I feel a little less useless, too,” I said. The transfer completed in only a few seconds; there wasn’t much there.

\leavevmode\llap{“}Hey, you’re certainly not useless.” She laughed as she pulled out a set of earbuds. “Hell, you kicked some serious flank in Mareford.”

\leavevmode\llap{“}Sneaky I can do.” The size of the data-store’s contents might have been a huge number of text files, or perhaps a single audio log. I was hoping for the latter, and with the context of why the device had been left behind, it seemed the likely answer.

Starlight inserted one of the earbuds, then paused. “So, um… I was wondering something.”

\leavevmode\llap{“}Yeah?” The data-recovery tool loaded, slowly displaying what it could make of the corrupted file structure.

\leavevmode\llap{“}Well, you feed—” she paused, glancing toward the door, then spoke again in a quieter tone. “You feed on love. So, uh, does ‘making love’ actually, you know, \textit{make} love?”

I blinked and looked up from my terminal. I was rather concerned about why she would ask a question like that, but my immediate response was, simply, “What?”

\leavevmode\llap{“}It’s just that Dazzle seems to have an interest in you,” Starlight quickly explained, gesturing with one of her hooves in the general direction of the gate. “And I know you need love to survive, and have been pretty hungry at times, and… well, I know you were getting a bit angry with her, but then you let her off easy, and I was just wondering if that might, you know, be able to help you.”

I relaxed and chuckled. “Thank you for the concern, but you don’t have to worry. I’m getting enough from you and the others to keep myself healthy.”

\leavevmode\llap{“}Oh, okay.” She nodded. “Good.”

\leavevmode\llap{“}In any case, it doesn’t quite work that way. ‘Making love’ is just a euphemism. Sex doesn’t produce love.” I shrugged. “Not in itself, anyway. It can be a very useful tool for manipulating ponies, including in ways that could develop further affection, but I never had a use for that.”

She tilted her head ever so slightly. “Why’s that?”

\leavevmode\llap{“}Because I don’t like manipulating ponies.” I smiled. “Sure, I’ll do it when it’s necessary, but remember, I was a love collector. I gathered food for the hive. Most of the ponies I interacted with were regular folks. I didn’t need to use sex or any other manipulation to build affection. I just made friends.” I paused, then chuckled softly. “It could possibly be useful to \textit{maintain} a relationship, though. Or further one.”

\leavevmode\llap{“}Oh. Did you, uh… made use of that?”

I paused, considering her for a moment, but honesty still seemed the best policy. “There were a few times relationships developed to that point,” I said, though my ears drooped a bit as I said it. “I tried to avoid it, though. Ponies tend to associate intercourse with strong attachments, which I tried to avoid. I might be recalled or reassigned, and I didn’t want to hurt somepony by suddenly breaking off a relationship that they felt strongly about. It was easier if it never got to that point.”

Her ears perked up, curious. “Even if it would get you more love? I mean, it would, right?”

\leavevmode\llap{“}Sure,” I said, nodding a little. “But I could get enough without it. It was better for everyone, that way.”

\leavevmode\llap{“}But you still… \textit{did} with some of them?”

\leavevmode\llap{“}On occasion.”

She stared at me, expectantly. I held out for several seconds before giving in with a sigh.

\leavevmode\llap{“}Well, there was Lucky. That was a mistake, for all the reasons I just gave. I thought he wouldn’t attribute too much significance to intimacy, but he did. I tried to ease things down, but it just soured things between us. On the other hoof, there was Tumbleweed. Heh, even he joked that he was the dumbest stallion in all of Appleloosa, but that wasn’t fair. He wasn’t book-smart at all, but he was clever enough, and probably the nicest and most genuine pony in that town. I… think he was the only one who really knew I could never be anything more than a good friend, but he was okay with that. Even after he married Mayflower, we remained close.

\leavevmode\llap{“}And then there was Sweet Treat.” I smiled. “She was one of the most flirtatious and playful ponies in town, though much more selective than some ponies asserted. We were best friends, and had very similar outlooks on intimacy. There were no complications, there. She reminded me of Desire, which I think is what first caught my attention.”

\leavevmode\llap{“}Because she reminded you of Desire?”

\leavevmode\llap{“}Yeah,” I said, chuckling a little. “Desire was always the flirtatious one. Very friendly and playful. Think of Dazzle, only much more talented.”

Starlight grimaced. “Ugh. I hope she wasn’t \textit{really} like Dazzle, because…”

\leavevmode\llap{“}I only mean superficially,” I said, smiling. “Dazzle is flirtatious, but she’s a bit blunt about it. Desire, though? She was a natural at appealing to a pony’s desires.”

\leavevmode\llap{“}So… she was good, huh?”

\leavevmode\llap{“}Oh, yes,” I said, nodding. “I didn’t see her work out in the field, of course, but I saw plenty during training. She knew better than to pursue things too aggressively with someone she wanted to seduce, like Dazzle was doing. She could tease just enough to put you off-balance and get you excited, but could keep things subtle and slow enough that you’d feel comfortable with every single move she made. She’d make Dazzle’s shower and massage look amateur.”

\leavevmode\llap{“}Huh.” Starlight was staring off into space, and I caught her shifting her position slightly, her tail curling in close alongside her. It wasn’t hard to see where the conversation was taking her mind, so I quickly moved on.

\leavevmode\llap{“}I was always more like Shadow, though. Or Ripple. We were the quiet ones of the group. Subtle, I suppose. Shadow was much sneakier than me, though. I don’t have a clue what they had her doing, but I’m sure she excelled at it.”

Starlight’s eyes refocused as she shifted her position again, taking advantage of the distraction to further change the subject. “So, did you have a lot of pony friends?”

\leavevmode\llap{“}Yes,” I said, and gave a little chuckle. “Enough that it was practically a full-time job to keep up with all of them.”

She nodded slowly. “...How come you never talk about any of them?”

My smile slowly faded. The question hung in the air for several long seconds before I quietly replied.

\leavevmode\llap{“}Just over a month ago, I helped throw Meadowlark’s twenty-fifth birthday party. The week before that was a foal shower for Tumbleweed and Mayflower. Then there were the dinners with Legerdemane and Marblehoof, and my weekend vacation to Manehattan with Sweet Treat.” I slowly shook my head. “Then I wake up here, and they’ve all been dead for two hundred years…”

Starlight’s expression wilted. “I’m sorry.”

\leavevmode\llap{“}It’s not your fault,” I said, then quickly added, “Thank you.”

She looked down at her hooves, chewing on her lip.

After a moment of silence, I touched my portable terminal. “I should really get to work on this.”

\leavevmode\llap{“}Oh. Yeah. I guess so.” She gave an awkward smile, and after a moment, turned back to her PipBuck, slipping an earbud into her ear.

I drew in a deep breath, sighed, and returned to my work.

The copied contents still sat there, unreadable. The data-recovery tool was unable to make heads or tails of the file or files.

That didn’t surprise me. Whatever was there was almost certainly encrypted, which would complicate data retrieval. The plus side was that the encryption was almost certainly one of the more commonly known methods the hive used, to ensure we could reveal her message.

I spent a while messing with the various software tools in an attempt to find an easy solution, but none of them were able to produce anything significant, except to finally single out the actual data from the damaged spell matrix that contained it. A quickly written script iterated through various ciphers and keys, outputting a new file for each one in the hopes that one of them would decode into a meaningful file.

Slowly, meaningless jumbles of random values filled the output directory.

And then one of the files resolved as a valid audio file.

I stared, my ears standing on alert as a hint of adrenaline burned in my gut. Starlight noticed my reaction, removing one of her earbuds and looking at me with a concerned expression.

I took a slow breath. “I… think it might have worked.”

Starlight’s ears perked, and she sat up.

I stared down at the portable terminal, the audio file highlighted, waiting for me. I took a slow, deep breath, turned on the speakers at a low volume, and pressed play. The sound from the speaker was marred by the occasional bit of static or squelch of distortion, but none of that could hide the beautiful, melodious voice of Queen Ephema.

\terminal{
\textit{Hello, my children.}

\textit{I am sorry I can not be there for you. The chrysalis that had protected me has failed. I can only assume from the good condition of the others that my body had put greater demands upon it, and that this has led to its failure. As I look at you all, sleeping peacefully, I at least can take some comfort that you are safe and healthy.}

\textit{I cannot open the door. Even if I were able to override the lockdown, I could not. The terminal here tells me troubling things. I find it hard to believe that eighty years could have passed, all in a single, dreamless sleep. I never imagined this endeavor would have lasted this long, but it seems it must continue even longer. According to the terminal, the outside world is poison.}

\textit{If I stay here, I will slowly starve, but if I open the door, we will all die. I can’t do that. As your Queen, my greatest duty must be to the well-being of our hive, even if that means sacrificing my own life so that others may survive.}

\textit{Please, do not mourn me. My choice, as ever, is made for the good of the hive. The hive needs you, now, more than it needs me.}

\textit{As sad as I am to know I will never see you again, I can feel only pride as I look upon you now. Our home is gone, lost to the balefire that has consumed the world, but our hive is more than a hole in the ground. It lives on in you.}

\textit{Gossamer. Trickle. Whisper. Slab. Bolt. Surge. Midnight. Aegis. Slip.}

\textit{The task ahead of you is great, but I trust in you. You are all here because you are the greatest, the most capable that our hive has to offer. You will lead the hive into the future. For you, I leave all the love I still hold. Take it. Find your sisters. Ensure that our hive lives on.}

\textit{I love you all. Goodbye.}
}

The recording clicked off, and I heaved a deep, shuddering breath. Tears were running down my cheek, but I found myself smiling.

Starlight scooted up close beside me, a foreleg slipping around my shoulders to give a gentle squeeze. As I reached out to tenderly brush a hoof along the portable terminal, she said, “She sounds nice.”

My first attempt to speak made a sound halfway between a sob and a chuckle. My second attempt was a little more coherent. “She was. I was afraid I’d never get to hear her voice again.”

\leavevmode\llap{“}Yeah,” Starlight said, softly. “It helps.”

I leaned into her, and while I had to wipe the tears from my cheek, my smile grew a little more. “Yeah.”

She gave another gentle squeeze. “You okay?”

I sniffled, but nodded. “Yes. This… this is good.” I looked at the terminal for a moment. “...And I was right. I have a purpose.”

\leavevmode\llap{“}And we’ll do everything we can to help you,” Starlight said, offering a soft smile.

\leavevmode\llap{“}Thank you,” I said, my voice cracking.

\leavevmode\llap{“}And, um… if you ever need to talk about any of this stuff, you know…”

I gave a weak chuckle. “I wouldn’t even know where to start.”

She thought for a moment. “Well… maybe tell me more about your sisters? Or your friends?”

I swallowed, hesitant, but nodded. “Okay.”

{\br}%
We managed to talk about mostly nothing for the rest of the evening. Mostly, it was about the regular, day-to-day life in Appleloosa. To me, it was completely mundane; the simple job of keeping shipping records, the work involved in moving from my original apartment into a small house, and the myriad little stories of my interactions with the other ponies in the town.

Mundane to me, but practically alien to Starlight. She threw in her own contrasting stories, and while she and her mother had technically had a small house on the edge of a small village near the Dodge City ruins, they had really lived in the burned-out buildings and ancient facilities they scavenged, and the rolling hills and deserts they had hunted. While my life had been all about social interaction and paperwork, theirs had been a regular search for survival.

Most of our conversation was spent at Pumpkin’s place, enjoying a nice dinner, even though we had to speak quietly when discussing certain things.

Dazzle approached us at one point with a flirtatious greeting, but Starlight very politely informed her that we needed some privacy. To Dazzle’s credit, she accepted it without any argument, and only a little hint of flirting when she promised to catch up with us later.

It was getting dark when we returned to our suite again. Sickle had returned, to Dusty’s apparent dismay. He was sitting at the table, his half-finished book set before him. More than a dozen bottles of various types decorated the table, half of which were empty. Dusty himself was nursing a bottle of beer, while Sickle held a larger liquor bottle in her hooves. I hoped most of the empty bottles were from her.

\leavevmode\llap{“}It’s still a load of shit,” Sickle grumbled to him before looking over at us and giving a sneer. “Hey, cunts. You want a drink?”

Dusty was rolling his eyes, half hidden as he took a tiny sip of his beer.

\leavevmode\llap{“}Yeah, I’ll pass,” Starlight said, and I shook my head.

\leavevmode\llap{“}You see?” Sickle said, looking at Dusty as she gestured our way with her bottle. “Everypony is a stuck-up, no-fun bitch in this town.”

\leavevmode\llap{“}So you’ve said,” Dusty wearily said.

Sickle snorted and tilted back her bottle, taking several deep gulps from it, then lowering it again to stare at it. “Huh. This shit ain’t half bad.”

Starlight, unfortunately, took the bait. “What is it?”

\leavevmode\llap{“}One of the bottles the green bitch sold me,” Sickle said, looking over the label. “Something called port. It’s weak, but kinda good. Like wine that ain’t shit.” She swung the bottle around, offering it to Starlight. “Try some.”

\leavevmode\llap{“}No thanks.”

\leavevmode\llap{“}Oh, for fuck’s sake,” Sickle growled, gesturing again with the bottle. “Stop being such a little chicken-shit and take a taste. Ain’t like I’m asking you to chug the whole fucking thing.”

Starlight glared back at her over the offered bottle before snatching it in her magic. “Fine,” she shot back, and took a quick swig from the bottle. She lowered it again, opened her mouth to reply—and instead coughed, her eyes widening. She recovered quickly enough. “Urg. There. I tried it.”

Sickle leaned over the table, crossing her forelegs. “Yeah? How is it?”

\leavevmode\llap{“}It’s okay,” Starlight said, despite an expression of distaste.

\leavevmode\llap{“}See?” Sickle said as she grabbed another bottle. “That didn’t kill you, did it?”

Starlight snorted. “I prefer things to be a lot better than, ‘it didn’t kill me’.” She held the bottle out to Sickle, but the other mare waved it off.

\leavevmode\llap{“}Keep it, I’ve got another.” She bit down on the cork and pulled it out, sending a splash of purple liquid over her snout and neck, then spitting the cork across the room.

\leavevmode\llap{“}I don’t want it,” Starlight said, still holding it out.

\leavevmode\llap{“}I don’t care. Drink it, pour it out, shove it up your ass, whatever!” She licked the liquid from her lips before tilting back the new bottle, swallowing a couple times before lowering it again. “And seriously, lighten the fuck up and have some fun every now and then instead of obsessing over all your stupid shit. I mean, look at me! I don’t give a shit, and I have more fun than all of you cunts combined. More than this whole fucking stuck-up bitch-ass town!”

Starlight frowned as she set the bottle on the table. “What the hell has you so worked up now, anyway?”

Dusty groaned, mirroring my own thoughts. I was going to nudge Starlight away from the table, but Sickle spoke first. “Worked up? Hah! Ain’t that the fucking word for it. I spent the last two days trying to find any stallion worth a damn in this little shitstain of a town, but I couldn’t find a single one that wasn’t an uptight prude. Just that weird cunt with the cleaning fetish. I mean, I don’t give a shit if you’re married. Bring your bitch along, too, make it a party, but nooo…”

As Sickle took several more deep gulps from her new bottle, Starlight was rolling her eyes. “Charming as ever, I see.”

Dusty grumbled. “She’s been bitching about this for hours.” He followed by taking another sip of his drink.

\leavevmode\llap{“}Oh, fuck the both of you. Ain’t my fault this town is full of dumbasses. Shit, at least when I was still rolling with my old gang I could get fucked every night.” She snorted around the neck of the bottle as she took another drink, more fluid running down her neck as she licked her lips. “Heh, shit, more like three or four times a day. That was good.”

Starlight rolled her eyes. “And maybe ponies don’t want to sleep with someone who’s been with half the Wasteland. Or who looks like somepony fed her through a meat grinder. Or maybe they just don’t like the idea of knocking up some random stranger.”

\leavevmode\llap{“}Hah, don’t have to worry about that one,” Sickle said, grinning. “I can’t have kids.”

Starlight’s ears perked up in surprise, her expression turning to concern. Seeing the conversation going even further into territory I’d rather avoid, I quickly stepped up to her, speaking quietly. “Maybe we should—”

\leavevmode\llap{“}Why not?” Starlight asked, oblivious to my concerns. I suppressed a groan.

\leavevmode\llap{“}Cause of this bad boy,” Sickle said, thumping a hoof against her chest over a large, puckered scar, one of the larger signs of injuries dotting her body. “Hard to get knocked up when you ain’t got a uterus any more.”

Starlight blinked, and I have to admit, I was a little confused as well—and possibly a little concerned at how happily she had just mentioned missing a somewhat significant internal organ. “Wait,” Starlight said, lifting a hoof to point at her. “That’s your chest. The uterus is, like…” She lowered her hoof, pointing down more to Sickle’s belly.

Sickle blinked, then snorted out a laugh. “It’s a bullet wound, dumbass. Ain’t like it stops at the skin. Shit, I thought you were smarter than that.” She took another swig, then set the bottle down with a thump. “Yeah, some bitch with a monster fucking rifle shot me in the chest this one time. I didn’t have the heavy armor I got now, not that it would have done much. Still got almost halfway to her before I passed out. Woke up the next day, all fucked up.

\leavevmode\llap{“}Cutter said the bullet went through a lung, stomach, intestines… I think the liver? Then the uterus, and finally lodged in the pelvis. I guess none of those cunts thought I’d live, but I showed them. Cutter said I lost the uterus and some of the intestines, but he sewed me up, and I was out kicking ass again in a week.”

She sat back, taking another draw from the bottle before thumping it down, empty. “Heh, we found out I was pregnant, too. Guess I dodged a fucking bullet on that one.” She blinked, wavered a moment, then started snickering uncontrollably.

Everyone else’s reactions were much less amused. Dusty grimaced, taking another drink, while Starlight looked at her wide-eyed, her ears pinning back. “That’s horrible!”

\leavevmode\llap{“}Nah,” Sickle said, still snickering. “Sure, it hurt like fuck, and it sucked when I couldn’t walk. I nearly beat Crunch to death, trying to fuck me with a broken pelvis. Still, wasn’t the worst I had.”

Starlight drew her head back. “I mean losing your child,” she said, her voice subdued.

\leavevmode\llap{“}What, that?” Sickle snorted, pushing aside some of the bottles as she fetched a beer. “Like I give a shit. The hell would I would want with a kid, anyway?” She bit off the cap, spitting it out and draining half the bottle in one go. She thumped it down on the table, letting out a bitter laugh. “Shit, I’d probably stomp the little brat to death within a week.”

Starlight blanched, weakly repeating, “That’s horrible.”

Sickle took another drink, looking off into space for a moment. Then she let out another chuckle, and touched a hoof to the side of her jaw, where the mass of scar tissue had left her skin bare. “Nah, actually, this one, that’s probably the one that hurt the worst. That cunt Char caught me right in the face with a fucking molotov. I don’t know what it is about getting burned, but that shit hurts worse than anything else.” She grinned darkly. “I’m guessing Char agreed, with the way she screamed.”

Starlight shuddered, then took up the bottle again to take a quick gulp. She shuddered again at the taste of the alcohol. “Ugh. You have got to be the most unpleasant pony I’ve ever met.”

\leavevmode\llap{“}What?” Sickle said with a snort. “Fuck you, runt. I’m trying to be \textit{nice}, here.”

\leavevmode\llap{“}This is you trying to be \textit{nice?}”

\leavevmode\llap{“}Yeah!” Sickle gestured to the bottles, knocking several empty ones over. “I’m giving you my booze, sharing some stories, and not stomping anypony’s ugly face in.” She grabbed her bottle again, downing the rest of it, and angrily tossing it aside. “Shit, most of the fighting types I’ve known \textit{love} scar stories.”

Starlight had cocked her head to the side, looking over Sickle more closely. I think she was thinking the same thing I was at that moment: that, as awkward and aggressive as it may be, this seemed to be Sickle’s attempt to be \textit{friendly}.

After a few seconds, Starlight set the bottle on the table again and pulled out a chair to sit on. “They do, huh?”

\leavevmode\llap{“}Yeah,” Sickle said with a snort. “Dirt and I shared ours years ago, even if he ain’t got shit on me.” She delivered the last part with a grin aimed at him, which he answered with a sigh. “Hell, I’ve got some good new ones traveling with you cunts, too!”

Starlight glanced my way, and when I shrugged, prompted Sickle. “Oh?”

I reluctantly claimed another chair for myself as Sickle laughed. “Hell yeah,” she said, grinning. “I think Gutfuck shooting me in the ass is going to be a new favorite.” Then she lifted a hoof, thumping the side of her muzzle. “And shit, I get to brag about getting shot in the face with a fucking minigun! How badass is that, huh?”

\leavevmode\llap{“}I… guess that is kind of impressive, yeah,” Starlight quietly said.

Sickle swept a hoof over to gesture at her. “See? Hell, I got a lot of stories.” She grabbed yet another bottle, and then, as if an afterthought, offered a beer to me. I accepted it reluctantly, and she sat back, taking a swig before speaking again; from the amount of alcohol I’d witnessed her drink in the short time since we had arrived, I was surprised she wasn’t slurring her words.

\leavevmode\llap{“}I’ve been shot more times than I can count. Most of those are pretty boring. You know, they shoot me, I don’t give a fuck because I’m big and tough and drugged out of my mind, that sort of thing.” She started to point out parts of her body as she continued, her hide an illustration of her violent encounters. “Nearly lost my leg to some stallion with a double-barrel. Shotguns don’t do shit against armor, but the stuff I had then didn’t cover my legs. Put both barrels into my leg at close range. You could see the bone and everything, and we didn’t have any healing potions, so I couldn’t walk on it for weeks. Oh, and that zebra! She had this thing that was like a machete strapped to the end of a pole, and was slippery as fuck. She just kept slashing away and dancing out of range. Cut my thigh open, sliced my lip, and damn near caught me in the throat. She was pretty good.”

The tales of violence and injury continued for a good while, interrupted only by Sickle taking another drink. She managed to finish off another two beers and a half-empty bottle of rum before I thought I could detect a faint slurring of her words. And, while the subject matter was grotesque, there was something strangely refreshing about Sickle making the attempt to be friendly—however horrific that attempt might have been.

I made a point to avoid thinking of who these ponies were that she had been fighting. It sounded like plenty of her fighting had been with other raiders, but I also knew what raiders did to regular ponies.

Eventually, she ran out of stories, and she sat there, slowly spinning the empty rum bottle with a hoof. “...Okay, come on. I’m out of stories. Someone else go.” When we looked around silently, she groaned. “Star, your turn. You keep going on like you’re hot shit. You got any good fighting stories?”

She frowned, setting the bottle of port down again, and I should note I was much relieved that she had only had the occasional sip rather than making any attempt to emulate Sickle’s prodigious rate of consumption. “I didn’t get into many fights before traveling with you. Just the raider ambush.” She shook her head. “I dunno. My mom and I took down some big critters when we went hunting. I shot a few feral ghouls, too, but that wasn’t very impressive.”

\leavevmode\llap{“}Hunting, huh?” Sickle gave the rum bottle another spin. “What kind of big critters?”

\leavevmode\llap{“}We took down manticores a couple times. Mom even let me take the shot once. Probably, oh… quarter mile? Vaporized its head. Got a good amount of caps trading all the meat.”

\leavevmode\llap{“}Hmm,” Sickle mused. “I’ve never fought a manticore before. Not bad.”

Starlight slowly smiled. “Wait a minute. Are you saying there’s something I’m better at than you?”

Sickle snorted and laughed, reaching over to give her a shove that almost sent her toppling over. “Yeah, right, runt. I’m just saying I ain’t fought one, yet. After, then we’ll see.”

\leavevmode\llap{“}Y-yeah,” Starlight said, regaining her balance, though her confidence returned quickly enough. “Yeah, let’s see you take one out with one hit and not a scratch.”

Sickle snickered, sitting back. Then she looked my way. “How about you? The buggy little super-spy got any fun stories?”

I smiled, more to keep the mood going than out of any real humor. “Not unless you count paperwork and making friends as fun stories.”

\leavevmode\llap{“}Bo-ring,” Sickle announced.

Starlight gave a salute with her bottle. “Well \textit{I} thought your friend stories were nice.”

I smiled.

After a moment, a mischievous look crossed Starlight’s expression, and she turned to Dusty. “What about you? A Mareford Ranger must have a few good stories.”

Dusty shot her a look, but it was Sickle who replied. “Nah, he’s being an uptight cunt today. He’s barely said more than like three words since I got back. He’s just been moaning and bitching about me moaning and bitching.” She turned to him. “Seriously. You need to go out there and get laid or some shit.”

\leavevmode\llap{“}Not everyone is as obsessed with sex as you are,” Dusty grumbled.

\leavevmode\llap{“}Oh, shit, he speaks!” Sickle grinned. “Also, that’s a load of shit, Dirt. You’ve been obsessed with pussy since before we first met.” She leaned in, her eyes narrowing a bit, her grin turning predatory. “‘Cept it’s always been one pussy in particular, ain’t it?”

Dusty glared. “That’s none of your business.”

\leavevmode\llap{“}Yeah, sure.” She sat back. “But really, get over it, and get laid. You could use a good fucking.”

\leavevmode\llap{“}Some of us don’t solve our problems with random sex,” Dusty muttered.

Sickle snorted. “Yeah. Some of us are fucking stupid and whine about the same shit for years.” She abruptly turned back to Starlight and myself. “Come on, somepony come up with some other story or some shit. Just… fucking anything!”

Starlight and I exchanged glances as we tried to think of anything, and Sickle groaned. “Errgh, fuck all of this. How long are we going to be in this lame-ass town.”

\leavevmode\llap{“}Well,” I cautiously said, “we’re here for a week, and this is day three, so… we’re almost halfway there.”

Sickle groaned again. “Shit. I really hope that trader was carrying booze. I’m almost out already.”

Starlight looked up from the bottle she was cradling in her forehooves. “You’ve drank all of it already?”

Myself, I wasn’t at all surprised, given the rate I’d been watching her consume it.

\leavevmode\llap{“}Just about!” Sickle replied. “I need \textit{something} to do, but I’m almost out of booze, I ain’t been in a fight all week, and I ain’t had a proper fuck since Spot!” She snorted, hoofing lazily at the rum bottle before pausing to pick it up. “Heh. Guess I can make do with some of these, but it ain’t the same as a real stallion. Not like there are any of those in this lame-ass town.”

Starlight’s nose scrunched up. “Gross.”

Sickle didn’t seem to hear her. She was staring down at the bottle, the hints of a grin forming at the corner of her mouth.

I caught the glance over to Dusty; he didn’t.

Sickle rose up, her forehooves catching Dusty around the chest, and pushed. He toppled backwards with a shout as she drove him down to the floor. An instant later, he was pinned on his back, and she straddled him, sitting on his hips.

\leavevmode\llap{“}Damnit, Sickle!” he snapped, shoving uselessly at her chest with his forehooves while his hind legs stuck out awkwardly behind her. “Get off!”

\leavevmode\llap{“}That’s the idea,” she said, lips curling back in a leer.

\leavevmode\llap{“}Sickle!”

She laughed. “You ain’t fucked a mare in over a year, and it was, what, another year before that? And I know you ain’t jerked it the whole time we’ve been traveling.” She rocked back, very plainly grinding her hips against his. “Shit, most stallions would explode, trying to hold it that long.”

\leavevmode\llap{“}Yeah, well I’m not ‘most stallions’,” Dusty countered, which just made her laugh again.

\leavevmode\llap{“}No shit. Dusty, you need to get laid more than any stallion I’ve known. And hey, I need somepony to fuck. Works out nicely for both of us.” She ground her hips again, her grin growing. “Feels like that’s a ‘yes’.”

\leavevmode\llap{“}It’s not and you know it!” Dusty said, his hind legs kicking once as he squirmed.

\leavevmode\llap{“}Hey, it ain’t like it’d be the first time we fucked. You had a lot of fun with it, too, even if you like to pretend you didn’t.”

\leavevmode\llap{“}I was drunk!” Dusty snapped, shoving at her chest again.

She didn’t even budge, grinning down at him. “You’re drunk now.”

He glared, huffing a couple deep breaths before replying. “I am not nearly drunk enough to have sex with you, Sickle.”

She chuckled. Dusty grunted and pawed at her body as she leaned back, grinding her hips against his as she snatched up a bottle of whiskey, then leaned over him again, thumping it down on the floor beside his head.

For several seconds, he glared angrily up at her lurid grin, silent except for the heavy breathing. Then, with an irritated snort, he snatched up the bottle. “I fucking hate you sometimes.”

\leavevmode\llap{“}Good!” Sickle said as she got up. “I like angry sex.”

Dusty snorted again and popped open the bottle. He got only a single gulp down before Sickle grabbed him around the chest and hauled him up, sending a splash of whiskey down his chin. “Damnit, Sickle!”

She just laughed, hauling him along into her room, and kicking the door shut hard enough that it rebounded open several inches.

Leaving Starlight and I sitting there, very still and silent, with similarly strained expressions.

Starlight, as usual, was the one to break the silence. “So… that happened.” She lifted her bottle, taking a quick sip before lowering it again. “Like, right in front of me and everything.”

\leavevmode\llap{“}Yeah,” I quietly agreed, having no more useful thoughts of my own to contribute. Not that I was unused to sexually active individuals, I just wasn’t quite certain what to think of that particular event.

The occasional sound crept out from Sickle’s room, mostly the occasional chuckle from her, the shuffling of hooves, or a sound suspiciously like that of a grown stallion being dropped on an ancient bed.

Starlight started to raise the bottle again, then thought better of it and set it on the table.

Moments later, the sound of a bed protesting loudly emanated from the room, mixed with the muffled sound of voices, or maybe grunts. After a few seconds of that, a new sound joined the mix: the deep thump of the bed knocking against the wall. That sound repeated a moment later. And then again.

Starlight jumped to her hooves, breathlessly blurting, “Okay I’m going to bed goodnight!” as if it were one long word, and hustling off to our room.

I sighed, looking down at the beer I still held, the same one Sickle had first passed to me. There was only a little left in it, and I was surprised to find myself, at that moment, a little disappointed at the fact. I finished it off, set it on the table, and went to bed myself.

When I entered the room, Starlight had a hoof laid across her head in an attempt to block out the sound of the energetic coupling going on in the other bedroom. The extra wall did rather little to muffle the sound.

As I slid into bed, I asked, “Are you all right?”

\leavevmode\llap{“}Peachy,” she grumbled, fidgeting and rolling around a bit before giving up and placing her pillow over her head.

I sighed softly, laying my head down, and tuned out the sound. Starlight struggled to do so for quite a while longer. She kept shifting around, pawing at her pillow, and generally doing everything except sleeping.

I was near to drifting off when she finally started to still. A few seconds later, she murmured, “Fuck it.”

The bed shifted as she moved, then the blankets lifted up, and suddenly Starlight was right there. Her body moved over mine as she straddled me, beneath the blankets. I ended up on my back, her belly and hips brushing against mine. She looked down at me, breathing heavily, her forehooves planted on either side of me.

\leavevmode\llap{“}I want to have sex,” she said, in what was easily the bluntest and most awkward way I’d ever had the subject broached.

I found that I had moved my hooves to her chest, supporting her, but also placing a fragile barrier between us. I have to admit, the touch of her lower body, without even the faintest attempt to rub against me or otherwise tease, was surprisingly enticing.

Despite that, I still had to voice my concern. “What happened to not being interested in mares?”

In the faint, monochrome light of her PipBuck screen, I couldn’t see for sure, but the way her ears twitched back suggested that she was blushing. “Well… I mean, it’s different. You can change stuff like that, so it’s not \textit{really} like being with a mare, right?”

I hesitated, while she looked down at me. The soft coat of her belly brushed against mine with every breath. “Starlight, changing what I look like won’t change anything about who or what I am beneath that.”

Her ears flicked back, as if from a flash of embarrassment, but then stood tall again. “Well, maybe I like what’s beneath that, too.”

After just a moment of consideration, I called up my magic. Starlight squeaked and jerked back as the green fire flashed over my form, stripping away my disguise. Suddenly, her soft belly was brushing against smooth, hard chitin. She blinked away the dazzling flash of light, and once she had looked back, I fixed her with a flat stare. “You mean this?”

She stared down at me, her eyes slowly moving over the distinctly non-pony form, from the nearly luminescent and featureless blue eyes, to the glossy carapace reflecting the green PipBuck light.

Then she pushed forward, slipping past my hooves as her body pressed against mine, and mashed her mouth against mine in a clumsy kiss that was far more passionate than it was skilled. She pressed and twisted, showing no sign of hesitation even when her tongue met sharp teeth.

Then she drew back, ending the kiss as abruptly as it had started. Her muzzle hovered just above mine as her eyes darted over my expression. A faint tremble ran through her body, though I couldn’t say whether it was from nervousness or excitement. The feeling of affection flowed strong.

She slowly smiled. “...Yeah.”

I have to admit, I wasn’t sure how to reply. I didn’t need to. She pressed in once more. Her muzzle slipped in beside mine to nuzzle affectionately, her body rubbing against mine, and a hoof slid down my smooth side to grab at my hip.

It was an interesting night.