The sun had been up for several hours before I finally extricated myself from the bed and made my way over to the wash basin. I was thankful for the opportunity to sleep in my natural form, and not just for the comforting familiarity of it. Lying across Starlight’s foreleg would have likely been rather uncomfortable in a pony guise, with the limb squeezing soft flesh against hard bone, never mind the PipBuck that had been wedged against my side.

I fetched a worn washcloth, and for a moment simply enjoyed the sensation of the damp fabric gliding over my carapace. Another plus of my natural form; chitin cleans much easier than a coat of hair. I had gotten to cleaning between my hind legs when Starlight groaned and stirred, rubbing lazily at the leg I had been lying on. A moment later her eyes opened. “Holy crap, it’s noon.”

\leavevmode\llap{“}Guess we needed the sleep,” I said, finishing up with scrubbing my forehooves clean.

\leavevmode\llap{“}Yeah, guess so.” Starlight groaned again as she sat up, rubbing a hoof over her eyes. “Urgh. Explains why I’m so hungry, too.”

With a flash, I retook my earth pony disguise, and began the careful examination to make sure I had gotten every detail correct. “You should probably clean up before going out,” I said as I brushed a hoof along my chest, ensuring the coat laid just right.

\leavevmode\llap{“}I’m not—” She halted herself, raising a hind leg up slightly as she looked down. A hint of color tinted her cheeks as she snatched the washcloth in her magic. “Gimme that.”

She was about halfway through her own cleaning when she paused, her ears slowly falling back. “Um… crap, I… \textit{really} should have asked before, but, uh…” She swallowed. “Changelings and ponies can’t, um, you know…” Her expression looked strained as she raised her forehooves, awkwardly gesturing them toward each other in a way that I might have thought meant “have sex” if not for that question having an obvious answer. When I didn’t show any sign of comprehension, she meekly finished. “...Have kids?”

\leavevmode\llap{“}Oh! No. Our species aren’t biologically compatible.”

Starlight exhaled, giving a relieved nod.

\leavevmode\llap{“}In any case, I make all my forms sterile. It’s a standard precaution, since a changeling shapeshifted into a pony and a regular pony \textit{are} biologically compatible, which can lead to all sorts of complications.” I paused before adding, “And yes, you really should ask questions like that before it becomes important.”

\leavevmode\llap{“}Yeah,” she said, ears still hanging low. “I was a little preoccupied… I mean, I figured, but it’s good to make sure. Just… maybe make sure earlier.”

I gave a little smile to soften things up. “Earlier would be better, yes.”

She gave a little sigh, her hoof returning to the washcloth as she finished giving herself a quick cleaning. “I am \textit{really} hungry. Thirsty, too.” She looked over to me. “Want to get breakfast?”

I nodded. “Sure. I’m pretty hungry, too.”

She tossed the washcloth back beside the basin and crawled out of bed, slowly fetching her holster and saddlebags. Once she’d gathered them, she simply sat there, holding them in her lap. “...That was really good. I mean, I figured it had to be, but… yeah, that was good.”

I slowly nodded. “It can be.” Finishing my inspection, I turned to look at her again. “This was your first time?”

Her ears drooped again, and she gave a weak, self-deprecating laugh. “It showed that badly, huh?”

\leavevmode\llap{“}Not really,” I said, giving a soft smile. “Open and honest passion is a good deal better than simple technical skill.”

She chuckled a little as she started to strap on her holster. “Yeah, I was maybe a little worked up. And then that thing you did with your tongue…” She huffed faintly and shook her head. “Nope, not thinking that right now.” She tugged on the last strap. “Do we have any plans for today?”

\leavevmode\llap{“}Not that I’m aware of,” I said.

She hummed softly, thinking. “...I dunno, want to go shooting again? Not much else to do around here.”

\leavevmode\llap{“}I’d rather not waste too much more ammo before Dusty starts teaching me. It sounds like we’ll go through plenty, then. I might tag along, though.” I slipped on my saddle bags before asking, “What would you normally do for fun?”

\leavevmode\llap{“}Climb around in some ruins,” she said. “Jump from one building to the next, crawl through windows, explore all those empty places. Maybe even find some place nopony’s been to in centuries.” She shrugged. “I kinda had to make my own fun, growing up.”

\leavevmode\llap{“}There seems to be a lack of extensive ruins around here,” I noted.

\leavevmode\llap{“}Yeah,” Starlight grumbled, but then her ears perked up. “Though there is that mine behind Arclight’s place. Underground ruins are a bit too serious-mode for playing around in most of the time, but that could work. Just as long as nothing’s living in it. Better than climbing all over the buildings ponies are living in now. Hmm.” She idly tapped a hoof against her leg, then looked back to me. “What about you? What were you thinking of doing?”

I shrugged. “I don’t know. I was thinking of digging around through those files we got at Paradise Beach. The C.L.T. stuff could use a more thorough double-check, and I’ve got plenty of time now that we’re not walking constantly. I might look through the stuff from the other companies, too.”

Starlight was rolling her eyes halfway through my statement, and ended with a flat stare. “Come on, Whisper. We’re supposed to be relaxing and having fun.”

My ears pinned back defensively. “Well, I’d be lying here in bed. It’d be hard to argue that it isn’t relaxing.”

When Starlight continued to stare, frowning, I sighed. “Maybe I could see if I could borrow that book once Dusty’s done. That should pass an evening or so.” After another moment of thought, I shook my head. “Actually, I suppose I could just tag along with you or Dusty. Socializing and ‘hanging out’ are always good.”

\leavevmode\llap{“}Then it’s settled,” Starlight said as she rose to her hooves. “We’re getting some food, then you’re coming with me to explore the mine.”

\leavevmode\llap{“}A mine that’s already been explored,” I pointed out, though I rose to follow her.

\leavevmode\llap{“}Shush,” she said, walking to the door, and I followed her out.

Dusty and Sickle were both there. Dusty was sitting hunched over the edge of the table, a couple empty beer bottles set nearby. Sickle was kicked back against the nearby wall, I assume because it let her sprawl back in her typical lewd fashion. I missed whatever it was she was saying to Dusty as we entered. I just noticed how the conversation immediately stopped.

A grin quickly spread across Sickle’s muzzle. She lifted her forehooves and started to clop them together, slow and loud. “Yeah-heh-heh! Damn, it’s about fucking time, bitches!”

Starlight stopped with a squeak, her cheeks instantly turning red.

\leavevmode\llap{“}Guess I was wrong about you two,” Sickle said, chuckling. “Here I thought you two were fucking the whole time and just being all sneaky quiet and shit, but \textit{damn} was that wrong. Hoo!”

Starlight fell back to her haunches, her ears hanging low. “You… heard that?”

Sickle practically cackled. “Heard it? Fuck me, runt, you probably raised every dick in town with how loud you were!”

\leavevmode\llap{“}You weren’t that loud,” I quietly said, casting a disapproving glare Sickle’s way, while Starlight covered her face in her hooves.

\leavevmode\llap{“}Sure she wasn’t,” Sickle said, giving another snicker as she addressed me. “Shit, you had her going for what, an hour or two? Dirt and I finished, and you two just kept on going on and on. Started getting me horny again! What the hell were you doing to her in there?” Her ears perked up, her grin growing. “Oh, shit, did you do the hellhound thing? I told you it was fucking awesome!”

My glare was turning into a glower. “I did \textit{not} do the ‘hellhound thing’.”

Beside me, Starlight quietly murmured, “Changeling tongues are amazing.”

I lurched a little, caught off guard. Her cheeks were still burning red, with her chin tucked down and her eyes on the floor. It almost succeeded in hiding the smile that was forcing its way out.

Naturally, Sickle busted out laughing, thumping a hoof against the floor. “Ahaha! Oh, shit, this is too good!”

While Sickle continued to laugh, Starlight cast a glance my way. I’m not sure if it was supposed to be apologetic or amused, but when I raised an eyebrow in reply, her smile grew a bit more, despite her apparent effort to constrain it.

\leavevmode\llap{“}Ahhh, shit,” Sickle said as her laughter died off, and she laid her head back against the wall. Still grinning, she patted her crotch with a hoof. “Hey, how about you show me how good that tongue is, Whimper? I ain’t ever fucked a bug before.”

My eyes narrowed, and I found myself baring my teeth, despite how unimpressive that gesture is with a herbivore’s flat teeth. “First off, \textit{keep it down}. Your voice carries, and I don’t want to end up in trouble because \textit{you} can’t handle basic secrecy. And second…” My eyes glanced down along her body, then returned to meet her eyes. “...If you’re going to insist on making passes at us, you would do a lot better if you put some effort into making the offer less revolting.”

\leavevmode\llap{“}Oh, yeah, sure,” Sickle said, smirking. “‘Cause you sounded all kinds of revolted about fucking last night, huh?”

\leavevmode\llap{“}I’m talking about basic hygiene,” I said, frowning at her. “We all know you’ve had sex with every living creature you could get your hooves on, we don’t need to see and smell it, too.”

She chuckled, and though I refused to look, I could see the movement of her hoof patting between her legs, and the suggestive look she gave with it. “Hey, plenty of ponies like it messy, but you know, if you want to clean me up down there…”

\leavevmode\llap{“}There is a marked distinction between ‘messy’ and ‘filthy’,” I replied, and turned toward Dusty to signal the end of that conversation. “Are you okay?”

\leavevmode\llap{“}M’fine,” he grumbled, his hooves tightening around a bottle. After a moment, he spoke louder, though slowly, as if carefully sounding out his words. “I am lamenting the passing of my late self-respect.”

\leavevmode\llap{“}Aaand he’s back to being an uptight cunt,” Sickle said, reaching out with a hind hoof to lightly thump the side of his chair, which almost knocked him to the ground. “Only you could get so mopey over getting your dick wet.”

I shot a look her way. “Shut up, Sickle.” While she made a crude gesture, I turned back to Dusty. “Seriously. Are you all right?”

Dusty grumbled, but when he finally looked up to me, he managed a small, uneven smile. “I will be. Just give me some time.”

\leavevmode\llap{“}Yeah,” Sickle said. “He’s just pissed because he knows I was right.”

Dusty sighed as he finally lifted the bottle he was holding. “Yeah, pretty much,” he said, then tipped back the bottle to take a drink.

Sickle blinked in surprise, then laughed again. “Hah! About fucking time!”

\leavevmode\llap{“}You’re still a bitch,” he said around the mouth of the bottle.

\leavevmode\llap{“}The biggest, bestest bitch around,” Sickle proudly declared, to which Dusty just rolled his eyes.

I leaned in a little. “Did you want to talk about it?”

\leavevmode\llap{“}Fuck no,” he said, taking another quick drink before setting the bottle down. “Don’t worry. It’s done with.”

\leavevmode\llap{“}If you say so,” I said, with just enough of a frown to show I had my doubts.

He merely grunted in reply.

\leavevmode\llap{“}Eh, he’s fine,” Sickle said. “Shit, maybe better than fine. Woke up to him crawling on top of me for a morning fuck, and—”

\leavevmode\llap{“}Okay!” Starlight said, leaping to her hooves again. “Breakfast time. Food. Leaving now. Bye.”

She quickly made her way to the door, and with a parting look of disapproval toward Sickle, I followed.

Breakfast was a quick meal of grilled carrots and boiled cabbage from Pumpkin, and then we made our way to Arclight’s. While he expressed confusion as to why anypony would want to go wandering around in the mines, he allowed us in, on the condition that we couldn’t take any of the gemstones that his work depended on. He even assured us that there was nothing living in the tunnels, or at least, not as far as he’d explored.

He unlocked the gate, and we entered, my flashlight and Starlight’s PipBuck lighting the way. A set of cart tracks followed the slowly curving tunnel, leading further into the hill.

After a minute of quiet walking, we emerged into an open space. The tracks continued around a large pit, with offshoots leading down tunnels. One offshoot instead ended at a lift, suspended over the edge of the pit, with a set of steep metal stairs leading down. Beside the top of the stairs was a small, windowed structure, likely a foremare’s office.

\leavevmode\llap{“}Hey, this is a little more like it,” Starlight said, trotting right up to the edge of the pit to peer into the depths. The bottom was barely visible in the darkness, maybe a hundred feet below. The metal stairs wound back and forth, anchored to the edge of the pit.

\leavevmode\llap{“}It is?” I asked, but she had already turned around. She gave a short run-up before leaping and catching the edge of the small office, swinging her hindlegs up in a smooth motion. She grinned in the darkness, standing atop the structure, though she had to duck her head to not knock her horn on the ceiling.

\leavevmode\llap{“}What are you doing?”

\leavevmode\llap{“}Having fun,” she said with a grin, trotting along the edge of the roof. “And practicing. It’s kinda weird having this thing on my leg instead of around my neck. Don’t want it throwing my balance off at the wrong moment.”

With that, she halted, swinging her rear out over the open space while her forehooves caught the edge of the roof, and neatly slipped in through one of the windows. I trotted up to see her standing inside, looking around her. There wasn’t much to see, just a bare desk, a chair, and an open and empty filing cabinet.

A moment later, she was climbing out the opposite window and back onto the roof. “Yeah. Yeah, I think I’ll get used to this pretty quick.” The sound of hoofsteps echoed dully through the metal structure. “Did we have an extra flashlight? The PipBuck worked better as a light when it wasn’t at ground level.”

\leavevmode\llap{“}I think we had an extra,” I said. “If not, I doubt Sickle is going to use the one we gave her.”

\leavevmode\llap{“}That could work,” she mused. “Okay then! Let’s head on down.” There was a clatter of hooves as she leaped from the roof—and missed the edge of the pit, falling into the void.

My heart lurched as I tore away my disguise and lunged forward, but even as my transformation was finishing, I heard the impact of hooves on metal. I came skidding to a halt at the edge of the pit, wings flicking for balance. Starlight looked over her shoulder from where she stood on the stairs, and she chuckled at my wide-eyed expression. “What?”

\leavevmode\llap{“}Don’t do that!” I said, probably a good deal more emotionally than I normally would.

\leavevmode\llap{“}Do what?” she said, smiling. “I’m just having some fun.”

\leavevmode\llap{“}And nearly giving me a heart attack,” I said, hopping over the edge to land beside her with a soft buzz of wings. “This structure is at least two hundred years old. What if it gave out when you jumped on it?”

She grinned. “Why do you think I landed right on a support?” She thumped her hoof on the metal grating, where an I-beam ran beneath it. “First thing a good scavenger does in a ruin is check out how stable the place is. Look for the supports. Big, solid beams, sunk deep in the rock, no sign of corrosion? Sickle could have jumped down here, and it could probably take it.”

I frowned as I looked at the beam, taking a moment to come up with an objection that didn’t sound somewhat infantile. “...Okay. Just, maybe a little warning next time?”

\leavevmode\llap{“}Hey, I’m going to jump into this hole now?” she said, smirking. Then she reached out, playfully thumping her hoof against my chest-plate. “And you know I love the armor, but seriously?”

\leavevmode\llap{“}I wasn’t putting any thought into my transformation,” I replied, drawing back a step. “It was a bit of a panic moment. I thought I was going to have to catch you.”

She snickered. “Well, relax. I’m not going to jump off a cliff without knowing I’ll be perfectly safe. I know what I’m doing.” She followed that up by climbing up onto the railing of the stairs, balancing precariously on the thin metal bar, though she maintained her balance with no apparent effort.

\leavevmode\llap{“}I can’t help feeling a little nervous about a wingless pony around long drops,” I said, forcing my wings to lie flat.

\leavevmode\llap{“}As if this is the most dangerous thing we’ve done,” she said, then grinned. “Going down!”

Even with what technically could pass as a warning, I lurched again as she fell off the railing. At least, it looked like a fall at first, until the hoof she hooked around the rail swung her under the walkway. She dropped a good ten feet to where the stairs doubled back and landed with a loud clatter of hooves, while I hopped over the edge to glide down to her.

She grinned as I landed on the railing nearby. “Relax, Whisper. We’re here to have fun, right?”

\leavevmode\llap{“}Preferably without breaking any bones,” I said.

\leavevmode\llap{“}Nah, I’m not going to break anything.” She hopped up on the railing again, swinging out to climb down the outside of the stairs. “Maybe some scrapes or bruises at most, nothing serious.”

It was a completely impractical way of getting down, though she made surprisingly good time. I hovered beside her as she made her way down. The last ten feet were covered in a single leap, producing a loud “Oof” as she landed beside the tracks.

I landed beside her, a flash of green illuminating the chamber as I retook my disguise. Starlight was shaking her PipBuck-clad leg.

\leavevmode\llap{“}You okay?” I asked.

\leavevmode\llap{“}Oh, yeah,” she said, placing her hoof down again. “Just still not used to wearing this thing like this. It’s all good.”

To demonstrate her point, she hopped up onto the cart tracks, walking easily while balanced on the thin strip of metal. Her balance was almost perfect, with only the rare waver. I followed along beside her on the much easier flat ground.

We walked on in silence, save for the crunching of grit and gravel beneath my hooves and the soft metallic clunks from Starlight’s. After a time, I noticed her smile fading, her ears slowly lowering. I was about to ask if something was wrong when she finally spoke. “So, uh… you know, about last night…”

I’d been wondering when it would come up again. “Yes?”

\leavevmode\llap{“}I, uh… I just, you know… what happens now?”

\leavevmode\llap{“}That’s up to you.”

She turned to look my way, wobbling for a moment as she continued walking. “What, you don’t care?” Her tone struck me as disappointed.

\leavevmode\llap{“}Of course I care,” I replied, looking back at her. “We’ve only known each other for a little over a month, but we’ve been through a lot in that time. That sort of thing can build strong emotional connections. And even with how bad the world has gotten and how rough things have been, you’re still cheerful and friendly. It’s… a kind of idealism I think the world could use more of. It’s something I can admire.”

\leavevmode\llap{“}Huh,” was all she could reply with, looking off into space as her pace slowed.

\leavevmode\llap{“}You’re also one of the rare ponies I can be completely open with. I don’t have to hide things from you, so there isn’t some barrier of secrecy and duty between us. Even with my closest sisters, there was still that barrier there. There’s a lot of reasons I like you, and because of all of that, I want to see you happy. That’s why I say it’s up to you. As long as you choose what will make you happy, I’ll be happy.”

\leavevmode\llap{“}Really?” she asked, cocking her head as she glanced my way. “So, you’d be fine with me choosing… whatever?”

\leavevmode\llap{“}I’m a changeling,” I said, giving a weak smile. “We’re adaptable.”

\leavevmode\llap{“}Well, sure, but…” She paused, chewing on her lip for a moment as she continued slowly walking along the rail. “...But, I mean, you’ve got to \textit{want} something, right? Like, if it was entirely up to you?”

I looked down at my hooves, contemplating the question for several long, silent seconds, before finally shaking my head. “I don’t know. I… don’t think I’m in a good place to make a decision like that right now. Right now, I’m focused on finding my hive, and everything else is falling into the background. I know what my training suggests, but that’s all about manipulating and deceiving ponies. I’d rather just… follow your lead, to be honest. I may have some thoughts and insights to share, but I’m willing to put my trust in you.”

After a moment of silence, she gave a small smirk. “Just so long as I’m not jumping into deep pits?”

I huffed out a weak chuckle. “As long as you give a little more warning before doing so,” I said. “Also, that’s a rather effective metaphor.”

\leavevmode\llap{“}Um… thanks?” There was a pause as she hopped up onto a toppled minecart, laid across and blocking the tracks. “It just feels like, you know, this is some huge change, and I’m not really sure what to make of it.”

\leavevmode\llap{“}A change, maybe,” I said, “but it doesn’t have to be a big one. I know some ponies like to divide relationships up into a few, very firm categories, with certain things only belonging in certain categories, but real relationships are a lot more varied.” I paused, frowning for a moment. “...Plus, social pressures are much less of a concern when there’s practically no society left.”

\leavevmode\llap{“}Score one for the apocalypse?” Starlight said, and hopped off the cart for the tracks beyond. Her hooves landed square on the rail, though one slipped off to hit the ground beside it. “Damnit.” She quickly regained her footing and continued on. “So you’re saying, just… do whatever?”

\leavevmode\llap{“}I’m saying, do what feels right. Don’t feel like you’re forced to do something, for whatever reason.”

\leavevmode\llap{“}Hmm.” She mused over that for a moment. “So you’d be okay if, you know, we… just kinda keep on going like we have been?”

I nodded. “Yes.”

She continued walking for a couple seconds before the corners of her mouth twitched upwards. “Just… maybe with the occasional, um, you know…”

I smiled. “Sex?”

Her ears pinned back in embarrassment, though her smile grew. “Uh, yeah, that.” She shook her head. “Eesh, okay, it’s still a little weird talking about, with you being a mare most of the time.”

I couldn’t help a little teasing. “I was a mare most of last night, too.”

Her balance wavered. “Y-yeah, well… I was a little distracted by other things. And once you started… um, doing that thing with your tongue, you know… yeah, I kinda had other things on my mind.”

I chuckled a little. “You know, for a pony who claims to not be into mares, you did a pretty good job of copying that ‘tongue thing’.”

\leavevmode\llap{“}I may have been a teensy bit worked up and excited and…” She shook her head, nearly losing her balance again. “And anyway, I’m not into mares! I’m into \textit{you}.”

She abruptly halted to bring a hoof to her face. “Luna smite me, that has to be the cheesiest thing I’ve ever heard.”

I stood there, quiet for a moment as I contemplated her. Then I stepped over, sitting beside her. “Actually, I think I understand exactly what you mean. I’m kind of the same way.”

She lowered her hoof, cocking her head as she looked at me.

\leavevmode\llap{“}When you get down to it, I’m not really into ponies,” I said.

\leavevmode\llap{“}Uh…” Starlight blinked a couple times. “Haven’t you slept with, like, half a dozen different ponies?”

\leavevmode\llap{“}Four,” I said, then quickly corrected, “Five, now. But it’s still true.”

I pulled at my magic, transforming back to my natural form, sans armor, and raised a hoof to touch to my chest. “I’m a changeling. We aren’t like ponies. When I think of two bodies touching each other, I expect them to be firm and smooth, gliding against one another. But with ponies…” I retook my earth pony guise. I pressed again with my hoof. “There’s all this soft flesh that squishes and wobbles in all sorts of strange ways as you move. When two ponies come together, their bodies mush against each other, all squishy and flabby, and squeezed between the hard endoskeletal structure inside them. It’s weird, alien, and kind of disturbing.”

\leavevmode\llap{“}Wow,” Starlight said with a flat tone. “Charming.”

\leavevmode\llap{“}So, yeah, I’m not into ponies.” I flashed a smile at her. “Just \textit{certain} ponies.”

She held her flat glare for a couple seconds before rolling her eyes, slowly relaxing. “Okay, that’s the \textit{second} cheesiest thing I’ve ever heard.” Despite that, she smiled as her eyes returned to me. “But thanks.”

I nodded.

After a moment of comfortable silence, I rose to my hooves again, and we continued on.

{\br}%
We spent almost two hours following different tracks through the tunnels. Starlight enjoyed the sense of exploration, and treated every piece of mining equipment or outcropping of crystals as her own makeshift jungle gym. Myself, I enjoyed the company and conversation.

Afterwards, we took a rest in the town square, sitting on a couple benches beside Pumpkin’s place. We mostly relaxed and chatted about nothing in particular. Dazzle came by to socialize, and when she saw us dusty from the mines, offered to let us freshen up in her shower.

Starlight quickly declined, but Dazzle held up a hoof. “Hooves-off, I won’t even be in the room. I’m not trying anything, I just thought you’d like that chance to freshen up. I’d just ask for a couple caps to cover water costs.”

Starlight hesitated before replying. “Maybe next time.”

\leavevmode\llap{“}Okay, then,” Dazzle said. She remained for a while longer, trying to carry on a conversation with only minimal flirting, before eventually excusing herself and returning to the gate. Watching her walk off, her enthusiasm long since faded, I felt a little sad for her. Her chances were poor enough before, but now they seemed practically nonexistent. Judging from Starlight’s expression, I think she was thinking the same thing.

The day was steadily progressing from relaxing to boring when, about half an hour later, the town bell rang out. It was a lazy, un-urgent ringing, and we could see Dazzle, who had been lying back against her cannon, sitting upright to look out over the wall. A minute later she turned to call back. “Open up!” Then she waved out over the wall. “Hey, Wheels! Good to see you lot again!”

The caravan rolled its way into town with three wagons, the largest of which was pulled by a pair of brahmin. Each wagon was heaped high, and accompanied by several ponies. All of the ponies carried a weapon of some sort, though only four looked to be guard types. Other than the pistols, I saw a couple of pipe rifles, a shotgun, and a long bolt-action. It left me in the curious position of considering them lightly armed in comparison to myself and my companions. Then again, they were probably as well-armed as the raiders I’d seen, and maybe even better; none of them were relying on knives or spears.

While I was evaluating their capacity for survival in the Wasteland, Starlight had sat up, smiling. “Hey, maybe some fresh faces will liven things up. Think we should introduce ourselves?”

\leavevmode\llap{“}Certainly worth a try,” I said as I rose to my hooves. “At least then we can make some sort of impression before Sickle does.”

Starlight laughed and hopped up, and we went to meet the new ponies. She called out as we drew near. “Hi there!”

A couple of the ponies had noticed our approach, and now one of the guard ponies, the stallion with the shotgun, let out a low whistle. His eyes traced over my body. “Celestia above, I love this town already.” The pair of stallions with the pipe rifles snickered, and one of them thumped him lightly on the shoulder before he continued. “You all part of the welcoming committee?” he asked, grinning.

\leavevmode\llap{“}Nah,” Starlight said, smiling back. “We’re just here for a few days, thought we’d say ‘hi’.”

\leavevmode\llap{“}Well I’m glad you did,” he said, turning his smile her way. “It’s always nice to meet a couple of fine mares.”

An older stallion atop the lead wagon called back. “Don’t go harassing the locals, Scatter. I don’t want a repeat of Mareford.”

The other guards laughed, while Scatter’s ears flicked back. “Aw, that mare didn’t know how to take a compliment. ‘Sides, these two ain’t locals, ain’t that right?”

The older stallion sighed. “I don’t care if they’re local or not, just don’t go causing any trouble. ‘Specially not here, okay?” He looked our way. “You two wouldn’t happen to be friends of Dazzle, would you?”

Seeing where Scatter’s mind was going, I leaped on the opportunity and flashed a smile. “You could say that.”

The older stallion smiled, with just a hint of mischievousness to his expression.

The conversation was disrupted by an icy voice from the rear wagon. “It’s about time we got here. It’s bad enough having to travel with you imbeciles without the trip taking twice as long as it should have.”

We looked back to see a golden-orange pony step from the wagon, giving the vehicle one last disdainful look as she did so. Her perfectly groomed coat and elegant looks had caught Dazzle’s attention, and she was leaned out over the wall to get a better view.

Beside me, Starlight’s voice turned icy. “Amber.”

The mare in question stopped, turning to look down her nose at us. “Oh. It’s \textit{you}.” She said it with the kind of bored contempt that went beyond simple loathing, expressing a feeling much like one might have towards an unsightly stain on someone else’s carpet: unpleasant, undesired, and of absolutely no consequence to herself.

The older stallion, who I had assumed was the caravan leader, gave a quiet snort. “Ah. Y’all have met before, I take it?”

\leavevmode\llap{“}Yeah,” Starlight said, a fire rising in her voice. “She pulled a gun on us.”

\leavevmode\llap{“}A reasonable precaution when a group of hired killers practically force their way into my room,” Amber said as she retrieved her saddlebags from the wagon. “Funny how you can remember that, but you can’t remember my proper title. Now if you’ll excuse me, I’ve wasted all the time I intend to with you.” Without another word, she turned and walked to the far side of the wagon.

Starlight snorted, muttering under her breath.

\leavevmode\llap{“}Glad we’re done with that bitch,” Scatter muttered before looking back to us, an eyebrow raised. “Hired killers?”

Starlight grumbled. “That sounds so much worse than mercenary.” She frowned. “Uh, mercenary sounds kind of bad, too. We help ponies. Just… I guess it tends to involve a lot of shooting.”

\leavevmode\llap{“}She hired us for a job,” I said. “It involved killing some raiders.”

\leavevmode\llap{“}Yeah?” Scatter said, and smiled again. “Well, ain’t nothing wrong with that. Good riddance. How many of them scum did you bag?”

Starlight looked to me. “It was, what, twenty?”

\leavevmode\llap{“}About that.”

We looked back to Scatter, whose smile had disappeared. His tone no longer sounded amused, but doubtful. “The two of you took down twenty raiders, huh?”

\leavevmode\llap{“}Not just us,” Starlight said, smiling again. “We’re only half the team. Heck, the other two did more than us in that fight.”

I gave a dry chuckle, to emphasize my own self-deprecating statement. “I’m not even sure if I hit any of them.”

Starlight chuckled along with me. “I’m reasonably certain you didn’t,” she said, then gave a thoughtful look. “Though, you know, when you came around the corner on that pack of five or six of them, you laid out a lot of fire. You might have gotten some of them.”

Scatter was simply staring at us by now, and I enjoyed his expression of stunned disbelief.

The fourth guard, with the bolt-action rifle strapped across his back, stepped past Scatter. “Sounds like you two have some pretty good tales to tell.” He smiled. “How’s about when we get these wagons parked and gear stowed, we all get together and swap some stories?”

\leavevmode\llap{“}Heck yeah!” Starlight said, giving a happy little hop and grinning from ear to ear.

While the wagon crews pulled the wagons around behind Emerald’s store, we headed in with the guards and the old caravan master. Inside we found Dusty and Emerald, both with their forelegs crossed on the store counter as they chatted. Emerald looked up on our entrance, and smiled.

\leavevmode\llap{“}Wagon Wheel! I was starting to wonder when you’d make your way around here again. How have you been?” As she spoke, she stepped out from behind the counter, and gave the older stallion a hug.

\leavevmode\llap{“}Oh, not so bad,” he replied with a smile as he hugged back. “My knee’s been feeling a lot better lately, too. Still ain’t going to be running any marathons, but at least it doesn’t hurt to walk.”

\leavevmode\llap{“}Good to hear!” Emerald said, releasing him. “I hope you’re all staying the night? I can get Pumpkin to whip up something for everypony.”

\leavevmode\llap{“}Sure am,” he said.

\leavevmode\llap{“}Well, good! These fine folk here have the northern suite, but the southern one’s still open. You all go ahead and take a load off, and I’ll see about getting us all some dinner.”

Wagon Wheel’s reply was cut off by an icy voice. “How utterly charming, I’m sure.” Amber stepped forward, her eyes slowly tracing around the room. By the time her gaze reached Emerald, the green mare had retreated behind the counter, her smile having vanished. Amber stepped up to the counter, looking down her nose at Emerald. “I require lodgings separate from the rest of these… individuals.”

Emerald eyed her warily. “I can do that, miss…”

\leavevmode\llap{“}It’s \textit{Lady} Amber,” Amber scornfully replied. “Not that anypony seems to be able to remember that simple detail.”

\leavevmode\llap{“}\textit{Lady} Amber,” Emerald echoed, giving a slow nod and a strained smile. “I have plenty of rooms available. Eight caps per night. All the ground floor rooms are open. You can take your pick.”

Amber scoffed faintly as she drew out a pouch, casually retrieving several caps. “I suppose it’s too much to hope for that the doors lock?”

\leavevmode\llap{“}They latch from the inside.”

\leavevmode\llap{“}Then I suppose that will have to do.” Amber tossed the small collection of caps onto the counter. “I will pay you each night. Other than that, I expect to remain completely undisturbed. Do you understand?”

Emerald’s smile faltered as she nodded. “I understand.”

\leavevmode\llap{“}Good.” With that, Amber turned and walked away. She paused a moment as she passed Dusty, eying him, but then continued on, her nose high.

Dusty sighed as soon as she disappeared. “I see she’s as charming as ever.” He gave a weary smile Emerald’s way. “Well, I’ll get out of your mane. Talk to you later.”

As he turned to leave, Wagon Wheel stepped forward, his brows furrowed in concern. “Hold up a sec. Are you Dusty Trails?”

Dusty halted, his ears standing alert. He turned to face Wagon Wheel, and I felt an eerie twinge as I recognized he had just set his hooves the same way he did when shooting. “I am,” he replied, his voice even and calm in a way that put me on edge.

The other stallion eyed Dusty for a moment before taking a half-step back. “Ain’t none of my business,” he said, shaking his head, “and I don’t plan on \textit{making} it my business, but I figure Emerald here ought to know what’s what.”

Emerald looked up from the single bottle cap she held in her hoof, blinking a couple times as she caught up with the conversation. “...What’s that?”

\leavevmode\llap{“}Dusty Trails here is wanted in Mareford,” Wagon Wheel replied. “They say he killed a bunch of ponies. They put out a bounty on him.” He held up a hoof. “I ain’t got any interest in bounties. Neither does my crew. Hell, as far as I’m concerned, anypony under Emerald’s roof might as well be under Celestia’s wing. I just figure Emerald deserves to know who the pony is that she’s dealing with, and what might be following them.”

Emerald looked back and forth between them, slowly turning the cap over in her hooves. It was a few seconds before she replied. “Well... I like to think I’m a good judge of character, and Dusty strikes me as a good pony. I wouldn’t be surprised to hear that he’s killed a good number of ponies, given his line of work. The real question is who those ponies were.”

She ended looking right at Dusty.

He slowly sighed before speaking. “In this case… twenty some mercenaries under the employ of Mareford’s mayor, and three Militia Rangers.”

He was met with various looks of surprise, discomfort, and even fear. Emerald just looked inquisitive.

\leavevmode\llap{“}But it ain’t who I killed,” Dusty continued, staring back at them. “It’s why. Those ponies, they ambushed me and my friends. They tried to murder all of us, on mayor Big Gun’s orders, to cover up what \textit{he} did. And you know what he did?”

He waited just a moment, looking around at the other ponies before stepping up close to Wagon Wheel. “That water caravan that got hit a few weeks back? That was his work. He sold out his own ponies to a gang of raiders.”

Several ponies murmured. One of the pipe-rifle guards said, “Brahminshit.”

\leavevmode\llap{“}He told the raiders when and where they’d be,” Dusty said, glaring at the guard. “The mercenaries he had guarding them? They abandoned the caravan right before the raiders showed up. These were ponies he was supposed to protect, and he sold them out to a bunch of butchers. I saw the wreckage. The raiders slaughtered them. They cooked and ate a stallion in front of his family. They made a mother watch as they tied up and raped her little filly! And \textit{he’s} the one who made it all happen!”

Dusty was trembling, and forced himself to take a step back. The other ponies looked around, uncertain, but when nopony said anything, he continued. “That’s the kind of shit he does. I’ve seen it before. Maybe not as bad as this, but bad all the same. I used to be a Ranger. I was on the ground in Stinkpit. I went in, did my job, got Big Gun’s trader out. You know, I heard a lot of talk, afterwards. Ponies were talking about how Stinkpit had gone raider, how they’d massacred some other travelers, skinned some ponies, even tortured the trader they’d captured, stuff like that.

\leavevmode\llap{“}But I was there, and when I look back, all I see is a bunch of scared ponies defending their homes from the ponies attacking them. They weren’t raiders. Hell, the trader we were supposed to be rescuing was hosted in their makeshift inn, not a scratch on him. He was hiding under his cozy little bed. And you know, I would have just thought it was all some horrible mistake, some… misunderstanding or miscommunication. Except the same damn thing happened again in Hayseed, and more innocent ponies died. And it just keeps on happening. Only this time, this time we found out what he’d done, and he tried to have us killed for it.”

The other ponies’ looks had grown decidedly uncomfortable. A couple of the ponies in the back were quietly murmuring to each other.

\leavevmode\llap{“}So what’s the word on Rust?” Dusty asked, which was met with several blinks of surprise before Wagon Wheel spoke up.

\leavevmode\llap{“}What about Rust?”

\leavevmode\llap{“}Big Gun didn’t have a water caravan slaughtered for giggles,” Dusty said. “Wild Runner might, but not him. He did it for profit and power. He’s already taken two towns by force, just to get cheaper goods. Now Mareford’s water caravan gets hit right after leaving Rust? How long until he starts pushing for a change of management?”

More murmurs sounded across the crowd. The bolt-action guard spoke up first. “I heard rumors in Mareford. Bunch of ponies grumbling about Rust, saying it was them that hit the caravan.”

\leavevmode\llap{“}Brahminshit,” Wagon Wheel said with a grunt. “I know Steel Shot. He wouldn’t put up with anything like that, and he sure as Tartarus wouldn’t go hiring some raiders. Hell, Rust puts out a hefty bounty on raiders. No way.”

\leavevmode\llap{“}You’re right,” Dusty said. “He wouldn’t. But Big Gun would.”

Wagon Wheel mulled it over for several seconds. “You sure about all this?”

\leavevmode\llap{“}Not a doubt,” Dusty said. “We hit those raiders a day or two after they hit the caravan. They had a message telling them exactly when and where the caravan would be left unguarded. We rescued a couple ponies that confirmed the guards left them just before the raiders showed up. And then when we go looking into it, Gun’s mercs attack us, and we find out it was on his orders.”

Wagon Wheel cursed.

\leavevmode\llap{“}That would explain some things,” Emerald said, quietly. “I’ve heard of some questionable things around Mareford, and the rumors about Stinkpit and Hayseed.”

\leavevmode\llap{“}And that’s just the stuff we know about,” Dusty said. “There’s been a lot of caravans getting hit by raiders lately.” He looked to Wagon Wheel again. “Might be good to get the word out to the other caravans. If he’s associating with raiders and selling out his own ponies, there’s no telling what he might be willing to do to other traders.”

Wagon Wheel slowly nodded. “I think I’ll do that, yeah.”

\leavevmode\llap{“}...Out of curiosity,” Dusty asked, “how much of a bounty did he put on my head?”

Wagon Wheel hesitated before saying, “Four thousand caps for bringing in proof of your death. Another five hundred for each pony with you.”

\leavevmode\llap{“}Shit. Bounty like that’ll bring out every two-bit bounty hunter and wannabe merc in southern Equestria.” Dusty shook his head. “Still, if that’s the price for doing the right thing, I’ll take it.”

After a moment of consideration, Wagon Wheel spoke again. “I’ll share your side of the story, too. Won’t say anypony’ll believe it, but I’ll put it out there.”

\leavevmode\llap{“}Thanks,” Dusty said, and offered a hoof. They shook. “And I’ll get out of your manes. Just be careful out there. Seems like all the worst shit is stirring up, lately.”

\leavevmode\llap{“}Yeah, I’ll do that,” Wagon Wheel said, though I could still see a hint of skepticism to his expression as Dusty walked off.

Scatter looked back to Starlight. “You two are with him?” When we nodded, he added, “And those raiders he was talking about, those the same ones you were talking about?”

\leavevmode\llap{“}Yep,” Starlight said.

The bolt-action guard stepped up again, his smile uneven. “Well, now I \textit{really} want to hear that story.”

{\br}%
We spent most of the evening in the caravan’s suite, talking with the guards and crew. I even produced Gutrip’s notebook, showing the message in question. It got passed around, to muttered curses and dark looks.

If that hadn’t been enough to draw their sympathy, the story of Silverline and Quicksilver certainly was. Wagon Wheel was nearly in tears halfway through that part of the story, and shared a supporting hug with his wife, Summer Breeze. Scatter, on the other hoof, looked almost murderous.

Thankfully, the story put everypony on the same side, relieving the tension that had hung in the air. Soon we had all moved on to more pleasant stories. There was still the occasional bout of violence, of course. Fairwind, the guard with the bolt-action, told a story of fighting off a small band of ill-equipped raiders that had tried to ambush the caravan some years back. Listening to a story of four malnourished raiders charging a small caravan with machetes, throwing spears, and a single rusty shotgun, only to fail miserably in the face of superior firepower, seemed almost quaint in comparison to my own experiences.

Once again, I found myself spending a good while in quiet reflection at how I had come to such a point as to think of a life-and-death experience, however small, in such terms of insignificance.

But there were also more relaxed stories of simple Wasteland life. Various funny anecdotes and happy encounters filled most of the tales. There was always some undercurrent of the realities of the Wasteland, whether it was looking for food and water, or the simple tedium of being a guard on the watch for raiders and bandits, but the stories of regular life and happy times made me smile.

Sickle joined the gathering as soon as she learned of the dozen new ponies in town. It was clear enough that she’d been hitting the booze and chems; she smelled of alcohol, her pupils were mismatched in size, and she’d twitch and shudder on occasion. That said, she actually managed to be relatively pleasant.

Admittedly, “relatively” for Sickle meant she didn’t threaten to crush anypony’s skull or the like, and she didn’t pin anypony to the ground and sit on them when blatantly trolling for sex.

Given his prior interest in Starlight and myself, I wasn’t at all surprised when Scatter’s initial reaction of suspicion and distaste was replaced with interest in what she offered. It also didn’t help that Sickle practically sprawled between the guards—dwarfing all of them, even lying on her side—and started prompting them for stories of a more erotic nature.

We eventually split into two groups: those who remained with Sickle, telling tales of excess and prior conquests, and those of us who discussed less lecherous topics. It wasn’t too long before the tales in the other group came to the point that Sickle led Scatter and the two pipe-rifle guards—I never did get their names—back to her own room. I’d say she practically dragged them, given her own aggressive enthusiasm, but they didn’t show any signs of reluctance. Among those who remained, there were a few snickers and the shaking of heads, but nopony seemed to think too much of it.

It reminded me of the seedier stories I had heard about soldiers and sailors; away from home and loved ones for days, weeks, even months, then arriving in some town and seeking out whatever quick pleasures they could find in the brief window of opportunity.

They returned about half an hour later. Scatter walked in, rubbing a hoof at his snout and occasionally drawing a hoof back to look at it, as if expecting to find blood. One of the other guards was snickering and nudging his shoulder, while the other just looked kind of awkward.

Scatter finally lowered his hoof as he passed by us, giving us a disgruntled look. “Your friend’s kind of a bitch.”

\leavevmode\llap{“}Only kind of?” Starlight said with a snicker. “Wow. She must have really liked you.”

The rest of the gathering chuckled, and a fair amount of light-hearted ribbing followed, including some teasing at how desperate they must have been. It’s probably good Sickle hadn’t accompanied them back, as she likely would have maimed someone on principle.

The only one who didn’t show up at the gathering was Dusty. Even Emerald showed up a couple times, bringing some food and exchanging some friendly words with Wagon Wheel, but she seemed distracted and quickly excused herself. Not that I’m surprised Dusty avoided the gathering. After the mention of bounties and the discussion that had followed, his presence would probably be awkward for all involved.

It occurred to me that I had a bounty on my head, too. That was certainly a first. Admittedly, the bounty was for Whisper Winds, the earth pony, not Whisper, the changeling, but I’d put a lot of commitment to my current alias. I could shake the bounty with a simple change of form, but it was an option I’d rather avoid.

There was at least some dark humor that, if somepony did kill me, they’d be faced with the difficulty of convincing other ponies that the bug-creature they brought in was the earth pony they were trying to claim the bounty on; it seemed unlikely that they would be able to profit from my death.

That wasn’t much consolation.

Deciding to check up on Dusty and discuss a few things about our newfound criminal status, I excused myself from our little gathering. While Starlight stayed to talk with the traders, I made my way back to our suite.

Dusty wasn’t there, but Sickle was, lying against the outer wall with a foreleg hanging out the window, and looking precisely as if she had just had wild and vigorous sex with three different stallions in rapid succession. Her head wobbled as it turned my way, her pupils pinpricks despite the dim lighting, and she smiled upon seeing me. “Wiiiisp,” she said in a quiet and almost dream-like tone. She raised a hoof, beckoning me over. “Wisp, c’mere.”

I took a hesitant step forward. “Are… you okay?”

She gave a quiet chuckle, her head leaning to the side to rest on the edge of the window, and her hoof dropped to her side. “Yeah, I’m good.” Her eyes shifted, staring off into space. “I think the buck wore off.”

\leavevmode\llap{“}Something’s still working,” I noted, and she cracked a smile again.

\leavevmode\llap{“}Yeah, I loaded up on painkillers. They’re great for relaxing.” She trailed off, once again staring off into space. A small frown slowly formed.

I took another step closer. Even with the excessive amounts of drugs likely involved, such erratic swings in behavior are always concerning. “Is something wrong?”

\leavevmode\llap{“}Nah,” she said. “Just thinking.”

I immediately imagined all the snarky things Starlight might say in response to that, ranging from comments on smoke or grinding gears, to simple expressions of concern.

Sickle, oblivious to my thoughts, beckoned with her hoof again. “C’mere already.”

\leavevmode\llap{“}What were you thinking about?” I asked, taking another cautious step forward.

\leavevmode\llap{“}Eh, nothing,” Sickle drawled, then immediately contradicted herself. “That green bitch.”

I halted, ears perking up. “Emerald?”

\leavevmode\llap{“}Yeah, green bitch.” She stared out the window, blinking a few times. “She thinks I’m a good pony or some shit.”

I moved up beside her, looking on with curiosity. “She does?”

\leavevmode\llap{“}She’s stupid.” Sickle blinked a few more times before realizing how close I was, then smiled as she reached out. I was too close and too slow to react as she looped a foreleg around my shoulders and dragged me off my hooves. I ended up laid out against her side, pinned under a heavy foreleg.

Her head wobbled as she leaned over, her eyes struggling to focus on me, and giving me a face-full of sour breath as she spoke in a low, slurred voice that I assume was supposed to be seductive. “Hey, you want to do your shape thingy and change into that big-ass stallion? Bet you could put all three of those little colts to shame.”

My ears pinned back as I frowned at her. “I’d rather not, thank you.”

\leavevmode\llap{“}Oh. Okay.” Her tone was disappointed, her smile fading a bit. She shifted her position. Her leg lifted from my chest, but before I could capitalize on my freedom, her hooves had closed on my sides, and she bent down, shoving her massive muzzle between my hind-legs.

\leavevmode\llap{“}Hey!” I snapped, planting my hooves on her head and shoving. “Sickle, knock it off!”

\leavevmode\llap{“}Settle down,” she mumbled, shaking her head to throw off my hooves and pressing in again, her snout practically ramming against my groin.

I kicked and twisted, my heart pounding. “Sickle! Stop it!”

Her head twisted as I shoved, shaking off my hooves again, and I kicked wildly to push her away, but she ignored it. “I’m just trying to—damnit! Stop squirming!” Her hooves tightened around me, pinning me to the floor as she pressed in again, overpowering any attempt I could make to stop her. “Settle down, I—ow!”

One of my wild kicks had managed to catch her in the neck, and while I doubt it did anything to harm her, it was apparently just enough to catch her attention. Her head snapped back, eyes wide and blinking, as if surprised by the blow. Then her expression hardened into one of furious rage.

She hit me.

I know this only from later deduction, as I have no memory of the blow itself. The whole transition from that look of rage to what came after is a jumbled mess of confused thoughts.

The brain does strange things when recovering from unconsciousness.

For some undecipherable period of time, I was convinced I was walking through a tunnel leading out from my hive. In that dreamlike state, the faint, wavering light in front of me was the end of that tunnel, leading out into the open air beyond. My face felt odd, as if there was some weight resting across it. I thought it was wet. I drifted through the tunnel like a ghost.

Slowly, the feeling of my body manifested once again. Something touched the side of my face, which I was slowly coming to realize felt \textit{wrong}. My eyes cracked open, returning a blurry view of a silhouette before me. The lip of a bottle touched my lips, a cold fluid splashing into my mouth. I drunkenly reached up to grip at the object, holding on as I swallowed.

A tingle ran through me, mostly my face, and the world slowly coalesced. The light I had been following through the tunnel revealed itself to be the bare bulb hanging from the room’s ceiling. The taste that lingered in my mouth was that of a healing potion. The silhouette looming above me was Sickle.

Her ears hung low, and her expression was one I had never seen on her before: concern. It struck me as completely bizarre, even as my brain struggled to come up to speed.

As I was slowly piecing together exactly what had led to that moment, Sickle spoke.

\leavevmode\llap{“}Sorry.”

The ember of anger that was flaring up, ready to consume my emotions, was instantly snuffed out. If it had been anyone else, that one word, on its own, would have been grossly insufficient, but this was Sickle. Rather than showing any form of contrition over the terrible things she had done, she wore them with a sense of pride.

Now she looked ashamed.

I lay there for several seconds, blinking as my eyes finished focusing. “...What was that—” I halted immediately; my voice was wrong. I lifted my head to look down at my black, hole-filled hooves, still clutching the bottle of the healing potion Sickle had fed me.

My head reeled, and I laid it down again with a soft groan. The surface it met was soft. I was lying in a bed.

Sickle rumbled, her voice low and quiet. “You changed when I hit you,” she said. “I thought I might have killed you.”

I focused on breathing for a couple of seconds, until my head cleared up, and tried speaking again. “What was that all about?”

She grunted faintly, rolling her jaw. I could see her eyes better; the pupils still looked constricted, but much less so than before. Finally, she grumbled. “I just… I dunno, wanted to do something nice for you.” She looked away, reaching up to wearily rub a hoof at the side of her face. “Sure fucked that up.”

My ears pinned back. “And that was supposed to be something \textit{nice?}”

She grimaced. “...Shit. The only things I’m good at is fighting and fucking. I know you had fun fucking Star. Thought maybe you’d like some more fucking. It made sense at the time. Dunno why…” Her face slowly contorted into a grimace. “And fuck, it ain’t like that kick even hurt! I just got so pissed off…”

The look of anger quickly bled away, leaving her staring blankly at the floor.

I stared at her for a long time. A part of me wanted to snap at her; to just verbally lay into her over what a stupid idea it had been. The more logical part of my mind recognized how pointless it would be. She was already making an unprecedented apology. Venting might be cathartic, but it wouldn’t be productive.

So instead, I asked, “Why did you want to do something nice for me?”

She shrugged weakly, without answering. Several seconds passed before she turned further, presenting her back to me, and flopped down on her side. The impact jostled me and produced a loud screeching groan from the bed, but the tortured piece of furniture held.

After a long silence, I spoke again. “Sickle?”

Still no answer.

Eventually, I rolled to my side and weakly pushed myself up. My head spun, my heartbeat loud in my ears, but I eventually made it. Touching a hoof to my sore muzzle revealed that it was sticky with congealing blood.

I looked around. I was in Sickle’s room, which was littered with empty cans, various alcohol and pill bottles, and the thick slabs of metal that formed her armor. It took a moment to find the wash basin, and my horn lit up, floating over a washcloth. Even that minor effort sent a faint throb through my head.

Sickle continued to lie there, her eyes half lidded as she stared at the wall.

I had cleaned away most of the blood when Sickle finally spoke.

\leavevmode\llap{“}I’m leaving in the morning.”

I finished wiping away the blood that had run down my cheek, and floated the washcloth back over to the wash basin. Then I looked to her. “Why?”

Her eyes closed. “‘Cause I’m going to kill one of you if I don’t.”

\leavevmode\llap{“}...You’re scared something like this will happen again.”

Her jaw tightened. “I ain’t scared of shit.”

I quickly rephrased that in a more palatable fashion. “You’re concerned for our well-being.”

She slowly relaxed, and eventually grunted. “Yeah. Sure.”

I reached out, gently resting a hoof on the side of her thick neck. “You’re not used to caring about other ponies, are you?”

She gave a faint snort that I took as an affirmation.

\leavevmode\llap{“}I’m guessing you haven’t had many friends before?”

She went still, her eyes opening again. For a moment, she didn’t move, or even breathe. She simply stared at the wall in front of her. Then she took a long, slow, breath, and spoke. Her words were quiet, but hard. “There’s only been one pony I ever thought of as a friend, and I beat him to death.”

\leavevmode\llap{“}...Was it—”

\leavevmode\llap{“}On purpose,” she said. “And I was sober. And I made sure he suffered.”

The muscles of her neck had tightened under my hoof. A tremble ran through her body. Cautiously, I asked, “What happened?”

Her ears flicked, and she closed her eyes.

When it was clear I wasn’t getting an answer, I changed tracks. “Don’t leave.”

\leavevmode\llap{“}...Why not?”

I stroked my hoof gently along her neck. “Because when you’re not being intentionally grotesque or trying to smash my face in, I’ve come to somewhat like you.”

She snorted. “So, what, when I’m asleep?”

\leavevmode\llap{“}No,” I said. I scooted forward, gingerly lowering myself to lie against the back of her shoulders and neck. My foreleg rested gently across her neck, while my head rested against the back of hers; I ignored the dirty, oily smell of her scraggly mane. “When you set aside the whole emotional armor thing you’ve built up, and try to be friendly.”

She was silent for a long time before giving a soft huff, deflating as the tension in her body slowly faded away. After that, she remained still and silent.

I remained there, slowly stroking along her neck as she lay there, until I drifted off into unconsciousness once more.

{\br}%
I distantly heard the sound of the door shutting, and the soft clopping of hooves on the wooden floor. A hoof touched my side, giving a gentle but firm shake, and words pierced the fog of sleep to reach my groggy brain.

\leavevmode\llap{“}Whisper, put your disguise on.”

It was Dusty’s voice. I groaned something unintelligible and slowly focused on my magic. My head throbbed as I did so, but a few seconds later, my magic washed over me, transforming me into my favored earth-pony guise.

I rolled onto my back, my foreleg sliding away from Sickle’s neck, and slowly blinked up at Dusty.

\leavevmode\llap{“}You need to get up,” Dusty said, his expression serious. “We have a job.”