I staggered blearily from Sickle’s room, squinting against the morning light that shone through the open window. Even dulled by the ever-present clouds, it was uncomfortably bright to me. My head felt better than it had the night before, but the headache still lingered in the background, and I found my balance wasn’t quite as it should be. Despite the handicap, I made my way to the table and collapsed onto one of the chairs, groaning softly. Dusty was still in Sickle’s room, and I could hear him trying to rouse her.

It was then that I realized Starlight was sitting at the table as well, wearing an expression of concern. Only then did I realize how the situation must have looked.

I groaned softly, raising my hooves to rub at the side of my head. “Okay,” I murmured. “Just so there are no misconceptions, no, we didn’t have sex. Sickle is… well, I’m not sure exactly what’s going on with her, but I think she needed someone to be there for her last night.”

Starlight cocked her head to the side, staring at me as if I’d just babbled gibberish. “...Seriously? Sickle?”

\leavevmode\llap{“}Yeah,” I grunted, letting my hooves fall to the table. I slowly sank down until my head rested on the surface. “It’s… I don’t know. I’m not even sure what to think of it. Something’s wrong.”

\leavevmode\llap{“}Well, yeah,” Starlight said. “It’s Sickle. There’s probably a \textit{lot} wrong.” She was frowning. “Are you okay?”

\leavevmode\llap{“}Yeah,” I repeated. Then, “I think I might have a tiniest bit of a concussion.”

\leavevmode\llap{“}A \textit{concussion?}” Starlight sat upright, ears standing alert. “What the hell happened? Did she hit you?”

\leavevmode\llap{“}Yeah,” I said once more. When Starlight’s expression grew more surprised, I hastily added, “Though I kicked her first. But that was because… uh, it doesn’t matter. It’s all taken care of.”

\leavevmode\llap{“}Taken care of?” Starlight said, as if it was the dumbest thing she’d ever heard. “You’re nearly passing out on the table because of a concussion and it’s \textit{taken care of?}”

\leavevmode\llap{“}I’m just groggy and waking up still,” I weakly replied. “And she said she’s sorry.”

\leavevmode\llap{“}Oh, well that makes it all better! She’s—” Starlight halted, blinked, then turned another skeptical expression my way. “Wait, she said she’s sorry? Like, she used those actual words and everything?”

\leavevmode\llap{“}Yeah,” I said, one more time.

Starlight sat back in her chair, blinking. In the end, the only reply she could come up with was a distant, “Huh.”

I slowly pushed myself up, wobbling a little, but held. “Look, I’ll take care of… whatever it is going on with Sickle. Don’t worry about it. What’s this ‘job’ Dusty was talking about?”

\leavevmode\llap{“}Not a clue,” Starlight said with a shrug. “He just woke me up, told me we had a job, then went to get you two.” She grit her teeth. “He better not have taken a job from Amber.”

I groaned again, sharing her concern.

It was a minute before Dusty returned with Sickle in tow. She plodded along after him, her expression tired and dark, brows furrowed. I’d seen her angry several times before, but I don’t think I’d ever seen her looking grumpy. Something about it struck me as incredibly dangerous, as if she might simply beat to death the next pony to commit the offense of being cheerful in her presence.

Starlight looked my way, quirking an eyebrow questioningly, but I just shrugged.

We followed Dusty downstairs to one of the inn’s back rooms, and filed in one at a time. Inside, I was surprised to meet not Amber, but Emerald.

\leavevmode\llap{“}Good morning,” she said, giving a halfhearted smile. “Have some coffee.”

I eagerly took one of the cups and downed its contents, and started in on a second as we got situated at the table. Sickle simply sat on the floor beside the table, looming like a dark cloud off to our side. Her eyes remained fixed on Emerald the whole time.

\leavevmode\llap{“}So,” Dusty said as he set his cup down, his hooves placed evenly on either side of it. “What in the wild world of Equestria do you want to hire us for?”

\leavevmode\llap{“}Saving some lives, I hope,” Emerald said, her smile fading.

Dusty gave a smile that looked more like a grimace. “So you’ve said. I was hoping for a little more detail than that.”

\leavevmode\llap{“}Of course, sorry. I’m… not terribly used to this sort of thing.” She cleared her throat, repositioning herself, and spent a few seconds fiddling with her cup before quickly setting it down. “There’s some farmsteads nearby. I learned that one of them was hit by raiders in the last few days. I know the couple that lives there, Quartz and Flint. They’ve got a couple of foals. I want to make sure they’re safe, and since there are raiders out, I’d rather like to have some capable ponies around in case they come across me.

\leavevmode\llap{“}So I want to hire you to accompany me to their farmstead. If the raiders took Quartz and Flint, then they need to be rescued. And… and I want you to make sure these raiders are never able to do something like this again.”

Dusty slowly nodded. “Yeah… yeah, we might be interested in that. Though, no offense, but it might be better if you stay in town. We can check on them for you, and if we get in a scrap with a bunch of raiders, it’ll be safer if you were back in town.”

\leavevmode\llap{“}I appreciate that, hon,” Emerald said with a sad smile. “All the same, I need to go there myself. I know what kinds of things raiders can do to a pony. I’m sure they’ll appreciate a group of well-armed ponies galloping to their rescue, but they’re going to need a friendly face. ‘Sides, it’s all well and good to talk about ideals when I’m hiding behind a wall.”

\leavevmode\llap{“}I suppose so,” Dusty said. “All the same, it makes the job a fair deal more complicated than it needs to be.”

\leavevmode\llap{“}Oh.” Emerald looked down to her cup again. “Sorry about that, but I’m afraid I’m going to have to insist. I need to be there. If it’s any consolation, I’ve spent my time out in the Wasteland, on my own, sometimes for months at a time. Those are lessons I don’t think I’ll ever forget.”

Dusty frowned, idly tapping a hoof against the table. “Well… can’t say I like it, but if that’s what you’re hiring us for…” He looked back to us. “Sound good with all you?”

Starlight nodded, as did I.

\leavevmode\llap{“}Yeah,” Sickle rumbled, without any apparent enthusiasm. She was still glowering at Emerald.

\leavevmode\llap{“}Okay then,” Dusty said, turning back to Emerald. “We’ll need to discuss some conditions, but for now, let’s go with it.” He leaned forward, crossing his forelegs on the table. “Now let’s hear the details of this job.”

Emerald extended her leg, displaying her PipBuck and the map on its screen. She’d already prepared a set of markers, highlighting a pair of locations out in the Wasteland. “The farmstead is about half a day to the southeast. I’m not sure exactly where the raiders call home, but it seems they’re based further south, likely in one of the ghost towns near this other mark. I can copy all of these over to your PipBuck, too.”

\leavevmode\llap{“}Thanks,” Starlight said with a nod, still staring at the screen. “That’s a long ways from town if raiders are around. Why were they out there?”

\leavevmode\llap{“}Not much choice,” Emerald said. “There ain’t so many places you can grow crops nowadays. Quartz and Flint got a working well. Barely enough water for some small fields, but it feeds their family with a bit spare to trade. I’m guessing the raiders decided the food should go to them, instead.”

Dusty hummed softly. “What do we know about these raiders?”

\leavevmode\llap{“}Not much, I’m afraid. They’ve been hitting the occasional trader and farmstead, but this is as close as they’ve come to Gemstone. They’ve let some ponies go alive, too, always with some warning about what happens to ponies that fight back, so I’ve heard a few things. They’re led by some mare named Boomer, and they seem well-equipped for raiders. From what I’ve heard, they’ve cobbled together a bunch of heavy armor and have a real thing for explosives.”

\leavevmode\llap{“}Boomer?” Starlight echoed. “What a dumb name. Wonder if she’s related to Banger?”

\leavevmode\llap{“}We’re not that lucky,” Dusty said, then turned to Sickle. “You know anything about Boomer?”

\leavevmode\llap{“}No.”

Dusty hesitated a moment, then shook his head and turned back to Emerald. “Any idea on numbers?”

\leavevmode\llap{“}Sorry,” she said. “The stories are all over the place. At least six, maybe double that.”

\leavevmode\llap{“}Not much to go on.” He stared down at the map, frowning, but finally nodded. “Yeah, we can work with that. You’re sure they’re based around here?”

\leavevmode\llap{“}Not entirely, but the areas they’ve hit form a nice semi-circle around that area.”

\leavevmode\llap{“}Makes sense,” Dusty said. “Raiders tend to be lazy about setting up shop. From what I saw with the Militia, they always seem to establish themselves in existing structures rather than build anything from scratch, and I’m not seeing many other places they could commandeer.” He sat back. “On the plus side, raiders also tend to be incredibly unsubtle. If they’re in the area, we should be able to find them, assuming we can’t track them from the farmstead.”

Normally, I’d expect Sickle to chime in with some comment, but she remained silent.

There were only a few more questions, such as descriptions of Quartz and Flint, and any other details Emerald could come up with. It was very brief.

\leavevmode\llap{“}So that’s about the sum of it,” Emerald said. “Which I guess brings us to the matter of pay.” She produced a large sack, loaded with several pounds of bottle caps, and set it on the table. “Fifteen hundred caps, to check on the farmstead and eliminate those raiders.”

Dusty slowly nodded. “Suits me fine,” he said, while Starlight and I nodded. “Still seems strange, you hiring some ponies to kill some other ponies, with all that Kindness and Generosity talk.

\leavevmode\llap{“}Believe me, hon, I understand.” Emerald’s ears hung low. “I’d love to find some peaceful solution to this situation, but allowing somepony to be hurt because you refuse to act isn’t showing anypony Kindness.” She gave a weak, halfhearted smile. “At least I can make a claim to Generosity by offering some of my savings to help these ponies.”

\leavevmode\llap{“}Don’t get me wrong,” Dusty said. “I think it’s the right thing to do. Hell, I feel a bit scummy taking your caps when there might be lives on the line.”

Emerald quickly shook her head. “I wouldn’t ask you to do this for free. It’s a dangerous business, and if you’re going out there to risk yourself for strangers, you deserve all the material reward I can offer.”

Dusty looked back to us. “Well, I’m up for it. You guys?”

\leavevmode\llap{“}I’m good,” Starlight said.

I nodded.

Sickle made a single grunt.

\leavevmode\llap{“}Well, good,” Emerald said as she stood. “I’ll go get my stuff and meet you out front when you’re all ready to go.”

\leavevmode\llap{“}No, hold on there,” Dusty said, raising a hoof. “We aren’t quite done, yet. Like I said, if we’re going to take this job, and you’re insisting on going out with us, then we need to set some conditions.”

Emerald hesitated, but nodded. “I suppose that might be fair. What conditions?”

\leavevmode\llap{“}Just the one, I suppose.” Dusty gestured a hoof in the general direction of the town gate. “As soon as we’re outside those walls, you follow my orders to the letter. If I tell you to do something, I need you to do it right then, no questions asked, no hesitation, no second thoughts. Got it?”

Her ears flicked back. “Well, I guess that depends on what sort of thing you’re asking me to do.”

\leavevmode\llap{“}No, it doesn’t,” Dusty said, his expression firm. “And it won’t be asking, it’ll be telling. You’re asking us to go with you into a dangerous situation, where something can go wrong without any notice. You might be the kindest, most giving pony I’ve ever met, but when it comes to fighting, I don’t know a thing about you.”

He swept his hoof back to indicate the rest of us. “I’ve fought with these ponies. I know what they can do, and I trust them to do their job. I don’t know you like that, and that means you’re a liability. If you do something wrong, or something unexpected, or even just hesitate at the wrong moment, it could be one of them that ends up paying for it. If you’re going with us, I need to know you’ll follow my orders, whatever they are.”

Emerald was frowning by the time he was done. She reached out to hold her cup again, slowly rolling it between her hooves. “I think you’re a good pony and all, but you’re asking for a lot of trust, there.”

\leavevmode\llap{“}I’m not going to tell you to do anything immoral,” Dusty said, “but you’re asking me to trust my life and the life of my companions with you. If we’re going to do this, you’re going to have to show the same trust back.”

Emerald chewed her lip, thinking, but finally nodded. “Fair enough. You have a deal.”

Dusty slowly nodded. “Then there’s one last thing I need you to consider.”

\leavevmode\llap{“}What’s that?”

\leavevmode\llap{“}I can not guarantee your safety,” Dusty said, slowly and clearly. “I’ll do everything in my power to keep you safe, but there are no guarantees in this business. You can stay here, and you’ll be safe, but if you insist on coming with us, you’re going to be in danger, and there might not be a single thing we can do about that. You need to be perfectly clear that having some ponies guarding you doesn’t mean this is safe, okay?”

Surprisingly, Emerald replied with a soft smile. “I understand, hon. Heck, couldn’t really say I’m living up to Generosity if I’m not willing to give something, could I?”

When she was met with Dusty’s critical look, she replied in a more somber tone, “I understand, and I’m still going. I’m willing to accept that risk.”

Dusty contemplated her a moment longer before nodding. “Okay, then. Gear up.”

{\br}%
I stepped out of the store and into the chilly morning air, all geared up and ready to go. My saddlebags rested a bit heavier, loaded with four days of food and water, plus half a case of spare rifle ammunition. My ammo pouch rested against my chest, the magazines all topped off, with a pair of grenades tucked in alongside them. My electronics were stashed in one bag, and a small collection of explosives were stashed in the other. My medical box was once again serving its original purpose, holding a pair of healing potions safely inside it. And my rifle, with its new suppressor attached, hung from the strap around my neck.

It was an absurd abundance of equipment compared to what I was used to, especially when most of it was intended to kill ponies, but I found the weight comforting.

Other than the new armor and the location of her PipBuck, Starlight looked no different than when we had first met. She gave me an awkward smile, which I mirrored. We both sat on the store’s porch, waiting. Dusty was still inside with Emerald, going over her equipment. My head was feeling a little better, though a headache still lingered at the edge of my perception, lurking like a shadow.

The dull thump of heavy hooves and the clattering of metal on metal preceded Sickle’s arrival. She emerged from the front door with a tight frown half hidden under her muzzle. It was hard to read her expression under her helmet, but I had the impression of her glaring out through those eye slits.

She was walking past me when she halted, her head turning to me. “Whisper.”

My ears flicked back as I looked up at her. She jerked her head to the side, then turned and walked in that direction. The message was clear.

I placed a hoof on Starlight’s side. “Wait here. I’ll be right back.”

She gave a worried look, but nodded, and I stood to trot after Sickle.

Falling in beside her, I asked, “What did you—”

\leavevmode\llap{“}Shut up,” she rumbled. Her tone wasn’t sharp or angry; if I had to describe it in a word, that word would be ‘dark’. My mouth snapped shut so quickly you could hear my teeth click.

We walked in silence, until we reached a small, dusty clearing, tucked in behind the town’s wall and well away from where most ponies traveled. She came to a halt and sat with a crash of metal.

\leavevmode\llap{“}Sit down.”

I obeyed, sitting beside her.

For almost a minute, we sat in silence, save for the soft clinking and scraping of her armor shifting with every breath. She sat staring at the ground ahead of her. Under her helm’s muzzle, she was still frowning, her teeth clenched as if holding back her anger. At that moment, the only thing that seemed more dangerous than sitting next to her was trying to leave.

Then she reached up. Her hoof caught the clasp at the side of her helm, undoing it with a soft click, and she shook off the muzzle to hang against her neck. She returned to staring at the same point for a couple more seconds before speaking. “You’ve been asking a lot of questions.”

My ears flicked back nervously. It sounded like an accusation, especially with the hint of tension in her voice. I had no idea if she expected me to answer or remain silent, but I carefully offered a quiet and inoffensive reply. “Yeah, I have.”

I also silently tried to plan my escape, if things went poorly. None of those plans were terribly optimistic.

There was another pause of silence before the metal plates rattled and scraped a little louder; she drew in a deep breath, let it out in something halfway between a sigh and a growl, and spoke again. “My dad got sick when I was fourteen,” she said, and my ears shot up. Plans for escape and evasion were immediately shelved as I focused my full faculties on the words she said.

\leavevmode\llap{“}It was really bad. He couldn’t even stand. Mom had me and my little sister watch over him while she went to town for medicine. Should have been a couple days each way.

\leavevmode\llap{“}Dad died a week later. We waited another week before we were sure mom wasn’t coming back. We were pretty much out of food, so we set out in the same direction mom did, looking for any signs of life, or even some old place we could scavenge from.”

She huffed faintly. “Sis only made it four days. We were both starving. We dug through a bunch of buildings, but none of them had shit in ‘em. Then we went in one, and the floor broke under my fat ass. Fell into the basement with all the junk and shit down there. I was fine, just some scrapes and bruises, but sis… she got a broken leg, and sliced up her side on some nails or something. Just a couple little cuts, but we couldn’t get the bleeding to stop.

\leavevmode\llap{“}I kept going. Found some ugly looking plants to eat that only made me a little sick, but it was food. Managed to live off that for a few more days. I dunno, maybe a week? Finally crushed some stupid spitting fly thing. Tasted like shit, but it was the first good meal I’d had since leaving home.

\leavevmode\llap{“}Anyway, a couple days later I finally stumbled into some ponies, with a nice walled-off fort.” She snorted. “Yeah, ‘cept I was too happy to find ponies to notice all the spikes and skulls and shit. Walked right up to a fucking raider camp and said ‘hi’. Must have made their fucking day.

\leavevmode\llap{“}So yeah, they grab me, all laughing and cheering over their luck. Bunch of ‘em pin me down, then they start arguing over who gets me first. That’s when this one asshole shows up. He was pretty much the boss’s second-in-command, but nopony liked him, ‘cause he was the kind of asshole that always pulls rank to get what he wants. But, you know, the boss said he outranked them, so they have to let him have first crack at the pony they caught.

\leavevmode\llap{“}So he fucked me,” she said. My ears pinned back, but otherwise, I forced myself to remain silent and neutral. “I just went still, let him finish. Soon as he pulls out, he’s all grinning and boasting to everypony else, and that’s when I kick him as hard as I fucking can. And yeah, I wasn’t as big as I am now, and was pretty light on food, but I was still big and strong. Caught him right with the edge of the hoof, too, right in the junk. Tore off one of his balls and cut him open good. Blood all over the place.”

Her lips curled back, baring her teeth. “He went down, and I got on top of him and just started beating the fuck out of him. And you know, the other raiders hated his ass, so they were all laughing and cheering me on, like it was some show. I’d beaten him till he couldn’t move before they finally decided he’d had enough and grabbed me again.

\leavevmode\llap{“}‘Cept then, the real boss showed up, made ‘em stop. He was a big fucker.” She lifted a hoof to thump against her chest. “‘Bout as big as me now. And him, he liked what he saw. Said some bullshit about… beautiful rage or something. You know what he did?”

Her head turned to look at me. I nearly winced, and gave a tiny shake of my head.

She turned away again. “He offered me a place in his gang. I’d beat the shit out of one of his best ponies, so he thought I’d make a good replacement. Guess he saw potential in me or some shit. I’d get to be his… I dunno, apprentice or whatever the fuck you’d call it. Hell, he even offered to let me finish off that asshole that fucked me. And you know, I was still so fucking pissed, I went for it.” She lifted a hoof, thumping it down into the dry dirt. “I just kept hitting him until I’d crushed his skull to paste.”

She let out a dry, humorless chuckle. “‘Course, a couple of those cunts whined that they didn’t get the chance to fuck me. The boss? Heh, he tells them they can fuck me all they want. ‘Cept then he points to the pony I’d just beat to death, and told ‘em all that I might do that to them if I didn’t like it. And I’m just sitting there all blood-spattered, panting, and glaring back at those fuckers, and you know what I saw?”

Her mouth slowly parted in a savage grin. “They were scared of me. Not like… terrified or some shit, more like… I dunno, respect for how strong I was. Heh. That morning, I’d been lost, alone, barely making it day to day, and now? Now I had twenty fucking raiders around me, and they were all \textit{scared} of me. I felt like I was the baddest fucking pony in the Wasteland. Like nothing could fucking touch me any more. I \textit{liked} it.

\leavevmode\llap{“}‘Cept, you know, they still tried to fucking rape me. So the next morning, I walk down from the boss’s roost, grab the first one of those dipshits I come across, pin him down by his neck, and fuck his little pea-brain out. Right in front of everypony, give ‘em a good show. Sure enough, one of the others tries to get some. I give him one warning, then I beat his ass until he can’t walk. And you know, the boss is kinda pissed that I broke \textit{another} of his goons, ‘cept he goes down and kicks the guy’s ass himself for trying shit after he warned their asses about what would happen.

\leavevmode\llap{“}So yeah, message delivered. Heh. Nopony fucked with me.”

She paused, her smile slowly fading away as she thought. “...Went on my first raid, what, a week later? I dunno. Some dinky little caravan, only had two ponies. They killed one of ‘em, grabbed the other. Some young stallion, kinda scrawny. Half the gang started tearing through their cart, but the others decided to have fun with him. Beat the shit out of him, then started fucking him.”

She huffed faintly. “Hell, couple times I thought, maybe I should feel more, you know, sympathy or some shit. I’d almost been there. ‘Cept I wasn’t. I was stronger than those other raiders, so I came out on top. Except I wasn’t just stronger than them. I was stronger than everypony. \textit{Everypony}. And that scrawny little fucktoy was another reminder of that. I wasn’t some helpless little bitch. As long as I had ponies like him squirming under my hoof, I was in charge.

\leavevmode\llap{“}So I dived right in and helped them out. Hell, it was fun.”

I sat silently, trying not to fidget or edge away as she described these horrible things. Even knowing that she had been a raider wasn’t enough to prepare me for hearing her discussing those things so casually. And yet, as uncomfortable as I was over the topic itself, I listened intently; every word she said helped me understand her a little better, and maybe even raiders as a whole.

\leavevmode\llap{“}Pretty soon, I was looking to prove myself. Every time we went out on a raid, I’d look for the meanest motherfucker out there and go head-on with ‘em. Every time, I’d come out on top. Got torn up pretty good a few times, but the boss made sure I got the best armor they could cobble together, then set me loose to tear shit up. Even started calling myself Sickle, ‘cause it sounds more dangerous.

\leavevmode\llap{“}Got into chems during some dull stretch between raids. Getting drunk and fucking half the camp was a good way to pass the time. Never had any problems getting rutted. Guess it ain’t surprising, it was almost all stallions, and they were a horny bunch of cunts. Bunch of them, and just four mares before I showed up. Heh, and two of those bitches didn’t last long once we started butting heads. The stallions, though, once they got it through their thick heads that I was above them, we got along great. So long as I got my share of the chems, they could have everything else, and I was always up for a quick fuck. Hell, everypony wanted to be in when I was leading a raiding party. You ain’t ever had a good rutting like a half dozen blood-crazed raiders after a good hard fight.”

She paused, her pleased smile slowly fading away before speaking again. “It was the boss I really liked, though. He taught me how to fight, helped me grow strong, got me some good armor, all that shit. Introduced me to Buck, too. That helped a lot with the ‘getting stronger’ part. He liked me, too. Said it was ‘cause I was like him. Said I was the biggest, meanest cunt in his gang, just like him. Said a bunch of… what’s the word?”

She tapped her hoof on the ground a couple times before saying, “Philosophical. Yeah. He liked his philosophical shit. He said I was better than all those other ponies, because I wasn’t scared of the Wasteland. ‘Cause I’d run right out there and beat it into submission, while other ponies try to hide from it. Said a lot of other stuff, too. I dunno, most of it was bullshit, but he liked me.

\leavevmode\llap{“}And holy shit, the sex.” Her mouth split into a grin again. “He was the best fuck I’d ever had from a pony. Spot’s the only one who’s ever matched him. I mean, we were big fucking ponies. If I went all-out on any other pony, I’d just break ‘em. Yeah, sometimes that’s fun and all, but shit, sometimes you want somepony who can give as good as they get. But with each other? We could go fucking wild. There were times we’d walk away bruised and bleeding. Hell, first time I tried Dash, we ended up breaking down the fucking wall!” She snickered, but after a few moments, her smile started to fade again. Before long, she was expressionless, staring once more at that same spot in the dirt.

\leavevmode\llap{“}...Some raiders like collecting trophies,” she said, her voice quieter than before. “Usually some body part. Ears, teeth, skulls. Him, he collected cutie marks.” She lifted a hoof, brandishing the blades welded to her leg armor. “He’d take his blades, and cut them right out of their flank. Most of the time, he’d do it when they were still alive and kicking. He said… he said he wanted them to know. He wanted them to know that he wasn’t just taking their life, he was taking what made them… \textit{them}, like he was taking their soul. Said some bullshit about it making him stronger, or showing that he was stronger, or whatever. That philosophical shit again. And hell, he had a fuckton of ‘em before I’d even got there, and he just got more over the years. Must have been a couple hundred, just this giant pile of little, colorful hides. Some of the others in the gang even pitched in, cutting off the cutie marks of their kills to give to him, like… tribute, I guess.

\leavevmode\llap{“}I never really paid much attention to it. I did it too, just ‘cause, you know, why not? It made him happy, and it was fun. But that’s about all I cared about ‘em. They were his thing, not mine. Once they went in the pile, I barely ever looked at ‘em again. There were some that had been there for years, and I never even saw them.

\leavevmode\llap{“}But sometimes I’d get really bored, run out of chems and stallions, and I’d need something to do. So there were a few times I’d laze around and hoof through a bit of his collection. Sometimes I’d recognize a cutie mark, maybe from some pony I’d beaten down, maybe from a fight he’d gotten into. A few came from fights we’d both been in. Those were my favorite, mostly ‘cause they usually ended with us fucking.

\leavevmode\llap{“}Then this one time, I found another cutie mark I remembered. It was years old by then, all tattered and faded and shit, but I could make it out. It was an ice-cream cone on a faded pink coat.”

She paused, taking a slow, deep breath, before speaking again. Her voice was quiet, but hard as steel. “It was my mom’s.”

Her jaw was tight, her teeth clenched, and I could hear the faint shudder of her breath as her fury welled up. I remained as still and silent as possible, to avoid drawing any attention toward myself. I didn’t even breathe. At that moment, as she seethed beside me, I was certain a single wrong word or gesture could lead to a grisly death.

\leavevmode\llap{“}I hurt him,” she said in a low growl, her spiked hooves grinding into the dirt beneath them. “And it wasn’t some pussy-ass slow shit. I fucking let loose on him.” She lifted a hoof and stomped for emphasis. “He didn’t even see it coming. I snapped off his horn. I broke his legs. I beat him until my hooves hurt.”

Her armor rattled with the angry shudder of her body. “Couple of the others came in to see what was going on. I threw their fucking heads out as a warning to the others, then got back to work on him.”

\leavevmode\llap{“}But I didn’t just kill him.” She snorted, lips peeling back in an angry sneer. “No, I wanted to \textit{hurt} him. And you know, he was always going on about being stronger, about taking everything from a pony, all that philosophical shit. And the one thing he valued the most? His reputation. His name. He wanted to be the biggest, baddest, scariest motherfucker in the world. Some king of the raiders that everyone in the Wasteland would know and fear. He talked about it like it was some kind of fucking immortality, about how he’d still be there even after he was dead. He really thought he could do it, too.

\leavevmode\llap{“}I didn’t really give a shit about any of that, but he did, and I knew that was how I could \textit{really} hurt him. Broken bones weren’t shit. He’d taken so much from me, so I was going to take \textit{everything} from him.” Her hoof slammed against her breastplate. “I took the armor he was so proud of, wore it while I hacked away at his flanks until there wasn’t a trace of his cutie mark. I told him I was going to wear that armor, and \textit{I} was going to be the scariest motherfucker in the Wasteland, so that whenever somepony saw that armor, the only pony they’d think of was me.

\leavevmode\llap{“}I told him… that I was taking everything he’d built up, and burning it to the fucking ground. That I was going to go out there, kill his entire fucking gang, kill every raider boss he’d ever had dealings with, hell, kill every pony out there who even knew his fucking name. By the time I was done, there wouldn’t be a single pony who even knew he’d existed. He wasn’t going to have his ‘immortality’. I wasn’t just going to kill him. I was going to \textit{destroy} him. And he screamed and flailed all the way to the end. I was halfway through gutting him when he finally passed out.”

She shook her head, a quick, rough motion that rattled the armor plates, and took a few slow, deep breaths before continuing. “And yeah, I could have just left, or taken over, or any of that shit. He was dead, after all. Like I said, I don’t buy into that philosophical brahminshit. But I had a rule, ever since my first day as a raider: when I make a threat, I \textit{always} follow through. And he knew it. So I walked out of the roost, wearing the old boss’s armor, covered in his blood, and I killed every single motherfucker in that camp. I hung them around the place, pissed on their corpses, then set the whole place on fire and walked off.”

She fell into silence again, just breathing as she glared at the same spot in the dirt. I remained still and silent, waiting for her. Eventually, she huffed out a sigh and shook her head. “So… yeah. That’s how it all happened.”

I felt as if she were prompting me to speak, so, cautiously, I hazarded a quiet question. “And that’s why you’re killing raiders now, instead of being one?”

She gave a snort, cracking a smile. “Nah. That’s just why I killed those raiders. That was years ago. Now I kill ‘em because it’s fun.”

As the silence stretched on, I hazarded another question. “If you don’t mind me asking,” I said, hoping I was neither overstepping nor coming across as insensitive, “why did you decide to tell me all this?”

Sickle shrugged. “I dunno. It’s like… I guess I still wanted to do something for you, and you’ve been asking all these fucking questions. I figured this was better than smashing your face in. ‘Sides, already told you I killed my last friend. Figured I’d give the rest of the story.”

I stared up at her, and to my surprise, felt myself slowly starting to relax. “...Thank you.”

She grunted.

\leavevmode\llap{“}...Could I ask one more question?”

She grunted again.

\leavevmode\llap{“}If your name isn’t really Sickle, what is it?”

Her jaw tensed ever so slightly. “That \textit{is} my name.”

\leavevmode\llap{“}And before?”

She sat silently for a moment, frowning, but eventually answered. “It’s just shortened from another nickname.” She gave a quiet huff before cutting off my next question. “Popsicle.”

I blinked. “Popsicle?”

\leavevmode\llap{“}Yeah, it…” She paused, tensing up a little… and then slowly relaxing again. “It’s what my mom nicknamed me.”

She took a slow breath and started talking again. “She made ice cream. I know, it seems like the dumbest fucking thing to do in the Wasteland, but for a little filly it was great. She’d found this compressor in some ruins, and slapped together this crude freezer. Made treats for me and my sis. Was hard to find the ingredients for ice cream, but any time we found some canned fruit, or juice, or even just some old sodas, she’d mix it into some water and freeze it up, and we’d get popsicles.

\leavevmode\llap{“}So whenever she decided we got a treat, she’d call out, like, ‘Berry, popsicle!’ and I’d come running. Before long, it was just ‘Popsicle!” She joked I responded to it better than my real name, so she started calling me that.” She finished with a shrug.

\leavevmode\llap{“}Berry?”

Sickle froze, and for a moment, I was gravely concerned that I had stepped too far. Then she sighed. “Yeah,” she said, her voice tight. “That’s what my mom named me. Strawberry Shake.”

I’d like to thank my training and experience as an Infiltrator in giving me the skill to keep a straight face, even as my mind teetered between boggled skepticism and hilarity over the utter absurdity of it all. I’m certain neither of those reactions would have been welcome. Instead, I stared silently, responding only with a wary nod.

Sickle huffed, then stood with a clatter of metal. “Anyway, enough of this shit. Got a job to do.” She raised a hoof to walk off, then stopped. She set it down again and turned her head to stare right at me. “You tell anypony else any of this, and I’m stomping your ass.”

I quickly nodded again. “I won’t say a word.”

She stared at me for a couple more seconds before giving a sharp nod. “Good.” Then she started walking again.

\leavevmode\llap{“}Sickle.”

Part of me immediately regretted speaking up, but I knew if I didn’t then, I’d probably never say what I wanted to say.

Sickle stopped and looked back at me, and I, having committed myself, spoke again.

\leavevmode\llap{“}Since we’re having a bit of a… heart-to-heart here…” She snorted at that phrase, which gave me a moment of pause, but I pushed on. “What almost happened last night? That wouldn’t have happened if you were sober.”

She grimaced, staring at me for a long moment before finally speaking again. “Yeah. It wouldn’t.”

I nodded. “Good. I just wanted to make sure you were considering that.” Then I stood, approaching her. Outwardly, I did my best to remain calm and focused. I stopped right in front of her. Then, with a quick breath to steel my nerves, I reached up with a hoof and thumped it firmly against the center of her chest. “Because if you ever get so drugged up that you try to rape somepony, like Starlight… I will stop you.”

Her head had drawn back, seemingly surprised by my sudden assertiveness. Then it lowered again, glaring silently at me.

For my own part, I lowered my hoof to the ground and stood there, appearing firm and defiant, while inside I desperately hoped that I understood her as well as I thought I did.

Slowly, a smile spread across her muzzle, an eerie sight of scarred lips and bared teeth. I fought back a tremble as she chuckled, but it wasn’t the angry, eager chuckle I feared. She actually sounded pleased. “Good,” she said with a nod, then turned to continue walking. “Let’s go.”

I completely failed to hide my breath of relief, and turned to follow alongside her. I only made it a few seconds before frowning. “I hope you didn’t take that as encouragement, as if I meant you didn’t have to worry because I’d watch your back and make sure you didn’t do anything you might regret, because—”

\leavevmode\llap{“}Whisper,” she rumbled, turning her head to smirk at me. “You’re talking too much again.”

I shut up and nodded, and we continued on in silence.

Dusty and Emerald were waiting out front when we returned. Emerald looked almost unrecognizable. The green shopkeeper was clad in rugged full-body barding, which I’m pretty sure I had seen hanging up in her shop before. A magical energy rifle, one of Arclight’s designs by the look of it, was slung across her back, with a regular pistol holstered at her side. Large saddlebags were supplemented by additional packs on her back. Several folds of thick, tan cloth hung around her neck, along with a pair of goggles; if she were to don the goggles and wrap the cloth around her head, the only part of her that would be visible would be her tail. She looked as well-equipped and ready to go as any of the rest of us.

Dazzle was there, too, clad in her heavy barding, but unlike Emerald, she looked particularly agitated.

\leavevmode\llap{“}It’s still stupid!” Dazzle was saying, gesturing wildly with a forehoof. “I’m sorry, Emerald, but it is!”

\leavevmode\llap{“}Oh, wonderful,” Sickle grumbled, pausing for a moment to latch her muzzle back in place before continuing on.

Despite Dazzle’s apparent frustration, Emerald was smiling calmly. “I understand your concern, Dazzle, but I’m still going. I’ve hid behind these walls for too long, but there’s a lot of good to be done out there.”

Dusty sighed and looked over as we approached, giving a weary shake of his head.

\leavevmode\llap{“}Then why don’t you want me coming, too?” Dazzle demanded. “‘Cause I’m sure as hell not going to sit on my tail while you go out there trying to get yourself killed!”

Emerald stepped up, silencing Dazzle’s protests with a hug. “I’ve got some very capable ponies watching out for me, hon. I’ll be as safe as I can be outside of these walls, but if something does go wrong, and those raiders decide to come after Gemstone, the ponies here will need you.”

It took a couple of seconds before Dazzle stopped resisting and relaxed, wearily raising a hoof to return the hug. Her voice was considerably quieter, and if we hadn’t walked up beside Dusty already, we might not have heard it. “They need you, too.”

\leavevmode\llap{“}I appreciate the sentiment,” Emerald said, giving a squeeze. “But I think you’d all manage just fine.” She released, drawing back just enough to look Dazzle in the face. She raised a hoof, gently touching the younger mare’s cheek. “Don’t worry. I fully intend to come back, but even if I knew I wouldn’t, I’d still go. There are ponies out there who need our help, and we shouldn’t shy away from helping them just because it’s dangerous. Even if something bad were to happen to me, goddesses forbid, don’t you despair. One should never regret giving something to help their fellow ponies. Putting others before ourselves, that’s how we beat the Wasteland. You remember that, you hear?”

Dazzle’s expression slackened, and she stared back at Emerald for several seconds before swallowing. She gave a slow, almost timid nod. “I will,” she quietly replied, blinking. I think she was near tears.

As for myself, my ears had perked up, and I watched Emerald closely.

Something was wrong there.

She patted Emerald on the shoulder and stepped back. “Now you go run along. We’ll go find that family, and we’ll be back before you know it.”

Dazzle reluctantly left, casting a couple glances back our way as she made her way back to the gate. Emerald watched her go with a soft, almost motherly smile.

I was surprised when Sickle stepped forward to stand beside Emerald. She rumbled, but kept her voice quiet. “You know they’re already dead, right?”

Starlight winced. “Shit, Sickle, come on.”

Emerald drew in a breath and sighed. “Probably.” Her smile wavered, slipping for a moment before holding strong. “But it doesn’t change anything.”

Sickle’s armor rattled as she shrugged.

As Dazzle climbed the stairs to the wall top over the town gate, Emerald turned back to us. “Okay, then. Dusty’s already made sure I have the proper supplies and equipment to take care of myself. Mostly, I’ll stay out of your way, but if you need any aid, just ask. I have extra supplies for any ponies we find, plus all the medical supplies I had in stock. You already traded for most of what I had, but I scrounged up a few magic-laced bandages. All of it’s free if you need it.”

\leavevmode\llap{“}You sure you’re going to be able to carry all of that?” Dusty asked. “We can have Sickle carry some, if you need.”

Sickle grumbled. “Ain’t your fucking pack mule.”

\leavevmode\llap{“}Thank you,” Emerald said, nodding to Dusty. “I think I’ll manage. I try to keep in shape, but it’s been a long time since I’ve done any traveling. Guess we’ll see.”

Straps were tightened and equipment was checked. Finally, Dusty raised his rifle. He pulled back the bolt, peered into the chamber, and let it slam shut, chambering a round. “Okay,” he said, giving a final nod to us. “Let’s go.”

I mimicked his actions, and then we were walking. The gate opened, and we passed through it, while Dazzle watched us pass below her with a sad expression.

But mostly, I watched Emerald, and waited.

We made our way down the path leading away from Gemstone, and followed alongside the ancient railroad tracks. Our path led us out along the level low-ground. We walked, while I bided my time. It must have been ten minutes and most of a mile before we made our way around the edge of a hill and passed out of sight of the town.

I was just drawing in a breath to speak when Emerald spoke first.

\leavevmode\llap{“}Hold up,” she said, coming to a halt.

I shut my mouth, eying her with a mixture of wariness and curiosity.

When everyone had halted, Emerald drew in a steadying breath, then turned to one of her packs. She reached in, slowly drawing out a large bag, and tossed it. It landed between us with the clinking rattle of bottle caps. “I’m doubling your pay for one extra condition.”

\leavevmode\llap{“}What the hell?” Dusty frowned at her. “You couldn’t have asked us in town?”

Emerald shook her head, blinking slowly. Her own ears had drooped, and she swallowed in a way that suggested she had a lump in her throat.

Something was very wrong.

Dusty looked down to the bag, then back to Emerald. His expression softened just a hair. “What’s the condition?”

Emerald swallowed again. Her voice was thick as she spoke. “Once you’ve done what I hired you for…” She hesitated, casting a quick glance back the way we had come before looking to Dusty again. “You go back to Gemstone, and you tell them I died fighting the raiders.”

Starlight’s eyes went wide, her head drawing back. Sickle just tilted her armored head.

And Dusty glared back at Emerald. “Seriously? That’s what this is all about? You’re faking your own death?”

\leavevmode\llap{“}I am,” Emerald said. “I have to.”

\leavevmode\llap{“}Why?” Dusty demanded. “What possible reason could you, of all ponies, have to fake your own death?” His expression abruptly softened, looking concerned. “Did something happen?”

She slowly shook her head. “I’d really rather not say. I’m sorry.”

\leavevmode\llap{“}Well you’d better say, if you want any chance of me picking up that sack. Shit, Emerald, you know how many ponies you’re going to hurt, just disappearing like that? I’m not about to put that kind of pain on a pony unless it’s for a damn good reason, and I’m going to need to know what that reason is.”

Emerald looked around at us, then to the sack, sitting in the dirt. None of us moved toward it. After a moment, she deflated, slowly sinking to her haunches. A hoof went up to her chest, slipping into a pouch. “It’s because of this,” she said, and pulled out a single, uncrimped bottle cap.

We all looked on in varying degrees of confusion.

She cradled the cap in her hooves, looking down at it as she slowly turned it over. “That job you took from Amber. She paid you with caps like this, didn’t she?”

\leavevmode\llap{“}She did,” Dusty said, brows furrowing. “It was odd, sure, but what’s that got to do with this?”

\leavevmode\llap{“}Because I know where they came from,” Emerald said.

\leavevmode\llap{“}...And?”

\leavevmode\llap{“}And…” Emerald stared at the cap. After a moment, she tucked it back into the pouch she’d retrieved it from and rose to her hooves. “And I know the only way for Gemstone to be safe is for me to leave.”

\leavevmode\llap{“}Hold up there,” Dusty said, raising a hoof. “I’m going to need a bit more than that.”

\leavevmode\llap{“}That’s why I’m paying you extra.”

\leavevmode\llap{“}That’s not what I mean, damnit!” Dusty shook his head angrily. “It ain’t about the caps! I don’t care about caps if it means doing the wrong thing, and no offense intended, but this is sounding all sorts of stupid to me.”

\leavevmode\llap{“}I’m sorry,” Emerald said, her ears falling as she looked away. “I can’t tell you any more. Not without it being dangerous to you, too.”

Dusty cocked his head, staring at her for a second. “Emerald, what the hell are you getting us into?”

She stood there, silent, chewing on her lip. I stepped in to give just a little more pressure.

I spoke with a soft, gentle tone. “Emerald, you’ve talked a lot about Kindness and Generosity. How about Honesty?”

She gaze shifted to me, her expression sad. I replied with a soft, supporting smile, and she sank down as the final resistance faded.

\leavevmode\llap{“}I know where those caps came from,” she said, slowly and carefully. “Which means I know the pony Amber works for. And I know how bad that is, because I used to work for the same pony.”

A few looks were exchanged between us before Starlight spoke up. “But… if \textit{you} worked for them, then why—”

\leavevmode\llap{“}It was a long time ago,” Emerald said, and slowly shook her head. “I was a different pony back then. Did some things I’m not proud of. Things I’m still ashamed of.” She cast a glance toward Sickle, then quickly looked away again. Sickle stared back, silent, her jaw tightening.

Emerald chewed her lip for a moment before continuing. “And the pony I did those things for, they had a near-unlimited supply of unused bottle caps, the same ones Amber’s using.”

Starlight’s gaze shifted around. “Uh… what kind of bad things are you talking about?”

Emerald hesitated, and I could practically see her forcing herself to speak. “Mostly, I just scouted places out, gathered info, stuff like that. I rarely got involved directly, but… but I still saw plenty. Saw whole families grabbed up and marched off to live the rest of their life in captivity. Sure, I might not have been one of the ponies doing the grabbing. I was just the pony telling them where to find these helpless, isolated ponies.”

Dusty’s head had drawn back, his ears flat. “You’re saying you used to work for \textit{slavers?}”

\leavevmode\llap{“}Yes,” Emerald said, and though the shame was clear in her expression, she pressed on. “And worse, I’m sure. But the really terrible thing is, I didn’t feel bad for any of those ponies they took. I never even thought about it. I was just doing a job.”

\leavevmode\llap{“}What changed?” I asked, and she gave a weak, appreciative smile.

\leavevmode\llap{“}I spent some time with one of those families,” she said. “I’d found a farm, one that looked more built-up than the others I’d come across. I went in to appraise how well they could defend themselves. Ends up, they were some of the nicest ponies I’ve ever met. They were poor farmers, but they welcomed me, fed me, and showed me every measure of hospitality and generosity, even though I was a complete stranger to them. Heh, they treated me better than my own family did.”

She finished with a smile, though it quickly faded again. “Something about that generosity made me reconsider things. How could I condemn those ponies to a lifetime of slavery after the hospitality they had showed me? I couldn’t.

\leavevmode\llap{“}Problem was, there was no way I could stop things, and this wasn’t exactly a job you could just ‘quit’. These are ponies who see such things as treachery. You’re in for life, one way or another. So, I got out the only way I could. I went out on my scouting, and I just disappeared. They probably figured I died out in the Wasteland. It happened from time to time.”

\leavevmode\llap{“}That’s why you left Serenity?” I asked.

She gave me a concerned look, but it quickly softened to a faint, sad smile. “Yes. It hurt leaving my family behind, but they were too tied up in things. To them, I’d be a traitor. I still love them, though, even if they’re misguided. Maybe, someday…”

She trailed off, looking out into the distance, then quickly shook her head. “Amber is working for the same ponies. I left home more than twenty years ago, so I doubt she’d recognize me even if we had met, but somepony might. If they did, everypony in Gemstone could be in danger.”

Dusty’s ears perked. “Why?”

\leavevmode\llap{“}Because… do you remember way back, how I said the folks back home were a touch paranoid? I… might have been understating it. If they think I might have shared any of their secrets, they’ll do whatever it takes to contain that information.”

Dusty’s expression hardened. “Such as?”

\leavevmode\llap{“}With the arsenal they have at their disposal, they could flatten Gemstone. Or maybe they’d throw their near-endless supply of bottle caps at some mercenary group to do it for them.” She slowly shook her head. “Or maybe we’d get lucky and they’d settle with just killing me. I just can’t take that risk.”

\leavevmode\llap{“}You’re sure Amber is with them?” Dusty asked.

\leavevmode\llap{“}She’s been spending thousands of their caps on mercenaries, and she’s looking to hire more. She’s with them.” Emerald frowned, glancing back in the direction of Gemstone, concealed behind the curve of the hill. “And whatever her intent is, she’s already hostile enough for my PipBuck to recognize it.”

\leavevmode\llap{“}Wait a minute,” Starlight said. “She’s red to you, too? I thought it was just because she’d pulled a gun on us before.”

\leavevmode\llap{“}Red?” Dusty asked. “You mean she’s showing as hostile? Shit, Starlight, that’s the kind of thing you need to be sharing.”

\leavevmode\llap{“}What?” Starlight said, shrugging. “I mean, it isn’t like anypony \textit{didn’t} know she was a hostile bitch.”

\leavevmode\llap{“}You should still tell us,” Dusty said. “Communication is important.” He turned back to Emerald. “What if we helped protect Gemstone?”

Emerald gave a sad smile. “I appreciate the offer hon, but it wouldn’t change anything. These ponies aren’t secretive and paranoid because they’re weak. They’ve spent decades and who even knows how many caps to see to their safety, and have amassed an arsenal of the best tech to be found. Four ponies, even four exceptional ponies, wouldn’t so much as slow them down. Besides, even if you did, it’d be a lot of death. I don’t want that, on either side. No, better I disappear again.”

We all stood in silence, but as much as everyone wanted to argue, it seemed none of us could summon up a good argument. Eventually, Dusty broke the silence.

\leavevmode\llap{“}Where are you planning to go?”

Emerald looked around at us, but reluctantly answered. “There’s a little town way off south, called World’s End. Fitting enough name, given the location. From what I hear, they take on ponies that aren’t welcome anywhere else, and they don’t ask questions. Sounds like the kind of place for making a new life.”

\leavevmode\llap{“}We’re familiar with the place,” Dusty said. “They didn’t seem to care for us.”

\leavevmode\llap{“}Does seem like the kind of place that might be a bit wary of random mercenary types showing up on their doorstep,” Emerald said.

Dusty grunted. “So, what, it’s a refuge for ponies hiding from the law?”

\leavevmode\llap{“}It’s a refuge for ponies looking for a second chance,” Emerald said, and gave a wry smile. “All things considered, I think I’ll fit in well.”

\leavevmode\llap{“}Well…” Dusty looked around, but none of us said anything. “... Shit. Don’t suppose you’d want an escort there?”

\leavevmode\llap{“}Thank you for the offer, hon, but I’m afraid you’ll be needing to go back to Gemstone after we’re done. Don’t worry. I used to travel a lot. ‘Sides, there’s about to be a lot less raiders in the area.”

\leavevmode\llap{“}I doubt we’ll be staying long, with the news we’ll be delivering,” Dusty said with a shake of his head. “We could meet you after that.”

Again she hesitated, but this time she smiled and gave a small nod. “I can’t say I’d mind the company.”

\leavevmode\llap{“}And maybe on the way, you can fill us in on this ‘Serenity’ place.”

The smile vanished. “I… can’t do that.” When Dusty started to speak again, she cut him off. “I know, they’ve done some terrible things, but… but it was still my home, and it’s still my family living there. I know I cut ties with them, but I’m not ready to go that far.”

Dusty mulled that over, and slowly shook his head. “At the very least, they’re preying on innocent ponies that don’t even know they’re out there. I know you might not want anything bad to happen to the ponies you used to live with, but you’re talking about whole families being put in chains. Ponies need to know that’s happening.”

\leavevmode\llap{“}Believe me, hon, I’ve thought of that.” Emerald sighed, looking away. “Pretty much every night since I left, I thought of it. Problem is, I can’t see any way it wouldn’t just make things worse.”

\leavevmode\llap{“}Worse?” Dusty asked. “You were just saying how they might wipe out a whole town just to keep their secret.”

I chimed in. “And then there’s whatever Amber is hiring mercenaries for.”

\leavevmode\llap{“}And that,” Dusty said, gesturing a hoof in my direction.

\leavevmode\llap{“}I know!” Emerald said, her voice growing thick. “I know, and I hate it. Do you have any idea how much it hurts to hide stuff like this from all the ponies I love? To have this horrible danger that I have to keep secret, all because they’d be in even more danger if they knew?”

\leavevmode\llap{“}What about us?” I asked. “It sounds like you’ve already told us enough that these ponies would want us dead. You won’t be putting anypony in danger by telling us, and you’re already trusting us to keep your secret. We might even be able to help.”

She stared at me, and slowly, the tension in her body began to relax. “Yeah… yeah, you’re right.” She took a slow, deep breath, raising a hoof to wipe at her cheek. “It’s still quite the thing you’re asking for, but… heck, might be nice to finally tell somepony. I don’t know. Just… I need to think on it a while, okay?”

Dusty nodded. “We’ve got a lot of traveling ahead of us,” he said. “Plenty of time to share. At least we’ll have something to talk about.”

\leavevmode\llap{“}That we will,” Emerald quietly replied, nodding.

As we fell silent, Sickle rumbled. “Are you cunts all done crying into each others’ manes, yet? Let’s get to killing some fucking raiders already.”

Dusty shot her a glare, but she just shrugged it off. Shaking his head, he looked back, paused for a moment, and walked over to the bag of caps. He picked it up in his teeth, then stopped, looking at Emerald. “You’re sure about this?”

She nodded. “I’ve got enough to make a good start of it. Figure you deserve it for what I’m asking of you.”

\leavevmode\llap{“}I don’t mean the caps,” Dusty said.

\leavevmode\llap{“}I know,” Emerald said, and gave a sad smile. “And yes, I’m sure.”

Dusty hesitated, but eventually sighed and turned to Sickle. “You mind carrying this?”

\leavevmode\llap{“}Oh, hey, you learned how to fucking ask,” Sickle replied, and popped open one of her armored saddle-bags.

With the caps tucked away, Dusty looked around at us. “Okay. Take two. Let’s go.”

As we set off again, I wondered what other surprises were waiting for us.