I took things about as well as could be expected.

I sat back, staring down at her in silence, my hooves moving to my muzzle. Even with the seed of suspicion planted with Emerald’s final pleas, I wasn’t entirely prepared for what I saw. While Dusty and Starlight gaped and murmured, I simply stared, and tried to think, to piece everything together, to make sense of it all.

That lasted about five seconds before I broke down crying.

Emerald was dead. One of the kindest mares I’d met, and she’d died in pain and terror, choking on her own blood. The first changeling I had discovered since losing my own hive. One who professed the same kind of outlook as my own sisters had. One who could have even been a descendant of my own hive. One who had died in my own hooves, and me, unable to prevent it.

A changeling who, if her story were true, had been as isolated from her own kind as I was. The two of us, so close to discovering that we were not alone.

I sank down, escaping Starlight’s comforting hooves to grasp Emerald’s body, clutching her tightly as I sobbed into her still chest. An irrational part of me wanted to shake her, to beg her to wake up, as if my pleading might do what first aid and magical bandages could not. I even stripped away my own disguise at some point, as if to show her, belatedly, that she wasn’t alone.

Eventually, my cries faded, while Starlight gently rubbed a hoof along my back. As the sudden wave of emotion started to break and recede, my mind started to engage.

My first thoughts turned to shame and recrimination. Not simply at breaking down over the death of another changeling, mind you, or even over the sense of failure at having been unable to protect her. No, I felt shame for how selfish my thoughts were. This was a mare who had given so much, given \textit{everything}, and in the face of her example, I was crying over what her death cost me. I was crying over the lost opportunity to reconnect with my own kind.

I was probably being a bit too harsh with myself, but I suppose it’s understandable, given the situation.

In any case, sorrow and guilt weren’t going to help us now. Slowly, my mind turned toward more productive thoughts.

I sniffled, drawing in a deep breath as I pushed myself upright. Starlight pressed up against my side as I sat up, her forelegs wrapped around me, but I ignored her for a moment. My horn lit up, grasping Emerald’s PipBuck and lifting it. I undid the strange latch on the back—which now made sense to me—and removed it. The medical screen flashed fresh errors, but I ignored them, pressing buttons as I sought one particular piece of information.

After a few seconds, I froze, staring down at the screen.

Starlight gave another gentle squeeze. “What is it?”

I swallowed, and when I spoke, my voice came out thick and rough. “Serenity.”

Starlight and Dusty scooted in, looking down at the map screen with me. The map marker seemed so insignificant amidst the hundreds of other marks. It wasn’t labeled as a settlement, or even a ruin. It was just a generic landmark tag, which could so easily blend in with all the others.

\leavevmode\llap{“}That’s where she came from,” I said. “Her family.”

\leavevmode\llap{“}Oh, shit,” Starlight murmured, a hoof moving to her mouth. “You mean… other changelings?”

I nodded, but Dusty wasn’t quite as sure.

\leavevmode\llap{“}Or it could have just been ponies she had worked for. Hell, maybe still did.”

\leavevmode\llap{“}What?” Starlight said, straightening up. “No way she was still working for those slavers!”

\leavevmode\llap{“}We don’t know any of that,” Dusty replied, shaking his head, and his eyes fell over Emerald’s still form. “Maybe that was just another lie. I… I don’t know. Sorry. Not the time for it.”

I lowered the PipBuck, looking down at her as well. My throat constricted as tears started to well up once again. “No,” I croaked. “We know.”

Dusty looked at me. I could see he wasn’t convinced, but he didn’t argue. He merely looked down upon her once more.

We sat in silence for a minute before I finally stirred, reaching out with my hooves and my magic. Slowly and carefully, I disentangled her body from the barding and equipment, and after a few moments, Starlight and Dusty joined in to help me.

Soon she was lying bare on the floor.

I wish I could have seen her like that in life. She was a striking changeling in many ways, elegant and fit, and while her carapace was healthy and smooth, age had faded the glossy shell to a duller gray. It was the look of a changeling who had lived a long, happy life, full of love.

Laid out on her other side, to conceal the jagged hole and the majority of the blood, she looked almost peaceful.

I stood over her for a long moment, taking in every detail. Then I lowered my head, touching my horn to hers, and called up my magic.

Green fire flashed into being, rippling steadily across her form. I stepped back, as did the others, and watched as it rapidly consumed her. Seconds later, there was nothing left but a fine layer of ash.

Starlight was the one to eventually break the silence. “What now?”

\leavevmode\llap{“}Fall back or push on,” Dusty murmured, slowly shaking his head. “Normally I’d just make the call, but I’m not feeling so hot about my judgment, lately.”

\leavevmode\llap{“}Fuck falling back,” Sickle growled. “I was already going to murder the shit out of them for those pussy-ass mines. Now I’m going to get fucking \textit{nasty}.”

Starlight eyed her skeptically. “Why, because of Emerald? You didn’t even like her.”

\leavevmode\llap{“}Fuck no, I didn’t like her.” She followed that with an armor-rattling shrug. “But you cunts did, and that’s good enough for me.”

I sniffed, wiping at my cheeks, and threw in my own two bits. “I’m with Sickle. We press on. Kill them all.”

\leavevmode\llap{“}Fuck yeah,” Sickle rumbled.

Dusty nodded, though he threw in a word of caution. “Just keep in mind, we’re out of decent medical supplies. There’s going to be no margin for error.”

\leavevmode\llap{“}They’ll have some,” Sickle said. “Just make sure to kill them all before they can use ‘em.”

\leavevmode\llap{“}And after we’ve taken out the raiders,” I said, “I want to go check out Serenity.”

Dusty’s ears folded back, giving me a concerned look, but he didn’t argue. Instead, he opted for a more neutral position. “Let’s just focus on dealing with these raiders, first.” He sat back, looking around, and slowly shook his head. “Let’s take a few minutes, get all our gear sorted and everything. Then we’ll set off.”

I stood without a word and walked off, the PipBuck floating beside me. I retrieved the magazines I had left on the ground, then reloaded them with the spare ammo I carried, a process made much easier with magic. Soon that was done. Lacking anything else to do, I started to disassemble and clean my rifle, trying to remember exactly how Dusty had done it. The interior was surprisingly filthy, caked with carbon and dirt. I focused, meticulously scrubbing at every part.

I was so focused that I was caught by surprise when Starlight touched my side. I froze, glancing her way to see her look of concern. I held her gaze for a couple seconds before drawing in a slow, calming breath, and forced myself to relax. “...I’m trying to not make this all personal,” I said, my voice quiet as I turned back to my weapon. “I don’t think I’m doing a good job of it.”

Dusty spoke up from across the room. “Just keep your mind on the mission. That'll help.” I looked over to see him slowly loading fresh rounds into his own magazines, while his eyes scanned out the windows. “There’ll be plenty of time to go over it all once you’re not in the field.”

\leavevmode\llap{“}Sounds familiar,” I murmured, focusing on the bolt and all its little, fiddly pieces as I scrubbed it clean. “The mission comes first.” I sighed, trying to suppress the bitter feelings that threatened to bubble up. “...You’ve been here before, I take it?”

I heard his sigh. “Yep. I led a Ranger squad for a few years, and we got called in for all the worst shit. Got into combat probably fifty times, mostly against small raider bands, bandits, and the rare wanted criminal. Had more than a dozen casualties under my lead. Three of them died. Every time, we had to press on and finish the mission, and we had to focus, so more ponies wouldn’t join them.” He slid the last magazine into its pouch and closed his saddlebags. “Just focus on the mission. We can deal with the rest afterward.”

I nodded. “Sounds a lot like being an Infiltrator. Keep going, complete your mission, and don’t let your own emotions get in the way of what you’re doing.”

\leavevmode\llap{“}Yeah, pretty much,” he agreed. “And you know, you seem to be pretty capable. Just stay focused, and I think you’ll do fine.”

\leavevmode\llap{“}Maybe,” I said, though without any enthusiasm. “It’s been a rough month.”

\leavevmode\llap{“}It’s been an outright hellish month,” Dusty corrected. “And yeah, it’s taken its toll, but you’ve kept going. You’ve done a lot better than most ponies would.”

I was tempted to argue, but I held back. “...Thanks.”

We settled into our work. Starlight spent some time working on the broadcaster before declaring it a totally lost cause, with its circuit board broken in half and at least two gems cracked. Afterwards, we searched the raiders for any supplies we might have missed in our frantic scramble for potions.

There wasn’t much.

The collection of weapons seemed almost pitiful when compared to our own. The pair in the saloon had one of those little short-barrel submachine guns with a drum that was larger than it was, and a smooth-barrel pipe rifle that still had a misfed round jammed sideways in its breach. The sniper-pony’s bolt-action rifle was the best of the lot, though it was badly worn, and its scope was freshly broken thanks to Dusty’s grenade. We took the submachine gun and its ammo, just in case, and Dusty searched the sniper for what little rifle ammo he had.

We claimed their food and water as well, while Sickle cut away the right ear of each raider, or in the case of the submachine-gun mare, tore it away from the mess of flesh and bone that had once been her head.

She spent the rest of her time hacking apart the raider inside the saloon. Starlight grimaced and walked out, looking somewhat ill. I merely felt a slight, distant concern that I wasn’t more bothered by Sickle’s actions.

With nothing left for us in that ghost of a town, it was time to move on. I had no more excuse to delay.

I floated up Emerald’s PipBuck, regarding it in silence. I felt so torn over it, so many warring emotions all demanding attention. Instead, I did as Dusty had said. I set them aside for the moment, and pressed on.

A quick flicker of green flame hid part of the armor over my left foreleg, and I floated the PipBuck into place. The latch closed, and the screen flashed various notifications as it took in its new situation.

My vision flashed and flickered as the Eyes Forward Sparkle came online, overlaying information across my vision. Notifications scrolled rapidly by as the device calibrated. I turned my head, and the compass display at the bottom swung around. A single green blip marked Starlight’s position.

The notifications abruptly ended, and I looked back to the screen. The status display was content once again. The cute cartoon pony had been replaced by a similarly stylized changeling.

I blinked.

So many questions welled up, but I pushed them aside. There would be time for that later. Right now, I needed to focus.

I looked around again, familiarizing myself with the elements of the E.F.S. display. It was fairly simple and, I was thankful to note, unobtrusive, hovering at the edges of my vision.

\leavevmode\llap{“}Pretty cool, huh?” Starlight asked, though she lacked any real enthusiasm. I appreciated the effort, though, and nodded in agreement.

\leavevmode\llap{“}Get real familiar with that thing,” Dusty said. “Those PipBucks are probably the most tactically useful piece of kit we’ve got.”

\leavevmode\llap{“}Yeah, they’re pretty great,” Starlight said. A real smile started to creep out across her muzzle. “Did you see that grenade I tagged in mid-air? S.A.T.S. is awesome.”

Dusty smirked. “I meant the whole friend-or-foe system. Picking up threats and friendly locations through solid walls is a huge tactical advantage.”

I looked down at the screen again, and its strange, smiling changeling. Another bout of emotion welled up in protest to the thought that came next, but I focused on the practical. “Maybe you should have it, then.”

Dusty looked down at it as well, mulling the idea over. It was obvious that he saw merit in the idea, but he shook his head. “No, you keep it. Figure you’ve got a better claim on it. So long as you’re quick and clear on communicating anything your E.F.S. picks up, that should be good enough. Besides, you’ll probably get more out of S.A.T.S. than I would.”

\leavevmode\llap{“}...Thanks.”

\leavevmode\llap{“}Speaking of which,” Dusty said, “you might want to give it a try just to get used to it. Better to familiarize yourself with it now instead of in the middle of combat.”

A ruined building thirty yards away supplied me with targets. I loaded one of the submachine gun magazines into my pistol, using the raider’s ammo instead of my much more uncommon subsonic rounds.

I started with a test round, taking my time and firing a couple bullets at each of three small sections of barely-standing wall. It was an unfamiliar sensation, firing my pistol while holding it in my magic. For one, the sights were much further forward. There wasn’t the same physical kick, merely the sudden movement as the pistol tried to twist out of my magic’s grip.

Still, it was reasonably easy, so long as I took my time.

I lowered the pistol, scanning over my targets again. Then I triggered S.A.T.S. and brought my weapon up.

It’s hard to describe exactly what the Stable-Tec Arcane Targeting Spell is like. It was as if I was hyper-aware of my weapon and targets. Every little movement, every little detail. As I brought my pistol onto the first target, I corrected the alignment of my sights, smoothly pulling back the trigger to fire the moment the weapon was on-target. It bucked, and I smoothly compensated for the weapon’s recoil, bringing it back for a follow-up shot.

The moment the pistol recoiled, I transitioned to the next target, snapping off two more shots before reversing direction and firing twice on the final target.

For that moment, I felt as if I really knew what I was doing.

S.A.T.S. fell off around the final shot, and I lowered the pistol to survey my work.

I wasn’t Dusty; no simple targeting spell was going to change that. I’m sure he could have done better, likely even in the midst of combat. I was shooting in a calm situation, with my hooves firmly planted, and without the stress of combat or the threat of death looming over me. It wasn’t some grand accomplishment, or an amazing display of skill, but if those three bits of ruined wall had been ponies, every round would have hit.

I slowly nodded, looking over the results of my shooting. “Okay. I think I’m ready.”

{\br}%
We trekked across the roadless desert, seeking the locations Emerald had given us. They weren’t far, now. Our journey took only a couple of hours.

The whole way, I kept glancing at the information her PipBuck was showing me, watching the compass for the first sign of hostile contacts.

But every now and then, I would look back over my shoulder, the compass tape swinging around to show the navigation marker I had set.

Serenity.

Then I would turn back, focusing on the task at hoof for a few minutes more.

{\br}%
Once again, we found ourselves lying on a ridge, scouting out the territory ahead. Half a mile away, in the gloom of the rapidly failing evening light, we could see the raiders’ base.

According to Emerald’s PipBuck, it had once been the Palomino Army Base. Two centuries later, the place was in ruins. The chain-link fence that had surrounded the heart of the base was broken and fallen. The rusted-out remains of a couple of tanks lay abandoned, as did the small collection of skywagons and motorwagons in what had once been a motor pool. Now it was nothing but a vehicle graveyard.

Only two of the original buildings stood, side-by-side; one looked like a single-story barracks, while the other was a narrow, two-story office building of some sort. Every other building had been torn down, apparently scavenged for materials. Most of those materials went into the pair of walls that stretched between the two buildings, enclosing a small courtyard between them. Even the buildings themselves had been built up, with their outer walls reinforced and additional structure tacked on the sides and even the tops. All told, the pair of buildings had been turned into a single multi-level fort maybe a hundred feet wide.

A single gate appeared to be the only way in or out, with its approach lined by the hulks of ruined vehicles, metal spikes, strands of barbed wire, and various bones; a crude collage of Wasteland warning signs. The gate itself was watched over by one of the two watchtowers built atop the walls. They were small, only enough for one or two ponies, and didn’t look terribly stable, but they gave good vantage points. As for the walls themselves, they were uneven, especially where they connected the two-story office building to the single-story barracks. Despite that, they looked to be heavily reinforced, and the walkways behind them offered good fighting positions to hold off an attack from any direction. The additions built atop the tallest building almost doubled its height, giving an even higher vantage point than the watchtowers, and possibly serving as a final hold-out if the walls were breached.

The raiders had themselves a small, crude, but effective fortress.

On top of that, everything was packed in tight inside those walls. A stealthy intrusion would be difficult.

Suffice to say, it wasn’t looking good.

\leavevmode\llap{“}Close tower,” Dusty said, and we looked with him. “Mare, heavy armor, combat shotgun. That looks like the tip of a rocket launcher leaning on the wall next to her.”

\leavevmode\llap{“}Yeah, I see her,” Starlight said. “Sure looks like it.”

\leavevmode\llap{“}Okay, treat that as a high-threat target. That thing could ruin our day.” His binoculars shifted a fraction. “Stallion in the other tower has a pipe rifle. Nothing special there. Looks like he’s got four grenades on that shelf next to him, though, something to be aware of.”

Sickle groaned, and I lowered my binoculars to glance her way. She lay sprawled out on her belly beside us, her chin resting on the ground. “Boooored…” Other than her occasional protests, she lay perfectly still. She’d even given up flicking her tail or shaking her head to chase off the flies that still pestered her.

Dusty grimaced, but ignored her. “Star, let me know if you see that pony that was on the walls, see if you can scope out what gear she’s got.”

\leavevmode\llap{“}Can’t see much of anything in there,” Starlight replied. “Caught a glimpse of something at the top of that tall building, but only barely. Some pony in armor.”

\leavevmode\llap{“}Let me know if you see them again.” He frowned. “Also, let me know if you see another way in beside those gates.” He pondered the scene for a moment before asking me, “Do you still have those demolition charges?”

I nodded. “The small charges, yes. Four blocks.”

\leavevmode\llap{“}Think you could knock down that gate with them, if it comes to that?”

I raised my binoculars, peering out across the distance. “Maybe. I’d feel a lot more confident if we could see how it’s mounted and barred. I’ve only got five pounds, so placement is going to matter. Maybe if we can pull one of those vehicle hulks over to tamp the explosives.” I glanced towards Sickle. “Though even if the charges don’t break down the gate, they should damage them enough that Sickle could bust them open pretty quickly.”

Dusty grunted and nodded.

\leavevmode\llap{“}What about flying?” Starlight asked.

\leavevmode\llap{“}Not in daylight,” Dusty said with a quick shake of his head. “Way too visible. If they don’t have any lights, it might be viable after dark.”

Sickle groaned impatiently.

\leavevmode\llap{“}And I kind of doubt Whisper can lift Sickle,” Dusty added.

\leavevmode\llap{“}Maybe if I turn into a dragon or something,” I mused.

Starlight lowered her Lancer to stare at me. “Holy crap, you can do that?”

\leavevmode\llap{“}A little dragon, sure,” I said, scanning over the rooftops. “Big enough to lift Sickle? I’m not sure if I have enough magic for that. Even if I did, I’d probably be tapped out and useless afterwards.”

\leavevmode\llap{“}I can get over the wall fine on my own,” Sickle cut in, though she still hadn’t moved from where she lay. “Even if I couldn’t, I could go \textit{through} it. Why aren’t we killing these fuckers already?”

Dusty sighed, shaking his head. “Because we have no margin for error, so I want to gather as much intel as possible before we make a move.”

Sickle gave a particularly exaggerated groan. “Fuuuuck. I swear, Dusty, only you could make killing raiders \textit{boring}.”

\leavevmode\llap{“}Boring is good,” Dusty said. “Boring means we’re not dying.”

\leavevmode\llap{“}Means we ain’t living, either,” Sickle muttered.

\leavevmode\llap{“}Anyway, we have flexibility in how we approach this. We can take the time to figure out the best way to proceed.” He looked over to Starlight and me. “Any suggestions?”

Sickle spoke up first. “Yeah. Charge on down there, bust the fucking door in, kill every motherfucker we see, and have a nice big celebratory fuck at the end of it all.”

Dusty grimaced, but ignored her.

After rolling her eyes at Sickle’s response, Starlight asked, “Isn’t tactics kinda supposed to be your thing?”

\leavevmode\llap{“}Yeah,” Dusty said, ears drooping a bit. “Like I said, I’m not so sure of my judgment lately.”

\leavevmode\llap{“}Why?”

He frowned. “That’s not really important. I’ll deal with it afterwards. We need to deal with this, first.”

I had my own problems to dwell on, but this seemed important enough to speak out on. “I hope you’ll pardon me,” I said, “but if you’ve gone from a confident tactical thinker and leader to hesitant to take responsibility, that seems like something we should deal with before getting into another fight.”

Dusty’s ears pinned back as he stared back at me for several long, unwavering seconds. Finally, he sighed, looking away again. “It’s all this shit with Emerald. And I don’t mean losing somepony under my lead. It’s the whole... changeling thing. I didn’t see it coming. I \textit{should} have seen it coming, but I didn’t. What else am I missing?”

Starlight set her Lancer down. “Hey, we didn’t know Whisper was a changeling, either. I mean, passing themselves off as something else is kinda their whole thing.” She gave a quick glance my way, as if I might be offended by what she had said, but I was already nodding in agreement.

\leavevmode\llap{“}Sure,” Dusty said, a hint of bitterness in his voice, “but we didn’t even know changelings were a thing. Now we do, and Emerald, shit, how could I not see it? The whole double life, secret shady past, working for ‘ponies’ that act behind the scenes, not to mention the whole ‘Kindness and Generosity’ act.”

My ears pinned back, my jaw and neck tightening. “That wasn’t an act.”

\leavevmode\llap{“}I’m just saying it makes sense for a changeling. You guys feed on love. I figure she got plenty from that.”

My hooves dug at the ground. “She didn’t do that for \textit{food}, Dusty.”

\leavevmode\llap{“}Maybe—”

I pushed myself up. “Not maybe! She gave her last healing potion to another pony even though she knew she was dying. It wasn’t a fucking act!”

Dusty’s ears pinned back, blinking a couple times, while I tried to control my breathing. Somewhere behind me, Sickle grumbled.

Starlight’s hoof touched my side, and after a moment of silence, I relaxed and sagged back down to the ground.

After a moment, Dusty quietly, and cautiously, spoke again. “Maybe she didn’t realize how bad it was.”

Thankfully, Starlight took the opportunity to answer that one. “She had a PipBuck, Dusty. Trust me, they aren’t exactly subtle about telling you you’re bleeding to death.”

Dusty looked away, back toward the raider compound in the distance. His ears hung low. “Even so, there were the other signs. She lied to me, and I didn’t even suspect it.”

\leavevmode\llap{“}Us,” I said, swallowing back the final bit of the receding anger. “None of \textit{us} realized it, and that includes the changeling Infiltrator who’s much better trained and equipped to handle such a situation than you are.”

He looked back to me, his eyes wary. “You never even suspected?”

\leavevmode\llap{“}Not until the very end. Before then, I made a point to avoid doing so.”

His head tilted a hair to the side, and I answered his unspoken question. “It’s far easier to see changelings where there are none, than it is to find an actual changeling. I’m guessing you never heard of the Changeling Scare?”

When he shook his head, I continued. “It was before my time, thankfully. After Chrysalis led her hive against Equestria, ponies started to suspect changelings everywhere. Ponies can be panicky like that. Strangers were changelings trying to steal your love. Unfriendly strangers were changelings that hated ponies. Charity workers were changelings trying to ingratiate themselves upon the vulnerable and unfortunate. Friends and family that had an off day were changelings who were bad at acting. It was like a precursor to the kind of xenophobia that would kick off during the war.”

I gave a weak, derisive snort. “Of course, the real changelings were all playing normal, ordinary, consistent ponies. We’re taught to blend in. We’re also taught to avoid falling into the same suspicions those ponies did. We’re trained to \textit{not} see changelings in everything, because ninety nine percent of the time it’s wrong, and constant paranoia over low-probability threats detracts from more legitimate concerns.”

He frowned, staring down at his binoculars for a moment. “And… what if they really were a changeling?”

\leavevmode\llap{“}In general?” I shrugged, then lifted my binoculars again. “It didn’t matter.”

\leavevmode\llap{“}But you’re \textit{trying} to find other changelings now.”

My ears drooped a little. “Yes. But I’m not going to find them by trying to figure out which pony is secretly a changeling. Not unless they do something stupidly obvious, like try to feed off me.”

He remained silent, still frowning.

\leavevmode\llap{“}If it helps,” I said, “she was going to tell us. She just… never got the chance.” My throat started to tighten up again; I focused on glaring through my binoculars.

He mulled that over for several seconds before lifting his own binoculars again. “...Any suggestions on how to crack this?”

Sickle lifted her head barely off the ground. “We should just charge—”

\leavevmode\llap{“}I heard you the first time,” Dusty replied sharply, then moderated his tone by adding, “I’d like to hear any other ideas before committing to that.”

I scanned again over the roofs, considering the layout of the small fortress. “If we wait for dark, I can do recon. I can fly over low, inside E.F.S. range.”

\leavevmode\llap{“}Could be useful,” Dusty agreed. “Though we’ll get that information as soon as we get up close, anyway. Doesn’t really help us get inside.”

I focused my gaze on the watchtower, with the bored-looking mare sitting beside the rocket launcher. “No, but if we’re waiting for night, I think I might be able to take care of that.”

{\br}%
The dark desert floor passed beneath me, the wind flowing silently under the wings of my chimeric body. Normally, I would avoid a form that blatantly combined elements of different races or species, much as I’d avoid any other disguise that stood out as ‘unusual’. At the moment, however, function trumped appearance, and the difficulty of incorporating such fine alterations was well worth the result.

At that moment, my form was mostly like that of the so-called ‘bat ponies’, with golden slit-pupil eyes that soaked in what little light penetrated the nighttime cloud cover, and large, tufted ears that easily picked up any wayward sound in the still night air. All of that was complemented by the dark charcoal coat, blending in with the dark clouds above.

While already unusual enough just by virtue of the rare breed, my form stood out even further with the wings; rather than the membranous wings one would expect, I sported a pair of feathered wings, but not a normal pony’s wings. They were thick and soft, with carefully arranged feathers and edge shape to minimize the sound they made passing through the air. A skilled observer would recognize the wings as belonging not to a pegasus, but an owl.

My unusual appearance was of little importance. Success depended not on blending in, but in never being seen in the first place.

I had cast off most of my belongings in the name of stealth. I had only two tools that would be useful for this stage of the plan, and so they were all I carried. One was Emerald’s PipBuck, clasped to my foreleg, its screen turned off to avoid giving away my position. The other was my pistol, strapped to my shoulder with its two spare magazines.

I entered a shallow bank as I passed over the raider compound once more. It was my third pass, each lower than the last. Tick-marks on my E.F.S. lazily drifted off to my side as I passed by. I confirmed my previous count: nine red marks, and not a single green.

There were lights in the compound, but only a few. Most were inside, sending narrow blades of light through loosely-fit boards. Only two lights were outside, one in each of the watchtowers. Their feeble light lit up the inside of the tower itself and little else. Likely they were so the ponies could find their way across the darkened rooftop and walkways. To me, they were a mixed blessing. On the one hoof, the light would impede the night vision of the ponies who stood guard, leaving me effectively invisible outside the short radius of their glow. On the other hoof, they illuminated the two places I absolutely had to go.

Two raiders remained standing guard after nightfall, although ‘standing’ was something of a misnomer. My pass revealed that both were laid back in their towers. While the mare by the front gate was tipping back a bottle to drink, and thus clearly awake, the stallion in the rear tower had his chin tucked in against his chest, apparently asleep.

Only one step remained before committing myself. I turned my head, teeth clasping down on the bit of my pistol, and drew it. I checked that the magazine was full, the safety was disengaged, and a round was chambered.

With a slow, deep breath, I pitched down, tightening my turn as I descended toward the gate-side watchtower. I flared my wings, feathers fluttering near-silently as I bled off energy, keeping my glide nice and slow. My turn took me over the rear tower, then across the old barracks building. By the time I was closing in on the front tower, I was perfectly level with it, and coming from directly behind the relaxed and unaware raider. I back-winged, bleeding off the last of my speed as the faint light in the tower started to illuminate my dark coat.

Even as silent as my form was, there is only so much that one can do to mask the passage of a pony-sized object through the air. The raider mare’s ear twitched in response to some barely heard sound or faint air current, but I didn’t give her the time to consider it further. I was barely a yard away and in a hover when I pulled the trigger.

My weapon gave a sharp clack, like a hammer striking a nail, and the bullet smashed into the back of her head with an audible smack. The mare jerked and spasmed with startling violence, sending her bottle clattering to the floor and kicking the wall of the tower. I hurtled myself forward, diving into the tower. I grappled with her flailing limbs as I placed the tip of my suppressor against her head and fired again, but she gave no reaction, nor did it stop her movements. She continued spasming, emitting a weak, wet gurgle. I simply held on, trying to muffle the sound as much as possible. Within seconds, the spasming weakened, and soon stilled, though her body remained tense, her legs at full extension. Her eyes were still open, unseeing, her expression slack as blood dribbled from the back of her skull.

Once she had stopped, we lay together, still and silent. The walls of the tower concealed us from the other guard’s position, but only if he didn’t wake and investigate the sound of struggling.

I heard nothing but my own heartbeat hammering away.

My attention turned to my E.F.S. None of the red marks were moving. I waited another ten seconds or so before hazarding a peek over the watchtower walls. The other guard was still out of sight, presumably still dozing and unaware of what had happened to his compatriot.

I huffed out a quiet sigh of relief, then turned to the lantern. It was a simple spark-powered camping lantern, its dim light painful against my night-adjusted eyes. I turned it off, plunging the inside of the tower into darkness.

I stepped out, carefully unfurling my wings, and slowly beat them. It was just enough to stay level as I crossed the courtyard to the other tower; flying was more assuredly quiet than risking a walk on those ancient roofs, even as sturdy as they looked.

My ears picked up his faint snoring as I came up to the tower, and I back-winged again, coming to a halt right at its entrance. With all the time in the world, I carefully aimed at the center of his sleeping face and pulled the trigger. Once again, the sharp clack of my weapon echoed in the still night. The stallion twitched with the impact, but that was the extent of it. The casing clattering across the roof produced more noise than he did.

I slipped into the tower, extinguishing the lantern there, and sat in silence once more. Still no sounds of ponies coming to investigate. Still no movement on my E.F.S. So far, everything had worked perfectly.

I flew back to the front tower. After another cautious glance around, I lifted my left foreleg, placing the attached PipBuck across the top of the wall, pointing out. I turned on the screen, with the brightness set low, and turned it off again. I repeated the action twice more, then left it off.

The hulk of ruined skywagons and other metal decorations stretched out from the gate. Even with my altered eyes, I could only make out the closest in any detail. The rest rapidly turned to silhouettes, slightly lighter shapes against the darkness beyond.

Out in the distance, past the end of the wreckage, a faint green glow flickered into life, vanishing an instant later.

I turned back, watching over the rest of the compound for any ponies who might intrude. Mostly, I watched the addition built atop the two-story building; a door opened onto the roof, and from the light seeping through the cracks, I assumed at least one of the pips Emerald’s PipBuck showed was inside there.

Every few seconds, I’d glance back outside the walls. Soon, green pips started to appear, superimposed over the E.F.S.’s compass. Not long after, I could hear the rattle and clank of Sickle’s armor approaching.

I waited, keeping my eyes out for threats, until they had reached the base of the wall beside me. I slipped out from the tower and over the wall, dropping down to the ground with a quick flutter of my wings.

Starlight and Dusty crouched behind an overturned skywagon with crude spikes protruding from it. Starlight’s lancer was still strapped across her back. Instead, she held Emerald’s magical energy rifle in her teeth. Sickle, meanwhile, stood directly in front of the gate, unconcerned.

Dusty stepped out to crouch beside me, and I quickly filled him in.

\leavevmode\llap{“}Single story has two raiders,” I whispered, lifting a hoof to point to the left. “South side of the building. I can clear that silently once we’re inside. Two story…” My hoof swung to the right. “...has five, spread out along it. There were two more in the towers, but I took care of them already.”

Dusty gave a sharp nod, his rifle bobbing with the motion, and stood.

With a near-silent flurry of wings, I floated over him, wrapped my forelegs around his barrel, and lifted. It was a thankfully short flight to the roof of the taller building. I deposited him there, and as he crouched to cover the approaches, I descended again.

Starlight stepped out as I drew near, clutching the rest of my belongings, and I lifted her as well. Once I had released her, she crouched beside Dusty. In the overcast darkness, with the uneven wall top as a backdrop, they were as good as invisible to a normal pony.

Moving to the edge of the roof, I gave the courtyard a more thorough looking over. It looked trashed. More skywagon and motorwagon wrecks lined either side of the courtyard, forming a crude wall of metal hulks. A single rusted-out tank sat at the back of the courtyard, missing its tracks and hatches. The huge machine gun atop the turret was the only thing that appeared to be in good condition, and I could see it was loaded.

The ground itself was torn up, and even cratered in places, with bits of debris scattered randomly. Even with my enhanced night-time eyes, I couldn’t make out all of the details. I found myself relieved by that. I was fairly certain that some of the debris was body parts.

There were no ponies, and it didn’t appear that any of the angry red marks on the E.F.S. compass were near the doors. I slipped over the edge and dropped to the ground. The gate was barred by a single metal beam, which produced only a faint squeak as I removed it.

The gate creaked open to show Sickle’s hulking form through the opening. I stepped back, and she walked in, armor rattling with each step. Once she was inside, I held up a hoof. She halted, though the way her head turned to me indicated she was glaring underneath that helmet.

That was fine with me. She’d been patient so far, and that was about the best I could ask for. She’d have the opportunity to act soon enough. But first, I had one more thing I wanted to take care of.

Since the two hostile contacts in the single-story building were on the south end, near the back of the compound, I entered through the door near the north end. My suspicions were proven correct; it was a barracks building of some sort, mostly open space, though that space was filled with boxes, barrels, and heaps of junk. The light at the southern end struggled to reach my end of the building, leaving me creeping along carefully, barely able to see my hooves.

A small room along one side, perhaps a commanding officer’s office or bedroom, offered me both a moment of rest and an opportunity to change my form. With the flash of magic hidden by those walls, I stripped away my disguise, returning to my natural form, with my as-yet unused armor. I did perform one slight alteration, and hid my fangs; gripping my pistol in my mouth would be impossible with them, and I couldn’t risk the glow my magic would produce while holding it. The altered dentistry, with my sharper omnivorous teeth, changed how the grip fit in my mouth, but it was easy to shift the bit around and align the sights once more.

I slipped out of the office again, and started slowly picking my way across the junk-filled space.

I could already hear the two raiders ahead of me. There was a stallion and a mare, but with the way they were grunting and panting, on top of the rapid creaking of well-worn furniture, I suspected the chances of them hearing my approach were minimal.

As I drew closer, the light grew enough that I could clearly make out the objects I was passing. Most of it seemed to be junk; random tools, worn clothing and bags, the broken remains of a cart, and other rubbish like that. Army crates with stenciled words faded by two centuries lined the other side of the room.

Closer to the raiders, the space was filled with barrels, presumably full of water, and heaps of food. Some were in cans or packages. Others were loose vegetables, which I imagined had been taken from the farm they had just hit.

Rounding a pile of discarded cans and boxes, I could see part of the final room, bathed in the light of a bare bulb. From the half of it I could see on my approach, it appeared to be serving as a crude kitchen, with a rickety stove and numerous knives and pans.

There was also a table, with the hacked-up remains of a pony lying atop it.

At first, I thought she—I think it had been a mare—had been badly burned and maimed. Then I realized that wasn’t quite accurate. She had been \textit{cooked}. Her legs were missing, and enough of her chest had been carved away to reveal ribs. The metal spit was even still there, piercing through her pelvis and out her mouth. Several slabs of meat lay on a stained platter at the edge of the table.

I stared, simply processing that for several seconds, before I realized the sounds further in the room had stopped. I could still hear the rapid panting of the two raiders, but the sounds of copulation had ceased.

I moved forward again, peeking around the edge of the crates that formed a crude wall. The pair lay on an old army cot. The mare lay on her belly, panting, and wore a lazy grin. Heavy metal armor enclosed her chest, painted red and adorned with spikes, and matching her wild, spiked mane. The stallion that still lay atop her was fairly scrawny, wearing only a thick metal collar, and his legs were crisscrossed with scars. His cutie mark was a crosshair; I assumed that made the pipe rifle lying on the floor his, which would in turn make the large-bladed spear leaned against the wall hers.

The stallion was panting into the mare’s mane, giving a few firm nuzzles. His lips pulled back in a grin as he nuzzled into her ear, murmuring something that led both of them to snicker.

It almost seemed tender, as if, under the spikes and scars, these two were really just a pair of ponies.

But my eyes glanced back to the table, with the innocent pony they had murdered and butchered. I thought of the pair of foals, brutalized in their own home. I thought of Emerald, the first changeling I had encountered in two centuries, choking on her own blood.

I prefer to plan my actions through detached logic, but emotion can be a powerful motivator.

I was already calling up S.A.T.S. as I walked smoothly around the corner. I brought the weapon up, and in the middle of my stride, tongued the trigger. At maybe two yards distance, the arcane assistance was more than enough; my weapon bucked simultaneously with the wet smack of the bullet smashing into the side of the stallion’s head.

The muzzle swung down to the mare, who jerked in surprise as the stallion collapsed. I pulled the trigger, but her head turned toward me, as if to seek the sudden sound. The round struck her in the muzzle. I fired a third round as smoothly as if I had planned it the whole time, and this one struck her squarely in the center of her head. She jerked and collapsed, forelegs twitching once before going still.

S.A.T.S. disengaged as the final casing clattered to the floor, leaving me panting softly. The moment felt surreal, as if I had killed them in a trance that I was waking up from. I knew, logically, that every single action I had taken had been my own, but something about the spell felt unnatural and unnerving.

It was also undeniably effective, I recognized, as I looked down upon my hoof-work. Even Dusty couldn’t have done much better.

I shook off the feeling, focusing again. Four raiders down; five to go.

Emerging from the same door I had entered, I walked up to Sickle, standing in the darkness where I had left her. I glanced around, spotting one of the ramps leading to the wall-tops, and gestured for her to follow. She grunted, sounding annoyed, but did so. I tried to suppress the urge to wince at every clank of her armor or groan of the boards.

We rejoined the others. While I took my belongings from Starlight, I reported to Dusty in a whisper. “The single-story is clear. Just the five in this building now.”

He nodded and whispered back. “Soon as you’re set, lead us out. Sickle, you follow her. Then me, then Starlight. If things go loud, Whisper, you fall in behind me. Good?”

I gave a quick nod. Even though it was all part of the plan, I felt the burn of adrenaline building. There were too many raiders too close together within the building to be sure of stealth; we were just hoping to eliminate as many as possible before things turned into a firefight.

With my bags strapped on and rifle resting across my chest, I was ready. I glanced around, getting two nods and an impatient grunt in reply, and set off across the roof.

I paused at the door for everypony to gather behind me, the light seeping from between the boards playing over their bodies like zebra stripes. I put my eye to one of the cracks, trying to see inside, but the narrow sliver of view was useless. I pulled back, horn lighting up as I gripped the latch of crude door, slid it back, and strode straight in.

I was ready to trigger S.A.T.S. at a moment’s notice, and hit it the instant I saw the raider sitting at the table on the far side of the room. He looked up, and in the hyper-focused state, I could see his questioning expression past the sights of my pistol. I also saw that he wasn’t wearing armor.

He hadn’t fully processed what was happening by the time I fired, putting three quick rounds into his torso as I advanced. S.A.T.S. disengaged as he tumbled back off the chair, legs flailing. I think he might have made a pained groan, but I’m not sure. His legs clutched at his chest, his eyes wide with shock at the sudden violence.

They were still wide when I halted just above him. Even I didn’t need S.A.T.S. to put a final round into his head, ending his life.

A clatter of metal preceded the sound of Sickle’s blades sinking into flesh. I looked back. While this half of the room had tables, chairs, and couches, well-lit by the ceiling-mounted bulb, the darker half had a couple of cots. Sickle was at one, pinning a struggling raider down by the neck as her other foreleg rose and fell, stabbing them with her leg-blades. Dusty and Starlight were moving in as well, each of them smartly covering the other two doors of the room.

A mare’s voice called out from above. “The fuck was that?”

From below, a more muffled voice sounded. “Is somepony shooting?”

I had already swapped out my pistol magazine for a fresh one, thanks to my magic. On hearing the voices, I holstered it, swapping to my rifle. The raiders knew something was up. It was time to hit them as hard as possible before they finished putting the pieces together.

The only problem with that was Sickle. The raider beneath her was still very much alive, emitting faint gurgles and grunts as his forelegs flailed and kicked against her. Sickle should have killed him already, but she hadn’t. I could see then that she’d been stabbing him again and again in the hips and thighs; painful, crippling injuries, but not immediately fatal.

Dusty scuttled over to her, hissing something to her, but she kept stabbing.

The door at his end of the room opened, revealing a raider. I didn’t get a good view of him before firing. S.A.T.S. was still recharging, so I went without. He tumbled back down the stairs beyond the door, and I only then realized Dusty had been firing as well.

A shout came from below, answered by a yell from above. “What the fuck’s going on down there?”

I glanced up, just as a metal mask peeked up in the doorway. Dusty and I both fired, and it dropped down again. I thought we had hit, but a voice immediately shouted out. “Luna fuck me, it’s Sickle!”

I shouldn’t have been surprised that a raider might know who Sickle was. Heck, she might as well be a raider celebrity.

Dusty dropped his rifle to his hooves and plunged his muzzle into a pouch. It came back a moment later with a grenade, which he quickly primed and threw through the doorway.

A deep thump sounded above, followed by the upstairs-mare’s voice, this time amplified by some loudspeaker. “Get to the—”

The blast of the grenade cut her off, but only for a moment. “Get to the fucking can! I’ll handle that bitch!”

The ceiling rattled as massive hoofsteps sounded above us, accompanied by the groans and squeals of machinery.

My heart was pounding even harder.

Dusty shouted past me. “Star! Lancer!”

The hoofsteps banged down. Whatever was up there was \textit{massive}.

I looked back. Sickle was looking up at the ceiling, grinning wide in excitement. Starlight was running over to us, quickly swapping Emerald’s rifle for her own Lancer.

The hoofsteps thumped in unison, and the ceiling groaned loudly in protest.

An instant of silence followed, broken by the deep slam of the hooves landing on the roof outside. The floor trembled under me, and outside, machinery groaned and hissed.

The loudspeaker crackled as the amplified voice returned. “Hey, bitch! You in there?”

A strange, vaguely mechanical thump followed her statement. It was lost immediately behind a deafening explosion as the wall across from us was reduced to flying splinters. An armored leg came down on me, throwing me to the ground as explosion after explosion hammered around us. The first explosion had knocked out the light, leaving only the strobe of explosions to illuminate the room. The only thing I could see was Sickle’s head, tucked in tight to shield her face as she crouched over us. Her armored bulk sheltered us from the worst of the barrage.

The sound relented, plunging us into smoke-choked darkness. My ears were ringing, but the amplified laughter of the mare outside cut through it.

I felt the floor tremble and the screech and groan of machinery returned. “Hah, you still alive in there, Sickle?”

Sickle rose, growling as she shook off several boards and bits of debris. I scrambled to my hooves, my mind racing at how to get away. I blinked away the after-images of the explosions as my eyes rapidly adjusted to the darkness once again. Through the dispersing smoke, I caught a glimpse of a huge, pony-shaped form moving outside, but to my relief, not in our direction.

It was then that I realized the explosions had knocked out power throughout the entire little fortress. There wasn’t a single light to be seen. I was our eyes.

Hoping that the mare outside couldn’t see any better than the ponies I was with, I hurried over to where the wall used to be. Only a few fragments of it remained, sticking up like wooden ribs of the devastated structure and giving scant cover. Starlight stumbled and scrambled after me while I peeked out.

That’s when I saw Boomer. She was every bit as huge as Sickle. Hydraulics whined and metal scraped and screeched as she walked, each hoofstep sending another small tremble through the structure. At first glance, through the cloud of dust and smoke, I thought ‘she’ was a pony-shaped \textit{machine}.

Then it struck me.

She was wearing power armor.

I felt completely inadequate with my tiny little gun, immediately understanding why Dusty had called for Starlight’s Lancer. Fortunately, the power-armored raider was moving away from us down one of the walls, taunting us the whole way.

\leavevmode\llap{“}Yeah, you think you can just come in here and take \textit{my} gang, huh? Hah!”

Sickle staggered past me, coughing, her head turning from side to side as she tried to spot our adversary, but it would have been hard enough for her to see in that darkness even without her helm restricting her view.

The power-armor had a battle saddle. Through the darkness I could see the chunky body of a huge gun with a short, thick barrel; an automatic grenade launcher, the very weapon that had just torn apart the side of the crude structure.

But what really caught my attention was the contraption on her back. It looked like a long set of rails with some bulky mechanisms along the underside, and an object nestled in the base of those rails. I didn’t realize what it was until I caught a faint wisp of sickly green.

I’d never seen one before, but I’d heard them described; somehow, this power-armor-clad raider had a Balefire Egg Launcher. I realized then that she wasn’t running away from us as she crossed the wall to the other building. She was just getting to a safe distance.

\leavevmode\llap{“}Starlight!” I shouted over the buzz in my ears. “Shoot her!”

Starlight coughed against the smoke, but brought her Lancer around. She squinted, searching in the darkness outside. “Where? I don’t see her.”

My hoof shot out, pointing. “Right there!”

She squinted a bit more, her Lancer swaying well off from where I indicated. “I can’t see anything,” she said, then added, “Are you pointing?”

Outside, Boomer continued to taunt, her amplified voice echoing off the buildings. “You think you’re such hot shit, huh? Well you ain’t taking a fucking thing from me!”

She stepped onto the roof of the opposite building.

\leavevmode\llap{“}Starlight!” I shouted, my wings flicking to life as I lifted off. “I’ll illuminate her!”

I shot out, arcing up into the sky and banking around to fly directly over the raider.

She was still walking, nearly to the middle of the roof. “This is my gang. \textit{My} home. I ain’t going to let some buck-guzzling \textit{bitch} take it from me, even if I have to flatten the whole fucking place myself!”

She turned just as I fluttered to a stop over her. I kicked on the PipBuck screen, cranking the brightness up to max. The green light spilled out, lighting the twisted amalgamation of scrap metal that formed Boomer’s armor.

A powerful flash of red split the air a moment later with a sharp crack. I recoiled, blinking furiously. All I could see was the after-image of the Lancer’s shot.

My heart sank as I heard the laughter, distorted and amplified. As my vision returned, I saw Boomer recovering her balance. The shot had vaporized part of her chest-plate, leaving a few glowing bits of molten metal, but had failed to penetrate.

\leavevmode\llap{“}So that’s how you want to play it?” Boomer called out, clearly amused at her seeming invincibility. “Okay, then. Catch this, you fucking—”

Her head snapped to the side as Sickle came barreling out of the darkness.

I had never before seen a pony simply \textit{take} Sickle’s charge.

Though Boomer remained standing, the impact rocked her back. The Balefire Egg Launcher discharged. I back-winged, lurching back as the projectile passed me, sailing well over its intended target.

Below me, Boomer turned and threw her shoulder into Sickle, sending her staggering, and followed up by rearing back and kicking out. It was immediately clear to me that Boomer, with her power armor, was at least as strong and durable as Sickle, if not considerably more so.

But with how big and bulky she was, it was easy to forget how terrifyingly quick Sickle could be. She slipped to the side, catching only a glancing blow that her armor easily turned, and grappled the other mare. The difference in skill was telling, and a few seconds later, Sickle had gotten a grip across Boomer’s back.

That was the end of it. Sickle twisted backward, hauling the power armor off its hooves and swinging it over herself to slam down on the roof. The power armor lacked the flexibility to fight back effectively, and Sickle alternated between holding on and jamming her blades into the armor.

The balefire egg finally landed, several hundred yards away. A brilliant flash of vivid green cast everything into highlights and shadows, even casting a glow across the clouds above. The sharp blast of the explosion was followed by a deep, rumbling echo, and the distant fireball climbed into the sky, rapidly burning out. In moments the light had faded, plunging the world into darkness once more.

\leavevmode\llap{“}You missed,” Sickle happily growled, jamming a leg-blade into the shoulder of Boomer’s armor and tearing away a chunk of armor plate.

Dusty’s voice echoed across the courtyard. “Whisper! Status!”

\leavevmode\llap{“}We’re good over here!” I replied, drifting a little closer as I did. In the aftermath of my shout, I heard another mechanical squeal, but not from the struggle behind me. My gaze dropped down to the courtyard. The turret of the ruined tank was slowly turning, its cannon swinging towards the building where Dusty and Starlight were.

We’d forgotten about the other raider!

I lurched and dove, my magic digging inside the pouch strapped across my chest as I sped toward the top of the turret. My eyes glanced down to the E.F.S. compass; the red mark was centered right on the tank. That raider was inside, slowly traversing the giant cannon toward my friends. I had to stop him!

I didn’t know much of anything about the inside of a tank. I didn’t know where the gunner would sit, though I guessed somewhere in the turret, and my E.F.S. could help narrow it down. I didn’t know what I might find if I tried to get in there to fight him. But I did know one thing: the inside of a tank is a small, enclosed space.

Grenades love small, enclosed spaces.

I levitated the grenade from my pouch as I swooped by the turret, pulling its pin and slapping the explosive in through one of the open hatches. Then I swooped up, getting distance as I banked around to watch and evaluate the effectiveness of my attack.

The muffled bang sounded almost like a huge, metal drum, deep and hollow, and oddly unsatisfying. It was followed a moment later by a quieter thump, and then the vehicle erupted. Plumes of flame poured from every opening, roaring like rockets. I banked sharply away, dazzled again by the brightness that lit the compound and the surrounding area.

The plumes of flame rapidly dwindled, and moments later had died out, leaving only a few bits of flame flickering inside the burned-out hulk. The violence of the conflagration had knocked the turret askew. The red mark had vanished from my compass.

I swung around in a circle, searching, but the only remaining red mark was the one in Sickle’s hooves. “That’s the last one,” I called out.

Boomer was snarling and growling furiously, her voice still amplified by her armor’s speakers. She even tried firing her grenade launcher. The thump of them firing was almost drowned out by the metallic ‘chunk’ of the weapon cycling. The first three rounds sailed harmlessly out of the compound. Then Sickle attacked the weapon itself, striking it with her blades and spiked hooves. It fell silent, inoperable.

I glided down and landed next to Sickle. Despite the power armor’s strength and durability, Sickle had done some horrible damage to it. Several pieces were completely torn off, and one of the forelegs seemed locked in place, unmoving.

It was an incredibly crude piece of technology. Maybe it had once been Steel Ranger armor, patched time and time again until it was more scrap metal than original armor. Maybe it was something somepony had cobbled together after the war. In either case, it looked to be an amalgamation of all manner of scrap metal welded haphazardly together over a heavy robotic frame. The grenade launcher was simply bolted to the side, and several compartments were built into the armor. Jagged spikes of metal protruded from the armor, and likely would have posed a significant problem for anypony less armored than Sickle.

While crude, I imagine it was horrifyingly effective. What could the average caravan or isolated farmer hope to do against such a terrifying machine of war?

A loud shriek of metal made my ears pin flat against my skull as Sickle peeled back a section of armor along Boomer’s back, then laughed. “Hah, I got you, you little bitch! Time to come out and play!”

Boomer continued to scream obscenities and struggle ineffectively as Sickle pulled and pried at her armor. Metal squealed, followed by several loud cracks and pings as parts broke. Finally, the damaged armor gave one final screech as Sickle tore away the back, leaving a squirming, pale-blue body exposed.

Sickle reached in. The loudspeakers abruptly cut off as she pulled the kicking and screaming raider from the armor, lifted her up, and slammed her down onto the roof.

The difference was stark and shocking. Boomer couldn’t have been any bigger than Starlight, and just as lean. Her coat was ragged and worn, and looked as if it were slightly too small for her, so that her joints protruded sharply.

Sickle pinned her down, looming over her and laughing. “Heh, you’re just a little runt, ain’tcha? So cute and tiny!”

Boomer responded to the mocking by kicking Sickle in her armored gut.

Sickle, naturally, laughed off the feeble blow. “Oh, you want to play rough, huh?”

Her demeanor changed in an instant. A hoof came down on Boomer’s head, roughly pinning it to the roof. While Boomer grunted in pain, Sickle lowered her head, pressing her blood-and-gore stained muzzle into the smaller mare’s face. All hints of amusement were gone. “Why the fuck were you gunning for that mare, you flimsy little runt?”

Despite her situation, and the grimace of pain, Boomer grinned. “Aww, did we kill your marefriend, you obese mother—graaah!”

Sickle had pressed down, twisting her hoof a little. Blood started to trickle down Boomer’s face where the spikes had dug in. I cringed, more than a little uncomfortable with where this was going, and stepped in. “Sickle, stop.”

She did stop, though she raised her head to glare at me. “Why should I?” she asked, her teeth bared in a snarl.

A short time ago, that would have been enough to send me scurrying away. For whatever reason, I felt much more comfortable with it, now. “Torture and the threat of torture or death is an extremely unreliable method of extracting information. Ponies say anything to get out of it, and we’d have to waste time verifying her answers. I should know. Getting information from ponies who don’t want to give it is my specialty.” I raised a hoof, gesturing to Boomer. “Let me try.”

Sickle’s head tilted slightly as she considered it.

Beneath her, Boomer was looking at me with a grin. “Wow, that is one fucked up face you got—errrg!”

\leavevmode\llap{“}Shut the fuck up,” Sickle said as she twisted her hoof again, thinking. After a moment, she relaxed, and flashed me a grin. “Sure, let’s see this. But once you’re done, this little bitch is mine.” She sat back, keeping Boomer pinned down with one hoof, while her attention turned to the torn-up power armor.

I nodded, stepping up close to lie down face-to-face with Boomer.

She tried to spit on me, but couldn’t get the distance from her position. I frowned at her. “You seem to have developed a very abrupt interest in Emerald, haven’t you?”

\leavevmode\llap{“}Oh, was that her name?” Boomer replied, her mouth splitting in a cruel grin. “Hey, I don’t see any green ponies here. Did she not make it?”

Sickle growled and looked back, but I lifted a hoof, and the growl quieted to a mere grumble.

Boomer laughed, cold and condescending. “Hah! I never thought the big scary Sickle everypony’s always pissing themselves over would be some deformed runt’s little bitch!”

\leavevmode\llap{“}Yeah, keep talking you mouthy little cunt,” Sickle growled without looking back, while she pulled a surprising variety of explosives from the armor’s compartments. “That’s gunna end well for you.”

\leavevmode\llap{“}You haven’t had any interaction with Emerald before,” I said, dragging the conversation back on topic. “You’ve never seen her, you only vaguely knew about her, and you had no personal reason to specifically target her. Someone hired you to kill her, didn’t they?”

She sneered back at me. “I don’t know what you’re talking about.”

\leavevmode\llap{“}It was a rhetorical question,” I said flatly. “I already know the answer.”

She gave another condescending laugh, something I suspected was a defense mechanism in the face of her near-certain death. “Yeah, well you can suck my rhetorical dick, you bug-faced bitch!”

\leavevmode\llap{“}You shouldn’t use words you don’t understand,” I chided. “I know the idea to kill her came from outside your charming little following. I just want to know who.”

The smug sneer returned. “Still don’t know what you’re talking about.”

\leavevmode\llap{“}Yes, you do.” I said. “But let me ask you another question: was it worth it? You’ve lost everything you’ve ever worked for. You lost your gang. You lost your home. You’re not going to live to see the dawn.” I considered how to put the next part in appropriate raider-ese. “The individual who hired you for this fucked you. She’s the reason you’ve lost everything. Chances are, she was hoping it’d end like this. It’s tidier that way.

\leavevmode\llap{“}Except, you see, she fucked us, too.” I leaned in a little closer. Boomer had gone silent, though her lips curled back to bare her teeth at my approach. “So you and I have exactly one thing in common: we both want to get back at the pony who fucked us. I’m willing to make you a deal. You give us her name, and we’ll make sure she pays for what she’s taken from us.”

Boomer went silent, her grin having vanished. She glared back at me, eye-to-eye, and held there for several long seconds. Then her sneer returned. “Sorry, bug-face. Never did get a name.”

I nodded, standing, and glanced toward Sickle. “So they were hired.”

Sickle rumbled and nodded. “Figures.”

\leavevmode\llap{“}Yeah, and both of you fuckers can go suck a grenade!”

I started to turn away, but stopped halfway as I remembered a question Starlight had asked earlier. “You know Banger?”

She spit again. “What about him?”

I’m thankful it was dark, even with the PipBuck screen turned way up; it likely hid the hint of surprise I showed. I hadn’t expected any connection. I quickly switched gears, my mind racing to pick out the correct course of lies to get the information I wanted. “He’s caught up in this, too,” I said, looking down at her. “If you don’t know who she is, he will. She’s fucked him over, too, but now we can’t find him. The entire mercenary band he was in was wiped out, but he’s not among the dead. We need to talk to him. Where would we find him?”

Boomer had gone quiet, the wall of defiance vanishing for a moment. “...Fuck if I know.”

I watched her for a second before reluctantly accepting that it was probably true. “Pity.”

\leavevmode\llap{“}You done, then?” Sickle said, a bit too eagerly for my tastes.

\leavevmode\llap{“}Yes, she’s all yours,” I said, feeling a little dirty as I said it. “Just make it quick. No torture.”

While Boomer cursed and kicked, Sickle simply grinned. “Yeah, I’m not exactly the slow-torture kinda mare.” She lifted a foreleg, then sank her leg-mounted blades into the roof beside Boomer. “Going to make this plenty gruesome, though. You want to watch?”

I sighed, turning away. I could see the glow of Starlight’s PipBuck as she headed our way, leading Dusty to the wall connecting the two buildings.

Sickle chuckled behind me, then spoke. “I only got one question for you, string-bean. That farm your gang hit a few days ago, with the the pair of ponies and their two foals. Did you actually get in on that, or were you hiding back here like a little chickenshit?”

\leavevmode\llap{“}Yeah, I was there,” Boomer spat back. “Should have seen those little fucks crying when we killed their kids. Friends of yours?” She laughed.

That laugh was cut off by a scream of pain and profanity. I winced, but the cry quickly diminished to the labored, whining breathing of a wounded pony. Most notably, a very not-dead pony.

Dusty shouted out from the opposite roof. “What’s going on over there?”

I looked back. Sickle was opening one of the containers strapped to her side. Her helm’s muzzle hung to the side, and fresh blood was dribbling from her chin. Boomer had her forehooves pressed to the side of her head, and in the monochrome lighting, I could see the wetness of blood spattered across her face.

\leavevmode\llap{“}Sickle, what are you doing?”

She paused, looking up at me, then spit the bloody ear into the open container. “What? This thing’s worth fifty caps!”

I blinked. “...You could have taken it after she was dead.”

She paused, her head tilting as she considered what I said. “Guess so,” she finally said with a shrug, and turned back to Boomer. “Too bad, I could have a lot of fun with you, you scrawny little rat. Let’s get this over with.” I looked away again, waiting for it to be done with. The anger that had burned in the back of my mind had burnt out. The adrenaline had faded, and in its absence, I felt so tired. I’d seen enough ponies die for one day.

Boomer’s pained whines grew to a flurry of cusses and grunts, accompanied by the sound of a struggle as her hooves scraped and banged uselessly against Sickle’s armor. Her voice rose abruptly to shrill, pained screams, furious and panicked. I felt like something was withering inside me, especially as the screams of pain turned to struggles once more. Sickle was chuckling.

My ears flattened in irritation at that, and I turned back to shout. “Sickle!”

I had just turned back when Sickle swung around, hurtling Boomer out over the courtyard, spinning and cursing.

Boomer exploded.

I staggered and fell over out of pure shock at the unexpected detonation.

I scrambled back to my hooves and rushed over to the edge of the roof. Boomer’s remains lay on the ground below, her belly completely blown out. Everything to the rear of her chest was torn and mangled. A severed hind-leg lay several yards away, and the other looked to be attached only by a small section of skin.

\leavevmode\llap{“}What the fuck was that?” Dusty shouted. He and Starlight were picking themselves up on the walkway behind the front tower.

Sickle was still chuckling with satisfaction as I turned toward her. “What the hell did you just do?”

Her chuckle stopped as she looked at me. “What? That scrawny little cunt killed Emerald. You’re really going to complain about this?”

\leavevmode\llap{“}I know that, but…” I looked down at the mangled corpse. Then I looked back to the collection of explosives Sickle had pulled from the power armor. “...but this…”

\leavevmode\llap{“}How about those foals, then?” Sickle said. “You know why that colt was missing his head? It’s ‘cause they stuck a grenade in his mouth and pulled the pin.”

She stepped in, pressing her face close to mine as she gave a savage, bloody grin. “Now guess where they stuck it in the little filly.”

I drew back, horrified.

Sickle’s grin grew a little wider. “Yeah.” She gave another dark chuckle as she walked past me. “I love me some fucking irony.”