Dusty stared down at the crate he had just opened. “A mortar.” His voice was halfway between awe and exasperation. “Shit, I don’t know if we’d ever find a use for it, and I’m \textit{still} tempted to take it.”

Starlight glanced over from the crate she was prying open. “What would we even use a mortar for? I mean, at least I can see a use for that little grenade launcher you snagged, but isn’t a mortar a bit excessive?”

\leavevmode\llap{“}There’s no such thing as too much firepower or too many tools,” Dusty replied. “Just too much weight. And since we’ve got Sickle…”

I looked up from the crate I was looking through, with its variety of explosives. We’d gotten halfway through the line of crates, and the amount of munitions kept piling up. There were mines, grenades, rockets, cannon shells, mortar rounds, and just about every flavor of explosive I could think of.

\leavevmode\llap{“}We still can’t carry it all,” Starlight said, “even with the cart they’ve got. They must have found some buried munitions bunker or something.”

Dusty shook his head. “We aren’t taking everything. Just what we can carry or haul in the wagon. We’ll demo the rest.”

\leavevmode\llap{“}Demo… you mean blow up?” Starlight asked. “Shit. Seems like a waste.”

\leavevmode\llap{“}Better than some other ponies wandering across it.”

\leavevmode\llap{“}Yeah, I guess,” Starlight muttered. “Still seems like a waste.”

The door banged open as Sickle entered. “Okay, Miss Medium Well is buried.”

Starlight grimaced, keeping her eyes fixed on her crate. “Did you bury \textit{all} of her?”

\leavevmode\llap{“}Yeah, yeah,” Sickle said, snickering under her helm. “I still say it’s a waste of meat.”

\leavevmode\llap{“}You’re disgusting,” Starlight grumbled.

\leavevmode\llap{“}We already went over this,” Dusty said, frowning as he pulled the mortar tube out of its crate. “We’ve got plenty of food. No eating ponies.”

Starlight grunted, digging around inside her crate. “Can’t believe we even need to say that.”

\leavevmode\llap{“}Do raiders count as ponies?” Sickle asked with a grin. “‘Cause I don’t usually go for extra-crispy, but Whisper fried one up pretty good in that tank.”

Starlight muttered quietly.

I was feeling much too tired to deal with this. “Sickle, knock it off.”

\leavevmode\llap{“}Fuck you, too,” she replied, grinning. “And shit, did you really kill those two while they were fucking? That’s just cold.”

\leavevmode\llap{“}They’d just finished,” I said. “Not that it makes any difference.”

She paused, considering it for a moment, then chuckled. “Nah, okay, that’s not so bad. Guess they went out on a high note.” She looked back toward the kitchen, where the bodies still lay; unlike the remains of the ponies we had hoped to rescue, we weren’t bothering with burying the raiders. “Shit, you kinda went on a murder-fest in here, didn’t you? How many of these fuckers did you kill?”

I grit my teeth, but paused in my inventory-counting to think back, knowing she likely wouldn’t relent without an answer. “Six.” Possibly seven, but Dusty and I had both shot at the raider on the stairs, and I figured he was more likely to have gotten the killing blow than I was.

Sickle thought for a moment, then snorted. “Fuck! Even with the two cunts from earlier, I only got four. ‘Course, one of those was in power armor, but fuck!” She thumped me unpleasantly hard on the shoulder. “You need to lay off the killings, Whimper. You’re going to make me look bad.”

I restrained the urge to bare my nice sharp teeth, though my voice carried enough sharpness to make up for it. “Believe me, I would like nothing more than to never have to kill a pony again. Unfortunately for me, that doesn’t seem to be very likely.”

\leavevmode\llap{“}Hey, if you’ve got to kill a bunch of ponies, you might as well learn to fucking enjoy it,” Sickle said with a grin and another pat. I shook it off with a quick shrug of my shoulders. She actually laughed at my display of irritation. Thankfully, she didn’t push it any further, and instead turned her attention to Starlight. “Hey, runt! You want me to haul that power armor down from the roof? Should be just your size.”

Starlight’s head came up, the expression of irritation immediately twisting in confusion as the barb she had expected instead seemed to be a genuine offer to help. “Uh… sure, I guess?”

\leavevmode\llap{“}Might be a bit of a fixer-upper,” Sickle said with a chuckle as she turned to head out again. “I fucked that shit up good.”

When we had finished with what was stored in the barracks, we moved on to the other building. Doing so meant passing through the courtyard, and therefore, passing by Boomer’s remains. I avoided looking, but the mere presence was enough to bring it to the forefront of my mind.

The whole subject left me feeling conflicted. What Boomer had done was horrific. I wasn’t at all upset that she was dead. The method, however, troubled me, not only because it was equally horrific, but because I could appreciate the almost karmic justice of it. Sickle’s method of execution seemed like something I should object to, \textit{did} object to, but could still sympathize with.

I felt dirty.

We scoured the other building. It lacked the stockpile of the barracks, but we searched all the same. Mostly, we turned up personal belongings, a few scattered caps, some low-quality weapons, and a modest assortment of drugs. The most interesting was another broadcaster, wired up in similar fashion to the one we had found on the raider sniper.

The three healing potions were a bitter prize.

But the capstone was what we found in Boomer’s quarters. There were quite a few items of interest: tools, scraps of metals, various machinery parts, and a large floor crane, not to mention yet more explosives. All of that seemed insignificant compared to the case we found under Boomer’s cot.

We sat around the open case, staring down at its contents.

I’m sure my expression was one of wide-eyed shock and fear.

Dusty stared with narrowed eyes, as if appraising a dangerous situation.

Starlight’s eyes were as wide as mine, but where I looked on in apprehension, she was struggling to restrain a grin.

And Sickle merely sat there, head tilted slightly to the side, until she broke the silence with a single word. “Dibs.”

\leavevmode\llap{“}\textit{Fuck} no,” Dusty said with a start. “You’re psychotic enough already. No way in Tartarus am I arming you with a case of balefire eggs.”

\leavevmode\llap{“}What?” Sickle said, gesturing at the case, and the egg-shaped objects within. They cast off a deep green glow, while necromantic energies swirled within them. “Hey, it’s half a case at most.” Technically, that was true; while the hard foam within the case had eight slots, only three were occupied.

Starlight snickered, not even hiding her grin as she looked down on the balefire eggs. “I like how you didn’t argue the ‘psychotic’ part.”

\leavevmode\llap{“}Well, yeah,” Sickle said with a grin I could only describe as proud.

\leavevmode\llap{“}We’re demoing these with the rest of the excess,” Dusty said. “These things are more dangerous than they’re worth, it’d be like… using a megaspell to dig a ditch. And there’s no way I’m letting these get loose for some other pony to use. Shit, we’re lucky Boomer didn’t decide to hit a settlement just for laughs!”

Starlight looked away from the dancing lights just long enough to glance up at Dusty. “Weren’t you just saying something about how there was no such thing as too much firepower?”

\leavevmode\llap{“}I can at least think of a tactical use for a mortar!” Dusty said, gesturing wildly at the case. “How could we possibly make use of a balefire egg?”

\leavevmode\llap{“}By blowing up everything ever,” Sickle helpfully noted.

\leavevmode\llap{“}Yeah!” Starlight said, grinning. “Heck, if we had these, we wouldn’t have had to come in here. We could have had Whisper fly over and drop one right in the middle of the place. Boom! No more raiders!”

Sickle laughed. “Just kick back on that hillside and watch the fireworks!” Her grin rapidly faded. “Wait. Then I wouldn’t get to do any killing. Fuck that, that’s a shitty plan.”

Starlight rolled her eyes, still grinning. “Come on, I’m sure you’d get a kick out of watching something like that.”

\leavevmode\llap{“}Well, sure,” Sickle said, then raised a blood-spattered hoof. “Still ain’t as fun as doing it by hoof.”

Starlight grimaced a bit at all the blood, and turned to me. “You’re like our demolitions expert, right? Think you could make use of them?”

I frowned, staring down at the trio of balefire eggs. I really wanted to argue the ‘expert’ part, seeing as I had fairly limited training and experience, but I suspect that would have all been moot after the events in Mareford. As much as I didn’t want to take responsibility for anything involving balefire, it was my turn to contribute.

\leavevmode\llap{“}If I wired them up with an initiator, they’d make for an extremely compact and powerful demolition charge,” I said. As Starlight’s grin widened, I added a word of caution. “Also, an extremely volatile one. I wouldn’t want to take one into a combat situation. Take a blow to the bags while carrying one of those, and we all die.”

Starlight looked back to the eggs, and the hooves she had placed on the edge of the case slid back an inch. “They’re that volatile?”

\leavevmode\llap{“}They’re sturdy enough to not go off when fired from a Balefire Egg Launcher, but volatile enough to detonate when they hit the ground. I’d guess their durability at around that of a glass bottle.” I gave a wary look her way. “Just, a glass bottle that kills you and everyone in the general vicinity if it cracks.”

She looked warily down at the eggs, as if they might decide to crack of their own volition at any moment. “...Are they safe as long as they’re in the case?”

\leavevmode\llap{“}It doesn’t look armored, so a bullet might still set them off. Other than that, the foam casing will probably protect them from impacts, so long as we don’t do something stupid like toss the case off a high-rise.” I reached out to tap the corner of the foam, where a small gem was embedded. “Though it looks like the case was enchanted, too, so it might be more durable than that. Emphasis on ‘might’.”

After a moment of consideration, Dusty finally turned to me. “Okay, appraisal: would taking these with us be safe?”

\leavevmode\llap{“}There’s no such thing as one-hundred percent safe when you’re dealing with primary explosives,” I said, frowning down at the case and mentally shelving my own pondering as to whether balefire eggs technically counted as an explosive or not. I suspect they’d be classified as incendiaries, though the difference seemed academic in this case. “If they’re kept in the case and stored where they’re unlikely to take a stray round, they should be about as safe as we can make them. I also wouldn’t take them out if there’s any possibility of a fight, which limits how useful they are, but… well, as much as I hate to say it, given that I’d be the one stuck carrying the things, I can see the use of a low-profile but extremely powerful explosive device.”

Dusty frowned, mulling it over, while I took some minor comfort that I was not responsible for making such a decision.

After a few moments, Dusty sighed. “Fine. If we’ve got room in the cart, we’ll take them.”

Starlight seemed much less enthusiastic about the decision than she had been just a minute earlier.

{\br}%
The heavily laden cart creaked as Sickle hauled it up the slope, following the lights of our PipBucks and flashlights.

Starlight was walking awkwardly on three legs, the new broadcaster slotted into her PipBuck as she checked on it. “Okay, looks like this thing is working just fine. They wired straight into the existing systems without tearing anything out like a bunch of animals, so the PipBuck connector works just fine. We’ll want to find something to seal up the case where they cut into it, though. Don’t want to get dirt and moisture in there.”

\leavevmode\llap{“}Good,” Dusty said as he turned and sat with a sigh, looking back the way we had come. We were back at the same ridge we had first observed the raider fortress from. “At least we have one functioning broadcaster. That’ll be useful.”

Starlight trotted up to sit beside him. “It’ll only be one-way, though,” Starlight pointed out. “PipBucks can pick up its broadcast, but only the broadcaster can send them.”

\leavevmode\llap{“}One-way is good enough,” Dusty said, then quickly corrected, “Well, it’s not as good as two-way, but better than no-way. It gives us a bit more tactical flexibility. Means we can do stuff like post you up in a good overwatch location with your Lancer, but we can still talk to you to give targets or call you back.”

\leavevmode\llap{“}Great,” Sickle rumbled as she shook off the cart harness. “Now you cunts can talk too much at long range, too.”

Dusty smirked a little. “Being able to split our forces like that also means we can be more aggressive with our maneuver element, too. You’ll get into the action quicker.”

\leavevmode\llap{“}Yeah, we’ll see,” Sickle said, her armor crashing loudly as she flopped down on her side.

I sat beside them, looking in the same direction. Two pinpricks of light stood out in the darkness. I had turned on the lanterns in the watchtowers, and they cast a feeble glow across the raider compound’s walls.

Dusty looked over to me. “Well, Whisper, guess you can do the honors.”

I nodded, remaining silent as I retrieved my remote detonator, turned it on, and disengaged the safety. “Fire in the hole.”

I pressed the trigger, and in eerie silence, the compound erupted in a fireball. A ghostly flicker of a shockwave tore across the ground as the explosion illuminated the world around it, dividing everything into bright light and stark shadows. The only sound was a faint thrum, barely audible, that seemed to come from all around.

Beside me, Dusty grunted. “That’s going to be loud,” he said, his ears lying flat as he tucked his head down.

I mimicked him just an instant before the shockwave hit us like a hoof to the chest, a deafening, sharp blast that receded into deep, rumbling echoes, punctuated by a few distant cracks and pops of secondary explosions.

Within moments, the great, rising fireball had burned out, plunging the world into darkness once more. The only light remaining to be seen out in the valley came from the wide-flung embers of burning building materials, now scattered wildly around where the buildings had once been. The sounds of impacts faintly reached our ears as bits of debris fell to earth. I think some pieces landed behind us.

Dusty slowly straightened again, blinking into the sudden darkness. “In hindsight, we probably should have dug the graves further away.”

\leavevmode\llap{“}What’s this ‘we’ shit?” Sickle said, though she was chuckling.

Shaking his head, Dusty started to undo the straps of his saddlebags. “Let’s get settled in and get some rest before daylight. We still have plenty of traveling to do.”

{\br}%
The day’s travel was uneventful and quiet. Nobody felt particularly talkative, knowing what lay ahead of us. Even Sickle remained quiet, plodding along behind us.

But while most of us were thinking of what awaited us at Gemstone, I was also thinking beyond that.

We halted early that evening, still some ten miles from Gemstone. While I’m sure we could have pressed on and made it by dark, or shortly after, I don’t think we were in that much of a hurry to get there.

With the remaining light, Starlight climbed into the cart, finally getting both the time and the lighting to examine the remains of the bulky power armor. She poked and prodded with her magic, peered into gaps, and even slid in through the torn-open back to see how she fit, though it seemed her PipBuck made for a tight squeeze. Her appraisal came only a few minutes later.

\leavevmode\llap{“}Yeah, Sickle wasn’t kidding. She tore the shit out of this thing. Still… I think I could fix it.” She tapped a hoof on the armor’s shoulder. “It’s all pretty crude and basic stuff. Very loose-tolerance design. Big, clunky hydraulics and spark-powered motors, and we found a good amount of spare parts. Yeah, should be doable.”

Dusty looked up from a can of food. “How long?”

Starlight gave a dry snort of laughter. “Too long. Would be faster if I had a good workshop, but most of my tools are made for portability and quick fixes. Even with the ones we looted, it’ll be slow going. Like, trying to build a skyscraper with a tack hammer slow. A couple of weeks at best.”

Dusty nodded, thinking for a moment. “How about Rust? They did a lot of metalworking and such. Maybe they might be able to handle it?”

\leavevmode\llap{“}Yeah, probably,” Starlight said, smiling a bit. That smile faded fairly quickly. “Not sure it’ll be that useful, though. I mean, yeah, it’ll be all big and tough and stuff, but it looks super slow and clunky. I’d \textit{rather} get that Enclave armor working. That’s some professional work. Nice and light and agile. ‘Cept it’s also more complex than a PipBuck, and there’s no way I could fix it on my own. Not anytime this year, anyway.”

\leavevmode\llap{“}Well, fixing up this suit would give us more options,” Dusty said. “Super heavy armor and an automatic grenade launcher can go a long way to make up for poor mobility. It could be very useful to keep around.”

\leavevmode\llap{“}Yeah, maybe,” Starlight said. “I mean, it \textit{is} kinda cool. Even if we really need to cut off all those raider spikes.” She contemplated it a moment longer before her eyes darted my way. “Hey! Whisper could use it!”

I coughed into my half-eaten can of pears, feeling particularly alarmed at the thoughtful look Dusty had directed my way. As soon as I got my coughing under control, I shook my head. “No way. I’m not even good at this regular soldiering stuff, much less playing at being a walking tank. Besides, that thing would be more obvious than Sickle. I kind of rely on \textit{not} drawing attention to myself.”

\leavevmode\llap{“}Still might be useful,” Dusty mused. “Would give you great protection and firepower in a pitched fight, and you could always get out of it if you need to do the sneaky bug thing.”

I scowled. “Why don’t \textit{you} use it, then?”

His expression faltered slightly. “I’m… not sure that would be a good idea. I’ve spent a lot of time training to fight in a specific way. Changing that up means a big step back, and I wouldn’t gain much from it.”

Starlight chimed in. “I don’t think he’d fit. It was pretty snug on me.”

Dusty raised a hoof to gesture to her. “There. See?”

I fixed him with a flat glare.

\leavevmode\llap{“}Oh, hey!” Starlight said, suddenly grinning. “We could mount that minigun opposite the grenade launcher! You did good with that last time.”

\leavevmode\llap{“}She’d burn through all our ammunition in a single firefight,” Dusty said, poorly hiding a chuckle before turning more serious. “I’m thinking the heavy machine gun. We’ve got close to two hundred rounds for the thing, but no way to use it.”

I turned back to my pears. “There’s something seriously wrong with all of us if I end up being the most heavily armed and armored.”

\leavevmode\llap{“}Agreed,” Sickle said, grinning widely. I think she was enjoying this far too much. On a slightly positive note, the grin wasn’t quite as disturbing as it would have been earlier in the day. We’d used our PipBuck maps to locate a small, murky creek and made her clean up before heading into town.

Thankfully, Dusty decided to take a somewhat more diplomatic turn in the conversation. “Anyway, we’ve got lots to do before we’ll have a chance to get that thing fixed up. We can settle all that later.”

Lots to do. My mind returned to previous subjects as I continued eating. When I had finished the rest of the can and gotten a drink, I finally broached the subject.

\leavevmode\llap{“}I want to go to Serenity.”

Dusty sighed, but didn’t seem at all surprised by my declaration. I imagine he had been waiting for this. “I know you want to look into anything to do with your kin, but I’m not sure that’s a good move.”

\leavevmode\llap{“}We know there are changelings there,” I insisted, but Dusty shook his head.

\leavevmode\llap{“}No, we don’t,” he said. “We know there \textit{were} changelings there. And yeah, there’s a good chance there are more, but we don’t know that. Even if they are... “ He paused, his ears drooping. “Shit, all we know about them is that they scared Emerald so much that she thought it was better to abandon everything she’d built up and fake her death rather than being found by them. They’re very likely the ones who just contracted a raider band to kill her. I think it’s safe to say these aren’t good people we’re talking about.”

The reply hurt, largely because most of what he said was absolutely true. I still pressed on. “Maybe. Likely, it’s a lot more complicated than that. I’m not expecting some miraculous reunion where everything’s suddenly okay, but we’ve suddenly got solid evidence that other changelings \textit{have} survived, and there’s the possibility of an entire hive living out there. I can’t just ignore this.”

\leavevmode\llap{“}I get that,” Dusty said. “I’m just concerned that you’re looking too much at the ideal and not considering the risks. What if everything Emerald said was true? What if they really are slavers who will wipe out entire settlements just to remove any evidence of their existence? If this Serenity really is a bunch of changelings, then they just murdered one of their own. Do you think they’re just going to welcome you with open hooves?”

I glared at him. “Dusty, I’ve been involved in espionage and conspiracy for my entire life. I’m quite well aware of the dangers. I’m not talking about naively walking in and asking if there are any changelings around, and given how things went during the war and the sundering of the hive, I’m certainly not going to make the mistake of assuming every other changeling out there is my friend. I’m talking about doing reconnaissance, scouting out who and what is out there, and \textit{then} deciding what to do.”

Dusty’s jaw tightened a bit at the sharpness of my tone, but he didn’t rise to match me. “Even that’s a risk. This isn’t going to be like the raiders we’ve dealt with. We’re talking about a secretive organization with apparently unlimited funding. They’ve been hiring mercs and raiders to do their dirty work, and if they’re really a bunch of changelings, they could impersonate anypony they want. They’re likely to take security a good deal more seriously, and probably have the numbers to make good on that. We just lost someone to a relatively disorganized band of raiders, and these guys you’re wanting to scout out are likely to be a lot more dangerous.”

\leavevmode\llap{“}I’m aware of that,” I said, and made an attempt to sound more even than I had previously. “I still want to go.”

When Dusty didn’t immediately reply, Starlight chimed in. “I think we should check it out.”

He didn’t seem to notice. He simply sat there, his eyes fixed on the ground before him without really seeing. Several seconds passed like that before he spoke. “If we do this, we’re back on the old rules. If I say we back out, we back out, right then and there, no complaints. Deal?”

\leavevmode\llap{“}I hadn’t realized that rule had ever been rescinded,” I said. “So I guess that’s a deal.”

Dusty frowned, though it looked more thoughtful than disapproving. “...Guess it hadn’t. Not as such, anyway. Just wanted to say it again, make sure it’s clear.” He turned to face me, looking me straight in the eyes. “Changeling hive or not, if I say we’re leaving, we’re leaving. No objections, no ‘I’ll just do it myself’. We \textit{all} leave, and we’ll work out what to do next once we’re safely away.”

I disliked the restriction, but I could understand the reason behind it. “Agreed.”

Besides, if worst came to worst, I could probably slip away and do some scouting without them ever knowing.

He stared at me for a couple seconds, almost as if he had heard that thought, before finally sighing. “Okay. We can go and take a look after we stop in town.” He gestured to Emerald’s PipBuck. “Let’s see where we’re going.”

I lifted my leg and switched over to the map. As I was starting to scroll over, Starlight suddenly pressed against my side. “Woah, wait! Go back!”

I scrolled back a bit, and she quickly shook her head. “No, no! Switch back to the status screen.”

\leavevmode\llap{“}What?” I asked in confusion as I switched modes. The screen switched to the status display, complete with cartoon changeling. “Oh. Yeah. That.”

\leavevmode\llap{“}Holy crap, it knows you’re a changeling.” Starlight stared down, wide-eyed and open-mouthed. “That… wow. Holy \textit{crap}. Did Stable-Tec \textit{program} them to recognize changelings? Like, how would they even do that? Were they working \textit{with} changelings?”

\leavevmode\llap{“}Doubtful,” I said, and switched back to the map. “It doesn’t really matter.”

\leavevmode\llap{“}What do you \textit{mean} it doesn’t matter?” Starlight said, staring at me like I’d gone insane. “This is huge! Stable-Tec knew enough about you guys to design the PipBucks with you in mind? The guys who made the Stables that kept ponies alive through the balefire? And maybe some not-so-ponies?”

\leavevmode\llap{“}That’s one possible explanation,” I said, scrolling across the map. “But also one that doesn’t materially change things. There is little functional difference between Stable-Tec intentionally harboring some changelings and changelings secretly infiltrating their Stables, which was always a possibility. Personally, I find it unlikely. Stable-Tec had enough attention from our own Infiltrators that such a collaboration would have been unlikely to have avoided attention. For that matter, if collaboration seemed plausible, I expect we wouldn’t have had so many difficulties outfitting our hive.”

\leavevmode\llap{“}Unlikely,” Starlight repeated. “Not impossible.”

\leavevmode\llap{“}Not impossible, but likely to be a dead end. Even if it were true, it’s likely to be a largely academic point. Stables were intended to last a couple decades. It might turn up regions that are more likely to have changelings still living there, but that’s a lot of time for them to have moved on.”

Dusty grunted. “Intended to. Yeah, some of them didn’t quite go that way. Some Stables stayed shut a lot longer. Heck, that mare the radio was talking up came from a Stable that just opened up a few months ago. There’s probably even more out there, still sealed up. Wouldn’t surprise me if some ponies open the door, take one look at the Wasteland, and decide to say ‘screw that’.”

I contemplated that for a moment before slowly shaking my head. “It still doesn’t materially change things. If C.L.T. doesn’t turn up any relevant information, Stable-Tec would be a reasonable next step, and even if true, this wouldn’t change that order of priority. Besides…” I gave Emerald’s PipBuck a wiggle. “If this came from Serenity, which I’m guessing it did, they might have reprogrammed it themselves.”

Starlight sat back, ears low as she frowned at the PipBuck. “I guess that could make sense.”

I nodded. “Though to tell the truth, it wouldn’t surprise me if this is simply a result of Stable-Tec being Stable-Tec. While much of Equestria was falling into xenophobia, Stable-Tec was rather egalitarian. They had stables dedicated to Equestria’s griffin population, and even zebras. It wouldn’t surprise me if they simply designed their PipBucks to automatically adapt to any user, regardless of species.”

\leavevmode\llap{“}Huh.” Starlight looked down at her own PipBuck. “You really think they could do that?”

\leavevmode\llap{“}They can distinguish between irritation and hostile intent at a hundred yards. At this point, I think I’d be more surprised to find out these devices \textit{couldn’t} do something.”

While she considered this, I turned back to Dusty, presenting the map screen. “There it is.”

He looked it over, eventually reaching over to zoom the map out. “West-northwest of Mareford, probably… what is that, a hundred miles? Pretty isolated. No settlements nearby. Well, we’re certainly not going to blend in as normal traffic. Only thing up that way is Old Appleloosa.”

\leavevmode\llap{“}As tempting as it might be to visit my old home, I think I might pass on that.”

\leavevmode\llap{“}Yeah, one stalker alicorn is enough, thank you.” Dusty gave a dry snort. “Well, it’s a little out of the way, but not too bad. We’ll have to be careful, but it should be doable.”

\leavevmode\llap{“}After Gemstone, then?”

He sighed. “Yeah. After Gemstone.”

{\br}%
We arrived shortly before noon. I once again wore my regular pony disguise. I’d tucked Emerald’s PipBuck away in my bags, after confirming that the little cartoon changeling turned into a little cartoon pony when I transformed.

A few ponies stood atop the wall as we came up to the town. One of them was Dazzle. She stood the moment she saw us, her ears standing tall and alert. Then they drooped.

The gate was already opening by the time we drew near. Dazzle had hopped down to meet us. The look of desperation rapidly turning to grief was heartbreaking.

\leavevmode\llap{“}Where is she?” Dazzle asked, her voice catching. “...What happened to Emerald?”

We drew to a halt, right at the gate. Dusty cast an uneasy glance back at us before taking on the duty of passing on the bad news. “The raiders had a sniper. Picked her off, right in the middle of us.”

Dazzle’s legs wavered, and she sat down, sagging. The other guards were in the same state of shock and sadness, with tearful eyes and drooping ears.

\leavevmode\llap{“}I’m sorry,” Dusty said.

Tears were building in Dazzle’s eyes. My own throat was tightening, and I had to blink several times to clear my vision.

\leavevmode\llap{“}...But why her?” Dazzle said, her voice weak and trembling. “She was the nicest… s-she…” Her voice caught again, her head drooping.

\leavevmode\llap{“}I don’t know,” Dusty said. “But I intend to find out.” He stepped up closer. There was a hint of iron to his voice when he spoke again. “Where’s Amber?”

Dazzle swallowed. “S-she left just after…”

She halted, eyes slowly widening as she looked up at Dusty. Confusion was quickly giving way to dawning realization. “...She had something to do with this?”

Dusty nodded. “Yes.”

She continued to stare, her chest rising and falling as her breathing picked up. “That… that bitch!” Dazzle trembled, tears starting to roll down her cheek. “W-we welcomed her in, gave her a place to stay, a-and…”

I couldn’t bear to see it. I couldn’t blame her for growing angry, but as much as anger can be a strong motivator, it can be a very destructive one. Here, in this place, it felt like a blow against everything Emerald had lived for.

So I stepped forward and gripped Dazzle in a tight hug, burying my muzzle against her neck.

Maybe I was thinking of Starlight, then. It was how she would comfort me.

Dazzle stiffened, her breath catching. It was very possible that I had just made the wrong move. I squeezed a little tighter. Then, with a shudder, the tension bled away from her, and she sagged against me, sniffling.

\leavevmode\llap{“}She was trying to help ponies,” I murmured. “She’s helped so many. Don’t let that end here.”

She shuddered again in my grip, but I felt her head bob in a shaky nod.

{\br}%
We left just two hours later, having transferred all our new belongings into the old wagon. We stayed just long enough to seem appropriate, then left. The town still seemed shocked by the news, as if they couldn’t process that Emerald was really gone.

Dazzle had almost broken down again when Starlight offered up Emerald’s rifle. Instead, she pushed it back against Starlight’s chest, saying to keep it.

I felt a little guilty at having hidden away Emerald’s PipBuck. It was entirely practical to do so; if anypony had seen it, there’s a good chance they’d want it returned. It was an incredibly valuable piece of arcane technology in addition to any sentimental attachment, but it was also an incredibly powerful tool for my own mission. The mission came first, yet I still felt uncomfortable with the decision. As I watched these ponies grieving, trying to hold onto the values that Emerald had encouraged, it felt selfish.

After Dazzle pushed the rifle back, I felt even worse. It was possible Dazzle might have insisted I keep it.

Generosity.

I felt it was unlikely, but possible, and that was enough to twist the blade of doubt.

It feels strange to say it about Gemstone, but I was relieved when we finally left.

{\br}%
The journey took four days.

We woke on the second day to see the glow of sunlight creeping under the clouds ahead. By noon, we had passed from the thick and unbroken overcast and into clearer skies, dotted by scattered clouds that blew and drifted in seemingly random directions.

As silly as it was, there was still something uplifting about it. The somber mood that had clung to us since Gemstone faded. Part of me wanted to sprout wings and fly up into the glow of the sun, to revel in its warmth while it lasted. By evening, we were passing under the cloud cover once more.

The weather turned on the third day.

It was no surprise that Dusty was the first to notice the signs, and told us to prepare for rain. “You feel the humidity?” he asked as he tightened straps, bundling up. The rest of us hadn’t noticed. “Only time it starts getting humid this quickly is when it’s about to storm. Damn pegasi just let the rain build up till the clouds practically burst. Ain’t like they got cause to care.”

The sky darkened ahead of us, and we watched as a wall of rain spread with tremendous speed, crashing down to the earth like a tidal wave. It passed overhead, and I looked up to see the water descending upon us.

The rain struck fast, growing to a torrential downpour in seconds. Visibility fell, and the ground rapidly turned to mud. The temperature plummeted. I huddled under my cloak, throwing on a quick transformation to trim my mane and tail short while adding a good inch of fluff to my coat. It was still miserable, but less so.

Our progress slowed to a crawl. Sickle stubbornly pressed on, hauling the wagon through the mud, but even she couldn’t keep up the same pace. Dusty had us halt several times to rest before moving on again.

Darkness came early. Those of us who fit huddled under the wagon, gaining temporary respite from the rain, though not from the mud and puddling water. Sickle curled up beside the wagon and tucked her muzzle in under a foreleg. Despite weathering the storm all night long, she never once complained.

Even with the gear and preparation, we were soaked through. Temperatures dove further during the night, and even the extra fluff to my coat did little to ward it off. Starlight and I spent the night huddled together, sharing a pair of sodden blankets.

The rain was still falling in the morning, though it had started to give signs of slacking. We pressed on after an unenthusiastic breakfast. The whole world was mud. Dusty noted that we’d be less likely to be detected in this weather, though from his dour expression, I think even he wasn’t particularly impressed by this moment of optimism.

The downpour steadily diminished as we continued on. It had fallen to what I would have once described as an “average” rain by the time we reached our destination.

{\br}%
Once again, we lay on a low ridge, ignoring the mud that soaked into our coats. Our binoculars were up, peering through the rain at the cluster of ancient buildings half a mile away. We’d left the wagon almost a mile back, hidden as well as we could manage.

Serenity wasn’t much to look at. It wasn’t a thriving settlement. It wasn’t a slaver base. It wasn’t even a fortified entrance to an underground compound.

It was a half-built office building with about a dozen smaller buildings around it. Stacks of concrete slabs and pipes were arranged by one side of the building. The broken remains of a crane lay toppled beside it. Several earth-moving vehicles lay rusting in the mud, while various broken-down cargo skywagons sat surrounded by empty pallets and broken crates. An open pit that had likely been intended as the foundation of another large building now formed a steep-sided pond, with a bulldozer half submerged in the water. All around the site were a number of temporary structures, much like other construction sites I had seen during the war, though most of the ones here had been broken down and ruined by centuries of neglect.

Whatever Serenity was originally intended to be, it looked as if it had never been finished.

There were no signs of habitation. There wasn’t even any indication that anyone had been there in years. The buildings all looked to be in poor repair or partially collapsed, save for the two that had long ago burnt out, and there seemed to have been no attempt made to repair them.

We continued to scan for several minutes, sharing murmurs about not seeing anything. That lasted right up until Dusty grunted. “Shit.”

I glanced over to him. “What is it?”

He lowered his binoculars, glowering out into the rain. He slowly rolled his jaw, mulling the situation over. It was obvious he didn’t like whatever it was.

Finally, he sighed. “You see the trailer-offices there?” he asked as he raised his binoculars again.

I quickly raised my binoculars again, sighting in on the temporary structures he had indicated. “Yes?”

\leavevmode\llap{“}Look closely at the offices just past them.”

I shifted my view. A single-story building with two broad front windows stood behind those temporary structures. The windows were long since shattered, revealing upturned desks and chairs within. They were a pair of small offices. The faded gear logo of Stable-Tec was easy to pick out, but I had to squint at the other for a moment before making out a distinctive teal, faceted heart, with the words Crystal Life Technologies written beside it.

My eyes widened. “Oh.”

\leavevmode\llap{“}Yeah,” Dusty grumbled.

My heart had decided to start pounding in my ears once again, and I did my best to hide the sudden excitement. Dusty wasn’t going to share in my enthusiasm, after all.

Dusty lowered his binoculars again. “And you want to check it out, I’m sure.”

\leavevmode\llap{“}I needed to find C.L.T. facilities,” I quickly replied, “and we know changelings have been here, too, so—”

\leavevmode\llap{“}I know,” Dusty cut in. “I can put that together, too. Relax. We’ll see about getting you your info.”

I tried my best to restrain my grin. “Thanks.”

He just grunted, and started to survey the surrounding area, looking for approaches.

We moved quickly, following Dusty as he guided us through the muddy low-ground, dotted with deep puddles. Nobody objected; we were already as thoroughly muddy as we could get. From the low-ground, there was a short trot to a rusted-out skywagon, then a dash to the ruined temporary construction office. At each point, we halted, while Dusty peeked around the corner and listened, his rifle up and ready. We heard nothing but the hollow patter of rain on metal. My E.F.S. showed only my friends.

The final dash took us across the paved walkway and in through the vacant window of the C.L.T. office. Dusty advanced into the office with a purpose, his rifle held up and level as we passed desks and knocked-over dividers. I followed as he made his way into a larger, individual office with a desk and terminal. He swept past the desk before exiting the room again, and we made our way to the back room. There was nothing there but a table and some chairs, with several empty bottles lying on the floor. The back door hung halfway open, letting in the sound of the rain outside.

We returned to the main room, where Sickle was shaking off the mud caked to her armor.

\leavevmode\llap{“}We’ll stand guard,” Dusty said, moving to stand behind a desk that gave him a good view out the broken front window. “Make it quick.”

There was little left to find in the main room. Desk drawers lay on the floor from whatever scavenger had rifled through them, and filing cabinets lay toppled and open. I returned to the larger single office, with its terminal. The desk was as thoroughly ransacked as the others. Nothing remained but a few broken pens and other office implements.

I turned to the terminal, fetching my own portable terminal and connecting the two devices. I hit the power button. Nothing happened. Starlight was at the rear of the terminal before I had even started to ask, pulling open the back panel. Within moments, a spark battery was clipped in place, and the terminal screen flickered to life.

\leavevmode\llap{“}Thanks,” I said, earning a pleased smile in return. The boot sequence finished in moments, replaced by a simple message.

\terminal{
\textbf{Client Error Code 4}

\textbf{Server connection failed}
}

My own smile faded as I backed out from the error and surveyed what little was there. “It’s just a dumb terminal,” I said, starting to frown. “The kind that depends on a remote connection to server, only that connection is down. The cache is empty, too. Somepony must have cleared it out, but…”

I stared at the terminal for several seconds before turning to my own terminal, loading up the data recovery tools. While I got to work, Starlight wandered off.

There’s one fun quirk about these arcano-tech devices that many people don’t realize; deleting a file doesn’t necessarily mean it’s gone. The data is usually still there, embedded in the spell matrix until something else overwrites it. It took only a minute before I had extracted a text file from the cache.

\terminal{
\textit{Error log event:}
\textit{Client Error Code 4}<br/>\textit{Server connection failed∩σéust a minor twist. She’ll probably be pretty sore for a few weeks, but she’ll be fine as long as she doesn’t go leaping off any second floor balconies again any time soon.}

\textit{As for your other concerns, I’m a little relieved to find someone else with questions, but sad that I can’t provide any answers. You know there’s a lot of secrecy involved in this collaboration (I assume you got the same stack of NDA papers I did), but it looks like Facet himself is the only one in C.L.T. that knows the full extent of the deal. You remember that mare I mentioned out at Site Alpha? That IT pony that could dig up absolutely anything I needed? She hadn’t even heard it. Heck, she practically fell over herself trying to get info from me! I felt bad I couldn’t help her out after that data she dug up to help with Permafrost, but I haven’t got a clue what’s going on over there.}

\textit{And no, no clue why Stable-Tec had consultants there. None of them mentioned anything before they left? Or were they just as in the dark as you?}

\textit{Sorry you have to put up with this. I can’t imagine how boring it is sitting at a desk for consultation when they’re not consulting you for anything. I’ll see what I can do over here. If Serenity doesn’t need a C.L.T. consultant for whatever they’re doing, maybe we can get you back at Paradise Beach where you can do some good.}

\textit{Hope to see you soon,}
\textit{Skyfrost\&æµ}
}

The file ended with gibberish and fragments of previous messages, long since overwritten into oblivion. I read through the message again. My eyes lingered on the word ‘Serenity’, a name from before the megaspells. A name I hadn’t heard of at the time.

Was Serenity a group that had survived since before the end? Or was this some other group who had taken up their name?

I looked up to speak to Starlight, only to stop myself. She was sitting beside an open hatch in the floor, angling her PipBuck to shine her light down below. She noticed my attention, looking up to me and asking, “Find anything?”

\leavevmode\llap{“}Not really,” I said, standing to walk over to her. “What did you find?”

\leavevmode\llap{“}Looks like an underground utility accessway, like Paradise Beach.” She turned her attention down the hatch again. “You said the terminal was connected to a server somewhere? Well, the cables from it run down here. Might be able to follow it, find the server.”

\leavevmode\llap{“}If it’s on-site,” I said, leaning over to look down the hole. A ladder led down to a concrete tunnel some ten feet below us. “Probably worth checking out, though.”

\leavevmode\llap{“}I just hope it’s not all flooded with the rain.”

We returned to the main room to fill Dusty in on what little we had found. I remember he was a little hesitant about going down into the accessway, but the early-warning ability of our multiple PipBucks minimized the risk.

Things get fuzzier from there.

I remember climbing down into the tunnels. I remember dampness, and following bundles of cables down dark passages. Then there were some rooms. Utility rooms, I think. Machinery. I remember walking alongside a long series of huge pipes. There was some light, spinning in the darkness, and shadows. Then I remember Emerald’s PipBuck making a sound and displaying something, though I can’t remember what. I think I was concerned about it.

And then?

Nothing.