I murmured and rolled to my side, pulling my thick blankets in tight as I nestled into the plush softness of my bed. It was so warm and comfy that I just wanted to stay snuggled up there all day long.

I made a good attempt at it, but consciousness was unrelenting. Eventually, I pushed back the pile of blankets and slowly stretched, yawning as I met the day. I’d slept well past dawn, and the sun lit my cozy bedroom brightly. I must have been quite exhausted to have slept in so late, but for the life of me, I just couldn’t place what I might have been doing.

Maybe I had just stayed up late. That was probably it.

I rolled over to the edge of my bed, reflecting on how it was really too large for just a single pony. Maybe Starlight should be there? No, she had her own house. Still, it was quite large enough for a visit...

My hooves set down on the thick carpet, and I took a moment to enjoy the soft feeling, combined with the warmth of the sun flowing over my side. They were such simple pleasures, so easily available, yet I soaked them in as if it had been ages since I’d enjoyed their comfort.

With a smile, I turned and slowly walked past the end table and dresser, to approach the broad window. I stood my front hooves on the sill, soaking in the sun, and looked out at Serenity.

My home was situated on a loop, and from my second-story window, I could see all the houses that lined that loop, with their spacious yards and lush gardens. The street continued off from the loop, leading to the rest of our pleasant little town of some thirty homes and a hoofful of shops, surrounded by lush grassy hills and light forests.

I swung the window open, drawing in a deep breath of the fresh morning air. Yes, moving to Serenity was the best decision I had ever made.

I couldn’t really remember making that decision, but I must have done so to be there, and that was the important part.

Shutting the window, I turned back to my room. I looked over at the closet, and gave a cursory glance over the contents. I had a good collection of dresses and accessories, after all, and it kind of seemed like a shame to not use them. As I looked through them, I found myself coming up empty. I could have sworn I had a particular cloak, but I couldn’t find it. I know it wouldn’t have matched anything else I had, and it was far more practical than fashionable, but it was disappointing to not find it. I knew I had it. I must have simply misplaced it when unpacking.

Deciding against wearing anything, I made my way to the door. I was nearing the stairs when I heard quiet voices drifting up from below.

I had guests? I didn’t remember having guests, but I couldn’t imagine anyone sneaking in just to chat in my living room. They must be guests, after all. Still, I paused. Snooping in on conversations really is rude, but I couldn’t help it. There was something wonderfully mischievous about it that just seemed so appealing.

\leavevmode\llap{“}...longer than usual, but it shouldn’t be a problem.” The voice was male, with a rich tone that struck me as handsome. I couldn’t picture that voice coming from anything but an incredibly attractive stallion.

Another voice sounded, this one female, with a delicate and clear tone that sounded equally pretty. “Control would say so. They’re not the ones who have to wait in here.”

\leavevmode\llap{“}They’re waiting just like us,” the stallion said, with an inflection that seemed like the auditory equivalent of rolling his eyes. “It’s not like they’re able to just kick back and relax like we are. Someone has to monitor the data. They’re still not sure why she isn’t awake yet. Medical insists she’s fit.”

\leavevmode\llap{“}Fit, except for sleeping for thirteen hours. I’m starting to wonder if she’s ever going to wake up. Control said the brain activity was weird. What if she’s got brain damage?”

There was a long pause before the stallion spoke again. “No, Control says they’re sure it’s not brain damage. They say the brain activity is weird, but familiar. They’ll figure it out.”

\leavevmode\llap{“}Mmm, good for them,” the mare said with a sigh. “I’m bored of waiting. I’m going to see if they thought to stock any drinks. Care to join me?”

There was a huff of amusement from the stallion, but he agreed, and I heard them moving to the kitchen.

Had I taken a physical when I moved here? That must be it. It still seemed weird, but that made sense. I sighed and started down the stairs to join my guests. It seemed like the proper thing to do.

And yet…

I could easily avoid them. It seemed like such a sneaky thing to do, slipping out on guests that I must have invited, but I felt in far too good of a mood to bog things down with medical discussions.

But more importantly, it seemed so mischievous and exciting, like I’d be getting away with something I shouldn’t.

I stepped back to the landing, returning to my room. I could easily fly out from my bedroom window without them ever knowing I was up.

Oh, I wouldn’t let them wait too long. I had still invited them over—probably—and I didn’t want to be rude by completely neglecting them. I just wanted to get out and enjoy the morning a bit, first. A pleasant stroll through the lush park under those clear skies and warm sun seemed so…

The first word that came to mind was “rare”, but that wasn’t right. Serenity was scheduled for warm, clear weather most days. I settled on “pleasant”, even if the word seemed somehow insufficient.

I stepped up to the window, swinging it open, then hesitated. I wasn’t entirely sure why. Sure, I was a changeling, but Serenity was a place of friendship, love, and tolerance. They wouldn’t care if I was a changeling, or a griffin, or even a zebra. So why was I disguised? I must have had a good reason. I looked down at my chest, raising a leg to run a hoof through the thick fluff of my chest. Not only was I disguised, I was disguised in the wrong form! Why had I shortened my mane and tail, and thickened my coat? It was far too pleasant of a day to need that much insulation.

The weather must have been bad before. Yes, it had been cold and rainy, that was it. But not here. Serenity had been scheduled for sunny days with the rare shower. It must have been before I arrived, and I simply hadn’t bothered to change yet. Yes, that was it.

It was only as I went to remove my disguise that I realized I was dangerously low on love. It was far too little to squander on transformation. I was tempted to strip my current disguise to save energy, but I had kept myself disguised for a reason, and while I couldn’t remember what that reason was, I was certain it was a good one. No matter; I knew exactly where to go to get love.

With flying off the table, I instead climbed out the window, moving silently to the edge of the roof. It was just a short drop down to the soft grass below; I’d made more strenuous leaps before.

It did seem a little silly, sneaking out of my own home, but I couldn’t deny that it was exciting.

After a quick brush-down to ensure my thick coat was lying smoothly, I casually trotted off around the loop.

It really was a nice neighborhood. Willow and Rose’s garden was in full bloom, gracing their yard with a rainbow of colors. At the next house over, Ricochet, one of Serenity’s griffin residents, was maneuvering a small cloud to water her lawn. We exchanged a quick wave as she swooped around, and I had the sudden desire to fly up in the air, banking and looping around without a care in the world.

The next house was Strawberry’s. She was out in the yard, working on the fence. The old fence must have needed replacing, judging by the way she bucked one of the posts, snapping it off. She noticed me passing by, and called out to me.

\leavevmode\llap{“}What the fuck are you smiling at? You enjoying this shit, you brain-dead little cunt? Or do you need someone to go over there and fuck-start your head?”

Strawberry has such a colorful way with words. I smiled and gave a little wave as I continued on.

She responded with a snarl as she bucked down the rest of the fence. “Pull your head out of your ass and get a clue, Whisper! You retarded little shit!”

I trotted on with a light step, thinking that I really should take the time to pay Strawberry a proper visit. Maybe I could do that after meeting with my guests. As mischievous as it was sneaking out on them, I couldn’t let them wait too long. That would just be mean.

Starlight’s house was just a few doors down. I was just passing the house of her neighbor, Flay, when her front door opened. I halted, turning to admire the lilac bush at the corner of Flay’s lawn. I wasn’t quite certain why I did that. It was unobtrusive, something that would be unlikely to be noticed, and it let me watch the earth pony couple that exited Starlight’s house without being obvious about watching them.

I wasn’t sure \textit{why} I wanted to watch them, but it seemed like the right thing to do. It was certainly better than going up to a pair of strangers and asking them why they were leaving my friend’s house.

It was another mare and stallion pair. They gave cheerful goodbyes and waves as they exited. I could barely make out what the mare said after the door shut.

\leavevmode\llap{“}She’s certainly the most promising of this lot.”

In the corner of my eye, I could see the stallion nod as they walked toward the street. “That she is. If she loves this ‘Whisper’ as much as she seems to, we should be…”

I waited, listening in for a couple more seconds before I realized they weren’t there. I blinked, looking around, but there was no sign of them. Even more strange, I couldn’t quite place what had happened. I’d been watching them in the corner of my eye, and listening to them talk. I had seen them at one point, then a couple of seconds later I realized I didn’t see them, but I had no memory of them actually leaving.

A creeping feeling ran through my spine. Something wasn’t quite right, and my mind spun as I focused on this new problem, attacking it like some new puzzle. I couldn’t just miss something like that while observing a pair of ponies. If one of them were a unicorn, I would have guessed they used some sort of magic on me. Instead, I was left with the possibility that my perception was compromised. I could recall how muddled my perceptions were after waking up from two hundred years in a cocoon, or the concerningly rising number of times I may have suffered a concussion.

Or maybe I was just more hungry than I thought.

I blinked. The creeping sense of wrongness grew even more as I tried to correlate these seemingly impossible flashes of memory. It was maybe twenty years since I hatched, not two hundred, and in any case, I’d never been in a cocoon. Strawberry would have never tried to kill me, and I absolutely, positively, under no circumstances, had ever been blown up. Not even a tiny bit. I’d had a nice peaceful life in Equestria, among friendly and loving ponies, and that had only gotten better once I had moved to Serenity.

I was losing my mind. That was the solution that came screaming to the forefront of my mind, until I shook the thoughts away. I’d just been sleeping for more than half a day. I must be remembering dreams. Yes, that’s it. The gray skies, the barren, dusty land, the flashes of blood; it was all just a nightmare, and now I was awake.

Suppressing a shiver, I walked up to Starlight’s door.

Moments after knocking, the door opened to reveal Starlight, and her expression lit up the moment she saw me. “Whisper!”

Her forelegs wrapped me in a crushing hug, and her mouth met mine, delivering an eager and energetic kiss that I, after a moment of surprise, happily returned.

It was a blissful moment, tempered only by a single flaw; while I could feel Starlight’s love, it seemed surprisingly distant. Not weak, mind you; it was nice and strong, but it felt as if I were trying to feed from across a room.

One more factoid pointing to possible brain trauma. I was starting to think I should really go meet with those guests of mine.

I must have given away some sign of my inner thoughts, as Starlight stepped back from the kiss, a brow cocked curiously. “You, uh…” Her eyes glanced downward, and she smirked. “Trying out a new look, huh?”

\leavevmode\llap{“}Oh!” I looked down at myself again. “Right, that. I guess I forgot to change at some point, and now I’m a little low on love…”

She chuckled softly, stepping back. “Well, why don’t you come in instead of just standing in the doorway? I’m sure we can fix your little problem.”

I gave a weak chuckle as well, stepping in and turning to shut the door behind me. The moment I did so, Starlight pressed against me, sending me staggering and falling onto the couch. She was above me in an instant, giggling, then lowered her head to nuzzle firmly against my chest. “Mmm, so fluffy!”

\leavevmode\llap{“}This look does have its advantages,” I said, raising a hoof to rub at her shoulder. “Though it may be a bit too warm for the current weather.”

\leavevmode\llap{“}Well let’s get you some love before you overheat,” she said, smirking as she slid up, her mouth meeting mine again. Her hooves gripped at my side, her breath quickening as her body pressed and rubbed against mine. It was exciting, exhilarating, and it took a force of will to press my hoof against her chest, gently pressing her back a bit.

She drew her head back, blinking in confusion. That confusion immediately turned to concern as she saw the fear that had overtaken my expression. “Whisper? What’s wrong?”

\leavevmode\llap{“}I… I think there’s something wrong with me.” I said, slowly shaking my head. “I can barely feed. It’s there, I just… I can’t get at it.” I shook my head, swallowing. “I’ve been getting flashes of memories that make no sense, and I can’t even tell they’re wrong, except they contradict everything else I remember. And then, just a few minutes ago, I… I must have zoned out. I was watching a couple of ponies, and I didn’t even realize they’d left until they were out of sight. I don’t even remember the time passing, I…”

\leavevmode\llap{“}Woah, easy,” Starlight said, her hooves gripping at my shoulders. I was shivering. “Take it easy. Maybe… maybe we should get you to the clinic? You’ve taken a lot of blows to the head, maybe you’ve got a concussion. That would explain things, right?”

The shivering stopped as I looked wide-eyed up at her. “...I have? The blows to the head, I mean.”

\leavevmode\llap{“}A bit more than I’d like, yeah,” she said, giving an awkward smile. “Heck, last time you kinda got…”

She trailed off, blinking, and a weight dropped in my gut.

\leavevmode\llap{“}Were you about to say ‘blown up’?”

\leavevmode\llap{“}Yeah,” she said, sitting back and staring off into space. “I don’t know why. You couldn’t have been blown up. I mean, I know you play with explosives a lot, but—” She blinked again. “Wait a minute, when the hell did you get explosives?”

\leavevmode\llap{“}We found them,” I replied automatically.

She blinked a couple more times, then shook her head. “No, no. That’s not right. It must have been a—”

\leavevmode\llap{“}Dream,” I finished for her, and she froze, mirroring my own look of concern.

I thought for a moment, scrambling for stray thoughts. My ears perked up. “A land mine. Do you remember a land mine?”

Her hoof moved to her neck, her eyes widening for a moment, but she quickly shook her head. “N-no. I remember a dream, but… no, where would we have ever ran into a land mine? But… but \textit{you} remember it, too?” Her ears pinned back, and she looked around. “Oh, shit. Are we dreaming?” She looked back to me. “Wait, if I’m dreaming, are you even real?”

\leavevmode\llap{“}We’re not dreaming,” I said, pushing myself up to a more upright position. “But something isn’t right. Something’s messing with our heads.”

\leavevmode\llap{“}Oh, Luna,” Starlight murmured, her hoof moving to her head. “Am I going insane? What’s going on?”

\leavevmode\llap{“}I don’t know, but we need to figure it out.” I sat up, reaching out to grip Starlight by the shoulders. “What do you remember? How did we get here?”

\leavevmode\llap{“}Emerald’s PipBuck,” she answered. Then her ears drooped. “Oh, no. Emerald. Did she really…”

I swallowed around the lump that tried to form in my throat. My brain was telling me that what I remembered couldn’t be true, that I could have never witnessed another pony dying like that, but it was clear I couldn’t trust my own memories. My own mind was working against me.

That was a problem. I knew how good I was at telling a lie.

I shook off the thought. “And \textit{why} did we come to Serenity?”

\leavevmode\llap{“}Because it’s such a nice place,” Starlight said, shuddering. “And you thought you might find—”

She froze again, her eyes widening. “...Your family.” Her shoulders heaved as her breathing accelerated. “Changelings.”

I nodded. Yes, that sounded familiar.

\leavevmode\llap{“}Changelings,” Starlight murmured. “Changelings make themselves look like something they’re not.” She looked around the room. “Oh, Luna, goddesses, is any of this—”

She jumped and yelped loudly at the knock on her door. As she clamped her hooves over her mouth, a smooth-spoken stallion’s voice called from outside.

\leavevmode\llap{“}Miss Starlight? Are you okay?”

She lowered her hooves to shout back. “I’m fine!”

\leavevmode\llap{“}Can we come in?”

Starlight scrambled to the window, peering out. “Just a second!” She leaned in close to me, quickly whispering. “It’s the welcoming committee, again. I don’t know why they’re back. Are they changelings, too?”

I looked around, quickly trying to form a plan. I could practically feel my grip on the situation slipping as my mind told me everything was fine. “I’m going to hide. Let them in, see what they want. Just don’t tell them I’m here.”

She trembled, staring at me as if she feared she’d never see me again. “W-why?”

Giving my best reassuring smile, I reached up, holding her by the shoulders once more. “Sneaky bug stuff.”

The look of fear cracked as she gave a timid smile, and she nodded.

She waited until I had slipped up the stairs and out of sight before opening the door.

\leavevmode\llap{“}Hello.” She sounded nervous. “I wasn’t expecting to see you again so soon.”

The stallion answered her. “We heard you shout. Is everything okay?”

\leavevmode\llap{“}Uh… yeah, yeah, I’m fine. I, uh… the knock just kind of surprised me, is all.”

\leavevmode\llap{“}Is something wrong?” the stallion asked. I could faintly hear the sound of hooves as he stepped inside. “You know, we’re here to help you. Why don’t you tell us what’s bothering you and we can help out.”

\leavevmode\llap{“}Oh. Yeah.” The nervousness had vanished from Starlight’s voice. “Sorry, I was just feeling a little freaked out.”

A mare’s voice spoke up. “Why don’t you tell us what’s bothering you? I’m sure we’ll be able to help.”

\leavevmode\llap{“}I’m not really sure how to describe it,” Starlight said. “It’s like… I’m remembering things, but they don’t make sense. Like, guns and fighting, and… ruins. And there were explosions, and… a land mine. And I remember Whisper was there.”

I winced at my name, fearing what she might say next.

\leavevmode\llap{“}And… and it all feels like a dream, but I know it wasn’t. It was too real, but how could it be real? It doesn’t—”

\leavevmode\llap{“}It’s okay,” the stallion said, cutting her off. “You must be remembering your term in the Army. That’s what it is.”

\leavevmode\llap{“}I… was in the Army?”

\leavevmode\llap{“}For a very short while, yes. You were just given a medical discharge. It was nothing serious, but I guess you got knocked around a bit if you’re having trouble remembering. It’ll clear up on its own in a few days, but you might want to pay a visit to the clinic. A little medical magic will help speed up your recovery.”

There was a moment of silence, followed by a faint chuckle. “Oh, that… that makes a lot of sense, actually. Sorry about that.”

\leavevmode\llap{“}No need to apologize,” the stallion replied. “Stress can have a tremendous impact on a pony, and especially our soldiers, but it’s something we’ve become quite adept at diagnosing and treating. A couple days of confusion is completely normal. You can ask your neighbors. Several of them came from similar backgrounds, and they’ve gone through the same thing you have.”

\leavevmode\llap{“}That’s a bit of a relief, yeah,” Starlight said. “It’s still, you know, just a little freaky not remembering stuff like that, but… but yeah, it’s kinda coming back. Sorry. I feel a little silly now, freaking out like that.”

\leavevmode\llap{“}Please, don’t worry about it. We’re here to help you. Was there anything else bothering you?”

\leavevmode\llap{“}No, that was it. Thank you. I… I think I’ll head down to the clinic in a bit. Seriously, thank you.”

The mare answered, sounding pleased. “It’s what we’re here for.”

They said their goodbyes, and moments later the door shut again. I crept down the stairs, until I could see Starlight giving a slow, deep sigh. She turned and smiled as I made my way down.

\leavevmode\llap{“}Are you okay?” I asked, and she grinned.

\leavevmode\llap{“}Yeah. Sorry about all that. You know, you should have stayed. Ponies are going to think you’re weird if you keep hiding any time somepony comes by.”

She stepped in, nuzzling under my chin, but I leaned back. “I’d say we have more important things to worry about. We need to figure out what’s messing with our heads, and I’m pretty sure those ponies are in on it.”

\leavevmode\llap{“}Don’t worry about it,” Starlight said with a chuckle. “Those two were with the welcoming committee, they were just here to help. And the whole ‘head’ thing was just stress messing with us.”

I froze as she gave back the story those ponies had fed her, and she slipped in again, nuzzling. “Starlight, this isn’t stress. Those memories, they’re real, but they don’t fit with everything else. Something is messing with our heads.”

\leavevmode\llap{“}It’s just the stress,” Starlight repeated, and chuckled. “I can’t believe I’d forgotten we were in the Army, but that explains where all that shooting and explosions came from. It’s all coming back now.” She drew back, looking me in the eyes with a look of sudden realization. “That’s where we met, wasn’t it?”

I stared at her, heart hammering. The Army made so much sense; I could remember fighting alongside her. Dusty and Strawberry were there, too. Were they in uniform? Yes, Dusty was. But I couldn’t remember if the others were. Why else would we be fighting? The idea of serving, of following a mission, that sounded completely right. The Army was the only way that made sense.

With a shudder, I pushed away the thoughts. I already knew someone was messing with my mind. I couldn’t trust my own memories. I couldn’t trust my own \textit{mind}.

To say that was a problem is quite the understatement. The mind is an Infiltrator’s best weapon.

An Infiltrator. I wasn’t a soldier. I was never in the Army. I did not serve Equestria. All of this was a lie.

I took a moment to evaluate my situation, to weigh my options. It was clear that something was messing with my mind. I seemed to be forcing past it, though it was still a muddled mess. Maybe, if I was lucky, I might be able to help Starlight get through it, but she seemed far too quick to latch onto those ponies’ story. It would be difficult. I had no idea if Dusty or Strawberry could be brought around, though from the behavior I had seen earlier, I doubted Strawberry would take much convincing.

But what then? It wasn’t just enough to know the truth. If they were messing with our minds, we were vulnerable. I had no idea what kind of troubles we might face outside of this lie. I was certain this place was a lie, but I had no idea how far that lie extended. I had no idea what to expect, and therefore, no ability to plan for it. Our captors—if that’s even what was going on—had every advantage. We couldn’t fight this.

And if I couldn’t fight it, the only way to get through was to go along with it.

I put on a reassuring smile, lifting a hoof to tenderly touch Starlight’s cheek. “Yes. Yes, that’s exactly right.”

Her expression brightened up, and she leaned in, giving me another kiss. I took a few moments to enjoy the sensation before gently drawing back. “I should get back home. I have a welcoming party of my own I need to talk to.”

Starlight put on a mock-pout. “Aww.”

\leavevmode\llap{“}Don’t worry,” I said, still wearing that smile. “I’ll see you soon.”

The smile vanished the moment I had stepped outside. My heart hammered as I walked around the loop to my own house. Strawberry was nowhere to be seen, and a pair of ponies were floating a new fence into place where the old one had been. As I passed her house, I heard the clop of hooves trotting on the street. I looked back in time to see a pair of ponies, the same two I had first seen leaving Starlight’s house, now hurrying back to her door.

As I approached the door of my own house, I could hear the muffled sounds of the ponies inside. They sounded like they were arguing.

The argument stopped the moment I opened the front door. The mare quickly set down the hoof she had been gesturing wildly with, and called out to me. “Oh, thank goodness! There you are, Whisper! You gave us quite the scare, there. Where did you disappear to?”

\leavevmode\llap{“}I snuck out,” I said. “But now I’m back, and I’d like to talk.”

\leavevmode\llap{“}Well, that’s what we’re here for,” the stallion said. “But you know, there’s no need to sneak around, here. Serenity is a nice, peaceful place.”

\leavevmode\llap{“}I’m sure,” I said in a dry tone. Adrenaline teased at my senses as I took a calculated gamble. “Are you changelings?”

The mare blinked. “What? No, no changelings here. Why do you ask?”

The stallion beside her, however, effectively torpedoed her words. He stared at me, his eyes widening in dawning realization. He opened his mouth, gasping a single word. “Disconnect.”

The mare’s head turned, drawing my attention for just an instant. In that instant, I realized the stallion had vanished.

A moment later, I realized the mare had vanished, too.

I twisted around, looking this way and that, until the entire world went away.

{\br}%
Light and sound twisted around me in an incoherent jumble. The world turned, and hooves pressed against me. I tried to move my head against the pressure that tried to hold me as up turned to down, and something soft pressed against my side. Something tugged on my forelegs, and something warm wrapped around my hooves.

Among the jumbled colors, a pale-blue orb drew my attention, though my addled brain made no sense of it until it turned to me and narrowed, mirrored by a twin just beside it. My view focused rapidly on the glossy black around them, until I could make out the expression of an angry changeling.

I jerked, adrenaline flowing. I tried to lift my head, only to find myself restrained. I tried to call out, only to produce a muffled moan; I was muzzled. More hooves gripped and pressed at my sides, and I twisted my head to see several more changelings. I was lying down, strapped to a gurney, with my legs bound with goo. The changelings were working over me. The green light of PipBuck screens shone from their forelegs. The jumble of sounds I heard were words.

\leavevmode\llap{“}She’s regaining focus,” the angry one near my head said.

\leavevmode\llap{“}Tertiary leads disconnected. That’s the last of it.”

\leavevmode\llap{“}No, hold the sedative. I want her lucid.”

\leavevmode\llap{“}Get those legs restrained. Lay it on, she’s waking up!”

\leavevmode\llap{“}Get those guards in here.”

I twisted my head the other way. I couldn’t see much past the changelings over me. I saw one of the guards stepping up, clad in armor while a magical energy weapon floated beside her head.

\leavevmode\llap{“}Move her.”

The gurney rocked under me as it started to roll, surrounded by changelings. I looked around with wide eyes, producing more muffled sounds as I tried to call out to them. So many changelings, so close. They were right there!

As we moved, I got a parting glimpse of the room. I was being wheeled away from a white contraption that looked as if it had split open. It took me a moment to place it as the white eggshell of a suspended animation pod, just like the discarded remains in the lab I had woken up in. More pods filled the wide room. There were dozens of them, maybe sixty in total, and I could see faces inside them.

With a lurch, I tried to search out Starlight and the others, but the door shut behind us, cutting me off.

I was rolled down a hall and into a small room, bare except for a pair of plain benches. It looked like a jail cell.

The group of changelings hauling the gurney parked me by the back wall, engaging the wheel brakes. Most stepped back, while the angry-looking one returned to look me in the face. Her horn glowed brightly, grabbing my eyelids so I couldn’t blink, and shined a light in my eyes. A few seconds later, she stepped back, addressing the pair of guards who flanked her. “She’s fully responsive. Keep a close eye on her.”

One of the soldiers grunted in reply, then addressed me, her large magical energy weapon leveled straight at me. “If you attempt any magic, we will immediately shoot and kill you. Do you understand?”

The straps made nodding difficult, but I managed.

I was there for several long, silent minutes, with only the pair of wary and suspicious guards for company. Unable to attempt conversation, I remained still. I didn’t want to test their nerves, or their reflexes.

I found myself staring at one of the soldiers. A changeling, dressed in armor much like my own, with a PipBuck on her leg. I’d found changelings! But this changeling was standing ready to kill me at a moment’s notice. As excited as I was to find changelings, I was still in an incredibly dangerous and uncertain situation.

And there was a room nearby with several dozen ponies—and other species—held in suspended animation. While I could think of a few reasons to do so, one stood out as the most likely reason a group of changelings would organize something like this, and it was a troubling one.

It would also explain why I felt so drained of love.

I must have been in that room for about five minutes before several guards entered. To my shock, two Enclave soldiers entered with them. A moment later, I realized my error. The soldiers were clad in Enclave armor, certainly, but I could see the fanged, chitinous muzzle below the armor’s visor. They were changelings wearing Enclave armor, and I noticed then that the back-plate had been painted a dark, iridescent blue, as if to mimic a changeling’s coloration.

\leavevmode\llap{“}Move her,” one of the power-armor soldiers ordered, and the guards rolled me out on the gurney.

This journey took quite a bit longer, leading me through many halls and an elevator. The construction was rugged but refined, with reinforced metal walls, hydraulic doors, and plentiful lighting. It looked like Stable-Tec construction.

Finally, we rolled into a large room. As we were coming to a halt, a beautiful voice, rich and melodious, called out. “Release her.”

My heart hammered, while the guards stepped in, undoing the straps that held me. Moments later I was floated off and set on the ground, and the goo that bound my legs dissolved away. I got a hoof under me to push myself up, and looked in the direction of that voice.

Some twenty feet away lay a large cushion, and lying atop it was a young changeling queen, her head held in a regal pose. Flanking her were a pair of soldiers in black-painted Steel Ranger armor, much larger and bulkier than the Enclave-armored soldiers I had seen before. They stood tall and proud like statues, sporting heavy magical weapons.

The queen’s slit-pupil eyes were fixed on me, half-lidded as if bored with me. Her fanged mouth opened as she spoke again. “Lose the disguise.”

I gulped, well aware of the many guards around me, and tugged at the strings of my magic. My flames stripped away my disguise, leaving me in my natural form—minus my armor, which I kept concealed for now.

The queen continued to stare at me for several long seconds, those bright green eyes silently judging me. Finally they twitched to the side, looking at the group that had brought me. “Leave us.”

They bowed and left without comment. The two armored hulks beside her remained still.

Once the doors had shut, the young queen stood, advancing toward me in a slow, graceful strut. Her long mane fell across her shoulders, while those beautiful green eyes remained fixated on me. I tried my best not to stare.

She halted a couple of yards away, looking down at me. “Who are you?”

I swallowed again. “My name is Whisper,” I said, then quickly bowed my head as an afterthought. “Your Highness.”

She hummed quietly to herself as she considered me. Her posture tightened, her head rising slightly, proudly, before speaking again.

\leavevmode\llap{“}I am Queen Chrysalis.”

My gut dropped, and I completely failed to hide my reaction, eyes widening at those words. There was no possible good reason a changeling queen would adopt \textit{that} name.

The situation had just gotten worse.

Her eyes narrowed, glaring down her snout at me. “Is there a problem?”

\leavevmode\llap{“}S-sorry,” I stammered, allowing the fear to show for only a moment before tightly constraining my expression to one of confusion. “I’ve heard that name before, but… I’m not very well-versed in history, but I thought Queen Chrysalis lived before the Great War.”

Her lip twitched, baring her fangs a little more. She spoke again, her voice darkening with irritation. “I am Queen Chrysalis the \textit{Sixth}.”

I forced my body language to relax. “Oh. My apologies. That makes much more sense.” I gave a little twitch, then bowed my head. “Your Highness.”

She gave a faint snort. “It doesn’t matter. Now tell me, Whisper. Why are you here?”

I looked up at those waiting eyes, watching me like a predator, ready to pounce. My mind raced, scrambling to piece together an appropriate story. “I… I’ve been looking for other changelings. I learned that there might be changelings around here, so I came looking.”

The queen’s voice was sharp and demanding. “\textit{Where} did you learn that?”

\leavevmode\llap{“}F-from another changeling!” I quickly replied, suppressing a shiver. “Except I didn’t know she was a changeling. It was a pony named Emerald. At least, I thought she was a pony, until a raider shot and killed her. She had a PipBuck, and after digging around on it, I found that she’d come from here. I thought I might find some other changelings here, or at least clues to where they were.” I looked around, putting on a slow, awed smile. “I didn’t think I’d find a whole hive!”

\leavevmode\llap{“}And \textit{why} were you looking for us?”

I flinched a little, bowing my head again. “M-my queen and my hive are… are dead. I’ve been on my own for so long, I…” I slowly sagged, bowing my head again. “I didn’t know what else to do. I didn’t want to be on my own any more. When I learned there might be more changelings—”

\leavevmode\llap{“}How did your hive die?”

I looked up, blinking, my ears pinning back. I gulped, covering for the moment of thought. “I think they starved. I was in a cocoon because we lacked enough love for everyling. When I woke up, they were all dead.”

She slowly walked to the side, looking off in thought. “Another hive. Noling has heard of another hive in at least a century. You must have been very good at hiding.”

\leavevmode\llap{“}We tried to stay low-key,” I said. “We didn’t even have a proper hive, certainly nothing as impressive as you have. We had to hide among ponies.”

\leavevmode\llap{“}And yet, your hive failed.”

Wincing, I ducked my head. “It was always difficult finding enough love. Ponies can be… paranoid.”

She gave a slow nod, humming thoughtfully, then looked back to me. “So now you come here, hoping to… what? Join some \textit{other} queen’s hive?”

My eyes widened slightly as I looked up at her. “If… if you’d have me.”

She frowned, and I prostrated myself, bowing my head until my nose touched the floor. “Please, Queen Chrysalis. I have nowhere else to go. I have no purpose on my own. I’ll do anything you ask of me, without hesitation, just to have a purpose again.”

Her head tilted as she looked down, towering over me. “You seem quite eager to cast aside your loyalty.”

I closed my eyes, ears hanging low. “I will never betray my hive,” I said, my tone firm despite the tremble in my voice. “But there is nothing remaining to be loyal to.”

\leavevmode\llap{“}So you’re certain every member of your \textit{former} hive is dead?”

I inhaled sharply, eyes opening to look up at those piercing eyes. “...My queen is dead, and my hive is shattered. I know most of them are dead. If any others did manage to survive… if they do not serve the same queen I do, then they are no longer of my hive.”

The corner of Queen Chrysalis’s mouth twitched upwards. “Hmm.” She turned, slowly pacing to my side as she thought. I remained still, keeping my head bowed. “Then I suppose I have one more question,” she said, turning to face me again. “What are your thoughts on ponies?”

I blinked in surprise. I hadn’t expected a question like that. Here I was trying to convince her that I would be a loyal and obedient subject, and she instead wants to know my opinions on something completely unrelated? It made no sense, and I had nothing ready.

I considered what a queen who would adopt that particular name might want to hear, and cautiously offered it. “Ponies are necessary, but… problematic. They’re the best source of love, but they can be dangerous and paranoid. And lately… since my hive fell, I’ve seen some of the worst ponies have to offer. I’ve seen what raiders do to other ponies, and they’re even worse with non-ponies…”

Noting that the corner of her mouth had risen in a faint, smug smile, I pushed just a little harder. “And I can’t help but note that it was ponies who created the megaspells that put us all where we are now.”

Queen Chrysalis smiled, revealing her sharp teeth. “Yes, it was, wasn’t it?”

I nodded silently.

\leavevmode\llap{“}Tell me, how did your \textit{former} queen deal with ponies?”

\leavevmode\llap{“}We hid,” I said. “We stayed in the shadows, trying to steal what love we could find without drawing attention.”

\leavevmode\llap{“}And because of this,” Queen Chrysalis said, “her hive now lies dead.”

I winced, then nodded. “Yes, Your Highness.”

She gave a pleased hum, turning to slowly strut back to her throne-like cushions. “You’re right, you know. Ponies are a problem. They’ve always been a problem. We’ve had to hide in the shadows for centuries because of them, living like thieves and vultures. They’ve already tried to murder our entire species. They turned the world into a wasteland, and even then, they manage to find new forms of barbarism. Petty warlords, slavers, raiders.”

I watched her, ears perked attentively; a good, eager, enraptured audience.

She turned and sat primly atop her cushion, her head held high and proud. “You have come to us at a great time, Whisper. The Grand Pegasus Enclave, the final bastion of the old world, is tearing itself apart. The great slaver army of the north has been shattered. The twisted Goddess behind the monstrous alicorns has been slain. Even the remnants of the Steel Rangers have turned on each other, decimating their numbers.

\leavevmode\llap{“}Destroying the world wasn’t enough for them. Ponies have had every opportunity to change their ways, but even in this wasteland, they continue to spread death and destruction, and we suffer for it. The queens before me have allowed this to stand for too long, but I will do what they never had the ability or courage to do. It is time for a change.”

She looked down at me, seeing my smile. Her own grin grew, sharp-toothed and eager; I think she liked having an audience. “The ponies are divided, and their power is broken. A tremendous opportunity has presented itself to us. So, tell me, Whisper… what do you think we should do?”

I stared back, my heart hammering as I considered the question, knowing exactly what she had in mind. My eyes darted to the black-painted power armors flanking her, a small portion of what seemed to be a well-equipped fighting force, while I thought of the tremendous resources available to the hive. The expected answer was obvious. “We could rule.”

\leavevmode\llap{“}The reign of ponies is over,” Queen Chrysalis said. She held her smug smile for a moment before turning to one of the motionless soldiers. “Call in Ocelli.”

The soldier nodded, the first time I had seen them move. Meanwhile, the queen turned back to me. “Answer all of her questions, and follow all of her directions. Do this, and you will be allowed to remain as a member of my hive.”

I grinned wide, and bowed my head, blinking as my eyes teared up. “Thank you! Thank you, my Queen!”

Ocelli was a small, lean changeling, but her body language was full of confidence, even as she bowed to her queen. She led me off to a side room, accompanied by a pair of guards. I followed, grinning like a loon and occasionally pausing to wipe away tears.

\leavevmode\llap{“}Sit,” she said, indicating a chair beside a plain table, while she sat opposite it.

I followed her direction, giving a sniff and another wipe at my cheek, my wings fluttering a couple times before lying flat again. “Heh, sorry. I’m probably not making the best first impression, getting so emotional and all. It’s just… it’s been a long time.”

\leavevmode\llap{“}So I gather,” Ocelli said with a faint smile, while she lay one foreleg across the table to view her PipBuck screen. “Which means we’re going to have a lot to talk about.”

She started in with the questions, which I answered dutifully. I told her of Queen Shadow, and how she had guided our nomadic hive around the edges of pony society, sneaking in to steal what love we could and scurrying off before any suspicion could be aroused. I told her of my incomplete training as a scout, cut off when I was placed in a cocoon to conserve my hive’s dwindling supply of love. I described my confused experience, waking up in the depths of a mine near Rust, surrounded by the remains of my dead hive, and wandering out to find the slaughtered raider camp above.

Then I described my time wandering the Wasteland. Meeting Starlight, Dusty, and Sickle. Our encounters with raiders and mercenaries while scouring for old-world ruins. And of course, though I was hesitant to mention it, my eventual uncovering.

\leavevmode\llap{“}Wait,” Ocelli said, her expression skeptical. “They know you’re a changeling?”

I nodded. “I managed to hide it for a while, but I had no idea what I was doing. I guess it was probably inevitable, but… what could I do, really? I needed the food, and…” I slowly shook my head. “Hell, I was scared when they found out, but it worked out. Probably helps that they had no idea what a changeling was. I even managed to convince them to help me look for more of my own kind.”

\leavevmode\llap{“}Interesting,” she said, tapping a couple buttons on her PipBuck. “Does anypony else know?”

\leavevmode\llap{“}No!” I shuddered. “No, I was scared enough that they knew, and I think they were scared of other ponies finding out. I was more useful if nopony else knew what I could do.”

\leavevmode\llap{“}I see. So, what does that make them to you? Friends?”

I stared off into space, considering that question for a moment. “More like… pets, I guess? They were good food and decent company, and I’d rather not see them harmed if it’s convenient, but I wouldn’t consider them friends, no.”

She hummed and nodded, reading something from her screen. “...That big one, Strawberry—”

\leavevmode\llap{“}Sickle,” I said, then smiled awkwardly. “Sorry. She hates that other name, and I learned not to offend the huge, short-tempered pony who could casually crush my skull.” I raised a hoof, rubbing at the side of my head. “One concussion is more than enough, thanks.”

Ocelli nodded. “Sickle, then. We’ve been having difficulty with her.”

\leavevmode\llap{“}I don’t doubt it,” I said with a soft snort.

A smile flickered for a moment on Ocelli’s face. “It sounds like you were able to keep her in line and get love from her. How?”

\leavevmode\llap{“}Well… keeping her in line is more like knowing when to let her loose and what direction to point her. She loves to fight and kill, and the best I could do is make sure she fights and kills the right ponies. She gets bored when she can’t fight, too. Drugs and sex help, but she still tends to be pretty aggressive.”

\leavevmode\llap{“}We obviously can’t have her killing others in the simulation,” Ocelli mused. “Sure, it won’t actually kill them, but I can’t imagine the extra work the simulation staff would have to put in to deal with the chaos that would cause. Drugs are out, too, unless she’d be content with a little alcohol and some cigarettes.”

\leavevmode\llap{“}A \textit{lot} of alcohol,” I said. “Though that only mellows her a little. Combine that with hard drugs or sex, and that could keep her pleasant.”

Ocelli pondered that, tapping a hoof to her chin. “Sex we could manage. Maybe the sim staff could steer one of the stallions to her. Or does she prefer mares?”

\leavevmode\llap{“}I think she’s fine with either, but prefers stallions,” I said. Then I clarified. “Um, stallions plural. Unless you’ve got one just as big and aggressive as her, she’s not going to be satisfied by just one.”

Ocelli frowned thoughtfully, then slowly shook her head. “Sounds like she’s going to take more work than she’s worth. Pity. The raider types can be tricky. The staff was planning on euthanizing her and being done with it, but they hoped you might have some insight.”

\leavevmode\llap{“}I’m afraid not,” I said with a slow shake of my head. “I think she’s too well-adapted to the Wasteland. I know the hive has employed raiders in the past, though. It’s part of how I found my way here. If she isn’t useful in that ‘simulation’, she might be useful as some sort of hired agent.”

Ocelli hummed. “I’m sure it’s under consideration. Now why don’t you tell me what happened after they discovered you were a changeling?”

I continued on to tell her how I convinced the others to help me look for any signs of other changelings. How we’d followed a clue about a possible changeling hive in the badlands, only to find a gaping crater in its place. How we’d scoured old-world offices, looking for clues. How after Emerald had been killed, we had realized Lady Amber was a changeling, and came looking for Serenity. How we had seen Stable-Tec and C.L.T. offices there, two of the companies she had sent us looking for at Paradise Beach.

The whole way, she kept slipping in quick questions, clarifying little details. We must have spent three hours at it before she finally called it quits. “I think that’s satisfactory. I’ll pass this information on, then we can get you situated. Come along.”

She led me out, and I followed her down a series of halls, while the guards remained behind.

The whole place was in excellent condition, well maintained, and full of changelings going this way and that. The hive was alive and thriving, and I grinned as I looked around. So many changelings, all carrying out their business, and I moved through them as if I truly belonged there.

I caught the faint smile Ocelli wore, and gave a sheepish smile of my own. “Sorry. I’d gotten so used to being alone.” I glanced to the side and quickly changed the subject. “Is this a Stable? I’ve seen pictures before, and the architecture seems pretty distinctive.”

\leavevmode\llap{“}It is,” Ocelli said with a nod. “Ironic that the ponies should have become better than us at underground shelters, but thankfully, their wartime preparations could be repurposed to allow our hive to survive.”

We approached a door, flanked by a pair of chatting guards.

\leavevmode\llap{“}...It’s still eight times I’ve killed you,” one of them was saying, grinning smugly.

\leavevmode\llap{“}It’s random chance, could have happened to anyling,” the other guard said, giving a short snort, then cocking her head. “Wait, eight? The Thunderhead defense made seven.”

\leavevmode\llap{“}I got you in the the convoy breakthrough, too.”

\leavevmode\llap{“}The convoy—we were on the same side!”

The first guard’s grin grew a touch wider. “I shot, you died. It totally counts.”

The second guard started laughing. “That should count \textit{negative} you—” She abruptly stopped on seeing our approach, straightening up and giving Ocelli a quick nod. “Ma’am.”

She didn’t so much as pause as she walked by them. “Friendly fire. I see your training is going well.”

The first guard’s grin had turned sheepish. “Ah, yes ma’am.”

We passed through the door the guards were flanking, and entered into a workspace. A few technicians were working over PipBucks, with at least thirty more PipBucks arrayed on shelves behind them. As we approached the technicians, I picked up the pace to move beside Ocelli and quietly ask, “What, are changelings immortal in this hive?”

\leavevmode\llap{“}Oh, that?” She smirked, shaking her head. “They’re talking about combat simulations. It’s for training purposes, but many of the soldiers see them as nothing but a game.”

\leavevmode\llap{“}Ah. I see.”

Ocelli had one of the technicians retrieve a PipBuck and make a few quick adjustments to its systems before presenting it to me.

\leavevmode\llap{“}Every member of the hive gets one,” Ocelli said. “Don’t remove it unless absolutely necessary, and \textit{always} keep it on you. This one is also heavily restricted at the moment. I’m sure you understand, it’s just a precaution. I’m sure the restriction will be relaxed once you’ve been here a while.”

It also gave them an easy way to track my movements, of course.

\leavevmode\llap{“}Thank you!” I said, smiling as she clasped the device to my leg. Lights flickered before my eyes, quickly forming into the increasingly familiar E.F.S. readout. I wasn’t surprised to see that S.A.T.S. was disabled. Then I looked at the compass, and blinked. “Should I be concerned about that cluster of hostile contacts?”

\leavevmode\llap{“}Hmm?” She turned her head, looking in the same direction I was, then relaxed, chuckling softly. “Oh. That’s the zoology department. They study Wasteland wildlife, and most of it is quite hostile. You learn to tune it out after a while.”

\leavevmode\llap{“}Oh, good,” I said, relaxing with a soft sigh. “Sorry. First day here, and I thought I’d already offended someling.”

\leavevmode\llap{“}Don’t worry about it,” she said, smiling. “Also, you might see the occasional hostile contact along the west side of the hive. Some of the food-ponies flash hostile every now and then. In fact, do you see a hostile over there right now?”

I looked over, then shook my head. “All green.”

\leavevmode\llap{“}Hmm, well there’s something,” she said. “Your pink ‘pet’ has shown up as hostile to every other member of the hive.”

I frowned. “Considering the number of times she’s nearly killed or raped me, I question these things’ definition of ‘hostile’.”

Ocelli blinked in surprise, her head tilting. “I… guess so.” She slowly shook her head, and changed the subject. “Anyway, the equipment you and your companions had is also stored here. If there’s anything you need, or that you think would be useful to the hive, I can see about getting it returned to you eventually.”

\leavevmode\llap{“}I think I’m good,” I said. “I can’t imagine needing any of my weapons in here.”

\leavevmode\llap{“}No, I expect not,” Ocelli said. “Anyway, let’s get you a place to rest. You’ll be staying with me for now. Just a temporary thing, I’m sure.”

\leavevmode\llap{“}Sounds good.”

Naturally, they’d want to keep an eye on the new ‘ling. The queen may have said I was accepted into her hive, but I knew that wasn’t quite true. I was allowed to stay and prove myself worthy of being a member of the hive, but they were going to keep a close eye on me until then. That, or they were hoping to get more information out of me. Either way, it was a sensible precaution.

She led me out and down new halls. “Speaking of equipment, that was quite the arsenal you walked in here with. You said you were a scout?”

\leavevmode\llap{“}Training to be a scout,” I said. “I’d only gotten basic weapons training, but I’ve been learning quickly. Dusty, the yellow stallion, helped with that.” I gave a short chuckle. “A couple months ago, I’d have thought that gear I had was absurd overkill. After the experiences I had out there… well, overkill has a lot going for it.”

\leavevmode\llap{“}Better than the alternative, I suppose,” Ocelli said with a momentary smile. “And the explosives?”

\leavevmode\llap{“}That’s mostly new. I’m surprised how simple it is, though. Connect two wires to a blasting cap, put it in the explosive, hit the trigger when you’re far enough away, boom.” I shook my head. “Still a little unnerving carrying something that dangerous, though. Same for the grenades.”

\leavevmode\llap{“}And the computer gear?”

\leavevmode\llap{“}Basic computer intrusion training,” I said. “In case I ended up scouting out any old-world facilities. I was lucky enough to find some good equipment at Paradise Beach. Ended up making a lot of use out of that recently. Heck, it’s a surprisingly fun pass-time. Like… a puzzle, I guess?”

She nodded. “I guess I can see that.”

\leavevmode\llap{“}Not that any of that helped us,” I noted. “I’m still not sure what happened, here. We went underground, hoping to follow some cables to a central server, and then everything just got… fuzzy. Was it gas?”

\leavevmode\llap{“}It was,” she said, though she didn’t elaborate.

We exited the hallway, entering a public atrium. More changelings walked by, but others stood or sat around, talking or relaxing. As she led me along, she spoke again. “I know we just spent a lot of time with all the questions, but I’d kind of like to hear some more of your past. Maybe once we get back to my place, you could share some stories? It’s a good way to pass the time.”

Or in other words, maybe I could give her more useful information I hadn’t shared yet. “Sure,” I said, smiling, and she smiled back. It was a soft, pleasant smile. She turned back to watch where she was going, but I noted her head was turned ever so slightly, keeping me in her vision. Watching. Analyzing.

I avoided looking too close at her, letting her watch. Instead, I let my gaze wander over the changelings we passed. There were so many! Even the spacious Stable-Tec-designed atrium felt pleasantly crowded, filled with changelings traveling to and fro, relaxing on benches, chatting, and even snuggling up together. I caught bits and pieces of conversation as we passed.

\leavevmode\llap{“}...for ten hours, but I’ve got the next two days off while we wait for the techs to do the final engine tests before…”

\leavevmode\llap{“}...almost eight hundred yards, and with a carbine! I told you I’m a good shot!”

\leavevmode\llap{“}Your team must have put a thousand rounds into those buildings. One of you were bound to get lucky. That’s not so…”

\leavevmode\llap{“}...of the new armor. She ate dirt so hard! The whole requisition team was laughing their shells off, and she…”

\leavevmode\llap{“}...cockpit is just weird. How do they even fly with their wings inside the vehicle?”

\leavevmode\llap{“}I dunno. Magic?”

My mind raced as I fixated on a small group we were passing; most of the group was chatting happily, while two of them were cuddling up and nuzzling affectionately.

My gaze lingered just a little too long as we passed the group, and when I looked ahead again, I caught a glimpse of Ocelli’s sly smirk and look of amusement. My ears flicked back in embarrassment, and I quickly looked away again, rather obviously pretending to have not noticed.

As we continued down busy hallways and busy public rooms, I hunted down a few similar scenes among the hundreds of changelings. A pair nuzzling in affection. A couple of changelings curled up intimately, legs intertwined as they dozed on a bench. A trio lying sprawled over each other, chatting while hooves rubbed at sides and flanks before teasingly slipping between hindlegs.

It occurred to me that there were certain aspects of a changeling hive Sickle might appreciate. For one, the close quarters and enclosed spaces tended to result in greatly diminished expectations of privacy. There were certain advantages to that.

I soon noticed that Ocelli’s walk had changed, putting on a subtle but pleasant sway to her hips, her tail held a bit too high. I have to admit, she was rather pretty, with her near-perfect curves and uniform, glossy carapace. There was something very pleasant in the way her flanks shifted and flexed with every strutting step.

She noticed my lingering gaze, her eyes half-lidded as she looked my way. I quickly looked away again, tucking my tail down between my legs.

\leavevmode\llap{“}So, you must have been on your own for a very long time,” Ocelli said, her eyes watching me closely. She had seen an opening, and she was taking it.

I nodded awkwardly. “It’s… been very lonely.”

\leavevmode\llap{“}Mmm, I bet.” She smiled, taking advantage of the busy hallway to move closer and brush against my side. My ears perked up. She knew exactly what she was doing. “Well, you’re not alone any more, and I’m sure we can make you feel \textit{very} welcome.”

I was breathing hard, and my tail crept up before quickly tucking down again. She merely smiled knowingly. I started to smile a little, then swallowed and looked away again.

A minute later, she purred beside me. “We’re here.”

A single guard stood by the door of her room, and gave us a nod as Ocelli opened it. “Come on in,” she said over her shoulder, her hips swaying so nicely. Even the guard cast a quick glance out of the corner of her eye before pretending she hadn’t noticed.

I followed Ocelli into a small room filled with a variety of furniture, adorned with various trinkets and pictures. The one detail that most immediately caught my attention was the single, decently sized bed. The heavy hydraulic door thumped shut behind her, and suddenly Ocelli was right in front of me, her muzzle so close I could feel her breath. I halted, ears perking up, alert and excited.

\leavevmode\llap{“}This is my room,” she purred, moving in to gently brush the tip of her muzzle against mine. “I’m lucky enough to have a place of my own, so it’s just the two of us.”

My mouth parted, but the only sound that came out was a soft panting.

Her muzzle slipped to the side as she nuzzled along and under my jaw. “Mmm. You know, most changelings spend their whole lives in the hive. We’ve gotten \textit{very} good at keeping ourselves entertained…” She gave a slow, teasing lick at my neck, and I responded with a shuddering huff of breath. “...But I’d absolutely \textit{love} to hear about the outside world.”

\leavevmode\llap{“}Y-yeah,” I huffed, her nuzzling working its way back up along my jaw, until her mouth was right by mine, lips parted just barely and so close to my own. Her eyes met mine with a sultry, half-lidded expression, sly and inviting.

I pressed forward, my mouth meeting hers, and she purred into the kiss. Soon I was gripping at her shoulders with my forehooves, ignoring the awkward balance as I pressed up to her. One of her hooves tucked around my shoulder, holding me close as she moved back, and a moment later we were on her bed.

I clutched at her sides, finally breaking the kiss to look down at her. We both panted softly for a few seconds before she smiled again, giving a soft, pleased hum.

That was sign enough for me. I pressed in again, kissing and nuzzling and licking with unrestrained eagerness, while her hooves teased along my sides and flanks. Moments later I was sliding down, giving only a few cursory licks and nuzzles across her underbelly before plunging my muzzle between her hind legs.

I played her like an instrument, every twist of my tongue producing a new melody, her voice rising to a crescendo and falling, again and again. Her hooves stroked across my head and horn, her hind legs wrapped around my shoulders.

We were both panting by the time I finally climbed over her again, muzzles brushing as our eyes met again. It lasted only a moment before her forelegs gripped around my shoulders, pulling me into another passionate kiss. When she finally broke the kiss again, she licked at her lips, purring. “Mmm. We really must get you taken care of,” she said, a hoof slipping from my shoulder to tease down along my side and under my belly. “Alone all this time, I can’t imagine how pent up you must be.”

As the hoof traveled lower, I shuddered, a faint moan escaping my lips. I drew back just a little, ears flicking back. “Would you, um… mind if I turned into a male for…?”

Her grin grew, sharp-toothed and eager. “You have no \textit{idea} how much I’d like that,” she said, finishing up with a slow lick across her lips.

I slid back, calling up a quick transformation, then slipping a hoof under her flank, nudging upward. She hummed softly as she followed my direction, rising to her hooves, and gave a sultry smirk over her shoulder. Her tail was held high and inviting, and I eagerly climbed atop her. Moments later, she was moaning again, while I nuzzled and nipped at the back of her neck.

Her voice rose again, her head tilting back and eyes shutting. I tilted my own head back as well—then snapped it forward, slamming a stunning spell down into the back of her head.

She gave a single twitch and fell limp, collapsing to the bed while I caught my balance, panting, above her.

Immediate appraisal: complete and immediate unconsciousness. She had been sufficiently distracted to not see the attack coming. There was no opportunity to throw off or avoid my attack, and certainly no time to get out an alarm or even cry for help. It was as perfectly executed a takedown as could be managed.

Still panting, I sat beside her, trying to calm my pounding heart and the various emotions currently flooding my mind. I focused on simply breathing deep, calming breaths, then turned to analyzing my situation.

I was alone, trapped in a guarded room without any equipment except a partially disabled PipBuck, my hidden armor, and whatever I could scavenge. I was in a Stable, deep underground, with likely only a single way out. My friends were trapped in a simulated world, unaware that they were even prisoners, and held in a reasonably busy area. I had an unknown amount of time before Sickle would be killed in her sleep. Our confiscated equipment was under guard. And lying between us and freedom was an entire Stable packed full of a thousand or more changelings, following a Queen that had taken the name Chrysalis, and all equipped with arcano-tech devices that could detect hostile intent at a glance.

I frowned, looking down at the unconscious would-be interrogator, and came to a simple conclusion.

\leavevmode\llap{“}We are so completely fucked.”