\textit{I’m not going to hurt anyone.}

\textit{I just want to go my way in peace.}

\textit{I am not your enemy.}

I opened my eyes, looking down at the unconscious changeling laid out on the bed before me, then scanning slowly around. The wall of green contacts remained steady, save for the cluster of red Ocelli had warned me of. The weight of the PipBuck felt unusually heavy. I had no idea how they decide who is or is not hostile, or whether my own mental declaration of intent could possibly influence it.

One fact did give a measure of encouragement: despite having rendered one of their members unconscious, none of the other changelings were showing as hostile. This suggested that there needed to be some sort of active intent involved. So long as my intentions were not to cause harm, it was possible I would not show up as an enemy.

Or maybe they showed up as non-hostile because they didn’t know what I had done, and therefore had no reason to consider me an enemy. I could be marked with a red pip to every changeling in the hive, and I had no way of knowing.

If so, then hopefully my mark would be lost in the sea of other contacts. Considering that it would be a lone red mark in an otherwise solid wall of green, that seemed unlikely.

Still, there were no guards coming in and no alarms sounding. I was in a precarious position, but I had not yet fallen. Now it was time to act.

I swapped my restricted PipBuck for Ocelli’s, a task made simple with the latches they had been retrofitted with. If anyone did a tag search, they’d see “me” here in this room, even if “Ocelli” was elsewhere.

Next, I restrained Ocelli. This involved copious amounts of wax—or changeling goo, as many ponies call it. Her legs and wings were bound, her muzzle bound shut with just enough of a gap to breathe, and her horn covered. I laid it on thick enough that I felt thoroughly drained by the end of it.

With that more immediate necessity out of the way, I turned to her PipBuck and the information it contained.

It was a matter of moments to get information on Ocelli herself. She had recorded her title as “Infiltration Operations, Intelligence”. Kind of a big deal. Good news: I now had top-level security clearance and a high-ranking disguise. Bad news: she was important enough to be both well-known and for her absence to be swiftly noticed.

Her PipBuck also had a detailed map of the entire Stable, and I studied it intently. Tracing back our route, I found the “Equipment Depot \#1” where I had been given a PipBuck, and where Ocelli had mentioned our confiscated equipment. Tracing further back, I found “Simulation Chamber \#1”, which from the layout, looked to hold around fifty pods. Three simulation chambers of similar size filled out the rest of that entire level of the Stable.

The level above that appeared almost entirely military, with barracks and armories. Above that was the entrance.

I quickly traced out an intended route, a plan formulating in my mind. Soon, there was only one final thing to do before leaving.

Looking down at Ocelli again, I hesitated. I felt so conflicted about what I had to do, but it needed doing. There was no way I was going to do what I needed on the tiny amount of love I had.

I pressed a button on the PipBuck now clasped to Ocelli’s leg. “I’m sorry.” Another press ended the brief recording, and I focused on the unpleasantness ahead. I leaned in close, and pulled.

Ocelli twitched, then jerked, moaning out as she instinctively tried to cling onto the love I tore from her, but her unconscious mind was unable to resist effectively. Soon, her moans turned frantic and fearful before devolving into weak and pitiful whimpers.

When I was done, I carefully tucked her into the bed, as if trying to make up for the nightmares I had inflicted upon her. I doubt it did much good.

The first step in escaping Serenity was, simply, escaping this one room. There had been a guard outside the room, which made walking out troublesome. I couldn’t leave as myself, and if I left as Ocelli, it might lead to a conversation where I had to act out a personality I had virtually no experience with. There were too many pitfalls there. I also couldn’t leave as some other changeling without raising even more questions.

The only other way in or out of the room was the ventilation, which was far too small for a changeling to fit through.

In our natural form, that is. There was a good reason I had needed Ocelli’s love.

I gave a quick search around the room, and thankfully found exactly what I needed: a picture. There were a small collection of framed pictures, about a dozen in total, but there was one in particular that fit my needs. It showed Ocelli and a few other changelings, including a couple of soldiers, posing atop the half-constructed office building I had seen above. Each of them was grinning or waving at the camera. Ocelli’s smile looked particularly smug and prim.

The ventilation grate was easy to pry open. With that done, I focused on pulling up my magic, digging deep into my reserves. Green flames blotted out the world for a moment, and when it returned, everything looked huge. The world had grown to gigantic proportions. Even the bound changeling beside me on the bed was a giant, her head larger than me in my entirety.

I had disguised as a raccoon, easily small enough to fit into the vent, and with dexterous little paws. The addition of a changeling horn sprouting from the racoon’s head certainly resulted in an unusual look, but I was hoping this form wouldn’t be seen at all.

Between my grasping paws and diminutive magic, I was able to haul Ocelli’s PipBuck and the “borrowed” picture up atop the dresser and into the vent, pulling the grate shut behind myself. I scurried down the tiny passage, passing more grates along the way. Most of these opened into other quarters, and I saw that Ocelli’s was unusual in belonging to a single changeling. The first room had six changelings, though only three beds if one counted the worn couch. The next held only four, three of which were sleeping in a pair of beds, while the fourth was typing on a terminal. The third held seven changelings, four of whom were sharing drinks and conversation, while the other three were being quite intimate and passionate in the bed nearby.

Every room had multiple beds and a good number of changelings, mostly sleeping. Assuming these rooms were even remotely representative of the hive as a whole, it seemed likely that the hive was hot-bunking. There might be even more changelings there than I had initially estimated.

After passing several more rooms and a crowded hallway, I found myself looking into a small cleaning closet. It was perfect.

I pried open the grate and climbed out, dropping to the floor. A quick tug of my magic unravelled my disguise, and I clamped the PipBuck to my leg once more. Then I brought out the picture, studying it. Specifically, I studied one of the soldiers, and their armor. It wasn’t entirely unlike mine, but there were a few details I would need to address if I wanted to pass without notice. Guards had enough authority to get away with more than an average changeling would, while from what I had seen, were still common enough to be somewhat anonymous.

With at least a thousand changelings living here, I hopefully wouldn’t need to imitate any specific changeling. I just needed to avoid standing out.

I revealed what parts of my armor fit with this hive’s armor, which to my relief, was all but the hoof-boots and helm. With those in place, I focused, taking my time with a particularly difficult change.

Assuming new forms is easy. Adding artificial accessories, like a hat or dress, was more complex. Adding detailed, intricate, and relatively bulky accessories, such as several pieces of armor, was particularly complex and difficult—and just to add insult to it all, it would be almost worthless as armor, though I at least had good cause to expect that detail to not matter.

A minute later, I had perfected the change. My armor looked spot-on for that of the soldiers in the picture. My appearance had been minutely altered to the point where I no longer looked like myself, without specifically imitating any particular individual. Nodding in satisfaction, I tucked the picture behind one of the racks of cleaning supplies, turned to the door, and stepped out.

I kept my mannerisms completely casual as I stepped out into the busy hallway. There was no hesitation or looking around. I simply stepped out, shut the door behind me, and walked down the hallway as if there was nothing unusual about it.

I understand the psychology behind it, but it’s always amusing to me how readily people will accept something as being completely normal if you simply act as if it’s normal.

I walked steadily through the crowd, my eyes watching my way through the hall without ever engaging with anyling. Noling paid any attention to me as I walked along. I was just one more anonymous face in the crowd. Adrenaline continued to tug at my nerves as I followed the route I had memorized.

I had spent years as an Infiltrator, passing myself off as a pony. I had been ready to undertake great personal risk in the service of my hive. I had even daydreamed of infiltrating one of the ministry hubs, or even Canterlot Castle, but in all that time, I had never imagined I would ever be infiltrating a changeling hive. Even the most experienced and capable Infiltrators might hesitate at such a task, full of danger and difficulty. The successful infiltration of a changeling hive was like a ghost story, some fanciful tale of suspense told to eager-faced young Infiltrators. Actually doing so was the stuff of legends; while such things would obviously be cloaked in secrecy, I knew of only three times a hive attempted to infiltrate another, and none of them ended well.

Yet there I was, right in the middle of some other hive.

I took a deep, steadying breath just before rounding the final corner, and walked in through the door of the room I had woken up in just a few hours earlier.

I was able to get a much better view of it this time. There were a large number of pods, arranged in a pair of concentric circles, and brightly lit by the overhead lights. Most were full, and I saw a wide variety of ponies, as well as a small number of griffins and zebras.

Unlike the rest of the hive, this section was fairly quiet. There were only two changelings in the large chamber, having just pulled Sickle out of one of the pods and laid her onto a gurney. A moment of fear passed before I saw her side slowly moving. With the concern for her life alleviated for the moment, I was able to wonder how they had managed to cram her into that pod to begin with. It must have been an incredibly tight fit.

I quickly glanced around the rest of the room. Four more changelings lay in pods, as still as the ponies around them. An observation room was set above a set of doors in the back, overlooking the chamber, and a couple of changelings sat within it, watching instruments.

Among the dozens of ponies, Dusty and Starlight were easy to find, resting just beside Sickle’s now-vacant pod.

The changelings around Sickle finally noticed me when I was only a few steps away from them. The closest raised a brow. “Is there something you need?”

\leavevmode\llap{“}Is she still alive?” I asked, nodding my head toward Sickle. Though I knew the answer already, it was a good lead-in.

\leavevmode\llap{“}Sedated, but alive for the moment,” the other changeling replied. “We’re just getting her completely disconnected and ready to move first.”

\leavevmode\llap{“}Ah, good,” I said. “Ocelli wants her kept alive just a little longer. She said to keep her sedated, but lightly enough that she can be woken up for questioning.”

The changeling sighed, but nodded. “Great. Yeah, we’ll put her in one of the holding rooms. When will Ocelli be getting here?”

\leavevmode\llap{“}She said to tell you she’s occupied for the moment, but will be here at nine. Will that be long enough for the pony to be regaining consciousness?”

She checked her PipBuck for the time; that was just forty five minutes away. “We might need to administer a stimulant when Ocelli gets here. Did she want anything else?”

\leavevmode\llap{“}That was all.”

\leavevmode\llap{“}Very well. The pony will be ready for her.” She gave a smirk. “Just tell her to not take too long getting to us. This pony was violent and destructive in the sim, even after we cranked up the pacification controls. I’d hate to see what she’s like unrestricted.”

\leavevmode\llap{“}Just make sure she’s restrained,” I said. “I’ll go inform Ocelli.”

She nodded, returning to securing Sickle to the gurney, and I turned and left.

So far, so good. Sickle wasn’t in immediate danger, and I had forty-five minutes, maybe a bit more, before the changelings in Simulation Chamber \#1 started wondering what was up.

On to phase two. I consulted Ocelli’s PipBuck as I made my way back to the equipment depot.

The last few steps involved passing a pair of guards. My heart hammered as I approached the most likely point of failure in my plans, but forced myself to keep a perfectly neutral expression.

I passed by without even a glance from them. I was just another anonymous soldier, one of the crowd.

I approached the first changeling I saw inside the depot, a technician working over a banged-up and half-disassembled PipBuck. “Excuse me.”

She looked up. “Hmm? What?”

\leavevmode\llap{“}Ocelli sent me,” I said, banking once more on the influence of her name. “I’m to retrieve the equipment from those ponies we caught. Is it all here?”

\leavevmode\llap{“}She wants their gear?” she asked, her head tilting a fraction. “What for?”

\leavevmode\llap{“}Heck if I know,” I said with a wry smirk. “Probably looking for intel. Maybe it’s something to do with the new ‘ling.”

\leavevmode\llap{“}Yeah, what’s up with that?” she said, resting her forelegs on the table on either side of the PipBuck. “They caught some changeling from another hive sneaking in here, and now she’s just chilling here? There’s some other hive out there?”

\leavevmode\llap{“}All I know is that the queen has invited her into the hive,” I said, catching the tiny flinch the other changeling gave. “Though I think Ocelli’s keeping a close eye on her. Also sounds like her whole hive died off because they were too incompetent to feed themselves.”

She gave a little snort. “Yeah, maybe.”

\leavevmode\llap{“}The equipment?”

\leavevmode\llap{“}Oh, right.” She gestured over her shoulder. “The two PipBucks are here. The rest of it is still in the back. It’s all inventoried and awaiting inspection. Row eight, section B, um… I forget which shelf.”

She raised her own PipBuck to check, but I casually waved it off. “If that pink pony’s armor is there, it’ll be easy to find. Speaking of, do you have any carts or the like for hauling stuff? I don’t think I could even carry that armor if it’s as heavy as it looked.”

\leavevmode\llap{“}Yeah, got a set of carts and pallet jacks in the back. If you need someling to run the forklift, I can do that.”

\leavevmode\llap{“}The cart should do fine,” I said, and after retrieving the pair of confiscated PipBucks, I headed back.

The equipment depot was impressive. Rows upon rows of shelves, stocked with all manner of tools, materials, electronics, armor, and other equipment. One entire row was filled with containers marked “bottle caps”. It was an enticing hoard of wealth, but I resisted the urge to start picking out items to pilfer. For the moment, I needed to focus on the mission.

I made my way through the empty aisles to the rear of the depot. The carts the technician had mentioned were small things, good for fitting down hallways, but they wouldn’t carry very much. Fortunately, they also could hitch together. I connected a pair together, then hitched myself up to the first, guiding the pair back to row eight.

Sickle’s armor made it easy to find our gear, laid out in a haphazard jumble across an entire shelf. Aside from the PipBucks I had already retrieved, everything was there, including weapons. Labels had been attached to almost every item, probably for inventory purposes, and like items were bundled together in bags and boxes.

I started transferring items over to the carts. It took only a couple of minutes. Sickle’s armor was the hardest, weighing easily more than I did.

I hesitated as I picked up my holstered pistol, its suppressor detached and set beside it. It presented additional options and more flexibility, but there was no chance such a thing would not be read as a hostile act. Even considering the use of it might be enough for a PipBuck to decide I have hostile intent.

Reluctantly, I tucked the weapon, the suppressor, and the magazines of subsonic ammo into the lead cart. Plans could change, but for now, it wasn’t an option. If it became an option, it would only take a few seconds to ready. That would have to do.

Once everything was in the carts, I pulled out a pair of blankets, draping them over the top to conceal the contents. I hitched myself up to the lead cart again, then paused to review the map on Ocelli’s PipBuck. I analyzed the layout, picking out a route, and set off again.

As I reached the front of the depot, I halted just out of sight of the technicians. Fortunately, being essentially a warehouse, there were few changelings in this area. It gave me the opportunity to peek out, my magic reaching out to snag another PipBuck from the shelves behind the technicians. Another shelf held dozens of broadcasters, and four of them floated away in my magic.

Once I had them all tucked away in the cart, I continued on. The technician I had spoken with hardly looked up from the PipBuck she was working on.

I made my way out into the hall, changelings stepping aside to make way for my carts. I continued on, just another cog in the giant social machine. I was as good as invisible.

At least, I was as good as invisible until someone wondered where Ocelli was, or she woke up and freed herself. Neither gave me much time.

I returned to the simulator chambers through a back passage, the same way I had been wheeled out originally. I caught a questioning look from some random passer-by as I wheeled the carts down the back hall, but I didn’t engage her by meeting her eyes, and she evidently didn’t feel curious enough to impose upon a guard’s business.

Sickle had been parked in the same room I had been held, strapped to a gurney that looked about ready to collapse under her weight. Another changeling, one of the ones who had been removing her from the pod, was standing beside the door, watching her. She looked curiously at me as I rolled the carts in. “What’s all that?”

\leavevmode\llap{“}Their equipment,” I said. There wasn’t much point in lying about that, especially if she decided to look. “Ocelli told me to bring it here.”

She frowned. “Why?”

\leavevmode\llap{“}I didn’t ask,” I said as I folded the blankets up again. “How’s the pony?”

\leavevmode\llap{“}Stable and sedated,” she said. “Glamor had me stay to keep tabs on her in case she started to wake up. Apparently this pony has a bad combination of high body mass and high resistance that makes drug effectiveness unpredictable.”

\leavevmode\llap{“}I think I heard something about that,” I said as I turned to look over Sickle. She looked healthy enough, though now that I looked closer, something caught my eyes. While she was heavily scarred all over, there seemed to be several fresh marks, all thin, straight, and pink. “Are those incisions?”

\leavevmode\llap{“}Hmm?” The other changeling stepped forward, peering at Sickle before realizing what I was talking about. “Oh, yeah, those. The autodoc pulled about half a pound of metal out of her when we were getting her ready for the pods. Was a pain in the flank getting her in there, too. What a waste of time.”

\leavevmode\llap{“}Couldn’t have known that at the time,” I said, then leaned in closer. I lifted a hoof, pointing at her belly, just below the crook of a hind-leg. “Uh, what’s this?”

\leavevmode\llap{“}What’s what?” she asked, leaning in past me as I made way. A moment later, my stunning bolt struck the back of her head. My magic wrapped around her body, halting her fall. With a quick heft, I tucked her into the rear cart, draping a blanket over her unconscious form.

Phase three was on. Unfortunately, it was where the risk of failure started to skyrocket.

I returned to the lead cart and the several bags of confiscated drugs, separated by type. It made finding Sickle’s collection of Dash inhalers quick and easy. Retrieving one, I returned to Sickle, sticking the inhaler nozzle into her open mouth and nudging her jaws shut around it. I waited until she started to inhale her next breath and squeezed, the inhaler hissing as it discharged its load.

Sickle immediately twitched, and I started gently stroking a hoof along her scraggly mane as her breathing grew deeper. A few moments later she produced a groan, ears flicking, and finally, her eyes fluttered open, looking blearily up at me and blinking as she tried to focus.

\leavevmode\llap{“}I’m Whisper,” I said quietly, continuing to soothingly stroke her.

\leavevmode\llap{“}Whisper,” she murmured, still blinking, and tried to lift her head only to be stopped by the straps. Her legs jerked, tugging against the bindings that held her down. “What the—”

\leavevmode\llap{“}Relax,” I said, magic lighting up the buckle of the closest strap. “We’ve been captured by a changeling hive. I’m busting us out.”

She laid her head back down, blinking up at me for a moment. “We… that… wow, that was one fucked-up trip.”

Once I’d undone enough straps, she pulled free, pushing herself up to sit on the gurney despite its whines of protest. “Ugh,” she said, face scrunching up and sticking out her tongue. “I feel like I haven’t had anything to drink since—”

She halted, a hoof touching her chest. Her expression quickly hardened as she bared her teeth. “Where the fuck is my—”

As she turned, she halted again, staring at the heavy, muzzled helm floating before her in my magic. She stared in surprise for a moment before breaking out in a toothy grin, reaching up to take the helm. “I knew you were a smart bug.”

\leavevmode\llap{“}Yeah, well you’re not going to like the next part,” I said. “You can’t hurt anyling on the way out.”

She gave a snort, setting down the helmet as she started pulling out pieces of her armor. “Uh, no, I’m pretty sure I can hurt them plenty.”

\leavevmode\llap{“}There are well over a thousand changelings here,” I said. “They have power armor, magical energy weapons, and extensive combat training, while we’re trapped in a Stable with a single way out. If we get into a fight, we all die.”

\leavevmode\llap{“}I’m still for killing every motherfucker here,” Sickle said as she slid the massive breastplate over her head and settled it into place. “Guess I’ll have to settle with just killing any dumb cunts that get in our way. This ain’t your hive, right?”

\leavevmode\llap{“}No killing!” I raised my leg, with its attached PipBuck. “Every changeling in this hive has one of these, and that means they can detect hostile intent. If we go out there with the intent of hurting any changeling, they’ll all know it, soldiers show up, and we’re back to us all dying.”

\leavevmode\llap{“}What if I only hurt them a \textit{little?}”

\leavevmode\llap{“}No!” I said. “I might need you to hold and subdue someling until I can stun them. It seems I can get away with that without being deemed hostile. But it’s \textit{vitally important} that we don’t hurt anyling!”

Sickle considered that for a moment before weighing in again. “Okay, seriously, ‘anyling’ is about the dumbest word I’ve ever heard.”

\leavevmode\llap{“}Sickle!”

\leavevmode\llap{“}Okay! I won’t kill any of the fuckstains that kidnapped us, fucked around with our heads, and will probably try to kill us on our way out.” She shoved her helmet into place before looking back to me. “Does it count if I \textit{accidentally} kill them? Like, holding the little bugs a bit too hard and squishing them?”

\leavevmode\llap{“}I’m going to assume that would be perceived as hostile,” I dryly replied.

\leavevmode\llap{“}Figures,” she snorted, and let out a tired groan. “Fine, we’ll do it your way. The fuck do we do now?”

\leavevmode\llap{“}You stay here for a moment while I scout ahead. If anyling comes in, grab them, make sure they don’t alert anyling else, but \textit{don’t kill them!} I’ll stun them when I get back.”

\leavevmode\llap{“}Yeah, fine,” she said, turning to root through the carts, and pulling out a bottle. “Don’t be too long.”

I frowned. To tell the truth, I didn’t think there was any chance of getting her to not show up as hostile, but I didn’t want to risk myself showing up as hostile by way of permitting the use of lethal force. I quickly shook off the thought. “I’ll be right back.”

I slipped out, making my way back to the main chamber with its dozens of suspended animation pods. Looking in, I could see one changeling, the other one I had spoken with before, going around the various pods, a clipboard floating in her magic. I backed out, turning to the stairs nearby. As I expected, it led up into the control room overlooking the chamber. There were two changelings there, monitoring the various dials and terminal screens. One looked up from the console in front of her. “Need something?”

At least a cover story was easy to come by. “I was just wondering where you have the pony Ocelli wanted.”

\leavevmode\llap{“}Holding room three,” she replied immediately. “Anything else?”

\leavevmode\llap{“}No, that will do,” I said, nodding. “Thank you.”

I turned and returned down the stairs, quickly assembling a plan of attack. Engaging more than one at a time would be extremely risky, so it quickly became a matter of isolating them. The first one was easy.

I returned to the main chamber and approached the lone changeling there. “Excuse me.”

She turned, looking back with a questioning expression. “Yes…?”

\leavevmode\llap{“}Ocelli wishes to speak with you about that pink pony,” I said, inclining my head back towards the rear door of the room.

\leavevmode\llap{“}Oh! She’s here already? We weren’t expecting her for another twenty minutes or so.”

\leavevmode\llap{“}I guess her business concluded early,” I said with a shrug. “Whatever the reason, she’s here now and wants to speak with you.”

\leavevmode\llap{“}I see,” she said with a frown, then lifted her clipboard. “If she’ll give me about five minutes, I’ll be done with my checks, and I can see her.”

\leavevmode\llap{“}It sounded urgent,” I said, and she hesitated for a moment before sighing and setting down the clipboard.

\leavevmode\llap{“}Fine,” she grumbled, and turned to walk. “What’s so important that it can’t wait five minutes?”

\leavevmode\llap{“}I didn’t ask.”

We returned through the back way, making our way to the holding room where “Ocelli” was waiting. The changeling I was following paused by the door, wiping away her frustrated expression, and gripped the handle of the door in her magic.

As the door opened, my stunning bolt struck, and she sank into my magic. Sickle stood beside the door, her head tilted as she watched me drag the other changeling in. “No killing, huh?”

\leavevmode\llap{“}She’s unconscious and uninjured, just like the other one in the cart.” I stashed the new changeling beside the previous, then turned back to Sickle. “Two more, then we can get Starlight and Dusty.”

Sickle grunted and nodded, and I slipped out again.

While my tactic worked well the first time, it ran into a snag this time.

\leavevmode\llap{“}Sure,” the changeling I spoke to in the observation room said, her gaze still playing over the readouts. “Give me a minute to get one of the immersion teams out so they can keep an eye on my station.”

\leavevmode\llap{“}Is that necessary?” I asked. “It’ll only be a couple minutes.”

\leavevmode\llap{“}Yeah, it’s been the rule in here since what happened last year. Always have to have two ‘lings watching the systems at all times.”

\leavevmode\llap{“}Ah,” I said, quickly throwing together a backup plan. “You know what? You stay here. I doubt Ocelli would want to interrupt your work. We’ll be right back.”

\leavevmode\llap{“}It wouldn’t be any trouble,” she said, but I shook my head.

\leavevmode\llap{“}No, don’t worry. It’ll only be a moment.”

She looked questioningly at me, but didn’t say anything and remained at her station. She was still sitting there when I returned a couple of minutes later, and looked up to greet me only to receive a bolt of magic to the face.

The second changeling looked over, both at the sharp grunt from her companion and the explosive clash of metal. She had only an instant to process the scene, jerking back at the sight of the armored monstrosity charging her. There was a loud crash and a shout of pain, then Sickle reared back and slammed the changeling down to the floor, pinning her under spiked shoes.

\leavevmode\llap{“}Sickle!” I hissed as I scrambled over. “Don’t hurt her!”

\leavevmode\llap{“}She’s alive,” Sickle replied with a sneer. “I didn’t even kill her a little.”

The changeling’s horn lit up, but Sickle’s reflexes were quicker, and she delivered a painful swat to the glowing horn, disrupting the forming spell and eliciting another sharp cry.

I got in close. “I’m sorry about this,” I said as my horn glowed. She started to cry out, perhaps for mercy, before falling unconscious.

A faint throb was starting to build in the back of my head. I shook it off. We quickly hauled the two unconscious changelings back to the holding room, then returned to the observation room. The controls for all the pods were there, and I had to figure out how to get Starlight and Dusty out.

If all else failed, I could just ask Sickle to do it, but I’d prefer a slightly more quiet way of opening the pods.

Fortunately, there was a set of operating manuals, giant three-ring binders worn with age, with all the instructions on the functions of the pods. The index quickly led me to the section dealing with emplacing or removing occupants, and I followed the instructions step by step. A red light came on over the two pods, accompanied by a loud buzzer that fell silent a second later.

As the system ran through the final preparations, I quickly scanned through the index, looking for anything that might help with the four changelings in those pods, which I assumed were the “immersion team” the other changeling had spoken of. I also assumed they were the “welcoming committee” inside the simulation, and if so, they could talk with the changelings outside the simulation, as well as disconnect themselves.

Which meant they were one casual call to an unresponsive “control” away from ruining my entire plan.

I found a lockdown command, and quickly enacted it. The lights over their pods turned to flashing red as I locked them shut. If I dug longer, I might find a more robust solution, perhaps even locking them in the simulation itself, but time had become a critical resource. There wasn’t much traffic in and out of this chamber, but it would only take a single changeling showing up to start the situation deteriorating.

Starlight and Dusty’s pods hissed open, and Sickle and I hurried down to retrieve them. She slashed through the leads connected to them, and we hauled them away to the holding room. Without sedatives, they woke as quickly as I had, groaning and jerking as consciousness quickly returned. Dusty’s awakening was particularly violent, suddenly twisting around and lashing out, blindly slamming a hoof into the back of Sickle’s head.

Sickle just chuckled. “Calm the fuck down, dumbass. You’re being rescued.”

\leavevmode\llap{“}Rescued?” he blearily asked as we stepped into the holding room. “But… I was in my kitchen, how—”

\leavevmode\llap{“}You were in some form of telepathic arcano-tech simulation,” I said, while Sickle set the pair of them down. “Short version, Serenity is a changeling hive, they captured us, and we’re in the middle of a breakout. It would really help if you both woke up.”

Starlight had managed to focus on me. “Whisper? Where did you…” Her ears pinned back. “You’re not Whisper.”

\leavevmode\llap{“}I am, I’m just disguised.” I smiled. “Congratulations on picking out differences between two changelings, though. You’d be surprised how many ponies can’t do that.”

She was silent for a moment, slowly blinking at me. “...What?”

I shook my head. “Nothing important. Look, we need to move right now if we’re going to get out of here. I’ve got all our gear here. I need you to get your stuff and get ready to go, right now. Can you do that?”

Dusty wearily rose to his hooves, while Starlight continued to lie there, blinking and looking around. “But… what’s going on? And where are we? I just laid down on my couch for a nap, how did we—”

I placed my forehooves on either side of her head, holding her gently. “Starlight, that version of Serenity was all a lie. This is the real Serenity, and we’re in a lot of trouble. If we’re going to get out of here alive, we need to act right now. I promise I’ll explain everything once we’re out and safe, but we don’t have the time right now. Right now, I need you both focused on acting. Can you do that?”

She swallowed, her gaze dancing around, but she finally nodded and pushed herself up to her hooves.

\leavevmode\llap{“}Good,” I said, taking a step back. “Your stuff is in the carts. Get any critical gear ready immediately. Those respirator masks? Keep them accessible; it was gas that got us on the way in. Everything else gets packed in bags and sorted through when we’re safe. I want to be moving in sixty seconds. Hurry.” Quick, concise, clear orders in a stressful situation; I felt a little like Dusty.

\leavevmode\llap{“}Right,” Dusty said, staggering toward the cart before getting his balance, then quickly pulling out his barding and weapons. Starlight was a little slower to get moving, but the sight of her Lancer motivated her into action. As they geared up, I started gathering my own equipment, while quickly explaining our situation.

\leavevmode\llap{“}Okay. We’re in the middle of a changeling hive established in a Stable. The guards are extremely well-equipped and trained, and there’s only one way in or out. If we’re lucky, we can hide you in the carts and get you out that way, but it’s going to be tricky. We might have to improvise along the way.”

Dusty slapped a magazine into his rifle and chambered a round. “So… this is Serenity?”

\leavevmode\llap{“}Yeah, and we can do the whole ‘I told you so’ thing later,” I said. “We’ve got more problems. Number one? You’re not using that. We’re not killing anyling on the way out.”

\leavevmode\llap{“}Avoid fighting if possible,” Dusty said, giving his rifle a final check before slinging it. “I’d say that’s standard escape and evasion, but I don’t think this situation is standard in any way.”

\leavevmode\llap{“}Not ‘if possible’,” I clarified. “Period. We’re not going to hurt any changeling in Serenity.” Dusty’s head started to come around to voice some objection, but I cut him off. “And no, this isn’t a changeling thing or a hive thing or anything like that. It’s a PipBuck thing. Every single changeling in this hive has one. I assume you understand the difficulty that poses.”

He remained frozen for a moment, mouth hanging halfway open before recovering. “Oh, we are so fucked.”

\leavevmode\llap{“}That was my appraisal as well,” I said, tucking the last of my electronics into my saddlebags, right alongside my pistol. “So we’re going out with the intent of \textit{not} harming anyling, because we’re \textit{not} hostile.”

\leavevmode\llap{“}This is so weird,” Starlight murmured, while Dusty muttered to himself and returned to gathering his equipment.

I finished with my own belongings. My rifle was loaded and set alongside my bags, with a pair of spare magazines tucked inside the bags alongside the suppressor, having not even given myself the extra ten seconds or so it would take to attach it. I didn’t plan to use the weapon, but it wouldn’t fit in the bags. Maybe I could scare someling away from attacking us without actually shooting them?

\leavevmode\llap{“}Okay, time’s up,” I said. “Everything else goes in bags. And keep those PipBucks powered off.” I pulled out one of the matrix disruption grenades, one of the pair I had in my own bags, and pressed it into Dusty’s hooves. “If things start to deteriorate, trigger this. It’ll kill any chance of stealth, but it’ll also kill any active PipBucks and power armors around us. No E.F.S., no broadcasters.”

\leavevmode\llap{“}I’m familiar with these,” Dusty said. “It’ll probably kill Starlight’s weapons, too.”

Her ears perked up, forehooves tightening around her rifle. “Wait, we can’t kill my Lancer!”

\leavevmode\llap{“}It’s only temporary,” I said. “And hopefully we won’t have to use it.”

The last of our equipment disappeared into the bags, and I directed them into the carts, while Sickle ditched the pair of unconscious changelings hidden within the lead cart. The blankets came out again, and I draped them across the carts. “Okay. Be quiet and think happy, peaceful thoughts.”

Sickle gave a discouraging snicker, but we had little choice. I hitched up the cart and set off, though slower than before.

Slower was something we couldn’t afford, but the substantial extra weight was hindering progress. A little reluctantly, I asked, “Sickle, do you have any Buck on you?”

She snickered again, followed by rustling as she rooted through her containers. Several seconds later, the corner of the blanket flipped up to reveal a thick tablet resting on a spiked hoof. “Here.”

I floated it over in my magic, tucking the blanket back in place, and downed the pill. Moments later, I grit my teeth and really put my shoulders into the harness, hauling it along at a brisk pace. Even pushing that hard, it didn’t feel like I was straining myself, though I wonder now if that was from increased strength or altered perception. I found myself thinking I could probably plow through any guards that got in our way, and was already starting to smile at the thought before quickly wiping away those thoughts. Instead I reflected that taking a drug known for increasing aggression was probably not ideal, given my situation.

Soon we were making our way through crowded halls, and I put on my mask of bored neutrality. Inwardly, I was growing increasingly worried. While the changelings made way for a guard hauling a pair of carts, it still slowed my progress. I nearly jumped each time a changeling went buzzing overhead, suddenly paranoid that they’d land on one of the carts, only to find its contents rather more soft and squishy than they should be.

My heart was pounding furiously when we reached the freight elevator, and I found myself suppressing trembles as the adrenaline urged me into action. My body screamed at my attempts to still it, clamoring for action, while I did my best to appear calm. I also resisted the urge to look back; I feared that my companions might fidget, drawing attention, but there wasn’t anything I could do about it either way. I stayed stock still for the agonizing wait.

A deep thump sounded from the elevator, and the hydraulic doors hissed open. I gave a quick sigh of relief and pulled the carts in, and quickly shut the doors. We were alone as I pressed the button that sent the lift up.

\leavevmode\llap{“}We’re on our way up to the entry level,” I said as I lined the carts up, ready to move. “The lift goes to a freight-handling area. After that are security positions, the Stable door, and some underground storage rooms with ramps up to the surface. If we’re found out, trigger the grenade and run for the exit.”

In silence, I watched the needle of the elevator’s dial make its way up to the ‘1’ at the top, and the elevator thumped and rattled to a halt. The doors opened, and I walked out into a large room cluttered with a wide variety of equipment. A concerning amount of it was military. There were at least ten suits of heavily battered Enclave power armor stored there, one of which was being inspected by a pair of changelings. Dozens of magical energy weapons were stacked in a pile. Two semi-portable plasma-cannon turrets rested on pallets, with one bearing obvious fire damage. Containers of all sorts were stacked neatly, ranging from metal barrels to wooden crates, and even a small collection of metal-and-plastic containers with cloud locks.

Four more changelings were overseeing the loading of a heavy wagon, which was already carrying a literal ton of machinery. They paid me no attention as I walked by.

\leavevmode\llap{“}...spark coils should be ready by the time the weather clears, but I’m not sure we have enough to get everything going.”

\leavevmode\llap{“}We’ll make do. I’m more worried about raw materials. Parts we have, or can get easily. Structural steel is the limitation.”

\leavevmode\llap{“}Plenty of places to get more. It’s just heavy…”

I wheeled our carts through the door and into the connecting hallway. It was a broad, reinforced strip with a high, vaulted ceiling. It was more like a road tunnel than a Stable hall. You could drive a tank down it with room to spare.

At the end of the tunnel, I could see the Stable door, standing open and inviting.

Between it and us was the “entryway security” I had seen marked on the map, but it was not at all what I had imagined. They weren’t simple guard stations. It was a full-fledged fortress, with firing slits peering out from yards-thick concrete walls on either side of the tunnel. Two more plasma-cannon turrets sat by the sides of the fortifications, flanking the entrance to the tunnel, with cables leading back to wire into the Stable’s power. Further trench-like fighting positions crossed in front of the main positions, all overlooking the open kill-zone just inside the Stable door. I could see more than half a dozen soldiers in the forward fighting positions, all clad in black-painted Steel Ranger armor. I could only guess how many more were inside the fortifications themselves.

The adrenaline screamed at me to run as fast as I could. I instead focused on walking calmly, passing by the ominous, darkened firing slits, and overly conscious of my excessively hostile passenger. If one of those soldiers noticed that the ever-present red mark on their E.F.S. was actually moving, we were in trouble.

The soldiers remained standing and sitting by their fighting positions, talking with each other, and paying no mind to the cargo-hauling guard approaching them.

A klaxon blared out of nowhere. I jumped. The soldiers froze, their attention snapping up. An icy fear clawed at my gut, but they quickly spread out across their fighting positions, setting up and facing the entrance. Moments later a buzzer sounded, and a spinning light lit up above the giant Stable door.

I lurched and continued at a trot. I was passing the soldiers when they realized I was there.

\leavevmode\llap{“}Hold up!” the closest one called out, her voice amplified and staticky. “You know the deal, lockdown means noling in or out.”

\leavevmode\llap{“}I just need to deliver this!” I called back, picking up the pace. With a tortured shriek of metal, the door started to move, slow and ominous.

\leavevmode\llap{“}I don’t care, rules are rules.” When I didn’t stop immediately, she broke into a trot after me, her armored hooves smacking loudly on the concrete floor. It would take only an instant to use the heavy weapons at her side. “Hey, get back here!”

\leavevmode\llap{“}Okay, okay,” I said, slowing my pace, and she slowed to a casual walk. “Dusty, you’re up.”

\leavevmode\llap{“}Huh?”

Past the sound of her confusion, I heard the click of the matrix disruption grenade arming. A moment later, the edge of the blanket lifted, and the grenade clattered noisily to the ground.

\leavevmode\llap{“}What the—”

A soft thump preceded the sharp discharge of the grenade, and all chaos broke loose. My vision was immediately filled with a flash of insanity across my E.F.S. as Ocelli’s PipBuck was overwhelmed, only to die an instant later. It felt like someone had smacked me in the horn. Even as I staggered from that, I was already pulling at the cart straps and shouting. “Run!”

My vision cleared to a scene of partial darkness and flying sparks. Several of the overhead lights had exploded with the discharge. The glowing lights of the plasma-cannon turrets were fading, and the soldier was frozen like a statue, teetering forward off-balance until she crashed face-first to the ground.

Sickle exploded out of the lead cart with a roar, spiked hooves clattering and scraping the concrete as she quickly looked for targets. I heard Dusty shout from behind her. “Go! That way!”

I’d just gotten the straps undone when Dusty came galloping past me, followed closely by Starlight. I grabbed my belongings in my magic and took off in the same direction, racing toward the spinning orange light, and Sickle growled and galloped after me.

I glanced back; I could see changelings stepping out of the fortifications. Weapons floated in their magic. I turned back and put everything into running, but no shots came.

The door was halfway shut as we reached it. Dusty and Starlight were out first, and I leaped out after them, emerging into a dimly-lit warehouse-like space with similar all-concrete construction. Sickle caught the edge of the door and tumbled, crashing to the ground, but safe.

I looked back past the steadily closing door. A few changeling soldiers faced our way, still back by the fortifications. One was looking at her weapon, while others were quickly swapping out spark packs.

I reached into my pack with my magic, drawing out the second matrix disruption grenade. I only had a few seconds before the door would be fully shut. I armed it, dropping it just inside, and stepped back. The door had barely shut when the pulse went off, followed by a loud whine of machinery winding down. The external control panel let out a loud squawk, its lights flickering before going dark. The lights ringing the door flickered, all but one going out.

Panting, I stepped back, staring up at the monumental fortified door that we were safely on the outside of. Then I registered the numbers emblazoned across it: “112”.

I blinked, my ears lying flat. “What? That’s not… there are only…”

\leavevmode\llap{“}Whisper!” Dusty called out, grabbing my shoulder with a hoof. “Come on, we’re not—”

Suddenly the hoof was gone. I was already turning to face him, which gave me just enough time to see his head snap around before his rifle blared. I cringed back, ears ringing and vision dazzled. By the time I recovered my balance and got a look in the direction he had fired, I saw a dark form scurrying behind a small storage container. An armored changeling lay crumpled on the ground beside it.

\leavevmode\llap{“}Don’t!” I shouted, leaping to Dusty’s side. “No killing!”

\leavevmode\llap{“}The situation’s changed!” Dusty replied, keeping his rifle leveled as he jerked a hoof to the side. “Move!”

\leavevmode\llap{“}Damnit!” I slipped behind him and galloped past rows of pallets, loaded with machinery and scrap metal. There was no point in arguing it now; we were outside of the Stable proper, and there was no way that these changelings’ PipBucks hadn’t decided we were entirely hostile.

A flash of movement ahead drew my attention, and I swung my rifle around in my magic to aim on a surprised and unarmed changeling. “Don’t move!”

She replied by instead throwing herself back behind the container she had stepped out from behind, and while the action was technically contrary to my command, I didn’t object. Starlight and Dusty were already passing me, and I picked up the pace, with Sickle close on my heels.

We rushed past equipment and containers. The chamber split in two directions. A quick glance down one way revealed about a dozen changelings, scurrying about. I saw no weapons, but we ran the other way.

Two changelings in stained coveralls dove behind a partially loaded sky wagon as we galloped by. An armored changeling trotted around the corner ahead of us. Plasma and muzzle-flashes lit the dim space for an instant. Dusty tumbled to the ground. The armored changeling staggered back, her rifle swinging away.

I brought my rifle around, snapping off several shots; my light rifle sounded like a balefire bomb in the bare-concrete chamber, and the flash from the muzzle nearly blinded me. When I stopped firing, the changeling was on the ground, her hooves kicking out.

Dusty had rolled to his belly and snapped off a couple more rounds into the changeling. Her legs kicked again and went still.

Dusty leaped to his hooves, and we were galloping again. At some point, I noticed smoke wafting from Dusty’s chest, but I didn’t have the time or focus to examine it. My head was pounding, and the violent crashing of Sickle’s spiked hooves on the concrete floor sounded muted in my ears.

A couple more changelings galloped for safety, their abandoned containers of packaged food fallen and spilled across the floor. We leaped over the spilled goods and continued on, passing a half-laden cart and running by a line of motorwagons.

We were halfway past when Starlight shouted out. “Wait!”

I skittered to a halt, looking back. Starlight had abruptly veered off, leaping up to the window of one of the motorwagons and nimbly sliding into it.

It was then that I recognized that these weren’t some ancient, rusted-out hulks. They looked like the ones we had seen in the Trotsen convoy: armored up, worn from regular use, and by all appearances, fully operational.

We turned as one and scrambled after her. The vehicle she had claimed was a rust-colored amalgamation of armor plates, angular and sloping from the thick prow in the front to the heavy machine gun mounted to the roof. My wings flicked as I leaped up over the short rear-end, dropping into the narrow open space behind the gun that had once served as an open cargo bed, and which was now surrounded by armor plates sloping back from the roof. I was just perching my forehooves on the roof beside the gun when Sickle’s spiked hoof landed on my back, flattening me into the tiny back seat. The whole vehicle rocked violently as she settled in, occupying most of that rear space.

Twisting around to make room—and to avoid being crushed under her—I could barely catch the wild grin on her face. “Yeah! Let’s fucking do this!”

Dusty was hauling himself in through the window beside Starlight, in the row of full-sized seats in front of me. “How quick can—”

He was cut off as the vehicle roared to life, lurching forward and throwing me back into Sickle’s chest. My helmet slammed into her breastplate with a loud crack, followed by a tremendous slam that threw me sideways into the armored wall of the vehicle. I couldn’t tell what was going on outside; I was in a violently shaking can that roared and creaked and banged as it threw me about.

Starlight blurted out some unintelligible curse, and the vehicle lurched forward again, swerving wildly as I scrambled to brace myself. Metal scraped violently on concrete. Sickle roared with laughter.

Grabbing the back of the front seats, I hauled myself up. Dusty was twisting around to brace himself in the passenger seat, while Starlight gripped the motorwagon’s steering wheel. Past them was the narrow front window, showing me a thin slice of the outside world just before Starlight jerked the wheel, veering around a concrete pillar. The engine roared, and I clung to the seat before me as she accelerated down the length of the large room. Between the forces throwing me around and the very restricted view, I was just barely able to see the upcoming offshoot.

\leavevmode\llap{“}Starlight!” I shouted, pointing a hoof. “Turn right!”

The vehicle lurched, pitching forward with a loud squeal and pressing me against the front seats. Then the engine roared again, throwing me back into the rear seats before the whole world spun again, slamming me into the side of the vehicle, and then back against my seat as the whole vehicle pitched back.

An instant later, the reverberating echo of the spark-motor cut off as we emerged from the tunnel. The world brightened just in time to twist all around, and for an instant, I found myself floating weightless toward the ceiling.

Gravity reasserted itself with a tremendous crash and a sudden spray of dampness. I landed heavily on the floor, wedged tightly between the two rows of seats, and chose to simply brace myself in place there. I was rewarded for my decision a moment later when the vehicle swerved and skidded sideways before slamming sideways into something with a deep, hollow drumbeat of metal on metal.

Dusty swore from somewhere up front. “Goddesses damnit, Star! Don’t kill us!”

\leavevmode\llap{“}Hey, I’ve never driven before!” she snapped back as the engine roared again. “It’s a lot harder than it looks.”

Sickle was still laughing.

I took the opportunity to scramble up and get into a seat properly. We were outside, and the spray of moisture wasn’t blood as my mind was wanting to insist it must be, but the light rain coming in through the windows. The half-built office building was beside us, with a ramp leading down into the underground storage and parking area. On the other side was one of the abandoned bulldozers, right up against the window after our collision.

The wheels of the motorwagon spun in the mud, slipping uselessly for a second before starting to catch, and the whole vehicle shuddered and took off again. I focused on just staying seated, while we quickly tore out past several temporary structures.

Dusty grunted from the seat beside Starlight, grabbing a flying strap, then quickly pointed out the front window. “No, go for the high-ground! The low-ground’s all mud, we’ll bog down!”

The vehicle swerved again as Starlight oversteered, wavering a few times before settling on the correct course.

\leavevmode\llap{“}And calm down,” Dusty grunted, wincing as he pulled the strap across his chest.

I leaned forward. I could still see the edges of where the shot had impacted, with the outer layer of the barding scorched away to reveal warped metal. “Are you okay?”

He grunted and nodded, though I saw the tightness in his jaw. “Non-critical. The plate stopped it, just singed me pretty good.” He finally got the strap in place and called back. “Sickle! If you’re going to be on the gun, keep an eye out!”

\leavevmode\llap{“}Yeah, no shit! Shut the fuck up and let me enjoy the ride!”

Dusty grumbled and sat back, hauling his rifle up to rest beside him. I suddenly realized I had lost track of my own; a quick search found it in the bed of the cargo area, between Sickle’s hooves, and I floated it back to me.

\leavevmode\llap{“}What about you?” Dusty asked as I set my rifle on the seat beside me. “You were going good, then you just froze up at the door.”

My ears pinned back. “That was…” I quickly shook my head, turning to the other window to look back. “It’s nothing.”

There was a moment of silence from Dusty before he gave a quiet, “Umm…”

\leavevmode\llap{“}It’s just that the door said that was Stable 112, but the last Stable that Stable-Tec finished was 101. Stables aren’t subtle things, and my hive had enough espionage on Stable-Tec to steal a Stable door and tons of equipment. They couldn’t have made more without us knowing!” I frowned, glaring out the window as I tried to ignore the constant spray of rain. “Though I’m sure they were constructing more, even if 101 was the last one they had finished. Where else would we have gotten Stable parts from? And if this group had the same kind of resources my hive did… maybe they finished an incomplete Stable. Maybe their hive was the original Serenity, and this was a collab with Stable-Tec. Maybe like a… a licensed Stable?”

A thump sounded through the roof. “Holy fuck,” Sickle called out past the roar of wind and motor. “We just snuck and fought our way through a hive-Stable full of a fuckton of changelings and tore out of there in a fucking armored motorwagon, and you’re whining that the place had the wrong fucking \textit{number?} Are you fucking serious?”

\leavevmode\llap{“}Hey!” I shouted up at her. “Factual information is an extremely valuable resource, and—”

\leavevmode\llap{“}Enough!” Dusty shouted. “Focus. We’re not out of this yet.”

I went quiet, though I grumbled under my breath. Of course Sickle wouldn’t appreciate why that detail was so significant.

\leavevmode\llap{“}That door,” Dusty said, glancing back my way. “How long do you think you knocked it out for?”

I shrugged, glaring out the window. “Dunno. They could have it working again in a few minutes if they’re lucky and know what they’re doing. Maybe a few hours if we’re lucky and they’re incompetent.”

\leavevmode\llap{“}Well, that’s a lot better than nothing,” Dusty said with a slow nod. “Good thinking.”

I grunted again.

It was less than two minutes later when the motorwagon skidded to a halt beside our partially concealed wagon. Dusty was already unstrapping by the time we stopped. “Everyone out! Get everything transferred over to the motorwagon. Quick!”

The vehicle lurched as Sickle leaped out of the back, landing with a great splash of mud, and I climbed out through the space she had vacated, taking a moment to strip away my generic-changeling-soldier guise. We quickly got to work, hauling equipment and dumping it into the cargo area of the motorwagon. After just a couple trips, Sickle got sidetracked, slowly walking around with a sway to her hips, a big grin plastered across her face.

Dusty noticed. “Sickle, what—”

\leavevmode\llap{“}My ass feels \textit{amazing},” Sickle declared, which drew a snort from Starlight.

Dusty merely paused, cocking his head with a questioning look. “...Are you high already?”

\leavevmode\llap{“}Nah, this ain’t drugs. I know drugs.” Sickle slowly strutted along, which I can assure you is some of the most bizarre imagery I have ever encountered. “This just feels \textit{good}. Ever since that mine went off under me, walking felt like I was getting fucked in the ass with a barbed-wire dildo.”

Starlight winced. “Ugh. Thanks for \textit{that} charming imagery. Fuck.”

\leavevmode\llap{“}You never said anything about that,” Dusty said, and Sickle laughed.

\leavevmode\llap{“}Well, yeah, ‘cause I ain’t some whiny little cunt.” She paused, rolling a shoulder. “Oh, wow.”

\leavevmode\llap{“}One of the changelings tending you said they put you in an autodoc,” I said while hauling several cases of ammunition between wagons. “Said it pulled about half a pound of metal out of you.”

\leavevmode\llap{“}Huh,” Sickle said, twisting her head one way and the other, then stretching her back. “Mmm. Fuck me, I think I forgot what it feels like to not have a bunch of bullets rattling around in me. Ain’t half bad.”

\leavevmode\llap{“}Good,” Dusty said. “Then move your ass and help us get this stuff over... No, power armor last. We’ll have to leave it behind if we don’t have room.”

\leavevmode\llap{“}Ugh, fine,” Sickle said, dumping the damaged power armor in the mud and grabbing a water barrel. “Way to spoil the mood.”

Though it was a tight fit, we got everything in, including the pair of ruined power armors. The last half of loading was spent with Dusty scanning the horizon behind us, peering out through the light rain for any sign of pursuit.

\leavevmode\llap{“}That’s all of it,” Sickle said, shoving the power armor into place and climbing across it to sit behind the gun again. We’d made sure to have any cases and other solid items at the front of the cargo hold, protecting any loose equipment from being trampled by Sickle, and conveniently giving her a makeshift seat.

\leavevmode\llap{“}Okay, mount up,” Dusty said, hauling himself up to the passenger-side window; the lack of functioning doors was a bit of a hindrance, but the armor plates welded across the side of the vehicle rendered them useless.

Sickle snickered. “Mount \textit{this},” she said, slapping a spiked hoof against her armored flank. We all ignored the comment.

I slid into the back seat, having gathered our collection of PipBucks. It was cramped, packed into the very middle of the vehicle, and the narrow windows beside me meant I had to either enter through the front seat and climb back, or enter through the cargo bed where Sickle stood. Fortunately, I had the small space to myself, which gave me enough room to lay out my equipment beside me.

As I was getting settled, Dusty looked back, then up at the roof. “Sickle, have you ever used a gun before?”

\leavevmode\llap{“}Ain’t like they’re hard to use,” she replied. “And before you say shit, I ain’t fitting in there, so don’t even fucking ask.”

\leavevmode\llap{“}You can have the gun if you’re good with it,” Dusty said firmly. “Otherwise, I want Whisper up there.”

\leavevmode\llap{“}Let her have it,” I said, floating up Starlight’s PipBuck. “I’ve got to get working on these before we can use them.”

Dusty frowned, contemplating it for a moment before sliding back into his seat. “Fine, for now. If she doesn’t cut it, though, you’re swapping. Starlight, take us out, continue on southeast for now.”

He had to point out the direction to her. “Sorry,” she said as the vehicle accelerated. “I can’t really tell southeast from west without my PipBuck.” She cast a quick glance over her shoulder before turning back to where she was going; the ride was already getting rough as we picked up speed. “It’s not damaged, is it? It’s fine, right?”

\leavevmode\llap{“}It’s fine,” I said as I pulled out my portable terminal and cables, connecting the two devices. “But PipBucks have tags that let others locate them. I need to get into these and change those tags so they can’t just follow us when we turn them on.”

Not that I’d ever done so before, but Emerald had obviously managed, so it was possible. I simply had to work out how.

The vehicle rattled and rocked as it crossed a patch of rocky ground, then accelerated down the slope of the hill, jostling us again before hitting the flat ground below. I remained focused on my work, sheltering behind the front seat from the spray of rain splashing from the motorwagon’s hood. I only glanced up on occasion, when the vehicle shook particularly violently from some minor dip or bump in the terrain. Even on the relatively flat ground, I could hear the creaking and groaning of the ancient vehicle, nearly hidden behind the deep thrum of the spark-powered motor and the cacophonous hammering of rain on bare metal.

Each time we hit a bump, I heard Dusty hiss softly under his breath. After a couple minutes, he finally called out. “Sickle? Keep a close watch out behind us. You’re our eyes right now.”

He settled back into his seat fiddling around with something. It wasn’t until I heard him quietly hissing through his teeth again, despite the smooth ride, that my curiosity was piqued, and I poked my head up to see around the seat. He had opened up his barding, and was in the process of slowly peeling it back from his chest. The flesh beneath it was pink and raw, with most of the coat singed away, and the fabric of his barding clung to the wound.

\leavevmode\llap{“}Holy shit,” Starlight said, casting worried glances his way between looks back to where she was driving. “Do you need a healing potion?”

\leavevmode\llap{“}No,” Dusty said through grit teeth, and let out a groan of relief as he pulled the last of the barding away. The wound was oozing. He retrieved a bottle of water, splashing it over his hooves. “We’re low on potions. Save them for critical injuries. This is just a second degree burn. It’ll be fine unless it gets infected. Whisper, do you still have that soap?”

I had kept one of the containers in my bags, as silly as it might seem, one of those simple things I still held onto. I dug it out and passed it over. He quickly washed his hooves, then proceeded to carefully explore around the wound before gently cleaning the raw flesh. He managed to remain silent, though I could see the strain in his neck and jaw.

I sat back, returning to my own work. “...So I’m guessing I earned an ‘I told you so’.”

Dusty merely grunted at first. It was several more seconds before he replied. “You made your case. I made the call.”

He returned to tending to himself. It seemed that was all he had to say on the subject.

The ensuing silence lasted until Starlight finally spoke up again. “So, speaking of... now that we’re out of there, and we don’t \textit{seem} to have a whole army of shapeshifting bugs chasing us down, uh… think you can fill us in on what the \textit{hell} just happened?”

So as we rolled across the rain-soaked Wasteland, I filled them in on everything they’d missed.

\leavevmode\llap{“}Wait, Chrysalis?” Starlight said, the vehicle swerving a little as she looked back before straightening out again. “She was that evil old-world queen you were talking about, right? This queen named herself after \textit{her?}”

\leavevmode\llap{“}It sounded like all of their queens had done so,” I said over the PipBuck screen; it was currently scrolling through data in a sort of debug mode while I double-checked my work.

\leavevmode\llap{“}That’s… that’s like super bad, isn’t it?”

I gave a quiet huff. “A changeling hive numbering in the thousands, with vast resources, advanced arms and armor, soldiers extensively trained in arcano-tech simulated environments, a stockpile of imprisoned ponies to feed their entire population, agents who have been secretly employing mercenaries and raiders, and a lot of equipment being moved in and out of their heavily fortified base. All led by a queen that was practically salivating over the opportunity to step forward and end ‘the reign of ponies’, and who has named herself after the most infamous pony-loathing changeling in all history.” I snorted, pulling the cables from Starlight’s PipBuck and holding it out. “Yeah. It’s bad.”

Starlight gently took her PipBuck. “Wonderful.” Lacking the time to mount it on her leg, she set it beside the steering wheel, switching it over to display the map.

I had hooked up the next PipBuck, ready to run the same process that I had just perfected on that first one, when I paused. “Actually, it’s even worse than that. Mind, I never met the first Chrysalis, but the impression I always got from others was that she was a selfish and sadistic megalomaniac. This Chrysalis didn’t seem that way. She spent time explaining and justifying her position. I don’t think she’s just driven by some simple lust for power or hatred of ponies. She presented good reasons to support whatever it is she’s going to do.”

\leavevmode\llap{“}Good reasons?” Starlight said. “You don’t really think—”

\leavevmode\llap{“}Hold up,” I said, raising a hoof, even though in hindsight Starlight wouldn’t see the gesture. “Don’t think for a second that her having good reasons means I agree with what she’s \textit{doing}. I think her treatment of ponies is abhorrent, for one, and I don’t see that changing. But I’m still an Infiltrator, and that means I need to understand individuals I might find repugnant. I don’t have the luxury of simply dismissing their motivations as inherently flawed and unreasonable. This Chrysalis has some very good reasons supporting whatever it is she plans on doing, and that makes her hive considerably more dangerous.”

Dusty grunted as he finished strapping his barding back on, covering up the thick bandage he had loosely packed over his wound. “What kind of reasons?”

\leavevmode\llap{“}She blames ponies for everything that’s wrong in the world,” I said. “Ponies made the megaspells that turned Equestria into a balefire-blasted wasteland. Xenophobia still holds strong, even towards the zebras that are so much more similar to ponies than changelings are. Then you’ve got the pervasive violence and cruelty bred by the Wasteland. Warlords, slavers, and raiders, she said. Ponies that prey on other ponies, because the Wasteland isn’t cruel enough on its own. They’re fairly sound and convincing arguments, especially to a non-pony.”

Starlight snorted. “Yeah, okay, I hate raiders as much as anypony, but they ain’t exactly \textit{normal}. Shit. And what the hell is she complaining about slavery? She’s got a bunch of ponies captive as… as food!”

\leavevmode\llap{“}I imagine it’s easy to see a difference between slavery for economic gain and slavery for basic survival needs, especially when the slaves in question belong to a group you already have cause to dislike. They could even make the argument that the ponies they’ve captured are probably a good deal healthier and happier than slaves out in the Wasteland.”

\leavevmode\llap{“}That’s still fucked up,” Starlight grumbled.

\leavevmode\llap{“}I don’t agree with her conclusions, either,” I said. “But I recognize how the reasons behind it could be very convincing to others.”

\leavevmode\llap{“}You said this makes her more dangerous,” Dusty said. “How so?”

\leavevmode\llap{“}Not her,” I corrected. “Her hive. If she took the time to explain all this to me, a newcomer to her hive that wasn’t even fully trusted, then it’s likely that many others in the hive had heard all those reasons. I don’t think this hive is following a tyrant because she demands their unwavering loyalty. I think they’re following an \textit{idea}, and an idea is much harder to kill.”

Dusty mulled that over for several seconds before slumping back in his seat. “Shit.”

\leavevmode\llap{“}So what do we do?” Starlight said.

She was answered with only the roar of wind whipping through the windows.

After a minute, Dusty finally spoke again. “We need to get away from here. They know who we are, and even with PipBucks, I doubt we’d be able to see them coming. As much as I hate to say it, I don’t think we’ll be safe anywhere around here. Maybe Trotsen is far enough away to be out of their reach.” He looked up at the metal roof above him. “But I kind of doubt it. Maybe northern Equestria.”

Starlight shot him a look. “Wait, you mean run away?”

He glumly nodded. “This is way too big for us to fight.”

\leavevmode\llap{“}On our own, maybe,” Starlight said.

\leavevmode\llap{“}And who else would we call on?” Dusty said, his voice rising. “Mareford has the most capable military force in the region, and they’d still be lucky to get past that entryway, not to mention they’ve got bounties out on our heads. Who else? Gemstone? Rust? We’re talking a hoofful of semi-skilled fighters against an organized military force. They’d be slaughtered, assuming they haven’t already infiltrated them. Hell, that’s assuming it’s even a stand-up fight! We don’t even know who’s already on their side!”

Starlight frowned, but said nothing.

\leavevmode\llap{“}Look, I don’t want to leave, either. Mareford is my home, but we’re running out of places we can go.”

\leavevmode\llap{“}We can still go to Baltimare,” I said, looking up from the PipBuck. The second re-tagging was proceeding much more easily than the first, now that I knew what to do. “That’ll take some time. Maybe after that, we’ll have come up with a better plan.”

Dusty grunted. “It gets us out of the area for a while, at least. And yeah, still need to check up on that. Afraid this might complicate the search for your own hive-mates.” His expression shifted, hesitating before reluctantly adding, “Assuming these changelings aren’t their descendents.”

\leavevmode\llap{“}Unlikely,” I said, as debug information flashed across the screen of the current PipBuck; the tag alteration was successful once again. “Not impossible, but there are many unlikely factors. This looks more like some other hive’s survival plan.”

\leavevmode\llap{“}Still… this complicates things, especially if all your leads are in this region. If they’ve been scouring the Wasteland, they might have found any other C.L.T. facilities.”

I grimaced. “I know. But that doesn’t really change anything. I was already aware that I might be the last survivor of my hive. There was a chance I’d never find anything, anyway.” I pulled the cables, holding out the cleaned PipBuck to Dusty. “But we know there was one Cocoon site they hadn’t found. There still might be more.”

He looked at the PipBuck, sighed, and took it. “Baltimare.” He undid the flap in his barding covering his left leg, slipping the PipBuck in and securing it to his leg. He blinked a few times as the E.F.S. sparkled in his eyes, then settled into his chair again, slowly browsing through the device’s menus. “We never did deal with Big Gun.”

\leavevmode\llap{“}We still can,” I said as I prepped the next PipBuck. “Just get me near Mareford, and I can take care of the rest.”

Dusty mulled that over for a long, silent moment. “How long would it take you?”

\leavevmode\llap{“}Depends on the situation I find,” I said, eyes dancing across the screen. “Assuming he isn’t out of town, travel time plus six hours should give enough time and flexibility for almost any situation. Plus twelve would be almost decadent. Either way is a maximum; depending on the situation, it might be considerably quicker.”

He slowly nodded. “And you’re sure you want to do it this way?”

I paused, looking up from my screen. “I would prefer a non-violent solution, but given all the factors involved, I believe killing Big Gun is the best option we have.”

\leavevmode\llap{“}Even over doing nothing?”

\leavevmode\llap{“}\textit{Especially} over doing nothing.”

Dusty looked at me intently. Eventually he nodded once more. “Okay. We’ll get you to Mareford.”

I nodded as well, returned to my work, and started to plan.