Lemon Tart arrived at Mareford in the late afternoon. A large caravan was just arriving, and he fell in behind them, following them into the town. The Militia guards gave him only a cursory look. The light yellow unicorn carried no weapons and wore no barding, carrying only some worn but sturdy bags and a thin cloak. They waved him through, continuing their inspection of the caravan.

Mareford was busy, as was expected. The day was steadily making its way towards night, and ponies were all about, finishing up their business for the day. It was a lively place.

Lemon Tart wound his way through the thin crowd of ponies as he navigated old, half-remembered streets. Patched-up buildings passed on either side as he made his way further into town, until he finally reached his destination: a small restaurant, just across from the town hall.

With an eager smile, he approached the owner. A minute later he was counting out caps to the kind stallion, while the cook started pulling out ingredients.

As the grill started to sizzle, Lemon Tart kicked back at one of the rickety tables out front, popping the top of an ancient Sparkle-Cola and taking a long swig.

It was a nice enough place. Ponies passed by on the street, and Lemon Tart watched them going about their business. There was an elderly couple, carrying bags freshly loaded with food. Several younger ponies ran by, laughing and calling out to each other. A pair of armed ponies, mercenaries by the looks of them, stepped out from the town hall, glancing around before continuing on to the street.

Lemon Tart took another sip, content to simply kick back, enjoy his drink, and watch.

When the meal came, he ate slow and casual, taking his time to enjoy it, while chatting with the restaurant owner.

It was just random, idle conversation, such as the weather…

\leavevmode\llap{“}Oh, yes. Heck of a storm. The roof of my apartment finally gave in, flooded me and my wife’s bedroom. It’s okay, we’ve just been staying here at the restaurant while we get everything dried up.”

...and business…

\leavevmode\llap{“}Yeah, meat’s always been a bit hard to come by, but I’ve got some friends in the caravans, made some good deals with traders. No, the real hard part is fresh veggies. Ever since the whole fiasco with Hayseed, it’s been harder to get what I need. Big Gun paid a bunch of farmers to grow more cotton. Don’t know why, guess it brings in more caps, but it means the food the others make goes for a premium, and the preserved stuff ponies dig up just doesn’t cut it.”

...and recent events.

\leavevmode\llap{“}Such a horrible thing. Sure, you hear about ponies getting killed all the time, but first the water caravan, and now this? It’s just a bit too close to home. Hell, half the town heard the explosion. Sandy, the new boss, she’s been trying to get anypony who’ll sign up, but I guess ponies ain’t too eager to throw in with them after a massacre like that. And then there’s the Rangers. Lots of good ponies died out there that day.”

\leavevmode\llap{“}It’s a shame,” Lemon Tart said, and took another drink.

Time passed, the sun slowly crept toward the horizon, and before long the food was all gone. Lemon Tart gave his thanks to the stallion, as well as a few extra caps in tip, and walked across the street. Another trio of mercenaries passed by as he made his way across the courtyard and up to the steps of town hall.

He opened the doors and stepped through, walking briskly through the wide lobby. A pony sitting at a desk looked up questioningly, but Lemon didn’t look over. He simply carried on with his business, walking across the lobby with the sharp clip-clop of hooves on polished stone. The other pony returned to his work; obviously, the yellow stallion knew where he was going.

Lemon trotted up the marble stairs and turned, following the well-worn carpet leading to Big Gun’s office.

He drew short. The doors were open, and he could hear the voice of a mare speaking with him. Instead of continuing on, Lemon turned and claimed one of the chairs nearby. He could wait until Big Gun’s business was concluded.

The conversation lasted only a couple of minutes before going silent, and moments later Lemon heard a door open and shut. He stood and walked over to the doors again.

Stepping through, he found Big Gun sitting behind his desk, typing on his terminal. He looked up as Lemon Tart stepped through the door.

\leavevmode\llap{“}Mister Gun,” Lemon said as he shut the doors behind him. “I brought something you need to see.”

Big Gun sat back in his chair, frowning. “And you are?”

\leavevmode\llap{“}Lemon Tart,” he said, quickly approaching the desk. “I work for Sandy. A couple of us found something and… well, it’s about Banger, sir.”

Big Gun’s expression tightened slightly, his brows lowering. “Is that so?”

\leavevmode\llap{“}Yes sir,” Lemon Tart said with a quick nod, and turned to his saddle bags. “We thought you should see it right away.”

As Big Gun watched, Lemon Tart pulled out a PipBuck. His eyes widened in interest, ears perking up. “Where did this—”

His gaze rose to see the next item Lemon Tart had pulled from the bag: a pistol with attached suppressor, presented muzzle-first.

The sharp metallic clack of the pistol echoed in the room as Big Gun jerked, then dropped. His face smashed against the edge of the desk as he collapsed to the ground, emitting only a momentary, gasping gurgle as the breath left his lungs.

Lemon darted around the desk, pistol tracking Big Gun as he checked on the older stallion. The shot had been calmly made and well-placed, and Big Gun hadn’t had the time to process the threat. The subsonic hollow-point bullet had struck just inside the left eye, shattering the orbit as it punched into the cavity of the skull. There was no exit wound. Despite the small twitches and the curling of Big Gun’s leg, the pony was very dead.

Tucking the pistol away again, Lemon grabbed Big Gun’s body in his magic, sliding the limp pony under the desk where it would be better hidden. Blood seeped from the wound, but he laid the body face-up to keep it from all draining out. Then he stepped back.

With a flash of green flame, Lemon Tart ceased to exist.

I was now Big Gun; mayor, industrial leader, and back-room schemer.

I hunted down and snatched up the spent shell casing, tossing it into the open bag, then shed my cloak and tucked it in as well. Next, I returned to the desk. Pulling out a cable, I connected Emerald’s PipBuck to the terminal, then slid the PipBuck out of sight. To any pony entering the room, there would be nothing out-of-place. Just me, Big Gun, typing away at my terminal.

The transfer was done in moments, and I loaded up the text editor I had prepared, sending it on a search through the files for any mention of a small set of words. Banger, raider, water caravan, Quicksilver, Silverline, and a few others. In-depth analysis would have to wait, as time was critical here, but I needed to know if the information we wanted was here.

Nothing leaped out as an obvious smoking gun. The only mention of Banger was a week before the water caravan was hit, but that was simply a list of personnel assigned to the caravan rather than anything incriminating. Silverline was mentioned only twice. The first was simply listing her and Quicksilver as survivors of the water caravan massacre. The second was a brief commentary from two weeks after her return in what seemed to be a personal planner crossed with a diary.

\terminal{
\textit{Silverline continues speaking out re: caravan raid. Loud, no support. Ignore.}
}

Hardly incriminating. A simple tweak would improve that. I skimmed through a few more entries to get a brief understanding of his typing style, then returned to the entry in question.

\terminal{
\textit{Silverline continues speaking out re: caravan raid. No evidence, but loud. Ponies getting curious. Need silence. Send WR to visit daughter?}
}

I saved the file again, and left it up on the screen, scrolled to the current day. Hopefully anypony investigating would be curious enough to look into it, perhaps to find any suggestion of who might have killed him.

Yeah, okay, as far as planting evidence goes, it was pretty pathetic. I was working with what I had, and I didn’t have time to do anything more thorough. If it convinced anypony, that would be a nice side benefit, but it wasn’t why I was here.

I tucked everything into my saddlebags and pushed Big Gun’s chair up to the desk, better hiding the body tucked beneath it. With that done, I turned to the door at the back of the office.

As I had hoped, the door led to Big Gun’s personal apartment. The room I emerged into was a living room, filled with an assortment of furniture. My initial impression was mixed; For most of my life, seeing a room with such a mish-mash of styles, all thoroughly worn out through centuries of use, would have come across as jumbled and poor. Compared to the places I’d seen since then, it came across as a declaration of wealth and luxury. Neither were terribly good impressions.

But it did mean I was unlikely to run into any ponies other than Wild Runner. As she wasn’t in the living room, I took the moment to prepare. The PipBuck came back out, and I latched it onto my leg. The E.F.S. flickered to life as I pulled out my pistol again. Then I continued on, moving past the small kitchen and dining area and into the hall beyond.

One door revealed a small bathroom, dimly lit but meticulously cleaned. The next was a spare room, cluttered with a variety of weapons, tools, and diagrams.

The final door opened to a bedroom. Wild Runner was there, kicked back at the foot of the bed with a disassembled rifle. She looked up to see Big Gun entering, an unfamiliar pistol clutched in his teeth.

\leavevmode\llap{“}Gun?”

S.A.T.S. kicked in as I advanced briskly, tonguing the trigger. She started to jerk back in surprise, but at such close range, all three rounds struck her squarely in the chest. She gasped and fell back, her legs kicking out and sending several parts of her weapon tumbling. Her hooves shot out, whether to scramble away or grab one of the other weapons nearby, but all coordination had already left her limbs.

I took no chances, advancing to just outside bucking range and placing two more rounds into her chest, then taking a moment to line up on her head. The fight had left her, and she tried to mouth something as I pulled the trigger again. Her head jerked.

A flash of green fire ripped across her, revealing the very dead changeling. I staggered back, wide-eyed. So many thoughts ran through my head in that instant: recognition that I had just killed a changeling who might not have deserved to die, concern that the situation was drastically different than I had believed, and of course, all the scenarios that could be the cause and result of a changeling replacing the second-most-influential pony in Mareford.

After a moment of shock, I shelved all those thoughts to focus on the present. Focus, adapt, proceed.

There were only two immediate needs: get out of there as soon as possible, and hide any evidence of changeling involvement. I still relied on the secret of our existence at least as much as Serenity did, assuming this was one of their Infiltrators.

Hiding the evidence was easy. I quickly added a horn to my current form, then focused my magic. A moment later, the other changeling’s body was burning away to ashes.

As the fire rose, I darted around the cluttered room, looking out shuttered windows. While the living room and office windows looked out over the street, still moderately busy in the failing light, the bedroom windows looked over the enclosed courtyard behind the town hall. It was perfect.

The body had been reduced to ashes by that time, and the carpet and end of the bed were starting to smolder. I quickly appraised the room. With the amount of furniture, the room would probably burn quite well, but the stone construction should limit its spread. I let it continue as I changed again, this time taking the form of a dark-blue pegasus, lean and lithe except for the powerful wing muscles. It was a form built entirely for speed and agility.

Tucking my pistol away in my bags, I hoofed through the small collection of not-Wild-Runner’s weapons, selecting a small submachine gun, much like the ones I had seen in the mouths of raiders. I loaded a magazine, chambered a round, and leveled it at the wall beside the door.

A quick tongue of the trigger and a twist of my head sent out a painfully loud barrage of shots and blew off chunks of plaster and wallpaper from the walls. With the alarm thrown, I tossed the weapon into the smoldering ashes, threw open the window, and darted out.

A quick half-loop brought me low over the roof, and I banked sharply as I took off, wings pumping, toward the ruins of Dodge City and the crater within. I skimmed low over roof-tops, visible for mere moments whenever I passed over a street.

If I was lucky, nopony would see me. Even if I wasn’t, seeing a pegasus fleeing the scene would point any investigation in the completely wrong direction.

Buildings flashed by beneath me as I sped away. Only the town walls stood in my way, and not so much in the physical sense, but in the armed guards that would be there, watching for attacks.

Fortunately, that meant that any ponies nearby were looking outward. I didn’t even see any on the section of wall I slipped over, though I assumed the tower just a hundred yards away was probably occupied. If they saw me, they didn’t try to shoot at me, and a few seconds later I was low over the ancient, debris-filled streets, winding between ruined buildings.

I continued like that for almost half a mile before slowing, flying a little higher along a long, main road. A faint ache was already building in my wings, and I had a ways to go.

The ruins passed below me, and every now and then, a red pip would show up on my E.F.S. before quickly sliding away behind me. I caught a couple glimpses of feral ghouls or very sickly ponies, and once, to my concern, saw a manticore sleepily poke its head up over a ruined wall, tracking my flight for a few moments before settling in to nap again.

As I approached the faintly glowing Dodge City crater, I banked again. Staying low, and screening myself from Mareford by the ruins of the city, I flew off in a completely different direction. Even if the Rangers tried to follow me, they would have no idea where I was going.

{\br}%
Half an hour later, I caught sight of the rocky formation we had made camp at. I skimmed low over the surrounding hills, popping up just enough to be visible. As I drew closer, I could already see Dusty, his binoculars up and watching me, in my natural form, flying in.

Starlight got to her hooves, walking toward me as I landed, though her downcast expression and slack stance made her look every bit as worn out as I was. Past her, Sickle lay still and dozing, sprawled out across the motorwagon’s cargo bay. Last I’d seen her, she’d been aggressively pestering Dusty for sex.

My wing-muscles ached.

\leavevmode\llap{“}How’d it go?” Dusty asked.

I simply stood there. I’d been thinking about it the whole flight back, and still had little idea how to answer that. “That’s a surprisingly complicated question to answer.”

Dusty’s ears flicked back. “What went wrong?”

\leavevmode\llap{“}With the mission?” I asked. “Nothing. It went perfectly. If anything, it was almost anticlimactic. It couldn’t have gone much smoother.” I sat beside my belongings with a weary sigh. “And a few days ago that would have been fine, but I think you’d be concerned if you saw just how easily a changeling Infiltrator can walk straight into a well-defended town and kill the most influential and powerful pony there.”

He was frowning. “You’re thinking of Serenity.”

\leavevmode\llap{“}Of course I am.” I dug through my possessions as Starlight stepped up to sit beside me. “Though I guess, despite how smoothly it went, it could also be said that I didn’t accomplish my mission.”

I waited for the inquisitive looks that followed before clarifying. “I didn’t kill Wild Runner. I killed the changeling that had replaced her.”

Starlight’s ears fell back. “Oh. Oh no.”

\leavevmode\llap{“}What do you mean?” Dusty said, stepping in. “Serenity is spying on Mareford?”

\leavevmode\llap{“}Assuming it was Serenity,” I said as I pulled out a package of veggies; despite the large dinner, I was feeling hungry again. Starlight’s proximity was taking care of the other hunger I felt. “Which is probably a safe bet, at least. I suppose it’s not even surprising that they’d be getting into local leadership. It’s just another thing to be concerned about.” I looked over to Dusty. “If they’ve infiltrated Mareford, they might have infiltrated the Militia. If they’ve infiltrated the Militia, then they hold an uncontested majority of the military power in the region.”

Dusty grumbled. “Shit.”

\leavevmode\llap{“}Yeah.” I threw back a couple soggy pieces of broccoli, mashing them up before swallowing.

\leavevmode\llap{“}Well at least you’re okay,” Starlight said, reaching a foreleg around my shoulders to give a hug. I leaned into her. “So… I guess you’re the expert on changeling infiltration. What do we do?”

I sighed, slumping a little. After a few moments of silence, I shook my head. “I don’t know. Keep pressing on, I guess.”

Her ears drooped. It was a little painful to see that expression from her. “There has to be something we can do, right?”

\leavevmode\llap{“}I don’t know.” There was one thing, but I wasn’t willing to consider that just yet. “Maybe we’ll come up with something. Right now, I have nothing.”

She sat silently, her gaze turned down.

After a few moments, Dusty gestured back to the motorwagon. “You two turn in. It’s a long trip to Baltimare, even with the wagon. Get some sleep.”

Despite feeling so drained and tired, I didn’t sleep well that night.