Change is a strange thing.

One of the earliest lessons taught to a prospective Infiltrator is that you do not focus on making a perfect disguise. There is no such thing. No matter how much research you invest in a role, there will always be information you lack. Some small detail will always be off. There will be closely held memories shared only with rare individuals, subtleties of behavior that only someone with a lifetime of experience would recognize, even some hidden subtlety of physical form from some decades-old injury.

It’s easy to stress over these tiny differences, and it’s easy to be consumed by it. The majority of those who washed out of Infiltrator training were due to being unable to handle the stress. Obsessing over the impossible task of creating a perfect disguise, or paranoia over the inevitable shortcomings, was the most significant source of that stress. While we could aim for as much accuracy as possible, the end result was only ever “good enough”.

A successful Infiltrator was one who recognized that it truly was good enough.

When it comes down to it, our perceptions are incredibly limited and flawed. Sometimes, this can be directly manipulated by an Infiltrator. Memories are malleable, and the right comment at the right time can significantly alter what an individual remembers. More often, Infiltrators benefit from a more passive but prevalent quirk of perception: our brains are constantly filling in periphery information with assumptions and extrapolations. A consequence of this is that, so long as someone isn’t aware that something has changed, their brain tends to fill in the details as if it hadn’t.

This change blindness is a great boon to an Infiltrator. It’s not infallible, hence the amount of research an Infiltrator will put into their impersonations, but so long as you get the majority in place, your mark’s own brain will work to help you.

As we cut across the Wasteland in our rattling motorwagon, it would have been easy for me to not notice how things had changed. Yes, there was hardly any plant-life, but the area was a desert since long before the war. If I had woken in the middle of the Wasteland, absent the significant and direct evidence of the passage of time, I might have simply thought it was an overcast day. Even now, it was interesting how little had changed in this little part of the world.

Change became much more apparent when we rolled up the slope of a hill, cresting to look out over the valley beyond. The distant cluster of buildings were worn down by the wear of centuries, only to be patched up by crude repairs and broken-down fortifications. There was an outer chain-link fence, reinforced by bits of scrap and piles of debris in some places, and fallen and broken down in others. A gatehouse, just large enough for a single pony, now lay collapsed and ruined beside the broken-down gate. Beyond that, a pair of old huts sported crude scrap-metal ramparts, and the supports of a skywagon shelter stood in isolation, long since missing the roof they had once held up.

Past that was the chipped and scarred concrete of a bunker, with a sloped ramp leading down into the ground. The outermost door gaped open.

\leavevmode\llap{“}Looks about like I remember it,” Dusty said as we looked it over through binoculars and scopes. “I don’t see any signs of repairs. That broken-down section of fence on the north side is where my squad breached, and it doesn’t look like anyone fixed up any of the battle damage. Not seeing any signs of life, either.”

Regardless, we didn’t head straight in once we’d gotten back in the motorwagon. Instead, Dusty directed us to a small rise, about a quarter mile from the gate. When we rolled to a stop, he again surveyed the site for a minute.

\leavevmode\llap{“}I doubt there’s anypony there, but let’s take it careful anyway,” he said. “Sickle and I are the assault element. Starlight, Whisper, you’re our base of fire. Your job is to stay here, and if somepony opens up on us, hit them hard. Suppress with the machine gun, pick off exposed targets with the Lancer. Keep them from shooting back while we get to cover.”

\leavevmode\llap{“}You got it,” Starlight said, sitting beside the motorwagon with her Lancer ready. I gave the machine gun a quick check, ensuring the belt was in position and unobstructed, and that one of the gigantic rounds was chambered. With a sharp \textit{clack}, I disengaged the safety lever, freeing the trigger.

Dusty had opened the flap covering his PipBuck to look at the screen. “Call it… five hundred yards to the gate, about six to the bunker.”

I reached up, nudging the dial on the side of the machine gun’s sights to “5”, and let the tip of the front sight post hover over the intact building closest to the gate.

He’d already re-secured the flap, and gave his own weapon a quick final check. “Okay. We’ll call when it’s time for you two to move up. Sickle? Let’s go.”

\leavevmode\llap{“}Yeah, yeah,” Sickle rumbled, lazily walking after him. Despite the precautions, she wasn’t expecting a fight.

Neither were the rest of us, but I certainly didn’t mind the precaution. We were so close, now.

I watched their progress in the edge of my vision, keeping my eyes fixated on the building, ready to shoot, and painfully conscious that I’d never fired this weapon before. I’d never even seen it fired. I had no idea what to expect. Judging from the size of the rounds, I could only expect it would be incredibly loud.

A few minutes later, they reached the gate. Dusty halted by the collapsed gatehouse and the reinforced fence, leaning around the corner with his rifle. After a moment, he sat back, fiddling with something. My earbud crackled.

\leavevmode\llap{“}Bring it up. New base of fire here at the gate.”

Starlight picked herself up, stashing her Lancer in the passenger seat as she slid in behind the steering wheel. Moments later, we were rolling forward. I kept the muzzle of the machine gun elevated a bit as we bounced and rattled across the dry ground; the last thing I wanted to do was accidentally shoot one of my companions because we hit an unexpected bump.

We rolled to a stop just behind the fence, and Dusty waved us forward. “Pull up until you’ve got a clear line on the huts and the bunker entrance.”

\leavevmode\llap{“}Say when!” Starlight called out before creeping forward.

The nose of the motorwagon was poking out past the ruined gatehouse by the time I called out to stop, having just cleared the built-up fence. It offered me a narrow view of the two huts and the bunker beyond. I once again fixed the closest hut in my sights before realizing they were well within E.F.S. range, and nothing was showing. I swung over to aim at the gaping black entrance of the bunker.

\leavevmode\llap{“}Keep overwatch while we move up. Don’t forget to adjust your range.”

I quickly reached up to the range dial, annoyed that I hadn’t thought to do so myself. I doubted it would make much difference at such a short range, but I could use every bit of help I could get.

He was moving by the time I settled into a firing position again. He and Sickle headed out, looking as different as could be; while Dusty moved with his weapon up, ready for a fight at a moment’s notice, Sickle plodded along, looking almost bored.

When they reached the bunker and its wide entrance, Dusty took a moment to look inside, first with his rifle, then with a flashlight. Finally, he called us up. We were halfway to the bunker when the first marks appeared on my E.F.S. Non-hostile, at least for the moment. Still, the tension suddenly ramped up. I could hear my heartbeat.

As we pulled up, Dusty directed us to the side of the bunker, telling us to park there and hop out. I made sure to engage the machine gun’s safety before dismounting.

\leavevmode\llap{“}We’ll go in together,” Dusty said as we gathered around. “There’s only a few rooms this side of the sealed door, if it’s still shut. Front one was the biggest, looked like loading and unloading. Then a hall, two side rooms, not sure what they were for. Lots of junk all over the place. Made rooting out the last few bandits a bit of a chore.”

\leavevmode\llap{“}It’s occupied,” Starlight noted, and Dusty gave a small nod.

\leavevmode\llap{“}We don’t know what by,” he said. “Could be radroaches. Could be hellhounds. We’ll take it slow and careful. Just as a warning, when we hit this place, we found the remains of some ceiling turrets. Some of those contacts might be more, and I wouldn’t trust them to stay non-hostile.”

\leavevmode\llap{“}Turrets,” Starlight grumbled. “Wonderful.”

Dusty nodded. “If we’re lucky, Whisper can get into their controls and shut them down.”

\leavevmode\llap{“}And if not?” she asked.

\leavevmode\llap{“}Then you get to float a rifle around a corner and try to take them out without exposing ourselves. Anypony got a mirror?”

\leavevmode\llap{“}I do,” Starlight said, nudging one of her packs. “Part of my salvage gear. It’s useful for working in tight spaces.”

\leavevmode\llap{“}Good,” Dusty said, then turned to me. “Hop back to the wagon, grab all the grenades you can carry. They’ll probably be mediocre against turrets, but they’ll be great for everything else.”

My bags hung heavy by the time I finished loading them, and I’d only put a small dent in the haul we’d taken from Boomer’s crew. We certainly had grenades to spare.

I returned and, almost as an afterthought, stripped away my disguise. My armor lay flush against my carapace, snug and comforting. A small modification to my form blunted my fangs, allowing me to grip my rifle’s bit.

PipBuck screens were turned up, while Starlight and I held flashlights in our magic. Dusty gave us a quick look-over, nodded, and rounded the corner.

It was almost slick and professional, how we spread out on the ramp, advancing at a steady walk with weapons leveled. Lights cut through the darkness to illuminate lumps of trash and debris as we made our way down the ramp. It was wide and tall enough to easily fit our motorwagon, and descended about thirty or forty feet before opening into a wide room with thick supporting columns. Old crates and scrapped skywagons were arranged to form barricades at the bottom of the ramp, and semi-private rooms along the side.

The signs of a battle were clear. Several sections of the barricade were broken and askew. Divots in the concrete floor, walls, and ceiling marked where bullets had struck, sending out a hail of debris that now crunched underhoof. Larger divots and scarring marked where grenades had detonated, tearing up large chunks of the ground and nearby walls.

Dusty advanced to the barricade and halted, keeping himself mostly in cover as he swept the muzzle of his rifle around the room. Still no hostile contacts on the E.F.S.

As I swept my light around the room in time with my own rifle’s movements, I could see the dark stains on the ground. They lay in thick splotches and lines, long since dry and faded with the years until they were barely visible. Bloodstains.

A quiet squeak broke the silence as one of the non-hostile marks on my E.F.S. abruptly moved. I quickly swung my rifle over to it as the light glinted in the eyes of a rapidly scurrying creature. It took me a moment to realize it was a rat, darting into the safety of one of the crude shelters.

Dusty spoke up. “Whisper, Starlight, sweep the left side of the room. Sickle, with me.”

He stepped past the barricade, and after an exaggerated roll of her head, Sickle followed.

I followed through the same gap, but cut the other way. The debris scattered around the room made progress slow, and even with the knowledge our PipBucks gave us, I couldn’t help but note just how many hiding places there were, if someone had been waiting for us.

We picked our way through the debris of the first room, confirming that the chamber truly was unoccupied, aside from a few rats that did their best to hide from us. A quick check of the side rooms beyond revealed them to have been converted to living spaces, all ruined by the fighting that had taken place there.

Then we were at the door, a heavy piece of metal that would have risen into the ceiling to open. Now its weight held it shut as much as its own machinery did, as if it had been designed to be hard to open. We tried the button beside it, but it remained still.

Dusty turned to Starlight. “You’re up.”

With a nod, Starlight started breaking out her tools, while we backed off. A minute later, her cutting torch lit up, throwing sharp, vivid shadows across the walls as she cut into a panel beside the door.

I sat beside Dusty, looking out into the outer room with its dancing shadows. “So you fought your way into here?”

It wasn’t so much a question as it was a conversation starter, and Dusty nodded. “Yeah. My squad of Rangers, plus two squads from the Militia for support. It was pretty brutal. In a good way, I mean.”

\leavevmode\llap{“}The defenses here kind of remind me of Serenity.”

Dusty gave a dry, humorless chuckle. “Not even close.”

\leavevmode\llap{“}Smaller scale, certainly,” I said. “But still an underground compound with a single entrance watched by defensive positions.”

Dusty lifted a hoof to point toward the glow of sunlight coming down the ramp. “You saw those barricades, right?”

\leavevmode\llap{“}Yes?”

\leavevmode\llap{“}Half-inch plywood and… I don’t know, maybe sixteenth-inch sheet-metal? Hell, I think those signs are aluminum, even. Your rifle will punch straight through that. Might lose a little power on the way, but it’s still plenty lethal. It might stop a pistol round or fragments, but that’s about it. The bandits? If one of them had armor, it was scrap metal and other junk, no better than the barricade. Weapons? Some shotguns, submachine guns, smoothbore pipes, and a bunch of pistols. Only two bolt-action rifles, and the ponies carrying those died outside.

\leavevmode\llap{“}Us? We were straight-up better. We had body armor that would stop anything but the bolt-actions. We had assault rifles and machine guns, all top-notch weapons. We had grenades and grenade launchers. We had our PipBucks. We had the better ground, more numbers, and started the fight on our terms.. And most of all, we had our training. Even the regular Militia grunts all had hundreds of hours of training each, and spent a small fortune in ammo. Us Rangers had even more. The bandits? They bullied traders, maybe had some small skirmish with scared folks trying to fight them off with the old family rifle. They might have gotten into some regular fights, but I doubt a one of them had ever been in a \textit{battle}.

\leavevmode\llap{“}And their nice defensive position? They were stuck down there. They couldn’t run away. Their only option was to sit and watch that entrance, ready to cut us down when we charge in. We knew that, pretty obvious, so we didn’t. Instead, we stepped back and lobbed grenades down the ramp. Put probably twenty or thirty down there. That many explosives in an enclosed space, shrapnel kicking around everywhere? That’d take the fight out of just about anypony.

\leavevmode\llap{“}We followed it up with some smokes to blind whoever was left, then set the machine guns at the lip of the ramp, firing down it. Put some flares down when the smoke started to thin out, but everypony who’d tried to hold the barricade was dead. From there it was just pushing up under cover of the machine guns, putting frags into every space, then following them in. Eight bandits managed to make it into the bunker, and not a single one of them managed to fight back.”

I eyed the rubble and wreckage. “I see what you mean about brutal.”

\leavevmode\llap{“}But Serenity?” He shook his head. “Power armor, energy weapons, and heavy concrete fortifications. It’s like this place on Buck—”

\leavevmode\llap{“}Buck and Stampede,” Sickle helpfully interjected.

\leavevmode\llap{“}Point is, it’s a completely different level than this,” Dusty said. “You know how the Rangers would have dealt with something like that?”

I continued to stare.

\leavevmode\llap{“}We’d take one look at it, say ‘fuck that shit’, and blow the entrance.”

I blinked, contemplating his words. “...That might work.”

\leavevmode\llap{“}It’s an option,” Dusty said, slowly nodded, “but it only puts the problem off for later. Probably not even that long.”

\leavevmode\llap{“}Yeah.”

We fell into silence as Starlight continued to work. There was a certain familiarity to the process. Several minutes were spent cutting, followed by peering inside the hole. A few more minutes of cutting followed that, to get to the exact mechanisms she needed to work on. More minutes were spent working on those, getting them to disengage and free the massive door. Then it was our turn to help, working the prybar until the door lifted enough for her to wedge the screw-jack under it. From there, it was a matter of slowly cranking the door higher, the sound of metallic squeaks echoing softly in the hall.

\leavevmode\llap{“}Hold up a second,” Dusty said, once the door was almost a foot off the ground. “Let me see that mirror.”

When Starlight passed it to him, he laid down, using the mirror to peer under the door. He turned it back and forth, then moved it in further, tilting it up. The motion stopped. “Yep. There’s a turret about thirty feet past the door.”

Starlight looked up, staring straight at the door. “It’s not showing as hostile.”

\leavevmode\llap{“}And I don’t plan to give it the chance to change its mind,” Dusty said, rolling to lay on his side as he brought his rifle around. He stuck the rifle under the door, and had to scoot forward enough that his muzzle was almost under the edge before he could elevate the rifle enough. He fired twice, the sharp crack echoing in the space beyond the door like a drum. One of the E.F.S. contacts disappeared.

\leavevmode\llap{“}There we go,” he said as he slid back and stood, then gestured toward the jack. Starlight resumed cranking.

A couple of minutes later, it had reached as high as the jack would go, about two feet up. Plenty of room for Dusty, Starlight, and myself to crawl under. Another quick check with the mirror confirmed there were no more turrets, and Dusty led the way, sliding under the door.

Starlight was just getting to her hooves on the far side when she staggered. “Oh, shit.”

\leavevmode\llap{“}Like I said,” Dusty quietly, his rifle leveled down the hall.

I scurried under the door to join them, raising my own rifle as well. “What’s wrong?”

\leavevmode\llap{“}Those red marks,” Dusty said, his rifle remaining steady even as he spoke around the bit. “I’m guessing the turrets don’t want us trespassing.”

I looked around, eyes on my E.F.S. “I don’t see any red marks.”

He spared a glance my way before focusing down the hall again. “Huh.”

Starlight looked my way. “Maybe it’s because you’re a changeling?”

\leavevmode\llap{“}Maybe,” I said, trying not to sound too hopeful. While it would be promising if they had been programmed to not shoot at changelings, it could also be that they were programmed to only shoot at ponies.

There was a loud clatter of metal as Sickle stuck her head and neck under the bottom of the door, her shoulders jamming against it. With a deep growl, she pushed against the floor, the door squealing and grinding as she forced it upwards. Soon she was standing, the massive door opened almost all the way.

\leavevmode\llap{“}Hold it there!” Starlight called out, and slipped past Sickle. She went to the panel she had cut open, fiddling with something for a moment before a soft \textit{thunk} sounded from the wall. “Okay, let it down, \textit{slowly}.”

Sickle did as she asked, letting the door slide down an inch before another thump sounded, and the door held in place.

\leavevmode\llap{“}Perfect,” Starlight said, grinning as she retrieved her jack. “There’s a ratcheting brake system to hold the door open. It won’t be able to shut without power now. That, or someone taking a sledgehammer to the brake.”

\leavevmode\llap{“}Good,” Dusty said with a nod, then stood and started slowly advancing down the hall. I followed behind him, my flashlight floating above us to light the way.

The hall reminded me of the ones where I had woken up, a stark concrete corridor with metal-grate floors and exposed conduits and pipes above. The darkness loomed ahead, as if consuming our light. Only tiny glints of reflection shone in the distance. We advanced, peering into the doorways we passed to reveal desolate rooms that had long ago fallen into decay. Lights hung askew, cables fell draped across furniture, and stagnant water pooled in corners.

\leavevmode\llap{“}No power here, either,” Starlight noted. “I don’t hear the sound of machinery or electronics anywhere. The turrets must be on independent power.”

Still no power. That wasn’t good.

When we reached a corner, Dusty held out a hoof to stop us. “Looks like a turret around the corner, unless it’s on a different level. Starlight, use that mirror to check.”

She did as he asked, floating the mirror and a flashlight out past the corner, then turning the mirror to search the neighboring hall. “Um… there! Found it. Another ceiling gun.”

\leavevmode\llap{“}Good,” Dusty said. “This might be a little tricky, but…”

He trailed off; Starlight was already floating her Lancer up to the corner, poking it around as she lined it up with the mirror.

\leavevmode\llap{“}...I guess you’ve done this already,” Dusty concluded.

\leavevmode\llap{“}Yeah,” Starlight said, squinting as she tried to aim the weapon with the tiny view the mirror offered. “The hazards of scavenging old-world sites. Hidden turrets, psychotic robots, and whatever else moved in. Turrets were nasty, since they can be so hard to find.” Her Lancer discharged, filling the hall with a flash of red.

Starlight drew her Lancer back, smiling. “On the plus side, they’re dumb as hell.”

We passed a few more rooms, including a kitchen and a cafeteria. All the equipment was where it had been left two hundred years ago. At the next corner, we paused while Starlight repeated her mirror-trick. This time, the shot was followed by sudden screeching and fluttering, and I cringed back as several bats flew by, scattering from the loud noise and flash. Pips swung and darted on my E.F.S. as the creatures passed us.

\leavevmode\llap{“}Must be an opening somewhere,” Starlight noted. “Probably something small, some burrowing critter or the like. That’s… not a good sign.”

A minute later, a cluster of non-hostile E.F.S. contacts turned red, accompanied by a skittering sound. We halted instantly, ready for a fight. I almost laughed when the radroaches started scurrying out of the nearby doorway and toward us. Starlight calmly vaporized several with her Repeater before Sickle shoved her way past, smashing the rest under her spiked hooves.

Most of the non-hostile contacts ended up being rats, who simply avoided us as we swept through the area. A few were turrets, only showing as hostile to my companions.

We made our way through the underground facility, quickly looking over rooms as we passed. The food stored near the kitchen had long ago been destroyed or consumed by the wildlife that had broken into the place. Labs contained equipment, and while most had been destroyed due to time, moisture, or the attention of animals, there was still a good amount that looked like it would still work. Such devices might have once cost a small fortune. Now, most of them were good for little more than scrap.

One room held the maneframe for the facility. More radroaches had made their home in the midst of its arcane circuitry. Once they had been crushed under hoof, I examined the devices. The damage was extensive: gnawed wiring, missing gems, destroyed and eroded connections. The data-storage arrays were filled with droppings and corroded wires, utterly ruined. Even if we had restored power, or had pulled the arrays from the maneframe, I couldn’t have recovered the data. I could get something out of damaged or degraded information, but I lacked the tools and skill to extract that information from such catastrophically damaged hardware.

We kept searching. Starlight scoured devices to find more spark batteries, finding a fair number. A small medical station had once been well-stocked, but only a couple of healing potions had survived the animals’ intrusion. Ministry of Peace medical boxes turned up another four, protected in the metal shells, along with several bandages, both magical and non, painkillers, splints, and other simple first-aid supplies.

I was following Starlight as she stepped up to another doorway, only to halt, her ears drooping. My heart fell as she glanced back to me, her expression full of concern and sadness.

I swallowed and stepped forward as she stepped back, looking through the doorway with my flashlight held high.

The room was one of the larger labs, and was in complete disarray. Equipment had been moved around, with much of it crammed in the back corner of the room. The tables had been shoved to the walls, and wiring and medical gear was strewn across them. Cables dangled from the ceiling, and hanging from those were ragged, organic strips, translucent in the light of my flashlight. I knew immediately what they were: the remains of changeling cocoons, the same sort of altered chrysalis that I had woken up in all those weeks back.

I cautiously stepped forward. The floor of the lab was covered in an inch of murky water, with cables running through it to the various pieces of equipment. Closer still, and I could see the few wires that were still caught up in the remains of the cocoons. My flashlight tilted downward, to cast its light across the jumble of thin exoskeletal plates that lay below. They were all dead.

I stared at the remains. The rational part of my mind noted that the exoskeletons were disassembled. They’d likely been eaten by the vermin that had broken into the place, their parts scattered. My light swept around, finding more remains in similar states, roughly corresponding to the tattered ribbons of destroyed cocoons.

I trudged out of the room, slumping to sit against one of the walls of the hallway. I just needed a moment to sit, absorb the information, and sort out my thoughts. My throat felt tight, but my mind was relatively calm. At least part of that was the lack of surprise; between the facility being powered down and the animal infestation, I had already recognized that the chances of anyling surviving was virtually nonexistent. It was still painful, finding another group of my sisters, long deceased.

Still, despite the rational logic behind it, I worried that I was feeling too \textit{little}. That, rather than being rational and healthy, I was simply becoming numb. That finding another dozen or so dead changelings had lost its significance after the hundreds of dead changelings I had come across before.

And then I started worrying that having such concerns suggested self-doubt and other failures at coping, followed by a somewhat cynical recognition that my own practical psychological knowledge was possibly creating a feedback loop of concerns, like an inverted and self-destructive rationalization. Essentially, that I was descending into the mindset that anything that could be wrong absolutely was, and that delving so deeply into those concerns was a sign that I wasn’t thinking as clearly and calmly as I should.

It was all muddled and confused thoughts, circular reasoning, and irrational concerns. I focused on setting them aside, trying to think calmly and clearly.

The moment of clarity came when Starlight’s hoof settled gently on my shoulder. I looked up, blinking the blurriness from my eyes to meet her gaze, her expression both concerned and comforting. I swallowed past the lump in my throat, focusing on her.

She opened her mouth and paused for a moment, likely trying to work out how to gently ask a potentially uncomfortable question. “...Should we gather them?”

\leavevmode\llap{“}Yes,” I said, my voice weaker than I had expected. With that, I had a direction. I recognized that as a coping mechanism even as I used it to sideline the other concerns, but that was fine. Coping mechanisms can be useful things if done right, and one that helped me focus on what needed to be done instead of pointless self-doubt was quite useful. “Thank you.”

It was a slow and unpleasant affair, gathering the disjointed remains from the muck-covered floor. Parts of shells had been scattered around the room, and had to be fished out from beneath tables or behind equipment. It took about half an hour, full of painful moments, but it was progress.

We moved the remains into a neighboring lab with a dry floor. Soon, we had yet another funeral pyre going. Starlight quietly checked that we had the respirators and air bottles we had scavenged from my hive. I’m sure she was trying to be subtle about it, during a sensitive time, but I appreciated the concern and attention to detail.

The magical flames burned hot, swiftly reducing the remains to a fine ash.

Dusty stood quietly at my side, watching. “Sorry about this.”

\leavevmode\llap{“}It’s—” I caught myself; I’d almost said ‘okay’, one of those reflexive platitudes that was so expected in casual conversation. I shook my head as I rephrased. “It’s not unexpected.”

He nodded, silent.

\leavevmode\llap{“}There’s still another experimental facility,” I said, quietly. “And even if that’s no better, there are other C.L.T. facilities.”

He gave a quiet grunt, as if he wanted to point out how much the last statement sounded like grasping at straws. I couldn’t argue with him on that. It absolutely was. Even as I said it, I was already thinking of what was coming. The chance that the final experimental facility held any still-living members of my hive was minimal. The chance that some other C.L.T. facility held any was essentially nonexistent. Pinning my hopes to that was merely setting myself up for disappointment.

I had to recognize that the odds were increasingly on the side of me being the only member of my hive to have survived, and that I had to start planning what I would do next. That was troubled by the knowledge that Queen Chrysalis (the sixth) was leading her hive on some form of offensive, whether covert or overt, and I was likely to be caught up in that one way or the other.

Very few options presented themselves. Two, in fact.

The first was simple: run. Serenity’s influence would be limited, likely not extending beyond the local region. I could leave, flee to some other place in Equestria or beyond, and try to live out the rest of my life as best I could.

The other was to fight back. Face the threat Serenity posed to the ponies of the region, and work to combat that. Counter-Infiltration, armed intervention, or even the simple disclosure of information. It would be a difficult struggle, a fight against a force that could easily become dominant in the Wasteland, where I would be exposing myself to a great deal of danger. There were a great number of ponies, and others, who were at risk, and there was a chance I might make a difference.

The safe option was to run.

But being an Infiltrator was never about taking the safe option. It was about taking a measured risk for the sake of others. It was about putting my own life on the line to accomplish something important, something that would benefit so many other lives.

Fighting back, helping ponies, that was something that would give me a purpose. Something to live for beyond myself.

Those were the thoughts that ran through my head as we checked over the rest of the facility. Dusty had offered to leave right then, but while I appreciated the gesture, I refused. We could use whatever salvage Starlight found, and she did turn up a fair amount, gathering a large collection of spark batteries and some of the more valuable parts from some of the ruined scientific equipment.

Between that distraction and the number of contacts already showing on the E.F.S., none of us noticed the addition of one more.

It took perhaps half an hour to scour the rest of the facility, pausing at intersections to allow Starlight to destroy turrets from around the corner. She also spent some time looking over the spark generators, in case anything could be salvaged and used with our motorwagon, but she shook her head. The few that hadn’t failed catastrophically and burned out were corroded from decades of moisture.

We made our way back to the entrance, the door that had originally been sealed. Once we were on the other side, Starlight called out clearly. “Cover your ears.”

We did so, and she jabbed inside the mechanism with her prybar. The gears whined as they spun free, and the door dropped to the ground with a heavy thud that reverberated right through our hooves.

With the facility sealed once more, we turned to leave, returning to the main chamber. From there, we started to pick our way through the debris, starkly lit in our lights and silhouetted against the darkness beyond.

As we progressed through the cluttered room, none of us noticed that one of the lumps hadn’t been there before, until it rose up, giant wings spreading to block out the light of the ramp.

I lurched, heart hammering in surprise, and grabbed for my gun.

There was a dazzling purple flash, and my teeth closed on thin air.

My head snapped up again, immediately spotting where my rifle floated in midair, wrapped in the purple glow of magic. My pistol was right beside it, as well as all of Dusty and Starlight’s weapons and all of our grenades.

Between us and our weapons, a matching glow surrounded a long horn, illuminating the alicorn who stood imperiously before us.