The ways that fear influences an individual is a complex subject.

The common adage describes the reaction as “fight or flight”, but I consider that to be overly simplistic. In both cases, the individual is still taking an action. Fear can, after all, be a great motivator, although it’s equally capable of motivating one into making bad decisions as it is to make good ones. For example, fear might convince a pony that their only chance of survival was to charge the powerful and terrifying alicorn standing before us, with all of our stolen weapons arrayed behind her.

I find a spectrum of action-to-inaction to be a better way of classifying the reactions to fear. When an individual chooses fight or flight, it’s typically because the action was one that immediately presented itself as the solution to their problem, and they took it, possibly without fully considering the actual merits of that action. When no good options present themselves, or too many compete all at once, individuals tend toward the other side of the spectrum: inaction. They freeze up, question themselves, and fail to take any decisive action to save themselves.

Neither extreme is a good response to fear, and both can be thoroughly deadly. Given an option of the two, however, I felt some measure of relief that our group fell more into the “inaction” side of the spectrum.

Except for Sickle, who I don’t think was actually afraid. If anything, I think she was amused by this development.

The alicorn wasn’t attacking. She stood tall, her wings spread in an upright fan that I had always associated with the princesses and other royalty, as if making themselves seem larger than they were. Her head was held high, with her muzzle tilted slightly upwards, and her eyes hard as she stared back at us.

Given the lack of attack, I took just a moment to quickly appraise our options. That was a fairly simple appraisal, given how limited our options were. We couldn’t flee, as even if we hadn’t sealed the door behind us, that would still leave us with the alicorn between us and freedom. Not that I expected we’d even make it to the door, if she decided to stop us. Fighting struck me as exceedingly long odds, between our lack of weapons and how swiftly I had seen her casually \textit{disassemble} a pony.

It was a strange situation, being uneasy with the conclusion that talking was the best option.

Dusty evidently came to the same decision I had, but was quicker to act upon it. He was also rather more indelicate than I would have chosen to be. “What do you want?”

The alicorn’s head turned to fix him with a stare, her head tilted ever so slightly. There was a long second of tension before she spoke. Her voice was strong but elegant, her enunciation precise. “Understanding.”

As vaguely creepy single-word non-answers went, that was certainly up there.

While I was thinking that, Dusty spoke again. “What’s that got to do with us? Why have you been following us?”

\leavevmode\llap{“}Because you are intriguing,” she replied, before taking a few slow, casual steps, her movements precise and elegant. Regal. She stepped smoothly across the debris-strewn ground, without having to look where she placed her hooves. Instead, her eyes turned to me. Something about the intensity of her stare struck me as a predator hungrily eying its prey. “Especially the insect.”

My ear gave the tiniest twitch, and I took a half-step back. I don’t like to be “intriguing” to dangerous individuals. Surprisingly, her expression immediately changed. Her head tilted slightly once more, her expression softening into something more contemplative.

She hummed softly, almost absently, before speaking. “So there is a difference in implication between ‘bug’ and ‘insect’. Interesting.”

That wasn’t the direction I had expected the conversation to take, and while I couldn’t say that ‘thoughtful and inquisitive pony-disassembling alicorn’ was unthreatening, it was at least less so than ‘regal and imperious pony-disassembling alicorn’.

\leavevmode\llap{“}...It’s mostly about correlation with their common use,” I said, my voice coming out in a low creak. I cleared my throat and, as she had yet to reply, continued. “They both carry diminutive connotations, but ‘insect’ is almost always used in a condescending manner. ‘Bug’ is more varied in its use.”

She had looked away, staring off into space as she gave a tiny nod. She seemed lost in thought. “Hmm. I see. Yes, that makes sense…”

I was tempted to allow the silence to continue as long as she would allow it, but I couldn’t see how that would do anything but delay whatever was coming. At least if I spoke up, I might be able to guide the conversation.

Unfortunately, I only saw one easy way to steer the conversation, and it was a concerning topic. At the same time, it was also a topic of conversation that I was, for better or worse, very curious about. “You find me intriguing?”

She blinked once, her attention snapping back to the here-and-now, her eyes returning to me with their previous intensity. “Part of that interest lies in your uniqueness. Changelings are a rarity in the Wasteland. Prior to coming across you, we remember only two other changelings.

My ears perked up at that, and not only for the change of pronouns. Perhaps it was optimism, or perhaps it was just reading too much into a simple statement, but I had the feeling she wasn’t speaking of Serenity. “You know of other changelings?”

\leavevmode\llap{“}Knew. One was dead, and we assisted in their dissection. The other we worked alongside, and only briefly.”

I swallowed, silently hoping that she had nothing more to learn through dissection. “The one you worked with, where is she?”

\leavevmode\llap{“}Dead, I expect,” the alicorn replied with a dismissive flick of her wings. She started to slowly walk again, circling me as if to get a better view of me. Despite the apparent attention, her expression was haughty almost to the point of boredom. Her mane and tail trailed unnaturally through the air behind her, almost as if it were floating underwater. “It was over two hundred years ago.”

I added ‘ancient’ onto the growing list of troubling descriptive terms for this alicorn. There was the added concern that she would have been my contemporary, yet I had no knowledge of her. It did fit with my earlier impression that the Ministry of Arcane Science had progressed further than I had thought. The possible M.A.S. connection fit unpleasantly well with the whole ‘dissection’ comment, as well.

Cautiously, I asked, “And the other part?”

She frowned, coming to a halt beside me. I stayed still, hoping she couldn’t hear how much my heart-rate had kicked up with that simple expression. “At first, you were simply a curiosity, a single specimen of a species that had been seemingly exterminated. A changeling, near death, feeding on a pony.”

Her eyes flicked Starlight’s way before returning to me. “We know very little of your kind, but it was enough to make you very intriguing. Much of what we remember is nothing more than rumor and speculation.” She paused, her frown returning for a moment before she spoke again. “For example, there was one rumor that your species shared a telepathic hive-mind of some form. Is there any truth to that?”

I blinked, a bit surprised by that, then shook my head. “No.”

Her frown deepened as she looked away. “No. No, of course not. Foolish.” She slowly paced away, wings folding at her side as she muttered quietly. “...Grasping at straws… focus…”

\textit{Great}, I thought. \textit{Now the powerful, terrifying, vaguely creepy }ancient\textit{ alicorn is talking to herself.}

And she was still between us and all our weapons.

\leavevmode\llap{“}So,” Sickle rumbled from behind us, “are we fighting, or am I in for another long and boring talk?”

The alicorn replied almost absentmindedly. “A fight would imply some degree of parity.”

Sickle’s armor rattled as she cocked her head to the side, then turned to look at me.

I translated. “I believe she’s saying that any violence between us would be too one-sided to be accurately described as a fight.”

\leavevmode\llap{“}That is precisely what I intended,” the alicorn said, turning back to face us once more, or more specifically, me. She was in regal mode once more, her head held high. “But we are getting sidetracked. I have yet to fully answer Whisper’s question.”

She stared at me for a couple of seconds, until I cautiously nodded. She gave a prim nod in reply, and spoke. “While we knew very little of your kind, it was enough to catch my interest. I have been seeking an understanding of many things, but you offered an understanding of the most significant. I decided to follow and observe you. I have watched your interactions with ponies, both honest and dishonest, and I have listened in on your conversations and recordings. Those observations led me to two significant conclusions.”

Her head turned, scanning over us. “One: you, as a group, with the possible exception of the former raider, are motivated to help ponies in general.”

Her gaze fixed on me, hard. “And two: you, specifically, know what it is like to be a part of something greater than yourself, only to have that torn away.”

I tensed, though my exoskeleton made that much less obvious than it would have been otherwise. \textit{Oh shit}, I thought. \textit{She sees a connection between the two of us}.

On the plus side, I was pretty sure she was less likely to kill us outright. On the other hoof, that was because she \textit{expected} something from us. From \textit{me}.

\leavevmode\llap{“}...I suppose that would be accurate,” I said, concealing the nervousness I felt over this development.

\leavevmode\llap{“}I have been trying to make sense of things,” she said, her voice softening. “This world is… chaotic. Without direction.” She paused, frowning slight as she thought. After a moment, she spoke again. “You know of my kind.”

It was a statement, not a question. All the same, I nodded. “Very little.”

\leavevmode\llap{“}The radio said you were servants of the Goddess,” Dusty said.

The alicorn went rigid. Her mane and tail flared slightly in the intangible currents. “She was our mother.”

Thankfully, Dusty shut his mouth rather than continuing on that vein.

The alicorn shook her wings out before tucking them neatly against her side once again, and the regal demeanor returned. “We have heard many things said about our mother. Some called her, and her daughters, monsters.” Her eyes fixed on me. “They see only the surface, but not beyond. They clung to their short-sighted fears, and failed to see what we were attempting to accomplish.”

I slowly, cautiously nodded. “I can appreciate how appearances and first impressions can be misleading,” I offered. “What was it that you were hoping to accomplish?”

\leavevmode\llap{“}It \textit{should} be perfectly obvious,” the alicorn said, staring down her muzzle at me. “We sought to \textit{help} ponies.”

Somehow, I didn’t find that statement terribly reassuring. “I’m afraid I know very little about you,” I said. “How did you seek to help ponies?”

Her wings spread abruptly, her mane flowing behind her. “By making them like \textit{us},” she said, her voice filling the space with her declaration. “Perfect, immortal beings, combining the strengths of every tribe. Untouched by age, disease, and radiation. We would have elevated ponies above their meager life of scavenging. We would have turned this wasteland into a paradise, and brought forth a new society that could thrive and prosper.”

She folder her wings again, her expression hard. “And for that, one of the ponies we would have saved murdered our mother.”

\leavevmode\llap{“}I’m sorry for your loss,” I said, hoping it wouldn’t be taken poorly.

\leavevmode\llap{“}Hmmph.” She looked away, her expression still hard. After a few tense moments, it started to relax. “I would say you have no idea what I have lost, but I suspect you’re one of the few beings in the Wasteland who might be capable of conceiving it.” She sighed, staring off into space. “We had everything. My sisters, our mother, our purpose. We were one. Our thoughts were legion. They were always there, in Unity. Now?” She slowly shook her head. “Now there is only silence. I can no longer hear them.”

I’ll admit, that was a little creepy. Not so much for the suggestion that she had been hearing voices, as I could assume from that statement and her earlier question that there must have been some form of telepathy involved. More concerning to me was what might have happened to the mental state of an extremely powerful individual who was suddenly deprived of that.

How would I have responded if my own sisters had been a constant presence in my own mind, like a conversation always going on in the background, only to wake and be met with crushing silence? If I was reading her earlier inquiry about a telepathic hive-mind correctly, it suggested significant reason to be concerned.

She shook her head again, as if clearing her thoughts, and I thought I heard her murmur something to herself before speaking again. “That pony may have destroyed our best chance at a better world, but I am still a daughter of the great and powerful Goddess, and some of that greatness lives on in me. I will find a way to use that power in honor of her memory, to accomplish that which she died for.” Her eyes locked onto mine. “And you will help me do this.”

Sickle gave a quiet snort of amusement, and out of the corner of my eye, I caught Dusty’s glance toward where our weapons floated.

Myself, I tried to remain steady under her gaze. “How are you expecting us to help you?”

She turned, slowly pacing with precise, graceful steps. “I have been thinking of how to carry on our mother’s work ever since she was cruelly murdered. The means of our ascension were destroyed by that short-sighted pony, which left me uncertain of how to proceed. But then, I came across \textit{you}.”

She paused, looking my way for a moment before returning to her pacing. “A changeling, with the magic of transformation and a keen knowledge of what it is to be a part of something greater than themselves. A creature that could help resurrect our plans for Unity.”

\leavevmode\llap{“}Changelings can’t change others,” I said.

\leavevmode\llap{“}Of course not,” she said with a dismissive flick of her ethereal mane. “But your kind’s transformative magic is more advanced than any unicorn’s. We remember much of the study and creation of magic, and we remember its unlimited potential. We remember many experiments, delving into magics once thought impossible. I will dissect your magic, figure out exactly how it works and how to replicate it, and with that, we will finally have a means to raise ponies above this downtrodden life.”

Starlight spoke suddenly. “You’re not \textit{dissecting} her!”

The alicorn halted, shooting her an annoyed look. “It’s a metaphorical dissection, and in any case, the subject of the statement was her magic, not her. I probably won’t need to do any invasive physical examination to understand her magic.”

\leavevmode\llap{“}Probably,” Starlight echoed, clearly no more relieved than I was.

\leavevmode\llap{“}If all you want to do is study my magic, then—”

\leavevmode\llap{“}It’s hardly the \textit{only} thing I want to do,” the alicorn said. “But it will suffice to start with.”

\leavevmode\llap{“}...Okay. If all you want to do \textit{right now} is study my magic, then I think we can accommodate you. We’re in the middle of going somewhere, though, so you’ll have to do so while we travel, and of course we’ll need our equip—”

\leavevmode\llap{“}No,” she said, shaking her head. “Studying on the move is too awkward and unproductive.”

I swallowed, hoping this wasn’t going where I thought it was going. “Then I’m afraid you’ll have to wait for us to finish our own tasks.”

\leavevmode\llap{“}No,” she said again. “I am working to save all ponies. That is more important than your tasks. We will stay here.”

Yes, it was going where I thought it was. “You said you’re immortal. I’m sure you can afford to wait a few days or weeks until we’ve taken care of what we need to do.”

\leavevmode\llap{“}And how many ponies will die while you pointlessly delay their salvation for your fruitless search? What if you die? It would be almost impossible to find another changeling that cares for ponies enough to help. No, this is more important.”

\leavevmode\llap{“}So, what, fuck changelings?” Starlight abruptly said, her voice sharp with anger. “Whisper’s trying to save her kind, too, you know!”

\leavevmode\llap{“}I have yet to decide about changelings,” the alicorn said with a shuffle of her wings that seemed to approximate shrugging. “On the one hoof, they are undeniably versatile creatures, and I might even describe them as more fit for survival if not for the crippling emotional dependency. I would consider incorporating some of their capabilities into our ascension, if possible. On the other hoof, changelings are a parasite that feeds on ponies, and from what I have observed, are currently one of the greatest threats in the Wasteland. If allowed to continue, they are likely to become the single most significant obstacle to our Unity. I am left undecided as to whether they should be integrated or destroyed.”

Starlight stared, wide-eyed and open-mouthed, as this alicorn casually contemplated the genocide of my entire species.

Metal rattled as Sickle plodded forward. The alicorn turned to face her, a wary glare flashing before settling into an imperious display of condescending indifference. She stood tall, looking almost bored as she stared down her muzzle at the armored mare.

Sickle halted just a couple feet away, staring right back into the alicorn’s eyes. It’s easy to forget just how big Sickle is, having gotten used to her being around, so it was a bit surprising to realize she stood eye-to-eye with the alicorn. With her bulk for comparison, Sickle managed to make the alicorn look small, if only just.

Sickle just stood there, staring at the alicorn, her expression unreadable under her helm.

After a couple of seconds, the alicorn gave a derisive snort. “I do hope you’re not attempting to intimidate me.”

\leavevmode\llap{“}Nah,” Sickle said. “Just thinkin’.” She went silent for a moment before continuing. “Yeah. I wouldn’t normally do this, but I’m wondering. Your mom. You anything like her?”

The alicorn’s head rose just a hair higher. “I would like to believe so.”

\leavevmode\llap{“}Yeah, I thought so,” Sickle said. A touch of a smile crossed her lips, half-hidden behind the bars of her muzzle. “I think I see why that pony killed her.”

The alicorn’s eyes widened, much as I’m sure everyone else’s did. Then she bared her teeth in a snarl. Purple magic flared, throwing Sickle into the wall with a tremendous crash of metal. “You \textit{dare!}”

To my side, Dusty twitched, almost launching into action, but the alicorn still stood between us and our weapons.

I hurried forward, hoping to do what I could; if we couldn’t fight and couldn’t flee, then words were the only way we were getting out of this intact. “Wait! Please!”

Her glare turned to me, and I nearly staggered back under the withering look she gave me. “Just… please listen. I’m sure you’ve noticed Sickle can be a bit blunt, but I think she actually had a good point.”

\leavevmode\llap{“}Of course I had a good fucking point!” Sickle called out. She didn’t even sound angry, despite being pinned to the wall in a field of purple magic. Well, no more angry than usual.

The alicorn kept Sickle pinned in place, but her attention remained on me. “And exactly what point would that be, \textit{insect}?”

I knew I was taking a gamble pressing this, but what option did I have? I took a steadying breath, and began. “Your approach needs a lot of work.”

She blinked. I could only imagine Starlight sharing a similar reaction behind me. That was perfectly fine with me; surprise and confusion was much preferable to righteous anger. I continued. “We said we were willing to help, but instead of accepting what help we were willing to offer, you’re pushing for more, until we aren’t—”

Her head drew back in surprise. “You do not \textit{want} to help?”

\leavevmode\llap{“}I do,” I said, firmly. “But with your approach, you seem determined to turn potential allies into actual enemies. We have things we need to accomplish, things that are important to us, but rather than work in a way that helps all of us achieve our goals, you were insisting on only solving your own goals while hindering ours. If that’s how you’re planning on approaching your Unity, then there are going to be many who don’t like that. They’ll fight you, and if they can kill a goddess, I’m sure they can kill one of her children. You’re putting your own goal at risk by approaching it this way.”

Her expression turned distant, her head tilting again. She murmured quietly to herself. “Logical. Fits the data. Possible problem. I don’t…” She blinked and shook her head again, and with another crash of metal, Sickle fell to the floor.

She laughed as she picked herself up. “What, tired already?”

\leavevmode\llap{“}Goddesses’ sake,” Dusty muttered. “Are you \textit{trying} to get yourself killed?”

\leavevmode\llap{“}I ain’t scared of her.”

\leavevmode\llap{“}You’re too dumb to be scared.”

Starlight thumped a hoof against Dusty’s shoulder. “Guys, seriously, could you \textit{not} do this right now?”

I watched Sickle as she stood, rolling a shoulder as if stretching, but she didn’t seem any worse for wear after the alicorn’s treatment. In fact, she was smiling.

The alicorn was looking at me again. “I do not appreciate the implication that my mother’s death was her own fault.”

\leavevmode\llap{“}I wasn’t commenting on whether it was right or wrong,” I said. It was a nicely diplomatic answer, I thought. “I merely intend to show why others might act as that pony did.”

\leavevmode\llap{“}Hmm.” She frowned, but after a moment, slowly nodded. “You are more experienced in dealing with ponies than I am. That is one of the topics I seek understanding of. You will help me with this.”

\leavevmode\llap{“}Okay. First lesson: ask me to help you.”

She blinked. “Did I not just do so?”

\leavevmode\llap{“}You did not,” I said. “You \textit{told} me to help you. It’s an important distinction.”

\leavevmode\llap{“}Hmmph.” She stared at me for a second before speaking again. “Fine. \textit{Will} you help me?”

\leavevmode\llap{“}I already am.” I stepped up, as if to take charge of the conversation, while trying to ignore the huge size difference. “There are many different ways of convincing someone to help you. So far, you’ve been using demands and the unspoken threat of your intimidating nature, but that’s one of the poorest long-term options. They might help you, but they’re not motivated to do so. They’re motivated to protect themselves, and the moment they find a better option to do so, they’ll take it, whether it’s abandoning your work or turning on you.”

It was my turn to start pacing as I spoke, and despite the alicorn’s imposing nature, I noticed that she watched intently, almost like a student listening to her teacher, if that student were twice as tall and significantly more powerful. “Furthermore, it’s going to be complicated by the moral judgement of your actions. Forcing others to work for you looks like extortion at best, and slavery at worst. Many will have strong feelings on that. There are many who might be amicable to your goals, but who strongly and even violently oppose you for your methods.

\leavevmode\llap{“}And if that isn’t reason enough, seeing such things will lead people to question your motives. You made some impressive claims, ones which will be hard for people to believe. If they see you taking unscrupulous means to accomplish those claims, it’s going to make others doubt your honesty. If all they see is you using the threat of force to get others to do as you wish, with unverified claims of noble goals and benefits for them, it’s going to be hard to believe you.”

The alicorn’s brow creased. “Are you saying you do not believe me?”

\leavevmode\llap{“}To be honest, I do have some reason for skepticism,” I said. “I don’t \textit{disbelieve} you, but your forceful demands and complete lack of compromise or negotiation suggests a disregard for the concerns of others. That’s enough to make some question whether your concept of an ideal world will really be what \textit{they} consider an ideal world, and that’s especially true when you’re willing to even \textit{consider} the genocide of \textit{my entire species}.”

I ended with a pointed look at her.

\leavevmode\llap{“}I did say there were good arguments against it,” she said, though her ears flicked back as she did so.

\leavevmode\llap{“}A willingness to exterminate innocents does not speak well of your ideal future,” I said, my eyes holding firmly to hers. I could hear my heart pounding in my ears, but I stood steadily.

Her ears had pinned back, and she held my stare for a few long, uncomfortable seconds before her gaze wavered ever so slightly. “I… can see how a non-pony might find that disconcerting.”

Dusty snorted. “Yeah, plenty of ponies, too.”

\leavevmode\llap{“}Hell yeah,” Starlight said. A glance their way showed me that she was glaring daggers at the alicorn.

\leavevmode\llap{“}I see,” the alicorn said, frowning. After a moment, she nodded. “Very well. I shall avoid mentioning such things again.”

\leavevmode\llap{“}No,” I said, meeting her eyes once more. “You’ll need to do more than that. Whatever your ideal future is, genocide needs to have no place in it.”

\leavevmode\llap{“}I can understand why you would have personal feelings on the matter,” the alicorn said, “but I am working to create a better world for as many as—”

\leavevmode\llap{“}\textit{No},” I said, more firmly. “Any future that necessitates the genocide of innocents is insufficiently good. It would still be causing death and suffering, you’re just moving it around. We can do better than that. If you really want to make the world a better place, then we \textit{have} to do better than that.”

Another long moment of contemplation. “That does sound good in theory,” she said, although her voice was cautious, “but I am concerned with the difficulty of taking such a course.”

\leavevmode\llap{“}You said you wanted to honor your mother. Do you really think taking the easy way out would be the best way to do that? Or do you perhaps think that striving for something better, regardless of the difficulty, would honor her more?”

She looked to the ground in thought, silent and frowning, with only her eerie mane and tail slowly drifting in the still air. I remained still as well, tense as I awaited her answer.

Finally, she spoke. “You are very clever and talented at manipulating others, changeling.” Her eyes looked up to me, my heart pounding a little harder at the intensity of her look. “All the more so for how logical your arguments are. Yes, I would prefer the best possible outcome. I am concerned with the practicality of achieving such a goal, but… if you have any ideas, I would be willing to listen.”

I huffed out a quiet sigh of relief. I felt that the hard part was passed, and now I was on to the much simpler matter of working out a convincing plan to save the world, and maybe convincing her that genocide was wrong.

Somehow, this was an improvement.

\leavevmode\llap{“}Okay. Good. The basic plan is pretty simple. Actually, it’s pretty much exactly what we’ve been doing this whole time. The short version is, we go out and help others. Stop raiders that are hurting others, help people get what they need to survive and prosper, that sort of thing. Make the world better for them. Go from there.”

\leavevmode\llap{“}That sounds like such a petty effort,” the alicorn said, though her tone didn’t carry the scorn I might have expected of the statement. “I intend to improve life for \textit{all} ponies, not just a few dozen.”

I held up a hoof. “Okay, first off: all \textit{people}. Not just ponies. Zebras, griffons, donkeys, and yes, even changelings. They’re all worth saving.”

She slowly nodded. “I suppose that is a worthy goal, if it is possible.”

\leavevmode\llap{“}It certainly is,” I said. “Second, this isn’t about solving the world’s problems in one fell swoop. It’s about setting things up so that’s even possible. It’s like building a house. You need a good foundation to build on.”

\leavevmode\llap{“}That’s a simplistic metaphor.”

\leavevmode\llap{“}That’s what metaphors are for,” I said. “But the reasoning is solid. Try this: imagine that you were an ordinary pony.”

Her frown deepened. “Hmmph.”

\leavevmode\llap{“}Now imagine how that ordinary pony might react to somepony like you. Don’t think about what you know, think about what they see. Imagine they see you, using threats to force others to follow your orders, maybe even following through on those threats if they continue to refuse. Then instead imagine if their experience of you is seeing you save ponies from raiders, leading them to safety, maybe even giving up a generous share of your own food and supplies so they can get back on their hooves. Which one do you think is going to motivate people more to help you?”

\leavevmode\llap{“}It seems to me that both would be very well motivated to assist me,” she said. Then her ears flicked back. “But yes, I believe I understand what you are attempting to say. We… we remember our first reactions to alicorns. To our Unity. There was much fear there, so many ponies who didn’t understand what was happening. If only there had been some way for us to understand how wonderful that change would be.” She stared off into space, her voice quieting. “We remember using time-altering magics. If only I understood how they worked…”

The thought of time-manipulation sounded like trouble on a colossal scale, not the least of which for the very tempting possibilities that immediately leaped to mind. “I’m guessing these changes you’re speaking of were not voluntary.”

She was frowning, still looking away. “No, they were not.”

\leavevmode\llap{“}But if ponies saw alicorns as benevolent and helpful, and had the opportunity to see what benefits come with it, perhaps it could have been.”

\leavevmode\llap{“}Yes, I was paying attention to what you had said,” the alicorn said with a flicker of a glare, though she looked away again just as quickly. “And… yes, I can see the benefits that would bring. It would certainly be slower, but…”

\leavevmode\llap{“}But is less likely to have people actively opposing you,” I said.

\leavevmode\llap{“}Yes,” she said, a smile touching her lips. She was regaining that regal stance once more. “And more likely to understand that I am saving them.”

\leavevmode\llap{“}Which leads us to another question,” I said, taking a step forward to take charge again. “How will you respond if someone decides they don’t want to be like you?”

She scoffed, but followed it with a grin. “They will see the benefits offered to them, and with this plan, they will have no reason to fear it. They will not refuse the opportunity.”

I shook my head. “I can tell you now, if you’re expecting ponies, or anyone else, to be of a unanimous mind on something, you’re only setting yourself up for disappointment. I can assure you, there will be those who see what you’re offering, understand it fully, but still not want to take part in it. I want to know how you would respond to them.”

She simply waved a hoof. “Nonsense. Who would turn down such a gift when they aren’t blinded by petty fears?”

\leavevmode\llap{“}I mean no offense,” I said, “but I would.” Her head snapped back as if I had struck her, and I quickly continued. “I’m no stranger to change, but I’d rather stay what I already am than become an alicorn. If you’re truly immune to the effects of radiation, disease, and aging, I might want to see if I could incorporate such alterations through my own shapeshifting, but it wouldn’t be the sort of change you seem to have in mind.”

She stared wide-eyed at me for another moment before blinking, then shaking her head. “No, well, that is hardly surprising. You are a changeling, you can achieve such a change on your own without my interference. Ponies do not have that option. They will gladly accept this gift.”

I could have glanced back at the rest of my group, hoping for backup. I expected that, of the three of them, at least one would be willing to decline. Despite how helpful it would be, I didn’t want to put them on the spot like that.

Fortunately, I didn’t have to. In the moment of silence that followed her statement, Dusty spoke up. “Uh, yeah, I think I’ll pass, thanks.”

The alicorn’s head snapped around, eyes wide, her reply sharp with surprise. “\textit{What?}”

\leavevmode\llap{“}Hell, it’s a nice offer and all,” he said with a shrug. “I kind of like myself how I am, thanks.”

The alicorn’s ears had fallen, her expression sagging like a little filly that had just seen their ice cream fall into the dirt. “But… you…”

Dusty quickly held up a hoof. “Hey, it’s okay, I get it. Ain’t like I couldn’t find a lot of benefits to magic and flight, but I’m fine without. Who knows, maybe when I get older I might change my mind, but for now… yeah, I’ll pass.”

\leavevmode\llap{“}Same here,” Starlight said. “Flying was fun, but… no. Plus, uh… well, I’d rather not be quite that big. Sorry.”

Then they both glanced to Sickle.

Sickle wore one of the most delighted grins I’d ever seen on her. “You want to give me wings and magic? Are you fucking stupid?”

I quickly stepped in before anyone could answer that question. “I’m sure there will be those who would gladly take what you’re offering, but there will be others who do not. They’ll still need our help, too.”

\leavevmode\llap{“}But…” Her gaze wavered, her stance off-balance, as if her whole world was crumbling around her. “If they will not accept my gift, and you claim I should not force them to accept it, then…”

I stepped up, unnoticed in her apparent existential crisis. I was close now, my horn level with her neck. So many options presented themselves.

I raised a hoof, gently touching it to her chest. I offered a small, comforting smile. “Then you give your gift to those who do accept it, and find another way to help those who decline.”

She absently brushed my hoof away, seemingly before realizing I had stepped in close. Her gaze focused on me, her confusion clear in her expression. “But how?”

\leavevmode\llap{“}You’ve been watching us. You’ve seen us help ponies, and others as well. None of us are an immortal alicorn. You could do a lot of good simply by spreading Generosity and Kindness.”

Her ears flicked back. “Magic. Laughter. Loyalty. Honesty.” Her expression went abruptly still. “We remember these.”

\leavevmode\llap{“}They’re all things that the world could use much more of,” I said.

She remained still and silent for several long, tense seconds. I considered saying more, nudging her in the right direction, but I expect that wouldn’t have worked any more than the reassuring touch had.

Slowly, her stance straightened once more, her head rising and her expression setting, looking bold and confident as she declared in a firm, clear voice, “I have come to a decision.”

A little melodramatic, I thought, but I certainly wasn’t going to say so to her. “And that is?”

\leavevmode\llap{“}I will accompany you,” she declared. “I will study your magic for any way to implement my plan, while assisting you with yours, until I have gathered enough data to make an informed decision as to which course is best for all—” I caught the momentary hitch as she changed words. “—people.”

Once she had finished, a flicker of a frown broke the confident image she was projecting. Her eyes darted towards me. “Would that be acceptable?”

I looked back. Starlight looked tense, but gave no reply. Sickle looked like she didn’t care about anything we were talking about. Dusty merely looked back with a level look, and gave a tiny shrug.

I turned back. “I suppose that could be acceptable, yes. That is, assuming that talk of genocide is no longer in consideration.”

\leavevmode\llap{“}I believe the data will speak for itself,” she said, the frown vanishing. “I will not refuse a course of action without giving it due consideration, but you have already provided good arguments against it. Unless I make some discovery that directly contradicts that, I expect it will prove to be an unnecessary or even inappropriate action.”

Progress, I suppose. “I guess that will have to do.” I drew in a deep breath and sighed. “Very well. If you wish to accompany us, we can do so, though there will have to be some conditions.”

A hint of a frown appeared. “Conditions?”

\leavevmode\llap{“}Yes. The main condition is that, while you’re traveling with us, if we tell you to not do something, then you can’t do that.”

The frown deepened. “If your decision is well-reasoned, then you hardly need such a rule. If it is \textit{not} well-reasoned, then I should hardly be expected to obey it.”

\leavevmode\llap{“}You seem to be reasonably logical and have listened to my arguments with an open mind, which is why I’m willing to consider this arrangement. You’re wanting to travel with us, and that means whatever you do, you’ll have done with our assistance, however small. That means we’re at least partially responsible for what you do. If you’re asking us to take on this responsibility, then you will have to make some concession to that fact.”

Her head tilted slightly. “Even if you consider yourself responsible for any action I undertake while in your company, do you truly believe I would do something objectionable?”

I couldn’t help giving her a flat, ‘are you serious?’ sort of look. “You’re open to the idea of exterminating an entire species of intelligent beings. That does raise certain concerns about what else you might be willing to do.”

She scoffed, waving a hoof dismissively. “We have already discussed that. I think your personal stake in the matter is clouding your objectivity.”

Dusty gave a sharp, humorless laugh before I could even reply. “Shit, lady, I thought you’d been watching us. If you think Whisper’s not happy with it because she’s a changeling, you weren’t watching very close. That changeling isn’t the only one who doesn’t like all this talk of mass murder, but she’s the one that’s actually giving you a chance.”

\textit{Thank you, Dusty}. I nodded in agreement. “And I’m not saying you have to do exactly what we tell you to do, forever. It’s just while you’re traveling with us. If you find the arrangement too constraining, then you’re welcome to part ways with us, though personally, I hope you’ll find enough value in what we do to stay.” \textit{You’re less likely to go off and do something terrible that way}. “I think we have a lot we could learn from each other.”

She hummed softly. “Mmm. Yes, I believe we could.” She considered it for another moment before giving a sharp nod. “Very well. If it will ease your mind, I shall agree to take no action that you explicitly forbid so long as I remain in your company.”

I could read all sorts of loopholes into that statement. “So long as you make an attempt to follow the spirit of what we say, then that is acceptable.”

A flicker of a frown appeared again, though the tilt of her head made it look more confused than offended. “I… shall try.”

\leavevmode\llap{“}Good. Which comes to the second, and I think final, condition, which is the same condition that falls on all of us: if we end up in any combat-related situation, and I expect we will, then Dusty’s word is law. When he tells you to do something, you do it immediately and without question. You can object afterwards, even leave if you decide to, but not in the middle of a fight.”

\leavevmode\llap{“}Hmmph.” The frown had returned once more. “I would question that, but I have seen your group in many fights, and have witnessed its efficiency. It is hardly what my sisters and I shared, but I suppose such an arrangement of authority is the best that a collection of disjointed minds can come to approaching a true unity. Very well. I shall accept this restriction.”

\leavevmode\llap{“}Good,” I said. “I guess that’s it. Well, I suppose I should include the return of our equipment in our agreement.”

\leavevmode\llap{“}Yes, of course,” she said, floating our weapons back to us. As my magic reached out for my equipment, she spoke again. “I do hope this displays at least some indication of goodwill on my behalf. I am not ignorant to the fact that you are a deceptive creature, and could very well be attempting to convince me to return your weapons only so you could turn them upon me.”

I slung my rifle, trying to look as casual as possible as I did so. “If I wanted to kill you, I would have stabbed you in the neck with my horn. I was close and you were distracted. And then, given your size and plainly obvious magical nature—” I gestured a hoof at her eerily flowing mane. “—I probably would have followed up by hitting you with magical bolts until I was drained of energy or convinced you were completely dead. I assume you have seen how I’ve dispatched threats in the past?”

\leavevmode\llap{“}Yes,” she said. “Enough to know that, if you were of a mind to kill me, you would give absolutely no indication of that fact before striking, and you would do so with ruthless and cold-blooded efficiency. I must admit, it does make your objection to my earlier comments seem somewhat hypocritical. Still, you passed up an opportunity to try, so I suppose I will extend a measure of trust. Not that it truly matters. Your tiny horn and weak magic could not kill me any more than those weapons you use.”

\textit{Noted}. Despite that little tidbit, I did feel the need to clarify something. “It’s not hypocrisy. I’ve killed individuals who have caused direct and intentional harm upon others, or who were trying to do so. You were talking about killing individuals because of what someone else of their species might do.”

She stared off into space for a few seconds, considering this. “Hmm. I think I see. Most species lack the Unity we shared, so I suppose it only makes sense to judge them separately.” She abruptly scowled. “I certainly wouldn’t want to be judged off the actions \textit{some} of my sisters have chosen after our Unity was… disrupted.” She quickly shook her head, then looked to me. “This whole conversation would have been much simpler if you had just presented this argument to begin with.”

I blinked. “I hadn’t thought it would be quite so effective,” I admitted. “I take it you’ve decided against genocide as an option.”

She gave a sharp, imperious nod. “Yes. Unless some critical new piece of information turns up, I believe it would cause more harm than good.”

\leavevmode\llap{“}Well… that’s good.” I looked back to my companions. Starlight had a thoroughly mixed expression, somewhere between surprise, amusement, and confusion. She met my eyes and gave a helpless shrug.

\leavevmode\llap{“}Okay,” I said, retrieving and stowing the rest of my small arsenal. Dusty had already finished, still eying the alicorn warily. “Then I guess there’s just one final thing we should address before traveling together.”

Her eyes narrowed slightly. “What is it now?”

\leavevmode\llap{“}Do you have a name?”

Her expression immediately relaxed as she stared off into space. It took a couple of seconds before she replied. “We remember many names,” she said, her voice distant. “Many names, but none of them are… mine.” She stared for another moment before blinking, her attention returning to me. “I have chosen a name for myself: Echo. I feel that name befits me.”

\leavevmode\llap{“}Echo,” I said, and raised a hoof to gesture to the dim glow coming down the exit ramp. “Shall we go?”

\leavevmode\llap{“}Oh, good,” Sickle rumbled. “You dumb cunts are finally done talking. I was about to nod off.”

Echo frowned, looking sideways at Sickle. “I understand you prefer to put on an abrasive front, but while we are traveling together, I would appreciate if you showed at least some fraction of the respect I am due.”

Sickle laughed. “Respect? Right. And \textit{I’d} appreciate it if you ate my ass, you retarded purple bitch.” She even turned, shaking her armored flanks at the alicorn, her tail raised high to give a clear view.

\leavevmode\llap{“}Okay, knock it off,” Dusty called out, stepping between them.

Echo had grimaced at Sickle’s reply. “Surely you can’t be serious.”

\leavevmode\llap{“}Nah,” Sickle said, chuckling. “Doesn’t have to be the ass. I ain’t that picky. As long as you put that snout between my legs and get to work, it’s all good.”

My wings fluttered as I took off, interposing myself between the two of them and gently nudging Echo away. “Okay, yes, Sickle got her crude comments in again, let’s move on, shall we?”

Echo scoffed, then raised her head and walked on as if it was all beneath her notice.

Behind me, I heard the metallic rattle of Dusty thumping Sickle on the shoulder, followed by a quiet but angry, “The hell is wrong with you?”

Sickle’s reply was much less quiet. “The fuck are you talking about? What, because I’m not playing all super-nice with her? Hey, you cunts want to be little bitches, lick her hooves and suckle her teats, you go right ahead. If she’s just going to act like she’s got a colossal fucking log rammed up her ass, then yeah, she gets treated like the uptight cunt she is. If she wants to pull that log out, hey, we all win.” I could practically hear the sneer that followed. “‘Sides, ain’t like I wouldn’t return the favor. Big bitch like that? I bet we could get some good rough fucking in, even if she \textit{is} a mare. Been a long time since I wrestled with a pony my size.”

I quickly ushered Echo away, moving up the ramp and into the outside world. After the darkness of the underground facility, even the overcast skies were surprisingly bright.

Hoping to distract from Sickle’s crudeness, I got down to business. “So! We’re still planning on doing some traveling, but our motorwagon is a bit crowded. With Sickle taking up the rest of the room in the back, I’m afraid the only open space would be the back seat, which will probably be a little cramped.”

\leavevmode\llap{“}That sounds quite unpleasant,” Echo said, looking over the vehicle as it came into sight. “Also, unnecessary. I will simply follow you from above.”

I nodded, pleased with her decision. Seeing as I sat in the back seat, it would have been cramped for me, as well. “I assume that means you can keep up with it?”

\leavevmode\llap{“}Of course,” she said, walking up to the vehicle. “Though if we have the time to spare from analyzing your magic, I would enjoy the opportunity to examine this vehicle. We remember a good deal of the working of arcane technology, but we do not remember ever working with a motorwagon. A simple disassembly and reassembly should answer any questions I have.”

\leavevmode\llap{“}Maybe if we’re going to be in one place for a while and don’t need to travel,” I said, while hoping such an opportunity didn’t present itself. I had only a vague idea of how complex such a machine was, and I had no idea if she’d actually be able to reassemble it. Then, as an afterthought, “but you should probably ask the others, as well. Dusty’s kind of in charge, and I think Starlight considers the vehicle to be hers.”

\leavevmode\llap{“}I will do so,” she said. There was a flicker of a frown, and she added, “I must admit, I prefer machines over ponies. They are… simpler.”

I nodded, feeling a little more comfortable with this topic. “Very true. Machines are built for a clear, defined purpose, and produce entirely predictable results from their input. Ponies—or any other people—are much more complex. While their behavior can still be predicted if you have the correct information, the amount of complexity makes it much harder to get all the information you need.” I gave a little shrug. “It becomes easier with practice.”

Echo had stopped, her head high as she stared off into space. “Hmm. Yes, I suppose that does make for a very good metaphor, even if I had not originally intended it to be one.” Her focus returned. “I simply meant to say that machines are much simpler in their function, mechanically. I can disassemble even a complex machine and reassemble it into working order with ease. So far, doing so with ponies eludes me.”

And we were right back down to creepytown. “I can’t say I’m surprised,” I said, cautiously. “Most living things do not respond well to being disassembled.”

She dismissively waved a hoof. “I am not concerned with that. The goal is not to perfect disassembling ponies. That is trivially easy. The goal is to perfect reassembly, so that I can repair damage. I can repair a pump or skywagon that has not functioned for two hundred years. It… frustrates me that I can not do the same for a pony.”

\leavevmode\llap{“}I don’t think it’s possible to bring back the dead.” Other than necromancy, anyway, but I wasn’t going to suggest that to an already morally-ambiguous pseudo-goddess.

\leavevmode\llap{“}Of course it’s possible. It’s simply more complex than I had initially thought. My efforts to reassemble ponies has been incomplete. Superficial. It’s like…” She paused, cocking her head to the side for a moment before giving a sharp nod. “Like a computer, yes. Repairing a pony is like repairing a computer that is still running. Damaged hardware can damage the data in the computer. Disassembling it while it is operating, in an attempt to repair it, can also do so. A pony is the same, with the hardware being the body and the software being their brain and thoughts. I simply need to figure out how to repair that hardware in a way that preserves that software.”

\leavevmode\llap{“}If you’re talking about healing living ponies, I’m sure there are healing spells that—”

She scoffed. “Of course there are. We remember them quite well, even if I do not understand them well enough to use. No, I am looking for more in-depth knowledge, a proper understanding of how ponies function, so as to better aid them. Cures that go beyond simply knitting flesh and bone.”

I considered that, and nodded. “I suppose that’s a noble enough of a goal,” I said, if a little reluctantly. “But I think we’ll have to say no more disassembling people. Ponies aren’t going to take that well.”

\leavevmode\llap{“}I doubt they will care much,” she said with a shrug. “I have been making use of raiders. Many of them were ponies that you four have killed.”

\leavevmode\llap{“}No, that’s… well, yeah, it might help a little, but there’s still going to be plenty of ponies who find the idea of dissecting other ponies to be rather creepy. Not to mention disrespectful. No non-raiders, at least. And definitely no living people.”

\leavevmode\llap{“}I do not—” She cut herself off, her mouth shutting. Then, more slowly, she said, “I suppose there were two raiders who were alive when I disassembled them, but seeing as I was going to kill them anyway, it hardly makes a difference.”

Okay, that was one I had to put my hoof down on. “It \textit{absolutely} makes a difference. What you’re talking about is essentially torture. It’s that sort of thing that makes raiders so despised, and while you might have better intentions, it doesn’t change that the means are horrific. If you truly want to make the world a better place, you need to start by \textit{being} better.”

\leavevmode\llap{“}I \textit{am} better,” she grumbled, and when I went to speak again, she quickly cut me off. “Yes, I understand what you are saying. It is simply a lot to think on, and a lot of complication added into an already complex situation. It seems as if all these restrictions simply get in the way of doing what needs to be done. I have to wonder if the world would already be a better place if we didn’t have the absurd restrictions constraining our actions.”

\leavevmode\llap{“}Just the opposite,” I said. “I might have missed the last two hundred years, but I’ve caught up quickly, and I understand ponies rather well. As far as I see it, the world is still so badly off because people \textit{do} take those shortcuts. They do horrible things in the name of survival or personal interest, or even occasionally for some greater good, but in the process, they keep spreading this misery around. If you pursue your own noble goals through such horrible means, you’re simply continuing the same process that has kept the Wasteland going for centuries.”

Echo had fallen silent, staring at the ground, deep in thought. I continued. “You recited the Elements of Harmony just a few minutes ago. You understand what they are, correct?”

Her ears pinned back. Her voice was quiet, distant. “We remember them very well.”

\leavevmode\llap{“}Then you should know that Equestria was at its greatest when the ponies there embraced the values the Elements represented. Those were the values that made Equestria such a wonderful place. It was only when ponies started to compromise them, forget them, that things became so bad.”

Echo frowned, silent.

\leavevmode\llap{“}If we’re going to make the world a better place, we need to bring those values back.”

Her eyes returned to me, staring. “And you think this would be sufficient?”

I nodded. “I’ve seen it. You probably have, too. You’ve been watching us, right? Did you watch Emerald?”

\leavevmode\llap{“}The innkeeper,” Echo replied. “Yes.”

\leavevmode\llap{“}Someone who embraced the ideals of Kindness and Generosity. She made Gemstone into a wonderful place, one that is already on its way to being what Equestria once was. That’s what one pony—one changeling, even—can do. She made a small part of the world a better place, and she’s inspired others to do the same. That’s the only way the world is going to get better than all of this.”

\leavevmode\llap{“}By embodying the Elements,” Echo murmured, as if to herself. After a moment of thought, her gaze hardened, glaring at me. It was hard to read the intent behind those eyes. I couldn’t tell if she was angry, suspicious, or something completely different.

\leavevmode\llap{“}Is there something wrong?” I asked, almost fearing the response.

She didn’t answer. Instead, she held her stare for a long moment, until her ears flicked and her attention turned back to the ramp. My companions were walking up to join us.

Echo abruptly spread her wings to their full extension, her head rising. “I shall follow you from above,” she declared before turning her hard glare back to me. “We will continue this discussion later.”

She immediately beat her wings, lifting into the sky, while I staggered at the volume of air she displaced. As I caught my balance, Dusty trotted up to me. “Problem?”

\leavevmode\llap{“}I don’t know,” I said, looking up to watch Echo ascending. “I think I might have upset her, but I’m not entirely clear why, or why she immediately broke off the conversation instead of talking. Maybe she just wants some time to think. I’ve thrown rather a lot at her.”

\leavevmode\llap{“}Well that sounds ominous.” He sighed, shaking his head, while Sickle walked past us to the motorwagon. Finally, Dusty fixed me with a look. “Okay, what’s the plan? Are we really taking her with us? Or is this just delaying until we’re sure of a way to kill her safely?”

\leavevmode\llap{“}We’re not killing her,” I quickly said. “She’s not malicious. She’s just… unguided. She seems like a child, in some ways.”

\leavevmode\llap{“}Oh, great,” Dusty said, clearly not comforted by the comparison. “Have you been around children? I saw a little colt throw a shitstorm of a tantrum because he ate all of the filling out of his birthday snack-cake and that made it ‘broken’. Now you’re saying this alicorn might be like that?”

\leavevmode\llap{“}No,” I said, shaking my head. “Foals do stuff like that mostly because they have no sense of cause and effect. Many times they don’t even have a concept of object permanence. She clearly understands these things, and she seems quite intelligent. When I said she was like a child, I don’t mean that her mental faculties are limited. I mean that she lacks the experience necessary to understand why something might be moral or not.”

He grimaced. “No concept of morality. Yeah, \textit{really} not selling me on this.”

\leavevmode\llap{“}Consider that she’s trying to get help with that,” I said. “She’s been listening to me, and I think we’ve already made some good progress. She’s \textit{looking} for guidance. I think we can help each other.”

\leavevmode\llap{“}Assuming she doesn’t decide we’re part of the problem and kill us. Or decide that changelings really \textit{do} need to be exterminated, and kills you. Or decides that us not wanting to be ‘perfect’ alicorns is unacceptable and forces us to change. Or just kills us, because why not?” He shook his head. “Look, I get that you want to help her, and yeah, she’d be pretty damn useful, but she’s a fucking ticking bomb, and I don’t like the idea of keeping her around waiting to see if she blows up on us.”

The motorwagon shook as Sickle flopped down in the back with a grunt, followed immediately by calling out, “A bomb, huh? Bigger or smaller than the balefire eggs I just sat on?”

He turned to her. “You know what I mean.”

\leavevmode\llap{“}Sure, sure,” Sickle said, lazily waving a spiked hoof. “It’s just that what you mean is stupid.”

\leavevmode\llap{“}Look,” I said, drawing his attention back. “I said a lot about ideals to her, about the Elements of Harmony, and that applies just as much to us as they do to her. I think she’s hurt and lost, and we need to help her because it’s the right thing to do.

\leavevmode\llap{“}And yes, if she does decide to hurt others, we’ll do what we can to stop her from doing so, but we’re not going to do so preemptively just because she \textit{might} become a problem later on. We have to be better than that.”

Dusty grunted, looking away. “I don’t much like it, but… hell, you’re the whole psychology expert, I guess.” He looked back. “Fine. It seems like a dangerous gamble, but this one’s your call. But if she does try to hurt somepony, I’m doing what I can to stop her.”

I nodded. “Of course. And while I hope it won’t come to that, I will help. I don’t intend to sit back and let innocents be hurt if there’s anything I can do about it. The thing is, I think she’s one of those innocents, right now.”

Dusty frowned, silent for a moment before sighing. “Yeah, maybe. She’s just a lot more dangerous than most.”

\leavevmode\llap{“}So is Sickle,” I said. “Hell, apparently so am I.”

\leavevmode\llap{“}Yeah, yeah,” Dusty said, waving a hoof. “I get it. Shit. I won’t kill the alicorn, ‘less she does something bad enough to force my hoof.”

\leavevmode\llap{“}Good enough,” I said. “Not that I’m entirely sure we could stop her, even if we wanted to. I’m not sure what alicorns are capable of, but she seemed confident in her safety.”

\leavevmode\llap{“}I know they can be killed,” Dusty said. “Heard that much on the radio, at least.”

I nodded. “Hopefully we’ll never have to find out,” I said. With that, I turned to the motorwagon. Starlight was already inside, watching us through the side window.

\leavevmode\llap{“}As an aside,” I said casually as I approached the vehicle, “Echo’s observation of us apparently included conversations, even fairly private ones. It’s quite possible she has some form of magical eavesdropping that’s letting her listen in on every word we’ve said.”

Dusty froze, one hoof on the side of the motorwagon. “...Shit, you mean she just heard me talking about… that? You think you could have told me that a little earlier?”

\leavevmode\llap{“}If she heard you considering it, she also heard why you’ve decided against it. Consider it to be a demonstration of morality.”

\leavevmode\llap{“}Hmmph.” He pulled himself into the motorwagon, grumbling. “Still could have told me.”

I said nothing as I hovered up beside the window and slipped in. In the front seat, Starlight gave a quiet chuckle. “Sneaky bug,” she murmured, before turning to me. “Also, \textit{holy shit that actually worked!}”

I groaned softly as I sank into the rear seat. “So far. We’ve got a good ways to go before we can really say it ‘worked’.”

\leavevmode\llap{“}Hey, we’re all still alive, and it sounds like she might kinda maybe sorta help us.”

I shrugged, though I did give a thin smile. What had started as a particularly dangerous situation was now… a somewhat less dangerous situation with more potential. It wasn’t perfect, and it could still collapse around us at any moment, but we had made progress. A better outcome was in sight.

Starlight had turned to Dusty. “Where to?”

\leavevmode\llap{“}Start heading out west,” he grumbled. “\textit{Somepony} has been complaining about the lack of adequate company, so we’re stopping by Rust to see if that shuts her up for a bit. Not that I’d mind a real bed, for a change.”

\leavevmode\llap{“}Rust it is,” Starlight said, and the motorwagon started off. Soon we were rolling along at a good clip, with Starlight casting the occasional glance to her PipBuck’s map, and the strange alicorn trailing us in the sky above.

We continued on across the dry, dusty desert, and thick plumes of dark smoke rose from the horizon before us.