Enclave soldiers were gathering when we exited our tent in the morning. Ponies were checking over each other, readying gear, and organizing into groups. Probably half the camp was gathered.

Commander Aurora had already split off from them and was approaching us. “Leaving already?”

\leavevmode\llap{“}We have some places we need to be, and shouldn’t delay for too long,” Dusty said. “Looks like you’re leaving, too. Something up?”

\leavevmode\llap{“}Just routine patrols,” Aurora said, though the size of the group suggested otherwise to me. “Sorry, but I can’t discuss the details of our operations.”

Dusty held up a hoof and shook his head. “I understand, believe me.”

She gave a curt nod. “I was hoping to talk more when we returned, but I suppose I’ll have to do without. If you come back through the area, I wouldn’t mind the opportunity to talk. Our camp won’t be in the same place, but the patrols will see you coming in and can direct you.”

\leavevmode\llap{“}I appreciate it,” Dusty replied. “I’m not sure where our business will take us next, but if we pass by, I’ll be sure to stop and say hello.”

\leavevmode\llap{“}Good,” she said. “One final thing: I was hoping you might be able to do us a small favor. Some of my patrols have been taking ground fire from various locals who don’t know the difference between Loyalist and Council forces, and haven’t noticed that my patrols always break contact without returning fire. I’d appreciate it if you could help spread the word that we’re not the same Enclave they might be familiar with. You can point them our way if they need help, too. The ponies in Gemstone are already spreading the word, as are a few other groups we’ve encountered, but the more ponies getting word out, the better.”

\leavevmode\llap{“}I’ll do that,” Dusty said. “Though on that subject, maybe you could do us a favor, too, and help get out the word about Serenity.”

\leavevmode\llap{“}We can do that,” she said, though her helmeted head turned slightly, her gaze clearly shifting to me. “Though I assume you’re wanting me to keep your friend’s... involvement a secret.”

Dusty looked to me.

Hesitantly, I answered. “If you don’t mind.”

She simply nodded. “We’ll see what we can do.”

\leavevmode\llap{“}Thank you,” Dusty said. “I think that just leaves the PipBuck we lent your medical staff, if you don’t mind.”

\leavevmode\llap{“}Of course.” Aurora turned to another soldier. “Tailwind, go to Lifeline and return these ponies’ PipBuck.”

The other soldier saluted, and as he flew off, Aurora turned back to us. “If you’ll excuse me, I have a briefing to take care of. Good journeys.”

\leavevmode\llap{“}Thank you,” Dusty said. “And good luck.”

She gave another curt nod, turned, and returned to the gathered soldiers.

Tailwind caught up with us as we were climbing into our motorwagon. I took the PipBuck, and settled into the back seat.

\leavevmode\llap{“}So,” Starlight said as she got behind the wheel. “Where to?”

\leavevmode\llap{“}One more C.L.T. facility,” Dusty said, bringing up his map. “It’s a good distance west of here, about halfway to Trotsen, but we should make it today easily enough.”

She grinned. “You got it.”

Moments later, we were rolling.

As we made our way out of the camp, I was pulling out my diagnostic tools and hooking up the spare PipBuck to my own. Dusty looked back. “What are you up to?”

\leavevmode\llap{“}Changing the tags again,” I said.

\leavevmode\llap{“}Worried about them tracking it?”

\leavevmode\llap{“}Not really,” I said. “They just let a known changeling leave their camp with minimal fuss. It’s possible they let us go with the intent of following us, though I find that doubtful. I don’t think they intend us any harm. Still, I don’t intend to let them track us, whether they have hostile intentions or not.”

\leavevmode\llap{“}Fair enough,” Dusty said, sitting back in his seat.

We rolled on.

{\br}%
We stopped around noon to get a quick meal and stretch our legs. Echo joined us, giving me the opportunity to present the freshly re-tagged PipBuck to her.

\leavevmode\llap{“}Thank you,” she said as she took the PipBuck in her magic. Despite her almost rigid stance of casual superiority, she inclined her head as she peered at the device, a hint of a smile appearing. It vanished a moment later as she placed it on her foreleg, closing the clasp, and addressed me in a matter-of-fact tone. “This should be most helpful.”

She sat as we broke out lunch. She managed to hold the calm and disinterested look for perhaps half a minute before her eyes drifted back to the PipBuck. A minute later, she gave up any pretense, and began examining the device closely. She didn’t stop at simply looking through the menus and examining its functions, either. Soon she was turning it this way and that, examining the case, dials, and buttons.

To my surprise, I caught a sense of emotion from her. I couldn’t make out exactly what it was. What I could tell was that it wasn’t directed at the PipBuck. It seemed somehow intangible, as if directed toward a memory or idea rather than a physical thing in her presence, and it made me think less of affection, and more of passion. It was the first sense of a solid positive emotion from her. I hadn’t even sensed that small degree of positive emotion from her when she had spoken of her mother, though I had been more distant and more distracted at the time.

\leavevmode\llap{“}I may need to borrow that small electronics toolkit you carry,” Echo quietly murmured as she twisted her leg around to examine the underside of the main selector dial. “I am sorely tempted to dismantle this device to work out precisely how it works.”

Dusty and Starlight frowned and grimaced at that remark, before looking to me. It seemed she was my responsibility. I suppose that was fair enough.

\leavevmode\llap{“}I don’t mean to disparage your talent, but of all the devices we have, a PipBuck is probably the most complex, and you know what disassembly can do to complex things. At the very least, it would take much longer than a quick lunch break. Maybe it should wait until after you’ve taken care of your research?”

She hesitated, but finally lowered her hoof. “Yes, you are quite correct. I should prioritize and focus on my primary goal, rather than interesting diversions.” She paused again, sneaking a quick glance down at her foreleg. “Though as much as I appreciate this gift, and as much help as I am sure it will be, I fear it will also be quite thoroughly distracting. It is such a fascinating device.” She glanced back toward the motorwagon. “One of many.”

Starlight looked up from her can of mystery vegetables. “You really like machines, don’t you?”

\leavevmode\llap{“}Very much so, it would seem,” she said, peering at the vehicle for several more seconds, before shaking her head. “We remember a great many things, which can make it quite difficult to sort out my own thoughts.”

There was a moment of silence before Starlight cautiously asked, “You mean you don’t know what you like?”

\leavevmode\llap{“}I bet you like fucking,” Sickle said around a mouthful of oats, and snickered as Starlight shot her a dirty look. “Hey, I know you do, little Star. You’re pretty loud for a runt.”

\leavevmode\llap{“}It is complicated,” Echo said. “When we were in Unity, everything made sense. We all had a place. Ever since the Destroyer ruined everything, I have been… adrift. The world is a confusing and mysterious place.” She frowned, lifting her hoof to look at the PipBuck again. “I suppose I like things that make sense. I can peel away a little bit of that mystery.”

I slowly nodded. “That sounds pretty reasonable.”

\leavevmode\llap{“}Hmmph.” She stared at the PipBuck for a moment before setting her hoof down. “Though on that note, I should take advantage of this device you have generously lent me to continue my studies. Whisper, as you appear to have finished your meal, would you please perform some transformations while I analyze your magic?”

I sighed, chewing and swallowing the last mouthful of stale oats before rising to my hooves. “Okay. Tell me what you need.”

\leavevmode\llap{“}When I say so, I would like you to transform into an alicorn. You may copy my appearance, if that helps you.”

\leavevmode\llap{“}That’s a pretty big transformation,” I said, frowning a little. “It takes a lot of energy and effort.”

She dismissively waved a hoof. “You have quite an adequate supply of affection to draw upon. That should not be a problem for you.”

\leavevmode\llap{“}That’s… well, that’s true, though I still won’t be able to do that very often. What I mean is, shouldn’t we start with something simpler?”

\leavevmode\llap{“}Of course not. An alicorn is our end-goal. We will be best served by analyzing the complete transformation and working backwards from there. That you will expend more magic in the effort will be of benefit, as the stronger magical energies will provide a much better impression of the actions involved. Once I have a good grasp of the general behavior, we can work on smaller changes to refine the data.”

With that, she stood, stepping up to me. “Now then, we need to remove anything that could impact the tests and contaminate our data. Revert to your natural form and remove your barding and all personal effects.”

I did so, resisting the urge to grumble. A minute later I had stripped down, standing there in nothing but glossy chitin.

\leavevmode\llap{“}Good,” she said, and her horn lit up. My vision tinted purple, and I felt a faint sensation that started in my horn and quickly spread through my body, as if my magic itself were vibrating. “Transform.”

I obeyed, focusing and pushing a good deal of my magic outward. It flowed through me as I steadily built it up, and with a flash, the flames engulfed me.

The whole world had changed. I stood eye-to-eye with Echo, and towered over Starlight and Dusty. Everything seemed so much smaller, and while I certainly had more mass, the lean form I wore now felt as agile as ever.

I may be familiar with transformations and the changes in perception that typically accompany them, but there was always something intriguing about it.

The first thing I did was turn my head to look back at my mane and tail. To my satisfaction—and, I must admit, a tiny bit of surprise—I had managed to mimic the strange, ethereal nature of her mane, which floated silently behind me. Despite my happiness at being able to mimic such a thing, I also noted how much energy the form was taking. A larger form should naturally be more draining, but this form was consuming my reserves even faster than usual.

\leavevmode\llap{“}How long do I need to hold this?”

\leavevmode\llap{“}Not long,” she said, tilting her head as she peered at me. The sensation of her magic on me fluctuated and changed several times, and she regularly turned to her borrowed PipBuck to record data. It was only about a minute before she nodded. “That should be good. Please return to your natural form.”

I happily did so, and the world returned to its correct size. I sighed softly in relief as the gentle pressure of holding that magic relaxed.

Echo took a few more notes before giving a satisfied nod. “Yes, that will be very useful. Interesting data. Some interestingly familiar aspects. Notable departures from traditional transmutations. Curious… yes, this is a very promising set of data. It appears to confirm that there is value in this pursuit, and warrants further testing.” She looked back to me, eyes eager and determined, and a vaguely concerning smile touching the corners of her mouth. “Again.”

{\br}%
I climbed out through the window of the motorwagon, giving a mild groan as I moved. Echo was immediately at my side, her wings kicking up dust before quickly folding at her sides. “Are you certain you are well?”

\leavevmode\llap{“}I’m fine,” I grumbled, wings fluttering as I softened my drop to the ground. I unconsciously started to raise a hoof to rub at my head before catching myself and setting it down again. “The headache is mostly gone.”

\leavevmode\llap{“}Yes, well, that is good,” she said, peering down at me with a concerned expression. “I had not realized it would be \textit{quite} so straining upon you. Perhaps further study should be done at a more relaxed pace, or at least less stressful transformations. I would not wish to cause injury to you. If nothing else, it risks delaying further experimentation or even compromising the data.”

I grimaced, but said nothing else. I could appreciate the practicality of the statement—I had, in fact, been thinking something similar—but at that moment I could only think of how irritatingly insensitive it seemed. Even though I recognized how emotionally driven that thought was, it was hard to shake. I blamed the lingering remnants of the headache.

As I silently levitated out the rest of my gear, she spoke up again. “At least you can take some comfort that your efforts will go to aid all of ponykind.” She blinked. “All person… personkind?” She frowned. “There must be some term that isn’t species-specific.”

\leavevmode\llap{“}All people,” I offered as I strapped on my helmet and slung my rifle. “Or just ‘everyone’.”

\leavevmode\llap{“}Hmmph. It seems to lack the gravitas of ‘ponykind’, but I suppose it shall have to do.”

Starlight trotted up to my side. “Hey. Feeling better?”

\leavevmode\llap{“}Much better,” I said, smiling.

She smiled as well, though it faltered before she asked, “Are you… hungry?”

I sighed and shook my head. “There’s no need to worry about that. I’d built up a good reserve, and I have plenty of opportunity to ‘nibble’ on a bit of affection. I’m fine.”

She nodded, then leaned in to bump me with her shoulder. “Well, if you \textit{do} need some more, um… \textit{affection}, just, uh… let me know?”

Sickle snickered, immediately drawing out a blush from Starlight.

\leavevmode\llap{“}That’s not what I meant and you know it,” Starlight shot her way. “Not that I’m against—not that it’s any of your business anyway!”

While Sickle continued on her way to join Dusty, Echo looked down at me. “I suppose since it was my own tests that led to this, I should extend the same offer.” She cast a glance to Starlight, and added, “The offering of magical energy, that is, not the implied sexual interaction.”

Starlight groaned, covering her face with a hoof. “I wasn’t implying that.”

Just ahead of us, Dusty grumbled as he peered through his binoculars. “I’m surrounded by crazy mares.”

He then grunted as Sickle flopped down, a heavy foreleg across his shoulders. “Ah, Dusty, see, you’re lookin’ at it all wrong. Crazy mares are great! They’ll do shit the sane ones won’t.”

I crouched down as I moved up beside Dusty, and peered out at the C.L.T. Experimental Site Beta just a quarter mile away.

As with the other sites, there was little on the surface to see. In fact, one of the things I noted the most was what I \textit{didn’t} see: any sign of salvaging, rebuilding, or habitation. While the skywagon shelter had collapsed and the two vehicles beneath it were rusted out wrecks, they didn’t appear to have been picked over for parts. The gatehouse’s windows were broken, but the desk and chairs were still upright and the door intact. At the back of the compound was the broad entrance protruding from the side of a small hill, with a sign declaring the name of the facility in faded but intact letters.

But those were only suggestive details, bits of evidence that could support a possibility, but were not decisive.

More decisive was the one notable detail the other facilities had lacked, parked directly in the middle of the small, fenced-in compound.

\leavevmode\llap{“}Holy shit,” Starlight said, leveling her Lancer to peer through the scope. “That’s a Sentinel bot.”

Like its surroundings, it looked worn by the centuries of exposure, but otherwise intact. The four-legged robot slowly rolled along, like something halfway between Sickle and a tank. Many gems glittered from a magical energy weapon mounted on one side of the robot’s turret-like torso, while the gaping muzzle of a short-barreled cannon was mounted on the other side. In case that wasn’t enough, a pair of pods were mounted on its back, with large muzzles pointing upwards. Some form of mortar or grenade launcher.

\leavevmode\llap{“}Ultra-Sentinel,” I corrected. “The pinnacle of Equestrian combat robotics. Multiple modular weapon systems, heavy armor, and high mobility. It’s about the deadliest ground unit the Equestrian Army had short of an actual tank.”

\leavevmode\llap{“}Great,” Dusty grumbled. “And we need to get past it. Well, you know all that pre-war stuff. Any good news?”

\leavevmode\llap{“}Yeah,” I said, frowning. “The good news is it isn’t a \textit{zebra} robot. Those were even worse.”

Out in the distance, the bot was slowly rolling across the paved courtyard. It would go on for several seconds before coming to a halt, slowly panning its weapons around as if scanning for threats, then turning and rolling off to a different part of the compound to repeat the cycle.

An endless, meaningless task, repeated for some two hundred years. If I were the type to anthropomorphize unintelligent objects, I might have felt sorry for it.

\leavevmode\llap{“}I meant, any good news about how to get past it?”

\leavevmode\llap{“}Well, there is the good news that it \textit{might} not be hostile.” I turned to look at him. “So, if you want to walk up to it and see if it opens fire…”

Starlight was already lying down beside Dusty, bracing her Lancer on the rocks. “I’ve seen lots of bots patrolling old-world facilities,” she said. “Never seen any that didn’t immediately open fire on any pony it saw.”

Dusty nodded. “Same. Well, this complicates things.”

\leavevmode\llap{“}Perhaps there is some way we could safely disable and commandeer it,” Echo said, peering out intently. “I can think of many uses for such an impressive and advanced automaton. Whisper, you are skilled at computer hacking, are you not?”

\leavevmode\llap{“}My specialties are security circumvention and cryptography, as well as basic networking and database skills. I don’t have any experience with AI programming, if that’s what you’re suggesting. Besides, I would need direct access to its computer. I don’t think it’s going to let me walk right up, pop it open, and find a place to plug in. Heck, I don’t even know if it \textit{has} a cable port, and even if it does, I’d be surprised if any of my debug cables work on its hardware. If they put any decent security in there, it could take me days to bypass.”

She frowned thoughtfully, continuing to stare. “So… not likely, but possible?”

\leavevmode\llap{“}Unlikely on the order of needing some small miracle to pull off. Make that \textit{several} small miracles.”

\leavevmode\llap{“}I’ve got this,” Starlight said, shifting her position slightly as she lay out, taking a stable, braced firing position. “Mom took out a bot a lot like this, guarding some factory in Dodge City.” She squinted into her scope. “Told me how, afterwards. There’s a panel on the back, where you can get to the spark battery or generator or whatever they’re powered by. It’s thinner than the armor. Most robots have something like that, just got to know where to look.”

\leavevmode\llap{“}Long range, small target,” Dusty muttered. “And you’d only get one shot.”

\leavevmode\llap{“}I can do it,” Starlight said, her voice calm and confident. Her entire attention was focused down that scope. “Though this one’s a bit bigger than the one I remember.”

Dusty considered it for a moment before replying. “Hold up a minute. We’ve got some heavy weaponry, so let’s get ready in case the shot doesn’t take it out. Whisper? Fly back, get on the machine gun. If we fall back from the ridge, it’ll have to come over the crest to get to us. That’ll bring it nice and close, and make it an easy target for that machine gun. That thing should get through its armor, right?”

\leavevmode\llap{“}The Model 1 heavy machine gun fires the same round as the anti-machine rifle, which was developed specifically to destroy zebra combat robots,” I said. “I don’t know how well it performs against this specific model of robot, but it’s probably the most capable of all the weapons we have.”

\leavevmode\llap{“}Not quite,” Dusty said, scooting back from the ridge. “I’m getting that Balefire Egg Launcher. If we’re going to carry the damn things around with us, we might as well be ready to use them, and there’s not many things that need that kind of firepower.”

\leavevmode\llap{“}Serenity might,” I noted, but his comment stirred another thought. “I still have two more matrix disruption grenades in the motorwagon. They’d do just as well.”

\leavevmode\llap{“}Except it has to get close for that,” Dusty said. “You can’t throw a grenade nearly as far as the launcher can reach, and especially not with accuracy. Still, it’ll be a good backup if it gets close.”

Echo stepped up. “Throwing will not be necessary. Give the grenades to me, and I can deliver them with unerring accuracy.”

I immediately thought back to her trick of teleporting away all of our weapons. “How far can you teleport something?”

\leavevmode\llap{“}A few hundred yards with ease,” she said, her head rising proudly. “Even further, if I am willing to allow a small degree of uncertainty in the destination. Less, if the object to be teleported is particularly heavy, but anything under several hundred pounds would give me no difficulty.”

\leavevmode\llap{“}Huh,” Dusty said, a smile slowly spreading. “I like it. Okay, Echo gets the matrix disruption. I’ll dig out one of the other heavy machine guns instead, and set up on-line with Whisper. Starlight will lead off, and if the shot doesn’t take it out, fall back behind us and get set up for a follow-up shot when it crests. In fact, we’ve got a damn case of mines. I’m going to seed a few in front of our position just in case.”

A few minutes later, we were set and ready. Dusty was a good thirty yards to my flank with another machine gun, while Starlight, Echo, and Sickle were spread out on the ridge before us. Somewhere beyond them were a half dozen mines, and past that, the heavily armed Ultra-Sentinel that lay between us and the C.L.T. facility.

The earbud crackled in my ear, followed by Dusty’s voice. “We’re set. Starlight, you’re clear to fire.”

Another crackle preceded Starlight’s reply. “Give me a minute. I need it to turn around again.”

Silence followed. I tried to resist the nervous urge to fidget, with the result that I double-checked the range on my sights only three times between adjusting my position in the back of the motorwagon. My only comfort was the massive weapon I was using. It was almost ridiculously big. Even the barrel alone was longer than I was.

The shot came out of nowhere. One moment was silent, save for the creaking of the motorwagon as I moved a few inches to the side, and the next moment, the sharp crack of the Lancer splitting the air echoed across the hills. My gut twisted, heart-rate picking up in anticipation.

Starlight opened the breach of her Lancer, quickly swapping out crystals. She was just sealing the chamber again when her head dropped to the ground.

An instant later, a huge spray of dirt flew into the sky from the far side of the ridge, followed by the sharp and powerful blast of an explosion.

Starlight scrambled back several feet as she keyed up her broadcaster, her voice blasting in my ears. “It’s still up! It’s still up!”

I could just barely hear Sickle shout back, “No fucking shit!”

\leavevmode\llap{“}Fall back,” Dusty called on the radio, his voice reassuringly calm. “Echo, you’re up.”

Echo had already stood, a sphere of purple energy snapping into being around her. A spray of magical bolts filled the air, throwing up puffs of dirt when they hit the slope and sailing overhead when they did not, like the most terrifying fireworks show ever. Echo didn’t seem to care as she advanced a few steps to peer over the top of the ridge. A few bolts impacted her shield, which gave only a faint shimmer. She didn’t react to them.

The fusillade stopped, and Echo’s head tilted up, tracking something high in the air. Her voice reached out across the distance, as clear as it was unconcerned. “We have incoming projectiles.”

\leavevmode\llap{“}Take cover!” Dusty called out, not quite as calmly as before. I ducked down, hunkering low in the motorwagon, with just my eyes and horn above the edge of the armor.

I watched as Echo’s eyes narrowed, focusing on the incoming projectiles. Small purple flashes appeared in the air above us. Then her gaze returned to the ground before her, and a second later, I heard the first of the distant explosions echoing across the Wasteland.

A moment later, she sat down. A loud crack split the air again, followed by a whistle and the distant boom of the Ultra-Sentinel’s cannon firing. The round exploded somewhere behind us a second later. Another burst of magical energy followed.

I gripped my machine gun, waiting.

Echo continued to sit there, looking calm and content, for a good twenty seconds. At that point she stood, looked out over the ridge, and sat again. Another explosion tore away a chunk of the ridge before her, and I ducked down behind the armor, while whistles of fragments sounded overhead.

I peeked up again just as Starlight skidded to a halt, huddling behind the motorwagon. “Holy \textit{shit!}” she said, panting lightly. “That damn thing doesn’t want to die. Nailed it right where mom said, even saw a bunch of flames, but it just won’t stop!”

\leavevmode\llap{“}They’re made to be durable,” I said reasonably. “We’ve got plenty of firepower left.”

Echo had stood again, the matrix disruption grenade floating out before her. With a flash, it vanished, just as a burst of magical bolts saturated the area. Several struck her shield, which flickered heavily, before the burst of fire abruptly stopped. She sat again, and let the shield drop. From where I was, I could just see her drawing in a deep breath before bringing the shield up again, though it looked a little more transparent than it had been before. It seemed to me that it wasn’t as impenetrable as she claimed.

She stood to look out again, and after a moment, called back. “It appears that its weapons have been rendered inoperable, but the robot is still mobile.” She had hardly gotten those words out when a flash bloomed from the top of her shield, followed an instant later by the boom of the cannon firing. Echo fell back on her haunches as the shield vanished. I could actually see the shell sail through the air past us, having failed to detonate with the glancing hit.

\leavevmode\llap{“}Correction,” Echo called back with the faintest hint of a waver to her voice. “It appears the cannon is still functional.”

Dusty cupped his hooves around his mouth as he shouted back. “Stop popping up in the same place!”

Echo stood in a low crouch, walking a short distance from her initial position, while I focused down the sights, the front post hovering directly over the point on the ridge where the previous shell had struck.

\leavevmode\llap{“}Steady,” Dusty’s voice reassured us. “We have the advantage here, just be patient and don’t rush your shot.”

I drew in a deep breath and exhaled, focusing. I tried to push all the worry and uncertainty from my mind, and instead fixated on my task, eyes looking down the sights, waiting for the first sign of the Ultra-Sentinel amongst the dust that now hung over the ridge.

A good twenty seconds later, a plume of dust and debris flew into the air, followed by a sharp bang unlike the cannon. Echo stood again, peering over the ridge without the benefit of her shield. She remained there for only a moment before sitting again and calling back to us. “It appears to have been immobilized.”

Dusty cupped his hooves beside his mouth again and shouted. “Are its weapons still up?”

\leavevmode\llap{“}It appears that only the cannon is still functional,” Echo replied. “Its capability is greatly diminished. The robot is missing one of its legs, and should not be able to traverse its weapon far from where it is currently aiming.”

\leavevmode\llap{“}Where is it aiming?”

\leavevmode\llap{“}Directly at me,” Echo called back. She sounded almost proud of the fact.

Dusty turned back to his PipBuck, and my earbud crackled with his voice. “Star, mount up! You two take the wagon down the low-ground here to the right, north. Go about two hundred yards, then pop up and hit it from the side!”

Starlight dashed over to the motorwagon, practically leaping in through the window, and a moment later we were tearing off through the rocky low-ground. I clung to the gun for balance as Dusty spoke up again. “Short exposure! Pop up, put a few good bursts into the target, then back up into cover before it can engage you. Keep shifting positions until this thing is dead!”

The motorwagon bounced and rattled, our equipment sliding around behind me. Soon we passed out from the edge of the small hill we had been behind, rolling along a shallow gully that had once been a stream. Its steep sides were just barely high enough to conceal us.

Moments later, we slowed, and Starlight called back to me. “This far enough?”

I swung the massive barrel around, pointing the weapon roughly where I expected the hostile robot to be. We were still outside of E.F.S. range. “Bring it up here,” I called out. “Slowly. I’ll tell you when to stop.”

\leavevmode\llap{“}Got it,” she said. The vehicle turned a little—I corrected my aim—and rolled forward. Starlight slowed further as we reached the edge of the gully, and had to gun it to make progress up the steep slope, the vehicle pointing upwards at an awkward angle.

I saw the settling dust and thin trail of smoke even before we had cleared the edge of the gulley. I adjusted my aim, and as Starlight brought my weapon over the edge of the gully, I was pointed directly at the robot, maybe a hundred and fifty yards away.

\leavevmode\llap{“}Stop!”

The vehicle lurched to a stop, my aim wavering with the momentum. As my sights resettled, I could see the Ultra-Sentinel lying askew. One of its legs lay twisted at an awkward angle, largely intact but apparently crippled by the mine, and the hoof-like tread ball was torn apart. The robot’s cannon was pressed into the dusty earth before it, as if using it in an attempt to right itself. Its body was pocked by fragments and scorched by explosions, and wisps of smoke leaked from multiple points.

As I got it in sight again, the legs were moving, trying to pull itself around to engage us.

I placed the front sight post over the robot, flicked my ears back in anticipation of the sound, engaged S.A.T.S., and hit the trigger.

It was more than just loud. The concussion of the gun firing hammered at my head and chest. The muzzle blast threw dust up from the ground before me. I laid out a second-long burst, surprised at how manageable the recoil was for this beast of a weapon. Down-range, small puffs of debris or fragments marked impacts on the armored robot, accompanied by several larger clouds of dirt from rounds that missed and struck the ground around it.

I paused, letting off the trigger. The robot continued to move despite the dozen massive rounds I had put into it, and I hit the trigger again, loosing another second-long burst. Even without S.A.T.S., I landed most of the rounds on-target. I saw more puffs of impacts, and something bright flashed from inside the robot. Even as the rounds struck, it continued to awkwardly lurch itself around.

As I let off the trigger, I was already shouting. “Reverse!” A moment later we lurched back down the slope, with me clinging to the gun. The last I saw of the robot was a flash of blue and yellow arcing out from its back.

The tires of the motorwagon ground in the loose soil as it skidded to a halt at the bottom of the gully, and I shouted out again. “Okay, move down the gully a bit, we’ll—”

That was as far as I got when there was another flash, the same blue and yellow as before, but shockingly bright, and followed an instant later by the blast of an explosion. Dust swirled in the air. Something struck the ground nearby with a soft thump. I hurriedly ducked down, squeezing under the lip of the armored roof beneath the gun. A few more thumps sounded around us, and something small pinged off of the hood of the motorwagon.

\leavevmode\llap{“}Holy shit,” Starlight said, though I barely heard her over the pounding of my heart in my ears.

The sporadic pattering of falling fragments soon ended, as did the rolling echo of the explosion. I got up again, grabbing ahold of the gun despite the distinct impression that I wouldn’t need it any more. “Bring us up again.” My words felt mushy in my ears.

The motorwagon lurched up the slope, coming to a sharp halt exactly where we had been before.

Through the cloud of dust and rising smoke, I could see what little remained of the Ultra-Sentinel. Its torso had been torn open by the force of the explosion, and what internal mechanisms remained were glowing red-hot from the energy that had just been unleashed. The barrel of its cannon lay a dozen yards away. I saw no trace of the rest of the weapon. All but one of the legs had been torn away from the frame. Blown-off bits of robot littered the area around it.

Up on the ridge, I could see Echo peeking over the ridge, surveying the scene before her.

I almost jumped as Dusty’s voice spoke in my ear. “I take it the bot’s down?”

I quickly hit the button on the broadcaster and replied. “Yeah.”

\leavevmode\llap{“}I’m bringing us up,” Starlight said, and the motorwagon pulled itself up the slope and came to a halt on the level ground beyond. “Wow,” she said, then laughed. “See, \textit{that’s} what I expected!”

I crouched down to look at her. “You expected it to blow up like that?”

\leavevmode\llap{“}Well, yeah,” she said, turning back to grin. “I was trying to shoot it in its power source. You have any idea how much energy a big spark battery packs? Heck, with the size of that thing, it might have had a full-on spark generator!”

Sure, wiring spark batteries with a small initiator was one of the techniques taught in my improvised explosives course, but I had never imagined the results would be quite so dramatic.

She chuckled. “Yeah. Just don’t get too near it for a while. If it’s anything like the one my mom popped, it’s probably going to be pretty radioactive for a bit.”

\leavevmode\llap{“}Lovely,” I said, casting a quick glance at my PipBuck. I’d always thought the prominent radiation gauge was a strange design choice, but it was moments like this where I could appreciate it.

We pulled up a short distance from the wrecked robot and dismounted as the rest of the group gathered.

Echo was the first, calmly strolling by us. She was frowning again. “Was it entirely necessary to destroy it so completely?”

\leavevmode\llap{“}I didn’t expect it to blow up like that,” I said, resisting the urge to be overly defensive; it had, after all, been trying to kill us. “And it’s not like we had a lot of options for stopping it.”

\leavevmode\llap{“}I suppose,” she grumbled, continuing on right past us to the wreckage.

\leavevmode\llap{“}Hey, wait,” Starlight said, taking a step forward before stopping herself. “It’s radioactive!”

\leavevmode\llap{“}That is of no concern,” Echo replied, walking straight up to the ruined robot. Her PipBuck started clicking loudly. “I am an alicorn. Radiation is as beneficial to me as it is harmful to the lesser species.”

\leavevmode\llap{“}Oh,” Starlight said, looking a little sheepish. “Right. You’re sure?”

\leavevmode\llap{“}Of course I am.” She casually lifted a few random parts, all apparently ruined by the damage we had caused and promptly discarded. “I have been in far more radioactive environments than this. I have bathed in the radiation at the heart of a balefire crater, and all that it did was make me stronger.”

Starlight hesitated before cautiously replying, “Uh, \textit{I’ve} spent hours in a megaspell crater. Had to have some RadAway, sure, but it’s not—”

\leavevmode\llap{“}Radiation diminishes over time,” Echo said, tilting her head to peer into the glowing inside of the ruined robot. “\textit{You} have been in places that have had two hundred years to dissipate. \textit{I} was there mere minutes after detonation. The radiation there would have killed you in seconds.”

\leavevmode\llap{“}Oh,” Starlight said. “I… kinda keep forgetting you’re that old.”

\leavevmode\llap{“}Age has nothing to do with it. I am referring to an event approximately three months ago.”

Starlight’s ears flicked upright in surprise. “What? There was a megaspell three months ago?”

Echo set down the leg she had been examining and looked over her shoulder at Starlight. “Of course there was. Do you really suppose that anything less than a megaspell could kill a goddess?”

\leavevmode\llap{“}Oh,” Starlight said, then her expression tightened as she realized what Echo meant. “Oh.”

Echo turned back to the wreckage. She continued her rummaging for a minute before grunting and turning her attention to her insistently clicking PipBuck. “Is there any way to silence this infernal racket?”

\leavevmode\llap{“}Oh, yes!” Starlight said, starting to step forward before once again stopping herself. “I’ll, uh… I’ll talk you through it.”

While she was doing that, Sickle came lazily walking up, her armor rattling as usual. She was frowning behind the bars of her muzzle as she looked at the wreckage. She stopped beside me, silent for a moment before looking my way. “Have fun blowing shit up?”

I wasn’t sure how to respond to that, so I just shrugged.

Dusty arrived soon after, carrying the five un-detonated mines. He gave a nod to me. “Good job.”

\leavevmode\llap{“}Thanks. Good plan.”

While he stowed the mines, Echo dropped the part she had rooted out of the robot and turned to approach us. “Utterly ruined. There does not seem to be a single component worth salvaging, and even \textit{I} wouldn’t dream of being able to repair it.”

Starlight quietly muttered, “Gee, sorry.”

\leavevmode\llap{“}Hmmph,” Echo said, frowning at her for a moment before raising her head in her usual regal fashion. “Apology accepted. With any luck, we will find some more robots, and will be able to disable them in a less destructive fashion.”

\leavevmode\llap{“}Yeah, lucky us,” Starlight said, rolling her eyes. I’m sure Echo must have seen it, but she did not dignify it with a response.

Dusty grunted as he hopped down from the motorwagon. “Lucky or not, chances are good we’ll be running into more robots. I doubt they’d have just the one.”

Echo’s ears perked up, a smile crossing her face. “Well then! What are we waiting for?”

\leavevmode\llap{“}Not much,” Dusty said, before looking over to Starlight. “We’ve just got almost two hundred pounds of gun back there to pick up.”

\leavevmode\llap{“}Oh, right,” Starlight said, already climbing back into the motorwagon. “I’m on it!”

{\br}%
The heavy doors leading into the underground compound were shut, but what could have been a tedious obstacle instead turned out to be nothing at all. I had approached the control panel knowing it was likely nonfunctional, and was instead surprised to find indicator lights glowing when I opened it. The facility still had power.

Better yet, the doors weren’t locked. A simple press of a button was all it took, and with an ear-piercing shriek of metal, the great doors slowly ground open.

There had been another robot inside the main entryway, and thankfully, it was just a regular Sentinel bot, rather than the more powerful Ultra-Sentinel. Even more fortunately, we were perfectly aware of it even before the doors opened; it was well within E.F.S. range. While it wasn’t showing as hostile, we remembered the turrets at the previous facility, and while Echo gave a weak protest to our “destructive tendencies”, we were determined to not take the chance.

Starlight stood ready with her Lancer, and I waited further back on the motorwagon’s gun. The moment the door had opened enough, Starlight took her shot.

She didn’t wait to reload, instead scurrying immediately behind the cover of the thick concrete wall, but it wasn’t necessary. The mark on the E.F.S. blinked red before winking out. When we cautiously entered, we found the Sentinel with a ragged hole blown in the upper part of its torso, still glowing slightly from the impact. It had burned deep through the front armor, severing the small head-like turret and destroying something vital inside the robot’s torso. It smoldered, but to Echo’s delight, did not explode.

While Echo immediately trotted up to the robot, her usual prim and proper behavior momentarily forgotten, the rest of us continued on. The entryway was tall and open, almost like an office lobby, complete with several benches and what appeared to be a receptionist’s desk. There was power there, too. While less than half of the lights still worked, the plain construction, lack of clutter, and white-painted walls combined to make the best of what light there was.

One side of the room hadn’t fared as well. The ruins of another Sentinel lay there, shoved up against a wall that was pockmarked and charred. A few other scorch marks marked the opposite wall, near where we came in. There had been a brief fight here at some point, though the robot was the only sign of casualties.

At the far end of the room were a set of double doors, and above them, raised and only slightly worn letters declared a greeting.

<div style="text-align:center">
\textbf{Welcome to Crystal Life Technologies}

\textbf{Experimental Site Beta:}

\textbf{Permafrost development and testing}
}

Persuading Echo away from the disabled Sentinel with promises that she could examine it after our exploration was complete, we pushed open the doors and passed inside.

Other than the occasional shadowed area where multiple lights had failed in sequence, the facility was well lit, making exploration much easier. The white paint on the walls had held up remarkably well, shielded from the elements as they were, and while it was a dull and sterile aesthetic, it also gave the place a sense of cleanliness and order that the world was in short supply of. Even the thin layer of dust on everything failed to dispel that impression.

The entryway had led to a common area, and we began our search, proceeding through the so-called atrium and into a cafeteria. Along the way, I noted a few clusters of bullet holes, scorch marks, and splotchy stains. None of us remarked on them.

Given its proximity to our entrance, the first place we examined was the kitchen. Surprisingly, the water still worked, though it is perhaps generous to call the brown murk that came out of the faucets ‘water’. There was a huge walk-in fridge and freezer setup, but its cooling system had failed at some point; we immediately closed the door when we saw the muck that had once been food, thankful that two hundred years had rendered it so decayed as to no longer have a stench.

The cabinets were better. While the bags of flour, oats, and other such goods were thoroughly ruined, there were plenty of sealed foods that appeared intact, including enough canned food to last our group for several weeks. Another large cabinet held an array of spices, many of which were still sealed.

But there was one cabinet that left Dusty in awe. When he opened it, he gazed wide-eyed into it for several seconds before quietly murmuring, “Sweet Goddesses above, that’s a lot of coffee.”

Dozens of cans were arrayed on the shelves, and he immediately noted the multiple coffee machines nearby. “We’re definitely taking these,” he said.

Starlight, on the other hoof, left the kitchen beaming, with almost a dozen cartons of snack cakes tucked into her bags.

As for myself, I tucked away a full set of utensils, as well as a proper plate, bowl, cup, and even a real can-opener. It felt slightly strange just how pleased I was about the acquisition.

It was soon perfectly clear that our initial impression was correct: the place had never been looted. Our next stop was the facility’s medical clinic, its supply untouched.

\leavevmode\llap{“}Dibs,” Sickle said the moment we opened the drug cabinet to find the stock of painkillers.

\leavevmode\llap{“}You can have \textit{most} of them,” Dusty allowed. “We need to keep a few for actual medical use.”

\leavevmode\llap{“}Sure, sure,” Sickle said, popping open one of her cargo cans to shovel in the bottles and vials.

The drugs were far from their only supplies, of course. We found bandages, splints, saline, antibiotics, RadAway, and enough healing potions for everyone to take a couple, with a few more left over as spares. There was even an autodoc, powered and functional, though we could hardly be displeased that we had no need of its services at the time.

There were a few more support sections, dealing with things as mundane as laundry or as critical as power and water purification. While the centuries had been rough on the equipment, a fair amount of it still worked. The spark generators powering the facility were obviously functional, but Starlight immediately trotted past them to a small cluster of equipment at the back of the room, with all sorts of displays, conduits, and machinery. She looked at the various dials and displays, and began fiddling with the controls.

\leavevmode\llap{“}What are you doing?” Dusty asked as we approached.

\leavevmode\llap{“}I’m just checking…” She flipped a large switch, and when a large button started flashing red, pressed it. There was a soft thump and a flicker of lights on the display panel, before a machine about the size of a small oven hummed to life, a light above it coming to life.

Starlight turned to us, grinning. “They’ve got a set of backup spark generators,” she said proudly, and placed a hoof atop the machine. Three more stood beside it. “And they still work!”

\leavevmode\llap{“}Could be useful,” Dusty said. “Think it could power the motorwagon?”

\leavevmode\llap{“}Probably!” Starlight patted the humming machine. “Heck, even if it isn’t enough to run the thing, we can use it to recharge when we’re stopped. No more worrying about running out of batteries!”

\leavevmode\llap{“}Sounds good.” Dusty sat, raising his PipBuck to poke a couple times at it. “Okay, got it marked for later, we’ll see if we can remove it safely once we’re done checking the rest of the place.”

The rest of the front section of the facility was almost entirely living spaces. Most looked like they had been abandoned quickly, with personal belongings still laid out, untouched for centuries. It was eerie, as if all the ponies here had simply vanished.

A few rooms had details that dispelled that imagery. Walls that were gouged and scorched by weapons fire. A desk riddled with fragments. An upturned bed, laid as if to create a defensive position, with a dark stain running down to the floor.

But still, no ponies.

During our exploration, we came across several destroyed turrets, and only a couple of functioning ones. Starlight dispatched them with the same trick-shot she had used before. We also came across the wreckage of a few more robots, much smaller than the Sentinels and with multiple spindly arms. Despite that, we didn’t find a functional one until we reached the accessway leading to the rear half of the facility.

We gathered outside the doorway leading into the short hall. According to our E.F.S., a non-hostile contact was just beyond. Dusty cracked the door open to let Starlight check with her mirror. She floated it out in her magic, then quickly drew it back. “Yep. Another Sentinel.”

Dusty nodded. “Take it out.”

\leavevmode\llap{“}Fuck that,” Sickle said, pushing forward. “\textit{I’ll} take this one out.”

Dusty quickly stepped forward to block her path. “Sickle, that thing’s armed to the teeth. If it turns hostile before you get to it, it’ll mulch you.”

She shoved her face close to his. “Fuck you, Dirt! I’m here to fucking fight, and I’m tired of sitting back hoofing myself while you cunts are having all the fun!”

\leavevmode\llap{“}Don’t blame me for that,” Dusty said, glaring back. “When your entire tactical range consists of ‘run up and kick the thing’, yeah, sometimes you’re going to have to sit back ‘hoofing yourself’.”

Echo stepped in. “Perhaps we could find a way of disabling this one without destroying it?”

A sharp crack and flash of red silenced the conversation. Starlight drew her Lancer back, turning a flat glare at the arguing ponies. “There, it’s dead. Can we move on, now?”

\leavevmode\llap{“}What?” Sickle shoved past Dusty to look through the doorway, then trotted in. By the time I had followed the others in, she was at the ruined robot, and was already starting to snarl. “You fucking… fuck!” She spun around, kicking the ruined robot into the wall.

Echo bound past me, calling out, “Stop that!”

The room itself looked like another lobby, only this time, past the receptionist-style desk, there was a massive blast door at the back. It wouldn’t have looked out of place at the front of a Stable, aside from not being circular. It stretched from floor to ceiling, and a sign beside it was labeled “Secure Labs”.

I kept half an eye on Sickle and Echo to make sure they weren’t about to get into a fight over the robot, while Dusty and Starlight approached the door. Starlight poked a button on a panel set in the wall beside the door. It beeped angrily at her.

\leavevmode\llap{“}It’s locked,” she said, ears flicking back.

Dusty stood beside her, frowning. “Hmm… it’s a keypad lock, right? Do you think Whisper could hack the lock?”

I sighed. “I don’t think ‘hacking’ works the way you think it does.”

He looked back at me. “...That’s a no?”

\leavevmode\llap{“}Most likely, it’s an independent system that isn’t connected to any other computer, so I’d have to get into the physical circuitry of it, and at that point, you could just physically bypass the whole thing. You don’t need to do anything with the computer. Even that’s assuming they used a spell matrix complex enough to even qualify as a proper computer.”

\leavevmode\llap{“}Good luck on getting into this thing,” Starlight said, peering at the panel itself. “It’s recessed three inches into a concrete wall and reinforced with steel plate.” She tapped it with a hoof. “I could maybe get into it, but it’ll take time. Hours, probably.”

\leavevmode\llap{“}Well, I don’t intend to turn around empty-hooved,” Dusty said. “Get started. We can wait.”

I gestured back to the receptionist-style desk nearby. “I might not be able to hack the keypad, but I can at least see if there’s any record of the passcode.”

\leavevmode\llap{“}Sounds good.”

I walked around behind the desk, with its terminal and surprisingly plush office chair, which had held up remarkably well for two hundred years of disuse. Settling in, I reached out and hit the power button on the terminal, which beeped and whirred as it booted up.

I then promptly ignored it, opening the drawers, starting with the shallow pen drawer just below the keyboard. Various writing implements and papers filled the space. It took me only a few moments to find what I was looking for: a sticky note stuck to the bottom of the drawer, near the back. I closed the drawer.

\leavevmode\llap{“}Hey, Starlight,” I called out, catching her attention. She hadn’t even gotten all her tools out, yet. “Try A-B-one-C-three.”

She blinked in surprise, then turned to the panel. There were five beeps as she pressed the keys, followed by the deep thumps of the door unlocking. A warning buzzer sounded, and with a squeal, the door slowly swung open.

\leavevmode\llap{“}Holy crap,” Starlight said, then turned to flash me a grin. “Well that was quick!”

\leavevmode\llap{“}I’m good at what I do,” I said with a smile.

The screen before me flashed as the computer finished booting. It didn’t ask for a login, instead immediately going to the main screen. It seemed the computer had been wiped clean, save for a single message. I opened it.

\terminal{
\textit{Okay, it’s simple, but I don’t have a lot of time, and I **really** want someone to be able to get in, so… 13: NO1P3.}

\textit{Yeah, yeah. My crypto teech would be ashamed. And if this **is** Goldbug, I’m sorry you had to see that, please don’t leave me.}

\textit{Also, fuck irony. Like, seriously.}

\textit{CoolBugz}
}

\leavevmode\llap{“}You okay?”

Starlight was beside me. I hadn’t noticed her approach.

\leavevmode\llap{“}Yeah,” I said, hitting the power button. The terminal whined as it powered down, and I heaved a sigh. “They were here. It was a message from my hive.”

She wrapped a foreleg around my shoulders, giving a squeeze. “That’s good, right? This place still has power!”

\leavevmode\llap{“}Yeah, that’s good.”

But I was thinking of an earlier C.L.T. message I had seen. I remembered the remarks about the mortality rate of Permafrost. I remembered how the Sweetdreams project—which had failed all but one of the changelings relying on it—was the ‘safe’ option.

And if the irony referred to was what I thought it was, I was very likely about to find several more of my deceased sisters.

{\br}%
The secure labs were extensive, with a great amount of equipment, both scientific and industrial. The hum of machinery was ever-present, with overhead conduits pumping fluids and air. One water pipe had broken and collapsed, bringing some of the lighting down to block a hallway, but it had either ran out of fluid or some automated system had closed it off.

Each lab was a large, open space, with tables loaded with scientific equipment and abandoned papers. The first one we entered had a freezer the size of a small skywagon set against one of the walls. Tubes and wires ran from it, and it hummed quietly, still functioning after all that time.

A frosted window gave a view in, and a switch conveniently labeled “lights” illuminated the inside well enough for us to see. Inside were dozens of cylinders arranged on shelves, each with a simple lid, and so frosted over that we couldn’t discern any markings.

I looked over the table nearby for any documentation that might suggest the contents. The first thing I found was a lazily scrawled note.

\textit{I know we can’t afford proper test subjects, but I never expected management would accept that proposal. It was a dumb joke made in frustration. I didn’t think they would take it seriously. After the idiotic budget cuts, I thought they’d stick us all on cheap “theoretical” research, if they didn’t throw us out altogether and close shop. Instead they do this. I don’t know what to think any more.}

\textit{But now we have alternative test material, and even if it’s far from ideal, everypony here is eager to continue testing. All the doom and gloom of the budget cuts has been forgotten.}

\textit{Speaking of which, the results of the initial tests:}

\textit{The Neighapolitan was bland to the point of vileness. Seeing as this is identical to its pre-Permafrost state, this would suggest everything is working precisely as intended. More “scientific” testing revealed only a fractional percent of crystallization in the outermost layers (See report \#212618), and none in the inner layers. The difference in patterns was peculiar, a complete reversal of the previous issues during cryo-set. It would seem we overshot our corrections. Ice Topaz noted additional crystallization in the container itself, which may warrant investigation. I doubt the solution to all our problems is some cheap waxed cardboard, but it would be rather amusing if this lark actually produced something substantial.}

\textit{Ice Topaz claimed “dibs” on the rocky road for tomorrow’s tests. She can have it. I have my eyes set on a nice, quality vanilla bean that I am certain will be scientifically enlightening.}

Starlight stood beside me, her head cocked to the side as she read. “Scientists are weird.”

The door of the freezer rattled loudly, and we turned to see Sickle pull at the handle, then growl and kick at it. “Damnit. Open this shit up!”

\leavevmode\llap{“}Sickle, this is a cryogenics freezer,” I said. “It’s probably very—”

\leavevmode\llap{“}I don’t give a fuck!” Sickle snarled, and with a powerful kick of her forehooves, sank her leg-blades almost an inch into the freezer door. “I ain’t had ice cream in like ten fucking years, so either figure out how to unlock this shit or I’m tearing it open!”

I stared for a moment as I made connections. Then I nodded. “Okay. It might take a minute to figure it out.”

She pulled her blades free, sitting heavily on her haunches and glaring at the door while I got to work, looking over documents and the freezer’s switches and dials.

Starlight stood back, murmuring, “Didn’t think she had such a thing for ice cream.” In a more conversational tone, she added, “The only ice cream I ever had was some freeze-dried brick from some military rations. It tasted like chalk.”

Sickle merely grumbled, staring at the door.

Fortunately, like any good lab, they had detailed checklists of how to operate their experimental equipment. A binder beside the freezer detailed the steps to reverse the cryogenic process, and an insert noted the alterations to procedure to bring the subject temperature to just below freezing, rather than all the way to room temperature. Within a minute, I was watching the temperature dial steadily climb, while warning lights blinked over the door. Finally, the temperature reached the desired temperature. The warning lights went out, a green indicator light turned on, and with a soft thunk, the door unlocked.

Sickle shoved past us, wrenched open the door, and started rooting around. I returned to the side of the freezer, watching through the window. She filled the cramped space, bumping against racks as she scraped the frost off several tubs of ice cream. She eventually found what she was looking for, snatched it up, and backed out.

As soon as she was free, she tore off the container’s lid before looking to me. “Give me one of those fucking spoons you grabbed.”

I didn’t argue. I simply levitated out a utensil and passed it to her. I could always get more.

She snatched it from the air, then sat, slapping at the clasp of her helm’s muzzle to let it dangle free. Then she dug the spoon into the ice cream—strawberry, I noted—and took a bite.

Sickle sat still for a long, tense second, then let out a slow, pleased sigh, the tension fading from her body. She even smiled as she took another big scoop. “Fuck. I almost forgot how good that is.”

Starlight was staring. She opened her mouth to say something, but thought better of it, shook her head, and wandered off.

We continued searching, with Sickle trailing behind, eating her ice cream.

The next lab contained another cryogenic freezer, much like the previous, though with a good deal more wiring and an attached terminal. It had a light switch in the exact same place as the last. I flipped it, expecting to find something similar to the previous freezer.

I almost staggered when I instead saw four changelings, frozen in place.

They lay on metal trays, unmoving and frosted over, with wires connected at various points on their bodies. For a moment, I simply stared at the scene, heart pounding. Then I stepped up to the window and looked closer, hunting out details.

I could tell they weren’t in the greatest of condition. I could see cracks in their exoskeletons, with frozen crystals clustered around them, as if they had burst out from the carapace. One was frozen in mid-grimace, as if they’d been in pain.

There wasn’t much I could do from there. I hurried over to the terminal, which quietly hummed away, still on after all this time.

Starlight was at my side, barely restraining a grin. “Are they okay?”

The screen displayed a log of status updates, sorted by “test subject”.

I loaded up the first.

\terminal{
\textit{+00:00:21 - Caution: freezing rate variation exceeding safe tolerance, crystallization likely.}

\textit{+00:00:38 - Caution: crystallization detected in surface layers.}

\textit{+00:00:42 - Warning: crystallization exceeding 0.1\% in surface layers. Abort recommended.}

\textit{+00:00:48 - Danger: intracranial crystallization detected. Abort immediately!}
}

But there had either been noling there to abort, or they ignored the warnings, reasoning that a risk of death was better than the near-certainty they would face outside. I couldn’t even guess which of those scenarios had happened.

These would have been intelligent changelings. They would have done their research. They must have seen the same mortality rates that I had seen. They must have known that the odds of surviving were not in their favor, but they still went through with it.

The rest of the log was filled with more of the same. Updates on crystallization levels in different layers and organs. Notices of damage caused by the uneven freezing. The eventual critical damage to circulatory and nervous systems, finally ending with the inevitable conclusion:

\terminal{
\textit{+00:01:43 - Notice: intracranial damage exceeds survivable levels. Subject Alpha deceased.}
}

I numbly switched to the other logs. Beta had been declared deceased for similar reasons. Delta had extensive fractures all along her back from aggressive crystallization, severing her spine in multiple locations before further fractures formed in her skull, killing her.

But Subject Gamma lacked a declaration of death.

\leavevmode\llap{“}The third one,” I croaked, then cleared my throat, pointing to one of the frozen changelings. “She might still be alive.”

Dusty looked back to me. “Might?”

\leavevmode\llap{“}She’s in bad shape,” I said, my throat tight. “There’s… heavy damage to her heart, liver, both kidneys, and one lung. Multiple splits in her carapace. Several torn arteries. Burst vessels in the brain. It’s… it’s bad. Really bad. But we’ve got a lot of healing potions.”

Dusty frowned, his voice softening. “That’s a lot of damage for some healing potions.”

\leavevmode\llap{“}We have an autodoc, too!” I swallowed past the lump.

He remained silent for several long seconds before slowly nodding. “It’s your call.”

I froze, considering the situation. I knew what I \textit{wanted} to do, but I needed to stop, think, and be sure I was doing the right thing. The more I thought on it, the more convinced I was that it was the right course. Short of finding a completely intact pre-megaspell medical center with an inexplicably still-living staff, we were as good as we were going to get.

\leavevmode\llap{“}I don’t think we’ll ever be better prepared for this.”

Initiating the thaw was even easier than the last time. I simply told the terminal to thaw them out, and it did all the work. I simply stood back, trying not to fidget and fret too much.

The wait was painful. Almost a minute passed before noticeable progress was made. The needle on the thermometer started steadily creeping up. There were no visible changes until it finally approached the freezing point. Soon the frost was melting, water trickling and then steadily flowing from their bodies. Soon it was joined by a thin trickle of blood seeping from old wounds.

Subject Gamma—I had no real name for her—twitched as she thawed, her right legs weakly kicking in a spasmodic rhythm. I wasn’t sure what was causing it, but I could imagine it wasn’t good.

The terminal beeped softly. I looked at the screen.

\terminal{
\textit{Beginning resuscitation.}
}

There was a flicker of magic across Gamma’s head and chest. I jumped as she reacted violently, her back arching, her body going rigid and spasming, rattling around on the metal tray. Blood was flowing steadily from the cracks in her carapace.

Starlight stepped back, a hoof going to her mouth. I rushed past her to the door, already digging out potions. It rattled, still locked. I looked up at the warning lights, waiting for the moment they changed and the door unlocked.

The instant it did, I threw open the door, rushing in. The inside of the cryo-freezer was balmy and hot, and filled with the rattling and banging of Gamma’s thrashing. I was at her side immediately, hooves going to her head to hold her as I brought a potion over.

Her jaw was clenched tight, half muting her gurgling grunts. There was no coordination or intelligence to her movement, just mindless spasming. I gave up my attempts to open her mouth, instead pouring the potion over her teeth, hoping enough would get inside.

But I knew that was hopeless. “We need to get her to the autodoc!”

\leavevmode\llap{“}Here,” Dusty said, moving up behind me. “Get her on my back.”

Echo’s powerful voice cut through the racket. “Give her to me. I will see her there!”

I hesitated, but she did not. Gamma was already floating in the purple glow of Echo’s magic. There was a momentary pause as Echo’s eyes met mine. Then, with a purple flash and soft pop, they were gone.

I shoved past Dusty and broke into a gallop, ignoring the returning pounding in my head and the varied terrifying scenarios playing out in my mind. My hooves skittered on the smooth floor as I pushed myself, rushing out from the secure labs to the front of the facility.

I practically slid into the medical clinic, to find Echo standing there, securing the spasming Gamma in the autodoc. She didn’t bother sparing me a glance. I stood there, panting, as she closed the autodoc’s door.

The device beeped, noting its subjects unrecognized physiology, and asking if we wanted it to make its best guess at treatment or abort. Echo looked to me, and I quickly hit the button to approve treatment.

It whirred to life. The screen started listing injuries. Many were the same as I’d seen before, but now there were new ones. Blood volume was down. Her heart had stopped again, having gone just long enough to cause serious intracranial hemorrhaging.

I watched the text updating on the screen as the autodoc tried to patch up the damage while resuscitating her. I was still watching as the chaotic brain activity came to an end. The machine switched entirely to resuscitation and life support.

Starlight had sat beside me. Her foreleg looped around my shoulder, comforting and familiar. I simply stared, waiting, hoping.

Minutes stretched on. Brain activity remained at zero.

I’m not sure how long the machine continued in its steadfast attempt to resuscitate Gamma. My perception was focused entirely on that screen, barely even aware of my companions around me.

Eventually, the message disappeared, replaced by a red alert: <i style="font-family:IBM Plex Mono">Patient deceased}.

I slowly sank into Starlight’s embrace, sinking my face into her chest as the tears finally came. We sat there for a long time, holding onto each other as I silently cried.

Once more, I had found my sisters in their bid for survival. Once more, I had found only death.

Even if I had expected that outcome, it was still painful. Until then, I could hold out hope.

The tears eventually came to an end. I sniffled, straightening and wiping at my cheeks. Starlight was red-eyed, her cheeks wet. She met my eyes, her expression full of sympathy and concern.

I’m so very glad she was there. I reached up, giving one of her hooves a gentle squeeze that she returned. Then I swallowed the heavy lump in my throat, rose to my hooves, and continued on.

I returned Gamma to her companions, wondering who she had truly been. Was this CoolBugz, a sister I had only known through a false name in scattered C.L.T. systems?

I gathered them together, so unlike the other sisters I had committed to the flame. These were no empty husks, or even decayed ghouls. They were preserved, almost lifelike past the cracks in their carapaces. It was a raw sensation, something that I couldn’t distance with the centuries that had passed. Gamma might have been killed by the cryogenic process two hundred years ago, but she died right before me.

The green fire consumed them all the same, granting them one final transformation.

I remained sitting there for a while, trying to gather my thoughts. Starlight remained sitting by my side the whole time. Dusty tried to say a few comforting words, but I didn’t really hear him. I’m not even sure what Echo was doing. She was probably just passively observing. I barely even noticed when Sickle sat heavily beside me, despite the crash of metal.

But I did notice when, a minute later, Sickle held the tub of ice cream in front of me. I stared down at it, uncomprehending. It was only half full, and the ice cream half melted, with a thoroughly messy spoon speared into the middle of it. It just remained there. Then she gave it a wiggle.

I almost declined. I wasn’t hungry, or in the mood for treats, but then it clicked. The meaning of the gesture.

My magic took hold of the spoon, scooping out a bite of half-melted ice cream.

It was pretty good.

Sickle reclaimed the spoon, taking a much larger scoop for herself, then gave me a solid pat on the shoulder. In usual fashion, it was a jarring impact, and I’m sure the spikes would have drawn blood if not for my armor and exoskeleton. Still, I didn’t mind.

Instead, I rose to my hooves again, and we walked silently away from the ashes.

Dusty cautiously mentioned that we should still search the rest of the facility, as if concerned that I would take offense to getting back to business, but I soothed that concern by agreeing. I can’t say I was enthusiastic about it in the slightest, but I knew I had to move on. It’s not as if there was much left to explore.

The rearmost labs were the largest yet, with rows of lab tables at one end, a bank of cryogenic freezers set in the wall at the other end, and an array of ancient medical and examination equipment in between. A ring of lights had been rigged over the equipment in the middle, to give plenty of light when working, but they had fallen at some point in the past, crushing lighter equipment and scattering broken glass around the middle of the room. Otherwise, the room was quite intact, if a little dim.

We made our way past the lab tables and their scattered papers. I paused to shine my flashlight over some of them. I’m not entirely sure why. The few legible documents mostly discussed chemistry and thermodynamics that I didn’t understand, and even if I did, would have been completely irrelevant to me. Still, it was information, and I was there. I needed something to do.

Leaving that behind, we picked our way over the glass-strewn floor to the freezers. Starlight was first, bounding up onto a medical bed and hopping across to a clear spot of floor. I lagged behind, starting to pick my way across the floor, until the sight of my own holed legs reminded me that I wasn’t mimicking an earth pony. I spread my wings, flying across the rest of the floor in a short hop.

Echo simply appeared in a flash of purple. I naturally looked to see the source of the bright flash. When I looked back to Starlight, I froze.

She had her hooves up on the rim of the frosted freezer window, her flashlight floating beside her. She was staring through the window, her eyes wide and ears back. “Uh… Whisper?” She looked my way, her expression uncertain, maybe even unnerved.

I stepped forward, nervously placing my forehooves on the rim and rising up to look inside.

The interior was dimly lit. Most of the freezer’s contents were visible only as a multitude of rounded silhouettes. There were dozens of them, maybe even hundreds. Starlight’s flashlight was still floating in place, piercing the gloom. Its beam illuminated the closest of these identical shapes, and I fixated on it, staring, barely able to comprehend what I saw.

It was a changeling egg, perfect in every way.