While Starlight celebrated, I sat, and I thought.

I was no longer the only member of my hive. One hundred and twenty three eggs were held in cryogenic suspension. Every one had been meticulously hooked up to medical scanners, allowing the lab’s computer to monitor and record their status.

I had searched through those logs. Entry after entry came up clean. In the end, only a single egg had any warning over uneven freezing and crystallization, and even that was well below the threshold the program considered hazardous. They had all survived.

Starlight had stood nearby, waiting and watching. I could see her holding back the nervous excitement as I continued searching the logs. When I finally allowed a smile to show, she grinned and cheered, hopping around in excitement.

And so, she celebrated, while I sat, the smile fading away as I considered my new situation.

I do not mean to say that I was disappointed. I wasn’t. I was so wonderfully relieved to have found something after all of my searching. At the same time, I had hoped the changelings I had found would be \textit{adults}, individuals who could help with the many difficulties our hive would face. Experts that could help us rebuild, perhaps even soldiers and other Infiltrators that could help combat the threats rising in the Wasteland. Instead, I had one hundred and twenty three eggs, all dependent on me.

So, while I wasn’t disappointed, I was concerned.

It was several minutes before Dusty approached me. “Something wrong?”

\leavevmode\llap{“}No,“ I said, giving another weak smile, but it faded away almost immediately. “Not exactly. I’m just thinking.”

He nodded, but he seemed to pick up on some of the seriousness of the situation. “About what?”

I considered brushing it off, but this was something that needed to be addressed, and to be honest, something I thought needed to be discussed.

I stood, turning to face the rest of the group. Starlight immediately stopped, grinning at me. Echo stood nearby, tall and proud, though a hint of a smile touched her lips. Off to the side, Sickle lay kicked back against a cryo-freezer, the mostly empty ice-cream container resting on her belly.

\leavevmode\llap{“}Everyone,” I said, looking around at them. “First off, I wanted to say… thank you. Thank you for helping me. You’ve gone out of your way just to help me find my hive when it would have been easier to just walk away. I couldn’t have done this without your help.”

\leavevmode\llap{“}Of course we had to help!” Starlight said, laughing softly.

Dusty nodded along, giving a soft smile. Sickle grunted something unintelligible.

\leavevmode\llap{“}That said… I have concerns.” With my words, Starlight’s grin instantly vanished. I continued on. “My hive will survive, but it’s still in a tenuous position, and its recovery will be even slower than I had expected. There are more than a hundred eggs. I… I can’t raise all of them on my own. I can’t \textit{feed} all of them on my own.”

Starlight immediately spoke up. “We can help! I mean, I can help.”

\leavevmode\llap{“}I appreciate the offer, but there are too many, even for all of us. They’ll need to be fed, cared for, educated, and protected. The best scenario I can think of is raising a small number of them until they’re old enough to help raise more. It means my hive will recover, but it’s going to take time. We’re talking two, maybe three generations before my hive becomes self-sufficient. Decades. Until then, it’s going to be in a very fragile state. It will be vulnerable.

\leavevmode\llap{“}Right now, those young changelings are safe and stable. It would be... \textit{irresponsible} of me to put them in danger. I can’t thaw them now.”

Starlight stepped forward. “But—”

I held up a hoof. “Not yet. They almost died once, already. I can’t waste the opportunity that’s presented itself. I have to do what I can to make sure the world is \textit{safe} for them.”

\leavevmode\llap{“}What exactly did you have in mind?” Dusty asked.

\leavevmode\llap{“}Serenity,” I said. “They’re already a problem. Whatever it is they’re doing, it’s going to be bad for ponies. Even speaking in purely practical terms, my hive will need peaceful, friendly ponies, and Serenity puts that in danger. And if they should find out about my hive? I don’t doubt that they’d put every effort into wiping us out completely.

\leavevmode\llap{“}I can not in good conscience hatch these changelings with a threat like that looming over them. Not until Serenity has been stopped. Since I’m the only active Infiltrator in my hive, that means the duty falls to me.”

Dusty was frowning, thinking. “That’s a pretty big thing you’re talking about. Maybe you should think a bit on it before deciding.”

\leavevmode\llap{“}I’ve been thinking about this for days, now,” I said, slowly shaking my head. “This isn’t an impulsive decision. This is something I need to do, for both my hive and for the other people of the Wasteland.”

\leavevmode\llap{“}If you’re sure,” Dusty said. “What are you thinking?”

\leavevmode\llap{“}Serenity has two primary advantages,” I said. “So we destroy those.”

\leavevmode\llap{“}What, the big fortified base and huge army?” Starlight asked. “How the heck do we do that? I mean, I guess we do have some balefire eggs…”

\leavevmode\llap{“}Those are powerful, but too small to wipe out an entire Stable. Besides, those aren’t the advantages I was referring to.”

She cocked her head. “What \textit{did} you mean?”

\leavevmode\llap{“}Their first advantage is their secrecy. Most ponies don’t even know Serenity is out there. A few do, and some are spreading the word, but even they don’t know the details of Serenity’s capabilities. They don’t know how changeling Infiltrators work, what kinds of tactics and options they have, or how to effectively combat these changelings. I do. My hive has always tried to aid ponies with knowledge and assistance, working behind the scenes. My hive’s survival is going to depend on working with ponies, maybe even more openly than ever before.”

Dusty was slowly nodding. “Information is good. Good intel was one of the best advantages we could hope for, when I was in the Rangers. Still… I’m sure Serenity has near-perfect intel on every settlement around, and nopony has the forces to oppose them. Not even those Enclave guys.”

\leavevmode\llap{“}Which is their second advantage: unity. They can focus all of their efforts against enemies that are completely disorganized. Right now, Serenity has the opportunity to pick apart ponies one settlement at a time. There is no unified front, just a bunch of small, easily defeated groups. Some of them are a hair’s breadth from fighting each other. If ponies don’t pull together, they’ll be picked off one-by-one.” I looked around the group. “We already saw that at Rust.”

Starlight’s ears drooped. Dusty’s expression, on the other hoof, hardened.

\leavevmode\llap{“}We can’t fight them on our own,” I said. “Nobody can. The only way I can see for overcoming Serenity is going to as many ponies as I can, impress upon them exactly the level of danger we’re all facing, and convince them to work together to face it.”

Dusty gave a dry snort. “Oh, is that all? Shit, most settlements can’t even agree to things within their own walls.”

Starlight nudged him, managing a smile. “I dunno. If anyone can talk everypony into doing something, it’s Whisper.”

\leavevmode\llap{“}I don’t expect it will be easy,” I said, “but a mutual threat can be a strong motivator to cooperate, and I expect I can leverage that to our advantage. Even if I can’t get everypony to work together, getting the information out will weaken Serenity’s position, perhaps enough that those who do band together will have a fighting chance.”

\leavevmode\llap{“}And if they don’t?” Dusty asked.

\leavevmode\llap{“}Then we lose nothing that we wouldn’t have lost, anyway,” I said. “The alternative would be to stand by and do nothing. Let hundreds or thousands of ponies be conquered, enslaved, or killed, and give up on any chance of my hive being able to thrive as it once had.”

\leavevmode\llap{“}Yeah, yeah,” Dusty said, waving a hoof. “I get it. Shit. I don’t particularly \textit{like} it, but I get it.”

\leavevmode\llap{“}I don’t like it, either,” I said, “but I think this is something I have to do.”

\leavevmode\llap{“}Yeah,” Dusty repeated, then sighed. “I see some problems with that idea, though.”

\leavevmode\llap{“}What’s that?”

\leavevmode\llap{“}Serenity’s already hit one settlement. We might not have much time. We also don’t know if we can even walk into Mareford without being shot. Sure, you can go in on your own, but the rest of us are all wanted ponies.”

\leavevmode\llap{“}I am not,” Echo said from behind him, but he waved off her retort.

\leavevmode\llap{“}The point is, it’s going to be hard dealing with Mareford, and she’d be basically on her own in a town we \textit{know} has been infiltrated before.”

\leavevmode\llap{“}It wouldn’t be the first time,” I said, “but that was when acting as an Infiltrator, impersonating a common citizen, rather than making myself the focus of attention. Given my recent experience, I’d much rather be able to have you nearby.” I cast a glance around. “That is, assuming you wish to help.”

\leavevmode\llap{“}Of course!” Starlight said, grinning.

Dusty nodded. “If there’s a way to help ponies against Serenity, I’m all for it.”

Sickle made a vague, quiet grunt.

We looked to Echo. She was frowning, looking at me for a second before speaking. “Given your combination of persuasive argument skills and remarkable stubbornness, I presume any attempt short of physical restraint would fail to dissuade you, and I am still in need of you for my research. Very well, I shall assist.”

\leavevmode\llap{“}Thank you,” I said, sharing a smile. Then I turned back to Dusty. “Mareford is still a possibility, but there might be other places to start. If we can get other groups involved, we might be able to use that to leverage Mareford. You know more about the political disposition of settlements in the region. Any suggestions?”

\leavevmode\llap{“}Well…” He frowned, thinking for a moment. “Mareford isn’t the only big settlement. There’s also Trotsen, and we’re closer to it than Mareford. The two towns are trading partners. If we can get Trotsen in on this, that’s going to carry a lot of weight, and would give a good way to catch Mareford’s ear.”

\leavevmode\llap{“}Starting big is probably a good idea,” I said, nodding. “Smaller settlements may be hesitant to commit if they aren’t sure the bigger settlements are in.”

\leavevmode\llap{“}I have my doubts that they’ll be willing to work together,” Dusty said. “They might be trading partners, but the towns aren’t exactly friends. Still, it’s worth a shot, and even if they don’t act together, at least we might get them all acting. And hell, getting Trotsen stirred up could be useful on its own. They’re about the only force around that could compete with the Mareford Militia.”

\leavevmode\llap{“}Oh?”

Dusty nodded. “Yep. The Militia is the better fighting force, mind you. More disciplined, better trained, and better equipped. Then there’s the Rangers, who are even better. Still, Trotsen has at least a dozen combat-focused motorwagons, and that’s just what we know about. Mareford has a pair of whirligigs, but that’s only enough to move a couple Ranger teams. The mobility Trotsen has in the field is a huge advantage.”

\leavevmode\llap{“}I can certainly appreciate the advantage of mobility,” I said, thinking of our own motorwagon. “Though I imagine Serenity tops everyone in that regard.”

\leavevmode\llap{“}Not the Enclave,” he noted. “Though it seems they’ve got their own fight.”

\leavevmode\llap{“}If we do get other settlements to work together, we might try approaching them again,” I said. “They don’t want to compromise their own fight, but if we show them we’ve got a good chance of beating Serenity without excessive expenditure on their part, they might be willing to pitch in. I think I might be able to use the \textit{Cumulonimbus} as a point of leverage. Despite how Commander Aurora dismissed it, I imagine they don’t like the idea of their own ship being in the hooves of a genocidal enemy of ponies.”

Dusty frowned at that, but nodded. “Yeah, I imagine not. Be careful pushing it too hard, though. If she realizes you’re trying to—”

\leavevmode\llap{“}She’d be upset, yes,” I said, giving a lopsided smile. “People don’t tend to like being manipulated, and military types tend to be more \textit{forceful} about it.”

Dusty gave a single chuckle. “Yeah, just a bit. So… Trotsen?”

I nodded.

\leavevmode\llap{“}Okay, then,” he said, giving one final nod and turning to the others. “Let’s get—”

\leavevmode\llap{“}Wait,” I said, holding up a hoof. “There’s one more thing, first.”

He cocked an eyebrow, but listened.

\leavevmode\llap{“}I’m hesitant to ask it, but… I need to ask you all a favor.”

\leavevmode\llap{“}Sure!” Starlight replied, then asked, “What is it?”

\leavevmode\llap{“}I’m… rather uncomfortably aware that I am here at least partially by chance. There have been several times that I could have easily died. One lucky shot, a random piece of shrapnel, almost anything. Chances are, my odds of dying were probably better than my odds of getting here.”

Starlight’s smile had vanished, her eyes widening a touch in alarm. “What are you saying?”

\leavevmode\llap{“}I’m saying that, right now… I’m the only \textit{active} member of my hive. I’m the only member able to do anything, and the only one carrying our knowledge and values. If I were to die, they would be on their own. Taking on Serenity, it’s going to be dangerous. I’m already a target, and spreading the word about Serenity is going to catch their attention. I’ve been fortunate to get this far, but it would be irresponsible of me to endanger the future of my hive. So, I want to ask all of you for a favor.”

They watched and waited intently as I sat. It was difficult to say what I had to say. “I’d like to ask you to promise that, if I die, one of you will come back for them. That… if you’re the last one of us left, you won’t keep fighting. You’ll save yourself, leave, and come here. That you’ll make sure they still have a chance at life.”

Starlight’s ears had drooped as she slowly nodded. “Y-yeah… but we’re not letting you die.”

Dusty was frowning, looking down at the ground as he considered the request. “I don’t know. That’s…” He looked up, meeting my pleading eyes. He stared silently, as if trying to come up with a suitable argument, but he couldn’t hold my gaze. He instead looked over at the freezer, with the hundred-plus eggs within. His ears flicked back, and he sighed. “Yeah.”

\leavevmode\llap{“}Well,” Echo said, “I suppose if you were to get yourself killed, I would be in need of another helpful changeling, anyway, and I do imagine a child would be more amenable. Still, I would prefer if you do not die, so I shall do my best to ensure your safety. I can shield you from harm just as well as I can shield myself.” She cocked her head to the side, looking off into space as she mused, “Perhaps I could repair that power armor you have acquired. It would certainly improve your odds of survival.”

\leavevmode\llap{“}Thank you,” I said, feeling my throat tighten just a touch. I swallowed past the lump, doing my best to ignore it. Instead, I lifted my PipBuck-clad leg, touching a hoof delicately to the device. “I’ve been making recordings about what’s happened to me since waking up. I’ve talked a lot about my hive and its values. I’ve been keeping it all heavily encrypted, but… I’m going to decrypt the files. I’ll leave a copy of what I have here, maybe give you guys copies, too, but I’m going to be recording more. If I don’t make it, I’d like you to copy those files so these changelings can hear it. So they know who they are, where they come from.”

Starlight was nodding. “Yeah,” she said, her voice ever-so-slightly strained. “Now can we stop talking like you’re going to die?”

I gave a soft, reassuring smile. “I don’t plan on dying, but it would be irresponsible to not account for the possibility.”

Starlight stepped forward and wrapped me in a tight hug, her words coming out slightly choked. “Will you \textit{please} stop being so depressingly practical for a bit?”

I couldn’t help chuckling slightly as I returned the hug. “Okay. I’m done.”

\leavevmode\llap{“}Good,” she said. She still kept hugging me.

When she didn’t immediately stop, Dusty spoke up. “Okay, then. We should get ready to go. Starlight, see if you can get one of those spark generators. Everyone else, scavenge any essentials we might need, like food and water. We should head out as soon as possible.”

Starlight finally released me, and reluctantly walked off to begin the salvage. Echo said something about robots before hurrying off. As for myself, I simply remained sitting, lacking anything better to do with myself.

A minute passed before Sickle pushed her way up to her hooves and lumbered over to me. She came to a stop beside me, speaking in a quiet rumble. “So, yeah, it’s been fun and all, but I think it’s about time I took off.”

I looked up to her in surprise. “What? Why?”

Her armor rattled with a shrug. “Ain’t much for me to do around here,” she said. “Hell, figured I’d head up north a bit. Sounds like there’s still plenty of raiders and warlords and shit up there. Might be fun.”

\leavevmode\llap{“}Going north?” I stared at her, legitimately shocked at her decision. “But… why? There’s still so much going on here.”

She snorted. “Yeah, sure. You’re going to go around and talk at a bunch of ponies. Woo. Loads of fun.”

\leavevmode\llap{“}You know there’s going to be violence,” I said. “Serenity isn’t going to stop without a fight.”

\leavevmode\llap{“}Yeah, great,” she said, and I’m pretty sure she rolled her eyes somewhere under that helmet. “And I’m sure I’ll have just as much fun as these last fights.”

And now it all made sense. “That’s what this is about? You’re feeling useless here?”

\leavevmode\llap{“}I’m feeling \textit{bored} is what it’s all about. I ain’t getting nearly enough fucking to hang around in the back doing nothing while you cunts have fun fighting. And Serenity? Hah. Bet those cunty bugs’ll all be flying and shit. Ain’t much for me to do.”

\leavevmode\llap{“}There’s \textit{plenty} you could do,” I said, reaching up a hoof and placing it gently on her shoulder. “They won’t all be flying, and I’m sure there’ll be other fights, too.”

\leavevmode\llap{“}Dusty and Star can handle the long-range shit just fine, and that Luna-wannabe will probably do well, too. Ain’t much of a fight for me, and I ain’t playing second-up. So unless you’re planning on offering me some of the best fucking ever, I ain’t got much reason to stick around.”

Her head inclined slightly, as if waiting to see if I took up the not-so-subtle offer. I tried a different approach. “I think you’re wrong,” I said. “There’s still plenty you can do, even right in the front-line of the fight. Even against Serenity.”

She turned her head to face me more directly. “Like what, huh? Name one thing.”

I frowned, stepping up to face her squarely, and meeting her gaze without any sign of hesitation or fear. “Sickle, you’re probably the most stubborn, combative, unrelenting pony I’ve known. If you really think you’re going to be useless, why don’t you find a way to \textit{make} yourself useful, instead of running away?”

Her head drew back a touch, jaw tightening. “You know… I kinda like that you ain’t so scared of me any more.” She lifted a hoof, pointing the vicious leg-blades at my chest, her lips curling back. “But don’t think I won’t beat your fucking ass to a pulp if you push me. I’ve killed plenty of ponies for less.”

\leavevmode\llap{“}Because they were insulting you, no doubt,” I said, refusing to let my eyes waver despite the adrenaline teasing at my senses. Then I put on a thin smile. “But I’m not insulting you. I’m \textit{challenging} you.”

She stared back at me for several long seconds before replying. “That clever mouth of yours is going to get you beat some day.”

\leavevmode\llap{“}Maybe,” I replied, “but not today.”

We stood there, squared off, the metal-clad beast of a pony looming above me.

Sickle broke the silence with another snort, and shoved her way past me.

I staggered, wheeling around to watch her walking off. I mentally scrambled, trying to think of something else to say, and eventually just called out. “Sickle!”

She stopped, head half-turning, but said nothing.

Still, nothing came. Finally, I sighed. “Good luck,” I said, ears drooping. “And… thank you.”

Her head turned a little further, inclining almost curiously. Then, she looked away again and continued walking. She stepped out into the hall, and then she was gone.

I stood in the empty lab, watching the door as if I expected her to come back. Eventually, I turned away, slowly wandering.

I found myself again at the window of the giant cryo-freezer, rearing up to rest my forelegs on the rim of the window. I stared out into the chamber and the rows of dimly lit eggs. There were so many of them. They were safe, but they were also so fragile.

Hoofsteps approached some untold number of minutes later, moving right up beside me. Starlight’s voice was soft and pleasant. “Hey.”

\leavevmode\llap{“}Hey,” I replied, still staring out over the eggs.

She stood beside me, looking through the window with a gentle smile. After a moment, she placed a hoof on my shoulder, giving a gentle rub. “You did it.”

\leavevmode\llap{“}Yeah,” I quietly replied. Then I drew in a deep breath, and slowly let it out. “Still a lot more to do.”

She nodded. “Yeah.” There was a long, lingering silence as she shared the view with me. Eventually, her attention shifted more toward me. “So, I guess this puts you in charge of your hive, huh?”

\leavevmode\llap{“}It’s quite the responsibility,” I said, slowly nodding.

\leavevmode\llap{“}So does that make you the queen, now?”

I flinched, ears flicking back. “No,” I quickly replied. “I’m not a queen.” I emphasized this by gesturing toward the eggs. “One of them will be. Not me.”

She paused, considering me. After a moment, she smiled. “Well, I think you’d make a great queen.”

My first impulse was to argue the point, but I looked to her and that comforting smile, and knew she intended it as a sincere compliment. “Thank you.”

Her smile grew a touch, and she turned to look at the eggs again. “You going to be okay leaving them here?”

\leavevmode\llap{“}They’re about as safe as they can be,” I said, despite the many fears that lingered in the background. “Nopony knows about this location but us, and it’s far from any settlements. I’ll be locking the labs up again, and I should be able to set a new passcode. They’ll be safe.”

She nodded. “We should probably get on that, then. Dusty wants to move out soon.”

We headed out. Once we’d left the secure labs, I focused on the lock for the giant blast doors, while Dusty led Starlight off to help him break into some vending machine. It only took me a few minutes to figure out how to set a new passcode. I locked the labs up tight and rejoined them, to find Dusty pulling packs of cigarettes from an opened machine.

Starlight was sitting on top of it, her hooves lazily swinging off the edge. She was smirking down at him. “Yeah, no more making fun of me for hoarding snack cakes, Dusty.”

\leavevmode\llap{“}I didn’t make fun of you,” Dusty quietly replied, steadily shoveling packs into his bag.

\leavevmode\llap{“}Okay,” Starlight said, and laughed. “No more rolling your eyes silently while ‘not making fun of me’, then.”

Despite his focus, the corner of Dusty’s mouth crept upwards. “Not like I won’t have plenty of other reasons to roll my eyes at you.”

Echo stood back, watching them all with a tight frown, but said nothing.

Dusty noticed my approach as he buckled his bags. “Good timing. We all set to go?”

\leavevmode\llap{“}I am,” I replied.

\leavevmode\llap{“}Good,” he said with a nod, then asked, “Where’s Sickle?”

\leavevmode\llap{“}I don’t know,” Starlight said. “Couldn’t find her.”

\leavevmode\llap{“}She left.”

They all turned to look at me, blinking in surprise.

\leavevmode\llap{“}Why?” Dusty asked.

\leavevmode\llap{“}She was... bored,” I said. “She decided it was time to move on.”

I left it at that. I didn’t feel particularly like elaborating, and I doubted that she would have liked me explaining the conclusions I had drawn.

Dusty stared for a moment before sighing. “Shit. We haven’t even started, and we’re already losing ponies.”

\leavevmode\llap{“}I can’t believe she just left,” Starlight said. “I mean… hell, I don’t exactly like her, but… shit.”

In the background, Echo had cocked her head to the side, and finally broke her silence. “What are you talking about? She did not leave.” She turned her head, looking towards the front of the facility. “She is currently in the back of your motorwagon, rummaging through the cargo.”

Dusty’s ears perked up as he turned to look that way. I did too, then turned my attention to the E.F.S. and the single contact it reported in that direction.

We made our way out to the entrance and stepped outside once again. Sure enough, Sickle was in the back of the motorwagon, hunched over something.

I walked toward her. “Sickle? What are—”

\leavevmode\llap{“}Well it took you fuckers long enough,” she grumbled, sitting back and tossing the minigun-armed battle-saddle at my hooves. I heard a sharp inhale from Echo as she stepped forward, catching it at the last moment in her magic.

Sickle was rooting around again. “You want me to stick around? You pull that weak-ass shit off that harness…” She reared back, swinging up one of the massive heavy machine guns and thumping it down on the edge of the cargo bay. “...and mount this motherfucker in its place!”

Echo floated the battle-saddle close to her chest, casting a disapproving glare at Sickle, but after a moment said, “That should be a trivial modification.”

\leavevmode\llap{“}Those things can put guns on both sides, right?” Sickle asked. “‘Cause I’m thinking of tearing that grenade launcher off this rust-bucket power armor and putting it on the other side.”

\leavevmode\llap{“}Uh, wait a minute,” Starlight said. “I can’t be the only one worried about giving Sickle a gun, am I?”

\leavevmode\llap{“}Fuck you, runt.”

\leavevmode\llap{“}And I thought you were leaving?” Starlight added, looking at me for confirmation. I nodded.

\leavevmode\llap{“}There’s going to be a good fight, right?” Sickle gave an amused snort. “But hey, if those bugs are going to cheat by flying, I’m going to cheat by bringing a fucking gun.”

Dusty was watching, his expression looking as if he’d bitten into something sour and was trying to hide it. “The idea of you with a gun and grenade launcher is… terrifying,” he said, before adding, “Hopefully in a good way.”

\leavevmode\llap{“}Good!” Sickle said, grinning savagely. “I like terrifying.”

\leavevmode\llap{“}I assume you intend to wear this,” Echo said, frowning down at the harness. “It is woefully insufficient for a pony of your girth and length. It will require extensive modification.”

\leavevmode\llap{“}Well then, you better make yourself fucking useful and get on that, huh?”

Echo scowled. “You could at least have the courtesy to politely \textit{ask} for my assistance.”

\leavevmode\llap{“}Yeah,” Sickle said with a derisive chuckle. “And you could have the courtesy to eat me, bitch.”

I stepped forward. “Sickle, there’s no need to be nasty.” Then I turned to Echo. “Would it be possible to make the modifications?”

\leavevmode\llap{“}It is certainly \textit{possible},” Echo said, glaring at Sickle. “I would need to requisition some additional material from some of the unused equipment to enlarge the harness. However, I am not terribly inclined to do any favors for someone so relentlessly rude.”

\leavevmode\llap{“}I understand,” I said. “Could you \textit{please} make those modifications?”

Her frown deepened as she looked down at me, then raised her head again to her usual superior pose. “I shall do this task for \textit{you}.”

\leavevmode\llap{“}Thank you.”

Sickle snickered, and I immediately turned to her.

\leavevmode\llap{“}I’m glad you decided to stick around, but if you continue to be rude to Echo when she’s trying to help you, I can always withdraw my request.”

\leavevmode\llap{“}Yeah, yeah,” Sickle said, waving a hoof dismissively. “Still wouldn’t hurt her to pull the fucking log out of her ass.”

\leavevmode\llap{“}No more than it would hurt you to ease up on the hostility, especially when she’s doing something for your benefit.”

Sickle just shrugged.

\leavevmode\llap{“}Have you ever even fired a gun?” Dusty asked, skepticism clear in his expression.

\leavevmode\llap{“}Sure, a few times,” Sickle replied, kicking back in the bed of the motorwagon and kicking her rear hooves up on the edge of the roof. “Ain’t like it’s hard.”

Dusty raised an eyebrow. “In a fight?”

\leavevmode\llap{“}Nah.” She lifted a foreleg, wiggling a spiked hoof. “Never needed a gun.”

\leavevmode\llap{“}Great,” Dusty grumbled. “And how long ago was this?”

\leavevmode\llap{“}I dunno,” Sickle said. “Five or six years ago? Maybe more?”

\leavevmode\llap{“}No experience \textit{and} one of our biggest guns. This will only end well.” Turning his attention to Echo, he asked, “How hard would it be to make it so we can swap out weapons?”

\leavevmode\llap{“}Trivial,” Echo replied, floating the battle-saddle before her. With a few clicks, the minigun floated free. “These harnesses were explicitly designed to allow the swapping of weapons with a minimal use of tools. The only difficulty will lie in fabricating mounting hardware for new weapons, but that should take mere minutes.”

\leavevmode\llap{“}Good,” Dusty said with a nod. “In that case, I’ve got a different weapon I’d like you to mount first, just so we can get her some practice shooting.”

He climbed into the motorwagon beside Sickle, who made some quiet and obscene comment that he ignored. A minute later, he climbed out again, holding a rifle. It was another Model 4 rifle, like my own, but it had a thicker, longer barrel, with a bipod mounted beneath it.

\leavevmode\llap{“}That tiny thing?” Sickle said. “I’d do more damage hitting someone with that than shooting them!”

\leavevmode\llap{“}We have less than three hundred rounds for the HMG, and we’re not wasting them on training. We’ve got probably a thousand rounds for this gun, we can spare a few.”

He passed it over to Echo, who examined it with a critical eye. “Magazine fed. That will pose some difficulty. The battle-saddle lacks a reloading mechanism. Designing one would take some time, as would adapting the minigun’s feed mechanism to this weapon.”

\leavevmode\llap{“}No need,” Dusty said. “It’s just for training, so we can make do with manual reloading. Actually, Whisper, I was thinking you might want to consider using this one, once Sickle is done with it.”

I cocked my head, looking at it more closely as I asked, “Why is that?”

\leavevmode\llap{“}You tend to be a bit heavy on the rate of fire, but you’ve gotten to be a pretty reliable soldier in general. That one’s designed to handle automatic fire better. It’s got a heavier barrel, lets you fire more without overheating it, and it’s a more stable platform. We could load you up with some drums and let you lay out some heavy fire.”

\leavevmode\llap{“}I guess,” I said, frowning a little as I looked at it. “I don’t know, though. I kind of like this rifle. It’s light. That with a drum mag seems a little awkward.”

\leavevmode\llap{“}It’ll be heavier and slower, sure,” Dusty said with a nod, though he wore a faint smile; it seems he approved of my observation. “But it’s also much more capable for longer-ranged engagements. If we get you some practice with it, you could swap out depending on the situation. They’re based on the same weapon, so their operation is identical.”

\leavevmode\llap{“}I suppose that makes sense.”

Meanwhile, Echo had floated out several spare parts and a toolkit from the motorwagon and gotten to work. It took only a couple of minutes before she had the rifle fitted to the right side of the battle-saddle. Another minute was spent alternating between the weapon’s built-in sights and the aiming reticle of the battle-saddle before she was satisfied with its alignment.

After that was several minutes spent rebuilding the frame and replacing straps, and after coaxing a lethargic Sickle from the motorwagon, a few minutes fine-tuning the adjustments to fit snug and secure over her armor.

Sickle did not make it easy.

\leavevmode\llap{“}Get this shit out of my face,” she grumbled, roughly prodding the arm that held the firing bit and aiming reticle.

\leavevmode\llap{“}Calm yourself,” Echo replied, standing proudly as her magic did the work of pulling on the straps. “That part is necessary to aim and fire the weapon. You will simply have to deal with it.”

\leavevmode\llap{“}It’s going to be in the way when I’m kicking the shit out of ponies,” Sickle shot back. “Fuck, I can’t even move my head down all the way!” She demonstrated by smacking her armored muzzle against the firing bit, and followed up by wiggling her head, swinging the long spike atop her helmet. “How the fuck am I supposed to stick ponies with this if I can’t even move my head right?”

\leavevmode\llap{“}I suppose you will simply have to settle with shooting them.”

\leavevmode\llap{“}Fuck that,” Sickle replied, swatting the metal arm again, and I’m pretty sure bending it a bit. “You don’t see the fucking Enclave birdies with metal sticks jammed in their faces, do you, bitch?”

Echo’s magic glowed around the protrusion as she held it in place. “That is because they are wearing power armor, and all the systems required for aiming and firing are built into their helmets. They—”

She abruptly stopped, ears perking up. A smile crossed her lips. “I believe I may have a solution to your problem. Give me your helmet.”

Sickle frowned. “What?”

Echo repeated her request more slowly, and Sickle scowled. “I heard you the first time, you stuck-up bitch. I mean, \textit{why} do you want my helmet?”

\leavevmode\llap{“}Because if you do not want a rigid bit, I will need to incorporate those mechanisms into your helmet. Now remove your helmet and give it to me.”

Sickle stared at her for several long seconds before answering. “Fine,” she growled, a warning tone to her voice as she sat and unstrapped the helm. “But if you fuck it up, I’m kicking your ass.”

\leavevmode\llap{“}Hmmph.” Echo took the helm and walked over to the motorwagon, only to stop again. She turned to Starlight, who was relaxing on the hood of the vehicle. “I am uncertain as to who claims ownership over the damaged pegasus power armor, so I shall ask you. May I remove some parts necessary for this project?”

Starlight glanced over to Dusty, who didn’t bother looking up from the drum magazines he was loading. She turned back and shrugged helplessly. “I guess?”

\leavevmode\llap{“}Good.”

That took a bit longer, as Echo dismantled part of the power armor’s helmet to remove the components she was seeking.

Sickle lay where they had been previously working. She tried to look disinterested, but every now and then she would crane her head a little to try to see what Echo was doing before pretending she didn’t care. A spiked hoof dug at the ground.

I took advantage of the inactivity to move a short distance away and continue my recordings.

Several minutes later, Echo finally straightened again. “It is done.”

\leavevmode\llap{“}‘Bout fucking time,” Sickle grumbled, pushing herself up to sit again, and snatching the helmet as it was offered to her. She immediately stopped as she looked inside, lips curling back. “What the fuck?”

Despite the remark, she slid the helmet on, then turned her head about, the thick-barred muzzle swinging beneath her chin. “What the fuck did you do to my helmet?”

\leavevmode\llap{“}I removed the E.F.S. projectors from the pegasus power armor helmet and mounted them in yours, and set an adjustable firing bit inside your helmet’s muzzle. The spark battery compartment I attached at the rear of the helmet provides the power for those devices, and the cable currently dangling from the rear right side of the helmet provides an electrical linkage between the helmet-mounted systems and the battle saddle.” Her nose rose a fraction as she put on a proud smile. “It is a flexible solution that will give you full E.F.S. functionality, including a projected point-of-aim, without compromising your hoof-to-hoof mobility.”

\leavevmode\llap{“}You really fucking love to listen to yourself talk, don’t you?” Sickle grumbled, still swinging her head around in every direction. “This sparkly color shit is stupid.”

\leavevmode\llap{“}It is actually quite advanced technology,” Echo said. “The spell matrix involved is—”

\leavevmode\llap{“}It’s still stupid,” Sickle growled.

Echo frowned. “Yet I am sure you will agree that it is less… ‘stupid’ than the rigid arm you objected to before.”

\leavevmode\llap{“}Less stupid is still pretty stupid,” Sickle grumbled.

\leavevmode\llap{“}Oh for fuck’s sake,” Starlight called out. “Say ‘thank you’, you ungrateful bitch!”

\leavevmode\llap{“}Fuck you, runt,” Sickle replied with a sneer. “Let’s see if this damn gun-thing works before we start thanking anypony.”

Despite her tight frown, Echo took the time to adjust the firing bit to fit Sickle’s mouth. Attaching the rifle itself was completely straight-forward. Finally, she connected the cable to link the helmet to the battle-saddle.

\leavevmode\llap{“}There,” Echo said with a short nod. “It is complete. When you disable the safety, you should see the aiming pipper. It will show the point of aim. With the necessary data and some time, Whisper should be able to add proper range adjustments to the spell matrix.”

\leavevmode\llap{“}Yeah, okay,” Sickle muttered as she turned to look out across the open fields nearby. After a moment, she asked, “The fuck is a safety?”

Dusty sighed.

{\br}%
We eventually abandoned our plans to head out that day, once it became clear that proper firearm safety and handling was going to take more than a minutes-long lesson. More than an hour later, Dusty still hadn’t even given her any ammo.

Eventually, he had nearly told her off. “Listen, Sickle! If you want to carry one of the big guns, then you’re going to have to put in some damn work. I ain’t gearing you up with a weapon that’s more likely to kill us than our enemies!”

\leavevmode\llap{“}I know what way to point a fucking gun, dumbass!” Sickle replied.

\leavevmode\llap{“}Not giving a shit might work great for running up and kicking someone, but it doesn’t work with guns! If you keep half-assing it like this and not caring about what you’re doing, you’re going to end up shooting one of us on accident.”

Sickle snarled. “At this rate, it wouldn’t be an accident!”

\leavevmode\llap{“}And that’s not helping,” Dusty said, leveling a hoof at her before sweeping it back in my direction. “And what about Whisper? You seem to like her. If you don’t pay attention to this stuff and treat it seriously, you could accidentally kill her, too. Do you really want that?”

Dusty metaphorically dragged her through the lessons, with Sickle grumbling and arguing the whole way. I hung back, having finished another audio recording, and now sat beside Starlight on the hood of the motorwagon. Echo was nearby; she had decided to not insist on further “research” with me after our previous session, and was instead in the back of the motorwagon, examining the less advanced of the two ruined power armors.

\leavevmode\llap{“}Do you think this is a good idea?” Starlight asked, watching the so-called training with me.

\leavevmode\llap{“}Maybe not,” I said, half-distracted by sorting through the contents of my PipBuck. “But it’s still better than the alternative. This is the price of Sickle staying, and as uneasy as I am with some parts of that, it’s unfortunately likely that we’ll need all the advantages we can get.”

\leavevmode\llap{“}You sound so optimistic,” she grumbled.

\leavevmode\llap{“}I am,” I said. “With all the factors in play, I think we have a very good chance of achieving our goals.” I gave a shrug, giving up on my PipBuck and lying back beside Starlight. “Still, no reason to not stack everything as far in our favor as possible, not to mention taking precaution against any problems that might come up. Even if I’m optimistic of our chances, there’s still going to be risk.”

Echo spoke up from the cargo bed. “Which is why I hope to get this armor functional. While I am entirely confident in my shields, I would prefer to have redundant safety measures in place for Whisper. Her health is of great value to both of our plans.”

Starlight rolled her eyes. “Gee, glad she’s so useful to you.”

Echo didn’t look up from her work. “Given your strong emotional attachment, I would think you would be pleased by my efforts to protect her.”

\leavevmode\llap{“}That’s not…” Starlight sighed, closing her eyes and laying her head back against the motorwagon. “Yeah, sure, I’m happy you’re trying to protect her. It’s the ‘why’ that’s dumb.”

\leavevmode\llap{“}Ah,” Echo said, her magic floating some mechanical part into place on the armor. “You object to my motivations in helping her, not in the help itself.”

\leavevmode\llap{“}It’s just all clinical, like… I dunno, like she’s a \textit{tool} to you.”

\leavevmode\llap{“}Despite my lengthy observations, we have only directly interacted for a little less than twenty four hours,” Echo said, looking up from her work for a moment to meet Starlight’s eyes. “Given the limited interaction, yes, I have not formed any sort of emotional attachment to any of you which would significantly influence my behavior.”

Starlight quietly snorted, and muttered, “Behold, the savior of ponykind: kind of a dick.”

\leavevmode\llap{“}Well, she’s trying,” I said. “And to be fair to Echo, it took more than twenty four hours for me to start thinking of you as a friend instead of just a traveling companion. I’m not sure exactly where I would put that. When we got to Rust, perhaps?”

Starlight gave another snort, though there was a bit more humor behind it this time. “So, like, two days instead of one?”

\leavevmode\llap{“}Or thereabouts,” I said, cracking a smile. “Mind, I’d be lying if I said there was no selfish interest in staying with you. You were pretty much my only opportunity for love and survival knowledge prior to Rust, and still my best prospects after it, but that was only part of it. An increasingly small part, at that.”

\leavevmode\llap{“}Sure, I get all that,” she said. “I mean, it’s still a \textit{little} weird when I think about, but I guess I don’t really think about it much. Like, I’ve gotten used to it.”

Echo spoke up again. “Whisper is much better at putting on friendly pretenses than I am.”

\leavevmode\llap{“}I’m sure I am,” I said, “but you’d be mistaken if you think that’s the case here. I don’t generally \textit{need} to put on pretenses, because I do legitimately care about people, even ponies. I took up my profession to help others. Changelings, yes, but one of the advantages of being an Infiltrator is that it becomes much easier to see the ways we are similar rather than different. I might not have thought of Starlight as a friend right away, but I \textit{liked} her immediately.”

\leavevmode\llap{“}Wasn’t I pointing a gun at you?” Starlight said with a smile.

I chuckled. “But after you put the gun down you were all smiles and cheerfulness. Considering how bleak everything seemed, it stood out to me. And you know, even though I had my own problems, spending some time around you made me want to help you with your own. Sure, again, there was a bit of a selfish side to it. I needed food, and, well… seeing you happy gave me hope that good things could still thrive in the Wasteland.”

Her smile steadily grew until she finally gave a soft laugh and thumped me on the shoulder. “Okay, that is \textit{ridiculously} cheesy, you silly little bug!”

I grinned. “Plus, you have a nice laugh.”

She lay back, still chuckling.

After a moment of enjoying the good humor, I looked back to Echo. “In any case, I think there’s an important point to all this. You and I have certain similarities. We’re both trying to help ponies, and it seems we both have a similarly methodical thought process. I think the difference is, while you’re trying to help ponies as a whole, you seem to overlook the individuals in the process.”

Echo’s head came up again, her work pausing as she considered this. “Hmm. I believe I see what you are trying to say. I… I must admit, most of our lives, our memories, are from our time in Unity. What benefited the whole benefited us. The chaos of individuality is most troubling.”

\leavevmode\llap{“}It’s certainly more complicated,” I said with a nod. “But the variety makes the world far better for everyone involved, I’ve found.”

Echo hummed again. “I do have to admit, as frustrating and incomprehensible as it seems at times, I am certainly finding the variety to be \textit{intriguing}.” She returned to her work, floating some mechanical piece into place along the back of the crude power armor. “There was certainly no opportunity to work on such interesting arcane technology when we were together in Unity.” There was a momentary pause in her work, brief enough that I almost missed it. “Nor was there any desire for such, now that I think on it.”

I considered that for a moment. “I take it this Unity wasn’t much for individuality?”

\leavevmode\llap{“}What need did we have for individuality when we were one?” Echo replied. “We were the whole, and the whole was us. What was good for one was good for all.”

\leavevmode\llap{“}Wow,” Starlight said. “Yeah, I’m switching my vote on alicornhood from ‘no’ to ‘hell no’.”

\leavevmode\llap{“}There is no need for you to be concerned about that,” Echo grumbled. “That aspect of our Unity was a gift from our mother. Without her, we are adrift and alone.”

\leavevmode\llap{“}I don’t mean to diminish your loss,” I said, “and I recognize it’s not quite the same thing, but you’re not entirely alone.”

She scoffed. “It is a meager shadow of what I once knew,” she said in a low tone, keeping her attention focused on her work. Tools and parts floated in purple magic. “Still, I appreciate the gesture, and will strive to make do with what I have. Even I must admit to have found \textit{some} silver lining to these unfortunate events.”

I nodded. “Discovering your own interests?”

She paused, looking off into space for a moment before resuming her work. “I am uncertain if it is discovering something very old or something very new, but yes.”

The conversation lapsed, and I sat there for a while, thinking, until Starlight’s words brought my attention back to the present. “Oh boy. He’s giving Sickle ammo.”

I looked over just in time to see Dusty finish inserting the drum and chambering a round. The rifle looked ridiculously tiny on her side, even with the suppressor extending the weapon’s length.

\leavevmode\llap{“}Remember,” Dusty was saying. “Keep the weapon pointed downrange at all times. Safety on unless you’re expecting to shoot. Never point it at anypony unless you’re intending to shoot them.”

\leavevmode\llap{“}Yeah, yeah,” Sickle grumbled. I had to give Dusty credit for perseverance; he’d apparently worn her down from ‘belligerently hostile’ to ‘irritated but resigned’, and she followed his directions, even if every inch of body language suggested her annoyance.

\leavevmode\llap{“}Okay,” Dusty said, stepping back before pointing with a hoof at a dead tree some hundred yards away. “Go ahead and disengage the safety, then line up the sights on the target.”

\leavevmode\llap{“}Uh-huh,” Sickle muttered around the bit. I saw her jaw shift slightly as she worked the safety latch, then her head twitched upwards. She adjusted her stance, first lowering her chest a bit, then sticking her rump up, and finally arching her back. “Well this is awkward as shit. How the fuck am I supposed to aim this?”

\leavevmode\llap{“}Practice, mostly,” Dusty replied. “I’d say it took the average soldier a good week of combat drills and a few hundred rounds of ammunition to become acceptably proficient with battle-saddle mounts, and specialists put in many times that. You’re getting the crash-course version.”

\leavevmode\llap{“}Lucky me,” Sickle grumbled. “No wonder Rattle couldn’t hit shit.” She bit down, and a single sharp crack echoed across the shallow basin. I could see Sickle frown, then she bit down again, and again. The weapon fired a few more times, then stopped.

\leavevmode\llap{“}What the fuck?” Sickle snapped, standing upright again and turning to glare at the weapon. “Did this shit break? I know they hold more shots than that!”

\leavevmode\llap{“}They do,” Dusty said. “But I only loaded five rounds into the mag.”

\leavevmode\llap{“}Well give me a full one!” Sickle shot back. “And why was it only firing one at a time? This shit’s supposed to be full-auto, right?”

\leavevmode\llap{“}It can be,” he said, removing the drum from her weapon. “I just wanted to make sure you have the basics of weapon handling down before you get to playing around too much. I’ll give you a few more rounds, you can get some practice in using the weapon. Once you’re doing well enough, we’ll step you up.”

Sickle groaned. “Leave it to you to make guns even \textit{more} boring.”

\leavevmode\llap{“}Trust me,” Dusty said as he slowly loaded a few more rounds into the magazine. “When it comes to guns, boring is good. Exciting means something’s gone wrong.”

\leavevmode\llap{“}And this is why I kick things instead of shooting them,” Sickle grumbled.

Dusty gave a chuckle. “So far, you aren’t shooting things because your aim is horrible. You didn’t even come close to the tree.”

\leavevmode\llap{“}Oh, fuck off,” Sickle replied. “I had that circle-cross thingy right over the tree. Not my fault the fucking sights are off.”

\leavevmode\llap{“}Getting the sights aligned is part of why we’re doing this.” He slid the partially loaded drum into place again, racked the bolt, and gave her a pat on the side. “You’re loaded. Keep the aim-point at the center of the tree, right where it splits into two branches. Fire three rounds, I’ll adjust, we repeat. Got it?”

With little else to do, I watched the brief training session. There were several cycles of firing and adjusting, with Sickle grumpily following Dusty’s directions. Eventually he switched the rifle to full-auto, letting her fire a few bursts that peppered the tree with bullets. With the weapon securely mounted to her side, I was hardly surprised at how easily she could control the recoil, and with the aid of the aiming device Echo had rigged up for her, she was even reasonably accurate.

On the other hoof, it still took her a good five seconds to line up a shot.

It was getting late when he finally decided she was ready.

The heavy-barrel rifle came off, and Dusty hefted the heavy machine gun in its place. The mounting bracket Echo had rigged up attached easily, and after a minute, the weapon was set. Next came the ammunition. The can holding the ammo fit into a bracket Echo had attached across the back of the harness, with the belt feeding down through a simple chute and into the weapon itself.

Dusty racked back the charging handle, chambering a round. “Okay, weapon’s hot. Now remember, we don’t have much ammo for this. If you spend this belt, you might have to do without for a while. We’ll try to make sure you have some ammo, but if you want more, you’ll have to spend some of your share of the caps… so try not to waste too many rounds.”

\leavevmode\llap{“}Yeah, okay,” Sickle said with a resigned sigh.

\leavevmode\llap{“}I’ve got it set to single-shot right now to check the aim,” he said, stepping back and sitting to put his hooves over his ears. “Put one round into the tree, same point.”

Sickle’s jaw tightened, and the monstrous gun thundered, kicking out a small wake of dust and echoing across the landscape. Fragments of dry wood flew from where the top of the dead tree had been moments earlier. For the first time in a few hours, Sickle cracked a smile. “Yeah, that’s more fucking like it.”

\leavevmode\llap{“}Looks like the sight is aligned,” Dusty said, lowering his hooves. “Okay, it’s yours, now. It’s an expensive piece of hardware, so if you want to keep using it, I expect you to take care of it.” He turned to his saddlebags and pulled out a bundle. “Which means it’s time to teach you how to clean it.”

Sickle’s smile vanished. “Aaand we’re back to boring.”

{\br}%
We spent the night there, enjoying the relative comfort of the abandoned facility. Sure, the air was a little musty due to the lack of maintenance in the air system, and everything was coated in a fine layer of dust, but the beds were more comfortable than anything I’d had since leaving my chrysalis.

When we returned to the motorwagon that morning, we found Echo slumped over the power armor she had been working on, with several disassembled pieces of scientific equipment all neatly arrayed around her. She was snoring softly.

There was an amused silence as we looked over the scene, until Starlight spoke up with deliberate loudness. “She looks so cute when she’s not being so arrogant.”

Echo’s head jerked up and she slid back to a sitting position, blinking several times before the scene and words finally registered. “I am not arrogant,” she said, and wobbled a little before bracing herself. “...What time is it?”

Starlight was grinning. “You’re wearing a PipBuck.”

Echo frowned and looked down at the device, wobbling a little as she lifted her hoof. “Right.”

Dusty climbed up to the motorwagon’s window, sitting on the edge for the moment. “Did you stay up all night working on that?”

\leavevmode\llap{“}Of course not,” Echo said, shuffling her wings before raising her head, taking up her usual prim and proper pose, though she remained sitting. “I obviously slept, and for a perfectly reasonable time. I simply overslept is all.”

Starlight snickered. “Uh-huh. Who’s got a problem about honesty now?”

Echo’s expression tightened, eyes widening and ears standing alert. Her mouth hung open for a moment before she formulated a response. “I… suppose ‘reasonable’ is a very \textit{subjective} term that we might not exactly agree on, so I am not \textit{technically} being dishonest.”

\leavevmode\llap{“}Ah, yes,” I said. “Technically true, the best kind of true.” Then I smiled. “Mostly because it’s also the best kind of lie.”

She scowled, raising a hoof to rub at her eyes, but catching herself halfway there and quickly setting her hoof down again. “It is much too early to have someone twisting my words around over something so unimportant.” She pointedly turned to look at Dusty. “I assume from this gathering that you intend to depart?”

\leavevmode\llap{“}Yep,” he replied. “How’s the armor doing?”

\leavevmode\llap{“}It is taking me longer than I had hoped,” Echo replied with a hint of a grumble. “The \textit{brute} caused a considerable amount of damage when she disabled it, particularly in the torso. Unfortunately, the torso articulation is the most complicated of the entire armor. I have made great progress, but it will require several more hours to fabricate the necessary replacement parts from what I have.”

\leavevmode\llap{“}Several hours, got it.” Dusty nodded. “Well, it’ll have to wait. We’ve got a long ride to Trotsen, but since we’re setting out early, we might make it today.”

\leavevmode\llap{“}That will be a lengthy journey,” Echo noted, and her magic reached out to grab the various parts gathered around her. “Very well. I shall continue my work once we have arrived there.”

In moments, all of the various parts were tucked neatly away, and the power armor was once again laid out on its side at the back. Echo stood atop the motorwagon, spreading her wings. “Again, I shall follow you from above.”

With that final statement, she beat her wings, rising up into the sky.

\leavevmode\llap{“}Bitch talks way too much,” Sickle said as she climbed up into the rear of the motorwagon, the vehicle creaking under her weight. My attention again turned to the massive barrel sticking out past her chest. Sickle was menacing enough on her own, but I had gotten used to her presence. The addition of the huge gun changed that, and I found myself regularly glancing over at it.

I tried to shake off the nervous feeling, reasoning that I would eventually get used to it, just as I had with the leg blades, spear-like horn, and general demeanor. I climbed into the rear of the motorwagon, stowing my bags and gear beside me.

That gear included the new rifle, along with a pair of pouches holding loaded drums. Dusty had me put a drum through it in steady bursts, and I had to admit, it controlled nicely, especially when I was lying down with the bipod out. It might be clunky compared to my regular rifle, but when I was putting tight bursts into a dead tree probably three hundred yards away, I could appreciate its advantages. It was more light machine gun than rifle.

Still, it would probably live there in the motorwagon, except for the occasions where I needed to use it.

\leavevmode\llap{“}Open up your map,” Dusty said to Starlight as he climbed in, setting his own rifle beside him. “Scroll up north, about thirty miles.”

Starlight did so, and Dusty gave a few corrections before finding the right place. “There. That’s an old road, goes all the way to Trotsen. You’ll make your way north until we hit that, then follow it west all the way to the city. Good?”

\leavevmode\llap{“}You got it,” Starlight said, scrolling the map again. “Terrain’s a little rough between here and there, but I think we can do it, and it’ll all be smooth sailing from there.”

\leavevmode\llap{“}Good,” Dusty said with a nod. “Let’s move out.”

{\br}%
It took us almost two hours to wind our way through some particularly rocky terrain, but we eventually found our way to the road. It wasn’t much of a road, mind you. It certainly wasn’t the paved street or highways you might see in some cities. It was an old dirt road, unmaintained for two centuries. Still, it was a level path across the Wasteland, and almost entirely free of debris.

\leavevmode\llap{“}Trotsen convoys make the trip on this road,” Dusty had said. “I’m sure they make sure it stays clear. We heard that a few raider gangs tried taking them on, but none of them were up to fighting a convoy of heavily armed motorwagons. Most just steer clear.”

He turned to give us a serious look. “But we aren’t a convoy, so keep your eyes out.”

So, while I spent a good portion of the journey adding to my recordings, and hoping the background noise wouldn’t be overwhelming, I kept an eye out.

{\br}%
A rapid cacophony of impacts broke the monotony of driving, accompanied by the chatter and crack of automatic fire.

\leavevmode\llap{“}Shit!” Starlight blurted as the motorwagon swerved sharply, throwing me against the edge of the window I was looking out, then back into the seat as she corrected. I quickly pushed myself back up. I had been watching out our left, and now turned my attention right. Dusty was grabbing his rifle, shouting out at the same time. “Step on it! Contact close right, high-ground!”

I slid across the seat as the motorwagon roared, snatching my rifle up in my magic and sticking it out the window. There was a small bluff less than a hundred yards away. Dusty was firing rapidly, peppering me with shell casings and kicking up plumes of dirt and dust from the ridge. At our speed, I couldn’t see any ponies. I was still searching when another series of snaps and cracks made me duck, with a couple rounds pinging off the side armor.

I came up firing, putting rounds out in the general direction of the low cliffs. I didn’t stop until the magazine ran empty, the cliffs already falling behind us.

That’s when we saw the twin plumes of dust kicking up from the low-ground nearby, their sources obscured by a low rise. I had just finished reloading when a pair of motorwagons came surging over that rise, tearing across the open ground between us.

\leavevmode\llap{“}Whisper!” Dusty called out. “Get on the gun!”

I set my rifle down and scrambled over the back of my seat to climb up behind the machine gun. It was a bit cramped with Sickle there, but she didn’t complain about me taking the gun; she had her own, now, and was already turning to face the incoming vehicles, a grin on her face.

The attacking motorwagons had split up, with one swinging towards the road behind us, and the other speeding across the field to our side, running parallel to us. I focused on the one at our side. It was smaller than our motorwagon, but covered in heavy plates, and several long poles were topped by pony skulls. I swung the machine gun around, bracing against the wild bumps and lurches of the rough road, and hit the trigger.

I fired a short burst, just a few rounds, but I knew as I fired that I had missed. I fought against the bumping and swaying of the wagon to get my aim on-target. There was movement in the back of the other motorwagon, and something long pointed in our direction. I hit the trigger again, laying out another short burst. I couldn’t tell if I had hit, but the motorwagon immediately swerved away.

I looked behind us, where the second motorwagon had just pulled onto the road, swerving as it plunged into the trail of dust we were kicking up. This motorwagon was similar in size to our own vehicle, but taller, and featuring a massive wedge of metal welded to the front like a giant, murderous plow. Through the dust, I could just make out a pair of ponies riding in the back, clutching spears in their mouths and wearing thick metal armor.

Getting the gun pointed behind us was difficult, and I had to press one rear hoof against Sickle’s side to push myself halfway onto the roof, awkwardly wedging myself alongside the gun as I got it turned around.

The driver of the other vehicle saw what I was doing, and swerved off the road again on our left. Behind it, a great plume of dirt and smoke burst from the receding cliffs, and a purple, winged form arced up into the sky. Echo had joined the fray.

Despite driving off the road, the close motorwagon was still gaining on us. I dropped down again before swinging the gun all the way around, but I hadn’t even started climbing up again before the other vehicle swung over, plunging through our dust-trail to the other side of the road.

As I got down again, Sickle reared up in the back of our vehicle, pointing a bladed hoof. “Fuck off, you little shits, or I’m coming over there and kicking your asses!”

I doubt they heard her. I could barely hear her over the clatter and roar. Still, if I had seen Sickle pointing and yelling at me, I would have reconsidered what I was doing.

Instead, the attacking vehicle centered on the road, rapidly closing on us.

\leavevmode\llap{“}Sickle!” I shouted out as loud as I could over the cacophonous noise. “Shoot them!”

\leavevmode\llap{“}Fuck that!” she shouted back, planting her hooves on the edges of the cargo bay.

I cast a quick glance off to the side. The other vehicle was driving straight away from us, perhaps deciding we were too dangerous of a target. Black smoke mixed with the plume of dust behind them. I’d evidently hit something. In any case, they were not currently a threat, especially as I saw Echo swooping into a steep dive toward them.

I gave up on the machine gun, snatching my rifle from the back seat. A bullet cracked by my head. Another smacked loudly against Sickle’s armor. She roared in reply.

The other vehicle was pushing up beside us as I floated my rifle around. It was almost impossible to aim, but it was a point-blank shot. I switched it to automatic and held down the trigger, trying to aim for the windows.

As the front end of the attacking vehicle got beside us, it swerved. Sickle leaped. The other vehicle slammed into the rear corner of ours with a tremendous thud, throwing me to the side. My helmet hit the side armor. Dust flooded over everything. Our motorwagon swerved again, shuddering hard and bouncing off the road. All the cargo slid around violently as the world spun.

I leaped for safety, wings beating to lift me clear of the chaos. The entire road turned to dust as I surged upwards, still reeling from the blow to the head. I caught a glimpse of the other motorwagon, with Sickle clinging to the hood and kicking at the window, before it disappeared into the cloud of dust kicked up by our own wagon’s uncontrolled skid.

Sickle came flying out of the cloud, completely airborne, followed a moment later by the tumbling motorwagon. Our own wagon shuddered as it slid and skipped sideways across the ground, my heart lurching as it tipped, but it finally came to a rest upright. The cloud of dust it had kicked up washed over everything.

I shook myself from gawking and turned, wings beating as I swooped down toward the hostile motorwagon, changing magazines as I closed in. Through the dust, I could see it had landed on its side. My E.F.S. showed at least one hostile being within.

Sickle was nearby, slowly pushing herself up and shaking her head. “...Mother\textit{fucker!}”

Something vaguely pony-shaped moved in the back of the motorwagon. I back-winged, drawing short, and put out a long burst. I couldn’t tell if I hit, but whatever it was retreated into the shelter of the vehicle.

Sickle was already trotting toward the vehicle, favoring a foreleg. I swung wide behind her, following her in.

She just went right up to the rear of the vehicle, a cargo bed much like on our own, and stuck her head in.

There was a shout, then gunshots. Sickle jerked back, then roared again, wedging her upper body in through the rear window. There was cursing and a few more gunshots, and Sickle pulled back, dragging out a dirt-caked and bleeding pony, still clutching a pistol in his mouth.

Despite the broken leg dangling uselessly at his side, the pony twisted his head around, firing another round into the only part he could currently aim at, Sickle’s side. It did as little as you might expect against her thick armor, and Sickle responded by rearing up, gripping the pony in both forelegs, and bashing him against the rear of the wagon.

The fight seemed to go out of the pony, but after a moment to recover, he turned his head and fired several more times into her armored shoulder. Sickle responded by smashing the pony against the motorwagon again and again and again.

I landed on the upturned side, blinking against the dust that stung at my eyes. My heart hammered as I peeked through the side window, rifle floating beside my head. I saw movement, hastily aimed, then stopped. It was the rear leg of a pony, kicking in slow, weak spasms at the far side of the interior. The rest of her body had been sticking out of the window, and was now crushed under several tons of motorwagon.

I pushed out my magic, casting a bright green glow through the dust-choked interior and checking that there were no more ponies. My E.F.S. confirmed it.

At the rear of the wagon, Sickle finally ceased her banging, tossing aside the limp and excessively dead pony.

Two cracks sounded from somewhere nearby, and I quickly scanned around, but the slowly settling dust still hung thick in the air. A moment later, my earbud crackled with Dusty’s voice. “Whisper, check in.”

\leavevmode\llap{“}Here!” I said into the broadcaster, still looking around. “I’m at the other motorwagon. They’re dead.”

\leavevmode\llap{“}Is Sickle there?”

\leavevmode\llap{“}Yes. She’s fine.”

\leavevmode\llap{“}Good,” he said. “I’ve got another contact due south of my position, obscured by dust. Get airborne and get eyes on them.”

\leavevmode\llap{“}On it!”

I shot upwards, clear of the cloud of dust. My E.F.S. was showing a single contact, and I turned to face it. Through the haze of dust, I spotted the silhouette of a pony, low to the ground. I slowed to a hover, leveled my rifle, and kicked on S.A.T.S. Two bursts kicked up several sprays of dirt, and while the form barely moved, the contact marker winked out.

\leavevmode\llap{“}They’re down,” I reported over the broadcaster.

\leavevmode\llap{“}Copy. Get a good three-sixty scan, then get back down here.”

I looked around, taking in the area. Another body lay a short distance from the motorwagon, close enough that I could see the ragged wound across her side. My E.F.S. showed no signs of life. There were no other ponies nearby. Looking further, I could see that the other motorwagon was continuing on, still trailing smoke, while Echo flew swiftly in our direction.

I dove down again, back-winging in time to land atop our motorwagon. Dusty was in the rear, perched on an uneven pile of jumbled gear. His rifle was up, and his eyes glanced my way as I landed.

\leavevmode\llap{“}I didn’t see anyone else around,” I said, then pointed out in the direction of the fleeing vehicle. “The other motorwagon is running away, and smoking pretty badly.”

\leavevmode\llap{“}Good,” he said, relaxing slightly. “That… could have gone a lot worse.”

\leavevmode\llap{“}The hell was that?” Starlight said, perching on the edge of the window, and dabbing a hoof at the corner of her mouth, wiping away a tiny bit of blood. “Since when do raiders have motorwagons?”

\leavevmode\llap{“}Motorwagons are supposed to be more common around Trotsen,” Dusty said as he climbed up on the roof for a better view; the dust was finally settling. “It’s where they were made, originally. I don’t know if these were raiders, exactly, but I guess it’s not too surprising other ponies would get their hooves on some motorwagons. We’ve seen raiders sporting some impressive hardware, after all.”

Meanwhile, I had dropped off the edge of the roof to hover beside Starlight. “Are you okay?”

\leavevmode\llap{“}Yeah,” she said, wiping at her mouth again, then smiling. “Face-planted into the steering wheel when we spun out. Just split my lip is all. I’ve gotten worse just playing around.”

\leavevmode\llap{“}When your ‘playing around’ is climbing and jumping all over ruined buildings, I’m hardly surprised.” Still, I eyed the injury warily, as if I might discern something that her PipBuck hadn’t already told her.

A burst of wind made me flinch back, and I looked up to see Echo directly above us, looking down with wide eyes. Her voice was surprisingly loud. “Is everyone okay?”

\leavevmode\llap{“}We’re fine!” Dusty called out, then gestured with his PipBuck-clad hoof. “We need to get you fixed up with a broadcaster so we can communicate with you.”

\leavevmode\llap{“}Yes, of course,” she replied, her voice back to a conversational volume as she landed lightly on the rear of the motorwagon. “And the attacking ponies?”

\leavevmode\llap{“}Dead or driven off,” he said, gesturing in the direction of the other motorwagon. The dust had cleared enough for me to see Sickle rooting around inside it.

\leavevmode\llap{“}Well, that is good,” she said with a sharp nod, and followed it up with a frown as she looked down into the cargo bed. “We really must find a better way for you to secure your cargo.” Her magic enveloped the contents, rapidly placing them back in their respective places.

Starlight hopped down and trotted over to the other motorwagon, and I followed.

Our own vehicle sported only a shallow dent and some scrapes on the rear corner. The other motorwagon had not fared nearly so well. One of the front wheels was bent almost entirely sideways, and the body itself was visibly twisted from the crash. Everything was coated in dirt.

Sickle was sitting beside the wagon, checking over the pony she had killed. It looked as if his fashion choice had been much like hers, though his metal armor was both thinner and less complete in its coverage. Several spikes were welded across his back, most of which were now bent from Sickle’s assault.

If these ponies weren’t raiders, they were certainly taking to the raider aesthetic.

Starlight paused, watching Sickle for a moment before speaking. “Okay, I’ve got to admit, ending a motorwagon chase by jumping over and kicking the other wagon to death? That was pretty cool.”

\leavevmode\llap{“}Fuck yeah it was!” Sickle said, grinning behind her muzzle. “Think I cracked some ribs. Oh, that looks good.” She pulled something away from the body—a pill, I think—and slapped it between the bars of her muzzle to swallow it.

Starlight started looking over the motorwagon, joined moments later by Echo.

\leavevmode\llap{“}Well, the front axle is toast, obviously,” Starlight noted. “Must have landed right on it. Look at how cleanly the struts sheared!”

\leavevmode\llap{“}The vehicle’s chassis was deformed by the collision,” Echo said, leaning in close to examine the underside of the vehicle. “It has much lighter armor than your vehicle. I assume that and the lighter cargo load explains its superior speed.”

\leavevmode\llap{“}Probably,” Starlight agreed. “Think we could fix it up?”

Echo gave a sharp nod. “Undoubtedly. My only concern is whether the motor or transmission has been damaged.”

I moved to the passenger compartment, looking around for anything we should take, while they continued their conversation. I did my best to ignore the now-still legs sticking through the window, and rooted around.

There were a few soft thumps from the undercarriage, followed by Starlight’s voice. “I’m not seeing any external damage on them.”

Dusty joined us. “Find anything?”

\leavevmode\llap{“}Not yet,” I said.

Starlight called out, rather happily, “I think we can fix it!”

\leavevmode\llap{“}Fix it?” Dusty asked, as if the thought hadn’t occurred to him until that moment. “How long will that take?”

\leavevmode\llap{“}A few hours,” Echo said. “A day at most.”

\leavevmode\llap{“}More delays,” Dusty said. “And in territory where we’ve already been attacked once. I know we’ve got a lot of firepower, but I don’t like tempting fate. We should move on before we attract any more attention.”

Sickle called out from somewhere more distant. “Fuck that, I like the attention!”

\leavevmode\llap{“}Seems like a shame to just leave it,” Starlight said, climbing up atop the upturned vehicle to peer in the side window, and smiled when she saw me there.

\leavevmode\llap{“}We don’t really need a second motorwagon,” Dusty noted.

\leavevmode\llap{“}Well, maybe Echo wouldn’t have to fly everywhere?”

\leavevmode\llap{“}I am perfectly content with flying,” Echo said. “Still, I suppose it would be more relaxing.”

\leavevmode\llap{“}You can always perch on the roof,” Dusty said.

\leavevmode\llap{“}I suppose.” From her tone, I could picture the frown she must have been wearing.

\leavevmode\llap{“}Well, what about selling it?” Starlight asked. “A working motorwagon is worth a small fortune if you can sell it, and Trotsen seems like the place that would buy them, right?”

\leavevmode\llap{“}They probably have enough already,” Dusty said, though his tone had turned more thoughtful. “Still… would be a shame to pass up something that valuable. Hmm. Tell you what. If you two can get this thing mobile in, say, thirty minutes, we’ll take it with us. You can finish repairs once we get to Trotsen, or we can find somepony to buy it. Sound good?”

\leavevmode\llap{“}You bet!” Starlight said, immediately galloping for our motorwagon and the tools she had there.

Echo flew after her. “I do not think we can repair the axle in time, but perhaps we could arrange a way to tow the vehicle…”

A half-hour later, the damaged motorwagon had been righted, its front end lifted and secured to the rear of our own by a quickly kludged-together hitch. It was an awkward-looking arrangement, but it sufficed to move.

Looting had come up light. There was a pistol and a rifle, both pipe weapons, and a small supply of ammunition for each. There was a five-gallon canister about half-full of water, a few cans of food, and a few drugs that Sickle had quickly snatched up. A small set of tools were scattered around the cab, and while they looked brand new, we already had more than enough of our own.

Still, we gathered it up. Every piece was something we could trade for caps. The only things we left were the armors they had been wearing, despite Sickle’s suggestion that Starlight could use some better armor.

Starlight declined, naturally. “I’m not wearing raider armor.”

She did, however, snatch the goggles one of the ponies had been wearing. On seeing it, I immediately started looking for a second set for myself. The closest I found was a gas mask. I declined to take it.

We piled in once more and continued on our way, a little slower as we towed the second vehicle, while Echo flew close overhead.

{\br}%
“Trotsen is pretty much the industrial center of the region,” Dusty said as I finished unloading the machine gun. “So I guess that much hasn’t changed.”

I floated the ammo can back, setting it in the bed of the vehicle before leaning in under the gun itself. “Probably about the only thing that hasn’t, then.”

\leavevmode\llap{“}True,” Dusty said. “The stripes hit the place with some sort of seismic megaspell. Tore the ground right up. Not sure why they did that instead of balefire. Maybe they figured it’d wreck factories better or something.”

I pulled out the thick pin holding the mount in place, then struggled to lift the gun. Dusty had asked me to take down the gun; if raiders were driving around in motorwagons, he wanted us to do everything we could to not look hostile. “How bad is it?”

\leavevmode\llap{“}Not sure,” Dusty said. “I’ve never been here, before. Way I hear it, the ground split open in some places, and shot hundreds of feet into the sky in others. Ah, there we are.”

The vehicle rattled as we rounded another rocky hillside, and I finally got the gun down, placing it in the cargo bed. I climbed back into the rear seat, and through the front windows, past the jagged rock formations that hemmed in the rocky road, I could see massive iron gates spanning between two cliff faces. They were overlooked by battlements, with a wild variety of ancient signs, strips of canvas, and other seemingly random adornments arrayed around the tops.
I settled into my seat, gathering my belongings. My armor was already hidden with my disguised form, but I took the time to remove most of the combat-related equipment from my walking-around gear. The pistol should be more than enough.

I was almost done when Starlight gave a quiet gasp. “Oh shit.”

Looking forward, I didn’t immediately see what drew that reaction. It wasn’t until I noticed she was looking upwards that I leaned my head out of the window to see what she had seen.

What I found sent a chill through me.

Above the massive gate, suspended by her neck, hung the corpse of a changeling.