I’ll admit to a small measure of irony in our direction and leadership. As of late, our goals had been entirely of my own creation. Sure, at least some of those goals resonated with my companions, especially when they served to help ponies, but I still appreciated just how much they were willing to help me.

Yet even as I provided the motivation, we all deferred to Dusty’s leadership. He had the experience with the Wasteland that I lacked, and his understanding of tactics and coolness under fire had likely saved our lives many times. On top of that, he made a decent face for our little group. He might not have the social skill training of an Infiltrator, but he was a decent pony. Blunt and occasionally gruff, but decent, and I think ponies tended to respect him for it.

I was happy with that arrangement. I know it might seem strange for an Infiltrator to stand back and let someone else do the talking for them, but it could be equally nice to enjoy the benefits of being one of the background ponies, there but not really seen. A good Infiltrator needs to know when to follow a pony’s lead.

But a good Infiltrator also needed to know how to adapt to a changing situation.

So I had been the first to dismount, approaching the guard with a soft smile, while Dusty remained in the background, tending our cargo.

\leavevmode\llap{“}We’re looking to unload some cargo,” I said in answer to the question of our intentions. I followed up by offering a hoof, the light-tan coat quite different from my familiar default. “I’m Summer Breeze.”

\leavevmode\llap{“}Uh-huh,” the guard said, following the minimum standards of social etiquette by giving my hoof a single cursory shake before returning his hoof to the ground. He was a rather rugged type, clad in a mix of metal and leather that could have passed for raider garb if it were a bit dirtier. A large-bore pipe rifle hung at his side. “And where did you get \textit{two} motorwagons?”

\leavevmode\llap{“}Oh, I lucked out on that!” I said with a soft chuckle. “Our ride came from some slaver types, and my crew nicked it when they made their escape. I bought it from them for a steal, on the condition I hired them. I’ve got to say, it was one of the best deals I’d ever made!”

It was an absurdly flimsy story. If there really were Serenity changelings in Trotsen, and they recognized my companions, then it would be a natural conclusion that the one unrecognized pony was the changeling known to be in their company. On top of that, there was the general risk that always came with lies. Most notable of those was the risk that one of my companions might flub their part of the story. We had agreed to mitigate that risk by them saying as little as possible.

I was also quite conscious of Echo’s poorly concealed disapproval of my methods, as she stood rigid and frowning beside our wagon.

We could only hope that any Infiltrators were more interested in a changeling going by the name of “Whisper”, and might not immediately recognize the ponies she was known to travel with. I just wished Sickle wasn’t quite so distinctive.

\leavevmode\llap{“}The other one came from some raiders that attacked us earlier today,” I continued. “They wrecked trying to drive us off the road, and hey, free motorwagon! I mean, we don’t \textit{need} another motorwagon, but I figure we could make some good caps off it.” My smile grew as I leaned in toward the guard. “I figure you guys already got a lot, so I could \textit{probably} get a better price at Mareford, but, you know, we’re already here, so if somepony were to offer, I \textit{suppose} I could let it go…”

Of course the guard wasn’t the pony I should talk to about that, and he showed the appropriate lack of interest in my offer—even with the pretty mare smiling at him—but I hadn’t expected him to be interested. I was selling a role, not a motorwagon.

\leavevmode\llap{“}Uh-huh,” he said, looking over the two vehicle. “We’ll have to inspect your cargo.”

\leavevmode\llap{“}Sure thing!” I said, giving a nod, and stepped to the side, gesturing forward with my hoof. “Just be gentle. It’s mostly weapons and ammunition we took from raiders. Like, three or four groups, now.” I gave an awkward laugh. “It’s been an \textit{interesting} month.”

\leavevmode\llap{“}Uh-huh,” he said again, approaching the wagon itself.

The pair of guards who had been standing behind him followed. I followed lazily behind, hopping up to sit on the hood of the motorwagon as they conducted their search.

The courtyard behind the gate was wide open, with the bare dirt criss-crossed with tire tracks. Behind us, the giant gates loomed overhead, shut now, with a few more guards keeping an eye on us. Ruined buildings lined the small canyon ahead of us, with structures built right into the cliff faces. At the tops, pipes and broken walls hung over the edge where the ground had split long ago, and several piles of rubble had been shifted aside to clear a road through the canyon.

I turned back to the guard, who hung on the side of the motorwagon, looking over our cargo. “Speaking of interesting, what’s with that bug over the gate? You guys got some sort of infestation? I’ve seen lots of mutated insects out there, but never one so pony-like.”

\leavevmode\llap{“}You could say that,” the guard replied, but remained focused on his work.

\leavevmode\llap{“}That so?” I grinned, tapping a hoof against the hood as I mused, “Maybe it’s good we picked up so many munitions. Bugs that big must take some ammo. This trip might be more profitable than I thought. Hmm…” After a moment of feigned thought, I looked back to the guard. “But why’s it hanging from the gate? That’s kind of, you know… gross?”

The guard grit his teeth. “That \textit{thing} is a changeling, and it’s hanging there as a warning to others like it.” He shot me a harsh glare. “And part of this inspection is making sure \textit{you’re} not changelings.”

I cocked my head to the side, showing a moment of confusion before snickering and pointing a hoof to my face. “Do I \textit{look} like a bug?” I laughed softly, then paused, my smile fading away. “What’s a changeling, anyway?”

\leavevmode\llap{“}Shapeshifting bugs,” he said in a low grumble, turning back to the cargo and pushing a few boxes around in his search. “They kill ponies and take their place, then they get all buddy-buddy with you so they can drain you dry.”

I stared, mouth hanging half-open for a moment before snapping shut again. “You’re messing with me. Seriously?”

\leavevmode\llap{“}Yes, seriously,” he said without looking up.

I sat there, blinking a few times. “That’s… really fucking creepy.” I shook my head, then looked over to Starlight and Dusty. “Okay. New rule! No splitting up. Like, at all. And… yeah, I think we’ll need a change of plans. I know you guys want some time to kick back and relax, but I think we’re leaving as soon as our business is done.”

Sickle grumbled, just as I expected, and I waved a hoof. “I know, I know,” I said, putting on a show of conciliation. “And I’m sorry. Once we get to Mareford, I’ll add a couple days to your break to make up for it. Okay?”

She answered with a grunt.

The guard poked at something, then looked to me. “Is this artillery?”

I climbed onto the roof of the motorwagon to see what he had found, then smiled. “Oh, yeah, the mortar! Got a dozen rounds for it, too. Feel free to make an offer!”

Dusty’s gaze flicked my way, and I was pretty sure the guard saw it. I immediately moved to respond to the look of concern. “Yeah, I know,” I said, giving a dismissive wave of my hoof, though I chuckled as I did it. “‘It’s useful’. I know you like keeping equipment available for emergencies, but I have to make some caps. Besides, what do we need a mortar for? A raider ambush? It’ll all be over before you can set it up.”

While he still looked concerned, he gave a shrug. “I guess.”

I looked back to the guard. “But if you want \textit{real} heavy firepower, you’ll want to see what we’ve got in that case. The one in the back, behind the clunky looking armor. I got three balefire eggs in there. I’ll offer you a good deal for them. Twenty five hundred caps each, or I can sell them all for seven thousand. I’ll even throw in the case for free!”

The guard snorted. “Do I look like a fucking merchant?”

\leavevmode\llap{“}No,” I said, smiling a little more. “But I like to practice my sales pitch. Besides, I tell you, word gets out, maybe whoever buys the supplies for you guys decides you could use a bit more firepower! Especially with the whole bug-pony infestation.” I paused, tapping my chin with a hoof. “...Though I guess if they’re in town, that might be overkill. Oh well. I’ve got plenty of other merchandise. Maybe you could use them for something else? I suppose you’d be the one to know.”

\leavevmode\llap{“}No, we don’t want it,” he grumbled. “And like hell you’re bringing it into town.”

I let my ears droop. “But how am I supposed to sell them if I can’t bring them in?”

\leavevmode\llap{“}I don’t care,” he said. “You’re not bringing a bunch of balefire eggs when anypony could be one of those bugs.”

\leavevmode\llap{“}Surely there has to be some sort of compromise?”

\leavevmode\llap{“}No compromises,” the guard said. “Not for some unknown merchant. You can either let us hold them while you do your business, or you can get lost.”

I frowned. “That’s going to make it hard to sell them.”

\leavevmode\llap{“}I don’t care.”

I continued to frown for a moment before sighing. “Fiiine. Maybe I can work out a deal to transfer it when we’re out of town, but to tell the truth, I kind of doubt I’ll be able to move those things.” I turned. “Sickle? Would you kindly unload the case for this gentlecolt?”

She snorted and hauled out the case, while I turned back to the guard. “So, where can we park? I hope it won’t be too far from any markets.”

\leavevmode\llap{“}You can park anywhere there’s enough room,” the guard said as he gave one final check, then hopped down. “Just keep the speed down. You run into anything or anypony, you’ll be paying for it, one way or another.”

\leavevmode\llap{“}We’ll be careful,” I said, smiling again. “So, I’m looking to sell a good deal of munitions, some high-tech equipment, and possibly the second motorwagon, once it’s repaired. Are there any shops or ponies I could go to?”

\leavevmode\llap{“}Yeah, sure,” the guard grumbled, gesturing a hoof to the small canyon, the one path into the rest of the town. “Over there.”

\leavevmode\llap{“}Well, I’m sure we’ll find something,” I said as I dropped into the cargo bed. Sickle was already climbing back in, the case of balefire eggs left in the care of the guards. I hoped we would see them again. “Thanks for the help. Let’s go.”

We left the scowling guard behind as Starlight drove us slowly forward. As I settled into the back seat, Dusty turned back to me, speaking quietly. “I don’t like leaving those balefire eggs with them. If any of them are changelings—”

\leavevmode\llap{“}We don’t have a choice,” I said, shifting around to get comfortable. “Part of being an Infiltrator is accepting that things aren’t always in your control, and sometimes you just have to roll with what you’re given. On the plus side, if there was any infiltration of the guards, it’s small. It’s the scenario that best fits the situation. The balefire eggs should be well-guarded. It’s certainly not impossible for them to be stolen, but they’re probably more safe in their care than they are in ours.”

\leavevmode\llap{“}We could have turned around and gone somewhere else.”

\leavevmode\llap{“}Where?” I asked. “We know they’ve gotten into Trotsen and Mareford. We know at least one of their agents has been going around smaller towns. There is no avoiding this. There are no safe havens, unless we \textit{make} it safe.”

The motorwagon slowly wound through the canyon, passing several houses built along the side of the road, and beneath a few walkways crossing overhead.

\leavevmode\llap{“}This is sounding worse and worse,” Dusty said as he settled back into his seat.

\leavevmode\llap{“}Counterespionage is a \textit{bitch},” I said. “It’s a bit out of my field, but I had enough education on the basic topic to understand the difficulties and uncertainties that abound.”

\leavevmode\llap{“}You’re not making this sound any better.”

\leavevmode\llap{“}I know. Right now, all we’re doing is gathering information. Then we’ll see if there’s some action we can implement, or if we’ll just move on like with our cover story.”

Dusty sighed. “I really don’t like this whole damn thing.”

Beside him, Starlight cracked a grin. “I dunno, it’s kind of exciting, like I’m in some spy story or something.”

\leavevmode\llap{“}Just don’t get too excited,” I said. “Espionage is mostly long stretches of boring mundanity set to the backdrop of ever-looming danger.”

Dusty grumbled, but said nothing.

As we emerged from the short canyon, the ground to one side dropped several hundred feet, giving a spectacular view of the ruined city of Trotsen.

It looked as if the ground had been torn apart and clumsily thrown back together, forming a wide cauldron of erratic terrain. Jagged spires, some still topped by ancient buildings, loomed over wide crevices. Ancient factories lay in ruins, with many upended and broken where the ground moved beneath them. Newer buildings made of scavenged materials dotted the broken landscape, and wide dirt paths wound their way through patches of level ground. Stretches of canvas, like great sails, hung over several of those paths and other public areas, while colorful ponies and the occasional banner broke up the grays and browns and bare steel of the settlement.

The path was surprisingly wide as it followed a shallow slope, and we descended into the town.

An impressively well-made bridge spanned a narrow, deep chasm, and we rolled slowly across the softly creaking structure to enter the town proper. Ahead of us, the path split up, shooting off in different directions between the haphazard buildings and uneven terrain.

A pair of ponies sat on a patio overlooking the chasm we had just crossed, watching our progress with curiosity. I had Starlight stop us, and climbed up to sit on the edge of the window. After giving a friendly wave, I called out, “I was hoping to do some trading, but we don’t really know our way around. Any chance you could point us in the direction of any shops or markets?”

Still looking a little confused and uncertain about our presence, they both pointed to one of the paths. “Thanks!” I said with a wide grin, then slipped back inside to pass the directions on. A moment later, we were rolling again.

The path was nice and wide, easily able to accommodate our motorwagon with plenty of room on either side, even as the tall buildings, mostly made of salvaged metal, loomed above us. The scattered ponies wandering the path casually made way for us, though several did watch us pass with curiosity, and perhaps a measure of suspicion.

Quite a few of those ponies wore armor of welded metal, with various embellishments and decorations. Short, blunt spikes seemed the most common, but there were a wide variety of patterns and designs. One lean, elegant-looking mare wore a set of fairly skimpy armor, polished to a fine shine and adorned with long strips of dyed cloth. A less refined-looking pony wore a set patterned to resemble a skeleton, complete with a helmet that was currently hanging from his shoulder.

It seemed it was the local fashion choice. Even the many who did not wear anything that could be described as armor tended to have some small neck-piece or other adornment.

The path opened into a small square, with huge stretches of canvas hanging overhead and a small number of shops, their fronts opened up to let passers-by see their wares. While the town looked to be almost as big as Mareford, the pace of the little market was rather relaxed. Business appeared to be slow but reasonably steady, and the shopkeepers that weren’t currently tending customers were mostly relaxing.

I spotted a pair of likely shops with a convenient open stretch of dirt nearby, and directed Starlight to park there. The shopkeepers were watching us with varied expressions as I climbed out the window.

\leavevmode\llap{“}That’s a nice set of wheels you have there,” said the smiling stallion, whose shop appeared to deal primarily in arms and armor. Even with my experiences in the Wasteland, I was still a little surprised to see such a specialized shop. “Don’t think I’ve seen this one, before. Where’d you get it?”

\leavevmode\llap{“}Belonged to some slavers that tried to take my crew,” I said, and gave the roof a loving pat with my hoof before hopping down. “And now it belongs to us.”

\leavevmode\llap{“}More likely she stole them,” said the mare opposite us. Her shop featured many pieces of wartime technology and other old-world artifacts, which I had figured might be useful both for unloading the equipment we had acquired, and to supply any parts Echo might need for her repairs. Given the glare the shopkeeper was giving us, I suddenly questioned whether we could hope for a fair price.

\leavevmode\llap{“}If some slavers or raiders attack you, it’s hardly stealing to keep their stuff,” I said, offering a smile in hopes of softening her reaction.

Sickle backed me up with a chuckle. “Yeah. Ain’t like they were going to use ‘em any more, being all dead as fuck.”

\leavevmode\llap{“}Anyways,” I continued, attempting to divert the conversation in a more productive direction. “I’ve got a lot of equipment I was hoping to trade, if—”

\leavevmode\llap{“}You a changeling?” the mare asked, eyes narrowed at me.

I blinked at the bluntness of the question. “What, those bug-things the guard was talking about? No, of course not.”

\leavevmode\llap{“}Uh-huh,” she said in a clearly suspicious tone. “That’s just what a changeling would say.”

The other shopkeeper called out. “That’s what a pony would say, too.” He turned and shot me a smile. “Don’t mind Cactus Rose. She’s prone to dramatics and as prickly as her name.”

The mare wheeled around and shouted. “Oh, bite me, Sagebrush! You know there are changelings all over the place. Any stranger could be one! Well, I’m not going to let those nasty little bugs take advantage of me!”

\leavevmode\llap{“}Seems to me, if they’re going to impersonate somepony, it’d be a pony we all know and trust, instead of some outsider,” Sagebrush replied, his smile turning sly and playful. “Maybe even some pony that’s always saying \textit{other} ponies are changelings.”

Cactus Rose’s eyes widened, then narrowed in anger. “Well at least I know \textit{you’re} not a changeling. No bug could be such a perfectly intolerable ass as—”

\leavevmode\llap{“}Woah, woah,” I said, stepping in and raising a hoof. “No need for us to all fight amongst ourselves. I just wanted to do some trading, nothing more.”

\leavevmode\llap{“}Well I’ll be happy to trade,” Sagebrush said with a smile and a nod before looking to the other mare. “Rose?”

She frowned at me for several long seconds before replying. “I don’t trust her. She could be a changeling.”

\leavevmode\llap{“}I’m not,” I said, nice and casual. “All I want to do is trade some goods and make some caps. Okay?”

She eyed me for another second before giving a snort. “Fine. I’ll trade.” Then she lifted a hoof, pointing at me. “But I’ve got my eye on you!”

I held up a hoof in mock surrender before turning back to my ‘crew’. “Okay, let’s start unloading some of the trade goods. Dusty, I’ll let you take care of any munitions. You know that sort of stuff better than I do.

\leavevmode\llap{“}You got it, boss,” he said, with a poorly hidden smirk, and Sickle snickered behind him.

While they did that, I took the opportunity to browse Sagebrush’s goods. It was mostly on the simpler side of things, with several pipe guns and simple metal armor, and even some spears and blades.

\leavevmode\llap{“}Got some armor, if you’re looking for protection,” he said. “It’s a dangerous world, you know. Would be good to have some sort of protection. Get some proper armor, we could get you looking like a proper rider in no time.”

\leavevmode\llap{“}Thanks for the offer,” I said, giving a charming smile. “But I’m really not much of a fighter, and the wagon has better armor than I could carry.” Then I chuckled, inclining my head. “Besides, if my alicorn friend back there gets that power armor working, she’s going to try to stuff me into it.”

\leavevmode\llap{“}Yeah, that’s a fine piece of hardware,” he said, peering past me to catch a glimpse of the armor in question. “Not very practical for walking around town, though.”

I raised an eyebrow. “I hope it’s not so dangerous that I \textit{need} armor here in town,” I said, putting just a hint of unease into my tone. “I mean, I saw everypony walking around in armor, but…”

\leavevmode\llap{“}Oh, no,” he said with a chuckle. “That’s just the local style. Everypony wants to be a rider, so they all dress up like it. Though I guess there is the whole changeling mess. To be honest, I think a pony’s more likely to have trouble with ponies thinking they’re a changeling than they are from \textit{real} changelings, even assuming there are even any still in town.”

\leavevmode\llap{“}Wait,” I said, ears perking up alertly. “You mean there’s this whole mess with the cranky guards and suspicious ponies, and nopony even knows if there’s actually any more of these changelings?”

\leavevmode\llap{“}Oh, we know!” Cactus Rose shouted out from her storefront, while Echo tried to get her attention.

Sagebrush rolled his eyes at her shout before looking to me again. “You saw the one they strung up by the gate, I take it?”

I nodded.

\leavevmode\llap{“}That’s the only changeling we’ve seen,” he said. “Got the guards all shook up, though. It killed the captain of the guard and took his place. I guess the guards just stumbled into discovering what happened. Now everypony’s paranoid. They figure, if they replaced a pony that high up, who else might have been replaced?”

I gave a show of considering that, wearing a faint frown. After a moment, I glanced to him again. “You seem rather relaxed about this. You’re not worried?”

\leavevmode\llap{“}More like, what can I do?” He shrugged. “I don’t even know if there’s anything \textit{to} worry about, or if it was just some lone bug. If any pony could be one of those things, I could worry myself to death trying to figure out who is, without even knowing if there’s anything worth worrying about. If anything, I’m more afraid of what other \textit{ponies} are going to do.” He gave a subtle gesture in the direction of Cactus Rose. “She ain’t the only one worked up about it, even if she’s maybe the most unhinged.”

\leavevmode\llap{“}It’s really that bad?”

\leavevmode\llap{“}Well, it ain’t \textit{good},” he said. “Ponies are worrying that if Captain Iron Hoof could be replaced, anypony in power could be. Maybe even Sandstorm.”

\leavevmode\llap{“}I’m sorry,” I said, holding up a hoof. “I’m afraid I don’t know a whole lot about this town. Who’s Sandstorm?”

\leavevmode\llap{“}She’s the top rider,” he said. “Means she’s in charge here. Also means some ponies think she’d be a perfect target for those changelings to replace.”

Cactus Rose shouted out again. “Don’t tell her all that! She could be a spy!”

\leavevmode\llap{“}She’s not a spy, you paranoid twit!” he shot back. “A spy would already know all this!”

\leavevmode\llap{“}Maybe it’s an act!” Rose replied. “Act all dumb-like, so we \textit{think} she’s not a spy, only she is!”

\leavevmode\llap{“}Why don’t you tend to your own customer?” Sagebrush said, gesturing to Echo, who was frowning down at the inattentive shopkeeper, an old blender suspended in her magic.

When Cactus Rose turned away, grumbling, Sagebrush returned to me. “Sorry about her. Anyway, see anything here you like?”

\leavevmode\llap{“}I’m afraid we’re already pretty well-stocked for weapons and ammunition,” I said. “We’ve got some good quality pieces you might like, if you’re interested in stocking some more high-end weaponry, but I’ll let my associate handle that. He’s my gun stallion.”

\leavevmode\llap{“}I’ll certainly take a look,” he said with an appreciative smile. “The riders are always looking for new toys to play with.”

\leavevmode\llap{“}I just hope they’re not going to be turning them on each other,” I said, slowly shaking my head. “Sounds like things are a mess.”

\leavevmode\llap{“}Yeah,” he said, the smile vanishing again. “Hell, this whole thing… I doubt you’ll have any trouble, if you’re just passing through, but…” He glanced past me for a moment before giving me a serious look. “You might want to keep that big mare with you, just in case.”

\leavevmode\llap{“}That’s sounding like a good idea,” I said, pinning my ears back in a look of concern. “I hope things aren’t getting, um… violent.”

\leavevmode\llap{“}Ponies are scared and don’t know what’s going on,” he said, giving a weary shrug. “I mean, it’s been great for business, but maybe not so much for my health. Hell, normally I’d say Trotsen’s a great place and tell you to relax, but we’ve already got three dead ponies because of this mess. If I had some wheels of my own, I might do the whole wandering merchant thing too, at least till this blows over. Speaking of, I don’t suppose you’d entertain any offers for one of your wagons?”

I had perked my ears up, widening my eyes a bit. “W-wait, \textit{three} dead ponies? You mentioned the guard captain—Iron Hoof, right?—but who were the others?”

He sighed, ears drooping a bit. “Hell, I’m almost surprised you didn’t hear about it already. Whole town’s been talking about it, which sure as shit ain’t helping the whole paranoia thing.”

\leavevmode\llap{“}It isn’t paranoia!” Cactus Rose shouted, while Echo glowered with annoyance behind her. “One of those bugs tried to kill Sandstorm!”

Sagebrush rolled his eyes and ignored her. “Somepony named Anvil ran at Sandstorm with a shotgun. Put a shot into her armor before he got gunned down by the guards. I don’t know. His family said he was acting strange before that, so they and a bunch of ponies say he was replaced. Except, some of the ponies he hung out with said he’d been talking about how a changeling could have replaced Sandstorm and nopony would know. Some ponies think he was trying to be a hero.

\leavevmode\llap{“}And then there’s Ivy and Lily. They’re sisters. \textit{Were} sisters, I guess. Yesterday, Ivy shot Lily in the head. She said Lily had been acting all weird, like she wasn’t her sister, and everypony was talking about these changelings that could impersonate anypony. Said she realized what had happened, so she pulled a gun, started demanding to know where her sister was. Guess she didn’t get the answer she wanted. Now she’s in jail and nopony knows what to do with her, ‘cause they don’t know if the mare she killed was a pony or a bug.”

I didn’t have to fake the look of unease, not with the cold sensation that was gathering in my gut. They might not know, but I did. If either of those ponies had been changelings, there wouldn’t have been any doubt.

{\br}%
We found accommodations at an unusual establishment, consisting of several separate, small buildings set on the side of one of the jagged monoliths protruding up into the sky. A few such buildings had been built further up, home to the town’s few griffin residents, but the small cluster of buildings forming this particular establishment were owned by a pony. She, in turn, rented the small huts to visitors. The one we had been given had two bedrooms, with a main room overlooking the town. It gave a decent view, and more importantly, a good degree of privacy.

I sat on the worn cot, staring off into space and idly rolling my last matrix disruption grenade between my hooves. While the others cast off their gear and settled in, I was lost in thought.

We’d visited several other merchants. Some were as paranoid as Cactus Rose, while others were more welcoming. Despite those differences, almost all of them were wary of other ponies, whether strangers or not. I’d caught narrow-eyed glances at other nearby ponies, and the generally cautious, closed reactions they gave. Even the innkeeper, an elderly mare who looked like the perfectly archetypical kindly grandmother, gave us all a long, wary look, as if she might be able to pick out a changeling’s disguise through careful scrutiny.

It was wartime Equestria in miniature, but even more volatile. There were no megaspells, but there was also no veneer of a greater society with its laws and traditions. If things continued as they were, Serenity might not even have to set hoof in Trotsen again. Ironically, the truth was working better for them than any deception they could have tried. With the exposure of a single agent, they were tearing a town apart. They had bred anger and paranoia, but the ponies of Trotsen had nowhere to direct those feelings, and so they turned inward on themselves.

They had surely not intended to lose an Infiltrator simply for that, but that didn’t change how it worked in their favor.

As paranoid as ponies were, it wasn’t hard to subtly steer conversations with other merchants in directions where they shared more information, though it mostly all told the same story. Ponies were scared. Anypony could be a changeling. The ponies in charge, the riders, were trying to keep order and find out if anypony else had been replaced, but every single action they took was seen by some as changeling spies trying to secure their hold over the town. Some even talked of dissent among the riders themselves, as those in power worried that their ranks might have been infiltrated.

It was a mess of rumor, hearsay, and speculation. A black pit of misinformation from which no knowledge could be extracted.

We needed to set a course of action, and we needed to do it before the whole situation exploded.

Dusty had finished stowing his gear when he approached me. “You’re being all quiet again. Have you figured out how we should handle this?”

\leavevmode\llap{“}Maybe,” I said, slowly rolling the grenade between my hooves. “It’s a messy situation.”

He snorted. “No shit.”

\leavevmode\llap{“}Well, they obviously know changelings are a problem,” Starlight said, before frowning. “Which I guess is only \textit{mostly} a good thing.”

\leavevmode\llap{“}Sure,” I said. “On the plus side, they know there’s a threat, and they’re eager to strike back. Motivating them to fight will be easy.” I rolled the grenade the other way. “On the other hoof, they’re paranoid. Some stranger coming to them, offering them information on their mysterious and deceptive enemies? They’d have to be shockingly naive to not think that we were changelings, ourselves. It’s too convenient. How did we get this information? How do we explain how we know where their hive is? How would we have gotten that information?”

Starlight shrugged. “They did capture us. Wouldn’t that work?”

\leavevmode\llap{“}Oh, really?” I said, putting on the persona of some anonymous but suspicious official. “So they captured you, took you down into a heavily fortified Stable, and you just walked right out the front door? They just let you go?”

Starlight frowned. “Well… I mean, it’s true. Except they didn’t \textit{let} us anything.”

\leavevmode\llap{“}‘True’ is not the same as ‘believable’,” I said. “They’d want to know how and why. How? I’m a changeling Infiltrator, and I used my evil shapeshifting powers to impersonate others and sneak us out. And then they shoot us. Or we come up with some complex lie to explain how we got out, and hope we all do such a meticulous job of storytelling that they don’t see the inevitable flaw and shoot us. Or we do everything perfectly, come up with a perfectly plausible and believable story for how we could have escaped… and they think our story is flawless because we’re changeling spies trying to manipulate them, and shoot us anyway.”

Starlight’s frown deepened.

\leavevmode\llap{“}Then there’s the information I can give on combating changeling Infiltrators. How do I know that? Long experience facing them? Then how are we still alive, and how has nopony else heard of these changelings? Experience at espionage? Now I’m a professional liar. I’m actually a changeling? I’m one of the enemy. Oh, ‘but I’m one of the good ones!’ That’s just what a spy would say.”

Sickle snickered. “Or maybe you should stop whining about it, storm right up to whoever is in charge, and lay down how it is.”

\leavevmode\llap{“}Close,” I said.

Sickle stopped, cocking her head slightly to the side as she looked at me. “Yeah?”

\leavevmode\llap{“}There’s only three ways I can see this going,” I said. “I don’t want to cut and run. Yes, we could get out before the paranoia boils over and we get caught in the crossfire, but if we do that, lots of ponies are going to die, and one of the largest obstacles to Serenity goes down with them hardly lifting a hoof.”

\leavevmode\llap{“}I’m not against a tactical retreat when it’s necessary,” Dusty said, “but that’s a ‘last resort’ kind of thing.”

\leavevmode\llap{“}Agreed,” I said. “At the same time, I also don’t want to try some elaborate lie to pass on this information, whether by planting bits of information or coming up with some complicated backstory for how we acquired it. It would be difficult enough to pull off if I were the only one involved. With five of us, I’d say it’s impossible. Even if we carefully plotted and rehearsed everything, there’s always going to be gaps, and that means improvisation. With how dissimilar our training and experience is, there’s no way we’re going to improvise along similar lines, and it will be impossible to predict what the others might have said. That means any attention paid to our story would turn up flaws, and any flaws are going to be seen as a sign that we’re changeling spies.”

\leavevmode\llap{“}Which is so stupid,” Starlight said, cracking a wry smile. “Only \textit{one} of us is a changeling spy.”

I gave a chuckle, though the humor faded almost immediately. “But the fact is, every option we have is problematic. Whatever we do is going to have risks. With all that said… I think deception is going to do more harm than good.”

\leavevmode\llap{“}Finally!” Echo blurted with a sudden exhalation, as if she had been holding the word back for some time. She continued in a more conversational tone. “It has been most uncomfortable remaining silent in the face of your scheming. It is good that you should cast off the habit of deception and return to the values of Harmony.”

I sighed. “I told you, I prefer the truth when possible.”

Starlight was snickering softly. “You know, Echo, you sure are super gung-ho over the whole Elements thing for somepony who barely knew they existed a few days ago.”

Echo turned on her, her mane flaring and eyes narrowing. “I know the Elements quite well! We have seen them. We have touched them. We have \textit{used} them!” She stomped a hoof, looking away from Starlight in disdain. “Except for my sisters, I likely know more about the Elements than anypony alive.”

At least, I think that last bit was what she said. I didn’t quite catch it. I think there was a moment of others speaking, as well, though I definitely didn’t catch that. It wasn’t until Dusty spoke my name that I realized I was gawking at Echo, mouth hanging halfway open.

The purple alicorn who stood before me wasn’t just a mere pony. She wasn’t even “just” an alicorn. I knew, or at least, strongly suspected, their origin. She was a testament to Equestria’s mastery of magic. Perhaps the greatest project of the Ministry of Arcane Sciences, and the final legacy of the Mare who led them.

\leavevmode\llap{“}Are you Twilight Sparkle?”

Echo’s deep, violet eyes locked with my own. “...No,” she said, before turning away again. “But we remember being her, just as we remember being so many others before we came together in Unity. We remember them, but they are not me.”

\leavevmode\llap{“}Are you sure? Because—”

\leavevmode\llap{“}I am quite sure,” she replied sharply, eyes narrowing a touch. “And this inquiry into my past is a useless distraction from the more important matter at hoof.”

I shut my mouth, despite the many questions and concerns racing through my mind, and finally nodded. “Okay.”

Starlight cautiously raised a hoof. “Assuming we’re done with… whatever that was, I have a question.”

I tore myself away from staring at Echo to address Starlight. “Yes?”

\leavevmode\llap{“}Yeah… isn’t being honest one of those ‘then they shoot us’ things?” Starlight asked. “I mean, we’re all worried about them finding out you’re a changeling because they’d think you’re a spy, right?”

\leavevmode\llap{“}Like I said, there are going to be risks, so we need to take a few steps to minimize that risk.” I looked back to Echo. “To start with, how far could you teleport all of us, in an emergency?”

Her expression softened, losing the glare as she quickly considered the problem presented to her. “Without any time to prepare, and all together? A hundred yards should be quite easy, though I could make no promises for the smoothness of the journey. With a few moments to prepare and properly align the arcane energies, I could easily double that or more.”

\leavevmode\llap{“}Okay. Do you think you could teleport the motorwagon, if it was necessary?”

Her ears flicked back, and she frowned. There was a momentary pause before she replied. “I am a great and powerful child of the Goddess. No task of magic is beyond me. However… I must admit that I have never attempted to teleport anything quite so massive. I could make no concrete promises of distance without having ample time to practice for the task.”

\leavevmode\llap{“}Hmm. That’s not ideal.” I looked around. “I’d like to have a way of getting our motorwagon out of town in a hurry, if it becomes necessary. We can always leave without it, but I’d rather not.”

\leavevmode\llap{“}Oh, that is trivial,” Echo said. “We have sufficient explosives to breach their gate many times over, and I am certain the vehicle can climb over whatever is left.”

\leavevmode\llap{“}Preferably \textit{without} causing massive destruction,” I clarified with a disapproving stare.

\leavevmode\llap{“}Oh,” she said, frowning in thought. “Well, I suppose I could teleport into the gate room and force it open from there. It would take several more seconds, and I suppose it is more practical, but it does seem to lack that dramatic flair of making an explosive exit.”

\leavevmode\llap{“}I like to minimize dramatics,” I said. “Next up: I know you’ve only just started studying changeling magic, but you should have enough knowledge to make a guess. Could you produce a spell to undo a changeling’s disguise?”

She tilted her head, thinking for a moment. “There are some notable differences between changeling and unicorn magic that would make replicating such a spell difficult, but it is much easier to disrupt a spell than it is to form one. I believe I could create such a spell, yes.”

I nodded. “And how long would that take?”

\leavevmode\llap{“}Hmm. For a properly formatted counterspell to a rather different method of spellcasting? I suppose it depends. Are we concerned for the well-being of the subject?”

\leavevmode\llap{“}We absolutely are,” I said.

\leavevmode\llap{“}I had thought so. In that case, I would estimate a few weeks for a refined and efficient spell, though I could likely produce a crude, brute-force method in only a few days. I must caution that these are rough approximations, however, and do not account for unexpected hindrances or breakthroughs.”

\leavevmode\llap{“}That will probably take too long for what I had in mind,” I said. “Still, I’d like you to start on that. It would give us more options in the future. As for now…” I held up the grenade I had been holding the whole time. “We need to hit the markets tonight, and find as many matrix disruption grenades as we can. If we’re lucky, there might be a few for sale.”

Dusty raised an eyebrow. “What for?”

\leavevmode\llap{“}A spell matrix is nothing more than an artificially cast and sustained spell. Matrix disruption grenades are designed to disrupt them. With a little tweaking, they can be altered to affect other magical patterns. Do it just right, and you can disrupt the magic a changeling uses to sustain their transformation. You force them back to their natural form.”

\leavevmode\llap{“}Oh,” Dusty said, his eyes brightening up. “And you know how to do that?”

\leavevmode\llap{“}In theory.”

The look of wariness returned as he echoed, “In theory.”

\leavevmode\llap{“}So long as you know the appropriate output values, it’s a very simple modification,” I said. “I just haven’t actually done so, before.”

\leavevmode\llap{“}So you’re hoping to uncover changeling spies we don’t even know are there using modifications you’ve never performed to matrix disruption grenades that we don’t have.”

\leavevmode\llap{“}Oh, no, of course not,” I said, shaking my head. “It would be wonderfully convenient to uncover a changeling spy as a way to influence these ponies’ view of us, but I would never bank on luck. They might be something I can leverage in negotiations, but they’re also a cheap and low-risk shot in the dark. More importantly, they’re a good precaution, just as having Echo prepared to teleport us to safety is.”

\leavevmode\llap{“}Uh-huh,” he said, the frown returning. “How likely do you think it is that we’ll succeed?”

\leavevmode\llap{“}Unfortunately, it’s impossible to say,” I said. “I can say that our odds of escaping if things \textit{do} go poorly are very good, thanks to Echo.”

\leavevmode\llap{“}Let’s just hope we don’t have to find out,” Dusty said with a shake of his head. “Okay. What’s the plan?”

{\br}%
We walked right in the front gate.

Sandstorm, along with many of the riders, lived in the partially intact ruins of the F\&F Motorworks factory. They had a wall with gun platforms, armed motorwagons, and at least a dozen armed ponies milling about.

We arrived early in the morning, but there was already a good deal of activity going on, with armed ponies loading up a pair of motorwagons. The guards on the walls were spending more time watching that than they were the approaches, and they didn’t even notice us until we arrived at the open gate. I greeted them with a smile and pleasant introduction. It was easy enough to arrange a meeting with Sandstorm, especially seeing as we had a motorwagon we were looking to sell.

A guard led us into the main factory building, the front half of which was intact, while the rear half had been obliterated when the ground under it had jutted a good hundred yards upwards. The inside of the main building was dimly lit by the overhead windows, and living arrangements had been made among and beneath the ancient, corroded machinery. Several ponies were gathered around a cooking pit, while others lounged around chatting nearby. It was a small community within a community.

We were led up a set of stairs to the main offices, high above the factory floor. The guard opened the door for us, and we stepped in. It was an appropriately fancy place, with old wood paneling on the walls. While the broad windows looking into the factory itself were boarded over, the back of the room had windows overlooking the front grounds on either side of the large balcony. The room was well-furnished, as well, with a grand desk and an assortment of chairs and couches.

Aside from the two guards within, there were two earth ponies, and it was immediately clear which one was Sandstorm. While she wasn’t particularly big, perhaps even a bit on the lean side, she had a grizzled, sand-blasted look to her. Her yellow coat was marred by several scratches and shallow scars, and looked dry and weather-worn. Beneath that, however, she looked quite fit and athletic, and particularly so for someone who looked to be in their forties, if not older.

She also looked like she was ready for a fight. She wore metal barding with thick, angular plates and blunt spikes along the back. A pipe rifle hung at her side, with a wide, stubby barrel. Unlike most of the pipe rifles I had seen, this one looked almost like a work of art, with extensive engravings covering its length, and a pair of long, black feathers dangling from the barrel.

Surprisingly, she wore a PipBuck on her foreleg.

But what struck me most was her expression. It was hard and attentive, and her eyes practically bored into us. It wasn’t an angry or paranoid expression. It struck me as the look of someone who knew, absolutely, that they were in charge, and who was not about to let anyone forget it.

I worried that her gaze might have lingered ever so slightly longer on me than any of my companions, though I couldn’t say for sure.

She stood by one of the windows, and beside the massive desk. A brown stallion, about the same age as her, sat behind it, and while he had his own armor and had a certain degree of roughness to him, he lacked the mare’s presence.

Sandstorm spoke, her voice firm and slightly gravelly. “You’re quite the unusual group for some merchants,” she said, eyes watching closely for reactions. “Why are you here?”

I took a single step forward, enough to be the forward most of our group, without moving close enough to seem a threat. “My name is Whisper, and I’m here because you have a changeling problem. So do we. I think we can solve our own problem by helping you with yours.”

The reaction was predictably icy. I’m sure the guards behind us had tensed, and the stallion behind the desk eyed us more critically. As for Sandstorm, she held us in the same glare for a long, tense moment before speaking again. “You’ve had run-ins with changelings, have you?”

\leavevmode\llap{“}Yes,” I said. “They want us silenced or dead, and I’m probably about to make us one of their top priorities by coming here.” I looked around the room at the other ponies. “In fact, if any of the ponies in this room have been replaced, I wouldn’t be surprised if they break disguise to attack me when I tell you what I’ve come to do.”

\leavevmode\llap{“}I see,” Sandstorm said, turning to face me more squarely. “And what, exactly, \textit{did} you come here to do?”

I turned my head slightly to indicate my saddlebags. “If you’ll allow me?”

Her eyes narrowed ever so slightly, but after a moment, she nodded.

I calmly opened the flap of the bag and slipped my muzzle in, pulling back a moment later with a datastore between my teeth. Stepping up to the desk with calm, careful steps, I placed it on the edge, then stepped back again. “The changelings you’ve been dealing with have a hive in Stable 112, an undocumented Stable located at a development site called Serenity. I’ve recorded the location on that datastore. They’re led by a changeling calling herself Queen Chrysalis the Sixth, and I’ve included what little knowledge we have on her, as well as the historical connotations of that name. I’ve also included a layout of their Stable, what little information we have on their available assets, which include several motorwagons and an under-repair Raptor-class cloudship, details on how to modify matrix disruption grenades to strip away changeling disguises, and some basic information on changeling infiltration tactics.”

She hadn’t even glanced at the datastore. “That’s a lot of \textit{very specific} information.”

\leavevmode\llap{“}It is,” I said, before answering the unspoken question. “We had gone to investigate the ruins there, not knowing of the Stable beneath. They captured us. They intended to keep us captive as food sources. As for the inevitable question as to how we escaped, the full answer is long and complex, but the part I imagine you would find most relevant is that I am also a changeling.”

There was a single silent moment as several ponies processed that, yes, I had just admitted to that. A second later, the brown stallion rose, quickly reaching for his pistol. He never got there. Purple light flashed around the room, leaving a collection of weapons held above us in Echo’s grasp.

\leavevmode\llap{“}There is no cause for alarm,” Echo said evenly. “If we had intended you harm, we would have already done so.”

The guards, stripped of their weapons, shuffled angrily, clearly wanting to take action, but recognizing just how futile the attempt would be, especially as Sickle turned to square off with the nearest one, grinning as if daring him to try something. Dusty and Starlight both had their weapons out now, though they kept them lowered, not quite pointed at anypony.

The brown stallion cursed. Only Sandstorm had retained her weapon. Her head had turned slightly towards it, but she hadn’t actually reached for it, which was apparently enough for Echo to let her retain it.

Sandstorm eyed the floating weapons, then fixed her eyes on me. “So you’re one of those bugs?”

\leavevmode\llap{“}I am a changeling,” I said. “I come from a different hive, one that’s directly opposed to Serenity’s methods. I would even say we were at war with them if my hive were in any state to be considered a credible opposition. The Wasteland is not an easy place for a species that lives on love and isn’t willing to commit the crimes that Chrysalis condones.”

\leavevmode\llap{“}Uh-huh,” Sandstorm said, continuing to eye me as if her glare might bore right through my disguise. Finally, she said, “Show me.”

I frowned, then gave a short sigh as I unwound my disguise. Green fire flashed. The stallion behind the desk flinched. Sandstorm did not.

Once I had returned to my natural form, I met Sandstorm with a flat glare of my own. “Why is the first response when I tell ponies I’m a changeling always to ask me to show them? What would I gain from lying about \textit{that}?”

Okay, I know, it’s probably more a matter of curiosity combined with a desire to see a rather unusual claim backed up, but still...

As Sandstorm continued to stare, one of the guards shuffled a bit to the side. “Uh, Sandy?”

\leavevmode\llap{“}Relax,” she said, slowly easing her stance. “We’re just having a conversation, aren’t we? So, you’re a \textit{friendly} bug, huh?” One could hardly miss the clear and contemptuous emphasis on ‘friendly’.

\leavevmode\llap{“}Friendly enough,” I replied. “I like ponies. I’ve worked alongside them most of my life, and I don’t like what these other changelings are doing. If you want a more cynical and self-serving reason, we need happy and loving ponies to survive, and given the balance of power, it’s far more in our interests to work \textit{with} ponies rather than \textit{against} you.”

\leavevmode\llap{“}Uh-huh.” She took a slow step forward, and while her posture was more relaxed, her eyes were as hard as ever. “That’s awfully convenient, isn’t it?”

\leavevmode\llap{“}Not from my side of things,” I said. “Convenient would have been arriving \textit{before} some hostile changeling had stirred up paranoia. I could have come here without some pre-existing fears influencing how ponies reacted to me. Instead, I’m putting my life at risk merely talking to you, even \textit{without} revealing what I am. That’s the kind of danger we’re all facing, now.”

There was a pause, as if she was considering what I said. “And what, exactly, do you want from us?”

\leavevmode\llap{“}Minimally, nothing,” I said, and inclined my head toward the desk and the datastore sitting upon it. “I’ve delivered information about the Serenity hive. Even if we aren’t able to do anything else here, that information weakens them. It will help ponies defend themselves, and the further that information spreads, the better it will be for everyone. But that’s just the minimum. Ideally, I’d like to work with you to combat this threat.”

\leavevmode\llap{“}Against your own kind?” Sandstorm asked, her voice level but her intentions clearly suspicious.

\leavevmode\llap{“}Changelings are no more united than ponies are,” I replied. “These changelings are as much my kind as raiders are yours.”

That finally drew a response, a contemptuous snort. I pressed the point. “Serenity wants to take over the Wasteland. They want to enslave enough ponies to keep themselves well fed, and they’ll kill any who get in the way of that, pony or changeling. They already have. I’ve had one of the kindest changelings I’ve ever known bleed out in my hooves because of them, and I’ve walked through the ashes of a pony settlement they leveled just to gain access to some raw materials. My hive won’t survive them, and I expect the losses among ponies will be devastating.”

\leavevmode\llap{“}Uh-huh.” Sandstorm rolled her jaw, eyes looking to the datastore before returning to me. “And let me guess: you have a plan.”

I nodded. “I’d like to help you as an advisor. I know how changeling Infiltrators work, and I’ll offer any knowledge and expertise I can in order to help combat this threat.”

\leavevmode\llap{“}And if I told you to fuck off?”

I hesitated. “Then I’d ask that you let me fully explain things, and if you still feel that our assistance is unnecessary, we would leave.”

\leavevmode\llap{“}Then start talking,” she said. “I want to get this over with.”

Not the best note to begin with.

\leavevmode\llap{“}To start with,” I said, “I don’t think you realize the full extent of this threat. Ponies are paranoid that any of them could be replaced by a changeling, but the fact is, that paranoia isn’t going to help them. You know that changelings are posing a direct threat, but you just had a changeling walk right into your office and disarm every pony in the room. If I had been with Serenity, I could have killed and replaced every pony here, and not a single pony outside this room would know it. You might have a strong fighting force, and might be one of the dominant factions in this part of the world, but for defending against Serenity, all of that strength means exactly \textit{nothing}.”

She snorted derisively. “Sure it doesn’t. That’s why they’re sneaking around instead of trying anything.”

\leavevmode\llap{“}They don’t need to try anything,” I said, and gestured at the window. “The ponies out there are doing their work for them. At least two ponies are already dead, and everypony is growing paranoid and suspicious. The whole thing is a giant bomb, and all that’s needed is a single careless spark to set the whole thing off. If I can see that, you can bet they’re going to see that.”

\leavevmode\llap{“}We don’t know those were ponies.”

\leavevmode\llap{“}Changeling shapeshifting is an actively sustained spell,” I said, my voice softening. “It requires a constant supply of energy to maintain. Not much; a changeling can maintain an easy disguise like a pony for weeks, but it still needs that energy. Without it, the disguise fails, and they turn back to this.” I turned a hoof toward myself before setting it down again. “A dead changeling means no more energy. I’m sure you can see where I’m going with this.”

She had stopped, eyes drifting away as she considered that. Her ears drooped ever so slightly. The slip in her expression lasted for only a moment before her eyes returned to me, though her glare wasn’t quite as hard as it was before. “Assuming you’re telling the truth.”

I sighed. “Yes. Assuming I’m telling the truth.”

She stared, silently judging me for several long seconds before speaking again. “Okay then, bug. You act like you know what they’re up to. If you were in charge of these changelings, how would \textit{you} run things?”

I took a step forward before sitting, hoping it would engender a more conversational tone. “That depends entirely on their small-scale goals,” I said. “Overall, they intend to exercise control over the region and eliminate any resistance Trotsen and other major settlements might offer, but there are a few ways of doing that.

\leavevmode\llap{“}The first is by taking over. They replace a few key members with their Infiltrators, influencing the leadership of a settlement to serve their purposes. That could be either isolating settlements so that the rest of the hive can strike against disorganized opposition, or exerting enough control over the leadership of a settlement to assume indirect control over the populace. Given that the only known Infiltrator had replaced the captain of your guard, a position of some military importance and presumably authority, it seems likely this was their original plan.”

I gestured to her. “Which would also mean that you, or a pony near you, would be a prime target for replacement. Other high-ranking ponies would almost certainly be targeted as well.”

\leavevmode\llap{“}Of course we would,” Sandstorm said. She remained standing. “You’re not telling me anything I don’t already know.”

\leavevmode\llap{“}The second option would be to promote chaos. Ponies are already getting paranoid and lashing out at each other. A combination of high-profile replacements to weaken faith in a strong leadership combined with seemingly indiscriminate replacements among the populace to spread distrust would quickly lead to a loss of social order. Infiltrations are short-term, with agents assuming an identity only long enough to stir up further paranoia before moving on and leaving the ponies to deal with the consequences. The final goal would be either complete societal breakdown, leading to the dissolution of the settlement, or delaying and weakening the settlement long enough to secure other goals, followed by cleaning up with either their own forces or with other factions they’ve taken control of.

\leavevmode\llap{“}Given the state of the population and the uncovering of one of their Infiltrators, I expect they may be transitioning to this method, although the lack of activity indicates they haven’t fully done so yet. My intervention, and particularly the knowledge of how to disrupt changeling disguises, may accelerate their transition to this plan.”

\leavevmode\llap{“}...You’ve put a lot of thought into this,” Sandstorm said, eying me critically.

\leavevmode\llap{“}I am well-trained,” I said. “The only way to conduct a successful counterespionage operation is to understand the methods and goals of a hostile agent.”

I was a little surprised when the suspicious look faded again. “Uh-huh.”

I continued. “The final option comes if the previous options fail to get the desired results: direct action. First, actions would be taken to isolate the settlement in question, whether through cutting off lines of communication or by advancing activities in other settlements to the point that they no longer presented a threat. I’m not entirely clear on the geopolitical situation here, but it seems that the only real contact you have with other settlements would be by your motorwagon convoy, so that would be a priority target and a likely starting point.”

Sandstorm’s ears twitched and stood alert, her gaze drifting away to stare into space.

I tilted my head slightly. “Is there something to be concerned about?”

\leavevmode\llap{“}No,” she immediately replied, her attention returning to me, and she finally sat. “Keep talking.”

\leavevmode\llap{“}After the threat of outside forces has been removed, focus turns to local defenses. Infiltrators target command, control, and communications inside the settlement to sow chaos and disrupt the ability to coordinate actions. Special operations teams target isolated units, likely disguised as friendly forces to achieve total surprise and taking measures to prevent communication with other defenders. Attacks are carried out quickly and aggressively to cause the most damage before any alarm can be sounded. The moment that momentum starts to fade or there is danger the alarm may sound, the main attack commences. In this case, several hundred soldiers attack, with power armor and heavy weapons. They might come in over a poorly defended section of canyon wall, or the earlier assault might have secured one of the entrances into town, allowing them to bring in more heavy equipment. Either way, they have a powerful military force and multiple ways of bypassing defenses.”

Sandstorm was frowning. Though she looked deep in thought, she quietly mused, “You seem to have some awfully thorough plans for taking out a town.”

\leavevmode\llap{“}Planning like this dates back to the war,” I said. “They were developed at a time when there were many hives, with thousands of changelings in each, all waging a silent war of espionage in pony territory. I can’t say for sure how much of that knowledge this other hive has retained, but I would much rather plan for the worst than not plan enough.”

She gave a dry snort, perhaps amused, perhaps not. After a moment, she asked, “You mentioned communications several times. Why?”

\leavevmode\llap{“}Information is an Infiltrator’s most important asset,” I replied, then inclined my head towards Dusty. “From what I’ve seen out in the Wasteland, it’s one of the most important things for a soldier, too.”

\leavevmode\llap{“}Absolutely,” Dusty said with a nod.

\leavevmode\llap{“}Serenity needs to disrupt communications and control the flow of information so that they can keep their secrecy. It’s harder to defend against an enemy you don’t know is there, and it’s impossible to strike back if you can’t find them. On top of that, if they can keep settlements isolated from each other, they can hit each with overwhelming force and minimum risk. They’ll pick ponies apart one settlement at a time.”

\leavevmode\llap{“}Uh-huh,” Sandstorm said. “And you think they’d do that by attacking our convoy?”

\leavevmode\llap{“}It’s the most likely target. A small force with no reinforcements or communication, and one vital to your settlement.” I eyed her curiously. “Why?”

\leavevmode\llap{“}Doesn’t matter,” she said, expression hardening again. “You know, I’m hearing a lot of talk about how fucked we are, but nothing about how we fuck them instead.”

Sickle snickered.

\leavevmode\llap{“}The Serenity hive relies on being able to act without threat of retaliation,” I said. “They can take their time, strike when opportunity presents itself, and always fight on their own terms. They can isolate us and fight us one-by-one until there isn’t anything left.” I raised a hoof, gesturing to the desk and the datastore sitting atop it. “But we know where they live. We can’t win on the defensive, so we go on the offensive. We get as many people together as we can—ponies, griffins, zebras, changelings, \textit{everyone}—and hit back while we still have a chance.”

\leavevmode\llap{“}Hmm.” Sandstorm stood and walked over to the desk. She hopped up to sit on the edge before picking up the datastore. “Just like that, huh?”

\leavevmode\llap{“}Hardly,” I replied, remaining seated where I was. “Before we can even start to deal with Serenity, we need a certain degree of security. I have three matrix disruption grenades that I have modified to disrupt changeling magic, which we can use to reveal any hostile Infiltrators. If we can clear a number of higher-up ponies and established a strict buddy system to minimize the risk of later abduction and replacement, we can make it much harder for Serenity to act against us. We won’t be able to screen the whole populace until Echo finishes her spellcrafting, but it gives us more ponies we can trust, and if we’re very lucky, might even net us one of their agents.”

\leavevmode\llap{“}Or it’s a bomb and you blow up some of my most trusted riders,” Sandstorm mused.

I shrugged. “Feel free to examine them. You could even test one on me, if you feel the need, though we don’t have many of them.”

She didn’t answer, instead giving a vague grunt, and slotted the datastore into her PipBuck.

While she started looking over the data, I continued. “The main problem is, we can’t just attack head-on. We need allies, preferably a lot of them. Serenity is too strong for you to fight alone.”

\leavevmode\llap{“}We’re tougher than you think,” Sandstorm said, her eyes remaining on the screen.

\leavevmode\llap{“}You’ve certainly got your strengths,” I admitted. “The problem is, Serenity has every one of those and more. They’ve got motorwagons, too, but they don’t even need them.”

I spread my wings, flicking them through a couple beats before holding them out for show. “Every one of their soldiers can fly. You can’t catch them or outmaneuver them. Then there’s the power armor, and the magical energy weapons, and now they’ve even got a Raptor.”

I folded my wings again. “And if that isn’t enough, they’ve got numbers on their side. The hive population was at least a thousand, and maybe double that. A heavily militarized hive can support more than fifty percent of its population as active military, and most of the rest can be mobilized when necessary.”

\leavevmode\llap{“}More wartime knowledge?” Sandstorm asked with a hint of disdain.

\leavevmode\llap{“}Changeling history,” I said. “Specifically, the original Queen Chrysalis and her hive. I doubt Serenity’s queen is going to be any less militant than her namesake.”

She muttered, but finally finished her reading, lowering her PipBuck to look back to me. “So you think we need allies, huh?”

\leavevmode\llap{“}Yes,” I said, nodding. “We’re stronger together than we are apart.”

She snorted. “That’s pretty rich coming from an underhooved little sneak that preys on ponies.”

I held her gaze. “From a lifelong spy who recognizes the old ways won’t work, and that it’s time for things to change.”

She held the glare for a moment before cracking a thin smile. She hopped down from the desk, and I stood to meet her. “Okay, then,” she said, and extended a hoof. “I think we might be able to work together.”

I smiled and gave her hoof a shake.

Or at least, I tried to. The moment our hooves met, she hooked her leg around mine and pulled in close, shoving her face close to mine. There were a few shouts from my companions, but I was focused more on what she said. “I don’t trust you for a fucking second,” she said in a low growl. “The only reason I’m even listening to you is because this fancy legwarmer says you’re not hostile, but I know damn well there’s a big difference between ‘not hostile’ and ‘friendly’. If you try to fuck us over, I will kill you, painfully, and your fancy Luna-knockoff won’t save you. Got it?”

\leavevmode\llap{“}I’ve got it,” I said, calmly. “And I’m not asking you to trust me. All I’m asking is that you listen and consider what I have to say.”

Her lips peeled back in a sneer. “Then we’ll get along just fine.” She ended by pushing me back, sending me staggering. “And give my ponies their weapons, already.”

I recovered my balance, flicked my wings smoothly against my back, and turned to give Echo a nod. Her magic flashed around the room, returning weapons to their holsters.

The guards both jerked in surprise, then looked to Sandstorm. “Uh…”

\leavevmode\llap{“}Relax,” she said, her tone sharp, and she turned to the stallion who still stood, awkwardly, behind the desk. “Axle. Gather the head riders. Don’t tell them why, and not a word about what’s happened here.”

He looked surprised, his eyes darting to me before looking back to Sandstorm. “Uh, are you sure—”

Sandstorm stepped in, voice clear and loud as she cut him off. “Did I fucking stutter?”

\leavevmode\llap{“}No,” Axle quickly replied, while Sickle snickered some more.

I took the moment to resume my Summer Breeze disguise. The instant the magical fire had passed, Sandstorm was glaring at me. “What the \textit{fuck} do you think you’re doing?”

I cocked my head to the side and raised an eyebrow, finally lifting a hoof to gesture to freshly ponified myself. “I would think it’s pretty obvious.”

\leavevmode\llap{“}Oh, that’s fucking hilarious,” she dryly replied. “Drop the pony act. I’m not going to have any bugs parading around pretending to be ponies, whether they say they’re helping or not.”

\leavevmode\llap{“}I doubt having a changeling standing beside you is going to help your credibility at this time,” I said, and given by the way her snarl vanished, she recognized the merit of the argument. “Besides that, we have a very narrow window of opportunity. I don’t expect my nature will remain secret for long, but until then, the only individuals who know it are in this room. Serenity’s agents will know that I’m a changeling, but at this moment, they don’t know that I’m working \textit{openly} with you. That means they won’t know how much danger they’re in. We should take advantage of that to do as much damage as we can to any high-level infiltration efforts.”

\leavevmode\llap{“}Hmm… yeah, okay.” She pointed a hoof at me. “But you’re staying where I can see you, then. No sneaking off to pull any shit when I’m not looking.”

An annoying restriction, but one I could hardly object to. “As you wish,” I said. “One more thing: it’s possible that one of your ponies in this room has been replaced and is remaining silent. Individuals close to the leadership would be prime targets for replacement, and if anyone here has been replaced, they could get the warning out and make the whole gambit pointless. We should make sure you’re all ponies before anyone leaves.”

Sandstorm mused on that for a moment, until a hint of a smile appeared. “You heard the bug,” she said as she turned to Axle, then pointed. “Middle of the room. And you two dunces. Great job keeping guard, by the way.”

Axle looked at her as if she’d asked him to gnaw his own hoof off. “Wait, what? You’re seriously taking orders from a \textit{changeling?}”

He’d barely gotten the final word out when she struck him in the side of the head, sending him sprawling.

\leavevmode\llap{“}I ain’t taking orders from \textit{anyone},” she snapped. “But I want to see this thing work.”

\leavevmode\llap{“}But Sandy,” one of the guards said, stepping up while giving me a wary look. “What if it’s a bomb?”

She turned to me. “Give me one.”

I obliged, and she snatched it from me. Gripping the end in her teeth, she twisted and removed the outer sleeve, exposing the internals. She seemed to know what she was doing as she examined it.

\leavevmode\llap{“}It’s not a bomb,” she said. “It’d take more than tweaking two of the crystal leads to rework the spell matrix into something deadly.” I was impressed; either she knew a good deal about arcane technology, or she was great at bluffing. “Now quit being such babies and group up.”

She reassembled the device as the three other ponies reluctantly gathered. The sleeve slid back into place and locked, protecting the delicate wiring. Then she turned to me. “Well? What are you waiting for? Get your little bug-butt in there.”

I opened my mouth to object, but caught myself; it was a reasonable request, and one that might make them feel more at-ease. I’d even offered to let them test it on me, so I could hardly back out now. “Okay,” I said, shucking off my saddlebags and removing my PipBuck.
With my gear left safely in the care of my companions, I approached the trio of nervous ponies, stripping away my disguise and finally showing my armor.

\leavevmode\llap{“}Hey!” Sandstorm snapped. “Change back. You said this thing undoes your disguise, and I want to see it work. And where the hell did that armor come from?”

\leavevmode\llap{“}No,” I said, my tone a bit more grumpy than I had intended. “I’ve been hit with one of those during training, and it’s an experience I don’t intend to repeat. Besides, if I were lying to you, I’d just drop my disguise when it goes off and pretend it worked. There’s no point to it. As for the armor, it was always there, just shapeshifted away.”

\leavevmode\llap{“}Wait,” one of the guards said, tensing. “How bad is this going to be? You didn’t say anything—”

\leavevmode\llap{“}You’ll probably barely notice,” I said, then inclined my head to the other guard, the only unicorn in the group. “He’s the only one who’ll really feel it, like someone tapped on his horn. The discharge resonates with changeling magic, and it’s too different from unicorn magic. But me? Imagine the most painful sound you’ve ever heard, then imagine it getting jammed right into your brain. The more magic I’ve got flowing around, the worse the resonance. Hell, one of my fellow trainees passed out.”

Sandstorm gave an exaggerated sigh. “Luna’s teats, you love to talk.”

\leavevmode\llap{“}She really does,” Sickle said, grinning and clearly enjoying the situation far more than it warranted.

\leavevmode\llap{“}Whatever,” Sandstorm said, gesturing her hoof at me. “Just get in there.”

I obliged, ignoring the anxious and angry looks of the ponies I stood beside. When I turned back, I addressed Sandstorm. “You should be in here, too.”

\leavevmode\llap{“}Not happening,” she said, already stepping back. I considered insisting—we could easily force the matter—but decided against it. I’d just have to keep an eye on her until we could be sure.

She led everypony else away from me and the other unlucky ponies, giving us plenty of room and keeping their fancy arcane technology safely away. Finally, Sandstorm pulled the pin and tossed the matrix disruption grenade our way.

I didn’t see the impact. The moment it left her hoof, I closed my eyes, bracing for what was about to come.

The discharge hit me, sending an electric twinge through my horn and a deep shudder through my body. It was as if the small sound of its discharge had resonated through my nerves. I huffed out a sharp breath as it passed, blinking as I reoriented myself. The world felt lopsided, and my horn had gone slightly numb.

\leavevmode\llap{“}See, that wasn’t so bad,” Sandstorm said as she walked up, giving me a critical look before looking to Axle. “Now go get the head riders.”

\leavevmode\llap{“}Yeah, I’m on it,” he said before walking off, grumbling quietly under his breath.

Sandstorm had turned to the guards. “As for you two, keep your mouths shut about this. Not a word.”

The same guard spoke again. “But Sandy—”

\leavevmode\llap{“}Not a fucking word!” she said, stepping in. “I hear anypony talking about our changeling ‘friend’ here, and you two will be riding into battle strapped to the hood of my wagon, \textit{got it?}”

The guard winced. “Yeah.”

\leavevmode\llap{“}We’ve got it,” the other replied.

\leavevmode\llap{“}Good.” Sandstorm half turned, then stopped, glaring at me. “And what the fuck are you still doing all bug-like.”

\leavevmode\llap{“}Oh for fuck’s sake,” Starlight grumbled. “First you bitch about her shapeshifting, now you’re bitching about her \textit{not} shapeshifting.”

Sandstorm shot her a sharp look. “Nopony asked you,” she said before looking back to me. “But if we’re going to keep this between us, we can’t have you going around like that.”

\leavevmode\llap{“}Give me a minute,” I said, heaving a deep, steadying breath. “It’s still a bit of a shock, and I—”

\leavevmode\llap{“}Just make it quick,” Sandstorm said. “I want to fetch some gear before everypony shows up.”

I took a few more breaths before carefully feeling with my magic. It’s not that it was hard to cast something, but more that the burst of magical energy had overwhelmed my senses. It’s like being blinded by a spotlight; your vision is going to be spotty for a bit and all the colors are off. In this case, it meant diminished magical precision. I had to focus long and hard before taking my Summer Breeze disguise, and hoped that I had gotten the transformation accurate enough. Nopony said anything, so I assumed it was good enough for casual work.

The hint of a headache made me grumpily wonder if I was doing any lasting damage to myself with the past day or so of activities, even though I logically knew the chances of that were minuscule.

Once I had gathered my equipment, Sandstorm led us out, her expression hard. A few of the ponies we passed along the way took notice of this, but none commented. That, or they were wondering about the strange procession of ponies trailing behind her.

We made our way out from the main factory building, past a collection of motorwagons, and to a large side building. Along the way Echo stepped up beside me.

\leavevmode\llap{“}I do not like this plan,” she said. “You finally agree to cast off deception, and the very first plan you enter into is one that depends on secrecy and lies.”

Sandstorm’s ears twitched our way.

\leavevmode\llap{“}We’re potentially dealing with hostile changelings,” I quietly replied. “Unfortunately, that means a certain degree of deception is necessary at this stage.”

\leavevmode\llap{“}I do not question its effectiveness,” she said, “but recent lessons and events have made it clear to me that ‘effective’ is not the same thing as ‘right’.”

I sighed softly. “It’s like I said: Honesty is not just about telling the truth.”

\leavevmode\llap{“}Hmmph.” She did not elaborate, and instead slipped back to the rear of our procession.

When we reached the side building, Sandstorm led us in.

\leavevmode\llap{“}Raindrops!” she called out as we entered what looked to be a living room, with well-worn wartime furniture. “Get your shit! We’re going out!”

There was a clatter in the next room, followed by a stallion’s voice. “What’s up now?”

\leavevmode\llap{“}Maybe something, maybe not,” Sandstorm answered vaguely as she made her way to one of the doors leading further into the building. I followed her into a workshop, where a blue stallion stood by a workbench, setting the breastplate of an armor suit atop it. He was about Sandstorm’s age, with a similarly weathered but fit appearance, though he lacked any armor; presumably, the piece he had just set on the workbench was his. He looked at me with curiosity as I entered, then at Sickle and Dusty as they followed behind me.

His eyes widened slightly, ears flicking back. His attention snapped back to me, and the little pip on my E.F.S. turned red.

I stepped back, expression hardening as I dropped into a combat stance. “Echo, bubble him.”

Contingency planning paid off. Echo immediately did what I asked, conjuring a shield around the stallion even before giving me a questioning look.

\leavevmode\llap{“}What the \textit{fuck!}” Sandstorm shouted, snapping around to face us. Her head turned, once again starting to reach for her gun but holding short, well aware of how futile the gesture would be. Instead, she turned to face me. “Let him go!”

\leavevmode\llap{“}He knows what I am,” I said, keeping my eyes on him.

\leavevmode\llap{“}She’s a changeling!” he shouted, giving the shield a desperate kick. It didn’t even flicker.

Sandstorm cast a quick glance his way, and I took the opportunity to throw out a quick explanation.

\leavevmode\llap{“}He didn’t recognize me when I came in the room. I’ve never used this form before. It wasn’t until he saw my companions that he realized who I was and turned hostile.” I held up my PipBuck-clad foreleg to clarify that last part. I didn’t mention that she was now showing as hostile, too. “The only ones who would possibly know that would be Serenity.” I didn’t mention the Enclave Loyalists, either. No need to confuse the situation any more than it already was.

\leavevmode\llap{“}They’ve got a bounty on them!” Raindrops said, pointing a hoof. “In Mareford. They killed a bunch of ponies there!”

I inwardly cursed. It was true, and would certainly explain his reaction. Still, I didn’t quite buy it.

Curiously, from the glance Sandstorm gave and the hint of unease creeping in past her anger, it seemed she didn’t quite buy it, either. Still, her expression hardened a moment later as she refocused on me. “Is that true?”

\leavevmode\llap{“}Partially true,” I replied, as diplomatically as possible. “We killed several ponies there, but that was because they ambushed us to cover up their collaboration with local raiders. It wasn’t the murder that Big Gun tried to sell it as.” My eyes narrowed as I focused on him. “Regardless, I have to wonder why he seems to be the only one in town to know, and more importantly, that wouldn’t have told him I was a changeling.”

\leavevmode\llap{“}It’s the PipBuck!” he shouted. “It’s the same kind you got from the changeling impersonating Iron Hoof!”

I glanced at Sandstorm’s PipBuck. Was that where she had gotten it? Her own expression was torn, predominantly angry, but I could see the unease growing.

\leavevmode\llap{“}My companions have the same PipBucks,” I pointed out, keeping my voice calm and reasonable. “So why am I the only changeling?”

\leavevmode\llap{“}They could be changelings too,” he quickly replied, “but I don’t recognize her.”

Sandstorm still hadn’t spoken. I turned to her again.

\leavevmode\llap{“}You know this looks suspicious. That’s how Infiltrators operate. Replacing someone near the leadership lets them influence that leadership without suffering the same scrutiny that the actual leaders do. We should make sure he isn’t a changeling.”

Sandstorm’s expression hardened again. “Is this what you’re here for? Fucking with our heads, making us suspicious of each other? Is that your fucking plan?”

I replied sharply. “We can find out for sure if he’s a changeling or not, so what would be the point? One quick test, and this whole thing gets cleared up.”

\leavevmode\llap{“}Test?” Raindrops asked, voice wavering slightly.

Sandstorm visibly winced at the hint of fear in his voice. “Fuck you, bug,” she growled. “You’re not using that fucking thing on him, period.”

\leavevmode\llap{“}Then at least question him!” I said, quickly running out of options; I didn’t want to have to force the situation, though we seemed to be quickly approaching that point. “Was there anything suspicious he said lately? Any time he acted just slightly strange? Some detail he couldn’t remember? Any time he prompted you to fill in details that he should already know?”

The anger cracked again, and I hammered the point. “If you don’t want use one of the devices on him, then ask him a question. Something only he would know. Something obscure enough that nobody would think to ask him in an interrogation.”

\leavevmode\llap{“}Don’t listen to the changeling!” Raindrops shouted. “She’s trying to trick you! Sandy!”

Her eyes wandered, thinking for a moment before fixing on me. “Okay, bug,” she growled before turning her head slightly towards Raindrops, eyes remaining on me. “What was your first ride?”

\leavevmode\llap{“}Sandy, don’t do this,” he said, placing his forehooves against the shield. “She’s a fucking changeling, she’s trying to—”

\leavevmode\llap{“}Just answer the question,” Sandstorm said, voice low, glaring at me. “We’ll get this all sorted out.”

Raindrops hesitated. “I… I don’t know, it was so long ago, and I’ve been with you for so long…”

I watched as Sandstorm’s expression crumbled. The impostor had taken a hopeless shot in the dark, and missed.

\leavevmode\llap{“}Sandy…”

She turned, her expression slack, ears sagging, eyes fixing on him in slowly dawning horror. A tremble, subtle at first, steadily grew and spread through her body.

He was slowly shaking his head, eyes starting to tear up. “Sandy, they’re trying to trick you. It’s what they do. You know it’s me!”

Sandstorm turned her head, drawing her rifle before facing him again. She was trembling, every muscle taut with rage.

Tears started to trickle down his cheeks. “Sandy, please. Don’t listen to her.”

Sandstorm’s voice was quiet and cold, betraying only a hint of a waver. “Drop the shield.”

I nearly winced at her tone. “If he’s been replaced, we should question—”

Her head snapped around, and I flinched back as everything turned purple; Echo had raised another shield, separating us from Sandstorm, but it had been an unnecessary precaution. The gun was still pointed down, even as she snarled at us. “Drop. The fucking. \textit{Shield!}”

So many concerns danced through my head. The state of our fragile alliance, the future of the region, and the fate of this captured spy. With Echo’s help, we held all the power in the room, but despite that, I felt almost helpless.

Being an Infiltrator often means having to face situations you can’t control, where the only choices available are not good and bad, but bad and worse.

So I turned to Echo and gave a small nod, hoping for the best and dreading what I might have just done.

Echo stared back silently, but eventually the shield dropped. Raindrops was exposed, but hardly any less trapped. There in the corner of the workshop, he had a wall of ponies between him and any exit.

\leavevmode\llap{“}Sandy, don’t—”

She wheeled around, slamming a hoof into the side of his head, and he toppled to the ground. She was immediately on top of him, driving a hoof into his gut, then pinning him down by his neck. The muzzle of her gun hovered inches from his face. “Shut up! Shut the fuck up! You don’t get to sound like him! You don’t get to wear his face!”

Raindrops was gasping past the pain and the hoof constricting his breathing. When she finished shouting, he calmed. His eyes darted around the room, looking for an escape but not finding it. Then he smiled, though it was awkward and forced, showing too much teeth. “Why not? He’s not using it any more.”

I quickly stepped forward, but Echo’s second shield was still up between us. “Sand—”

The rifle blared loud in the small space, hammering away until the magazine ran dry. When it was done, the mauled corpse of a changeling lay in Raindrop’s place, a puddle of blood steadily spreading beneath her. Sandstorm stood above the broken form, panting and seething with rage as tears ran down her cheeks.

I swallowed, and tried to offer some comfort. “He might still be alive. They take—”

\leavevmode\llap{“}Shut the fuck up!” she snarled, her trembling growing as she glared at me. “If you say one more goddesses-damned word, I will beat you to death with my bare hooves!”

It was an empty threat, but I shut my mouth, and after a moment, gave a small nod in reply.

The front door of the building banged open, and hooves raced our way. Seconds later, several armed ponies burst into the workshop. The lead pony, clad in heavy armor and carrying a shotgun, first pointed his weapon at us, still safely behind Echo's shield, before noticing the dead changeling with Sandstorm still standing over it. “What the fuck happened—”

\leavevmode\llap{“}You!” Sandstorm said, spinning towards him, and he visibly flinched at the trembling fury in her voice. “Sound the horn. Gather \textit{everypony}.” When he didn’t immediately reply, she stepped towards him, roaring, “Now!”

He turned and quickly ran past the other gathering ponies, many of whom were gawking at the dead changeling. Sandstorm ignored them, taking a moment to wipe a hoof across her cheek before going over to a locker at the foot of the workbench. She pulled out heavy saddlebags and a large bundle, slinging them across her back before grabbing a trio of spears. Finally, she turned back to the gathered ponies.

\leavevmode\llap{“}You!” she growled, singling out one hapless pony. “Grab that… \textit{thing} and follow me.”

She took a single step before stopping, turning her head to glare at me. I wanted to say something, \textit{anything} to console her and maybe smooth things over, but I knew it was pointless. Instead, I lowered my gaze, looking to the floor.

She gave a quiet snort. “You too,” she growled. “Come on.”

One of the other ponies looked between us. “Are they—”

\leavevmode\llap{“}They’re with me,” Sandstorm snapped. “Get the fuck out of the way.”

Echo finally lowered the shield, and we awkwardly followed behind Sandstorm. Every step she took was an expression of anger, as if she were beating the earth into submission. Her head was low, eyes narrowed, and every movement was sharp, tense. A few ponies watched with concerned, anxious faces. Everypony stayed out of her way.

As we neared the main building again, ‘the horn’ sounded. It started as a low moan, but slowly grew in pitch and volume until the eerie and unmistakable wail of an air-raid siren echoed through the canyons. The sound rose and fell as we entered the factory, returning to the office.

Once there, we waited in silence. Sandstorm sat in the chair behind the desk, silent and furious, staring off into space. Nobody wanted to be the first to speak.

I kept looking at the mangled changeling. She was a grotesque sight. The head only vaguely resembled what a head should look like, and the multiple bullet wounds across its body left the carapace shattered, flexing in ways no changeling should flex. I looked away, but in the awkward silence, my eyes kept drifting back.

The only interruption came when a guard came in. “Sandstorm? The head riders are here. Should I—”

\leavevmode\llap{“}Tell them to wait out front with everypony else,” she coldly replied, and the guard quickly stepped out and shut the door.

Minutes passed after the siren fell silent, until the sound of ponies grew outside. Sandstorm remained silent, still save for the steady tremble of rage. Another minute passed before she stood, walking over to the window. She looked outside, then turned and walked up to me.

\leavevmode\llap{“}Give me the grenades.”

I nodded and retrieved the last two matrix disruption grenades. “We only have—”

\leavevmode\llap{“}Shut up,” she growled, snatching them from me, then looked to the pony who had brought the deceased changeling. “Bring that thing.”

With that, she walked to the door at the back end of the room, and stepped out onto the balcony. We followed into the brisk morning air.

A sizable crowd had gathered within the front grounds of the factory complex. At least three hundred ponies stood below, with more making their way up the path. The ponies closest to the balcony were all decked out in armor and carrying weapons, while those further away were more lightly equipped, with few weapons. They were talking amongst themselves, likely questioning why they were there. I even spotted a hoofful of griffins, perhaps a dozen, amid the sea of ponies. The hum of conversation rapidly dwindled to a few murmurs as Sandstorm emerged.

She glared out over the crowd, her gaze harsh. After a moment, she took up the two matrix disruption grenades. They were below the rim of the balcony as she armed them, so the first the crowd saw of them was when she tossed them over the edge.

I heard questioning murmurs, but only one voice of alarm, some pony who realized what she had just thrown out. The grenades dropped into the crowd. One pinged off the back of an armored pony near the front before falling under hoof. Another pony, a bit further back, reflexively caught the one aimed at him. He panicked the moment he realized what he held, fumbling the device. A few more shouts sounded, but the few attempts to run were thwarted by the weight of the crowd and the surrounding walls.

Flashes of panic made way for confusion when the devices discharged. Some unicorns winced, but within moments the crowd was murmuring again in confusion. Sandstorm stood at the railing, looking over the crowd. Not a single changeling was visible.

The volume of murmuring grew rapidly as Sandstorm stepped back from the railing, then surged as she hefted the changeling corpse up over the railing. The body tumbled down just before the crowd, hitting the ground with a muffled crunch.

Sandstorm was seething again. The trembling grew as she reared up, planting bloodied hooves on the railing, and shouted out to the crowd. “We know where they live!”

The murmurs surged, then rapidly quieted.

Sandstorm bared her teeth in a savage snarl. “These fucking bugs thought they could break us. They tried to turn us against each other. They pitted family against family. They’ve murdered loved ones and ruined lives!” Her voice shuddered with rage as she hammered a hoof against the railing. The emotion was contagious, as angry murmurs sounded in the crowd below.

\leavevmode\llap{“}They thought they could fuck with us, but now the tables have turned!” She was practically roaring now. “Now we know where they live! Now we can take the fight to them!” The crowd’s volume grew. “Now we’re going to show these bugs that nobody fucks with Trotsen!”

The armed ponies in the front cheered and hefted weapons, full of eager, savage grins. The mood was rapidly spreading through the crowd.

\leavevmode\llap{“}Get your weapons!” Sandstorm shouted. “I want every single motorwagon readied with at least a week’s supplies! I want every fucking pony who can carry a weapon! I don’t care if you’re riding cargo in the hauler or are hanging off the side of a wagon. If there’s room for you, then today you are a rider!” She hammered her hoof against the railing again. The cheering had spread, faces further in the crowd lighting up.

\leavevmode\llap{“}You’ve got one hour to gear up and gather at the main gate. Anypony who isn’t there will answer to me!” She looked over the crowd once more. “Now mount up!”

Another cheer tore through the crowd as ponies started splitting off, running in all directions. I could see the news traveling along the path below, spreading amongst those who had yet to arrive.

\leavevmode\llap{“}Axle!”

The stallion stepped out from among the riders below at Sandstorm’s call, shouting back, “Here!”

Sandstorm looked down at him, lips curling back into a savage snarl beneath tear-stained cheeks. “Bring out the Beast.”

{\br}%
Ponies ran about in a flurry of activity. Supplies were thrown haphazardly into motorwagons in the rush, while arms and armor were checked over and donned. Every now and then, another motorwagon would hum to life and rumble across the dusty courtyard. Each was laden with a small gang of ponies crammed in every available space, and all grinning with savage, animalistic excitement, all in anticipation of the fight to come.

Sickle chuckled darkly beside me. “I think I like this town.”

Sandstorm stood nearby. She was no longer shaking with barely controlled anger, as if she might murder the next pony to approach her. Instead, she stood tall, her harsh gaze watching the steady progress. It did not make her look any less dangerous, but it did make her look far more focused.

We stood beside one of the intact side buildings of the factory complex, waiting.

Half the motorwagons had already departed. The massive cargo motorwagon I had first seen at Mareford was making its way out the gate, loaded with dozens of armed ponies and crates full of supplies. I had to wonder if they were leaving anything in town for those who weren’t coming. For that matter, I had to wonder if there \textit{were} many who weren’t coming, not to mention the concern of what Serenity’s Infiltrators might do while we were gone. I had to hope that they saw this force as the more immediate threat.

The deep thrum of a motorwagon’s motor sounded from inside the building beside us, unremarkable at first, but in moments it had grown in volume beyond even that of the cargo wagon. Ponies were opening the great doors at the front of the building. A small, savage smile crossed Sandstorm’s muzzle as she started walking that way, and we followed.

A metallic screech and rattle grew from inside, slow but rapidly building. It combined with the growing roar of the motor into a cacophony of sound, tremendous and terrifying. I could feel the sound with my hooves.

The giant muzzle of a cannon thrust out from the open doors, followed by the massive vehicle it was mounted to. It was all blocky angles, made even more menacing with the massive plow-like ram mounted to the front and the array of spikes along the top. Axle was riding atop the huge machine, a heavy machine gun before him. The massive tracks tore at the dirt as the vehicle lurched, grinding to a halt.

Sandstorm grinned, dark and savage as she approached her Beast.

We had a tank.