A long, thin line of dust cut through the Wasteland.

At least two dozen motorwagons tore down the bare dirt trail. It was the same trail the Trotsen caravans had used for years, but this time, it bore a different cargo. Two hundred ponies, maybe more, were tucked into every available space. They carried weapons of all sorts, from spears to machine guns, with expressions both angry and eager.

At their head rumbled Sandstorm’s Beast, a relic of an earlier age. A mighty war machine, eager to return to the role it had been built for centuries ago. It roared like its namesake, a warcry echoed by those who followed.

And I was following right behind it, surrounded by ponies looking for a fight.

I had turned these ponies loose on the Wasteland. Now, I could only hope I could nudge them in the right direction.

{\br}%
The great convoy had halted for the evening, parked in a chaotic cluster of vehicles. Even with our speed limited to that of the slowest of the vehicles, we had already covered half the distance to Mareford, and we could expect to arrive the next afternoon. While several eager mechanics had already detached our second vehicle to work on fixing it up—without even bothering to ask us—I made my way to where Sandstorm consulted with her riders. Echo and Sickle followed on my flanks, like a pair of large and terrifying bodyguards.

Sandstorm was standing beside a folding table, along with a small group of ponies. Axle was at her side, speaking while she looked at the map spread across the table. “Gangrene and Howler caught up with us, but there’s still no word of Shaft, Buckeye, or Clanger’s patrol. I don’t know if they’ll have time to catch up before we get to this ‘Serenity’ place.”

I was almost to them when a pony stepped in front of me. “Turn around,” she said, magic glowing around the grip of her shotgun. “Riders only.”

Sandstorm looked up. She was dusty from the day of travel, and her eyes were still reddened, but her expression looked as hard and determined as ever. That expression darkened the moment she saw me. “Let her through.”

The guard frowned, but stepped aside, eying me suspiciously.

I continued forward, giving an appreciative nod to Sandstorm. “Thank you.”

She ignored me, turning back to Axle. “What were you saying?”

\leavevmode\llap{“}The patrols,” he said, casting repeated wary glances my way. “Gangrene and—”

\leavevmode\llap{“}Right,” Sandstorm said, nodding. “Nothing to worry about. They’ll have plenty of time to catch up. They’ll be faster, and they can go direct while we swing by Mareford.”

\leavevmode\llap{“}Wait,” Axle said, his ears shooting up, and casting me another quick glance. “We’re really going to Mareford?”

Sandstorm’s eyes narrowed ever so slightly, a look that seemed particularly dangerous to me. “I want more guns and ammo,” she said. “Everything we can get, and those Mareford fucks are going to give us a damn good deal on them if they know what’s good for them. Hell, won’t hurt to spread word about these damn bugs. Maybe if they see their own head on the chopping block, they might get off their fat asses and do something for a change.”

She was going to Mareford, spreading information, and giving them the opportunity to join in, all while keeping a position of power by not \textit{explicitly} going there for help. I didn’t have the time to fully consider the stance before she turned to me and quite bluntly asked, “What the fuck do you want?”

I blinked, but quickly recovered. “I was hoping to find out what the plan was.”

One of the other riders, a mare with spiked armor, cut in. “Who the hell is this? Sandy, what’s going on?”

Sandstorm scowled as she turned on the rider. “What’s going on is this dipshit has a pair of motorwagons and some hired guns. She’s willing to go along with the whole ‘stomp the bugs’ plan, so she gets to play at being a rider.”

The mare glanced warily between us. “Just like that? She could be a changeling!”

\leavevmode\llap{“}Of course she could be a fucking changeling,” Sandstorm said, an edge creeping into her voice. “Hell, so could you, or any of the rest. That’s the problem, ain’t it?” She lifted a hoof, gesturing to me. “Right now, she’s helping us, so we’ll \textit{let} her help us. If she decides she’s \textit{not} going to help us any more, well, we’ll just have to make a \textit{new} arrangement…”

She trailed off with a warning glare at me.

The other mare grumbled, but begrudgingly backed down, casting her own glare my way. “Fine.”

A nearby stallion with a spiky red mane grumbled. “I don’t like this.”

Sandstorm’s jaw clenched. She turned to him with a dangerous purpose to her movements. “You going to bitch to me about not liking the situation?” She took a very deliberate step towards him. “You really want to go down that fucking road with me right now?”

He wisely backed down. “No, ma’am. Sorry.”

\leavevmode\llap{“}Good,” she growled, and turned back to the table. “Then let’s stop whining about all this stupid shit and start focusing on the \textit{real} problem.” Her hoof came up, jabbing at the map. It landed right on a penciled-in mark: Serenity.

One of the other riders, a silver-maned mare, quickly stepped forward to help shift the subject back. “We’re slower than the usual convoy, but we’ll still make Mareford by mid-day. Best time from there to this ‘Serenity’ place would probably be around six hours, depending on what the old roads are like in that area. That’d put us there around nightfall, maybe a bit after, but that doesn’t give us any time at Mareford.”

\leavevmode\llap{“}And I don’t like the idea of showing up at night,” Sandstorm said. “So mid-day, day after tomorrow. Longer than I’d like, but it’ll have to do.”

\leavevmode\llap{“}We’d be there tomorrow evening if we just go straight there,” Axle pointed out, but Sandstorm gave a dismissive wave of her hoof.

\leavevmode\llap{“}We could split up,” another rider suggested. “Take the fastest wagons and best riders out to Mareford, while the Beast and other wagons go direct. We’ll have to gun it, but it’ll give us some time to work out a deal and still meet with you well before dark.”

The first rider grunted. “I dunno. I mean, hell, neither group would be an easy target, but you know how bad the raiders have gotten lately. Something’s up with them.”

My ears perked. “You’ve been having raider problems?”

The looks from most of the ponies was predictably icy at my intrusion. Sandstorm came to my defense, whether intentional or not. “Motorwagons,” she said. “Sure, raiders get their hooves on a working motorwagon every now and then. It happens. Either they dig one up and get it running, or take out an inexperienced crew and steal theirs. Usually, they don’t last long before we take ‘em out, but lately they’ve been flush with ‘em. We’re up to, what, eight new wagons this last month?”

She looked around until Axle gave a nod, and gestured to me. “Nine, including the one she captured.”

\leavevmode\llap{“}Nine,” Sandstorm echoed. “I figure they must have turned up some old wagon yard or something. They ain’t done much with ‘em yet, ‘cept lose the one that tried hitting our convoy, but they’re being more of a pest than usual. If it weren’t for the fucking bugs stirring shit up, I’d have my riders out putting those raiders down and finding out where they got their rides. We can always use some more wagons.”

\leavevmode\llap{“}A sudden upswing in raider activity and equipment,” I noted, frowning. “It seems like that’s been happening a lot, lately. This might be Serenity’s doing.”

A couple of the cold looks had been replaced by questioning ones, so I explained myself. “They’ve used raiders before. Pass on equipment or information, and let the expendable raiders do their dirty work. And Serenity has motorwagons.” I inclined my head towards where my companions had set camp. “We swiped our first wagon from them, and they had several more.”

There were a few murmurs at the news—whether that of Serenity’s involvement with raiders or my mention of previous contact with them—but Sandstorm cut them short by speaking up. “Doesn’t matter, anyway,” she said with another wave of her hoof. “We’re not splitting up. I want a show of force when we roll up on Mareford. We’re going to let those sedentary morons know we mean business.”

I nodded, glad she’d made that call, even if her intent was a bit more aggressive than I would have liked.

\leavevmode\llap{“}So,” she said, looking over the gathered riders. “On to Mareford in the morning. We set camp there, get a good deal on all the guns and ammo we can carry, maybe convince a few of their so-called Militia to get off their asses and actually help ponies for a fucking change.”

One of the riders snorted. “Ain’t like we need \textit{their} help.”

I spoke up. “Against Serenity, I think we can use all the friends we—”

The spiky-haired stallion cut me off. “There ain’t no fucking ‘we’, bitch. You ain’t one of us. I don’t think you’re even—”

\leavevmode\llap{“}\textit{Hey!}” Sandstorm’s shout cut across the group, instantly silencing the stallion. She leveled a hoof at him. “She’s our guest, so watch your fucking mouth you disrespectful cunt.”

As he cringed back, she turned to look at me. “Well? Keep talking, bitch.”

There were a few snickers from the gathered riders, as well as a look of silent annoyance from the stallion. I wasn’t surprised that Sickle snickered as well.

I ignored that and continued. “What I was saying was that we could use all the friends we can get, and I think I have some friends that might help out.”

She frowned, pausing for a moment before speaking. “Don’t think we need any ‘friends’ here, but hell, I ain’t turning away anypony who wants to squash some bugs. They want to tag along, fine. Who are they?”

\leavevmode\llap{“}Enclave Loyalists,” I said. “About fifty or sixty soldiers, maybe more.”

In my defense, calling them “friends” was more of an exaggeration rather than an outright lie. Echo didn’t directly call me out on the claim, but I’d still like to get that down for the record.

Several of the ponies looked at me with perked ears and looks of surprise at my unusual claim, and I clarified. “They’re the ‘good guy’ side of the civil war going on up there. They’ve been trying to help ponies down here, and they’ve got good reason to dislike Serenity. We’ve met with them before. If they see hundreds of ponies gathering to fight Serenity, they’ll want to pitch in and make sure we win.”

Sandstorm’s expression had soured. “I trust the birdies about as much as I trust the bugs,” she said with distaste, before her expression mellowed. “Still, be nice to have some more fliers, since it looks like changelings can fly. Fuck it, why not?” She lifted a hoof, tapping the edge of the map. “Where are they?”

I quickly consulted my PipBuck, comparing locations for a moment before reaching out to tap at the map a short ways east of Rust. “They were camped here last we saw them, but they had been moving regularly. They probably won’t be there, but we should come across one of their patrols easily enough.”

Axle grunted. “That’s way out of the way! That’d add a whole day to our trip!”

\leavevmode\llap{“}At least ten hours,” another pony said, leaning over the map. “Maybe twelve. Terrain is a bit rough there.”

\leavevmode\llap{“}And that’s if we stumble across them right away,” Sandstorm noted, and shook her head. “Sorry, not happening. I’m not giving these bugs any more time to prepare.”

My ears flicked back. “But we could use their help, and it’s only a small delay.”

\leavevmode\llap{“}I said it ain’t happening,” she said, and gestured a hoof around. “This ride ain’t stopping. Be glad we’re even swinging by Mareford. You want to bring in these Enclave pricks, you can haul your tail over there and tell ‘em yourself. Put a hustle on it and you can catch up with us at Mareford.”

I frowned, looking at the map. It’d probably be doable, assuming the Loyalists hadn’t moved camp or we found them quickly enough, but there was little room for complications. “That might work,” I said, reluctant. “Though my wagon is a bit heavily loaded. We’d make better time if we could offload some of our cargo to one of your wagons.”

There were a few grumbles from the riders, including a few who spoke up. “We’re not your mules.”

\leavevmode\llap{“}Consider it collateral, then,” I said, “for our good behavior. If we don’t show up again, you get to keep it.”

\leavevmode\llap{“}I won’t turn down free shit,” Sandstorm said, “especially since most of it is weapons. The hauler won’t even notice the load, and it’s still faster than the tank. Deal.” She held out her hoof, and I shook it, as she added, “Feel free to not come back.”

\leavevmode\llap{“}I’ll meet you at Mareford,” I said evenly, gave a parting nod, and walked off.

As I left, I heard Axle speak up. “You’re just letting her go?”

Sandstorm’s groan brought a smile to my face. “Seriously, you bitches whine that she’s here, now you’re whining that she’s leaving. Buck up, already. We’ve got a fight to look forward to.”

The rest of the conversation faded into the background as the distance grew.

{\br}%
We set off early in the morning, before the sky had fully brightened.

It was easy to forget just how much of an arsenal we had accumulated from the mercenaries and raiders we had fought. It wasn’t until we started unloading our motorwagon that the truly excessive scale of it became apparent. Dozens of grenades and mines. Multiple heavy weapons. Two sets of damaged power armor. Roughly a hundred pounds of explosives. Enough small arms to outfit an entire squad of ponies, with enough ammunition that it would have been easier to measure it by weight instead of by round, if only we had scales. And that wasn’t even counting the two drums of water, the large stash of canned and packaged food, an extensive variety of spare parts and mechanisms Starlight had picked out as valuable, or the assortment of barely-used camping gear we had forgotten beneath all the other stuff.

Almost all of it was unloaded. When we left, we were stripped down to a bare combat load: our personal gear, some spare ammo, and three days’ worth of food and water. All told, we probably offloaded a literal ton of equipment, and I could see that the wagon sat noticeably higher on its suspension.

We carefully inventoried everything, and persuaded the increasingly impatient rider taking the cargo to verify the count. Then we climbed into our lightened vehicle and set off, rattling and bouncing across the Wasteland with renewed speed.

{\br}%
Starlight made exceptional time. It was a rough ride, as she drove the motorwagon across the uneven terrain at speeds she wouldn’t have risked—or possibly even been able to reach—with all our cargo.

It was exhausting, and it was exhilarating. We tore across the dry Wasteland at speeds I would normally only experience when flying. Starlight was exuberant, with a huge grin, eyes narrowed in excitement behind her goggles. Sickle stood tall in the rear, her hooves braced against the vehicle frame, giving the occasional enthusiastic yell.

I managed to hold out for almost half an hour, my mind occupied by concerns over current events, before their enthusiasm seeped into me and planted its hooks.

By the time we neared the Enclave camp, my squishy pony body felt sore and bruised from the journey, but I was grinning just as much as Starlight was.

The good mood quickly faded as we drove up to the camp at a more sedate speed. Sure enough, the Loyalists had moved on. The camp was abandoned, the tents removed. The few bits that did remain were clearly worse for wear.

Dusty ordered me onto the gun as we approached. I slid out over the back of the seat, and reared up to grip the machine gun. I pivoted it around as I scanned over the remains of the camp, keeping the barrel elevated in case any friendly ponies were out there.

The signs of magical energy weapon strikes were clear on the abandoned earthworks. The rearmost tower had collapsed. A few tattered tents had been left behind, and several craters peppered the interior of the camp. There had been a serious fight here, but there was no sign of either side.

\leavevmode\llap{“}This looks bad,” Dusty said, already turned to look out from the camp. I turned the gun around to do the same. “Serenity must have hit them before they moved out,” he continued. “Hard to say how the fight turned out, and there’s no telling where they went.”

\leavevmode\llap{“}So, what now?” Starlight asked. “Drive around looking for a patrol? That could take hours.”

\leavevmode\llap{“}We don’t even know if they’re patrolling this area any more,” Dusty said. “If Serenity hit their camp, that means they either evaded their patrols or hit too hard and fast for Aurora’s forces to hold them off. Either way, it means Serenity has the upper hoof in this area. She may not risk sending patrols around here.”

I mulled over that for a moment, while Echo spiraled down, landing in the midst of the camp and slowly searching it. I watched for a bit before ducking down, looking under the roof at Dusty. “Okay, you’re the military pony. Say you were in charge of these Loyalists. You’re in unfriendly territory, and just got driven back by a superior force from Serenity. What would you do, and where would you go?”

He frowned around the bit of his rifle, considering it for several long moments. “Depends on how poorly it went. I’d certainly want to pull back and establish a better position. Ideally one Serenity doesn’t know of or will have a hard time locating. Even better, fall back to friendly positions. Biggest problem with that is ‘friendly positions’ means up in the clouds, and last we heard, they hadn’t been able to locate other Loyalists.”

\leavevmode\llap{“}Okay,” I said, nodding along. “Let’s assume going above the clouds isn’t an option, because if they’ve gone up there, we wouldn’t be able to find them anyway. What does that leave them with?”

\leavevmode\llap{“}Short term, they could stay on the move,” he said. “They’re mobile. Keep scouts out for early warning, keep moving any time hostile forces are detected.” He frowned. “Except they would have been doing the same thing for defending this camp, and that clearly didn’t work. Plus, staying mobile is exhausting, especially if they have to move casualties. On the other hoof, digging in means getting crushed by superior numbers. There’s not much of a good play, here.”

\leavevmode\llap{“}It’s a bad situation,” I agreed. “So, given that, what would you do?”

He slowly scanned across the barren terrain as he mulled over the question. “Honestly? I’d either keep retreating at speed until it was clear there was no pursuit, or until I found friendly forces that could help mount an effective defense. ‘Cept they don’t have any friendly forces.” He gave a quiet snort, and after a moment, added, “Myself, I’d go for Mareford. Good, strong defenses, and probably the safest place in the Wasteland. Granted, that’s ‘cause I lived there, so I know what it’s like. Don’t know if Aurora would consider that a valid option or not.”

\leavevmode\llap{“}It’s a possibility,” I said. “Would be awfully convenient.”

Dusty snorted. “Yeah. Too convenient to hope for.”

\leavevmode\llap{“}Maybe.”

\leavevmode\llap{“}Hmm. You know…” Dusty lowered his rifle, looking back to me. “Aurora said she’d been sending patrols by Gemstone regularly. It’s about the only place we know they might go by, and if they took any serious casualties, they’ll need to rest somewhere. If Aurora doesn’t consider Mareford viable, she might try sheltering there, at least temporarily. It’s not a good position, but it might be the best she has. Even if she isn’t there, she might still be in contact.”

\leavevmode\llap{“}Might be worth checking out,” I said.

\leavevmode\llap{“}Yeah,” he said, though his tone didn’t sound convinced. Still, he shored up his expression and gave a decisive nod. “Let’s do it.”

{\br}%
The drive to Gemstone was less exuberant, but just as swift. I spent most of it in my natural form, with my armor, to protect against the banging and jostling of the wagon.

We were five miles out when Dusty called out, “Two fliers inbound, south-east high! Looks like Enclave.”

I quickly retook my disguise while Dusty brought out his binoculars. By the time I was ponified once more and on the gun, Dusty had them in sight. “Blue and rainbows. Looks like Loyalists.”

I grunted at how he said that. “Looks.”

\leavevmode\llap{“}Yeah,” he said. “Keep an eye on them in case they attack. Hopefully they’re friendly, but I don’t want to take the chance.”

\leavevmode\llap{“}Yeah,” I said. “I assume they’ve seen us?”

\leavevmode\llap{“}Oh yeah,” Dusty replied. “They’re diving towards us, and one of ‘em pointed. Hey, give them a wave. If these are really Loyalists, we want to look friendly.”

I did so, giving an exaggerated wave to ensure they could see it. When I finished, my hooves returned to the gun, and I gave a dry snort. “You know, I appreciate the irony of me saying this, but sometimes I \textit{really} hate dealing with changelings.

Sickle chuckled and gave me a heavy, spiky-hoofed pat on the back. “Yeah, we all do.”

\leavevmode\llap{“}Thanks,” I grumbled, rolling my shoulder; the cloak had given enough padding to keep the spikes from drawing blood, but only just.

Echo had swooped down to fly just above us. As the flying ponies drew nearer, they veered to come in at an angle, the ominous gems of their weapons no longer pointing directly at us. I took that as a good sign, and gave another wave. One of the ponies returned the gesture, and soon were banking around, circling us as they bled off the last of their altitude. Two pips popped up on my E.F.S. as they swooped in beside us: non-hostile.

\leavevmode\llap{“}Hey!” the lead mare called out in greeting as she slipped in, matching speed to fly just beside our motorwagon. “You heading in to Gemstone?”

\leavevmode\llap{“}Yeah,” I called back. “We were looking for you guys, too. We need to talk.”

She held up a hoof, then turned her head away. I could barely hear her words over the wind and rattling of the wagon. “Yeah, it’s that changeling and her friends. Yeah, the same one. Says she’s looking for us.” There was a long pause. “You got it.”

Lowering her hoof, she looked back to us. “Okay, you’re cleared into town. Just don’t go pointing that thing at anypony!”

She immediately banked, wings pumping as she veered away, her partner mirroring her actions perfectly. Moments later they were both climbing up into the sky.

\leavevmode\llap{“}Well that wasn’t the warmest welcome ever,” Starlight said from below.

\leavevmode\llap{“}Warmer than getting shot,” Dusty said. “Seeing as they probably got in a big fight with Serenity, I imagine they’re going to be a bit wary.” There was a pause as he thumped his hoof against the roof. “Hey, Whisper?”

I slid down to peer in over the back seat. “Yeah?”

He’d turned to look back at me. “You sure you want to do this?” he asked. “These ponies know you’re a changeling, and if they’ve had trouble, they might not look too kindly on the fact. This could be dangerous for you.”

I frowned. He was right, after all. “Could be,” I said, slowly nodding, but I quickly hid the frown to put on a show of determination. “But I’m not sure there is any place that isn’t dangerous for me, right now. At least here we have the chance of improving our situation.”

\leavevmode\llap{“}Fair enough,” he said with a nod, and turned back.

Minutes later, we came into sight of Gemstone. As we rolled over the tracks and up the path to the small town, we could see several figures atop the walls. One was a bright blue pony, while four more were clad in Enclave armor, the menacing black broken up by the Loyalist colors. The trio of magical energy weapons atop the wall swiveled to us; my heartbeat ratcheted up, but they simply tracked us, waiting in case we became a threat.

We came to a halt in front of the gate, waiting under the eyes of the Loyalist soldiers as the gate slowly swung open. Once it had, we rolled slowly through the opening.

There were a few more Loyalist soldiers beyond the gate, two of which were trotting our way, and further in I could see a few town ponies. One of the wall-top pegasi took wing, and once we were beyond the gate, flew in to hover before us, a hoof held up in a clear command to halt. The wagon ground to a halt once more, as black-armored pegasi surrounded us.

I started to worry that we had made a horrible mistake.

\leavevmode\llap{“}Okay!” the lead pegasus called out. “Exit the vehicle, and leave all your weapons behind. You can have them back when you leave, but you’re not carrying them in town.”

The bright blue pony atop the wall was a unicorn stallion, and he reacted with surprise at that declaration. “What are you talking about?” he called out. “We don’t disarm our guests.”

\leavevmode\llap{“}You don’t,” the pegasus replied, his attention focused on us. I couldn’t help but imagine him glaring behind those eyepieces. “But we do, especially for these ponies.”

\leavevmode\llap{“}Now hold on a minute!” the stallion said, trotting down the stairs to approach the Loyalist soldier, while we remained carefully still and quiet in our motorwagon. “These ponies are \textit{our} guests, and besides, this ain’t the first time they’ve been here. Well, ‘cept the big purple one, but I figure if they vouch for her, she must be all right.”

\leavevmode\llap{“}They aren’t all ponies,” the pegasus replied, his gaze unwavering. “The gray one’s a changeling. Maybe the others, too.”

\leavevmode\llap{“}Hey!” Starlight called out, thumping a hoof against the steering wheel. “Come on, really? Why don’t you shout it a little louder? There might be ponies in Mareford that didn’t hear you!”

I winced a little. I appreciated Starlight leaping to my defense, but I couldn’t see it helping us.

A mare’s voice cut across the argument. “What the hay is going on out here?”

I recognized that voice, ears perking up as I looked out the window. Sure enough, the Enclave Loyalist trotting up to the scene was Sergeant Hail Burst. The mask that would cover her muzzle hung at her side, letting everyone see that she looked thoroughly unhappy, a look only furthered by the pocked and charred surface of her armor. It seemed someone had unloaded a magical energy weapon into her side.

\leavevmode\llap{“}I ordered these ponies to disarm,” the first pegasus said, gesturing our way before inclining his head to the unicorn guard. “Blueberry objected.”

Hail Burst turned to the approaching guard. “You understand that at least one of these individuals is a changeling, and that we can’t verify whether or not they work with the group that we have been fighting?”

The unicorn halted, casting a glance our way, frowning. “Can’t say I know anything about that,” he said, a cautious tone to his voice, but it vanished as he followed up. “Can’t say it makes any difference to me, either. We ain’t in the habit of assuming the worst of our guests, if you remember.”

Hail Burst had immediately turned back to the other pegasus. “Snowfall, your orders are to assist the locals in guarding the settlement, not to take over its operation. Unless they ask you to do something that directly violates your orders or our laws, you are to follow their direction. They can keep their equipment.” She then turned to look pointedly at us. “But keep a close eye on them, all the same.”

While she was saying that, I had climbed over the back of the seat, and pulled myself up onto the roof where I was more open and visible. “I appreciate that my kind doesn’t have the best reputation at the moment,” I said, hoping the openness might defuse some of the tension, “but we came here looking for you because there are events underway that you need to know about.”

There was a tension in Hail Burst’s jaw, the only part of her face I could actually see. Despite that, she replied evenly. “What kind of events?”

\leavevmode\llap{“}There’s an army gathering,” I said. “The ponies of the Wasteland are preparing to hit Serenity. We’ve got one chance to stop Serenity before it’s too late for hundreds, if not thousands, of people. We’ve met you before, so they sent us to see if we could convince you to join the fight.”

She frowned.

It was the guard, Blueberry, who spoke up. “What do you mean, an army?”

\leavevmode\llap{“}Trotsen mobilized every vehicle they have. They’ve got a few hundred soldiers, dozens of motorwagons, and even a tank. Right now, they’re making their way to Mareford, which has the best fighting force in this part of the Wasteland and is the largest producer of weapons and ammunition. We’re also reaching out to any others who are willing to join the fight. Every extra person we can get pushes the odds a little more in our favor, and we’re only going to get one shot at this.”

There was a moment of silence. Hail Storm stood there, as if thinking hard on what I had said. Blueberry gave her a critical look. Behind them, a few more ponies were looking on from porches or storefronts.

Then Blueberry turned back to me. “Fuck it. I’ll go.”

Hail Storm’s head whipped around to look at him.

I opened my mouth, about to say that it wasn’t necessary, but I realized just how hypocritical that would be. Instead, I nodded. “I appreciate it.”

Some of the onlookers were approaching, and a couple of the other Gemstone guards were trotting up to Blueberry. “What’s going on?”

\leavevmode\llap{“}They’re gathering an army,” Blueberry replied. “Taking on the group that wiped out Rust.”

As they fell into a hushed conversation, Hail Storm watched, her expression difficult to read behind those amber eye lenses. Finally, she turned to me, her tone a bit softer than it had been. “We should speak with Commander Aurora.”

The pegasus guard, Snowfall, stepped up. “Commander—”

He fell silent as she held up a hoof. She lowered it again, looking to me. “Come with me.”

I hopped down from the wagon, with Echo landing beside me. From behind the wheel, Starlight called out, “I’m going to park the wagon, then I’ll join you!”

I gave her a nod, then turned to follow Hail Burst to Emerald’s store.

Not Emerald’s store. Not any more. I hesitated a moment at the thought, then huffed a deep breath and pushed on.

I felt like an intruder as I stepped into the store. It was as if it had somehow become some alien place, even though almost everything was just as I remembered it. Only one thing had changed: Emerald was gone. A different pony was behind the counter.

Dazzle was slumped across the counter, head resting on her forelegs, and lifting wearily as we entered. There were the faintest of bags forming under her eyes, hinting at fatigue, and her well-groomed mane had just a couple of hairs sticking out of place. For anypony else, it wouldn’t have looked unusual. For Dazzle, it looked like she was completely run-down.

Despite that, her expression slowly brightened as she recognized me. “Hello again,” she said, her voice soft. It was friendly, if not enthusiastic; the events surrounding our last meeting still hung over us. “Wasn’t sure if you’d be coming back.”

Hail Burst snorted. “Who says ‘she’ has? This is a changeling.”

I winced, then gave Hail Burst a pointed look. “The same changeling you had no problem with just a few days ago.”

\leavevmode\llap{“}Things change,” Hail Burst said.

\leavevmode\llap{“}Wait,” Dazzle said, looking between us in confusion and perhaps a touch of alarm. Her eyes settled on me. “You’re a changeling?”

I sighed. At this rate, the entire Wasteland would know before nightfall. “Yes,” I said. “I always was, and—”

Her eyes suddenly widened, ears perking high, and she pointed an accusing hoof at me. “\textit{That’s} why your coat and mane were so immaculate! You… you… \textit{cheater!}”

\leavevmode\llap{“}I’m sorry, I—”

My mouth snapped shut as she started laughing, her hoof returning to the counter. “Holy crap,” she said, and I stared in momentary confusion at her broad grin. “Okay. I’ve got to admit, I’m a little envious!”

I’m not used to stumbling over my words, but after a few aborted attempts at a reply, all I managed was, “Oh.”

She gave another laugh. “Oh, goddesses, that would be the best thing ever. So you can really look like anything you want? Like, not just cosmetic changes, but \textit{anything?}”

\leavevmode\llap{“}Uh…” I glanced at Hail Burst, who was frowning again. I looked back to Dazzle’s excited grin. “...More or less. Bigger changes take more out of me, but anything pony-sized is fairly easy.”

Hail Burst coughed. “Yes, well, that’s all great, but you’re going to have to wait on… whatever this is. Our little changeling friend here is going upstairs to talk with Commander Aurora.”

\leavevmode\llap{“}Oh,” Dazzle said with a subtle wince, her smile halving in intensity. “I hope we can catch up afterwards?”

I hesitated, still a little surprised by her reaction, but after a moment I relaxed, smiling back. “I’d like that.”

We parted as I followed Hail Burst up the stairs. Her armored tail flicked faintly, an agitated expression. Her behavior was clear enough to me; she was not at all pleased with how amiable my encounter with Dazzle had been. Given how bluntly she had outed me, I imagine she had hoped it to sour any existing relationship, instead of being a new source of interest. Between everything I had seen and heard, the conclusion was increasingly obvious: they had encountered Serenity, and that encounter had gone poorly.

It wasn’t until I saw Commander Aurora that I knew just how poorly it had gone.

I hadn’t heard a reply when Hail Burst knocked, and when I followed her in, I saw why. Commander Aurora wasn’t in her armor. Instead, she was in a bed, slowly and agonizingly pushing herself up to a sitting position with her remaining foreleg. There was no sign of the other leg, only a thorough canvas of bandages wrapped around her chest, covering the misshapen place where the shoulder should have been. I couldn’t tell if her wing was hidden under those bandages, but from the contours of her body, I suspected it was missing as well. More bandages wrapped around her neck and up to her face, even over her right eye. Glimpses of badly burnt and partially healed flesh showed at the edges of the cloth.

She wheezed slow, ragged breaths as she finished sitting, and turned to look at me with her one good eye. Despite the tremendous pain I’m sure she must have been in, her eye was hard and unflinching.

When she spoke, it was in short fragments, and her voice was wholly changed; the hints of scratchiness had become raspy, gravelly tones that almost overtook the words themselves. “If I thought… you had anything… to do with what happened…” She paused, taking a few more rasping breaths before continuing. “I’d have you taken out back… and shot.”

It was simultaneously concerning and reassuring.

\leavevmode\llap{“}I hope it doesn’t come across as making light of the situation,” I carefully replied, “but I’m glad you’re not doing that.”

\leavevmode\llap{“}I’m not… stupid…”

She abruptly broke out into rough coughing, her body shaking with its violence. She almost fell over as she fumbled for a glass of water on a stand beside her bed, and Hail Burst trotted over to help her.

While they were occupied, I glanced around the room. It was furnished nicely enough, particularly given how everything had to be scavenged. There were some maps and other papers on one of the tables, as well as a terminal. The other table held an array of medical supplies, and soiled bandages filled a small trashcan beside it. There were even two empty potion bottles set in front of a large trauma kit; Aurora had likely been given at least two healing potions while here, and who knows how many before arriving in Gemstone, and was still in such bad shape.

There was a quiet murmur as Aurora waved off Hail Burst, her eye meeting me again. Her voice was a little clearer. “The supply team didn’t expect us. We caught them by surprise. No warning.” She paused for another short coughing fit, but it passed easily. “Their response force chased scouts. Hunted for us. They didn’t come straight for our camp. It gave us time… so either they wasted an opportunity to wipe us out… just to make it look like you didn’t tell them anything… or you didn’t tell them anything.”

I just nodded. There was little I could add.

\leavevmode\llap{“}Which doesn’t mean you aren’t trying to play us,” she rasped. “Just that you aren’t doing it for Serenity.” Her head turned, as if signifying the end of the conversation, and she faced Hail Burst. “Why did you bring her here?”

Hail Burst cleared her throat. “Because she brought some information and a… proposal… and I thought you should make the call on what we do about it.”

Aurora sighed slightly, the sound grating and unpleasant. “You’re the acting commander… that means you—”

\leavevmode\llap{“}With all due respect,” Hail Burst said, her voice firm, “this is significantly bigger than organizing camp defenses and sending out a few patrols while you recover.”

There was a long pause as Aurora stared back at her, but finally, reluctantly, she looked back to me. “Okay... What is it?”

\leavevmode\llap{“}We’re gathering an army,” I said, and gave her a brief overview of the forces involved. Once I had laid out the situation, I added, “And we could use your help. I can see that things haven’t gone well for you, but I imagine this has also shown just how dangerous Serenity can be when you’re on your own. This fight is inevitable. They’re going to come after us until there are no more threats to them. The one choice we have is whether we face it together or all alone.”

Aurora had broken her hard stare, looking down with a more thoughtful expression, and eventually followed up with a slow shake of her head. “We’re not a fighting force any more,” she rasped. “When those changelings caught up with us, there must have been more than a hundred of them. We took more than fifty percent casualties. Eight confirmed dead, twelve missing. Many of the wounded will never recover. We lost Lifeline and most of the medical supplies. We have barely enough hooves to man the walls and do local patrols.”

\leavevmode\llap{“}Mareford has doctors and supplies that could tend to your wounded,” I offered, hoping I remembered correctly. “And they have a much more defensible position, with a large fighting force. I’m sure they’ll be willing to help you if you’re willing to help them. Your wounded get the best treatment available in the Wasteland, while your able-bodied soldiers get the help of an entire army to strike back at the people who attacked you and killed their comrades. An army that can help you take back the \textit{Cumulonimbus} before Serenity can turn it on the settlements around here.”

Her eye looked up again, fixing me with a hard stare, as if she could see the juicy carrot I was dangling in front of her. Still, she remained silent for a few moments as she mulled it over. Her reply was a change of tactics. “And why are you so interested in getting \textit{us} into the fight?”

\leavevmode\llap{“}I’m interested in getting \textit{everyone} into the fight,” I said. “Heck, one of the guards here already volunteered to join in when he overheard us.” I raised a hoof, gesturing to Aurora. “As for your group, specifically, I may not be all that versed in tactics, but I’ve been in enough fights to appreciate the value of a hard-hitting force to break the odds. You’re a group of trained soldiers in heavy armor, carrying heavy firepower, and with excellent mobility. We’ve got an army to engage Serenity’s forces on even terms, but the more mobile and aggressive forces we have, the better we’re able to hit them where we want, when we want. Your ponies could be the difference between victory or defeat, and the stakes are far too high for all of us to not push things as heavily in our favor as we can arrange.”

She watched me warily, even as she carefully considered what I said. “Could be,” she rasped, giving a little not, but then added, “but it could also be that your army doesn’t stand a chance, and my ponies are better off withdrawing. Once our war is done, then we can come back and deal with them properly.”

\leavevmode\llap{“}After hundreds or thousands of ponies have died!” I said, and quickly softened my tone again. “At least come to Mareford. See the people who are gathering to fight. You can judge for yourself whether they have any chance of pulling this off, but at least meet with them.”

Another long pause. “I have eighteen wounded soldiers. Will Mareford have the capacity to care for them?”

\leavevmode\llap{“}Yes,” I said; even if they didn’t have enough medical facilities, I’m sure something could be arranged. “They’re a much larger settlement than Gemstone.”

She grunted weakly, followed by a few suppressed coughs. It took her a moment to recover and speak again. “And what if these changelings move into Gemstone when we leave?”

I frowned, alarmed at the possibility, but I quickly shook it off. “I would imagine they’d put a priority on dealing with the gathering army rather than hitting a small settlement. That said, and I hope you don’t take offense at this, but given how your previous encounter with Serenity turned out, I think it’s unlikely that your presence here would change the outcome.”

She grunted again, grimacing slightly, but the expression faded away over the next few seconds. Finally, she gave a slow nod. “Okay. We’ll meet with your army. I think we can do that little.” She turned her head to look at Hail Burst again. “Make it happen.”

Hail Burst gave a sharp nod. “Yes ma’am.” She then turned, giving a jerk of the head that made it clear I was to follow her.

We exited the room. I’d barely stepped into the hall and shut the door before Hail Burst abruptly turned to face me, muzzle close to mine. I drew to a halt, expecting some hostile gesture.

Instead, she immediately got down to business. “This army we’re meeting. When will it arrive in Mareford, and how long do we have to get there before it leaves?”

Regaining my composure, I answered. “They should be arriving sometime this evening, probably in the next few hours. As for when they set out for Serenity, I’m not sure, but they’re eager to start the attack and doubt that you’ll show up. I doubt they’ll stay any longer than necessary, which might mean setting out at first light.”

My response was met with a snort. “You sure don’t like giving a lot of time, do you? You expect us to displace all our wounded and equipment just like that?”

\leavevmode\llap{“}Less ‘expect’, more ‘hope’,” I replied.

\leavevmode\llap{“}Wonderful,” she dryly replied. “Go talk to your friends. I’ve got a lot of preparations to organize and a short time to do it, so the last thing I need is some changeling getting in my mane.”

She turned and walked briskly to the stairs, her mouth clenched in a tight frown.

\leavevmode\llap{“}I’m sorry for what’s happened to you,” I said, trying to ease some of the tension. “I know you’ve had bad experiences with changelings, but I’m not your enemy. I’m trying—”

\leavevmode\llap{“}\textit{I know},” she replied, the words coming out in a clenched-teeth growl. She looked back over her shoulder. “And for the record, this isn’t me treating you like an enemy. I shoot my enemies. This is me treating you as a bad reminder of just how hard we got fucked. So you just go hang out with your friends. Stay out of my way. Give us the time to go meet this army, get a feel for what’s going on, and let \textit{this} crap…” She raised a hoof, gesturing back and forth between us. “...settle down and sort itself out, ‘cause nopony’s going to just take your word about anything right now.”

I paused, and finally nodded without saying anything else.

\leavevmode\llap{“}Good,” she said, turned, and headed down the stairs.

I gave her a few moments to gain some distance before heading downstairs myself. When I stepped into the main room again, she was just stepping out the front door. Starlight and Dusty were at the counter, along with Dazzle and the gate guard, Blueberry. Starlight had been watching Hail Burst’s exit, and turned to me with a worried look. “What’s wrong?”

\leavevmode\llap{“}They’ve had a hard time,” I said with a shake of my head. “But they’re going to go to Mareford, so they may be on board. I guess we’ll find out when—”

I halted; Dazzle had stepped out from behind the counter, grinning expectantly. The moment my mouth shut, she said, “Well, come on! I want to see what you look like!” Blueberry looked over with curiosity, while Starlight’s ears had perked up with alarm, looking anxiously around the gathering.

I opened my mouth to reply, but stopped and sighed. There really wasn’t any point in arguing it. I called up my magic, and after taking a moment to slip out of my cloak and saddlebags, stood before her in nothing but my chitin.

Dazzle walked up, no smiles now, just staring intensely. She moved to the side, eyes tracing over every inch of me. “That’s so weird,” she murmured before her lips twitched upwards with a hint of a smile. “You’re all glossy and shiny.”

\leavevmode\llap{“}Thank you.”

Her eyes hesitated at my legs. “What’s with the holes?”

I shrugged. “Nothing’s really ‘with’ them. That’s just how changelings are.”

\leavevmode\llap{“}That’s so weird,” she repeated, though she was smiling openly again. “I like it. It’s exotic!”

I could hear Starlight’s hoof meeting her face. “Oh goddesses no.”

Dazzle laughed loudly, taking a step back and raising a hoof. “Hey, relax. I’m not going to get between you two lovers. I learned my lesson.”

\leavevmode\llap{“}We’re not lovers,” Starlight groaned.

The front door swung open, and Sickle stuck her head in, grinning beneath her muzzle. “Hey, is someone making the runt squirm without me?”

Starlight abruptly set her hoof down, glaring at Sickle. “Go away!”

\leavevmode\llap{“}Fuck you,” Sickle said, still grinning as she entered. “Oh, wait, I forgot. That’s Whisper’s job.”

Starlight groaned. “Why are you even in here? Don’t you have anything better to do?”

\leavevmode\llap{“}I know when I’m needed,” Sickle smugly replied. “Also, no.”

Starlight grumbled and turned away from her. “\textit{Anyway}, didn’t we have some actual business to deal with?”

\leavevmode\llap{“}You mean other than admiring your exotic marefriend?” Dazzle said with a light, teasing tone, then blinked. She turned to me, head craning a little, with a questioning look at my flanks. “Wait, are you actually a mare?”

I resisted the abrupt urge to tuck my tail in close and protective. “I am female,” I replied as evenly as possible. Dazzle just smiled, giving a little chuckle. I added, “I do have to say, it’s a nice change to have ponies react with curiosity instead of fear or revulsion.”

\leavevmode\llap{“}Well, we try to be friendly,” Dazzle said with a shrug, and leaned against the counter. “That’s what Gemstone’s all about. You’re a good… well, not-pony, I guess, but you know what I mean. You’ve been nice and friendly, and you’ve helped us out before. What you look like isn’t going to change that, even \textit{if} some other changelings are causing problems. I think Emerald taught us better than that.”

That name sucked any humor out of the conversation. Starlight looked away, and despite the difference in species, it was apparent that my own discomfort was clear. “Hey, hey,” Dazzle said, raising her forehooves. “I didn’t mean to kill the mood. I know, it hurts that she’s gone, but… look, she always tried to cheer up ponies, right? I don’t think she’d like her name making them sad.”

I swallowed. “It’s… not that.”

Starlight eyed me.

Dazzle’s expression was still restrained, but curious. “Then what?”

I just stood there, silent, while my mind raced, bouncing from one piece of information to another, weaving it together, sorting out the benefits and risks.

There is one particularly dangerous side to secrets: the damage they cause can depend heavily on how the come to light.

I took a deep breath, gave a silent apology, and spoke. “Okay. Emerald made me promise not to tell you this, but—”

\leavevmode\llap{“}Woah, woah,” Dazzle said, raising a hoof. “If she made you promise, that’s that. She must have had good reason to—”

\leavevmode\llap{“}She did,” I said. “But the situation’s changed, and I’m certain that if she were still here, she’d want you to know.” I hesitated before adding, “And you’re going to figure it out soon, anyway. Better you learn all of the details now instead of having to make assumptions.”

Concern had etched itself into Dazzle’s expression. “...What are you talking about?”

\leavevmode\llap{“}Emerald was a changeling.”

Both Dazzle and Blueberry stared at me, blinking. Dazzle spoke first, and with an uncharacteristic crudeness. “Brahminshit.”

I shook my head and pushed on. “Did she ever tell you where she came from?

Dazzle stared open-mouthed at me for a few seconds before replying. “She never really talked about her past, but that doesn’t mean she was a changeling!”

\leavevmode\llap{“}But she did talk a little about it,” I said. “She even mentioned it to us, vaguely, on one of our visits. Do you remember the name of the place she grew up at?”

\leavevmode\llap{“}Why is that so important?” Dazzle demanded. Her body was tense.

\leavevmode\llap{“}Please,” I said, keeping my tone gentle.

She glared silently at me for several seconds before replying. “Like I said, she didn’t really talk much about her past. Yeah, I remember her saying something about it, but… I don’t know, I can’t quite remember the name of the place. It’s just…”

\leavevmode\llap{“}Serenity.”

Blueberry’s ears went up, his expression tightening.

\leavevmode\llap{“}That’s the place,” Dazzle said, thumping a hoof lightly on the counter before noticing the change in Blueberry’s expression. “What?”

\leavevmode\llap{“}That’s the group the pegasi were talking about,” he said, his eyes fixed on me. “The one that hit them so hard. The one that wiped out Rust.” A hoof came up, pointing at me. “And she was talking about leading an army there.”

\leavevmode\llap{“}Emerald was born there,” I said. “Her hive taught that ponies were just monsters, responsible for everything wrong with the world. That the only thing you were good for was food. Then she got here, and found out that wasn’t true at all. She found out just how nice ponies could be. She couldn’t go on helping her hive hurt ponies, so she… she \textit{left}.” I looked over Dazzle and Blueberry. “I don’t know if I can convey how significant that is to a changeling. To a changeling, turning away from your hive is… it’s like a pony cutting off their own cutie mark.”

Dazzle and Blueberry both winced at that imagery.

\leavevmode\llap{“}I want to make it clear,” I said, my voice gentle. “She was still the same person you knew. She wasn’t trying to deceive you, and it tore her up that she had to keep it secret. And I know you’re going to think it, but no, it wasn’t because she didn’t trust you. I think she knew you’d understand. She didn’t tell you because it would be \textit{dangerous} for you.”

Dazzle looked to me with damp eyes. “Dangerous?”

\leavevmode\llap{“}Serenity,” I said. “At the time, they were mostly passive, hiding, but they guarded their secrecy. If they found out some ponies had information that pointed even \textit{slightly} in their direction, they’d see it as a threat, and they’d be ruthless in removing it. If she told you, and Serenity ever caught word of it, they’d see every pony in Gemstone as a risk. They’d have done the same thing here that they did to Rust.”

Dazzle didn’t reply. She simply stared, her gaze lowered to the ground, as if unable to fully process everything that was said.

\leavevmode\llap{“}That’s why she insisted on going on that job,” I said. “She knew who Amber was. She knew Amber was another agent of Serenity, and that if she slipped up in even the slightest way, she’d be discovered. She also knew that if Serenity had any reason to suspect that she told you anything, all of Gemstone would be in danger. That’s why she planned on going out and faking her own death, to keep you safe.”

\leavevmode\llap{“}Fake?” Dazzle said, her eyes rising once more. “Is she still alive?”

That little glimmer of hope hurt. “I’m sorry. Amber must have caught on that something was up. Serenity killed her.”

She deflated ever so slightly.

\leavevmode\llap{“}But it’s only because of Emerald that we even know Serenity is a thing.” I raised my PipBuck-clad hoof. “Because of her, we know where they are. Because of her, we were able to discover that Serenity isn’t just hiding any more. Their queen wants to put every pony under her hoof. They’ve been arming raiders and have already wiped out one settlement. We’ve turned up agents infiltrating both Trotsen and Mareford. Serenity is gearing up to make a big move, but Emerald has given us a chance to fight back.”

Dazzle slowly nodded, silent.

\leavevmode\llap{“}These other changelings,” Blueberry said. “What happens if they aren’t stopped?”

\leavevmode\llap{“}It wouldn’t be just taking over,” I said. “The only value they put on ponies is food. Most likely, they’ll wipe out any groups that could be a threat, like Mareford or Trotsen, as well as what’s left of my hive. They’ll probably kill most ponies and keep just enough to be harvested for love, with a small breeding population, all kept under heavy guard.”

Dazzle’s expression had turned uneasy. “What do you mean, harvested?”

\leavevmode\llap{“}Changelings feed on love,” I said. “Serenity has dozens of ponies held prisoner in suspended animation, and they drain them of love to feed the hive.”

The look of unease grew, with a touch of fear. “That’s how you guys feed?”

\leavevmode\llap{“}That’s how \textit{they} feed,” I replied sharply, eyes narrowing for a moment before I relaxed again. “\textit{My} hive survives by making friends, to earn willing affection, even if we can’t always be open about it.”

I might have gone on, but Blueberry had abruptly turned and walked off toward the door, his expression grim. I might have said more to him, but Dazzle asked how the whole love-feeding thing worked, so I settled in to give her a brief answer. That led into discussing Queen Chrysalis the Sixth and the Serenity hive, and the differences between those and my own queen and hive, which of course necessitated explaining more details of our history.

And yes, there was certainly a large part of me that was anxious about sharing so much information. At the same time, there was something almost cathartic about it. It was almost like unloading, like a weight had been lifted, if only temporarily. It also seemed to help Dazzle. She started out tense and uneasy, but steadily relaxed until she sat beside me, fascinated by this new and unknown subject.

We must have talked for half an hour. It finally came to an end when several Enclave Loyalists entered, bearing a stretcher, with Hail Burst in the lead. She approached me. The rest continued on to the stairs, though their helmets turned to track me, expressions unreadable behind the amber lenses.

\leavevmode\llap{“}We’re about ready to go,” Hail Burst said as she came to a halt. “We’re loading the last of the wounded right now. Dust-off is in ten minutes.”

I stood. “I guess we should get ready to go.”

\leavevmode\llap{“}Right,” Dazzle said, quickly rising to her hooves. While she trotted to the back of the store, I called up my magic, restoring my disguise. Hail Burst’s frown tightened slightly, but she said nothing, simply turning to leave.

\leavevmode\llap{“}Wait!” Starlight said, and Hail Burst looked back at her. “What about Singe? Is she okay?”

\leavevmode\llap{“}The civilian?” Hail Burst asked. “She’s stable. We’ve already loaded her up.”

Starlight relaxed, smiling at the good news. “Thank you.”

Hail Burst nodded, turned, and left.

Dusty spoke for the first time since I came downstairs. “Let’s get back to the wagon,” he said. “Where’d you park?”

We followed Starlight out the back door of the store, and I almost ran into her back as she abruptly halted.

Some forty ponies had gathered there. Some were guards clad in varying degrees of heavy armor. Others wore lighter barding, or even none at all. Almost all were armed with the Wasteland-made energy weapons Gemstone was known for. Arclight was there, too, with a small wagon of his goods, and was in the midst of passing out his creations to the few ponies not already armed.

Echo sat in the back of the wagon, warily watching all the ponies gathered around her.

I saw Blueberry near the front of the pack, and still grim-faced as he helped tighten the straps of another pony’s armor. At the sight of our appearance, he turned to face us.

Starlight, being in front of us, spoke first. “Uh, what’s going on?”

\leavevmode\llap{“}We’re all going, too,” Blueberry said, backed by several sounds of affirmation from the ponies around him.

I have to admit, I was a little concerned. These were just regular ponies. \textit{Good} ponies, certainly, but not soldiers. Some were part-time guards, but most weren’t even that. Given Dusty’s glance my way, eyebrow raised, he was thinking the same thing.

I stepped around Starlight. “I don’t want to turn away anyone who wants to help, but are you sure you know what you’re getting into?”

\leavevmode\llap{“}We know,” Blueberry said, while a few other ponies nodded along. “Hell, we saw what they did to these pegasi when they arrived.”

\leavevmode\llap{“}It’s going to be even worse than that,” I said. “This isn’t going to be like fighting raiders, even if it was the biggest band of raiders to ever exist. The changeling hive we’re going to be facing has professional soldiers with extensive training and the best equipment available, and that’s the \textit{least} scary thing about them.” I looked around, wondering how far the word of my nature had spread. After a moment, I decided it didn’t really matter anymore. “I may not know all that much about combat tactics, but I \textit{do} know changeling infiltration tactics. We can expect anything from impersonating friendly or neutral forces, or embedded Infiltrators passing on information, or even replacing or assassinating leadership, and chances are good we won’t even know it’s happening until ponies start dying.”

There were a few looks of concern among the crowd. I could see Blueberry considering what I said, but his look of grim determination returned a moment later. “We all know it’s going to be bad, but that’s why we’re going. Hell, I had friends in Rust, and now we find out they’re the ones that killed Emerald? People like that need to be stopped. But then you say they’re holding a bunch of ponies hostage? Yeah, I ain’t going to sit around all safe and pretty when I could be helping. Far as I see it, it can’t be any worse for us than it already is for them.”

I hesitated, looking over the group of ponies. “Like I said, I’m not going to turn away any pony that could help, but… but the world is already short enough on good ponies.”

\leavevmode\llap{“}It’ll be a lot shorter on ‘em if we weren’t willing to help,” Blueberry said. “Emerald was right about that. Gemstone isn’t just hollow talk from behind a wall of turrets. We’re about doing what’s right, even if it costs us, because that’s what the Wasteland needs.”

There were murmurs of agreement as looks of unease faded. Some of the ponies stood a little taller, a few smiles starting to overtake grim expressions.

The door behind me thudded open, immediately followed by Dazzle’s voice. “Okay, I grabbed all the—woah…”

I looked back. She had donned her heavy barding, and had slung two bulging and hastily packed saddlebags across her back, while her magical energy rifle hung from its sling around her neck. The look of surprise on her face lasted only a moment before melting into a pleased smile. “...Well, all right. We’re all going?”

Several ponies called out in the affirmative, and her smile grew as she approached the rest of the group. She only paused when she saw Arclight. “You too?”

He looked up from the wagon of weapons. “Somepony’s got to maintain the weapons and do repairs. I’ll be more useful with you ponies than I will sitting in my workshop.”

\leavevmode\llap{“}Well we’ll be glad to have you along,” she replied.

Dusty and I exchanged glances before he stepped forward. “Okay, I’m not going to complain about having a few more hooves, but we’re on a tight time-table. We need to get to Mareford as quickly as possible, and we don’t have enough room to carry everypony.”

\leavevmode\llap{“}The pegasi have sky-wagons!” some pony in the crowd called out.

\leavevmode\llap{“}They have two,” Dazzle said, “and they’re probably full-up with wounded.” She then gestured to our motorwagon. “How much can that pull? Can it pull a wagon?”

Dusty frowned. “Our motorwagon’s up to it, but I wouldn’t trust a normal wagon to hold up to that kind of speed.”

It was Arclight who spoke up next. “We’ve got a couple of wagons that should be up to the trip. They wouldn’t hold up to full-speed driving, probably, but they’ll hold up to a modest pace so long as we stay to the old caravan road.”

Dusty considered that for a moment, clearly still having some concerns, but finally nodded. “Okay, but it’ll have to be quick. The Loyalists are taking off in about five minutes. Echo, Starlight, could you help them?”

\leavevmode\llap{“}Should be easy enough,” Starlight said, already trotting towards the motorwagon. “We still have the rig we welded on to tow the other motorwagon, shouldn’t take much to modify it.”

What followed was a frantic scramble. Dusty and I helped load a few ponies and their supplies into our motorwagon, giving up our own seats to join Sickle in the cargo bed. Six ponies crammed into the cab. Dazzle climbed up to sit straddled across the side-armor of the cargo bay, and a few other ponies followed her example, clinging to the vehicle. Our wagon sagged once more under the load of ponies.

Behind us, a pair of wagons were brought in, one of which already carried two of the gate’s magical energy cannons. Echo and Starlight got to work hooking them up end-to-end, cutting, welding, and just plain hammering scrap metal parts to serve their purposes, all with impressive haste. Echo’s magic, particularly the ability to levitate several hundred pounds and hold it steady, seemed to help a lot.

They had just finished getting the wagons connected when a Loyalist soldier swooped in, backwinging to come to a hover beside us. “We’re lifting now. Hail Burst wants to know if you’re setting out now, or if we’re meeting in Mareford.”

\leavevmode\llap{“}We’re ready to move,” Dusty replied. “We won’t be making the best of time, but we should still make Mareford by nightfall. If she wants to travel together for mutual security, we’d certainly appreciate it.”

\leavevmode\llap{“}I’ll let her know,” the soldier replied, and zipped off.

Dusty gave one last look back at the pair of wagons behind us, linked end-to-end and packed with ponies, then turned to rap a hoof against the roof of the wagon’s cab. “Okay, Starlight. Take us out.”

The motor hummed, dirt crunching softly under the tires as we started to roll. New squeaks and groans joined the usual soft cacophony of sounds, and as we built up to the speed of a brisk trot, the wagons behind us rattled along.

We wound our way out from behind the store and toward the town gate. The heavy gate itself was already open, and several of the town’s ponies were gathered on either side or atop the walls. Ponies called out cheerfully, waving to each other, though I caught an undercurrent of worry in the occasional damp eye or wavering smile.

As we rolled through the gate, I looked back at the trailing wagons and their cargo. The ponies there waved back happily to the ponies they were leaving behind. Their grins were sure and proud. They were good ponies, following me in the hopes that they could do the right thing and help others who couldn’t help themselves.

I only hoped I wasn’t leading them to their deaths.

{\br}%
It was dark when we rolled up to Mareford.

The old dirt road was level enough to make decent speed without destroying the towed wagons, though it had been a rough ride for the passengers. Several times, the ponies in the wagons had started looking distinctly miserable. Each time, some pony made a comment we couldn’t make out, and was answered by laughs and grins. Despite the unpleasant ride, it seemed their spirits were high.

The Loyalists descended as we neared our destination, flying alongside us at a relaxed pace, with the two military sky-wagons trailing at the rear. I’m not sure if they counted as sky-tanks when they didn’t carry weapons, but they were still armored flying vehicles. I’d noticed Dusty looking at them several times during our trip, no doubt contemplating ways to make use of such hardware.

Lights danced and flickered from campfires set outside the gate, illuminating the Trotsen motorwagons and the ponies milling around them. The Gemstone ponies started murmuring amongst each other, craning to get a good look as we slowly drew closer. The Loyalists, in turn, drew back at Hail Burst’s barked order, and formed into neat columns behind us.

Sandstorm’s ‘Beast’ was easy to find, still at the head of the pack, its cannon pointed squarely at the gate. Under Dusty’s direction, Starlight drove us up to the tank, and with a slow, rattling groan, our wagons finally came to a halt.

It was Axle who popped up from the tank at Dusty’s call. He stared out at us for a second before snorting. “Didn’t think you’d actually make it,” he said, casting a glance back at the Loyalist forces, who had landed neatly behind us.

\leavevmode\llap{“}We told you we’d be here,” Dusty replied evenly. “Is Sandstorm up?”

\leavevmode\llap{“}Yeah,” Axle said, pointing off to the gate. “She’s still in town, talking with their mayor.”

\leavevmode\llap{“}Guess we’d better get in there, too,” Dusty said.

Starlight stuck her head out the window, twisting to look back at us. “Uh, Dusty, you sure that’s a good—”

\leavevmode\llap{“}It’s fine,” Dusty quickly said, cutting her off, and ignoring the questioning look Starlight gave him. Instead, he turned to address Hail Burst. “You should probably make introductions, too.”

\leavevmode\llap{“}Of course,” she replied, her head turning to look at the gathered Trotsen force before looking back to Dusty. “Will Mareford be making accommodations for my ponies, or will we be camping outside of the walls?”

Dusty shrugged. “I suppose that depends on how our meeting goes.”

\leavevmode\llap{“}I see.” Hail Burst turned and called out. “Cyclone! You’re in charge while I’m gone. Get everypony settled in case we’re staying in the field, and set pickets. Downdraft, you’re with me.”

Dazzle nudged Dusty’s shoulder. “Should we stay out here, too?”

\leavevmode\llap{“}You should make your introductions, too,” he replied. “Besides, they better not be turning away Gemstone ponies at the gate. We can at least get all of you some decent beds for the night.”

\leavevmode\llap{“}Sounds good to me,” Dazzle replied with a smile.

The motor hummed again as we slowly rattled our way up to the gate, with Hail Burst and Downdraft hovering alongside us, all under the eyes of the guards at the gate.

There must have been at least twenty militia gathered atop the walls and by the gate itself, many half-hidden in the shadows. Rifles were slung in easy reach. Light machine guns rested atop the walls, ready to pour out a hail of fire. In the recesses of the half-collapsed upper floor of some office building, the firelight flickered in a lens, the shadows almost entirely concealing the barrel of a monstrous rifle.

Three ponies stood by the gate itself, clad in the sandy-brown barding of the Mareford Militia. The two flanking the gate gripped the bits of their rifles, holding them ready, while the third stood her ground in the middle of the path, her own rifle slung across her chest. As we drew closer, she held up a hoof. “Hold up there!”

We ground to a halt once more, and she set her hoof down again. “We told you, you’ll have to wait until the mayor is done talking with your boss. Until then, you’re staying outside.”

Dusty placed his forehooves on the roof and pulled himself up so he could be seen. “Hey, Rose. We’re not Trotsen. We’re bringing in representatives from Gemstone and the Enclave Loyalists. They’re looking to join the fight.”

\leavevmode\llap{“}The fight? What—” The mare halted, blinking as she peered out in the dim light. Her voice sounded a little strained as she spoke again. “Dusty Trails?”

His tail flicked beside me. Even when faced with destruction, it seemed we were still wanted. “Yeah, it’s me.”

There was a moment of silence. Dusty didn’t elaborate further, while I wondered if it was the wise choice or a missed opportunity to explain his position. The guard mare, Rose, stood silently for a moment, obviously thinking over the situation. Finally, she took a slow step back and to the side; the adrenaline spiked as I noted it was a move entirely consistent with getting out of the line of fire, until she spoke. “Maybe you’d better come in, then. I think Mayor Hardwood’s going to want to talk with you.”

Dusty’s expression immediately brightened. “Hardwood’s mayor again?”

\leavevmode\llap{“}He is,” she replied, raising a hoof and giving a circular motion. A moment later, the gate groaned and creaked open. “I don’t know if he’ll be so happy to see you, but I expect he wants an explanation. And Dusty? You and yours better be on your best behavior, understand?”

\leavevmode\llap{“}Of course,” Dusty replied, nodding. I resisted the urge to look questioningly at Sickle. She’d just see it as encouragement.

We were waved through the gate. On the other side, a squad of militia ponies waited to escort us through town. I couldn’t blame them for the show of caution, considering we were supposedly wanted ponies with several dozen armed ponies following us, but it didn’t make me feel any more comfortable about the situation.

Even restricted to a walking pace, it took only a couple of minutes to arrive at the town hall. I was pleased to see it was apparently intact, with no signs of fire damage.

Sandstorm was coming out as we pulled up. She was frowning. Not a great sign.

The motorwagon came to a halt, and we dismounted, several dozen ponies climbing down and stretching their legs. I hopped down from the wagon and slipped past the other ponies to approach her. “How’d it go in there?”

She snorted, continuing to walk right past me. “Fucker likes to talk as much as you do.”

I followed along. “Did he agree to help?”

Her tail flicked in irritation. “Only thing he decided was that it was getting late, and we should talk more in the morning.”

\leavevmode\llap{“}And will you?”

\leavevmode\llap{“}Fuck off,” she grumbled, pointedly not looking my way, but following up with, “Yeah, I’ll be there.”

I came to a halt, letting her walk off on her own, and turned to rejoin the rest of my group. A pair of soldiers parted from the others to head inside. Dusty informed me that they had asked us to stay put while they went to see if the mayor would see us.

Echo landed unannounced, drawing several startled reactions from both the Gemstone ponies and the militia soldiers, and neatly tucked her wings in at her side and stood calm and proud, as if nothing was unusual about her abrupt appearance. “Do you suppose they will try to kill us?” she casually asked.

\leavevmode\llap{“}Hah!” was Sickle’s immediate reply as she hopped down from the motorwagon with a solid thump and rattle of armor. “I’d like to see ‘em try. Seriously. I could use a good fight.”

\leavevmode\llap{“}Settle down,” Dusty said, earning a crude gesture from Sickle.

I heard the soft clomping of Hail Burst’s power armor behind me, and turned to see her frown. “I take it there’s a problem with your little army?”

\leavevmode\llap{“}No problem, just a delay,” I said, hoping it was true. “It’s a bit late for a big meeting.”

She gave a quiet snort. “It’s a waste of time. It isn’t like our enemies just stop as soon as night falls.”

\leavevmode\llap{“}He’s a mayor,” I said, “not a general. I imagine he’s used to a more civilian schedule.”

\leavevmode\llap{“}Hopefully whoever leads the ‘soldiers’ around here is a little more disciplined.”

\leavevmode\llap{“}They are,” Dusty replied.

It was a couple of minutes before the soldiers returned. The stallion leading them approached us and spoke up clearly for everyone to hear. “Dusty Trails. Hardwood will see you and your companions. As for the rest of you, there will be a meeting in the morning at oh-eight-hundred—eight o’clock—to discuss possible arrangements. Until then: Gemstone ponies, that building across the way—” He lifted a hoof to point to an old and mostly-intact apartment building. “—serves as a shelter and inn. There should be enough room for all of you. As for the rest, we have to ask that all military forces remain outside of the city until an agreement has been reached.”

\leavevmode\llap{“}Wonderful,” Hail Burst grumbled, while the Gemstone ponies started unloading their gear.

Starlight called out to the soldiers. “Uh, can you guys watch over our wagon while we’re in there? We don’t want anypony stealing it.”

The soldier in charge eyed her, but said, “Yeah, we’ll keep an eye on it.”

We parted ways. Hail Burst and Downdraft took off to return to their camp, while Dazzle and the other Gemstone ponies made their way to their accommodations. As for Dusty and the rest of us, we entered the impressive town hall building, escorted by a squad of soldiers.

I would say it seemed excessive, but the barrel of Sickle’s heavy machine gun was bobbing right next to my head as we walked, and a living pseudo-goddess followed close on my flanks. If anything, it was insufficient.

I hoped these soldiers hadn’t come to the same conclusion. It would be an unnerving recognition, and fearful ponies are dangerous ponies.

There were some distinctly uncomfortable looks from the few ponies in the lobby as we entered. They certainly had good reason to be concerned. It was distinctly unusual, enough that I had to consider the implications. If they considered us a threat, allowing us all to enter a room with their mayor would be a significant risk. Either they were making a risky decision, or one of those two conditions weren’t true.

Which meant either that they were leading us somewhere \textit{else}, or whoever was in charge didn’t think we were a risk.

So it was just a little reassuring when they led us up the stairs and down the hall to the same office I remembered from my previous visits.

What was much less reassuring was the signs of recent repairs: small patches of plaster on the walls, consistent with patched bullet holes, fresh chips and gouges in the banister, and a few places where no amount of cleaning had been able to remove the bloodstains.

A new pony sat behind the large desk where I had once seen Big Gun. He was just as old, though a bit rounder and softer in appearance. He sat back in his chair as we entered, eying us carefully, though his expression struck me as less critical, more concerned.

Dusty naturally took a place at the front of us, giving a deferential nod to the mayor. “Hardwood.”

\leavevmode\llap{“}Dusty,” Hardwood replied, his voice soft and tired. He remained silent for a couple of seconds before sighing, slowly leaning forward to rest his forelegs on his desk. “Been a lot of strange stories turning up, lately. If you’d shown up a month ago, you’d be telling me your story in cuffs. But now… ever since Gun died, things have been turned upside down. Ponies keep turning up more shady shit he might have been involved in, Silverline’s been up in arms about him murdering her husband and how you were framed, hell, I’ve got a herd of zebras that showed up out of nowhere singing your praises. Then we’ve got Militia soldiers trying to stage a coup—” Dusty’s ears perked in alarm. “—Gun’s mercs turning bandit, all this nonsense about these so-called ‘changelings’. Now you show up in the middle of it all, and…” He drew to a halt, silent for a moment before slowly shaking his head. “Hell. What’s going on, Dusty? What happened to you? I knew you. You were a Ranger. I have a hard time buying that you’d turn on your own, but we had a bunch of dead ponies and no answers. Just for once, I want a simple, no brahminshit story.”

\leavevmode\llap{“}Simple story?” Dusty said. “Okay. I didn’t turn on them. They turned on us. They set an ambush for us, tried to kill us, all on Big Gun’s orders. He’s the one that set those raiders on the water caravan, and we knew. He wanted to silence us for good.”

Hardwood was slowly shaking his head, only to be interrupted at the soft thump of a small notebook landing atop his desk. Both he and Dusty looked back to me as I rebuckled the flap of my saddlebag. “The notebook belonged to a raider boss named Gutrip,” I said. “He’s the one who led the attack on the caravan, and took Silverline and Quicksilver. Check the last page. They were told exactly where the caravan would be, and more significantly, that the guards would leave them unprotected there.”

Hardwood reached out, taking the dingy notebook, and slowly flipped through the pages until he reached the end. He stared at it long and hard, without visible reaction, before finally giving a slow, long sigh and setting it down. “I heard some traders saying the same thing. Hell, I wanted to believe you, but it just seemed so absurd to believe that some of the Militia—some of the Rangers, even!—would be involved in something so… so…” He raised a hoof, giving a weak gesture as he tried to come up with the right word, and finally gave up. “Then some of the Militia officers, ponies I’d known for years, tried to take over.”

Dusty stepped in close to the desk. “What happened?”

\leavevmode\llap{“}The day after Big Gun and Wild Runner were murdered, it was chaos. Ponies were scared, and even more so when they looked through some of Big Gun’s records. Some of the staff asked me to come in and help out, just to reassure ponies until we figured out what happened and had a new mayor elected.” He shook his head again. “I was here when some Rangers and Big Gun’s mercs came in, said they were taking charge until things settled down. We all said we had it handled, and then they tried to arrest us all, saying we’d murdered Gun and Runner. Guess they must have expected the rest of the Militia to go along with it, but the ponies standing guard there refused. Next thing I know, everyone’s shooting.

\leavevmode\llap{“}I spent four hours, bleeding from the leg, while Rambler held me and the others at gunpoint. Rambler! I shared drinks with him every month! I’d been friends with his wife since we could hardly walk! I’d helped take care of his kids! And he was holding a gun on me, ready to kill me like he’d killed Marionberry.” He was trembling faintly, and he took a moment to draw a deep breath, calming down.

Dusty’s ears flicked back. “They killed ponies?”

\leavevmode\llap{“}Some,” Hardwood said, his voice quiet. “She tried to run when they herded us into the office. Only one of the soldiers guarding the place lived, and she lost a hoof. A Ranger died when they stormed the place, too.” He gave a quiet sigh. “It was a bad day.”

Dusty murmured something quietly, slowly shaking his head.

Hardwood looked up again. “So they turned on you?”

\leavevmode\llap{“}They did.”

Hardwood stared for a moment before slowly nodding. His eyes slowly drifted away, looking over the rest of us. “Interesting company you keep these days.”

\leavevmode\llap{“}It’s been an interesting couple of months,” Dusty replied. “You know why we’re here.”

\leavevmode\llap{“}Yes,” Hardwood said with a tired sigh. “The supposed ‘changelings’.”

\leavevmode\llap{“}There’s nothing supposed about them,” Dusty said. “I’ve seen them.”

Hardwood raised an eyebrow. “You have?”

\leavevmode\llap{“}Yes, sir.”

Another short pause. “And how bad is it?”

\leavevmode\llap{“}To be blunt? They scare the shit out of me.”

Hardwood fell silent again, thinking for a good while before finally shaking his head once more. “This whole thing is a mess. Has been for months.” He slowly slipped out of his chair, walking around the desk with a pronounced limp. He came to a halt in front of Dusty, and raised a hoof.

Dusty lifted his own hoof, and they shook.

\leavevmode\llap{“}I never really bought what they said,” Hardwood said. “I know some called you a traitor for leaving, but I know why you left, and it just doesn’t jive with you being some murderer. I knew there had to be more to it.” He lowered his hoof again, looking past Dusty to one of the nearby soldiers. “They’re free to go.”

The soldier nodded.

\leavevmode\llap{“}Thank you,” Dusty said, and Hardwood gave a weak smile, nodding in reply.

\leavevmode\llap{“}I get the feeling it’s going to be more chaos heaped on all the crap we’ve already got, but it’s good to see you again, Dusty. I… also want to hear all the details of what happened. There’s still a lot of unanswered questions.” He groaned slightly as he leaned against the table, taking some weight off one of his rear legs. “But that can wait for tomorrow. It’s too late to be getting into all of that.”

\leavevmode\llap{“}Of course,” Dusty said, offering a smile. “We’ll talk in the morning?”

\leavevmode\llap{“}If I have any time with all the other talking I’m going to be doing,” Hardwood said, weakly mirroring the smile, though it quickly faded.

\leavevmode\llap{“}Well, we’ll get out of your mane, then. Goodnight, Hardwood.”

Hardwood nodded, and Dusty turned, heading for the door. We followed, while the soldiers slowly dispersed as word was passed, casting only a couple of wary glances our way. The four watching over our motorwagon were a bit more wary, but another soldier came trotting up, passing on the news, and they let us pass.

Starlight parked the motorwagon beside the makeshift inn, and we made our way in. Dusty handled getting the rooms, but was otherwise tight-lipped.

He remained so until we had gone upstairs to a vacant common room, with the doors into our rooms, and well away from any prying ears.

\leavevmode\llap{“}A coup,” Dusty said as we came to a halt by one of the room's doors. “Shit like that’s exactly what I was worried would happen if Big Gun was killed. A bunch of ponies \textit{died} because of it.”

I gave a quiet sigh. “I know.”

\leavevmode\llap{“}Yeah, you know,” he grumbled.

\leavevmode\llap{“}I know it’s not always the most persuasive of arguments,” I said, “but it’s likely it saved far more ponies.”

He snorted irritably.

\leavevmode\llap{“}I don’t like what happened, either,” I said, stepping forward to look him a little more squarely in the face. “I don’t like people dying as a result of my actions, but I still think we made the right call in a difficult situation.”

\leavevmode\llap{“}Oh, shut up,” he grumbled. “I don’t care. Fuck, I’m not even disagreeing with you. I’m just pissed.” He waved a hoof off to the side. “That’s your room.” Then he walked across the common room to another door.

I frowned, contemplating whether I should say more, but decided against it. These events were a little close to home for him, even in a more literal sense. I figured he could use some time alone.

Though with the way Sickle followed him, I doubt she intended to give him that opportunity.

Instead, I turned, entering the room Starlight and I would share for the night.

{\br}%
I woke at exactly six, having made use of the PipBuck’s alarm-clock function for the first time since I had acquired it.

I stretched, rose, and took care of the usual morning prep. Dusty was waiting in the common room, with a couple plates loaded with cooked antique boxed mush. He gave a little nod to us and gestured to the plate he wasn’t eating from, which seemed to say to me that he didn’t particularly want to talk, but wasn’t holding a grudge.

We settled in to our mediocre breakfast, joined several minutes later by a very lethargic and possibly hungover Sickle. She flopped noisily onto a couch that was a little too small for her, and sprawled out on her back with a quiet groan.

When he finished eating, Dusty started bringing out all his weapons, unloading and stripping them down. “There’s going to be fighting, soon,” he said quietly, not looking up from his rifle as he removed the bolt. “You should tend to your weapons. You too, Sickle.”

She grumbled something unintelligible, and didn’t budge.

As for myself, I agreed with Dusty, and started pulling out my own weapons.

Starlight sat beside me. “Guess I should maintain my weapons, too.” She then sat there silently for a second. “Oh, look, I’m done.”

Dusty snorted softly. “Magical energy weapons need maintenance, too.”

\leavevmode\llap{“}Sure,” Starlight said. “Keep the dirt out of the case, make sure things don’t get knocked out of alignment, maybe clean the lens. It takes a couple of seconds, tops.”

\leavevmode\llap{“}Well, if you’re not cleaning your weapons, how about you help Echo looking over the motorwagon. We drove it pretty hard, I’d rather not have it break down to something we could catch early.”

Starlight’s expression brightened. “Okay, that sounds more like it.” She quickly snatched up her saddlebags. “Don’t take too long!” she called out as she trotted off down the stairs.

\leavevmode\llap{“}Guess that answers where Echo is,” I said as I opened up my rifle, while hoping the offer of casual conversation might break the ice.

To my relief, Dusty took the offered gesture. “She’s been anxious about it being left alone,” he said, though his attention was focused on the bolt of his rifle. “Something about all that advanced pre-war tech just lying out there in the open.”

\leavevmode\llap{“}I suppose that makes sense,” I said, then paused as a thought occurred to me. “Shouldn’t that be wartime tech, though?”

Dusty looked up, blinking in surprise as he thought on that. “Huh. Everypony says pre-war, but I guess most of this stuff isn’t from \textit{before} the war. Never really thought of it before. I wonder why that is.”

\leavevmode\llap{“}I guess because it’s less of a mouthful than ‘pre-megaspell-apocalypse’,” I offered, and he snorted in amusement.

He fell into silence again, but I was satisfied that things were good between us. Being an experienced soldier, I imagine he might be familiar with the idea of even good decisions having hard costs. I know the idea of a commander making a decision that will kill some of his soldiers in order to save far more is a common cliche, but it’s one that always struck me as having a solid basis in fact.

After a moment, he addressed Sickle again. “Seriously, though, you should look over your weapon. It won’t take long.”

She groaned a little louder, a hind-leg lazily kicking in the air. “Fuuu… It’s too goddesses-fucking early for that shit.” She cracked a smile, lazily flopping a forehoof across her crotch. “Tell you what: you come over here and fuck me ‘till I’m good and awake.”

He rolled his eyes, returning to his weapons. “Not happening.”

\leavevmode\llap{“}Aww,” Sickle said in mock disappointment. “That’s not what you said last night.”

Dusty’s jaw tensed, but he didn’t reply.

As we lapsed into silence, I focused on the task at hoof. For a relatively mundane task, there was something satisfying about working on that rifle. It was an intricate and complicated machine, where so many parts worked together to produce a single result. It wasn’t quite as satisfying as coding, but there was certainly a degree of puzzle-ness to the procedure.

The similarity kind of fell apart when I pulled the pin from the bolt and started brushing it clean. Carbon build-up is hard to map to a coding analogy, though I did crack a smile when I considered that perhaps my rifle just had horrible memory management.

I had just started reassembling the bolt group when Starlight returned, walking up to where I sat. “Hey, Whisper?”

The firing pin slid neatly through the bolt, holding the rotating cam in place, and I carefully picked up the retaining pin; it was a bit awkward with just my mouth and hooves to work with, but having an earth pony as my standard disguise had given me enough practice to manage it. “Hmm?”

\leavevmode\llap{“}Yeah, I just thought of something I should probably ask you about,” she said. There was a pause while I slid the retaining pin into place and gave a gentle tug on the rear of the firing pin to confirm it. Then Starlight spoke again. “Um… in private?”

I looked up to see her awkward half-smile.

Before I could say anything, Sickle chuckled. “Soooomepony’s getting their morning fucks.”

I sighed, but didn’t bother shooting her an irritated glance. She’d just find it amusing. Starlight didn’t, either, though her ears flicked back for a moment. “Sure,” I said, looking at the reassembled bolt. It’d take only a couple of seconds to put it back in and close up the rifle, but I still hadn’t gone over the barrel or gas system. “Dusty, could you watch my stuff?”

\leavevmode\llap{“}Of course,” he said, in the midst of checking over his magazines.

\leavevmode\llap{“}Thanks,” I said, setting the bolt assembly down and rising to my hooves. Sickle just lay there, watching us as we left.

Starlight followed me into the room. She looked concerned, and absently left the door open as she entered. I stepped back, shutting it behind her.

Outside, I heard Sickle finally getting up, her armored hooves thumping heavily on the floor.

Now, I’m going to have to digress slightly.

People have a certain psychological need for control in their lives. It can manifest in all manner of strange and even unforeseen ways, but it’s there.

This is a danger to Infiltrators for two reasons.

First, we have to recognize that there are many situations where we do \textit{not} have control. We might be able to stack the odds more in our favor, but in the end, our fate is often completely out of our hooves. A mistake by someone else, compromised information networks, even completely baseless or unreasonable assumptions made by someone else might lead to an Infiltrator’s capture or death. Recognizing that lack of control can be terrifying, and it’s one of the hardest things that an Infiltrator must overcome.

But equally dangerous are the situations where we \textit{do} have control. When you act in secrecy, arranging things behind the scenes, there are times when you set something in motion that your target, whether a person or an organization, has absolutely no chance to prevent. A good scheme, properly executed, is like a work of art. It’s a remarkably pleasant sensation, that feeling of power, where for a fleeting moment, you’re the one pulling the strings. For that moment, you hold the fate of a project, a life, a country, in your hooves.

In a life where we normally have so little control over our fate, there is a natural desire to hang onto that fleeting sensation for as long as possible. To drag it out just a little bit, to savor the feeling. To show your target that, for just that moment, you have absolute power over them. It’s one of the psychological factors addressed in our training. No matter how tempting or satisfying it is, a good Infiltrator can’t indulge in such dangerous pleasures. A good Infiltrator doesn’t taunt their defeated foe. They don’t give clever one-liners. They don’t monologue and explain their masterstroke like some Con Mane or Daring Do villain.

A good Infiltrator lures their target into a false sense of security, and then shoots them in the back without a word.

I never heard the shot.