It took all of two hours for things to go wrong.

The first sign was when the Loyalists abruptly changed formation. Half the pegasi flying at our flanks ascended and spread out before us, while the others adjusted to fill in the gaps. Hail Burst remained low with a couple of other Loyalists. Judging by their hoof gestures, they were having an urgent and animated conversation.

Dusty caught on right away, and leaned out of the window to shout up. “Hail Burst! What’s going on?”

Her head twitched his way as if she heard, but then ignored him.

It was then that I caught a dot of darkness on the horizon, just peeking up from behind the low hills in the distance.

I turned to retrieve my binoculars, tucked into the bags I had stashed beside me. By the time I found them, the black dot on the horizon had grown and ascended, like a dark cloud rising over the Wasteland. It must have been ten miles or more away, judging by the hills, yet it was still clearly visible. Calls and shouts started to rise from other ponies as they spotted it, and I raised my binoculars, fearing the worst.

Now, what I had expected to find would have been scary, but in retrospect, it might have been a good thing. I had \textit{expected} to see a swarm of changelings, loaded with magical energy weapons and clad in power armor. I’m not an expert on tactics, so I didn’t have the knowledge to weigh the costs and benefits of launching a massive assault on our concentrated army, rather than any number of defensive tactics. All I knew was that a swarm of changelings that large would mean a huge fight was minutes away.

But when I focused on the dot, I didn’t see changelings. I saw angular shapes. I saw the slowly swirling form of dark clouds, laced with lighting. I saw a single long word spelled out in white paint.

\leavevmode\llap{“}Dusty,” I said, trying to keep my voice even. In the periphery of my vision, I saw his head turn to me, but I remained focused down my binoculars. “It’s the \textit{Cumulonimbus}.”

They’d gotten the Raptor flying again. We’d been too slow to stop them.

Dusty hurriedly fetched his own binoculars, taking a moment to confirm before turning and shouting. “Bitsy!”

\leavevmode\llap{“}Woah,” Bloodbeak said, having leveled a third set of binoculars at the distant cloudship. “What is \textit{that?}”

\leavevmode\llap{“}A cloudship,” I quietly replied. More shouts were going out. I heard ponies trotting and galloping around, but I kept my eyes fixed on the distant Raptor. “Why is it heading away from us?”

\leavevmode\llap{“}What?” Dusty raised his binoculars, watching for a moment before saying, “That’s more perpendicular to us than away.”

\leavevmode\llap{“}Yeah, but it’s not flying \textit{towards} us,” I said.

\leavevmode\llap{“}Might be trying to circle around behind us.” Dusty said, sweeping his binoculars along ahead of the Raptor. “Or maybe they just want to get altitude before getting close. Other than the Loyalists, we don’t have much that can reach altitude. Maybe Gemstone’s cannons. I doubt the tank can elevate that much.”

\leavevmode\llap{“}That thing’s \textit{huge},” Bloodbeak said. “And it flies. That’s kinda awesome.” She paused, then asked, “That’s the other changelings?”

I lowered my binoculars. “Yeah.” Despite all of the eager chatting, it was the first time Bloodbeak had even acknowledged the existence of changelings, even while speaking to me.

The Militia ponies were still spreading out, the closest ones already taking what cover could be found in the rough, rolling terrain, while those further back were still trotting into position. Two Bits was up front, shouting at Sandstorm as her tank and motorwagons continued rolling along.

\leavevmode\llap{“}Damnit,” Dusty grumbled. “Starlight, take us up to Sandstorm, I need to yell at her to stay put.”

\leavevmode\llap{“}You got it,” Starlight replied, and we started picking up speed. By the time we got there, she and Two Bits were already arguing about whether they should be stopping or not. Dusty started adding his own contribution to the argument. It didn’t take them too long to convince Sandstorm to halt, and the next few minutes were spent arranging everypony. I didn’t see much of the tactical arrangements, mostly noting that ponies were spreading out widely enough that a blast from one of the Raptor’s weapons couldn’t hit multiple ponies. Mostly, my attention was focused on the Raptor, waiting for that inevitable moment when it turned towards us.

It didn’t. It just kept flying straight.

Mile after mile, minute by minute, it continued on its course, as if unconcerned by our presence. While everypony settled into their positions and waited, we fell further and further behind it.

\leavevmode\llap{“}Well this is a fucking waste of time,” Sandstorm said several minutes later. She stood atop the turret of her tank, and banged a hoof against the roof. “Fire it up! We’re moving.”

\leavevmode\llap{“}Crap,” Two Bits grunted, then turned, walking back from us as he spoke into his broadcaster. “All units…”

As he started giving directions to his subordinates, Dusty raised his binoculars again, looking at the receding Raptor once more as he quietly murmured. “Where are you going?”

\leavevmode\llap{“}They couldn’t have missed us,” I said, also watching. “Not with all the dust the scout wagons were kicking up. Besides, they have to still have some agents tracking our progress. There’s no way they all returned home after the first attack.”

Dusty gave a tiny nod. “And if this was a diversionary tactic, they would have hit us with their maneuver force already. It’s got some destination in mind.” He glanced down at his PipBuck, then returned to the binoculars. “It’s not heading to their hive. That’s northwest and it’s heading south.”

I lowered my binoculars. “What’s south?”

Dusty was frowning. “A whole lot of nothing, mostly.” He watched in silence for a few more seconds before lowering the binoculars and returning to his map. “...No, Gemstone is well east of its path.”

Starlight pulled herself up to sit on the edge of her side window, pushing up her goggles to look back at us. “Well they’ve got to be going somewhere. What else is south?”

\leavevmode\llap{“}Nothing,” Dusty said. “There’s World’s End, but that’s all the way across The Pale, and I doubt they’re going there anyway.” His ears flicked as a thought occurred to him, and he looked over to me. “You don’t think they’re going to your hive?”

I grimaced, but quickly shook off the feeling. “I don’t like the idea of them rooting around there, but I can’t imagine them finding anything useful. It’d be a waste of time that we can use to our advantage.” Still, I frowned. “They might have pulled the location from Starlight’s PipBuck, but it has a good century’s worth of location tags, and shouldn’t have any identifying information for the hive. They might have taken a guess at what the location was, but… that seems like a lot of resources dedicated to a guess, especially when they know an army is coming for them.”

Dusty grunted and gave a flash of a frown, but I suspect he had been thinking the same thing.“Yeah, even if they did know what’s there, it’s a big gamble. We might even make the hive before it could get back. I can’t see what else they’d be doing. There’s nothing in World’s End they’d want.” He paused, ears perking slightly. “Though it’s kind of a refuge for ponies trying to get away. Maybe they’ve had another changeling go rogue? Still seems like overkill to send a Raptor for what a half dozen soldiers in power armor could do.”

A moment of silence followed as we all thought it over, until Starlight’s head came up, her ears perked high. “Oh shit.”

Dusty and I both turned questioning looks to her as she looked back. “What about Pale Sands? Ponytown?”

There was a moment of confusion before my heart dropped. Dusty’s eyes widened, and a moment later he was pulling himself up out of his window, shouting back at full volume. “Bitsy! We might have a problem!”

{\br}%
Fifteen minutes later, we were speeding across the barren landscape, pushing our motorwagon to its limits. All around us, a dozen of Trotsen’s lightest and fastest motorwagons bounced and weaved in a loose pack. Most of the extra Trotsen ponies had been left behind to lighten their loads, leaving just the vehicle’s crews and a few of the more experienced riders. Two of the wagons were now adorned with hastily lashed-down and bolted-on energy cannons, courtesy of Gemstone. Dazzle and a few of the other Gemstone ponies were riding along with them.

Overhead, the Loyalist forces flew in pace with us in full force. The whirligigs were there, too. A few of their Ranger passengers were visible, sitting at the sides of the passenger cabin, hooves and weapon muzzles hanging over the edge. Two Bits was in the lead whirligig, having left the commander of one of the Militia units in charge of the main force.

Splitting our forces seemed like a bad choice, but Dusty and Two Bits had decided it was the lesser of two bad options.

I clung to my seat, having returned to my natural form for my own safety. I might have been in much better condition than the previous day, but the ride was hard and rough, and I grit my teeth a few times as one of the many jolts and shudders sent a twinge of pain through my side. I wasn’t enjoying it nearly as much as I had our last outing, nor as much as Bloodbeak or Sickle enjoyed this one. Bloodbeak looked thrilled, standing up and bracing against the edge of the roof to catch more of the rushing wind, even when some of the bumps and dips sent her staggering. Sickle, on the other hoof, had a dangerous-looking grin that said she was looking forward to enjoying what came after the drive just as much.

I glanced back, checking on our equipment once more. We’d recovered most of our gear, mostly the weapons and explosives, but I wasn’t really concerned about those. I was more focused on the armored case secured just behind my seat, and the three balefire eggs contained within it.

If Serenity was going to play with balefire, we’d play with balefire.

My earbud crackled, followed by Hail Burst’s voice. “Okay, listen up everypony. The motorwagons are going faster than the \textit{‘Nimbus}, but you’re losing ground fighting terrain. You might be able to catch up in Pale Sands, but it’ll have a good head start.

\leavevmode\llap{“}Good news is, my scouts got good eyes on her. The bugs might have gotten her up and flying, but she’s hurting. She’s missing more than half her engines and turrets. I doubt she can manage any faster than she’s pulling right now. The hangar still looks wrecked, so they won’t be launching any heavy equipment.

\leavevmode\llap{“}Bad news is, looks like they relocated some of the functioning turrets, so there’s no obvious unguarded approach. Boarding would be suicidal unless we take out some of those guns, and even then, we don’t know how many bugs they’ve got packed in there. All we know is they have enough to send a patrol out to chase off our scouts, but they turned back maybe a quarter mile out.”

Dusty pressed the transmit button on his own broadcaster. “I know you’d like to recover your ship, and hell, I’d love having that much firepower at our back, but—”

I pressed the button on my own broadcaster. “I hate to interrupt, but I want everyone to remember that we’re broadcasting in the clear, and every single Serenity changeling has a PipBuck. Expect them to hear everything we say on the radio. We need information security. All planning needs to be done face-to-face, and none of the details ever go out over the radio.”

\leavevmode\llap{“}Figures,” Hail Burst said with a sigh. “I’ll be down in a sec.”

\leavevmode\llap{“}Me too,” came Two Bit’s reply. “Find some place to stop and Vulture will drop me off.”

\leavevmode\llap{“}That’ll take too long,” Hail Burst said. “Have them fly you nearby, I’ll have one of my soldiers transfer you.”

The earpiece crackled again, filling with the sound of rushing wind. “Hello? Is this device functioning?”

Dusty pressed the button again. “We can hear you, Echo.”

\leavevmode\llap{“}Excellent.” She was flying above us, and was now descending to join in the meeting. “Do not worry about carrying him. Simply bring him nearby, and I shall do the rest.”

Hail Burst snorted softly as she keyed in again. “Fine, whatever. Just get down there.”

Within moments, Echo and Hail Burst had drawn even with us, flying alongside our bouncing and rattling wagon. The larger of the two whirligigs, Vulture, descended a bit more slowly. The Rangers at the edge of the passenger compartment moved aside, clearing the way for Two Bits to lean out, looking down at us.

There was a purple flash, and he vanished, appearing in the cargo bed with a shout and flailing of limbs. He ended up on his back, blinking up at me as I leaned over the back of my seat. “...Holy \textit{shit} that was weird.”

He sat up, seemingly unconcerned by the buffeting of the rough ride.

\leavevmode\llap{“}Neat trick,” Hail Burst called out, shouting over the roar and rattle of our vehicle. “So what was that you were going to say, Dusty?”

He climbed back through the passenger cabin, squeezing past me to slip into the cargo bed. After a quick nod to Two Bits, he looked over to Hail Burst and shouted back, “I’d love to take the ship, but the megaspell comes first! If we can take it, great! If not, we just get close enough to hit them with the B.E.L. We’ve got three eggs, that should take out one of those clouds!”

\leavevmode\llap{“}The \textit{‘Nimbus} is tough!” Hail Burst shouted back. “They fixed her up after she fell out of the sky. We either take her, or I’m using those eggs to scuttle her. Either way, we need to get on that ship!”

Dusty shouted back. “That’s great, but how are you getting past the turrets?”

Echo’s voice boomed out, loud and clear even over all the sound. “You are all thinking far too linearly. The turrets can only attack when you are in the space \textit{around} the ship, but thanks to my talents, you need not traverse that space to arrive \textit{on} the ship.”

Two Bit’s looked stunned by the revelation. “Holy shit. How many ponies can you teleport like that? And how far?”

Her booming voice sounded surprisingly casual. “A half dozen should be no difficulty, and I can do so from much further away than they could hit a maneuvering, pony-sized target.”

Hail Burst seemed less optimistic. “How safe is it?”

\leavevmode\llap{“}Perfectly safe,” Echo replied. “If these changelings have not rearranged the interior of the ship, I am sure you can direct me to some location that should be open. The spell also has a certain degree of safety measures incorporated into it, such that it will attempt to locate an individual into an open space rather than, say, intersecting a wall. So long as the base magical throughput of the caster exceeds the resistance of the displacement, which is the distance squared times the coefficient—”

Dusty cut her off. “Safety measures, got it! Good!”

\leavevmode\llap{“}No, not good!” Hail Burst shot back. “I’m not going to have one of my soldiers teleported into a wall!”

\leavevmode\llap{“}There is little risk of that!” Echo replied. “Besides, if their initial destination were to intersect a wall and the magical throughput is insufficient to reach an open space, it will still likely be enough to teleport out the obstructing material and leave the individual unharmed.”

\leavevmode\llap{“}\textit{Likely?}” Hail Burst shouted back, and Dusty quickly stepped in again.

\leavevmode\llap{“}Settle down! Let’s avoid blind teleports! Hail Burst, the \textit{Cumulonimbus} took a lot of damage, and with half the turrets, I’m guessing it doesn’t have perfect coverage close-in. Is there some place she could teleport a team onto the hull or into an opening without being exposed to the turrets?”

She looked off after the distant cloudship. “Maybe. I’ll have to scout it out. Maybe the hangar section.”

\leavevmode\llap{“}Good! Then I’m thinking that should be our plan. Ground forces to draw away and distract as many defenders as possible, while the Loyalists and Rangers teleport in, try to take the ship, or demo it if there’s too much opposition. Sound good?”

Hail Burst gave a nod before shouting back. “Yeah, that’ll work.”

\leavevmode\llap{“}I like it,” Two Bits said. “That’s a hell of a nice mobility option. I’d prefer to get some training in to practice it, but we’re a bit tight on time. Let’s do it.”

\leavevmode\llap{“}All right,” Hail Burst called out. “Give me that case.”

Sickle hauled up the armored case of balefire eggs, and Hail Burst swooped in, grabbing hold. “Okay. I’m heading up and briefing my ponies.”

As she ascended, Two Bits turned to Dusty, smiling. “It’s damn good to have you back, Dusty.”

\leavevmode\llap{“}Thanks,” Dusty said, smiling, though the expression slipped a moment later, his ears flicking back. “Sorry. I hope I wasn’t stepping on your hooves there. Been too long since I was in the Militia. Got used to being the one that has to call the shots.”

\leavevmode\llap{“}Shit, step on them,” Two Bits said with a dry laugh. “I’m feeling a little in over my head. I could use the help, and she seems more ready to listen to you than me.”

Dusty gave a soft chuckle. “I don’t know about that, but yeah, if you need any help, I’ll be here.”

\leavevmode\llap{“}Thanks.” He pushed himself up, rocking with the motions of the vehicle, and looked to me. “Small again?”

I reached up, tapping a hoof against the roof just an inch above my horn. “It’d be a little cramped. Plus I don’t have any armor that fits me when I’m big, and… well, I kind of make a big target like that.”

\leavevmode\llap{“}Fair enough,” he said with a nod. Then he took a deep breath and turned to Echo. “Can you get me back on Vulture?”

\leavevmode\llap{“}Of course,” Echo replied, and with a sudden flash of purple, he was gone.

\leavevmode\llap{“}Now we’ve just got to find us the fastest route south,” Dusty said as he settled back into his seat, already consulting his PipBuck’s map. “Starlight, in about a mile, there’ll be a saddle—a low pass—between the hills on our right. Go through there, then head due south again.”

\leavevmode\llap{“}You got it,” Starlight replied.

We continued on, skirting a line of rough, rocky hills. I raised my head again to look off to the south, past them. The \textit{Cumulonimbus} was even further away.

A minute or two later, Starlight turned, the motorwagon rocking and rattling as we aimed for the low-ground between a pair of hills. The motor strained, propelling us up the short slope at a breakneck pace, the Trotsen wagons turning to follow us.

We came over the ridge at full speed, and my stomach lurched as the wheels left the ground. For a split second, we were weightless, and I floated up from my seat until I hit the bare metal roof. A moment later the vehicle crashed down, and gravity reasserted itself, throwing me back into the poorly cushioned seat, a sharp stab of pain shooting through my side.

The loud smashing of metal-on-metal announced Sickle’s near-simultaneous landing just behind me. “Motherfucker!”

\leavevmode\llap{“}Sorry!” Starlight called back.

Bloodbeak was laughing and cheering, too preoccupied to notice my condition. I was possibly a little unfair in taking note of that.

I gathered myself up, wincing softly as I sprawled out on the seat, and braced my hooves against the interior of the wagon. It wasn’t the most comfortable of positions, but I’d had enough impromptu flight lessons for the day.

Starlight spared a momentary glance back at me before turning back to her driving. “You okay?”

\leavevmode\llap{“}I’ve had worse,” I said, in a tone rather more grumbling than I had intended. “I’m fine.”

She cast another glance back, but said nothing, focusing instead on her driving.

Between the front seats, past the sloping hood of our motorwagon, the distant cloudship was dead ahead.

We sped on.

{\br}%
I had never felt so beat down and exhausted from lying in one place.

The pace was brutal as our wagon tore across the rugged, uneven terrain, throwing us back and forth, up and down. Despite my chitin and armor, I still felt bruised and battered by the experience. The ride was violent enough that I soon found a slowly rising sense of nausea, and had to focus on the horizon ahead to fight it off. Everything was caked in dirt. Dusty vocally worried about damaging our vehicle by the pace, and just an hour in, one of the Trotsen motorwagons swerved and threw up a tremendous plume of dirt as it skidded to a stop, one of its wheels broken.

We couldn’t wait for them. Every second counted in this race. They were left behind to fix their wagon on their own.

Even our return to Pale Sands and its relatively smooth terrain only did so much to alleviate the punishing ride, though I was finally able to sit upright. The pain had faded once more, lingering in the background.

The \textit{Cumulonimbus} had slowly, inexorably drawn further away from us in the rough and rugged Wasteland, but as we blew past the downed chain-link fence marking the edge of the Pale Sands Spell Range, there was only smooth, open ground between us and Ponytown. Motorwagons strained and roared across the broad land, throwing up trails of dust in our wake, and the cloudship’s lead started to ebb. Mile by mile, we drew closer. The black, angular form and lightning-laced clouds slowly and steadily grew.

After an hour of that breakneck pace, an unpleasant conclusion became clear: we weren’t fast enough.

\leavevmode\llap{“}We’re out of time,” Hail Burst called over the radio. “Enclave, advance in line! Echo, get up here with us. You ground-pounders catch up as soon as you can!”

\leavevmode\llap{“}Damnit,” Dusty grumbled before hitting his transmit button. “Be careful. Remember our priorities here!”

\leavevmode\llap{“}Yeah, we got it.”

Two Bits called in next. “Air, follow the Loyalists in. Hold short and maintain two miles distance from the Raptor.”

I leaned over to the side window to peer up. Pegasi were beating their wings faster, surging ahead in a loose formation. Echo was climbing to join them, while the whirligigs followed in their wake.

Ahead of us, I could just make out the distant, bright shapes of buildings, still many miles away.

One of the Trotsen motorwagons veered and pulled up beside us. Axle was in the back, rising up over the spiked and armored side to shout at us. “Where the fuck are they going?”

Dusty poked his head out of the window. “They’re moving in to harass the Raptor and buy us time. We’re making a beeline for the megaspell tower. It’s about a mile east of the town itself. We either get there before the Serenity changelings do and fight them off, or we get close enough to blow it!”

\leavevmode\llap{“}Blow it?” Axle shot back, his expression clearly stating how insane he thought Dusty was. “You want us to blow a fucking \textit{megaspell?}”

Dusty shouted back. “If it comes down to it, yes! We can either blow it here or wait to see whose town they drop it on!”

Axle stared for a few seconds before shouting back a rather succinct conclusion. “...Fuck!” Then he ducked down, shouting commands to the driver.

Dusty returned to his seat, giving Starlight some quick directions to skirt the left side of the upcoming town before turning back to me. “You good to take the gun?”

As much as I would have rather remained sitting, I nodded. “I can do that.”

\leavevmode\llap{“}Hopefully you won’t have to do much,” he said. “We’re basically the command and communications element for the ground forces. Once a fight’s coming, I want us behind the front line so we can keep an eye on everything and get orders where they need to go. Your job is local security. If any fliers get past the formation, you and Sickle keep them off us.”

\leavevmode\llap{“}About fucking time to put this thing to use,” Sickle rumbled, rolling over to rise to her hooves.

I gingerly climbed out over the back seat, rising up to brace my fore-hooves beside the gun. We hit a small bump, and I lurched, but kept my balance. I felt like a hard bump would knock me over, or even throw me from the vehicle, but at least standing on my hooves gave me a tiny bit of cushioning against the impact.

I looked out past the gun. The \textit{Cumulonimbus} was still several miles away, but the black, cloud-clad form looked terrible and imposing. The receding line of pegasi already seemed so small in comparison, like mosquitoes approaching a dragon.

It was about then that the distant sound started to rise over the roar of the motor and the creaking of the frame. The tone rose from the background, half hidden behind the noise, but soon becoming clear enough; the air-raid siren near Ponytown had started up once more.

A flash of light drew my attention upwards once more, and it was with a start that I realized the \textit{Cumulonimbus} had opened fire! A bolt of searing, unnaturally vivid pink-purple flew through the air, but my shock of alarm was short-lived; it was fired away from the incoming formation, at something on the ground.

There was another flash from the ship’s belly, and another bolt of magical fire streaked away. The first disappeared somewhere behind the distant buildings.

Dusty’s voice crackled in my earbud. “What are they engaging?”

Hail Burst’s reply was almost automatic in its speed and conciseness. “Unclear. First impact was south-southwest of town, distance two miles.”

The ship’s belly turret fired again and again, sending down a meteor-storm of magical plasma.

Hail Burst radioed again. “I see it now. They’re firing on an observation bunker. I see signs of habitation.”

\leavevmode\llap{“}Ponies?” Dusty asked.

\leavevmode\llap{“}Unknown,” she replied. “Too far out. Someone’s down there, but not for long. Shit, we’ve got fliers!”

Dark forms were emerging from the cloudship. I squinted against the wind and distance; using my binoculars would be pointless with our rough ride, so I could barely make out any details. There were dozens of changelings at the very least, and as they surged away from the cloudship, it looked as though they outnumbered the Loyalist forces by a fair margin. Moments later, a pair of skywagons dropped from the bottom of the ship to join the rest of the fliers.

As the barrage continued, most of the force wheeled around and flew, not toward the Loyalist forces, but in the direction of the bombardment. Only a small, loose cluster of Serenity’s soldiers remained to guard the \textit{Cumulonimbus}. They were outnumbered, but backed by the cannons of the ship.

Dusty banged a hoof against the roof before calling out to get my attention. “Whisper!”

I ducked down, almost face-planting into the edge of the roof with an ill-timed bump. “What?”

\leavevmode\llap{“}Observation bunker. Why would they be going there?”

I frowned. I knew only a little of the details of Equestria’s wartime megaspell testing, mostly what had been publicly disseminated by the Ministry of Image, but I could make some educated guesses. “If it was intended to observe megaspell testing, there’s a chance the megaspell could be detonated from there.” My ears perked as another thought occurred to me. “And it probably has controls for the warning sirens. Someone turned those on, so there might be someone sitting on the trigger.”

\leavevmode\llap{“}Oh, wonderful!” Dusty replied, already going for his broadcaster. “Hail Burst! Can you intercept that group that broke off?”

\leavevmode\llap{“}Negative. Continuing as planned.”

The \textit{Cumulonimbus} had started to turn, while its ventral turret continued the bombardment. It was skirting along the west side of the town. Sensible; the maneuver kept it well away from the megaspell, while keeping the speed up against the closing Loyalist forces.

Our motorwagons, on the other hand, were aiming for the opposite side of the town.

It was an eerie moment of calm as we roared across the dusty basin, the town drawing closer, and the Serenity changelings descending behind it. We were still a few miles from the town, while the \textit{Cumulonimbus} must have been passing it. The bombardment continued, and as the changelings descended on their targets, tiny flickers of light announced the firing of their own weapons. It was too far away to tell what was happening.

I sat down, grabbing onto the rear of the back seat, and called out to Dusty. “I’m going to be off the radio for a sec! Let me know if something comes up!”

He gave a sharp nod before turning his attention front again, and I looked down to my PipBuck. My horn lit as I turned the dial to manually scan frequencies. The PipBuck only detected one broadcast aside from our occasional communications, and it was weak, distant music almost entirely obscured by static. Not what I was looking for.

I’d scanned the whole dial four times before a burst of noise jabbed at my ears. I adjusted the tuning, and the static dropped away, my earpiece filling with a warbling, computerized sound.

A second later it ended, replaced with soft static.

I waited, ears straining and eyes glued to my PipBuck screen.

Seconds passed, and then the sound exploded in my earpiece again, the same chaotic digital nonsense.

\leavevmode\llap{“}Damn.”

Despite the noise of our ride, Dusty’s ear flicked at the word, and he looked back. “Something wrong?”

\leavevmode\llap{“}No. It’s what I had expected. They’re using broadcasters as well, but it’s not analog voice, and it’s not any digital data-type the PipBuck recognizes. It’s probably encrypted.”

\leavevmode\llap{“}Figures.”

His ear twitched, eyes glancing away as he heard something. I switched back to the frequency we were using just in time to hear Two Bits speaking. “—see ponies down there,” Two Bits called. “Shit, at least twenty dead around the bunker. They’re burning. I’m not seeing any weapons. Wait, scratch that. Just saw a pony with a spear.”

There was a pause. “Ground, they’ve lifted bombardment. They might turn that big gun on you, so stay spread out.”

I stood again, bracing against the roof. No more bolts flew from the monstrous ship. From that distance, I could only imagine the belly turret turning our way.

\leavevmode\llap{“}Will do, thanks,” Dusty replied. Not that we had to do anything to spread out; there was no semblance of a formation.

Hail Burst called out to her soldiers. “Prepare for attack. Be ready to condense on your team leaders.”

\leavevmode\llap{“}That detachment is hitting the bunkers now,” Two Bits reported. “Correction, they’re splitting. Dusty, two skywagons and some thirty soldiers just turned your way. Four miles distant, flying an intercept course. ETA two minutes, tops.”

\leavevmode\llap{“}Copy,” Dusty replied. “Keep us advised.” As soon as he finished, he leaned out the window, shouting out to Axle in the neighboring wagon. “Heads up! We’ve got Serenity forces flying our way! We’ll be making contact in a minute or two!”

Axle made some quick gesture, then turned, lifting a rifle with one hoof while giving out a loud yell. Several more weapons and shouts were raised from other wagons, spreading the word.

The air raid siren warbling tone continued, echoing eerily even over the sounds of the motorwagons. Then the tone fell, slowly winding down until it fell silent. I’m not sure if the silence was better or worse.

A few seconds later, I saw the dark gray form of a pair of skywagons, skimming low over the horizon, and then the faint black dots of the changelings flying alongside them. My heart lurched, adrenaline flowing. They were coming for us.

Two Bits called out on the radio. “They’ve split again. Most turned and are heading more directly for you. The skywagons and a few changelings are continuing on away from town.”

\leavevmode\llap{“}Reference the gantry tower east of town,” Dusty radioed back. “What’s their heading relative to that?”

\leavevmode\llap{“}They’re heading straight at it.” They were going for the megaspell.

I looked that way, spotting the distant tower and the barely visible swirl of colors in its midst. Then I looked down to my PipBuck, calling up the map, and finally to the pair of distant skywagons.

They were going to beat us there.

I wanted to tell Dusty that, but he had to know it. We couldn’t get there first, but maybe we could get close enough to stop them. We just had to get past the thirty soldiers flying our way.

The earbud crackled with Hail Burst’s voice. “Loyal one, go.”

A new voice popped up. “One, collapse!”

I looked over to the distant pegasus formation. It was hard to make out individuals as a few distant, dark dots drew closer, but I didn’t miss the flicker of purple as several disappeared.

Silence on the radio. I could practically hear my heartbeat even over the roar and rattle of the motorwagon. Then, relief: “Loyal one set.”

Hail Burst immediately called out again. “Loyal two, go!”

Another new voice. “Two collapsing!”

Another flash of purple. A single dot appeared. Another flash. Half a dozen disappeared.

\leavevmode\llap{“}Two set!”

Radio calls continued rapid-fire as the Loyalist force disappeared one-by-one. Too late, flickers of light flashed at the side of the Raptor, sending pink bolts out at their formation, but they were too far out, too nimble.

As the fifth team was calling out “Set!” my earpiece exploded with a piercing shriek of sound. I winced, flailing at the volume dial, and the vehicle swerved beneath me. I fell, hard, and cried out, clutching at my side. The earpiece had fallen out.

\leavevmode\llap{“}You okay back there?” Dusty called out.

\leavevmode\llap{“}Ow,” I replied, gritting my teeth as I pushed myself up to sitting again. A deep breath drew a jab of pain, but carefully moving my shoulder produced none. Bracing myself, I rose up again, grabbing onto the back of the gun. My side protested, but the adrenaline muffled the pain.

One of the motorwagons flashed brightly, and for a moment, I thought it had exploded! Then I saw the bolt of energy sail away, the magical energy cannon glowing brightly as it charged its next shot.

I swung the rear of the gun around, pointing it at the incoming changelings. The violent rocking made it all but impossible to line up the sights, which swung randomly across the distant group. They were still too far away, and the vehicle far too unstable, for me to have a hope of hitting.

Behind me, Sickle turned, and even past all the noise, I could hear her rumble. “The fuck is this shit?”

I glanced back to see her looking off to our side, and followed her gaze to see a Trotsen motorwagon, adorned with a blade-like plow and a spiked roof. It bounded across the dry earth as it swung in close beside us.

It was only because of Sickle’s comment that I was looking to see the pony in the cargo bed swing around a large tube and line up on us.

My vision was abruptly cut off by Sickle’s armored leg, the world lurched as I was pulled of my hooves, and everything exploded.

I tumbled, with no up or down. E.F.S. indicators flashed in my vision. I don’t remember hearing anything, even as I slammed down against something hard. I don’t even remember feeling pain. I was lying on my side. There was dirt in my mouth and smoke in my nose, and as I turned my head, I saw the side of Sickle’s gun, up-close and personal.

She roared. I don’t know if I heard it, or saw it, or \textit{felt} it, but she roared, and I threw up a hoof. The gun thundered, the sound hitting as hard as the impact against my leg. I turned and curled up, desperate and terrified and completely lost as to what was going on, while her gun pelted me with spent casings.

A searing pain lit up the sensitive membrane at the base of my wing. Whatever scream I produced was lost behind the sound of Sickle’s gun, and I flailed until I had dislodged the massive shell casing that had lodged against one of my armor plates.

The shooting stopped. Sickle was still moving. The first sound I remember hearing was her shouting past me, though the only words I made out of the exchange was “Fucking changeling cunts!”

An impact. For a moment I was weightless. Then I slammed down again. I only then recognized that I was still in the bed of the motorwagon. We had just hit a bump. A couple of scalding-hot casings rolled against my side, and I swatted them away. One bounced, tumbled, and disappeared through a gap torn in the bottom of the bed. I paused, looking at the hole.

The side of the cargo bed was torn open, roughly alongside where I had been standing. Metal was twisted, scorched, and shredded.

Opposite the torn-up armor, Bloodbeak lay against the other side of the bed, her eyes wide as blood ran down her side.

That shook me out of my shock. “Bloodbeak’s hurt!” The words felt mushy and slurred in my ears. I quickly rose. My leg gave out. I sprawled, caught myself, pushed myself up to her side. She blinked, eyes turning to me without quite focusing, and said something I didn’t catch. Another bump almost sent me sprawling again, sending fresh stabs of pain through my side.

I grit my teeth and focused on Bloodbeak, hooves going to her side. There was a nasty cut across the side of her belly, and more blood along her back. I pushed to roll her to the side, and she complied, looking thoroughly dazed and lost.

A jagged chunk of metal, some three inches wide, protruded from her back. It had cut through her side, and while it looked shallow, I couldn’t be sure.

I removed my PipBuck, the ever-present E.F.S. indicators vanishing. Bloodbeak was moving her arm, but I was able to grab it and hold her in place long enough to attach the device. The medical screen popped up many warnings, such as severe bleeding and a minor concussion, but it lacked the one I had been worried about: internal organ damage.

I reflexively turned to search my bags for a healing potion, only to realize I hadn’t been wearing them. “I need a healing potion here!”

No answer. I repeated the call, a little more urgently.

A blow struck me on the shoulder. I fell across Bloodbeak, caught myself against the side of the cargo bed, and turned to look for the source. I saw only Sickle’s receding hoof as she said something to me—I heard only a vague rumble—and pointed to the armored case at her side.

I staggered my way over, nearly collapsing against her side as I clung to the battle saddle, and popped open the lid of the case. It was full of a chaotic assortment of junk, but I quickly found the healing potion.

Throwing shut the lid, I hurried back to Bloodbeak, almost falling on her again. Her mouth moved, and this time I could make out the words, even if they were muffled. “This kinda hurts.”

\leavevmode\llap{“}Sorry,” I said as I nudged her to her side again. “This is going to hurt even more.”

I know the general advice for an impaling injury is to not remove the object, but that kind of goes out the window when you have magical healing available. She was already bleeding seriously. She needed a potion, and she needed it now.

So I grasped the metal shard in my magic and pulled. Bloodbeak’s eyes and mouth went wide, then she clamped her beak shut, smothering a moan of pain.

The piece of shrapnel came free, and a thick stream of blood followed, as if I had uncorked a bottle. I quickly consulted the PipBuck screen. It was reporting the worsened bleeding, but most importantly, there was no more indication of foreign objects.

I opened the potion, bringing it to her beak. She didn’t have to be told what to do, grasping the bottle and downing it. While she did, I retrieved my PipBuck, clasping it onto my leg. The E.F.S. returned, flashing warnings once more. It helpfully informed me that I had a minor concussion, partial fracture of my ventral chest plate, and was currently suffering from the effects of shock.

I found myself very tempted to level some snarky comment at the inanimate object, but I refrained.

There was another thump at my side, lighter. I looked back so see Sickle offering me several pills; a pair each of painkillers and Buck.

One painkiller went to Bloodbeak. The other I downed myself.

I went to return the Buck, but Sickle put up a hoof to stop me, and said something I couldn’t understand.

\leavevmode\llap{“}What?”

Her lips curled, then she shouted loud enough for me to understand. “Fucking take it! You’re going to need it!” Then her hoof raised, pointing past me.

I turned, looking past her hoof, past the mounted machine gun, to the black forms flying through the air, weapons flashing with magical fire.

Right. There was a fight going on.

I turned to grab the gun, only to have my side scream in pain, my leg giving out once more. I collapsed to the floor of the cargo bed. Sickle roared out something obscene and fired a few more rounds.

I might disapprove of Sickle’s casual chem use, but this was hardly a casual situation. I spared only a moment of regret and uncertainty before throwing back one of the thick tablets, swallowing, and pushing myself up once more.

Grabbing ahold of the machine gun again, I once again took in the scope of the situation in all its chaos. Changelings were swooping in over the line of motorwagons, keeping a few hundred yards up as they strafed us. Guns were fired in return, forcing some of the attacking soldiers to swerve away, but not enough. As I swung the gun around into position, I saw a salvo of pink-red bolts tear savagely into a motorwagon a hundred yards ahead of us, throwing off molten bits of metal and pink ash. A half-dozen changelings banked away from that ruined motorwagon to line up on us. Half of them were in Enclave power armor.

I hit the trigger, letting loose a bone-rattling burst of fire. The shots were wild and inaccurate, but the incoming changelings banked and veered away, avoiding any easy shot on them. I tracked one of the power armor soldiers that flew parallel to us, desperately trying to get the sights roughly on-target.

The sound of gunfire was finally registering, the sounds echoing across the basin. Clouds of dust and bursts of fire engulfed another armed motorwagon at the edge of the loose group. I lost track of the changeling I had been tracking, and swung the weapon around in an attempt to line up on a trio of power-armor-clad changelings diving at the other wagon, unleashing a storm of magical fire. I was too slow. An instant after I saw the changelings, the wagon flashed and erupted in a blast of multicolored magical energy, fragments peppering the landscape around the doomed vehicle.

The changelings didn’t emerge unscathed from the Trotsen ponies’ return fire. Only two of the trio pulled away from their strafing run. The third hurtled through the air, unresponsive, and crashed into the wake of the burning motorwagon.

More gunfire. Another explosion. Bolts of magic flew both ways as some of the changelings closed on one of the wagons with the Gemstone ponies, only to be driven back by the flurry of return fire, the air filling with searing lines of light and magical bolts. Ponies in the back of speeding wagons fired rifles into the air. Serenity changelings swarmed around, keeping their distance.

They were everywhere. It was too much to keep track of. I spotted one, in power armor, making another strafing run. I swung the weapon around, but she was already banking away, her speed and distance far too great to hit with how much our own wagon was shaking.

Tracking that changeling, I spotted a pair banking around behind us, the gems of their battle-saddles glittering as they lined up on our wagon.

\leavevmode\llap{“}Sickle!” I shouted, giving a quick point, then hauled myself up on the roof to get the gun turned around. I held the gun tightly as I steadied it, and managed to keep the sights roughly on-target. The Buck must have been working.

Sickle was already firing as I hit S.A.T.S., using the extra little bit of help to get things lined up, and fired.

It was just a short burst, maybe five rounds, but the changelings veered off again, one plummeting straight down. I felt a moment of elation, but it vanished as the changeling rolled and pulled out of her dive, speeding away from us.

The vehicle lurched under me, and I clung to the gun as we swerved, roaring past a ruined and still-tumbling motorwagon. A cloud of dust washed over us, stinging at my nose and eyes, and then we were clear again.

More shooting. More chaos. There was too much to keep track of, too much going on. Several sharp cracks drew my attention to the side, where I saw Dusty’s rifle sticking out the window, firing. I swung the gun around in that direction, spotting a changeling in Enclave armor who had swooped in behind another motorwagon. A pony in the back threw a spear at her. She replied with a burst from her own weapons, tearing into the back of the wagon.

S.A.T.S. was ready again. I engaged it, lined up, and hit the trigger. I put out a longer burst this time, and when I let off the trigger, was met with the sight of the changeling tumbling across the ground, throwing up dirt in her wake. I’d actually hit.

A loud \textit{bang} and flash of pink shook me from the moment, and I winced as a wave of cinders slapped across my side. I skittered back, abandoning my precarious perch on the roof for the safety of the cargo bed as bolts of magic landed all around us. I snapped the gun around, blindly firing up into the stream. The barrage stopped a moment later, and I finally spotted the pair of changelings, still at high altitude, banking away from the attack. I didn’t have a hope of hitting them at that range, but I’d dissuaded them from their attack.

But I knew I couldn’t keep that up. They’d just try again, and eventually they’d hit us. I’d bought us only a few seconds.

I looked around, hunting for targets, or just to make sense of the scene. I only saw a few wagons, but there was so much dust and chaos that I had no idea how things were going. The volume of fire had diminished, and the few changelings I saw were getting distance. I couldn’t even guess at how many of them were still up.

The occasional flash of magical light cut through the air after the changelings, but even Gemstone’s weapons were having difficulty finding their targets.

Then, as one, every changeling banked into a slow turn, coming around until they had lined up on our formation.

\leavevmode\llap{“}Fucking bring it!” Sickle roared, planting both hooves on the side of the wagon. I lined up the gun, watching the terrifying force bearing down on us once more. My heart pounded.

A couple lines of light flashed in the sky as a few of the Gemstone ponies started firing. The magical energy cannons fired a moment later, sending their bolts of magic arcing through the air.

I distinctly remember one single changeling firing, a single string of magical bolts flying forth like the first drops of a torrential storm. More were starting to fire as I hit the trigger, my own gun thundering in reply. Explosions ripped across the ground all around as bolts of magic kicked up sprays of dirt. Guns fired and bolts flew. My entire world narrowed down to that narrow view down the sights, bobbing and sweeping uncontrollably across the incoming forms.

A bang, and the vehicle jolted, swerved, and skidded. I let off the trigger, clinging to the gun as a spray of pink and red cinders washed over me again. Then we straightened out once more, and I looked up to see the changelings veering away again. The return fire was intense, if inaccurate, and I lined up to add a few shots of my own into the mix. I saw a puff of light as some magical weapon hit its target, though I didn’t see if it downed them.

I spared a second to glance around. I couldn’t find most of the changelings that had been attacking us. I’d completely lost track of them in the confusion, and only saw the dozen or so that were climbing away. I kept the sights aimed in their direction, waiting for them to turn back. They kept going.

There was a bang of a hoof on metal from inside the cab, followed by a shout from Dusty that I couldn’t make out.

\leavevmode\llap{“}What?”

Sickle’s hoof thumped me in the side, then pointed to the front. “He said to shoot the fucking skywagon!”

I looked to the front again. Past the spray of dust from the badly scorched motorwagon in front of us, the test tower was less than half a mile away and closing swiftly. The pair of skywagons hovered alongside it. I didn’t see any sight of the balefire bomb.

I swung around, lining up the sights as best as I could with how much the vehicle shook. I was about to fire when I stopped myself, turning my attention to the sights and dialing up the range. The dial could range up past two thousand yards, which seemed excessively optimistic even in ideal circumstances. The eight hundred I set it for still seemed rather optimistic, given my skill and our movement.

I lined up again and hit the trigger. It was just a short burst, perhaps three or four rounds. Then I was fighting the vehicle’s shaking to get back on-target, while trying very, \textit{very} hard to not think too closely on what I was shooting at. Half a mile away was far too close, but the decision had been made. We had a mission. Stop Serenity from getting that megaspell, by any means necessary.

One of the Gemstone cannons started firing, lobbing an inaccurate spray of plasma at the distant skywagons. I had no idea where my own rounds had gone, but I fired again, putting out a few more rounds.

The skywagons started moving. I adjusted to lead them and engaged S.A.T.S. This time, I put out a slightly longer burst.

I couldn’t tell where my rounds were going. I was just blindly guessing as I fired again, hoping that I’d put enough rounds down-range to hit out of pure luck.

I hit the trigger again. The weapon thundered once, twice, and then fell silent. “I’m out!”

Dusty squirmed out past the back seat, pushing past me. I have to admit, I gawked a bit as he searched for more ammo; the side of his barding was speckled with scorch marks, and the hair on his face was singed. It took him only a moment to find the new box. He pulled the old can off the mount and replaced it with the new one, opening it and the massive top cover of the gun to feed the new belt in. A second later it was shut and he racked the massive handle, chambering a round.

He gripped the weapon, calling out. “Starlight, halt!”

The motorwagon lurched as she hit the brakes, throwing me against the edge of the roof, then sending me tumbling back to the floor as it settled violently into place. Dusty kept his place, and a moment later was firing in long, well-controlled bursts. I pushed myself up with surprising ease—thank you, Buck—and leaned to peer around him. We were almost right behind the skywagons now, and I saw a few puffs from the one on the right. He was hitting! The vehicle started to bank, but he adjusted and fired again, and a second later was rewarded by a few more puffs along its side.

He fired again, a shorter burst, but he’d gotten their measure. I could see the impacts along the front edge of the skywagon. Its maneuver immediately ceased, and the nose slipped downward. A few dark forms flew from the stricken vehicle as it fell.

Dusty was already firing on the other one, which had entered a dive, weaving back and forth. His fire was joined by the Gemstone cannon, and I looked over to see it stopped maybe a hundred yards away. Even Starlight joined in, with the searing red flash and loud crack of her Lancer firing from inside the wagon. The shot threw off a cloud of incandescent sparks from the skywagon’s side.

Despite the fusillade of fire, the distant skywagon kept going, bobbing and weaving. Dusty kept firing, in short, careful bursts, but I couldn’t tell if any of them hit. The tail end of the belt disappeared into the gun, and it finally fell silent moments before the skywagon, skimming the ground, disappeared behind the brightly colored buildings of Ponytown.

\leavevmode\llap{“}Damnit!” Dusty snapped, ducking down to shout to Starlight. “Move! Head towards the Raptor! We might cut them off!”

I staggered back into Sickle as the tires churned at the ground, kicking up a spray of dirt as we took off once more. Once I’d recovered my balance, I scanned the desert, looking for the other skywagon. I found it, crumpled on the desert floor, abandoned.

Dusty still stood there, holding onto the gun for balance, his jaw tight as he glared at where the skywagon had disappeared. Then he turned to look at the \textit{Cumulonimbus}. It was well past the town and still headed slowly southward, putting us even closer to it than the fleeing skywagon. We still had a chance.

Dusty’s ear flicked, and he turned to his PipBuck, hoof turning one of the dials. I realized what he was doing and searched for my displaced earbud, tracing the cable until I found it caught in the strap of my armor’s shoulder-plate. I slipped it in.

\leavevmode\llap{“}—Disabled. CIC secured. Be advised, we found and defused demolitions here, they may be trying to scuttle the ship.”

\leavevmode\llap{“}Copy that,” Hail Burst replied. “All teams, eyes out for more demo. Four, status?”

Dusty hit the transmit button. “Hail Burst, it’s Dusty, they have the megaspell! It’s in a skywagon, last seen heading northwest from Ponytown thirty seconds ago.”

\leavevmode\llap{“}Understood,” Hail Burst replied before continuing as if he hadn’t spoken. “Four, status?”

\leavevmode\llap{“}Lead, Four. We hit strong resistance here, but it’s thinned out. Looks like they fell back somewhere to the aft, maybe engineering.”

\leavevmode\llap{“}Negative,” another voice called. “Six holds engineering. Some of the bugs were trying to set demo, but we stopped them. We’ve had no contact for the past minute.”

I looked out at the cloudship. I could see several dark forms flying away from it, with a few more trickling out from some place along the bottom. It seemed the Loyalists were winning.

Two Bit’s voice came over the radio. “Ranger lead has eyes on that skywagon, about a quarter mile northwest of town, still continuing northwest.”

\leavevmode\llap{“}Lead, three! Bridge secured. They abandoned the position. There’s demo set—”

\leavevmode\llap{“}Fuck,” Dusty said, his head snapping up. My earbud suddenly crackled with multiple shouts and calls all at once, and I looked up to see bits of armor plating and machinery hurtling through the sky, a thick cloud of smoke quickly washing away in the wind to reveal the yards-wide wound that had just been torn out of the Raptor’s nose.

Hail Burst’s voice cut through the cacophony. “Clear comms! Three, status?”

Silence.

\leavevmode\llap{“}Three, report!”

Another stretch of silence, finally broken by the voice of a stallion, sounding very much like he was fighting back pain. “Pinwheel here. I… I think I’m the only one left. The whole bridge just… fucking exploded.”

\leavevmode\llap{“}Copy that. Stay put. Five! Pick it up and get to the bridge. Everyone else, you fucking scour your compartments for demo! Four and six, coordinate with each other on ship comms, I want flight control!”

Several calls of affirmation went out, while Dusty cursed and turned to me. “How are changelings for endurance?”

\leavevmode\llap{“}About the same as a pony,” I said. “More if they’re good with shapeshifting. If you’re asking about how long they can fly that skywagon, hours at least, and they can just trade out pilots while others rest in the back.”

He frowned grimly. “So we can’t catch them.”

\leavevmode\llap{“}The Loyalists might be able to,” I said, though I looked off to the northwest and the distant, barely visible forms of flying changelings. “Though they’d have a lot of opposition to get through, and they’ve got to be running out of steam after flying that long. It’s looking iffy.”

\leavevmode\llap{“}And the whirligigs would get torn up by fliers,” he said with a grunt. “Damn. They’re going to fucking get away with it.”

I felt a little helpless. I had no good ideas to suggest. I could have shifted into a fast-flying form, perhaps Rainbow Dash in the prime of her youth, but I could hardly do anything on my own. Heck, with my side feeling the way it was, I couldn’t even be certain I’d catch them even then.

\leavevmode\llap{“}Slow it down,” Dusty called to Starlight, then turned to wave. I looked over to see Axle’s wagon a short ways off, beaten and burnt from the attack, but still rolling.

As the wagon drew closer, Axle reared up in the back, looking even more dusty and disheveled than before. “What the hell is going on now?”

\leavevmode\llap{“}They got away,” Dusty called back. “The Loyalists are securing the Raptor. The fight’s over. It’s time to round up every pony that made it.”

\leavevmode\llap{“}What?” Axle said, casting a glance at the \textit{Cumulonimbus}. “You mean the fucking birdies were so goddess-damned obsessed with their ship they just let the fucking megaspell slip right by them?”

\leavevmode\llap{“}We’ll work out the details later,” Dusty said with a shake of his head. “Right now, let’s backtrack. I saw a lot of wagons knocked out. Some ponies are going to need a ride.”

\leavevmode\llap{“}Fuck!” Axle shouted, then ducked down. I heard more yelling inside the wagon before it turned, heading back the way we came.

\leavevmode\llap{“}Follow him,” Dusty called out to Starlight before turning back to his broadcaster. “Bitsy, we’re backtracking to pickup casualties and recover any functioning wagons.”

\leavevmode\llap{“}Copy that. The Loyalists seem to have the ship. Alpha’s heading down to check that bunker they were bombarding. Bravo, stay up here to keep an eye on things and respond as needed.”

Both Dusty and another pony replied in affirmation as one of the whirligigs banked away, descending to our south.

The ride back was more sedate and melancholy, especially as we approached the first smoldering motorwagon. The area all around it was torn up from incoming fire and fragments. The entire front end was an open, gaping wound; one of the incoming bolts must have ruptured the vehicle’s spark pack. My PipBuck clicked rapidly in my ear as we passed by, then fell silent again.

Looking around at the motorwagons trailing along with us, we were concerningly thin in numbers. Only four wagons were still with us, including Axle’s and one with a Gemstone cannon atop it. Fortunately, not all of the missing wagons were destroyed. The very next wagon we came across had the missing Gemstone cannon, and it was mostly intact. The crew sat wearily atop the roof, awaiting our return. They had lost a wheel, and some lucky shot had struck the cannon and blew out some vital parts, but except for a slightly singed gunner, they had escaped injury. The gunner even smiled, saying that she was sure Arclight could fix the cannon easily.

The next was even worse than the first. A young stallion, barely an adult, had been the only survivor in his wagon, and was horribly burned across almost all of his body, crying out at even the most gentle of touches. The rest of his crew, six ponies, were still trapped within their smoldering, twisted wagon. The charred and nearly skeletal face of the driver leered out the side window. The stench was horrific.

Serenity’s force hadn’t escaped unscathed, either. Time and time again, I spotted the limp, black lump of a downed changeling. They were few in number compared to our losses, but it could have been far worse.

One of Serenity’s soldiers had been shot down and crashed near one of the disabled motorwagons. The three members of the crew that had survived the attack had tied her broken corpse across the hood of their wagon. Some of them laughed and made crude gestures in my direction as we passed. One of the gestures showed off the newly acquired PipBuck strapped to a foreleg.

I ducked my head below the roof. “Starlight, go ahead and stop us here.”

As we came to a stop, I was transforming again, returning to my queen disguise. The world warped and shrunk around me. When it was finished, I stood tall, calling out, “Axle!”

His vehicle had just passed us, slowing as ours did, and finally came to a halt as he stood up in the rear. “What?”

I hopped down, wings flickering to soften the landing, and my horn lit again, my saddlebags floating out from the motorwagon. “Come with me, please,” I asked as I turned, walking toward the gruesomely adorned vehicle.

I heard a loud mumbling of obscenities, but somewhere in that string of curses must have been some order, because his driver pulled up beside me. “What the fuck is it now?”

Two of the ponies we were approaching had stopped their gestures, instead staring with narrowed glares of open hatred. The third still looked amused, pushing the changeling’s head so the corpse was looking at me.

\leavevmode\llap{“}I’d like to borrow that PipBuck,” I said, coming to a halt just a few yards from the ponies. I looked to Axle, making it clear I was asking this of him and not them. “And any other PipBucks we can recover, as well.”

\leavevmode\llap{“}What?” the PipBuck’s wearer said. “Why the \textit{fuck} would I give it to you, bitch?”

\leavevmode\llap{“}Several reasons. I expect the most important to you would be that Serenity has the tags of every PipBuck here. Unless I change it to something they can’t track, they’ll know your precise location, no matter where you go. You’ll be like a beacon, advertising our exact position, and they’ll be gunning for you.”

I turned back to Axle. “More importantly, the data on that PipBuck could be useful to our fight. I have extensive experience in data intrusion, cryptography, and intelligence analysis. If I collect all the information I can, I may be able to find something that helps us. I also have additional reasons to examine the device that I’d rather not discuss in public.”

\leavevmode\llap{“}Like I fucking care,” the stallion said. “It’s mine, fair and square.”

\leavevmode\llap{“}I’m not asking to keep it,” I elaborated, still talking to Axle. “He’ll get it back.”

\leavevmode\llap{“}Hey, I said—”

Axle cut him off. “Oh for fuck’s sake, Skim, just give it to the bitch. I’m way too tired and \textit{way} too fucking pissed about far more important things to have any patience for this brahminshit!”

Skim gaped for a moment before replying. “Are you fucking kidding me?”

Axle practically snarled. “Do I look like I’m fucking kidding? Give it to her before I stomp your damn face in!” Then he turned his glare at me. “And you, you’re giving it back to him by the end of the day or I’m tracking you down, breaking off that ugly fucking horn, and jamming it up whatever passes for a cunt in you bugs, got it?”

\leavevmode\llap{“}Understood,” I replied with a polite nod.

Axle grumpily sat back, barking out a command, and his motorwagon started rolling again.

Skim took his time removing the PipBuck. “If I don’t get this back, you won’t have to wait for Axle to find you. I’ll have fun making you scream.”

\leavevmode\llap{“}Mmm,” I hummed as I took the PipBuck in my magic. “And two hundred years ago, I might have even found that intimidating.” I pulled up a bit more of my magic reserves, and with a flash, the changeling corpse burst into flames. The mare beside it yelped, scrambled back, and fell off the hood of the motorwagon. I simply turned and walked away, not even watching as the corpse was reduced to a fine ash.

Mind you, my heart was pounding, and I was fighting adrenaline to remain smooth and calm in appearance. I was playing a role, and I had to keep it up, even as much as everything in me told me not to turn my back on someone who had so much reason to hurt me.

Several curses and shouts followed me, but they didn’t try to attack me. Maybe it was because they knew Axle would get on them for it. Or maybe it was because of Sickle’s eager grin, and Dusty’s rifle protruding from the side of our motorwagon, held low but ready.

As I drew nearer, Starlight leaned forward. “Everything okay there?”

That broke my calm acting, as I winced. I had somehow not seen her face since the fighting had started; her muzzle was caked in blood. “What happened to you?”

She flashed an awkward smile. “Smashed my face into the steering wheel when that rocket hit. Again. It’s fine.”

I hesitated. “Are you sure?”

\leavevmode\llap{“}Yep. It doesn’t even hurt anymore. It just kinda itches now.” Seeing that I was still concerned, she lifted her PipBuck-clad leg for emphasis. “I’m fine. It says so.”

\leavevmode\llap{“}If you say so,” I said, and my wings beat for a few moments, carrying me up to the cargo bed once more. “Do you need a healing potion? Painkillers.”

\leavevmode\llap{“}I’m \textit{fine},” she said, nearly laughing as she said it. The motor thrummed as the vehicle started to roll again. “What I need is a rag and some water.”

That I was able to do. We continued on, only now we were aiming for all those little black lumps dotted across a couple of miles of the basin. We stopped at each one, and Starlight got cleaned up while I scoured them for PipBucks. Every soldier without power armor had one. At Starlight’s insistence, we opened up a pair of the least damaged power armors, loading them into the back of our wagon.

One of those had been the one I had downed. The round had struck low on the side of the chest. Starlight said that was great, since there was little in the way of articulation around that point, so it probably did very little damage to the armor itself.

The same couldn’t be said for the poor changeling that had been wearing it. It was an unpleasantly thorough look at what that gun could do to a person. The entire ventral plate of her chest had been obliterated, and the impact had cracked the carapace all the way across her back. The inside of the armor was a gruesome mess of blood and former changeling. My stomach tightened unpleasantly at the sight, and the knowledge that I had done this to her.

By the end of it, I had gathered seven PipBucks from twelve downed changelings, piled together like some morbid trophy collection.

We eventually caught up with Axle and the rest of the Trotsen ponies. They had stopped by the first motorwagon to have been knocked out, the same one that had fired on us. Sickle had torn it up with her machine gun, and it had eventually come to rest there. The Trotsen ponies had pulled out the corpse of the driver, a changeling, still garbed in the clothing of the pony she had been impersonating. She’d been hit by at least two of Sickle’s rounds. Most of her head was simply gone, and a severed foreleg was tangled in the crude barding.

Ponies stood nearby, arguing. I heard a couple names. I think they were wondering what had happened to the ponies they had replaced. I couldn’t say for sure, but I suspect they were dead.

All told, the Trotsen ponies had picked up ten ponies from knocked-out wagons, and repair crews were working on two of the wagons that had been damaged but not destroyed. Many were wounded, even among the crews of surviving wagons. The Gemstone ponies were all fine; the singed gunner was the worst of their injuries, and even that had been superficial. The firepower they had brought to bear had forced the enemy to keep its distance, and once they were immobilized, the magical energy rifles would have been much more stable and accurate.

Bloodbeak was doing better, too. She had recovered from the shock of her injury, and was sitting against the side of the cargo bay. She was idly turning over the mangled fragment of metal, a souvenir, while looking out at the trail of disabled vehicle left behind us. “Wow. Holy crap. I missed a hell of a fight.”

As soon as we stopped, Starlight scrambled out from the driver’s seat, hurrying to the front of the vehicle. I rose up, looking across the roof, to see her examining a jagged hole in the hood, surrounded by a broad scorch mark. She opened it up, examining the inside for further damage, while I noted a second hit on the side of the vehicle, right beside where Dusty sat. It had been a shallow, glancing hit, but still enough to open a small hole. It explained the burns on the side of his barding.

As for Dusty, he remained standing in the rear of the motorwagon, his forelegs crossed atop the roof, still looking out to where the skywagon had disappeared. He’d been silent for quite a while, but he finally spoke to me. “This cost us,” he grumbled. “Serenity got their balefire bomb, and we lost, what, a quarter of Trotsen’s motorwagons? A fifth? Plus however many Loyalists died in that ship.”

\leavevmode\llap{“}At least we got the \textit{Cumulonimbus},” I said. “It’s a poor consolation prize for that megaspell, but at least we’re not entirely empty hooved.”

He grunted. “Yeah. If they can hold it. If it even matters, with that megaspell in their hooves. What do you think they’re going to do with it?”

\leavevmode\llap{“}I don’t know,” I said, frowning. “Maybe hit the army. Maybe hit Mareford. Maybe use it for intimidation. I don’t know.” Silence followed, until I added, “I’m still curious why the \textit{Cumulonimbus} was even here.”

Dusty gave another grunt, but didn’t reply.

\leavevmode\llap{“}I’ve been trying to figure it out since we left the army. It seems to me that if their goal were the megaspell, they’d do just as well to send a small group out to retrieve it. We’d never know it was happening, so we wouldn’t have a chance to stop it. Moreover, it would leave the \textit{Cumulonimbus} in a position to hit the army, and they’d have a lot more support to hold onto it. Instead… they made a move that tipped us off to their intent.”

Dusty’s ear flicked, and he looked my way.

\leavevmode\llap{“}It seems like a poor decision on multiple levels,” I continued. “An illogical one, even, especially from a group that has been operating in secrecy for at least two hundred years. It doesn’t make sense, and any time something doesn’t make sense, I start to suspect deception. That goes double when changelings are involved.”

He gave a faint snort. “Yeah. Same here.”

\leavevmode\llap{“}I see two possible deceptions they were trying to play. One is that this was intended as a trap. They dangle the \textit{Cumulonimbus} in front of us, knowing the Loyalists will want to take her back. They send it out to help retrieve the megaspell, and if we figure out where it’s going, that’s even more motivation. The Loyalists have to get through the ship’s cannons, then fight through the interior of the ship. Even if they start to win, Serenity can blow the ship and kill even more of them. Maybe even use the megaspell for that purpose. It’d be costly, but they’re our hard-hitters and air power. That trade might be in their favor, at least before Echo’s teleportation shortcut past their defenses.”

\leavevmode\llap{“}Might be,” Dusty said with a grumble, then paused. A moment later, he pressed the transmit button. “Echo, are you okay?”

There was a momentary pause. “Of course I am. Why are you asking?”

\leavevmode\llap{“}Just checking,” he said, and looked to me again.

I continued. “Possibility two is also that this was bait, but that it was intended to draw off as much of our hard-hitters as possible, divide us up, and then hit the main army while we’re gone. I didn’t get a good count of how many changelings there were, but I’d guess at around a hundred. They’ve got a lot more than that.”

Dusty grimaced. “Or they were trying to do both of those. But yeah, that’s something we had considered before splitting up. I trust the militia to do the best they can while we’re gone. If it gets too bad, they’ll dig in and wait for us to get back, but they’re probably fine.” He paused before adding, “Hopefully. We’ll see.”

\leavevmode\llap{“}We will.” I looked with him at Ponytown. “There’s a good chance we’ll get another shot at that megaspell. We’ll just have to be ready.”

He grunted, but didn’t answer, and we fell into silence. The radio was still alive with transmissions, and while we waited, I listened in on the Loyalists, finishing up their sweeps of the \textit{Cumulonimbus}. It was interesting to listen to, but there was nothing terribly important.

Dusty’s attention slowly drifted away, until he was looking over the rest of our gathered force. Eventually he brought up his broadcaster. “Hail Burst, it’s Dusty. Does that ship have medical facilities in good condition?”

Hail Burst replied. “The \textit{‘Nimbus} has a good sickbay, but it’s a bit stripped bare at the moment. Do you have wounded?”

\leavevmode\llap{“}We’ve got a good twenty ponies down here that could use care, and I don’t think we have space on the wagons to haul all of them. Some are in pretty bad shape.”

\leavevmode\llap{“}Understood,” Hail Burst said. “Ranger Lead, if you can get those whirligigs to pick them up, you can drop them off at the hangar. I’ll have a couple soldiers posted to bring them in.” The radio clicked off, but a second later her voice returned. “While we’re at it, is Whisper still on this net?”

I blinked, then gently pressed the button to broadcast. “I am here.”

\leavevmode\llap{“}Yeah. I think you should get up here.”

Many questions leaped to mind, but I stuck to the simplest one. “Why?”

\leavevmode\llap{“}Because we have prisoners.”