The sun had not yet started to lighten the eastern clouds when Dusty started rousing everypony. When he made his way to the motorwagon to wake me, I stuck my head out the window, grinning. “Dusty! Get in here!”

I missed his precise reaction, as I immediately returned to my network of PipBucks, but several seconds later he was climbing into the front seat. Once there, he stopped and stared at me with a questioning, quirked eyebrow.

I answered with an even wider grin, leaning towards him. “I \textit{own} Serenity!”

He blinked. “Uh…”

\leavevmode\llap{“}I mean, not in the literal, physical, possessive sense. The colloquial sense. What I mean is, I just got us \textit{huge} advantage over them! Maybe. It’s not a perfect one, there’s security measures they could take that make all of this a lot harder, we need to be very careful about what we do and say and make sure that they think that we \textit{don’t} have this, or they can make changes, but if we keep them from doing that, I’ve got them!”

Dusty continued to stare. “Have you gotten any sleep?”

\leavevmode\llap{“}Of course,” I lied, reining in my grin to a less manic smile. “I’m just excited. This is… this \textit{could be} big.”

\leavevmode\llap{“}Oookay,” he said with a slow nod, then asked, “What is it?”

My smile vanished as I grabbed him by his shoulders, fixing him with a serious stare. “What I’m going to tell you has to remain secret. Super secret. Like, more secret than ‘Whisper is actually a changeling’ secret. If any \textit{suggestion} of what I’m telling you gets out, this opportunity is gone.”

He looked even more concerned. “Maybe you shouldn’t be telling me, then.”

\leavevmode\llap{“}No!” I said, giving a little squeeze with my hooves. “This whole thing will involve me passing on information, information that needs to get out to the army itself. I \textit{need} you. Can you do this?”

The eyebrow came up again. “Maybe if you’d tell me what ‘this’ is?”

I let him go, sitting back. “Right. Yeah. I should do that.”

\leavevmode\llap{“}And maybe get some sleep, too.”

I waved off the comment. “After. This first. And I’ll start with the basics, so that I can build up and make the final reveal of what I’ve gotten us all the more dramatic and impressive!”

\leavevmode\llap{“}Uh…”

\leavevmode\llap{“}So, basics: every Serenity PipBuck has a program in its spell matrix to encrypt radio traffic. It’s an amazingly well-crafted piece of spell programming. It runs an encrypted, multi-channel communications network, letting everyling communicate easily with anyone on the same channel. Soldiers can talk inside their squad, leaders can talk straight to other leaders, all that, and we can’t understand a word of it. It’s an incredibly useful tool, and the spell itself is amazingly complex.

\leavevmode\llap{“}Heck, they even partially encrypted the spell itself!” I waved a hoof at my network of PipBucks. “If I didn’t have all the software tools from my hive, the override cables, multiple PipBucks, and my programming experience, I couldn’t have done anything with them. But I do, and I did, and it's… and I figured out how to repurpose their audio encryption for our own communications! I even tweaked it so you can set different encryption keys for different channels, which was a pain in the flank, but worth it to prevent stealing a key from a low-level user giving access to our entire network. We get this out to anyone with a radio, give them the key for their channels, and Serenity can’t listen in on us!”

\leavevmode\llap{“}Okay,” Dusty said with a slow nod. “Hell, that’s pretty nice. I’m not downplaying it or anything, but I don’t see how—”

\leavevmode\llap{“}That’s not the big thing,” I said, waving another hoof in some vague gesture that made sense at the time. “This is just the setup for the big thing! Now, see, their own channels are encrypted to Tartarus and back. Cracking the encryption they used on the spell itself was difficult enough, but I could halt the process and analyze the spell matrix during execution to see what was going on. The spell matrix has to decode it to run, right? Right.

\leavevmode\llap{“}But the encryption on the communications itself is a different beast. Cracking it is is basically impossible. I mean, technically it’d be possible, but it’d take forever. Like, several orders of magnitude longer than Equestria has existed. Did exist. Whatever. Point is, we can’t crack their encryption, and even if we could, they took extra security measures that would make all that work pointless: they change keys every day.”

I stopped, staring at him with an expectant smile. It took a few seconds before he finally spoke. “Okay. So they’ve got crazy good encryption and they’re being smart about keeping—”

I leveled a hoof at him as he spoke the key word, my grin beaming. “It’s stupid!”

He blinked at my interruption, and I quickly continued. “Yeah, changing all their keys every day sounds clever, but it’s the sort of short-sighted choice a rookie Infiltrator might make. It’s theoretically smart, but only to someone who lacks the experience to consider practical field concerns. It’s the same mistake pony security ‘professionals’ made with computer security and passwords. Nobody can remember super-complex rotating passwords or long blocks of random characters.”

My grin grew as I said, with every ounce of emphasis I could muster, “\textit{They write them down!}” My hoof swung to point at the PipBucks. “I have every encryption key for the next two and a half months! As long as they don’t realize we have them—” I grabbed him by the shoulder for emphasis. “—And we need to keep this so super-secret that they don’t even \textit{think} of the possibility that we have them!—then we can listen in on every single radio conversation they have without them ever knowing!”

I was still holding him, beaming like some sleep-deprived maniac. Eventually, he nodded. “...Yeah, okay, that could be useful. Damn useful. Maybe don’t get your hopes up too much that—”

\leavevmode\llap{“}I know, I know,” I said as I finally released him, sitting back. “I’m just excited. And I’m optimistic. I think we might have found one of their flaws. Their army, it’s thoroughly trained, but it’s completely inexperienced. Rust might be the first time they’ve had a proper combat operation outside of their simulators. They know how to fight, tactics and all that, but there’s a good chance they’ll be weak on the operational side of things. That means overlooking things that \textit{should} be obvious because they haven’t experienced it before. How likely do you think it is that their simulations include the possibility of the enemy capturing their PipBucks and extracting encryption keys?”

He was frowning. “I couldn’t say.”

\leavevmode\llap{“}Exactly!” I said with an eager grin, which immediately faltered as I parsed his statement. “Wait, no. You were supposed to say ‘unlikely’. Which is maybe optimistic, but I think the odds are good. We’ll see.”

\leavevmode\llap{“}Uh-huh,” he said, still frowning. “Wouldn’t rolling out our own encryption clue them in to what we did?”

\leavevmode\llap{“}Maybe,” I said, fidgeting for a moment before stopping myself. “That’s why this has to remain a secret for now. We might have to choose one or the other, but I think I can figure out a way to get both. I just need to think on the problem.”

Dusty was slowly nodding, but stopped and fixed me with a serious look. “Which means you need to get some sleep.”

I opened my mouth to protest before recognizing the truth of the situation and the futility of arguing against it. “I could maybe use a nap,” I admitted, slowly slumping back against the seat. Now that I had finally told someone, the all-consuming excitement that had fueled me faded rapidly.

His hoof touched my leg. I blinked. He was giving a soft smile. “Hey,” he said, his voice softened a touch. “You did good. This could save a lot of ponies’ lives.”

I smiled, and he climbed out of the wagon again. I slid down a bit, the thin cushion surprisingly comfortable all of a sudden. Time slipped away from me. I remember Starlight passing me a warmed can of beets before things slid away again.

The next thing I remember was Dusty’s hoof gently tapping on my armored side. The vehicle was rattling and creaking with our movement. “Rise and shine. It’s time to see if you’re right.”

{\br}%
As the motorwagons rolled, I double-checked my equipment, ears perked alertly for the slightest sound from either of the two separate earbuds. One of the PipBucks in my array was steadily flashing a “waiting” message, ready to automatically record any transmissions coming in on the Serenity frequency. Another was showing a screen of various numbers, a quick and crude display I had whipped up to show Serenity transmissions. If I picked up a transmission, and the key I used decrypted it, the display would highlight what channels they were talking on. Yet another was showing a spell compiler and a copy of one of the programs I had been working on. My late-night coding had produced functioning and so-far bug-free programs, but they were \textit{sloppy}, and thus needed to be corrected.

Then there was the final PipBuck, which currently held my attention. I had the receive/broadcast screen active, waiting. It was set to play all channels concurrently, but I could filter it down to just one once things started getting too busy.

My right earbud crackled; friendly communications. Two Bits was calling out again. “Militia lead, Ranger lead. Please reply.”

The reply was, again, a burst of warbling static. There were still several hills between our approaching wagons and where the Loyalist scouts had spotted the dug-in army, barely five miles from where we had parted.

\leavevmode\llap{“}Say again. You are quiet and garbled.” Two Bits spoke slowly and clearly, firmly enunciating every word. It seemed that he wasn’t reading them too much better, even with the altitude.

Then my left earbud crackled, the number “28” highlighted, and a voice spoke in raspy tones turned unnatural with the mild audio artifacts. “Lead, Two. Eyes on cloudship inbound, south-south-east, distant, low. Looks like the \textit{Cumulonimbus}.”

It was working. A shot of adrenaline teased at my senses. I was listening in on Serenity. Despite all my earlier excitement, there was a real sense of relief as those decrypted words reached my ears.

\leavevmode\llap{“}Copy,” another voice replied, as the same channel number highlighted once more. “I see it. Hold position, keep your heads down.”

I had to caution myself. This didn’t mean I’d found a weakness. It could be that they suspected what I had done and might try to lure me out with false information. Maybe they were testing the waters, seeing if they had been compromised by seeing how I reacted.

And so, for the moment, I didn’t react.

The second voice spoke again, this time on channel 22. “Command, Two. We’ve spotted the \textit{Cumulonimbus} inbound, one-six-zero, twenty miles, five hundred. It’s moving slow, probably still escorting ground forces.”

Okay. The first channel was probably a squad or platoon-level radio, and this was the leader of that element passing information up the chain of command. So far, so good.

Two Bits called out again for our army. I ignored him, putting a hoof up to the other earbud to listen more closely.

There was a new changeling, broadcasting on the same channel as the last. The computerized distortion of their voice was more pronounced, but they were still understandable. The signal was worse. Presumably, this meant they were further away. “Understood. Scouts are tracking at least eight motorwagons directly under the—”

More voices spoke on another channel, overlaying the conversation in my ear. I quickly switched the receiver to single-channel.

\leavevmode\llap{“}—along the dry creek bed two-three is occupying. Your platoon’s job will be to conduct an ambush of the ground convoy. There are at least three high-value targets in the motorwagons. Prioritize leadership elements if possible, but don’t go chasing them, and don’t get into a prolonged fight. They’ll have heavy fire support from the \textit{Cumulonimbus}, so do some damage quick and break contact before they can pin you down. One, move to take up a line five hundred yards back from Two. If these ponies give chase, you’ll punish them.”

Two platoons. I was still a little loose on the numbers that entailed, but it wasn’t good.

Affirmative calls went out, then the channel fell silent. Channel 28 was highlighted again, and I switched to it.

\leavevmode\llap{“}—Listen up. We’re conducting an ambush on ground forces. Two and three will be the primary elements. Three, do you have good eyes down the creek?”

\leavevmode\llap{“}Affirmative. Clear visibility of the low-ground out to about four hundred yards.”

\leavevmode\llap{“}Copy that. Two, find a position on either slope that gives your squad good eyes into the creek. You’re setting an L-shaped ambush with three. One, Four, you’ll be staying up on the ridges, but move to get good overwatch. You’ll be covering the withdraw, but I want you keeping your horns down and out of sight until things kick off. Everyling find good concealment, they’ve got eyes in the sky. Call when set.”

Multiple affirmative replies followed, but I was focusing on my map, zooming out until I could see the reported location of our own army. We were barely over twenty miles away. Assuming one-six-zero was a compass bearing, I scanned along the reverse direction.

Two Bits spoke again, but the words were different. “Pineapple, excursion, triangle.” The seemingly nonsensical words brought a smile to my face. Our army was still there, and with the secret code-phrase delivered, they knew that we weren’t Serenity forces pretending to be their absent friends.

The reply was too distorted by static for me to hear if they gave the proper counter-phrase. Running signals intelligence from ground level was showing its limitations, but there was nothing I could do about that at the moment. It was something to consider for later. At least I could assume the counter-phrase was correct, and Serenity wasn’t impersonating our army. Two Bits was unlikely to overlook an incorrect counter-phrase.

I shook my head and returned to my map.

There. A string of low hills just two miles south of our destination, split by the narrow depression of a long-dry creek that meandered and wound its way all the way south to us. Dozens of heavily armed changelings were waiting there to kill us. The touch of adrenaline returned, urging me to action even though I could see there was no immediate threat; at our current rate of travel, it would be more than half an hour before we reached their lines. We had plenty of time to arrange a reaction that both avoided the waiting Serenity forces and protected the secrecy of our advantage.

So I sat on the information for ten minutes, listening in on the occasional radio conversation. Channel 31 spent a couple of minutes filled with rock puns and overacted groans. Someone started laughing on 30, saying that “Three is all kinds of ‘special’ today.”

There was something surreal in listening to changelings joyfully bantering with each other, just having fun, all while they fully intended our imminent and violent demise. It also notably lacked the indicators of a stress-coping mechanism. These changelings were completely unconcerned with the oncoming confrontation.

Finally, I slid forward. “Dusty. We might have a problem.”

He turned to look over his shoulder. “Yeah? Wait, is that stuff working?”

\leavevmode\llap{“}It is,” I said with a nod. “Serenity has scouts tracking our movements, and their ground forces are getting ready.” I held my leg out, pointing to the locations on my map. “There’s an entire platoon setting up to ambush us here, and a second platoon here to support them.”

He leaned in close to the map, looking over the terrain. “Yeah, that seems like a natural place for an ambush. We’ll have to go around.”

\leavevmode\llap{“}We’ll have to do so in a way that doesn’t tell them we know where they are,” I said. “At least, not this early. If we start looking overly well-informed about their intentions and reacting to things we shouldn’t know about, they might get suspicious, and we lose this advantage.”

He frowned, still looking at the map. “Well we can’t just roll straight into an ambush, even with the \textit{Cumulonimbus} giving fire support. That’s just not happening. So, since intel and deception is your field, I’m open to suggestions. How would you handle it?”

\leavevmode\llap{“}Basic misdirection,” I said, giving a hint of a smile. “We create a plausible reason for our actions, and allow them to discover it. Until we’ve rolled out our own encryption, our radios give a perfect vector for misinformation.”

A minute’s collaboration hammered out a rough script, and with a final nod, Dusty pressed the button on his broadcaster. “Hey, Bitsy. We can’t make out the militia traffic from down here. Have they relayed any information on Serenity forces in the area?”

\leavevmode\llap{“}Nothing recent,” Two Bits replied. “Last contact was some sporadic fire just after sunset. Things have been quiet since then.”

Dusty blinked, then cast a glance my way. That was much earlier than either of us had expected. Despite that, I gave Dusty a quick nod, and he turned back to his radio.

\leavevmode\llap{“}Well, uh… I don’t suppose they have any idea where they went to? Because I expected them to try to hit us before we regrouped, and this whole silence thing makes me think they’re up to something. I’ve been around a changeling long enough to know how tricky they can be.” He paused, visibly measuring out about half a second before adding, “Uh, no offense intended, Whisper.”

I flashed a sly smile before returning to neutral and hitting the button on my own broadcaster. “None taken. It’s a fair assessment. And I’ve got to agree with Dusty. You don’t throw away an advantage unless it gets you a better advantage. If they’re going to take advantage of this situation, it’s going to be soon.”

There was a long pause before Two Bits spoke again. “You think they’re setting an ambush, then?”

I blinked; even when one couldn’t be seen, keeping one’s physical reactions in line with one’s act is a good way to keep in-character. “That wasn’t quite what I was thinking, but it’s certainly a possibility.”

\leavevmode\llap{“}What were you thinking?”

\leavevmode\llap{“}We’re moving slowly, under a very visible cloudship, and this dry creek bed gives a very clear idea of our course. They’ve probably kept tabs on us since Pale Sands, and even if not, they probably saw the \textit{Cumulonimbus} an hour ago, if not more. We’re behaving predictably. So if I were them? I’d bury a few hundred pounds of explosives or some balefire eggs along a stretch of the creek. Either set some trigger or command detonate it when the lead vehicle hits the furthest explosive. They’ve probably had scouts or spies watching us to tell them exactly how long to make the kill box.”

A nice and plausible reason to avoid going through that particular stretch of Wasteland, with the added benefit of being completely incorrect.

There was a notably longer pause before Two Bits spoke again. “Shit. Yeah that makes a lot of sense. We’ll need a new route. Dusty, can you handle that?”

\leavevmode\llap{“}I’m on it,” Dusty said, a smile touching his lips. “And you might want to get ahold of the militia, tell them what’s going on so they’re ready to move. If we do run into something, we might need their help.”

\leavevmode\llap{“}Will do,” Two Bits replied, followed by radioing ahead to the main army. “Militia lead, Ranger lead…”

Dusty sat back in his seat, nodding to Starlight. “Okay. Take us up to Axle.”

The wagon rocked as we pulled out of the line and accelerated forward. Over the noise of our travel, I would have missed Echo’s snort if she hadn’t followed it up with words. “I am fairly certain you just told an elaborate lie without a single technical falsehood.”

I smiled over my shoulder. “In my profession, that’s what we call ‘a good lie’.”

Her expression tightened slightly, broken only by another snort, as if she were too proud to admit that she found the statement amusing.

Sickle, naturally, was less restrained. “Yeah, Whisper’s all proud about how much of a weaselly little shit she can be.” At least her tone was amused, though it immediately darkened. “Also way too proud of steering us \textit{away} from fights.”

\leavevmode\llap{“}Don’t worry,” I said, holding a steady expression despite my sudden urge to frown. “I’m sure we’ve got a big fight ahead of us. Plenty of time for you to have fun.”

\leavevmode\llap{“}Plenty of time for me to have fun right now,” Sickle said, grinning beneath her muzzle, but she didn’t press the matter.

We bounded past several Trotsen motorwagons before pulling up beside Axle’s. I lost most of their conversation as I pressed a hoof over my ear, isolating the voice coming across the radio. The channel indicator showed \textit{01}. “Alpha, new sigint update. Incoming enemy forces might be diverting to take a less predictable path. Orders for now are to continue to hold position, but keep eyes out and be ready to move quickly. If they change course, you’ll need to displace quickly to new positions.”

Whoever Alpha was acknowledged the call, and the information started filtering out through lower-level commanders across multiple channels. As for myself, I looked at the clock on my PipBuck, noting the time.

I remained silent until Dusty had directed Starlight onto a new heading. We pulled away, and behind us, the Trotsen’s motorwagons turned to follow us. Then I spoke up. “There was barely a minute between radio intercept and intel being passed on. They’ve got good signals intelligence, probably directly attached to…” I paused, counting the levels the radio information had filtered through. “...either company or whatever level is above company, I’m not quite certain.”

Dusty gave a low whistle. “Battalion, I think? Or was that regiment? I’m not sure. The Militia rarely deploys even a single company as a whole. It’s more a few squads here and there, maybe a platoon if something big is going down. Going above company level is some old-world shit.”

While our motorwagons raced north across the barren Wasteland, almost parallel to the line of hills where Serenity lay in ambush, I returned to my map and radios. There was still regular chatter, mostly on lower-level channels. I made the occasional note, slowly getting a better picture of their communications structure.

A couple minutes later, the indicator for channel 00 gave a brief flash. The PipBuck I was using to listen in on Serenity blinked a message: “Map updated.”

As I switched over to the map, channel 01 opened up again. “Alpha, reference tags ‘Hill 1’ and ‘Hill 2’. You’ll be setting up a defensive line between those two positions. Move on the west side of the ridge to keep out of sight until you’re in position.”

Sure enough, two new map tags had appeared on my map. Fancy. Channel 00 was probably a data channel, then. I made a mental note to whip something up to extract any data coming across that for more immediate use, then filed it away for later as I switched to my own map screen, adding marks at the same location.

With that done, I scooted forward. “Hey,” I said, sticking my PipBuck out beside Dusty. “Serenity’s moving an entire company to form a line between these two points.”

He leaned over the screen, squinting for a moment, then muttered something obscene under his breath. “Of course they are. Are they there yet?”

\leavevmode\llap{“}Not yet. The call to move went out about thirty seconds ago.” I glanced back another PipBuck to see most of the lower-tier channels broadcasting. The one automatically picked up in my ear was relaying the basics of the command. “Seems the command is still filtering down. They haven’t started moving yet, but it’s probably just seconds away.”

\leavevmode\llap{“}Shit,” Dusty muttered, switching to his own map. He scrolled around, eyes darting from feature to feature. “Damnit, it’ll be close. Star, turn northwest and step on it. In a quarter mile, you’ll hit a dirt track. Follow it left.”

\leavevmode\llap{“}You got it,” Starlight said, the vehicle lurching slightly as we turned, the engine roaring louder. I slid back into my seat, grasping my equipment in my magic.

I’d just gotten ahold of the last datastore when a new channel lit up. 82. I switched away from the squad-level discussions and caught a broadcast in-progress. “—voy is starting to make their run. Looks like they’ll be coming in on the caravan route.”

The broadcast was strong and clear, without a hint of audio artifacts. That would be our tail, the scouts that Serenity commander had noted. That channel immediately went on the priority list.

A much more distorted voice replied in acknowledgement, and the channel went silent. I switched over to channel 01, waiting.

Fifteen seconds later, the commander’s voice returned. “Alpha, command. The convoy is starting its run. They should be coming in along the caravan road. Are you moving?”

\leavevmode\llap{“}Command, Alpha is stepping off now. We’ll beat them there. How long until they reach that line?”

\leavevmode\llap{“}Unknown. I’ll find out.”

So, a fifteen second gap between the scout’s report and the commander passing the information on. Assuming there were no other factors involved, that would suggest a single relay to get the information to the commander. That seemed like a natural division of labor. The commander in charge of the overall leadership, with subordinates coordinating other elements and passing on relevant information. It reminded me of the command center back home.

Back on channel 82, someling was asking the scouts for an estimate on our arrival. Our vehicle lurched, then turned again, the ride smoothing out just a little. Looking forward, I could see we were on a winding but relatively flat section of land that could be generously described as a road.

\leavevmode\llap{“}Hey, Dusty!” I called out over the sounds of the vehicle. “Is this the same road the Trotsen caravan usually uses?”

\leavevmode\llap{“}Yeah. Why?”

The scouts gave their answer: five or six minutes.

\leavevmode\llap{“}Because they know we’re coming in on it. Some scouts are trailing us, relaying our position.”

\leavevmode\llap{“}Guess that’s no surprise,” he called back, bracing as we roared around a corner. Through the front window, I could see the hills where Serenity changelings were hoping to ambush us.

Channel 01 broadcast again. “Alpha, command. Enemy forces will be hitting your line in five minutes. Will you be able to get in position in time?”

\leavevmode\llap{“}It’ll be tight, but we’ll make it.”

I inwardly cursed before calling out to Dusty again. “That company is saying they’re going to beat us there.”

I could see Dusty saying a quiet curse, though it was lost behind the rattling and engine roar. He looked over his shoulder, calling out louder. “By how much?”

\leavevmode\llap{“}They’re saying it’ll be tight.”

\leavevmode\llap{“}Good! And they’re coming in from the south?”

\leavevmode\llap{“}Yes.”

He was looking at his map again. “Okay. We’ll keep going. If we start getting close, we’ll just pretend like we saw them and swing north. They’ll have a hard time crossing the valley without the \textit{‘Nimbus} seeing them.”

I hesitated, uncertain of how good of a plan that was, but finally nodded. “Sounds good.” He was the tactician. I was just providing the information. I’d have to trust that he was as much of a professional as I was.

The hills drew rapidly closer.

My right ear filled with a crackle of static, followed by Two Bit’s voice. “Got eyes on changeling fliers, two-eight-five. Maybe… two miles out, flying left to right along the backside of those hills.”

He was answered by Hail Burst, her voice firm and grim. “We see them.”

I looked out to the hills again. I couldn’t see anything. They must have been flying low enough to remain concealed from those of us on the ground.

My left ear crackled. “Alpha, be aware, enemy air has spotted you.”

Less than ten seconds from intercepting communications to relaying emergency information. They had a solid sigint setup. I was looking forward to destroying that advantage.

A deep sound thundered over the sound of our motorwagon. I leaned over to the window to see the bolt of magic fire streaking through the air, a fuchsia so vivid and bright that it looked like some unnatural tear in reality. It sailed out toward the hills ahead like a vengeful meteor. A moment later, there was a second flash from one of the cloudship’s great cannons, sending another bolt on its way.

I turned back to my equipment. The radio net was going wild. I tuned to channel 02, which I had concluded was their Alpha company channel. Redundant reports of the incoming fire were coming in, until the commander spoke over them, barking short, quick orders. The last command was for the first platoon to hurry north to the opposite hill.

The replying changeling was less optimistic about this plan. “One will try, but that’s a lot of open air to cross.”

Dusty wore a grim grin as he directed Starlight, and we veered right, aiming to swing well clear of the hill the Loyalists were pummeling. It was a terrifying amount of fire. The massive ventral guns threw up huge plumes of smoke and dirt with every shot, and their heavy firepower was supplemented by several smaller turrets letting loose a withering hail of smaller bolts. Even in its diminished state, the firepower a Raptor could bring down was nothing short of awe-inspiring.

The streaks of magic, bursts of flame, and swirling smoke and ash rapidly choked the side of the hill. It almost hid the flying forms emerging from behind the hill, still a mile away. I quickly leaned forward to point them out, automatically mimicking the very professional-sounding mannerisms I’d been hearing on the radio. “Dusty, I’ve got eyes on Serenity soldiers in the open, moving to cross the road to the northern hills.”

He gave a quick look the way I was pointing, followed by a sharp nod before keying up his radio. “Hail Burst, some of those changelings are slipping north across the valley. Can you pin them down?”

Her reply was as methodical as before. “We’ve got them.”

Several seconds later the fire shifted. The impacts of the smaller guns rapidly swept sideways along the hill, and suddenly the bolts of magic were raining down among the flying changelings. Much as with the Loyalist’s approach to the \textit{Cumulonimbus} the previous day, they were too far away to be easily hit, but from what little I could see, it was disrupting them. Changelings veered this way and that to avoid being hit. Their northward advance was halted in a moment, and soon I saw several flying off to the south again.

Two Bits was on the radio again. “Militia lead, Ranger lead. We are in contact to our west, your east-southeast. If you’ve got any mobile forces ready to assist, we’d appreciate it.”

To my relief, the reply was understandable, if still a bit heavy with static. “Copy that. We can see the fireworks from here. Keep it up. Mobile forces are on the way.”

\leavevmode\llap{“}Fuck yes,” Dusty said, allowing a grin before quickly turning serious again. “Whisper, any sign of other forces in the area?”

\leavevmode\llap{“}None that I know of,” I said. I was starting to lose sight of the Serenity force as we came around the slope of the hill we were approaching, the valley slowly slipping away behind it. “None that have been broadcasting. With how urgently they were trying to get to this hill, they probably don’t have any other forces in the area, but I couldn’t swear to it.”

\leavevmode\llap{“}Probably,” he noted, but nodded. “Okay. Starlight, keep straight ahead. We’ll go over the hill here and swing wide of all that stuff to the south.”

The engine roared as we climbed the slope, weaving around the occasional rock or scraggly bush. A couple of the more agile Trotsen wagons weaved and roared past us, and as we climbed the slope, we drew closer and closer to the Raptor’s protective cannons, pouring out fire into the valley. I switched the receiving PipBuck to play all channels again, the earbud exploding with multiple overlapped conversations. I could only pick out occasional snippets of elevated voices and urgent reports. The idle amusement of earlier was gone, but despite the tremendous amount of fire, there was no panic evident.

We came over the crest of the hill at full speed, and I looked out the window to see the shallow valley still being peppered with cannon fire. Dead trees and bushes burned with unnatural colors, and a pall of dust and smoke choked the air. I could only barely pick out the forms of a few changelings. Only a few had made it past the road, and one of the small cannons was tracking them, bolts slamming into the earth around them as they moved.

A louder voice, laced with excitement, cut over the cacophony of radio chatter. “Vics cresting due north!”

Barely a second later, my heart lurched as a thin stream of magical bolts flew from those same changelings, still half a mile away. The shots arced up into the air, but fell behind us, peppering the entire slope of the hill with inaccurate fire. I clung to the edge of the window as we plunged down the slope. The \textit{Cumulonimbus} was answering their fire with the heavy ventral turret, but still more shots came our way. I didn’t see where they were going, as my attention was suddenly drawn to the radio. A voice was loudly and clearly shouting over all the others. “Fall back! Fall back!”

Channel 02 lit up, and I switched back to single-channel to listen more clearly. “All platoons, disengage and fall back immediately. Keep altitude to avoid ground splash. If you have wounded, evac them, do not stop.”

As acknowledgements came in, channel 01 lit up, and I switched to follow. “—mand, Alpha. Friendly forces are under Raptor fire and withdrawing south. Enemy ground forces have bypassed us to the north. Unable to pursue without engaging enemy air.”

\leavevmode\llap{“}Copy that,” the replying changeling said, her tone professional, but I thought I could hear a hint of disappointment or disapproval in her voice. “Do not engage the \textit{Cumulonimbus}. Fall back to your original positions and await further orders.”

\leavevmode\llap{“}Understood.”

I grinned. “Dusty! They’re pulling back!”

\leavevmode\llap{“}Good!” He said, flashing a smile, and ignoring the wildly inaccurate shots peppering the ground on either side of our convoy. One landed maybe fifty feet in front of us, eliciting a blurted curse from Starlight as she swerved away from the flash of flame and bits of kicked-up dirt. It was the closest that any shot got to hitting us.

Moments later, even that fire ended. In the distance, I could see black forms swerving and speeding south, the cloudship’s magical fire still raining down around them.

A minute later, the last changeling disappeared behind a ridge some two miles away. The guns of the \textit{Cumulonimbus} fell silent.

{\br}%
We pulled into the edge of the army camp some five minutes later, flanked by the motorwagons that had rushed out to meet us. Mareford Militia ponies were already dismounting from the lead vehicles, trotting to take up defensive positions.

The camp itself was spread across the valley floor, with more ponies set on the low hills on either side. We could just see the front line of troops ahead, dug into whatever cover they could get. A few clusters of boulders and some rocky ridges made for natural defenses, and I could see a few heavy weapons situated among these. It made for a decent defensive position, about a mile across. Dusty was already on the radio, passing on the need to spread out further. The knowledge that Serenity had a balefire bomb made even that wide space feel claustrophobic.

The only comfort was that they had fought hard to keep us from regrouping intact. Their initial plan wasn’t to gather the army in one place and wipe us out with the megaspell.

Of course, plans change.

Many of the Trotsen ponies were cheering and laughing as we pulled in, sharing waves with their compatriots as they rejoined. Any disappointment over the failure to secure the megaspell had been relieved by evading Serenity’s trap. Even the Gemstone ponies were getting into the mood, laughing amongst themselves. Dazzle was probably the most composed, kicked back against the roof-mounted plasma cannon as the motorwagon bearing it pulled up. She was smiling softly, her short mane flowing silkily in the breeze like some mane-care commercial. Even lightly coated in dust, she managed to look cleaner and more well-kempt than everypony around her.

The motor of our wagon hummed softly as we pulled up beside another vehicle, and with a final faint whine of metal, we came to a stop. Echo dismounted immediately. I was honestly a little surprised she’d lasted that long. I know she was insistent on remaining close to protect me, but she had spent most of the time pressed firmly against the side of the cargo bed, as if to get just a little less contact with Sickle. Sickle, of course, sprawled as lazily and lewdly as ever. She remained sprawled out as I slid out over the back of the seat and conjured up my magic, retaking my queenly disguise.

There were a few looks from various ponies, of course, but none that particularly lingered. It seemed they were becoming more accustomed to me. I idly pondered whether looking like a queen was a help or hindrance. On the one hoof, it was bigger and scarier. On the other, it was very unlike the changelings they had been fighting. I let the thought fade, leaning gently against the roof of the wagon as I looked around the camp from my slight vantage point.

Despite how well-established the defensive lines appeared to be, I could see that Serenity had caused some damage. Small craters pock-marked the ground near the defensive lines. A pair of much larger craters crossed the front line, providing new defensive positions. The explosions that caused them must have been massive. Balefire eggs, perhaps, or a heavy bomb dropped from high above. Another pair of craters were in the midst of the camp, with one still surrounded by tents. Of the scant brush and rare dead tree near the defensive line, almost all were charred.

And then there were the dead. Out past our lines, I could just make out some twenty or so black forms, scattered across the ground or clustered around rocks and other cover. Behind our lines, I could see patches of freshly-dug earth, arranged in neat lines. There weren’t as many as I had feared, but still more than I had hoped.

Dusty climbed partially out of the window to sit on the rim. “Hey, Whisper. Two Bits is trying to get all the leadership and faction representatives together to see if we can’t unfuck this mess. We need to get this army moving, sort out the chain of command, that sort of stuff. I’m thinking our resident changeling queen should be there.”

\leavevmode\llap{“}I’ll be there,” I said with a nod. I may not have gotten much sleep, but that didn’t seem like a problem. “When and where?”

\leavevmode\llap{“}ASAP,” he replied, then inclined his head toward the nearby tents. “The Militia commander has a headquarters tent we’ll be using. I’m going to go round up the ponies that don’t have a radio.”

The mention of the radio reminded me of my own plans. “I assume Hail Burst will be at the meeting?”

\leavevmode\llap{“}Of course. Why?”

\leavevmode\llap{“}I was thinking of what we discussed earlier.” I gave a little smile. “Go ahead and get the others. I’ve got a radio call to make.”

As he departed, I raised my PipBuck and pressed the “transmit” button. “Hail Burst? This is Queen Whisper.”

There was a long pause before her voice came across the radio, sounding so tired that I imagined the preceding silence had covered up a deep sigh. “Yes?”

\leavevmode\llap{“}I understand you’re coming down. I was hoping I might ask a favor of you. I know you’ve recovered a good number of PipBucks. I’d like to make use of them. All of them, if possible, or at least what you can spare.”

There was another pause before she replied. “Why do you need them?”

\textit{Thank you for asking that}. “Not me, specifically. A sizable portion of our force has no radios, and it’s already caused some issues with communications. In addition, I’ve been poking at that program Serenity uses to encrypt their communications. I can’t access most of it, but from what I can tell, we should be able to feed it new encryption keys, at which point we can talk without them listening in on us.”

When she spoke again, there was lightness to her tone. Not quite excitement, but more of a relaxing. It seems I was delivering good news. “Well that could be damn useful. If you’ve figured out their encryption, does that mean we can listen in on them?”

My first thought was that I really wish she hadn’t said that. Despite that, I put on a wry smile, looking for all the world as if I was taking the statement in light humor. “I wish. No, cracking encryption is impossible, or close enough. The PipBucks we’d captured presumably still had their encryption keys entered, and I was hoping it would let us listen in on them, but it seems they’ve changed keys since our encounter yesterday. Given that these are changelings who have remained hidden in secrecy for centuries, I’m guessing they take information security very seriously. They’re probably changing keys regularly to prevent exactly what I was trying to do.”

\textit{That’s right, Serenity. Your daily key changes are making my job harder. You should keep doing that.}

\leavevmode\llap{“}Okay,” Hail Burst said, with a subtle flatness that suggested she didn’t really care about the fine details of what I had said. But then, they hadn’t been for her.

Before she could say more, I continued. “But we should probably reserve any further discussion until we’re either face-to-face or have our own encryption up. If we can’t listen in on their communications, at least we can level the field. So, could you spare those PipBucks?”

This time she keyed in before sighing. “Yeah, I’ll bring them when I come down.”

\leavevmode\llap{“}Thank you.”

{\br}%
Half an hour later, we converged on the army’s makeshift headquarters. It was little more than a canvas shelter over a folding table. I was among the first to arrive, having followed Dusty in, and lay quietly beside him. While I planned to offer what help I could, I remained silent for the time being. I was getting enough uneasy looks without inserting myself into conversations where I wasn’t needed.

Fortunately, most of the ponies that attended the meeting were already familiar with me. There weren’t any random observers. While every faction had a couple representatives, guards were set to keep most ponies well away from the meeting. The last thing we needed was a Serenity Infiltrator walking into the meeting with a balefire egg and incinerating the entire command structure of our little army.

I found myself in a place long since made familiar through my years as an Infiltrator: lying there, nice and relaxed, apparently distracted by work, while secretly on high alert. The E.F.S. indicators were constantly in my awareness, ready to show the first sign of hostile intent. The PipBuck concealed in my saddlebags sat ready to feed any Serenity transmissions into my ear.

While it was a fairly exclusive meeting, there were still a good number of ponies there. Two Bits was accompanied by Sandalwood, the senior member of the regular Militia units and Two Bits’ second-in-command. Hail Burst had another soldier I didn’t recognize. And there was an ever-irritated-looking Sandstorm, with Axle at her side.

Dazzle was there to represent Gemstone, having somehow found a way to clean the dust from her coat. Arclight had come with her. Seroon was there, too, whether as an advisor or as the representative of the few members of his tribe who had come along with our army. And of course, there was Echo, who insisted on remaining by my side for protection, Sickle, who was probably just bored, and Starlight, who figured that if everyone else was going, she should too.

While the various ponies talked, I tended to the small pile of PipBucks Hail Burst had brought down. Each one needed a copy of the slightly modified radio encryption, as well as wiping and resetting their tags so Serenity couldn’t easily track them. It was trivially easy, which also meant it didn’t distract me very much. It was just a little time consuming.

I also made the point of recording the new tags to my own PipBuck. I didn’t want Serenity tracking them, but being able to track them myself seemed like a useful piece of information. My meager experience with combat had taught me that quality information is particularly hard to come across in the heat of battle.

The initial matter the gathered leaders discussed was also the most immediately important: survival. Specifically, ensuring that Serenity’s new megaspell couldn’t simply wipe out our entire army. Most of the discussion dealt with the precarious balance of needs. If the army was too tightly packed, then it could be gutted or even outright destroyed with that single weapon. If it was spread out enough to minimize losses, then Serenity could launch conventional attacks on isolated forces, devastating them and pulling back before we could bring our weight to bear. “Defeat in detail”, as Dusty called it, a term that I silently filed away for later use.

The solution was to keep forces spread out in clumps, with a heavy and highly mobile force ready to relocate on a moment’s notice. Fortunately, we had plenty of room; Serenity forces had fallen back to positions about five miles out. Or at least, that’s what our limited ground-based scouts had determined. Dusty was optimistic that airborne scouts would greatly improve that information.

Of course, the plan relied on that mobile force getting to where they were needed in time to help. Between the Trotsen motorwagons and the Loyalist cloudship, we could move a lot of firepower, but we needed to do so quickly, at the first sign of trouble. If not, they might be too late to help.

The first part of the solution was scouting. I missed some of the details with my work, but the gist of it was that the \textit{Cumulonimbus} would give a high vantage point to watch for approaching forces, while the whirligigs would roam outside our lines, hoping to detect any incoming attacks even earlier. Then came the more difficult part.

\leavevmode\llap{“}The main trick,” Dusty had said, “is coordination and communication. That’s especially true once we get this army moving. We need scout reports to get back quickly, and for us to get the reaction forces moving in the right direction as early as possible. Trotsen’s motorwagons might be quick, but the lack of radios makes it hard to get word out fast enough.”

He stepped back, more even with me, and inclined his head my way. “Fortunately, Whisper has a solution.”

I looked up from the PipBuck I was working on. I considered standing, but given the size difference, I chose to remain sitting and, hopefully, a little less threatening. I quietly cleared my throat, and spoke. “One of the problems we’ve faced is a disparity in information and communications. Serenity likely still has some spies, and certainly has gathered detailed information on us and our forces. Meanwhile, we’ve had problems just getting information to the individuals who need it, especially without Serenity being able to listen in. We’ve had to resort to face-to-face meetings like this for conveying any sensitive information. That works for planning stages, but once things become active, the rapid and secure distribution of information becomes key.”

My horn lit up, casting its soft green glow as I lifted one of the borrowed PipBucks. “This is one of the greatest advantages Serenity has. Serenity came from a Stable, and every one of their soldiers appears to have either a PipBuck or power armor. That means they can all be in communication. A scout or spy can discover some information, and seconds later it can be filtering out through their army. Worse yet, they’ve found a way to do so without us overhearing them.”

I slowly rotated the PipBuck, as if showing it off. “We captured a small number of Serenity’s PipBucks yesterday, and I’ve spent the time since going over them. They each contain a very complex multi-channel radio encryption spell. They can pass information quickly and securely, meaning they can coordinate their army far more effectively than we can, and without giving us any information.

\leavevmode\llap{“}I’ve found a way to change that balance.” I turned the PipBuck to show the radio screen, with the Serenity-modified interface. “The spell itself is partially encrypted, but I’ve been able to make some minor modifications to serve our purposes. I understand the Mareford Militia already has enough PipBucks to support their communications, but with the ones we have captured, we have enough to outfit other key positions. For example, the commanders of most of the motorwagon force.”

I saw Sandstorm’s ears twitch and perk a little higher. I’d just said that I intended to give her a good number of PipBucks. I’m not sure if she was pleased by the gift, suspicious of my intent, or both.

\leavevmode\llap{“}Additionally, the encryption spell means Serenity won’t be able to listen in on us, either. We can pass on information quickly and securely. We both alleviate one of the problems we’ve been facing, and remove one of Serenity’s advantages.”

I finished by turning to look to Dusty, who nodded in reply. “Thank you. With this, we’ll be able to easily coordinate our response to any action Serenity takes. We can talk to Sandstorm on the command channel, and she can pass on information to her riders through their own channel. With each wagon carrying additional troops, we can have them scattered around the army for support and scouting, but if Serenity starts to push us somewhere, we can rapidly redeploy them for support.”

Sandstorm’s expression darkened. “Right. So you’re relying on us for all the fighting.”

Sickle barked out a laugh. “Shit, I thought you were \textit{here} to fight, now you’re whining about it?”

\leavevmode\llap{“}Fuck you, bitch!”

\leavevmode\llap{“}Any time,” Sickle said with a grin.

\leavevmode\llap{“}That’s enough,” Dusty said, taking a step forward. “And no, we’re not having you do all the fighting. We might just have Militia troops riding along with you. Maybe some heavy weapons teams, too. Gemstone’s cannons proved themselves yesterday.” He finished with a nod to Dazzle, who smiled in return.

\leavevmode\llap{“}I’ve been sitting on that gun for a few years, now,” she said with a soft chuckle and a shrug of her shoulders. “I’m kind of glad I got to put it to use.”

Sandstorm muttered something, but didn’t push the matter.

Dusty returned to sit beside me as Two Bits spoke again. “We can work out the details later, but I think between radio-equipped motorwagons and the \textit{Cumulonimbus}, we’ve got a decent reaction force. Before we get to that, though, I think there’s something else we need to resolve.” He paused, gesturing around with his hoof. “This? What we’re doing now? Well, it needs to change.”

Several voices spoke at once, and he quickly held up a hoof. “Listen! We’re basically running things by committee here. Once we’re in the shit, we can’t be wasting time debating and negotiating. You heard what Queen Whisper said. They’ve got good communications. That means they’ll have one voice at the top that can call all the shots. Maybe their own queen. That means they can act quickly and in unity, without having to convince parts of their army to go along with a plan.

\leavevmode\llap{“}Right now, they act faster than us. Hell, just trying to coordinate things yesterday was a pain in the ass, and that was just a small part of our force. Sooner or later, we’re going to face Serenity in a major battle, and we can’t do that if we’re divided. We need somepony, one voice, calling the shots when things get hot.”

\leavevmode\llap{“}Oh, right,” Sandstorm said, eyes narrowing again. “And I suppose you’re oh-so-graciously volunteering for the job.”

Two Bits snorted out a laugh. “Fuck that. That job sucks. Actually, I’ve got somepony much better in mind.”

He raised a hoof, and to my surprise, gestured my way.

I blinked, my ears folding back. “What? Oh, no, no, no. I’m a horrible choice! I have no military experience. I barely know enough to keep myself alive in a fight. I’m completely unqualified to be a military leader, and that’s not even considering the social impact of trying to put a \textit{changeling} in charge!”

Two Bits’ hoof had lowered slightly, and the corner of his mouth twitched upwards slightly. “Not you,” he said, a hint of humor to his voice before his hoof came up again. He wasn’t pointing at me. He was pointing just beside me. “Him.”

I looked over in time to see Dusty blink, his ears shooting up. “What?”

\leavevmode\llap{“}Oh,” I said, and gave a small nod. “Yes, that makes much more sense.”

\leavevmode\llap{“}No it doesn’t!” Dusty said, looking back and forth between me and Two Bits. “I was a sergeant. The most I’ve ever led is a single squad, and even that was years ago.”

Two Bits had a very pleased smile, bordering on smug. “I seem to recall some ops where you were directing a lot more than just a squad. How many units were involved in the Firestorm raid, or the east crater cleanup? Hell, yesterday and today would have gone a lot worse if you hadn’t stepped up like you did.”

I was nodding thoughtfully. “You’re also an independent. Someone that can be looked on to make decisions fairly, rather than being biased for or against any one faction.”

He shot me a sharp look. “I came from Mareford.”

\leavevmode\llap{“}And you left when you became concerned about their actions. You put what was right over blind obedience and partisanism.”

He grunted, but didn’t argue it.

Two Bits joined in again. “You’ve also got the ear of every single leader here. You helped bring everypony together, and they’re at least willing to listen to you. As far as I see it, you’re the best pony for the job.”

Dusty frowned, silent for a moment before jerking his head toward Hail Burst. “What about her? She’s active military, even.”

She snorted, and I thought I caught a hint of amusement behind it. “Hey, I was a sergeant too. Besides, I’ve got my hooves full handling the \textit{‘Nimbus}. I’m not going to pledge loyalty to some commander outside of the Enclave, but if you’re stepping up to run things, I think I could follow your lead for now.”

Dusty’s ears fell flat.

Two Bits looked around. “Any objections? Sandstorm?”

She grimaced, glaring our way for a few long seconds. “...Fine. For now.”

\leavevmode\llap{“}Good!” Two Bits said, turning back to Dusty. “Then I guess it’s decided. Welcome to command.” He flashed a smile. “Sir.”

Dusty grunted. “Don’t call me that, Bitsy.”

Two Bits laughed. “Yes, sir.” A few ponies snickered. I couldn’t help a smile.

Dusty just grunted again, deeper.

\leavevmode\llap{“}So,” Two Bits said, still smiling. “Now that that’s settled, what’s the plan?”

\leavevmode\llap{“}Fuck if I know,” Dusty replied. “You dump this on me and expect me to have a plan already? Shit.” He sighed, shaking his head. “It’s getting late, and we still need to get those PipBucks and encryption out to everyone. We’ve already lost a lot of time. We need to get moving first thing in the morning. I’ll… I’ll work something out by then. Just tell everyone to be ready to move at dawn.”

Two Bits nodded, his smile now thoroughly smug. “You got it, sir. Anything else?”

Dusty rolled his eyes before replying. “Nothing I can think of. Not much to do until morning, except helping Whisper get our comms squared away.”

He looked to me, as if looking for a response. “I have a few more PipBucks to finish working on, then I’ll be ready to start making rounds. Say, thirty minutes?”

\leavevmode\llap{“}Good, get on that.” Dusty stopped, looking around the group. “...Dismissed, I guess.”

The small crowd dispersed. I followed Dusty back towards our motorwagon, silently amused by his reluctance.

As soon as we were no longer surrounded by ponies, he grumbled. “Well, shit.” He stopped, looking back—and up—at me. “Did you really have to back him up on that?”

I smiled gently in reply. “Can you think of a better pony for the job?”

He grunted again. “Doesn’t mean I’m happy about it.”

Sickle walked by us, speaking out in a mocking tone. “Oh, whaaah, I’m in charge of the biggest army in two hundred years, my life suuuucks.” She continued on her way, snickering.

He just sighed.

I raised a hoof, gently touching him on the shoulder. “Two Bits was right, though. You guided things through the fights yesterday and today. You took charge when it was needed. This just means that you’ll have an easier time doing it.” I smiled a little more. “It also makes my intel work simple.”

He heaved another sigh. “Yeah. I guess it does.”

\leavevmode\llap{“}If you want to help me out, though, I could use a good communications plan for our force. Some plan to break down different units into individual channels. I’ll need that before I start giving out encryption keys.”

\leavevmode\llap{“}Hmm.” He looked thoughtful as we started to walk. “The Militia and Rangers already have a comms plan. I could probably use that as a basis for the rest of the army. Might need some help with that, though.”

I gave a nod. “Just tell me what you need.”

{\br}%
Reprogramming the last of the PipBucks was mostly just rote repetition of the same task, which left me plenty of time to help Dusty lay out a basic plan of how to arrange our radio network. While my PipBuck screen was filled with spell matrix outputs and internal system settings, his displayed a text file, steadily doling out radio channels to the diverse collection of forces we had assembled.

Throughout the day, there were the occasional, scattered transmissions from Serenity forces. Mostly, they weren’t immediately important. Status updates, low-level movements, stuff like that.

We were almost done with our planning when a transmission caught my attention. “All forces, be advised: package Braconid is entering the AO from the northwest. Expect arrival at enemy camp in ten minutes. Be prepared for updates and orders as the situation develops.”

My ears flicked back, and I turned to my small PipBuck array. The transmission had been on channel 01, their apparent headquarters channel. “Dusty, Serenity might be up to something. What’s an AO?”

\leavevmode\llap{“}You mean Area of Operations?” he asked, as if I would know. “Basically just means the area a mission or operation is taking place in. What’s up?”

\leavevmode\llap{“}I’m not entirely sure, but they just alerted their entire force. They’re sending a ‘package’ to our camp. It’s northwest, ten minutes out.”

\leavevmode\llap{“}A package,” Dusty echoed, his own ears twitching a little. “That sounds ominous. Vague, but ominous.”

\leavevmode\llap{“}It’s possible it’s their megaspell,” I said, my heart beating a bit harder. “Could be just about anything.”

\leavevmode\llap{“}But clearly something important.” He frowned, still for a moment. “Ten minutes?”

I nodded.

\leavevmode\llap{“}Okay,” he said, slowly nodding. “I’ll give the scouts three minutes, but if nopony sees anything, I’m sending out an alert. If that’s the megaspell, it could do a lot more damage than just losing your spying.”

I frowned—I really didn’t want to lose this advantage I’d just gotten!—but nodded. Even with the army dispersed, a megaspell could still do tremendous damage. “Agreed. Though at least try to pass it off as if you saw something. It might not fool them, but it’s worth a shot.”

He agreed, and we sat in tense silence for any word. A minute passed. Two minutes.

Two and a half minutes, and my earbud crackled. “Command, Ranger Lead. Vulture has eyes on suspicious activity. A flight of changelings, about eight strong, just flew past Serenity positions to the northwest. They’re flying high and level, straight toward the main camp.”

Dusty quickly raised his broadcaster, his expression serious. “Copy that. Get me some details. What kind of force is this?”

\leavevmode\llap{“}They look lightly equipped. No power armor. Might be a scout team, but eight—no, seven, seems a bit heavy for that.”

Dusty frowned, silent for a moment before speaking up. “Understood. Keep tracking them. Everypony else, I want you on full alert. Keep eyes out in all directions. This could be a diversion.”

Several voices sounded in reply. Dusty turned, our planning abandoned for the moment, and hauled himself up to sit on the edge of the window. While he peered through his binoculars, I carefully set aside my PipBucks and scooted over to do the same.

Two Bits called again. “Command, the changelings just split. All but one peeled off and are heading back towards Serenity’s lines. The last one is holding course.”

Dusty raised his broadcaster to speak. “I see them now.” Letting off the button, he cast a glance my way. “Suicide mission?”

Hail Burst’s voice sounded in my ear. “\textit{Cumulonimbus} has eyes on. Standing by.”

\leavevmode\llap{“}I don’t know,” I said, raising my own binoculars and hunting the skies for the distant changelings. “I’m inclined to say no, but some changelings could be very fanatic toward their queen, and Chrysalis is a name practically synonymous with fanaticism.” A dark dot flashed across my field of view, and I panned back, finally finding the inbound changeling—and my ears immediately fell flat. “Oh.”

In the corner of my vision, I saw Dusty turn my way again. He’d no doubt caught the sudden concern in my voice. “What?”

\leavevmode\llap{“}It may be worse than that,” I said, staring at the white banner clutched in the changeling’s hooves as it flapped wildly in the wind. “They want to talk.”