There are many forms that danger can take.

The most apparent are also the most immediate. They tend to be the ones that people think of when the word “danger” comes up. In my previous life, that would have been the threat of discovery. The threat of the Ministry of Morale ambushing me, dragging me off, and extracting every vital secret I carried in my head.

In my new life, it meant raiders, corrupt mercenaries, and assassins. I had been in an alarming number of firefights. I had conducted armed and violent infiltrations of facilities. I had been the perpetrator of, witness to, or victim of multiple assassinations and attempted assassinations. I had ridden at the head of an army that marched steadily towards the inevitable violent clash that would decide the future of this land.

But immediate is not the same as greatest. Apparent is not the same as significant. The greatest and most significant dangers are often the most subtle. You do not always need an army or a megaspell to cause devastation to your enemies. Sometimes, all you need is the right word, whispered in the right ear. Nations have risen and fallen on as much.

So after all the raiders and ghouls and monsters I had faced in the Wasteland, I regarded this small, unassuming changeling as one of the most dangerous threats I had come across.

I stood beside Dusty at the headquarters shelter, watching her approach. She had initially flown near the outermost defensive line, holding back as she waved her white banner, until one of the Militia ponies had finally indicated for her to land. An entire squad of ponies walked her further into the camp. She carried nothing with her. She wasn’t wearing a PipBuck. Even the white flag had been taken from her, but the soldiers escorting her were still thoroughly wary. It was a good instinct, I thought, but probably not as useful as they might hope. The danger she posed wasn’t likely to be a physical one.

Even her appearance was a threat. She was slightly smaller than the average pony mare, both in height and weight, but she didn’t have to be. Her ears hung a fraction too low, her demeanor shy and uncertain, but showing emotion was different from feeling it. She could have looked like whatever she wanted, and Serenity could have sent any individual they liked. This was their choice, and it had meaning.

Small. Weak. Non-threatening. I’d spent most of the time since her sighting thinking on what they might try to pull, but on seeing her up close, I quickly revised those expectations. They weren’t starting off with a threat. They were starting with something more subtle and dangerous. They wanted ponies to empathize with them, even if only to a small degree.

Not that I expected her to get much mileage from the charade, of course, but it was only a part of her tactics. A hint of what was to come.

As for myself, I was already at a disadvantage, fatigued by my lack of sleep. The Mint-als made everything seem a touch too sharp, as if everything were too real. I would have gone to Dusty to make use of his coffee, but we didn’t have the time to brew it. Instead I went to Sickle, who had been so overly pleased by my request. I now had a dose of just about every drug in existence tucked away in my bags, just in case I needed it. She’d even cheerfully slipped a Dash inhaler into the mix, despite my objections.

I disliked the idea of relying on chems, but they could be useful tools, and my personal preferences came secondary to survival. Yesterday, it had been Buck and painkillers to fight off a minor concussion. Today it was Mint-als to fight off the dulling of fatigue. Both dangerous situations where I couldn’t risk being anything less than one hundred percent.

The Serenity changeling continued her slow approach until one of the soldiers called out to halt. She obeyed, slowly looking around the group with an uneasy eye. Once again, all the leaders of our army had gathered. This time all the looks of suspicion and distaste were focused on a different changeling, and with significantly more intensity.

She paused, swallowed, and quietly spoke. “Um… hello.”

There were a few raised eyebrows and glances at that, expressions that practically shouted “Seriously?” Sickle snickered as if thinking the same thing.

It was a couple of seconds before Dusty noticed the eyes turning his way, silently electing for their newly appointed commander to take the lead. He gave a momentary grimace before replying. “I take it you want to talk?”

\leavevmode\llap{“}Ah, yes,” she said with a hesitant nod before pausing again. “Um… before we begin, I was wondering, would you prefer me remaining like this, or would you be more comfortable if I looked like a pony? I know some ponies find our appearance… unpleasant.”

More displays of shyness, and now empathy and a desire to compromise for mutual benefit. I could practically see the plan steadily unfolding, and I really didn’t like where it was going.

\leavevmode\llap{“}We’re familiar enough with changelings,” Dusty replied, his head inclining toward me. I remained passive, standing tall and confident, though without looking down my muzzle as Echo was.

\leavevmode\llap{“}Ah,” the changeling said, her eyes flicking to me before darting away shyly. “Yes, I suppose you are.”

Dusty’s expression was still mostly neutral, but I detected a hint of distaste in how the corner of his mouth shifted ever-so-slightly. “How about you tell us your name, and then explain just what it is you want.”

She nodded. “Of course. My name is Cheerlight,” she said, though I suspected that was a fabrication created specifically for this conversation. “I was sent because… because my queen was hoping to defuse this situation before hundreds die. We are capable of defending our hive, but the Wasteland has already seen so much death. We may live hidden from the rest of the Wasteland, but we still don’t want to see hundred of ponies dying just because they believed a lie.”

As she ended, her eyes flicked momentarily towards me.

\leavevmode\llap{“}Ah,” I said. I might have laughed if the situation weren’t so serious. “So that’s how you’re trying to play this.”

She looked at me again, her eyes narrowing slightly even as she shifted her weight back, wings flicking anxiously. Intimidated, but defiant. Uncowed by the terrifying queen standing before her.

Dusty shot a look to me as well. “What’s up?”

I just shook my head. “I’ll let her explain.”

He gave me a questioning look that I answered with a faint smile and shrug. Then he turned back to Cheerlight. “Okay, fine. Let’s hear it.”

The changeling opened her mouth, then stopped, closing it again. Her expression was concerned. All of it was an act, I was sure. Finally, she spoke again. “I’m not sure if you’re the one I should be discussing it with.”

Dusty frowned. “And why’s that?”

\leavevmode\llap{“}Because you’ve been with Queen Whisper for months,” she said, warily eying him, glancing to the other leaders, then looking back to him once more. “We’re still not sure if you’re actively aiding her goals, or if she’s been misleading you like all the others.”

I could see Dusty’s jaw tighten. “Since we’ve been working together, the only goals she’s had have been helping her hive and stopping \textit{you}.”

\leavevmode\llap{“}Technically true,” Cheerlight said, her voice slightly quieter. “But that’s how she likes to lie, isn’t it? Yes, she wants to stop our hive. She’s been trying to destroy us for almost a decade.”

I turned my head slightly towards Dusty. “And now you see where she’s going with this.”

Somewhere that I couldn’t defend myself. Somewhere that my own skills and training worked against me.

\leavevmode\llap{“}Yeah, I see,” he said, his eyes hard. “That’s a bald-faced fucking lie.”

She gave a slight nod, though her eyes had taken on a soft, subtly pitying expression. “Because she told you otherwise, and she wouldn’t lie to you.”

Dusty bristled, but he shook it off almost immediately. Instead, his expression turned firm, serious, and calm. It was how he looked in combat. “Because we’ve been working together for two months, and she didn’t learn about Serenity until a month ago.”

Cheerlight was nodding again. “Because that’s what she told you.”

\leavevmode\llap{“}Because we were there when she discovered it, and it blindsided her. Then she insisted we investigate, and we get blindsided again.”

Her head tilted slightly, her expression sad. “I don’t think you realize how convincing an Infiltrator can be. You are aware that she claims to have spent years in old Equestria, hiding among ponies and collecting their love, yes?”

\leavevmode\llap{“}I’m more familiar with her past than you are.”

\leavevmode\llap{“}And do you have any idea how demanding that is?” she asked, and touched a hoof to her chest. “I tried to become an Infiltrator myself, so I could help feed my hive. I couldn’t manage it. It’s beyond just ‘demanding’. You have to be able to play a role perfectly, without even the slightest slip. You have to be comfortable with living a lie for years, without letting anyone in. She claims to have done this for \textit{centuries}. How hard do you think it would be for her to hold an act together for just a couple of months? To \textit{pretend} to be surprised by information as a way to convince you of her sincerity? How long did she lie to you, pretending to be something else, only to change her story later on?”

\leavevmode\llap{“}That’s a load of shit,” Dusty said, raising a hoof to point at her. “And if all you’re going to do is keep telling a bunch of lies, you can fuck right off.”

I didn’t smile, despite how much I wanted to. Dusty knew what to do. I’m glad, because for the moment, I had to remain silent. I was a known Infiltrator. A liar and a manipulator. Anything I said could be regarded with suspicion. It hardly mattered that the same could be said of her. She didn’t need them to trust her. She only needed them to not trust me. This entire little war hinged on the idea that I, a self-admitted professional liar and manipulator, was telling them the truth.

Cheerlight’s eyes had widened slightly, ears drooping, as if shocked by Dusty’s sudden profanity. She looked around, focusing on several of the other leaders. I could see the switch in tactics before she spoke, engaging the other important ponies before Dusty could completely shut down the conversation. “Please, listen to me! She’s been lying to you from the start. First she pretended to be a pony. Then she was a changeling. Now she’s a \textit{queen}. What will she be tomorrow?”

Sickle snorted out a laugh from behind me. “I’ve been trying to get her to turn into a hellhound for weeks. Maybe that can be tomorrow.”

There were a moment of silence, as ponies blinked at the unexpected comment. It lasted only an instant before Sandstorm stepped up. “Yeah, fuck all of your shit. You fucking roaches killed Raindrops, so you can take all these fucking lies and cram ‘em up your ass. I’m going to enjoy watching you all burn.”

\leavevmode\llap{“}That wasn’t us!” Cheerlight cried out in despair, then leveled a hoof at me. “Don’t you think it’s a little suspicious that a known changeling spy comes to you in the middle of a changeling scare, points you at a rival hive, and then \textit{immediately} uncovers another changeling spy? She’s been manipulating all of you from the start!”

\leavevmode\llap{“}Oh, yeah,” Sandstorm said with a derisive sneer. “And you’re all innocent and peaceful, ain’t you? Let me guess, it wasn’t you that murdered all those ponies back at Mareford, either?”

Cheerlight flinched, ears folding back, and I could already see the machinations behind the suddenly reluctant behavior. You don’t try to sell a lie you know your target won’t buy; instead, you give them the truth they know, and use that as leverage to work a different lie. “That… was unpleasant, but we’re running out of options. You were assembling an army with the goal of wiping us out! We had to do something to protect ourselves! And for the record, I was against the idea. It was an act of desperation that would make any attempts at negotiation that much harder, but… but as much as I disagreed with the decision to conduct the attack, and despite how callous and calculating the logic is, I have to agree that the conclusion was sound. If it did work, it would have stopped this conflict and removed the threat Queen Whisper poses to the Wasteland. Far fewer ponies would have died than if this turns into a war.”

Two Bits had tensed, his eyes hard. “Unpleasant? You murdered our mayor and a bunch of other ponies, and you call it \textit{unpleasant}? And now, when that doesn’t work, \textit{now} you want to talk?”

\leavevmode\llap{“}This is new to us!” she said, raising a hoof pleadingly. “We’ve only survived so long because we’ve remained hidden from ponies who wanted to kill us for centuries! We’ve never worked openly like this.” Her eyes glanced my way, her expression hardening. “And besides, you’ve had this queen whispering lies to you this whole time. She’s already poisoned you against us, and anything we could say, she could come up with a lie to counter.”

I allowed a soft snort of amusement and a faint smile. This seemed like a relatively safe place to slip in a few words. “Cute symbolic use of my name to stir up an emotional response. And I only wish these people trusted me as much as you seem to think they do.”

\leavevmode\llap{“}Some of us trust you.” It was Seroon who spoke, standing placidly a few yards away.

Cheerlight turned to him. “Because she saved you? She didn’t have to do a thing. She just let you walk along with her as she went where she was going anyway. She didn’t do it to help you. It was an act. She acts nice and sympathetic, and in return, she gets a loyal ally convinced that she can do no wrong.”

Seroon smiled softly. “And if all the people of the Wasteland were to act nicely to each other, even out of self-interest, I would dare say the world would be a much better place.”

\leavevmode\llap{“}Is that so?” Cheerlight said, her expression turning serious. “And do you know what happened when \textit{we} tried to be nice to her?”

I tilted my head slightly, signaling my curiosity. Oh, I knew where she was going with that, but it would be better to feign ignorance.

Cheerlight’s cast a sharp glare at me before jerking away, looking to Seroon and Sandstorm with a less hostile expression. “When we came across her, she claimed her hive was dead. We welcomed her into our home. And how did she repay us?” Cheerlight’s ears flicked back as she grimaced, looking away with her expression hard and tight, as if remembering some horrible injustice. “She broke into our computer to steal and destroy records, stole equipment, sabotaged the hive, destroyed our food reserves, killed six, and wounded more than a dozen changelings, many of which were unarmed workers in the wrong place at the wrong time.” Her glare returned as she faced me. “\textit{That’s} the kind of person Queen Whisper is. We extended a hoof in friendship to a lost and lonely changeling, and she stabbed us in the back.”

Dusty gave an angry snort. “You \textit{welcomed} her? You gassed us! You stuck us in some mind-fuck prison so you could feed on us!”

Cheerlight stared in surprise and confusion at Dusty. “What? But you weren’t—” Her ears flicked, mouth snapping shut. Then her expression turned to concern, and she took a hesitant half-step back. “So, that answers that question. She hasn’t tricked you. You really are helping her lie to these ponies.”

\leavevmode\llap{“}Hey.” A rattle of metal rose behind me as Sickle stood. I looked back to see her grin behind the bars of her muzzle. Her rumbling voice was amused, dark and deadly. “I was there, too, you dumb cunt. You chickenshits gassed me. Wanted to kill me in my sleep. Go on. Call me a liar again.” Any sense of amusement instantly vanished, like a light being switched off. “\textit{I fucking dare you}.”

Cheerlight opened her mouth to reply, but hesitated. No doubt she’d been thoroughly briefed on all of my companions and knew as well as I did that Sickle would have no qualms about killing her. Likely, she was considering whether provoking an attack would serve her purposes, and whether the other ponies here would be willing and capable of stopping Sickle in time. If she was really clever and devoted, she was putting more weight on the former.

Fortunately, I didn’t have to intervene to prevent that. Sickle took Cheerlight’s momentary silence as conceding the point. “Yeah, I thought so.” She gave a deep snort before addressing the other ponies. “And why the fuck are you dumbasses listening to this lying little bitch, anyway?”

\leavevmode\llap{“}Good question,” Dusty said, and gestured to the nearest couple of soldiers. “Get her out of here.”

Cheerlight staggered back another step, her eyes wide in panic. “Wait!” she said, eyes desperately darting around until they locked on Hail Burst. “What about Rust?!”

The soldiers stopped, casting curious looks back towards Dusty. I tilted my head again, genuinely curious how she was going to play that one. Obviously she was going to play it off as not being her hive, which almost certainly meant blaming me, but I was interested to see her technique. It was a desperation play, a gamble, unless she had some information I wasn’t aware of. It would be better to not let her speak any more poisonous words, of course, but I was effectively powerless to affect that.

Hail Burst’s head had tilted as well, and while it was hard to judge her expression with only her mouth visible under her helmet, she was clearly suspicious.

\leavevmode\llap{“}I said enough,” Dusty said, waving a hoof at the soldiers. “Get her—”

\leavevmode\llap{“}Hold up,” Hail Burst said, her tone much too casual. “I think I’d like to hear this. Are you really trying to say you didn’t have anything to do with Rust?”

\leavevmode\llap{“}Of course not!” Cheerlight said, desperate and pleading. “We were \textit{trading} with Rust! We’ve gathered a huge amount of equipment and caps, more than enough to trade for some scrap metal. Why would we wipe out our own trading partners? And as for—”

Echo’s voice cut over her. “Rust could harvest and prepare at most a few hundred pounds of quality metal in a day. Judging from the repairs to the \textit{Cumulonimbus}, you likely required somewhere in the neighborhood of a hundred tons of good-quality structural steel to make the vessel flight-worthy once more. As such, I would assume you concluded that a year or more was simply too long to wait, and chose to expedite the process.”

Cheerlight’s ears were laid back as Hail Burst added, “And we hit one of your scavenging groups that had just looted the place.”

\leavevmode\llap{“}Of course we scavenged what we could!” Cheerlight said. “That’s how \textit{everyone} lives in the Wasteland. But we didn’t kill anypony!” She calmed herself, presenting a more stable and reasonable persona; a gentle and shy diplomat, driven to near-panic by the impending violence she hoped to avoid. “We lost contact with our traders, and sent some scouts to investigate. They were almost there when they spotted Enclave soldiers flying in, so they hid to wait until everypony was gone.” She glanced my way again. “And wouldn’t you know it, moments later, Queen Whisper and her companions show up. I’m sure it’s purely a coincidence that they always show up to a crisis at exactly the right moment.”

Hail Burst stared for several long seconds, expression unreadable. “...Nope. Not buying it.”

Cheerlight’s expression softened. “Of all the ponies here, you know most of all what it’s like to be lied to by the ponies you should be able to trust, and to be put in conflict with those who should be your—”

\leavevmode\llap{“}Don’t even fucking try that,” Hail Burst shot back, lips curling. “And just so you know, I don’t particularly trust Whisper. I trust what I see, and I’ve seen what your so-called Serenity has done with my own two eyes. You’re murderers and butchers. We’ve got a witness to everything you did at Rust. Hell, just yesterday you slaughtered a bunch of uninvolved ponies so you could get your hooves on a fucking megaspell. And you…” she leveled an armored hoof at Cheerlight. “You’re a slimy little lying piece of shit, and a transparent one at that. I may not trust Whisper, but at least when she gets all manipulative, she helps ponies.”

I allowed a small, soft smile. Not enough to look smug, even as much as I felt it. Just pleased, as one might expect. Maybe a little relieved. The last part wasn’t even an act.

Cheerlight’s ears had fallen flat again. “Please. I’m sure your witness saw changelings, but they weren’t \textit{our} changelings. I know it’s not pleasant to think that you might have been misled again, but think—”

\leavevmode\llap{“}I said, don’t fucking try that,” Hail Burst said. “I’m done with the scheming changeling crap.” She turned to Dusty. “Are we done with her yet?”

\leavevmode\llap{“}Yes,” Dusty said grimly, motioning again to the soldiers.

\leavevmode\llap{“}Wait!” Cheerlight cried out as the closest two soldiers grabbed her shoulders. “We just want to talk! Surely we can find some sort of middle-ground?”

\leavevmode\llap{“}Hold up.” The soldiers stopped as Dusty walked slowly up to her. When he stopped, he was face-to-face with her, noses almost touching. “You want a middle-ground? Here it is: your hive surrenders, disarms, and releases every pony you’ve got imprisoned for food. That’s our middle-ground.”

Cheerlight’s focus danced between Dusty’s eyes, shifting and anxious and entirely an act. After a moment she looked past Dusty towards the other ponies. “Please, we don’t take ponies, and he knows—”

\leavevmode\llap{“}Wrong answer,” Dusty said, cutting her off. “I was there.”

\leavevmode\llap{“}Please!” Cheerlight called out to the others. “He’s lying! We’ve never done anything like that! These are all more of Whisper’s lies!”

Starlight had finally had enough and leaped up to her hooves. “Oh fuck off!”

Dusty snorted and waved a hoof to the guards before turning to walk away. “Get her out of here.”

\leavevmode\llap{“}We still have the megaspell!”

Dusty stopped cold in his tracks, jaw tightening. The mood over the gathering had abruptly chilled.

\leavevmode\llap{“}We don’t want to use it,” Cheerlight said, visibly trembling. “We don’t want to cause any more deaths than we have to, but we will defend ourselves. The analysts back home… since your army is spread out, they’ve decided the army is too hard of a target. That it wouldn’t cause enough damage. They say the best target now is the army’s industrial and logistical base. If we don’t find some way to peacefully resolve this, they’re going to use the megaspell on Mareford!”

Dusty leveled a murderous glare at her. Everyone was silent. Finally, he turned to look to Two Bits.

Two Bits caught his eyes, but looked away. For a few seconds, he simply stood there, eyes unfocused. I could practically see the mental struggle going on in his head.

Finally, he turned, his eyes locking onto Cheerlight. “Fuck you.”

\leavevmode\llap{“}You heard him,” Dusty said, waving his hoof once more. “Get her out of here.”

The Mareford soldiers started guiding Cheerlight away, pushing her ahead despite her protests. “Don’t trust her!” she shouted. “She isn’t trying to help you! If Whisper really cared so much about you ponies, how come she only showed up two months ago?! Wait!”

\leavevmode\llap{“}Hey!” one of the soldiers snapped, giving her another shove. “Shut it before I gag you with your own damn flag.”

Finally, her protests and verbal maneuvers ceased. She’d taken her shots. They led her away in silence.

\leavevmode\llap{“}Well,” Dusty said, shaking his head. “Did they really think that would work?”

I looked over at Two Bits’ concerned expression, and Hail Burst’s tense stance. She might not have broken up our little army, but it remained to be seen if she’d caused any damage.

As soon as Cheerlight was out of sight, Two Bits turned to Hail Burst. “Hey. I’m not going to give in to her threat, but the safety of Mareford is still my responsibility. Can I get you to send out some scouts, so if they do try to get that megaspell to Mareford, we have a chance at stopping it? I know it’s a long shot, but we’ve got to try.”

\leavevmode\llap{“}Of course,” Hail Burst said, giving a grim nod. “It’ll leave us a little thin on the \textit{‘Nimbus}, though. If you can spare some soldiers to give ship security, I can spare some scout flights.”

He nodded in return. “I’ll get a couple of squads together for you.”

\leavevmode\llap{“}Deal.”

A moment of silence followed before Hail Burst turned my way. “You’re awfully quiet all of a sudden.”

I shrugged. “She made the entire conversation about me being a liar and a manipulator. There isn’t much I can say in my own defense there.” Then I put on a soft smile. “Though given my line of work, it’s refreshing to have the truth working in my favor for a change.”

She gave a mild snort as she looked away, though I caught the corner of her mouth lift. “Yeah, well, it doesn’t help that she was so full of shit you could smell it. And like I said, you might be scummy as hell at times, but at least you’ve helped ponies. That’s more than I can say for Serenity.” Another snort. “Hell, most ponies.”

I couldn’t help smiling a little more. That might have been the nicest thing Hail Burst had said to me.

She mused quietly, a thin smile slowly spreading as she looked out at where Cheerlight had disappeared from sight. “It kind of seems like they’re getting desperate, if they’re throwing a move like that.”

\leavevmode\llap{“}I doubt it,” I said, earning a concerned frown from Hail Burst. “Remember: changeling. She could have come in with any tactic she wanted, any appearance she wanted. She \textit{chose} to look weak.”

\leavevmode\llap{“}Hmm.” She looked back again. “But why?”

I shrugged. “Hard to say. Maybe they hoped to tap into some pony empathy. Break up the army to reduce casualties. Maybe they wanted to make us overconfident. Maybe it’s a diversion, getting us to expect one thing before doing something else. Maybe it’s something we’re just not seeing. Maybe it’s a \textit{lot} of things. Whatever it is, there’s a good chance our reaction to this will play into their plans.”

She grunted. “Changelings.”

\leavevmode\llap{“}Yep.” I smiled.

\leavevmode\llap{“}...So what was that whole ‘two month’ thing about?”

My smile vanished. There were so many ways I could answer that, all of varying degrees of honesty. The full truth was complicated and unusual enough that I really didn’t want to rely on it, especially right after being so strongly accused of deception. The temptation to tell a much more believable lie was strong, but I sighed, settling on a more abbreviated truth. “I woke up from a changeling chrysalis—a cocoon—a little over two months ago. It was my hive’s plan to survive some hard times. It… didn’t work very well. Mine was the last one. Even… even my queen, my predecessor, died.”

\leavevmode\llap{“}Ah,” she said. “Sorry for that.” A pause. “So, your searching. Did you ever find any others?”

My smile returned. “I did. Eggs. It will be some time before they can care for themselves, but my hive will have a future… assuming any of us do.”

\leavevmode\llap{“}And we should probably get to work on that,” Dusty said. “Whisper, I want that encryption deployed by the end of the day. It’s going to be a fight once we start moving, and I don’t want Serenity listening in on us.”

\leavevmode\llap{“}Of course,” I said, nodding. The sensation was ever-so-slightly off, as if my sense of balance was delayed by a fraction of a second. It seemed the Mint-als were wearing off. “I think I might take that coffee now.”

{\br}%
Half an hour later, with caffeine buzzing through my veins, I made my rounds of the army. Fatigue was becoming a factor, but this part didn’t require any significant brainpower. I could autopilot through most of it.

I still double-checked my radios. Both of them. The modified encryption program let anyone tune into multiple channels, so my PipBuck was tuned into both the command channel and the new private channel I had setup. That channel was just for us, my closest companions and me. Somewhere that we could talk without worrying at all about outsiders overhearing. Somewhere I could pass intercepted data to Dusty without anyone ever knowing.

And in the other ear, I continued to monitor Serenity radio traffic. There was still no uptick in activity. No plans being discussed, no attack imminent. No reaction at all to the apparent failure of their negotiations. Nothing.

It was enough to make me a little paranoid.

Most of the PipBucks Hail Burst had supplied went to Trotsen ponies. Sandstorm still had the one she had taken off the spy in Trotsen, so I gave her a copy of the encryption program and the key to the command network, then helped her distribute the new PipBucks to her riders. Once that was done, I took the last three to Dazzle. They would make sure that she and those impressive magical energy cannons were always within reach.

Then it was on to the Mareford Militia, and there’s where things got tedious. Way back when Mareford’s ancestors left whatever Stable they had lived in, they had brought along a great number of PipBucks. The town had several dozen of them, which meant the regular Militia could have one for every squad, plus the various levels of HQ units. I had to update every single one, and that meant flying all around our now-spread-out army.

If I’d had access to all of them in one place, I could have done the job in half an hour, tops. Instead, it was nearing evening as I wearily returned from my rounds. The caffeine had long since faded, leaving me feeling heavy, dull, and with a strangely acidic feeling in my stomach.

It irrationally irritated me that Echo showed absolutely no sign of fatigue as she flew close beside me. I knew the precise psychological leaps that led to those feelings, somewhere between envy and a selfish desire for special consideration by the universe. I was just feeling too worn-out to really care. Fortunately, I was also feeling too worn-out to make a fool of myself by acting on it. I just wanted to finally be done with it.

Dusty was back at the army HQ, with our motorwagon parked close by. Sickle was nearby, too, kicked back and lazily chatting with a cluster of Trotsen ponies. As I landed, I could tell from her slow and slightly slurred speech that she’d had plenty of booze, and probably some other drugs, too. Her lewd sprawl also made it plainly obvious to all that she’d had sex with at least one stallion while I was flying all around the army.

The knowledge of this irritated me. This in turn led to the strange recognition that it irritated me that this irritated me so much. I needed sleep.

Only a few ponies were in the headquarters. Dusty was comparing his PipBuck’s map to the large one on the table, while Starlight sat nearby, head bobbing slowly to the music playing in her earbuds. A couple of Mareford Militia ponies were going over some papers of their own, but remaining close by in case Dusty needed them.

Dusty looked up from the maps. “Hey. You finished your rounds?”

\leavevmode\llap{“}I’ve gotten Trotsen, Gemstone, the Militia, and the Rangers,” I said with a weary nod. “I even caught up with the whirligigs. I’m going up to the \textit{Cumulonimbus} next to update the Loyalists. I wanted to stop and check in with you first. I’m thinking of staying up in the cloudship. The hills limit radio reception, and I’d like to be able to monitor the whole network.”

I inclined my head slightly, my great horn tipping towards the two Militia ponies, who were still preoccupied by their own work.

Dusty nodded knowingly. “Of course. Let me know if you hear anything interesting that isn’t filtering up.” He understood perfectly.

\leavevmode\llap{“}Aww,” Starlight said, pulling out one of her earbuds. “You’re bailing on us? But I like having you around.”

So many conflicting thoughts and emotions stirred at that comment, all urged on by the feeling of affection I was sensing from her. “And I’d love to stay around,” I said, putting on a soft smile that really didn’t convey the complex and sleep-deprived feelings rioting around in my head. “But I probably wouldn’t be much good for company. I’ve got a lot of work to do.”

She gave an overacted groan. “Fiiine. How long are you staying up there?”

\leavevmode\llap{“}Not long. It’ll only be a few days until the army reaches Serenity.” I lifted my PipBuck. “And we’ve got the private channel if we want to chat.”

Dusty gave an amused snort. “I swear, if you two start getting all lovey-dovey on the radio, I’m confiscating your broadcasters.”

Starlight stuck her tongue out at him.

I couldn’t come up with any appropriate response, so I simply moved on. “Anyway, I need to get on that. I still need to get the Loyalists on the new net, and I don’t even know if I need to tweak the program to get it to work on the spell matrix in those armors.”

\leavevmode\llap{“}Well, good luck with that,” Dusty said. “Stay out of trouble.”

Echo quietly snorted, but said nothing.

\leavevmode\llap{“}See you later,” Starlight said, giving a lopsided smile that nicely summed up the mixed feelings.

I lingered as my fatigued mind conjured up some very compelling arguments in support of me staying right there, but I reluctantly pushed those thoughts aside. Duty first, especially when hundreds of lives and the future of my hive was at stake. I reminded my tired mind that it was a very temporary and short-term arrangement. I don’t think it listened.

It was a short flight to the \textit{Cumulonimbus}, which was making a slow orbit over the heart of the army. A call on their unencrypted frequency announced my presence, and a pair of armored soldiers met Echo and myself at the ruined hangar once more. The halls of the ship were still a maze to me, but I was starting to recognize a few intersections.

We were led to the C.I.C. once again. The space was a little more well-lit than last time, and a few more pegasi were at the consoles. The large screen at the front wall was currently showing a map, much like a PipBuck’s. The \textit{Cumulonimbus} was right in the middle, with several other marks denoting both friendly and suspected enemy positions.

Hail Burst looked over to us and nodded. “Welcome aboard. This is about the encryption?”

\leavevmode\llap{“}It is,” I said, mirroring her nod. “I need to distribute the encryption spell and the appropriate keys to every Loyalist armor. How would you like to do this?”

\leavevmode\llap{“}We can handle the distribution,” she said. “Give me a copy of them. I will see that they’re properly distributed.”

I frowned slightly. I didn’t like the idea of letting that information slip out of my control, but neither could I blame her for wanting to take charge of her own forces security. “Very well. There is one possible complication, though. I don’t know the specifics of the pegasus power armor’s spell matrix. I’ll need to examine one to see if the spell needs to be modified for you.”

Hail Burst paused for a moment, a small frown crossing her muzzle for just a moment before she nodded. “Very well. You can hook up to my armor.” She turned her head, awkwardly nipping at the back of her shoulder until a panel popped open, revealing a cable port.

I promptly got to work, and was pleased to see that the power armor’s systems were based on Stable-Tec computers. Better yet, while both Serenity and the Enclave appeared to have made minor post-war modifications to the spell matrices, a good half-hour of examination found that none of the encryption spell’s functionality depended on those modifications. It should work just fine.

With that out of the way, and a copy of the spell and a list of Loyalist encryption keys delivered, I moved on to the next topic. “I hope it isn’t imposing, but I was wondering if I could ask a favor.”

With her helmet off, I could see the raised eyebrow that question brought, and didn’t wait for her to vocalize the question. “Dusty wanted me to monitor all our radio traffic, in hopes I might be able to improve situational awareness. The hills give some interference, so we were hoping you might have room for me somewhere. Preferably some place that won’t block out radio signals.”

She sighed. “Sure, why not? We’re a flying hotel at this point, anyway. There’s another room next to where we stuck that… \textit{energetic} griffin. You can quarter there. The guards will show you the way. I assume you have your own radio equipment?”

\leavevmode\llap{“}I do.”

\leavevmode\llap{“}Good. Then we’ll find you a good place for you to set up in the morning.”

\leavevmode\llap{“}Thank you.”

Echo cut in. “I have another request.”

This time, I mirrored Hail Burst’s raised eyebrow.

\leavevmode\llap{“}What is it?” Hail Burst asked.

\leavevmode\llap{“}We have a suit of damaged pegasus power armor,” Echo said. “It is mostly in good condition, but some parts are irreparably damaged and will require replacements before it will function. I would like to request the spare parts necessary to effect those repairs.” Her eyes turned to me, while her head remained fixed forward. “If Whisper is going to insist on putting herself in danger, we should at least ensure she has adequate protection.”

I sighed; I had no desire to be stuck in some power armor, and I didn’t particularly like the insult it might cause among our pegasus allies to be wearing what was essentially their uniform.

Hail Burst hesitated, frowning, but eventually replied. “I can not permit the distribution of Enclave military equipment to non-Enclave personnel—”

Echo’s mane stirred on an intangible breeze, wings rising at her side, voice sharp. “Given Whisper’s importance to our future, and all that we have done for you, it seems the \textit{least} you can do to show appreciation for our great effort is—”

\leavevmode\llap{“}\textit{But!}” Hail Burst snapped, eyes narrowing to glare. “Given that we’ve captured several suits of Serenity’s power armor, we may be able to find the parts you need from the salvaged \textit{enemy} equipment.” She took a step toward the alicorn. “Unless you’d like to continue objecting to my extremely generous and questionably legal compromise?”

Echo’s wings returned to her sides, her mane settling. “No. That should suffice quite nicely.”

\leavevmode\llap{“}Sorry,” I said, giving Hail Burst a tired smile. “We’re still working on teaching her the finer details of social interaction.” I then turned to Echo. “The proper response to someone granting you a favor is to express gratitude.”

Echo’s head tilted ever so slightly. “I had thought that was implied by my statement.”

I sighed again. “Say ‘thank you’.”

She frowned, and after a moment turned to regard Hail Burst formally. “I appreciate your cooperation in this endeavor.”

\leavevmode\llap{“}Close enough. I guess.”

Hail Burst eyed Echo before turning a smirk toward me. “A stuck-up alicorn learning social skills from \textit{you}. Celestia help us all.”

Echo’s wings rose again. “I will have you know that Queen Whisper is an \textit{excellent} teacher and does not deserve such ridiculous scorn!”

\leavevmode\llap{“}Relax,” I said. “Maybe the next lesson should be on general banter and friendly ribbing. Or maybe just tact.”

\leavevmode\llap{“}Mmm,” Echo said, pausing thoughtfully, and nodded. “If you think that best, then it sounds like an excellent course of study.”

Hail Burst snorted out a barely restrained laugh, then shook her head. “Yeahhh, okay. Back on-topic, get us a list of parts that you need, and we’ll see what we can do. We might be able to spare a technician if you need any help.”

\leavevmode\llap{“}I will not,” Echo replied quite primly, her nose lifting a little higher. “We remember a great deal of arcanotech engineering. Repairing the armor should be trivial, given the correct parts.” She turned her head to regard me. “Given that you are in the heart of a Raptor-class cloudship, do you suppose you will be able to refrain from getting yourself killed without me for a few minutes?”

I gave a wry smile. “Yes, I do believe I can manage that.”

Echo frowned. “Hmm. I would prefer more certainty, but I suppose that shall suffice. I will retrieve our salvaged power armor and return shortly.”

With a flash, she was gone.

\leavevmode\llap{“}Well she’s even more charming than I remember,” Hail Burst said.

\leavevmode\llap{“}Believe it or not, this is progress,” I said. I mean, she didn’t even mention genocide once. “She’s still new to this. She hadn’t had any proper social interaction prior to about a week ago. Kind of.” I frowned. “She’s complicated.”

With the encryption delivered, we parted ways. The escort guided me through the maze of dim and damaged corridors to my temporary quarters. We had almost arrived when I heard a faint pop. I might not have even noticed if I hadn’t heard it again, a few seconds later and slightly louder. Then again, and again, rapidly drawing closer.

I stopped at an intersection of hallways just as a dazzling purple flash appeared right before me, signaling Echo’s return. “There you are!” she said, turning to face me. The damaged set of pegasus power armor floated behind her as she glared at me. The look lost most of its impact when both of us were ducking under the low ceiling. “I leave you for hardly a minute and you’re already trying to get lost.”

\leavevmode\llap{“}I’m being escorted by a pair of Loyalist soldiers in their own ship,” I noted, leveling my best flat glare. “I am hardly in danger of anything, least of all getting lost.”

She blinked, then shook her head. “Well. I suppose that is technically true, but I can hardly protect you if you run off without letting me know where you are going.”

\leavevmode\llap{“}Echo, any soldier on this ship could have told you where I was, and you can always call me on the radio.” I lifted my PipBuck for emphasis before setting it down and fixing her with a hard stare. “And this overprotective thing is getting extremely old.”

\leavevmode\llap{“}You tried to blow yourself up with a megaspell,” she countered, horn tapping the ceiling as she tried to stand a little taller. “I hardly think I am overreacting.”

\leavevmode\llap{“}You’re being overbearing and rude,” I said, not relenting. Irritation was growing in my fatigued mind, despite attempts to quash it. “I have no problem with you playing bodyguard and trying to protect me, but the more obnoxious and overly critical you are about it, the more I want to just get away from you.”

Her eyes went wide, head drawing back as if I had slapped her. It resulted in her banging the back of her head against a low-hanging pipe, but she didn’t even seem to notice; the only pain evident in her expression was in response to my words.

I groaned, a hoof rising to my face, and spoke before she could come up with the words to reply. “I’m not saying I hate you, Echo. It’s nothing like that. It’s…” I lowered my hoof again. “Do you remember our first talk?”

The growing look of shock and outrage were immediately wiped away by a thoughtful expression as she thought back. “Yes? To which part are you referring? We discussed several subjects.”

\leavevmode\llap{“}The part about how you present things,” I said, mellowing my tone as much as possible. “Being demanding and overbearing will drive ponies away, even if you’re trying to act in their best interests. It’s counterproductive to your goals. Not to mention, it’s just plain rude.”

She had frowned, and it took several seconds before she replied. “I had expected that you, at least, would not have been as susceptible to such an emotional reaction.”

\leavevmode\llap{“}I’m exhausted,” I said. “And it’s not as if you restrict this behavior only to me. I think you would have a lot more success if you didn’t act quite so… condescending towards others.”

She continued to frown thoughtfully for another few seconds before giving a slow nod. “I see. That will be difficult, given the great disparity in power and capability, but… I shall try.”

\leavevmode\llap{“}Good,” I said, choosing to ignore the low-key condescension for the sake of my own sanity. I even reached up to give her a friendly pat on the shoulder, which merely produced a confused look at the offending hoof. Then, remembering the skeptical-looking soldiers, turned to give them a smile. “Which way?”

The closest soldier snapped out of it immediately. “That room, right there,” she said with a raised hoof.

\leavevmode\llap{“}Thank you,” I said with a smile, and entered my new quarters, with Echo following close behind. It was a decent enough space. It probably even counted as roomy by warship standards, with the tiny desk, one chair, a locker, and single bunk-bed. I had just removed my saddlebags and was considering the regular-pony-sized bed when a familiar high-pitched voice came from the open doorway.

\leavevmode\llap{“}Oh, hey,” Bloodbeak said, peeking her head in. “I thought I heard you over here.”

\leavevmode\llap{“}Hello again,” I said, flashing another smile. “Looks like I’ll be quartered here in the \textit{Cumulonimbus} for a few days.”

\leavevmode\llap{“}Cool,” she said, casually strolling in. The room was getting very cramped.

Echo sat down the armor. “I am going to find Hail Burst to get those parts she promised.”

\leavevmode\llap{“}Please try to be nice about it,” I said. “Please and thank you and all that.”

\leavevmode\llap{“}Of course,” Echo replied primly, and slipped out the door.

Bloodbeak blinked after her, then flashed a wry smile at me. “She’s funny. You fixing up this armor?”

\leavevmode\llap{“}She is. She thinks I need more protection.”

\leavevmode\llap{“}Huh. Neat.” She paused, letting out a long, loud yawn that I struggled to not echo.

\leavevmode\llap{“}Tired, huh?” I said, stating the obvious in a way to open up further conversation.

She cracked a smile again. “I’ve been running around this ship for hours. Even \textit{I} have to run out of energy eventually!” She chuckled as she turned and flopped back in the chair—then hissed, grabbing at her side where she had been injured. “Oww, crap! Why do I keep doing that?” She was already chuckling again by the end of the sentence. At least she didn’t seem to be in much pain.

\leavevmode\llap{“}Is that still giving you trouble?”

\leavevmode\llap{“}Only when I’m being stupid,” she said, beaming, though she steadily slid down to slouch in the chair. She looked every bit as tired as I felt. “So it looks like we’re neighbors for a bit. Does that mean we get to hang out?”

I looked at my saddlebags, sitting beside the bunk-bed with the vital PipBucks nestled inside. I’m pretty sure I lingered just a little too long, long enough that Bloodbeak had surely noticed my hesitation. I quickly spoke up before she could consider it. “Sure. I’m going to be pretty busy over the next few days, but I’m sure I’ll have free time.” Or at least, I could manage a bit of socializing with the radios playing in my ear.

Bloodbeak smiled. “Cool. I mean, I’m inside this super-awesome flying ship from the ancient past, going to fight some super-secret underground baddies. It’d just be all sorts of wrong if I was \textit{bored} in the middle of all this.”

I chuckled. “Well, we can’t have that.” Still, I was eying the too-small bed. I called up my magic, stripping away my regal disguise, and sat on the cot with a soft groan. “But I think that’s going to have to wait. I’m exhausted.”

Of course, what I \textit{wanted} to do was listen in on the radio. Serenity was still quiet. Not silent, mind you. There was still the regular chatter, but it was all suspiciously uneventful.

\leavevmode\llap{“}Hah, I hear you there,” Bloodbeak said, lifting a hand to cover another, smaller yawn. “Catch you for breakfast, then? Oh, hey, then you can tell me what happened with all that shooting earlier!”

\leavevmode\llap{“}Hmm? You didn’t see what happened?” I looked over at the wall. “I guess warships don’t have much in the way of windows.”

\leavevmode\llap{“}Yeah, these pegasi just got all all super-serious and told me to stay in my room. It was dumb and boring.” She paused, giving a weak, uneven smile. “Uh, maybe a little unnerving, too.”

I grunted and frowned. “I can imagine. Hearing the fight and not having any idea of what’s happening…”

\leavevmode\llap{“}Still kinda silly,” she said, and with a huff, hauled herself back up to her feet. “I mean, this is probably the safest place in the whole army. Just, you know… a window would be nice.”

\leavevmode\llap{“}How about I talk to Hail Burst in the morning?” I said. “Maybe we can arrange something that doesn’t have us stuck in some dark hole the whole time.”

She grinned. “Hey, thanks. Well, I think I’ll go turn in.” She was just exiting the door when she stopped. “Hey, uh, Whisper?”

I had laid back, sinking into the thin cushion of the bunk. “Yes?”

\leavevmode\llap{“}It’s just…” She turned, looking to me with a softly concerned expression. “Well, I remember when we met, you were talking about finding your family, and, well…” her gaze wavered awkwardly. “Is this your family?”

I shook my head. “No. This is a different hive.”

\leavevmode\llap{“}Ah,” she said, a bit of a smile returning for just a moment, before she spoke again. “So… did you ever find them?”

I smiled. “Yes. I found them.”

Her smile returned, soft and warm. She didn’t say anything. She just smiled, and nodded, and then she slipped out of the room.

I floated my bags over, depositing them close by my side so the earbuds’ wires weren’t too tight, and curled up in a thin cot made luxurious by way of fatigue.

The radio crackled occasionally with distant conversations. Echo returned with several parts, quietly tinkering with the armor. None of it mattered to me. I wrapped the blankets snugly around me, nestled my head into the inviting pillow, and I settled in to finally get some much-deserved sleep.