If there’s one thing I admire the most about ponies, it’s the optimism.

I know, it’s not a universal trait. Back during the war, faced with the seemingly unending news of violence, death, and destruction on a grand scale, there were many who fell into a more cynical mentality. The hardships of the Wasteland kept that way of thinking alive. It wasn’t surprising that many, faced with such insurmountable and existential vileness, might lose hope of seeing better days. It’s a cloud that’s hung over the world for more than two centuries now.

But even in the face of seemingly unending suffering, that optimism was still there. I had seen it in the ponies I lived with in Appleloosa, who frowned and worried about the news, but still treated each other warmly. I saw it in the ponies of Gemstone, who embraced Kindness and Generosity as the solution for the world we found ourselves in. I even saw it in Bastion, laughing along with the Mareford ponies who walked beside him, despite the pronounced limp as he kept his weight off his heavily bandaged leg.

Changelings have a long history of living in relatively harsh conditions, maneuvering in the shadows and hiding from other species that we depended on for food. That kind of history bred a certain amount of stoicism in our cultural learning. We endured. That’s particularly true of my peer group, those with the skill and mental fortitude to become Infiltrators. Those who were expected to go into hostile territory with calmness, determination, and an unburdened mind, capable of playing a role without personal fears betraying us.

But even among those of us who held to great ideals, who looked ahead to a better future, there was much to admire in the optimism of ponies, even as the weight of the war slowly buried it. I think, of all the things my hive learned from our infiltration of Equestria, all the espionage and subterfuge, that was possibly the most important. In the aftermath of the sundering of the hive, it was the ideal that our hive had embraced. The ideal that would lead us to a better future. The ideal that we were working not just to survive, but to become something better.

We, this gathered army, had taken a pounding. The night had been long, full of sporadic gunfire and harassing raids. More wounded filled the medical tents, and new graves had been dug. Even the \textit{Cumulonimbus}, previously an awe-inspiring symbol of the army’s gathered might, lay in ruins, a crumpled tomb to more than a hundred changelings and ponies. All of that weighed on the army.

In the dim pre-dawn twilight, the atmosphere in the camp was far from joyful, but these ponies held strong. While the dead were missed, there was an air of satisfaction that, after Serenity’s nighttime assault, they still stood strong. They had held their own, and emerged from the darkness victorious. The destruction of the mighty \textit{Cumulonimbus} wasn’t a crushing loss of their greatest weapon, but a tale of a few dozen ponies holding out against hundreds, and when all seemed lost, turning Serenity’s own trap on them. Soldiers worried about what the following days would bring, but when one pony smiled at some small pleasantry, I saw that bit of brightness reflected in the faces around them.

All around, the camp was coming to life, packing and preparing for the day. We planned to set out in less than an hour. Most of us in the headquarters were getting a quick breakfast of canned goods—seasoned corn that had lost most of its flavor, in my case—and reviewing our plans. The radios were pleasantly quiet in my ear.

Bastion looked away from the ponies who walked alongside him to see me, and he smiled. He was quite athletic and handsome, for a pony, with a white coat and close-cropped blue-and-silver mane. It was a look that seemed so stereotypically military, but there was a genuine warmth to that smile. As he drew closer, he addressed me with a nod. “Your Highness.”

I gave a single soft chuckle, deciding not to interrupt the niceties by insisting on a less formal title. Not unless it started catching on. “Sergeant Bastion,” I said, dipping my jagged horn in greeting. “It’s good to see you. I’d been hoping to catch up with you after breakfast.” I floated up the can before setting it down again. “When I heard you were injured, I had feared the worst.”

\leavevmode\llap{“}What, this?” he said, raising his bandaged leg. “It’s nothing. I’ve burnt myself worse trying to cook. No, my armor took the brunt of the damage.”

\leavevmode\llap{“}Better it than you,” I said. “Still, I’m glad to see you’re up and active. I wanted to thank you for everything you did last night. We were badly outnumbered, but your leadership saw us through. You likely saved my life, and many others.” I bowed my head a little. It seemed like the queenly thing to do.

\leavevmode\llap{“}Oh, I was just doing my job,” he said with a dismissive wave of his hoof. “I just told ponies where to go. It’s the ponies who held the line who deserve the credit. Actually, I came here to thank you.” He glanced past me, to where Echo stood, my ever-vigilant bodyguard. “When you two evacuated the wounded, you might have saved our flanks. If we had tried to fight past that third force to evacuate them ourselves, I don’t think any of us would have gotten out of there. You might have saved a lot of ponies last night.”

He finished by extending his good hoof, and I smiled more as I shook it. He then turned to Echo with the same gesture. She hesitated, uncertain, before accepting and shaking it as well.

\leavevmode\llap{“}I hope you’re well enough to travel?” I asked, hoping it didn’t seem insensitive, but he waved it off.

\leavevmode\llap{“}A singed leg isn’t going to keep me from flying,” he said with a smile. “I take it we’re moving out soon? I haven’t caught up with Hail Burst yet.”

That was more of a military matter, and Dusty answered it. “We are. We’ve got a good ways to go before we get to Serenity, and I’d rather not give them any more time than necessary.”

\leavevmode\llap{“}I hear that,” Bastion said with a nod. “Better get as much progress as possible before the rain hits.”

Dusty’s ears perked up. “Rain?”

\leavevmode\llap{“}Yeah,” Bastion said, his head inclining a bit. “You saw the way the clouds out west are churning, right?”

Dusty glanced that way, as did I. To my eyes, there wasn’t anything unusual.

\leavevmode\llap{“}I guess I don’t know clouds as well as you,” Dusty said. “How long do we have?”

\leavevmode\llap{“}With that much density and current? Two, maybe three days. Going to be bad, too. Those clouds are completely unregulated. With a heavy load, it’ll probably be a full, uncontrolled release. One or two days of heavy rain and near-blackout conditions.”

I frowned, thinking back to my first days in the Wasteland.

Dusty was looking over his map. “That’s a little tighter than I was hoping for. We might make Serenity in two days, if we don’t get bogged down. It’ll be a hard push, but doable.”

\leavevmode\llap{“}Great,” Starlight said around a mouthful of half-chewed carrots. “So it’s a race.”

\leavevmode\llap{“}We wanted to get this done as quick as possible,” Dusty said, turning back to his own food. “This just gives us a time-table. Heck, the weather might even give us an advantage. How well can they fly in rain like that?”

Bastion gave a dry chuckle. “If they’re anything like pegasi? They’ll be grounded. Even the Wonderbolts wouldn’t want to fly in that kind of weather. That’s a good way to get killed.”

\leavevmode\llap{“}Well, we’d have that, at least,” Dusty noted, then shook his head. “But we’ll aim for getting to Serenity before the rain. The army won’t be able to march in weather like that. Not safely. If we can force them back to the Stable, the rain won’t matter.”

\leavevmode\llap{“}Sounds good to me,” Bastion said with a smile. “Anyway, I need to go check in with Hail Burst. I expect we’re going to have a busy couple of days.”

That earned a wry smile from Dusty. “I don’t doubt it.”

{\br}%
An hour later, the army was moving.

\leavevmode\llap{“}We’ll be heading north to here,” Dusty said, showing me the location on his PipBuck’s map. “Serenity likely put most of their defensive plans on our west side, so I’m hoping we’ll run into less resistance that way.”

\leavevmode\llap{“}There’s some discussion about that on Serenity’s net,” I said with a nod. “Sounds like they’re working out a new plan, but they have nothing concrete yet.”

\leavevmode\llap{“}Good. Let me know if you get any details. We’ll only be going a couple miles before turning west. The hills restrict our movements a bit, but the main obstacle is probably going to be the Rotwater. The old river cut a deep ravine, steep enough to be a problem for ponies on the hoof, much less wagons. There’s a pre-war rail bridge near where we’ll meet it, but Serenity will probably blow it to stop us, so we need to find a place where the banks are shallow enough for motorwagons. The only places indicated on the maps are here…” He indicated a position, then scrolled over to indicate another. “...and here. Serenity will probably try to take advantage of that. Anything you hear about those locations could be critical.”

I nodded again.

\leavevmode\llap{“}And of course, any word about their megaspell would be good,” he said with a shrug, and sat back in his seat. We were still parked, while the core of the army marched. I could just hear the distant sound of scattered shots to our west. Almost a mile away, some hundred-plus ponies were engaging Serenity forces in a small-scale skirmish that Dusty hoped would keep the enemy defenses pinned down and unable to move against the maneuvering army. “Is everything set up back there? We need to get going soon.”

\leavevmode\llap{“}I’ll go check,” I said.

While Dusty took the opportunity to pull out a cigarette, I turned back to my radio equipment, which had been nicely expanded. Starlight hadn’t stopped at merely acquiring some cloud tech and cables. She’d brought back about two hundred pounds of electronics, much of it radio equipment, which was currently strapped down just behind my seat. I had to wonder if the Loyalists had actually approved of all the sensitive equipment she had taken.

I climbed out over the back of my seat, a task made more difficult by just how heavily loaded we were. It wasn’t just the new electronics, of course. Sickle was kicked back atop a makeshift bed of ammo canisters and cases, taking up most of the space on her own. Then there were the two power armors wedged in alongside her, with Echo perched protectively above them. There wasn’t a single inch of floor to be seen beneath the gathered equipment. Even Bloodbeak was there, though she made room for me by climbing onto the roof of the wagon, sitting back against the heavy machine gun.

A quick beat of my wings lifted me over the various obstacles, and I alighted on the rear wall of the cargo bed to look down on Starlight and her project. My hooves had just touched down when the mare helping her called out. “Eyes!”

I turned my head, bringing up a hoof to shield my eyes. A second later a searing-bright and flickering light illuminated everything around me, accompanied by the crackling sound of the welder. It lasted for only a couple of seconds before everything dimmed again, but I kept my hoof in place until the voice spoke again. “All clear.”

I lowered my hoof, looking on the small project. Starlight had snagged an entire antenna array, bristling with a dozen antennas of different sizes, and now mated to a pair of cloud-based cargo jacks and tethered by a lengthy cable. That wasn’t all she had brought back for this project, though. She’d also brought the red mare, who currently had her goggles raised to inspect the weld, the welding torch still clutched in her teeth.

Singe looked much better than the last time I had seen her. The ash and dirt had been cleaned from her coat, and while she still showed some signs of her injured ribs in her movements, she seemed otherwise in good health.

She gave a firm tug on the cargo jack before setting down the welding torch and looking up, only to visibly flinch the instant she saw me. I was still in my natural form, to better fit in the wagon, not that I’m sure any of my standard disguises would be any more comforting. Still, she immediately returned to business, as if pretending the reaction hadn’t taken place. “The welds are all good. If the cable’s secure, it’s all set to go up.”

\leavevmode\llap{“}It’s on there good,” Starlight said, reaching over to pat the again-repurposed towing rig she had welded on so many days ago. Several bolts now held the end of the long cable secure. “I even doubled-up on the connectors to make sure it won’t pull free. We probably won’t want to go crazy while we’re dragging this thing, but it’ll hold up to regular use.”

\leavevmode\llap{“}Good,” Singe said with a nod, then looked up to me again. Her shoulders tensed, as if wanting to pull away, but she forced herself to face me, unflinching. “Then all that’s left is to wire things in on your end.”

I nodded and smiled, trying to open my mouth only the minimum required to talk without flashing all my sharp teeth at her. “Sounds good. Thank you again for all your help.”

There was a momentary falter in her expression, but she held firm. “I’m just glad to be helping. Doing something.” Her mouth opened again, then shut, falling silent.

\leavevmode\llap{“}Well, we need to get going. Are you all set to travel?”

\leavevmode\llap{“}Yes,” she said, not quite meeting my eyes. “The Mareford ponies are giving me a ride in a medical wagon. I can’t really walk that well yet.”

\leavevmode\llap{“}I’m sure that will be better soon,” I offered, hoping it might be comforting.

\leavevmode\llap{“}Thanks,” she said, quietly, before finally meeting my gaze again. “Good luck.”

I smiled a little more. “You too, Singe.”

She nodded, passing the borrowed welding equipment back to Starlight before turning to walk to the waiting medical wagons.

Starlight climbed up on the rear of the wagon, her magic grasping the contraption she had hooked up to one of the many wires coming from the long cable. It was little more than a spark battery and a dial. “Okay,” she said, holding the device up. “Let’s see if this thing works.”

The dial twisted, and the desk fan bolted onto the bottom of the antenna array buzzed to life, kicking up bits of dirt as the whole assembly floated slowly but surely into the air.

\leavevmode\llap{“}Aw, yeah!” Starlight said, grinning. “We are awesome.”

\leavevmode\llap{“}You did good,” I said, mirroring her grin.

\leavevmode\llap{“}Aw, heck, it was nothing,” she said with a chuckle and wave of her hoof. “Let’s just wait till it gets up and brings up all the slack, and we’re all set to roll out!”

She hopped down to trot around to the driver’s seat, and I gathered up the bundle of wires, all wired up to new connectors and conveniently labeled with bits of pencil-marked tape, thanks to Starlight’s foresight.

Echo didn’t wait for me finish. “You should be wearing this armor,” she said, still fixated on the subject. “That is why we had it repaired. It doesn’t do anyone any good just sitting there empty.”

\leavevmode\llap{“}Sorry,” I said with a dismissive shrug. “It won’t really fit in the cab.”

\leavevmode\llap{“}It is not that bulky!” Echo snapped, and I flinched slightly, regarding her a little more carefully. I hadn’t expected her to be quite so upset over the subject. “I have spent days repairing this armor for \textit{your sake}. Why are you so stubbornly opposed to making use of it?”

Her ears were pinned back, eyes narrowed. Even her mane flowed more wildly, a form of body language I was still getting used to. I took a few seconds to more carefully formulate my reply. “Echo, my experience and training as an Infiltrator has always taught me to make use of the best tools at my disposal, regardless of my personal preferences.” I reached up to touch my rifle, hanging across my chest. “It’s a lesson that my time in the Wasteland has reinforced. I promise you, if we’re approaching a situation where I would be better off using that armor, I will, but right now, it would just get in the way of what I need to do.”

The anger in her expression faded, covered under a thoughtful frown. “I suppose that seems sensible, though I question the accuracy of your risk assessment. I should point out that the one time in the past week where the armor would have made a difference came with no warning. You must certainly be aware of how unexpected a changeling assassination attempt can be.”

\leavevmode\llap{“}I am,” I said with a sigh, “and it’s something I will be keeping in mind in the future.”

She held her frown, but after a couple of seconds, finally gave a faint snort that vaguely sounded like an acquiescence.

I replied with a nod, then spread my wings, making a short, buzzing hop over the pile of equipment, wires in tow.

I stopped again as I once again saw Bloodbeak sitting by the gun. I slipped the end of the wires in over the back seat, then stood again to speak to her. “Are you sure about this?”

\leavevmode\llap{“}Hmm?” She looked back at me. “About what?”

\leavevmode\llap{“}About coming with us.”

She broke out in a grin, waving her claws at the gun and motorwagon in front of us. “Seriously? Heck yeah, I’m sure! I get to ride with you guys on the coolest wagon, \textit{and} you’re setting me up with a flank-kicking super-gun!”

\leavevmode\llap{“}You remember what Dusty and I told you, right? If you do come with us, that’s it. This is the headquarters for the whole army, and Serenity is sure to have spies. We’re taking information security seriously. There are things that will be said that Serenity can not learn, under any circumstances. If you’re in, you’re in until Serenity is done. No alone time, no wandering off without one of us with you, no off-duty time. Are you sure?”

She wiped away the grin, replaced with a thin but determined smile. “I pulled guard duty with the Dawnbringers for years. Never napped or wandered. Duty first.” The grin started to return. “I’m in all the way, superspy. No place I’d rather be.”

I hesitated. “I’m not really a superspy.”

She just waved it off. “Well, that’s what Starry was calling you. I mean, I get it. I’m guessing you’ll be talking lots of spy stuff you don’t want others hearing, and that means you don’t want me repeating it. Makes sense. So yeah, I’ll chill with you guys for a few days. My beak is sealed.”

\leavevmode\llap{“}And Seroon?” I asked. “You sure you don’t want to travel with him and the other Dawnbringers?”

She chuckled. “Heck, he was telling me I should try to help you guys. He’s got all of Mareford watching his back. Said you could use someone to help watch yours.”

\leavevmode\llap{“}And you’re absolutely sure you want to stay, then?”

She wrapped a foreleg around the machine gun, grinning. “You’d have to break out Starry’s prybar to get me out of this wagon.”

I cracked a smile. “Well, okay then. I hope you enjoy the ride.”

She gave a mock salute, and I ducked down, squeezing into the backseat once more. It took only a few moments to sort out the cables, and only a few more to plug the connectors into the proper ports of my increasingly convoluted arrangement of networked PipBucks. It was a chaotic jumble of cables and distributed computational power, but it worked. Somehow. I had the distinct sense that it might be overkill for what I was doing with it, but I didn’t really have the luxury of time to streamline things. Sometimes, you just had to settle with a jury-rigging.

The moment I had the right cable in place, the Serenity channel I was monitoring turned garbled for a moment, then cleared up perfectly. The antenna was doing its job.

I pulled out another cable, reaching forward to offer it to Dusty. “Here you go.”

He took it, eying the connector suspiciously. “You’re sure this will work?”

\leavevmode\llap{“}It’s all hooked up and ready,” I said. “I’m using the main antenna, but that’ll hook you up to one of the secondaries. Just give it a test to make sure the antenna is working right.”

He settled back into his seat, slipping the cable around the chair and plugging it into his PipBuck. The radio gave its electronic squawk as he hit the button to transmit. “Ranger Lead, Command. Radio check.”

It was mere seconds before the reply came back, loud and clear. “Command, Ranger Lead. Roger.”

Dusty looked back to me, giving a nod of approval.

\leavevmode\llap{“}All right,” Starlight said, finally sliding into the driver’s seat. “The cable’s as taut as it’s getting. We’re good to roll.”

\leavevmode\llap{“}Good,” Dusty said. “It’s time we got going. Bring us up to the Trotsen wagons.”

\leavevmode\llap{“}You got it,” Starlight said with a grin.

The wagon rocked gently as Echo took to the wing, and the engine thrummed with magical power, accelerating smoothly. Half a mile ahead, we could make out the gathered wagons, with Hail Burst and her Loyalists flying along above.

I looked back to double-check the cable. The welded-on rig creaked slightly, and the floating antenna dragged behind us at a fairly steep angle, but it wasn’t showing any signs of coming loose. “Looks like it’s all holding together just fine.”

\leavevmode\llap{“}Good,” Dusty said, already consulting his map to plan and coordinate the movements of the force we had assembled.

{\br}%
We made it less than an hour before the fighting kicked off.

It was inevitable. For all my intelligence gathering, all of Dusty’s clever maneuvering, all the scouting and rapid movements, we still faced the one insurmountable advantage Serenity had over us: their entire force could fly.

Minutes after our wagon started rolling, Serenity started to pull back from the forces attempting to pin them in place. I listened to broadcasts while scanning my PipBuck’s map, trying to track movements. The maneuver was simple and elegant. A few squads kept their position while the rest of the company withdrew, repositioning with incredible speed. A minute later, the maneuvering units had established long-range fire, covering the front-most squads as they fell back.

The Militia ponies tried to press the attack to keep them engaged, but they had to dart from cover to cover, advancing on hoof and under fire, while Serenity’s soldiers could rapidly fly back to their new lines, sweeping low to the ground at high speed. It was hopeless. In less than three minutes, the entire company had broken contact, flying rapidly away from the battlefield.

Ten minutes after we started moving, I heard Serenity organizing raids on our column. My heads-up to Dusty was largely superfluous. He was already aware of the possibility, but at least I could tell him where and when the attacks were going to come in. While he didn’t want to give away our advantage by acting preemptively, it meant he wasn’t surprised by the maneuvers. He had time to plan ahead, and when Serenity made their move, his counter-moves were immediate.

The first raid came in on the main army. I turned to look out the window just as the black dots surged over a ridge barely a mile away. An instant later, Dusty was on the radio. “Loyal Lead, Command! Eyes on enemy fliers, south. Move to engage. Remain within three hundred yards of the column. Gemstone! Take positions and concentrate air defense south. Move at your discretion to remain alongside the column.”

Lines and bolts of light were already cutting through the sky as acknowledgements came in. Gemstone’s three magical energy cannons had been supplemented by four more from the \textit{Cumulonimbus}, with Arclight working on repairing two more. A little over half were in our portion of the army, and they sent up a dazzling wall of magical death to meet the oncoming attackers.

Above, the Enclave Loyalists banked, coming around in a clean and coordinated formation. They were only a fraction of the oncoming force’s size, but it was enough; as changeling soldiers weaved to avoid fire from the ground, it left them unable to properly engage the pegasi.

Hail Burst didn’t have that problem. She led the first group of pegasi straight on, opening up a withering salvo of long-range fire. Fuschia-colored magic etched the sky, cutting through the loose Serenity formation, though none found their mark. It did, however, break up the formation even further.

Then the flurry of fire stopped, and the pegasi banked around in a neat, tight turn. As they did so, the next group was already turning to make their own run, and the air once again filled with magic.

A few changelings tried to brave the volume of incoming fire to straighten out and return some shots of their own. A few bolts flashed out in return. One of the changelings paid for her bravery, a purple-pink flash of a direct hit enveloping her for a moment before she plummeted towards the ground.

Still, they closed on the column. Half a mile, now. The lead pegasi had banked away, flying back the way they came, while the next batch had turned in towards the oncoming changelings, loosing their own salvo. Nearby, a few ponies had rifles pointed into the sky, firing a few rounds into the air at desperately long ranges, but that volume of fire—and its accuracy!— would only grow as the enemy came closer.

Even if the incoming fire hadn’t hit many of the attackers, it was clearly having an effect. My left earbud crackled. “Lead, One. We’re taking a hell of a lot of fire! Multiple M.E.W. cannons. We’re not going to be effective here.”

A flash of green sliced across the sky, lancing one of the closing changelings. I traced it back to one of the Trotsen wagons, with one of Arclight’s cannons bolted to its roof. I could just make out Blueberry, adjusting his aim before firing again. It was slower firing than the powerful plasma cannons, but its beam was like Starlight’s Lancer; accurate, lightning-fast, and judging by the way the dark form crumbled into glowing green ashes, remarkably powerful.

Another shot barely missed a weaving Serenity soldier, who immediately broke off her approach to enter a spiraling dive to avoid any follow-up shots.

\leavevmode\llap{“}One, Lead,” the left earbud buzzed again. “Disengage. Break off southeast and rejoin.”

\leavevmode\llap{“}Copy.”

The incoming changelings veered off, diving towards the ground to pick up more speed and avoid incoming fire. A few let off long-ranged bursts of fire before turning away. I cringed as the bolts arced through the air, seeming to curve as if homing in on us, and ducked as they came crashing down.

Given my expectation, it was rather anticlimactic. There were no loud explosions. Just a rapid pattering of dull puffs and thumps and several shouts. I peeked out the window again to see the column marching along, relatively unscathed. Some of the shouts were from a line of Mareford ponies, one of which was on the ground. Several other ponies had gathered around him to render aid, while the others were continuing to march under the orders of their commander. Well down the line, I could see one of the Trotsen griffins beating at the smoldering spot on the side of her wagon’s armor.

Above, the Loyalists gave a brief pursuit, diving and laying out a parting salvo of fire before breaking off and returning to the column.

Suddenly, it was quiet once more. The Loyalist skywagon swooped in along the line, picking up the unlucky pony who had been struck by one of the long-distance shots and delivering him to the medical wagons. It took a minute for a full casualty report to come in; no dead, three wounded, and only one seriously. Serenity had taken a shot at us, and we’d weathered it almost unscathed, returning better than we got.

But we were only fifteen minutes in.

Ten minutes later, the head of the army was approaching the first of the Serenity ground forces. Two squads were waiting on the back slope of a hill, ready to ambush our force the moment they had advanced far enough along the narrow valley floor. It was a good place for an ambush, if a bit too far to cause real damage.

\leavevmode\llap{“}They don’t need to hurt us much,” Dusty said when I brought it up, eying the map with all the markers I had provided. “They just need to kick up enough of a fuss that we have to take them seriously. It’s delaying tactics. The slower we are, the more time they have to prep their positions.”

And so, in a calculating move, we once again took no preemptive action. Five minutes later, the lead element crossed into Serenity’s sights.

A moment later, the radio squawked in my left ear. “Lead, One.” Despite the distance, the channel was crisp and clear, without any signs of distortion. The antenna was working wonderfully. “Enemy recon wagon has just passed RP Snare, continuing west along the valley. No contact.”

The reply came swiftly. “Copy. Enemy vanguard should be about five to ten minutes behind. Hold tight.”

\leavevmode\llap{“}One copies.”

Dusty muttered to himself as I passed that on, then called for a location report from all Mareford units. As that went on, the recon wagon halted at the end of the valley, its position relayed by both the Serenity ambush force and the scout team onboard. I quickly checked my map, doing a little quick geometry. The recon wagon was about half a mile from the ambush force. Closer than Dusty and I would have liked, but still far enough to be somewhat safe.

Still, we waited. Dusty watched the map closely, silently counting down to the moment when the vanguard of our army reached the location tag that marked the intended ambush.

I was almost two miles away, hidden behind a line of hills, and I still felt the adrenaline teasing at my nerves.

By my count, we were about thirty seconds from the ambush when Dusty hit the key to transmit. “Trotsen Lead, Command. Enemy spotted to the south of vanguard elements. Orders for Reaction Force One: move to hill 313, dismount at the top, and assault west into enemy positions on the west slope of that hill. Best speed.”

\leavevmode\llap{“}About damn time,” came the reply from Sandstorm.

Radio chatter quickly filtered down the lines, and the reaction force—six Trotsen motorwagons bearing several squads of Mareford Militia—was already moving before Serenity’s broadcast went out.

\leavevmode\llap{“}Eyes on enemy infantry, squad-plus, at RP Snare.”

I looked to Dusty. “Our ponies just entered the ambush site.”

He gave a sharp nod, eyes fixed on his map.

I turned back to my own map, with the jumble of intercepted location tags denoting Serenity positions and points of interest, while mentally overlaying our own force’s positions. The calm was unnerving.

Radio traffic practically exploded, and I filtered out most of the low-level communications. The platoon-level report came in calm and clear, despite the loud gunfire. “Contact, enemy infantry, due south of One, five hundred yards. One is under heavy but distant fire.”

\leavevmode\llap{“}Understood, One. Take cover, hold position, and pin them down. Mobile units are already on the way.”

Said mobile units were already climbing the opposite slope of the hill. It was a tense minute of listening to them moving and disembarking, all while I silently tracked their position on my map.

The Serenity channel opened with an urgent voice. “One and Two! Enemy forces approaching from your—”

The broadcast was immediately drowned out by explosions and gunfire. “Close contact east! Two is—”

The broadcast cut off, giving an instant of silence, while the numbers indicating squad-level radio traffic flashed and stayed lit. Chaos had descended upon the ambush.

Seconds later, the platoon-level channel opened again. “Lead, One! Two Lead is down. We are being overrun! Infantry and vehicles!”

\leavevmode\llap{“}Break contact. Pull back. I’m calling for support.”

\leavevmode\llap{“}We’re trying!”

In the other ear, the leader of the vanguard element reported that he was lifting fire. The Militia pony relaying information for the reaction force simply reported that they were in contact.

Dusty was nodding in satisfaction, and after a few seconds, keyed in again. “Ranger Lead, Command. If the reaction force has that ambush locked down, I want you to keep the column moving at good speed. We can’t get bogged down here. I’ll get some more air recon up there for you.”

\leavevmode\llap{“}Ranger Lead copies. Wilco.”

It was just two minutes later when the final details of the conflict came over the radio. One dead and two wounded in the vanguard, with one more dead in the assault on the Serenity positions. In exchange, the timely counter-assault at point-blank range had devastated the ambushers. The final tally was twenty one casualties, all deceased. At least one had been merely wounded. It seems she had played dead until one of the Militia ponies came near, then tried to bring her rifle up to shoot him. They hadn’t taken any more chances after that.

I frowned when that information was passed on, but said nothing. I didn’t like it, but I understood it.

The leader of the assault estimated that no more than half a dozen changelings had managed to get away. The order was passed down to rapidly secure weapons and equipment, then fall back to the main column.

Dusty took a moment to pass on a request to Hail Burst, sending a pair of recon flights over to scout ahead. With that resolved, he brought up his map once more, scrolling another mile past the ambush point. I did the same, eying the multitude of location markers that had been passed over the Serenity network.

\leavevmode\llap{“}Okay,” Dusty said, looking back to me. “What’s next?”

{\br}%
Ten hours.

I thought I had acquired a decent experience with combat. I thought I had seen battle, or at least enough to have a good idea of what it was like. The carnage at Paradise Beach. The mercenary attack in the outskirts of Dodge City. Multiple firefights with raiders. All terrifying, chaotic, dangerous, and even traumatizing events filled with death and desperation.

But the longest of those fights was still measured in minutes. When our diverse army encountered Serenity’s first significant resistance, it kicked off ten continuous hours of relentless battle.

For those ten hours, battle raged, and I saw almost none of it.

Serenity launched five more raids over the course of the rolling battle, hoping to capitalize on the distraction of combat to strike exposed groups in the rear. Two tried to target the center group, where I was. One even descended straight down from the clouds, in what could have been a devastating attack if Dusty hadn’t been warned and ready to respond immediately. I could see the changelings in the sky, turned back by the Gemstone and Loyalist defenders. A few bolts of magic struck amidst the column, but as callous as it sounds when describing casualties, the damage they caused was minimal. It was the closest I got to the actual fighting.

The rest of the time, I might be able to see groups of ponies on hills or ridges, as much as a mile away, or the rapid movement and dusty plume of motorwagons displacing in reaction to some new threat. Sometimes I even saw them firing on distant enemies I couldn’t see.

Yet at the same time, I probably had a better picture of what was going on than anyone else, in either army.

That isn’t to say my view was perfect. There was still plenty of uncertainty. To determine where any group was, I had to rely on radio reports. Sometimes they came from that unit, while sometimes they came from others. Information came in too quickly for me to process all of it, so I had to prioritize general strategy over fine detail. Despite those limitations, I had a wealth of information. I tracked where everyone went to the best of my ability, listened in on their plans, and passed the information on to Dusty.

It was fascinating to watch him work, his eyes fixed upon the map as he passed down orders, a cigarette all but forgotten on his lips. The movements of the armies unfolded with agonizing slowness, like some glacial dance. Dusty would give the order for one of the reaction forces to move to counter an anticipated threat, and we might wait five minutes to hear that they were disembarking at their destination. Other times, the dance accelerated to a frantic pace; multiple platoons of Serenity soldiers moving at high speed, trying to exploit some perceived weakness in our lines, and our rapid and urgent responses to counter that threat.

Serenity had so many advantages on us. They were faster. Their soldiers were well-trained and exceptionally equipped. They were a single, unified force, without any inter-faction conflicts that might diminish their effectiveness.

Yet every time they made a move, their foe adapted instantly. Every time they exhibited some weakness, their foe exploited it. Every time they attempted a ruse, their foe refused to take the bait. By all appearances, Dusty was a master of war.

Of course, we were cheating. Neither of us had any problem with this.

As he told me, so much of what makes good tactics and strategy is intuiting what your enemy is doing and balancing the risks you take. Was that flank really weak, or was there another unit that could punish any attempts to exploit it? Was that ambushing force on its own, or did they have other units giving security? Did that enemy force really retreat, or had they just fallen back to better defensive positions? Was that withdrawing unit in good order or in shambles? What lay over that ridge? Where was the rest of their army?

Risk is a part of warfare, but when you know exactly where the enemy is and what they plan to do, you cut out most of the risk.

When the lead units came into contact, Dusty already knew where they were, and how to counter them. I watched as he directed platoons down poorly defended approaches, pinned down exposed defenders, and launched assaults on weak positions. Serenity’s more agile forces found themselves outmaneuvered time and again.

Through it all, there was one prevailing order: keep pushing. Stop to fight when needed, but then get moving again. If you weren’t in contact, you were advancing. Serenity lay before us. We had to push them back to their hive. The word had gone out: if we take Serenity, we win.

The dark clouds churned above us.

Despite our overwhelming advantage in information, Serenity’s soldiers tried their best, and their discipline showed. While Dusty managed to reverse their traps on them, they fought back fiercely. They rarely panicked, and never surrendered.

They even managed a few surprises. No mention had been made on the radio of land mines until the recon motorwagon lost a wheel to one. That kicked off a quick scramble as Dusty directed the reaction force to save them, narrowly fending off an assault by a Serenity force, to minor casualties on both sides. From then on, the recon element included one of the Militia combat engineers, a unicorn adept at detecting and disarming explosives. They found only six more mines during the march; few enough to be a minor expenditure, but enough to keep us wary.

Our motorwagon followed as the army continued its slow but steady pace, and half an hour after the vanguard made contact with the first real opposition, I saw another side of the battle.

The first corpse I saw was a changeling, not far from the path we rode along. She lay beside a dead bush at the edge of a shallow depression. Even as we passed just thirty yards away, I couldn’t see any signs of the injury that had killed her. If not for the awkward contortion of her neck and hindlegs from her sprawled position, or the bit of dirt scattered atop an extended wing, I might have thought she was asleep.

I didn’t spare many glances away from my map and radios, but it was enough to take in a bit of what the casualty reports had already told me. Serenity wanted to slow us down, and they tried to withdraw before Dusty could pin them down in a fight. Casualties were relatively light on both sides, but it was a slow trickle that continued on, hour after hour. The Loyalist’s skywagon flew back and forth, ferrying medical ponies to the front, or bringing the worst of the wounded back to the medical wagons. The less injured were patched up and resumed the march, or sat and waited for the next available wagon.

The dead were left for the logistics ponies to collect. I would see the occasional scattered corpse where Serenity had managed a clean escape. Where they hadn’t, I saw clusters of bodies. Little clumps of intense violence, signified by a dozen or so corpses. Most of these were changelings, but a few were ponies, killed where Serenity’s soldiers had fought back more effectively, or even managed some small-scale surprise.

I caught Dusty looking over some of those groups of fallen ponies with grim eyes. Then he took a deep drag on his cigarette, turned back to his map, and ordered more ponies to their deaths.

We rolled on, following the trail of bodies for ten hours.

{\br}%
We had almost two hours of light left when we reached Rotwater Creek. The lead elements of the army had taken up sheltered positions just a quarter mile from where the narrow ravine opened up into wider banks. On the map, it looked to be a passage about three hundred yards wide.

It sounded like a wonderfully spacious and open piece of terrain, until you factored in just how many soldiers were determined to kill us there.

\leavevmode\llap{“}Show me,” Dusty said, turned in his seat as I presented my PipBuck. Intercepted location markers dotted the far shore, noting Serenity positions, built-up defences, fall-backs, and support. Markers on our side of the creek noted sectors of responsibility for various units, and now, markers for “enemy” positions. They were making excellent use of the PipBuck technology. Any commander could put down a custom location tag, and their communications network would rapidly distribute it to every single Serenity changeling, and unknown to them, one particular non-Serenity changeling.

Our own mark showed us just a quarter mile back from the head of our army. It was the closest I’d been to the front all day.

I scrolled to the cluster of marks near the creek. “Their Charlie company has been setting up here. Our swing north forced them to relocate, and they arrived on-site about eight hours ago. They’ve been setting up defensive positions.” I pointed out several marks. “There’s a fortification on either side of the crossing, right by the edge of the ravine, to give a good crossfire, with mines scattered around the creek itself. There’s supposed to be a line of defenses forming a semicircle, extending about a hundred yards back from the creek. Then there’s a second pair of fortifications on a line two hundred yards back from that for supporting fire, with a few defensive positions between them. Details are pretty vague on how substantial the defenses are, but there was talk of prefabricated structures and heavy materials, as well as digging earthworks along each line. Good news is, they’ve been scrambling. Lots of chatter about how we’re coming on a lot quicker than they expected. The defenses are not nearly as complete as they’d like, and they’re probably tired.”

Dusty gave a satisfied grunt as I continued. “Their Bravo company arrived three hours ago, and they hauled a lot of material from the crossing they were originally guarding. It sounded pretty confused on the radio, and I think I’m only getting part of the conversation. Probably some face-to-face. They’ve split responsibility, so Charlie has the northern side of the defenses, and Bravo has the southern.

\leavevmode\llap{“}Delta and a freshly reinforced Alpha company were the units trying to delay us, and they got mauled pretty bad. They’ve been merged to form a single company, though they reported that they’re still ‘substantially’ under-strength and disorganized. They didn’t have a solid number on how many casualties they took today, but they’re guessing about a hundred-plus.”

\leavevmode\llap{“}That sounds about right for what logistics has picked up,” Dusty said with a nod. The non-combatants in our army hadn’t been at rest; as the army marched and fought, they’d roamed behind the lines, ferrying up ammo, and collecting bodies and equipment. “Last tally I heard was ninety six.” He frowned. “I’m still a little uncomfortable that there weren’t any wounded.”

I grimaced. Our own reports had come back, and while the total casualties were about the same, at least half of ours were wounded, with many expected to recover quickly. Then there was the substantial amount of equipment we had recovered, including sixteen sets of pegasus power armor in good enough condition to be rapidly pressed into service. The advantage of controlling the field after a battle, Dusty had said.

I continued. “The merged company, which took on the Alpha designation, was pulled back to the rear to rest and reorganize. They’ve brought forward Echo company instead, which sounds to be a mixed unit, like… reserves or something. It’s unclear. In any case, they deployed out here…” I scrolled the map two miles to the northeast, where a lone map marker—Echo flank—was tucked in a narrow valley. “Their orders are to wait until we start the assault, then press us from the flanks. They discussed using deception techniques to disrupt cohesion before shifting to regular tactics once we catch on. The plan is to disrupt the rear of our army and force it to close in with the front for safety, get us as condensed as possible, then hit us with the megaspell.”

\leavevmode\llap{“}So we won’t be letting that happen,” Dusty said. “That’s going to be rough. We’ll need enough air defense forward to fend off any megaspell attempt, but that might expose them to the enemy defenses. Any word on heavy weapons?”

\leavevmode\llap{“}Yes,” I said, scrolling back to the crossing. “At least two plasma cannons, one at each of the second pair of fortifications. Lighter equipment at the first pair, but still something. Maybe heavy machine-guns, by the sound of it. No word of artillery.”

\leavevmode\llap{“}They probably don’t need it when they control the skies,” Dusty noted. “We might be able to capitalize on that.”

\leavevmode\llap{“}Would be nice. There’s also a few separate units. Sky One through Three are air transports, probably skywagons, maybe sky-tanks. They’ve been mostly ferrying materials, and by last reports were lingering behind the force for further orders. Ghost One through Six are recon teams, and they’ve been roaming mostly on their own discretion, it seems. Then there’s another unit designated Mantis. No clear info on what that unit is, but it’s been relocated by Sky Two to this high ground here…” I scrolled to a rocky hill about half a mile west of the crossing. “Probably something that can’t be moved easily. Mantis has also been focused on vehicle sightings. It could be some sort of anti-vehicle unit.”

Dusty nodded again, eying the position. “Okay. Anything else?”

\leavevmode\llap{“}Their HQ and some unit designated Cicada—I have no idea what it is—are stationed in a hasty bunker two hundred yards back from the second defensive line. Logistics units are based just past that, with several motorwagons to ferry supplies. I don’t know if any of that helps us. There was talk about bringing in reserves from the hive, but they aren’t expected to be deployed until the morning, and there were concerns about proper equipment.” I shrugged. “And their megaspell is out there, somewhere. They plan to have it come in from the west, but that’s likely to change.”

Dusty slowly looked over the map again, eying every contour and defensive position. “All right. So, three companies, plus one understrength, and some light support. That’s almost certainly more than the Mareford Militia itself, but we still should outnumber them with everypony else. Not counting however many reinforcements they’ll be getting.” He frowned thoughtfully, mulling it over before continuing. “Guess it comes down to how good their defenses are. Let’s take a look. Starlight? Bring us up. Be ready to pull back if they lob shots our way.”

The engine thrummed as the wagon slowly creeped up the slope. The crest of the hill steadily drew closer, until the top of the distant hills showed above it. A few yards later, and we came to a halt, the valley open before us, with the distant line of the Rotwater snaking through the rough terrain.

Dusty brought up his binoculars, surveying the battlefield. I did the same, giving a quick look over the features. The crossing itself was a low depression of rough, rocky ground, where the steep walls of the ravine gave way to a low valley and gentle slopes. It formed a ring of high-ground over the crossing, and it was here that Serenity chose to fight. For having just eight hours to prepare, they’d established some significant defences.

The front-most fortifications were made of concrete blocks, with metal brackets visible to hold them together and cover any gaps. They must have brought those in by skywagons. The front two were set right where each ravine ended, with the steep, rocky slopes effectively protecting their flanks. Each had a long, low slit to let the occupants fire out of. Curiously, they were not pointed forward to where we would be coming. Instead, each fortification—or pillbox, as Dusty called them—faced the other, three hundred yards apart.

Low walls had been established on the high ground, surrounding the crossing. Most of those walls were simply places where Serenity had dug up dirt and piled it in front of their positions. In some places, large canvas bags had been filled with dirt to form large blocks, which were then used to form walls. Then there were a few places, notably on either side of the pillboxes, where concrete slabs had been used as a backdrop, and the dirt piled in front of it. Some of the walls even extended out on the flanks of the pillboxes, lining the edge of the ravine for some twenty or thirty yards. It looked as though these positions would give good cover over the ravine and anyone attempting to climb out of them, preventing us from simply going around to get behind the fortifications. The intent was clear: they wanted to funnel our largely ground-bound force through the crossing itself, where they could maul us with the greatest amount of firepower.

The second defensive line was further up the gentle slope, allowing the positions to fire down on the crossing. It, too, was built around a pair of concrete fortifications, though it was less extensive. The pillboxes were actually slightly larger, with a second level of barriers surrounding the plasma cannons atop them, but the line of defensive walls were scattered points rather than a continuous line. It looked like this line relied more on the rocky terrain and curvature of the slope to give cover, with earthen walls formed where cover was lacking.

Between the two lines, changelings were hard at work. At least sixty were digging, piling up mounds of dirt as they hurriedly added low lines of walls leading back between the two defensive positions.

\leavevmode\llap{“}Pretty serious defenses,” Dusty noted as I lowered my binoculars. Now that I had a good idea of the layout, my attention was better spent on the radios. “Looks like they know what they’re doing, too. They’re setting up secondary positions and cover for falling back. They’re going to make us fight for every inch, but they’re planning to give ground instead of dying on it.”

\leavevmode\llap{“}Any way to go around?” Starlight asked.

\leavevmode\llap{“}The nearest passable crossing is almost a day’s march south, and we can’t spare that much time if we’re going to beat the weather. Once the rain hits, that’s a couple more days for them to dig in. Besides, if we go for the other crossing, they can still get there first. We’d be facing the same thing there.”

\leavevmode\llap{“}I mean something more, uh… local? I mean, sure, the motorwagons can’t climb a cliff, but maybe a bunch of soldiers could go around and hit them from behind?”

Dusty slowly shook his head. “They’ve got good recon, and I’m going to assume Whisper’s right about them having good espionage. If we detach any significant force, there’s a good chance Serenity would know exactly where they are. I don’t want to split our forces in the face of a more maneuverable enemy. Something small-scale, maybe… but the bulk of our thrust is going to have to be right down their throat.”

Sickle snickered.

In my left ear, a conversation about logistics and rations was suddenly interrupted. “Break, break. Command, Mantis. Eyes on enemy command wagon, one one zero from our position, skylined on ‘enemy ridge’. Request permission to engage.”

Adrenaline came crashing down. “Dusty! Mantis sees us, and they want to shoot.”

He nodded calmly. “Starlight, roll us back.”

The motorwagon rocked as we drew back. I caught one last glimpse of the tall hill and its sheer cliffs, a mile away, before we slipped out of sight. “Heck of a reach they’ve got.”

Dusty grunted.

\leavevmode\llap{“}Mantis, Command. Negative. Hold fire for now. Keep eyes on them. Current intent is you will wait until the enemy forces are engaged in their attack, then take them out to disrupt leadership.”

\leavevmode\llap{“}Understood. Enemy command vic has withdrawn, now out of sight. They have something floating tethered to their vehicle, so we’ll track their position.”

\leavevmode\llap{“}Command copies.”

Crap. “Dusty? I didn’t really think of it, but they can still see the antenna, so they still know where we are.”

\leavevmode\llap{“}Of course,” he said, his eyes back on his PipBuck’s map. “I’m still trying to think if there’s some way to make use of that, lure them in or trick them or something. Still coming up blank there.”

I paused for a moment, thinking on the possibility of misdirection, before giving a shrug. “Nothing comes to mind.”

\leavevmode\llap{“}Yeah.” He sighed, silent for several long seconds. “Well, no point in delaying. Time to call everypony in.”

He brought up his broadcaster, and a minute later, leaders started converging on our position.

{\br}%
Fifteen minutes later, we were all gathered. Dusty hadn’t bothered setting up the tent this time, so we gathered in a level patch of ground, flanked by our motorwagon and Sandstorm’s tank. All the leaders were there. Sandstorm and Axle, Two Bits, Hail Burst, Dazzle, Seroon, and at least a dozen subordinates. All gathered around the table where Dusty had sketched out a rough layout.

He gave one final look over the group. “Okay. I’m not a big speech type of pony, so I’m not going to bore you with some big monologue about honor or destiny or any of that, but there’s one thing I do need to say: the fight here is going to be a big one. Probably \textit{the} big one. What we do here may well decide whether we win or lose. We’ve hammered them all day long, driven them back, but now they’re making a stand. If we can do what we’ve done all day, if we can deal them one more decisive defeat, then there will be nothing lying between us and their hive. They’ve been running from us all day. Now they’re standing and fighting. If we can push on just a little longer and crush them here, we win.”

There were murmurs and nods of approval.

\leavevmode\llap{“}I know we’re all tired after a day of marching, but they’ve had it worse than us. We’ve chased them across the Wasteland. They’ve been battered and bloodied. Right now, they need a chance to rest and recover. We’re not going to give it to them. We need to hit them before they dig in so hard that we’ll never uproot them. That means we need to hit them soon, we need to hit them hard, and we need to hit them \textit{smart}.”

He took a half step back, leading into the part we had rehearsed. “Now then, I’ve been discussing the situation with Queen Whisper, and she has a few things to say about our enemy.”

I nodded in gratitude before stepping up to the table. All eyes turned to me. There were no glares or looks of suspicion. All listened attentively.

\leavevmode\llap{“}We’re about to face a larger and more chaotic fight than most of us have ever experienced. Chaos leads to confusion, and this is something changelings are adept at exploiting. We’ve seen only a little of such trickery so far, but if they’re making a stand here, we can expect they’ll pull out every trick in the book. My kind’s greatest advantage is our shapeshifting ability. Changelings can look like anyone.” I put on a particularly grave and serious face. “This includes friendly soldiers on the battlefield.”

There were a few frowns and grimaces at this. Good. “Not only do we run the risk of having Serenity forces approach under the guise of friendly units, we run the risk of fighting our own forces if they mistake each other for changelings. We can’t allow that to happen. To that end, it’s going to be vital that commanders keep accountability. We have good communications. Know where your subordinates are, and know where nearby friendly forces are. As long as you do this, we’ll be able to punish them for any attempt, and deprive Serenity of its greatest advantage.

\leavevmode\llap{“}Above all, I would suggest restraint and caution. We don’t want to kill friendly forces just because we had a lapse in communication. If absolutely uncertain, keep suspicious groups at a distance and call for information.” I raised my PipBuck. “I will also be monitoring friendly radio traffic and tracking movements. If any suspicious circumstances arise, you can always ask Dusty, and we will be able to get to the bottom of it.”

I frowned. “And beware of individuals giving suspicious instructions or attempting to go somewhere or do something they aren’t normally allowed to do. It’s very likely Serenity have some Infiltrators in the army. If there’s any doubt about what someone says, stop them until you can contact someone higher up to confirm it.”

There were a few more nods, even if some ponies still looked concerned. When no questions or objections were voiced, Dusty stepped up again. “So we’ve got a lot to do,” he said. “This is what I want…”

I stood back, listening intently to every plan and detail, as Dusty slowly wove together a picture of what was about to unfold.