No matter how clever you are, how deceptive your schemes, how well you manipulate the course of events toward the outcome you desire, there will inevitably be times you have to intervene directly.

Hail Burst returned ten minutes after our meeting, with a pair of pegasi accompanying her. We had set tents by then, giving our second meeting more privacy. Five minutes after she stepped into my tent, she left, hauling the equipment I had supplied. Much of it I had gotten from her or the wreckage of the \textit{Cumulonimbus}: PipBucks, radio equipment, and cables. A few cases were strapped to the bundle, packing additional equipment. She left, returning to the Loyalist camp.

We both knew secrecy was important. As such, we ensured nobody could know what we had discussed in that tent. Aside from her presence and the equipment I had returned to her, the most any outside observer would have seen was my power-armor-clad head peeking out of the tent as she left, before securing the flap shut.

Hail Burst made good time back to her camp and roused her soldiers. Perhaps ten minutes later, those soldiers filed into the large tent Dusty had ordered erected for them, where Hail Burst and the returned equipment was waiting. Some of the soldiers were grumbling. One arriving pegasus called out, “So what’s going on, anyway?”

\leavevmode\llap{“}This is a mission briefing,” Hail Burst replied. “Operational security rules are now in full effect. No communications with anyone outside this tent until we finish our sortie. Understood?”

Replies of “Yes ma’am” rippled through the tent.

\leavevmode\llap{“}Good. Now, this mission is both sensitive and critical, so we’re bringing a specialist on-board.”

The latches of one of the cases snapped open, she lifted the lid, and a cat hopped out to stand before the gathered pegasi.

I allowed them a moment of staring before transforming, returning to my regal disguise. A few flinched from the sudden burst of magical flames, but mostly the reaction was murmurs and looks of discontent.

Hail Burst gave me a nod. “I’ll allow Queen Whisper to explain the initial situation.”

\leavevmode\llap{“}Thank you,” I said, with a tip of my horn, before looking over the gathered ponies. Without their armor, they looked like any brightly colored group of ponies, if more on the physically fit side of the spectrum. “The situation is this: we have uncovered a critical opportunity, and we are taking every measure to ensure that Serenity has no warning of our discovery. The matrix disruption grenades Hail Burst subjected you to were modified by me to disrupt changeling magic. While both she and I felt it extremely unlikely that a Serenity Infiltrator would have been able to replace and impersonate any one of you, we both agreed that we had to be absolutely certain. While Serenity has lost some of those assets in recent days, it would be foolish to ignore the threat they pose. We are operating under the assumption that they still have a strong and effective espionage force, and that it remains a significant threat.”

\leavevmode\llap{“}Fortunately,” I said, with a sly grin, “they are not the only ones skilled in espionage.”

I held the grin just a moment for dramatic effect before returning to a serious expression. “In just over four hours, changelings from the Serenity hive will hit the overloaded clouds above, kicking off a massive storm.” A few ponies blinked in surprise. Some murmurs rippled through the group. “Thirty minutes after this, the team carrying their balefire bomb will use the cover of the storm to deliver their weapon here. Their orders made it clear that they were expected to do this no matter what circumstances stand in their way, even if it costs them their lives.”

More murmurs, louder. One pony called out, “How the hell do you know this?”

\leavevmode\llap{“}I’m afraid the specifics of how I got this information will have to remain secret,” I said. “Right now, only a few of my companions, and Hail Burst, know.”

\leavevmode\llap{“}It’s a damn good source,” Hail Burst said. She was even smiling, small and predatory.

\leavevmode\llap{“}There’s also one more crucial piece of information I uncovered,” I said, allowing my own grin to return. “We know exactly where the megaspell is.”

Hail Burst stepped forward, her smile even sharper than before. “And we’re going to take it.”

{\br}%
Sunbeam, a cute yellow pegasus that looked deceptively pretty for a soldier, gave a firm tug on my back. “Okay. Chest is secure.” The power armor fit snugly around me, an exact fit.

I smiled, replying in a perfect mirror of her voice. “Thanks,” I said, shaking my head to flick the copied golden-blonde mane from my face. “Sorry you have to sit this one out.”

\leavevmode\llap{“}Eh, I never was good at night flying. Bad-weather night flying? Hah.” She made a cute scrunched-nose expression before returning to a more serious look. “Here, you’ll want to tuck the mane in loosely at the edge of the neck armor. It’s kind of a pain in the flank otherwise.”

She guided me through the procedure, weaving it back and forth until it was loosely secured and I could slide the helmet into place. “No pinching or pulling?” she asked.

I rolled my head to check. “It’s good. Comfy”

\leavevmode\llap{“}Good. That’s the helmet secure,” she said, giving a gentle tug on the helmet to make sure. “Okay! Let’s get your mission equipment loaded up, then we can step through system checks.”

She helped lift the package of equipment that Starlight had hastily modified. One of the heavy pieces of radio equipment salvaged from the \textit{Cumulonimbus} formed the base, with four of my salvaged PipBucks strapped on and plugged in, effectively turning it into the largest broadcaster attachment in history. A set of heavy cargo straps were looped around my body, cinching the equipment snugly against my underside. It was awkward to stand with, especially with the cluster of three antennas protruding from the back, scraping against the ground.

A few minutes were spent stepping me through a quick check of the armor’s systems and making sure the interface between the PipBucks and the armor was working. By the time we were done, I felt like I understood the armor a little better. I even finally figured out how to display the time.

\leavevmode\llap{“}Okay, that’s it. You’re good for flight.”

I thanked her one last time before waddling over to Hail Burst. The pose was awkward, but I couldn’t help but note how much better the armor fitted me. I’m not sure how much of it was because of being in pony form instead of my hard chitin, or because it was already adjusted to Sunbeam’s body, but it was much nicer than my previous experience. I was tempted to just walk around, enjoying the feeling of the well-fitted armor around the lean and athletic body, but the equipment strapped between my legs made that awkward. Besides, we had more serious matters at hoof.

I was, naturally, the last to be ready. Hail Burst gave me a quick last-minute rundown on what we were doing. We’d gone over it before, but I could appreciate the double-checking to ensure we were on the same page and not forgetting something. We were setting out on a difficult task, and I had never flown with them before; best not to take chances.

She called everyone into position, giving a final layout of formations. We shuffled around, arraying ourselves as we would fly. With a final look over our group, Hail Burst nodded. “Okay. Let’s do this.”

She turned, and we followed, exiting the tent. Her wings spread as she exited, taking to the air as she broadcast. “Command, this is Loyal Lead. Departing.”

\leavevmode\llap{“}Copy, Loyal Lead. Good journeys.”

She was already ascending, keeping a relaxed pace as more pegasi took to the sky, quickly falling into formation. I followed directions, just as she had briefed me. Downdraft trailed off her left wing, with Soaring Heart off her right. I positioned myself to trail similarly off their wings, directly behind Hail Burst, so we formed a simple diamond formation. My eyes glanced regularly to the E.F.S., making note of everyone’s position. In the darkness of the night, under those dark and roiling clouds, the black armor was already difficult to make out.

The Loyalists quickly fell into formation behind us, trailing off on either side like a giant, inverted V. Once the last team reported as in-position, Hail Burst radioed to us. “Kicking it up.”

She accelerated, and we followed, climbing towards the clouds. Our course was taking us east. Away from Serenity. Away from Point Firefly.

We were only a minute out when the Serenity scout channel came to life. “Lead, this is Ghost Five. Eyes on enemy fliers, about twenty strong, tracking east from point Target, ascending.”

\leavevmode\llap{“}Copy, Ghost Five. Shadow enemy fliers. Update when situation changes.”

\leavevmode\llap{“}Ghost Five copies, wilco.”

I reached down to the relevant PipBuck, casting quick glances to check on what I was doing while maintaining my position in the formation. It took several seconds before I confirmed I was on the right channel. Hail Burst and I had chosen an unclaimed channel for direct, private communications. “Hail Burst, an enemy scout has eyes on us and is trying to follow.”

Her head swung around, searching the sky below us, then around us. It was several seconds before she replied. “Any idea where?”

\leavevmode\llap{“}Negative,” I replied, perhaps unconsciously mimicking some of the professional radio habits I’d been listening in on. “I can’t really operate all this stuff while trying to maintain formation at speed. She’ll probably end up on our tail, or close to it.”

\leavevmode\llap{“}Understood. Keep me updated.” Then it was back to silence, with only the sound of the wind passing under wing.

Minutes later, we were approaching the underside of the cloud cover. It loomed ominously, ever closer. Miles away, the clouds flickered as lightning lit them from within. It was like a dark, hungry thing, waiting to devour us.

The world rapidly dimmed as we slipped into the edge of the clouds. The temperature dropped. Moisture gathered on my lenses and the underside of my wings. Visibility, already poor, plummeted. The erratic changes of air pressure made flying feel like running in sand, unpredictable and slippery, while sudden and unexpected gusts of wind tried to throw me around.

This wasn’t the first time I’d flown through clouds, though it wasn’t something I had a lot of experience in. In daytime, thin clouds might limit you to a few hundred feet of visibility, like a light fog. Thick clouds might limit that to a few dozen feet, which was really too close for flying at anything but a creeping pace.

In these churning storm clouds, in the dead of night, I was essentially blind, yet we kept flying at a swift and steady pace. Even after reverting to my natural eyes and their improved low-light sensitivity, I could barely make out the rare glimpse of the ponies just five feet ahead of me. I kept my eyes locked on the E.F.S. markers, making rough adjustments as I tried to keep them all aligned in their proper place, while hoping I was ascending at a steady rate.

The radio came alive with Hail Burst’s voice. “Leveling out, seven-three-hundred.”

I glanced over to the altimeter readout, seeing that I was just shy of the prescribed number. I hit the toggle Sunbeam had indicated, and an illusionary line appeared across my vision. It was supposed to act as an artificial horizon, giving me some semblance of up and down in the near pitch-black environment. I did my best to remain level, my altitude slowly weaving back and forth around the correct number, all while trying to keep the E.F.S. contacts in the right place.

I might have grumbled about how even the pegasi’s armor had the woefully short-sighted 2D design mentality behind their E.F.S., but I had too much on my hooves to spare even that much thought.

Hail Burst radioed again. “Turning right, two-six-two. Snooze.”

And that was it. We were alone. That last word was one of the codewords she had briefed me on. It meant we were to maintain radio silence until told otherwise.

The E.F.S. contacts started to swing right, and I banked to follow. In the darkness, I caught little glimpses of shadow and light. Every now and then, some thinning of the clouds gave me a glimpse of a silhouette. A flicker of distant lighting filtered through the clouds, giving me a strobe-like image of the pegasi in front of me before plunging us into darkness once more.

The numbers on the compass steadily drifted upwards, and I finally leveled out on the given bearing. My altitude wavered, but I caught the motion and steadied myself.

A minute later, Serenity’s scout broadcast again. “Lead, Ghost Five. No eyes on enemy fliers. They disappeared in the clouds.”

\leavevmode\llap{“}Understood. Sweep the area quickly. If you can’t re-establish contact, then return to station.”

A minute later, the army commander broadcast on the command net, alerting all her forces that the entirety of the Enclave forces had departed from the army, heading east, and that their current position was unknown.

It was inevitable that they would know we were making a move. I just hoped they couldn’t imagine what that move really was.

We flew on.

{\br}%
I don’t think I’ve ever been on a flight that was so mentally draining.

Every single moment was spent fighting the tumultuous environment in an attempt to maintain formation with ponies who, most of the time, I could only perceive through colorful E.F.S. indicators.

It was with immense relief that Hail Burst spoke, without assistance of the radio. “Popdown and rally.” The voice was quiet in the dense clouds, but both Downdraft and Soaring Heart echoed the command, and it made its way back along the formation, quickly passing out of earshot.

I nosed down, entering a gentle dive as I maintained position. The occasional flicker of light showed I had drifted above Hail Burst’s level, and I corrected.

We leveled out at the very edge of the clouds, slowing to a halt, and I breathed a sigh of relief. It was still quite dark, but now I could see much more of the formation. Better yet, I could see the ground spreading out below me. A quick glance at the map revealed we were directly above Point Firefly.

I wiped away some of the accumulated moisture from my helmet’s lenses, and looked down. Far below, nestled into a tiny valley in the rough terrain, I could see a half-dozen ghostly rectangular shapes, ever so slightly paler than the terrain around them.

Hail Burst gestured in a circle with her hoof, and the formation condensed. As they did so, Hail Burst drifted closer to hover right before me. “Any activity?”

\leavevmode\llap{“}None,” I said, with a shake of my head.

\leavevmode\llap{“}Good.” She looked around to her fellow pegasi. “Let’s make this quick and clean. Spread.”

The Loyalists quickly spread out, individual groups separating from the others. A few seconds later, Hail Burst made a sharp gesture with a forehoof, tucked her wings, and plummeted downward.

A second later, every single pegasus was diving, plunging toward the ground in silence.

Only I remained there, hovering at the edge of the clouds, watching the receding forms descending in the darkness.

I turned to my equipment, double-checking every PipBuck screen. Everything was ready. Serenity was, for the moment, silent.

The radio in my right ear squawked softly, followed by Hail Burst’s voice. “Alarm.”

There was a little spike of adrenaline, despite the simple meaning behind the codeword. It wasn’t a call to alert, like you might think. It was simply the opposite of “Snooze”. It meant we were no longer on radio silence.

Of course, we were no longer on radio silence because that was a matter of stealth, and stealth was about to no longer matter. My hoof moved to a button, hovering.

The left earbud came to life. “Hey! We’ve got fliers coming—”

My hoof jabbed down, and the transmission turned to garbled digital nonsense. The heavy communications equipment strapped to my underside hummed with arcane energy as it flooded the Serenity frequency with random noise, overpowering the weaker transmitter.

There’s a certain satisfaction in turning a foe’s own trick upon them.

I immediately moved my hoof to the broadcast button. “You’ve been spotted! Jammer is on.”

Far below, a storm of fuchsia lights erupted, illuminating the ground with flashes of impacts. A few shots sailed up into the air, return fire that had missed. Friendly channels were lighting up as individual team leaders directed their soldiers.

I switched over to another private channel to carry out my next responsibility. “Dusty, the raid has made contact with the enemy.”

His voice came back with only faint artifacts. “Copy.”

A few bursts of warbling nonsense sounded in my left ear. A couple channels had lit up, transmitting something that got through the jamming enough to not be discarded by the decryption program as random noise, but not clear enough to be understood. I turned in place, aiming the trio of antennas as I examined another PipBuck screen. Indicators popped up, pointing south.

I really wish I could have had more time, so I could whip up a program to filter out the noise I was flooding Serenity with to pick out their signal, but that was probably a multi-day project to get right. This close to the jammer, there was no way I was going to make out anything on the Serenity net. Still, if I couldn’t make out what they were saying, at least I could do direction finding.

There was just the small concerning fact that I didn’t know of any Serenity forces to our south.

I looked out to the south, scouring the dark folds of the earth below. I had a bearing, but no distance. I didn’t even know if the signal was important. Maybe they hadn’t even been related to our attack. Maybe this was a completely unrelated bout of communication, and they were still unaware.

Several bolts of magic arced through the sky, shots that had missed the attacking Loyalists and sailed onward.

No, it was safe to say that anyone within several miles knew something was going down.

Hail Burst sounded in my ear. “Three, break north. The skywagon lifted and is trying to make a run for it.”

A quick glance found the distant, dim outline of the skywagon leaving the camp, heading roughly north. They must have had someone in the harness, ready to fly. They were already leaving the heavy fighting behind. From what I could tell from my vantage point, the fighting was intense, and extremely one sided.

\leavevmode\llap{“}These bugs are fucking suicidal!” someone shouted over the radio.

\leavevmode\llap{“}They’re protecting the wagon,” Hail Burst replied. “Two, extend. Get distance, don’t get drawn into a close fight.”

\leavevmode\llap{“}Trying!”

\leavevmode\llap{“}One has casualties, will need medic once we’re secure.”

\leavevmode\llap{“}Same for two!”

The skywagon was arcing around in a turn. I could barely make out the black dots of soldiers escorting it, and a short distance away, the pursuing Loyalists. Streamers of magical fire reached out, and the escort turned to engage, flying straight at the attacking ponies.

\leavevmode\llap{“}Three has merged with enemy escort. No longer in pursuit. Target now tracking south.”

The skywagon had leveled out, sweeping past the dying fight at the camp. Several Loyalists broke away. “Four is breaking south, in pursuit.”

I quickly scanned ahead of the skywagon. If they turned to fly by the force attacking them, there must be a reason for it.

It was a good ten seconds before I caught a glimpse of movement, and a few more before I picked out exactly what I had seen. I quickly keyed in. “Enemy forces inbound from the south, about twenty or thirty of them, maybe three miles out.”

\leavevmode\llap{“}Copy. Four, change of orders. Bring that wagon down.”

As much as we might want to capture that megaspell, depriving Serenity of it was even more important. Capturing it had always been a long-shot; no doubt they’d be prepared to detonate it, rather than allow its capture and potential use against them. The Loyalists flew into this fight with full knowledge of this.

Magical bolts sailed out in long streams. Even the distant fire drew a few flashes of hits from the skywagon. The pursuing Loyalists were already faster, and as the skywagon weaved evasively to avoid the incoming fire, that edge grew.

I glanced out south again. “Enemy forces at two miles now.”

The fighting at the camp had ended. Soaring Heart swooped down to tend to the injured while the rest regrouped and sped south. I pushed forward, flying along above them as I skimmed the underside of the clouds. Several more flashes lit up the side of the skywagon, and it banked away again. The pursuing Loyalists were only a couple of hundred yards behind it, and as it banked into a turn, one scored an accurate burst. Fuchsia bolts smashed into the side of the wagon, producing several flashes and bursts of magical flame all around the cockpit.

The wagon continued its roll, inverted, and plunged downward.

\leavevmode\llap{“}Splash! Target going down!”

\leavevmode\llap{“}Bugout!” Hail Burst called, repeating it twice more. Every Loyalist banked hard, flying away from the stricken wagon at top speed.

The skywagon fell to the waiting ground, and at the last moment, I saw a flicker of sickly green at its rear, darting away.

\leavevmode\llap{“}Someling is carrying the bomb!” I called out. “They bailed out. It’s continuing south!”

\leavevmode\llap{“}Re-engage!” Hail Burst, and the Loyalists wheeled around again.

My radio direction finding gear was indicating more signals, almost all strong and from the south. The fleeing changeling was likely calling for help. It would have been impossible to pick her out in the darkness, but the faint glow from the megaspell was like a beacon.

Hail Burst was on the radio, rapidly giving orders to different groups and coordinating their approach. It was perfectly clear that they couldn’t catch the fleeing megaspell before it reached the approaching changelings. She was getting ready to smash through them.

As soon as the firing started, the difference in experience became clear. The majority of the Serenity force aimed straight at the center-most teams of the Loyalists, who were already turning away to pull their enemy in one direction. The other Loyalist teams, which had flown off to the other side, now banked around, lining up right on the Serenity soldiers’ flanks. Their opening exchange of fire was devastating.

Within moments the fight had devolved into a chaotic storm of swirling black forms and flashing magic. Changelings and pegasi were completely indistinguishable at such a distance.

For a terrifying moment, I lost track of the megaspell. Then the faint glow caught my eye again, speeding away in a new direction.

While the individual team channels were swamped with radio traffic, there was little on the Loyalist command channel. I keyed in. “The megaspell is escaping, heading east.”

\leavevmode\llap{“}Understood,” Hail Burst replied with remarkable calmness. “Pursue. Maintain visual. We will engage when able.”

\leavevmode\llap{“}On it,” I said, and beat my wings hard, picking up speed.

The fleeing changeling was still trying to transmit. Only garbled nonsense reached my ear. I glanced to my map, hoping to see who she was trying to contact. Her course was leading her right toward the general area of the enemy army opposing us.

That also meant she was heading right toward our army with the megaspell.

I switched back to our private channel. “Dusty, things are messy out here. We’re pursuing a changeling carrying their megaspell, but they’re heading toward the army. I’m not sure if we’ll stop them in time or not.”

There was a telling pause before he replied. “Understood.”

The furious furball of fighting had already died down to more sporadic fire. The number of black dots had dwindled.

\leavevmode\llap{“}Three,” Hail Burst called out. “Are you able to break off and pursue the megaspell?”

\leavevmode\llap{“}Three, affirm. Breaking off east. No joy on target.”

\leavevmode\llap{“}Whisper, guide them in.”

I pressed the button. “They’re almost directly to your east,” I said, pausing a moment as I looked back to the pursuing Loyalists, read the bearing, and did some quick math. “Eight five degrees from your position. About one mile out.”

\leavevmode\llap{“}Zero-eight-five, one mile, copy. Target altitude?”

\leavevmode\llap{“}Low,” I said. “She’s pretty much skimming the ground.”

I could see the cluster of forms breaking off from the rest of the fight, speeding east in pursuit. They made good speed, but there was a lot of distance to make up. I pushed myself harder, wings beating furiously against the weight hanging from my underside; I didn’t want to fall behind.

Miles ticked by with disturbing speed.

Hail Burst reported that the enemy was driven off or defeated and that they were joining the pursuit. Then she called for me. “Whisper, relay to Dusty that the bugs have changed tactics. They’re fighting like they don’t care if they live or not as long as they take us down with them.”

\leavevmode\llap{“}I’ll tell him,” I said. Then, after a moment of thought, added, “Are you all right down there?”

\leavevmode\llap{“}Casualties are light. Relay the message.”

I did so, repeating the information to Dusty before giving my own additions. “Any changeling would give their life to protect the hive. We might see suicide tactics or other desperate measures.”

There was another long pause before he replied, the background now filled with noise. “Noted.”

I turned my attention back to the pursuit. The fleeing changeling had made good progress, but the Loyalists had made more. “Three has tally on megaspell. Committed.”

They’d closed to about three quarters of a mile. It was too far for accurate shots, but they lobbed a few bolts. The megaspell-laden changeling veered as one passed nearby, then straightened out again, flying as hard as she could.

I double checked the map. She was ten miles from our army. With their army having pulled back three miles, that gave us… five or six miles until she reached the rearmost elements, and a \textit{lot} of support.

\leavevmode\llap{“}This is Whisper. She’s going to reach enemy lines before Three can catch her.” I pushed my magic out, pouring it into my chest and wings. Muscles toned and thickened, bones growing in density, the armor growing tight around my chest. “I am engaging.”

\leavevmode\llap{“}Understood,” Hail Burst said, with just a touch of skepticism.

I pitched down and plummeted, wings beating furiously. Within moments I was plunging downward at a tremendous speed, diving toward the rapidly-growing green dot. I quickly ran through the checks Sunbeam had described. Weapons showed a full charge. A toggle changed the display of SAFE to ARM. A targeting reticle appeared before my eyes. Fire mode was set to automatic.

The speed was almost too much, the wind whistling loudly around the equipment strapped to my chest. Maneuvering was growing difficult, with even gentle attempts at corrections threatening to send me out of control. I stopped beating my wings, holding them loosely at my sides, riding out the dive in a full stoop.

I could see the fleeing changeling in detail now, low to the ground and flying fast. She was clad only in light armor, the glowing megaspell clutched against her chest. A tiny shift of my wings and the angle of my tail adjusted my dive, the aiming reticle slowly drifting up until it was in front of her.

Fifteen seconds. I spread my wings slightly, pitching up a little more to track my target.

Ten seconds.

At five seconds, I bit down on the bit, loosing a stream of blindingly bright magic. I spread my wings more, pulling up to keep pouring shots into where I hoped she would fly. The reticle swung up over the horizon as my wings spread all the way, swooping up from my attack. I’m not sure how low I had gotten in the dive, but I’m certain the altimeter had dropped to two digits.

I banked, swinging back around and looked over my shoulder. My speed had brought me up a good ways, and I could see the lingering glowing remnants of my shots. A bright flash of green drew my attention back to the fleeing changeling, only to find feathered wings beating furiously away from me. She’d turned into a griffin!

I swung around, wings pumping hard to keep my speed up. I needed every ounce of it; she was flying even faster than before, likely having made the same kinds of alterations to herself that I had. If not for the advantage of altitude, she probably would have been out of my reach. I dove again.

At least she wasn’t heading toward the rest of her army. That happy thought lasted only a moment until I realized what lay just north of us. A quick check of the map confirmed it: we were just two miles from Serenity.

She couldn’t make it to the army before being intercepted, so she was trying for the closest bastion of safety, where hundreds of changelings could back her up.

\leavevmode\llap{“}Three, this is Whisper. She’s making a run for their hive, due north. We’re two miles out.”

\leavevmode\llap{“}Copy.”

Except now she was banking right again. I banked as well, quickly lining up and firing another burst, but I was practically perpendicular to her path. I misjudged the lead, with my shots passing harmlessly behind her, and then I was rolling level and climbing once more. Once I’d gotten a bit of height again, I started to turn, looking back to find her once more.

My radio blared. “Whisper! Break left!”

The urgency brought me into action before I’d really processed what had been said; I heard left, so I banked hard to the left, moments before a stream of magical bolts whipped through the air. She’d turned to engage me!

I tightened the turn, rolling almost inverted to dive, trading altitude for speed. A quick glance at the compass gave me a direction, and I pulled out of the dive low to the ground, speeding southwest and, hopefully, toward friendly Loyalists.

A quick glance over my shoulder immediately found her, but she hadn’t pursued me. She had instead turned north again, and now she was the one with the advantage of altitude.

With a whistle of wind, several Loyalists swept past me, flying faster than I could manage. It was up to them now.

I called up my magic again, the armor loosening as I undid my modifications. “This is Whisper, disengaging.”

\leavevmode\llap{“}Copy, Whisper,” Hail Burst replied. “Gain altitude, pursue, and observe.”

\leavevmode\llap{“}Will do,” I said, already banking around and climbing, the world opening up once more as my viewpoint ascended.

The pursuing Loyalists had taken advantage of the brief dogfight to close in, and they opened up from a little more than a quarter mile. It was still a difficult shot, but any attempt to evade brought the Loyalists a little bit closer to catching the fleeing changeling-griffin.

I’d finally gained enough altitude to see, past a distant ridge, the partially constructed office building. “She’s one mile out from Serenity.”

The Serenity soldier was speeding across the valley. Only a low ridge separated her from the safety of her hive. Her evasive maneuvers were tiny, little bobs and weaves, but it was enough. Shots passed all around her, a few coming so close they might have singed her feathers.

She shot over the ridge and dove toward safety.

The pursuing Loyalists lobbed a few more shots, but as they reached the ridge, they turned sharply away. “Three is aborting pursuit. Entering orbit.”

\leavevmode\llap{“}Understood,” Hail Burst said. “Whisper, where is it going?”

While the Loyalists circled the site at range, the lone Serenity soldier sped toward the half-constructed office building, stripping away her disguise in a flash of magic. She dove past a rusted bulldozer, right where we had escaped in our stolen motorwagon. “She entered the site itself,” I said. “She’s out of sight. Probably underground.”

\leavevmode\llap{“}Okay,” Hail Burst said. “This could work. All flights, establish one-half-mile orbit around Serenity. We’ll be holding and keeping the weapon penned in until ground forces get here. Whisper, call Dusty and get me an E.T.A. And tell him to hurry!”

I looked east as I switched channels. There, just a mile, maybe a mile and a half away, I could see lights. I allowed a small smile. I knew the plan; soldiers were told to keep their gear packed and ready to move out at first light. The moment I’d passed Dusty the word that we had engaged, he called the commanders he had previously briefed. He said he could have a hundred soldiers loaded and rolling out in motorwagons within five minutes of my call, maybe less.

After all, why make one sneaky move when you can make two with twice the distraction?

\leavevmode\llap{“}Dusty, Hail Burst wants to know your E.T.A.”

\leavevmode\llap{“}About three minutes. What’s up?”

\leavevmode\llap{“}The megaspell is at Serenity now. Hail Burst is trying to trap it there, but I’m guessing she wants reinforcements before the whole hive comes pouring out.”

\leavevmode\llap{“}At Serenity where?” Dusty asked. “On site, or in the Stable?”

\leavevmode\llap{“}Unknown,” I replied. “It’s not visible from the sky. It’s indoors or underground.”

\leavevmode\llap{“}Understood. We’ll figure it out when I get there.”

I passed on the message to Hail Burst, who replied with a simple acknowledgement and nothing more.

Seconds steadily ticked away. I could see faint forms stirring in the partially constructed building. At least a dozen soldiers emerged onto the top floor, and it looked like all of them had power armor.

The guiding light of the lead motorwagon was finally climbing the slope of the nearest hill. As they reached the top, they disgorged ponies, along with several of the magical energy cannons. Within seconds, they were pouring out fire at the ancient buildings. Serenity soldiers, hidden in the buildings, returned fire, but they lacked a proper response to the heavier weapons. The group that had gathered on the top floor disappeared into the building once more.

I could see Dusty dismount from our wagon, while Sickle hauled out the antenna, which had apparently been reeled in for travel. Once they were clear, the wagon was moving again, gathering with the other unloaded wagons.

As the convoy rocketed off down the slope on their return trip, Dusty radioed. “Whisper, how close would that megaspell have to be to Serenity to take it out?”

\leavevmode\llap{“}I’m not sure,” I said. “Stable-Tec claimed that a Stable should be able to survive a direct hit, but they seem to have been overly optimistic about a lot of things, and others were less convinced. I never saw any detailed studies, but from what little I heard, a detonation within several hundred yards, maybe a quarter mile, would probably lead to the failure of the Stable. Keep in mind that’s all speculation.”

\leavevmode\llap{“}So if they try to break out and we shoot them down, they might blow up their own hive. I suppose that might be some consolation.” He didn’t sound entirely convinced of that.

\leavevmode\llap{“}You’re far too close to survive that,” I noted.

\leavevmode\llap{“}Then let’s hope they don’t want to die more than they want to kill us.”

I sighed, but didn’t reply.

The ponies on the ground were pushing up under the supporting fire of the heavy weapons. Dusty was being aggressive. Fortunately, it seemed to work. Any Serenity soldier who opened fire faced a storm of return fire.

A cluster of six changelings burst from one of the buildings, shooting up into the sky. Hail Burst immediately directed two flights to pursue. “Don’t let them get to the clouds. If they can kick off that storm, they can sneak that megaspell right past us.”

I felt my heart hammer at that, and I radioed Dusty to make sure he knew.

\leavevmode\llap{“}That’s what I was thinking,” he replied. “We’re trying to take the entrance to pin them down. I’m concerned about the other underground tunnels. We know they cover a lot of this place. We need to secure any possible exit.”

Mareford soldiers had reached the edge of the site, taking position behind ruined cargo skywagons and the temporary construction shacks. The fighting was intensifying, close-range and hard, but Serenity’s defenders had been pushed back. Our side had the momentum.

The last of the changelings racing for the clouds fell back to earth, shot down by the Loyalists. It bought us some more time, but only a little. I may not have any experience with weather manipulation, but even I could feel the growing humidity.

A faint, rhythmic thumping caught my ear. Looking east, I could just pick out the pair of whirligigs coming in, quick and low, with the Loyalist skywagon leading them. The trio landed on the back edge of the ridge, behind the heavy weapons. They disgorged their cargo of ponies, some thirty or so, and then took to the air again, rushing back for their next load.

There wasn’t much for me to do but watch as the attack continued. Pushing the Serenity defenses back from the windows and doors was easy enough, but there the attack stalled. Ponies gathered at entrances, trying to force their way in, but it was slow going. The reinforcing ponies had taken up some of the side buildings, including the old C.L.T. offices we had previously investigated. Some of the initial assault force managed to take the ramp we had driven the motorwagon out of. Otherwise, it seemed we were at a stalemate.

I continued to circle above, keeping an eye on a situation that had essentially turned static. Minutes ticked by. I glanced down to one of the PipBuck screens, eying a readout and doing some quick math. “Dusty, I’ve got about eight minutes left on this spark battery. I’ll need to come down for a replacement.”

\leavevmode\llap{“}Make it quick,” he replied, and I banked around into a dive, descending towards his position.

I came in a bit too quick and back-winged too late, my hooves skidding across the dirt for a couple of yards before coming to a halt. Dusty was keeping his eye on the situation, but as I turned and trotted up to him, he opened the case set beside him. Two more heavy spark batteries lay inside. I reared up, using my wings for balance as he pulled the almost-drained spark battery from the communications equipment, and plugged the new battery in its place.

\leavevmode\llap{“}You’re set.”

The jammer whined back to life, and I gave a sharp nod before spreading my wings and taking off. It would have much better coverage at altitude.

That was about my grand total contribution to the fight for the surface of Serenity.

The whirligigs and skywagon returned several minutes later, unloading another thirty ponies that Dusty rushed to reinforce the uneasy hoof-hold. Serenity made counter-attacks, but Dusty was quite willing to give a bit of ground so that the heavy weapons could come back into play. We couldn’t push into the ruins or the tunnels beneath, but they couldn’t dislodge us. The rest of their army, weakened as it was, was either blind and deaf, or too caught up in a fight with the rest of our army to come aid the defense.

Not that they were a non-factor, mind you. It was ten minutes later when the flying vehicles returned again, flying close to the convoy of motorwagons for mutual protection. One of the whirligigs was smoking, with signs of magical energy weapon strikes along its side. When they landed, several of the ponies who exited were rushed to the makeshift hospital. None of them took off again; now that the rest of Serenity’s army was aware of what we were doing, the whirligigs were far too vulnerable to fly alone.

Once all the wagons were unloaded and returning for another batch of ponies, Dusty started giving directions, and that’s when the fight really kicked off. Another hundred ponies descended on the ruins. A cluster remained behind: Rangers, Mareford Militia using salvaged pegasus power armors, and the hulking form of Sickle. They loaded into the whirligigs and skywagon.

As Dusty directed the heavy weapons to lay down a storm of fire along the upper levels of the partial office building, the flying vehicles took off, rushing across the gap. One whirligig, Pidgeon, was small enough to land on the top floor. Even then, it was a narrow fit, slipping in between the open weave of girders that would have been higher floors, and which would have ripped off the vehicle’s blades for the slightest error in judgment. The other vehicles came to a hover beside the building, with ponies hopping across the gap.

It wasn’t a subtle move, and no doubt Serenity was already repositioning forces to deal with the new threat, but it opened up a new front. More importantly, it was yet another thing Serenity had to deal with, complicated by their impaired communications. Dusty was putting them on the back hoof, forcing them to react and keeping them off-balance, while the odds swung steadily in our favor.

On the ground level, ponies had pushed into the buildings. The ramp into the lower levels was firmly in our control, with more ponies heading in, pushing Serenity back. We were making progress, but I could see many casualties being pulled back from the fighting.

It was long and brutal, and all I could do was circle overhead, watching. The use of gas in the tunnels had been expected, and ponies quickly pulled back when it was used, giving back hard-fought territory. It prolonged the fighting, but every minute delayed was another minute closer to the next batch of pony reinforcements.

Less expected was the variety of booby traps. We first learned of these when a powerful explosion went off under one of the outer buildings, blowing it apart and collapsing an entire section of the tunnels. At least a dozen ponies were killed in the blast. Smaller charges showed up more frequently, hidden behind pipes or pillars. Casualties mounted.

Finally, a relieving report came back. “Command, Ranger Lead. We have secured the outer Stable entrance. The door is sealed.”

Serenity’s Stable was cut off from the outside world. We’d forced them to seal themselves up.

That also meant the rest of the changelings fighting in the tunnels were cut off, not that it slowed them down any. They fought fiercely, bringing us to a standstill. It wasn’t until another wave of ponies arrived that they could finally push into the remaining sections of tunnel by sheer weight of numbers.

Serenity’s soldiers didn’t give up. They never wavered. They fought with ferocity and skill, making those ponies fight for every inch, even long after the fight was lost.

In the end, they all fell, but they took a good number of ponies with them.

Dusty gave the word. “All tunnels secure. Ranger Lead, keep at least a platoon watching the Stable door. We’ll get a plasma cannon there to help. Every other unit needs to reposition for external defense. They’ve still got the remains of an army out there. Once defenses are established, start getting your ponies some rest. They’ve earned it.”

Even circling overhead, I could hear the many cheers going up. Serenity was trapped. We were entering a siege, but that was just a matter of time.

We had won.

{\br}%
All around the surface buildings of the Serenity site, ponies practically collapsed in exhaustion. Some had only a couple of hours of sleep before being woken up and stuffed in a wagon. A few didn’t even have that much.

Heavy weapons were arranged in the upper floor of the office building and in other sheltered locations. Sentries were posted. The rest of the force, hundreds strong, found places to sleep. They demonstrated some remarkable creativity in the endeavour. I saw ponies tucked into concrete pipe sections, nestled in the nook of a partially collapsed wall, or laid out across conduits running along a tunnel wall.

The Loyalists were taking a well-earned rest. By the time we had all landed, many were looking just about dead on their hooves. They might not have captured or destroyed Serenity’s megaspell, but unless it had somehow, inexplicably, slipped by us all, it was trapped somewhere in the hive. It was beyond our reach, but there was no way they could use it against us without destroying themselves.

Even Sunbeam looked exhausted when I returned her armor. She might not have participated in the raid, but she’d been flying rapid sprints with the skywagon to bring enough ponies into the fight.

When I looked at the weary Loyalists, I couldn’t help but notice that their numbers were thinner. I knew some were injured, off at the medical section with Soaring Heart, but that didn’t account for all of them. Five of the pegasi had not returned from the excursion.

The last convoy of motorwagons arrived almost an hour after the fight had ended. Exhausted ponies clung to battle-scarred wagons. They had been harried by Serenity forces on every trip, and the last had been the worst. Serenity had pummeled the last group of ponies defending the old camp, trying to crush them while they were out of contact. More than half of the defenders had been injured before the convoy had reached them, and Serenity hadn’t let up. Two of the motorwagons had been damaged and abandoned on the way back, leaving some ponies hanging precariously off the sides of those that were still mobile; leaving them out there with the disabled wagons would have been a death sentence.

The motorwagons descended the ramp, pulling into the underground storage chambers for shelter. The ponies who dismounted looked tired and battered, and none more so than the crews who had just made a half-dozen trips through hostile territory. Even the most obstinate and confrontational of the Trotsen ponies paid me no attention, despite the return to my queenly form. They were too exhausted for it.

Of course, I wasn’t there for them. I passed the first few wagons, until I reached our own.

Starlight slid out of the window, her usual nimble movements grown slow and slightly clumsy with fatigue. She dropped heavily to her hooves before looking up to me, and slowly smiling. She was still wearing the power armor Echo had repaired, though she had removed the helmet. “Heeeey. How’d it go?”

\leavevmode\llap{“}Well enough,” I said, and sat down to draw a little more even with her. “And you?”

\leavevmode\llap{“}I think I’m going to go sleep forever.”

I chuckled, raising a foreleg, and she stepped in, wrapping her forelegs wearily around my chest. I dipped my head, nuzzling gently as I hugged her back.

We were both asleep when, just an hour before dawn, the rain started to fall.