To start off, I’d just like to apologize if this particular recording isn’t up to my usual standards. It’s remarkably difficult to form a larynx that has sufficient audio fidelity with my natural voice while still fitting into such a small form, and the acoustics of the standard Stable-Tec ventilation duct leave a great deal to be desired.

Suffice to say, it’s been an interesting day.

{\br}%
Everything kicked off almost exactly twenty four hours ago, when all the leaders of our army came together to form a plan. We met in the center room of the incomplete office building, where a crude table had been made from sheet metal and old sawhorses. I led with a simple observation.

\leavevmode\llap{“}Right now, Serenity can simply bunker down and wait. We can’t siege them into surrender. They’re in a Stable. It was designed with the purpose of sustaining their population without any need for outside resources. Unless we want to have soldiers parked at their door for decades to come, we need to take some sort of action to force a surrender, or if necessary, destroy them.”

Hail Burst hummed softly. “What about sealing them in? Weld the door shut, collapse the whole site on them, all that? How long would that hold them?”

\leavevmode\llap{“}Not long. They’ve got plenty of equipment, and seem to have a decent industry. There’s an entire level of the Stable dedicated to workshops. If I had to guess, they’d be able to dig themselves out in less than a month. They might even be working on an escape tunnel right now.”

Dusty leaned forward. “I’m guessing you have some idea of how to deal with this?”

I smiled. He was right, naturally. “I do, and better yet, it’s one that focuses on saving lives. Serenity is entirely dependent on the dozens of ponies they’re holding captive. Without the love they provide, they’ll be forced to either come out or starve. It would give us the leverage to force a surrender.”

\leavevmode\llap{“}That would be nice,” Dusty said, “but I’m not sure how we do that. We’re not breaking through that entrance without massive casualties.” He glanced to Echo. “Not even with her able to teleport in explosives.”

\leavevmode\llap{“}I’m thinking something a bit more complicated, less head-on. I’m talking about another raid. We’ve already seen how dangerous a group of ponies can be when brought in behind enemy defenses, especially when done by surprise.”

Echo snorted softly. “While I appreciate your high appraisal of my abilities, I think you underestimate the difficulty of what you ask. You’re talking about blindly teleporting into a location I have never seen, over a distance that we can only estimate. I can assure safety for the act of teleportation itself, but I could not guarantee where we would arrive, at least not on the first trip. A small misjudgment could place us in the completely wrong room, or even the wrong level. Worse, any assault team could be split up, and I might not be able to quickly locate and evacuate them if that were to happen. This would be extremely dangerous.”

I nodded, still smiling. “I know, but what if it wasn’t blind?”

She cocked her head to the side. “Explain.”

Instead, I turned to Hail Burst. “The \textit{Cumulonimbus} had video cameras, correct? Do you still have any?”

\leavevmode\llap{“}Several, including one in each turret,” she said. “I’m sure we have at least one that still works.”

\leavevmode\llap{“}Good. Because if we take one of those, couple it with a broadcaster, and attach one of those little lift-cloud things, we can use it to to ‘test the waters’. Echo teleports it in, we use the cameras to figure out where it arrived, and we adjust from there.”

\leavevmode\llap{“}Could work,” Dusty mused. “They must know the danger Echo poses to them by now, so they’ve probably got internal defense already in place, but if we’re able to organize a hard, fast raid…”

Hail Burst was nodding. “Bust in, get those ponies out, and force Serenity to act instead of hiding. I like it.”

Dusty had frowned. “I’m not so sure that Serenity ‘acting’ is a good thing for us. Whisper, what’s your impression of their queen? Will she surrender, or do you think she’d do something desperate?”

\leavevmode\llap{“}I’ve had only brief encounters with Queen Chrysalis the Sixth, but the impression I’ve gotten was of a very driven and determined individual, absolutely sure of the correctness of her actions. I tried getting more insight from Calypter, and while she is a bit… distressed by recent events, she was of the opinion that Chrysalis would never surrender to ponies.

\leavevmode\llap{“}That said, I think I can still use the leverage the raid will gain us against the rest of her hive. I have no expectation of persuading all of them to surrender, but if we’ve removed their source of love and are offering the opportunity to surrender instead of just keeping them trapped until they starve to death, we might get some taking us up on the offer.”

Axle grimaced. “And then the ones who don’t surrender get trapped until they starve to death.” He shot me a look.

\leavevmode\llap{“}I’m not sure what to do about those who won’t surrender,” I said. “The fact is, a changeling queen holds a special place of reverence among changelings, much like Princess Luna and Princess Celestia did among ponies. There are some who will never surrender so long as their queen refuses to, and I don’t see Queen Chrysalis surrendering. Honestly, despite the harsh conditions and the inevitability of their defeat, I’m still a little surprised that we’ve convinced as many to surrender as we have. We’re up to…” I stopped, glancing to Two Bits. “How many are we up to, now?”

\leavevmode\llap{“}I believe we’re up to eighty two,” he said, double-checking on his PipBuck. While there hadn’t been another massive influx like the first group, surrendering changelings had slowly trickled in overnight and throughout the day. The lighter rainfall might have been a relief for them, but the rapidly dwindling supplies and numbers had convinced a few more to follow.

\leavevmode\llap{“}Thank you,” I said, nodding, before continuing on. “That’s already more than I had expected we would manage when setting out on this expedition, and I’m feeling more optimistic for it. We know some of the hive is willing to surrender even without Queen Chrysalis. If we can put more pressure on Serenity, make them desperate, and then give them a way out, we might convince even more to surrender. Even if we don’t, we still rescue a good number of ponies.”

\leavevmode\llap{“}Oh, yeah,” Axle grunted. “Let’s make them desperate while they’re sitting on a balefire bomb.”

Hail Burst’s eyes widened. “Holy shit. The megaspell. We just need to use that camera setup, figure out where that is, and then we can have Echo teleport in a bunch of explosives. Burn out the whole damn stable!”

\leavevmode\llap{“}Let’s focus on getting the captives out,” I said. “We can look into our options, including the possible use of the megaspell, once we’ve gotten that sorted out. For now, I’d like to come to a consensus on this rescue attempt. Are there any objections, or shall we do this?”

\leavevmode\llap{“}Seems like a good idea,” Hail Burst said. “Only question I have is who we’re sending in.”

\leavevmode\llap{“}You can work that out while we’re preparing the camera system,” I said. “Personally, I would imagine we want to sent our hardest hitters. Loyalists, Mareford Rangers, as many captured power armors as possible, all of that. Maybe some heavy weapons. I think I should go, as well. I’ve operated the suspended animation pods before, even if only briefly. I’ll also want to get inside so I can see about splicing into their public intercom. If we’re going to convince more of the hive to surrender, we need to communicate with them, and they’re not listening to the radio.”

Echo was frowning again, but didn’t say anything.

\leavevmode\llap{“}Works for me,” Hail Burst said. “The assault force goes first, though.”

I nodded. “Of course. There isn’t any point in me being there until we have secured the control room, after all.”

She nodded. “Okay. I’ll see about getting you the equipment you need. Anything else?”

\leavevmode\llap{“}I think that’s it,” I said, before looking around. “Are we agreed, then?”

Voices of agreement came from all around the table, and the group rose, heading off to their own tasks. I caught Dusty’s attention, asking to speak with him privately. Echo’s frown deepened, but she allowed us our privacy.

We stepped into a neighboring room, alone for the moment. Dusty stopped and turned, looking at me critically. “Putting off planning ahead doesn’t seem like you,” he noted. “What’s up?”

I smiled. I do really love his insight at times. “I am planning ahead. I just didn’t want to discuss it in public.”

He sighed. “Okay, \textit{that} seems more like you. Are you going to leave me guessing, or would you like to fill me in?”

\leavevmode\llap{“}That’s what I wanted to talk to you about.” I walked over to the window, sitting by the window. With the rain reduced to a light drizzle, we actually had a view, even it it was fairly bland. “This raid is important, and we need to get those ponies out, but I think we can do more with it. I want to use it as a distraction.”

\leavevmode\llap{“}A distraction for what?”

\leavevmode\llap{“}I’m an Infiltrator,” I said, shrugging. “Part of that includes scouting out or infiltrating facilities to gather vital information. We already know I can use their ventilation system to move around with some degree of secrecy, though I won’t say it’s entirely safe. That’s why I want to use a distraction. While they’re preoccupied with our raid, I want to use the opportunity to scout out the hive, and see what further action I might be able to take to end all of this.”

He was frowning, quiet and thoughtful. “...Depends. What ‘further action’ are you thinking of?”

\leavevmode\llap{“}Two come to mind,” I said. “The first is simple: locate the balefire megaspell, so that we can either take it or detonate it. We can’t leave it in their possession. I am concerned that, if they are driven too far into desperation, they may decide to use it to wipe us out, even if it destroys themselves in the process. They may see that as preferable to being subjugated by ponies.

\leavevmode\llap{“}The second is dealing with the greatest obstacle we face: Queen Chrysalis the Sixth. I don’t think she will ever surrender, and I expect the great majority of the hive will refuse to leave her side. I want to investigate the plausibility of removing her.”

\leavevmode\llap{“}You mean assassination,” Dusty said. It wasn’t a question so much as a clarification of what I said.

\leavevmode\llap{“}Yes. It’s a messy situation. Killing her may even harden some of the more devoted changelings, but without her presence, at least some might be willing to surrender. I think it’s worth investigating, to see if it’s plausible.”

He grunted. “I don’t know. You keep talking about how much changelings revere their queens. Killing her might make ‘em use the megaspell.”

\leavevmode\llap{“}Which is why the megaspell comes first,” I said.

He was silent for a few more seconds before sighing. “Okay, yeah. Scouting things out might be good. Hail Burst was right; if we know where the megaspell is being stored, we can end this any time we want. We’ll just need enough time to get everypony away, but it only takes a few dozen to hold the door. We’ve got transport to get them away quick.” He paused a moment before adding, “Good luck convincing Echo to go along with this.”

\leavevmode\llap{“}I think I can handle that.”

{\br}%
To start with, I visited Calypter again. Naturally, Echo wasn’t going to leave me alone and defenseless in the midst of all those changelings, so she walked with me, her critical eyes turning to any changeling who so much as looked at me.

My first stop was the center table, where the six love crystals sat, empty. For the second time, I pushed out my magic, the glow rekindling within them. I’d burned through a lot of magic in the past day. I was finding this regal disguise easier to hold, but it still drained a fair amount of magic. Add in feeding all these changelings, and it was starting to put some stress on me. Or more accurately, it was putting some stress on the people I was feeding on. Starlight had mentioned feeling more tired than usual. I’d have to start rationing a bit more.

With that done, I turned to find Calypter. She was sitting with a group of three other changelings, who all looked on uneasily as I approached them. Calypter looked particularly awkward, especially as I addressed her.

\leavevmode\llap{“}Hello again, Calypter. Can we talk?”

She glanced around before looking back to me, her ears drooping. “I can’t really say no, can I?”

\leavevmode\llap{“}You could,” I said. “You may all technically be our prisoners, but I’m not going to put that sort of demand on you. That said, I’d like to ask you something that might help your hivemates.”

She sighed and nodded. “Okay.”

I sat there, beside her and her fellow changelings. Echo remained standing watchfully behind me, while the other changelings watched, distrust and unease evident in their expressions.

\leavevmode\llap{“}I’ve been talking with Dazzle and Two Bits,” I said. “We’ve been working out how to get you all situated and fed, once this is all over. I’ve only got the basic outline settled so far, but I’d like to get feedback from you, or any of the other changelings here.”

Her head tilted ever so slightly. “Uh… okay? What is it?”

\leavevmode\llap{“}The short version is, they think there are places where they could use more hooves to help out. I think we’ll be able to arrange food and housing in exchange for work. We all agree it would be better to at least offer the opportunity rather than just dumping you out in the Wasteland to fend for yourselves. I don’t think that would be good for anyone.”

Calypter frowned. “So we get to be slave labor or starve. Wonderful.”

\leavevmode\llap{“}Absolutely not,” I said. “You’ll be treated the same as any pony in the same job. I was prepared to insist on it, but they had already decided to do so without my intervention. It might be a good while before you’ll be trusted with more sensitive work, like guard duty, and you’ll probably be watched carefully at first, but you’ll be treated fairly. And while I doubt it will be necessary, I \textit{will} be double-checking to make sure that promise is upheld.”

I could see their suspicion rising in their expressions. Perhaps I was playing the whole Generosity thing up too much.

I smiled and rolled my eyes. “If you’re looking for any self-interest, my hive will have to live alongside ponies as well, once it’s established again. It’s in my interest to promote the acceptance of changelings as friends and equals. I think we’ll all be better off working together.”

They continued to stare at me, until Calypter grunted quietly. “Guess we’ll see.”

\leavevmode\llap{“}There’s a lot to be gained from such a cooperation,” I said, still smiling. “We are far more versatile than ponies, able to adapt better to our roles. Then there’s the advantage of flight. You might have noticed there’s a severe lack of pegasi here below the clouds, which opens up a great many opportunities for us. We have a lot to offer. At the same time, ponies are also better than us at some things. Earth ponies have their innate magic, from strength to enhanced crafting to magical agriculture, and unicorns can perform magic that’s beyond all but the most talented of changeling queens.”

Calypter looked to the other changelings sitting nearby, who all looked equally unsure of what to think of all this.

\leavevmode\llap{“}What I’m saying is, you’re not going to be forced into dangerous or demeaning work, and there will be plenty of opportunities for better employment. Jobs like craftsmares, or couriers, or the like.” I paused, then gave a little chuckle as I glanced at Echo. “Or magical research.”

Echo eyed me warily.

I looked back to Calypter. “Actually, that might be a good example of cooperation. Echo here is conducting research into changeling magic. She believes she can make the world better for both ponies and changelings by crossing over the behavior of one species’s magic to the other. She’s been watching me shapeshift, though I have to admit, I’ve been a bit preoccupied lately. She might offer a job as research assistant. Love, food, and shelter, in exchange for shapeshifting every now and then. How does something like that sound?”

Echo’s wary glare was now fixed firmly upon me, the other changelings forgotten. Meanwhile, Calypter cast a quick glance to her companions before turning a suspicious eye to me. “That certainly \textit{sounds} generous…”

\leavevmode\llap{“}We’re trying,” I said, smiling and giving a little shrug. “Though it wouldn’t surprise me if Dazzle already talked your ear off about Generosity.”

The change in Calypter’s expression was subtle. Her ears twitched forward, head rising a hair, the hardness of her expression relaxing ever so slightly. “She has,” she said, and as she spoke, I caught a momentary flicker of emotion. It was hard to make out, some low-level but sincere appreciation, perhaps. Dazzle was making an impression on these changelings.

Both sides were following in the hoofsteps of Emerald, in their own way, and my smile grew at the thought.

\leavevmode\llap{“}Yeah, she’s good at that,” I said. “Anyway, I mostly just wanted to ask about that, to get a reaction to any plans for the future. There isn’t anything firm in place just yet. Probably won’t be, until this is all resolved. And…” I had steadily shifted to a frown as I talked, ending with my ears drooping slightly. “Well, there was another thing I wanted to ask you, and it’s not quite as cheerful.”

Concern had returned to Calypter’s face. “What’s that?”

I gave a sigh before continuing. “The situation is coming to a head. Right now, it looks like Queen Chrysalis intends to fight to the death, and she’ll take the rest of your hive down with her. I… I know the previous attempt wasn’t successful, but I was hoping you might have some insight on how we might convince your queen to surrender, instead.”

Calypter’s expression fell, ears drooping. She looked down, her voice quiet. “She’s… not my queen. She disowned me.”

\leavevmode\llap{“}And I think we both know that doesn’t make you any less devoted to her or your hive,” I said, my voice soft. “Or that it makes any of this less painful.”

She winced, turning away slightly. “...No.” She huffed in a deep breath before continuing. “I… I can’t think of anything.”

\leavevmode\llap{“}I’m sorry to hear that,” I said. “I’ll still give it my best try, but at this point… well, I wanted to make sure you were forewarned.”

Calypter’s breathing had deepened, and I saw her blink several times. She didn’t answer.

\leavevmode\llap{“}I’m sorry,” I said, rising to my hooves. “I hope I’ll have good news when I talk to you again.”

Still no answer. She sniffled once as I started to walk away.

I steadily made my way out, weaving through the small crowd of changelings. Every single one of them watched me.

We had just exited when Echo stepped up closer to me, her eyes narrowed. “What are you up to?”

\leavevmode\llap{“}Echo, I—”

\leavevmode\llap{“}You’re going to do something foolhardy and reckless, aren’t you?” she said, moving in close. With her hair flowing aggressively and wings spread, she did a great deal to make up the head’s difference in height between us. “That’s what that was all about? Right?”

I sighed, and motioned further down the tunnel. “We need some privacy.”

\leavevmode\llap{“}Fine.” She stalked past me, and I followed, avoiding her strangely ethereal tail.

Once we had gotten a safe distance down the spacious tunnel, she turned to glare at me again. “Well?”

\leavevmode\llap{“}To start with,” I said, coming to a halt before her, “I do not intend to be reckless. I plan on taking a carefully calculated risk, and—”

\leavevmode\llap{“}And you know quite well that your appraisal of risk and mine do not in any way match up. You risk not only your own life! You risk delaying the salvation of all ponykind!”

I habitually raised a hoof to correct her. “All people, not—”

\leavevmode\llap{“}Ugh!” she groaned, throwing her head back in an exaggerated show of frustration.

\leavevmode\llap{“}And in any case, I knew you would object, and that’s why I wanted to bring you to speak with Calypter.”

\leavevmode\llap{“}Yes, I understand exactly what you are trying to do,” she said, fixing me with a glare again. “You’re being deceptive and manipulative to get what you want, \textit{again}.”

\leavevmode\llap{“}I’m not being deceptive in the slightest,” I said, frowning. “Misleading or hiding information would be counterproductive. The entire intent was to establish another source for your research if something were to happen to me, so I could then use that to ease your concerns, and none of that would work if I didn’t present it upfront and clearly to you.”

She frowned as well. “...Yes, well, it was still very manipulative.”

\leavevmode\llap{“}Ponies might not like to say it, but any conversation where one party wants to convince someone to do something they don’t want to do is essentially manipulative in some degree. Coercion, rationalization, appeals to emotion, bartering, they’re all ways of getting someone to do something they’re not otherwise inclined to do. I’m bartering. You want a cooperative changeling to assist in your research, so I ensured you will have one, regardless of what might happen to me.”

I gave her a moment to contemplate that before adding, “And I could also note that I’ve already arranged that assistance for you, regardless of whether you choose to accept my proposal in return.”

Her thoughtful look vanished under a flat glare. “\textit{That} is manipulative.”

I smiled. “Maybe a little.”

She held the glare for a couple of seconds before looking away. “You are so incredibly frustrating. Part of me wants to be angry with you, while another part of me admires the way you construct arguments in such a rigorous fashion. It’s so… conflicting.” She sighed and shook her head, fixing me with a fresh glare. “Fine. What are you planning?”

{\br}%
Echo’s irritation was at least mollified once she started tinkering with the equipment I had requested.

The pair of cameras Hail Burst supplied us with were rugged devices, each about the size of a loaf of bread. While Echo and Starlight worked on getting one mated to a small lift-cloud generator salvaged from a cargo-lift, I hooked up a spare PipBuck and broadcaster to the other for testing purposes.

A few quick tests with my diagnostics equipment mapped the outputs, and a bit of spell-matrix wrangling adapted the existing data-channel functionality of Serenity’s encryption spell to work with the video output. More difficult was the awkward bridging of another PipBuck’s receiver to a banged-up video monitor. Convincing the PipBuck’s spell matrix to pass on the data stream was an awkward affair. I’m a little embarrassed to admit it, but in the interest of saving time, I kludged a solution by copying much of the functionality of the audio playback and rewiring the audio jack. I didn’t even have a soldering iron, so it was all twisted wires and a few bits of stripped insulation tied around it to prevent shorts, with a few circuit connections simply wonderglued in place.

I didn’t manage to get that all working until the next morning. As soon as we were done with breakfast, it was time to try it all out.

Both PipBucks were set to the new frequency. The monitor was turned on, showing static. Finally, I turned the camera to look out from the sheet-metal desk to where Echo and Starlight sat, and turned it on.

The static remained unchanged. I frowned.

A second later, a flicker darted across the very top of the screen. It repeated, just a hair lower. Then again, and again, and again. As it worked its way down, shapes and forms started to show, starting with the tip of Echo’s horn and making its way down.

It was at least twenty seconds before the off-center image was complete, a single frozen snapshot of time.

The top of the image then started to fill with the next frame, identical to the first. This was a problem. Contrary to what the screen was showing, Echo now had an expression of confusion and dissatisfaction, while Starlight wasn’t even there any more, having moved to look at the monitor.

\leavevmode\llap{“}Well,” she said, cocking her head to the side. “It kinda works.”

I’d finally adjusted the display to center the image, and another little tweak adjusted the horizontal and vertical size to more-or-less fill the display. The second frame was complete, slowly being replaced by a third. “Not well enough to be useful,” I grumbled. “I’ll have to check a few things. Maybe there’s something in the spell matrix that’s holding up the process.”

So it was time for one of the most time-consuming and difficult parts of any complex project: troubleshooting and debugging.

The first step was simple enough: remove all of the intermediary parts and ensure that the camera and monitor were functioning correctly. I disconnected the PipBucks and broadcasters, and plugged the two devices directly into each other. The result was a perfect image with good framerate. This meant there was a problem somewhere in my solution, but this was a good thing; it meant this was something I could work on fixing.

Having established that the hardware on both ends was functioning correctly, I reassembled the chain of devices to investigate all that lay between. The next likely suspect was the encryption process, so I hooked up my own PipBuck and all my nice debugging tools, watching the spell matrix as it processed the video feed. Sure enough, it was using almost all of its processing ability on this data stream. This led to a short diversion before a second look revealed that it was processing the data as fast as the camera could provide it. It wasn’t the bottleneck.

A little more digging turned up something unusual. The encryption program fed into a buffer that was then sent to the broadcaster for transmission, but that buffer grew at an incredible rate. Even with an entire frequency to itself, the broadcaster’s radio simply didn’t have enough bandwidth to transmit the data in real-time. I was trying to pour a waterfall through a garden hose.

I turned to tweaking the video feed. Stripping the color channels from the luminance channel turned the image black-and-white, but also gave a small improvement in the time-per-frame. Next was the much more complicated effort of messing with the camera’s output. Its simplistic spell matrix was, ironically, much harder to work with, as it left me with fewer options to tweak. Many things I expect would normally be programmable were handled by dedicated crystal arrays, and altering them would have required rebuilding the whole thing. I eventually gave up and started replicating some of their behavior in a new spell on the broadcasting PipBuck.

This took up the bulk of the time, at least two hours. What I ended up with was a crude and likely far-from-optimal piece of spell-work, but it accomplished my goals. It stripped down the data and let me recompile it, with simple variables to control the resolution and the range of output values. By reducing those, I was finally able to bring the size of the data stream below the bandwidth limitations of the broadcaster.

The resulting image was tiny and rapidly scrolling end-over-end. I had to tweak the monitor’s settings all the way to their limits to get the display working properly. In the end, the video was grainy and washed-out, but I had cut the time-per-frame to about a tenth of a second. The entire chain of multiple encodings and decodings, plus transmission time, had also led to a good quarter-second of latency, but I was willing to overlook that. If I had more time, I might have worked on improving it, but it was sufficient for our purposes.

The time this took gave Echo and Starlight plenty of time to finish their part. By the time we sat down to lunch, they had gotten the camera-cloud floating, with a pair of desk fans wired up to a receiver. A simple tone broadcast on the right channel would activate each fan, allowing it to pitch and yaw.

Echo waved a hoof dismissively when I praised the ingenuity. “Compared to advanced arcano-tech engineering, this was trivial.” She managed to hold out a whole three seconds before adding, “But it was fun.”

After we presented our work to Dusty, it was time to get things rolling. While I prepared the equipment I would need for my own mission, he contacted Two Bits and Hail Burst, calling them over to brief them face-to-face.

By the time I had returned, a small bag in tow, they were down to discussing plans and tactics. Dusty brought me in to brief them on what we would be facing.

\leavevmode\llap{“}This entire level appears dedicated to their suspended animation technology,” I said as I presented my PipBuck and the relevant map. We all huddled around the tiny display. “That presumably includes both the simulated Serenity where they keep their prisoners, and the combat simulations they used to train their soldiers. We were held in Simulation Chamber One, here.”

I tapped the map. It was one of three chambers, separated by long halls that split the level into thirds. The chambers themselves took up most of the level.

\leavevmode\llap{“}I only had the two brief experiences with the place, so I can’t say what most of their standard operating procedures were, but I can tell you what the situation was when I was there. The chamber appeared to have an operating staff of eight. The one policy I do know is that there is a hard minimum of two staff in the control room at the back of the chamber, here. Two more were roaming the section, checking systems and the like. And finally, there were four changelings in pods, managing the prisoners inside the simulation. I don’t know what percentage of their time they actually spend in the pod, and it’s possible there were extra that day because of the new prisoners. That said, they’re oblivious to the world outside, but the control room has a way to communicate with them, and they appear able to revive themselves if they don’t get a response.

\leavevmode\llap{“}So we can expect a minimum of four to eight changelings. Given that they’re certainly aware of Echo’s teleportation and will take steps to mitigate its threat, there may be soldiers stationed throughout the Stable. The staff might have also been armed.”

\leavevmode\llap{“}That’s a lot of territory to spread out guards,” Hail Burst noted. “And we cut off most of their army. Even if they prioritize a few key locations, they’ll be spread thin until they can reinforce. If we catch them by surprise and move quickly, we might be able to take a few defensive choke points and hold them. What are we looking at for access points?”

\leavevmode\llap{“}That depends on how much we plan to take and hold,” I said. “I have no idea what’s in the other two simulation chambers. Given the size of the simulated combats Serenity conducted, it’s possible that the entirety of those chambers was used for that purpose, but I can’t be sure. We’d have to actually go in to find out.”

\leavevmode\llap{“}Couldn’t you send in the camera?”

\leavevmode\llap{“}They’re likely to be occupied, and the teleportation isn’t very subtle. If we do it before kicking off our attack, they’ll know something is about to happen, and have a good idea of where it will be. During the attack itself, teleporting the camera means not teleporting soldiers, and let’s not forget that even Echo’s magic is finite.”

Two Bits leaned in to peer closer at the map. “...Okay, the first chamber will be the primary objective. If we use that back hallway as a choke point, then it’s just that and the two doors into the main chamber. We’ll probably want to push out a little, and if we hold each end of the hallway outside those doors, and the intersection between them, that’s four, with good fallback positions. We can lock that down with a few squads, while the rest push out to check the other chambers.

\leavevmode\llap{“}If we do need to hold them… hmm. It looks like there’s only four stairways and three lifts, and there are two pairs that open into the same room. That’s just five access points for the whole level. That’s easily doable. We’ll need more ponies to sweep the rest of the level, but once that’s done, they’ll have a hell of a time uprooting us.”

\leavevmode\llap{“}It may not be that simple,” I said. “Remember, these are changelings. We can be very tricky. Shapeshifting into a smaller form can turn any vent into an access point. They may not be able to make an assault out of the vents, but if there’s an unobserved room, they could easily arrange the same sort of surprise attack we’re planning.”

\leavevmode\llap{“}That… puts a damper on things. Hmm.” He looked over the map some more. “How long do you think it will take you to get ponies out of the pods?”

\leavevmode\llap{“}Assuming I remember the procedure correctly, it’s about thirty seconds or so for the pod to cycle open, and less than a minute before the subject recovers consciousness. They’ll probably be disoriented and erratic, so waking a large number at once might cause problems.”

\leavevmode\llap{“}Echo can teleport them out as soon as they’re out,” Hail Burst said. “Let the ponies out here deal with that mess.”

\leavevmode\llap{“}Not a bad idea,” I said, nodding. “Saves us time, too. Assuming you’re up to that much teleportation?”

Echo was frowning, her gaze shifting slightly before fixing on me again. “It should be well within my ability… so long as there aren’t too many.”

\leavevmode\llap{“}Even after teleporting everyone in?” Two Bits asked. “Because looking at this, I’m putting a hard minimum of two platoons to do this, if we have to push out to secure those other chambers, and that’s assuming we fall back quickly. I’d prefer three.”

Echo tilted her head. “How many is that?”

\leavevmode\llap{“}Eighty to ninety ponies, minimum. Preferably more.”

Echo’s frown deepened. “...Yes, I believe I should be able to do that… but I am not certain I’ll be able to get everyone out again without a rest to recover. I shall try my best.”

\leavevmode\llap{“}How long a rest?”

She contemplated that for a moment, her eyes darting across the ceiling as she made calculations. “Approximately an hour, if I am able to rest. Less, if we could find a source of radiation. Maybe as much as two, if there are a lot of ponies to be rescued.”

\leavevmode\llap{“}Two hours is fine,” Two Bits said. “If we can get two platoons down there, we should be able to hold that chamber indefinitely.”

\leavevmode\llap{“}Just be ready for any tricks,” I said. “They had gas defenses outside the Stable. They may have more they could use inside. They might also do like they did on the \textit{Cumulonimbus} and breach a wall or ceiling to make a new access point.”

He nodded. “Yeah, I’ll be planning internal security, too. My plan is to move quick to secure the secondary objectives, then fall back to the primary. Teleport out any ponies in the secondaries that we can, haul the rest back, and hold until Echo is able to get everyone out. That minimizes the risk of breaching. As for gas, the rangers have masks. I assume those power armors of yours do, too?”

Hail Burst nodded. “Our face-masks have filters. I’ll make sure everyone buttons up for the op.”

\leavevmode\llap{“}Good, because I definitely want you in on this. You, the Rangers, and all the captured power armors. Round out with experienced Militia units. Sound good?”

\leavevmode\llap{“}Yeah.”

They turned to Dusty, who nodded. “Good. Bitsy, you’re lead on this. You can have your pick of the army. Make this happen.”

Two Bits grinned. “Yes sir.”

{\br}%
Half an hour later, the army was in motion. Under Sandalwood’s command, the bulk of the Mareford Militia was setting out into the light rain, taking up scattered defensive positions all around the site.

I had frequently lamented the two-dimensional thinking behind the E.F.S. design, so it was with some satisfaction that we were now taking advantage of it. Any Serenity defender would see hostile contacts in all directions, obscuring our movements. We had no idea how much of the Stable was in E.F.S. range of the surface, but at least the upper levels were. Hopefully it would reach down to the level we were going to.

In the center room of the building’s ground floor, our assault force had gathered. Almost a hundred ponies, many in power armor, stood ready to begin the rescue.

Dusty stepped into our room, where we waited with Two Bits. “Okay. We’re all set up here. Bitsy, kick it off.”

\leavevmode\llap{“}Yes, sir,” he said, and turned to Echo. “Find me a way in.”

She nodded. “We should be directly above the target room,” she said as she stepped up to the floating camera-rig. I watched the delayed image of her movements in the monitor. “The only question is estimating the correct distance down.”

With a flash, the floating camera disappeared. The screen flashed with a single frame of nonsense, then turned dark. For a moment, I thought it had stopped transmitting, but then I saw the shadow of shapes. The room it was in was dark.

\leavevmode\llap{“}Rotate right,” I said, and Starlight twisted the corresponding dial. Somewhere below us, the camera slowly turned, and a quarter second later, so did the image it was sending us. As it turned, I could see shelves, loaded with boxes and other containers. “Bring it back.”

The camera returned with a flash as I turned to my PipBuck, consulting the map. “...Yeah, that matches up with the storage room here, two levels up from the target. Near the ceiling, too.”

\leavevmode\llap{“}I see,” Echo said. “I will try again.”

Another flash. The screen flickered, then started showing blackness.

\leavevmode\llap{“}Light,” I said.

Starlight pressed a button, and the screen of the camera’s attached PipBuck came to life, turned up to maximum brightness. It was near the floor, and as the camera panned around, we could see the room was plain, vacant, and sterile, with only a pair of benches within it. It was the same room I had been held in after waking up from Serenity’s simulation. The same room where I had rescued Sickle. A reasonably sized room, just off the main chamber, but used infrequently at best.

\leavevmode\llap{“}And you got it,” I said, grinning. “You’re low to the floor, but otherwise good.”

Echo nodded. “One last check.”

With a flash, she was gone.

A moment later, the video flashed, and Echo appeared, staggering as she dropped a foot to the ground. She straightened, and nodded, and teleported again. The flash of her arrival beat the flash of her departure in the video.

Echo gave a thin, proud smile. “We are ready.”

Two Bits turned to Hail Burst. “Okay. You’re up.”

Hail Burst nodded and stepped forward. Five more loyalists followed as they gathered around Echo. Then, with a flash, they were gone.

Two Bits called out. “Next team, move up!”

I watched Hail Burst’s team move to cover the door, while the next six Loyalists marched up to Echo. She looked at the monitor, and as soon as the first team had cleared a spot, she teleported the second group in.

Teleport after teleport, the number of ponies in the distant room grew. By the time the last Loyalist was teleported in, they were clearly running out of room.

The radio squawked and came to life with Hail Burst’s voice. “Taking initial positions. Be ready on the music.”

I cast a quick glance to the bulky communications equipment set beside the desk. The indicators were lit, and the spark generator it was plugged into was running. I keyed in. “Music is ready.”

The Loyalists were already heading out the door. They would be taking up initial positions in the access hall, which would give plenty of room and easy defenses, but the chances of a random passing changeling spotting them went up significantly.

The moment they were clear, Echo teleported Two Bits and the first Ranger team. Following teleports took the other Ranger team, then two groups of Mareford Militia in captured power armor, including the massive Steel Ranger suit. Sickle was with them, and gave me a toothy grin, eager to get to work.

Echo’s general air of calm pride steadily decayed, replaced with a look of grim determination. I assumed she was feeling the strain of tearing a few tons of people and equipment out of reality and popping them back into existence a hundred yards away.

As the next group of soldiers were teleported, Two Bits called on the radio. “Beginning assault. Start the music.”

The salvaged communications equipment whined as it came to life. The video feed flickered faintly as the jammer flooded the nearby Serenity frequency. “Music is on.”

My awareness of the events below was restricted to the rare communication on the command net and a tiny slice of video from the room below. I could only imagine what was going on.

Apparently, my imagination was lacking. I was guessing that the fighting must be kicking off when Two Bits radioed out. “Primary secure. Queen is cleared to enter.”

Echo grunted. “As soon as I get the last of these soldiers down there,” she said, horn flashing as another batch disappeared.

I called up my magic, stripping away my disguise. My armor reappeared, fitting snugly around my body. I checked the fit of my holster, and slung my pack across my back. Then it was down to waiting for my turn.

The last group vanished, and Echo turned to look at me.

As I stepped forward, Starlight’s hoof caught my leg. “Hey,” she said, giving a nervous smile. “Good luck.”

I smiled back. “See you soon.”

She smiled a little more, and lowered her hoof. I continued on to stand beside Echo.

The world twisted around me as Echo’s magic deposited us both in the distant chamber below the ground. A pair of Rangers were waiting for us, already wearing their gas masks. The closest gestured with a hoof, her voice muffled behind her mask. “This way, ma’am.”

The pair set out at a trot, and I kept pace with them, even as I pulled out and donned my own respirator mask. A burst of automatic fire echoed from down the hall, followed by the sound of magical energy weapons firing, before silence returned. The fighting was continuing, but it was still low-key. Serenity’s reinforcements hadn’t arrived yet.

The pair of Rangers led us to the control room. I hesitated before stepping across the thin dusting of pink ash that had been one of the changelings stationed there. Through the windows, I could see the main chamber itself. A few ponies were trotting toward one of the doors, while a half-dozen had taken up positions around the room. I could see the form of a downed changeling near the middle of the room, clad in armor. So they had some soldiers here, after all.

Two Bits was at the window, and looked back as I entered. “Welcome to the party. Hail Burst is breaching the second chamber right now. Should have word on that soon.”

\leavevmode\llap{“}Thank you,” I said, eyes roaming around the room. I quickly found what I was looking for and strode over, snatching up the binder and opening it.

\leavevmode\llap{“}What’s that?” Two Bits asked.

\leavevmode\llap{“}Operating manual.” I continued flipping until I found the relevant section. “No harm in refreshing my memory while I have the chance.”

He’d stopped, ear twitching, then focused on his broadcaster. “Understood.” He lowered it and looked to me. “Chamber two is vacant. They’re moving on the last chamber.”

I nodded, looking back and forth between the manual and the various control panels, mentally running through the procedure to open the pods. It was fairly straightforward.

The sound of weapon fire reached my ear again. Two Bits glanced back. “They’re running into some light resistance, but they should have the chamber secure in—”

A loud squelch cut him off as the Stable’s PA system came to life. “Alert! Alert! Intruders have breached the simulation level. Wireless communications are compromised. All active security not on entrance duty are to converge on the simulation level immediately. All inactive and emergency defense forces are to immediately assemble at your designated rally point and join the defense.”

Two Bits frowned at the speaker. “Well, they were going to catch on eventually.” He turned back to his broadcaster. “Hail, you heard the lady. It’s going to get pretty spicy, pretty quick.”

He was silent a moment, ears perked, before speaking again. “Understood. She’s on the way.” He lowered the broadcaster. “They’ve got ponies. Chamber Three. Snapshot, get Queen Whisper there. Double-time.”

The Ranger mare gave a sharp nod to him, then a wave of a hoof toward me. “Follow us, ma’am.”

I snapped the binder shut, floating it along with me as I followed. Snapshot set a brisk pace, setting off at a canter as she led us out through the main chamber and into the connecting hall. The sounds of combat were already picking up, with rapid fire echoing down the corridors. Rounding a corner, I could see the backs of several Mareford ponies, including a couple of power armors, taking cover a good fifty yards down the hall, ready to repel attackers. The door into the chamber was just behind them.

Snapshot came to a halt by the door, raising her PipBuck. “Friendlies coming in, south door.” A momentary pause, then she opened the door, leading us in.

Hail Burst was there to meet us, her armor amplifying her voice. “Whisper. We’ve got five ponies and a griffin in here. Everything else is vacant.” She pointed to the shattered windows overlooking us. “The control room is secure, but not the access hall. Use the window.”

\leavevmode\llap{“}Got it,” I said. “Thank you.”

While she passed word on ahead, Echo and I took to the air, flying up to the window. We passed Sickle along the way, sitting beside a mangled changeling soldier. She gave a cheerful wave as we passed. She’d managed to get herself all bloody again, and I think most of it wasn’t hers.

The control room was trashed, having been subjected to a withering amount of fire, and scorch marks and craters pocked the walls. Almost all of the glass had been blown out of the windows, leaving us plenty of room to slip in. Another pair of pegasi were waiting for us. One gave a curt nod before turning his attention back to the entrance.

I turned and scanned the controls. Fortunately, they were undamaged.

A quick scan of the indicators located the six occupied pods. With the flip of a few switches, buzzers sounded and lights flashed over the pods. Another couple of switches disengaged various systems, and in less than thirty seconds, the pod doors were swinging open.

I looked to Echo. “You’re up.”

She nodded, spreading her wings to fly down, and I followed. She floated the unconscious ponies and griffin from their pods, gathering them together. A couple of them were just starting to stir when they vanished with a flash.

\leavevmode\llap{“}Okay,” Hail Burst said in her mechanical voice. “Get your royal flank back to Two Bits. Enclave! Thirty seconds and we’re falling back!”

\leavevmode\llap{“}Good luck!” I called out, and then we were cantering alongside Snapshot again, dashing out into the hall. In the minute we’d been inside, the volume of fire had grown tremendously. We slowed to a trot once we got back inside the main chamber, sufficiently removed from the combat for the moment. Shortly after that, we were climbing the steps to the control room once more.

Two Bits greeted us with a wordless nod, continuing his conversation on the radio. “Queen has arrived safely. Continue falling back. Call if you need support.” He listened a moment further before lowering his PipBuck again. “If Hail Burst and company can fall back and don’t get pinned down, we’re good here. Echo, will you be able to evacuate these captives?”

She grimaced, but quickly hid the expression. She couldn’t hide how her strange, ethereal mane appeared to hang lower, as if it were somehow more physical than usual. “How many ponies are there?”

\leavevmode\llap{“}Fifty-five. Not including the two changelings still in their pods.”

Echo grunted. “That’s a lot. But… yes, I believe I can. It will leave me quite drained, however.”

\leavevmode\llap{“}That’s fine,” he replied. “The sooner we can get them out of this place, the sooner Whisper can start her thing.”

As she made her way back to the main chamber, I turned to the controls again. After a quick scan over the occupied pods, I started opening them in groups of five.

I had just opened the third set when Two Bits told me the Loyalists had fallen back to our primary defensive line. We were as dug-in and prepared as we could be.

Not that it dissuaded Serenity any. The fighting was ferocious, and several blasts shook the floor under my hooves. Two Bits was quiet, listening in on the radio, but barring some crisis, there was little for him to do.

Finally, the last prisoner vanished. I could see Echo give a weary sigh before slumping down to sit against one of the pods, a hoof moving to massage the side of her head.

The captives were safe. Time to make use of that.

Two Bits had supplied one of the PipBucks they had retrieved from slain Serenity changelings, with its precious encryption key. I set it in front of me, then turned to my own broadcaster and our private channel. “Hey, Starlight. We’re set down here. Could you kill the jammer?”

\leavevmode\llap{“}You got it.”

I floated the captured PipBuck, retaking my queenly disguise. After all, I wanted to properly sound the part.

Warbling sounds came from the PipBuck’s speakers, as transmissions struggled against the interference. Several seconds later, the traffic cleared up, and I hit the button to transmit.

\leavevmode\llap{“}Attention, Serenity hive. This is Queen Whisper. As you no doubt are aware, pony forces have conducted a raid inside your hive. Your defenses are incapable of protecting you. We have just teleported out the last captive held in suspended animation.

\leavevmode\llap{“}I understand the significance of what we have done, and the severity of the situation you find yourselves in. Despite this, we have no desire to see you starve. We are willing to offer safe shelter to all who surrender. Already, the majority of your army on the surface has surrendered. They are being cared for as we speak.

\leavevmode\llap{“}Please, do not throw away your lives. Lay down your arms and surrender to these ponies before it is too late.”

I released the key, bringing the transmission to an end, and immediately turned back to my own PipBuck. “Okay, Starlight. Turn it back on.”

\leavevmode\llap{“}Jammer on. Good luck.” She sounded so far away.

Two Bits looked to me. “Think it’ll work?”

I sighed. “No. But that’s why I’m here.”

I met up with Echo, and we made our way to the room we had first arrived in. A pair of ponies were there to watch the room’s lone vent. Snapshot ushered them out and shut the door behind her, leaving Echo and me in private.

With the door shut, I turned to the vent.

As I worked, the Stable’s PA speakers squawked, followed by Two Bit’s voice. He gave his own offer of surrender, both reaching those who hadn’t been listening to the radio and reaffirming my own words.

The vent popped free. Echo eyed the opening warily. “Are you sure about this?”

\leavevmode\llap{“}I am.” No point in elaborating.

I called up my magic, and the world expanded around me. When I was done, I was in the same changeling-horned raccoon form I had used before. I gathered up my PipBuck, hooking it on a strap of my bag. My holster was strapped on beside it. Finally, I took up the strap in my teeth. The bag only weighed about ten or fifteen pounds, and while that was proportionally a lot heavier than I was used to, due to my current size, the strap made it easy to drag.

I crawled into the vent, dragging my bag behind me. Once I’d gotten in far enough to shove it aside and backtrack, I snatched the grate that had covered the vent, pulling it back into place.

Echo had crouched down, looking at me through the gaps. “Be careful… and good luck.”

I smiled a raccoon smile, clumsily squeaking, “Thank you.”

Then I turned, took up the strap once more, and scurried off.

{\br}%
Progress was slow. The bag dragged behind me, and required a little extra attention on the corners. Fortunately, it wasn’t too encumbering, but it did slow me down. The ventilation ducts were dark, lit only by thin slices of light where a vent looked in on a lit room, and snaked their way around the level like a maze. Fortunately, my PipBuck was automatically mapping this new space.

I’d been crawling for barely a minute when a clattering sound reached my ears, echoing from the duct ahead of me. The source was immediately apparent to me: I wasn’t alone in these vents.

Scurrying back a couple of yards, I hauled the bag down a pitch-black side passage. From the map, I knew it was a dead-end, but I had no choice. I conjured a tiny flicker of light, barely a candle, to guide my way, quickly reaching the vent barely thirty feet from the intersection. The room beyond was dark, and the vent itself created a tiny nook. I pushed the bag back behind me, tucking both it and myself against the grate of the vent. I didn’t have the time to open the vent, especially without making enough noise to give myself away.

Instead, I used what little cover there was to minimize my silhouette, hoping they wouldn’t see me. I floated my pistol forward, gripping the cumbersome object in my much-too-small paws. When my magic released, the candle-like glow disappeared, plunging me into darkness.

The sounds grew louder. I had to hope that they continued on the other way, and didn’t notice the gray lump in the darkness.

Whoever it was navigating the tunnels, they didn’t cast any light. The sound grew louder, and I focused on keeping my breathing slow and steady.

At the end of the passage, I saw a dark form shuffle across the gap, all sharp edges and faint glossy highlights. Some sort of insectoid form, most likely. I couldn’t catch any details, but I assumed it was a form much more suited to combat than my own. I’m not sure if that was an entirely justified assumption, but I didn’t care to test it. Better to assume the worst.

The sound was fading again, as they continued on down the duct. A lone changeling, then, likely conducting reconnaissance, and I was now behind them. Of course, they would be conducting reconnaissance for a larger group. If she found a good approach, these narrow ducts might become uncomfortably crowded.

I counted out thirty seconds before daring to stir. Turning back to my PipBuck, I held the earbud to my ear before pressing the transmit button. I spoke in a low whisper. “Two Bits, this is Whisper. Serenity has changelings in the vents, looking for a place to make an entrance.”

\leavevmode\llap{“}Copy that, Whisper. We’ll keep them all under surveillance.”

I waited until I was sure he wasn’t going to say more before stowing the earbud again, and another twenty seconds before I dared move. Taking up the strap of my bag again, I crept up to the intersection.

There was only the sound of air slowly blowing through the duct.

I rounded the corner and moved on, ears perked and alert for further hostile changelings, but none presented themselves. Soon I had reached the central utility shaft, where the ducts, pipes, and conduits that served the Stable traveled between levels. It was my key to the rest of Serenity. The soft thrum of far-away fans flowed through the ducts.

I carefully moved forward, worried that I would run into another changeling, but none presented themselves. For the moment, I was alone.

Time to get started.

Step one was establishing a “safehouse” of sorts. A place where I could hide if necessary, where I wouldn’t be found. I already knew where to go.

The bag hung from the strap in my mouth as I slid my way down to a duct two levels below, then started making my way out. About half an hour after I entered the vents, I finally reached my temporary safe-haven: the end of one of the ducts over Serenity’s zoology department. I remembered my first visit to Serenity, and the cluster of hostile contacts the wildlife there had shown. I was still within E.F.S. range of the scattered ponies on the surface, but I might as well gather every advantage I could.

So I hid myself in the cluster of hostile contacts and stashed my bag. The only thing I took with me was my pistol, with the holster strapped securely around my chest.

With my safehouse established, I moved on to step two: planning for extraction. As important as my mission was, I wasn’t ready to declare it “assets expendable” at the moment, so that meant planning on how to get me out of here.

Fortunately, that ended up being easier than I had dared hope for. On the opposite side of the zoology department was an equipment storage room. It was a large room with a single entrance, and plenty of shelves to hide behind. I retrieved my PipBuck before prying open the vent and dropping in.

I removed my holster and resumed my natural form, armor and all, and started radioing directions to Echo. Not long after, there was a purple flash. I blinked away the spots in my eyes, blinded until Echo’s horn lit up again, casting the room in a soft purple glow.

She looked around and nodded. “Yes, this should—”

\leavevmode\llap{“}Shh!” I hissed, scooting in close to whisper. “Quiet. We can’t let them know we were here!”

She frowned, then nodded.

I led her to the back of the room before whispering again. “When I call for extraction, I’ll be hiding here, if possible.”

She nodded again.

\leavevmode\llap{“}Okay, good. That’s it. Just make sure someone is always awake and monitoring our channel.”

She nodded once more.

\leavevmode\llap{“}That’s it, then. Head on back. And… thank you.”

She smiled. Then her horn flashed again, leaving me alone in the dark.

I returned to my raccoon disguise and slipped into the duct once more. I let the vent swing down again, resting on its frame but not quite shut. Next, I returned to my safe-point, stashing the PipBuck before heading out again.

Step three was the most involved yet, as it involved the thorough reconnaissance of multiple levels of the Stable. It was a solid three hours of scurrying through air ducts and peering through vents, but it proved valuable. My understanding of the space rapidly improved, and I got a better impression of the disposition of Serenity’s defenses. Regular guard posts had been established near major rooms and intersections, with small clusters of soldiers ready to respond to any threat that might materialize out of thin air. A good number of the other changelings going about their business were armed, though I have no idea if those arms were distributed before or after our attack.

I ran into the first stumbling block when I made my way down to the utility levels. I was making my way down a duct in the central shaft when I heard a clatter and burst of conversation below. With adrenaline burning in my veins, I dove into an offshoot and froze, ears perked. There were two voices, and both were slow and awkward. I was familiar with that sound; these were changelings who had taken on a different form, but either not skilled enough or simply not wasting the effort required to make their voices sound normal.

Between the distance, the soft thrum of machinery, and the echoing of the ducts, I could only barely make out the louder voice. They were complaining.

\leavevmode\llap{“}...doing maintenance while ponies are running around \textit{in our hive!} I swear, Shale has the most idiotic priorities. The whole hive could be on fire and she’d \textit{still} have us checking the water recyclers for contaminants and—”

A soft, metallic clank cut off her words.

I waited in silence for almost a minute before I heard a distant thump and metallic whine. Lying still as I was, I could feel the subtle change in airflow through my fur, and hear the distant sound of machinery. A couple seconds later, there was another metallic clank, and everything returned to how it was before, save for the quiet sound of someone moving through the duct. I waited, listening. About ten seconds later the same series of events repeated, and afterwards, the sound of movement was gone once more.

I waited another minute, and this time, there was no disturbance. I cautiously resumed my journey, keeping hiding spots in mind.

I had a good idea of what I was going to find. Sure enough, there was a place where the duct had been cut open, a latching door had been welded into it, and a series of bars had been welded along one side of the duct like a ladder.

That complicated matters, but maybe it could help me. They were using at least part of the duct system for travel between levels. The chance of a random changeling coming across me went up. Heck, they could open the door as I was traveling past it.

On the other hoof, it meant that seeing someone in the ducts wasn’t necessarily an unusual event. I wouldn’t be able to adequately explain my presence or stand up to scrutiny, but I might escape peripheral detection.

Still, I made every effort to move past the traveled area as quickly as possible, keeping hiding spots at the front of my mind. Fortunately, traffic was low. Perhaps they were more focused on the intrusion several levels up. Either way, I didn’t see anyone, and had soon mapped out a route that avoided those entrances.

It was spaces like this that made the Stable a self-enclosed ecosystem, and not just a bunch of quarters with some public spaces. It was a proper hive, much like home, but packed even more tightly. The utility levels, with their spark generators, air and water filtration, and other systems necessary for life, were only part of it. One level held massive artificial farms, with orchards and rows of crops. Another level was dedicated to industry, a whole factory full of priceless industrial machines. One vent looked in on a small room full of bins, holding hundreds of pounds of bottle caps, all freshly stamped and painted.

As I explored further, one of the key details I sought out was the various storage rooms. A Stable was intended to last for decades without resupply, and that meant plenty of room to store everything that could be needed. That included multiple armories, though peering through the vents showed that they were mostly empty. Presumably, most of their weapons had already been distributed. One was particularly well-guarded, with at least a dozen guards around and inside it. My heart-rate leaped as I peered through grates of the vent at the swirling, sickly-green color of the balefire bomb within. I had never wanted to be close to such a terrifyingly destructive device, and I was acutely aware that I was currently stuck in here with it, with my closest exit several minutes away.

My final stop was the one place that might be even more uncomfortable, but was just as vital: the Overmare’s office and quarters, where Queen Chrysalis the Sixth ruled her hive. According to the map, that’s where I had met her. No surprise that she’d claim that space as her own.

Of course, it wasn’t quite so simple to get there. At some point, someling had decided that measures should be taken to preserve the queen’s privacy. To do so, they had welded a couple of plates into the vent and bolted a grate with heavy, thick bars in place, blocking off the vent.

This was a complication, obviously. A quick test with my magic proved that the bolts were far too secure for me to remove by magic alone. I eventually had to backtrack to my extract point and coordinate an equipment drop from Echo.

When I returned, it was with a small set of wrenches. They gave me the leverage I needed, though it was still awkward. I had to slip them through the bars and work half-blind, and even then I had to go slowly to keep them from squeaking, a sound that was disturbingly loud in those bare ducts.

I had to be quiet. I could hear voices echoing faintly down the duct.

After several minutes of very careful work, I slid the grate out of place, laid it flat, and slipped past.

The Overmare’s office had been converted to something of a throne room. It was where I had first seen Queen Chrysalis the Sixth, when she had been talking about ending the reign of ponies. Now she sat there fuming, eyes narrowed, as she listened to a trio of soldiers discussing how to deal with the rapidly devolving situation. They were avoiding her gaze as they talked among themselves.

\leavevmode\llap{“}...could be an opportunity, if we can take it,” one was saying. “We have them contained, now. Their teleportation is reliant on a single individual. That means low throughput, and a single point of failure. If we can take out that alicorn, then we have them trapped. If we can’t, they’re still limited in how quickly they can get out. A swift strike might be able to overwhelm their defenses and kill a significant number of them.”

\leavevmode\llap{“}They’re too heavily dug in,” another said. “The only way to dislodge them is to either use a great amount of explosives to break their defenses, or force a massive assault to overwhelm them. Either would constitute a significant loss of assets. We risk destroying an entire simulation chamber, and we’ll certainly lose an unacceptable number of our soldiers.”

Chrysalis spoke, her voice icy. “How many?”

The second soldier hesitated, her unease apparent. “In an assault of that scale, down long halls with no cover? I think we’d be lucky to suffer only a hundred casualties. It’d probably be closer to two, and even if we wiped out the entire raiding force in the process, it’d hurt us more than it hurt them.”

\leavevmode\llap{“}We need to find a way around them,” the third soldier said. “We might not have found a good place to stage an attack through the ventilation system, but there are other ways of bypassing their defenses. Our engineers have already identified a few places where we can breach walls and floors to gain entry. With enough breaches, we could overwhelm them in short order.”

\leavevmode\llap{“}And wreck half the level in the process,” the second soldier said, shaking her head. “At the very least, we’d be writing off Simulation Chamber One, and given how thorough their internal security is, we’d probably face stiff resistance. They seem to be expecting some sort of trick.”

\leavevmode\llap{“}And their forces are all masked up,” the first one said, “so we can’t gas them out.”

\leavevmode\llap{“}Enough,” Chrysalis said, waving her hoof dismissively. “I’m tired of this. You are the military experts, you’re supposed to handle this. Just tell me, is there any chance they will be able to break out and threaten the rest of the hive?”

They were all silent for several long seconds before the second soldier eventually replied. “With their current forces, I would say very likely not, unless they’re able to pull something unexpected. The problem is, they can presumably keep teleporting soldiers in and become an even greater threat.”

Chrysalis paused, a smile slowly spreading as she tapped a hoof against her chin. “Hmm…” After a few moments, she set her hoof down, fixing the second soldier with a firm stare. “Good. Now stop bothering me with this and resolve the situation. If you can not do so by noon tomorrow, then you will keep the pressure on, encourage them to bring in reinforcements, and then we will take more drastic measures.”

\leavevmode\llap{“}Drastic measures?” the soldier said, ears flattening. “Like what?”

\leavevmode\llap{“}Like giving the last balefire egg to one of our soldiers, and using it to kill that pesky alicorn. Then, when they’re trapped, we can kill them at our leisure.”

\leavevmode\llap{“}What? But that would destroy most of the chamber!”

\leavevmode\llap{“}And that’s why I’m giving you until noon to find a better solution. If you can’t, then I will \textit{gladly} sacrifice that small part of our hive for victory. It doesn’t matter how much damage this hive takes if we can break their army. They are the ponies’ last, dying gasp, and the only thing standing between me and victory. It doesn’t matter if this Stable ends up as a radioactive crater; so long as I survive and they do not, our hive will end up ruling this land.”

She stood up, tall and lean. I was struck again by just how young she looked. Her youth clashed with my own concept of an older, more experienced queen. She must have been several years younger than me. “I don’t want to hear any more about this, unless something significant happens. I expect you to do whatever it takes to secure our victory. Now go, and tell Ocelli to enter on your way out.”

They bowed and hurried out, while Chrysalis returned to her cushions. Soon, another changeling I recognized entered the room: Ocelli.

She bowed deep and respectfully. “My queen?”

Chrysalis fixed her with a cold glare. “Have you reestablished contact with any of our Infiltrators topside?”

\leavevmode\llap{“}Only briefly,” Ocelli said, rising to stand once more, though she kept her head low. “We’ve had no word from our asset within the enemy army, but we’ve been getting regular updates from another asset currently on external observation of the target. She’s been trying to infiltrate the pony army, but it’s been much too densely packed to do so without being detected, even during the storm. It’s possible our asset within their army hasn’t been able to get the privacy necessary to contact us, and now that the ponies have activated their radio jammer, communications will be iffy.

\leavevmode\llap{“}Our external asset’s last report was… concerning. She noted the army spreading out, and that an infiltrated agent should have been able to find a moment to send an asset-intact report, especially after missing so many reporting windows. She’s concerned that the asset may be lost.”

Chrysalis wore a deep frown. “Or they’ve joined the other traitors.”

\leavevmode\llap{“}That seems unlikely, but... possible. Even if they did betray us, we’ve exercised strict information compartmentalization, and any sensitive information they might have somehow acquired would be at least a week out-of-date. I don’t think they’ve turned, but if they have, they won’t be able to cause any damage with their information.”

\leavevmode\llap{“}I don’t care about information,” Chrysalis said, scowling. “I care about losing another Infiltrator, right when we need them the most! That vile little queen is sitting up there, laughing at us while the ponies she’s manipulating are rampaging through our hive! I want her dead.”

\leavevmode\llap{“}We’ll certainly try,” Ocelli said, still looking at the floor. “There’s standing orders to eliminate Queen Whisper if at all possible, but—”

\leavevmode\llap{“}I’m not talking about ‘if it’s convenient’,” Chrysalis snapped back. “I want our Infiltrators focusing on killing her at all costs. She’s the one behind all of this.”

\leavevmode\llap{“}She is,” Ocelli said, with a cautious tone to her voice. Her gaze finally lifted, looking to Chrysalis with concern. “But at this point, I don’t think her death would meaningfully affect the army.”

Chrysalis’s eyes narrowed. “I disagree. You have your orders.”

Ocelli ducked her head again. “Yes, my queen. But… even if we were able to get a message out past the ponies’ interference, I’m not sure if we have enough assets in place to effect an assassination. She is very well-protected. The alicorn has powerful shields and seemingly refuses to leave her side.”

\leavevmode\llap{“}The alicorn is preoccupied with teleporting ponies into my hive,” Chrysalis said, nearly spitting out the words in distaste. “Their queen is vulnerable.”

She stood, advancing until she stood right before Ocelli, who kept her head respectfully bowed. Chrysalis didn’t allow this. Instead, she reached down, hooking a hoof under the smaller changeling’s chin and lifting, forcing her to look up. When she spoke, her voice was surprisingly gentle. “She has slipped through your hooves once before. I am tasking you with this because you are more motivated than anyone else in the hive to see her end. Do not let her slip away again.”

Ocelli swallowed, squaring her shoulders. “Yes, my queen.”

Chrysalis nodded. “Go.”

Ocelli bowed deep, then turned and left.

I lingered a while longer, but there was nothing more of interest. Queen Chrysalis the Sixth was apparently done with business, and I didn’t feel the need to watch her eat. I waited a few more minutes to see if anything interesting turned up, but it seemed she was done with meetings.

I slipped away, scouting out the rest of the area, including what I could see of her quarters, but there was little of interest.

Having completed my reconnaissance, I returned to my hiding place to wait.

{\br}%
And that’s where we’re at right now. I’ve been hiding here for the past few hours. I had a brief exchange with Two Bits. I passed on word to not bring in too many reinforcements, no matter the situation. Better to retreat and vacate the hive than bring in too many to evacuate. He passed on that not a single changeling had surrendered. The conversation took only a few minutes, and then I was back to waiting. I had some time to kill, and once I had gotten past some preliminary planning, I had nothing to occupy my mind.

Fortunately, my hiding spot is far enough from any vents that I can speak quietly without any risk of being overheard, so I’ve been passing the time with my recording. It’s a good way to keep myself occupied on something other than worrying. After all, I’m in about the most hostile place I could possibly be, surrounded by hundreds of changelings that would happily kill me, and my only way out relies entirely on the actions of someone else. De-stressing is good.

If I’m being entirely honest, it’s not the only reason I’m doing this. I may have started these recordings of my experiences as a way of managing stress and sorting out my own thoughts, but it soon became more than that. It became a way of preserving those experiences in a way others could understand, even if I wasn’t there to present it to them. It could be a way of showing ponies what changelings, or at least my hive, are really like.

But more than that, it could tell that tale to those of my hive.

My journey has been rife with danger. My profession is a constant series of hazards. There have been many times where I could have died, and all those experiences would have been lost. I’ve now insured the continuation of my hive, at least in body. I’m sure that, if the worst were to happen to me, my friends would do their best to raise my hive’s children to be good people, but it would still be incomplete. My hive is more than just a lineage. It’s a vast collection of knowledge, and above all of that, tying it all together, an ideal.

So I’ve made these recordings, weaving in the knowledge and ideals of our hive, and illustrating how they have guided my actions. It’s my hope that, if worst comes to worst, I will at least have this one gift to guide those who come after me.

Once I’m done recording this, I’ll be encrypting the audio files and sending a copy to Starlight’s PipBuck. She already knows the password to decrypt them. I do hope she won’t listen to it before we’re done here, though. I don’t want to worry her with this sort of talk.

If you are listening to this before I get back, don’t mistake this for me being fatalistic. I’m just being “depressingly practical” again. You know how I am. And to be perfectly honest, I really doubt anything bad will happen to me. I’m in a good position, with a clear way forward, and fairly easily managed risks. This is just a reasonable precaution before a major, potentially game-changing event.

After all, at this moment, there are two changeling queens in this hive. By noon tomorrow, at least one of us will be dead.