And so, the destructive power of a megaspell was unleashed on Equestrian soil once more. In an instant, hundreds of lives were scoured away by balefire. Those who looked back saw a quarter-mile-wide swath of ground heave up, hang there for a moment, and come crashing back down.

The mighty Serenity hive was gone. Only a radioactive crater remained, laced with veins of balefire. Their machinations that had threatened the denizens of the Wasteland, pony and non-pony alike, had ended with their own destruction. The same balefire that had ended the Equestria of old had instead served to protect those who had survived.

In the aftermath, the survivors looked to the future.

{\br}%
Not all of Serenity’s forces perished with their hive. A few remained free: Infiltrators, scouts, and soldiers, who had been carrying out their duties in the Wasteland. Now, without a home, without a queen, the remnants scattered.

A few, whether driven by duty or desperation, tried to strike back. Some sought assassination and sabotage as their methods. Others, mostly soldiers, formed small raiding groups, taking the food and love they needed by force from travelers and small settlements. Both caused many problems for ponies, but their impact was short lived. Every month, a few more of these holdouts fell. Before long, the last gasp of the Serenity hive fell silent.

Most, however, sought other paths for survival. Some set out into the Wasteland, putting the grave of their hive behind them as they sought a new future elsewhere. Others, faced with the threat of starvation in a hostile and barren land, turned to the ponies they had so recently been aligned against. At tiny settlements across the land, new travelers and scavengers appeared. Some of these mysterious strangers went as swiftly as they came. Others lingered, only to disappear in the middle of the night. Suspicion was high, but every now and then, a wanderer would find a place where they fit in.

And finally, there were those who followed the example of Calypter, offering their open surrender.

{\br}%
The surrendered changelings returned with the army, fearfully awaiting their fate.

By agreement of the major settlement leaders, and under the guidance of Queen Whisper, the former Serenity changelings were soon situated alongside the very ponies they had so recently been fighting. Homes were built and jobs established. Most were settled at Mareford, being the largest settlement, but a number were welcomed by Gemstone.

Soon came the difficult business of learning how to live together. Tensions were high and interactions awkward at first. Changelings were fearful of the beings they had been taught to see as monsters, while ponies were understandably suspicious of the creatures who had so recently deceived and attacked them. Sometimes, these tensions boiled over into action: a desperate or depressed changeling lashed out at a pony, or a pony sought vengeance for past wrongs. Despite these difficulties, there was still progress. As the weeks rolled by, under the Kind and Generous example of individuals like Seroon and Dazzle, those tensions started to fade away.

{\br}%
Sixty-one individuals had been pulled from the Serenity hive, returned to a world that some no longer recognized. Some were ponies out of time, having lost decades in the simulated world. Others were distraught at finding themselves torn from a world of peace and comfort and plunged into the Wasteland.

Scouts and messengers were sent out to seek friends and family. More than a few tearful reunions were made with loved ones who had thought them long dead. Some more awkward reunions were made with those who had moved on with their lives long ago. Still others found nothing but silence, the ponies they had known either dead or unable to be found. Every accommodation was made for those poor individuals. While nothing could quite compare to the false lives they had lived in the simulation, life in the heart of Mareford and other established settlements still offered some level of comfort. Whether through guilt or compassion, ponies pitched in to make the transition as painless as possible.

Unfortunately, Serenity hadn’t selected their captives for their morals, but for how much love they could extract. Some had been unscrupulous individuals even before their captivity, including several raiders who had been controllable by the pacifying influence of the simulation. They were given a fair chance, but without that influence, some returned to their previous way of life with abandon. Six of the rescued captives, including a particularly violent griffin by the name of Ricochet, killed a pair of soldiers and escaped into the wilderness. They made it less than two hours before being hunted down and slain by a joint team of Loyalists and Mareford Rangers, leaving them as contenders for the most short-lived raider gang in history.

{\br}%
Having cast off the troubles of its recent past, Mareford soon reestablished itself as the heart of the southern Wasteland, a place ponies—and all others—could look to with pride. Serenity’s defeat had been the effort of a great many, but all recognized that Mareford had formed the core of their efforts. Its soldiers had given the army the strength it needed, and their professionalism had giving it direction. Now, the settlement was the center of rebuilding and moving forward, with a renewed image of hope.

Many names were suggested for the new mayor of Mareford. Dusty Trails and Seroon were popular suggestions, though both declined. Instead, the office went to a less-known mare, Silverline. She had stepped forward in memory of her fallen husband, a victim of the town’s darker history, and dedicated herself to repairing the harm that had been done in Mareford’s name. No longer would Mareford be a place of greed, exercising its power over lesser settlements. Instead, it would be a helping sister, ready to shield the weak and aid the vulnerable. A shining beacon in the Wasteland, that even Celestia could be proud of.

Some worried it was too idealistic. Some thought it was impossible. But the majority agreed: impossible or not, it was worth striving for.

{\br}%
Trotsen found itself scarred by the fight against Serenity. They had lost almost half their motorwagons, nigh-irreplaceable relics of the old world and the symbol of their might. Worse, their former head rider was dead, and with her, her mighty Beast. They had been beaten and battered, and had little to show for it.

Despite these setbacks and the large horseshoes he had to fill, Axle asserted himself as a strong and clever head rider. The riders under his command were soon roaming more aggressively than ever, hunting down the last of the local raiders, and even claiming a few more of their Serenity-supplied motorwagons. He capitalized on the image of Trotsen motorwagons riding to the rescue, using it to secure beneficial trade deals, security arrangements with nearby settlements, and even the occasional and lucrative transport contract.

With the newfound goodwill and rapidly spreading relations, Axle started seeking out valuable ancient technology. His ambition lit a fire in the heart of the Trotsen ponies, who soon discovered a higher goal: the rebuilding of the ancient motorwagon factories. Slowly and steadily, industry would return to the Wasteland.

{\br}%
Gemstone grew rapidly in the years that followed. Word of the town and its ideals had spread far and wide, perhaps even more than Mareford. A small settlement, advocating the seemingly naive ideals of Kindness and Generosity in a world that appeared openly hostile to such, had stood side-by-side with the most powerful forces of the Wasteland. If Mareford had been the core of the army, many saw Gemstone as its heart. Their tale of idealism and heroism drew the imagination of many, and soon ponies were traveling to see this wondrous place.

These newcomers found a welcoming settlement that embraced harmony. A small slice of the Wasteland that called back to a better time, before the war and megaspells. A place where former enemies lived together in peace.

The small portion of the former Serenity changelings who settled in Gemstone were welcomed warmly, much to their surprise. While there was some early caution, they soon found that they were with ponies that genuinely cared. Ponies who were pleased just to see them happy. Ponies who offered genuine sympathy over the death of their queen and sisters. Ponies who saw beyond the exterior and the circumstances of the past. Ponies who treated them like equals.

Even the most steadfastly suspicious among the changelings soon found their concerns fading away. Friendships started to grow, and even love. Gemstone stood as an example of the strength of Harmony, with Dazzle and Calypter leading the way, together.

{\br}%
Rust was nothing but a ruin, torn apart in Serenity’s quest for material, but it would not be the end. Ponies would soon seek out those burnt ruins, drawn by the promise of steel and water.

A band of settlers set out from Mareford, with Singe at their head. Sympathetic ponies from all around had pitched in, contributing what they could to rebuild the lost settlement. Arclight came from Gemstone to help repair the pump. Ponies and changelings from Mareford helped with the construction. In just two weeks, Rust had returned. All cheered when the first water caravan rolled out, with Mareford soldiers marching alongside.

{\br}%
With the war against Serenity concluded and the army returned to Mareford, the Loyalists under Sergeant Hail Burst turned to seeking out their compatriots in the sky. When they finally re-established contact, they found the situation above the clouds had significantly changed. The latest series of skirmishes had been joined by more widespread civilian uprisings. The Council forces were on the back hoof, and while there was still much work to be done, the outcome was growing more certain by the day. With a final offer of thanks to the ponies of Mareford, and a promise to return, they returned to the fight.

When the reunified Enclave returned to the southern Wasteland, it was Commander Hail Burst who led the way. They were welcomed not as the pegasi who had turned their back on Equestria and cut off the sun, but as the pegasi who had so recently fought and died for their ground-bound brethren.

{\br}%
The remote settlements of Stinkpit and Hayseed, though untouched by the war itself, found the winds changing in their favor. Mareford’s occupation and dominion over these settlements came to an immediate and unexpected end, with the new mayor personally visiting to make amends. While the former injustices encouraged resentment, they found some sympathy with the mare who had suffered similarly at the hooves of the very same pony.

While they did not return immediately to the same close relationship they had before their occupation, the new leaders did establish a guarantee of Militia protection, and a trade agreement favorable to the small settlements. With more lucrative trade and the freedom to guide their own future, both settlements were soon on the way toward improvement.

{\br}%
Death had finally come for the Pale Ponies.

For centuries, they had trotted alongside death. Their ancestors roamed without life, but still protecting their land. The mightiest implement of death and destruction, a balefire megaspell like those that had slain millions, stood sentinel over their lands, an ominous threat to any who came near.

In an ironic twist of fate, it was this very threat that brought about their destruction. Serenity, drawn by the power of the megaspell, tore through their home, slaying living and dead alike. They left only ash and bones. Pale Sands fell silent.

{\br}%
The settlement of World’s End remained oblivious to the events to the north. Life remained unchanged for the small but diverse band of outcasts. The only contact came two weeks later, when a pair of timid and starving ponies fearfully approached the settlement, looking for shelter.

Ever true to their standards, the denizens of the settlement never pried into these newcomers’ pasts. World’s End was a place for second chances, not judgment, no matter who you used to be.

{\br}%
The years that followed saw many great changes. The greatest of these was the activation of a megaspell, more powerful than any seen before, but one that harkened back to the very first megaspell; a spell not of destruction, but of healing. All across Equestria, the poison and radiation from that ancient cataclysm were wiped away, the land cleansed.

Rainbow shockwaves opened the skies, returning Celestia’s sun and Luna’s moon. Sources of water that had been poisoned by radiation instead ran clean. Land that had been toxic was turned fertile. Even in the relative desert of southern Equestria, plants swiftly returned. Desert shrubs and flowers soon dotted the land, surrounding rapidly spreading farms. The Wasteland steadily receded, reclaimed by life.

Soon, new settlements started taking hold, spreading along fresh rivers and fertile valleys. Trade grew and flourished, even reaching north into the heart of Equestria, where the nascent New Canterlot Republic, a loose alliance of settlements, was taking root.

Across the land, ponies and other creatures looked forward to a future that was looking increasingly bright.

And in an isolated research facility in a patch of remote wilderness, many days’ walk west of Mareford, a new hive was steadily taking form...

{\br}%
Long ago, the room had been the quarters of the head of management for the Crystal Life Technologies Experimental Site Beta. Recent years had seen renovations, including knocking down an adjacent wall for more room, and the construction of a much larger bed.

Several mattresses were arranged for convenient sitting. On the largest sat Queen Whisper, a soft smile on her muzzle. “So,” she said, her voice gentle and softly resonant. “Now you know the full story. Everything that happened to bring us to where we are.”

She looked around at the young changelings gathered around her. There were eight of them, all in that awkward age between children and adults. Each wore a PipBuck, with expressions ranging from curiosity to uncertainty.

One of the young changelings, Silver, raised a hoof. “Um… so is that it?”

Whisper’s smile grew as she chuckled. “Was it not long enough already?”

A few of the others chuckled, and Silver flashed an awkward smile. “Well… I guess. But what happened next?”

\leavevmode\llap{“}Next, I came here, and raised all of you,” Whisper said. “I’m afraid that part doesn’t make quite as exciting of a story, though I have kept a simpler journal over the years. No more exciting adventures, yet.” Her eyes wandered across them, her smile taking on a sly turn as her eyes fell upon one young changeling, Desire. “Despite some of your best efforts to make raising you an adventure.”

There were several giggles, and one very proud smile.

Once the giggling faded, Desire took the opportunity to ask her own question. “What about auntie Sickle? Was she really that… extreme?”

Whisper gave another chuckle. “Oh, yes. She’s mellowed out a lot.” She paused. “Well, a little.” Another pause, and a small frown. “Well, she’s a little less violent at least. And she figured out how showers work, so that’s an improvement for everyone.”

More chuckles.

Sandy was leaning forward on her cushion. “Ooh! I should go up to her and say ‘Hi Strawberry Shake!’ Would she be mad?”

\leavevmode\llap{“}You know, it took me a month to convince her to let me share that with you,” Whisper said with a smirk. “I don’t know if she’d be angry with you, or amused that you had the guts.” Then she leaned down, stage-whispering. “But she might not give you any more ice cream.”

Sandy’s eyes went wide. “I’ll be good.” The others laughed.

Desire cut in, her tone light and teasy. “Soooo, did she ever get you to do that ‘changeling thing’? And what \textit{is} that, anyway?”

\leavevmode\llap{“}Not for lack of trying, and I’ll tell you when you’re older.” Whisper paused, then added, “Though she has apparently had \textit{some} luck with the former Serenity changelings. And please don’t ask her for details.”

Silver had raised her hoof again, and with a nod from Whisper, spoke up. “I was wondering about… uh, Serenity.”

\leavevmode\llap{“}Yes?” Whisper asked. “What about it?”

\leavevmode\llap{“}Well…” She struggled for a couple seconds, suddenly finding it difficult to ask the question she had in mind. “Did… did you really have to blow it up? There wasn’t any other way?”

Whisper gave a soft sigh, her ears hanging a little lower. Silver started trying to apologize and take back her question, but Whisper shook her head. “No, it’s a good question. A very good question. It’s a question I’ve asked myself ever since that day. And… I don’t know. It troubles me. If I’d done things differently, maybe we could have saved more. I’ve second-guessed all my choices, wondering if there’s something I could have done differently. As it was… whether the decisions that brought us there were good or bad, when I hit that trigger, I think it was the right call at the time. I just wish we’d found some other way.

There was a long moment of silence before another changeling, Hope, spoke up. “What about the other changelings from there? What happened to them? Do they, you know… have their own hive yet? Their own queen?”

Whisper shook her head, though she gave a small smile. “No. They’ve been living alongside ponies quite happily for several years. Forming a hive separate of that would mean leaving the homes and friends they’ve made. There’s been some talk about raising a new queen, but nothing yet. Some have said Calypter should take the role. She’s probably the closest they’ve got to a queen, at least for the Gemstone changelings.”

Hope was nodding, though she still looked a little troubled. “...But they don’t have a hive or queen like we do. Maybe… you could be their queen, too?”

Whisper reached out, gently petting Hope on the head. “When our hive has grown stable, and we finally step out into the light, I intend our doors to be open to all, whether ponies or changelings or anything else. If they wished to be a part of our hive, I will be glad to welcome them, but I suspect most will prefer to remain where they are. They have their own homes, and… for some, I think the bad memories might be too much.” She lowered her hoof again. “Still, even if I’m not their queen, I’ve tried to help out as much as possible.”

The young changelings fell into silence, all thinking. Whisper waited patiently until another, Midnight, spoke up. “So… miss Echo never figured out how to make other ponies be like her?”

\leavevmode\llap{“}More like the reason for her work vanished in an instant,” Whisper said. “I think she might be the only person to actually be upset when all the radiation vanished.”

Several surprised looks met that statement, but Whisper chuckled, waving a hoof. “I don’t mean to say she’s upset about the world becoming a better place. She \textit{is} happy about that, too. She was just disappointed to have put so much work on something, just to have the main reason for it suddenly go away.

\leavevmode\llap{“}Still, she learned a lot from her studies, and she’s put it to good use. She’s figured out how to replicate our shapeshifting through unicorn magic, though she’s still the only pony to ever cast it successfully. She has remarkable talent. It makes me wonder just how much of Twilight Sparkle is in there, after all.” She gave another chuckle. “She’s even helped me work out some more advanced changeling magic.”

Midnight grinned. “Yeah? Like teleportation?”

\leavevmode\llap{“}Like teleportation,” Whisper said with a nod. “Or at least a changeling spin on it.”

\leavevmode\llap{“}Do you think she’d teach us?”

Whisper laughed. “I think she’d be thrilled to! You’d probably make her day just asking her. And if you’re interested in learning more advanced magic, I think that would be an excellent idea.” She put on a more serious, motherly expression. “Just be warned, it’s very difficult, and extremely exhausting. It would take a lot of work and dedication. Echo makes it look far easier than it really is.”

While Midnight and Silver started chattering about the kinds of magic they were going to learn, another of their sisters spoke up. “I, uh… was wondering,” young Emerald said. “When momma Starlight gets back, you were going to go visit Gemstone, right?”

\leavevmode\llap{“}I am,” Whisper said with a nod.

Aurora cut in. “That’s where uncle Dusty is staying, right?”

Whisper nodded again. “It is.”

Emerald hesitated, then asked, “Would it be okay if… if we came with you?” She swallowed, putting on a nervous smile. “I think I’d like to meet Dazzle and Calypter.”

Queen Whisper looked down to her, so small and fragile. A soft smile spread across her muzzle, and she leaned down. “I think that would be wonderful. I’m sure they’d love to meet you, too.”

The news was met with many bright smiles and excited murmuring. A trip! Seeing the world! Meeting new ponies and changelings and griffins and zebras!

Only one of the young changelings sat aside, with a quiet, troubled expression. Whisper scooted closer, dipping her head. “Is something wrong, Harmony?”

Harmony looked up, looking into her eyes as if she might find the answer to some question there. Eventually, she asked, “Why didn’t you want to be our queen?”

Whisper blinked. There was a second of silence before her smile returned. “I was an Infiltrator my whole life. I still am, I suppose. It’s what I love, and it was the best way I could serve my hive. I thought I’d do best to remain just an Infiltrator, and raise a new queen to lead us.” She reached up, placing a hoof gently on Harmony’s shoulder. “But I think the real reason was because I was scared.”

Harmony’s ears perked up, her head tilting.

\leavevmode\llap{“}I was,” Whisper said, nodding. “I was scared of taking on that responsibility. I was afraid I would be overstepping my bounds. There is so much reverence and significance to the title, and I was just an Infiltrator.” Her smile grew. “But I realized that I had a duty to my hive, to you and your unhatched sisters. I couldn’t shirk that responsibility, and I couldn’t pawn it off on someone else. I needed to shoulder it myself… and I think it’s become the happiest decision I’ve ever had to make.”

Harmony blinked up at her, eyes starting to water. Then the young changeling moved forward, wrapping her forelegs around Whisper’s shoulders and burying her tiny muzzle against Whisper’s neck. “I’m glad you’re our queen.”

In moments, there were seven more young changelings joining in. Queen Whisper did her best to hug back, nuzzling gently at the back of Harmony’s head.

\leavevmode\llap{“}So am I.”